### 2018-08-06 Tex/Old text/paper_old_rev0.tex
first commit

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
%Alessandro input: makecell package to permite line break inside tables
\usepackage{makecell}
\usepackage{cite}
\graphicspath{ {./images/} }

\title{Building a framework to perform automated verification of solar photovoltaic off-grid systems}
\author{Alessandro Trindade \thanks{Federal University of Amazonas, Av. Rodrigo Octavio 3000, Coroado, Faculdade de Tecnologia, Campus Universitário, Manaus-AM, Brazil, alessandrotrindade@ufam.edu.br} \and Lucas Cordeiro \thanks{Department of Computer Science, University of Oxford, UK}}
\date{}

\begin{document}

\maketitle

\begin{abstract}
The deployment of renewable energy in off-grid systems is growing in both developed and developing countries. With declining costs and increasing performance, off-grid renewable energy systems could become an important growth market for the future deployment of renewables according to International Renewable Energy Agency. The impact of off-grid renewable energy systems will not only be measured in terms of their usage or reduced costs for electricity consumption in rural areas, but also in the context of their effect on the lives of more than 1.3 billion people who today do not have access to electricity. Electrification of rural areas can improve the standard of education, health conditions, and living of this population. In addition, depending on the geography of the country, using renewable energy sources in off-grid mode is a feasible solution if compared to grid extension. Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to analyze, and evaluate rural electrification projects. This paper aims to build the framework to apply automated verification methods to mathematical models of a complete system of rural electrification with solar photovoltaic energy to validate its design from a formal verification perspective.

Keywords: Automated verification, model checking, energy systems, solar photovoltaic systems, off-grid systems. 
\end{abstract}

\section{Introduction}
According to \cite{Coelho} there are presently 1.3 billion people with no access to electricity worldwide. The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.

Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). Only a niche market a few years ago, PV are now becoming a mainstream electricity provider, changing the way the world is powered. Based in data from \cite{EPIA}, there was an increase of approximately 30\% from 2013 to 2014 in terms of new installations of PV. The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. The renewable energy leads to an advance all over the world by protecting the environment: it is clean (low greenhouse gases emissions), operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}. Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation. The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.

In order to validate or even simulate a potential PV solution, there are a myriad of tools. However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.

According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth. In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials. SPV systems can be classified into grid-connected and stand-alone systems. At this proposal, only off-grid or stand-alone systems will be considered. The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.

The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy. Apart from PV modules; the PV systems consist of battery bank, controller, and inverter, plus the load. Moreover, the optimum sizing of these devices is important for reliable operation. Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}.

In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization). Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.

Manufacturers and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.

Changing the subject to the design of complex systems, more time is spent on verification than on construction, as shown in \cite{Baier}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs, and more generally computer systems, may be viewed as mathematical objects with behavior that is, in principle, well determined. This makes it possible to specify programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification, as defined by \cite{Trindade}.

This area of research is referred as formal methods as defined in \cite{Clarkeetal}. Their aim is to establish system correctness with mathematical rigor.

In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of bugs in order to ensure the correctness of the system.

Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}. Algorithms can verify the system model through systematically explore all their states.

Bringing this idea to the field of solar photovoltaic systems, instead of finding a bug or a software inconsistence, the present work aim to verify a complete PV system project, informing in which condition the project do not meet user requirements or will fail. Among the non-deterministic variables evaluated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}. That is the main contribution of this paper.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{flowchart_verification.png}
\centering
\caption{Flowchart of the proposed computer verification of PV systems}
\label{fig:flowchartgeneral}
\end{figure}

The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a complete PV off-grid system, using the satisfiability modulo theories (SMT)-based verification method.

To the best of our knowledge, this is the first work to use an SMT-based verification tool to solve this kind of problem.

The implementation of the ideas will be done with the efficient SMT-based bounded model checker (ESBMC) tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, which permits to describe the problem as a C/C++ language code.

The remainder of this paper is organized as follows: Sect. 2 gives a background of solar PV systems. Section 3 describes the design and validation of a solar PV system. Section 4 describes the formal mathematical modeling of a generic PV system. Section 5 presents the automated verification theory, including details of the ESBMC process. The methodology is presented at Section 6. Section 7 discusses the related work. Section 8 presents the conclusion and describes future work. At the end of the paper, there is a list of all nomenclatures used at the text.

\section{Solar Photovoltaic System }
According to \cite{Roy}, a PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) type or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time (in particular cases, in both times). The most basic PV system can give supply only in daytime.  For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.

PV systems are broadly classified into three distinct types, as described by \cite{Mohanty}:

\begin{itemize}
\item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants; 
\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
\end{itemize}

Specifically concerning isolated communities, depending on the type of load, cost, resources availability, and requirements of the load, standalone systems can be split into several categories, which are described in this section. As the goal of this Thesis is just the solutions aimed to isolated/ off-grid application, therefore it is not considered the on-grid or hybrid configurations.

There is a resource, called maximum power point tracking (MPPT), which is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. That resource is found at modern PV systems and is strongly indicated due to its advantages.

\subsection{Unregulated standalone PV system with DC load }
Usually this type of system is for low power applications, as defined by \cite{Roy}. The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:unregSPV}. At night hours, the system will not provide any supply because of the absence of the battery.

\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{unregulatedSPV.png}
\centering
\caption{Unregulated standalone SPV system with DC load (Source: \cite{Roy})}
\label{fig:unregSPV}
\end{figure}

\subsection{Regulated standalone PV system with DC load}
It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:regSPV1}. Usually system with MPPT should have battery; otherwise, extra power will be waste.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV1.png}
\centering
\caption{Regulated standalone SPV system with DC load (Source: \cite{Roy})}
\label{fig:regSPV1}
\end{figure}

\subsection{Regulated standalone system with battery and DC load}
Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV2.png}
\centering
\caption{Regulated standalone SPV system with battery DC load (Source: \cite{Roy})}
\label{fig:regSPV2}
\end{figure}

According to \cite{Pinho}, PV systems that are used to feed loads with low variation on the consumption can be sized to operate without the controller. That is called of self-regulated standalone PV system with battery. However, the voltage from the PV panel must be compatible with the batteries voltage. Normally, the bank of batteries are oversized related to the PV panel and to the load. The drawback is the operation of the batteries, normally overloaded or with excessive discharges (that can damage the batteries).

\subsection{Regulated standalone system with battery, AC load}
This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}. This solution has an increase of cost because has more equipments. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units. That configuration is the focus of the present thesis since it is the most common nowadays all over the world, when off-grid or isolated regions is the target.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV3.png}
\centering
\caption{Regulated standalone system with battery, AC load (Source: \cite{Roy})}
\label{fig:regSPV3}
\end{figure}

\section{Design and Validation of a Solar photovoltaic system}
The design and validation of a SPV system can be done by hand or with the aid of a software tool.

In order to address different aspects of project system and systems design, there is a myriad of public domain and commercial software available for the SPV market. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization). Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.

Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
In this study, the most popular tools are presented:

\begin{itemize}
\item PVWatts 
\item SAM
\item Homer
\item RETScreen
\item Hybrid2
\end{itemize}

\subsection{PVWatts Calculator}
According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs. According to \cite{NRELDobos}, to use the calculator, it is necessary to provide information about the system's location, basic design parameters, and system economics. PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity monetary value. This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules. The production estimates that PVWatts computation do not account for many factors that are important in the design of a photovoltaic system, therefore it is necessary support of an energy expert. The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year. To represent the system's physical characteristics, PVWatts requires values for six inputs: System DC size; Module type; Array type; System losses; Array tilt angle; Array azimuth angle.

\subsection{SAM}
SAM or System Advisor Model is a software from the U.S. Department of Energy and National Renewable Energy Laboratory. According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications, and (also) to provide information for readers who do not plan to use the model, but want to learn about its capabilities. SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: Project managers and engineers; Financial and policy analysts; Technology developers; and Researchers. SAM makes performance predictions and cost of energy estimates for grid-connected power projects based on installation and operating costs and system design parameters that you specify as inputs to the model. Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement. SAM is an electric power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet electric load. It does not model thermal energy systems that meet a thermal process load. As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.

\subsection{HOMER}
As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro. HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources. HOMER Legacy is the original HOMER software version created at the National Renewable Energy Laboratory (NREL). HOMER Legacy is a free computer model that simplifies the task of evaluating design options for both off-grid and grid-connected power systems for remote, stand-alone, and distributed generation applications. HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options. Since 2016 Homer Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available. At the short-time only the commercial version will remain.

The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases. HOMER Pro put together three tools in one product: optimization, simulation, and sensitivity analysis. HOMER Pro provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use. It is adaptable to a wide variety of projects. For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project. For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations. Chronological simulation is essential for modeling variable resources, such as solar and wind power and for combined heat and power applications, where the thermal load is variable. HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.

\subsection{RETScreen}
As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.

RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options. The software can be used to evaluate benefits from both clean energy production from power generation projects and savings through energy efficiency projects, accounting for project costs, greenhouse gas emission reductions, and financial risk. The software is freely distributed (but with restrictions to save work or print), and had three different versions:

\begin{itemize}
\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform. However, this version works is only Windows-based. This version has a complete paid version, in an annual subscription way.
\end{itemize}

As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis. It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF). RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.

\subsection{Hybrid2}
The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems. Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system. Variations in wind speed and in load within each time step are factored into the performance predictions. The code does not consider short-term system fluctuations caused by system dynamics or component transients. This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, what is a limitation.

Table \ref{table:softwares} summarizes the tools described in this paper.  Where just Hybrid2 do not have technical support; only HOMER, RETScreen and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER and RETScreen are complete, including economical analysis or even optimization-sensitive analysis. However, only paid version of those softwares have all the features, and they run only at Windows-based operational systems.

\begin{table}[!t]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Comparative coverage of reference softwares}
\label{table:softwares}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{c | c | c | c | c | c}
\hline
\hline
Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen } & \rotatebox{90}{Hybrid2}\\
\hline
Support & X & X & X & X &  \\
Off-grid systems &   &   & X & X & X\\
Hybrid systems &  &  & X & X & X\\
Photovoltaics & X & X & X & X & X\\
Batteries &  &  & X & X & X\\
Main technical (T) or economical (E) & T & T & E & E & T \\
Optimization &  &  & X & X &  \\
Sensitive analysis &  &  & X & X & \\
\hline
\hline
\end{tabular}
\end{table}

\subsection{Paper Proposal x Reference Tools}
Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER and RETScreen remain for comparative. All tools need some parameters inherently from manufacturer's catalog, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. After that, the potential solution is analyzed in another tool to validate or even optimize the solution. Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution.

\section{Component models for stand-alone PV system }
The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load. The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}. The modular structure facilitates the modeling of the other system structures and replacing of elements as, for instance, a DC load instead of an AC load.

\begin{figure}[h]
\includegraphics[width=0.95\textwidth]{blockdiagramPVS}
\centering
\caption{Block diagram for the stand-alone PV system (Source: \cite{Hansen})}
\label{fig:blockdiagram}
\end{figure}

In the literature, there are several mathematical models available for each component of stand-alone PV systems. In this section, the mathematical model for each component of PV system is presented.

\subsection{PV generator (cell, module, array) }
A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. In the present modeling, the focus is only on cell/module/array.

The basic element of a PV System is the PV cell, also called a Solar Cell. A PV / Solar Cell is a semiconductor device that can convert solar energy into DC electricity. The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun). When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}. If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).

To increase their utility, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module). For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series. In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}. The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.

\begin{figure}[h]
\includegraphics[width=0.95\textwidth]{celmodarray}
\centering
\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
\label{fig:celmodarray}
\end{figure}

The PV modules are generally rated under standard test conditions (STC), which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5. The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution. However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.

These uncertainties lead to either over- or underestimation of energy yield from PV modules. An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}. The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}. Modeling PV modules is one of the major components responsible for proper functioning of PV systems. However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage. Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.

Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.

The performance of photovoltaic systems (solar cell/panels), that is, the output current/voltage curve ($I-V$ curve), is usually studied using an equivalent circuit model. This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}. Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}.

\begin{figure}[h]
\includegraphics[width=0.95\textwidth]{equivckt}
\centering
\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
\label{fig:equivckt}
\end{figure}

The 1-diode model, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in Equation \ref{eq:1diodemodel}.

\begin{equation}
\label{eq:1diodemodel}
I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right] 
\end{equation}

Where:
\begin{itemize}
\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed;
	\begin{itemize}
	\item $ N=1 $ in a single cell configuration. 	
	\end{itemize}	  
\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; 
	\begin{itemize}
	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
	\end{itemize}
\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
	\begin{itemize}
	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
	\end{itemize}	 
\end{itemize}

This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.

The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}.

\begin{equation}
\label{eq:1d1rmodel}
I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
\end{equation}

Where $R_{s}$ is the series resistor.

At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.

The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}.

\begin{equation}
\label{eq:1d2rmodel}
I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
\end{equation}

Where $R_{sh}$ is the shunt resistor.

At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).

And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}.

\begin{equation}
\label{eq:2d2rmodel}
I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
\end{equation}

This model has six unknown parameters with two exponential terms. 
Briefly, both single and double diode models require the knowledge of all unknown parameters, which is usually not provided by manufacturers. Nevertheless, the current-voltage equation is a transcendental expression \cite{Jakhrani}.

However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel.

For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths. The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}. However, due to implicit nature and nonlinearity of PV cell or module characteristics, it is hard to find out the analytical solution of all unknown parameters, as described by \cite{Hasan}. Thus, numerical methods such as Newton-Raphson method or Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}. This happens because numerical methods give approximate solution of the nonlinear problems without searching for exact solutions. However, numerical methods are time consuming and need long term time series data, which is not available in developing countries. \cite{Jakhrani} did a mixed methodology using analytical and numerical steps together.  \cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation (essays). And \cite{Tian} did a mix of analytical and experimental methodology to get the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use experimental technique.

Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on the simplified model of 1-diode, that was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested. In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation.

\subsection{Proposed PV Panel Model}
With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1d1rmodel}.

A single-diode without series and shunt resistances is considered. Equation 1 is used to write down expressions for currents and voltages at each key point shown in Fig. \ref{fig:ivcurve}.

\begin{figure}[h]
\includegraphics[width=0.90\textwidth]{ivcurve}
\centering
\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
\label{fig:ivcurve}
\end{figure}

Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.

\begin{equation}
\label{eq:Isc}
I_{sc}=I_{ph}\vert_{V=0}
\end{equation}

\begin{equation}
\label{eq:Voc}
V_{oc}=\dfrac{aNk_{B}T}{q}ln\left( 1+\dfrac{I_{sc}}{I_{0}} \right) 
\end{equation}

\begin{equation}
\label{eq:exp}
exp\left( \dfrac{qV_{oc}}{aNk_{B}T} \right) = \left(1+\dfrac{qV_{m}}{aNk_{B}T} \right) exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) 
\end{equation}

\begin{equation}
\label{eq:Im}
I_{m} =I_{ph}-I_{0}\left[ exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) -1 \right] 
\end{equation}

Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way. A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}. These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig. \ref{fig:ivcurve}, where the transition is a compromise between both behaviors. It is interesting to observe that the maximum power point corresponds to a trade-off condition, where the current is still high enough before it starts decreasing with increasing the output voltage (Fig. \ref{fig:ivcurve}).

Based on this, the tangent of the I-V curve can be used to evaluate the transition between current- to voltage-source controlled regions; this operation yields Equation \ref{eq:didv}.

\begin{equation}
\label{eq:didv}
\dfrac{dI}{dV}=-\dfrac{qI_{0}}{aNk_{B}T}exp \left( \dfrac{qV}{aNk_{B}T}  \right) 
\end{equation}

The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell. Therefore, the Equation \ref{eq:Vmderiv} is generated.

\begin{equation}
\label{eq:Vmderiv}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
\end{equation}

It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point. The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change on $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}. Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation 10 can be calculated as shown in Equation \ref{eq:dIdV_Vm}.

\begin{equation}
\label{eq:dIdV_Vm}
\dfrac{dI}{dV}\vert_{V_{m}} \cong -\dfrac{0-I_{sc}}{V_{oc}-0}=\dfrac{I_{sc}}{V_{oc}}
\end{equation}

Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, the voltage and the current at the maximum power point and consequently the maximum output power, are expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm} ($ P_{m}=V_{m}I_{m} $). These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.

\begin{equation}
\label{eq:Vmfinal}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) 
\end{equation}

\begin{equation}
\label{eq:Imfinal}
I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  
\end{equation}

\begin{equation}
\label{eq:Pm}
P_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right] 
\end{equation}

However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers. Therefore, Equation \ref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.

\begin{equation}
\label{eq:Iph}
I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right] 
\end{equation}

Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $.

In Equation \ref{eq:Iph}, $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at (STC or standard test conditions) reference conditions (provided by PV manufacturers). $ I_{ph,ref} $ can also be approximated to the reference short-circuit current that is provided by PV manufacturers ($ I_{sc,ref} $) as shown by \cite{Jakhrani}.

The cell temperature ($ T $) can be obtained from \cite{Ross} and is shown in Equation \ref{eq:Tcell}.

\begin{equation}
\label{eq:Tcell}
T = T_{air} + \dfrac{NOCT-20}{800}G
\end{equation}

Where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.

Furthermore, \cite{Villalva} have proposed a relationship, which allows the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature. In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).

\begin{equation}
\label{eq:I0}
I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1}
\end{equation}

Where $ V_{oc,ref} $ is the reference open-circuit voltage, and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).

The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. Using the maximum power point current equation (Equation \ref{eq:Pm}) and the saturation current in the reference temperature given by Equation \ref{eq:I0}, the diode quality coefficient is determined by Equation \ref{eq:a}.

\begin{equation}
\label{eq:a}
a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) }
\end{equation}

Where $ V_{mref} $, $ V_{oc,ref} $, $ I_{m,ref} $, and $ I_{sc,ref} $ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers.

The model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.

If the PV cells are in parallel, then there is a parallel array. Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.

\begin{equation}
\label{eq:Iarray}
I_{array} = (N_{cells in parallel})(I_{one cell})
\end{equation}

Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.

In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.

\begin{equation}
\label{eq:Varray}
V_{array} = (N_{cells in series})(V_{one panel})
\end{equation}

Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.

Besides the model verification, there is the prior stage of project sizing check, which is simple, based on manufacturer's data and information from the sizing and the site.

First is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$). That is done by Equation \ref{eq:Ecorrected}, according \cite{Pinho}. Where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.

\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }
\end{equation}

The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by Equation \ref{eq:NTPmin}, and the check is done with the Equation \ref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from Equation \ref{eq:NTPmin}.

\begin{equation}
\label{eq:NTPmin}
N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}
\end{equation}

\begin{equation}
\label{eq:NTP}
N_{TP} \geq N_{TPmin}
\end{equation}

Particularly, the total number of panels is series ($ N_{PSmin} $) and parallel ($ N_{PPmin} $) are given by the Equations \ref{eq:NPSmin} and \ref{eq:NPPmin}, respectively. With the check did by Equations \ref{eq:NPS} and \ref{eq:NPP}. $ V_{system} $ is the DC voltage of the bus, and is a design decision (normally 12, 24 or 48 V).

\begin{equation}
\label{eq:NPSmin}
N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}
\end{equation}

\begin{equation}
\label{eq:NPPmin}
N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}
\end{equation}

\begin{equation}
\label{eq:NPS}
N_{PS} \geq N_{PSmin}
\end{equation}

\begin{equation}
\label{eq:NPP}
N_{PP} \geq N_{PPmin}
\end{equation}

\subsection{The Battery Storage Model }
Because of the fluctuating nature of the output delivered by the PV arrays, batteries are necessary in a PV system. Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery. During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.

Several models have been presented in the literature. However, regardless of the model, normally the following parameters are required:

\begin{itemize}
\item Nominal capacity ($ q_{m} $), is the number of Ampère-hours ($ Ah $) that can maximally be extracted from the battery, under predetermined discharge conditions.
\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. Obviously $ 0<SOC<1 $. If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
\end{itemize}

The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components. The battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP). LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.

In general, the battery models view the battery as a voltage source $ E $ in series with an internal resistance $ R_{0} $, as shown in Fig. \ref{fig:batteryckt}.

\begin{figure}[h]
\includegraphics[width=0.7\textwidth]{batteryckt}
\centering
\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
\label{fig:batteryckt}
\end{figure}

The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.

Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.

The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.

The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data. However, it uses some data extracted from tested batteries in laboratory. Therefore is not suitable to this study.

Most of the created models were used to simulate and optimize PV storage system based on lead-acid batteries. That kind of battery is the most common used batteries in PV application, owing to their relative low cost and wide availability \cite{Copetti}.

Here, the model adopted is the based on \cite{Copetti}, who uses manufacturer's data and allows finding relations among voltage, current, state of charge and temperature.

The discharge voltage equation is shown in Equation \ref{eq:bat_Vd}. The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.

\begin{equation}
\label{eq:bat_Vd}
V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T)
\end{equation}

Where $ C_{10} $ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $ \Delta T $ is temperature variation ($ \Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $, $ SOC $ indicates how much electric charge is stored in the cell at given time, defined by Equation \ref{eq:SOCbat}.

\begin{equation}
\label{eq:SOCbat}
SOC = \left( 1 - \dfrac{Q}{C} \right) 
\end{equation}

Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.

The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the farction of discharge, i.e., $ DOC=1-SOC $.

The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}. This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).

\begin{equation}
\label{eq:CC10}
\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 \Delta T)
\end{equation}

Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.

For the charging process, however, the parameters are presented in Equation \ref{eq:Vcbat}.

\begin{equation}
\label{eq:Vcbat}
V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T)
\end{equation}

SOC can be calculated easily at any point during the discharge period; however, during recharge it is much more difficult \cite{Copetti}.

Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell. The efficiency drops to zero at full charge and the function that represents the charge efficiency ($ \eta_{c} $) variation with state of charge and current rate is given in Equation \ref{eq:efficcharge}.

\begin{equation}
\label{eq:efficcharge}
\eta_{c} = 1 - exp \left[ \dfrac{20.73}{\dfrac{I}{I_{10}}+0.55} (SOC-1) \right] 
\end{equation}

\cite{Copetti} show that, during overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (Equation \ref{eq:Vec}). It was created a function for the gassing voltage as well, as shown in Equation \ref{eq:Vg}. In addition, the overcharge phenomenon can be represented by Equation \ref{eq:Voverc}.

\begin{equation}
\label{eq:Vec}
V_{ec} = \left[ 2.45 + 2.011 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
\end{equation}

\begin{equation}
\label{eq:Vg}
V_{g} = \left[ 2.24 + 1.97 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
\end{equation}

\begin{equation}
\label{eq:Voverc}
V_{c} = V_{g} + (V_{ec} - V_{g}) \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
\end{equation}

Where $ Ah_{restored} $ represents the Ampère-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.

The function assumes that 95\% of the capacity was already restored at the start of overcharge.

The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by Equation \ref{eq:tau}.

\begin{equation}
\label{eq:tau}
\tau = \dfrac{17.3}{1+852 \left( \dfrac{I}{C_{10}} \right) ^{1.67} }
\end{equation}

Therefore, to model the voltage ($ V_{c} $) evolution of the battery, equation \ref{eq:Vcbat} can be used up the start of gassing ($ V_{c} \leq V_{g} $). And during overcharging ($ V_{c} > V_{g} $), Equation \ref{eq:Voverc} can be used until a constant final voltage ($ V_{ec} $) is reached.

The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.

\begin{equation}
\label{eq:stor}
Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
\end{equation}

Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.

As an example of this formula application, as shown by \cite{Abdulateef}, considering that an off-grid PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.

Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$. Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$). If a single battery of 12 V and 350 Ah is considered, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).

At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature. The equations are used to update the $SOC$ of the batteries, and have the number of hours ($ Num_{h} $) as a variable. There is a factor (1.15) which is present at the charging equation, and is necessary to express that during the charging process is usual to reach 115\% of the battery capacity

\begin{equation}
\label{eq:charge}
SOC_{charge} = SOC_{previous} + \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
\end{equation}

\begin{equation}
\label{eq:discharge}
SOC_{discharge} = SOC_{previous} - \dfrac{100*I_{drained}*Num_{h}}{capacity}
\end{equation}

Besides the model verification, there is also the prior stage of project sizing check, as did to the solar panel. First is necessary to define the total capacity of the battery bank, as shown by Equation \ref{eq:Cbank}.

\begin{equation}
\label{eq:Cbank}
C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}
\end{equation}

The variable $ autonomy $ is a design definition and normally has a value ranging from 6 to 48h. The other variables were discussed previously.

Following, is done the total (minimum) number of batteries, as show by Equation \ref{eq:Nbtotal}. Moreover, the Equation \ref{eq:batcheck} perform the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that were established to the project.

\begin{equation}
\label{eq:Nbtotal}
N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}
\end{equation}

\begin{equation}
\label{eq:batcheck}
\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total
\end{equation}

\subsection{Controller Model}
Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}. However, in this study, in order to simplify, the term used is controller.

The controller is a set of items (DC-DC converter, a MPPT and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. According to \cite{Pinho}, controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.

As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components. The use of battery as a storage form implies thus the presence of a charge controller.

In general, there are two main operating modes for the controller: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.

In \cite{Mellit} was established that the controller allows the management of energy between the load and the battery. The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $). The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).

According \cite{Hansen}, to protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and when the current required by the load is less than the current delivered by the PV arrays. PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $. This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}.

\begin{figure}[h]
\includegraphics[width=0.7\textwidth]{controllerover}
\centering
\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
\label{fig:controllerover}
\end{figure}

To protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold i and when the current required by the load is larger than the current delivered by the PV arrays \cite{Hansen}. The load is reconnected to the system, when the terminal voltage is above a certain value i, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}.

\begin{figure}[h]
\includegraphics[width=0.7\textwidth]{controllerdisc}
\centering
\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
\label{fig:controllerdisc}
\end{figure}

According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.).

The steps in the modeling of the controller process are summarized in Table \ref{table:controller}.

\begin{table}[!t]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Summary of the controller process (Source: \cite{Hansen})}
\label{table:controller}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{c | c | c }
\hline
\hline
Step  & Constraint & Command\\
\hline
\hline
(1) & \makecell{If $V > V_{max \textunderscore off}$ and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array from the system}\\
\hline
(2) & \makecell{If command (1) is done and $V < V_{max \textunderscore on}$} & \makecell{Reconnect PV array to the system}\\
\hline
(3) & \makecell{If $V < V_{min \textunderscore off}$ and $I_{load} > I_{pv}$} & \makecell{Disconnect the load from the system}\\
\hline
(4) & \makecell{If command (3) is done and $V > V_{min \textunderscore on}$} & \makecell{Reconnect the load to the system}\\
\hline
\hline
\end{tabular}
\end{table}

Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage.

As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. The output power ($ P_{out} $) of DC-DC converter is given by Equation \ref{eq:poutcont}.

\begin{equation}
\label{eq:poutcont}
P_{in = P_{out}}
\end{equation}

Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Equation \ref{eq:poutcont} is possible to reach Equation \ref{eq:potcont}.

\begin{equation}
\label{eq:potcont}
V_{in} I_{in} \eta_{c} = V_{out} I_{out}
\end{equation}

Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the current output of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $-I_{out}$ is the output current from the converter, when all the other values are known.

The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}).

A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}. In addition, there is the Cuk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.

For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.

\begin{equation}
\label{eq:voutvin}
\dfrac{V_{out}}{V_{in}} = \dfrac{D}{D-1}
\end{equation}

Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.

The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.

Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.

As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.

One more time, some steps must be done to check the sizing project of the controller, prior the verification phase. Initially the controller must meet the voltage requirement of the PV system, as shown by Equation \ref{eq:vcvsystem}.

\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}
\end{equation}

Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as shown by Equation \ref{eq:iscamb}.

\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right] 
\end{equation}

The controller must meet the maximum current from the PV array (Equations \ref{eq:icmin} and \ref{eq:icicmin}).

\begin{equation}
\label{eq:icmin}
I_{c,min} = I_{sc,amb} \times N_{PP}
\end{equation}

\begin{equation}
\label{eq:icicmin}
I_{c} \geq I_{c,min}
\end{equation}

The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}. In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.

\begin{equation}
\label{eq:numberofcmin}
number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} =  \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
\end{equation}

\begin{equation}
\label{eq:numberofc}
N_{controller} \geq number_{controllers}
\end{equation}

\subsection{The inverter model}
As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage (127 V or 220 V, for example), and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency \cite{Hansen}.

The inverter is characterized by a power dependent efficiency $ \eta_{i} $ given by \cite{Hansen} as shown by Equation \ref{eq:efficinv}.

\begin{equation}
\label{eq:efficinv}
\eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}}
\end{equation}

Where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be found from the inverter's data-sheet.

Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).

The sizing project check of the inverter is done through three Equations. Equation \ref{eq:vindc} ensure that the input voltage of the controller meet the voltage of the system. Equation \ref{eq:voutac} ensures that the output voltage of the controller meet the AC voltage of the load. Moreover, Equation \ref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.

\begin{equation}
\label{eq:vindc} 
V_{in}DC = V_{system}
\end{equation}

\begin{equation}
\label{eq:voutac} 
V_{out}AC = V_{AC}
\end{equation}

\begin{equation}
\label{eq:invcheck} 
\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right] 
\end{equation}

\section{Automated verification }
It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.

If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, resulting in a process known as formal verification. Verification may form part of a validation process, but in general, validation cannot be formalized because it relates a system design to intent.

Simulation may also be used for validation, but it is more problematic for verification. In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.

Testing can also be used for validation, but for the same reasons, it too is problematic for verification.

According \cite{Clarke2008}, verification procedure is an intelligent exhaustive search of the state space of the design. In addition, according to \cite{Forejt2011}, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system. One successful method in this domain is model checking.

Model checking is an automatic verification technique, as defined by \cite{Clarke2008}. Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.

The process of model checking can be divided in three components: modeling, specification, and verification method.

\begin{itemize}
\item In modeling, a model (normally mathematical) of the system is created; 
\item In specification, normally a list of properties to be satisfied by the system is stablished, i.e., the requirements, as reliability to performance for example. \item Normally is expressed in temporal logic form ($CTL$); 
\item The model checking is the verification method itself. 
\end{itemize}

The model checking algorithm can be described as:

\begin{itemize}
\item Given the model $ 'M' $ and a $CTL$ formula $ \phi $ as input;  
\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
\item It returns $YES$ if $ \phi $ is $TRUE$, or returns $NO$ if $ \phi $ is $FALSE$.

\end{itemize}
Specifically at the $FALSE$ situation, the algorithm returns a counterexample that is useful as diagnostic of the system, in order to discover in which situation the model is violated. \cite{Clarke2008} consider that the most important advantage of the use of model checking.

Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving). However, there is a main disadvantage of model checking: the state explosion problem.

The model checking problem can be defined as shown in \cite{Clarke2008}:

\begin{itemize}
\item Let $M$ be a Kripke structure (i.e., state transition graph);
\item $f$ be the specification in temporal logic (a formula);
\item Find all states $s$ of $M$ such that $M , s \models f$
\end{itemize}

Fig. \ref{fig:modelcheckstruc} shows the structure of a typical model checking system. A preprocessor extracts a state transition graph from a system (program or circuit).

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{modelcheckstruc}
\centering
\caption{Model Checker structure (Source: \cite{Clarke2008})}
\label{fig:modelcheckstruc}
\end{figure}

Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study.

The Fig. \ref{fig:systemverif} shows the process to convert a real system to a model in order to be verified by a model checking.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{systemverif}
\centering
\caption{From real system verification to model checking (adapted from \cite{Clarke2008})}
\label{fig:systemverif}
\end{figure}

In order to solve the problem of state explosion, many different techniques were developed at the last decades. One of the promising is the Bounded Model Checking (BMC).

BMC is a method that checks the model up to a given path in the path length. BMC algorithms traverses a finite state machine for a fixed number of steps, , and checks whether violation occurs with this bound. It uses fast SAT solvers, where SAT means satisfiability. SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression. SAT solvers are used in BMC, such that if there are some Boolean function, the solver would search the model for conditions (value of variables) that would make the formula $TRUE$. If SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.

CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++, as can be seen in \cite{Kroening}.

ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.  
The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.

\subsection{ESBMC }
According \cite{GadelhaSBMF}, ESBMC is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs. the efficient SMT based model checker, is a software verification tool for C and C++ code bases. Fig. \ref{fig:esbmcarch} shows the tool architecture.

\begin{figure}[h]
\includegraphics[width=0.9\textwidth]{ESBMCarch2}
\centering
\caption{ESBMC architecture (adapted from \cite{GadelhaSBMF})}
\label{fig:esbmcarch}
\end{figure}

As shown by \cite{GadelhaSBMF}, ESBMC has two alternative front-ends to parse the input program and generate an Abstract Syntax Tree (AST). One legacy CBMC-based front-end that supports both C and C++ and a new clang-based front-end that currently only supports C. The data types and bit vectors are created in the front-end when parsing the code.

Regardless of the chosen front-end, the output is an AST (tree representation of the abstract syntactic structure of source code written in a programming language) that will be used by the GOTO converter to generate a GOTO program, which has simplified control flow and is suitable for bounded unwinding. The next step is the symbolic execution, when the GOTO program is executed (unrolling loops up to the bound $ k $) and converted to Static Single Assignments (SSA) form. SSA form enables the simplification of algorithms and reduction of computational complexity, where each variable is a target of exactly one assignment statement in the program text.

During the symbolic execution, ESBMC aggressively tries to simplify the program \cite{Ramalho}; it propagates all constants and solves any assertions that can be statically determined. This is an important step for the verification, since ESBMC can fully verify programs without calling a solver, if the inputs are deterministic. That characteristic is useful at this work to perform the sizing check of the PV system project.

Following, the SSA expressions are then encoded using the chosen SMT solver supported by ESBMC: Boolector (default) \cite{Brummayer}, Z3 \cite{DeMoura}, MathSAT \cite{Cimatti}, Yices \cite{Dutertre} and CVC4 \cite{Barrett}.

Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied. If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is found to be unsatisfiable, there are no errors up to the unwinding bound , and this result is presented.

ESBMC can be invoked through the command-line interface or configured through the Eclipse plug-in. Specific problems and the solver can be selected that way.

ESBMC aims to support all of ISO/IEC 9899:1999 C programming language standard, and detects errors in software by simulating a finite prefix of the program execution with all possible inputs. Classes of problems that can be detected include: user specified assertion failures, out of bounds array access, illegal pointer dereferences, double-free of malloc'd memory, misaligned memory access; integer overflows, divide by zero, memory leaks, concurrent software, deadlock, and data races (i.e. competing writes).

\subsection{Cyber-physical systems x Energy x ESBMC}
According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes. Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa. The economic and societal potential of such systems is vastly greater than what has been realized, and major investments are being made worldwide to develop the technology. The technology builds on the discipline of embedded systems (computers and software embedded in devices) whose principle mission is not computation, such as cars, toys, medical devices, and scientific instruments. CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole.

Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}. For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies. Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation).

Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled. Then a model checking will be performed to do a verification of the project in order to guarantee that the design of an off-grid SPV solution will meet the requirements, specifications and regulations.

As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification. Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver. This work tracks the same path.

\section{Methodology }

Fig. \ref{fig:statetransition} shows the state diagram for the proposed framework.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{statetransition}
\centering
\caption{State transition diagram to the proposed framework}
\label{fig:statetransition}
\end{figure}

It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.

The PV input data (load power demand, load consumption of energy, the PV system project data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the non-deterministic variables of the model, are all written as C Programming language code.

Then the tool ESBMC is called to perform the verification of this code. The nondeterministic variables (solar irradiance, ambient temperature, state of charge of the batteries, load demand of power and the load consumption of energy) will suffer a heavy test at ESBMC runtime execution. In addition, depending if one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system, is not accomplished or satisfied, the tool accuses a fail, and the diagnostic counterexample shows in which condition the fail/violation happened.

Simply put, instead of the ESBMC find the defect of a software or if a hardware does not meet the some requirements (as reliability, performance, or safety), the tool will verify if the requirements of the solar PV project are met. Detailing the condition of violation, of not meeting the requirements, if this occurs.

With this information in hand, the user or the engineer can correct his/her PV project, and run the ESBMC again to insure that the new configuration of the project will work as expected.

Theorem: XXX

\section{Related work}
The CBMC, it is notable its prominence through international awards received in competitions. In the works related to the CBMC, much of the research is focused on the improvement of the tool (as software and hardware verifier) and its performance in the competitions, without addressing, however, the question of PV system validation, as can be seen in \cite{Kroening}. For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.

ESBMC was developed to perform bounded model checks on both sequential and concurrent programs using a range of SMT solvers, and has a proven track of bug finding in real-world applications \cite{Cordeiro}, \cite{Ramalho}. The tool also implements a technique to prove the correctness of (some) unbounded programs, the k-induction algorithm; this approach has been applied to a large number of benchmarks and has produced more correct results than similar competing tools \cite{GadelhaSBMF}, \cite{GadelhaK}. \cite{Trindade} show that is possible to perform the partitioning of hardware-software (optimization) using ESBMC as well. \cite{Bessa} show that is possible to use ESBMC to check the stability of digital control systems with uncertainty. In addition, \cite{Abateetal2017} show the approach to synthesize safe digital feedback controllers for physical plants represented as linear, time invariant models. However, the use of ESBMC to verify PV systems is unprecedented.

Concerning modeling and simulation of electrical energy systems, \cite{Kremers} used an agent-base model approach to evaluate the effect of loads (refrigerators mainly), shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study. However, that is a software development approach for the simulation of complex systems, without the formalism of automated verification.

In the other hand, the use of formal verification related to modeling and validation or even simulation of power systems or power networks is a young theme of research. According \cite{Abateetal2014}, where articles from seminars were issued at this thematic, the actual focus is on optimization and control of microgrids, HVAC systems (diagnostics and maintenance), models of generic wind turbine generation, modeling of transmission networks, and verification of smart grids. In addition, according with \cite{Abate2017}, recent research has attempted to formalize and implement a formal study of large population of PV panels (very common in European Union). The focus have been the modeling of the dynamics of PV panels and their interaction with the power grid. Those models do not use battery array, for example.

Therefore, the present work unites the versatility and power of the formal models, applied to a formal verification tool, with individual PV systems (off-grid), which is the most indicated and common option to solve the problem of energy in developing countries. Especially those that have isolated communities, either for long distances of the great centers, or for being riverside. This work includes, based on its off-grid characteristic, batteries and charge controllers, differently of on-grid systems of related work.

\section{Conclusions and Future Work}
The proposed framework seems to be a coherent and promising tool to perform verification of a PV project. The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field.

The framework presented here establishes the automated verification and the project sizing check. However, it is possible to perform the optimum sizing of the PV system. Moreover, the authors target the use of synthesis to perform the optimum sizing. That is an interesting issue, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a SPV system,  the idea of just to validate one given solutions is not enough. Probably is more useful to design a tool which starts from a list of commercial equipments, i.e., inputs, where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs, automatically. This is what a Counterexample Guided-Inductive Synthesis (CEGIS) does.

In the future, it is possible to expand the type of renewable used for power generation. Allowing the verification of wind generation or even hybrid systems, which can transform the tool into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.

Plus (need to think about it): verification in every-hour of a 48h cycle?, PV model math model can be improved, charge/discharge of batteries can be improved (is a simplified model), house's power consumption is not flat or constant, the dweller can buy more home appliances, synthesis need a data base of components, to test peak (surge) consumption (above the nominal), additional models for on-grid/off-grid farm, hybrid, and on-grid with batteries).

\section{Nomenclature }

text here

%\section{References}

\bibliography{trindadeThesis}{}
\bibliographystyle{ieeetr}
%\bibliographystyle{plain}
%\printbibliography

\end{document}

### 2018-08-06 code/battery_code_rev0.c

@@ -1,0 +1,30 @@
+//code for the battery by Alessandro, July 2018
+
+//#include <stdlib.h>
+
+#include<graphics.h>
+#include<stdio.h> 
+#include<string.h>
+#include<math.h>
+
+#define SOC 0.90
+#define AMBtemperature 32
+#define C10 195
+
+int main(){
+	float I, Vd, Vc;
+	int DeltaT;
+	
+
+	I = 23; //23 A has to be generated to feed the load demand (700W and 127V)
+	DeltaT = (AMBtemperature - 25);
+	Vd = (2.085-0.12*(1-SOC))-(1-0.007*DeltaT)*I*(0.02+4/(1+pow(I,1.3))+0.27/(pow(SOC,1.5))/C10);
+	printf ("----------Battery model validation-----------\n");	
+	printf ("Discharge voltage related to DeltaT= %i is Vd= %f\n", DeltaT, Vd);
+	Vc = (2 + 0.16*SOC)-(1-0.025*DeltaT)*I*(0.036+6/(1+pow(I,0.86))+0.48/(pow((1-SOC),1.2))/C10);
+	printf ("Charge voltage related to DeltaT= %i is Vd= %f\n", DeltaT, Vc);
+	getch();
+
+} 
+
+

### 2018-08-06 code/codePVsystem_rev0 (another copy).c

@@ -1,0 +1,224 @@
+/* --------------------------------------------------------------------------------------------------------
+Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <time.h>
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 501 W
+#define Phouse 501
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 9.34
+#define Vocref 45.5
+#define Imref 8.78
+#define Vmref 37
+#define Pmref 325
+
+
+int main(){
+
+     	int count, SOC, AMBtemperature, G, RemCap, drainedCurrent;
+	float PinDCmin, Idcmin, Idc, Vdc;
+
[…]

### 2018-08-06 code/codePVsystem_rev0 (copy).c

@@ -1,0 +1,223 @@
+/* --------------------------------------------------------------------------------------------------------
+Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 501 W
+#define Phouse 501
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 9.34
+#define Vocref 45.5
+#define Imref 8.78
+#define Vmref 37
+#define Pmref 325
+
+
+int main(){
+
+     	int count, SOC, AMBtemperature, G, RemCap, drainedCurrent;
+	float PinDCmin, Idcmin, Idc, Vdc;
+
[…]

### 2018-08-06 code/codePVsystem_rev0.c

@@ -1,0 +1,272 @@
+/* --------------------------------------------------------------------------------------------------------
+Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <time.h>
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 501 W
+#define Phouse 501
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 9.34
+#define Vocref 45.5
+#define Imref 8.78
+#define Vmref 37
+#define Pmref 325
+
+void pvmodel (int, int);
+int Parray, Iarray, Varray;
+
+int main(){
+     	int count, SOC, AMBtemperature, G, RemCap, drainedCurrent;
[…]

### 2018-08-06 code/codePVsystem_rev1.c

@@ -1,0 +1,278 @@
+/* --------------------------------------------------------------------------------------------------------
+Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <time.h>
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 501 W
+#define Phouse 501
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 9.34
+#define Vocref 45.5
+#define Imref 8.78
+#define Vmref 37
+#define Pmref 325
+
+void pvmodel (int, int);
+int Parray, Iarray, Varray;
+
+unsigned int nondet_uint();
+
+int main(){
[…]

### 2018-08-06 code/codePVsystem_rev2.c

@@ -1,0 +1,348 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0000000001
+#define precisionEXP 0.00000001
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 501 W
+#define Phouse 501
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 9.34
+#define Vocref 45.5
+#define Imref 8.78
+#define Vmref 37
+#define Pmref 325
+
[…]

### 2018-08-06 code/codePVsystem_rev3.c

@@ -1,0 +1,349 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.00001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 501 W
+#define Phouse 501
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 9.34
+#define Vocref 45.5
+#define Imref 8.78
+#define Vmref 37
[…]

### 2018-08-06 code/codePVsystem_rev4.c

@@ -1,0 +1,368 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 510 W
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+#ifdef HOUSE1 
+#define Phouse 510
+#elif HOUSE2
+#define Phouse 253
+#elif HOUSE3
+#define Phouse 263
+#elif HOUSE4
+#define Phouse 283
+#endif
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
[…]

### 2018-08-06 code/codePVsystem_rev4old.c

@@ -1,0 +1,363 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 510 W
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+#define Phouse 510
+//#define Phouse 253
+//#define Phouse 263
+//#define Phouse 283
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
[…]

### 2018-08-06 code/codePVsystem_rev5.c

@@ -1,0 +1,373 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220
+#define bankcapacity capacity*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 510 W
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+#ifdef HOUSE1 
+#define Phouse 510
+#elif HOUSE2
+#define Phouse 253
+#elif HOUSE3
+#define Phouse 263
+#elif HOUSE4
+#define Phouse 283
+#endif
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
[…]

### 2018-08-06 code/codePVsystem_rev5MENOR.c

@@ -1,0 +1,372 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220
+#define bankcapacity capacity*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 510 W
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+#ifdef HOUSE1 
+#define Phouse 510
+#elif HOUSE2
+#define Phouse 253
+#elif HOUSE3
+#define Phouse 263
+#elif HOUSE4
+#define Phouse 283
+#endif
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
[…]

### 2018-08-06 code/codePVsystem_rev6.c

@@ -1,0 +1,378 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 2
+#define NBP 2
+#define capacity 220
+#define bankcapacity capacity*NBP
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk 14.40*NBS
+#define Vfloat 13.20*NBS
+//PV system autonomy concerning batteries: 48h
+#define auton 48
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 510 W
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+#ifdef HOUSE1 
+#define Phouse 510
+#elif HOUSE2
+#define Phouse 253
+#elif HOUSE3
+#define Phouse 263
+#elif HOUSE4
+#define Phouse 283
+#endif
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
[…]

### 2018-08-06 code/codePVsystem_rev7ale.c

@@ -1,0 +1,308 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 4
+#define NBP 1
+#define capacity 120
+#define bankcapacity (capacity*NBP)
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk (14.40*NBS)
+#define Vfloat (13.20*NBS)
+//PV system autonomy concerning batteries: 6h
+#define auton 6
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 510 W
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+#elif HOUSE3
+  //Sandriane's house 263W and 2.5kWh
+  #define Phouse 263
+  #define loadcurve {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113}
+#elif HOUSE4
[…]

### 2018-08-06 code/codePVsystem_rev7ale_old.c

@@ -1,0 +1,309 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 80% (i.e., 20% of DOD) as usual to lead-acid batteries
+#define NBS 4
+#define NBP 1
+#define capacity 120
+#define bankcapacity (capacity*NBP)
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk (14.40*NBS)
+#define Vfloat (13.20*NBS)
+//PV system autonomy concerning batteries: 6h
+#define auton 6
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 510 W
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+#elif HOUSE3
+  //Sandriane's house 263W and 2.5kWh
+  #define Phouse 263
+  #define loadcurve {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113}
+#elif HOUSE4
[…]

### 2018-08-06 code/esbmc/10nodesESBMC2mod.c

@@ -1,0 +1,81 @@
+//#include <math.h>
+
+#define MAXn 10 //máximo número de nodes
+#define MAXe 13 //máximo número de edges (arestas)
+
+_Bool nondet_bool();
+int nondet_int();
+
+int tmp[MAXe];
+
+int main() {
+  int i, j, k, aux=0, softcost=0, comcost=0;
+  _Bool x[MAXn]; 
+  
+int s[MAXn] = {10, 15, 7, 4, 9, 10, 15, 7, 4, 9};  //
+int h[MAXn] = {5, 10, 3, 4, 8, 5, 10, 3, 4, 8}; //custo de hardware para cada nó
+int c[MAXe] = {5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5, 5}; //custo de comunicação de cada aresta
+
+int E[MAXe][MAXn] = {{-1, 1, 0, 0, 0, 0, 0, 0, 0, 0},
+                     {-1, 0, 1, 0, 0, 0, 0, 0, 0, 0},
+				     {-1, 0, 0, 0, 0, 1, 0, 0, 0, 0},
+				     {0, -1, 0, 0, 1, 0, 0, 0, 0, 0},
+				     {0, 0, -1, 0, 1, 0, 0, 0, 0, 0},
+				     {0, 0, -1, 1, 0, 0, 0, 0, 0, 0},
+				     {0, 0, 0, -1, 1, 0, 0, 0, 0, 0},
+				     {0, 0, 0, 0, 0, -1, 1, 0, 0, 0},
+				     {0, 0, 0, 0, 0, -1, 0, 1, 0, 0},
+				     {0, 0, 0, 0, -1, 0, 0, 0, 1, 0},
+				     {0, 0, 0, 0, 0, 0, -1, 0, 1, 0},
+				     {0, 0, 0, 0, 0, 0, 0, -1, 1, 0},
+				     {0, 0, 0, 0, 0, 0, 0, 0, -1, 1}};  //matriz incidente do Grafo (nó, arestas)
+
+
+ 
+  for(i=0; i<MAXn; i++) {
+    x[i] = nondet_bool();
+  }
+
+  //s(1-x)
+  for(i=0; i<MAXn; i++) {
+    softcost += s[i]*(1-x[i]);
+  }
+
+  //Ex
+  aux = 0;
+  for(i=0; i<MAXe; i++) {
+    for(j=0; j<MAXn; j++) {
[…]

### 2018-08-06 code/esbmc/mainESBMC1xyCRC32.c

@@ -1,0 +1,115 @@
+//#include <math.h>
+// CRC32 com x e y
+#define MAXn 25 //máximo número de nodes
+#define MAXe 32 //máximo número de edges (arestas)
+
+_Bool nondet_bool();
+int nondet_int();
+
+int tmp[2*MAXe + 1];
+
+int main() {
+  int i, j, aux=0; 
+  _Bool x[MAXn + MAXe]; 
+
+  int f [MAXn + MAXe] = {2,2,0,2,0,1,1,0,0,0,1,1,0,1,2,0,1,2,2,2,0,0,0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0};
+  int A [2*MAXe+1] [MAXn+MAXe] = {{-1, -2, -1, -1, -2, -1, -1, -3, -1, -1, -1, -1, -1, -1, -2, -1, -1, -2, -1, -2, -0, -0, -0, -0, -0,  11,3,8,4,10,8,5,4,4,9,10,10,7,2,8,3,2,10,11,7,7,6,6,1,12,8,2,10,3,2,7,6}, 
+{-1.0, 1.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, -1.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0},
[…]

### 2018-08-06 code/esbmc/mainESBMC2crc32.c

@@ -1,0 +1,94 @@
+// adequado para invariantes
+//#include <math.h>
+// CRC32 com módulo
+#define MAXn 25 //máximo número de nodes
+#define MAXe 32 //máximo número de edges (arestas)
+
+int nondet_bool();
+int nondet_int();
+int tmp[MAXe];
+
+int main() {
+  int tiph = nondet_int();
+  int i, j, aux=0, softcost=0, comcost=0, fobj, cont, hmax=0;
+  int x[MAXn]; 
+
+int s [MAXn] = {1,2,1,1,2,1,1,3,1,1,1,1,1,1,2,1,1,2,1,2,0,0,0,0,0};
+int h [MAXn] = {2,2,0,2,0,1,1,0,0,0,1,1,0,1,2,0,1,2,2,2,0,0,0,0,0};
+int c [MAXe] = {11,3,8,4,10,8,5,4,4,9,10,10,7,2,8,3,2,10,11,7,7,6,6,1,12,8,2,10,3,2,7,6};
+int E [MAXe] [MAXn] = {
+{-1.0, 1.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, -1.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0},
[…]

### 2018-08-06 code/esbmc/mainESBMC2modCRC32.c

@@ -1,0 +1,89 @@
+//#include <math.h>
+// CRC32 com módulo
+#define MAXn 25 //máximo número de nodes
+#define MAXe 32 //máximo número de edges (arestas)
+
+_Bool nondet_bool();
+int nondet_int();
+
+int tmp[MAXe];
+
+int main() {
+  int i, j, k, aux=0, softcost=0, comcost=0;
+  _Bool x[MAXn]; 
+
+int s [MAXn] = {1,2,1,1,2,1,1,3,1,1,1,1,1,1,2,1,1,2,1,2,0,0,0,0,0};
+int h [MAXn] = {2,2,0,2,0,1,1,0,0,0,1,1,0,1,2,0,1,2,2,2,0,0,0,0,0};
+int c [MAXe] = {11,3,8,4,10,8,5,4,4,9,10,10,7,2,8,3,2,10,11,7,7,6,6,1,12,8,2,10,3,2,7,6};
+int E [MAXe] [MAXn] = {{-1.0, 1.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, -1.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0},
[…]

### 2018-08-06 code/func_exp_rev0.c

@@ -1,0 +1,42 @@
+// 
+// Function that calculates the exponential of a number x (e^x) - Alessandro Trindade July 2018
+// 
+// Uses Tayler Series 
+// The exponential function has the following Maclaurin series
+// Sums: 1 + x + x^2/2! + x^3/3! + x^4/4! + x^5/5! + ...
+// and it converges for all x
+//
+// To get an approximation of e^x (all depends on the precision demanded by the code)
+//
+#include <stdio.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here
+#define precisionEXP 0.0001
+
+//from https://codereview.stackexchange.com/questions/123970/implementation-of-exp-function-in-c-using-taylor-series-expansion but with improvement in the while, to solve negative numbers
+double expESBMC (double num){  
+    double x1, sum=0.0;
+    int n=0;
+    // Stops when the next term to add becomes smaller than precision.
+    x1=1;
+    do {
+        sum += x1;
+        x1  *= (num/++n);
+    } while ((x1 > precisionEXP) || ((-1*x1) > precisionEXP));
+    return sum;
+}
+
+
+//main code just for test
+int main(void) {
+	double cont;
+	//for (cont=0; cont >= -10; cont=cont-0.2){ //test negative numbers
+	for (cont=0; cont <= 10; cont=cont+0.5){ //test positive numbers
+    		printf("num=%lf, sum=%lf, exp=%lf\n",cont, expESBMC(cont),exp(cont));
+		printf ("----\n");
+	}
+    	return 0;
+}
+
+

### 2018-08-06 code/func_exp_rev1.c

@@ -1,0 +1,60 @@
+// 
+// Function that calculates the exponential of a number x (e^x)
+// 
+// Uses Tayler Series 
+// The exponential function has the following Maclaurin series
+// Sums: 1 + x + x^2/2! + x^3/3! + x^4/4! + x^5/5! + ...
+// and it converges for all x
+//
+// To get an approximation of e^x.
+//
+#include <stdio.h>
+#include <math.h>
+
+#define precisionEXP 0.0000001
+
+long long int factorial (int);
+double expESBMC (double);
+
+int main(void) {
+	double cont;
+	//for (cont=0; cont >= -10; cont--){
+	for (cont=0; cont <= 10; cont=cont+0.5){
+    		printf("num=%lf, sum=%lf, exp=%lf\n",cont, expESBMC(cont),exp(cont));
+		printf ("----\n");
+	}
+    	return 0;
+}
+
+double expESBMC (double num){
+    double x1, sum=0.0;
+    int n=1;
+    // Stops when the next term to add becomes smaller than precision.
+    x1=1;
+    do {
+        sum = sum + x1;
+        x1  = pow(num,n)/factorial(n);
+	n=n+1;
+	//printf("x1= %lf, ",x1);
+    } while (x1 > precisionEXP);
+    return sum;
+}
+
+
+long long int factorial(int num)
+{
+    int i;
+    long int result = 1;
+
+    // show error if the user enters a negative integer
+    if (num < 0)
+        printf("Error! Factorial of a negative number doesn't exist.");
+
+    else{
+        for(i=1; i<=num; ++i){
+            result *= i;              // factorial = factorial*i;
+        }
+    }
+//printf("fatorial = %lli \n", result);
+    return result;
+}

### 2018-08-06 code/func_ln.c

@@ -1,0 +1,72 @@
+// 
+// Function that calculates the natural logarithmic of base e for a number x - Alessandro Trindade July 2018
+// 
+// log(m) base e = 2[ (m-1/m+1) + (1/3) * (m-1/m+1)^3 + (1/5) * (m-1/m+1)^5 + ... ]
+//
+// To get an approximation of log (all depends on the precision demanded by the code)
+// OBS: The natural logarithm function ln(x) is defined only for x>0. So the natural logarithm of a negative number is undefined.
+
+// Function logESBMC of natural base e
+#include <stdio.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here
+#define precisionLN 0.00001
+
+
+//code here from https://stackoverflow.com/questions/3343395/value-of-natural-logarithm
+double logESBMC1 (double x){
+	double logx, tty, ty;
+	int i;
+	i=1; 
+	logx = 0 ;
+	ty = (x-1)/(x+1) ;
+	do{
+	   	logx = logx + ty / i;
+    		tty = ty ;
+    		ty = (ty * ((x-1)/(x+1)) * ((x-1)/(x+1)));
+    		i = i + 2 ;
+	} while((tty - ty) > precisionLN);
+	logx = 2*logx ;
+	return logx;
+
+}
+
+double logESBMC2 (double d){ //from: https://www.youtube.com/watch?v=zaTdPTzw5Pc if 0<x<1
+	double result = 0.0, term = d-1;
+	int power_of_one=-1;
+	int denominator = 2;
+	double temp = term;
+	while (temp > precisionLN || -temp > precisionLN){
+		if (temp > precisionLN) result -= temp;
+		else result += temp;
+		term = term * (d-1);
+		temp = term * power_of_one;
+		temp /= denominator;
+		power_of_one *= -1;
+		denominator += 1;	
+	}
+	result += term;
+	return result;
+}
+
+double logESBMC (double x){
+	double answer;
+	if (x > 1.0) answer = logESBMC1(x);
+	else if (x>0.0) answer=logESBMC2(x);
+	else answer = NAN;
+	return answer;
+}
+
+
+//main code just for test
+int main(void) {
+	double cont;
+	for (cont=0.1; cont <= 50; cont=cont+0.1){ //test positive numbers
+    		printf("num=%lf, sum=%lf, log=%lf\n",cont, logESBMC(cont),log(cont));
+		printf ("----\n");
+	}
+    	return 0;
+}
+
+

### 2018-08-06 code/func_ln_rev0.c

@@ -1,0 +1,44 @@
+// 
+// Function that calculates the natural logarithmic of base e for a number x - Alessandro Trindade July 2018
+// 
+// log(m) base e = 2[ (m-1/m+1) + (1/3) * (m-1/m+1)^3 + (1/5) * (m-1/m+1)^5 + ... ]
+//
+// To get an approximation of log (all depends on the precision demanded by the code)
+// OBS: The natural logarithm function ln(x) is defined only for x>0. So the natural logarithm of a negative number is undefined.
+
+// Function logESBMC of natural base e
+#include <stdio.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here
+#define precisionLN 0.000000001
+
+//code here from https://stackoverflow.com/questions/3343395/value-of-natural-logarithm
+double logESBMC (double x){
+	double logx, tty, ty;
+	int i;
+	i=1; 
+	logx = 0 ;
+	ty = (x-1)/(x+1) ;
+	do{
+	   	logx = logx + ty / i;
+    		tty = ty ;
+    		ty = (ty * ((x-1)/(x+1)) * ((x-1)/(x+1)));
+    		i = i + 2 ;
+	} while((tty - ty) > precisionLN);
+	logx = 2*logx ;
+	return logx;
+
+}
+
+//main code just for test
+int main(void) {
+	double cont;
+	for (cont=0; cont <= 10; cont=cont+0.1){ //test positive numbers
+    		printf("num=%lf, sum=%lf, log=%lf\n",cont, logESBMC(cont),log(cont));
+		printf ("----\n");
+	}
+    	return 0;
+}
+
+

### 2018-08-06 code/func_ln_rev1.c

@@ -1,0 +1,52 @@
+// 
+// Function that calculates the natural logarithmic of base e for a number x - Alessandro Trindade July 2018
+// 
+// log(m) base e = 2[ (m-1/m+1) + (1/3) * (m-1/m+1)^3 + (1/5) * (m-1/m+1)^5 + ... ]
+//
+// To get an approximation of log (all depends on the precision demanded by the code)
+// OBS: The natural logarithm function ln(x) is defined only for x>0. So the natural logarithm of a negative number is undefined.
+
+// Function logESBMC of natural base e
+#include <stdio.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here
+#define precisionLN 0.00000001
+
+
+double logESBMC (double x){
+
+double tty;
+double ty = (x-1)/(x+1);
+double p = ty * ty;
+int i = 1;
+double logx = 0;
+do {
+  logx += ty / i;
+  tty = ty;
+  ty *= p;
+  i += 2;
+} while ((tty/(i-2) - ty/i) > 1e-6);
+
+
+	logx = 2*logx ;
+//	printf("\n ln (%g) = %g \n", x, logx);
+	return logx;
+
+}
+
+//main code just for test
+int main(void) {
+	double cont;
+	for (cont=0; cont <= 9; cont=cont+0.1){ //test positive numbers
+    		printf("num=%lf, sum=%lf, log=%lf\n",cont, logESBMC(cont),log(cont));
+		printf ("----\n");
+	}
+    	return 0;
+}
+
+
+
+
+
+

### 2018-08-06 code/func_ln_rev3.c

@@ -1,0 +1,46 @@
+// 
+// Function that calculates the natural logarithmic of base e for a number x - Alessandro Trindade July 2018
+// 
+// log(m) base e = 2[ (m-1/m+1) + (1/3) * (m-1/m+1)^3 + (1/5) * (m-1/m+1)^5 + ... ]
+//
+// To get an approximation of log (all depends on the precision demanded by the code)
+// OBS: The natural logarithm function ln(x) is defined only for x>0. So the natural logarithm of a negative number is undefined.
+
+// Function logESBMC of natural base e
+#include <stdio.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here
+#define precisionLN 0.00000000001
+
+double logESBMC (double d){ //from: https://www.youtube.com/watch?v=zaTdPTzw5Pc if 0<x<1
+	double result = 0.0, term = d-1;
+	int power_of_one=-1;
+	int denominator = 2;
+	double temp = term;
+	while (temp > precisionLN || -temp > precisionLN){
+		if (temp > precisionLN) result -= temp;
+		else result += temp;
+		term = term * (d-1);
+		temp = term * power_of_one;
+		temp /= denominator;
+		power_of_one *= -1;
+		denominator += 1;	
+	}
+	result += term;
+	return result;
+}
+
+//main code just for test
+int main(void) {
+	double cont;
+//	long double cont=0.01;
+//    		printf("num=%Lf, sum=%Lf, log=%lf\n",cont, logESBMC(cont),log(cont));
+	for (cont=0.05; cont <= 1; cont=cont+0.05){ //test positive numbers
+    		printf("num=%lf, sum=%lf, log=%lf\n",cont, logESBMC(cont),log(cont));
+		printf ("----\n");
+	}
+    	return 0;
+}
+
+

### 2018-08-06 code/graphdemo/demo2.c

@@ -1,0 +1,37 @@
+#include<graphics.h>
+#include<stdio.h>
+
+int main(){
+int gd=DETECT,gm;
+int i,x,y;
+initgraph(&gd,&gm,NULL);
+    circle(50, 50, 30);
+line(0,0,640,0);
+line(0,0,0,480);
+line(639,0,639,480);
+line(639,479,0,479);
+   // location of ellipse
+    x = 250; y = 200;
+ 
+    // here is the starting angle
+    // and end angle
+    int start_angle = 0;
+    int end_angle = 360;
+ 
+    // radius from x axis and y axis
+    int x_rad = 100;
+    int y_rad = 50;
+ 
+    // ellipse fuction
+    ellipse(x, y, start_angle,
+     end_angle, x_rad, y_rad);
+
+//random points of plotting
+for(i=0;i<=1000;i++){
+   x=rand()%639;
+   y=rand()%480;
+   putpixel(x,y,15);
+}
+  getch();
+  closegraph();
+}

### 2018-08-06 code/pixelplot.c

@@ -1,0 +1,122 @@
+#include<graphics.h>
+#include<stdio.h> 
+#include <string.h>
+
+#define AMPLIX 10
+#define AMPLIY 30
+#define Voc 45.5
+#define Isc 9.34
+
+int convertX(int);
+int convertY(int);
+void itoa(int, char *);
+void reverse(char *);
+
+
+int main(){
+	int gd=DETECT,gm;
+	int i,x,y;
+	char buffer[5];
+	initgraph(&gd,&gm,NULL);
+
+	outtextxy(100, 20, "PV modeling validation - Alessandro Trindade");
+
+	//drawing a rectangle around the windows borders
+	line(0,0,639,0); //top border line
+	line(0,479,639,479); //bottom border line
+	line(0,0,0,479); //left side line
+	line(639,0,639,479); //rigth side line
+
+	//drawwing the X axys and the Y axys
+	setcolor(1);
+	line (convertX(0),convertY(0),convertX((int)Voc),convertY(0)); //line(from xo, from yo, to x1, to y1)
+	line (convertX(0),convertY(0),convertX(0),convertY((int)Isc+1));
+
+	//dots to aid identify X and Y axys
+	for (i=2;i<=(int)Voc;i=i+2) putpixel(convertX(i),convertY(0),4); //X axys dots
+ 	for (i=2;i<=(int)Isc;i=i+2) putpixel(convertX(0),convertY(i),4); //Y axys dots
+
+
+
+	// X axys graphic caption
+	outtextxy((convertX(0)-10), (convertY(0)+10),"0,0"); //print 0,0 at the graphic
+	itoa((int)Voc,buffer);
+	outtextxy((convertX((int)Voc)-5), (convertY(0)+10),buffer); //print 0,maxX at the graphic	
+	itoa((int)Voc/2,buffer);
+	outtextxy((convertX((int)Voc/2)-5), (convertY(0)+10),buffer); //print 0,1/2 maxX at the graphic
+	itoa((int)Voc/4,buffer);
+	outtextxy((convertX((int)Voc/4)-5), (convertY(0)+10),buffer); //print 0,1/4 maxX at the graphic
+	itoa((int)Voc*3/4,buffer);
+	outtextxy((convertX((int)Voc*3/4)-5), (convertY(0)+10),buffer); //print 0,3/4 maxX at the graphic
+
+	// Y axys graphic caption
+	itoa((int)Isc,buffer);
[…]

### 2018-08-06 code/pvmodel (copy).c

@@ -1,0 +1,86 @@
+/* mathmatical model of PV system with the 1-diode model */
+
+#include <stdio.h>
+#include <math.h>
+#include<graphics.h> 
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, and air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 7.57
+#define Vocref 41.8
+#define Voc 45.5
+#define Imref 6.89
+#define Vmref 33.7
+
+
+
+int main(){
+//	int gd=DETECT,gm;
+//	int i,x,y;
+//	int N, NOCT;
+//	double Gref, Tref, mii, miv, Iscref, Iphref, Vocref, Imref, Vmref, Tair, G, kb, q, T, Tk, VT, a, Io, Iph, I, V, Voc;
+double Iphref, Tair, G, kb, q, T, Tk, VT, a, Io, Iph, I, V;
+
+	//graphical initiallization
+//	initgraph(&gd,&gm,NULL);
+
+	
+
+	//data from the site where the PV will be deployed
+//	Gref = 1000; //reference irradiance is 1000 W/m²
+//	Tref = 298.15; //reference temperature is 25oC or 298.15K
+//	mii = 0.053; //short-circuit current temperature coefficient (A/K)***
+//	miv = -0.31; //open-circuit voltage temperature coefficient (V/K)***
+//	Iscref = 7.57;
+	Iphref = Iscref; //mathematical approximation
+//	Vocref = 41.8;
+//	Voc = 45.5;
+//	Imref = 6.89;
+//	Vmref = 33.7;
+
+	//non-deterministic variables
+	Tair = 25;  //ambient temperature in degree Celsius. Depends on the day and the time
+	G = 1000; //irradiance of site in W/m2. Depends on the day and the time
+
+	//set up of parameters
[…]

### 2018-08-06 code/pvmodel.c

@@ -1,0 +1,75 @@
+/* mathmatical model of PV system with the 1-diode model */
+
+#include <stdio.h>
+#include <math.h>
+#include<graphics.h> 
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, and air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 7.57
+#define Vocref 41.8
+#define Voc 45.5
+#define Isc 9.34
+#define Imref 6.89
+#define Vmref 33.7
+
+
+
+int main(){
+
+	double Iphref, Tair, G, kb, q, T, Tk, VT, a, Io, Iph, I, V, Vm, Im;
+
+	Iphref = Iscref; //mathematical approximation
+
+	//non-deterministic variables
+	Tair = 25;  //ambient temperature in degree Celsius. Depends on the day and the time
+	G = 1000; //irradiance of site in W/m2. Depends on the day and the time
+
+	//set up of parameters
+	kb = 1.3806503*pow(10,-23);  //Boltzmann constant in Joule
+	q = 1.60217646*pow(10,-19);  //absolute value of the electron's charge
+	T= Tair + G*(NOCT-20)/800; //temperature of the p-n junction or cell temperature
+T=25;
+	Tk = T + 273.15; //is the temperaute T in Kelvin
+	VT = kb*Tk/q;
+printf("VT = %f\n",VT);
+
+	//a ideality/quality factor
+	a = q*(Vmref-Vocref)/(N*kb*Tk*log(1-Imref/Iscref));
+//a=1;
+
+	//Io = reverse saturation current of the diode
+	Io = (Iscref+mii*(Tk-Tref))/(exp (q*(Vocref+miv*(Tk-Tref))/(a*N*kb*Tk)) - 1);
+
[…]

### 2018-08-06 code/pvmodel2.c

@@ -1,0 +1,195 @@
+/* mathmatical model of PV system with the 1-diode model */
+
+#include<graphics.h>
+#include<stdio.h> 
+#include<string.h>
+#include<math.h>
+
+//amplify factor of axis X and Y
+#define AMPLIX 10
+#define AMPLIY 30
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, and air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 9.34
+#define Vocref 45.5
+#define Imref 8.78
+#define Vmref 37
+
+int convertX(float);
+int convertY(float);
+void itoa(int, char *);
+void reverse(char *);
+
+
+int main(){
+	int gd=DETECT,gm;
+	int i,x,y;
+	double Iphref, Tair, G, kb, q, T, Tk, VT, a, Io, Iph, I, V, Vmax, Imax;
+	char buffer[5];
+	initgraph(&gd,&gm,NULL);
+
+	outtextxy(100, 20, "PV modeling validation - by Alessandro Trindade May2018");
+
+
+	//drawing a rectangle around the windows borders
+	line(0,0,639,0); //top border line
+	line(0,479,639,479); //bottom border line
+	line(0,0,0,479); //left side line
+	line(639,0,639,479); //rigth side line
+
+	//drawwing the X axis and the Y axis
+	setcolor(1);
+	line (convertX(0),convertY(0),convertX((int)Vocref),convertY(0)); //line(from xo, yo, to x1, to y1)
+	line (convertX(0),convertY(0),convertX(0),convertY((int)Iscref+1));
+
+	//dots to aid identify X and Y axis
+	for (i=1;i<=(int)Vocref;i++) putpixel(convertX(i),convertY(0),4); //X axis dots
[…]

### 2018-08-06 code/pvmodel3.c

@@ -1,0 +1,81 @@
+/* mathmatical model of PV system with the 1-diode model */
+/* here the output is the MPPT (max power), with the highest values of voltage, current and power from the array of solar panels */
+
+#include<stdio.h> 
+#include<math.h>
+
+//definition of array arrangement of solar panels (star energy projet has 3x325W in serie)
+#define Ncellsparallel 1
+#define Ncellsseries 3
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
+#define N 72    //N=number of series-connected cells
+#define NOCT 45 //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
+#define Gref 1000 //reference irradiance is 1000 W/m²
+#define Tref 298.15 //reference temperature is 25oC or 298.15K
+#define mii 0.053 //short-circuit current temperature coefficient (A/K)
+#define miv -0.31 //open-circuit voltage temperature coefficient (V/K)
+#define Iscref 9.34
+#define Vocref 45.5
+#define Imref 8.78
+#define Vmref 37
+#define Pmref 325
+
+
+int main(){
+	int i,x,y;
+	double Iphref, AMBtemperature, G, kb, q, T, Tk, VT, a, Io, Iph, I, V, Vmax, Imax, Pmax, Parray, Iarray, Varray;
+
+	//model 
+	Iphref = Iscref; //mathematical approximation from the model
+
+	//non-deterministic variables (ESBMC will generate)
+	AMBtemperature = 25;  //ambient temperature in degree Celsius. Depends on the day and the time
+	G = 800; //irradiance of site in W/m2. Depends on the day and the time
+
+	//set up of parameters
+	kb = 1.3806503*pow(10,-23);  //Boltzmann constant in Joule
+	q = 1.60217646*pow(10,-19);  //absolute value of the electron's charge
+	T= AMBtemperature + G*(NOCT-20)/800; //temperature of the p-n junction or cell temperature
+
+	Tk = T + 273.15; //is the temperaute T in Kelvin
+	VT = kb*Tk/q;
+
+	//a ideality/quality factor
+	a = q*(Vmref-Vocref)/(N*kb*Tk*log(1-Imref/Iscref));
+
+
[…]

### 2018-08-06 code/codePVsystem_rev8ale (bak).c
updated material without real modification just test

@@ -1,0 +1,309 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 75% (i.e., 25% of DOD) as usual to lead-acid batteries
+#define NBS 4
+#define NBP 1
+#define capacity 120
+#define bankcapacity (capacity*NBP)
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk (14.40*NBS)
+#define Vfloat (13.20*NBS)
+//PV system autonomy concerning batteries: 6h
+#define auton 6
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 510 W
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+#elif HOUSE3
+  //Sandriane's house 263W and 2.5kWh
+  #define Phouse 263
+  #define loadcurve {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113}
+#elif HOUSE4
[…]

### 2018-08-09 code/tests/codePVsystem_rev8ale-rev2.c
updating of code and the results from 0808 tests

@@ -1,0 +1,318 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+------------------------------------------------------------------------by Alessandro Trindade, July 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+//#include <assert.h>
+
+void assert(int cond) {
+    if(!cond) 
+        map2check_error();
+}
+
+
+extern unsigned int __VERIFIER_nondet_uint(void);
+extern void __VERIFIER_assume(int cond);
+
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//requirements/restrictions
+//battery of 220 Ah capacity, and minimum SOC (before desconnect load) 75% (i.e., 25% of DOD) as usual to lead-acid batteries
+#define NBS 4
+#define NBP 1
+#define capacity 120
+#define bankcapacity (capacity*NBP)
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk (14.40*NBS)
+#define Vfloat (13.20*NBS)
+//PV system autonomy concerning batteries: 6h
+#define auton 6
+//power demand in Watt from the house served by the PV system (maximum is 700W considering Star Energy project): 510 W
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
[…]

### 2018-10-02 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated jorunal

--- 2018-08-06 Tex/Old text/paper_old_rev0.tex
@@
-\documentclass[10pt,a4paper]{article}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
+%% bare_jrnl.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% see http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[journal]{IEEEtran}
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[journal]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
+\usepackage{graphicx}
+\graphicspath{ {./images/} }
+%
+%\ifCLASSINFOpdf
+  %\usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+%  \DeclareGraphicsExtensions{.png}
+%\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+%\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
 \usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{graphicx}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
+%
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+\usepackage{algorithm,algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
+
+% *** ALIGNMENT PACKAGES ***
+%
+\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a larger sans serif font
+% than the serif footnote size font used in traditional IEEE formatting
+% and thus the need to invoke different subfig.sty package options depending
+% on whether compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
+% Axel Sommerfeldt. This package may be useful when used in conjunction with 
+% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
+% submissions have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.4.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/pkg/endfloat
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
 %Alessandro input: makecell package to permite line break inside tables
 \usepackage{makecell}
-\usepackage{cite}
-\graphicspath{ {./images/} }
-
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
+\begin{document}
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
 \title{Building a framework to perform automated verification of solar photovoltaic off-grid systems}
-\author{Alessandro Trindade \thanks{Federal University of Amazonas, Av.
-Rodrigo Octavio 3000, Coroado, Faculdade de Tecnologia, Campus Universitário, Manaus-AM, Brazil, alessandrotrindade@ufam.edu.br} \and Lucas Cordeiro \thanks{Department of Computer Science, University of Oxford, UK}}
-\date{}
-
-\begin{document}
-
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
+
+\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
+\thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil e-mail alessandrotrindade@ufam.edu.br.}% <-this % stops a space
+\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK e-mail lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
+\thanks{Manuscript received September 19, 2018; revised November 26, 2018.}}
+
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+% 
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+\markboth{IEEE TRANSACTIONS ON SUSTAINABLE ENERGY,~VOL.~X, NO.~Y, MONTH~2018}
+{Trindade \MakeLowercase{\textit{et al.}}: BUILDING A FRAMEWORK TO PERFORM AUTOMATED VERIFICATION OF SOLAR PHOTOVOLTAIC OFF-GRID SYSTEMS}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark.
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% make the title area
 \maketitle
 
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
 \begin{abstract}
@@
 This paper aims to build the framework to apply automated verification methods to mathematical models of a complete system of rural electrification with solar photovoltaic energy to validate its design from a formal verification perspective.
-
-Keywords: Automated verification, model checking, energy systems, solar photovoltaic systems, off-grid systems. 
 \end{abstract}
 
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+Automated verification, model checking, energy systems, solar photovoltaic systems, off-grid systems.
+\end{IEEEkeywords}
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
 \section{Introduction}
-According to \cite{Coelho} there are presently 1.3 billion people with no access to electricity worldwide.
+% The very first letter is a 2 line initial drop letter followed
+% by the rest of the first word in caps.
+% 
+% form to use if the first word consists of a single letter:
+% \IEEEPARstart{A}{demo} file is ....
+% 
+% form to use if you need the single drop letter followed by
+% normal text (unknown if ever used by the IEEE):
+% \IEEEPARstart{A}{}demo file is ....
+% 
+% Some journals put the first two words in caps:
+% \IEEEPARstart{T}{his demo} file is ....
+% 
+% Here we have the typical use of a "T" for an initial drop letter
+% and "HIS" in caps to complete the first word.
+\IEEEPARstart{A}{ccording} to \cite{Coelho} there are presently 1.3 billion people with no access to electricity worldwide.
 The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass.
@@
 
-Manufacturers and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
+Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
 
@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{flowchart_verification.png}
+\includegraphics[width=0.4\textwidth]{flowchart_verification.png}
 \centering
@@
 Usually this type of system is for low power applications, as defined by \cite{Roy}.
-The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:unregSPV}.
+The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:standaloneSPV} letter (a).
 At night hours, the system will not provide any supply because of the absence of the battery.
@@
 \begin{figure}[h]
-\includegraphics[width=0.6\textwidth]{unregulatedSPV.png}
+\includegraphics[width=0.5\textwidth]{reg_unreg4.png}
 \centering
-\caption{Unregulated standalone SPV system with DC load (Source: \cite{Roy})}
-\label{fig:unregSPV}
+\caption{PV standalone systems: (a) regulated standalone SPV system with DC load; (b) regulated standalone SPV system with DC load; (c) regulated standalone SPV system with battery DC load; and (d) regulated standalone system with battery and AC load  (Source: \cite{Roy})}
+\label{fig:standaloneSPV}
 \end{figure}
@@
 \subsection{Regulated standalone PV system with DC load}
-It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:regSPV1}.
+It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:standaloneSPV} letter (b).
 Usually system with MPPT should have battery; otherwise, extra power will be waste.
 
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{regulatedSPV1.png}
-\centering
-\caption{Regulated standalone SPV system with DC load (Source: \cite{Roy})}
-\label{fig:regSPV1}
-\end{figure}
-
 \subsection{Regulated standalone system with battery and DC load}
-Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}.
+Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:standaloneSPV} letter (c).
 Battery is used to store the extra power of PV system.
@@
 Extra charging and deep discharging can reduce the battery life \cite{Kim}.
-
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{regulatedSPV2.png}
-\centering
-\caption{Regulated standalone SPV system with battery DC load (Source: \cite{Roy})}
-\label{fig:regSPV2}
-\end{figure}
 
@@
 \subsection{Regulated standalone system with battery, AC load}
-This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}.
+This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:standaloneSPV} letter (d).
 This solution has an increase of cost because has more equipments.
@@
 
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{regulatedSPV3.png}
-\centering
-\caption{Regulated standalone system with battery, AC load (Source: \cite{Roy})}
-\label{fig:regSPV3}
-\end{figure}
-
 \section{Design and Validation of a Solar photovoltaic system}
@@
 Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-In this study, the most popular tools are presented:
-
-\begin{itemize}
-\item PVWatts 
-\item SAM
-\item Homer
-\item RETScreen
-\item Hybrid2
-\end{itemize}
+In this study, the most popular tools are presented: PVWatts, SAM, Homer, RETScreen, and Hybrid2.
 
@@
 \hline
+\hline
 Support & X & X & X & X &  \\
+\hline
 Off-grid systems &   &   & X & X & X\\
+\hline
 Hybrid systems &  &  & X & X & X\\
+\hline
 Photovoltaics & X & X & X & X & X\\
+\hline
 Batteries &  &  & X & X & X\\
-Main technical (T) or economical (E) & T & T & E & E & T \\
+\hline
+\makecell{Main technical (T) \\ or economical(E)} & T & T & E & E & T \\
+\hline
 Optimization &  &  & X & X &  \\
+\hline
 Sensitive analysis &  &  & X & X & \\
@@
 After that, the potential solution is analyzed in another tool to validate or even optimize the solution.
-Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution.
+Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than the listed-more common tools.
 
@@
 \begin{figure}[h]
-\includegraphics[width=0.95\textwidth]{blockdiagramPVS}
+\includegraphics[width=0.4\textwidth]{blockdiagramPVS}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.95\textwidth]{celmodarray}
+\includegraphics[width=0.4\textwidth]{celmodarray}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.95\textwidth]{equivckt}
+\includegraphics[width=0.48\textwidth]{equivckt}
 \centering
@@
 
-\begin{equation}
+\begin{multline}
 \label{eq:2d2rmodel}
-I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-\end{equation}
+I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - \\ I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
+\end{multline}
 
@@
 
-A single-diode without series and shunt resistances is considered. Equation 1 is used to write down expressions for currents and voltages at each key point shown in Fig. \ref{fig:ivcurve}.
+A single-diode without series and shunt resistances is considered. Equation 1 is
+used to write down expressions for currents and voltages at each key point shown in
+Fig. \ref{fig:ivcurve}.
 
 \begin{figure}[h]
-\includegraphics[width=0.90\textwidth]{ivcurve}
+\includegraphics[width=0.4\textwidth]{ivcurve}
 \centering
@@
 
-Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, the voltage and the current at the maximum power point and consequently the maximum output power, are expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm} ($ P_{m}=V_{m}I_{m} $).
+Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, the voltage and the current at the maximum power point and consequently the maximum output power, are expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm}.
 These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
@@
 
-\begin{equation}
+\begin{multline}
 \label{eq:Pm}
-P_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
-\end{equation}
+P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
+\end{multline}
 
@@
 \begin{itemize}
-\item Nominal capacity ($ q_{m} $), is the number of Ampère-hours ($ Ah $) that can maximally be extracted from the battery, under predetermined discharge conditions.
+\item Nominal capacity ($ q_{m} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery, under predetermined discharge conditions.
 \item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $.
@@
 \begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{batteryckt}
+\includegraphics[width=0.4\textwidth]{batteryckt}
 \centering
@@
 
-\begin{equation}
+\begin{multline}
 \label{eq:bat_Vd}
-V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T)
-\end{equation}
+V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \\ \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T)
+\end{multline}
 
@@
 
-The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the farction of discharge, i.e., $ DOC=1-SOC $.
+The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the fraction of discharge, i.e., $ DOC=1-SOC $.
 
@@
 
-\begin{equation}
+\begin{multline}
 \label{eq:Vcbat}
-V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T)
-\end{equation}
+V_{c} = [2+0.16SOC]+ \\ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T)
+\end{multline}
 
@@
 
-\begin{equation}
+\begin{multline}
 \label{eq:Voverc}
-V_{c} = V_{g} + (V_{ec} - V_{g}) \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
-\end{equation}
-
-Where $ Ah_{restored} $ represents the Ampère-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
+V_{c} = V_{g} + (V_{ec} - V_{g}) \\ \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
+\end{multline}
+
+Where $ Ah_{restored} $ represents the Ampere-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
 
@@
 
-\begin{equation}
+\begin{multline}
 \label{eq:charge}
-SOC_{charge} = SOC_{previous} + \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
-\end{equation}
-
-\begin{equation}
+SOC_{charge} = SOC_{previous} + \\ \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
+\end{multline}
+
+\begin{multline}
 \label{eq:discharge}
-SOC_{discharge} = SOC_{previous} - \dfrac{100*I_{drained}*Num_{h}}{capacity}
-\end{equation}
+SOC_{discharge} = SOC_{previous} - \\ \dfrac{100*I_{drained}*Num_{h}}{capacity}
+\end{multline}
 
@@
 \begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{controllerover}
+\includegraphics[width=0.4\textwidth]{controllerover}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{controllerdisc}
+\includegraphics[width=0.4\textwidth]{controllerdisc}
 \centering
@@
 \hline
-(1) & \makecell{If $V > V_{max \textunderscore off}$ and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array from the system}\\
-\hline
-(2) & \makecell{If command (1) is done and $V < V_{max \textunderscore on}$} & \makecell{Reconnect PV array to the system}\\
-\hline
-(3) & \makecell{If $V < V_{min \textunderscore off}$ and $I_{load} > I_{pv}$} & \makecell{Disconnect the load from the system}\\
-\hline
-(4) & \makecell{If command (3) is done and $V > V_{min \textunderscore on}$} & \makecell{Reconnect the load to the system}\\
+(1) & \makecell{If $V > V_{max \textunderscore off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
+\hline
+(2) & \makecell{If command (1) is \\done and $V < V_{max \textunderscore on}$} & \makecell{Reconnect PV array \\to the system}\\
+\hline
+(3) & \makecell{If $V < V_{min \textunderscore off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
+\hline
+(4) & \makecell{If command (3) is \\ done and $V > V_{min \textunderscore on}$} & \makecell{Reconnect the load \\to the system}\\
 \hline
@@
 
-\begin{equation}
+\begin{multline}
 \label{eq:numberofcmin}
-number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} =  \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
-\end{equation}
+number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \\ \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
+\end{multline}
 
@@
 \end{equation}
+
+\subsection{Joint work: controller and batteries}
+When batteries are charged, they go through three main different states - bulk, absorption and float, and it is necessary to understand those three states in order to comprehend the joint work of the controller with the battery.
+With impact to the inverter and to power supplied to the house.
+
+All the explanation at this section is related to $SOC$ and to the voltage at the DC-bus (controller output, which will be bigger than $V_{system}$) where the batteries are connected, all ruled by the charge controller.
+Moreover, it is important to mention that smart chargers, the most usual nowadays, will detect voltage and resistance from the battery prior to charging.
+
+Bulk - is the first stage of charging.
+Bulk begins when the sun comes out, or other source of electrical generation is turned on.
+This stage occurs when the batteries are at a lower $SOC$, generally anything not smaller than $75\%$ to $80\%$ (defined during system sizing).
+This stage is typically where the highest voltage and current the charger is rated for will actually be used.
+The bulk stage basically allows the PV panel to put as much current into the batteries as possible.
+For a typical 12 V battery, the charging voltage going into a battery will reach 14.16 V to 14.40 V at this stage, and there is no risk of overcharging in this stage because the battery hasn't even reached full yet.
+
+Absorption - once the batteries reach the programmed absorb voltage, usually somewhere between 14.16 and 14.40 V, the batteries will go into the absorption stage.
+Typically, when a battery reaches this stage its $SOC$ is around $85-95\%$.
+During this stage, the batteries are kept at the programmed voltage, and the current going into the batteries reduces as the batteries become more full.
+The absorption stage ends after the programmed time is reached or the number of Ampere going into the battery falls below a preset number.
+The lower current going into the battery safely brings up the charge on the battery without overheating it.
+Usually, this stage takes more time than the bulk stage.
+
+Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage a 12 volt battery can hold, and begin the float stage.
+The float stage brings the battery all the way through and maintains $SOC$ at $100\%$.
+The current will also decrease to a point where it's considered just a pulse.
+It's essentially the float stage where there is charge going into the battery at all times, but only at a safe rate to ensure a full state of charge and nothing more.
+Most smart chargers do not turn off at this point, however it is completely safe to leave a battery in float mode for months to even years at a time.
+
+Battery charging technology relies on smart micro-controlled devices.
+Therefore it is extremely important, that the program settings for the charge controller or inverter/charger are correct, and the list includes the bulk and absorption values.
+This will help preserve and extend the battery life.
+There are always default settings to the equipment, set by software, however those settings are not $100\%$ correct because there are difference among models of equipment and among manufacturer's.
+The ideal is to read the data-sheet from the manufacturers and perform a manual adjust.
+
+There are the possibility to combine batteries in a bank, with parallel and series connections, all depending the sizing of the project:
+
+\begin{itemize}
+\item Batteries connected in parallel are seen by the controller as one large battery of the combined Ah capacity of all the batteries.
+For example, two 12 V and 220 Ah batteries in parallel are seen as one 12 V and 440 Ah battery;
+\item In the other hand, although the batteries connected in series are also seen as a single battery, the result is different: two 12 V and 220 Ah batteries in series are seen as one 24 V and 220 Ah battery;
+\item In addition, a mixed bank arrangement can be useful: a bank with two 12 V and 220 Ah batteries in series connected in parallel with a similar arrange will produce an equivalent battery of 24 V and 440 Ah.
+\end{itemize}
 
@@
 \item In modeling, a model (normally mathematical) of the system is created; 
-\item In specification, normally a list of properties to be satisfied by the system is stablished, i.e., the requirements, as reliability to performance for example.
+\item In specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, as reliability to performance for example.
 \item Normally is expressed in temporal logic form ($CTL$);
@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{modelcheckstruc}
+\includegraphics[width=0.4\textwidth]{modelcheckstruc}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{systemverif}
+\includegraphics[width=0.4\textwidth]{systemverif}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.9\textwidth]{ESBMCarch2}
+\includegraphics[width=0.5\textwidth]{ESBMCarch2}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{statetransition}
+\includegraphics[width=0.5\textwidth]{statetransition}
 \centering
@@
 
-Then the tool ESBMC is called to perform the verification of this code.
-The nondeterministic variables (solar irradiance, ambient temperature, state of charge of the batteries, load demand of power and the load consumption of energy) will suffer a heavy test at ESBMC runtime execution.
+Then the tool ESBMC is put to perform the verification of this code.
+The nondeterministic variables (solar irradiance, and ambient temperature by default; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code) will suffer a heavy test at ESBMC runtime execution.
 In addition, depending if one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system, is not accomplished or satisfied, the tool accuses a fail, and the diagnostic counterexample shows in which condition the fail/violation happened.
@@
 
-With this information in hand, the user or the engineer can correct his/her PV project, and run the ESBMC again to insure that the new configuration of the project will work as expected.
-
-Theorem: XXX
-
-\section{Related work}
+\subsection{The case studies and the Algorithm}
+
+At the present work, it was performed two case studies to evaluate the proposed technique: (1) one concerning a PV system (700 W, with 48h autonomy) deployed at four different houses at an indigenous community called Nova Esperan\c{c}a (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited around 1.5 h by speedboat from Manaus (Amazonas-Brazil), with each house having a different power demand (253 W, 263 W, 283 W, and 501 W); (2) and one case concerning a system deployed as an individual system at ordinary house in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W) as an alternative to pay less electric bill and as backup at night supporting 915 W of the house's load (1,200 W system, but with autonomy of just 6 h).
+
+Related to 700 W system, the sized equipment were: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W.
+
+And to the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
+
+As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).
+At both case studies, it was considered historic data from Manaus city (because the indigenous community do not have data and is not far from Manaus).
+According with X and Y, the minimum average temperature during a entire year (21 years on record) is 23$^{o}$C and the maximum average temperature is 32$^{o}$C; and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight).
+
+Another characteristic of Manaus, analyzing the data from a entire year (solar irradiance analysis), is that there is PV generation only between 8:00 h and 16:00 h every day, with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day.
+
+Therefore, in order to reduce the computational effort, caused by the state explosion inherent of the technique, the 24h-day was divided, at the tests, in 3 parts of 8 h each (8:00h-16:00h, 16:00h-24:00h, 00:00h-8:00h); and only the 8:00h-16:00h period is where there is PV generation and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
+Within this 8h-period, $G$ and $T$ are automated verified with different values, and change their value every 1 h according with the algorithm created using the technique.
+
+Concerning the unique characteristic of each one of the case studies, close related to the autonomy of the batteries, it was created different algorithms to perform the automated verification of each one.
+Algorithm 1 describes the pseudo code used to the 700 W PV system, and Algorithm 2 the 1,200 W PV system.
+
+ \begin{algorithm}
+ \caption{Algorithm for the 700 W - 48 h PV system}
+ \begin{algorithmic}[1]
+ \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+ \renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \STATE Perform project sizing validation( )
+  \IF {(FAIL validation)} 
+  \STATE exit ("Project sizing error")  
+  \ENDIF
+  \STATE $SOC \leftarrow 100\%$
+  \\
+  \COMMENT {Now the 16:00h-08:00h period just discharging batteries}
+  \STATE $SOC \leftarrow SOC - 16\,h\, discharge$
+  \\
+  \COMMENT {Now the 08:00h-16:00h automated verification}
+ \\ \textit{LOOP Process}
+  \FOR {$h = 1$ to $8$}
+  \STATE $G \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
+  \STATE $T \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
+  \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting the values of $G$}
+  \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting the values of $T$}
+  \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ 
+  \\
+  \COMMENT {Now, testing if battery is empty:}
+  \IF {($SOC \leq SOC_{limit}$)} 
+    \STATE assert (PV panel is generating energy) \COMMENT {if there is no enough solar energy generation, then FAIL}
+    \STATE $house \leftarrow energy \, from \, PV \, panels$
+    \STATE $battery \leftarrow energy \, from \, PV \, panels$ \COMMENT {bulk stage}
+    \STATE $SOC \leftarrow SOC + 1\,h\, charge$
+  \ELSIF {($PV \, Array  \geq Vbulk$)}
+  	\STATE depending on the $SOC$, decide if Battery enter in absorption or floating stage
+	\STATE adequate the voltage at the DC-bus (PV panel feed the bus)
+    \STATE $house \leftarrow energy \, from \, PV \, panels$
+    \STATE $battery \leftarrow energy \, from \, PV \, panels$ \COMMENT {bulk or floating stage}
+    \STATE $SOC \leftarrow SOC + 1\,h\, charge$
+  \ELSE
+  	\STATE Adequate the voltage at the DC-bus (battery feed the bus)
+	\STATE $house \leftarrow energy \, from \, batteries$
+    \STATE $SOC \leftarrow SOC - 1\,h\, discharge$
+    \\
+    \COMMENT {the last case: batteries are charged but the panels are not generating}	  
+  \ENDIF
+  \STATE $h \leftarrow (h+1)$
+  \ENDFOR
+  \\
+\COMMENT {now enter again at the 16:00h-08:00h period}
+  \STATE $SOC \leftarrow SOC - 16\,h\, discharge$  
+  \STATE assert ($SOC \geq SOC_{limit}$)
+  \\
+  \COMMENT {Finally, perform the same 8h \textbf{for}-LOOP as above}
+  \\
+  \COMMENT {Batteries must conclude the 48h with enough capacity}
+  \STATE assert ($SOC \geq SOC_{limit}$)    
+ \RETURN $(\,)$ 
+ \end{algorithmic} 
+ \end{algorithm}
+
+There is a premise considering each algorithm: (1) to the 48 h autonomy, is considered that at the end of the first 8h-daytime cycle will be enough to charge the batteries.
+Otherwise, could be no sense to verify the system with the batteries low and with high probability to not meet the electric demand of the house.
+Therefore, that is the start point of this algorithm, beginning at 16:00h of the day 0 with the $SOC$ of batteries in 100\%.
+And perform the automated verification until the end of 48 h of sized autonomy; (2) related to the 6 h autonomy PV system, in the other hand, is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation during the 8h-daytime (from 8:00 h to 16:00 h) and plus the next 6 h, considering that the autonomy must ensure mainly the energy from the PV system during the 16:00 h to 22 h period.
+For both algorithms, there is a array, declared at the beginning of the C code, that defines the power demand/consumption at each hour of the day (aka load curve).
+Those are the same data used during the sizing of the project and ensure to consider the total energy (per day) supplied to the house during the verification.
+
+In both cases, if the  verification founds a combination ($SOC$, $G$ and $T$) where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
+And this information can be used by the designer to evaluate if it was a project error or if it was a combination of variables from the nature that has a low probability to occur at the field, considering the intermittent characteristic of solar PV generation.
+
+ \begin{algorithm}
+ \caption{Algorithm for the 1,200 W - 6 h PV system}
+ \begin{algorithmic}[1]
+ \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+ \renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \STATE Perform project sizing validation( )
+  \IF {(FAIL validation)} 
+  \STATE exit ("Project sizing error")  
+  \ENDIF
+  \STATE $SOC \leftarrow 80\%$ \\
+  \COMMENT {First the 08:00h-16:00h automated verification}
+ \\ \textit{LOOP Process}
+  \FOR {$h = 1$ to $8$}
+  \STATE $G \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
+  \STATE $T \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
+  \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting the values of $G$}
+  \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting the values of $T$}
+  \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ 
+  \\
+  \COMMENT {Now, testing if battery is empty:}
+  \IF {($SOC \leq SOC_{limit}$)} 
+    \STATE assert (PV panel is generating energy) \COMMENT {if there is no enough solar energy generation, then FAIL}
+    \STATE $house \leftarrow energy \, from \, PV \, panels$
+    \STATE $battery \leftarrow energy \, from \, PV \, panels$ \COMMENT {bulk stage}
+    \STATE $SOC \leftarrow SOC + 1\,h\, charge$
+  \ELSIF {($PV \, Array  \geq Vbulk$)}
+  	\STATE depending on the $SOC$, decide if Battery enter in absorption or floating stage
+	\STATE adequate the voltage at the DC-bus (PV panel feed the bus)
+    \STATE $house \leftarrow energy \, from \, PV \, panels$
+    \STATE $battery \leftarrow energy \, from \, PV \, panels$ \COMMENT {bulk or floating stage}
+    \STATE $SOC \leftarrow SOC + 1\,h\, charge$
+  \ELSE
+  	\STATE Adequate the voltage at the DC-bus (battery feed the bus)
+	\STATE $house \leftarrow energy \, from \, batteries$
+    \STATE $SOC \leftarrow SOC - 1\,h\, discharge$
+    \\
+    \COMMENT {the last case: batteries are charged but the panels are not generating}	  
+  \ENDIF
+  \STATE $h \leftarrow (h+1)$
+  \ENDFOR
+  \\
+\COMMENT {now 6h autonomy from 16:00h-22:00h period}
+  \STATE $SOC \leftarrow SOC - 6\,h\, discharge$  
+  \STATE assert ($SOC \geq SOC_{limit}$)  
+ \RETURN $(\,)$ 
+ \end{algorithmic} 
+ \end{algorithm}
+
+%\subsection{Subsection Heading Here}
+%Subsection text here.
+
+% needed in second column of first page if using \IEEEpubid
+%\IEEEpubidadjcol
+
+%\subsubsection{Subsubsection Heading Here}
+%Subsubsection text here.
+
+% An example of a floating figure using the graphicx package.
+% Note that \label must occur AFTER (or within) \caption.
+% For figures, \caption should occur after the \includegraphics.
+% Note that IEEEtran v1.7 and later has special internal code that
+% is designed to preserve the operation of \label within \caption
+% even when the captionsoff option is in effect. However, because
+% of issues like this, it may be the safest practice to put all your
+% \label just after \caption rather than within \caption{}.
+%
+% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
+% option should be used if it is desired that the figures are to be
+% displayed while in draft mode.
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=2.5in]{myfigure}
+% where an .eps filename suffix will be assumed under latex, 
+% and a .pdf suffix will be assumed for pdflatex; or what has been declared
+% via \DeclareGraphicsExtensions.
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure}
+
+% Note that the IEEE typically puts floats only at the top, even when this
+% results in a large percentage of a column being occupied by floats.
+
+% An example of a double column floating figure using two subfigures.
+% (The subfig.sty package must be loaded for this to work.)
+% The subfigure \label commands are set within each subfloat command,
+% and the \label for the overall figure must come after \caption.
+% \hfil is used as a separator to get equal spacing.
+% Watch out that the combined width of all the subfigures on a 
+% line do not exceed the text width or a line break will occur.
+%
+%\begin{figure*}[!t]
+%\centering
+%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
+%\label{fig_first_case}}
+%\hfil
+%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
+%\label{fig_second_case}}
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure*}
+%
+% Note that often IEEE papers with subfigures do not employ subfigure
+% captions (using the optional argument to \subfloat[]), but instead will
+% reference/describe all of them (a), (b), etc., within the main caption.
+% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
+% labels, the optional argument to \subfloat must be present. If a
+% subcaption is not desired, just leave its contents blank,
+% e.g., \subfloat[].
+
+% An example of a floating table. Note that, for IEEE style tables, the
+% \caption command should come BEFORE the table and, given that table
+% captions serve much like titles, are usually capitalized except for words
+% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
+% and up, which are usually not capitalized unless they are the first or
+% last word of the caption. Table text will default to \footnotesize as
+% the IEEE normally uses this smaller font for tables.
+% The \label must come after \caption as always.
+%
+%\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+%\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+%\caption{An Example of a Table}
+%\label{table_example}
+%\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+%\begin{tabular}{|c||c|}
+%\hline
+%One & Two\\
+%\hline
+%Three & Four\\
+%\hline
+%\end{tabular}
+%\end{table}
+
+% Note that the IEEE does not put floats in the very first column
+% - or typically anywhere on the first page for that matter. Also,
+% in-text middle ("here") positioning is typically not used, but it
+% is allowed and encouraged for Computer Society conferences (but
+% not Computer Society journals). Most IEEE journals/conferences use
+% top floats exclusively. 
+% Note that, LaTeX2e, unlike IEEE journals/conferences, places
+% footnotes above bottom floats. This can be corrected via the
+% \fnbelowfloat command of the stfloats package.
+
+\section{Results}
+
+This section is split into two parts. The setup is described in Section \ref{sec:setup}, while Section \ref{sec:results} describes all experimental results.
+
+\subsection{Experimental setup}
+\label{sec:setup}
+All experiments were conducted on an otherwise idle Intel Core i7-6700 (8-cores), with 3.4 GHz and 16 GB of RAM, running Ubuntu 64-bits.
+
+Concerning the SMT tool, ESBMC v5.0 was used. And regarding the solver, version 4.6.0 of Z3 was used.
+
+At the terminal, the command used to perform the verification is:
+\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
+
+Where:
+
+\begin{itemize}
+\item The first three parameters, after the filename, are related to options that are usual to find bug in software, for example, like bound check to arrays, pointer check, and division by zero, but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
+\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
+\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
+There are other options, but this parameter is necessary because the complexity of the algorithms.
+The incremental SMT solving uses few RAM memory, compared with other SMT solving.
+During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
+The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
+\item And the last parameter says to the tool that the Z3 SMT solver will be used.
+\end{itemize}
+
+\subsection{Experimental results}
+\label{sec:results}
+XXX
+
+\section{Related work }
 The CBMC, it is notable its prominence through international awards received in competitions.
@@
 
-\section{Nomenclature }
-
-text here
-
-%\section{References}
-
+% if have a single appendix:
+%\appendix[Proof of the Zonklar Equations]
+% or
+%\appendix  % for no appendix heading
+% do not use \section anymore after \appendix, only \section*
+% is possibly needed
+
+% use appendices with more than one appendix
+% then use \section to start each appendix
+% you must declare a \section before using any
+% \subsection or using \label (\appendices by itself
+% starts a section numbered zero.)
+%
+
+%\appendices
+%\section{Proof of the First Zonklar Equation}
+%Appendix one text goes here.
+
+% you can choose not to have a title for an appendix
+% if you want by leaving the argument blank
+%\section{}
+%Appendix two text goes here.
+
+% use section* for acknowledgment
+\section*{Acknowledgment}
+The authors would like to thank Newton Fund (Star Energy project), Coventry University, and Sustainable Amazonas Foundation (FAS), for the financial support and for the possibility to test the designed model with real data from solar photovoltaic system, deployed in June of 2018 at a small community at Cuieira River, distant around 1.5 hour by speedboat from Manaus city.
+The authors would like to thank, as well, to FAPEAM (Amazonas State Foundation for Research Support) for the financial support to the research.
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+%\ifCLASSOPTIONcaptionsoff
+%  \newpage
+%\fi
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
 \bibliography{trindadeThesis}{}
-\bibliographystyle{ieeetr}
-%\bibliographystyle{plain}
-%\printbibliography
-
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+%\begin{thebibliography}{1}
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%\end{thebibliography}
+
+%%%%%%%%%%%%%% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+\begin{IEEEbiographynophoto}{Alessandro Trindade}
+Alessandro Bezerra Trindade received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
+Currently, he is pursuing his PhD in Informatics at the UFAM, and hold a position as Assistant Professor at the Electricity Department from the Federal University of Amazonas.
+\end{IEEEbiographynophoto}
+
+% if you will not have a photo at all:
+\begin{IEEEbiographynophoto}{Lucas Cordeiro}
+Lucas Carvalho Cordeiro received his PhD degree from the University of Southampton in 2011.
+From 2009 to 2016, he was an Adjunct Professor at the UFAM (he is currently in unpaid leave).
+Since 2018, he is a Senior Lecturer at the University of Manchester, working with the Formal Methods Group.
+\end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+%\begin{IEEEbiographynophoto}{Jane Doe}
+%Biography text here.
+%\end{IEEEbiographynophoto}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
+% that's all folks
 \end{document}

### 2018-10-05 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal files

@@
 Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to analyze, and evaluate rural electrification projects.
-This paper aims to build the framework to apply automated verification methods to mathematical models of a complete system of rural electrification with solar photovoltaic energy to validate its design from a formal verification perspective.
+This paper aims to build the framework to apply automated verification methods to mathematical models of a system of rural electrification with solar photovoltaic energy to validate its design from a formal verification perspective.
+Results show that the proposed tool can find situations where the sized solar photovoltaic system fails to met the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same fail.
+Data from practical application of solar systems prove the results obtained by the tool.
 \end{abstract}
@@
 Only a niche market a few years ago, PV are now becoming a mainstream electricity provider, changing the way the world is powered.
-Based in data from \cite{EPIA}, there was an increase of approximately 30\% from 2013 to 2014 in terms of new installations of PV.
+Based in data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV.
 The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}.
-The renewable energy leads to an advance all over the world by protecting the environment: it is clean (low greenhouse gases emissions), operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}.
+The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
+%(low greenhouse gases emissions)
+operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}.
 Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
-The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
-
-In order to validate or even simulate a potential PV solution, there are a myriad of tools.
-However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.
-
-According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
-In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
-SPV systems can be classified into grid-connected and stand-alone systems.
-At this proposal, only off-grid or stand-alone systems will be considered.
-The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
 
@@
 
-In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
+The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
+
+In order to validate or even simulate a potential PV solution, there are a myriad of tools.
+However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.
+
+%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
+In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
+SPV...
+
+%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
 According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
@@
 
-Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
+%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
+
+PV systems can be classified into grid-connected and stand-alone systems.
+At this proposal, only off-grid or stand-alone systems will be considered.
+The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
 
@@
 
-Bringing this idea to the field of solar photovoltaic systems, instead of finding a bug or a software inconsistence, the present work aim to verify a complete PV system project, informing in which condition the project do not meet user requirements or will fail.
-Among the non-deterministic variables evaluated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
+Bringing this technique to the field of solar photovoltaic systems, instead of finding a bug or a software inconsistence, the present work aim to verify a PV system project, informing in which condition the project do not meet user requirements or will fail.
+Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
 That is the main contribution of this paper.
@@
 
-The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a complete PV off-grid system, using the satisfiability modulo theories (SMT)-based verification method.
-
-To the best of our knowledge, this is the first work to use an SMT-based verification tool to solve this kind of problem.
-
-The implementation of the ideas will be done with the efficient SMT-based bounded model checker (ESBMC) tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, which permits to describe the problem as a C/C++ language code.
+%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a PV off-grid system, using the satisfiability modulo theories (SMT)-based verification method.
+
+To the best of our knowledge, this is the first work to use a
+%n SMT-based 
+verification tool to solve this kind of problem.
+
+The implementation of the
+% ideas will be 
+proposed framework is done with the efficient SMT-based bounded model checker (ESBMC) tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, which permits to describe the PV system as a C/C++ language code.
 
@@
 
-PV systems are broadly classified into three distinct types, as described by \cite{Mohanty}:
-
-\begin{itemize}
-\item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
+PV systems are broadly classified into three distinct types, as described by \cite{Mohanty}: Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, Grid-connected systems, and solar PV hybrid system, where another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
+
+As the goal of this work is just the solutions aimed to isolated/ off-grid application, therefore it is not considered the on-grid or hybrid configurations.
+
+%\begin{itemize}
+%\item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
 Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants;
-\item Grid-connected systems, where the solar PV system is connected to the grid.
+%\item Grid-connected systems, where the solar PV system is connected to the grid.
 The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards.
 Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode;
-\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
+%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
 In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
-\end{itemize}
-
-Specifically concerning isolated communities, depending on the type of load, cost, resources availability, and requirements of the load, standalone systems can be split into several categories, which are described in this section.
-As the goal of this Thesis is just the solutions aimed to isolated/ off-grid application, therefore it is not considered the on-grid or hybrid configurations.
-
-There is a resource, called maximum power point tracking (MPPT), which is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}.
-That resource is found at modern PV systems and is strongly indicated due to its advantages.
-
-\subsection{Unregulated standalone PV system with DC load }
-Usually this type of system is for low power applications, as defined by \cite{Roy}.
-The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:standaloneSPV} letter (a).
-At night hours, the system will not provide any supply because of the absence of the battery.
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{reg_unreg4.png}
-\centering
-\caption{PV standalone systems: (a) regulated standalone SPV system with DC load; (b) regulated standalone SPV system with DC load; (c) regulated standalone SPV system with battery DC load; and (d) regulated standalone system with battery and AC load  (Source: \cite{Roy})}
-\label{fig:standaloneSPV}
-\end{figure}
-
-\subsection{Regulated standalone PV system with DC load}
-It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:standaloneSPV} letter (b).
-Usually system with MPPT should have battery; otherwise, extra power will be waste.
-
-\subsection{Regulated standalone system with battery and DC load}
-Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:standaloneSPV} letter (c).
+%\end{itemize}
+
+Specifically concerning isolated communities, depending on the type of load, cost, resources availability, and requirements of the load, standalone systems can be split into several categories.
+However, the configuration that is most common nowadays related to off-grid individual system, is the regulated standalone system with battery and AC load.
+
+This configuration includes PV array, battery, MPPT and AC load.
 Battery is used to store the extra power of PV system.
@@
 Extra charging and deep discharging can reduce the battery life \cite{Kim}.
-
-According to \cite{Pinho}, PV systems that are used to feed loads with low variation on the consumption can be sized to operate without the controller.
+Because of the AC load, an inverter (DC to AC converter) is required.
+This solution has an increase of cost because has more equipment.
+However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
+
+The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}.
+%That resource is found at modern PV systems and is strongly indicated due to its advantages.
+
+%\subsection{Unregulated standalone PV system with DC load }
+%Usually this type of system is for low power applications, as defined by \cite{Roy}.
+The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:standaloneSPV} letter (a).
+At night hours, the system will not provide any supply because of the absence of the battery.
+
+%\begin{figure}[h]
+%\includegraphics[width=0.5\textwidth]{reg_unreg4.png}
+%\centering
+%\caption{PV standalone systems: (a) regulated standalone SPV system with DC load; (b) regulated standalone SPV system with DC load; (c) regulated standalone SPV system with battery DC load; and (d) regulated standalone system with battery and AC load  (Source: \cite{Roy})}
+%\label{fig:standaloneSPV}
+%\end{figure}
+
+%\subsection{Regulated standalone PV system with DC load}
+%It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:standaloneSPV} letter (b).
+Usually system with MPPT should have battery; otherwise, extra power will be waste.
+
+%\subsection{Regulated standalone system with battery and DC load}
+%Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:standaloneSPV} letter (c).
+Battery is used to store the extra power of PV system.
+A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
+Extra charging and deep discharging can reduce the battery life \cite{Kim}.
+
+%According to \cite{Pinho}, PV systems that are used to feed loads with low variation on the consumption can be sized to operate without the controller.
 That is called of self-regulated standalone PV system with battery.
@@
 
-\subsection{Regulated standalone system with battery, AC load}
-This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:standaloneSPV} letter (d).
+%\subsection{Regulated standalone system with battery and AC load}
+%This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:standaloneSPV} letter (d).
 This solution has an increase of cost because has more equipments.
 However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-That configuration is the focus of the present thesis since it is the most common nowadays all over the world, when off-grid or isolated regions is the target.
+That configuration is the focus of the present work since it is the most common nowadays all over the world, when off-grid or isolated regions is the target.
 
 \section{Design and Validation of a Solar photovoltaic system}
-The design and validation of a SPV system can be done by hand or with the aid of a software tool.
-
-In order to address different aspects of project system and systems design, there is a myriad of public domain and commercial software available for the SPV market.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
+The design and validation of a PV system can be done by hand or with the aid of a software tool.
+
+In order to address different aspects of project system and systems design, there is a myriad of public domain and commercial software available for the PV market.
+According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization).
 Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
@@
 Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-In this study, the most popular tools are presented: PVWatts, SAM, Homer, RETScreen, and Hybrid2.
-
-\subsection{PVWatts Calculator}
-According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
+In this work, were evaluated the most popular tools, as PVWatts, SAM, Homer Pro, RETScreen Expert, and Hybrid2.
+
+%\subsection{PVWatts Calculator}
+%According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
 According to \cite{NRELDobos}, to use the calculator, it is necessary to provide information about the system's location, basic design parameters, and system economics.
@@
 
-\subsection{SAM}
-SAM or System Advisor Model is a software from the U.S.
+%\subsection{SAM}
+%SAM or System Advisor Model is a software from the U.S.
 Department of Energy and National Renewable Energy Laboratory.
@@
 
-\subsection{HOMER}
-As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
+%\subsection{HOMER}
+%As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
 HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources.
@@
 
-The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
+%The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
 HOMER Pro put together three tools in one product: optimization, simulation, and sensitivity analysis.
@@
 
-\subsection{RETScreen}
-As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
-
-RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options.
+%\subsection{RETScreen}
+%As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
+
+%RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options.
 The software can be used to evaluate benefits from both clean energy production from power generation projects and savings through energy efficiency projects, accounting for project costs, greenhouse gas emission reductions, and financial risk.
@@
 
-\begin{itemize}
-\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
-\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
-\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
+%\begin{itemize}
+%\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
+%\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
+%\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
 However, this version works is only Windows-based.
 This version has a complete paid version, in an annual subscription way.
-\end{itemize}
-
-As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
+%\end{itemize}
+
+%As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
 It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
@@
 
-\subsection{Hybrid2}
-The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
+%\subsection{Hybrid2}
+%The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
 Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
@@
 
-Table \ref{table:softwares} summarizes the tools described in this paper.
-Where just Hybrid2 do not have technical support; only HOMER, RETScreen and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER and RETScreen are complete, including economical analysis or even optimization-sensitive analysis.
+Table \ref{table:softwares} summarizes the off-the-shelf tools mentioned in this paper.
+Where just Hybrid2 do not have technical support; only HOMER Pro, and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER Pro and RETScreen Expert are complete, including economical analysis or even optimization-sensitive analysis.
 However, only paid version of those softwares have all the features, and they run only at Windows-based operational systems.
+RETScreen and HOMER have a web-based version but with limited resources.
 
@@
 \hline
-Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen } & \rotatebox{90}{Hybrid2}\\
+Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER Pro} & \rotatebox{90}{RETScreen Expert} & \rotatebox{90}{Hybrid2}\\
 \hline
@@
 \hline
-Batteries &  &  & X & X & X\\
+Batteries &  &  & X &  & X\\
 \hline
@@
 Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than the listed-more common tools.
+
+The comparative between the Homer Pro and the automated verification tool is presented at the Section \ref{sec:results}.
 
@@
 
-In the literature, there are several mathematical models available for each component of stand-alone PV systems. In this section, the mathematical model for each component of PV system is presented.
+In the literature, there are several mathematical models available for each component of PV systems. In this section, the mathematical model for each component is presented.
 
@@
 To increase their utility, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module).
-For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
+
+%For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
 In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}.
@@
 An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
-The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}.
-Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
+The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}, \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}.
+
+%Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
 However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage.
@@
 This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}.
-Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig.
-\ref{fig:equivckt}.
+%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}.
 
 \begin{figure}[h]
-\includegraphics[width=0.48\textwidth]{equivckt}
+\includegraphics[width=0.30\textwidth]{equivckt1D}
 \centering
-\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
+\caption{ 1-diode equivalent PV cell/panel circuit model (Source: \cite{Cubas})}
+%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
 \label{fig:equivckt}
@@
 
-The 1-diode model, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in Equation \ref{eq:1diodemodel}.
+The 1-diode model, shown by Fig. \ref{fig:equivckt}, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in Equation \ref{eq:1diodemodel}.
 
@@
 
-The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}.
-
-\begin{equation}
-\label{eq:1d1rmodel}
-I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
-\end{equation}
-
-Where $R_{s}$ is the series resistor.
-
-At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
-
-The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}.
-
-\begin{equation}
-\label{eq:1d2rmodel}
-I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-\end{equation}
-
-Where $R_{sh}$ is the shunt resistor.
-
-At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
-
-And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}.
-
-\begin{multline}
-\label{eq:2d2rmodel}
-I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - \\ I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-\end{multline}
-
-This model has six unknown parameters with two exponential terms. 
-Briefly, both single and double diode models require the knowledge of all unknown parameters, which is usually not provided by manufacturers.
+%The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}.
+
+%\begin{equation}
+%\label{eq:1d1rmodel}
+%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
+%\end{equation}
+
+%Where $R_{s}$ is the series resistor.
+
+%At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
+
+%The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}.
+
+%\begin{equation}
+%\label{eq:1d2rmodel}
+%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
+%\end{equation}
+
+%Where $R_{sh}$ is the shunt resistor.
+
+%At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
+
+%And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}.
+
+%\begin{multline}
+%\label{eq:2d2rmodel}
+%I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - \\ %I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
+%\end{multline}
+
+%This model has six unknown parameters with two exponential terms. 
+%Briefly, both single and double diode models require the knowledge of all unknown parameters, which is usually not provided by manufacturers.
 Nevertheless, the current-voltage equation is a transcendental expression \cite{Jakhrani}.
 
-However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel.
-
-For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
+%However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel.
+
+%For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
 The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
@@
 
-Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves).
-However, the present work will rely on the simplified model of 1-diode, that was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation.
+%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
+The simplified model of 1-diode was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested.
+In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing.
 
 \subsection{Proposed PV Panel Model}
-With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1d1rmodel}.
+With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
 
@@
 \subsection{The Battery Storage Model }
-Because of the fluctuating nature of the output delivered by the PV arrays, batteries are necessary in a PV system.
+%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are necessary in a PV system.
 Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery.
@@
 
-Several models have been presented in the literature. However, regardless of the model, normally the following parameters are required:
+Several models have been presented in the literature, as shown by \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.
+However, regardless of the model, normally the following parameters are required:
 
 \begin{itemize}
-\item Nominal capacity ($ q_{m} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery, under predetermined discharge conditions.
+\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
+%, under predetermined discharge conditions.
 \item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
-Obviously $ 0<SOC<1 $.
+%Obviously $ 0<SOC<1 $. 
 If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
 \item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
-It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
+%It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
 \item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
-\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
+%\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
 \end{itemize}
 
-The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
+%The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
 The battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
 LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.
-
-In general, the battery models view the battery as a voltage source $ E $ in series with an internal resistance $ R_{0} $, as shown in Fig. \ref{fig:batteryckt}.
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{batteryckt}
-\centering
-\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
-\label{fig:batteryckt}
-\end{figure}
-
-The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.
-
-Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
-
-The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.
+%
+%In general, the battery models view the battery as a voltage source $ E $ in series with an internal resistance $ R_{0} $, as shown in Fig. \ref{fig:batteryckt}. 
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{batteryckt}
+%\centering
+%\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
+%\label{fig:batteryckt}
+%\end{figure}
+%
+%The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.  
+%
+%Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
+
+%The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.
 
@@
 
-The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
-
-\begin{equation}
-\label{eq:stor}
-Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
-\end{equation}
-
-Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
-
-As an example of this formula application, as shown by \cite{Abdulateef}, considering that an off-grid PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
-
-Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$.
+%The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
+%
+%\begin{equation}
+%\label{eq:stor}
+%Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
+%\end{equation}
+%
+%Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
+%
+%As an example of this formula application, as shown by \cite{Abdulateef}, considering that an off-grid PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
+%
+%Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$.
 Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$).
 If a single battery of 12 V and 350 Ah is considered, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
-
-At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature.
+%
+%At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature.
 The equations are used to update the $SOC$ of the batteries, and have the number of hours ($ Num_{h} $) as a variable.
 There is a factor (1.15) which is present at the charging equation, and is necessary to express that during the charging process is usual to reach 115\% of the battery capacity
-
-\begin{multline}
-\label{eq:charge}
-SOC_{charge} = SOC_{previous} + \\ \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
-\end{multline}
-
-\begin{multline}
-\label{eq:discharge}
-SOC_{discharge} = SOC_{previous} - \\ \dfrac{100*I_{drained}*Num_{h}}{capacity}
-\end{multline}
-
+%
+%\begin{multline}
+%\label{eq:charge}
+%SOC_{charge} = SOC_{previous} + \\ \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
+%\end{multline}
+
+%\begin{multline}
+%\label{eq:discharge}
+%SOC_{discharge} = SOC_{previous} - \\ \dfrac{100*I_{drained}*Num_{h}}{capacity}
+%\end{multline}
+%
+%
 Besides the model verification, there is also the prior stage of project sizing check, as did to the solar panel.
@@
 The ideal is to read the data-sheet from the manufacturers and perform a manual adjust.
-
-There are the possibility to combine batteries in a bank, with parallel and series connections, all depending the sizing of the project:
-
-\begin{itemize}
-\item Batteries connected in parallel are seen by the controller as one large battery of the combined Ah capacity of all the batteries.
+%
+%There are the possibility to combine batteries in a bank, with parallel and series connections, all depending the sizing of the project:
+%
+%\begin{itemize}
+%\item Batteries connected in parallel are seen by the controller as one large battery of the combined Ah capacity of all the batteries.
 For example, two 12 V and 220 Ah batteries in parallel are seen as one 12 V and 440 Ah battery;
-\item In the other hand, although the batteries connected in series are also seen as a single battery, the result is different: two 12 V and 220 Ah batteries in series are seen as one 24 V and 220 Ah battery;
-\item In addition, a mixed bank arrangement can be useful: a bank with two 12 V and 220 Ah batteries in series connected in parallel with a similar arrange will produce an equivalent battery of 24 V and 440 Ah.
-\end{itemize}
+%\item In the other hand, although the batteries connected in series are also seen as a single battery, the result is different: two 12 V and 220 Ah batteries in series are seen as one 24 V and 220 Ah battery;
+%\item In addition, a mixed bank arrangement can be useful: a bank with two 12 V and 220 Ah batteries in series connected in parallel with a similar arrange will produce an equivalent battery of 24 V and 440 Ah.
+%\end{itemize}
+%
 
@@
 Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled.
-Then a model checking will be performed to do a verification of the project in order to guarantee that the design of an off-grid SPV solution will meet the requirements, specifications and regulations.
+Then a model checking will be performed to do a verification of the project in order to guarantee that the design of an off-grid PV solution will meet the requirements, specifications and regulations.
 
@@
 
-The PV input data (load power demand, load consumption of energy, the PV system project data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the non-deterministic variables of the model, are all written as C Programming language code.
+The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the non-deterministic variables of the model, are all written as C Programming language code.
 
 Then the tool ESBMC is put to perform the verification of this code.
-The nondeterministic variables (solar irradiance, and ambient temperature by default; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code) will suffer a heavy test at ESBMC runtime execution.
+The non-deterministic variables (solar irradiance, and ambient temperature by default; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code) will suffer a heavy test at ESBMC run-time execution.
 In addition, depending if one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system, is not accomplished or satisfied, the tool accuses a fail, and the diagnostic counterexample shows in which condition the fail/violation happened.
@@
 Simply put, instead of the ESBMC find the defect of a software or if a hardware does not meet the some requirements (as reliability, performance, or safety), the tool will verify if the requirements of the solar PV project are met.
-Detailing the condition of violation, of not meeting the requirements, if this occurs.
+Detailing the condition of violation, i.e., the state of each variable related to the system.
 
@@
 
-Concerning the unique characteristic of each one of the case studies, close related to the autonomy of the batteries, it was created different algorithms to perform the automated verification of each one.
-Algorithm 1 describes the pseudo code used to the 700 W PV system, and Algorithm 2 the 1,200 W PV system.
+Algorithm 1 describes the pseudo code used to perform the automated verification of any PV off-grid system.
 
  \begin{algorithm}
- \caption{Algorithm for the 700 W - 48 h PV system}
+ \caption{Algorithm to perform automated verification}
  \begin{algorithmic}[1]
@@
   \ENDIF
-  \STATE $SOC \leftarrow 100\%$
-  \\
-  \COMMENT {Now the 16:00h-08:00h period just discharging batteries}
-  \STATE $SOC \leftarrow SOC - 16\,h\, discharge$
-  \\
-  \COMMENT {Now the 08:00h-16:00h automated verification}
+  \STATE $SOC \leftarrow 80\%$ \\
+  \COMMENT {First the 08:00h-16:00h of automated verification}
  \\ \textit{LOOP Process}
@@
   \ENDFOR
+ \\ \textit{Start of battery autonomy verification:}
+%%  initialization\;
+\STATE $AutonomyCount \leftarrow 1$
+ \WHILE {$AutonomyCount \leq autonomy$}
+  %%\FOR {$Autonomy = 1$ to $auton$}
+
+  \STATE $SOC \leftarrow SOC - 16\,h\, discharge$
+  \STATE $AutonomyCount \leftarrow 16$
   \\  
-\COMMENT {now enter again at the 16:00h-08:00h period}
-  \STATE $SOC \leftarrow SOC - 16\,h\, discharge$  
+    \COMMENT {autonomy of 16:00h-08:00h discharge period}
+  \\
   \STATE assert ($SOC \geq SOC_{limit}$)  
   \\
-  \COMMENT {Finally, perform the same 8h \textbf{for}-LOOP as above}
-  \\
-  \COMMENT {Batteries must conclude the 48h with enough capacity}
-  \STATE assert ($SOC \geq SOC_{limit}$)    
+  \COMMENT {Perform the 08:00h-16:00h \textbf{for}-LOOP as above}
+  %%\ENDFOR
+  \ENDWHILE
  \RETURN $(\,)$ 
@@
 
-There is a premise considering each algorithm: (1) to the 48 h autonomy, is considered that at the end of the first 8h-daytime cycle will be enough to charge the batteries.
-Otherwise, could be no sense to verify the system with the batteries low and with high probability to not meet the electric demand of the house.
-Therefore, that is the start point of this algorithm, beginning at 16:00h of the day 0 with the $SOC$ of batteries in 100\%.
-And perform the automated verification until the end of 48 h of sized autonomy; (2) related to the 6 h autonomy PV system, in the other hand, is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation during the 8h-daytime (from 8:00 h to 16:00 h) and plus the next 6 h, considering that the autonomy must ensure mainly the energy from the PV system during the 16:00 h to 22 h period.
-For both algorithms, there is a array, declared at the beginning of the C code, that defines the power demand/consumption at each hour of the day (aka load curve).
+There are two premises considering the algorithm: (1) is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation during the 8h-daytime (from 8:00 h to 16:00 h), but without to account the battery autonomy (just considering charge and discharge process based on solar irradiation, load and battery charge), but after 16:00h is done the verification for the next hours when there is not solar photovoltaic generation.
+The process goes on until to verify all the autonomy demanded from the batteries; (2) there is an array, declared at the beginning of the C code, that defines the power demand/consumption at each hour of the day (aka load curve).
 Those are the same data used during the sizing of the project and ensure to consider the total energy (per day) supplied to the house during the verification.
 
-In both cases, if the  verification founds a combination ($SOC$, $G$ and $T$) where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
+If the  verification founds a combination ($SOC$, $G$ and $T$) where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
 And this information can be used by the designer to evaluate if it was a project error or if it was a combination of variables from the nature that has a low probability to occur at the field, considering the intermittent characteristic of solar PV generation.
-
- \begin{algorithm}
- \caption{Algorithm for the 1,200 W - 6 h PV system}
- \begin{algorithmic}[1]
- \renewcommand{\algorithmicrequire}{\textbf{Input:}}
- \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE Perform project sizing validation( )
-  \IF {(FAIL validation)} 
-  \STATE exit ("Project sizing error")  
-  \ENDIF
-  \STATE $SOC \leftarrow 80\%$ \\
-  \COMMENT {First the 08:00h-16:00h automated verification}
- \\ \textit{LOOP Process}
-  \FOR {$h = 1$ to $8$}
-  \STATE $G \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
-  \STATE $T \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
-  \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting the values of $G$}
-  \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting the values of $T$}
-  \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ 
-  \\
-  \COMMENT {Now, testing if battery is empty:}
-  \IF {($SOC \leq SOC_{limit}$)} 
-    \STATE assert (PV panel is generating energy) \COMMENT {if there is no enough solar energy generation, then FAIL}
-    \STATE $house \leftarrow energy \, from \, PV \, panels$
-    \STATE $battery \leftarrow energy \, from \, PV \, panels$ \COMMENT {bulk stage}
-    \STATE $SOC \leftarrow SOC + 1\,h\, charge$
-  \ELSIF {($PV \, Array  \geq Vbulk$)}
-  	\STATE depending on the $SOC$, decide if Battery enter in absorption or floating stage
-	\STATE adequate the voltage at the DC-bus (PV panel feed the bus)
-    \STATE $house \leftarrow energy \, from \, PV \, panels$
-    \STATE $battery \leftarrow energy \, from \, PV \, panels$ \COMMENT {bulk or floating stage}
-    \STATE $SOC \leftarrow SOC + 1\,h\, charge$
-  \ELSE
-  	\STATE Adequate the voltage at the DC-bus (battery feed the bus)
-	\STATE $house \leftarrow energy \, from \, batteries$
-    \STATE $SOC \leftarrow SOC - 1\,h\, discharge$
-    \\
-    \COMMENT {the last case: batteries are charged but the panels are not generating}	  
-  \ENDIF
-  \STATE $h \leftarrow (h+1)$
-  \ENDFOR
-  \\
-\COMMENT {now 6h autonomy from 16:00h-22:00h period}
-  \STATE $SOC \leftarrow SOC - 6\,h\, discharge$  
-  \STATE assert ($SOC \geq SOC_{limit}$)  
- \RETURN $(\,)$ 
- \end{algorithmic} 
- \end{algorithm}
 
@@
 \label{sec:setup}
-All experiments were conducted on an otherwise idle Intel Core i7-6700 (8-cores), with 3.4 GHz and 16 GB of RAM, running Ubuntu 64-bits.
-
-Concerning the SMT tool, ESBMC v5.0 was used. And regarding the solver, version 4.6.0 of Z3 was used.
+All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 32 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
+
+Concerning the SMT tool, ESBMC v5.1 was used. And regarding the solver, version 4.7.1 of Z3 was used.
 
@@
 Moreover, the authors target the use of synthesis to perform the optimum sizing.
-That is an interesting issue, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a SPV system,  the idea of just to validate one given solutions is not enough.
+That is an interesting issue, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system,  the idea of just to validate one given solutions is not enough.
 Probably is more useful to design a tool which starts from a list of commercial equipments, i.e., inputs, where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs, automatically.
@@
 \section*{Acknowledgment}
-The authors would like to thank Newton Fund (Star Energy project), Coventry University, and Sustainable Amazonas Foundation (FAS), for the financial support and for the possibility to test the designed model with real data from solar photovoltaic system, deployed in June of 2018 at a small community at Cuieira River, distant around 1.5 hour by speedboat from Manaus city.
+The authors would like to thank Newton Fund (Star Energy project), Coventry University, and Sustainable Amazonas Foundation (FAS), for the financial support and for the possibility to test the framework with real data from deployed PV systems.
 The authors would like to thank, as well, to FAPEAM (Amazonas State Foundation for Research Support) for the financial support to the research.

### 2018-10-09 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal files

@@
 \IEEEPARstart{A}{ccording} to \cite{Coelho} there are presently 1.3 billion people with no access to electricity worldwide. 
-The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass.
-Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
+%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
+%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
 
@@
 Based in data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV.
-The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}.
+%The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
 The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
@@
 Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
-
-The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy.
+% 
+%The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy.
+
 Apart from PV modules; the PV systems consist of battery bank, controller, and inverter, plus the load.
@@
 Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}.
-
-The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
-
+Furthermore, there is the need for proper modeling and simulation tools for people involved in their application.
 In order to validate or even simulate a potential PV solution, there are a myriad of tools.
-However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.
-
+
+%The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
+In order to validate or even simulate a potential PV solution, there are a myriad of tools.
+%However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.  
+%
 %According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
@@
 SPV...
-
+%
 %In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
@@
 
-PV systems can be classified into grid-connected and stand-alone systems.
+%PV systems can be classified into grid-connected and stand-alone systems.
 At this proposal, only off-grid or stand-alone systems will be considered.
@@
 
-Changing the subject to the design of complex systems, more time is spent on verification than on construction, as shown in \cite{Baier}.
+Desiging any complex system, as a PV for example, more time is spent on verification than on construction, as shown in \cite{Baier}.
 Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
-Programs, and more generally computer systems, may be viewed as mathematical objects with behavior that is, in principle, well determined.
+Programs may be viewed as mathematical objects with behavior that is, in principle, well determined.
 This makes it possible to specify programs using mathematical logic, which constitutes the intended (correct) behavior.
@@
 
-This area of research is referred as formal methods as defined in \cite{Clarkeetal}. Their aim is to establish system correctness with mathematical rigor.
-
+This area of research is referred as formal methods as defined in \cite{Clarkeetal}.
+% Their aim is to establish system correctness with mathematical rigor. 
 In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of bugs in order to ensure the correctness of the system.
@@
 Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
-Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
+%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
 Algorithms can verify the system model through systematically explore all their states.
 
-Bringing this technique to the field of solar photovoltaic systems, instead of finding a bug or a software inconsistence, the present work aim to verify a PV system project, informing in which condition the project do not meet user requirements or will fail.
-Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
+%Bringing this technique to solar PV systems, i
+Instead of finding a bug or a software inconsistence, the present work aim to verify a PV system, informing in which condition the project do not meet user requirements or will fail, as shown in Fig.\ref{fig:flowchartgeneral}.
+%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
 That is the main contribution of this paper.
@@
 Electric supply can be needed either in daytime or evening time (in particular cases, in both times).
-The most basic PV system can give supply only in daytime.
+%The most basic PV system can give supply only in daytime.
 For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.
@@
 
-Specifically concerning isolated communities, depending on the type of load, cost, resources availability, and requirements of the load, standalone systems can be split into several categories.
-However, the configuration that is most common nowadays related to off-grid individual system, is the regulated standalone system with battery and AC load.
-
+Specifically concerning isolated communities, 
+% depending on the type of load, cost, resources availability, and requirements of the load, 
+standalone systems can be split into several categories.
+However, the configuration that is most common nowadays is the regulated standalone system with battery and AC load.
 This configuration includes PV array, battery, MPPT and AC load.
@@
 Because of the AC load, an inverter (DC to AC converter) is required.
-This solution has an increase of cost because has more equipment.
-However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
+%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
 
@@
 According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization).
-Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-
-Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
+%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
+%
+%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
 In this work, were evaluated the most popular tools, as PVWatts, SAM, Homer Pro, RETScreen Expert, and Hybrid2.
@@
 However, only paid version of those softwares have all the features, and they run only at Windows-based operational systems.
-RETScreen and HOMER have a web-based version but with limited resources.
+RETScreen and HOMER have a free web-based version but with limited resources.
 
@@
 \subsection{Paper Proposal x Reference Tools}
-Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER and RETScreen remain for comparative.
-All tools need some parameters inherently from manufacturer's catalog, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries.
+Considering the focus of this paper, only HOMER and RETScreen remain for comparative. All tools need some parameters inherently from manufacturer's catalog in order to size the system.
+%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
 After that, the potential solution is analyzed in another tool to validate or even optimize the solution.
@@
 \section{Component models for stand-alone PV system }
-The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load.
+%The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load. 
 The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}.
@@
 \subsection{PV generator (cell, module, array) }
-A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. In the present modeling, the focus is only on cell/module/array.
-
-The basic element of a PV System is the PV cell, also called a Solar Cell.
-A PV / Solar Cell is a semiconductor device that can convert solar energy into DC electricity.
-The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
+A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
+%In the present modeling, the focus is only on cell/module/array.
+
+The basic element of a PV system is the PV cell, also called a solar cell. A PV / solar cell is a semiconductor device that can convert solar energy into DC electricity. 
+%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
 When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}.
 If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
-
-To increase their utility, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module).
+To increase their utility, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or module).
 
@@
 The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{celmodarray}
-\centering
-\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
-\label{fig:celmodarray}
-\end{figure}
-
-The PV modules are generally rated under standard test conditions (STC), which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{celmodarray}
+%\centering
+%\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
+%\label{fig:celmodarray}
+%\end{figure}
+%
+The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
+However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
+%, which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
 The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
 However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
-
-These uncertainties lead to either over- or underestimation of energy yield from PV modules.
+%
+%These uncertainties lead to either over- or underestimation of energy yield from PV modules.
 An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
-The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}, \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}.
-
+The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
+%
 %Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
@@
 Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
-
-Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
-
-The performance of photovoltaic systems (solar cell/panels), that is, the output current/voltage curve ($I-V$ curve), is usually studied using an equivalent circuit model.
+% 
+%Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
+
+The performance of photovoltaic systems, that is, the output current/voltage curve ($I-V$ curve), is usually studied using an equivalent circuit model, as shown by \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
 This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}.
@@
 \begin{figure}[h]
-\includegraphics[width=0.30\textwidth]{equivckt1D}
+\includegraphics[width=0.20\textwidth]{equivckt1D}
 \centering
@@
 
-This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.
-
+%This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.
+%
 %The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}. 
-
+%
 %\begin{equation}
@@
 %\end{equation}
-
+%
 %Where $R_{s}$ is the series resistor.
-
+%
 %At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
-
+%
 %The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}. 
-
+%
 %\begin{equation}
@@
 %\end{equation}
-
+%
 %Where $R_{sh}$ is the shunt resistor.
-
+%
 %At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
-
+%
 %And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}. 
-
+%
 %\begin{multline}
@@
 %\end{multline}
-
+%
 %This model has six unknown parameters with two exponential terms. 
@@
 Nevertheless, the current-voltage equation is a transcendental expression \cite{Jakhrani}.
-
+%
 %However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel. 
-
+%
 %For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
@@
 
-\subsection{Proposed PV Panel Model}
-With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
-
-A single-diode without series and shunt resistances is considered. Equation 1 is
-used to write down expressions for currents and voltages at each key point shown in
-Fig. \ref{fig:ivcurve}.
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{ivcurve}
-\centering
-\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
-\label{fig:ivcurve}
-\end{figure}
+\subsection{PV Panel Model}
+%With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
+%
+%A single-diode without series and shunt resistances is considered. 
+Equation 1 is used to write down expressions for currents and voltages at each key point of characteristic curve from a PV cell.
+% shown in Fig. \ref{fig:ivcurve}.
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{ivcurve}
+%\centering
+%\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
+%\label{fig:ivcurve}
+%\end{figure}
 
@@
 Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way.
-A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}.
-These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig.
+
+%A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}. 
+%These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig.
 \ref{fig:ivcurve}, where the transition is a compromise between both behaviors.
@@
 \ref{fig:ivcurve}).
-
-Based on this, the tangent of the I-V curve can be used to evaluate the transition between current- to voltage-source controlled regions; this operation yields Equation \ref{eq:didv}.
-
-\begin{equation}
-\label{eq:didv}
-\dfrac{dI}{dV}=-\dfrac{qI_{0}}{aNk_{B}T}exp \left( \dfrac{qV}{aNk_{B}T}  \right) 
-\end{equation}
-
-The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell.
+%
+%Based on this, the tangent of the I-V curve can be used to evaluate the transition between current- to voltage-source controlled regions; this operation yields Equation \ref{eq:didv}.
+%
+%\begin{equation}
+%\label{eq:didv}
+%\dfrac{dI}{dV}=-\dfrac{qI_{0}}{aNk_{B}T}exp \left( \dfrac{qV}{aNk_{B}T}  \right) 
+%\end{equation}
+%
+%The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell.
 Therefore, the Equation \ref{eq:Vmderiv} is generated.
-
-\begin{equation}
-\label{eq:Vmderiv}
-V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
-\end{equation}
-
-It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point.
+%
+%\begin{equation}
+%\label{eq:Vmderiv}
+%V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
+%\end{equation}
+%
+%It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point.
 The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change on $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}.
-Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation 10 can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
-
-\begin{equation}
-\label{eq:dIdV_Vm}
-\dfrac{dI}{dV}\vert_{V_{m}} \cong -\dfrac{0-I_{sc}}{V_{oc}-0}=\dfrac{I_{sc}}{V_{oc}}
-\end{equation}
-
-Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, the voltage and the current at the maximum power point and consequently the maximum output power, are expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm}.
+Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation \ref{eq:Vmderiv} can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
+%
+%\begin{equation}
+%\label{eq:dIdV_Vm}
+%\dfrac{dI}{dV}\vert_{V_{m}} \cong -\dfrac{0-I_{sc}}{V_{oc}-0}=\dfrac{I_{sc}}{V_{oc}}
+%\end{equation}
+%
+%Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im},
+
+As shown by \cite{Saloux} the voltage and the current at the maximum power point and consequently the maximum output power, can be expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm}.
 These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
@@
 
-Furthermore, \cite{Villalva} have proposed a relationship, which allows the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature.
-In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
+Furthermore, \cite{Villalva} have proposed a relationship, which allows the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature (Equation \ref{eq:I0}). 
+%In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
 
@@
 Where $ V_{mref} $, $ V_{oc,ref} $, $ I_{m,ref} $, and $ I_{sc,ref} $ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers.
-
-The model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
-
-If the PV cells are in parallel, then there is a parallel array.
+The model is now completely determined.
+%; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
+%
+%If the PV cells are in parallel, then there is a parallel array.
 Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
-
-\begin{equation}
-\label{eq:Iarray}
-I_{array} = (N_{cells in parallel})(I_{one cell})
-\end{equation}
-
-Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
-
-In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
-
-\begin{equation}
-\label{eq:Varray}
-V_{array} = (N_{cells in series})(V_{one panel})
-\end{equation}
-
-Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
+%
+%\begin{equation}
+%\label{eq:Iarray}
+%I_{array} = (N_{cells in parallel})(I_{one cell})
+%\end{equation}
+%
+%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
+%
+%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
+%
+%\begin{equation}
+%\label{eq:Varray}
+%V_{array} = (N_{cells in series})(V_{one panel})
+%\end{equation}
+%
+%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
 
@@
 
-The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
+%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
 This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
-
-\begin{equation}
-\label{eq:CC10}
-\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 \Delta T)
-\end{equation}
-
-Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
+%
+%\begin{equation}
+%\label{eq:CC10}
+%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
+%\end{equation}
+%
+%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
 
@@
 
-\subsection{Controller Model}
-Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
+\subsection{Charge Controller Model}
+%Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
 However, in this study, in order to simplify, the term used is controller.
 
-The controller is a set of items (DC-DC converter, a MPPT and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+The charge controller or controller is a set of items (DC-DC converter, a MPPT and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
 According to \cite{Pinho}, controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.
-
-As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components.
+%
+%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components.
 The use of battery as a storage form implies thus the presence of a charge controller.
-
+%
 In general, there are two main operating modes for the controller: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
@@
 PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $.
-This can be done by using a switch with a hysteresis cycle, as illustrated in Fig.
-\ref{fig:controllerover}.
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{controllerover}
-\centering
-\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
-\label{fig:controllerover}
-\end{figure}
-
-To protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold i and when the current required by the load is larger than the current delivered by the PV arrays \cite{Hansen}.
-The load is reconnected to the system, when the terminal voltage is above a certain value i, using a switch with a hysteresis cycle, as shown in Fig.
-\ref{fig:controllerdisc}.
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{controllerdisc}
-\centering
-\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
-\label{fig:controllerdisc}
-\end{figure}
-
-According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.).
-
-The steps in the modeling of the controller process are summarized in Table \ref{table:controller}.
+%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{controllerover}
+%\centering
+%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
+%\label{fig:controllerover}
+%\end{figure}
+
+To protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $ V_{min \textunderscore off} $ and when the current required by the load is larger than the current delivered by the PV arrays \cite{Hansen}.
+The load is reconnected to the system, when the terminal voltage is above a certain value $ V_{min \textunderscore on} $.
+%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{controllerdisc}
+%\centering
+%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
+%\label{fig:controllerdisc}
+%\end{figure}
+%
+%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
+%
+%The steps in the modeling of the controller process are summarized in Table \ref{table:controller}.
 
@@
 
-Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the current output of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $-I_{out}$ is the output current from the converter, when all the other values are known.
-
-The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}).
-
-A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
+Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter, when all the other values are known.
+
+%The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}). 
+% 
+%A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
 In addition, there is the Cuk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.
-
-For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.
-
-\begin{equation}
-\label{eq:voutvin}
-\dfrac{V_{out}}{V_{in}} = \dfrac{D}{D-1}
-\end{equation}
-
-Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
-
-The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
-
-Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.
-
-As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
+%
+%For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.
+%
+%\begin{equation}
+%\label{eq:voutvin}
+%\dfrac{V_{out}}{V_{in}} = \dfrac{D}{D-1}
+%\end{equation}
+%
+%Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
+% 
+%The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
+%  
+%Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.
+% 
+%As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
 
@@
 
-\subsection{Joint work: controller and batteries}
-When batteries are charged, they go through three main different states - bulk, absorption and float, and it is necessary to understand those three states in order to comprehend the joint work of the controller with the battery.
-With impact to the inverter and to power supplied to the house.
-
-All the explanation at this section is related to $SOC$ and to the voltage at the DC-bus (controller output, which will be bigger than $V_{system}$) where the batteries are connected, all ruled by the charge controller.
+\subsection{Joint work: charge controller and batteries}
+When batteries are charged, they go through three main different states - bulk, absorption and float, with impact to the inverter and to power supplied to the house.
+%, and it is necessary to understand those three states in order to comprehend the joint work of the controller with the battery. With impact to the inverter and to power supplied to the house. 
+%
+%All the explanation at this section is related to $SOC$ and to the voltage at the DC-bus (controller output, which will be bigger than $V_{system}$) where the batteries are connected, all ruled by the charge controller.
 Moreover, it is important to mention that smart chargers, the most usual nowadays, will detect voltage and resistance from the battery prior to charging.
 
-Bulk - is the first stage of charging.
-Bulk begins when the sun comes out, or other source of electrical generation is turned on.
+Bulk - is the first stage of charging. Bulk begins when the sun comes out.
+%, or other source of electrical generation is turned on. 
 This stage occurs when the batteries are at a lower $SOC$, generally anything not smaller than $75\%$ to $80\%$ (defined during system sizing).
@@
 The lower current going into the battery safely brings up the charge on the battery without overheating it.
-Usually, this stage takes more time than the bulk stage.
-
-Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage a 12 volt battery can hold, and begin the float stage.
+%Usually, this stage takes more time than the bulk stage.
+
+Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage that a 12 V battery can hold, and begin the float stage.
 The float stage brings the battery all the way through and maintains $SOC$ at $100\%$.
@@
 It's essentially the float stage where there is charge going into the battery at all times, but only at a safe rate to ensure a full state of charge and nothing more.
-Most smart chargers do not turn off at this point, however it is completely safe to leave a battery in float mode for months to even years at a time.
+%Most smart chargers do not turn off at this point, however it is completely safe to leave a battery in float mode for months to even years at a time.
 
 Battery charging technology relies on smart micro-controlled devices.
-Therefore it is extremely important, that the program settings for the charge controller or inverter/charger are correct, and the list includes the bulk and absorption values.
-This will help preserve and extend the battery life.
+Therefore it is extremely important that the program settings for the charge controller or inverter/charger are correct, and the list includes the bulk and absorption values.
+%This will help preserve and extend the battery life.
 There are always default settings to the equipment, set by software, however those settings are not $100\%$ correct because there are difference among models of equipment and among manufacturer's.
@@
 %
-
 \subsection{The inverter model}
 As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. 
-An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output.
+%An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
 The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage (127 V or 220 V, for example), and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency \cite{Hansen}.
@@
 
-Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
-
+%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
+%
 The sizing project check of the inverter is done through three Equations.
@@
 
-\section{Automated verification }
-It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.
+\section{Automated verification}
+%It is necessary to keep in mind that 
+Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.
 
 If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, resulting in a process known as formal verification.
-Verification may form part of a validation process, but in general, validation cannot be formalized because it relates a system design to intent.
+Verification may form part of a validation process.
+%, but in general, validation cannot be formalized because it relates a system design to intent.
 
@@
 
-Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
+%Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
 However, there is a main disadvantage of model checking: the state explosion problem.
@@
 
-Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study.
-
+%Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study. 
+%
 The Fig. \ref{fig:systemverif} shows the process to convert a real system to a model in order to be verified by a model checking.
@@
 
-In order to solve the problem of state explosion, many different techniques were developed at the last decades. One of the promising is the Bounded Model Checking (BMC).
-
+In order to solve the problem of state explosion, many different techniques were developed at the last decades.
+One of the promising is the Bounded Model Checking (BMC).
 BMC is a method that checks the model up to a given path in the path length.
-BMC algorithms traverses a finite state machine for a fixed number of steps, , and checks whether violation occurs with this bound.
-It uses fast SAT solvers, where SAT means satisfiability.
+BMC algorithms traverses a finite state machine for a fixed number of steps, $ k $, and checks whether violation occurs with this bound.
+It uses SAT solvers, where SAT means satisfiability.
 SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression.
-SAT solvers are used in BMC, such that if there are some Boolean function, the solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
+%SAT solvers are used in BMC, such that i
+%If there are some Boolean function, t
+The solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
 If SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
@@
 ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.
-The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
+%The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
+ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
 
@@
 SSA form enables the simplification of algorithms and reduction of computational complexity, where each variable is a target of exactly one assignment statement in the program text.
-
-During the symbolic execution, ESBMC aggressively tries to simplify the program \cite{Ramalho}; it propagates all constants and solves any assertions that can be statically determined.
+%
+%During the symbolic execution, ESBMC aggressively tries to simplify the program \cite{Ramalho}; it propagates all constants and solves any assertions that can be statically determined.
 This is an important step for the verification, since ESBMC can fully verify programs without calling a solver, if the inputs are deterministic.
@@
 Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied.
-If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is found to be unsatisfiable, there are no errors up to the unwinding bound , and this result is presented.
-
-ESBMC can be invoked through the command-line interface or configured through the Eclipse plug-in. Specific problems and the solver can be selected that way.
-
-ESBMC aims to support all of ISO/IEC 9899:1999 C programming language standard, and detects errors in software by simulating a finite prefix of the program execution with all possible inputs.
+If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is found to be unsatisfiable, there are no errors up to the unwinding bound, and this result is presented.
+
+%ESBMC can be invoked through the command-line interface or configured through the Eclipse plug-in. Specific problems and the solver can be selected that way. 
+%
+%ESBMC aims to support all of ISO/IEC 9899:1999 C programming language standard, and detects errors in software by simulating a finite prefix of the program execution with all possible inputs.
 Classes of problems that can be detected include: user specified assertion failures, out of bounds array access, illegal pointer dereferences, double-free of malloc'd memory, misaligned memory access; integer overflows, divide by zero, memory leaks, concurrent software, deadlock, and data races (i.e.
@@
 
-\subsection{Cyber-physical systems x Energy x ESBMC}
-According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes.
+%\subsection{Cyber-physical systems x Energy x ESBMC}
+%According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes.
 Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa.
@@
 CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole.
-
-Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}.
+%
+%Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}.
 For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies.
 Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation).
-
-Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled.
+%
+%Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled.
 Then a model checking will be performed to do a verification of the project in order to guarantee that the design of an off-grid PV solution will meet the requirements, specifications and regulations.
-
-As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification.
+%
+%As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification.
 Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver.
 This work tracks the same path.
-
+%
 \section{Methodology }
@@
 
-It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.
-
+%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.
+%
 The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the non-deterministic variables of the model, are all written as C Programming language code.
 
-Then the tool ESBMC is put to perform the verification of this code.
-The non-deterministic variables (solar irradiance, and ambient temperature by default; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code) will suffer a heavy test at ESBMC run-time execution.
+The non-deterministic variables (solar irradiance, and ambient temperature by default) will suffer a heavy test at ESBMC run-time execution.
 In addition, depending if one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system, is not accomplished or satisfied, the tool accuses a fail, and the diagnostic counterexample shows in which condition the fail/violation happened.
-
-Simply put, instead of the ESBMC find the defect of a software or if a hardware does not meet the some requirements (as reliability, performance, or safety), the tool will verify if the requirements of the solar PV project are met.
+%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
+% (as reliability, performance, or safety)
+
+Simply put, instead of the ESBMC find the defect of a software or if a hardware does not meet the some requirements, the tool will verify if the requirements of the solar PV project are met.
 Detailing the condition of violation, i.e., the state of each variable related to the system.
@@
 
-At the present work, it was performed two case studies to evaluate the proposed technique: (1) one concerning a PV system (700 W, with 48h autonomy) deployed at four different houses at an indigenous community called Nova Esperan\c{c}a (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited around 1.5 h by speedboat from Manaus (Amazonas-Brazil), with each house having a different power demand (253 W, 263 W, 283 W, and 501 W); (2) and one case concerning a system deployed as an individual system at ordinary house in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W) as an alternative to pay less electric bill and as backup at night supporting 915 W of the house's load (1,200 W system, but with autonomy of just 6 h).
-
-Related to 700 W system, the sized equipment were: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W.
-
-And to the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
-
-As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).
+At the present work, it was performed two case studies to evaluate the proposed technique: (1) one concerning a PV system (700 W, with 48h autonomy) deployed at four different houses at an indigenous community called Nova Esperan\c{c}a (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited around 1.5 h by speedboat from Manaus (Amazonas-Brazil), with each house having a different power demand (253 W, 263 W, 283 W, and 501 W); (2) and one case concerning a system deployed as an individual system at ordinary house in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W) as an alternative to pay less electric bill, supporting 915 W of the house's load (1,200 W system, but with autonomy of just 6 h).
+%and as backup at night
+
+The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W.
+
+And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
+
+%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude). 
 At both case studies, it was considered historic data from Manaus city (because the indigenous community do not have data and is not far from Manaus).
-According with X and Y, the minimum average temperature during a entire year (21 years on record) is 23$^{o}$C and the maximum average temperature is 32$^{o}$C; and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight).
-
-Another characteristic of Manaus, analyzing the data from a entire year (solar irradiance analysis), is that there is PV generation only between 8:00 h and 16:00 h every day, with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day.
-
-Therefore, in order to reduce the computational effort, caused by the state explosion inherent of the technique, the 24h-day was divided, at the tests, in 3 parts of 8 h each (8:00h-16:00h, 16:00h-24:00h, 00:00h-8:00h); and only the 8:00h-16:00h period is where there is PV generation and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
+According with X and Y, the minimum average temperature ($T$) during a entire year (21 years on record) is 23$^{o}$C and the maximum average temperature is 32$^{o}$C; and irradiance ($G$)varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight.
+%and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight).
+
+Another characteristic of Manaus, is that the PV generation can be despised from 16h to the 8h of the next day, independent of the season.
+%there is PV generation only between 8:00 h and 16:00 h every day, 
+%with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day.
+
+Therefore, in order to reduce the computational effort,
+% caused by the state explosion inherent of the technique, 
+the 24h-day was divided, at the algorithms, in 3 parts of 8 h each (8:00h-16:00h, 16:00h-24:00h, 00:00h-8:00h); and only the 8:00h-16:00h period is where there is PV generation.]
+% and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
 Within this 8h-period, $G$ and $T$ are automated verified with different values, and change their value every 1 h according with the algorithm created using the technique.
@@
 
-There are two premises considering the algorithm: (1) is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation during the 8h-daytime (from 8:00 h to 16:00 h), but without to account the battery autonomy (just considering charge and discharge process based on solar irradiation, load and battery charge), but after 16:00h is done the verification for the next hours when there is not solar photovoltaic generation.
+There are two premises considering the algorithm: (1) is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation from 8:00 h to 16:00 h, but without to account the battery autonomy (just considering charge and discharge process based on solar irradiation, load and battery charge), but after 16:00h is started the verification for the next hours when there is not solar photovoltaic generation.
 The process goes on until to verify all the autonomy demanded from the batteries; (2) there is an array, declared at the beginning of the C code, that defines the power demand/consumption at each hour of the day (aka load curve).
@@
 If the  verification founds a combination ($SOC$, $G$ and $T$) where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
-And this information can be used by the designer to evaluate if it was a project error or if it was a combination of variables from the nature that has a low probability to occur at the field, considering the intermittent characteristic of solar PV generation.
+And this information can be used by the designer to evaluate the designed system.
+%if it was a project error or if it was a combination of variables from the nature that has a low probability to occur at the field, considering the intermittent characteristic of solar PV generation.
 
@@
 \begin{itemize}
-\item The first three parameters, after the filename, are related to options that are usual to find bug in software, for example, like bound check to arrays, pointer check, and division by zero, but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
+\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
+but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
 \item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
@@
 The incremental SMT solving uses few RAM memory, compared with other SMT solving.
-During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
+%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
 The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
@@
 \section{Related work }
-The CBMC, it is notable its prominence through international awards received in competitions.
+%The CBMC, it is notable its prominence through international awards received in competitions. 
 In the works related to the CBMC, much of the research is focused on the improvement of the tool (as software and hardware verifier) and its performance in the competitions, without addressing, however, the question of PV system validation, as can be seen in \cite{Kroening}.
-For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.
-
-ESBMC was developed to perform bounded model checks on both sequential and concurrent programs using a range of SMT solvers, and has a proven track of bug finding in real-world applications \cite{Cordeiro}, \cite{Ramalho}.
+% For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.
+
+%ESBMC was developed to perform bounded model checks on both sequential and concurrent programs using a range of SMT solvers, and has a proven track of bug finding in real-world applications \cite{Cordeiro}, \cite{Ramalho}.
 The tool also implements a technique to prove the correctness of (some) unbounded programs, the k-induction algorithm; this approach has been applied to a large number of benchmarks and has produced more correct results than similar competing tools \cite{GadelhaSBMF}, \cite{GadelhaK}.
-\cite{Trindade} show that is possible to perform the partitioning of hardware-software (optimization) using ESBMC as well.
+Related to ESBMC, \cite{Trindade} show that is possible to perform the partitioning of hardware-software (optimization) using ESBMC.
 \cite{Bessa} show that is possible to use ESBMC to check the stability of digital control systems with uncertainty.
@@
 
-Concerning modeling and simulation of electrical energy systems, \cite{Kremers} used an agent-base model approach to evaluate the effect of loads (refrigerators mainly), shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study.
+Concerning modeling and simulation of electrical energy systems, \cite{Kremers} used an agent-base model approach to evaluate the effect of loads, shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study.
 However, that is a software development approach for the simulation of complex systems, without the formalism of automated verification.
@@
 In the other hand, the use of formal verification related to modeling and validation or even simulation of power systems or power networks is a young theme of research.
-According \cite{Abateetal2014}, where articles from seminars were issued at this thematic, the actual focus is on optimization and control of microgrids, HVAC systems (diagnostics and maintenance), models of generic wind turbine generation, modeling of transmission networks, and verification of smart grids.
+% According \cite{Abateetal2014}, where articles from seminars were issued at this thematic, the actual focus is on optimization and control of microgrids, HVAC systems (diagnostics and maintenance), models of generic wind turbine generation, modeling of transmission networks, and verification of smart grids.
 In addition, according with \cite{Abate2017}, recent research has attempted to formalize and implement a formal study of large population of PV panels (very common in European Union).
 The focus have been the modeling of the dynamics of PV panels and their interaction with the power grid.
-Those models do not use battery array, for example.
-
-Therefore, the present work unites the versatility and power of the formal models, applied to a formal verification tool, with individual PV systems (off-grid), which is the most indicated and common option to solve the problem of energy in developing countries.
+Those models do not use battery array, which is demanding in isolated off-grid places.
+%
+%Therefore, the present work unites the versatility and power of the formal models, applied to a formal verification tool, with individual PV systems (off-grid), which is the most indicated and common option to solve the problem of energy in developing countries.
 Especially those that have isolated communities, either for long distances of the great centers, or for being riverside.
@@
 \section{Conclusions and Future Work}
-The proposed framework seems to be a coherent and promising tool to perform verification of a PV project.
+%The proposed framework seems to be a coherent and promising tool to perform verification of a PV project.
 The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field.
@@
 The framework presented here establishes the automated verification and the project sizing check.
+Is was shown that, beside the time-consuming issue of the tool, it overcomes the results of off-the-shelf tools that only simulate the results.
+The tool was successful in found sizing errors of PV systems and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
+
 However, it is possible to perform the optimum sizing of the PV system.
 Moreover, the authors target the use of synthesis to perform the optimum sizing.
-That is an interesting issue, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system,  the idea of just to validate one given solutions is not enough.
-Probably is more useful to design a tool which starts from a list of commercial equipments, i.e., inputs, where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs, automatically.
+That is an interesting issue, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system.
+The future target is to design a tool which starts from a list of commercial equipment, i.e., inputs, where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs, automatically.
 This is what a Counterexample Guided-Inductive Synthesis (CEGIS) does.
@@
 
-Plus (need to think about it): verification in every-hour of a 48h cycle?, PV model math model can be improved, charge/discharge of batteries can be improved (is a simplified model), house's power consumption is not flat or constant, the dweller can buy more home appliances, synthesis need a data base of components, to test peak (surge) consumption (above the nominal), additional models for on-grid/off-grid farm, hybrid, and on-grid with batteries).
+%Plus (need to think about it): verification in every-hour of a 48h cycle?, PV model math model can be improved, charge/discharge of batteries can be improved (is a simplified model), house's power consumption is not flat or constant, the dweller can buy more home appliances, synthesis need a data base of components, to test peak (surge) consumption (above the nominal), additional models for on-grid/off-grid farm, hybrid, and on-grid with batteries).
 
@@
 The authors would like to thank Newton Fund (Star Energy project), Coventry University, and Sustainable Amazonas Foundation (FAS), for the financial support and for the possibility to test the framework with real data from deployed PV systems.
-The authors would like to thank, as well, to FAPEAM (Amazonas State Foundation for Research Support) for the financial support to the research.
+The authors would like to thank, as well, to FAPEAM (Amazonas State Foundation for Research Support) for the financial support.
 

### 2018-10-10 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal files

@@
 %Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
-
-Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV).
-Only a niche market a few years ago, PV are now becoming a mainstream electricity provider, changing the way the world is powered.
+%
+%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
+Only a niche market a few years ago, solar photovoltaic (PV) are now becoming a mainstream electricity provider.
+% changing the way the world is powered. 
 Based in data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
 %The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
-The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
+%The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
 %(low greenhouse gases emissions)
-operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}.
-Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
+%operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}. 
+%Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
 % 
@@
 
-Apart from PV modules; the PV systems consist of battery bank, controller, and inverter, plus the load.
-Moreover, the optimum sizing of these devices is important for reliable operation.
-Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}.
-Furthermore, there is the need for proper modeling and simulation tools for people involved in their application.
-In order to validate or even simulate a potential PV solution, there are a myriad of tools.
+%Apart from PV modules; the 
+%PV systems consist of PV modules, battery bank, controller, and inverter, plus the load. %Moreover, the optimum sizing of these devices is important for reliable operation.
+%Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}.
+%Furthermore, there is the need for proper modeling and simulation tools for people involved in their application.
+In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market.
 
@@
 
-Desiging any complex system, as a PV for example, more time is spent on verification than on construction, as shown in \cite{Baier}.
+Desiging any complex system, as a PV, more time is spent on verification than on construction, as shown in \cite{Baier}.
 Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
-Programs may be viewed as mathematical objects with behavior that is, in principle, well determined.
-This makes it possible to specify programs using mathematical logic, which constitutes the intended (correct) behavior.
-Then, one can try to give a formal proof or otherwise establish that the program meets its specification, as defined by \cite{Trindade}.
-
-This area of research is referred as formal methods as defined in \cite{Clarkeetal}.
+Programs may be viewed as mathematical objects.
+%with behavior that is, in principle, well determined. 
+ This makes it possible to specify systems as programs using mathematical logic, which constitutes the intended (correct) behavior.
+Then, one can try to give a formal proof or otherwise establish that the program meets its specification.%, as defined by \cite{Trindade}.
+
+This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
 % Their aim is to establish system correctness with mathematical rigor. 
-In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of bugs in order to ensure the correctness of the system.
+In the recent decades, research in formal methods has led to the development of very promising verification techniques.
+% that facilitate the early detection of bugs in order to ensure the correctness of the system.
 
@@
 %Bringing this technique to solar PV systems, i
-Instead of finding a bug or a software inconsistence, the present work aim to verify a PV system, informing in which condition the project do not meet user requirements or will fail, as shown in Fig.\ref{fig:flowchartgeneral}.
+%Instead of finding a bug or a software inconsistence, t
+The present work aim to verify a PV system, informing in which condition the project do not meet user requirements or will fail, as shown in Fig.\ref{fig:flowchartgeneral}. 
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
@@
 
-The remainder of this paper is organized as follows: Sect.
-2 gives a background of solar PV systems.
-Section 3 describes the design and validation of a solar PV system.
-Section 4 describes the formal mathematical modeling of a generic PV system.
-Section 5 presents the automated verification theory, including details of the ESBMC process.
-The methodology is presented at Section 6.
-Section 7 discusses the related work.
-Section 8 presents the conclusion and describes future work.
-At the end of the paper, there is a list of all nomenclatures used at the text.
+The remainder of this paper is organized as follows: Section II gives the background.
+Section III describes the design and validation of PV system.
+Section IV describes the mathematical modeling.
+Section V presents the automated verification.
+The methodology is presented at section VI.
+Section VII is devoted to the results, and section VIII to the related work.
+Section IX presents the conclusion and describes future work.
 
@@
 This load can be either Alternate Current (AC) type or Direct Current (DC) type.
-Electric supply can be needed either in daytime or evening time (in particular cases, in both times).
-%The most basic PV system can give supply only in daytime.
-For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.
-
-PV systems are broadly classified into three distinct types, as described by \cite{Mohanty}: Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, Grid-connected systems, and solar PV hybrid system, where another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
-
-As the goal of this work is just the solutions aimed to isolated/ off-grid application, therefore it is not considered the on-grid or hybrid configurations.
-
+Electric supply can be needed either in daytime or evening time.
+%(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
+For night hours or rainy days, one needed to have batteries, where power can be stored and used.% \cite{Gules}.
+
+PV systems are broadly classified into three distinct types, as described by \cite{Mohanty}: (1) standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system, where another source(s) of energy can work together with the solar PV.
+% system to provide the required demand.
+%, such as wind, biomass or diesel, 
+%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
+%
 %\begin{itemize}
@@
 Specifically concerning isolated communities, 
+%standalone systems are one the most used solutions, and 
 % depending on the type of load, cost, resources availability, and requirements of the load, 
-standalone systems can be split into several categories.
-However, the configuration that is most common nowadays is the regulated standalone system with battery and AC load.
-This configuration includes PV array, battery, MPPT and AC load.
+%standalone systems 
+%can be split into several categories. However, 
+the configuration that is most common nowadays is the regulated standalone system with battery and AC load. This configuration includes PV array, batteries, charge controller, inverter, and AC load.
+%PV array, battery, MPPT and AC load.
 Battery is used to store the extra power of PV system.
@@
 %This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-
-The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}.
-%That resource is found at modern PV systems and is strongly indicated due to its advantages.
+%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
+%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.
 
@@
 \section{Design and Validation of a Solar photovoltaic system}
-The design and validation of a PV system can be done by hand or with the aid of a software tool.
-
-In order to address different aspects of project system and systems design, there is a myriad of public domain and commercial software available for the PV market.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization).
+%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
+%
+In order to address different aspects of project system and systems design, there is a myriad of tools. 
+%public domain and commercial software available for the PV market. 
+%According to \cite{Brooks}, t
+The capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization). 
 %Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
@@
 Table \ref{table:softwares} summarizes the off-the-shelf tools mentioned in this paper.
-Where just Hybrid2 do not have technical support; only HOMER Pro, and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER Pro and RETScreen Expert are complete, including economical analysis or even optimization-sensitive analysis.
-However, only paid version of those softwares have all the features, and they run only at Windows-based operational systems.
+Where just Hybrid2 do not have technical support; only HOMER Pro, and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis.
+However, only paid version of those softwares have all the features, and they run only at Windows operational systems.
 RETScreen and HOMER have a free web-based version but with limited resources.
@@
 \subsection{PV generator (cell, module, array) }
-A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
+%A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
 %In the present modeling, the focus is only on cell/module/array.
-
-The basic element of a PV system is the PV cell, also called a solar cell. A PV / solar cell is a semiconductor device that can convert solar energy into DC electricity. 
+%
+The basic element of a PV system is the PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
 %The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
@@
 If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
-To increase their utility, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or module).
+To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
+package called panel or module.
 
@@
 %
-The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
-However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
+The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on meteorological conditions.
+%the meteorological conditions of the area to be serviced by PV solution. %However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
 %, which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
@@
 The 1-diode model, shown by Fig. \ref{fig:equivckt}, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in Equation \ref{eq:1diodemodel}. 
-
 \begin{equation}
@@
 \item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
-\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed;
-	\begin{itemize}
-	\item $ N=1 $ in a single cell configuration. 	
-	\end{itemize}	  
-\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; 
-	\begin{itemize}
-	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
-	\end{itemize}
+\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed; $ N=1 $ in a single cell configuration.
+%	\begin{itemize}
+%	\item $ N=1 $ in a single cell configuration. 	
+%	\end{itemize}	  
+\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes.
+%	\begin{itemize}
+%	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
+%	\end{itemize}
 \item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
@@
 Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
-
 \begin{equation}
@@
 As shown by \cite{Saloux} the voltage and the current at the maximum power point and consequently the maximum output power, can be expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm}.
-These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
-
+%These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
 \begin{equation}
@@
 Therefore, Equation \ref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.
-
 \begin{equation}
@@
 
-In Equation \ref{eq:Iph}, $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at (STC or standard test conditions) reference conditions (provided by PV manufacturers).
+In Equation \ref{eq:Iph}, $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at reference conditions (provided by PV manufacturers).
 $ I_{ph,ref} $ can also be approximated to the reference short-circuit current that is provided by PV manufacturers ($ I_{sc,ref} $) as shown by \cite{Jakhrani}.
@@
 The cell temperature ($ T $) can be obtained from \cite{Ross} and is shown in Equation \ref{eq:Tcell}.
-
 \begin{equation}
@@
 
-The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state.
-Using the maximum power point current equation (Equation \ref{eq:Pm}) and the saturation current in the reference temperature given by Equation \ref{eq:I0}, the diode quality coefficient is determined by Equation \ref{eq:a}.
-
+%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
+Using the maximum power point current equation (Equation \ref{eq:Pm}) and the saturation current in the reference temperature given by Equation \ref{eq:I0}, the diode quality (or ideality) coefficient is determined by Equation \ref{eq:a}.
 \begin{equation}
@@
 Where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
-
 \begin{equation}
@@
 The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by Equation \ref{eq:NTPmin}, and the check is done with the Equation \ref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from Equation \ref{eq:NTPmin}.
-
 \begin{equation}
@@
 $ V_{system} $ is the DC voltage of the bus, and is a design decision (normally 12, 24 or 48 V).
-
 \begin{equation}
@@
 
-Several models have been presented in the literature, as shown by \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.
+Several models have been presented in the literature, as shown by \cite{Copetti}, and \cite{Manwell93}.
+%, and \cite{Manwell94}. 
 However, regardless of the model, normally the following parameters are required:
@@
 If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
-\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
+%\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
 %It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
@@
 %Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
-
+%
 %The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.  
-
-The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
+%
+%The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
 However, it uses some data extracted from tested batteries in laboratory.
 Therefore is not suitable to this study.
-
+%
 Most of the created models were used to simulate and optimize PV storage system based on lead-acid batteries.
@@
 The discharge voltage equation is shown in Equation \ref{eq:bat_Vd}. 
-The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
-
+%The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
+%
 \begin{multline}
@@
 
-Where $ C_{10} $ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $ \Delta T $ is temperature variation ($ \Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $, $ SOC $ indicates how much electric charge is stored in the cell at given time, defined by Equation \ref{eq:SOCbat}.
-
-\begin{equation}
-\label{eq:SOCbat}
-SOC = \left( 1 - \dfrac{Q}{C} \right) 
-\end{equation}
-
-Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
-
-The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the fraction of discharge, i.e., $ DOC=1-SOC $.
+Where $ C_{10} $ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $ \Delta T $ is temperature variation ($ \Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $).
+%, $ SOC $ indicates how much electric charge is stored in the cell at given time, defined by Equation \ref{eq:SOCbat}.
+%\begin{equation}
+%\label{eq:SOCbat}
+%SOC = \left( 1 - \dfrac{Q}{C} \right) 
+%\end{equation}
+%
+%Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
+%
+%The ratio between $ Q $ and $ C $ represents t
+
+The depth of discharge ($ DOD $) or the fraction of discharge, is $ DOC=1-SOC $.
 
@@
 For the charging process, however, the parameters are presented in Equation \ref{eq:Vcbat}.
-
+%
 \begin{multline}
@@
 SOC can be calculated easily at any point during the discharge period; however, during recharge it is much more difficult \cite{Copetti}.
-
-Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell.
+%Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell.
 The efficiency drops to zero at full charge and the function that represents the charge efficiency ($ \eta_{c} $) variation with state of charge and current rate is given in Equation \ref{eq:efficcharge}.
-
-\begin{equation}
-\label{eq:efficcharge}
-\eta_{c} = 1 - exp \left[ \dfrac{20.73}{\dfrac{I}{I_{10}}+0.55} (SOC-1) \right] 
-\end{equation}
-
-\cite{Copetti} show that, during overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (Equation \ref{eq:Vec}).
+%\begin{equation}
+%\label{eq:efficcharge}
+%\eta_{c} = 1 - exp \left[ \dfrac{20.73}{\dfrac{I}{I_{10}}+0.55} (SOC-1) \right] 
+%\end{equation}
+%
+%\cite{Copetti} show that, 
+During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (Equation \ref{eq:Vec}).
 It was created a function for the gassing voltage as well, as shown in Equation \ref{eq:Vg}.
 In addition, the overcharge phenomenon can be represented by Equation \ref{eq:Voverc}.
-
 \begin{equation}
@@
 The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by Equation \ref{eq:tau}.
-
 \begin{equation}
@@
 First is necessary to define the total capacity of the battery bank, as shown by Equation \ref{eq:Cbank}.
-
 \begin{equation}
@@
 Moreover, the Equation \ref{eq:batcheck} perform the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that were established to the project.
-
 \begin{equation}
@@
 
-The charge controller or controller is a set of items (DC-DC converter, a MPPT and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power.
 According to \cite{Pinho}, controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.
+%
+%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
+%
 %
@@
 The output power ($ P_{out} $) of DC-DC converter is given by Equation \ref{eq:poutcont}.
-
 \begin{equation}
@@
 Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Equation \ref{eq:poutcont} is possible to reach Equation \ref{eq:potcont}.
-
 \begin{equation}
@@
 Initially the controller must meet the voltage requirement of the PV system, as shown by Equation \ref{eq:vcvsystem}.
-
 \begin{equation}
@@
 Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as shown by Equation \ref{eq:iscamb}.
-
 \begin{equation}
@@
 The controller must meet the maximum current from the PV array (Equations \ref{eq:icmin} and \ref{eq:icicmin}).
-
 \begin{equation}
@@
 In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
-
 \begin{multline}
@@
 
-\subsection{Joint work: charge controller and batteries}
-When batteries are charged, they go through three main different states - bulk, absorption and float, with impact to the inverter and to power supplied to the house.
+%\subsection{Joint work: charge controller and batteries}
+%When batteries are charged, they go through three main different states - bulk, absorption and float, with impact to the inverter and to power supplied to the house.
 %, and it is necessary to understand those three states in order to comprehend the joint work of the controller with the battery. With impact to the inverter and to power supplied to the house. 
@@
 Moreover, it is important to mention that smart chargers, the most usual nowadays, will detect voltage and resistance from the battery prior to charging.
-
-Bulk - is the first stage of charging. Bulk begins when the sun comes out.
+%
+%Bulk - is the first stage of charging. Bulk begins when the sun comes out.
 %, or other source of electrical generation is turned on. 
-This stage occurs when the batteries are at a lower $SOC$, generally anything not smaller than $75\%$ to $80\%$ (defined during system sizing).
+%This stage occurs when the batteries are at a lower $SOC$, generally anything not smaller than $75\%$ to $80\%$ (defined during system sizing).
 This stage is typically where the highest voltage and current the charger is rated for will actually be used.
@@
 For a typical 12 V battery, the charging voltage going into a battery will reach 14.16 V to 14.40 V at this stage, and there is no risk of overcharging in this stage because the battery hasn't even reached full yet.
-
-Absorption - once the batteries reach the programmed absorb voltage, usually somewhere between 14.16 and 14.40 V, the batteries will go into the absorption stage.
+%
+%Absorption - once the batteries reach the programmed absorb voltage, usually somewhere between 14.16 and 14.40 V, the batteries will go into the absorption stage.
 Typically, when a battery reaches this stage its $SOC$ is around $85-95\%$.
@@
 %Usually, this stage takes more time than the bulk stage.
-
-Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage that a 12 V battery can hold, and begin the float stage.
+%
+%Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage that a 12 V battery can hold, and begin the float stage.
 The float stage brings the battery all the way through and maintains $SOC$ at $100\%$.
@@
 %Most smart chargers do not turn off at this point, however it is completely safe to leave a battery in float mode for months to even years at a time.
-
-Battery charging technology relies on smart micro-controlled devices.
+%
+%Battery charging technology relies on smart micro-controlled devices.
 Therefore it is extremely important that the program settings for the charge controller or inverter/charger are correct, and the list includes the bulk and absorption values.
@@
 \subsection{The inverter model}
-As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. 
+%As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. 
 %An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
@@
 The inverter is characterized by a power dependent efficiency $ \eta_{i} $ given by \cite{Hansen} as shown by Equation \ref{eq:efficinv}.
-
 \begin{equation}
@@
 Moreover, Equation \ref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
-
 \begin{equation}
@@
 \section{Methodology }
-
-Fig. \ref{fig:statetransition} shows the state diagram for the proposed framework.
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{statetransition}
-\centering
-\caption{State transition diagram to the proposed framework}
-\label{fig:statetransition}
-\end{figure}
-
+%
+%Fig. \ref{fig:statetransition} shows the state diagram for the proposed framework. 
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.5\textwidth]{statetransition}
+%\centering
+%\caption{State transition diagram to the proposed framework}
+%\label{fig:statetransition}
+%\end{figure}
+%
 %It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.
@@
 
-At the present work, it was performed two case studies to evaluate the proposed technique: (1) one concerning a PV system (700 W, with 48h autonomy) deployed at four different houses at an indigenous community called Nova Esperan\c{c}a (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited around 1.5 h by speedboat from Manaus (Amazonas-Brazil), with each house having a different power demand (253 W, 263 W, 283 W, and 501 W); (2) and one case concerning a system deployed as an individual system at ordinary house in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W) as an alternative to pay less electric bill, supporting 915 W of the house's load (1,200 W system, but with autonomy of just 6 h).
+It was performed two case studies: (1) one concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (253 W, 263 W, 283 W, and 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (1,200 W inverter, but with autonomy of just 6 h).
 %and as backup at night 
-
-The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W.
-
-And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
-
+%
+%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
+%
+%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
+%
 %As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).
-At both case studies, it was considered historic data from Manaus city (because the indigenous community do not have data and is not far from Manaus).
-According with X and Y, the minimum average temperature ($T$) during a entire year (21 years on record) is 23$^{o}$C and the maximum average temperature is 32$^{o}$C; and irradiance ($G$)varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight.
+
+%At both case studies, it was considered 21 years of historic data from Manaus. 
+According with X and Y, the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight.  
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight).
 
-Another characteristic of Manaus, is that the PV generation can be despised from 16h to the 8h of the next day, independent of the season.
+Another characteristic of Manaus, is that the PV generation can be despised from 16:00h to the 8:00h of the next day, independent of the season.
 %there is PV generation only between 8:00 h and 16:00 h every day, 
 %with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day. 
-
 Therefore, in order to reduce the computational effort,
 % caused by the state explosion inherent of the technique, 
-the 24h-day was divided, at the algorithms, in 3 parts of 8 h each (8:00h-16:00h, 16:00h-24:00h, 00:00h-8:00h); and only the 8:00h-16:00h period is where there is PV generation.]
+the 24h-day was divided, at the algorithm, in 3 parts of 8 h each (8:00h-16:00h, 16:00h-24:00h, 00:00h-8:00h); and only the 8:00h-16:00h period with PV generation. 
 % and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
-Within this 8h-period, $G$ and $T$ are automated verified with different values, and change their value every 1 h according with the algorithm created using the technique.
-
-Algorithm 1 describes the pseudo code used to perform the automated verification of any PV off-grid system.
+%Within this 8h-period, $G$ and $T$ are automated verified with different values every one hour.
+%, and change their value every 1 h according with the algorithm created using the technique.
+
+Algorithm 1 describes the pseudo code used to perform the automated verification.
 
@@
 
-There are two premises considering the algorithm: (1) is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation from 8:00 h to 16:00 h, but without to account the battery autonomy (just considering charge and discharge process based on solar irradiation, load and battery charge), but after 16:00h is started the verification for the next hours when there is not solar photovoltaic generation.
+%There are two premises considering the algorithm: (1) is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation from 8:00 h to 16:00 h, but without to account the battery autonomy (just considering charge and discharge process based on solar irradiation, load and battery charge), but after 16:00h is started the verification for the next hours when there is not solar photovoltaic generation.
 The process goes on until to verify all the autonomy demanded from the batteries; (2) there is an array, declared at the beginning of the C code, that defines the power demand/consumption at each hour of the day (aka load curve).
@@
 
-If the  verification founds a combination ($SOC$, $G$ and $T$) where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
-And this information can be used by the designer to evaluate the designed system.
+If the  verification founds a situation where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
+And this information can be used by the designer to improve the system.
 %if it was a project error or if it was a combination of variables from the nature that has a low probability to occur at the field, considering the intermittent characteristic of solar PV generation.
@@
 
-Concerning the SMT tool, ESBMC v5.1 was used. And regarding the solver, version 4.7.1 of Z3 was used.
-
-At the terminal, the command used to perform the verification is:
-\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
-
-Where:
-
-\begin{itemize}
-\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
-but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
-\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
-\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
+Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter in order to reduce the memory usage. And regarding the solver, version 4.7.1 of Z3 was used.
+
+%At the terminal, the command used to perform the verification is:
+%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
+%
+%Where:
+%
+%\begin{itemize}
+%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
+%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
+%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
+%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
 There are other options, but this parameter is necessary because the complexity of the algorithms.
@@
 The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
-\item And the last parameter says to the tool that the Z3 SMT solver will be used.
-\end{itemize}
+%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
+%\end{itemize}
 
@@
 %The CBMC, it is notable its prominence through international awards received in competitions. 
-In the works related to the CBMC, much of the research is focused on the improvement of the tool (as software and hardware verifier) and its performance in the competitions, without addressing, however, the question of PV system validation, as can be seen in \cite{Kroening}.
+%In the works r
+Related to the CBMC, much of the research is focused on the improvement of the tool (performance mainly), without addressing, however, the question of PV system validation, as can be seen in \cite{Kroening}.
 % For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.
@@
 The tool also implements a technique to prove the correctness of (some) unbounded programs, the k-induction algorithm; this approach has been applied to a large number of benchmarks and has produced more correct results than similar competing tools \cite{GadelhaSBMF}, \cite{GadelhaK}.
-Related to ESBMC, \cite{Trindade} show that is possible to perform the partitioning of hardware-software (optimization) using ESBMC.
-\cite{Bessa} show that is possible to use ESBMC to check the stability of digital control systems with uncertainty.
-In addition, \cite{Abateetal2017} show the approach to synthesize safe digital feedback controllers for physical plants represented as linear, time invariant models.
+Related to ESBMC, \cite{Trindade} show that is possible to perform the partitioning of hardware-software (optimization).
+\cite{Bessa} show that is possible to use ESBMC to check the stability of digital control systems.
+In addition, \cite{Abateetal2017} show the approach to synthesize safe digital feedback controllers for physical plants.
 However, the use of ESBMC to verify PV systems is unprecedented.
 
-Concerning modeling and simulation of electrical energy systems, \cite{Kremers} used an agent-base model approach to evaluate the effect of loads, shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study.
-However, that is a software development approach for the simulation of complex systems, without the formalism of automated verification.
-
-In the other hand, the use of formal verification related to modeling and validation or even simulation of power systems or power networks is a young theme of research.
+%Concerning modeling and simulation of 
+Concerning electrical energy systems, \cite{Kremers} used an agent-base model approach to evaluate the effect of loads, shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study.
+However, it was restrict to simulation, without the formalism of automated verification.
+%that is a software development approach for the simulation of complex systems, without the formalism of automated verification.
+
+%In the other hand, the use of formal verification related to modeling and validation or even simulation of power systems is a young theme of research.
 % According \cite{Abateetal2014}, where articles from seminars were issued at this thematic, the actual focus is on optimization and control of microgrids, HVAC systems (diagnostics and maintenance), models of generic wind turbine generation, modeling of transmission networks, and verification of smart grids.
-In addition, according with \cite{Abate2017}, recent research has attempted to formalize and implement a formal study of large population of PV panels (very common in European Union).
-The focus have been the modeling of the dynamics of PV panels and their interaction with the power grid.
-Those models do not use battery array, which is demanding in isolated off-grid places.
+In addition, according with \cite{Abate2017}, recent research has attempted to formalize and implement a formal study of large population of PV panels.% (very common in European Union). 
+ The focus have been the modeling of the dynamics of PV panels and their interaction with the grid, without batteries.
 %
@@
 The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field.
-
-The framework presented here establishes the automated verification and the project sizing check.
-Is was shown that, beside the time-consuming issue of the tool, it overcomes the results of off-the-shelf tools that only simulate the results.
+%
+%The framework presented here establishes the automated verification and the project sizing check. 
+Is was shown that, beside the time-consuming issue of the proposed framework, it overcomes the results of off-the-shelf tools that only simulate the results.
 The tool was successful in found sizing errors of PV systems and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
 
-However, it is possible to perform the optimum sizing of the PV system.
-Moreover, the authors target the use of synthesis to perform the optimum sizing.
-That is an interesting issue, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system.
-The future target is to design a tool which starts from a list of commercial equipment, i.e., inputs, where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs, automatically.
-This is what a Counterexample Guided-Inductive Synthesis (CEGIS) does.
-
-In the future, it is possible to expand the type of renewable used for power generation.
-Allowing the verification of wind generation or even hybrid systems, which can transform the tool into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.
+%However, it is possible to perform the optimum sizing of the PV system. Moreover, 
+%The authors target the use of Counterexample Guided-Inductive Synthesis (CEGIS) to perform the optimum sizing of PV systems.
+That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system.
+The next step is to design a tool which starts from a list of commercial equipment, where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs, automatically.
+This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.
+
+Furthermore, it is possible to expand the type of renewable used for power generation.
+And to contemplate hybrid systems, which can transform the framework into a complete tool for design and verification of renewable systems.
+% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.
 
@@
 \section*{Acknowledgment}
-The authors would like to thank Newton Fund (Star Energy project), Coventry University, and Sustainable Amazonas Foundation (FAS), for the financial support and for the possibility to test the framework with real data from deployed PV systems.
-The authors would like to thank, as well, to FAPEAM (Amazonas State Foundation for Research Support) for the financial support.
+The authors would like to thank Newton Fund (Star Energy project), Coventry University, Sustainable Amazonas Foundation (FAS), and FAPEAM (Amazonas State Foundation for Research Support), for the financial support and for the possibility to test the framework with real PV systems.
 
@@
 \begin{IEEEbiographynophoto}{Alessandro Trindade}
-Alessandro Bezerra Trindade received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
+received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
 Currently, he is pursuing his PhD in Informatics at the UFAM, and hold a position as Assistant Professor at the Electricity Department from the Federal University of Amazonas.
@@
 \begin{IEEEbiographynophoto}{Lucas Cordeiro}
-Lucas Carvalho Cordeiro received his PhD degree from the University of Southampton in 2011.
+received his PhD degree from the University of Southampton in 2011.
 From 2009 to 2016, he was an Adjunct Professor at the UFAM (he is currently in unpaid leave).
-Since 2018, he is a Senior Lecturer at the University of Manchester, working with the Formal Methods Group.
+Since 2018, he is a Senior Lecturer at The University of Manchester, working with the Formal Methods Group.
 \end{IEEEbiographynophoto}

### 2018-10-14 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal files

@@
 \begin{abstract}
-The deployment of renewable energy in off-grid systems is growing in both developed and developing countries.
-With declining costs and increasing performance, off-grid renewable energy systems could become an important growth market for the future deployment of renewables according to International Renewable Energy Agency.
-The impact of off-grid renewable energy systems will not only be measured in terms of their usage or reduced costs for electricity consumption in rural areas, but also in the context of their effect on the lives of more than 1.3 billion people who today do not have access to electricity.
+With declining costs and increasing performance, the deployment of renewable energy in off-grid systems is growing in both developed and developing countries, with emphasis to solar photovoltaic systems.
 Electrification of rural areas can improve the standard of education, health conditions, and living of this population.
 In addition, depending on the geography of the country, using renewable energy sources in off-grid mode is a feasible solution if compared to grid extension.
-Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to analyze, and evaluate rural electrification projects.
-This paper aims to build the framework to apply automated verification methods to mathematical models of a system of rural electrification with solar photovoltaic energy to validate its design from a formal verification perspective.
+Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects.
+This paper aims to build the framework to apply automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective.
 Results show that the proposed tool can find situations where the sized solar photovoltaic system fails to met the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same fail.
@@
 % ideas will be 
-proposed framework is done with the efficient SMT-based bounded model checker (ESBMC) tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, which permits to describe the PV system as a C/C++ language code.
+proposed framework is done with the efficient SMT-based bounded model checker (ESBMC) %tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, 
+ which permits to describe the PV system as a C/C++ language code.
 
@@
 %According to \cite{Brooks}, t
-The capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization). 
+The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
+ to complex financial analysis software (with optimization). 
 %Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
@@
 Table \ref{table:softwares} summarizes the off-the-shelf tools mentioned in this paper.
-Where just Hybrid2 do not have technical support; only HOMER Pro, and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis.
+Where just Hybrid2 do not have technical support; only HOMER Pro, and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis;
+and that only HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis.
 However, only paid version of those softwares have all the features, and they run only at Windows operational systems.
@@
 \hline
-Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER Pro} & \rotatebox{90}{RETScreen Expert} & \rotatebox{90}{Hybrid2}\\
+Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen} & \rotatebox{90}{Hybrid2}\\
 \hline
@@
 
-\subsection{PV generator (cell, module, array) }
+\subsection{PV generator model}
 %A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
@@
 
-The performance of photovoltaic systems, that is, the output current/voltage curve ($I-V$ curve), is usually studied using an equivalent circuit model, as shown by \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
+The performance of photovoltaic systems, %that is, the output current/voltage curve ($I-V$ curve), 
+is usually studied using an equivalent circuit model, as shown by \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
 This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}.
@@
 
-Where:
-\begin{itemize}
-\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
-\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
-\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed; $ N=1 $ in a single cell configuration.
+Where: $I_{ph}$ is the photocurrent delivered by the constant current source; $ I_{0} $ is the reverse saturation current corresponding to the diode; $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed ($ N=1 $ in a single cell configuration); $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
+
+%\begin{itemize}
+%\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
+%\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
+%\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed; $ N=1 $ in a single cell configuration.
 %	\begin{itemize}
@@
 %	\end{itemize}	  
-\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes.
+%\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes.
 %	\begin{itemize}
@@
 %	\end{itemize}
-\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
-	\begin{itemize}
-	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
-	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
-	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
-	\end{itemize}	 
-\end{itemize}
-
+%\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
+%	\begin{itemize}
+%	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
+%	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
+%	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
+%	\end{itemize}	 
+%\end{itemize}
+%
 %This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.
@@
 
-\subsection{PV Panel Model}
+%\subsection{PV Panel Model}
 %With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
@@
 
-Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
-\begin{equation}
-\label{eq:Isc}
-I_{sc}=I_{ph}\vert_{V=0}
-\end{equation}
-
-\begin{equation}
-\label{eq:Voc}
-V_{oc}=\dfrac{aNk_{B}T}{q}ln\left( 1+\dfrac{I_{sc}}{I_{0}} \right) 
-\end{equation}
-
-\begin{equation}
-\label{eq:exp}
-exp\left( \dfrac{qV_{oc}}{aNk_{B}T} \right) = \left(1+\dfrac{qV_{m}}{aNk_{B}T} \right) exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) 
-\end{equation}
-
-\begin{equation}
-\label{eq:Im}
-I_{m} =I_{ph}-I_{0}\left[ exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) -1 \right] 
-\end{equation}
-
-Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way.
-
+%Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
+%\begin{equation}
+%\label{eq:Isc}
+%I_{sc}=I_{ph}\vert_{V=0}
+%\end{equation}
+%
+%\begin{equation}
+%\label{eq:Voc}
+%V_{oc}=\dfrac{aNk_{B}T}{q}ln\left( 1+\dfrac{I_{sc}}{I_{0}} \right) 
+%\end{equation}
+%
+%\begin{equation}
+%\label{eq:exp}
+%exp\left( \dfrac{qV_{oc}}{aNk_{B}T} \right) = \left(1+\dfrac{qV_{m}}{aNk_{B}T} \right) exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) 
+%\end{equation}
+%
+%\begin{equation}
+%\label{eq:Im}
+%I_{m} =I_{ph}-I_{0}\left[ exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) -1 \right] 
+%\end{equation}
+%
+%Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way. 
+%
 %A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}. 
@@
 
-\begin{multline}
+\begin{equation}
 \label{eq:Pm}
-P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
-\end{multline}
-
+P_{m} = V_{m} I_{m}
+\end{equation}
+
+%\begin{multline}
+%\label{eq:Pm}
+%P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
+%\end{multline}
+%
 However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
@@
 
-Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $.
-
-In Equation \ref{eq:Iph}, $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at reference conditions (provided by PV manufacturers).
+Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at reference conditions (provided by PV manufacturers).
 $ I_{ph,ref} $ can also be approximated to the reference short-circuit current that is provided by PV manufacturers ($ I_{sc,ref} $) as shown by \cite{Jakhrani}.
@@
 
-Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage.
-
-As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load.
+%Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage. 
+%
+%As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
 The output power ($ P_{out} $) of DC-DC converter is given by Equation \ref{eq:poutcont}. 
@@
 \label{eq:poutcont}
-P_{in = P_{out}}
+P_{in} = P_{out}
 \end{equation}
@@
 
-The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
+%The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
 In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
-\begin{multline}
-\label{eq:numberofcmin}
-number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \\ \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
-\end{multline}
-
-\begin{equation}
-\label{eq:numberofc}
-N_{controller} \geq number_{controllers}
-\end{equation}
-
+%\begin{multline}
+%\label{eq:numberofcmin}
+%number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \\ \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
+%\end{multline}
+%
+%\begin{equation}
+%\label{eq:numberofc}
+%N_{controller} \geq number_{controllers}
+%\end{equation}
+%
 %\subsection{Joint work: charge controller and batteries}
@@
 %An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
-The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage (127 V or 220 V, for example), and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency \cite{Hansen}.
+The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage, % (127 V or 220 V, for example), 
+and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency \cite{Hansen}.
 
@@
 
-Simulation may also be used for validation, but it is more problematic for verification.
+%Simulation may also be used for validation, but it is more problematic for verification.
 In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-
 Testing can also be used for validation, but for the same reasons, it too is problematic for verification.
@@
 One successful method in this domain is model checking.
-
-Model checking is an automatic verification technique, as defined by \cite{Clarke2008}.
+ % 
+%Model checking is an automatic verification technique, as defined by \cite{Clarke2008}.
 Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
@@
 The process of model checking can be divided in three components: modeling, specification, and verification method.
-
-\begin{itemize}
-\item In modeling, a model (normally mathematical) of the system is created; 
-\item In specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, as reliability to performance for example.
+In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in temporal logic form ($CTL$).
+
+%\begin{itemize}
+%\item In modeling, a model (normally mathematical) of the system is created; 
+%\item In specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, as reliability to performance for example.
 \item Normally is expressed in temporal logic form ($CTL$);
-\item The model checking is the verification method itself. 
-\end{itemize}
+%\item The model checking is the verification method itself. 
+%\end{itemize}
 
@@
 \cite{Clarke2008} consider that the most important advantage of the use of model checking.
-
 %Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
@@
 
-As shown by \cite{GadelhaSBMF}, ESBMC has two alternative front-ends to parse the input program and generate an Abstract Syntax Tree (AST).
-One legacy CBMC-based front-end that supports both C and C++ and a new clang-based front-end that currently only supports C.
+As shown by \cite{GadelhaSBMF}, ESBMC has two alternative front-ends to parse the input program.
+% and generate an Abstract Syntax Tree (AST).
+%One legacy CBMC-based front-end that supports both C and C++ and a new clang-based front-end that currently only supports C.
 The data types and bit vectors are created in the front-end when parsing the code.
-
 Regardless of the chosen front-end, the output is an AST (tree representation of the abstract syntactic structure of source code written in a programming language) that will be used by the GOTO converter to generate a GOTO program, which has simplified control flow and is suitable for bounded unwinding.
@@
 \subsection{The case studies and the Algorithm}
-
-It was performed two case studies: (1) one concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (253 W, 263 W, 283 W, and 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (1,200 W inverter, but with autonomy of just 6 h).
+It was performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (253 W, 263 W, 283 W, and 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (1,200 W inverter, but with autonomy of just 6 h).
 %and as backup at night 
@@
 %At both case studies, it was considered 21 years of historic data from Manaus. 
-According with X and Y, the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight.  
+%According with X and Y, t
+The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight.  
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight).
@@
 Those are the same data used during the sizing of the project and ensure to consider the total energy (per day) supplied to the house during the verification.
-
-If the  verification founds a situation where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
+%
+%If the verification founds a situation where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
 And this information can be used by the designer to improve the system.
@@
 
-\section{Results}
-
-This section is split into two parts. The setup is described in Section \ref{sec:setup}, while Section \ref{sec:results} describes all experimental results.
-
-\subsection{Experimental setup}
-\label{sec:setup}
-All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 32 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
+\section{Results} \label{sec:results}
+%
+%This section is split into two parts. The setup is described in Section \ref{sec:setup}, while Section \ref{sec:results} describes all experimental results.
+%
+%
+%\subsection{Experimental setup}
+%\label{sec:setup}
+All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
 
 Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter in order to reduce the memory usage. And regarding the solver, version 4.7.1 of Z3 was used.
+
+The total were five case studies evaluated by HOMER Pro and by the automated verification tool.
+Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shown that the restrictions were met by the five systems, without any indication of sizing error or even of performance.
+
+However, related to the results of the automated verification, the 1,200 W PV system failed during the sizing check.
+The number of panels in series was not the correct (the verification indicates 3 panels in series and the project has 2 in series and 2 in parallel).
+That verification took 3 days to be performed.
+Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
+
+And related to the four 700 W PV system, the sizing check was successful, but all the fail occurred during battery autonomy verification. XXXXXXX
 
@@
 %\end{itemize}
-
-\subsection{Experimental results}
-\label{sec:results}
+%
+%\subsection{Experimental results}
+%\label{sec:results}
+
 XXX
@@
 %The framework presented here establishes the automated verification and the project sizing check. 
-Is was shown that, beside the time-consuming issue of the proposed framework, it overcomes the results of off-the-shelf tools that only simulate the results.
-The tool was successful in found sizing errors of PV systems and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
-
+It was shown that, beside the time-consuming issue of the proposed framework, it overcomes the results of off-the-shelf tool that only simulate the results.
+The framework was successful in found sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
 %However, it is possible to perform the optimum sizing of the PV system. Moreover, 
@@
 That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system.
-The next step is to design a tool which starts from a list of commercial equipment, where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs, automatically.
+Next, the framework will be improved to starts from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs.
 This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.

### 2018-10-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-With declining costs and increasing performance, the deployment of renewable energy in off-grid systems is growing in both developed and developing countries, with emphasis to solar photovoltaic systems.
-Electrification of rural areas can improve the standard of education, health conditions, and living of this population.
-In addition, depending on the geography of the country, using renewable energy sources in off-grid mode is a feasible solution if compared to grid extension.
+With declining costs and increasing performance, the deployment of renewable energy in off-grid systems is growing in both developed and developing countries, with particular emphasis on solar photovoltaic systems.
+Electrification of rural areas can improve the education standard, health conditions, and also the life of this population.
+In addition, depending on the country geography, using renewable energy sources in off-grid mode is a feasible solution if compared to grid extension.
 Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects.
-This paper aims to build the framework to apply automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective.
-Results show that the proposed tool can find situations where the sized solar photovoltaic system fails to met the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same fail.
-Data from practical application of solar systems prove the results obtained by the tool.
+This paper aims to build a framework to apply an automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective.
+Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to met the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.
+Data from practical application of solar systems prove the results obtained by the proposed approach.
 \end{abstract}

### 2018-10-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
reviewed abstract and introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \usepackage{makecell}
+\usepackage{xcolor}
 
@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{A}{ccording} to \cite{Coelho} there are presently 1.3 billion people with no access to electricity worldwide. 
+\IEEEPARstart{A}{ccording} to Coelho et al. \cite{Coelho}, there are presently 1.3 billion people with no access to electricity worldwide. 
 %The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
@@
 % changing the way the world is powered. 
-Based in data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
+Based on data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
 %The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
@@
 %The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy. 
-
+%
 %Apart from PV modules; the 
@@
 %Furthermore, there is the need for proper modeling and simulation tools for people involved in their application.
-In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market.
+In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market \textcolor{red}{cite here those tools}.
 
@@
 
-Desiging any complex system, as a PV, more time is spent on verification than on construction, as shown in \cite{Baier}.
+Desiging any complex system, as a PV, more time is spent on verification than on construction, as described by Baier and Katoen\cite{Baier}.
 Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
@@
 Then, one can try to give a formal proof or otherwise establish that the program meets its specification.%, as defined by \cite{Trindade}.
-
+%
 This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
@@
 That is the main contribution of this paper.
+
+\textcolor{red}{This introduction is missing the description of the vision, approach and results. In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
 
@@
 
-The remainder of this paper is organized as follows: Section II gives the background.
+ %This paragraph is useless.
+%The remainder of this paper is organized as follows: Section II gives the background.
 Section III describes the design and validation of PV system.

### 2018-10-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal files

@@
 %Furthermore, there is the need for proper modeling and simulation tools for people involved in their application.
-In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market \textcolor{red}{cite here those tools}.
+In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.
 
@@
 
-Desiging any complex system, as a PV, more time is spent on verification than on construction, as described by Baier and Katoen\cite{Baier}.
-Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
-Programs may be viewed as mathematical objects.
+However, those tools are based in simulation models to validate a PV system.
+The use of simulation for verification is problematic, because is necessary to ensure the complete coverage of operating conditions, scenarios, and system inputs.
+
+Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs may be viewed as mathematical objects. 
 %with behavior that is, in principle, well determined. 
@@
 %
-This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
+%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
 % Their aim is to establish system correctness with mathematical rigor. 
-In the recent decades, research in formal methods has led to the development of very promising verification techniques.
+%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
 % that facilitate the early detection of bugs in order to ensure the correctness of the system. 
-
-Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
+%
+%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
 %Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
@@
 %Instead of finding a bug or a software inconsistence, t
-The present work aim to verify a PV system, informing in which condition the project do not meet user requirements or will fail, as shown in Fig.\ref{fig:flowchartgeneral}. 
+The present work aim to verify an off-grid PV system, with all their components modelated mathematically, informing in which condition the system do not meet user requirements or will fail, as shown in Fig.\ref{fig:flowchartgeneral}.
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-That is the main contribution of this paper.
-
-\textcolor{red}{This introduction is missing the description of the vision, approach and results. In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{flowchart_verification.png}
-\centering
-\caption{Flowchart of the proposed computer verification of PV systems}
-\label{fig:flowchartgeneral}
-\end{figure}
-
-%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a PV off-grid system, using the satisfiability modulo theories (SMT)-based verification method.
-
-To the best of our knowledge, this is the first work to use a
-%n SMT-based 
-verification tool to solve this kind of problem.
-
 The implementation of the
@@
  which permits to describe the PV system as a C/C++ language code.
+
+The results prove that the framework is more efficient in different case studies to found not proper functioning of PV systems than simulation with off-the-sheld tool.
+To the best of our knowledge, this is the first work to use a
+%n SMT-based 
+verification tool to solve this kind of problem. That is the main contribution of this paper.
+
+%\textcolor{red}{This introduction is missing the description of the vision, approach and results. In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
+
+\begin{figure}[h]
+\includegraphics[width=0.4\textwidth]{flowchart_verification.png}
+\centering
+\caption{Flowchart of the proposed automated verification of PV systems}
+\label{fig:flowchartgeneral}
+\end{figure}
+
+%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a PV off-grid system, using the satisfiability modulo theories (SMT)-based verification method.
 
@@
 \section{Solar Photovoltaic System }
-According to \cite{Roy}, a PV system is designed to give the electric supply to a load.
+%According to \cite{Roy}, a 
+A PV system is designed to give the electric supply to a load.
 This load can be either Alternate Current (AC) type or Direct Current (DC) type.
@@
 \subsection{The Battery Storage Model }
-%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are necessary in a PV system.
+%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system.
 Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery.
@@
 
-Fig. \ref{fig:modelcheckstruc} shows the structure of a typical model checking system. A preprocessor extracts a state transition graph from a system (program or circuit).
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{modelcheckstruc}
-\centering
-\caption{Model Checker structure (Source: \cite{Clarke2008})}
-\label{fig:modelcheckstruc}
-\end{figure}
-
+%Fig. \ref{fig:modelcheckstruc} shows the structure of a 
+In a typical model checking system, a preprocessor extracts a state transition graph from a system (program or circuit).
+
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{modelcheckstruc}
+%\centering
+%\caption{Model Checker structure (Source: \cite{Clarke2008})}
+%\label{fig:modelcheckstruc}
+%\end{figure}
+%
 %Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study. 
@@
 The next step is the symbolic execution, when the GOTO program is executed (unrolling loops up to the bound $ k $) and converted to Static Single Assignments (SSA) form.
-SSA form enables the simplification of algorithms and reduction of computational complexity, where each variable is a target of exactly one assignment statement in the program text.
+SSA form enables the simplification of algorithms and reduction of computational complexity.
+%, where each variable is a target of exactly one assignment statement in the program text.
 %
@@
 That characteristic is useful at this work to perform the sizing check of the PV system project.
-
-Following, the SSA expressions are then encoded using the chosen SMT solver supported by ESBMC: Boolector (default) \cite{Brummayer}, Z3 \cite{DeMoura}, MathSAT \cite{Cimatti}, Yices \cite{Dutertre} and CVC4 \cite{Barrett}.
+Following, the SSA expressions are then encoded using the chosen SMT solver supported by ESBMC. At this paper, it was used the Z3 solver as shown by \cite{DeMoura}.
+%: Boolector (default) \cite{Brummayer}, Z3 \cite{DeMoura}, MathSAT \cite{Cimatti}, Yices \cite{Dutertre} and CVC4 \cite{Barrett}.
 
@@
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
-
 Another characteristic of Manaus, is that the PV generation can be despised from 16:00h to the 8:00h of the next day, independent of the season.
@@
 That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system.
-Next, the framework will be improved to starts from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs.
+Next, the framework will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs.
 This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.
 
-Furthermore, it is possible to expand the type of renewable used for power generation.
-And to contemplate hybrid systems, which can transform the framework into a complete tool for design and verification of renewable systems.
+Furthermore, it is possible to contemplate other kinds of renewable energy and even hybrid ones, which can evolve the framework into a complete tool for design and verification for rural electrification.
 % into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.

### 2018-10-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal files

@@
 \subsection{The case studies and the Algorithm}
-It was performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (253 W, 263 W, 283 W, and 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (1,200 W inverter, but with autonomy of just 6 h).
+It was performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
 %and as backup at night 
@@
 
-However, related to the results of the automated verification, the 1,200 W PV system failed during the sizing check.
-The number of panels in series was not the correct (the verification indicates 3 panels in series and the project has 2 in series and 2 in parallel).
-That verification took 3 days to be performed.
+However, related to the results of the automated verification, the 1,200 W PV system (house 5) failed during the sizing check.
+The number of panels was not correct (the verification indicates 3 panels in parallel and the project has 2 in series and 2 in parallel).
+That verification took 63.3 hours to be performed.
 Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-
-And related to the four 700 W PV system, the sizing check was successful, but all the fail occurred during battery autonomy verification. XXXXXXX
+But it is understandable that this problem occurs because the system was purchased as a off-the-shelf solution and not as a specific design for the electrical charges of the house.
+
+And related to the four 700 W PV system, the sizing check was successful, but there were  found flaws in everyone, all related with the SOC that reached levels below of 75\%.
+The framework identified the flaws right after the first night-discharge cycle, before dawn, and before the system start to recharge the batteries.
+The framework took 409.3 hours to found an error at house 1, and the maximum of 456XXX hours to house 4.
 

### 2018-10-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal files

@@
 Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-But it is understandable that this problem occurs because the system was purchased as a off-the-shelf solution and not as a specific design for the electrical charges of the house.
+But it is understandable that this problem occurs because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house.
 

### 2018-11-01 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal text

@@
 %Furthermore, there is the need for proper modeling and simulation tools for people involved in their application.
+
 In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.
-
 %The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
@@
 Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-
+%
 %Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
-
+%
 %PV systems can be classified into grid-connected and stand-alone systems.
@@
 The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-
-However, those tools are based in simulation models to validate a PV system.
+However, those tools are based only in simulation models.
 The use of simulation for verification is problematic, because is necessary to ensure the complete coverage of operating conditions, scenarios, and system inputs.
@@
  This makes it possible to specify systems as programs using mathematical logic, which constitutes the intended (correct) behavior.
-Then, one can try to give a formal proof or otherwise establish that the program meets its specification.%, as defined by \cite{Trindade}.
+Then, one can try to give a formal proof or otherwise establish that the program meets its specification.
+%, as defined by \cite{Trindade}.
 %
@@
 
-The results prove that the framework is more efficient in different case studies to found not proper functioning of PV systems than simulation with off-the-sheld tool.
+The results prove that the framework is more efficient in different case studies to find not proper functioning of PV systems than simulation with off-the-sheld tool.
 To the best of our knowledge, this is the first work to use a
@@
 A PV system is designed to give the electric supply to a load.
-This load can be either Alternate Current (AC) type or Direct Current (DC) type.
+This load can be either Alternate Current (AC) or Direct Current (DC) type.
 Electric supply can be needed either in daytime or evening time.
@@
 The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
- to complex financial analysis software (with optimization). 
+ to complex financial analysis and project optimization. 
 %Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-In this work, were evaluated the most popular tools, as PVWatts, SAM, Homer Pro, RETScreen Expert, and Hybrid2.
+In this work, were evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.
 
@@
 \subsection{Paper Proposal x Reference Tools}
-Considering the focus of this paper, only HOMER and RETScreen remain for comparative. All tools need some parameters inherently from manufacturer's catalog in order to size the system.
+Considering the focus of this paper, only HOMER remain for comparative. All tools need some parameters inherently from manufacturer's catalog in order to size the system.
 %, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
@@
 Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than the listed-more common tools.
-
-The comparative between the Homer Pro and the automated verification tool is presented at the Section \ref{sec:results}.
+The comparative between the HOMER Pro and the automated verification tool is presented at the Section \ref{sec:results}.
 
@@
 %The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load. 
-The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}.
+The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
 The modular structure facilitates the modeling of the other system structures and replacing of elements as, for instance, a DC load instead of an AC load.
@@
 
-Where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
+Where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is find at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
 
@@
 In \cite{Mellit} was established that the controller allows the management of energy between the load and the battery. 
-The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
+%The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
 The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
-
 According \cite{Hansen}, to protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and when the current required by the load is less than the current delivered by the PV arrays.
@@
 %
-%The steps in the modeling of the controller process are summarized in Table \ref{table:controller}.
+The steps in the modeling of the controller process are summarized in Table \ref{table:controller}.
 
@@
 
-Where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be found from the inverter's data-sheet.
+Where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be find from the inverter's data-sheet.
 
@@
 \subsection{ESBMC }
-According \cite{GadelhaSBMF}, ESBMC is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs.
-the efficient SMT based model checker, is a software verification tool for C and C++ code bases.
-Fig.
-\ref{fig:esbmcarch} shows the tool architecture.
+According \cite{GadelhaSBMF}, ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs. 
+%The efficient SMT based model checker, is a software verification tool for C and C++ code bases. 
+Fig. \ref{fig:esbmcarch} shows the tool architecture.
 
@@
 Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied.
-If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is found to be unsatisfiable, there are no errors up to the unwinding bound, and this result is presented.
+If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is find to be unsatisfiable, there are no errors up to the unwinding bound, and this result is presented.
 
@@
 The framework identified the flaws right after the first night-discharge cycle, before dawn, and before the system start to recharge the batteries.
-The framework took 409.3 hours to found an error at house 1, and the maximum of 456XXX hours to house 4.
+The framework took 409.3 hours to find an error at house 1, and the maximum of 456XXX hours to house 4.
 
@@
 It was shown that, beside the time-consuming issue of the proposed framework, it overcomes the results of off-the-shelf tool that only simulate the results.
-The framework was successful in found sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
+The framework was successful in find sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
 %However, it is possible to perform the optimum sizing of the PV system. Moreover, 
@@
 That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system.
-Next, the framework will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs.
+Next, the framework will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is find from the inputs.
 This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.

### 2018-11-02 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
reviewed sections 1 and 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 With declining costs and increasing performance, the deployment of renewable energy in off-grid systems is growing in both developed and developing countries, with particular emphasis on solar photovoltaic systems.
-Electrification of rural areas can improve the education standard, health conditions, and also the life of this population.
-In addition, depending on the country geography, using renewable energy sources in off-grid mode is a feasible solution if compared to grid extension.
+Electrification of rural areas can improve the education standard, health conditions, and also the life of that population.
+In addition, depending on the country geography, using renewable energy sources in off-grid mode is a feasible solution if compared to a grid extension.
 Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects.
 This paper aims to build a framework to apply an automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective.
-Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to met the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.
-Data from practical application of solar systems prove the results obtained by the proposed approach.
+Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.
+\textcolor{red}{Data from practical application of solar systems prove the results obtained by the proposed approach...
+this last sentence should be stronger to emphasise your main contribution...
+maybe you could update this after obtaining the experimental results...}
 \end{abstract}
@@
 % changing the way the world is powered. 
-Based on data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
+Based on data from \textcolor{red}{from what?
+please be more formal!
+can you check the guidelines of the journal to see how you can cite references?}\cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV.
 %The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
@@
 
-In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.
+In order to validate or even simulate a potential PV solution, there are a myriad of tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.
 %The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
@@
 The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-However, those tools are based only in simulation models.
-The use of simulation for verification is problematic, because is necessary to ensure the complete coverage of operating conditions, scenarios, and system inputs.
-
-Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs may be viewed as mathematical objects. 
+However, those tools are based only on simulation models.
+\textcolor{red}{I don't understand this sentence since simulation and verification are two different things: The use of simulation for verification is problematic}, because is necessary to ensure the complete coverage of operating conditions, scenarios, and system inputs.
+
+Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process \textcolor{red}{add citation here...}.
+\textcolor{red}{What is the relation among formal methods, programs and your work?
+Programs may be viewed as mathematical objects.}
 %with behavior that is, in principle, well determined. 
@@
 %Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
- Algorithms can verify the system model through systematically explore all their states.
+ Algorithms can verify the system model by systematically exploring all their states.
 
@@
 %Instead of finding a bug or a software inconsistence, t
-The present work aim to verify an off-grid PV system, with all their components modelated mathematically, informing in which condition the system do not meet user requirements or will fail, as shown in Fig.\ref{fig:flowchartgeneral}.
+Here we will verify an off-grid PV system, with all their components modelled mathematically, and then report in which conditions the system does not meet user requirements or whether it will fail due to \textcolor{red}{????}, as illustrated in Fig.\ref{fig:flowchartgeneral}.
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
@@
 % ideas will be 
-proposed framework is done with the efficient SMT-based bounded model checker (ESBMC) %tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, 
- which permits to describe the PV system as a C/C++ language code.
-
-The results prove that the framework is more efficient in different case studies to find not proper functioning of PV systems than simulation with off-the-sheld tool.
+proposed framework is carried out by means of the efficient SMT-based bounded model checker (ESBMC) %tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, 
+ which allows one to formally verify the PV system as a C program.
+
+The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-sheld tool.
 To the best of our knowledge, this is the first work to use a
@@
 
+%--------------------------------------------------------
 \section{Solar Photovoltaic System }
+%--------------------------------------------------------
+
+\textcolor{red}{This section is too short! You should move it to another big section...}
+
 %According to \cite{Roy}, a 
@@
 %(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
-For night hours or rainy days, one needed to have batteries, where power can be stored and used.% \cite{Gules}.
-
-PV systems are broadly classified into three distinct types, as described by \cite{Mohanty}: (1) standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system, where another source(s) of energy can work together with the solar PV.
+For night hours or rainy days, one needs to hold batteries, where power can be stored and used.% \cite{Gules}.
+
+PV systems are broadly classified into three distinct types, as described by \textcolor{red}{who?} \cite{Mohanty}: (1) standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system, where another source(s) of energy can work together with the solar PV.
 % system to provide the required demand.

### 2018-11-02 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
reviewed sections 3, 4, 5 and 6
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-In this work, were evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.
+Here we evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.
 
@@
 
-Table \ref{table:softwares} summarizes the off-the-shelf tools mentioned in this paper.
-Where just Hybrid2 do not have technical support; only HOMER Pro, and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis;
-and that only HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis.
-However, only paid version of those softwares have all the features, and they run only at Windows operational systems.
-RETScreen and HOMER have a free web-based version but with limited resources.
+Table~\ref{table:softwares} summarizes the off-the-shelf tools employed in this study, where only Hybrid2 does not have technical support; HOMER Pro and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis;
+additionally, HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis.
+However, only paid version of those tools have all the features \textcolor{red}{which features?}, and they run only on Windows operating system.
+RETScreen and HOMER have a free web-based version, but they have limited resources.
 
@@
 
+%-------------------------------------------------------------------
 \subsection{Paper Proposal x Reference Tools}
-Considering the focus of this paper, only HOMER remain for comparative. All tools need some parameters inherently from manufacturer's catalog in order to size the system.
+%-------------------------------------------------------------------
+
+Considering the focus of this paper, only HOMER remains for our comparative evaluation.
+All tools need some parameters inherently from manufacturer's catalog \textcolor{red}{is this the correct term?
+to size the system}.
 %, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
 After that, the potential solution is analyzed in another tool to validate or even optimize the solution.
-Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than the listed-more common tools.
-The comparative between the HOMER Pro and the automated verification tool is presented at the Section \ref{sec:results}.
-
+Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than other state-of-the-art tools \textcolor{red}{cite them here...}.
+The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section \ref{sec:results}.
+
+%-------------------------------------------------------------------
 \section{Component models for stand-alone PV system }
+%-------------------------------------------------------------------
+
 %The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load. 
-The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
-The modular structure facilitates the modeling of the other system structures and replacing of elements as, for instance, a DC load instead of an AC load.
+The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram} \textcolor{red}{you should explain each element of the figure}.
+The modular structure facilitates the modeling of the other system structures and replacement of elements such as a DC load instead of an AC load.
 
@@
 \centering
-\caption{Block diagram for the stand-alone PV system (Source: \cite{Hansen})}
+\caption{Block diagram for the stand-alone PV system~\cite{Hansen}}.
 \label{fig:blockdiagram}
@@
 
+%-------------------------------------------------------------------
 \subsection{PV generator model}
+%-------------------------------------------------------------------
+
 %A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
@@
 %
-The basic element of a PV system is the PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
+The basic element of a PV system is a PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
 %The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
@@
 The performance of photovoltaic systems, %that is, the output current/voltage curve ($I-V$ curve), 
-is usually studied using an equivalent circuit model, as shown by \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
+is usually studied using an equivalent circuit model, as described in the available literature \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
 This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}.
@@
 \centering
-\caption{ 1-diode equivalent PV cell/panel circuit model (Source: \cite{Cubas})}
+\caption{ 1-diode equivalent PV cell/panel circuit model~\cite{Cubas}.}
 %\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process (Source: \cite{Hansen})}
+\caption{Summary of the controller process~\cite{Hansen}}
 \label{table:controller}
@@
 
+%-------------------------------------
 \section{Related work }
+%-------------------------------------
+
+\textcolor{red}{This section needs more work. You should describe here studies related to the design, verification or validation of PV systems and not about software model checkers!}
+
 %The CBMC, it is notable its prominence through international awards received in competitions. 
@@
 
+%-------------------------------------
 \section{Conclusions and Future Work}
+%-------------------------------------
+
 %The proposed framework seems to be a coherent and promising tool to perform verification of a PV project.
@@
 
+\textcolor{red}{You should revise all references according to the journal guideline.}
+
 % Can use something like this to put references on a page

### 2018-11-08 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
text updating

--- 2018-11-02 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
@@
 % Do not put math or special symbols in the title.
-\title{Building a framework to perform automated verification of solar photovoltaic off-grid systems}
+%\title{Building a framework to perform automated verification of solar photovoltaic off-grid systems}
+\title{Automated verification of stand-alone solar photovoltaic systems}
 %
@@
 \begin{IEEEkeywords}
-Automated verification, model checking, energy systems, solar photovoltaic systems, off-grid systems.
+Photovoltaic power systems, solar power generation, power system modeling, formal verification, model checking.
 \end{IEEEkeywords}
@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{A}{ccording} to Coelho et al. \cite{Coelho}, there are presently 1.3 billion people with no access to electricity worldwide. 
+\IEEEPARstart{A}{ccording} to \cite{Coelho}, there are presently 1.3 billion people with no access to electricity worldwide. 
 %The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
@@
 % changing the way the world is powered. 
-Based on data from \textcolor{red}{from what?
-please be more formal!
-can you check the guidelines of the journal to see how you can cite references?}\cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV.
+%Based on data from \textcolor{red}{from what? please be more formal! can you check the guidelines of the journal to see how you can cite references?}, t
+There was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV \cite{EPIA}. 
 %The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
@@
 
-In order to validate or even simulate a potential PV solution, there are a myriad of tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.
-%The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
-In order to validate or even simulate a potential PV solution, there are a myriad of tools.
+The increase in the number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researchers and practitioners involved in their application.
+In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.
+And even general purpose simulations as MATLAB/Simulink.
+
 %However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.  
@@
 The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-However, those tools are based only on simulation models.
-\textcolor{red}{I don't understand this sentence since simulation and verification are two different things: The use of simulation for verification is problematic}, because is necessary to ensure the complete coverage of operating conditions, scenarios, and system inputs.
-
-Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process \textcolor{red}{add citation here...}.
-\textcolor{red}{What is the relation among formal methods, programs and your work?
-Programs may be viewed as mathematical objects.}
+However, those tools are based on running experiments in simulation models.
+And simulation has the pros of be cheap and be employed before the system is declared concluded, however with the cons of an incomplete coverage, because the verification of all possible iterations and potential failures of systems is rarely pissible or feasible \cite{Clarke2008}.
+
+Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process \cite{Clarke2008}.  
 %with behavior that is, in principle, well determined. 
- This makes it possible to specify systems as programs using mathematical logic, which constitutes the intended (correct) behavior.
+ Using this technique, systems are specified as programs using mathematical logic, which constitutes the intended (correct) behavior.
 Then, one can try to give a formal proof or otherwise establish that the program meets its specification.
@@
 
+At this paper, mathematical models of each component of a stand-alone PV system, panel solar, charge controller, batteries, inverter, and load, are translated as a single software program.
+Those programs are viewed as mathematical objects, and the use of
 %Bringing this technique to solar PV systems, i
 %Instead of finding a bug or a software inconsistence, t
-Here we will verify an off-grid PV system, with all their components modelled mathematically, and then report in which conditions the system does not meet user requirements or whether it will fail due to \textcolor{red}{????}, as illustrated in Fig.\ref{fig:flowchartgeneral}.
+%Here it will be verified a stand-alone PV system, with all their components modeled mathematically, 
+and then report in which conditions the system does not meet user requirements (as electrical load, power demand) or whether it will fail due to weather conditions and/or battery autonomy, for example.
+
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
@@
 % ideas will be 
-proposed framework is carried out by means of the efficient SMT-based bounded model checker (ESBMC) %tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, 
+proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC) %tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, 
  which allows one to formally verify the PV system as a C program.
 
-The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-sheld tool.
+Formal methods provide facilities for the modeling of each component of any complex system \cite{Hall1990}.
+It allows for developing models for each component of the system.
+The behavior of each system can be analyzed and observed with the help of these formal models.
+A key benefit to this approach is that it helps in the detection of faults and flaws in the design phase of system development, thereby considerably improving system reliability \cite{Akram2018}.
+
+In previous studies, 
+%%%%%%%
+%%%%%%%%
+\textcolor{red}{This section needs more work. You should describe here studies related to the design, verification or validation of PV systems and not about software model checkers!}
+
+%The CBMC, it is notable its prominence through international awards received in competitions. 
+%In the works r
+Related to the CBMC, much of the research is focused on the improvement of the tool (performance mainly) \cite{Kroening}, without addressing, however, the issue of PV system validation.
+% For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.
+
+%ESBMC was developed to perform bounded model checks on both sequential and concurrent programs using a range of SMT solvers, and has a proven track of bug finding in real-world applications \cite{Cordeiro}, \cite{Ramalho}.
+The tool also implements a technique to prove the correctness of (some) unbounded programs, the k-induction algorithm; this approach has been applied to a large number of benchmarks and has produced more correct results than similar competing tools \cite{GadelhaSBMF}, \cite{GadelhaK}.
+Related to ESBMC, it is possible to perform the partitioning of hardware-software (optimization) \cite{Trindade}.
+And it is possible to use ESBMC to check the stability of digital control systems \cite{Bessa}.
+In addition,  there is the approach to synthesize safe digital feedback controllers for physical plants \cite{Abateetal2017}.
+However, the use of ESBMC to verify PV systems is unprecedented.
+
+%Concerning modeling and simulation of 
+Concerning electrical energy systems,  there is the use of agent-base model approach to evaluate the effect of loads, shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study \cite{Kremers}.
+However, it was restrict to simulation, without the formalism of automated verification.
+%that is a software development approach for the simulation of complex systems, without the formalism of automated verification.
+
+%In the other hand, the use of formal verification related to modeling and validation or even simulation of power systems is a young theme of research.
+% According \cite{Abateetal2014}, where articles from seminars were issued at this thematic, the actual focus is on optimization and control of microgrids, HVAC systems (diagnostics and maintenance), models of generic wind turbine generation, modeling of transmission networks, and verification of smart grids.
+In addition, recent research has attempted to formalize and implement a formal study of large population of PV panels.% (very common in European Union). 
+ The focus have been the modeling of the dynamics of PV panels and their interaction with the grid, without batteries \cite{Abate2017}.
+%
+%Therefore, the present work unites the versatility and power of the formal models, applied to a formal verification tool, with individual PV systems (off-grid), which is the most indicated and common option to solve the problem of energy in developing countries.
+Especially those that have isolated communities, either for long distances of the great centers, or for being riverside.
+This work includes, based on its off-grid characteristic, batteries and charge controllers, differently of on-grid systems of related work.
+
+%%%%%%%%
+%%%%%%%%
+
+%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
 To the best of our knowledge, this is the first work to use a
@@
 
-%\textcolor{red}{This introduction is missing the description of the vision, approach and results. In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{flowchart_verification.png}
-\centering
-\caption{Flowchart of the proposed automated verification of PV systems}
-\label{fig:flowchartgeneral}
-\end{figure}
-
+%\textcolor{red}{This introduction is missing the description of the vision, approach and results.
+In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
+%
 %The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a PV off-grid system, using the satisfiability modulo theories (SMT)-based verification method.
 
- %This paragraph is useless.
-%The remainder of this paper is organized as follows: Section II gives the background.
-Section III describes the design and validation of PV system.
-Section IV describes the mathematical modeling.
-Section V presents the automated verification.
-The methodology is presented at section VI.
-Section VII is devoted to the results, and section VIII to the related work.
-Section IX presents the conclusion and describes future work.
+The remainder of this paper is organized as follows: Section II gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
+Section III presents the automated verification technique.
+The methodology is presented at section IV.
+Section V is devoted to the results.
+Section VI presents the conclusion and describes future work.
 
@@
 
-PV systems are broadly classified into three distinct types, as described by \textcolor{red}{who?} \cite{Mohanty}: (1) standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system, where another source(s) of energy can work together with the solar PV.
+PV systems are broadly classified into three distinct types \cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system, where another source(s) of energy can work together with the solar PV.
 % system to provide the required demand.
@@
 %\begin{itemize}
-%\item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
+%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
 Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants;
@@
 Specifically concerning isolated communities, 
-%standalone systems are one the most used solutions, and 
+%stand-alone systems are one the most used solutions, and 
 % depending on the type of load, cost, resources availability, and requirements of the load, 
-%standalone systems 
+%stand-alone systems 
 %can be split into several categories. However, 
-the configuration that is most common nowadays is the regulated standalone system with battery and AC load. This configuration includes PV array, batteries, charge controller, inverter, and AC load.
+the configuration that is most common nowadays is the regulated stand-alone system with battery and AC load. This configuration includes PV array, batteries, charge controller, inverter, and AC load.
 %PV array, battery, MPPT and AC load.
@@
 
-%\subsection{Unregulated standalone PV system with DC load }
+%\subsection{Unregulated stand-alone PV system with DC load }
 %Usually this type of system is for low power applications, as defined by \cite{Roy}.
@@
 %\centering
-%\caption{PV standalone systems: (a) regulated standalone SPV system with DC load; (b) regulated standalone SPV system with DC load; (c) regulated standalone SPV system with battery DC load; and (d) regulated standalone system with battery and AC load  (Source: \cite{Roy})}
+%\caption{PV stand-alone systems: (a) regulated stand-alone SPV system with DC load; (b) regulated stand-alone SPV system with DC load; (c) regulated stand-alone SPV system with battery DC load; and (d) regulated stand-alone system with battery and AC load  (Source: \cite{Roy}).}
 %\label{fig:standaloneSPV}
@@
 
-%\subsection{Regulated standalone PV system with DC load}
-%It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:standaloneSPV} letter (b).
+%\subsection{Regulated stand-alone PV system with DC load}
+%It is similar to unregulated stand-alone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:standaloneSPV} letter (b).
 Usually system with MPPT should have battery; otherwise, extra power will be waste.
 
-%\subsection{Regulated standalone system with battery and DC load}
+%\subsection{Regulated stand-alone system with battery and DC load}
 %Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:standaloneSPV} letter (c).
@@
 %According to \cite{Pinho}, PV systems that are used to feed loads with low variation on the consumption can be sized to operate without the controller.
-That is called of self-regulated standalone PV system with battery.
+That is called of self-regulated stand-alone PV system with battery.
 However, the voltage from the PV panel must be compatible with the batteries voltage.
@@
 
-%\subsection{Regulated standalone system with battery and AC load}
+%\subsection{Regulated stand-alone system with battery and AC load}
 %This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:standaloneSPV} letter (d).
@@
 
-\section{Design and Validation of a Solar photovoltaic system}
+\subsection{Design and Validation of a Solar photovoltaic system}
 %The design and validation of a PV system can be done by hand or with the aid of a software tool. 
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here we evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.
+Here it was evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.
 
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Comparative coverage of reference softwares}
+\caption{Comparative coverage of reference software}
 \label{table:softwares}
@@
 %-------------------------------------------------------------------
-\section{Component models for stand-alone PV system }
+\subsection{Component models for stand-alone PV system }
 %-------------------------------------------------------------------
 
-%The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load. 
+%The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
 The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram} \textcolor{red}{you should explain each element of the figure}.
@@
 \centering
-\caption{Block diagram for the stand-alone PV system~\cite{Hansen}}.
+\caption{Block diagram for the stand-alone PV system (Source:~\cite{Hansen}).}
 \label{fig:blockdiagram}
@@
 %Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
-
 \begin{figure}[h]
@@
 \centering
-\caption{ 1-diode equivalent PV cell/panel circuit model~\cite{Cubas}.}
+\caption{1-diode equivalent PV cell/panel circuit model (Source:~\cite{Cubas}).}
 %\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
@@
 
-The 1-diode model, shown by Fig. \ref{fig:equivckt}, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in Equation \ref{eq:1diodemodel}. 
+The 1-diode model, shown by Fig. \ref{fig:equivckt}, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in (\ref{eq:1diodemodel}). 
 \begin{equation}
@@
 %Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
-The simplified model of 1-diode was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested.
+The simplified model of 1-diode was shown that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested \cite{Saloux}.
 In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing.
@@
 %A single-diode without series and shunt resistances is considered. 
-Equation 1 is used to write down expressions for currents and voltages at each key point of characteristic curve from a PV cell.
+Equation (\ref{eq:1diodemodel}) is used to write down expressions for currents and voltages at each key point of characteristic curve from a PV cell.
 % shown in Fig. \ref{fig:ivcurve}.
@@
 
-As shown by \cite{Saloux} the voltage and the current at the maximum power point and consequently the maximum output power, can be expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm}.
+The voltage and the current at the maximum power point and consequently the maximum output power, can be expressed by (\ref{eq:Vmfinal}), (\ref{eq:Imfinal}), and (\ref{eq:Pm}) \cite{Saloux}.
 %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
@@
 However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, Equation \ref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.
+Therefore, (\ref{eq:Iph}) is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.
 \begin{equation}
@@
 Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at reference conditions (provided by PV manufacturers).
-$ I_{ph,ref} $ can also be approximated to the reference short-circuit current that is provided by PV manufacturers ($ I_{sc,ref} $) as shown by \cite{Jakhrani}.
-
-The cell temperature ($ T $) can be obtained from \cite{Ross} and is shown in Equation \ref{eq:Tcell}.
+$ I_{ph,ref} $ can also be approximated to the reference short-circuit current \cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
+
+The cell temperature ($ T $) is shown in (\ref{eq:Tcell}) \cite{Ross}.
 \begin{equation}
@@
 
-Furthermore, \cite{Villalva} have proposed a relationship, which allows the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature (Equation \ref{eq:I0}). 
+Furthermore, (\ref{eq:I0}) allows the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature \cite{Villalva}. 
 %In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
@@
 %The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current equation (Equation \ref{eq:Pm}) and the saturation current in the reference temperature given by Equation \ref{eq:I0}, the diode quality (or ideality) coefficient is determined by Equation \ref{eq:a}.
+Using the maximum power point current (\ref{eq:Pm}) and the saturation current in the reference temperature given by (\ref{eq:I0}), the diode quality (or ideality) coefficient is determined by (\ref{eq:a}).
 \begin{equation}
@@
 First is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$).
-That is done by Equation \ref{eq:Ecorrected}, according \cite{Pinho}.
+That is done by (\ref{eq:Ecorrected}) \cite{Pinho}.
 Where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
@@
 
-The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by Equation \ref{eq:NTPmin}, and the check is done with the Equation \ref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from Equation \ref{eq:NTPmin}.
+The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by  (\ref{eq:NTPmin}), and the check is done with (\ref{eq:NTP}), where the sized number of panels ($ N_{TP} $) must be greater than the result from (\ref{eq:NTPmin}).
 \begin{equation}
@@
 
-Particularly, the total number of panels is series ($ N_{PSmin} $) and parallel ($ N_{PPmin} $) are given by the Equations \ref{eq:NPSmin} and \ref{eq:NPPmin}, respectively.
-With the check did by Equations \ref{eq:NPS} and \ref{eq:NPP}.
-$ V_{system} $ is the DC voltage of the bus, and is a design decision (normally 12, 24 or 48 V).
+Particularly, the total number of panels is series ($ N_{PSmin} $) and parallel ($ N_{PPmin} $) are given by (\ref{eq:NPSmin}) and (\ref{eq:NPPmin}), respectively.
+With the check done by (\ref{eq:NPS}) and (\ref{eq:NPP}).
+$ V_{system} $ is the DC voltage of the bus, and is a design decision, normally 12, 24 or 48 V.
 \begin{equation}
@@
 
-Several models have been presented in the literature, as shown by \cite{Copetti}, and \cite{Manwell93}.
+Several models have been presented in the literature \cite{Copetti}, \cite{Manwell93}.
 %, and \cite{Manwell94}. 
@@
 
-Here, the model adopted is the based on \cite{Copetti}, who uses manufacturer's data and allows finding relations among voltage, current, state of charge and temperature.
-
-The discharge voltage equation is shown in Equation \ref{eq:bat_Vd}. 
+Here, the model adopted \cite{Copetti} uses manufacturer's data and allows finding relations among voltage, current, state of charge and temperature.
+
+The discharge voltage equation is shown in (\ref{eq:bat_Vd}). 
 %The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
@@
 
-For the charging process, however, the parameters are presented in Equation \ref{eq:Vcbat}.
+For the charging process, however, the parameters are presented in (\ref{eq:Vcbat}).
 %
@@
 %\cite{Copetti} show that, 
-During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (Equation \ref{eq:Vec}).
-It was created a function for the gassing voltage as well, as shown in Equation \ref{eq:Vg}.
-In addition, the overcharge phenomenon can be represented by Equation \ref{eq:Voverc}.
+During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (\ref{eq:Vec}).
+It was created a function for the gassing voltage as well, as shown in (\ref{eq:Vg}).
+In addition, the overcharge phenomenon can be represented by (\ref{eq:Voverc}).
 \begin{equation}
@@
 
-The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by Equation \ref{eq:tau}.
+The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by (\ref{eq:tau}).
 \begin{equation}
@@
 
-Therefore, to model the voltage ($ V_{c} $) evolution of the battery, equation \ref{eq:Vcbat} can be used up the start of gassing ($ V_{c} \leq V_{g} $).
-And during overcharging ($ V_{c} > V_{g} $), Equation \ref{eq:Voverc} can be used until a constant final voltage ($ V_{ec} $) is reached.
+Therefore, to model the voltage ($ V_{c} $) evolution of the battery, (\ref{eq:Vcbat}) can be used up the start of gassing ($ V_{c} \leq V_{g} $).
+And during overcharging ($ V_{c} > V_{g} $), (\ref{eq:Voverc}) can be used until a constant final voltage ($ V_{ec} $) is reached.
 
@@
 Besides the model verification, there is also the prior stage of project sizing check, as did to the solar panel.
-First is necessary to define the total capacity of the battery bank, as shown by Equation \ref{eq:Cbank}.
+First is necessary to define the total capacity of the battery bank, as shown by (\ref{eq:Cbank}).
 \begin{equation}
@@
 
-Following, is done the total (minimum) number of batteries, as show by Equation \ref{eq:Nbtotal}.
-Moreover, the Equation \ref{eq:batcheck} perform the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that were established to the project.
+Following, is done the total (minimum) number of batteries, as show by (\ref{eq:Nbtotal}).
+Moreover, (\ref{eq:batcheck}) perform the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that were established to the project.
 \begin{equation}
@@
 MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power.
-According to \cite{Pinho}, controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.
+Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
 %
@@
 
-In \cite{Mellit} was established that the controller allows the management of energy between the load and the battery. 
+The controller allows the management of energy between the load and the battery \cite{Mellit}. 
 %The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
 The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
-According \cite{Hansen}, to protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and when the current required by the load is less than the current delivered by the PV arrays.
+To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and when the current required by the load is less than the current delivered by the PV arrays \cite{Hansen}.
 PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $.
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process~\cite{Hansen}}
+\caption{Summary of the controller process (Source:~\cite{Hansen})}
 \label{table:controller}
@@
 %As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of DC-DC converter is given by Equation \ref{eq:poutcont}. 
+The output power ($ P_{out} $) of DC-DC converter is given by (\ref{eq:poutcont}). 
 \begin{equation}
@@
 
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Equation \ref{eq:poutcont} is possible to reach Equation \ref{eq:potcont}.
+Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from (\ref{eq:poutcont}) is possible to reach (\ref{eq:potcont}).
 \begin{equation}
@@
 One more time, some steps must be done to check the sizing project of the controller, prior the verification phase.
-Initially the controller must meet the voltage requirement of the PV system, as shown by Equation \ref{eq:vcvsystem}.
+Initially the controller must meet the voltage requirement of the PV system, as shown by (\ref{eq:vcvsystem}).
 \begin{equation}
@@
 
-Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as shown by Equation \ref{eq:iscamb}.
+Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as shown by (\ref{eq:iscamb}).
 \begin{equation}
@@
 
-The controller must meet the maximum current from the PV array (Equations \ref{eq:icmin} and \ref{eq:icicmin}).
+The controller must meet the maximum current from the PV array (\ref{eq:icmin}), and (\ref{eq:icicmin}).
 \begin{equation}
@@
 
-The inverter is characterized by a power dependent efficiency $ \eta_{i} $ given by \cite{Hansen} as shown by Equation \ref{eq:efficinv}.
+The inverter is characterized by a power dependent efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
 \begin{equation}
@@
 The sizing project check of the inverter is done through three Equations.
-Equation \ref{eq:vindc} ensure that the input voltage of the controller meet the voltage of the system.
-Equation \ref{eq:voutac} ensures that the output voltage of the controller meet the AC voltage of the load.
-Moreover, Equation \ref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
+Equation (\ref{eq:vindc}) ensure that the input voltage of the controller meet the voltage of the system.
+Equation (\ref{eq:voutac}) ensures that the output voltage of the controller meet the AC voltage of the load.
+Moreover, (\ref{eq:invcheck}) ensures that the controller can support the total demand of the load and the surge power.
 \begin{equation}
@@
 
-According \cite{Clarke2008}, verification procedure is an intelligent exhaustive search of the state space of the design.
-In addition, according to \cite{Forejt2011}, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system.
+Verification procedure is an intelligent exhaustive search of the state space of the design \cite{Clarke2008}.
+In addition, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}.
 One successful method in this domain is model checking.
@@
 Specifically at the $FALSE$ situation, the algorithm returns a counterexample that is useful as diagnostic of the system, in order to discover in which situation the model is violated.
-\cite{Clarke2008} consider that the most important advantage of the use of model checking.
+That is the most important advantage of the use of model checking \cite{Clarke2008}.
 %Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
@@
 
-The model checking problem can be defined as shown in \cite{Clarke2008}:
+The model checking problem can be defined as \cite{Clarke2008}:
 
@@
 \centering
-\caption{From real system verification to model checking (adapted from \cite{Clarke2008})}
+\caption{From real system verification to model checking (adapted from \cite{Clarke2008}).}
 \label{fig:systemverif}
@@
 It uses SAT solvers, where SAT means satisfiability.
-SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression.
+SAT problem is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression \cite{Clarke2008}.
 %SAT solvers are used in BMC, such that i
@@
 
-CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++, as can be seen in \cite{Kroening}.
+CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}.
 
@@
 \subsection{ESBMC }
-According \cite{GadelhaSBMF}, ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs. 
+ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs \cite{GadelhaSBMF}. 
 %The efficient SMT based model checker, is a software verification tool for C and C++ code bases. 
@@
 \centering
-\caption{ESBMC architecture (adapted from \cite{GadelhaSBMF})}
+\caption{ESBMC architecture (adapted from \cite{GadelhaSBMF}).}
 \label{fig:esbmcarch}
@@
 
-As shown by \cite{GadelhaSBMF}, ESBMC has two alternative front-ends to parse the input program.
+ESBMC has two alternative front-ends to parse the input program \cite{GadelhaSBMF}.
 % and generate an Abstract Syntax Tree (AST).
@@
 That characteristic is useful at this work to perform the sizing check of the PV system project.
-Following, the SSA expressions are then encoded using the chosen SMT solver supported by ESBMC. At this paper, it was used the Z3 solver as shown by \cite{DeMoura}.
+Following, the SSA expressions are then encoded using the chosen SMT solver supported by ESBMC. At this paper, it was used the Z3 solver \cite{DeMoura}.
 %: Boolector (default) \cite{Brummayer}, Z3 \cite{DeMoura}, MathSAT \cite{Cimatti}, Yices \cite{Dutertre} and CVC4 \cite{Barrett}.
@@
 %\centering
-%\caption{State transition diagram to the proposed framework}
+%\caption{State transition diagram to the proposed framework.}
 %\label{fig:statetransition}
@@
 The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the non-deterministic variables of the model, are all written as C Programming language code.
+
+, as illustrated in Fig.\ref{fig:flowchartgeneral}
+
+\begin{figure}[h]
+\includegraphics[width=0.4\textwidth]{flowchart_verification.png}
+\centering
+\caption{Flowchart of the proposed automated verification of PV systems.}
+\label{fig:flowchartgeneral}
+\end{figure}
 
@@
 
-\section{Results} \label{sec:results}
+%----------------------------------------------
+\section{Results and discussions} \label{sec:results}
+%----------------------------------------------
+
+\textcolor{red}{reorganise the results as follows: experimental objectives and setup; results; and threats to validity.}
+
+\textcolor{red}{https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf}
+
 %
@@
 %-------------------------------------
-\section{Related work }
-%-------------------------------------
-
-\textcolor{red}{This section needs more work. You should describe here studies related to the design, verification or validation of PV systems and not about software model checkers!}
-
-%The CBMC, it is notable its prominence through international awards received in competitions. 
-%In the works r
-Related to the CBMC, much of the research is focused on the improvement of the tool (performance mainly), without addressing, however, the question of PV system validation, as can be seen in \cite{Kroening}.
-% For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.
-
-%ESBMC was developed to perform bounded model checks on both sequential and concurrent programs using a range of SMT solvers, and has a proven track of bug finding in real-world applications \cite{Cordeiro}, \cite{Ramalho}.
-The tool also implements a technique to prove the correctness of (some) unbounded programs, the k-induction algorithm; this approach has been applied to a large number of benchmarks and has produced more correct results than similar competing tools \cite{GadelhaSBMF}, \cite{GadelhaK}.
-Related to ESBMC, \cite{Trindade} show that is possible to perform the partitioning of hardware-software (optimization).
-\cite{Bessa} show that is possible to use ESBMC to check the stability of digital control systems.
-In addition, \cite{Abateetal2017} show the approach to synthesize safe digital feedback controllers for physical plants.
-However, the use of ESBMC to verify PV systems is unprecedented.
-
-%Concerning modeling and simulation of 
-Concerning electrical energy systems, \cite{Kremers} used an agent-base model approach to evaluate the effect of loads, shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study.
-However, it was restrict to simulation, without the formalism of automated verification.
-%that is a software development approach for the simulation of complex systems, without the formalism of automated verification.
-
-%In the other hand, the use of formal verification related to modeling and validation or even simulation of power systems is a young theme of research.
-% According \cite{Abateetal2014}, where articles from seminars were issued at this thematic, the actual focus is on optimization and control of microgrids, HVAC systems (diagnostics and maintenance), models of generic wind turbine generation, modeling of transmission networks, and verification of smart grids.
-In addition, according with \cite{Abate2017}, recent research has attempted to formalize and implement a formal study of large population of PV panels.% (very common in European Union). 
- The focus have been the modeling of the dynamics of PV panels and their interaction with the grid, without batteries.
-%
-%Therefore, the present work unites the versatility and power of the formal models, applied to a formal verification tool, with individual PV systems (off-grid), which is the most indicated and common option to solve the problem of energy in developing countries.
-Especially those that have isolated communities, either for long distances of the great centers, or for being riverside.
-This work includes, based on its off-grid characteristic, batteries and charge controllers, differently of on-grid systems of related work.
-
-%-------------------------------------
-\section{Conclusions and Future Work}
+\section{Conclusion and Future Work}
 %-------------------------------------

### 2018-11-08 code/codePVsystem_rev9d.c

@@ -1,0 +1,547 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+---------------------------------------------------------------------by Alessandro Trindade, JUL-AGO 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.001 //0.0000000001
+#define precisionEXP 0.001 //0.00000001 
+
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+//case study at urban area of 915W of demand and 4.88 kWh of energy
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define Psurge 501
+  #define Econsumption 3900
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24  //controller voltage
+  #define Vsystem 24  //DCbus
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define Psurge 722
+  #define Econsumption 3600
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24  //controller voltage
+  #define Vsystem 24  //DCbus
+#elif HOUSE3
+  //Sandriane's house 263W and 2.5kWh
+  #define Phouse 263
+  #define Psurge 732
[…]

### 2018-11-09 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
text updating

@@
 \markboth{IEEE TRANSACTIONS ON SUSTAINABLE ENERGY,~VOL.~X, NO.~Y, MONTH~2018}
-{Trindade \MakeLowercase{\textit{et al.}}: BUILDING A FRAMEWORK TO PERFORM AUTOMATED VERIFICATION OF SOLAR PHOTOVOLTAIC OFF-GRID SYSTEMS}
+{Trindade \MakeLowercase{\textit{et al.}}: AUTOMATED VERIFICATION OF STAND-ALONE SOLAR PHOTOVOLTAIC SYSTEMS}
 % The only time the second header will appear is for the odd numbered pages
@@
 Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects.
-This paper aims to build a framework to apply an automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective.
-Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.
+This paper aims to apply an automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective.
+Data from practical application of solar systems prove the results obtained by the proposed approach, where specific conditions that cause fails of the photovoltaic solar system are only detected with the verification tool when compared with a simulation commercial tool.
+%Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.
 \textcolor{red}{Data from practical application of solar systems prove the results obtained by the proposed approach...
@@
 In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.
-And even general purpose simulations as MATLAB/Simulink.
+And even general purpose simulation tools as PSpice, Saber or MATLAB/Simulink package.
 
@@
 However, those tools are based on running experiments in simulation models.
-And simulation has the pros of be cheap and be employed before the system is declared concluded, however with the cons of an incomplete coverage, because the verification of all possible iterations and potential failures of systems is rarely pissible or feasible \cite{Clarke2008}.
+And simulation has the advantage of be cheap and be employed before the system is declared concluded, however with the drawback of an incomplete coverage, because the verification of all possible iterations and potential failures of systems is rarely pissible or feasible \cite{Clarke2008}.
 
@@
 %with behavior that is, in principle, well determined. 
- Using this technique, systems are specified as programs using mathematical logic, which constitutes the intended (correct) behavior.
+ Using this technique, any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior.
 Then, one can try to give a formal proof or otherwise establish that the program meets its specification.
+User or project requirements can be added during the process of coding.
 %, as defined by \cite{Trindade}.
@@
 %Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
- Algorithms can verify the system model by systematically exploring all their states.
-
-At this paper, mathematical models of each component of a stand-alone PV system, panel solar, charge controller, batteries, inverter, and load, are translated as a single software program.
-Those programs are viewed as mathematical objects, and the use of
+ And finally, algorithms can verify the system model by systematically exploring all their states. That way, the formal proof can verify if the requirements are met by the system.
+
+Formal methods, in the other hand, provide facilities for the modeling of each component of any complex system \cite{Hall1990}.
+It allows for developing models for each component of the system.
+At this paper, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.
+The behavior of each system can be analyzed and observed with the help of these formal models, as the joint operation of the components, which in this case represent the operation of the solar PV system.
+A key benefit to this approach is that it helps in the detection of faults and flaws in the design phase of system development, thereby considerably improving system reliability \cite{Akram2018}.
+
+%Those programs are viewed as mathematical objects, and the use of 
 %Bringing this technique to solar PV systems, i
@@
 %Here it will be verified a stand-alone PV system, with all their components modeled mathematically, 
-and then report in which conditions the system does not meet user requirements (as electrical load, power demand) or whether it will fail due to weather conditions and/or battery autonomy, for example.
+Related to solar PV systems, the project requirements, as state of charge of batteries and power demand, beside weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automated verified during the formal process.
+The process of model checking reports in which conditions the system does not met the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
 
@@
 
-Formal methods provide facilities for the modeling of each component of any complex system \cite{Hall1990}.
-It allows for developing models for each component of the system.
-The behavior of each system can be analyzed and observed with the help of these formal models.
-A key benefit to this approach is that it helps in the detection of faults and flaws in the design phase of system development, thereby considerably improving system reliability \cite{Akram2018}.
-
-In previous studies, 
-%%%%%%%
-%%%%%%%%
-\textcolor{red}{This section needs more work. You should describe here studies related to the design, verification or validation of PV systems and not about software model checkers!}
-
-%The CBMC, it is notable its prominence through international awards received in competitions. 
-%In the works r
-Related to the CBMC, much of the research is focused on the improvement of the tool (performance mainly) \cite{Kroening}, without addressing, however, the issue of PV system validation.
-% For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.
-
-%ESBMC was developed to perform bounded model checks on both sequential and concurrent programs using a range of SMT solvers, and has a proven track of bug finding in real-world applications \cite{Cordeiro}, \cite{Ramalho}.
-The tool also implements a technique to prove the correctness of (some) unbounded programs, the k-induction algorithm; this approach has been applied to a large number of benchmarks and has produced more correct results than similar competing tools \cite{GadelhaSBMF}, \cite{GadelhaK}.
-Related to ESBMC, it is possible to perform the partitioning of hardware-software (optimization) \cite{Trindade}.
-And it is possible to use ESBMC to check the stability of digital control systems \cite{Bessa}.
-In addition,  there is the approach to synthesize safe digital feedback controllers for physical plants \cite{Abateetal2017}.
-However, the use of ESBMC to verify PV systems is unprecedented.
-
-%Concerning modeling and simulation of 
-Concerning electrical energy systems,  there is the use of agent-base model approach to evaluate the effect of loads, shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study \cite{Kremers}.
-However, it was restrict to simulation, without the formalism of automated verification.
-%that is a software development approach for the simulation of complex systems, without the formalism of automated verification.
-
-%In the other hand, the use of formal verification related to modeling and validation or even simulation of power systems is a young theme of research.
-% According \cite{Abateetal2014}, where articles from seminars were issued at this thematic, the actual focus is on optimization and control of microgrids, HVAC systems (diagnostics and maintenance), models of generic wind turbine generation, modeling of transmission networks, and verification of smart grids.
-In addition, recent research has attempted to formalize and implement a formal study of large population of PV panels.% (very common in European Union). 
- The focus have been the modeling of the dynamics of PV panels and their interaction with the grid, without batteries \cite{Abate2017}.
-%
-%Therefore, the present work unites the versatility and power of the formal models, applied to a formal verification tool, with individual PV systems (off-grid), which is the most indicated and common option to solve the problem of energy in developing countries.
-Especially those that have isolated communities, either for long distances of the great centers, or for being riverside.
-This work includes, based on its off-grid characteristic, batteries and charge controllers, differently of on-grid systems of related work.
-
-%%%%%%%%
-%%%%%%%%
+In mostly of previous studies, the evaluation of PV systems, concerning the meeting of user requirements, were performed by software simulation using MATLAB/Simulink \cite{Benatiallah2017}, \cite{Samrat2014}, and \cite{Natsheh2012} or HOMER Pro \cite{Lamnadi2017}.
+Some work was done toward the formal modeling of power smart grids \cite{Akram2018}, and to maximize the power point of solar panels \cite{Driouich2017}, however without to perform the automated verification and restrict to solar panels or smart grids.
+
+In addition, recent research that joint the formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels where the focus have been the modeling of the dynamics of PV panels and their interaction with the grid, without batteries \cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool \cite{Driouich2018}.
+Both restrict to the PV panels, and not including batteries, inverters, and charge controllers.
 
@@
 %n SMT-based 
-verification tool to solve this kind of problem. That is the main contribution of this paper.
+verification tool to evaluate a stand-alone solar PV systems, with weather conditions variation.
+The mains contribution of this paper are the automated verification of the PV system, and the modular modeling of each component of the PV system, which permits to change the mathematical models, besides changing the type of energy generation in the future to another renewable source, for example.
 
@@
 
-\textcolor{red}{This section is too short! You should move it to another big section...}
-
 %According to \cite{Roy}, a 
-A PV system is designed to give the electric supply to a load.
+%A PV system is designed to give the electric supply to a load.
 This load can be either Alternate Current (AC) or Direct Current (DC) type.
@@
 %(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
-For night hours or rainy days, one needs to hold batteries, where power can be stored and used.% \cite{Gules}.
+%For night hours or rainy days, one needs to hold batteries, where power can be stored and used.% \cite{Gules}.
 
@@
 %can be split into several categories. However, 
-the configuration that is most common nowadays is the regulated stand-alone system with battery and AC load. This configuration includes PV array, batteries, charge controller, inverter, and AC load.
+the configuration that is most common nowadays is the regulated stand-alone system with battery and AC load.
+This configuration, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
 %PV array, battery, MPPT and AC load.
@@
 
-\subsection{Design and Validation of a Solar photovoltaic system}
+\subsection{Design and Simulation of Solar PV systems}
 %The design and validation of a PV system can be done by hand or with the aid of a software tool. 
@@
 
-In the literature, there are several mathematical models available for each component of PV systems. In this section, the mathematical model for each component is presented.
+In the literature, there are several mathematical models available for each component of PV systems. At the next section, the mathematical model for each component is presented.
 

### 2018-11-10 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
text updating

@@
 
-%However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.  
+%However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
 %
@@
 %
-%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a PV off-grid system, using the satisfiability modulo theories (SMT)-based verification method.
+%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
 
@@
 
-PV systems are broadly classified into three distinct types \cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system, where another source(s) of energy can work together with the solar PV.
+PV systems are broadly classified into three distinct types \cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system.
+%, where another source(s) of energy can work together with the solar PV.
 % system to provide the required demand.
@@
 %\end{itemize}
-
 Specifically concerning isolated communities, 
@@
 %can be split into several categories. However, 
-the configuration that is most common nowadays is the regulated stand-alone system with battery and AC load.
-This configuration, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
+the configuration that is most common is the regulated stand-alone system with battery and AC load. This configuration is the focus of this paper.
+%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
 %PV array, battery, MPPT and AC load.
@@
 additionally, HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis.
-However, only paid version of those tools have all the features \textcolor{red}{which features?}, and they run only on Windows operating system.
+However, only paid version (restrict to the Microsoft Windows Operational System) of those tools have all the features, as to save the the project or to upload data from manufacturers.
 RETScreen and HOMER have a free web-based version, but they have limited resources.
@@
 %-------------------------------------------------------------------
-\subsection{Paper Proposal x Reference Tools}
+%\subsection{Paper Proposal x Reference Tools}
 %-------------------------------------------------------------------
-
-Considering the focus of this paper, only HOMER remains for our comparative evaluation.
-All tools need some parameters inherently from manufacturer's catalog \textcolor{red}{is this the correct term?
-to size the system}.
+%
+Considering the focus of this paper, only HOMER remains for a comparative with the proposed tool of this paper. %All tools need some parameters inherently from manufacturer's catalog.
 %, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
-After that, the potential solution is analyzed in another tool to validate or even optimize the solution.
-Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than other state-of-the-art tools \textcolor{red}{cite them here...}.
+%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
+And the challenge of this work is to prove that is possible to use automated verification in stand-alone PV solution and to prove that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro.
 The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section \ref{sec:results}.
@@
 %The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
-The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram} \textcolor{red}{you should explain each element of the figure}.
-The modular structure facilitates the modeling of the other system structures and replacement of elements such as a DC load instead of an AC load.
-
+The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
+It is identified the PV generator, batteries, charge controller, inverter, and AC load.
+
+The PV generator, which can be an panel or a array, is a semiconductor device that can convert solar energy into DC electricity.
+At the diagram, there are two variables that depend on the site where the system is deployed and from the weather (solar irradiance $ G $ and temperature $ T $).
+For night hours or rainy days, one needs to hold batteries, where power can be stored and used.
+The use of battery as a storage form implies thus the presence of a charge controller \cite{Hansen}, \cite{Mellit}.
+The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
+That converter is called of inverter.
+And the AC load dictates the behavior of electrical load from the house that will be feed by the system.
+%
+%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
+%
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{blockdiagramPVS}
+\includegraphics[width=0.48\textwidth]{blockdiagramPVS}
 \centering
@@
 
-In the literature, there are several mathematical models available for each component of PV systems. At the next section, the mathematical model for each component is presented.
+%In the literature, there are several mathematical models available for each component of PV systems. At the next section, the mathematical model for each component is presented.
 
@@
 %
-The basic element of a PV system is a PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
+%%%%%%The basic element of a PV system is a PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
 %The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
@@
 If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
-To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
-package called panel or module.
+%%%%%To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
+%%%%%package called panel or module.
 
@@
 %
-The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on meteorological conditions.
+%%%%%The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on meteorological conditions.
 %the meteorological conditions of the area to be serviced by PV solution. %However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
@@
 %
-%As an example of this formula application, as shown by \cite{Abdulateef}, considering that an off-grid PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
+%As an example of this formula application, as shown by \cite{Abdulateef}, considering that a stand-alone PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
 %
@@
 
-%The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
+%The number of controllers required for the stand-alone PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
 In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
@@
 %Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled.
-Then a model checking will be performed to do a verification of the project in order to guarantee that the design of an off-grid PV solution will meet the requirements, specifications and regulations.
+Then a model checking will be performed to do a verification of the project in order to guarantee that the design of a stand-alone PV solution will meet the requirements, specifications and regulations.
 %
@@
 %
-%Fig. \ref{fig:statetransition} shows the state diagram for the proposed framework. 
+%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
 %
@@
 %\centering
-%\caption{State transition diagram to the proposed framework.}
+%\caption{State transition diagram to the proposed automated verification.}
 %\label{fig:statetransition}
@@
 And related to the four 700 W PV system, the sizing check was successful, but there were  found flaws in everyone, all related with the SOC that reached levels below of 75\%.
-The framework identified the flaws right after the first night-discharge cycle, before dawn, and before the system start to recharge the batteries.
-The framework took 409.3 hours to find an error at house 1, and the maximum of 456XXX hours to house 4.
+The automated verification identified the flaws right after the first night-discharge cycle, before dawn, and before the system start to recharge the batteries.
+The proposed tool took 409.3 hours to find an error at house 1, and the maximum of 456XXX hours to house 4.
 
@@
 
-%The proposed framework seems to be a coherent and promising tool to perform verification of a PV project.
+%The proposed tool seems to be a coherent and promising tool to perform verification of a PV project.
 The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field.
 %
-%The framework presented here establishes the automated verification and the project sizing check. 
-It was shown that, beside the time-consuming issue of the proposed framework, it overcomes the results of off-the-shelf tool that only simulate the results.
-The framework was successful in find sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
+%The automated verification tool presented here establishes the automated verification and the project sizing check. 
+It was shown that, beside the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results.
+The proposed tool was successful in find sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
 %However, it is possible to perform the optimum sizing of the PV system. Moreover, 
@@
 That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system.
-Next, the framework will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is find from the inputs.
+Next, the proposed tool will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is find from the inputs.
 This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.
 
-Furthermore, it is possible to contemplate other kinds of renewable energy and even hybrid ones, which can evolve the framework into a complete tool for design and verification for rural electrification.
+Furthermore, it is possible to contemplate other kinds of renewable energy and even hybrid ones, which can evolve the algorithm into a complete tool for design and verification for rural electrification.
 % into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.
@@
 \section*{Acknowledgment}
-The authors would like to thank Newton Fund (Star Energy project), Coventry University, Sustainable Amazonas Foundation (FAS), and FAPEAM (Amazonas State Foundation for Research Support), for the financial support and for the possibility to test the framework with real PV systems.
-
-\textcolor{red}{You should revise all references according to the journal guideline.}
+The authors would like to thank Newton Fund (Star Energy project), Coventry University, Sustainable Amazonas Foundation (FAS), and FAPEAM (Amazonas State Foundation for Research Support), for the financial support and for the possibility to test the tool with real PV systems.
 
@@
 %\fi
-
 % trigger a \newpage just before the given reference

### 2018-11-11 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper updating

@@
 However, those tools are based on running experiments in simulation models.
-And simulation has the advantage of be cheap and be employed before the system is declared concluded, however with the drawback of an incomplete coverage, because the verification of all possible iterations and potential failures of systems is rarely pissible or feasible \cite{Clarke2008}.
+And simulation has the advantage of be cheap (when compared to test in real systems) and can be employed before the system is declared concluded, however with the drawback of an incomplete coverage, because the verification of all possible iterations and potential failures of systems is rarely pissible or feasible \cite{Clarke2008}.
 
@@
 At this paper, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.
-The behavior of each system can be analyzed and observed with the help of these formal models, as the joint operation of the components, which in this case represent the operation of the solar PV system.
+The behavior of each system can be analyzed and observed with the help of these formal models, as the joint operation of the components, which in this case represent the operation of the solar PV system itself.
 A key benefit to this approach is that it helps in the detection of faults and flaws in the design phase of system development, thereby considerably improving system reliability \cite{Akram2018}.
@@
 %Here it will be verified a stand-alone PV system, with all their components modeled mathematically, 
-Related to solar PV systems, the project requirements, as state of charge of batteries and power demand, beside weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automated verified during the formal process.
-The process of model checking reports in which conditions the system does not met the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
+Related to solar PV systems, the project requirements, as battery autonomy and power demand, beside weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automated verified during the formal process.
+The model checking tool reports in which conditions the system does not met the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
 
@@
 In addition, recent research that joint the formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels where the focus have been the modeling of the dynamics of PV panels and their interaction with the grid, without batteries \cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool \cite{Driouich2018}.
-Both restrict to the PV panels, and not including batteries, inverters, and charge controllers.
+Both restrict to PV panels, and not including batteries, inverters, and charge controllers.
 
@@
 %can be split into several categories. However, 
-the configuration that is most common is the regulated stand-alone system with battery and AC load. This configuration is the focus of this paper.
+the configuration that is most common or mode indicated is the regulated stand-alone system with battery and AC load. This configuration is the focus of this paper.
 %, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
@@
 %
-Considering the focus of this paper, only HOMER remains for a comparative with the proposed tool of this paper. %All tools need some parameters inherently from manufacturer's catalog.
+Considering the focus of this paper, only HOMER remains for a comparative with the proposed automated verification technique of this paper.
+%All tools need some parameters inherently from manufacturer's catalog.
 %, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
 %After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-And the challenge of this work is to prove that is possible to use automated verification in stand-alone PV solution and to prove that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro.
+And the challenge of this work is to show that is possible to use automated verification in stand-alone PV solution, proving that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro.
 The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section \ref{sec:results}.
@@
 
-The PV generator, which can be an panel or a array, is a semiconductor device that can convert solar energy into DC electricity.
+The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
 At the diagram, there are two variables that depend on the site where the system is deployed and from the weather (solar irradiance $ G $ and temperature $ T $).
@@
 That converter is called of inverter.
-And the AC load dictates the behavior of electrical load from the house that will be feed by the system.
+And the AC load dictates the behavior of AC electrical load from the house that will be feed by the system.
 %
@@
 
-The performance of photovoltaic systems, %that is, the output current/voltage curve ($I-V$ curve), 
+The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
 is usually studied using an equivalent circuit model, as described in the available literature \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
@@
 
-Where: $I_{ph}$ is the photocurrent delivered by the constant current source; $ I_{0} $ is the reverse saturation current corresponding to the diode; $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed ($ N=1 $ in a single cell configuration); $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
+Where: $I_{ph}$ is the photocurrent delivered by the constant current source; $ I_{0} $ is the reverse saturation current corresponding to the diode; $ N $ is the number of series-connected cells in the PV system to be analyzed ($ N=1 $ in a single cell configuration); $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
 
@@
 However, there is a main disadvantage of model checking: the state explosion problem. 
-
-The model checking problem can be defined as \cite{Clarke2008}:
-
-\begin{itemize}
-\item Let $M$ be a Kripke structure (i.e., state transition graph);
-\item $f$ be the specification in temporal logic (a formula);
-\item Find all states $s$ of $M$ such that $M , s \models f$
-\end{itemize}
+%
+%The model checking problem can be defined as \cite{Clarke2008}: 
+%
+%\begin{itemize}
+%\item Let $M$ be a Kripke structure (i.e., state transition graph);
+%\item $f$ be the specification in temporal logic (a formula);
+%\item Find all states $s$ of $M$ such that $M , s \models f$
+%\end{itemize}
 
@@
 In a typical model checking system, a preprocessor extracts a state transition graph from a system (program or circuit).
-
+%
 %\begin{figure}[h]

### 2018-11-11 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper updating

@@
 
-Where: $I_{ph}$ is the photocurrent delivered by the constant current source; $ I_{0} $ is the reverse saturation current corresponding to the diode; $ N $ is the number of series-connected cells in the PV system to be analyzed ($ N=1 $ in a single cell configuration); $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
+Where: $I_{ph}$ is the photocurrent delivered by the constant current source; $ I_{0} $ is the reverse saturation current corresponding to the diode; $ N $ is the number of series-connected cells in the PV system to be analyzed ($ N=1 $ in a single cell configuration); $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $ T $ the temperature of the p-n junction (or cell temperature) in Kelvin; $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
 
@@
 
-The voltage and the current at the maximum power point and consequently the maximum output power, can be expressed by (\ref{eq:Vmfinal}), (\ref{eq:Imfinal}), and (\ref{eq:Pm}) \cite{Saloux}.
+The voltage and the current at the maximum power point tracking (MPPT), can be expressed by (\ref{eq:Vmfinal}), (\ref{eq:Imfinal}), and (\ref{eq:Pm}) \cite{Saloux}.
 %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
@@
 %The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current (\ref{eq:Pm}) and the saturation current in the reference temperature given by (\ref{eq:I0}), the diode quality (or ideality) coefficient is determined by (\ref{eq:a}).
+Using the maximum power point current (\ref{eq:Pm}) and the saturation current in the reference temperature given by (\ref{eq:I0}), the diode ideality factor is determined by (\ref{eq:a}).
 \begin{equation}
@@
 
-Besides the model verification, there is the prior stage of project sizing check, which is simple, based on manufacturer's data and information from the sizing and the site.
+Besides the model verification, there is the prior stage of project sizing check, based on manufacturer's data and information from the sizing and the site.
 
@@
 %, and \cite{Manwell94}. 
-However, regardless of the model, normally the following parameters are required:
-
-\begin{itemize}
-\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
+%However, regardless of the model, normally the following parameters are required: 
+%
+%\begin{itemize}
+%\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
 %, under predetermined discharge conditions.
-\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
+%\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
 %Obviously $ 0<SOC<1 $. 
-If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
+%If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
 %\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
 %It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
-\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
+%\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
 %\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
-\end{itemize}
-
+%\end{itemize}
+%
 %The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
@@
 %
-Most of the created models were used to simulate and optimize PV storage system based on lead-acid batteries.
-That kind of battery is the most common used batteries in PV application, owing to their relative low cost and wide availability \cite{Copetti}.
-
-Here, the model adopted \cite{Copetti} uses manufacturer's data and allows finding relations among voltage, current, state of charge and temperature.
-
+Most of the created models were based on lead-acid batteries. That kind of battery is the most common used in PV application, owing to their relative low cost and wide availability \cite{Copetti}.
+
+Here, the model adopted \cite{Copetti} uses manufacturer's data. % and allows finding relations among voltage, current, state of charge and temperature. 
+%
 The discharge voltage equation is shown in (\ref{eq:bat_Vd}). 
@@
 
-Where $ C_{10} $ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $ \Delta T $ is temperature variation ($ \Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $).
-%, $ SOC $ indicates how much electric charge is stored in the cell at given time, defined by Equation \ref{eq:SOCbat}.
+Where $ C_{10} $ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $ \Delta T $ is temperature variation ($ \Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at given time.
+Mathematically, is the ratio between the present capacity and the nominal capacity (in $ Ah $, provided by manufacturer).
+If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged.
+%, defined by Equation \ref{eq:SOCbat}.
 %\begin{equation}
@@
 %The ratio between $ Q $ and $ C $ represents t
-
 The depth of discharge ($ DOD $) or the fraction of discharge, is $ DOC=1-SOC $.
@@
 
-SOC can be calculated easily at any point during the discharge period; however, during recharge it is much more difficult \cite{Copetti}.
+SOC can be calculated easily at any point during the discharge period, considering the current drained from batteries during a certain time period.
+%; however, during recharge it is much more difficult \cite{Copetti}.
 %Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell.
@@
 %\cite{Copetti} show that, 
-During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (\ref{eq:Vec}).
+%During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (\ref{eq:Vec}).
 It was created a function for the gassing voltage as well, as shown in (\ref{eq:Vg}).
 In addition, the overcharge phenomenon can be represented by (\ref{eq:Voverc}).
-\begin{equation}
-\label{eq:Vec}
-V_{ec} = \left[ 2.45 + 2.011 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-\end{equation}
-
-\begin{equation}
-\label{eq:Vg}
-V_{g} = \left[ 2.24 + 1.97 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-\end{equation}
-
-\begin{multline}
-\label{eq:Voverc}
-V_{c} = V_{g} + (V_{ec} - V_{g}) \\ \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
-\end{multline}
-
-Where $ Ah_{restored} $ represents the Ampere-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
-
-The function assumes that 95\% of the capacity was already restored at the start of overcharge.
-
-The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by (\ref{eq:tau}).
-\begin{equation}
-\label{eq:tau}
-\tau = \dfrac{17.3}{1+852 \left( \dfrac{I}{C_{10}} \right) ^{1.67} }
-\end{equation}
-
-Therefore, to model the voltage ($ V_{c} $) evolution of the battery, (\ref{eq:Vcbat}) can be used up the start of gassing ($ V_{c} \leq V_{g} $).
+%\begin{equation}
+%\label{eq:Vec}
+%V_{ec} = \left[ 2.45 + 2.011 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
+%\end{equation}
+%
+%\begin{equation}
+%\label{eq:Vg}
+%V_{g} = \left[ 2.24 + 1.97 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
+%\end{equation}
+%
+%\begin{multline}
+%\label{eq:Voverc}
+%V_{c} = V_{g} + (V_{ec} - V_{g}) \\ \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
+%\end{multline}
+%
+%Where $ Ah_{restored} $ represents the Ampere-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
+%
+%The function assumes that 95\% of the capacity was already restored at the start of overcharge.
+%
+%The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by (\ref{eq:tau}).
+%\begin{equation}
+%\label{eq:tau}
+%\tau = \dfrac{17.3}{1+852 \left( \dfrac{I}{C_{10}} \right) ^{1.67} }
+%\end{equation}
+%
+%Therefore, to model the voltage ($ V_{c} $) evolution of the battery, (\ref{eq:Vcbat}) can be used up the start of gassing ($ V_{c} \leq V_{g} $).
 And during overcharging ($ V_{c} > V_{g} $), (\ref{eq:Voverc}) can be used until a constant final voltage ($ V_{ec} $) is reached.
-
+%
 %The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
@@
 
-The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power.
+%The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+%MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power.
 Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
@@
 
-The controller allows the management of energy between the load and the battery \cite{Mellit}. 
+%The controller allows the management of energy between the load and the battery \cite{Mellit}. 
 %The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
@@
 The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage, % (127 V or 220 V, for example), 
-and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency \cite{Hansen}.
-
-The inverter is characterized by a power dependent efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
+and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
+%
+%The inverter is characterized by a power dependent efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
 \begin{equation}
@@
 %It is necessary to keep in mind that 
-Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.
+Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations \cite{Clarke2008}.
 
@@
 %
-The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the non-deterministic variables of the model, are all written as C Programming language code.
-
-, as illustrated in Fig.\ref{fig:flowchartgeneral}
+The flowchart of the automated verification proposed is illustrated in Fig.\ref{fig:flowchartgeneral}. 
+The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as C Programming language code.
 
@@
 
-The non-deterministic variables (solar irradiance, and ambient temperature by default) will suffer a heavy test at ESBMC run-time execution.
+The weather data (solar irradiance, and ambient temperature by default) will suffer a heavy test at ESBMC run-time execution, based in maximum and minimum values from the site where the PV system will be deployed.
 In addition, depending if one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system, is not accomplished or satisfied, the tool accuses a fail, and the diagnostic counterexample shows in which condition the fail/violation happened.
@@
 %----------------------------------------------
-
-\textcolor{red}{reorganise the results as follows: experimental objectives and setup; results; and threats to validity.}
-
-\textcolor{red}{https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf}
-
+%
+%\textcolor{red}{reorganise the results as follows: experimental objectives and setup; results; and threats to validity.}
+%
+%\textcolor{red}{https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf}
+%
+\subsection{Experimental objectives and setup}
+Experimental objectives: To evaluate the proposed verification methodology and the respective tool performance, in a comparative with the HOMER Pro tool in five case studies (described in Methodology section).
+Using functional information collected from owners of those five systems, which were deployed in 2018, serving as cross data about how the systems are behaving during four months of use.
 %
@@
 %\label{sec:setup}
-All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-
-Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter in order to reduce the memory usage. And regarding the solver, version 4.7.1 of Z3 was used.
-
+
+Experimental setup of automated verification tool: all experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
+Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter in order to reduce the memory usage.
+And regarding the solver, version 4.7.1 of Z3 was used.
+
+Experimental setup of HOMER Pro: all experiments were conducted on an otherwise idle Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10.
+It was used the version 3.12.0 of Homer Pro.
+
+\subsection{Results}
 The total were five case studies evaluated by HOMER Pro and by the automated verification tool.
-Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shown that the restrictions were met by the five systems, without any indication of sizing error or even of performance.
+Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shown that the restrictions were met by four systems, without any indication of sizing error or even of performance.
+The case study that was not successful during simulation was the 1,200 W (house 5), however without indication what are the fail of this PV system.
+All the simulations took less than 5 seconds (each) to be performed.
 
@@
 
-And related to the four 700 W PV system, the sizing check was successful, but there were  found flaws in everyone, all related with the SOC that reached levels below of 75\%.
-The automated verification identified the flaws right after the first night-discharge cycle, before dawn, and before the system start to recharge the batteries.
+And related to the four 700 W PV system, the sizing check was successful during automated verification, but there were found flaws in everyone, all related with the battery autonomy, when SOC reached levels below of 75\%.
+The automated verification identified the flaws right after the first night-discharge cycle, before the solar system start to recharge the batteries.
 The proposed tool took 409.3 hours to find an error at house 1, and the maximum of 456XXX hours to house 4.
+This functional problem was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
 

### 2018-11-12 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper updating

@@
 %n SMT-based 
-verification tool to evaluate a stand-alone solar PV systems, with weather conditions variation.
+verification tool to evaluate a stand-alone solar PV systems. %, with weather conditions variation. 
 The mains contribution of this paper are the automated verification of the PV system, and the modular modeling of each component of the PV system, which permits to change the mathematical models, besides changing the type of energy generation in the future to another renewable source, for example.
@@
 %\end{itemize}
-Specifically concerning isolated communities, 
+Specifically concerning the energy need for remote rural areas of developing countries or places where the grid extension is not possible or feasible, 
 %stand-alone systems are one the most used solutions, and 
@@
 HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options.
-Since 2016 Homer Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available.
+Since 2016 HOMER Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available.
 At the short-time only the commercial version will remain.
@@
 
-Where: $I_{ph}$ is the photocurrent delivered by the constant current source; $ I_{0} $ is the reverse saturation current corresponding to the diode; $ N $ is the number of series-connected cells in the PV system to be analyzed ($ N=1 $ in a single cell configuration); $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $ T $ the temperature of the p-n junction (or cell temperature) in Kelvin; $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
+Where: $I_{ph}$ is the photocurrent delivered by the constant current source; $ I_{0} $ is the reverse saturation current corresponding to the diode; $ N $ is the number of series-connected cells ($ N=1 $ in a single cell configuration); $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $ T $ the temperature of the p-n junction (or cell temperature) in Kelvin; $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
 
@@
 
-Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at reference conditions (provided by PV manufacturers).
-$ I_{ph,ref} $ can also be approximated to the reference short-circuit current \cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
+Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions
+(provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
 
@@
 With the check done by (\ref{eq:NPS}) and (\ref{eq:NPP}).
-$ V_{system} $ is the DC voltage of the bus, and is a design decision, normally 12, 24 or 48 V.
+$ V_{system} $ is the DC voltage of the bus, normally 12, 24 or 48 V.
 \begin{equation}
@@
 
-Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter, when all the other values are known.
+Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
 
@@
 % caused by the state explosion inherent of the technique, 
-the 24h-day was divided, at the algorithm, in 3 parts of 8 h each (8:00h-16:00h, 16:00h-24:00h, 00:00h-8:00h); and only the 8:00h-16:00h period with PV generation. 
+the 24h-day was divided, at the algorithm, in 3 parts of 8 h each (8:00h-16:00h, 16:00h-24:00h, and 00:00h-8:00h); and only the 8:00h-16:00h period with PV generation.
+The time step was adjusted to 1 hour.
 % and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
@@
   \\
-  \COMMENT {Perform the 08:00h-16:00h \textbf{for}-LOOP as above}
+  \COMMENT {Perform same 08:00h-16:00h \textbf{for}-LOOP as line 6}
   %%\ENDFOR
@@
 %Subsection text here.
-
 % needed in second column of first page if using \IEEEpubid
 %\IEEEpubidadjcol
-
 %\subsubsection{Subsubsection Heading Here}
 %Subsubsection text here.
-
 % An example of a floating figure using the graphicx package.
@@
 %\end{figure}
-
+%
 % Note that the IEEE typically puts floats only at the top, even when this
 % results in a large percentage of a column being occupied by floats.
-
+%
+%
 % An example of a double column floating figure using two subfigures.
@@
 % e.g., \subfloat[].
-
+%
+%
 % An example of a floating table. Note that, for IEEE style tables, the
@@
 %\end{table}
-
+%
 % Note that the IEEE does not put floats in the very first column
@@
 Experimental setup of HOMER Pro: all experiments were conducted on an otherwise idle Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10.
-It was used the version 3.12.0 of Homer Pro.
+It was used the version 3.12.0 of HOMER Pro.
 
@@
 However, related to the results of the automated verification, the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was not correct (the verification indicates 3 panels in parallel and the project has 2 in series and 2 in parallel).
+The number of panels was not correct (the verification counterexample demands 3 panels in parallel and the project size has 2 in series and 2 in parallel).
 That verification took 63.3 hours to be performed.
@@
 
-And related to the four 700 W PV system, the sizing check was successful during automated verification, but there were found flaws in everyone, all related with the battery autonomy, when SOC reached levels below of 75\%.
+Related to the four 700 W PV systems, the sizing check was successful during automated verification, but there were found flaws in everyone, all related with the battery autonomy, when SOC reached levels below of 75\%.
 The automated verification identified the flaws right after the first night-discharge cycle, before the solar system start to recharge the batteries.
@@
 %-------------------------------------
-
 %The proposed tool seems to be a coherent and promising tool to perform verification of a PV project.

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-With declining costs and increasing performance, the deployment of renewable energy in off-grid systems is growing in both developed and developing countries, with particular emphasis on solar photovoltaic systems.
+With declining costs and increasing performance, the deployment of renewable energy in \textcolor{red}{What is the difference between off-grid and stand-lone?
+In the title you mention stand-alone and in the abstract you mention off-grid...
+please keep a standard...} off-grid systems is growing in both developed and developing countries, with particular emphasis on solar photovoltaic systems.
 Electrification of rural areas can improve the education standard, health conditions, and also the life of that population.
 In addition, depending on the country geography, using renewable energy sources in off-grid mode is a feasible solution if compared to a grid extension.
-Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects.
+\textcolor{red}{half of your abstract is about the context...
+you should reduce it a bit further..} Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects.
 This paper aims to apply an automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective.
-Data from practical application of solar systems prove the results obtained by the proposed approach, where specific conditions that cause fails of the photovoltaic solar system are only detected with the verification tool when compared with a simulation commercial tool.
+Data from practical application of solar systems prove the results obtained by the proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the verification tool if compared to a simulation tools.
 %Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{A}{ccording} to \cite{Coelho}, there are presently 1.3 billion people with no access to electricity worldwide. 
+\IEEEPARstart{A}{ccording} to Coelho et al.~\cite{Coelho}, there are presently 1.3 billion people with no access to electricity worldwide. 
 %The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
@@
 The increase in the number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researchers and practitioners involved in their application.
-In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.
-And even general purpose simulation tools as PSpice, Saber or MATLAB/Simulink package.
+In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \textcolor{red}{Add citation to all those tools}.
+And even general purpose simulation tools as PSpice, Saber or MATLAB/Simulink package \textcolor{red}{Add citation to all those tools}.
 
@@
 However, those tools are based on running experiments in simulation models.
-And simulation has the advantage of be cheap (when compared to test in real systems) and can be employed before the system is declared concluded, however with the drawback of an incomplete coverage, because the verification of all possible iterations and potential failures of systems is rarely pissible or feasible \cite{Clarke2008}.
-
-Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process \cite{Clarke2008}.  
+Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded; however, it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of systems is rarely possible or even feasible~\cite{Clarke2008}.
+
+Formal methods based on software model checking offer great potential to obtain a more effective and faster verification in the design process~\cite{Clarke2008}.  
 %with behavior that is, in principle, well determined. 
@@
 %Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
- And finally, algorithms can verify the system model by systematically exploring all their states. That way, the formal proof can verify if the requirements are met by the system.
-
-Formal methods, in the other hand, provide facilities for the modeling of each component of any complex system \cite{Hall1990}.
-It allows for developing models for each component of the system.
-At this paper, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.
-The behavior of each system can be analyzed and observed with the help of these formal models, as the joint operation of the components, which in this case represent the operation of the solar PV system itself.
-A key benefit to this approach is that it helps in the detection of faults and flaws in the design phase of system development, thereby considerably improving system reliability \cite{Akram2018}.
+Finally, model checking algorithms can verify the system model by systematically exploring all their states. That way, the formal proof can verify if the requirements are met by the system.
+
+Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}.
+It allows one to develop models for each component of the system.
+At this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.
+The behavior of each system can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+A key benefit to this approach is that it helps in the detection of faults and flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
 
@@
 %Here it will be verified a stand-alone PV system, with all their components modeled mathematically, 
-Related to solar PV systems, the project requirements, as battery autonomy and power demand, beside weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automated verified during the formal process.
-The model checking tool reports in which conditions the system does not met the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
+Related to solar PV systems, the project requirements, as battery autonomy and power demand, beside weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
+The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
 
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the
-% ideas will be 
-proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC) %tool that uses the front-end of the C Bounded Model Checker (CBMC) or the clang-based front-end, 
- which allows one to formally verify the PV system as a C program.
-
-In mostly of previous studies, the evaluation of PV systems, concerning the meeting of user requirements, were performed by software simulation using MATLAB/Simulink \cite{Benatiallah2017}, \cite{Samrat2014}, and \cite{Natsheh2012} or HOMER Pro \cite{Lamnadi2017}.
-Some work was done toward the formal modeling of power smart grids \cite{Akram2018}, and to maximize the power point of solar panels \cite{Driouich2017}, however without to perform the automated verification and restrict to solar panels or smart grids.
-
-In addition, recent research that joint the formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels where the focus have been the modeling of the dynamics of PV panels and their interaction with the grid, without batteries \cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool \cite{Driouich2018}.
-Both restrict to PV panels, and not including batteries, inverters, and charge controllers.
+The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC), which allows one to formally verify a PV system as a C program.
+
+In most prior studies, the evaluation of PV systems, concerning the meeting of user requirements, were performed by software simulation tools using MATLAB/Simulink \cite{Benatiallah2017}, \cite{Samrat2014}, and \cite{Natsheh2012} or HOMER Pro \cite{Lamnadi2017}.
+Some studies were carried out toward the formal modeling of power smart grids \cite{Akram2018}, and to maximize the power point of solar panels \cite{Driouich2017}; however, those studies do not perform automated verification and they restrict themselves to solar panels or smart grids.
+
+In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus have been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
+Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.
 
 %The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
-To the best of our knowledge, this is the first work to use a
-%n SMT-based 
-verification tool to evaluate a stand-alone solar PV systems. %, with weather conditions variation. 
-The mains contribution of this paper are the automated verification of the PV system, and the modular modeling of each component of the PV system, which permits to change the mathematical models, besides changing the type of energy generation in the future to another renewable source, for example.
+To the best of our knowledge, this is the first initiative to use a verification tool to evaluate a stand-alone solar PV systems. %, with weather conditions variation. 
+The mains contribution of this paper are the automated verification of the PV system, and the modular modeling of each component of the PV system, which allows one to change the mathematical models, besides changing the type of energy generation in the future to another renewable source.
 
@@
 
-The remainder of this paper is organized as follows: Section II gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
-Section III presents the automated verification technique.
-The methodology is presented at section IV.
-Section V is devoted to the results.
-Section VI presents the conclusion and describes future work.
+\textit{Outline}.
+Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
+Section~\ref{sec:AutomatedVerification} presents the automated verification technique.
+The methodology is presented at section~\ref{sec:Methodology}.
+Section~\ref{sec:results} is devoted to the results.
+Section~\ref{sec:Conclusions} presents the conclusion and describes future work.
 
@@
 \section{Solar Photovoltaic System }
+\label{sec:SolarPhotovoltaicSystem}
 %--------------------------------------------------------
@@
 
+%--------------------------------------------------
 \section{Automated verification}
+\label{sec:AutomatedVerification}
+%--------------------------------------------------
+
 %It is necessary to keep in mind that 
@@
 %
+%----------------------------------------
 \section{Methodology }
+\label{sec:Methodology}
+%----------------------------------------
+
 %
@@
 %----------------------------------------------
-\section{Results and discussions} \label{sec:results}
+\section{Results and discussions} 
+\label{sec:results}
 %----------------------------------------------
@@
 \section{Conclusion and Future Work}
+\label{sec:Conclusions}
 %-------------------------------------

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed sections 3 and 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-PV systems are broadly classified into three distinct types \cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid, (2) grid-connected systems, and (3) solar PV hybrid system.
+PV systems are broadly classified into three distinct types~\cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system.
 %, where another source(s) of energy can work together with the solar PV.
@@
 %\end{itemize}
-Specifically concerning the energy need for remote rural areas of developing countries or places where the grid extension is not possible or feasible, 
+Specifically concerning the energy needed for remote rural areas of developing countries or places where the grid extension is not possible or feasible, 
 %stand-alone systems are one the most used solutions, and 
@@
 %can be split into several categories. However, 
-the configuration that is most common or mode indicated is the regulated stand-alone system with battery and AC load. This configuration is the focus of this paper.
+the configuration that is most common or more suitable is the regulated stand-alone system with battery and AC load. This configuration is the focus of this study.
 %, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
@@
 %
-In order to address different aspects of project system and systems design, there is a myriad of tools. 
+In order to address different aspects of project system and systems design, there are various software tools \textcolor{red}{add citations here}. 
 %public domain and commercial software available for the PV market. 
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here it was evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.
+Here it was evaluated the most popular ones, which are PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2 \textcolor{red}{add citations here}.
 
@@
 additionally, HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis.
-However, only paid version (restrict to the Microsoft Windows Operational System) of those tools have all the features, as to save the the project or to upload data from manufacturers.
+However, only commercial version (restricted to the Microsoft Windows OS) of those tools have all the features \textcolor{red}{these are really all features that are needed?}: to save the project or to upload data from manufacturers.
 RETScreen and HOMER have a free web-based version, but they have limited resources.
@@
 %
-Considering the focus of this paper, only HOMER remains for a comparative with the proposed automated verification technique of this paper.
+Considering the focus of this study, only HOMER remains for a comparative evaluation with our proposed automated verification technique.
 %All tools need some parameters inherently from manufacturer's catalog.
@@
 %After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-And the challenge of this work is to show that is possible to use automated verification in stand-alone PV solution, proving that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro.
-The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section \ref{sec:results}.
+The main challenge of this study is to show that it is possible to use automated verification in stand-alone PV solution, thus proving that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro.
+The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section~\ref{sec:results}.
 
@@
 The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
-It is identified the PV generator, batteries, charge controller, inverter, and AC load.
+It identifies the PV generator, batteries, charge controller, inverter, and AC load.
 
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
-At the diagram, there are two variables that depend on the site where the system is deployed and from the weather (solar irradiance $ G $ and temperature $ T $).
+In the diagram, there are two variables that depend on the site where the system is deployed and from the weather (solar irradiance $G$ and temperature $T$).
 For night hours or rainy days, one needs to hold batteries, where power can be stored and used.
-The use of battery as a storage form implies thus the presence of a charge controller \cite{Hansen}, \cite{Mellit}.
+The use of battery as a storage form implies thus the presence of a charge controller~\cite{Hansen,Mellit}.
 The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
-That converter is called of inverter.
-And the AC load dictates the behavior of AC electrical load from the house that will be feed by the system.
+That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
 %
@@
 The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-is usually studied using an equivalent circuit model, as described in the available literature \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
-This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}.
+is usually studied using an equivalent circuit model, as described in the available literature~\cite{Yatimi,Saloux,Mellit}.
+This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, in order to take into account energy losses in this model~\cite{Cubas}.
 %Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
@@
 
-The 1-diode model, shown by Fig. \ref{fig:equivckt}, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in (\ref{eq:1diodemodel}). 
+The 1-diode model, illustrated in Fig. \ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described in \eqref{eq:1diodemodel}. 
 \begin{equation}
 \label{eq:1diodemodel}
-I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right] 
-\end{equation}
-
-Where: $I_{ph}$ is the photocurrent delivered by the constant current source; $ I_{0} $ is the reverse saturation current corresponding to the diode; $ N $ is the number of series-connected cells ($ N=1 $ in a single cell configuration); $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $ T $ the temperature of the p-n junction (or cell temperature) in Kelvin; $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
+I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right], 
+\end{equation}
+
+\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells ($N=1$ in a single cell configuration); $a$ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $T$ the temperature of the p-n junction (or cell temperature) in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
 
@@
 %Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
-The simplified model of 1-diode was shown that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested \cite{Saloux}.
+The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
 In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing.
@@
 %A single-diode without series and shunt resistances is considered. 
-Equation (\ref{eq:1diodemodel}) is used to write down expressions for currents and voltages at each key point of characteristic curve from a PV cell.
+Equation \eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \textcolor{red}{Add citation here}.
 % shown in Fig. \ref{fig:ivcurve}.
@@
 
-The voltage and the current at the maximum power point tracking (MPPT), can be expressed by (\ref{eq:Vmfinal}), (\ref{eq:Imfinal}), and (\ref{eq:Pm}) \cite{Saloux}.
+The voltage and the current at the maximum power point tracking (MPPT), can be expressed by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm} \cite{Saloux}.
 %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
@@
 %
-However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, (\ref{eq:Iph}) is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.
+However, the photocurrent delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
+Therefore, (\ref{eq:Iph}) is used to calculate the photocurrent as function of irradiance and temperature~\cite{Villalva}.
 \begin{equation}
 \label{eq:Iph}
-I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right] 
-\end{equation}
-
-Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions
+I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right], 
+\end{equation}
+
+\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions
 (provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
@@
 \label{eq:Tcell}
-T = T_{air} + \dfrac{NOCT-20}{800}G
-\end{equation}
-
-Where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is find at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
-
-Furthermore, (\ref{eq:I0}) allows the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature \cite{Villalva}. 
+T = T_{air} + \dfrac{NOCT-20}{800}G,
+\end{equation}
+
+\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet \textcolor{red}{add citation here}, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
+
+Furthermore, \eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature~\cite{Villalva}. 
 %In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
@@
 \label{eq:I0}
-I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1}
-\end{equation}
-
-Where $ V_{oc,ref} $ is the reference open-circuit voltage, and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
+I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1},
+\end{equation}
+
+\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage, and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
 
@@
 \label{eq:a}
-a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) }
-\end{equation}
-
-Where $ V_{mref} $, $ V_{oc,ref} $, $ I_{m,ref} $, and $ I_{sc,ref} $ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers.
-The model is now completely determined.
+a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) },
+\end{equation}
+
+\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers; the model is now completely determined \textcolor{red}{which model?
+please be more specific}.
 %; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
@@
 
-Besides the model verification, there is the prior stage of project sizing check, based on manufacturer's data and information from the sizing and the site.
-
-First is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$).
-That is done by (\ref{eq:Ecorrected}) \cite{Pinho}.
-Where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
+In addition to the model verification, there is the prior stage of project sizing check, based on manufacturer's data and information from the sizing and the site.
+
+Firstly, it is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$).
+That is done by \eqref{eq:Ecorrected}~\cite{Pinho}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
 \begin{equation}
 \label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }
-\end{equation}
-
-The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by  (\ref{eq:NTPmin}), and the check is done with (\ref{eq:NTP}), where the sized number of panels ($ N_{TP} $) must be greater than the result from (\ref{eq:NTPmin}).
+E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
+\end{equation}
+
+The total minimum number of needed solar panels ($N_{TPmin}$) is computed by \eqref{eq:NTPmin}, and the check is performed using \eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from \eqref{eq:NTPmin}.
 \begin{equation}
 \label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}
+N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
 \end{equation}
@@
 \label{eq:NTP}
-N_{TP} \geq N_{TPmin}
-\end{equation}
-
-Particularly, the total number of panels is series ($ N_{PSmin} $) and parallel ($ N_{PPmin} $) are given by (\ref{eq:NPSmin}) and (\ref{eq:NPPmin}), respectively.
-With the check done by (\ref{eq:NPS}) and (\ref{eq:NPP}).
-$ V_{system} $ is the DC voltage of the bus, normally 12, 24 or 48 V.
+N_{TP} \geq N_{TPmin}.
+\end{equation}
+
+Particularly, the total number of panels is series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by \eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.
+With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}).
+$ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
 \begin{equation}
 \label{eq:NPSmin}
-N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}
+N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}.
 \end{equation}
@@
 \label{eq:NPPmin}
-N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}
+N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}.
 \end{equation}
@@
 \label{eq:NPS}
-N_{PS} \geq N_{PSmin}
+N_{PS} \geq N_{PSmin}.
 \end{equation}
@@
 \label{eq:NPP}
-N_{PP} \geq N_{PPmin}
-\end{equation}
-
+N_{PP} \geq N_{PPmin}.
+\end{equation}
+
+%------------------------------------------------------------
 \subsection{The Battery Storage Model }
+%------------------------------------------------------------
+
 %Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system.
@@
 
-Several models have been presented in the literature \cite{Copetti}, \cite{Manwell93}. 
+Several models have been presented in the literature~\cite{Copetti,Manwell93}. 
 %, and \cite{Manwell94}. 
@@
 %
-Most of the created models were based on lead-acid batteries. That kind of battery is the most common used in PV application, owing to their relative low cost and wide availability \cite{Copetti}.
-
-Here, the model adopted \cite{Copetti} uses manufacturer's data. % and allows finding relations among voltage, current, state of charge and temperature. 
-%
-The discharge voltage equation is shown in (\ref{eq:bat_Vd}). 
+Most proposed models are based on lead-acid batteries \textcolor{red}{Add citations here}.
+That kind of battery is the most common used in PV application, thus owing to their relative low cost and wide availability~\cite{Copetti}.
+
+Here, the model adopted~\cite{Copetti} uses manufacturer's data. % and allows finding relations among voltage, current, state of charge and temperature. 
+%
+The discharge voltage equation is described in \eqref{eq:bat_Vd}. 
 %The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
@@
 \label{eq:bat_Vd}
-V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \\ \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T)
+V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \\ \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T),
 \end{multline}
 
-Where $ C_{10} $ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $ \Delta T $ is temperature variation ($ \Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at given time.
-Mathematically, is the ratio between the present capacity and the nominal capacity (in $ Ah $, provided by manufacturer).
-If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged.
+\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at given time.
+Mathematically, it is the ratio between the present capacity and the nominal capacity (in $ Ah $, provided by manufacturer).
+If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged.
 %, defined by Equation \ref{eq:SOCbat}.
@@
 %The ratio between $ Q $ and $ C $ represents t
-The depth of discharge ($ DOD $) or the fraction of discharge, is $ DOC=1-SOC $.
+The depth of discharge ($DOD$) or the fraction of discharge, is $DOC=1-SOC$.
 
@@
 
-For the charging process, however, the parameters are presented in (\ref{eq:Vcbat}).
+For the charging process, however, the parameters are presented in \eqref{eq:Vcbat}.
 %
@@
 %
-Besides the model verification, there is also the prior stage of project sizing check, as did to the solar panel.
-First is necessary to define the total capacity of the battery bank, as shown by (\ref{eq:Cbank}).
+In addition to the model verification, there is also the prior stage of project sizing check, as performed for the solar panel.
+Firstly it is necessary to define the total capacity of the battery bank, as described by \eqref{eq:Cbank}.
 \begin{equation}
 \label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}
-\end{equation}
-
-The variable $ autonomy $ is a design definition and normally has a value ranging from 6 to 48h. The other variables were discussed previously.
-
-Following, is done the total (minimum) number of batteries, as show by (\ref{eq:Nbtotal}).
-Moreover, (\ref{eq:batcheck}) perform the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that were established to the project.
+C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}.
+\end{equation}
+
+The variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; the other variables were discussed previously \textcolor{red}{can you please refer to the section here?}.
+
+Secondly, the total (minimum) number of batteries is computed, as described in \eqref{eq:Nbtotal}.
+Moreover, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
 \begin{equation}
 \label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}
+N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}.
 \end{equation}
@@
 \label{eq:batcheck}
-\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total
-\end{equation}
-
+\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total.
+\end{equation}
+
+%---------------------------------------------------------
 \subsection{Charge Controller Model}
+%---------------------------------------------------------
+
 %Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
@@
 The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
-To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and when the current required by the load is less than the current delivered by the PV arrays \cite{Hansen}.
+To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \textunderscore off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}.
 PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $.
@@
 
-To protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $ V_{min \textunderscore off} $ and when the current required by the load is larger than the current delivered by the PV arrays \cite{Hansen}.
-The load is reconnected to the system, when the terminal voltage is above a certain value $ V_{min \textunderscore on} $.
+In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \textunderscore off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}.
+The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \textunderscore on}$.
 %, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
@@
 %
-The steps in the modeling of the controller process are summarized in Table \ref{table:controller}.
+The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.
 
@@
 %As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of DC-DC converter is given by (\ref{eq:poutcont}). 
+The output power ($ P_{out} $) of DC-DC converter is given by \eqref{eq:poutcont}. 
 \begin{equation}
 \label{eq:poutcont}
-P_{in} = P_{out}
-\end{equation}
-
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from (\ref{eq:poutcont}) is possible to reach (\ref{eq:potcont}).
+P_{in} = P_{out}.
+\end{equation}
+
+Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from \eqref{eq:poutcont} it is possible to reach \eqref{eq:potcont}.
 \begin{equation}
 \label{eq:potcont}
-V_{in} I_{in} \eta_{c} = V_{out} I_{out}
-\end{equation}
-
-Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
+V_{in} I_{in} \eta_{c} = V_{out} I_{out},
+\end{equation}
+
+\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
 
@@
 One more time, some steps must be done to check the sizing project of the controller, prior the verification phase.
-Initially the controller must meet the voltage requirement of the PV system, as shown by (\ref{eq:vcvsystem}).
+Initially, the controller must meet the voltage requirement of the PV system, as described in \eqref{eq:vcvsystem}.
 \begin{equation}
 \label{eq:vcvsystem}
-V_{c} = V_{system}
-\end{equation}
-
-Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as shown by (\ref{eq:iscamb}).
+V_{c} = V_{system}.
+\end{equation}
+
+Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as shown by \eqref{eq:iscamb}.
 \begin{equation}
 \label{eq:iscamb}
-I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right] 
-\end{equation}
-
-The controller must meet the maximum current from the PV array (\ref{eq:icmin}), and (\ref{eq:icicmin}).
+I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right]. 
+\end{equation}
+
+The controller must meet the maximum current from the PV array \eqref{eq:icmin} and \eqref{eq:icicmin}.
 \begin{equation}
 \label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP}
+I_{c,min} = I_{sc,amb} \times N_{PP}.
 \end{equation}
@@
 \label{eq:icicmin}
-I_{c} \geq I_{c,min}
+I_{c} \geq I_{c,min}.
 \end{equation}
@@
 %\end{itemize}
-%
+%-----------------------------------------------
 \subsection{The inverter model}
+%-----------------------------------------------
 %As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. 
@@
 \label{eq:efficinv}
-\eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}}
-\end{equation}
-
-Where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be find from the inverter's data-sheet.
+\eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}},
+\end{equation}
+
+\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be find from the inverter's data-sheet.
 
@@
 The sizing project check of the inverter is done through three Equations.
-Equation (\ref{eq:vindc}) ensure that the input voltage of the controller meet the voltage of the system.
-Equation (\ref{eq:voutac}) ensures that the output voltage of the controller meet the AC voltage of the load.
-Moreover, (\ref{eq:invcheck}) ensures that the controller can support the total demand of the load and the surge power.
+Eq.
+\eqref{eq:vindc} ensures that the input voltage of the controller meet the voltage of the system.
+Eq.
+\eqref{eq:voutac} ensures that the output voltage of the controller meet the AC voltage of the load.
+Moreover, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
 \begin{equation}
 \label{eq:vindc} 
-V_{in}DC = V_{system}
+V_{in}DC = V_{system}.
 \end{equation}
@@
 \label{eq:voutac} 
-V_{out}AC = V_{AC}
+V_{out}AC = V_{AC}.
 \end{equation}
@@
 \label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right] 
+\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
 \end{equation}
@@
 %It is necessary to keep in mind that 
-Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations \cite{Clarke2008}.
+Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{Clarke2008}.
+
+\textcolor{red}{I would suggest to replace Clarke2008 by this one https://dblp.uni-trier.de/rec/bibtex/reference/mc/ClarkeHV18. Or at least cite it in the next sentence which is more recent.}
 
@@
 In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-Testing can also be used for validation, but for the same reasons, it too is problematic for verification.
-
-Verification procedure is an intelligent exhaustive search of the state space of the design \cite{Clarke2008}.
+Testing can also be used for validation, but for the same reasons, it is too problematic for verification \textcolor{red}{Why is it problematic?!?}.
+
+Verification procedure is an intelligent \textcolor{red}{What do you mean by intelligent?} exhaustive search of the state space of the design \cite{Clarke2008}.
 In addition, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}.
-One successful method in this domain is model checking.
+One successful method in this domain is model checking \textcolor{red}{please cite here the reference given above}.
  % 
@@
 
-The model checking algorithm can be described as:
+The model checking algorithm can be described as \textcolor{red}{add citation here}:
 
@@
 \end{itemize}
-Specifically at the $FALSE$ situation, the algorithm returns a counterexample that is useful as diagnostic of the system, in order to discover in which situation the model is violated.
+Specifically for the $FALSE$ verification result, the algorithm returns a counterexample that is useful as diagnostic of the system, to discover in which situation the model is violated.
 That is the most important advantage of the use of model checking \cite{Clarke2008}.
@@
 %
-The Fig. \ref{fig:systemverif} shows the process to convert a real system to a model in order to be verified by a model checking.
+Fig.~\ref{fig:systemverif} shows the process to convert a real system to a model to be verified by a model checking procedure \textcolor{red}{Please try to adapt this figure to our context.
+How can it be applied to verify PV?}.
 
@@
 
-In order to solve the problem of state explosion, many different techniques were developed at the last decades.
+In order to solve the problem of state explosion, many different techniques were developed at the last decades \textcolor{red}{Please cite them here!!!}.
 One of the promising is the Bounded Model Checking (BMC).
@@
 BMC algorithms traverses a finite state machine for a fixed number of steps, $ k $, and checks whether violation occurs with this bound.
-It uses SAT solvers, where SAT means satisfiability.
+It uses Boolean Satisfiability (SAT) solvers, where SAT means satisfiability.
 SAT problem is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression \cite{Clarke2008}.
@@
 The solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
-If SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
+If a SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
 
 CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}.
+
+\textcolor{red}{ESBMC does not use CBMC as its main frontend.
+Please take a look at this paper and cite it: https://ssvlab.github.io/lucasccordeiro/papers/ase2018.pdf.
+I would also suggest to remove the above sentence.}
 
@@
 %The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
-ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
+ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models \textcolor{red}{add citation here}.
 
@@
 \centering
-\caption{ESBMC architecture (adapted from \cite{GadelhaSBMF}).}
+\caption{ESBMC architecture (adapted from \cite{GadelhaSBMF}). \textcolor{red}{This architecture is obsolete. Please see the paper https://ssvlab.github.io/lucasccordeiro/papers/ase2018.pdf}}
 \label{fig:esbmcarch}
@@
 
-XXX
-
 %-------------------------------------

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
updated bio
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{IEEEbiographynophoto}{Lucas Cordeiro}
-received his PhD degree from the University of Southampton in 2011.
-From 2009 to 2016, he was an Adjunct Professor at the UFAM (he is currently in unpaid leave).
-Since 2018, he is a Senior Lecturer at The University of Manchester, working with the Formal Methods Group.
+received his Ph.D.
+degree in Computer Science in 2011 from the University of Southampton, UK.
+Currently, he is a Senior Lecturer in the School of Computer Science at the University of Manchester, UK and leads the Systems and Software Verification laboratory.
+He is also a collaborator in the Postgraduate Program in Electrical Engineering and Informatics at the Federal University of Amazonas (UFAM), Brazil.
+Prior to joining the University of Manchester, he worked as a researcher / researcher engineer at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for 4 years as a software engineer at Siemens Mobile and CT-PIM.
+His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.
 \end{IEEEbiographynophoto}

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed sections 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-The flowchart of the automated verification proposed is illustrated in Fig.\ref{fig:flowchartgeneral}. 
-The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as C Programming language code.
+The flowchart of the proposed (automated) verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
+The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code \textcolor{red}{add citation here to the standard}.
 
@@
 
-The weather data (solar irradiance, and ambient temperature by default) will suffer a heavy test at ESBMC run-time execution, based in maximum and minimum values from the site where the PV system will be deployed.
-In addition, depending if one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system, is not accomplished or satisfied, the tool accuses a fail, and the diagnostic counterexample shows in which condition the fail/violation happened.
+The weather data (solar irradiance, and ambient temperature by default) will be evaluated by the ESBMC verification engine, based on maximum and minimum values from the site, where the PV system will be deployed.
+In addition, depending on one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system to check whether it is not accomplished or satisfied, the tool accuses a failure, and the diagnostic counterexample shows in which condition the fail/violation happened.
 %; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
@@
 
-Simply put, instead of the ESBMC find the defect of a software or if a hardware does not meet the some requirements, the tool will verify if the requirements of the solar PV project are met.
+\textcolor{red}{I didn't understand this sentence...
+it is completely broken...} Simply put, instead of the ESBMC find the defect of a software or if a hardware does not meet the some requirements, the tool will verify if the requirements of the solar PV project are met.
 Detailing the condition of violation, i.e., the state of each variable related to the system.
 
+%---------------------------------------------------------------------
 \subsection{The case studies and the Algorithm}
-It was performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
+%---------------------------------------------------------------------
+
+We performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
 %and as backup at night 
@@
 
-Algorithm 1 describes the pseudo code used to perform the automated verification.
+Algorithm~\ref{alg:verification-algorithm} describes the pseudo code used to perform the automated verification. \textcolor{red}{Can you please briefly explain this algorithm?}
 
@@
  \end{algorithmic} 
+ \label{alg:verification-algorithm}
  \end{algorithm}

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
minor corrections
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \label{eq:Vmfinal}
-V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) 
+V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right). 
 \end{equation}
@@
 \label{eq:Imfinal}
-I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  
+I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right).  
 \end{equation}
@@
 \label{eq:Pm}
-P_{m} = V_{m} I_{m}
+P_{m} = V_{m} I_{m}.
 \end{equation}

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
IEEE thesaurus

@@
 \begin{abstract}
-With declining costs and increasing performance, the deployment of renewable energy in \textcolor{red}{What is the difference between off-grid and stand-lone?
-In the title you mention stand-alone and in the abstract you mention off-grid...
-please keep a standard...} off-grid systems is growing in both developed and developing countries, with particular emphasis on solar photovoltaic systems.
-Electrification of rural areas can improve the education standard, health conditions, and also the life of that population.
-In addition, depending on the country geography, using renewable energy sources in off-grid mode is a feasible solution if compared to a grid extension.
-\textcolor{red}{half of your abstract is about the context...
-you should reduce it a bit further..} Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects.
-This paper aims to apply an automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective.
-Data from practical application of solar systems prove the results obtained by the proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the verification tool if compared to a simulation tools.
+With declining costs and increasing performance, the deployment of renewable energy systems is growing in both developed and developing countries, with particular emphasis on stand-alone solar photovoltaic systems where grid extension is not feasible.
+Tools to evaluate the design and validate those electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space.
+Automated verification using formal methods, in the other hand, is proven to be a reference technique to program verification.
+However, any kind of system can be verified by formal method, including the most complexes.
+At this paper, each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were coded as a mathematical model, and a algorithm using automated verification was created in order to validate its design from a formal verification perspective.
+Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro.
+Data from practical application prove the results obtained by the proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the verification tool.
 %Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.

### 2018-11-14 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper updating

@@
 The increase in the number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researchers and practitioners involved in their application.
-In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \textcolor{red}{Add citation to all those tools}.
-And even general purpose simulation tools as PSpice, Saber or MATLAB/Simulink package \textcolor{red}{Add citation to all those tools}.
+In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan}, \cite{Swarnkar}, \cite{NRELDobos}, \cite{NRELBlair}, and \cite{Mills}.
+And even general purpose simulation tools as PSpice, Saber or MATLAB/Simulink package \cite{Gow1999}, \cite{Benatiallah2017}.
 
@@
 However, those tools are based on running experiments in simulation models.
-Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded; however, it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of systems is rarely possible or even feasible~\cite{Clarke2008}.
-
-Formal methods based on software model checking offer great potential to obtain a more effective and faster verification in the design process~\cite{Clarke2008}.  
+Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded; however, it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of systems is rarely possible or even feasible~\cite{ClarkeHV18}.
+
+Formal methods based on software model checking offer great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
 %with behavior that is, in principle, well determined. 
@@
 %It is necessary to keep in mind that 
-Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{Clarke2008}.
-
-\textcolor{red}{I would suggest to replace Clarke2008 by this one https://dblp.uni-trier.de/rec/bibtex/reference/mc/ClarkeHV18. Or at least cite it in the next sentence which is more recent.}
+Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}.
 
@@
 
-Verification procedure is an intelligent \textcolor{red}{What do you mean by intelligent?} exhaustive search of the state space of the design \cite{Clarke2008}.
+Verification procedure is an intelligent \textcolor{red}{What do you mean by intelligent?} exhaustive search of the state space of the design \cite{ClarkeHV18}.
 In addition, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}.
@@
  % 
-%Model checking is an automatic verification technique, as defined by \cite{Clarke2008}.
+%Model checking is an automatic verification technique, as defined by \cite{ClarkeHV18}.
 Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
@@
 Specifically for the $FALSE$ verification result, the algorithm returns a counterexample that is useful as diagnostic of the system, to discover in which situation the model is violated.
-That is the most important advantage of the use of model checking \cite{Clarke2008}.
+That is the most important advantage of the use of model checking \cite{ClarkeHV18}.
 %Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
@@
 %
-%The model checking problem can be defined as \cite{Clarke2008}: 
+%The model checking problem can be defined as \cite{ClarkeHV18}: 
 %
@@
 %\centering
-%\caption{Model Checker structure (Source: \cite{Clarke2008})}
+%\caption{Model Checker structure (Source: \cite{ClarkeHV18})}
 %\label{fig:modelcheckstruc}
@@
 \centering
-\caption{From real system verification to model checking (adapted from \cite{Clarke2008}).}
+\caption{From real system verification to model checking (adapted from \cite{ClarkeHV18}).}
 \label{fig:systemverif}
@@
 It uses Boolean Satisfiability (SAT) solvers, where SAT means satisfiability.
-SAT problem is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression \cite{Clarke2008}.
+SAT problem is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression \cite{ClarkeHV18}.
 %SAT solvers are used in BMC, such that i
@@
 \section*{Acknowledgment}
-The authors would like to thank Newton Fund (Star Energy project), Coventry University, Sustainable Amazonas Foundation (FAS), and FAPEAM (Amazonas State Foundation for Research Support), for the financial support and for the possibility to test the tool with real PV systems.
+The authors would like to thank Newton Fund (Star Energy project), Coventry University, Sustainable Amazonas Foundation (FAS), and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support and for the possibility to test the tool with real PV systems.
 
@@
 received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
-Currently, he is pursuing his PhD in Informatics at the UFAM, and hold a position as Assistant Professor at the Electricity Department from the Federal University of Amazonas.
+Currently, he is pursuing his PhD at the Post-Graduation Program in Informatics (PPGI) at the UFAM, and hold a position as Assistant Professor at the Electricity Department from UFAM.
+Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked 12 years as R \& D and project manager at a non-profit foundation (Centre of Analysis, Research and Innovation Technology Foundation).
+His interest is in renewable energy, automated verification, and model checking.
 \end{IEEEbiographynophoto}

### 2018-11-14 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 The increase in the number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researchers and practitioners involved in their application.
-In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan}, \cite{Swarnkar}, \cite{NRELDobos}, \cite{NRELBlair}, and \cite{Mills}.
+In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan}, \cite{Swarnkar}, \cite{NRELDobos}, \cite{NRELBlair}, \cite{Mills}.
 And even general purpose simulation tools as PSpice, Saber or MATLAB/Simulink package \cite{Gow1999}, \cite{Benatiallah2017}.
@@
 %
-In order to address different aspects of project system and systems design, there are various software tools \textcolor{red}{add citations here}. 
+In order to address different aspects of project system and systems design, there are various software tools \cite{Rajanna}, \cite{Rawat}.
 %public domain and commercial software available for the PV market. 
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here it was evaluated the most popular ones, which are PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2 \textcolor{red}{add citations here}.
+Here it was evaluated the most popular ones, which are PVWatts, SAM, HOMER, RETScreen, and Hybrid2 \cite{NRELDobos}, \cite{NRELBlair}, \cite{Swarnkar}, \cite{Pradhan}, \cite{Mills}.
 
@@
 
-Table~\ref{table:softwares} summarizes the off-the-shelf tools employed in this study, where only Hybrid2 does not have technical support; HOMER Pro and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis;
-additionally, HOMER Pro and RETScreen Expert include economical analysis or even optimization-sensitive analysis.
-However, only commercial version (restricted to the Microsoft Windows OS) of those tools have all the features \textcolor{red}{these are really all features that are needed?}: to save the project or to upload data from manufacturers.
-RETScreen and HOMER have a free web-based version, but they have limited resources.
+Table~\ref{table:softwares} summarizes the off-the-shelf tools employed in this study, where only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis;
+additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
+RETScreen and HOMER have a free web-based version, but they have limited resources: it is not allowed to save the projects or even upload data from manufacturers.
+In other hand, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription range from US\$504.00 to US\$657.00.
 
@@
 %A single-diode without series and shunt resistances is considered. 
-Equation \eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \textcolor{red}{Add citation here}.
+Equation \eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
 % shown in Fig. \ref{fig:ivcurve}.
@@
 
-\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet \textcolor{red}{add citation here}, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
+\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet \cite{Ross}, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
 
@@
 
-\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers; the model is now completely determined \textcolor{red}{which model?
-please be more specific}.
+\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers; the PV generator model is now completely determined.
 %; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
@@
 
-In addition to the model verification, there is the prior stage of project sizing check, based on manufacturer's data and information from the sizing and the site.
+In addition to the model verification that will be performed by the proposed technique at this paper, there is the prior stage of PV system sizing check, based on manufacturer's data and information from the sizing and the site.
+That stage will guarantee if the system was well designed, considering the standard steps of project \cite{Pinho}.
 
@@
 
-Several models have been presented in the literature~\cite{Copetti,Manwell93}. 
+Several models have been presented in the literature and the most commum are based on lead-acid batteries ~\cite{Copetti,Manwell93,Pinho}. 
 %, and \cite{Manwell94}. 
@@
 %
-Most proposed models are based on lead-acid batteries \textcolor{red}{Add citations here}.
-That kind of battery is the most common used in PV application, thus owing to their relative low cost and wide availability~\cite{Copetti}.
-
-Here, the model adopted~\cite{Copetti} uses manufacturer's data. % and allows finding relations among voltage, current, state of charge and temperature. 
+That kind of battery has relative low cost and wide availability~\cite{Copetti}.
+
+Here, the model adopted~\cite{Copetti} uses only manufacturer's data, without the need of empirical tests. % and allows finding relations among voltage, current, state of charge and temperature. 
 %

### 2018-11-14 Tex/LaTeX2e Style File/Trindade_IEEE_journal_temp.tex
paper update

--- 2018-11-14 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
@@
 With declining costs and increasing performance, the deployment of renewable energy systems is growing in both developed and developing countries, with particular emphasis on stand-alone solar photovoltaic systems where grid extension is not feasible.
-Tools to evaluate the design and validate those electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space.
-Automated verification using formal methods, in the other hand, is proven to be a reference technique to program verification.
-However, any kind of system can be verified by formal method, including the most complexes.
+Tools to evaluate the design and validate electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space.
+Automated verification using formal methods, in the other hand, is proven to be a reference technique to program verification, and any kind of system can be verified by formal method, including the most complexes.
 At this paper, each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were coded as a mathematical model, and a algorithm using automated verification was created in order to validate its design from a formal verification perspective.
@@
 %Based on data from \textcolor{red}{from what? please be more formal! can you check the guidelines of the journal to see how you can cite references?}, t
-There was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV \cite{EPIA}. 
+There was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV all over the world \cite{EPIA}. That scenario brings the need for 
 %The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
@@
 %Furthermore, there is the need for proper modeling and simulation tools for people involved in their application.
-
-The increase in the number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researchers and practitioners involved in their application.
+%
+%The increase in the number of PV systems installed and been projected all over the world brings the need for %proper modeling and simulation tools for researchers and practitioners involved in their application.
+design validation - ensuring the correctness of the design at the earliest stage possible - which is a major challenge in any responsible system development process, and the activities intended for its solution occupy an ever increasing portions of the  development cycle cost and time budgets \cite{ClarkeHV18}.
+%The currently practiced methods for design validation in most sites are still the veteran techniques of simulation and testing \cite{ClarkeHV18}.
+
 In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan}, \cite{Swarnkar}, \cite{NRELDobos}, \cite{NRELBlair}, \cite{Mills}.
@@
 \subsection{PV generator model}
+\label{sec:PVmodel}
 %-------------------------------------------------------------------
@@
 \subsection{The Battery Storage Model }
+\label{sec:BATmodel}
 %------------------------------------------------------------
@@
 
-Here, the model adopted~\cite{Copetti} uses only manufacturer's data, without the need of empirical tests. % and allows finding relations among voltage, current, state of charge and temperature. 
-%
+Here, the model adopted uses only manufacturer's data, without the need of empirical tests~\cite{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature.
+
 The discharge voltage equation is described in \eqref{eq:bat_Vd}. 
@@
 
-The variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; the other variables were discussed previously \textcolor{red}{can you please refer to the section here?}.
+The variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; the other variables were discussed previously at Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
 
@@
 %--------------------------------------------------
-
 %It is necessary to keep in mind that 
@@
 %, but in general, validation cannot be formalized because it relates a system design to intent.  
-
+While simulation and testing explore some of the possible behaviors and scenarios of the system, leaving open the question of whether the unexplored trajectories may contain a flaw, formal verification conducts an exhaustive exploration of all possible behaviors.
+Thus, when a design is pronounced correct by a formal verification method, it implies that all behaviors have been explored, and the questions of adequate coverage or a missed behavior become irrelevant \cite{Clarke2012}.
 %Simulation may also be used for validation, but it is more problematic for verification.
-In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-Testing can also be used for validation, but for the same reasons, it is too problematic for verification \textcolor{red}{Why is it problematic?!?}.
-
-Verification procedure is an intelligent \textcolor{red}{What do you mean by intelligent?} exhaustive search of the state space of the design \cite{ClarkeHV18}.
+
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}.
+One successful method in this domain is model checking \cite{Clarke2012}.
+%
+%In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
+Testing can also be used for validation, however it is not feasible to cover all the aspects of the design space, and some times the real system must be used instead of a computing model.
+% 
+%Verification procedure is an intelligent \textcolor{red}{What do you mean by intelligent?} exhaustive search of the state space of the design \cite{ClarkeHV18}.
 In addition, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}.
@@
 
-The model checking algorithm can be described as \textcolor{red}{add citation here}:
+The model checking algorithm can be described as \cite{ClarkeHV18}:
 
@@
 \item It returns $YES$ if $ \phi $ is $TRUE$, or returns $NO$ if $ \phi $ is $FALSE$.  
-
 \end{itemize}
@@
 %Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
-However, there is a main disadvantage of model checking: the state explosion problem. 
 %
@@
 
-In order to solve the problem of state explosion, many different techniques were developed at the last decades \textcolor{red}{Please cite them here!!!}.
-One of the promising is the Bounded Model Checking (BMC).
+However, there is a main disadvantage of model checking: the state explosion problem.
+In order to solve the problem of state explosion, many different techniques were developed at the last decades.
+One of the first major advances was symbolic model checking with binary decision diagrams (BDDs).
+In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice.
+Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes.
+A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
+However, one of the promising is the Bounded Model Checking (BMC).
+
 BMC is a method that checks the model up to a given path in the path length.

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 %, but in general, validation cannot be formalized because it relates a system design to intent.  
-
+While simulation and testing explore some of the possible behaviors and scenarios of the system, leaving open the question of whether the unexplored trajectories may contain a flaw, formal verification conducts an exhaustive exploration of all possible behaviors.
+Thus, when a design is pronounced correct by a formal verification method, it implies that all behaviors have been explored, and the questions of adequate coverage or a missed behavior become irrelevant \cite{Clarke2012}.
 %Simulation may also be used for validation, but it is more problematic for verification.
-In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-Testing can also be used for validation, but for the same reasons, it is too problematic for verification \textcolor{red}{Why is it problematic?!?}.
-
-Verification procedure is an intelligent \textcolor{red}{What do you mean by intelligent?} exhaustive search of the state space of the design \cite{ClarkeHV18}.
-In addition, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}.
-One successful method in this domain is model checking \textcolor{red}{please cite here the reference given above}.
+%In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
+Testing can also be used for validation, however it is not feasible to cover all the aspects of the design space, and some times the real system must be used instead of a computing model.
+
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}.
+One successful method in this domain is model checking \cite{Clarke2012}.
  % 
@@
 %
-Fig.~\ref{fig:systemverif} shows the process to convert a real system to a model to be verified by a model checking procedure \textcolor{red}{Please try to adapt this figure to our context.
+Fig.~\ref{fig:systemverif} shows the process to convert a real PV system to a model to be verified by a model checking procedure.
+% \textcolor{red}{Please try to adapt this figure to our context.
 How can it be applied to verify PV?}.
@@
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{systemverif}
+\includegraphics[width=0.5\textwidth]{systemverif2}
 \centering
@@
 
-In order to solve the problem of state explosion, many different techniques were developed at the last decades \textcolor{red}{Please cite them here!!!}.
-One of the promising is the Bounded Model Checking (BMC).
+However, there is a main disadvantage of model checking: the state explosion problem.
+In order to solve this problem, many different techniques were developed at the last decades.
+One of the first major advances was symbolic model checking with binary decision diagrams (BDDs).
+In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice.
+Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes.
+A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
+However, one of the promising is the Bounded Model Checking (BMC).
+
 BMC is a method that checks the model up to a given path in the path length.
@@
 
-\textcolor{red}{ESBMC does not use CBMC as its main frontend.
+%\textcolor{red}{ESBMC does not use CBMC as its main frontend.
 Please take a look at this paper and cite it: https://ssvlab.github.io/lucasccordeiro/papers/ase2018.pdf.
@@
 
-ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.
+ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver. %, which can use CBMC as front-end.
 %The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
-ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models \textcolor{red}{add citation here}.
+ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models \cite{esbmc2018}.
 
 \subsection{ESBMC }
-ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs \cite{GadelhaSBMF}. 
+ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs \cite{esbmc2018}. 
 %The efficient SMT based model checker, is a software verification tool for C and C++ code bases. 
@@
 \begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{ESBMCarch2}
+\includegraphics[width=0.4\textwidth]{ESBMCarch4}
 \centering
-\caption{ESBMC architecture (adapted from \cite{GadelhaSBMF}). \textcolor{red}{This architecture is obsolete. Please see the paper https://ssvlab.github.io/lucasccordeiro/papers/ase2018.pdf}}
+\caption{ESBMC architecture (adapted from \cite{esbmc2018}).}
 \label{fig:esbmcarch}
 \end{figure}
-
-ESBMC has two alternative front-ends to parse the input program \cite{GadelhaSBMF}.
+ESBMC uses clang as front-end, a state-of-the-art compiler suite for C/C++/ObjectiveC/ObjectiveC++ widely used in industry \cite{esbmc2018}.
 % and generate an Abstract Syntax Tree (AST).
@@
 The data types and bit vectors are created in the front-end when parsing the code.
-Regardless of the chosen front-end, the output is an AST (tree representation of the abstract syntactic structure of source code written in a programming language) that will be used by the GOTO converter to generate a GOTO program, which has simplified control flow and is suitable for bounded unwinding.
+%Regardless of the chosen front-end, 
+The output is an AST (tree representation of the abstract syntactic structure of source code written in a programming language) that will be used by the GOTO converter to generate a GOTO program, which has simplified control flow and is suitable for bounded unwinding.
 The next step is the symbolic execution, when the GOTO program is executed (unrolling loops up to the bound $ k $) and converted to Static Single Assignments (SSA) form.
@@
 %, where each variable is a target of exactly one assignment statement in the program text.
+The feature called k-induction at Fig. \ref{fig:esbmcarch} allows BMC to find a property violation or even to prove (partial) correctness without fully unwinding loops. 
 %
@@
 %----------------------------------------
-
 %
@@
 The flowchart of the proposed (automated) verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
-The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code \textcolor{red}{add citation here to the standard}.
+The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code %\cite{ANSIC}.
 
@@
 
-\textcolor{red}{I didn't understand this sentence...
-it is completely broken...} Simply put, instead of the ESBMC find the defect of a software or if a hardware does not meet the some requirements, the tool will verify if the requirements of the solar PV project are met.
-Detailing the condition of violation, i.e., the state of each variable related to the system.
+In a nutshell, ESBMC will process the C code with constraints ($C$) and properties ($P$) from the PV system that were inputted by the user, and the tool will verify automatically if the requirements are met.
+If the return is a fail, then the tool details the condition of violation, i.e., the state of each variable related to the system.
+That information can be used as a feedback to improve the PV system project.
+In the other hand, if the verification succeeds, as indicated in Fig.
+\ref{fig:esbmcarch}, the PV system will present its intended behavior at the field.
 
@@
 
+Algorithm~\ref{alg:verification-algorithm} describes the pseudo code used to perform the automated verification.
+The line 1 indicates function call that performs the size checking of the entire PV system: using \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
+The verification is done by standard \textit{assert} macro from C language to each equation.
+The argument to \textit{assert} must be true when the macro is executed, otherwise the program aborts and prints an error message.
+If there is no fail, the algorithm goes on and the batteries are assumed to have SOC of 80\% (line 5).
+
 %At both case studies, it was considered 21 years of historic data from Manaus. 
@@
 The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight.
+That information is passed to the C code at lines 7 to 10 using the feature of non-deterministic variable from ESBMC to explore all the possible states from the variables and the \textit{assume} macro to limit the values considering a range.
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
@@
 the 24h-day was divided, at the algorithm, in 3 parts of 8 h each (8:00h-16:00h, 16:00h-24:00h, and 00:00h-8:00h); and only the 8:00h-16:00h period with PV generation.
-The time step was adjusted to 1 hour.
+The time step was adjusted to 1 hour, and from line 1 to line 29 the algorithm perform the verification from 8;00h to 16:00h, where there is PV generation.
+Therefore, the model from PV generator is used at the function call of line 11, to produce the voltage and current considering the actual $G$ and $T$.
+Following, related to every hour considered, the conditional \textit{if-else-endif} statements from lines 12, 17, 23 and 27, will perform the charge and discharge of batteries according the PV generation, the updated state of charge of batteries, the house's load and the set-up information of the system.
+After this process is started the battery autonomy verification, from line 30.
+Based on the fact that won't be PV generation after 16:00h, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.
+The formal verification is guaranteed by \textit{assert} macro to specific variables of the model, according lines
 % and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
@@
 %, and change their value every 1 h according with the algorithm created using the technique.
-
-Algorithm~\ref{alg:verification-algorithm} describes the pseudo code used to perform the automated verification. \textcolor{red}{Can you please briefly explain this algorithm?}
 

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 \begin{abstract}
-With declining costs and increasing performance, the deployment of renewable energy systems is growing in both developed and developing countries, with particular emphasis on stand-alone solar photovoltaic systems where grid extension is not feasible.
+With declining costs and increasing performance, the deployment of renewable energy systems is growing in both developed and developing countries.
+Particular attention is being given to stand-alone solar photovoltaic systems in rural areas or where grid extension is not feasible.
 Tools to evaluate the design and validate electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space.
-Automated verification using formal methods, in the other hand, is proven to be a reference technique to program verification, and any kind of system can be verified by formal method, including the most complexes.
+Automated verification using formal methods, in the other hand, is proven to be a reference technique to program verification.
+However, any kind of system can be verified by formal method, including the most complexes.
 At this paper, each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were coded as a mathematical model, and a algorithm using automated verification was created in order to validate its design from a formal verification perspective.
@@
 The main challenge of this study is to show that it is possible to use automated verification in stand-alone PV solution, thus proving that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro.
-The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section~\ref{sec:results}.
+The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section~\ref{sec:results_indeed}.
 
@@
 
-CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}.
-
+%CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}. 
+%
 %\textcolor{red}{ESBMC does not use CBMC as its main frontend.
@@
 %, where each variable is a target of exactly one assignment statement in the program text.
-The feature called k-induction at Fig. \ref{fig:esbmcarch} allows BMC to find a property violation or even to prove (partial) correctness without fully unwinding loops. 
+The feature called k-induction at Fig. \ref{fig:esbmcarch} allows the model checker to find a property violation or even to prove (partial) correctness without fully unwinding loops. 
 %
@@
 The flowchart of the proposed (automated) verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
-The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code %\cite{ANSIC}.
+The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code.
+%\cite{ANSIC}.
 
@@
 Therefore, the model from PV generator is used at the function call of line 11, to produce the voltage and current considering the actual $G$ and $T$.
-Following, related to every hour considered, the conditional \textit{if-else-endif} statements from lines 12, 17, 23 and 27, will perform the charge and discharge of batteries according the PV generation, the updated state of charge of batteries, the house's load and the set-up information of the system.
-After this process is started the battery autonomy verification, from line 30.
+Following, related to every hour considered, the conditional \textit{if-else-endif} statements from lines 12, 17, 23 and 28, will perform the charge and discharge of batteries according the PV generation, the updated state of charge of batteries, the house's load and the set-up information of the system.
+After this process is started the battery autonomy verification, from line 31.
 Based on the fact that won't be PV generation after 16:00h, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.
-The formal verification is guaranteed by \textit{assert} macro to specific variables of the model, according lines
+The formal verification is guaranteed by \textit{assert} macro to specific variables of the model, according lines 27 and 35.
 % and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
@@
   \STATE $T \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
-  \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting the values of $G$}
-  \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting the values of $T$}
+  \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting $G$ values}
+  \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting $T$ values}
   \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ 
@@
   \IF {($SOC \leq SOC_{limit}$)} 
-    \STATE assert (PV panel is generating energy) \COMMENT {if there is no enough solar energy generation, then FAIL}
+    \STATE assert (PV panel is generating energy?) \COMMENT {FAIL if not}
     \STATE $house \leftarrow energy \, from \, PV \, panels$
@@
   \ELSE
-  	\STATE Adequate the voltage at the DC-bus (battery feed the bus)
+  	\STATE Adequate the voltage of DC-bus (battery feed bus)
 	\STATE $house \leftarrow energy \, from \, batteries$
     \STATE $SOC \leftarrow SOC - 1\,h\, discharge$
+    \STATE assert ($SOC \geq SOC_{limit}$)
     \\
-    \COMMENT {the last case: batteries are charged but the panels are not generating}	  
+    \COMMENT {this ELSE: batteries $\geq SOC_{limit}$ but panels are off}	  
   \ENDIF
@@
 \subsection{Results}
+\label{sec:results_indeed}
 The total were five case studies evaluated by HOMER Pro and by the automated verification tool.

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 The flowchart of the proposed (automated) verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
-The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code.
-%\cite{ANSIC}.
+The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code \cite{ANSI2018}.
 

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Tools to evaluate the design and validate electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space.
-Automated verification using formal methods, in the other hand, is proven to be a reference technique to program verification.
-However, any kind of system can be verified by formal method, including the most complexes.
-At this paper, each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were coded as a mathematical model, and a algorithm using automated verification was created in order to validate its design from a formal verification perspective.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro.
-Data from practical application prove the results obtained by the proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the verification tool.
+Automated verification using model checking, however, has proven to be an effective technique to program verification.
+However, any kind of system can be verified by formal methods, including the most complex ones.
+Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were encoded into a mathematical model, and a algorithm using automated software model checking was created in order to validate its design from a formal verification perspective.
+Case studies, from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro.
+Data from practical applications show the effectiveness of the obtained results, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the proposed verification method.
 %Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-In order to model, simulate or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan}, \cite{Swarnkar}, \cite{NRELDobos}, \cite{NRELBlair}, \cite{Mills}.
-And even general purpose simulation tools as PSpice, Saber or MATLAB/Simulink package \cite{Gow1999}, \cite{Benatiallah2017}.
+In order to model, simulate, or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan}, \cite{Swarnkar}, \cite{NRELDobos}, \cite{NRELBlair}, \cite{Mills}; and even general purpose simulation tools as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999}, \cite{Benatiallah2017}.
 
@@
 %Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
-Finally, model checking algorithms can verify the system model by systematically exploring all their states. That way, the formal proof can verify if the requirements are met by the system.
+Finally, model checking algorithms can verify the system model by systematically exploring all their states. As a result, the formal proof can verify if the requirements are met by the system.
 
@@
 It allows one to develop models for each component of the system.
-At this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.
+In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.
 The behavior of each system can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
@@
 The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
-
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC), which allows one to formally verify a PV system as a C program.
-
-In most prior studies, the evaluation of PV systems, concerning the meeting of user requirements, were performed by software simulation tools using MATLAB/Simulink \cite{Benatiallah2017}, \cite{Samrat2014}, and \cite{Natsheh2012} or HOMER Pro \cite{Lamnadi2017}.
+The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to formally verify a PV system as a C program.
+
+In prior studies, the evaluation of PV systems, concerning the meeting of user requirements, were performed by software simulation tools using MATLAB/Simulink \cite{Benatiallah2017}, \cite{Samrat2014}, and \cite{Natsheh2012} or HOMER Pro \cite{Lamnadi2017}.
 Some studies were carried out toward the formal modeling of power smart grids \cite{Akram2018}, and to maximize the power point of solar panels \cite{Driouich2017}; however, those studies do not perform automated verification and they restrict themselves to solar panels or smart grids.
 
-In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus have been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
+In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus has been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
 Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.
@@
 %The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
-To the best of our knowledge, this is the first initiative to use a verification tool to evaluate a stand-alone solar PV systems. %, with weather conditions variation. 
+Given the current knowledge in formal verification, this is the first initiative to use a verification tool to evaluate a stand-alone solar PV systems. %, with weather conditions variation. 
 The mains contribution of this paper are the automated verification of the PV system, and the modular modeling of each component of the PV system, which allows one to change the mathematical models, besides changing the type of energy generation in the future to another renewable source.
@@
 Section~\ref{sec:AutomatedVerification} presents the automated verification technique.
-The methodology is presented at section~\ref{sec:Methodology}.
+The methodology is presented in section~\ref{sec:Methodology}.
 Section~\ref{sec:results} is devoted to the results.

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %can be split into several categories. However, 
-the configuration that is most common or more suitable is the regulated stand-alone system with battery and AC load. This configuration is the focus of this study.
+the most suitable configuration is the regulated stand-alone system with battery and AC load. This configuration is the focus of this study.
 %, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here it was evaluated the most popular ones, which are PVWatts, SAM, HOMER, RETScreen, and Hybrid2 \cite{NRELDobos}, \cite{NRELBlair}, \cite{Swarnkar}, \cite{Pradhan}, \cite{Mills}.
+Here it was evaluated the most popular ones, which are PVWatts, SAM, HOMER, RETScreen, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
 
@@
 
-Table~\ref{table:softwares} summarizes the off-the-shelf tools employed in this study, where only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system or battery backup analysis; %all the tools perform solar photovoltaic analysis;
-additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
+Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system or battery backup analysis.
+%all the tools perform solar photovoltaic analysis;
+Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
 RETScreen and HOMER have a free web-based version, but they have limited resources: it is not allowed to save the projects or even upload data from manufacturers.
-In other hand, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription range from US\$504.00 to US\$657.00.
+However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription range from US\$504.00 to US\$657.00.
 
@@
 %After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-The main challenge of this study is to show that it is possible to use automated verification in stand-alone PV solution, thus proving that this evaluation is more efficient and complete than other state-of-the-art tool, as HOMER Pro.
+The main challenge here is to demonstrate the use of automated verification in stand-alone PV solution, thus proving that this evaluation is more effective and complete than other state-of-the-art tool, as HOMER Pro.
 The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section~\ref{sec:results_indeed}.
@@
 For night hours or rainy days, one needs to hold batteries, where power can be stored and used.
-The use of battery as a storage form implies thus the presence of a charge controller~\cite{Hansen,Mellit}.
+The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen,Mellit}.
 The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
@@
 \centering
-\caption{Block diagram for the stand-alone PV system (Source:~\cite{Hansen}).}
+\caption{Block diagram for the stand-alone PV system~\cite{Hansen}.}
 \label{fig:blockdiagram}
@@
 The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-is usually studied using an equivalent circuit model, as described in the available literature~\cite{Yatimi,Saloux,Mellit}.
-This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, in order to take into account energy losses in this model~\cite{Cubas}.
+is usually studied using an equivalent circuit model~\cite{Yatimi,Saloux,Mellit}; this equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, in order to take into account energy losses in this model~\cite{Cubas}.
 %Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-is usually studied using an equivalent circuit model~\cite{Yatimi,Saloux,Mellit}; this equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, in order to take into account energy losses in this model~\cite{Cubas}.
+is usually studied using an equivalent circuit model~\cite{Yatimi,Saloux,Mellit}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
 %Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
@@
 \centering
-\caption{1-diode equivalent PV cell/panel circuit model (Source:~\cite{Cubas}).}
+\caption{1-diode equivalent PV cell/panel circuit model~\cite{Cubas}.}
 %\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
@@
 
-The 1-diode model, illustrated in Fig. \ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described in \eqref{eq:1diodemodel}. 
+The 1-diode model, illustrated in Fig. \ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described in Eq.~\eqref{eq:1diodemodel}:
 \begin{equation}
@@
 The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing.
+In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing \textcolor{red}{add citation here}.
 
@@
 %A single-diode without series and shunt resistances is considered. 
-Equation \eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
+Eq.~\eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
 % shown in Fig. \ref{fig:ivcurve}.
@@
 %\end{figure}
-
+%
 %Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
@@
 %Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, 
-
+%
 The voltage and the current at the maximum power point tracking (MPPT), can be expressed by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm} \cite{Saloux}.
@@
 However, the photocurrent delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, (\ref{eq:Iph}) is used to calculate the photocurrent as function of irradiance and temperature~\cite{Villalva}.
+Therefore, Eq.~\eqref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature~\cite{Villalva}:
 \begin{equation}
@@
 (provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
-
-The cell temperature ($ T $) is shown in (\ref{eq:Tcell}) \cite{Ross}.
+%
+The cell temperature ($ T $) is described in Eq.~\ref{eq:Tcell}~\cite{Ross}:
 \begin{equation}
@@
 
-Furthermore, \eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature~\cite{Villalva}. 
+Furthermore, Eq.~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature~\cite{Villalva}. 
 %In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
@@
 %The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current (\ref{eq:Pm}) and the saturation current in the reference temperature given by (\ref{eq:I0}), the diode ideality factor is determined by (\ref{eq:a}).
+Using the maximum power point current \eqref{eq:Pm} and the saturation current in the reference temperature given by Eq.~\ref{eq:I0}, the diode ideality factor is determined by Eq.~\ref{eq:a}:
 \begin{equation}

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}.
-
-If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, resulting in a process known as formal verification.
+If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, thus resulting in a process known as formal verification.
 Verification may form part of a validation process.
@@
 Testing can also be used for validation, however it is not feasible to cover all the aspects of the design space, and some times the real system must be used instead of a computing model.
-
+ %
 Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}.
@@
 %\end{itemize}
-
+%
 %Fig. \ref{fig:modelcheckstruc} shows the structure of a 
@@
 A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
-However, one of the promising is the Bounded Model Checking (BMC).
+However, one of the most promising approaches is Bounded Model Checking (BMC).
 
@@
 It uses Boolean Satisfiability (SAT) solvers, where SAT means satisfiability.
-SAT problem is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression \cite{ClarkeHV18}.
+SAT problem is a problem of determining if there are certain conditions or interpretations that satisfy a given Boolean expression \cite{ClarkeHV18}.
 %SAT solvers are used in BMC, such that i
 %If there are some Boolean function, t
-The solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
-If a SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
-
+The SAT solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
+If a SAT solver finds a substitution for the formula/function then the substitute induces a counterexample.
+%
 %CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}. 
@@
 I would also suggest to remove the above sentence.}
-
-ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver. %, which can use CBMC as front-end.
+%
+ESBMC is one of the most representatives context-bounded model checkers for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver~\cite{esbmc2018}.
+%, which can use CBMC as front-end.
 %The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
-ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models \cite{esbmc2018}.
+ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
 

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \centering
-\caption{Flowchart of the proposed automated verification of PV systems.}
+\caption{Flowchart of the proposed automated verification of PV systems. \textcolor{red}{shall we identify each step with a number? e.g., step 1, step 2, etc?}}
 \label{fig:flowchartgeneral}
@@
 That information can be used as a feedback to improve the PV system project.
-In the other hand, if the verification succeeds, as indicated in Fig.
+However, if the verification succeeds, as indicated in Fig.
 \ref{fig:esbmcarch}, the PV system will present its intended behavior at the field.
+
+\textcolor{red}{The algorithm should be part of the methodology!!!}
+
+\textcolor{red}{The case study should be described in the experimental evaluation section.}
 

### 2018-11-16 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
paper update

@@
 \ref{fig:esbmcarch}, the PV system will present its intended behavior at the field.
-
-\textcolor{red}{The algorithm should be part of the methodology!!!}
-
-\textcolor{red}{The case study should be described in the experimental evaluation section.}
-
+%
+%
 %---------------------------------------------------------------------
-\subsection{The case studies and the Algorithm}
+% \subsection{The case studies and the Algorithm}
 %---------------------------------------------------------------------
-
-We performed five case studies: (1) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (2) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
+%
+% 
 %and as backup at night 
@@
 %According with X and Y, t
-The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight.
-That information is passed to the C code at lines 7 to 10 using the feature of non-deterministic variable from ESBMC to explore all the possible states from the variables and the \textit{assume} macro to limit the values considering a range.
+Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are passed to algorithm at lines 7 to 10 using the feature of non-deterministic variable from ESBMC to explore all the possible states from the variables and the \textit{assume} macro to limit the values considering a range.
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
 Another characteristic of Manaus, is that the PV generation can be despised from 16:00h to the 8:00h of the next day, independent of the season.
+
 %there is PV generation only between 8:00 h and 16:00 h every day, 
 %with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day. 
-Therefore, in order to reduce the computational effort,
+Therefore, in order to reduce the computational effort of the algorithm,
 % caused by the state explosion inherent of the technique, 
-the 24h-day was divided, at the algorithm, in 3 parts of 8 h each (8:00h-16:00h, 16:00h-24:00h, and 00:00h-8:00h); and only the 8:00h-16:00h period with PV generation.
+every 24h-day was considered as a time-step of 1 hour, and was divided in 2 parts: (a) one where there is PV generation (day-time) of 8 h each (8:00h-16:00h, 16:00h-24:00h, and 00:00h-8:00h); and only the 8:00h-16:00h period with PV generation.
 The time step was adjusted to 1 hour, and from line 1 to line 29 the algorithm perform the verification from 8;00h to 16:00h, where there is PV generation.
+
 Therefore, the model from PV generator is used at the function call of line 11, to produce the voltage and current considering the actual $G$ and $T$.
@@
 %----------------------------------------------
-\section{Results and discussions} 
+\section{Experimental Evaluation} 
 \label{sec:results}
@@
 \subsection{Experimental objectives and setup}
-Experimental objectives: To evaluate the proposed verification methodology and the respective tool performance, in a comparative with the HOMER Pro tool in five case studies (described in Methodology section).
+Experimental objectives: To evaluate the proposed verification methodology and the respective tool performance, in a comparative with the HOMER Pro tool in five case studies.
 Using functional information collected from owners of those five systems, which were deployed in 2018, serving as cross data about how the systems are behaving during four months of use.
@@
 It was used the version 3.12.0 of HOMER Pro.
+
+We performed five case studies: (a) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (b) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
+The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is inputted at lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
+Another characteristic of Manaus, based on historic data, is related of the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is a demand of Algorithm~\ref{alg:verification-algorithm} as well).
 
@@
 %\label{sec:results}
+
+%---------------------------------------------------
+\subsection{Threats to Validity}
+%---------------------------------------------------
+
+\textcolor{red}{Write here threats to validity....}
 

### 2018-11-16 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 \begin{figure}[h]
-\includegraphics[width=0.48\textwidth]{blockdiagramPVS}
+\includegraphics[width=0.48\textwidth]{blockdiagramPVS2}
 \centering
@@
 ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs \cite{esbmc2018}.
-%The efficient SMT based model checker, is a software verification tool for C and C++ code bases. 
-Fig. \ref{fig:esbmcarch} shows the tool architecture.
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{ESBMCarch4}
-\centering
-\caption{ESBMC architecture (adapted from \cite{esbmc2018}).}
-\label{fig:esbmcarch}
-\end{figure}
-ESBMC uses clang as front-end, a state-of-the-art compiler suite for C/C++/ObjectiveC/ObjectiveC++ widely used in industry \cite{esbmc2018}.
+
+ESBMC's architecture can be summarized in three stages: (I) a front-end that can read and compile C/C++ codes, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, where all the constraints and properties of the system to be verified are coded in SMT format and solved.
+%
+%%The efficient SMT based model checker, is a software verification tool for C and C++ code bases. 
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Fig. \ref{fig:esbmcarch} shows the tool architecture. 
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{ESBMCarch4}
+%\centering
+%\caption{ESBMC architecture (adapted from \cite{esbmc2018}).}
+%\label{fig:esbmcarch}
+%\end{figure}
+%ESBMC uses clang as front-end, a state-of-the-art compiler suite for C/C++/ObjectiveC/ObjectiveC++ widely used in industry \cite{esbmc2018}.
 % and generate an Abstract Syntax Tree (AST).
-%One legacy CBMC-based front-end that supports both C and C++ and a new clang-based front-end that currently only supports C.
+%%%%%One legacy CBMC-based front-end that supports both C and C++ and a new clang-based front-end that currently only supports C.
 The data types and bit vectors are created in the front-end when parsing the code.
-%Regardless of the chosen front-end, 
-The output is an AST (tree representation of the abstract syntactic structure of source code written in a programming language) that will be used by the GOTO converter to generate a GOTO program, which has simplified control flow and is suitable for bounded unwinding.
+%%%%%%%Regardless of the chosen front-end, 
+%The output is an AST (tree representation of the abstract syntactic structure of source code written in a programming language) that will be used by the GOTO converter to generate a GOTO program, which has simplified control flow and is suitable for bounded unwinding.
 The next step is the symbolic execution, when the GOTO program is executed (unrolling loops up to the bound $ k $) and converted to Static Single Assignments (SSA) form.
 SSA form enables the simplification of algorithms and reduction of computational complexity.
-%, where each variable is a target of exactly one assignment statement in the program text.
-The feature called k-induction at Fig. \ref{fig:esbmcarch} allows the model checker to find a property violation or even to prove (partial) correctness without fully unwinding loops. 
-%
-%During the symbolic execution, ESBMC aggressively tries to simplify the program \cite{Ramalho}; it propagates all constants and solves any assertions that can be statically determined.
+%%%%%%%%%, where each variable is a target of exactly one assignment statement in the program text.
+%The feature called k-induction at Fig. \ref{fig:esbmcarch} allows the model checker to find a property violation or even to prove (partial) correctness without fully unwinding loops. 
+%%
+%%%%%%%During the symbolic execution, ESBMC aggressively tries to simplify the program \cite{Ramalho}; it propagates all constants and solves any assertions that can be statically determined.
 This is an important step for the verification, since ESBMC can fully verify programs without calling a solver, if the inputs are deterministic.
 That characteristic is useful at this work to perform the sizing check of the PV system project.
-Following, the SSA expressions are then encoded using the chosen SMT solver supported by ESBMC. At this paper, it was used the Z3 solver \cite{DeMoura}.
-%: Boolector (default) \cite{Brummayer}, Z3 \cite{DeMoura}, MathSAT \cite{Cimatti}, Yices \cite{Dutertre} and CVC4 \cite{Barrett}.
-
-Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied.
+%Following, the SSA expressions are then encoded using the chosen SMT solver supported by ESBMC. At this paper, it was used the Z3 solver \cite{DeMoura}.
+%%%%%: Boolector (default) \cite{Brummayer}, Z3 \cite{DeMoura}, MathSAT \cite{Cimatti}, Yices \cite{Dutertre} and CVC4 \cite{Barrett}. 
+%
+%Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied. 
 If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is find to be unsatisfiable, there are no errors up to the unwinding bound, and this result is presented. 
-
-%ESBMC can be invoked through the command-line interface or configured through the Eclipse plug-in. Specific problems and the solver can be selected that way. 
-%
-%ESBMC aims to support all of ISO/IEC 9899:1999 C programming language standard, and detects errors in software by simulating a finite prefix of the program execution with all possible inputs.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%
+%%%%%ESBMC can be invoked through the command-line interface or configured through the Eclipse plug-in. Specific problems and the solver can be selected that way. 
+%
+%ESBMC aims to support all of ISO/IEC 9899:2017 C programming language standard, and detects errors in software by simulating a finite prefix of the program execution with all possible inputs.
 Classes of problems that can be detected include: user specified assertion failures, out of bounds array access, illegal pointer dereferences, double-free of malloc'd memory, misaligned memory access; integer overflows, divide by zero, memory leaks, concurrent software, deadlock, and data races (i.e.
@@
 %
-The flowchart of the proposed (automated) verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
-The PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code \cite{ANSI2018}.
+The flowchart of the proposed automated verification tool is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
+As Step 01, the PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code \cite{ANSI2018}.
+At Step 02, occurs the sizing check of the PV system to make sure that the components followed accepted international requirements toward a well designed PV project.
 
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{flowchart_verification.png}
+\includegraphics[width=0.4\textwidth]{flowchart_verification3.png}
 \centering
-\caption{Flowchart of the proposed automated verification of PV systems. \textcolor{red}{shall we identify each step with a number? e.g., step 1, step 2, etc?}}
+\caption{Flowchart of the proposed automated verification of PV systems.}
 \label{fig:flowchartgeneral}
@@
 
-The weather data (solar irradiance, and ambient temperature by default) will be evaluated by the ESBMC verification engine, based on maximum and minimum values from the site, where the PV system will be deployed.
+The weather data (solar irradiance, and ambient temperature by default) will be evaluated by the ESBMC verification engine, in Step 03, based on maximum and minimum values from the site, where the PV system will be deployed.
 In addition, depending on one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system to check whether it is not accomplished or satisfied, the tool accuses a failure, and the diagnostic counterexample shows in which condition the fail/violation happened.
@@
 
-In a nutshell, ESBMC will process the C code with constraints ($C$) and properties ($P$) from the PV system that were inputted by the user, and the tool will verify automatically if the requirements are met.
+In a nutshell, ESBMC will process the C code with constraints %($C$) 
+and properties %($P$) 
+from the PV system that were inputted by the user, and the tool will verify automatically if the requirements are met.
 If the return is a fail, then the tool details the condition of violation, i.e., the state of each variable related to the system.
 That information can be used as a feedback to improve the PV system project.
-However, if the verification succeeds, as indicated in Fig.
-\ref{fig:esbmcarch}, the PV system will present its intended behavior at the field.
+However, if the verification succeeds, the PV system will present its intended behavior at the field.
 %
@@
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
-Another characteristic of Manaus, is that the PV generation can be despised from 16:00h to the 8:00h of the next day, independent of the season.
-
 %there is PV generation only between 8:00 h and 16:00 h every day, 
 %with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day. 
-Therefore, in order to reduce the computational effort of the algorithm,
+In order to reduce the computational effort of the algorithm,
 % caused by the state explosion inherent of the technique, 
-every 24h-day was considered as a time-step of 1 hour, and was divided in 2 parts: (a) one where there is PV generation (day-time) of 8 h each (8:00h-16:00h, 16:00h-24:00h, and 00:00h-8:00h); and only the 8:00h-16:00h period with PV generation.
-The time step was adjusted to 1 hour, and from line 1 to line 29 the algorithm perform the verification from 8;00h to 16:00h, where there is PV generation.
-
-Therefore, the model from PV generator is used at the function call of line 11, to produce the voltage and current considering the actual $G$ and $T$.
+every 24h-day was considered as a time-step of 1 hour, and it was divided in 2 parts: (a) one that there is PV generation, during daylight, with a duration in hours depending on each site; and (b) one the includes all the rest of the day (without PV generation).
+Therefore the proposed methodology depends on the  specific data about the solar irradiation levels in order to define the average amount of hours of PV generation.
+
+Following, the model from PV generator is used at the function call of line 11, to produce the voltage and current considering the actual $G$ and $T$.
 Following, related to every hour considered, the conditional \textit{if-else-endif} statements from lines 12, 17, 23 and 28, will perform the charge and discharge of batteries according the PV generation, the updated state of charge of batteries, the house's load and the set-up information of the system.
 After this process is started the battery autonomy verification, from line 31.
-Based on the fact that won't be PV generation after 16:00h, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.
+Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.
 The formal verification is guaranteed by \textit{assert} macro to specific variables of the model, according lines 27 and 35.
@@
   \STATE $SOC \leftarrow 80\%$ \\
-  \COMMENT {First the 08:00h-16:00h of automated verification}
+  \COMMENT {Starting with the PV generation time}
  \\ \textit{LOOP Process}
-  \FOR {$h = 1$ to $8$}
+  \FOR {$h = 1$ to $Hours \, of \, PV \, generation$}
   \STATE $G \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
@@
     \STATE $house \leftarrow energy \, from \, PV \, panels$
-    \STATE $battery \leftarrow energy \, from \, PV \, panels$ \COMMENT {bulk stage}
+    \STATE $battery \leftarrow energy \, from \, PV \, panels$ 
     \STATE $SOC \leftarrow SOC + 1\,h\, charge$
   \ELSIF {($PV \, Array  \geq Vbulk$)}
-  	\STATE depending on the $SOC$, decide if Battery enter in absorption or floating stage
-	\STATE adequate the voltage at the DC-bus (PV panel feed the bus)
+  	\STATE depending on $SOC$, Battery enter in absorp. or float.
+	\STATE adequate the voltage at DC-bus (PV panel feed bus)
     \STATE $house \leftarrow energy \, from \, PV \, panels$
-    \STATE $battery \leftarrow energy \, from \, PV \, panels$ \COMMENT {bulk or floating stage}
+    \STATE $battery \leftarrow energy \, from \, PV \, panels$ 
     \STATE $SOC \leftarrow SOC + 1\,h\, charge$
@@
 
-  \STATE $SOC \leftarrow SOC - 16\,h\, discharge$
-  \STATE $AutonomyCount \leftarrow 16$
+  \STATE $SOC \leftarrow SOC - ( 24 - Hours \, of \, PV \, generation)\,h\, discharge$
+  \STATE $AutonomyCount \leftarrow ( 24 - Hours \, of \, PV \, generation)$
   \\  
-    \COMMENT {autonomy of 16:00h-08:00h discharge period}
+    \COMMENT {autonomy verification during discharge period}
   \\
@@
   \\
-  \COMMENT {Perform same 08:00h-16:00h \textbf{for}-LOOP as line 6}
+  \COMMENT {Perform similar \textbf{for}-LOOP as defined in line 6}
   %%\ENDFOR
@@
 Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter in order to reduce the memory usage.
-And regarding the solver, version 4.7.1 of Z3 was used.
+At this paper, it was used the Z3 solver \cite{DeMoura} with version 4.7.1.
 
@@
 The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is inputted at lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
-Another characteristic of Manaus, based on historic data, is related of the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is a demand of Algorithm~\ref{alg:verification-algorithm} as well).
-
+Another characteristic of Manaus, based on historic data of solar irradiance, is related of the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is a demand of Algorithm~\ref{alg:verification-algorithm} as well).
 \subsection{Results}
@@
 This functional problem was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
-
 %At the terminal, the command used to perform the verification is:
@@
 %\label{sec:results}
-
 %---------------------------------------------------
@@
 %---------------------------------------------------
-
-\textcolor{red}{Write here threats to validity....}
+\textit{Model precision:} each component received a mathematical model, and the precision of the proposed tool depends on the precision of that model.
+Probably a evaluation in a laboratory to validate the model could give more reliability to the proposed tool.
+
+\textit{Time step:} The computing complexity is a issue, but the time step of one hours can be evaluated to approximate the algorithm of the real world, where a solar irradiance and ambient temperature can change in minutes.
+
+\textit{Case studies:} The studies were performed only at the municipality of Manaus, at the south hemisphere.
+A more complete evaluation can be performed if other places around the world could become case studies.
 
@@
 %The automated verification tool presented here establishes the automated verification and the project sizing check. 
-It was shown that, beside the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results.
+It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results.
 The proposed tool was successful in find sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.

### 2018-11-18 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
added additional comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
-However, one of the most promising approaches is Bounded Model Checking (BMC).
+However, one of the most promising approaches is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
 
 BMC is a method that checks the model up to a given path in the path length.
-BMC algorithms traverses a finite state machine for a fixed number of steps, $ k $, and checks whether violation occurs with this bound.
-It uses Boolean Satisfiability (SAT) solvers, where SAT means satisfiability.
-SAT problem is a problem of determining if there are certain conditions or interpretations that satisfy a given Boolean expression \cite{ClarkeHV18}.
-%SAT solvers are used in BMC, such that i
-%If there are some Boolean function, t
-The SAT solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
-If a SAT solver finds a substitution for the formula/function then the substitute induces a counterexample.
+BMC algorithms traverse a finite state machine for a fixed number of steps, $ k $, and checks whether violation occurs with this bound.
+It uses Boolean Satisfiability (SAT) or Satisfiability Module Theories (SMT) solvers.
+SAT problem is a problem of determining whether there are certain conditions or interpretations that satisfy a given Boolean expression \cite{ClarkeHV18}.
+SMT decides the satisfiability of first-order formulae using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and non-linear arithmetic, bit-vectors, tuples, arrays, and other decidable first-order theories~\cite{ClarkeHV18}.
+The SAT or SMT solvers would search the model for conditions (value of variables) that would make the formula satisfiable.
+If a SAT or SMT solver finds a substitution for the formula/function then the substitute induces a counterexample.
 %
@@
 %
-ESBMC is one of the most representatives context-bounded model checkers for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver~\cite{esbmc2018}.
-%, which can use CBMC as front-end.
+ESBMC is one of the most representatives bounded model checkers for embedded C/C++ software based on SMT solvers~\cite{esbmc2018}. %, which can use CBMC as front-end.
 %The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
@@
 
-\subsection{ESBMC }
+%--------------------------------------
+\subsection{ESBMC}
+%--------------------------------------
+
 ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs \cite{esbmc2018}. 
-
-ESBMC's architecture can be summarized in three stages: (I) a front-end that can read and compile C/C++ codes, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, where all the constraints and properties of the system to be verified are coded in SMT format and solved.
+%
+ESBMC's architecture can be summarized in three stages: (I) a front-end that can read and compile C/C++ codes, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, where all the constraints and properties of the system to be verified are encoded into SMT format and solved.
 %
@@
 %Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied. 
-If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is find to be unsatisfiable, there are no errors up to the unwinding bound, and this result is presented. 
+If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is find to be unsatisfiable, there are no errors up to the unwinding bound. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%
@@
 The flowchart of the proposed automated verification tool is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
-As Step 01, the PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code \cite{ANSI2018}.
-At Step 02, occurs the sizing check of the PV system to make sure that the components followed accepted international requirements toward a well designed PV project.
+As Step 1, the PV input data (e.g., load power demand and load consumption of energy), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
+In Step 2, occurs the sizing check of the PV system to make sure that the components accepted international requirements toward a well designed PV project.
 
@@
 \centering
-\caption{Flowchart of the proposed automated verification of PV systems.}
+\caption{Flowchart of the proposed automated verification of PV systems. \textcolor{red}{replace 01, 02 and 03 by 1, 2, 3.}}
 \label{fig:flowchartgeneral}
@@
 
-The weather data (solar irradiance, and ambient temperature by default) will be evaluated by the ESBMC verification engine, in Step 03, based on maximum and minimum values from the site, where the PV system will be deployed.
-In addition, depending on one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system to check whether it is not accomplished or satisfied, the tool accuses a failure, and the diagnostic counterexample shows in which condition the fail/violation happened.
+The weather data (e.g., solar irradiance and ambient temperature by default) will be evaluated by the ESBMC verification engine, in Step 3, based on maximum and minimum values from the site, where the PV system will be deployed.
+In addition, depending on one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system to check whether it is not accomplished or satisfied, ESBMC accuses a failure, and the diagnostic counterexample shows in which condition the fail/violation happened.
 %; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
@@
 
+\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above.
+For example, what does a failure mean?
+is it SAT?}
 In a nutshell, ESBMC will process the C code with constraints %($C$) 
 and properties %($P$) 
-from the PV system that were inputted by the user, and the tool will verify automatically if the requirements are met.
-If the return is a fail, then the tool details the condition of violation, i.e., the state of each variable related to the system.
+from the PV system that were provided by the user, and the tool will verify automatically if the requirements are met.
+If the return is a failure, then the tool details the condition of violation, i.e., the state of each variable related to the system.
 That information can be used as a feedback to improve the PV system project.
@@
 
-Algorithm~\ref{alg:verification-algorithm} describes the pseudo code used to perform the automated verification.
-The line 1 indicates function call that performs the size checking of the entire PV system: using \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
-The verification is done by standard \textit{assert} macro from C language to each equation.
-The argument to \textit{assert} must be true when the macro is executed, otherwise the program aborts and prints an error message.
+Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to perform the automated verification.
+Line 1 indicates a function call that performs the size checking of the entire PV system: using \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
+The verification is performed by the standard \textit{assert} macro from ANSI-C programming language to each equation.
+The argument to \textit{assert} must be \textit{true} when the macro is executed; otherwise, the program aborts and prints an error message.
 If there is no fail, the algorithm goes on and the batteries are assumed to have SOC of 80\% (line 5).
@@
 %According with X and Y, t
-Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are passed to algorithm at lines 7 to 10 using the feature of non-deterministic variable from ESBMC to explore all the possible states from the variables and the \textit{assume} macro to limit the values considering a range.
+Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using the feature of non-deterministic variables from ESBMC to explore all possible states and the \textit{assume} macro to limit the non-deterministic values considering a given range.
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
@@
 % caused by the state explosion inherent of the technique, 
-every 24h-day was considered as a time-step of 1 hour, and it was divided in 2 parts: (a) one that there is PV generation, during daylight, with a duration in hours depending on each site; and (b) one the includes all the rest of the day (without PV generation).
-Therefore the proposed methodology depends on the  specific data about the solar irradiation levels in order to define the average amount of hours of PV generation.
-
-Following, the model from PV generator is used at the function call of line 11, to produce the voltage and current considering the actual $G$ and $T$.
-Following, related to every hour considered, the conditional \textit{if-else-endif} statements from lines 12, 17, 23 and 28, will perform the charge and discharge of batteries according the PV generation, the updated state of charge of batteries, the house's load and the set-up information of the system.
-After this process is started the battery autonomy verification, from line 31.
-Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.
-The formal verification is guaranteed by \textit{assert} macro to specific variables of the model, according lines 27 and 35.
+every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one that there is PV generation, during daylight, with a duration in hours depending on each site; and (b) one that includes all the remaining day (without PV generation).
+Therefore, the proposed methodology depends on specific data about the solar irradiation levels to define the average amount of hours of PV generation.
+
+After that, the model from PV generator is used in the function call of Line 11, to produce the voltage and current considering the actual $G$ and $T$.
+Following, related to every hour considered, the conditional \textit{if-else-endif} statements from lines 12, 17, 23 and 28, will perform the charge and discharge of batteries according to the PV generation, the updated state of charge of batteries, the house's load and the set-up information of the system.
+\textcolor{red}{this sentence is unclear...
+After this process is started the battery autonomy verification, from line 31}.
+\textcolor{red}{this sentence is unclear...
+Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.} \textcolor{red}{what do you mean by The formal verification is guaranteed?...
+The formal verification is guaranteed by \textit{assert} macro to specific variables of the model, according lines 27 and 35.}
 % and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
@@
 Experimental setup of automated verification tool: all experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter in order to reduce the memory usage.
+Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter to reduce the memory usage.
 At this paper, it was used the Z3 solver \cite{DeMoura} with version 4.7.1.

### 2018-11-18 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 The SAT or SMT solvers would search the model for conditions (value of variables) that would make the formula satisfiable.
-If a SAT or SMT solver finds a substitution for the formula/function then the substitute induces a counterexample.
+If a SAT or SMT solver finds a substitution for the formula/function then the substitute induces a counterexample and is said satisfiable.
+In other words, is satisfiable only if the verified system contains errors.  
 %
@@
 %Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied. 
-If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is find to be unsatisfiable, there are no errors up to the unwinding bound. 
+If the SMT formula is shown to be satisfiable (SAT), a counterexample is presented; if the formula is find to be unsatisfiable (UNSAT), there are no errors up to the unwinding bound. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%
@@
 In Step 2, occurs the sizing check of the PV system to make sure that the components accepted international requirements toward a well designed PV project.
-
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{flowchart_verification3.png}
+\includegraphics[width=0.4\textwidth]{flowchart_verification4.png}
 \centering
-\caption{Flowchart of the proposed automated verification of PV systems. \textcolor{red}{replace 01, 02 and 03 by 1, 2, 3.}}
+\caption{Flowchart of the proposed automated verification of PV systems.}
 \label{fig:flowchartgeneral}
 \end{figure}
-
-The weather data (e.g., solar irradiance and ambient temperature by default) will be evaluated by the ESBMC verification engine, in Step 3, based on maximum and minimum values from the site, where the PV system will be deployed.
-In addition, depending on one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system to check whether it is not accomplished or satisfied, ESBMC accuses a failure, and the diagnostic counterexample shows in which condition the fail/violation happened.
+The weather variables (solar irradiance and ambient temperature by default) will be explored in all their states by the ESBMC verification engine, in Step 3, based on maximum and minimum values from the site, where the PV system will be deployed.
+As a consequence, all the formulas of the mathematical models used will also be updated.
+In addition, depending on one of the desired properties of the system, as autonomy of the batteries, the offer of the energy, or even the power supply from the system to check, whether it is not accomplished (said satisfied), ESBMC accuses a failure, and the diagnostic counterexample shows in which condition the property violation (system fail) happened.
 %; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
@@
 
-\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above.
+%
+%\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above.
 For example, what does a failure mean?
@@
 and properties %($P$) 
-from the PV system that were provided by the user, and the tool will verify automatically if the requirements are met.
-If the return is a failure, then the tool details the condition of violation, i.e., the state of each variable related to the system.
+from the PV system that were provided by the user, and the tool will verify automatically if the PV system requirements are met.
+If the return is a failure (verification satisfiable), then the tool details the condition of violation, i.e., the state of each variable related to the system.
 That information can be used as a feedback to improve the PV system project.
-However, if the verification succeeds, the PV system will present its intended behavior at the field.
+However, if the verification succeeds (said UNSAT or unsatisfiable), there is no failure, therefore the PV system will present its intended behavior at the field.
 %
@@
 The argument to \textit{assert} must be \textit{true} when the macro is executed; otherwise, the program aborts and prints an error message.
-If there is no fail, the algorithm goes on and the batteries are assumed to have SOC of 80\% (line 5).
+If there is no fail, the algorithm goes on and the batteries are assumed to have SOC of 80\% (Line 5).
 
@@
 % caused by the state explosion inherent of the technique, 
-every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one that there is PV generation, during daylight, with a duration in hours depending on each site; and (b) one that includes all the remaining day (without PV generation).
+every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent of the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation).
 Therefore, the proposed methodology depends on specific data about the solar irradiation levels to define the average amount of hours of PV generation.
 
-After that, the model from PV generator is used in the function call of Line 11, to produce the voltage and current considering the actual $G$ and $T$.
-Following, related to every hour considered, the conditional \textit{if-else-endif} statements from lines 12, 17, 23 and 28, will perform the charge and discharge of batteries according to the PV generation, the updated state of charge of batteries, the house's load and the set-up information of the system.
-\textcolor{red}{this sentence is unclear...
+After that, the model from PV generator is used in the function call of Line 11, to produce the voltage and current considering the states of $G$ and $T$.
+Following, related to every hour considered, the conditional \textit{if-else-endif} statements from Lines 12, 17, 23 and 28, will perform the charge or discharge of batteries according to the value of different variables: is there is PV generation (which depends on $G$ and $T$), the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+
+Next, representing the time of the day where is not possible PV generation anymore, starting at Line 31, the algorithm will only discharge the batteries (using the 1 hour step) until a new charging process (at the next day) to start.
+Specific macro commands, the \textit{assert} at Lines 27 and 35, it will check the state of charge from batteries, and it will violate the property if its level reach the minimum that represents a discharged battery.
+And, therefore, the PV system is not able to supply energy to the house.
+In the other hand, if the automated tool do not fail, then the code is finalized with success and the PV system do not need improvements or corrections.
+%
+%\textcolor{red}{this sentence is unclear...
 After this process is started the battery autonomy verification, from line 31}.
@@
 Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.} \textcolor{red}{what do you mean by The formal verification is guaranteed?...
-The formal verification is guaranteed by \textit{assert} macro to specific variables of the model, according lines 27 and 35.}
+The formal verification is guaranteed by  macro to specific variables of the model, according lines 27 and 35.}
 % and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
@@
 %, and change their value every 1 h according with the algorithm created using the technique.
-
  \begin{algorithm}
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE Perform project sizing validation( )
-  \IF {(FAIL validation)} 
+  \STATE Perform project sizing verification( )
+  \IF {(FAIL verification)} 
   \STATE exit ("Project sizing error")  
@@
  \end{algorithm}
-
 %There are two premises considering the algorithm: (1) is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation from 8:00 h to 16:00 h, but without to account the battery autonomy (just considering charge and discharge process based on solar irradiation, load and battery charge), but after 16:00h is started the verification for the next hours when there is not solar photovoltaic generation.
@@
 % \fnbelowfloat command of the stfloats package.
-
+%
 %----------------------------------------------
@@
 We performed five case studies: (a) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (b) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
-The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is inputted at lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
+The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is inputted at Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
 Another characteristic of Manaus, based on historic data of solar irradiance, is related of the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is a demand of Algorithm~\ref{alg:verification-algorithm} as well).
@@
 However, related to the results of the automated verification, the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was not correct (the verification counterexample demands 3 panels in parallel and the project size has 2 in series and 2 in parallel).
+The number of panels was not correct (the verification counterexample demands 3 panels in parallel and the sized project has 2 in series and 2 in parallel).
 That verification took 63.3 hours to be performed.

### 2018-11-19 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Particular attention is being given to stand-alone solar photovoltaic systems in rural areas or where grid extension is not feasible.
-Tools to evaluate the design and validate electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space.
+Tools to evaluate the design and validate electrification projects are available; however, those tools are based on simulations that do not cover all the aspects of the design space.
 Automated verification using model checking, however, has proven to be an effective technique to program verification.
-However, any kind of system can be verified by formal methods, including the most complex ones.
-Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were encoded into a mathematical model, and a algorithm using automated software model checking was created in order to validate its design from a formal verification perspective.
+Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, are encoded into a mathematical model, and a software model checking algorithm was developed to verify its design from a formal perspective.
 Case studies, from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro.

### 2018-11-19 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
+%------------------------------------------
 \subsection{Experimental objectives and setup}
+%------------------------------------------
 Experimental objectives: To evaluate the proposed verification methodology and the respective tool performance, in a comparative with the HOMER Pro tool in five case studies.
@@
 Another characteristic of Manaus, based on historic data of solar irradiance, is related of the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is a demand of Algorithm~\ref{alg:verification-algorithm} as well).
+
+%------------------------------------------
 \subsection{Results}
 \label{sec:results_indeed}
+%------------------------------------------
+
 The total were five case studies evaluated by HOMER Pro and by the automated verification tool.
@@
 %-------------------------------------
-%The proposed tool seems to be a coherent and promising tool to perform verification of a PV project.
-The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field.
-%
-%The automated verification tool presented here establishes the automated verification and the project sizing check. 
-It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results.
-The proposed tool was successful in find sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
-%However, it is possible to perform the optimum sizing of the PV system. Moreover, 
-%The authors target the use of Counterexample Guided-Inductive Synthesis (CEGIS) to perform the optimum sizing of PV systems.
-That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system.
-Next, the proposed tool will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is find from the inputs.
-This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.
-
-Furthermore, it is possible to contemplate other kinds of renewable energy and even hybrid ones, which can evolve the algorithm into a complete tool for design and verification for rural electrification.
+
+We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
+We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W.
+Although this verification method takes longer than simulation tools, it is able to find specific conditions that lead to failures in a PV system previously validated by simulation tools.
+In particular, the proposed method was successful in finding sizing errors and indicating in which conditions, in terms of temperature and solar irradiation, a PV system can fail.
+As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems.
+We also will consider other types of renewable energy and even hybrid ones, which will allow our method to design and verify typical rural electrification.
+
 % into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.

### 2018-11-19 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed Trindade's bio
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
-Currently, he is pursuing his PhD at the Post-Graduation Program in Informatics (PPGI) at the UFAM, and hold a position as Assistant Professor at the Electricity Department from UFAM.
-Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked 12 years as R \& D and project manager at a non-profit foundation (Centre of Analysis, Research and Innovation Technology Foundation).
+Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
+Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation (Centre of Analysis, Research and Innovation Technology Foundation).
 His interest is in renewable energy, automated verification, and model checking.

### 2018-11-19 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed Threats to Validity
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %---------------------------------------------------
-\textit{Model precision:} each component received a mathematical model, and the precision of the proposed tool depends on the precision of that model.
-Probably a evaluation in a laboratory to validate the model could give more reliability to the proposed tool.
-
-\textit{Time step:} The computing complexity is a issue, but the time step of one hours can be evaluated to approximate the algorithm of the real world, where a solar irradiance and ambient temperature can change in minutes.
-
-\textit{Case studies:} The studies were performed only at the municipality of Manaus, at the south hemisphere.
+
+We have reported a favorable assessment of the proposed verification method over a diverse set of real-world benchmarks.
+Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
+
+\textit{Model precision:} each component of the PV system is mathematically modelled, and the precision of the proposed method depends on the precision of that particular model.
+A careful evaluation in a PV laboratory to validate the model could add more reliability to the results produced by our method.
+
+\textit{Time step:} The runtime complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario, where a solar irradiance and ambient temperature can change in fractions of minutes.
+
+\textit{Case studies:} Our case studies are performed only in Manaus, in particular in the south hemisphere.
 A more complete evaluation can be performed if other places around the world could become case studies.

### 2018-11-19 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed experimental results
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The total were five case studies evaluated by HOMER Pro and by the automated verification tool.
-Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shown that the restrictions were met by four systems, without any indication of sizing error or even of performance.
-The case study that was not successful during simulation was the 1,200 W (house 5), however without indication what are the fail of this PV system.
+We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
+Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four systems \textcolor{red}{which four system?
+can you please identify each one by a number?
+they should also be described}, without any indication of sizing error or even performance.
+The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
 All the simulations took less than 5 seconds (each) to be performed.
@@
 However, related to the results of the automated verification, the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was not correct (the verification counterexample demands 3 panels in parallel and the sized project has 2 in series and 2 in parallel).
+The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
 That verification took 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-But it is understandable that this problem occurs because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house.
-
-Related to the four 700 W PV systems, the sizing check was successful during automated verification, but there were found flaws in everyone, all related with the battery autonomy, when SOC reached levels below of 75\%.
-The automated verification identified the flaws right after the first night-discharge cycle, before the solar system start to recharge the batteries.
-The proposed tool took 409.3 hours to find an error at house 1, and the maximum of 456XXX hours to house 4.
-This functional problem was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
+Surveying the owner of the 1,200 W system, we identified that, in fact, the system mostly of the time does not meet the battery autonomy (mainly when all the loads are turned on).
+However, it is understandable that this problem occurs since the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house.
+
+Related to the four 700 W PV systems, the sizing check was successful during automated verification, but flaws were found in all of them, all related with the battery autonomy, when SOC reached levels below 75\%.
+The automated verification identified the flaws right after the first night-discharge cycle, i.e., before the solar system starts recharging the batteries.
+The proposed method took 409.3 hours to find an error in house 1, and the maximum of \textcolor{red}{456XXX} hours to house 4.
+This functional problem \textcolor{red}{what is a functional problem?} was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
 %At the terminal, the command used to perform the verification is:

### 2018-11-20 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed setup and objectives
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %------------------------------------------
-\subsection{Experimental objectives and setup}
+\subsection{Objectives and Setup}
 %------------------------------------------
-Experimental objectives: To evaluate the proposed verification methodology and the respective tool performance, in a comparative with the HOMER Pro tool in five case studies.
-Using functional information collected from owners of those five systems, which were deployed in 2018, serving as cross data about how the systems are behaving during four months of use.
-%
-%This section is split into two parts. The setup is described in Section \ref{sec:setup}, while Section \ref{sec:results} describes all experimental results.
-%
-%
-%\subsection{Experimental setup}
-%\label{sec:setup}
-
-Experimental setup of automated verification tool: all experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter to reduce the memory usage.
-At this paper, it was used the Z3 solver \cite{DeMoura} with version 4.7.1.
-
-Experimental setup of HOMER Pro: all experiments were conducted on an otherwise idle Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10.
-It was used the version 3.12.0 of HOMER Pro.
-
-We performed five case studies: (a) four concerning a PV system (700 W inverter, with 48h autonomy) deployed at four different houses at an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) sited nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); (b) and one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
-The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is inputted at Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
-Another characteristic of Manaus, based on historic data of solar irradiance, is related of the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is a demand of Algorithm~\ref{alg:verification-algorithm} as well).
+
+Our experimental evaluation aims to answer three research questions:
+%
+\begin{enumerate}
+\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
+\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
+\end{enumerate}
+
+In order to evaluate the proposed verification method and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool.
+\textcolor{red}{This sentence is broken...
+Using functional information collected from owners of those five systems, which were deployed in 2018, serving as cross data about how the systems are behaving during four months of use.}
+
+All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
+Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode enabled with the goal of reducing memory usage \textcolor{red}{Can you please add a footnote of how you call the tool?}; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+
+Experimental setup of HOMER Pro: all experiments were conducted on an otherwise idle Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.
+
+We performed five case studies: (a) four PV systems (700 W inverter, with 48h autonomy) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
+The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
+Another characteristic of Manaus, based on historical data of solar irradiance, is related to the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
 
@@
 %------------------------------------------
+
+\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
 

### 2018-11-20 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
added description of the case studies
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
+
+%------------------------------------------
+\subsection{Description of the Case Studies}
+%------------------------------------------
+
+We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (700 W inverter, with 48h autonomy) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
+
+Note that the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
+Another characteristic of Manaus, based on historical data of solar irradiance \textcolor{red}{Add citation here}, is related to the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
+
 %------------------------------------------
@@
 Experimental setup of HOMER Pro: all experiments were conducted on an otherwise idle Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.
-
-We performed five case studies: (a) four PV systems (700 W inverter, with 48h autonomy) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
-The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
-Another characteristic of Manaus, based on historical data of solar irradiance, is related to the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
 

### 2018-11-20 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-The flowchart of the proposed automated verification tool is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
-As Step 1, the PV input data (e.g., load power demand and load consumption of energy), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, occurs the sizing check of the PV system to make sure that the components accepted international requirements toward a well designed PV project.
+The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
+In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
+In Step 2, the sizing check of the PV system takes place to make sure that the components meet international requirements \textcolor{red}{cite here those requirements} toward a well designed PV project.
 \begin{figure}[h]
@@
 \end{figure}
-The weather variables (solar irradiance and ambient temperature by default) will be explored in all their states by the ESBMC verification engine, in Step 3, based on maximum and minimum values from the site, where the PV system will be deployed.
-As a consequence, all the formulas of the mathematical models used will also be updated.
+%
+In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
+As a consequence, all the formulas of the employed mathematical models will also be updated.
 In addition, depending on one of the desired properties of the system, as autonomy of the batteries, the offer of the energy, or even the power supply from the system to check, whether it is not accomplished (said satisfied), ESBMC accuses a failure, and the diagnostic counterexample shows in which condition the property violation (system fail) happened.

### 2018-11-20 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
further changes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+
+\renewcommand{\baselinestretch}{0.97}
 
@@
 Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}.
-If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, thus resulting in a process known as formal verification.
+If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate the verification process, thus resulting in a process known as \textit{formal verification}.
 Verification may form part of a validation process.
@@
 While simulation and testing explore some of the possible behaviors and scenarios of the system, leaving open the question of whether the unexplored trajectories may contain a flaw, formal verification conducts an exhaustive exploration of all possible behaviors.
-Thus, when a design is pronounced correct by a formal verification method, it implies that all behaviors have been explored, and the questions of adequate coverage or a missed behavior become irrelevant \cite{Clarke2012}.
+Thus, when a design is pronounced correct by a formal verification method, it implies that all behaviors have been explored, and the questions of adequate coverage or a missed behavior becomes irrelevant \cite{Clarke2012}.
 %Simulation may also be used for validation, but it is more problematic for verification.
@@
  %
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}.
-One successful method in this domain is model checking \cite{Clarke2012}.
+
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}; one successful method in this domain is model checking \cite{Clarke2012}.
  % 
@@
 Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
-
-The process of model checking can be divided in three components: modeling, specification, and verification method.
-In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in temporal logic form ($CTL$).
+%
+The process of model checking can be split into three main components: modeling, specification, and verification method.
+In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in a temporal logic form (e.g., $CTL$).
 
@@
 \end{itemize}
-Specifically for the $FALSE$ verification result, the algorithm returns a counterexample that is useful as diagnostic of the system, to discover in which situation the model is violated.
-That is the most important advantage of the use of model checking \cite{ClarkeHV18}.
+Specifically for the $FALSE$ verification result, the algorithm returns a \textit{counterexample} (i.e., a sequence of states that leads to the property violation), which is useful as diagnostic of the system to discover in which situation the model is violated; this is the most important advantage of the use of model checking~\cite{ClarkeHV18}.
 %Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
@@
 However, there is a main disadvantage of model checking: the state explosion problem.
-In order to solve this problem, many different techniques were developed at the last decades.
+In order to tackle this problem, many different techniques were developed in the last decades.
 One of the first major advances was symbolic model checking with binary decision diagrams (BDDs).
 In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice.
-Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes.
-A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
+Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes \textcolor{red}{add citation here}.
+A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level of refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
 However, one of the most promising approaches is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
 
-BMC is a method that checks the model up to a given path in the path length.
+BMC is a method that checks a model up to a given path in the path length.
 BMC algorithms traverse a finite state machine for a fixed number of steps, $ k $, and checks whether violation occurs with this bound.
@@
 SMT decides the satisfiability of first-order formulae using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and non-linear arithmetic, bit-vectors, tuples, arrays, and other decidable first-order theories~\cite{ClarkeHV18}.
-The SAT or SMT solvers would search the model for conditions (value of variables) that would make the formula satisfiable.
-If a SAT or SMT solver finds a substitution for the formula/function then the substitute induces a counterexample and is said satisfiable.
-In other words, is satisfiable only if the verified system contains errors.  
+The SAT or SMT solvers search the model for conditions (value of variables) that make the formula satisfiable.
+If a SAT or SMT solver finds a substitution for the formula/function then the substitute induces a counterexample and is said to be \textit{satisfiable}, i.e., it is satisfiable \textit{iff} the verified system contains errors.
 %
@@
 %The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
-ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
+ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity is increasing and the SMT method has high-level and richer theories than SAT to represent models.
 
@@
 %
-ESBMC's architecture can be summarized in three stages: (I) a front-end that can read and compile C/C++ codes, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, where all the constraints and properties of the system to be verified are encoded into SMT format and solved.
+ESBMC's verification flow can be summarized in three stages: (I) a front-end that can read and compile C/C++ code, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, where all the constraints and properties of the system to be verified are encoded into SMT and checked for satisfiability.
 %
@@
 %Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied. 
-If the SMT formula is shown to be satisfiable (SAT), a counterexample is presented; if the formula is find to be unsatisfiable (UNSAT), there are no errors up to the unwinding bound. 
+If the SMT formula is shown to be satisfiable (SAT), a counterexample is presented; otherwise, the formula is unsatisfiable (UNSAT), i.e., there are no errors up to the given unwinding bound. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%
@@
 from the PV system that were provided by the user, and the tool will verify automatically if the PV system requirements are met.
-If the return is a failure (verification satisfiable), then the tool details the condition of violation, i.e., the state of each variable related to the system.
+If the return is a failure (i.e., SAT), then the tool details the condition of violation, i.e., the state of each variable related to the system.
 That information can be used as a feedback to improve the PV system project.
-However, if the verification succeeds (said UNSAT or unsatisfiable), there is no failure, therefore the PV system will present its intended behavior at the field.
+However, if the verification succeeds (i.e., UNSAT), there is no failure, therefore the PV system will present its intended behavior up the bound $k$, i.e., it does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
 %
@@
 Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to perform the automated verification.
-Line 1 indicates a function call that performs the size checking of the entire PV system: using \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
-The verification is performed by the standard \textit{assert} macro from ANSI-C programming language to each equation.
-The argument to \textit{assert} must be \textit{true} when the macro is executed; otherwise, the program aborts and prints an error message.
-If there is no fail, the algorithm goes on and the batteries are assumed to have SOC of 80\% (Line 5).
+Line 1 indicates a function call that performs the size checking of the entire PV system: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
+The verification is performed by the standard \textit{assert} macro from the ANSI-C programming language to each equation.
+The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints an error message indicating a property violation.
+If there is no property violation, then the verification algorithm continues and the batteries are assumed to have SOC of 80\% (Line 5).
 

### 2018-11-20 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 \author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
-\thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil e-mail alessandrotrindade@ufam.edu.br.}% <-this % stops a space
-\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK e-mail lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
-\thanks{Manuscript received September 19, 2018; revised November 26, 2018.}}
+\thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
+\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
+\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support.}
+\thanks{Manuscript received November 21, 2018; revised XXXXX 11, 2019.}}
 
@@
 \begin{abstract}
-With declining costs and increasing performance, the deployment of renewable energy systems is growing in both developed and developing countries.
-Particular attention is being given to stand-alone solar photovoltaic systems in rural areas or where grid extension is not feasible.
-Tools to evaluate the design and validate electrification projects are available; however, those tools are based on simulations that do not cover all the aspects of the design space.
-Automated verification using model checking, however, has proven to be an effective technique to program verification.
-Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, are encoded into a mathematical model, and a software model checking algorithm was developed to verify its design from a formal perspective.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro.
+With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
+Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is not feasible.
+Tools to evaluate electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space.
+Automated verification using model checking has proven to be an effective technique to program verification.
+However, any kind of system can be verified by model checking, including the most complex.
+Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were encoded into a mathematical model, and a algorithm using model checking features was created in order to validate its design from a formal verification perspective.
+Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro.
 Data from practical applications show the effectiveness of the obtained results, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the proposed verification method.
@@
 \begin{IEEEkeywords}
-Photovoltaic power systems, solar power generation, power system modeling, formal verification, model checking.
+Formal verification, model checking, photovoltaic power systems, power system modeling, solar power generation.
 \end{IEEEkeywords}
@@
 The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing \textcolor{red}{add citation here}.
+In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing \cite{Cubas}.
 
@@
 In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice.
-Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes \textcolor{red}{add citation here}.
+% Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes \textcolor{red}{add citation here}.
 A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level of refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
-However, one of the most promising approaches is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
+Meanwhile, one of the most promising approaches is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
 
@@
 
-However, related to the results of the automated verification, the 1,200 W PV system (house 5) failed during the sizing check.
+However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
 The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
 That verification took 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system, we identified that, in fact, the system mostly of the time does not meet the battery autonomy (mainly when all the loads are turned on).
-However, it is understandable that this problem occurs since the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house.
-
-Related to the four 700 W PV systems, the sizing check was successful during automated verification, but flaws were found in all of them, all related with the battery autonomy, when SOC reached levels below 75\%.
-The automated verification identified the flaws right after the first night-discharge cycle, i.e., before the solar system starts recharging the batteries.
-The proposed method took 409.3 hours to find an error in house 1, and the maximum of \textcolor{red}{456XXX} hours to house 4.
-This functional problem \textcolor{red}{what is a functional problem?} was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
+Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
+That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
+The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
+The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
+The proposed tool took 409.3 hours to find this error at house 1.
+This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
+Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
+
 %At the terminal, the command used to perform the verification is:
@@
 %-------------------------------------
-
 We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
@@
 Although this verification method takes longer than simulation tools, it is able to find specific conditions that lead to failures in a PV system previously validated by simulation tools.
-In particular, the proposed method was successful in finding sizing errors and indicating in which conditions, in terms of temperature and solar irradiation, a PV system can fail.
+In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail.
+New tests must be performed, in an improved setup (i.e., better computing performance), aiming to obtain the results from the houses that presented time-out condition.
 As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems.
 We also will consider other types of renewable energy and even hybrid ones, which will allow our method to design and verify typical rural electrification.
-
+%
+%It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results.
+The proposed tool was successful in find sizing errors and to indicate in which conditions a PV system can fails.
 % into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.

### 2018-11-20 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 The behavior of each system can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
-A key benefit to this approach is that it helps in the detection of faults and flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
+A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
 
@@
 A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level of refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
-Meanwhile, one of the most promising approaches is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
-
+
+Meanwhile, one of the most promising approaches to overcome state explosion problem is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
 BMC is a method that checks a model up to a given path in the path length.
@@
 In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place to make sure that the components meet international requirements \textcolor{red}{cite here those requirements} toward a well designed PV project.
+In Step 2, the sizing check of the PV system takes place to make sure that the components were selected in accordance with recognized design standards \cite{Pinho}.
 \begin{figure}[h]
@@
 After that, the model from PV generator is used in the function call of Line 11, to produce the voltage and current considering the states of $G$ and $T$.
-Following, related to every hour considered, the conditional \textit{if-else-endif} statements from Lines 12, 17, 23 and 28, will perform the charge or discharge of batteries according to the value of different variables: is there is PV generation (which depends on $G$ and $T$), the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+Following, related to every hour considered, the conditional \textit{if-else-endif} statements from Lines 12, 17, 23 and 28, will perform the charge or discharge of batteries according to the value of different variables: if there is PV generation (which depends on $G$ and $T$), the updated state of charge from batteries, the house's load and the set-up information of the PV system.
 
@@
 Note that the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
-Another characteristic of Manaus, based on historical data of solar irradiance \textcolor{red}{Add citation here}, is related to the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
+Another characteristic of Manaus, based on historical weather data \cite{Temperature}, \cite{Irradiance}, is related to the fact that only during 8 hours of the day is possible to have PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
 
@@
 In order to evaluate the proposed verification method and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool.
-\textcolor{red}{This sentence is broken...
-Using functional information collected from owners of those five systems, which were deployed in 2018, serving as cross data about how the systems are behaving during four months of use.}
+Every dweller, who own a PV system, was interviewed in order to get information about his/her PV system during four months of use.
+This information was used to know possible flaws from every system at the field.
 
 All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode enabled with the goal of reducing memory usage \textcolor{red}{Can you please add a footnote of how you call the tool?}; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{At the terminal, the command used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
 
@@
 %------------------------------------------
-
-\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
-
-We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
-Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four systems \textcolor{red}{which four system?
-can you please identify each one by a number?
-they should also be described}, without any indication of sizing error or even performance.
+%
+%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
+%\begin{enumerate}
+%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
+%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
+%
+We have evaluated five case studies in total.
+Related to the results of the automated verification and the evaluation if the results are correct: (a) the 1,200 W PV system (house 5) failed during the sizing check.
+The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 PV panels in parallel and the sized project has 2 in series and 2 in parallel.
+That verification took 63.3 hours to be performed.
+Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
+That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
+The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
+The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
+The proposed tool took 409.3 hours to find this error at house 1.
+This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
+Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
+
+We evaluated the same five case studies using HOMER Pro tool.
+The result of simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
+The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
+All the simulations took less than 5 seconds (each) to be performed with HOMER Pro.
+
+Despite the divergence of results for the house 1, comparing our automated tool with HOMER Pro, it is evident that the information collect from the dweller shows that the automated verification has the correct evaluation of the PV system.
+House 5 presented flaws from both tools, however only the automated verification showed which system project error was responsible for the flaw (the cause was the number of solar panels in parallel).
+However, houses 2, 3 and 4 did not have results from the verification tool, considering the established time-out for the experimental evaluation.
+%
+%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
+Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
 The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
 All the simulations took less than 5 seconds (each) to be performed.
-
-However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
+%
+%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
 The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
@@
 %---------------------------------------------------
-
 We have reported a favorable assessment of the proposed verification method over a diverse set of real-world benchmarks.
@@
 % (used to reserve space for the reference number labels box)
-
+%
 %\begin{thebibliography}{1}
@@
 %\end{thebibliography}
-
+%
 %%%%%%%%%%%%%% biography section
@@
 % or if you just want to reserve a space for a photo:
-
-\begin{IEEEbiographynophoto}{Alessandro Trindade}
+\begin{IEEEbiography}
+    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alessandro3por4_2}}]{Alessandro Trindade}
 received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
@@
 His interest is in renewable energy, automated verification, and model checking.
-\end{IEEEbiographynophoto}
-
+\end{IEEEbiography}
+%
+%\begin{IEEEbiographynophoto}{Alessandro Trindade}
+%received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
+Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
+Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation (Centre of Analysis, Research and Innovation Technology Foundation).
+His interest is in renewable energy, automated verification, and model checking.
+%\end{IEEEbiographynophoto}
+%
 % if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{Lucas Cordeiro}
+\begin{IEEEbiography}
+    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lucas3por4}}]{Lucas Cordeiro}
 received his Ph.D.
@@
 His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.
-\end{IEEEbiographynophoto}
+\end{IEEEbiography}
 

### 2018-11-21 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 %--------------------------------------
-
 ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs \cite{esbmc2018}. 
 %
-ESBMC's verification flow can be summarized in three stages: (I) a front-end that can read and compile C/C++ code, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, where all the constraints and properties of the system to be verified are encoded into SMT and checked for satisfiability.
+ESBMC's verification flow can be summarized in three stages: (I) a front-end that can read and compile C/C++ code, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, or SMT solver, where all the constraints and properties of the system to be verified are encoded into SMT and checked for satisfiability.
 %
@@
 If the SMT formula is shown to be satisfiable (SAT), a counterexample is presented; otherwise, the formula is unsatisfiable (UNSAT), i.e., there are no errors up to the given unwinding bound.
+
+% incremental ESBMC text here
+Related to the standardized input language to SMT solvers, aka SMTLIB logic format, there is a resource called \textit{assertion stack}.
+An assertion, in SMT solvers, is a constraint on the variables in formula that must hold if the formula is satisfiable \cite{Morse2015}.
+New assertions can be added to or old assertions removed from this stack, depending on the evaluated value of variables.
+This enables the solver to learn from previous checks for future checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and discart data during the process, incrementally.
+This technique is called "Incremental SMT" \cite{Morse2015}.
+The process of retraction to build and deconstruct the formula allow reduced SMT-conversion overhead of memory, mainly when the verified system is complex and the computing platform do not have large amount of RAM memory to deal with all the design space state.
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%

### 2018-11-21 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 % incremental ESBMC text here
-Related to the standardized input language to SMT solvers, aka SMTLIB logic format, there is a resource called \textit{assertion stack}.
+Related to the standardized input language to SMT solvers (SMTLIB logic format), there is a resource called \textit{assertion stack}.
 An assertion, in SMT solvers, is a constraint on the variables in formula that must hold if the formula is satisfiable \cite{Morse2015}.
 New assertions can be added to or old assertions removed from this stack, depending on the evaluated value of variables.
-This enables the solver to learn from previous checks for future checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and discart data during the process, incrementally.
+This enables the solver to learn from previous checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and discart data during the process, incrementally.
 This technique is called "Incremental SMT" \cite{Morse2015}.
-The process of retraction to build and deconstruct the formula allow reduced SMT-conversion overhead of memory, mainly when the verified system is complex and the computing platform do not have large amount of RAM memory to deal with all the design space state.
+The process of retraction to build and deconstruct the formula allow to reduce the overhead of memory, mainly when the verified system is complex and the computing platform do not have large amount of memory to deal with all the design space state.
 %
@@
 %------------------------------------------
-
 Our experimental evaluation aims to answer three research questions:
@@
 Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{At the terminal, the command used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+The experiments were performed without a predefined timeout.
 
@@
 Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
-The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
-The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
-The proposed tool took 409.3 hours to find this error at house 1.
-This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
-Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
-
-We evaluated the same five case studies using HOMER Pro tool.
-The result of simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
+That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during automated verification, but there was found flaws related with the battery autonomy, when SOC reached a empty-battery level.
+The automated verification identified the flaws (for all houses) right after the first night-discharge cycle, before the solar system start to recharge the batteries.
+The proposed tool took 409.3 hours to find this flaw at house 1; 611.2 hours to house 2; 615.8 hours to house 3, and 620.8 hours to house 4.
+This possible flaws were confirmed with the dwellers that owns the systems by interview: at least once a mouth is usual the system to turn off, normally in raining or clouds days, reaching the situation described in Step 3 of \ref{table:controller}; and after the sun rises, the systems returns to normal operation.
+
+The same five case studies were evaluated by HOMER Pro.
+The result of simulation shows that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
 The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
@@
 
-Despite the divergence of results for the house 1, comparing our automated tool with HOMER Pro, it is evident that the information collect from the dweller shows that the automated verification has the correct evaluation of the PV system.
-House 5 presented flaws from both tools, however only the automated verification showed which system project error was responsible for the flaw (the cause was the number of solar panels in parallel).
-However, houses 2, 3 and 4 did not have results from the verification tool, considering the established time-out for the experimental evaluation.
+Despite the divergence of results for the houses 1, 2, 3 and 4, comparing our automated tool with HOMER Pro, it is evident that the information collect from the dweller shows that the automated verification has the correct evaluation of the PV system.
+House 5 presented flaws from both tools, however only the automated verification showed which system project error was responsible for the flaw (number of PV panels).
+
+It is worth to mention that a PV design always uses daily average values of sun hours to each site, with impact at the PV components.
+Those hours are based on historic data and, in field, it is not unusual to find days where that number of hours was not reached, because of weather.
+The season has impact, as the fact that the case studies are from the Rain Forest, where the clouds are always present.
+With that in mind, the identified flaws at houses 1, 2, 3, and 4, are justified once again.
 %
@@
 
-\textit{Time step:} The runtime complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario, where a solar irradiance and ambient temperature can change in fractions of minutes.
+\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario, where a solar irradiance and ambient temperature can change in fractions of minutes.
 
@@
 In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail.
-New tests must be performed, in an improved setup (i.e., better computing performance), aiming to obtain the results from the houses that presented time-out condition.
+New tests must be performed, in an improved setup (i.e., better computing performance), aiming to obtain the results in less time.
 As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems.
@@
 \section*{Acknowledgment}
-The authors would like to thank Newton Fund (Star Energy project), Coventry University, Sustainable Amazonas Foundation (FAS), and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support and for the possibility to test the tool with real PV systems.
+To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to test real PV systems.
 

### 2018-11-21 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
updated incremental SMT description
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 % incremental ESBMC text here
-Related to the standardized input language to SMT solvers (SMTLIB logic format), there is a resource called \textit{assertion stack}.
-An assertion, in SMT solvers, is a constraint on the variables in formula that must hold if the formula is satisfiable \cite{Morse2015}.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}.
+An assertion, in SMT solvers, is a constraint over the variables in a formula that must hold if the formula is satisfiable~\cite{Morse2015}.
 New assertions can be added to or old assertions removed from this stack, depending on the evaluated value of variables.
-This enables the solver to learn from previous checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and discart data during the process, incrementally.
-This technique is called "Incremental SMT" \cite{Morse2015}.
-The process of retraction to build and deconstruct the formula allow to reduce the overhead of memory, mainly when the verified system is complex and the computing platform do not have large amount of memory to deal with all the design space state.
+This enables ESBMC, and the respective solver, to learn from previous checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called ``incremental SMT'' and allows us to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with all the design space state.
+
 %

### 2018-11-21 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-We have evaluated five case studies in total.
-Related to the results of the automated verification and the evaluation if the results are correct: (a) the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 PV panels in parallel and the sized project has 2 in series and 2 in parallel.
+The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check.
+The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the sized project has 2 in series and 2 in parallel.
 That verification took 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during automated verification, but there was found flaws related with the battery autonomy, when SOC reached a empty-battery level.
-The automated verification identified the flaws (for all houses) right after the first night-discharge cycle, before the solar system start to recharge the batteries.
-The proposed tool took 409.3 hours to find this flaw at house 1; 611.2 hours to house 2; 615.8 hours to house 3, and 620.8 hours to house 4.
-This possible flaws were confirmed with the dwellers that owns the systems by interview: at least once a mouth is usual the system to turn off, normally in raining or clouds days, reaching the situation described in Step 3 of \ref{table:controller}; and after the sun rises, the systems returns to normal operation.
+Surveying the owner of the 1,200 W system, it was identified that, in fact, the system most of the time does not meet the battery autonomy (mainly when all the loads are turned on).
+That behavior is expected since the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but we have found flaws related to the battery autonomy, when SOC reached a empty-battery level.
+Our verification engine identified the flaws (for all houses) right after the first night-discharge cycle, before the solar system started to recharge the batteries.
+Our verification engine took 409.3 hours to find this flaw in house 1; 611.2 hours to house 2; 615.8 hours to house 3, and 620.8 hours to house 4.
+This possible flaws were confirmed with the dwellers that owns the systems by interview: at least once a mouth is usual the system to turn off, normally in raining or clouds days, reaching the situation described in Step 3 of~\ref{table:controller}; and after the sun rises, the systems returns to normal operation.
 

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the sized project has 2 in series and 2 in parallel.
-That verification took 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system, it was identified that, in fact, the system most of the time does not meet the battery autonomy (mainly when all the loads are turned on).
-That behavior is expected since the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but we have found flaws related to the battery autonomy, when SOC reached a empty-battery level.
-Our verification engine identified the flaws (for all houses) right after the first night-discharge cycle, before the solar system started to recharge the batteries.
-Our verification engine took 409.3 hours to find this flaw in house 1; 611.2 hours to house 2; 615.8 hours to house 3, and 620.8 hours to house 4.
-This possible flaws were confirmed with the dwellers that owns the systems by interview: at least once a mouth is usual the system to turn off, normally in raining or clouds days, reaching the situation described in Step 3 of~\ref{table:controller}; and after the sun rises, the systems returns to normal operation.
+The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel.
+This verification took approximately 63.3 hours to be performed.
+Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on); this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but we have found flaws related to the battery autonomy, when SOC reached a empty-battery level.
+Our verification engine identified those flaws (for all four houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries.
+Our verification engine took approximately 409.3 hours to find this flaw in house 1; 611.2 hours for house 2; 615.8 hours for house 3, and 620.8 hours for house 4.
+These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a mouth is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of~\ref{table:controller}; and after the sun rises, the systems returns to normal condition operation.
 

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 This verification took approximately 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on); this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but we have found flaws related to the battery autonomy, when SOC reached a empty-battery level.
+Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on); this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level.
 Our verification engine identified those flaws (for all four houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries.
 Our verification engine took approximately 409.3 hours to find this flaw in house 1; 611.2 hours for house 2; 615.8 hours for house 3, and 620.8 hours for house 4.
-These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a mouth is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of~\ref{table:controller}; and after the sun rises, the systems returns to normal condition operation.
+These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a mouth is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}; after the sun rises, the systems returns to normal condition operation.
 
 The same five case studies were evaluated by HOMER Pro.
-The result of simulation shows that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
+The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues.
 The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
-All the simulations took less than 5 seconds (each) to be performed with HOMER Pro.
-
-Despite the divergence of results for the houses 1, 2, 3 and 4, comparing our automated tool with HOMER Pro, it is evident that the information collect from the dweller shows that the automated verification has the correct evaluation of the PV system.
-House 5 presented flaws from both tools, however only the automated verification showed which system project error was responsible for the flaw (number of PV panels).
-
-It is worth to mention that a PV design always uses daily average values of sun hours to each site, with impact at the PV components.
-Those hours are based on historic data and, in field, it is not unusual to find days where that number of hours was not reached, because of weather.
-The season has impact, as the fact that the case studies are from the Rain Forest, where the clouds are always present.
-With that in mind, the identified flaws at houses 1, 2, 3, and 4, are justified once again.
+All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
+%
+Despite the divergence of results for the houses 1, 2, 3 and 4 w.r.t.
+our proposed approach, it is evident that the information collected from the dwellers indicate that our approach has the correct evaluation of the PV system.
+House 5 presented flaws from both tools; however, only our approach indicated which system project error was responsible for the flaw (number of PV panels).
+%
+Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
+Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions.
+The season has impact since the case studies are from the rain forest, where clouds are always present.
+As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
 %

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.97}
+\renewcommand{\baselinestretch}{0.96}
 
@@
 With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
-Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is not feasible.
-Tools to evaluate electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space.
+Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
+Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
 Automated verification using model checking has proven to be an effective technique to program verification.
-However, any kind of system can be verified by model checking, including the most complex.
-Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were encoded into a mathematical model, and a algorithm using model checking features was created in order to validate its design from a formal verification perspective.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro.
-Data from practical applications show the effectiveness of the obtained results, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the proposed verification method.
+Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, are encoded into mathematical models and a software model checking algorithm formally verifies its design.
+Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate the proposed approach and also to compare it with specialized simulation tools.
+Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected by our method.
 %Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.
@@
 This enables ESBMC, and the respective solver, to learn from previous checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT'' and allows us to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with all the design space state.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows us to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with all the design space state.
 

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
-Only a niche market a few years ago, solar photovoltaic (PV) are now becoming a mainstream electricity provider. 
+Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider. 
 % changing the way the world is powered. 
@@
 %The increase in the number of PV systems installed and been projected all over the world brings the need for %proper modeling and simulation tools for researchers and practitioners involved in their application.
-design validation - ensuring the correctness of the design at the earliest stage possible - which is a major challenge in any responsible system development process, and the activities intended for its solution occupy an ever increasing portions of the  development cycle cost and time budgets \cite{ClarkeHV18}.
+design validation -- ensuring the correctness of the design at the earliest stage possible -- which is a major challenge in any responsible system development process, and the activities intended for its solution occupy an ever increasing portions of the  development cycle cost and time budgets \cite{ClarkeHV18}.
 %The currently practiced methods for design validation in most sites are still the veteran techniques of simulation and testing \cite{ClarkeHV18}.
 
-In order to model, simulate, or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan}, \cite{Swarnkar}, \cite{NRELDobos}, \cite{NRELBlair}, \cite{Mills}; and even general purpose simulation tools as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999}, \cite{Benatiallah2017}.
-
+In order to model, simulate, or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+%
 %However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
@@
 However, those tools are based on running experiments in simulation models.
-Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded; however, it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of systems is rarely possible or even feasible~\cite{ClarkeHV18}.
-
-Formal methods based on software model checking offer great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
+Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of systems is rarely possible or even unfeasible~\cite{ClarkeHV18} to be achieved in practice.
+
+Formal methods based on software model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
 %with behavior that is, in principle, well determined. 
- Using this technique, any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior.
-Then, one can try to give a formal proof or otherwise establish that the program meets its specification.
-User or project requirements can be added during the process of coding.
+Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
+User or project requirements can be added during the creation of the formal model to be verified.
 %, as defined by \cite{Trindade}.
@@
 
-Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}.
-It allows one to develop models for each component of the system.
+Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}, allowing the development of models for each system component.
 In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Automated verification using model checking has proven to be an effective technique to program verification.
-Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, are encoded into mathematical models and a software model checking algorithm formally verifies its design.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate the proposed approach and also to compare it with specialized simulation tools.
-Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected by our method.
+This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
+Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
+Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected by our automated verification method.
 %Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.
@@
 
-Formal methods based on software model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
+Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
 %with behavior that is, in principle, well determined. 
@@
 Finally, model checking algorithms can verify the system model by systematically exploring all their states. As a result, the formal proof can verify if the requirements are met by the system.
-
-Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}, allowing the development of models for each system component.
+%
+%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
+%
 In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %The increase in the number of PV systems installed and been projected all over the world brings the need for %proper modeling and simulation tools for researchers and practitioners involved in their application.
-design validation -- ensuring the correctness of the design at the earliest stage possible -- which is a major challenge in any responsible system development process, and the activities intended for its solution occupy an ever increasing portions of the  development cycle cost and time budgets \cite{ClarkeHV18}.
+design validation -- ensuring the correctness of the design at earliest stages -- which is a major challenge in any responsible system development process, and the activities intended for its solution occupy an ever increasing portions of the  development cycle cost and time budgets \cite{ClarkeHV18}.
 %The currently practiced methods for design validation in most sites are still the veteran techniques of simulation and testing \cite{ClarkeHV18}.
 
-In order to model, simulate, or evaluate a PV system, there are a myriad of specialized tools available in the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+In order to model, simulate, or evaluate a PV system, there are a myriad of specialized tools available in the market such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 %
@@
 However, those tools are based on running experiments in simulation models.
-Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of systems is rarely possible or even unfeasible~\cite{ClarkeHV18} to be achieved in practice.
+Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is rarely possible or even unfeasible~\cite{ClarkeHV18} to be achieved in practice.
 
@@
 %Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
-Finally, model checking algorithms can verify the system model by systematically exploring all their states. As a result, the formal proof can verify if the requirements are met by the system.
+Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
 %
@@
 In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.
-The behavior of each system can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
 A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
@@
 %Here it will be verified a stand-alone PV system, with all their components modeled mathematically, 
-Related to solar PV systems, the project requirements, as battery autonomy and power demand, beside weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
+Related to solar PV systems, the project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
 The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to formally verify a PV system as a C program.
-
-In prior studies, the evaluation of PV systems, concerning the meeting of user requirements, were performed by software simulation tools using MATLAB/Simulink \cite{Benatiallah2017}, \cite{Samrat2014}, and \cite{Natsheh2012} or HOMER Pro \cite{Lamnadi2017}.
-Some studies were carried out toward the formal modeling of power smart grids \cite{Akram2018}, and to maximize the power point of solar panels \cite{Driouich2017}; however, those studies do not perform automated verification and they restrict themselves to solar panels or smart grids.
-
+The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to formally verify a PV system as an imperative program.
+
+In prior studies, the evaluation of PV systems w.r.t.
+user requirements were performed by software simulation tools using MATLAB/Simulink~\cite{Benatiallah2017}, \cite{Samrat2014}, and \textcolor{red}{Tool name?}~\cite{Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
+Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and to maximize the power point of solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification and they restrict themselves to solar panels or smart grids.
+%
 In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus has been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
@@
 %The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
-Given the current knowledge in formal verification, this is the first initiative to use a verification tool to evaluate a stand-alone solar PV systems. %, with weather conditions variation. 
+Given the current knowledge in formal verification, this is the first initiative to use a formal verification tool to evaluate the design of a stand-alone solar PV system.
+%, with weather conditions variation.
 The mains contribution of this paper are the automated verification of the PV system, and the modular modeling of each component of the PV system, which allows one to change the mathematical models, besides changing the type of energy generation in the future to another renewable source.
+\textcolor{red}{why changing the mathematical model is a contribution?
+Please clarify it further!}
 

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-PV systems are broadly classified into three distinct types~\cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system.
+PV systems are classified into three distinct types~\cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which do not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system.
 %, where another source(s) of energy can work together with the solar PV.
@@
 %\end{itemize}
-Specifically concerning the energy needed for remote rural areas of developing countries or places where the grid extension is not possible or feasible, 
+Specifically for the energy needed for remote rural areas of developing countries or places where the grid extension is not possible or even feasible, 
 %stand-alone systems are one the most used solutions, and 
@@
 %can be split into several categories. However, 
-the most suitable configuration is the regulated stand-alone system with battery and AC load. This configuration is the focus of this study.
+the most suitable configuration is the regulated stand-alone system with battery and AC load; this configuration is the focus of this study.
 %, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
@@
 %
-In order to address different aspects of project system and systems design, there are various software tools \cite{Rajanna}, \cite{Rawat}.
+In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
 %public domain and commercial software available for the PV market. 
 %According to \cite{Brooks}, t
-The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
+The capabilities of those tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
  to complex financial analysis and project optimization. 
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here it was evaluated the most popular ones, which are PVWatts, SAM, HOMER, RETScreen, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
+Here we evaluated the most popular ones: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
 
@@
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-RETScreen and HOMER have a free web-based version, but they have limited resources: it is not allowed to save the projects or even upload data from manufacturers.
-However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription range from US\$504.00 to US\$657.00.
+RETScreen and HOMER have a free web-based version, but they have limited resources since they do not allow us to save the PV projects or even upload data from manufacturers.
+However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription typically range from US\$504.00 to US\$657.00.
 
@@
 %
-Considering the focus of this study, only HOMER remains for a comparative evaluation with our proposed automated verification technique.
-%All tools need some parameters inherently from manufacturer's catalog.
+In this study, only HOMER remains for a comparative evaluation with our proposed verification approach. %All tools need some parameters inherently from manufacturer's catalog.
 %, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
 %After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-The main challenge here is to demonstrate the use of automated verification in stand-alone PV solution, thus proving that this evaluation is more effective and complete than other state-of-the-art tool, as HOMER Pro.
+The main challenge here is to demonstrate the use of automated software model checking in stand-alone PV solution, thus proving that this evaluation is more effective and complete than other state-of-the-art tool such as HOMER Pro.
 The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section~\ref{sec:results_indeed}.

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-The main challenge here is to demonstrate the use of automated software model checking in stand-alone PV solution, thus proving that this evaluation is more effective and complete than other state-of-the-art tool such as HOMER Pro.
-The comparative evaluation between the HOMER Pro and the proposed verification tool is presented in Section~\ref{sec:results_indeed}.
+Thus, the main challenge here is to demonstrate the application of software model checking to formally verify a stand-alone PV solution, thus proving that this approach is more effective and complete than other state-of-the-art tool such as HOMER Pro.
+The comparative evaluation between HOMER Pro and our approach is presented in Section~\ref{sec:results_indeed}.
 
 %-------------------------------------------------------------------
-\subsection{Component models for stand-alone PV system }
+\subsection{Component models for a stand-alone PV system }
 %-------------------------------------------------------------------
@@
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
-In the diagram, there are two variables that depend on the site where the system is deployed and from the weather (solar irradiance $G$ and temperature $T$).
-For night hours or rainy days, one needs to hold batteries, where power can be stored and used.
+In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
+For night hours or rainy days, we need to hold batteries, where power can be stored and used.
 The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen,Mellit}.
@@
 \centering
-\caption{Block diagram for the stand-alone PV system~\cite{Hansen}.}
+\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
 \label{fig:blockdiagram}
@@
 
-The 1-diode model, illustrated in Fig. \ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described in Eq.~\eqref{eq:1diodemodel}:
+The 1-diode model, illustrated in Fig. \ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described by Eq.~\eqref{eq:1diodemodel}:
 \begin{equation}
@@
 The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing \cite{Cubas}.
-
+In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
+ %
 %\subsection{PV Panel Model}
@@
 %
-The voltage and the current at the maximum power point tracking (MPPT), can be expressed by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm} \cite{Saloux}.
-%These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
+The voltage and the current at the maximum power point tracking (MPPT), can be described by Equations \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm}  as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
 \begin{equation}
@@
 
-\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions
+\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions
 (provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
 %
-The cell temperature ($ T $) is described in Eq.~\ref{eq:Tcell}~\cite{Ross}:
+The cell temperature ($ T $) is described by Eq.~\ref{eq:Tcell}~\cite{Ross}:
 \begin{equation}
@@
 
-Furthermore, Eq.~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature~\cite{Villalva}. 
+Furthermore, Eq.~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\cite{Villalva} 
 %In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
@@
 
-\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage, and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
+\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
 
 %The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current \eqref{eq:Pm} and the saturation current in the reference temperature given by Eq.~\ref{eq:I0}, the diode ideality factor is determined by Eq.~\ref{eq:a}:
+Using the maximum power point current (cf.
+Eq.~\eqref{eq:Pm}) and the saturation current in the reference temperature given by Eq.~\eqref{eq:I0}, the diode ideality factor is determined by Eq.~\eqref{eq:a}:
 \begin{equation}
@@
 
-In addition to the model verification that will be performed by the proposed technique at this paper, there is the prior stage of PV system sizing check, based on manufacturer's data and information from the sizing and the site.
-That stage will guarantee if the system was well designed, considering the standard steps of project \cite{Pinho}.
-
-Firstly, it is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$).
-That is done by \eqref{eq:Ecorrected}~\cite{Pinho}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
+In addition to the model verification performed by the proposed technique, there is the prior stage of PV system sizing check, based on manufacturer's data and information from the sizing and the site; this stage ensures that the system meets its specification, thereby considering the standard project steps~\cite{Pinho}.
+%
+Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}~\cite{Pinho}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered as
 \begin{equation}
@@
 
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed by \eqref{eq:NTPmin}, and the check is performed using \eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from \eqref{eq:NTPmin}.
+The total minimum number of needed solar panels ($N_{TPmin}$) is computed by Eq.~\eqref{eq:NTPmin} and the check is performed using Eq.~\eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from Eq.~\eqref{eq:NTPmin}.
 \begin{equation}
@@
 
-Particularly, the total number of panels is series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by \eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.
-With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}).
-$ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
+Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.
+With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}), $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
 \begin{equation}
@@
 
-Several models have been presented in the literature and the most commum are based on lead-acid batteries ~\cite{Copetti,Manwell93,Pinho}. 
+Various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Manwell93,Pinho};
 %, and \cite{Manwell94}. 
@@
 %
-That kind of battery has relative low cost and wide availability~\cite{Copetti}.
-
-Here, the model adopted uses only manufacturer's data, without the need of empirical tests~\cite{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature.
-
-The discharge voltage equation is described in \eqref{eq:bat_Vd}. 
+that kind of battery has relative low cost and wide availability~\cite{Copetti}. 
+%
+Here, the model adopted uses only manufacturer's data without empirical tests~\cite{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature. 
+%
+The discharge voltage equation is described by \eqref{eq:bat_Vd} as
 %The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
@@
 
-\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at given time.
+\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time.
 Mathematically, it is the ratio between the present capacity and the nominal capacity (in $ Ah $, provided by manufacturer).
-If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged.
+If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.
 %, defined by Equation \ref{eq:SOCbat}.
@@
 
-For the charging process, however, the parameters are presented in \eqref{eq:Vcbat}.
+For the charging process, however, the parameters are described by Eq.~\eqref{eq:Vcbat} as
 %
@@
 \label{eq:Vcbat}
-V_{c} = [2+0.16SOC]+ \\ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T)
+V_{c} = [2+0.16SOC]+ \\ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
 \end{multline}
 
-SOC can be calculated easily at any point during the discharge period, considering the current drained from batteries during a certain time period.
+Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period.
 %; however, during recharge it is much more difficult \cite{Copetti}.
@@
 %\end{multline}
-
+%
 %\begin{multline}
@@
 In addition to the model verification, there is also the prior stage of project sizing check, as performed for the solar panel.
-Firstly it is necessary to define the total capacity of the battery bank, as described by \eqref{eq:Cbank}.
+Firstly we define the total capacity of the battery bank, as described by Eq.
+\eqref{eq:Cbank} as
 \begin{equation}
@@
 \end{equation}
-
-The variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; the other variables were discussed previously at Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
-
-Secondly, the total (minimum) number of batteries is computed, as described in \eqref{eq:Nbtotal}.
-Moreover, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
+%
+\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
+%
+Secondly, the total (minimum) number of batteries is computed, as described by Eq.~\eqref{eq:Nbtotal}.
+Additionally, Eq.~\eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
 \begin{equation}
@@
 %
-In general, there are two main operating modes for the controller: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
+In general, there are two main operating modes for the controller \textcolor{red}{add citation here}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
 
@@
 %\end{figure}
-
+%
 In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \textunderscore off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}.
@@
 %As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of DC-DC converter is given by \eqref{eq:poutcont}. 
+The output power ($ P_{out} $) of DC-DC converter is given by Eq.~\eqref{eq:poutcont} as
 \begin{equation}
@@
 
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from \eqref{eq:poutcont} it is possible to reach \eqref{eq:potcont}.
+Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Eq.~\eqref{eq:poutcont} we compute Eq.~\eqref{eq:potcont} as
 \begin{equation}
@@
 One more time, some steps must be done to check the sizing project of the controller, prior the verification phase.
-Initially, the controller must meet the voltage requirement of the PV system, as described in \eqref{eq:vcvsystem}.
+Initially, the controller must meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem}:
 \begin{equation}
@@
 
-Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as shown by \eqref{eq:iscamb}.
+Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by Eq.~\eqref{eq:iscamb}:
+%
 \begin{equation}
@@
 
-The controller must meet the maximum current from the PV array \eqref{eq:icmin} and \eqref{eq:icicmin}.
+The controller must meet the maximum current from the PV array given by \eqref{eq:icmin} and \eqref{eq:icicmin}.
 \begin{equation}
@@
 The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage, % (127 V or 220 V, for example), 
-and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
+and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by Eq.~\eqref{eq:efficinv} \cite{Hansen}:
 %
@@
 
-\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be find from the inverter's data-sheet.
+\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be obtained from the inverter's data-sheet.
 
@@
 %
-The sizing project check of the inverter is done through three Equations.
-Eq.
-\eqref{eq:vindc} ensures that the input voltage of the controller meet the voltage of the system.
-Eq.
-\eqref{eq:voutac} ensures that the output voltage of the controller meet the AC voltage of the load.
-Moreover, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
+The sizing project check of the inverter is carried out by means of three equations.
+Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
+Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
+Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 \begin{equation}

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %\title{Building a framework to perform automated verification of solar photovoltaic off-grid systems}
-\title{Automated verification of stand-alone solar photovoltaic systems}
+\title{Automated Verification of Stand-Alone Solar Photovoltaic Systems}
 %
@@
 %The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
-Given the current knowledge in formal verification, this is the first initiative to use a formal verification tool to evaluate the design of a stand-alone solar PV system.
-%, with weather conditions variation.
-The mains contribution of this paper are the automated verification of the PV system, and the modular modeling of each component of the PV system, which allows one to change the mathematical models, besides changing the type of energy generation in the future to another renewable source.
-\textcolor{red}{why changing the mathematical model is a contribution?
-Please clarify it further!}
+Given the current knowledge in formal verification, this is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system.
+In summary, this paper makes three original contributions.
+Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into first-order theories supported by software model checkers.
+Secondly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT).
+Thirdly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other state-of-the-art approaches based on simulation.
 
@@
 %--------------------------------------------------
-\section{Automated verification}
+\section{Automated Verification Using Model Checking}
 \label{sec:AutomatedVerification}
@@
 %----------------------------------------
-\section{Methodology }
+\section{Model Checking Stand-alone Solar Photovoltaic Systems }
 \label{sec:Methodology}
@@
 We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W.
-Although this verification method takes longer than simulation tools, it is able to find specific conditions that lead to failures in a PV system previously validated by simulation tools.
+Although this verification method takes longer than simulation methods, it is able to find specific conditions that lead to failures in a PV system previously validated by a commercial simulation tool.
 In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail.
-New tests must be performed, in an improved setup (i.e., better computing performance), aiming to obtain the results in less time.
+%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
 As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems.

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 \thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support.}
-\thanks{Manuscript received November 21, 2018; revised XXXXX 11, 2019.}}
+\thanks{Manuscript received November 23, 2018; revised XXXXX 11, 2019.}}
 
@@
 In prior studies, the evaluation of PV systems w.r.t.
-user requirements were performed by software simulation tools using MATLAB/Simulink~\cite{Benatiallah2017}, \cite{Samrat2014}, and \textcolor{red}{Tool name?}~\cite{Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
+user requirements were performed by software simulation tools using \textcolor{blue} {MATLAB/Simulink~\cite{Benatiallah2017, Samrat2014, Natsheh2012}}, or HOMER Pro \cite{Lamnadi2017}.
 Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and to maximize the power point of solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification and they restrict themselves to solar panels or smart grids.
@@
 %
-In general, there are two main operating modes for the controller \textcolor{red}{add citation here}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
+In general, there are two main operating modes for the controller \textcolor{blue} {\cite{Rawat}}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
 

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
updated references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to formally verify a PV system as an imperative program.
+The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
 
 In prior studies, the evaluation of PV systems w.r.t.
-user requirements were performed by software simulation tools using \textcolor{blue} {MATLAB/Simulink~\cite{Benatiallah2017, Samrat2014, Natsheh2012}}, or HOMER Pro \cite{Lamnadi2017}.
+user requirements were performed by software simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Samrat2014, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
 Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and to maximize the power point of solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification and they restrict themselves to solar panels or smart grids.
@@
 In summary, this paper makes three original contributions.
-Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into first-order theories supported by software model checkers.
+Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
 Secondly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT).

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %It is necessary to keep in mind that 
-Validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}.
+Validation is the process of determining whether a design meets the user requirements, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}.
 If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate the verification process, thus resulting in a process known as \textit{formal verification}.
@@
 The process of model checking can be split into three main components: modeling, specification, and verification method.
-In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in a temporal logic form (e.g., $CTL$).
-
+In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in a temporal logic form (e.g., CTL or LTL).
+%
 %\begin{itemize}
@@
 %\end{itemize}
-
+%
 The model checking algorithm can be described as \cite{ClarkeHV18}:  
-
+%
 \begin{itemize}
-\item Given the model $ 'M' $ and a $CTL$ formula $ \phi $ as input;  
+\item Given the model $M$ and a CTL (or LTL) formula $ \phi $ as input;  
 \item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
-\item It returns $YES$ if $ \phi $ is $TRUE$, or returns $NO$ if $ \phi $ is $FALSE$.  
+\item It returns \textit{YES} if $ \phi $ is \textit{TRUE}, or returns \textit{NO} if $ \phi $ is \textit{FALSE}.  
 \end{itemize}
-Specifically for the $FALSE$ verification result, the algorithm returns a \textit{counterexample} (i.e., a sequence of states that leads to the property violation), which is useful as diagnostic of the system to discover in which situation the model is violated; this is the most important advantage of the use of model checking~\cite{ClarkeHV18}.
+Specifically for the \textit{FALSE} verification result, the algorithm returns a \textit{counterexample} (i.e., a sequence of states that leads to a property violation), which is useful as diagnostic of the system to discover in which situation the model is violated; this is the most important advantage of the use of model checking~\cite{ClarkeHV18}.
 %Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
@@
 %Fig. \ref{fig:modelcheckstruc} shows the structure of a 
-In a typical model checking system, a preprocessor extracts a state transition graph from a system (program or circuit).
+%In a typical model checking system, a preprocessor extracts a state transition graph from a system (program or circuit).
 %
@@
 A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level of refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
-
-Meanwhile, one of the most promising approaches to overcome state explosion problem is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
+%
+Another promising approach to overcome state explosion problem is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
 BMC is a method that checks a model up to a given path in the path length.
-BMC algorithms traverse a finite state machine for a fixed number of steps, $ k $, and checks whether violation occurs with this bound.
-It uses Boolean Satisfiability (SAT) or Satisfiability Module Theories (SMT) solvers.
+BMC algorithms traverse a finite state machine for a fixed number of steps, $ k $, and checks whether a property violation occurs with this bound.
+It uses Boolean Satisfiability (SAT) or Satisfiability Module Theories (SMT) solvers to check the generated formula from BMC.
+
 SAT problem is a problem of determining whether there are certain conditions or interpretations that satisfy a given Boolean expression \cite{ClarkeHV18}. 
-SMT decides the satisfiability of first-order formulae using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and non-linear arithmetic, bit-vectors, tuples, arrays, and other decidable first-order theories~\cite{ClarkeHV18}.
+SMT decides the satisfiability of a fragment of first-order formulae using a combination of different background theories and thus generalizes SAT by supporting uninterpreted functions, linear and non-linear arithmetic, bit-vectors, tuples, arrays, and other decidable first-order theories~\cite{ClarkeHV18}.
 The SAT or SMT solvers search the model for conditions (value of variables) that make the formula satisfiable.
@@
 %The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
-ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity is increasing and the SMT method has high-level and richer theories than SAT to represent models.
+ESBMC comes as an alternative to overcome limitations of the system modeling, especially considering that the system complexity is increasing and SMT has richer theories than SAT to represent models.
 
@@
 %--------------------------------------
-ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs \cite{esbmc2018}. 
-%
-ESBMC's verification flow can be summarized in three stages: (I) a front-end that can read and compile C/C++ code, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, or SMT solver, where all the constraints and properties of the system to be verified are encoded into SMT and checked for satisfiability.
+ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+%
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C/C++ code, where the formal specification of the system to be verified is first handled; (ii) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the model simplification, thereby aiming to reduce the verification effort; and finally (iii) the SMT solving stage, where all the constraints and properties of the system to be verified are encoded into SMT and checked for satisfiability.
 %

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
-In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place to make sure that the components were selected in accordance with recognized design standards \cite{Pinho}.
+In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
+In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to the recognized design standards~\cite{Pinho}.
 \begin{figure}[h]
@@
 \centering
-\caption{Flowchart of the proposed automated verification of PV systems.}
+\caption{Flowchart of the proposed automated verification of PV systems.
+\textcolor{red}{replace ``show fail detail'' by ``show counterexample''.
+replace ``non deterministic test of variables'' by ``non-deterministic variables''.
+replace ``Project OK'' by ``Project meets the specification up to the given bound''.}}
 \label{fig:flowchartgeneral}
@@
 In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
-As a consequence, all the formulas of the employed mathematical models will also be updated.
-In addition, depending on one of the desired properties of the system, as autonomy of the batteries, the offer of the energy, or even the power supply from the system to check, whether it is not accomplished (said satisfied), ESBMC accuses a failure, and the diagnostic counterexample shows in which condition the property violation (system fail) happened.
+%As a consequence, all the formulae of the employed mathematical models will also be updated. 
+In addition, depending on one of the desired properties of the system such as battery autonomy, energy availability, or even system power supply, our verification engine is able to indicate a failure if those properties are not met; in this particular case, it provides a diagnostic counterexample that shows in which conditions the property violation occurred.
 %; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
@@
 is it SAT?}
-In a nutshell, ESBMC will process the C code with constraints %($C$) 
+In a nutshell, ESBMC will process the ANSI-C code with constraints %($C$) 
 and properties %($P$) 
-from the PV system that were provided by the user, and the tool will verify automatically if the PV system requirements are met.
-If the return is a failure (i.e., SAT), then the tool details the condition of violation, i.e., the state of each variable related to the system.
-That information can be used as a feedback to improve the PV system project.
-However, if the verification succeeds (i.e., UNSAT), there is no failure, therefore the PV system will present its intended behavior up the bound $k$, i.e., it does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
+from the PV system that are provided by the user, and the tool will automatically verify if the PV system requirements are met.
+If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
+However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
 %
@@
 Line 1 indicates a function call that performs the size checking of the entire PV system: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
-The verification is performed by the standard \textit{assert} macro from the ANSI-C programming language to each equation.
-The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints an error message indicating a property violation.
+The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation above.
+The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints a counterexample indicating a property violation.
 If there is no property violation, then the verification algorithm continues and the batteries are assumed to have SOC of 80\% (Line 5).
@@
 %According with X and Y, t
-Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using the feature of non-deterministic variables from ESBMC to explore all possible states and the \textit{assume} macro to limit the non-deterministic values considering a given range.
+Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using non-deterministic variables from ESBMC to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range.
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
@@
 % caused by the state explosion inherent of the technique, 
-every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent of the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation).
-Therefore, the proposed methodology depends on specific data about the solar irradiation levels to define the average amount of hours of PV generation.
+every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation).
+Therefore, our approach depends on specific data about the solar irradiation levels to define the average amount of hours of PV generation.
 
 After that, the model from PV generator is used in the function call of Line 11, to produce the voltage and current considering the states of $G$ and $T$.
-Following, related to every hour considered, the conditional \textit{if-else-endif} statements from Lines 12, 17, 23 and 28, will perform the charge or discharge of batteries according to the value of different variables: if there is PV generation (which depends on $G$ and $T$), the updated state of charge from batteries, the house's load and the set-up information of the PV system.
-
-Next, representing the time of the day where is not possible PV generation anymore, starting at Line 31, the algorithm will only discharge the batteries (using the 1 hour step) until a new charging process (at the next day) to start.
-Specific macro commands, the \textit{assert} at Lines 27 and 35, it will check the state of charge from batteries, and it will violate the property if its level reach the minimum that represents a discharged battery.
-And, therefore, the PV system is not able to supply energy to the house.
-In the other hand, if the automated tool do not fail, then the code is finalized with success and the PV system do not need improvements or corrections.
+With respect to every hour considered, the conditional \textit{if-else-endif} statements from Lines 12, 17, 23 and 28, will perform the charge or discharge of batteries according to the value of different variables: if there is PV generation (which depends on $G$ and $T$), the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+
+Next, representing the time of the day where PV generation is not possible anymore, starting in Line 31, the algorithm will only discharge the batteries (using the 1 hour step) until a new charging process (at the next day) starts.
+Specific \textit{asserts} in Lines 27 and 35 will check the state of charging from batteries, and they will violate the property if their levels reach the minimum that represents a discharged battery; therefore, the PV system is unable to supply energy to the house.
+Nevertheless, if the verification engine does not fail, then we can conclude that the PV system does not need further corrections up to the given bounds.
 %

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 5 and 6
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.96}
+\renewcommand{\baselinestretch}{0.97}
 
@@
  \begin{algorithm}
- \caption{Algorithm to perform automated verification}
+ \caption{Model checking algorithm for stand-alone PV}
  \begin{algorithmic}[1]
@@
   \IF {(FAIL verification)} 
-  \STATE exit ("Project sizing error")  
+  \STATE exit (``Project sizing erro'')  
   \ENDIF
@@
 %------------------------------------------
-Our experimental evaluation aims to answer three research questions:
+Our experimental evaluation aims to answer two research questions:
 %
@@
 In order to evaluate the proposed verification method and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool.
-Every dweller, who own a PV system, was interviewed in order to get information about his/her PV system during four months of use.
-This information was used to know possible flaws from every system at the field.
+Every dweller, who owns a PV system, was interviewed to get information about his/her PV system during four months of use.
+This information was used to know possible flaws from every system in the field.
 
 All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{At the terminal, the command used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
 The experiments were performed without a predefined timeout.
@@
 This verification took approximately 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on); this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level.
+Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level.
 Our verification engine identified those flaws (for all four houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries.
 Our verification engine took approximately 409.3 hours to find this flaw in house 1; 611.2 hours for house 2; 615.8 hours for house 3, and 620.8 hours for house 4.
-These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a mouth is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}; after the sun rises, the systems returns to normal condition operation.
+These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a month is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}, further affirming RQ1; after the sun rises, the systems returns to normal condition operation.
 
@@
 Despite the divergence of results for the houses 1, 2, 3 and 4 w.r.t.
-our proposed approach, it is evident that the information collected from the dwellers indicate that our approach has the correct evaluation of the PV system.
-House 5 presented flaws from both tools; however, only our approach indicated which system project error was responsible for the flaw (number of PV panels).
+our proposed approach, it is evident that the information collected from the dwellers indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
+House 5 presented flaws from both tools; however, only our approach indicated which design error was responsible for the flaw (number of PV panels), further answering RQ2.
 %
@@
 %---------------------------------------------------
-We have reported a favorable assessment of the proposed verification method over a diverse set of real-world benchmarks.
+We have reported a favorable assessment of the proposed method over a diverse set of real-world benchmarks.
 Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
@@
 %-------------------------------------
+
 We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
@@
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
-As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems.
-We also will consider other types of renewable energy and even hybrid ones, which will allow our method to design and verify typical rural electrification.
+As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems.
+We will also consider other types of renewable energy and even hybrid ones to allow our method to design and verify typical rural electrification.
 %

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 5 and 6
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-In general, there are two main operating modes for the controller \textcolor{blue} {\cite{Rawat}}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
+In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
 

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

@@
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{flowchart_verification4.png}
+\includegraphics[width=0.4\textwidth]{flowchart_verification5.png}
 \centering
-\caption{Flowchart of the proposed automated verification of PV systems.
-\textcolor{red}{replace ``show fail detail'' by ``show counterexample''.
-replace ``non deterministic test of variables'' by ``non-deterministic variables''.
-replace ``Project OK'' by ``Project meets the specification up to the given bound''.}}
+\caption{Flowchart of the proposed automated verification of PV systems.}
 \label{fig:flowchartgeneral}

### 2018-11-23 Tex/LaTeX2e Style File/Cover-Letter.tex
updated cover letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\documentclass[11pt]{article}

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{url}

%\usepackage{mathtools}
%\mathtoolsset{showonlyrefs}

\usepackage{color}
\usepackage{natbib}
% \usepackage[style=authoryear-comp,dashed=false]{biblatex}
% \bibliography{piecewise_lyapunov}

\textwidth 15cm
\setlength{\textheight}{1.1\textheight}
\newcommand\hi{\hspace*{\parindent}}
\newcommand\vi{\vspace{\baselineskip}}
\newcommand\lac{{\mbox{{\Huge\bf L}\hspace{-0.65em}
\raisebox{-1.2ex}{\Huge\bf A}\hspace{-1.1em}
\raisebox{-0.6ex}{\Huge\bf C~}}}}

\newcommand{\Real}{\mathbb{R}}

\pagestyle{empty}

\begin{document}

\hoffset -1.5cm \voffset .5cm

\sf

\vspace*{-2.5cm} \hspace*{-0.1cm} {\small
{\mbox{\begin{minipage}{1.5cm}
\centerline{\includegraphics[width=2cm]{manchester.jpg}}
\end{minipage}}} \hspace*{0.1cm}
\begin{minipage}{11.0cm}{\sf \large \textbf{UNIVERSITY OF MANCHESTER}}\\
{\sc School of Computer Science}
\end{minipage}
} \vspace*{0mm}

\hspace*{-.7cm} {\rule[-1ex]{15cm}{0.03cm}}

\begin{flushright}
\begin{minipage}{7.0cm}\small
{\bf Please Reply to:}\\
Dr. Cordeiro\\
University of Manchester\\
School of Computer Science\\
Kilburn Building, Manchester M13 9PL\\
{\em e-mail: lucas.cordeiro@manchester.ac.uk}
\end{minipage}
\end{flushright}

\vi
\hspace*{\fill}{\small Manchester, \today.}
\vi

\begin{flushleft}
      Badrul H. Chowdhury,  Ph.D. \\
	Editor-in-Chief \\
	University of North Carolina at Charlotte \\
	IEEE Transactions on Sustainable Energy 
    \end{flushleft}

\indent Dear Badrul
\vi

Please find enclosed our manuscript entitled as ``Automated Verification of Stand-alone Solar Photovoltaic Systems'' by Alessandro Trindade and Lucas Cordeiro which we would like to submit for publication in the journal of IEEE Transactions on Sustainable Energy.

The present work describes and evaluates a formal verification methodology for stand-alone solar photovoltaic systems, which employs the Efficient SMT-based Bounded Model Checker (ESBMC) tool to check the most common type of renewable energy used in rural areas or where grid extension unfeasible.

The evaluation of PV systems is usually performed by simulation tools, which are well known in the market. However, the exploration of all design space state is impossible with those tools, and some flaws can be originated from the design phase, reaching the field, after the PV deployment. This can cause dissatisfaction to the PV system owners, and to the wrong conclusion that intermittent renewable systems are not good.

In our study, experimental results, from five case studies, in a comparative evaluation of tools, showed that only the automated verification can find some failures in the PV systems, and with the plus of indicating the reason of failure. That can and must be used to improve the sizing of solar PV systems.

Finally, based on the fact that only since 2017 papers are dealing with formal verification applied to PV systems, with excellent results, but only related to PV panels or to grid-tied systems, our study is unique and based on data from four months of use from the case studies: putting together mathematical models, automated verification, simulation, empirical observation and interview from dwellers in remote communities.

The  authors  claim  that  none  of  the  material  in  the mentioned  paper  has  been  published  or  is  under  consideration for publication elsewhere.

\vi

Thank you for your time.
\vi

\indent
~~~~~~~~~~~~~~~~~~~~~~~~~~~Sincerely,\\

\begin{quote}
\begin{quote}
\begin{flushright}

%\vfill

Lucas C. Cordeiro~~~~~~~
\end{flushright}
\end{quote}
\end{quote}

\end{document}

### 2018-12-04 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r3.tex
paper update

--- 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
@@
 
-\renewcommand{\baselinestretch}{0.97}
+\renewcommand{\baselinestretch}{0.975}
 
@@
 %\title{Building a framework to perform automated verification of solar photovoltaic off-grid systems}
-\title{Automated Verification of Stand-Alone Solar Photovoltaic Systems}
+\title{Automated Verification of Stand-alone Solar Photovoltaic Systems}
 %
@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{A}{ccording} to Coelho et al.~\cite{Coelho}, there are presently 1.3 billion people with no access to electricity worldwide. 
+\IEEEPARstart{T}{here} are presently 1.3 billion people with no access to electricity worldwide~\cite{Coelho}. 
 %The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
@@
 %Based on data from \textcolor{red}{from what? please be more formal! can you check the guidelines of the journal to see how you can cite references?}, t
-There was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV all over the world \cite{EPIA}. That scenario brings the need for 
-%The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
-%The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
-%(low greenhouse gases emissions)
-%operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}. 
-%Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
-% 
-%The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy. 
-%
-%Apart from PV modules; the 
-%PV systems consist of PV modules, battery bank, controller, and inverter, plus the load. %Moreover, the optimum sizing of these devices is important for reliable operation.
-%Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}.
-%Furthermore, there is the need for proper modeling and simulation tools for people involved in their application.
-%
-%The increase in the number of PV systems installed and been projected all over the world brings the need for %proper modeling and simulation tools for researchers and practitioners involved in their application.
-design validation -- ensuring the correctness of the design at earliest stages -- which is a major challenge in any responsible system development process, and the activities intended for its solution occupy an ever increasing portions of the  development cycle cost and time budgets \cite{ClarkeHV18}.
-%The currently practiced methods for design validation in most sites are still the veteran techniques of simulation and testing \cite{ClarkeHV18}.
+There was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV all over the world \cite{EPIA}.
 
@@
 Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
-User or project requirements can be added during the creation of the formal model to be verified.
+%User or project requirements can be added during the creation of the formal model to be verified.
 %, as defined by \cite{Trindade}.
@@
 %Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
-Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
+%Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
 %
@@
 %
-In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load are created.
+In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is created.
 The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
+The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
 A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
@@
 %Here it will be verified a stand-alone PV system, with all their components modeled mathematically,   
-Related to solar PV systems, the project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
-The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
+
 The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
@@
 In prior studies, the evaluation of PV systems w.r.t.
-user requirements were performed by software simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Samrat2014, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
-Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and to maximize the power point of solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification and they restrict themselves to solar panels or smart grids.
-%
-In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus has been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
+user requirements were performed by software simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
+Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification.
+%
+In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of PV farms, where the focus has been the interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
 Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.
@@
 %The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
-Given the current knowledge in formal verification, this is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system.
+This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system.
 In summary, this paper makes three original contributions.
@@
 Secondly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT).
-Thirdly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other state-of-the-art approaches based on simulation.
+Thirdly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.
 
@@
 
-PV systems are classified into three distinct types~\cite{Mohanty}: (1) stand-alone systems, where the energy is generated and consumed in the same place and which do not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system.
+PV systems are classified into distinct types~\cite{Mohanty}.
+%: (1) stand-alone systems, where the energy is generated and consumed in the same place and which do not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system.
 %, where another source(s) of energy can work together with the solar PV.
@@
 %\end{itemize}
-Specifically for the energy needed for remote rural areas of developing countries or places where the grid extension is not possible or even feasible, 
+Specifically for the energy needed for remote rural areas of developing countries or places where the grid extension is not feasible, 
 %stand-alone systems are one the most used solutions, and 
@@
 %
-In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
+%In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
 %public domain and commercial software available for the PV market. 
 %According to \cite{Brooks}, t
-The capabilities of those tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
+The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
  to complex financial analysis and project optimization. 
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here we evaluated the most popular ones: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
+Here we evaluated the most popular ones and summarize at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
 
@@
 
-Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system or battery backup analysis.
-%all the tools perform solar photovoltaic analysis;
+%Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where 
+As highlights, only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-RETScreen and HOMER have a free web-based version, but they have limited resources since they do not allow us to save the PV projects or even upload data from manufacturers.
+RETScreen and HOMER have a free web-based version, but with limited features.
 However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription typically range from US\$504.00 to US\$657.00.
@@
 %
-In this study, only HOMER remains for a comparative evaluation with our proposed verification approach. %All tools need some parameters inherently from manufacturer's catalog.
+In this study, only HOMER has the minimum features for a comparative with our proposed verification approach.
+That evaluation is presented in Section~\ref{sec:results_indeed}.%All tools need some parameters inherently from manufacturer's catalog.
 %, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
 %After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-Thus, the main challenge here is to demonstrate the application of software model checking to formally verify a stand-alone PV solution, thus proving that this approach is more effective and complete than other state-of-the-art tool such as HOMER Pro.
+%Thus, the main challenge here is to demonstrate the application of software model checking to formally verify a stand-alone PV solution, thus proving that this approach is more effective and complete than other state-of-the-art tool such as HOMER Pro.
 The comparative evaluation between HOMER Pro and our approach is presented in Section~\ref{sec:results_indeed}.
-
+%
 %-------------------------------------------------------------------
@@
 %-------------------------------------------------------------------
-
 %The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
-The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
+%The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
 It identifies the PV generator, batteries, charge controller, inverter, and AC load.
-
-The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
-In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
+A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
+The PV generator (panel or array) is a semiconductor device that can convert solar energy into DC electricity.
+%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
 For night hours or rainy days, we need to hold batteries, where power can be stored and used.
@@
 \end{figure}
-
+%
 %In the literature, there are several mathematical models available for each component of PV systems. At the next section, the mathematical model for each component is presented. 
-
 %-------------------------------------------------------------------
@@
 %-------------------------------------------------------------------
-
 %A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
@@
 %%%%%package called panel or module. 
-
 %For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
@@
 %Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
-
 The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-is usually studied using an equivalent circuit model~\cite{Yatimi,Saloux,Mellit}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
+is usually studied using an equivalent circuit model~\cite{Yatimi, Mellit}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
 %Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
@@
 
-The 1-diode model, illustrated in Fig. \ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described by Eq.~\eqref{eq:1diodemodel}:
+The 1-diode model, illustrated in Fig.
+\ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described by ~\eqref{eq:1diodemodel}.
+This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
+In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
 \begin{equation}
@@
 %Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
-The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
+%The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
 In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
@@
 %A single-diode without series and shunt resistances is considered. 
-Eq.~\eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
+%%%%%%%Eq.~\eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
 % shown in Fig. \ref{fig:ivcurve}.
@@
 However, the photocurrent delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, Eq.~\eqref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature~\cite{Villalva}:
+Therefore, ~\eqref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature~\cite{Villalva}:
 \begin{equation}
@@
 %
-The cell temperature ($ T $) is described by Eq.~\ref{eq:Tcell}~\cite{Ross}:
+The cell temperature ($ T $) is described by ~\ref{eq:Tcell}~\cite{Ross}:
 \begin{equation}
@@
 
-Furthermore, Eq.~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\cite{Villalva} 
+Furthermore, ~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\cite{Villalva} 
 %In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
@@
 %The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current (cf.
-Eq.~\eqref{eq:Pm}) and the saturation current in the reference temperature given by Eq.~\eqref{eq:I0}, the diode ideality factor is determined by Eq.~\eqref{eq:a}:
+Using the maximum power point current (cf. ~\eqref{eq:Pm}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor is determined by ~\eqref{eq:a}:
 \begin{equation}
@@
 
-\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers; the PV generator model is now completely determined.
+\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions.
+%, usually provided by manufacturers; the PV generator model is now completely determined.
 %; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
@@
 
-In addition to the model verification performed by the proposed technique, there is the prior stage of PV system sizing check, based on manufacturer's data and information from the sizing and the site; this stage ensures that the system meets its specification, thereby considering the standard project steps~\cite{Pinho}.
-%
-Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}~\cite{Pinho}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered as
+In addition to the model verification performed by the proposed technique, we introduced a prior stage, the PV system sizing check; this stage ensures that the system meets the standard project steps related to the critical design month~\cite{Pinho}.
+%
+Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}~\cite{Pinho}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
 \begin{equation}
@@
 
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed by Eq.~\eqref{eq:NTPmin} and the check is performed using Eq.~\eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from Eq.~\eqref{eq:NTPmin}.
+The total minimum number of needed solar panels ($N_{TPmin}$) is computed by ~\eqref{eq:NTPmin} and the check is performed using ~\eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from ~\eqref{eq:NTPmin}.
 \begin{equation}
@@
 
-For the charging process, however, the parameters are described by Eq.~\eqref{eq:Vcbat} as
+For the charging process, however, the parameters are described by ~\eqref{eq:Vcbat} as
 %
@@
 In addition to the model verification, there is also the prior stage of project sizing check, as performed for the solar panel.
-Firstly we define the total capacity of the battery bank, as described by Eq.
-\eqref{eq:Cbank} as
+Firstly we define the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
 \begin{equation}
@@
 %
-Secondly, the total (minimum) number of batteries is computed, as described by Eq.~\eqref{eq:Nbtotal}.
-Additionally, Eq.~\eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
+Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}.
+Additionally, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
 \begin{equation}
@@
 %As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of DC-DC converter is given by Eq.~\eqref{eq:poutcont} as
+The output power ($ P_{out} $) of DC-DC converter is given by \eqref{eq:poutcont} as
 \begin{equation}
@@
 
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Eq.~\eqref{eq:poutcont} we compute Eq.~\eqref{eq:potcont} as
+Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from \eqref{eq:poutcont} we compute \eqref{eq:potcont} as
 \begin{equation}
@@
 One more time, some steps must be done to check the sizing project of the controller, prior the verification phase.
-Initially, the controller must meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem}:
+Initially, the controller must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem}:
 \begin{equation}
@@
 
-Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by Eq.~\eqref{eq:iscamb}:
+Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
 %
@@
 The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage, % (127 V or 220 V, for example), 
-and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by Eq.~\eqref{eq:efficinv} \cite{Hansen}:
+and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by \eqref{eq:efficinv} \cite{Hansen}:
 %
@@
 The sizing project check of the inverter is carried out by means of three equations.
-Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
-Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
+Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
+Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
+Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
 %

### 2018-12-04 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r3.tex
paper update

@@
 
-In order to model, simulate, or evaluate a PV system, there are a myriad of specialized tools available in the market such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 %
@@
 However, those tools are based on running experiments in simulation models.
-Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is rarely possible or even unfeasible~\cite{ClarkeHV18} to be achieved in practice.
+Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
@@
 The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
-The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.
+The model checking tool reports in which conditions a system does not meet the user requirements.
 A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
-
 %Those programs are viewed as mathematical objects, and the use of 
@@
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-
-The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
+The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
+%, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
 
 In prior studies, the evaluation of PV systems w.r.t.
-user requirements were performed by software simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
-Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification.
-%
-In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of PV farms, where the focus has been the interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
+user requirements were performed by simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
+Related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification.
+%
+In addition, recent research has attempted to formalize and implement a formal study of PV farms, where the focus has been the interaction with the grid~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
 Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.
@@
 This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system.
-In summary, this paper makes three original contributions.
-Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
-Secondly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT).
-Thirdly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.
+In summary, this paper makes two original contributions.
+% Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
+Secondly
+Firstly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT).
+Secondly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.
 
@@
 %\end{itemize}
-Specifically for the energy needed for remote rural areas of developing countries or places where the grid extension is not feasible, 
+Specifically for remote rural areas of developing countries or places where the grid extension is not feasible, 
 %stand-alone systems are one the most used solutions, and 
@@
 %According to \cite{Brooks}, t
-The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
+%%%%%%%%%%The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
  to complex financial analysis and project optimization. 
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here we evaluated the most popular ones and summarize at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
+Here we evaluated the most popular tools available in the literature and summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
 
@@
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-RETScreen and HOMER have a free web-based version, but with limited features.
 However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription typically range from US\$504.00 to US\$657.00.
@@
 For night hours or rainy days, we need to hold batteries, where power can be stored and used.
-The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen,Mellit}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
-That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}.
+The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
+The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
 %
@@
 The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-is usually studied using an equivalent circuit model~\cite{Yatimi, Mellit}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
+is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
 %Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
@@
 This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
+%In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
 \begin{equation}
@@
 
-\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells ($N=1$ in a single cell configuration); $a$ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $T$ the temperature of the p-n junction (or cell temperature) in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
+\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
+$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
 
@@
 %
-The voltage and the current at the maximum power point tracking (MPPT), can be described by Equations \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm}  as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
+The voltage and the current at the maximum power point tracking (MPPT), can be described by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm}  as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
 \begin{equation}
@@
 \noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions
-(provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
-%
+(provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Villalva} that is provided by PV manufacturers ($ I_{sc,ref} $).
+%\cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
+%%
 The cell temperature ($ T $) is described by ~\ref{eq:Tcell}~\cite{Ross}:
@@
 %
-Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}~\cite{Pinho}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
+Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
 \begin{equation}
@@
 
-Various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Manwell93,Pinho};
-%, and \cite{Manwell94}. 
+Various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Pinho};
+%, and \cite{Manwell93, Manwell94}. 
 %However, regardless of the model, normally the following parameters are required: 
@@
 %
-The discharge voltage equation is described by \eqref{eq:bat_Vd} as
+The discharge voltage equation is described by \eqref{eq:bat_Vd}.
 %The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
@@
 %---------------------------------------------------------
-
 %Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
 However, in this study, in order to simplify, the term used is controller.
-
 %The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
@@
 %
-In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
-
+%%%%%%%%%%In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
+%
 %The controller allows the management of energy between the load and the battery \cite{Mellit}. 
@@
 %As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of DC-DC converter is given by \eqref{eq:poutcont} as
+The output power ($ P_{out} $) of controller is given by \eqref{eq:poutcont}.
 \begin{equation}
@@
 
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from \eqref{eq:poutcont} we compute \eqref{eq:potcont} as
+Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from \eqref{eq:poutcont} we compute \eqref{eq:potcont}.
 \begin{equation}
@@
 
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}; one successful method in this domain is model checking \cite{Clarke2012}.
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking \cite{Clarke2012}.
+%%%%%%%%Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}; one successful method in this domain is model checking \cite{Clarke2012}.
+
 % 
@@
 If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
-However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
+However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
+%, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
 %
@@
 
-Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to perform the automated verification.
-Line 1 indicates a function call that performs the size checking of the entire PV system: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
-The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation above.
+Algorithm~\ref{alg:verification-algorithm} describes the pseudo-code used to perform the automated verification.
+Line 1 indicates a function call that performs the size checking of the each component of the PV system.
+%: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
+The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation of sizing check.
 The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints a counterexample indicating a property violation.
@@
 All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
-The experiments were performed without a predefined timeout.
+Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3}.
+% enabled with the goal of reducing memory usage; 
+We have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}. %The experiments were performed without a predefined timeout.
 
@@
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
-As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems.
+As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems.
 We will also consider other types of renewable energy and even hybrid ones to allow our method to design and verify typical rural electrification.
@@
 Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
-Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation (Centre of Analysis, Research and Innovation Technology Foundation).
+Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the Amazonas State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation.
 His interest is in renewable energy, automated verification, and model checking.
@@
 degree in Computer Science in 2011 from the University of Southampton, UK.
-Currently, he is a Senior Lecturer in the School of Computer Science at the University of Manchester, UK and leads the Systems and Software Verification laboratory.
+Currently, he is a Senior Lecturer in the School of Computer Science at the University of Manchester, and leads the Systems and Software Verification laboratory.
 He is also a collaborator in the Postgraduate Program in Electrical Engineering and Informatics at the Federal University of Amazonas (UFAM), Brazil.
-Prior to joining the University of Manchester, he worked as a researcher / researcher engineer at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for 4 years as a software engineer at Siemens Mobile and CT-PIM.
+Prior to joining the University of Manchester, he worked as a researcher at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for 4 years as software engineer at industry.
 His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.

### 2018-12-04 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r3.tex
paper update

@@
 Note that the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
-Another characteristic of Manaus, based on historical weather data \cite{Temperature}, \cite{Irradiance}, is related to the fact that only during 8 hours of the day is possible to have PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
+Another characteristic of Manaus, based on historical weather data %\cite{Temperature},
+\cite{Irradiance}, is related to the fact that only during 8 hours of the day is possible to have PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
 
@@
 \end{enumerate}
-
-In order to evaluate the proposed verification method and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool.
-Every dweller, who owns a PV system, was interviewed to get information about his/her PV system during four months of use.
-This information was used to know possible flaws from every system in the field.
-
 All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
@@
 
-Experimental setup of HOMER Pro: all experiments were conducted on an otherwise idle Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.
+In order to evaluate the proposed verification method and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool.
+%Every dweller, who owns a PV system, was interviewed to get information about his/her PV system during four months of use.
+This information was used to know possible flaws from every system in the field.
+Experimental setup of HOMER Pro: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.
 
@@
 %
-The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel.
+%The description of our experimental results can be broken down into two parts: 
+(a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel.
 This verification took approximately 63.3 hours to be performed.
@@
 %
-Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
+%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
 Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions.
@@
 %---------------------------------------------------
-We have reported a favorable assessment of the proposed method over a diverse set of real-world benchmarks.
+We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
 Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
 
-\textit{Model precision:} each component of the PV system is mathematically modelled, and the precision of the proposed method depends on the precision of that particular model.
+\textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
 A careful evaluation in a PV laboratory to validate the model could add more reliability to the results produced by our method.
@@
 
-\textit{Case studies:} Our case studies are performed only in Manaus, in particular in the south hemisphere.
-A more complete evaluation can be performed if other places around the world could become case studies.
+\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed if other places around the world could become case studies.
 
@@
 % into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements. 
-
+%
 %Plus (need to think about it): verification in every-hour of a 48h cycle?, PV model math model can be improved, charge/discharge of batteries can be improved (is a simplified model), house's power consumption is not flat or constant, the dweller can buy more home appliances, synthesis need a data base of components, to test peak (surge) consumption (above the nominal), additional models for on-grid/off-grid farm, hybrid, and on-grid with batteries).
-
 % if have a single appendix:
@@
 % is possibly needed
-
 % use appendices with more than one appendix
@@
 %
-
 %\appendices
@@
 %Appendix one text goes here.
-
 % you can choose not to have a title for an appendix
@@
 %Appendix two text goes here.
-
 % use section* for acknowledgment
@@
 To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to test real PV systems.
-
 % Can use something like this to put references on a page
@@
 %\IEEEtriggercmd{\enlargethispage{-5in}}
-
 % references section
-
 % can use a bibliography generated by BibTeX as a .bbl file
@@
 \end{IEEEbiography}
-
 % insert where needed to balance the two columns on the last page with
@@
 %\newpage
-
 %\begin{IEEEbiographynophoto}{Jane Doe}
@@
 %\end{IEEEbiographynophoto}
-
 % You can push biographies down or up by placing
@@
 % are being equalized.
-
 %\vfill
-
 % Can be used to pull up biographies so that the bottom of the last one
@@
 %\enlargethispage{-5in}
-
 % that's all folks

### 2018-12-05 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r3.tex
paper update

@@
 
-\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time.
-Mathematically, it is the ratio between the present capacity and the nominal capacity (in $ Ah $, provided by manufacturer).
-If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.
-%, defined by Equation \ref{eq:SOCbat}.
+\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $%, $ T_{ref}=25^{o}C $
+), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time.
+Mathematically, it is the ratio between the present capacity and the nominal capacity% (in $ Ah $, provided by manufacturer)
+. If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
 %\begin{equation}
@@
 %Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
-
 For the charging process, however, the parameters are described by ~\eqref{eq:Vcbat} as
@@
 %
-\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
+\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
+the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
 %

### 2018-12-27 Tex/LaTeX2e Style File/Trindade_IEEE_TC_r0.tex
updating text

--- 2018-12-05 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r3.tex
@@
 
-\documentclass[journal]{IEEEtran}
+\documentclass[10pt,journal,compsoc]{IEEEtran}
 %
@@
 %
-\usepackage{cite}
+%\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress]{cite}
+%\else
+  % normal IEEE
+%  \usepackage{cite}
+%\fi
+%\usepackage{cite}
 % cite.sty was written by Donald Arseneau
@@
 
-\renewcommand{\baselinestretch}{0.975}
+%\renewcommand{\baselinestretch}{0.975}
 
@@
 \author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
-\thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
-\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
+\IEEEcompsocitemizethanks{
+\IEEEcompsocthanksitem{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
+\IEEEcompsocthanksitem{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}}% <-this % stops a space
 \thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support.}
@@
 % The paper headers
-\markboth{IEEE TRANSACTIONS ON SUSTAINABLE ENERGY,~VOL.~X, NO.~Y, MONTH~2018}
-{Trindade \MakeLowercase{\textit{et al.}}: AUTOMATED VERIFICATION OF STAND-ALONE SOLAR PHOTOVOLTAIC SYSTEMS}
+\markboth{IEEE Transactions on Computers,~Vol.~14, No.~8, August~2015}%
+{Trindade \MakeLowercase{\textit{et al.}}: Automated Verification of Stand-Alone Solar Photovoltaic Systems}
 % The only time the second header will appear is for the odd numbered pages
@@
 
-% make the title area
-\maketitle
-
 % As a general rule, do not put math, special symbols or citations
 % in the abstract or keywords.
+\IEEEtitleabstractindextext{%
 \begin{abstract}
@@
 Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected by our automated verification method.
-%Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure.
-\textcolor{red}{Data from practical application of solar systems prove the results obtained by the proposed approach...
-this last sentence should be stronger to emphasise your main contribution...
-maybe you could update this after obtaining the experimental results...}
 \end{abstract}
@@
 Formal verification, model checking, photovoltaic power systems, power system modeling, solar power generation.
-\end{IEEEkeywords}
+\end{IEEEkeywords}}
+
+% make the title area
+\maketitle
 
@@
 
-\section{Introduction}
+\IEEEraisesectionheading{\section{Introduction}}
 % The very first letter is a 2 line initial drop letter followed
@@
 %Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
-Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider. 
-% changing the way the world is powered. 
-%Based on data from \textcolor{red}{from what? please be more formal! can you check the guidelines of the journal to see how you can cite references?}, t
-There was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV all over the world \cite{EPIA}.
+Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
 
@@
 user requirements were performed by simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
-Related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification.
-%
-In addition, recent research has attempted to formalize and implement a formal study of PV farms, where the focus has been the interaction with the grid~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
+Related to formal methods, studies were carried out toward the modeling of power smart grids~\cite{Akram2018} and solar panels~\cite{Driouich2017}; however, those studies do not perform automated verification.
+%
+In addition, recent research performed a formal study of PV farms, where the focus has been the interaction with the grid~\cite{Abate2017}; or to model a PV system and to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
 Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.
@@
 %The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
-This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system.
-In summary, this paper makes two original contributions.
+%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
+This paper makes two original contributions.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
 Secondly
-Firstly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT).
+Firstly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT), and that was never did before.
 Secondly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.
@@
 %%%%%%%%%%The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
- to complex financial analysis and project optimization. 
+% to complex financial analysis and project optimization. 
 %Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
@@
 %Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
-The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
+A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves).
+However, the present work will rely on the simplified model of 1-diode.
+It was demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
+
+%The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
+%is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
 %Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
@@
 \ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described by ~\eqref{eq:1diodemodel}.
-This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
+%This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
 %In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
@@
 \noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
-$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
+$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
 
@@
 And \cite{Tian} did a mix of analytical and experimental methodology to get the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use experimental technique.
-
 %Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
@@
 %%
-The cell temperature ($ T $) is described by ~\ref{eq:Tcell}~\cite{Ross}:
+The cell temperature ($ T $) in degree Celsius is described by ~\ref{eq:Tcell}~\cite{Ross}:
 \begin{equation}
@@
 %The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current (cf. ~\eqref{eq:Pm}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor is determined by ~\eqref{eq:a}:
+Using the maximum power point current (cf.
+~\eqref{eq:Imfinal}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor is determined by ~\eqref{eq:a}:
 \begin{equation}
@@
 %Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
-
-In addition to the model verification performed by the proposed technique, we introduced a prior stage, the PV system sizing check; this stage ensures that the system meets the standard project steps related to the critical design month~\cite{Pinho}.
-%
-Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
-\begin{equation}
-\label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
-\end{equation}
-
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed by ~\eqref{eq:NTPmin} and the check is performed using ~\eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from ~\eqref{eq:NTPmin}.
-\begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NTP}
-N_{TP} \geq N_{TPmin}.
-\end{equation}
-
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.
-With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}), $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
-\begin{equation}
-\label{eq:NPSmin}
-N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NPS}
-N_{PS} \geq N_{PSmin}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NPP}
-N_{PP} \geq N_{PPmin}.
-\end{equation}
-
 %------------------------------------------------------------
@@
 %
-In addition to the model verification, there is also the prior stage of project sizing check, as performed for the solar panel.
-Firstly we define the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
-\begin{equation}
-\label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}.
-\end{equation}
-%
-\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
-the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
-%
-Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}.
-Additionally, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
-\begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:batcheck}
-\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total.
-\end{equation}
-
 %---------------------------------------------------------
@@
 \label{eq:poutcont}
-P_{in} = P_{out}.
+P_{in} \eta_{c} = P_{out}.
 \end{equation}
@@
 %As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
-
-One more time, some steps must be done to check the sizing project of the controller, prior the verification phase.
-Initially, the controller must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem}:
-\begin{equation}
-\label{eq:vcvsystem}
-V_{c} = V_{system}.
-\end{equation}
-
-Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
-%
-\begin{equation}
-\label{eq:iscamb}
-I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right]. 
-\end{equation}
-
-The controller must meet the maximum current from the PV array given by \eqref{eq:icmin} and \eqref{eq:icicmin}.
-\begin{equation}
-\label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP}.
-\end{equation}
-
-\begin{equation}
-\label{eq:icicmin}
-I_{c} \geq I_{c,min}.
-\end{equation}
 
@@
 %
-The sizing project check of the inverter is carried out by means of three equations.
-Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
-Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
-%
-\begin{equation}
-\label{eq:vindc} 
-V_{in}DC = V_{system}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:voutac} 
-V_{out}AC = V_{AC}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
-\end{equation}
-
 %--------------------------------------------------
@@
 The process of model checking can be split into three main components: modeling, specification, and verification method.
-In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in a temporal logic form (e.g., CTL or LTL).
+In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in a temporal logic form as Computational Tree Logic (CTL) or Linear Temporal Logic (LTL).
 %
@@
 %
-Fig.~\ref{fig:systemverif} shows the process to convert a real PV system to a model to be verified by a model checking procedure.
+Fig.~\ref{fig:systemverif} shows a real PV system, and Fig.~\ref{fig:systemverif2} the conversion the system to be verified by a model checking procedure.
 % \textcolor{red}{Please try to adapt this figure to our context.
 How can it be applied to verify PV?}.
+%Fig.~\ref{fig:systemverif} shows the process to convert a real PV system to a model to be verified by a model checking procedure.
+% \textcolor{red}{Please try to adapt this figure to our context.
+How can it be applied to verify PV?}.
 
 \begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{systemverif2}
+\includegraphics[width=0.5\textwidth]{system_original_blocks}
 \centering
-\caption{From real system verification to model checking (adapted from \cite{ClarkeHV18}).}
+\caption{Real system verification (adapted from \cite{ClarkeHV18}).}
 \label{fig:systemverif}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=0.4\textwidth]{system_model_blocks}
+\centering
+\caption{Model checking verification \cite{ClarkeHV18}.}
+\label{fig:systemverif2}
 \end{figure}
@@
 In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to the recognized design standards~\cite{Pinho}.
+In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to critical month method~\cite{Pinho}.
 \begin{figure}[h]
@@
 Algorithm~\ref{alg:verification-algorithm} describes the pseudo-code used to perform the automated verification.
-Line 1 indicates a function call that performs the size checking of the each component of the PV system.
+%Line 1 indicates a function call that performs the size checking of the each component of the PV system.
 %: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
-The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation of sizing check.
+%The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation of sizing check.
 The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints a counterexample indicating a property violation.
-If there is no property violation, then the verification algorithm continues and the batteries are assumed to have SOC of 80\% (Line 5).
+If there is no property violation, then the verification algorithm continues and
+The batteries are assumed to have SOC of 100\% (Line 1), i.e., the batteries are charged. That is important because the system is said ready to use when the batteries are charged.
 
@@
 
-After that, the model from PV generator is used in the function call of Line 11, to produce the voltage and current considering the states of $G$ and $T$.
-With respect to every hour considered, the conditional \textit{if-else-endif} statements from Lines 12, 17, 23 and 28, will perform the charge or discharge of batteries according to the value of different variables: if there is PV generation (which depends on $G$ and $T$), the updated state of charge from batteries, the house's load and the set-up information of the PV system.
-
-Next, representing the time of the day where PV generation is not possible anymore, starting in Line 31, the algorithm will only discharge the batteries (using the 1 hour step) until a new charging process (at the next day) starts.
-Specific \textit{asserts} in Lines 27 and 35 will check the state of charging from batteries, and they will violate the property if their levels reach the minimum that represents a discharged battery; therefore, the PV system is unable to supply energy to the house.
+After that, the model from PV generator is used in the function call of Line 7, to produce the voltage and current considering the states of $G$ and $T$.
+With respect to every hour considered, the conditional \textit{if-else-endif} statements from Lines 8, 11, 13, 16 and 19, will perform the charge or discharge of batteries according to the value of different variables: if there is PV generation (which depends on $G$ and $T$), the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+
+Next, representing the time of the day where PV generation is not possible anymore, starting in Line 22, the algorithm will only discharge the batteries (using the 1 hour step) until a new charging process (at the next day) starts.
+Specific \textit{assert} in Line 26 will check the state of charging from batteries, and they will violate the property if their levels reach the minimum that represents a discharged battery; therefore, the PV system is unable to supply energy to the house.
 Nevertheless, if the verification engine does not fail, then we can conclude that the PV system does not need further corrections up to the given bounds.
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE Perform project sizing verification( )
-  \IF {(FAIL verification)} 
-  \STATE exit (``Project sizing erro'')  
-  \ENDIF
-  \STATE $SOC \leftarrow 80\%$ \\
+  \STATE $SOC \leftarrow 100\%$ \\
   \COMMENT {Starting with the PV generation time}
@@
   \\
-  \COMMENT {Now, testing if battery is empty:}
-  \IF {($SOC \leq SOC_{limit}$)} 
-    \STATE assert (PV panel is generating energy?) \COMMENT {FAIL if not}
-    \STATE $house \leftarrow energy \, from \, PV \, panels$
-    \STATE $battery \leftarrow energy \, from \, PV \, panels$ 
-    \STATE $SOC \leftarrow SOC + 1\,h\, charge$
-  \ELSIF {($PV \, Array  \geq Vbulk$)}
-  	\STATE depending on $SOC$, Battery enter in absorp. or float.
-	\STATE adequate the voltage at DC-bus (PV panel feed bus)
-    \STATE $house \leftarrow energy \, from \, PV \, panels$
-    \STATE $battery \leftarrow energy \, from \, PV \, panels$ 
-    \STATE $SOC \leftarrow SOC + 1\,h\, charge$
-  \ELSE
-  	\STATE Adequate the voltage of DC-bus (battery feed bus)
-	\STATE $house \leftarrow energy \, from \, batteries$
-    \STATE $SOC \leftarrow SOC - 1\,h\, discharge$
-    \STATE assert ($SOC \geq SOC_{limit}$)
-    \\
-    \COMMENT {this ELSE: batteries $\geq SOC_{limit}$ but panels are off}	  
+  \COMMENT {If-then-else sequence to imitate charge controller work}
+  \IF {($battery \, is \, empty$) AND ($PV \, is \, generating$)}
+    \STATE charge battery in 1h
+    \STATE PV feed the house
+  \ELSIF {($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
+    \STATE FAIL with assert macro
+  \ELSIF {NOT($battery \, is \, empty$) AND ($PV \, is \, generating$)}
+    \STATE stop battery charge
+    \STATE PV feed the house
+  \ELSIF {NOT($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
+    \STATE discharge battery in 1h
+    \STATE Battery feed the house
   \ENDIF
@@
   \STATE $SOC \leftarrow SOC - ( 24 - Hours \, of \, PV \, generation)\,h\, discharge$
-  \STATE $AutonomyCount \leftarrow ( 24 - Hours \, of \, PV \, generation)$
+  \STATE $AutonomyCount \leftarrow AutonomyCount+1)$
   \\  
@@
   \\
-  \STATE assert ($SOC \geq SOC_{limit}$)  
+  \STATE assert NOT($Battery \, empty$)  
   \\
-  \COMMENT {Perform similar \textbf{for}-LOOP as defined in line 6}
+  \COMMENT {Perform similar \textbf{for}-LOOP as defined in line 2-21}
   %%\ENDFOR
@@
 
-We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (700 W inverter, with 48h autonomy) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).
-
-Note that the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}).
+We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with surge of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
+
+Note that the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 5 and 6 of Algorithm~\ref{alg:verification-algorithm}).
 Another characteristic of Manaus, based on historical weather data %\cite{Temperature},
@@
 % use section* for acknowledgment
-\section*{Acknowledgment}
+\section*{Acknowledgments}
 To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to test real PV systems.

### 2018-12-27 code/codePVsystem_rev11.c

@@ -1,0 +1,554 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that performs the automated verification of a stand-alone solar photovoltaic system
+---------------------------------------------------------------------by Alessandro Trindade, DEZ 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.001 //0.0000000001
+#define precisionEXP 0.001 //0.00000001 
+
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+//case study at urban area of 915W of demand and 4.88 kWh of energy
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define Psurge 501
+  #define Econsumption 3900
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220.0
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24.0  //controller voltage
+  #define Vsystem 24.0  //DCbus
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define Psurge 722
+  #define Econsumption 3600
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220.0
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24.0  //controller voltage
+  #define Vsystem 24.0  //DCbus
+#elif HOUSE3
+  //Sandriane's house 263W and 2.5kWh
+  #define Phouse 263
+  #define Psurge 732
+  #define Econsumption 2500
+  #define PACref 700
[…]

### 2018-12-28 Tex/LaTeX2e Style File/Trindade_IEEE_TC_r0.tex
updating text

@@
 \noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions.
-%, usually provided by manufacturers; the PV generator model is now completely determined.
-%; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
+%, usually provided by manufacturers; t
+
+The PV generator model is now completely determined. It requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
 %
@@
 The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
-In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to critical month method~\cite{Pinho}.
+
 \begin{figure}[h]
@@
 \end{figure}
+
+In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
+In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to critical month method~\cite{Pinho}.
+The equations to check the PV sizing were not presented at this paper, however the standard from Engineering Manual was the reference~\cite{Pinho}.
 %
@@
 \end{enumerate}
-All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3}.
+
+All experiments were conducted on an otherwise idle Intel octa core Xeon CPU E5-2640 with 2.4 GHz and 264 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
+Concerning our verification engine, ESBMC v6.0.0 was used \footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 \phantom{}-boolector}.
 % enabled with the goal of reducing memory usage; 
-We have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}. %The experiments were performed without a predefined timeout.
+We have also used the SMT solver Boolector version 2.4.1~\cite{Brummayer}. %The experiments were performed without a predefined timeout.
 
@@
 %
-%The description of our experimental results can be broken down into two parts: 
-(a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel.
-This verification took approximately 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level.
-Our verification engine identified those flaws (for all four houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries.
-Our verification engine took approximately 409.3 hours to find this flaw in house 1; 611.2 hours for house 2; 615.8 hours for house 3, and 620.8 hours for house 4.
-These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a month is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}, further affirming RQ1; after the sun rises, the systems returns to normal condition operation.
+The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel.
+This verification took approximately 0.57 hours to be performed.
+In order to validate this possible flaw, it was surveyed the owner of the 1,200 W system; we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer who showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level.
+Our verification engine identified those flaws (for those three houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries.
+Our verification engine took approximately 5.1 hours to find this flaw in house 2; 5.8 hours for house 3, and 4.4 hours for house 4.
+These flaws were confirmed with the dwellers who own the systems by an interview process and from a local monitoring system with the Raspberry Pi controller: at least once a month is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}, further affirming RQ1; after the sun rises, the systems returns to normal condition operation.
+One more time the flaws were not caused by misuse of the system by the dwellers.
+Fig.
+\ref{fig:loadcurve} shows the monitoring result for the load curve of house 2 from June to July of 2018 (5 weeks), without undesired peaks from power demand of even unexpected energy consumption.
+The house 1 had an inconclusive result with the automated verification, because the solver did not presented any result from the SMT verification.
+
+\begin{figure}[h]
+\includegraphics[width=0.4\textwidth]{loadcurve.png}
+\centering
+\caption{Five weeks monitored load curve from House 1.}
+\label{fig:loadcurve}
+\end{figure}
 
@@
 All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
-%
-Despite the divergence of results for the houses 1, 2, 3 and 4 w.r.t.
-our proposed approach, it is evident that the information collected from the dwellers indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
+Fig.
+\ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software.
+
+\begin{figure}[h]
+\includegraphics[width=0.4\textwidth]{homer.png}
+\centering
+\caption{Homer simulation screen.}
+\label{fig:homerscreen}
+\end{figure}
+%
+Despite the divergence of results for the houses 2, 3 and 4 w.r.t.
+our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
 House 5 presented flaws from both tools; however, only our approach indicated which design error was responsible for the flaw (number of PV panels), further answering RQ2.
@@
 \section*{Acknowledgments}
-To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to test real PV systems.
+To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to use real PV systems.
 % Can use something like this to put references on a page

### 2019-01-16 code/codePVsystem_rev12a.c
updating code

@@ -1,0 +1,450 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that performs the automated verification of a stand-alone solar photovoltaic system CAV2019
+---------------------------------------------------------------------by Alessandro Trindade, JAN 2019 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.001 //0.0000000001
+#define precisionEXP 0.001 //0.00000001 
+
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+//case study at urban area of 915W of demand and 4.88 kWh of energy
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define Psurge 501
+  #define Econsumption 3900
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220.0
+  #define auton 24
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24.0  //controller voltage
+  #define Vsystem 24.0  //DCbus
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define Psurge 722
+  #define Econsumption 3600
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220.0
+  #define auton 24
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24.0  //controller voltage
+  #define Vsystem 24.0  //DCbus
+#elif HOUSE3
+  //Sandriane's house 263W and 2.5kWh
+  #define Phouse 263
+  #define Psurge 732
+  #define Econsumption 2500
[…]

### 2019-01-16 code/codePVsystem_rev9cBMC.c

@@ -1,0 +1,548 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+---------------------------------------------------------------------by Alessandro Trindade, JAN 2019 cbmc adapted */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+//case study at urban area of 915W of demand and 4.88 kWh of energy
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define Psurge 501
+  #define Econsumption 3900
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24  //controller voltage
+  #define Vsystem 24  //DCbus
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define Psurge 722
+  #define Econsumption 3600
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24  //controller voltage
+  #define Vsystem 24  //DCbus
+#elif HOUSE3
[…]

### 2019-01-16 code/codePVsystem_rev9eCBMC.c

@@ -1,0 +1,562 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that performs the automated verification of a stand-alone solar photovoltaic system
+---------------------------------------------------------------------by Alessandro Trindade, DEZ 2018 */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.001 //0.0000000001
+#define precisionEXP 0.001 //0.00000001 
+
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+//case study at urban area of 915W of demand and 4.88 kWh of energy
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define Psurge 501
+  #define Econsumption 3900
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220.0
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24.0  //controller voltage
+  #define Vsystem 24.0  //DCbus
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define Psurge 722
+  #define Econsumption 3600
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220.0
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24.0  //controller voltage
+  #define Vsystem 24.0  //DCbus
+#elif HOUSE3
+  //Sandriane's house 263W and 2.5kWh
+  #define Phouse 263
+  #define Psurge 732
[…]

### 2019-01-17 code/codePVsystem_rev9cUA.c
updating code

@@ -1,0 +1,547 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+---------------------------------------------------------------------by Alessandro Trindade, JAN-2019 UAutomizer adaption */
+//without pow, without NaN and without comments at the end of /@assert() command
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+//case study at urban area of 915W of demand and 4.88 kWh of energy
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define Psurge 501
+  #define Econsumption 3900
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24  //controller voltage
+  #define Vsystem 24  //DCbus
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define Psurge 722
+  #define Econsumption 3600
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24  //controller voltage
[…]

### 2019-01-18 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
CAV2019 paper

--- 2018-12-27 Tex/LaTeX2e Style File/Trindade_IEEE_TC_r0.tex
@@
-%% bare_jrnl.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[10pt,journal,compsoc]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-%\else
-  % normal IEEE
-%  \usepackage{cite}
-%\fi
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
+%
+\documentclass[runningheads]{llncs}
+%
 \usepackage{graphicx}
-\graphicspath{ {./images/} }
-%
-%\ifCLASSINFOpdf
-  %\usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-%  \DeclareGraphicsExtensions{.png}
-%\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-%\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
+\usepackage{makecell}
 \usepackage{algorithm,algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-%Alessandro input: makecell package to permite line break inside tables
-\usepackage{makecell}
-\usepackage{xcolor}
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-%\renewcommand{\baselinestretch}{0.975}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
+%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 %
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-%\title{Building a framework to perform automated verification of solar photovoltaic off-grid systems}
-\title{Automated Verification of Stand-alone Solar Photovoltaic Systems}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-
-\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
-\IEEEcompsocitemizethanks{
-\IEEEcompsocthanksitem{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
-\IEEEcompsocthanksitem{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}}% <-this % stops a space
-\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support.}
-\thanks{Manuscript received November 23, 2018; revised XXXXX 11, 2019.}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-\markboth{IEEE Transactions on Computers,~Vol.~14, No.~8, August~2015}%
-{Trindade \MakeLowercase{\textit{et al.}}: Automated Verification of Stand-Alone Solar Photovoltaic Systems}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\IEEEtitleabstractindextext{%
+\title{Automated verification of electrical systems: literature review and case studies of stand-alone solar photovoltaics\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM
+(Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}}
+%
+%\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{Alessandro Trindade\inst{1}\orcidID{0000-0001-8262-2919} \and
+Lucas Cordeiro\inst{2}\orcidID{0000-0002-6235-4272}}
+%
+\authorrunning{A. Trindade and L. Cordeiro}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Federal University of Amazonas, Av. Gen. Rodrigo Octavio, 6200, Coroado I, 69077-000 Manaus AM Brazil \email{alessandrotrindade@ufam.edu.br} \and
+The University of Manchester, Kilburn Building, Oxford Road, Manchester M13 UK
+\email{lucas.cordeiro@manchester.ac.uk}}
+% \and ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
+%\email{\{abc,lncs\}@uni-heidelberg.de}}
+%
+\maketitle              % typeset the header of the contribution
+%
 \begin{abstract}
-With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
-Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
+Around 1 billion of people do not have electrical energy nowadays on Earth.
+Energy poverty alleviation has become an important political issue.
+Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries.
+Particular attention is given to use renewables and stand-alone solar photovoltaic systems.
 Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-Automated verification using model checking has proven to be an effective technique to program verification.
-This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected by our automated verification method.
+The use of automated verification in electrical systems is a fresh subject with few issued literature.
+This paper do a state-of-art review about the use of automated verification on electrical systems and perform a comparative of tolls applied to five stand-alone solar photovoltaic systems.
+Information about the use of a commercial simulator and monitoring data from the deployed systems are used to validate the research.
+Data from experimental results shows that only some flaws can be detected by automated verification and that ESBMC verification engine obtain the best results, regardless using a high-end or low-end setup.
+
+\keywords{Automated verification  \and Model Checking \and Electrical systems \and Solar photovoltaic systems.}
 \end{abstract}
-
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Formal verification, model checking, photovoltaic power systems, power system modeling, solar power generation.
-\end{IEEEkeywords}}
-
-% make the title area
-\maketitle
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\IEEEraisesectionheading{\section{Introduction}}
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps.
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by the IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-\IEEEPARstart{T}{here} are presently 1.3 billion people with no access to electricity worldwide~\cite{Coelho}. 
-%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
-%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
-%
-%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
-Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
-
+%
+%
+%
+\section{Introduction}
+%%%%%In 2015, 193 Member States of the United Nations agreed as part of the Sustainable Development Goals (SDG) with a specific target to 'ensure access to affordable, reliable and modern energy for all by 2030' – universal access to electricity and clean cooking~\cite{IEAeao2017}.
+Therefore electricity has a important role, based on two main issues: %that are on the agenda of all current rulers and society in general, regardless of whether it is a developed, emerging or developing country:
+%%%%%the impact on the global climate change and poverty alleviation.
+%
+%%%%%Related to climate change, the 23rd session of the Conference of the Parties (COP23) to the United Nations Framework Convention on Climate Change (UNFCCC) in 2017 was the second session after the Paris Agreement, which aims to keep the maximum global average temperature rise as close as possible to 1.5 $^{o}$C.
+%During COP23, with respect to the future market development of renewable power and solar PV (photovoltaics) in particular, it was created an alliance of nations and states committed to moving the world from burning coal to cleaner power sources was a promising sign at COP23 \cite{Jager-Waldau}.
+%%%%%Decarbonization of our energy supply is an important component to achieve the targets, because 65.3\% of the worlds current CO\textsubscript{2} emissions (from energy supple) are due to burning fossil fuels according with 2016 data: 81.1\% of our total primary energy supply depended on burning fossil fuels, namely 27.1\% coal, 31.9\% oil and 22.1\% natural gas~\cite{IEAwes2018}.
+In terms of final energy consumption electricity only accounted for 18.6\%, but was responsible for 32\% of the total CO\textsubscript{2} emissions~\cite{IEAwes2018}.
+Photovoltaics (PV) is one of the key technology options for implementing the shift to a decarbonized energy supply, because it is abundant, cannot be monopolized  and can be deployed in a modular way almost everywhere on Earth.
+%
+%Related to poverty alleviation, 
+%
+%In reality, the biggest barrier to universal energy access is not the capacity to generate electricity, but rather the ability to get energy to those who need it most.
+The concept of energy poverty and access tends to focus on very small, incremental shifts in the delivery of energy to poor people.
+The total energy demand of these shifts constitutes only a small fraction of the ‘gap’ between electricity supply in much of Africa versus more industrialised countries, or the gap between the region’s current and projected electricity supply.
+https://policy-practice.oxfamamerica.org/static/media/files/FINAL_speakingpowertotruth_SH.pdf
+%
+%%%%%Poverty, in other hand, needs to be addressed through socio-economic development.
+Poverty %is conceptualized in material terms as not having access to adequate levels of food, water, clothing, shelter, sanitation, health care and education.
+This
+%%%%%can be translated into people having insufficient income. 
+%
+For numerous people around the world, a better life means getting access to basic needs such as food, health services, housing and clean water.
+None of these basic needs can be provided without energy.
+Energy is one of the most essential inputs into sustaining people‘s livelihoods.
+Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+
+Progress has been made worldwide.
+The number of people without electricity access fell below 1 billion for the first time in 2017~\cite{IEAweo2018}.
+To provide universal electricity for all, decentralized systems, led by solar PV in off-grid and mini-grid systems, will be the least-cost solution for three-quarters of the additional connections needed, but that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.
+
+%With worldwide over 400GW cumulative installed photovoltaic electricity generation capacity installed by the end of 2017, photovoltaics still is a small contributor to the electricity supply with a little of 2\%, but its importance for our future energy mix is now acknowledged and with the fastest growth (32\% whem compared with 2016 numbers)~\cite{Jager-Waldau}.
+%
 In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
-%
-%However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
-%
-%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
-In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
-SPV...
-%
-%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
-Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-%
-%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
-%
-%PV systems can be classified into grid-connected and stand-alone systems.
-At this proposal, only off-grid or stand-alone systems will be considered.
-The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
 However, those tools are based on running experiments in simulation models.
-Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+Simulation %has the advantage of being cheap (if compared to test in real systems) and can be
+is employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
 Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.
-%with behavior that is, in principle, well determined. 
 Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
-%User or project requirements can be added during the creation of the formal model to be verified.
-%, as defined by \cite{Trindade}.
-%
-%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
-% Their aim is to establish system correctness with mathematical rigor. 
-%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
-% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
-%
-%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
-%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
-%Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
-%
-%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
-%
-In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is created.
-The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+
+In this study, an updated review about the use of verification tools in electrical systems is performed, and is presented five case studies, where different model checking tools are compared in terms of performance and reliability when validating stand-alone solar PV systems.
+In order to perform the comparation and case studies, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used.
 The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
-The model checking tool reports in which conditions a system does not meet the user requirements.
+The model checking tools report in which conditions a system does not meet the user requirements.
 A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
-%Those programs are viewed as mathematical objects, and the use of 
-%Bringing this technique to solar PV systems, i
-%Instead of finding a bug or a software inconsistence, t
-%Here it will be verified a stand-alone PV system, with all their components modeled mathematically,   
-%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
-%, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
-
-In prior studies, the evaluation of PV systems w.r.t.
-user requirements were performed by simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
-Related to formal methods, studies were carried out toward the modeling of power smart grids~\cite{Akram2018} and solar panels~\cite{Driouich2017}; however, those studies do not perform automated verification.
-%
-In addition, recent research performed a formal study of PV farms, where the focus has been the interaction with the grid~\cite{Abate2017}; or to model a PV system and to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
-Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.
-
-%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
-%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
-This paper makes two original contributions.
-% Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
-Secondly
-Firstly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT), and that was never did before.
-Secondly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.
-
-%\textcolor{red}{This introduction is missing the description of the vision, approach and results.
-In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
-%
-%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
-
-\textit{Outline}.
-Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
-Section~\ref{sec:AutomatedVerification} presents the automated verification technique.
-The methodology is presented in section~\ref{sec:Methodology}.
-Section~\ref{sec:results} is devoted to the results.
-Section~\ref{sec:Conclusions} presents the conclusion and describes future work.
-
-%--------------------------------------------------------
-\section{Solar Photovoltaic System }
-\label{sec:SolarPhotovoltaicSystem}
-%--------------------------------------------------------
-
-%According to \cite{Roy}, a 
-%A PV system is designed to give the electric supply to a load.
-This load can be either Alternate Current (AC) or Direct Current (DC) type.
-Electric supply can be needed either in daytime or evening time.
-%(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
-%For night hours or rainy days, one needs to hold batteries, where power can be stored and used.% \cite{Gules}.
-
-PV systems are classified into distinct types~\cite{Mohanty}.
-%: (1) stand-alone systems, where the energy is generated and consumed in the same place and which do not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system.
-%, where another source(s) of energy can work together with the solar PV.
-% system to provide the required demand.
-%, such as wind, biomass or diesel, 
-%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
-%
-%\begin{itemize}
-%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
-Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants;
-%\item Grid-connected systems, where the solar PV system is connected to the grid.
-The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards.
-Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode;
-%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
-In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
-%\end{itemize}
-Specifically for remote rural areas of developing countries or places where the grid extension is not feasible, 
-%stand-alone systems are one the most used solutions, and 
-% depending on the type of load, cost, resources availability, and requirements of the load, 
-%stand-alone systems 
-%can be split into several categories. However, 
-the most suitable configuration is the regulated stand-alone system with battery and AC load; this configuration is the focus of this study.
-%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
-%PV array, battery, MPPT and AC load.
-Battery is used to store the extra power of PV system.
-A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
-Extra charging and deep discharging can reduce the battery life \cite{Kim}.
-Because of the AC load, an inverter (DC to AC converter) is required.
-%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
-%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.
-
-%\subsection{Unregulated stand-alone PV system with DC load }
-%Usually this type of system is for low power applications, as defined by \cite{Roy}.
-The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:standaloneSPV} letter (a).
-At night hours, the system will not provide any supply because of the absence of the battery.
-
-%\begin{figure}[h]
-%\includegraphics[width=0.5\textwidth]{reg_unreg4.png}
-%\centering
-%\caption{PV stand-alone systems: (a) regulated stand-alone SPV system with DC load; (b) regulated stand-alone SPV system with DC load; (c) regulated stand-alone SPV system with battery DC load; and (d) regulated stand-alone system with battery and AC load  (Source: \cite{Roy}).}
-%\label{fig:standaloneSPV}
-%\end{figure}
-
-%\subsection{Regulated stand-alone PV system with DC load}
-%It is similar to unregulated stand-alone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:standaloneSPV} letter (b).
-Usually system with MPPT should have battery; otherwise, extra power will be waste.
-
-%\subsection{Regulated stand-alone system with battery and DC load}
-%Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:standaloneSPV} letter (c).
-Battery is used to store the extra power of PV system.
-A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
-Extra charging and deep discharging can reduce the battery life \cite{Kim}.
-
-%According to \cite{Pinho}, PV systems that are used to feed loads with low variation on the consumption can be sized to operate without the controller.
-That is called of self-regulated stand-alone PV system with battery.
-However, the voltage from the PV panel must be compatible with the batteries voltage.
-Normally, the bank of batteries are oversized related to the PV panel and to the load.
-The drawback is the operation of the batteries, normally overloaded or with excessive discharges (that can damage the batteries).
-
-%\subsection{Regulated stand-alone system with battery and AC load}
-%This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:standaloneSPV} letter (d).
-This solution has an increase of cost because has more equipments.
-However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-That configuration is the focus of the present work since it is the most common nowadays all over the world, when off-grid or isolated regions is the target.
-
-\subsection{Design and Simulation of Solar PV systems}
-%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
-%
-%In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
-%public domain and commercial software available for the PV market. 
-%According to \cite{Brooks}, t
-%%%%%%%%%%The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
-% to complex financial analysis and project optimization. 
-%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-%
-%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here we evaluated the most popular tools available in the literature and summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
-
-%\subsection{PVWatts Calculator}
-%According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
-According to \cite{NRELDobos}, to use the calculator, it is necessary to provide information about the system's location, basic design parameters, and system economics.
-PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity monetary value.
-This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules.
-The production estimates that PVWatts computation do not account for many factors that are important in the design of a photovoltaic system, therefore it is necessary support of an energy expert.
-The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year.
-To represent the system's physical characteristics, PVWatts requires values for six inputs: System DC size; Module type; Array type; System losses; Array tilt angle; Array azimuth angle.
-
-%\subsection{SAM}
-%SAM or System Advisor Model is a software from the U.S.
-Department of Energy and National Renewable Energy Laboratory.
-According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications, and (also) to provide information for readers who do not plan to use the model, but want to learn about its capabilities.
-SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: Project managers and engineers; Financial and policy analysts; Technology developers; and Researchers.
-SAM makes performance predictions and cost of energy estimates for grid-connected power projects based on installation and operating costs and system design parameters that you specify as inputs to the model.
-Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement.
-SAM is an electric power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet electric load.
-It does not model thermal energy systems that meet a thermal process load.
-As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.
-
-%\subsection{HOMER}
-%As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
-HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources.
-HOMER Legacy is the original HOMER software version created at the National Renewable Energy Laboratory (NREL).
-HOMER Legacy is a free computer model that simplifies the task of evaluating design options for both off-grid and grid-connected power systems for remote, stand-alone, and distributed generation applications.
-HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options.
-Since 2016 HOMER Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available.
-At the short-time only the commercial version will remain.
-
-%The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
-HOMER Pro put together three tools in one product: optimization, simulation, and sensitivity analysis.
-HOMER Pro provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use.
-It is adaptable to a wide variety of projects.
-For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project.
-For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations.
-Chronological simulation is essential for modeling variable resources, such as solar and wind power and for combined heat and power applications, where the thermal load is variable.
-HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.
-
-%\subsection{RETScreen}
-%As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
-
-%RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options.
-The software can be used to evaluate benefits from both clean energy production from power generation projects and savings through energy efficiency projects, accounting for project costs, greenhouse gas emission reductions, and financial risk.
-The software is freely distributed (but with restrictions to save work or print), and had three different versions:
-
-%\begin{itemize}
-%\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
-%\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
-%\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
-However, this version works is only Windows-based.
-This version has a complete paid version, in an annual subscription way.
-%\end{itemize}
-
-%As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
-It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
-RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.
-
-%\subsection{Hybrid2}
-%The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
-Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
-Variations in wind speed and in load within each time step are factored into the performance predictions.
-The code does not consider short-term system fluctuations caused by system dynamics or component transients.
-This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, what is a limitation.
-
-%Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where 
-As highlights, only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription typically range from US\$504.00 to US\$657.00.
-
-\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Comparative coverage of reference software}
-\label{table:softwares}
-\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-\begin{tabular}{c | c | c | c | c | c}
-\hline
-\hline
-Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen} & \rotatebox{90}{Hybrid2}\\
-\hline
-\hline
-Support & X & X & X & X &  \\
-\hline
-Off-grid systems &   &   & X & X & X\\
-\hline
-Hybrid systems &  &  & X & X & X\\
-\hline
-Photovoltaics & X & X & X & X & X\\
-\hline
-Batteries &  &  & X &  & X\\
-\hline
-\makecell{Main technical (T) \\ or economical(E)} & T & T & E & E & T \\
-\hline
-Optimization &  &  & X & X &  \\
-\hline
-Sensitive analysis &  &  & X & X & \\
-\hline
-\hline
-\end{tabular}
-\end{table}
-
-%-------------------------------------------------------------------
-%\subsection{Paper Proposal x Reference Tools}
-%-------------------------------------------------------------------
-%
-In this study, only HOMER has the minimum features for a comparative with our proposed verification approach.
-That evaluation is presented in Section~\ref{sec:results_indeed}.%All tools need some parameters inherently from manufacturer's catalog.
-%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
-%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-%Thus, the main challenge here is to demonstrate the application of software model checking to formally verify a stand-alone PV solution, thus proving that this approach is more effective and complete than other state-of-the-art tool such as HOMER Pro.
-The comparative evaluation between HOMER Pro and our approach is presented in Section~\ref{sec:results_indeed}.
-%
-%-------------------------------------------------------------------
-\subsection{Component models for a stand-alone PV system }
-%-------------------------------------------------------------------
-%The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
-%The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
-It identifies the PV generator, batteries, charge controller, inverter, and AC load.
-A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-The PV generator (panel or array) is a semiconductor device that can convert solar energy into DC electricity.
-%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
-For night hours or rainy days, we need to hold batteries, where power can be stored and used.
-The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
-The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
-%
-%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
-%
-\begin{figure}[h]
-\includegraphics[width=0.48\textwidth]{blockdiagramPVS2}
-\centering
-\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
-\label{fig:blockdiagram}
-\end{figure}
-%
-%In the literature, there are several mathematical models available for each component of PV systems. At the next section, the mathematical model for each component is presented. 
-%-------------------------------------------------------------------
-\subsection{PV generator model}
-\label{sec:PVmodel}
-%-------------------------------------------------------------------
-%A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
-%In the present modeling, the focus is only on cell/module/array.
-%
-%%%%%%The basic element of a PV system is a PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
-%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
-When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}.
-If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
-%%%%%To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
-%%%%%package called panel or module. 
-%For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
-In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}.
-The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{celmodarray}
-%\centering
-%\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
-%\label{fig:celmodarray}
-%\end{figure}
-%
-%%%%%The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on meteorological conditions.
-%the meteorological conditions of the area to be serviced by PV solution. %However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
-%, which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
-The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
-However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
-%
-%These uncertainties lead to either over- or underestimation of energy yield from PV modules.
-An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
-The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
-%
-%Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
-However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage.
-Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
-% 
-%Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
-A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves).
-However, the present work will rely on the simplified model of 1-diode.
-It was demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-
-%The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-%is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
-%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
-\begin{figure}[h]
-\includegraphics[width=0.20\textwidth]{equivckt1D}
-\centering
-\caption{1-diode equivalent PV cell/panel circuit model~\cite{Cubas}.}
-%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
-\label{fig:equivckt}
-\end{figure}
-
-The 1-diode model, illustrated in Fig.
-\ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described by ~\eqref{eq:1diodemodel}.
-%This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-%In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
-\begin{equation}
-\label{eq:1diodemodel}
-I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right], 
-\end{equation}
-
-\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
-$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
-
-%\begin{itemize}
-%\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
-%\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
-%\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed; $ N=1 $ in a single cell configuration.
-%	\begin{itemize}
-%	\item $ N=1 $ in a single cell configuration. 	
-%	\end{itemize}	  
-%\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes.
-%	\begin{itemize}
-%	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
-%	\end{itemize}
-%\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
-%	\begin{itemize}
-%	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
-%	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
-%	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
-%	\end{itemize}	 
-%\end{itemize}
-%
-%This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.
-%
-%The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}. 
-%
-%\begin{equation}
-%\label{eq:1d1rmodel}
-%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
-%\end{equation}
-%
-%Where $R_{s}$ is the series resistor.
-%
-%At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
-%
-%The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}. 
-%
-%\begin{equation}
-%\label{eq:1d2rmodel}
-%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-%\end{equation}
-%
-%Where $R_{sh}$ is the shunt resistor.
-%
-%At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
-%
-%And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}. 
-%
-%\begin{multline}
-%\label{eq:2d2rmodel}
-%I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - \\ %I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-%\end{multline}
-%
-%This model has six unknown parameters with two exponential terms. 
-%Briefly, both single and double diode models require the knowledge of all unknown parameters, which is usually not provided by manufacturers.
-Nevertheless, the current-voltage equation is a transcendental expression \cite{Jakhrani}.
-%
-%However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel. 
-%
-%For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
-The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
-However, due to implicit nature and nonlinearity of PV cell or module characteristics, it is hard to find out the analytical solution of all unknown parameters, as described by \cite{Hasan}.
-Thus, numerical methods such as Newton-Raphson method or Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}.
-This happens because numerical methods give approximate solution of the nonlinear problems without searching for exact solutions.
-However, numerical methods are time consuming and need long term time series data, which is not available in developing countries.
-\cite{Jakhrani} did a mixed methodology using analytical and numerical steps together.
-\cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation (essays).
-And \cite{Tian} did a mix of analytical and experimental methodology to get the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use experimental technique.
-%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
-%The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
- %
-%\subsection{PV Panel Model}
-%With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
-%
-%A single-diode without series and shunt resistances is considered. 
-%%%%%%%Eq.~\eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
-% shown in Fig. \ref{fig:ivcurve}.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{ivcurve}
-%\centering
-%\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
-%\label{fig:ivcurve}
-%\end{figure}
-%
-%Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
-%\begin{equation}
-%\label{eq:Isc}
-%I_{sc}=I_{ph}\vert_{V=0}
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Voc}
-%V_{oc}=\dfrac{aNk_{B}T}{q}ln\left( 1+\dfrac{I_{sc}}{I_{0}} \right) 
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:exp}
-%exp\left( \dfrac{qV_{oc}}{aNk_{B}T} \right) = \left(1+\dfrac{qV_{m}}{aNk_{B}T} \right) exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) 
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Im}
-%I_{m} =I_{ph}-I_{0}\left[ exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) -1 \right] 
-%\end{equation}
-%
-%Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way. 
-%
-%A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}. 
-%These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig.
-\ref{fig:ivcurve}, where the transition is a compromise between both behaviors.
-It is interesting to observe that the maximum power point corresponds to a trade-off condition, where the current is still high enough before it starts decreasing with increasing the output voltage (Fig.
-\ref{fig:ivcurve}).
-%
-%Based on this, the tangent of the I-V curve can be used to evaluate the transition between current- to voltage-source controlled regions; this operation yields Equation \ref{eq:didv}.
-%
-%\begin{equation}
-%\label{eq:didv}
-%\dfrac{dI}{dV}=-\dfrac{qI_{0}}{aNk_{B}T}exp \left( \dfrac{qV}{aNk_{B}T}  \right) 
-%\end{equation}
-%
-%The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell.
-Therefore, the Equation \ref{eq:Vmderiv} is generated.
-%
-%\begin{equation}
-%\label{eq:Vmderiv}
-%V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
-%\end{equation}
-%
-%It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point.
-The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change on $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}.
-Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation \ref{eq:Vmderiv} can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
-%
-%\begin{equation}
-%\label{eq:dIdV_Vm}
-%\dfrac{dI}{dV}\vert_{V_{m}} \cong -\dfrac{0-I_{sc}}{V_{oc}-0}=\dfrac{I_{sc}}{V_{oc}}
-%\end{equation}
-%
-%Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, 
-%
-The voltage and the current at the maximum power point tracking (MPPT), can be described by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm}  as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
-\begin{equation}
-\label{eq:Vmfinal}
-V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right). 
-\end{equation}
-
-\begin{equation}
-\label{eq:Imfinal}
-I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right).  
-\end{equation}
-
-\begin{equation}
-\label{eq:Pm}
-P_{m} = V_{m} I_{m}.
-\end{equation}
-
-%\begin{multline}
-%\label{eq:Pm}
-%P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
-%\end{multline}
-%
-However, the photocurrent delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, ~\eqref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature~\cite{Villalva}:
-\begin{equation}
-\label{eq:Iph}
-I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right], 
-\end{equation}
-
-\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions
-(provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Villalva} that is provided by PV manufacturers ($ I_{sc,ref} $).
-%\cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
-%%
-The cell temperature ($ T $) in degree Celsius is described by ~\ref{eq:Tcell}~\cite{Ross}:
-\begin{equation}
-\label{eq:Tcell}
-T = T_{air} + \dfrac{NOCT-20}{800}G,
-\end{equation}
-
-\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet \cite{Ross}, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
-
-Furthermore, ~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\cite{Villalva} 
-%In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
-
-\begin{equation}
-\label{eq:I0}
-I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1},
-\end{equation}
-
-\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
-
-%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current (cf.
-~\eqref{eq:Imfinal}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor is determined by ~\eqref{eq:a}:
-\begin{equation}
-\label{eq:a}
-a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) },
-\end{equation}
-
-\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions.
-%, usually provided by manufacturers; the PV generator model is now completely determined.
-%; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
-%
-%If the PV cells are in parallel, then there is a parallel array.
-Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
-%
-%\begin{equation}
-%\label{eq:Iarray}
-%I_{array} = (N_{cells in parallel})(I_{one cell})
-%\end{equation}
-%
-%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
-%
-%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
-%
-%\begin{equation}
-%\label{eq:Varray}
-%V_{array} = (N_{cells in series})(V_{one panel})
-%\end{equation}
-%
-%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
-%------------------------------------------------------------
-\subsection{The Battery Storage Model }
-\label{sec:BATmodel}
-%------------------------------------------------------------
-
-%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system.
-Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery.
-During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.
-
-Various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Pinho};
-%, and \cite{Manwell93, Manwell94}. 
-%However, regardless of the model, normally the following parameters are required: 
-%
-%\begin{itemize}
-%\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
-%, under predetermined discharge conditions.
-%\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
-%Obviously $ 0<SOC<1 $. 
-%If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
-%\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
-%It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
-%\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
-%\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
-%\end{itemize}
-%
-%The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
-The battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
-LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.
-%
-%In general, the battery models view the battery as a voltage source $ E $ in series with an internal resistance $ R_{0} $, as shown in Fig. \ref{fig:batteryckt}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{batteryckt}
-%\centering
-%\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
-%\label{fig:batteryckt}
-%\end{figure}
-%
-%The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.  
-%
-%Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
-%
-%The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.  
-%
-%The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
-However, it uses some data extracted from tested batteries in laboratory.
-Therefore is not suitable to this study.
-%
-that kind of battery has relative low cost and wide availability~\cite{Copetti}. 
-%
-Here, the model adopted uses only manufacturer's data without empirical tests~\cite{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature. 
-%
-The discharge voltage equation is described by \eqref{eq:bat_Vd}.
-%The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
-%
-\begin{multline}
-\label{eq:bat_Vd}
-V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \\ \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T),
-\end{multline}
-
-\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $%, $ T_{ref}=25^{o}C $
-), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time.
-Mathematically, it is the ratio between the present capacity and the nominal capacity% (in $ Ah $, provided by manufacturer)
-. If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
-%\begin{equation}
-%\label{eq:SOCbat}
-%SOC = \left( 1 - \dfrac{Q}{C} \right) 
-%\end{equation}
-%
-%Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
-%
-%The ratio between $ Q $ and $ C $ represents t
-The depth of discharge ($DOD$) or the fraction of discharge, is $DOC=1-SOC$.
-
-%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
-This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
-%
-%\begin{equation}
-%\label{eq:CC10}
-%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
-%\end{equation}
-%
-%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
-For the charging process, however, the parameters are described by ~\eqref{eq:Vcbat} as
-%
-\begin{multline}
-\label{eq:Vcbat}
-V_{c} = [2+0.16SOC]+ \\ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
-\end{multline}
-
-Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period.
-%; however, during recharge it is much more difficult \cite{Copetti}.
-%Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell.
-The efficiency drops to zero at full charge and the function that represents the charge efficiency ($ \eta_{c} $) variation with state of charge and current rate is given in Equation \ref{eq:efficcharge}.
-%\begin{equation}
-%\label{eq:efficcharge}
-%\eta_{c} = 1 - exp \left[ \dfrac{20.73}{\dfrac{I}{I_{10}}+0.55} (SOC-1) \right] 
-%\end{equation}
-%
-%\cite{Copetti} show that, 
-%During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (\ref{eq:Vec}).
-It was created a function for the gassing voltage as well, as shown in (\ref{eq:Vg}).
-In addition, the overcharge phenomenon can be represented by (\ref{eq:Voverc}).
-%\begin{equation}
-%\label{eq:Vec}
-%V_{ec} = \left[ 2.45 + 2.011 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Vg}
-%V_{g} = \left[ 2.24 + 1.97 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-%\end{equation}
-%
-%\begin{multline}
-%\label{eq:Voverc}
-%V_{c} = V_{g} + (V_{ec} - V_{g}) \\ \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
-%\end{multline}
-%
-%Where $ Ah_{restored} $ represents the Ampere-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
-%
-%The function assumes that 95\% of the capacity was already restored at the start of overcharge.
-%
-%The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by (\ref{eq:tau}).
-%\begin{equation}
-%\label{eq:tau}
-%\tau = \dfrac{17.3}{1+852 \left( \dfrac{I}{C_{10}} \right) ^{1.67} }
-%\end{equation}
-%
-%Therefore, to model the voltage ($ V_{c} $) evolution of the battery, (\ref{eq:Vcbat}) can be used up the start of gassing ($ V_{c} \leq V_{g} $).
-And during overcharging ($ V_{c} > V_{g} $), (\ref{eq:Voverc}) can be used until a constant final voltage ($ V_{ec} $) is reached.
-%
-%The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
-%
-%\begin{equation}
-%\label{eq:stor}
-%Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
-%\end{equation}
-%
-%Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
-%
-%As an example of this formula application, as shown by \cite{Abdulateef}, considering that a stand-alone PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
-%
-%Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$.
-Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$).
-If a single battery of 12 V and 350 Ah is considered, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
-%
-%At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature.
-The equations are used to update the $SOC$ of the batteries, and have the number of hours ($ Num_{h} $) as a variable.
-There is a factor (1.15) which is present at the charging equation, and is necessary to express that during the charging process is usual to reach 115\% of the battery capacity
-%
-%\begin{multline}
-%\label{eq:charge}
-%SOC_{charge} = SOC_{previous} + \\ \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
-%\end{multline}
-%
-%\begin{multline}
-%\label{eq:discharge}
-%SOC_{discharge} = SOC_{previous} - \\ \dfrac{100*I_{drained}*Num_{h}}{capacity}
-%\end{multline}
-%
-%
-%---------------------------------------------------------
-\subsection{Charge Controller Model}
-%---------------------------------------------------------
-%Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
-However, in this study, in order to simplify, the term used is controller.
-%The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-%MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power.
-Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
-%
-%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
-%
-%
-%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components.
-The use of battery as a storage form implies thus the presence of a charge controller.
-%
-%%%%%%%%%%In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
-%
-%The controller allows the management of energy between the load and the battery \cite{Mellit}. 
-%The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
-The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
-To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \textunderscore off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}.
-PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $.
-%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{controllerover}
-%\centering
-%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
-%\label{fig:controllerover}
-%\end{figure}
-%
-In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \textunderscore off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}.
-The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \textunderscore on}$.
-%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{controllerdisc}
-%\centering
-%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
-%\label{fig:controllerdisc}
-%\end{figure}
-%
-%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
-%
-The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.
-
-\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process (Source:~\cite{Hansen})}
-\label{table:controller}
-\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-\begin{tabular}{c | c | c }
-\hline
-\hline
-Step  & Constraint & Command\\
-\hline
-\hline
-(1) & \makecell{If $V > V_{max \textunderscore off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
-\hline
-(2) & \makecell{If command (1) is \\done and $V < V_{max \textunderscore on}$} & \makecell{Reconnect PV array \\to the system}\\
-\hline
-(3) & \makecell{If $V < V_{min \textunderscore off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
-\hline
-(4) & \makecell{If command (3) is \\ done and $V > V_{min \textunderscore on}$} & \makecell{Reconnect the load \\to the system}\\
-\hline
-\hline
-\end{tabular}
-\end{table}
-
-%Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage. 
-%
-%As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of controller is given by \eqref{eq:poutcont}.
-\begin{equation}
-\label{eq:poutcont}
-P_{in} \eta_{c} = P_{out}.
-\end{equation}
-
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from \eqref{eq:poutcont} we compute \eqref{eq:potcont}.
-\begin{equation}
-\label{eq:potcont}
-V_{in} I_{in} \eta_{c} = V_{out} I_{out},
-\end{equation}
-
-\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
-
-%The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}). 
-% 
-%A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
-In addition, there is the Cuk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.
-%
-%For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.
-%
-%\begin{equation}
-%\label{eq:voutvin}
-%\dfrac{V_{out}}{V_{in}} = \dfrac{D}{D-1}
-%\end{equation}
-%
-%Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
-% 
-%The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
-%  
-%Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.
-% 
-%As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
-
-%The number of controllers required for the stand-alone PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
-In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
-%\begin{multline}
-%\label{eq:numberofcmin}
-%number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \\ \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
-%\end{multline}
-%
-%\begin{equation}
-%\label{eq:numberofc}
-%N_{controller} \geq number_{controllers}
-%\end{equation}
-%
-%\subsection{Joint work: charge controller and batteries}
-%When batteries are charged, they go through three main different states - bulk, absorption and float, with impact to the inverter and to power supplied to the house.
-%, and it is necessary to understand those three states in order to comprehend the joint work of the controller with the battery. With impact to the inverter and to power supplied to the house. 
-%
-%All the explanation at this section is related to $SOC$ and to the voltage at the DC-bus (controller output, which will be bigger than $V_{system}$) where the batteries are connected, all ruled by the charge controller.
-Moreover, it is important to mention that smart chargers, the most usual nowadays, will detect voltage and resistance from the battery prior to charging.
-%
-%Bulk - is the first stage of charging. Bulk begins when the sun comes out.
-%, or other source of electrical generation is turned on. 
-%This stage occurs when the batteries are at a lower $SOC$, generally anything not smaller than $75\%$ to $80\%$ (defined during system sizing).
-This stage is typically where the highest voltage and current the charger is rated for will actually be used.
-The bulk stage basically allows the PV panel to put as much current into the batteries as possible.
-For a typical 12 V battery, the charging voltage going into a battery will reach 14.16 V to 14.40 V at this stage, and there is no risk of overcharging in this stage because the battery hasn't even reached full yet.
-%
-%Absorption - once the batteries reach the programmed absorb voltage, usually somewhere between 14.16 and 14.40 V, the batteries will go into the absorption stage.
-Typically, when a battery reaches this stage its $SOC$ is around $85-95\%$.
-During this stage, the batteries are kept at the programmed voltage, and the current going into the batteries reduces as the batteries become more full.
-The absorption stage ends after the programmed time is reached or the number of Ampere going into the battery falls below a preset number.
-The lower current going into the battery safely brings up the charge on the battery without overheating it.
-%Usually, this stage takes more time than the bulk stage.
-%
-%Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage that a 12 V battery can hold, and begin the float stage.
-The float stage brings the battery all the way through and maintains $SOC$ at $100\%$.
-The current will also decrease to a point where it's considered just a pulse.
-It's essentially the float stage where there is charge going into the battery at all times, but only at a safe rate to ensure a full state of charge and nothing more.
-%Most smart chargers do not turn off at this point, however it is completely safe to leave a battery in float mode for months to even years at a time.
-%
-%Battery charging technology relies on smart micro-controlled devices.
-Therefore it is extremely important that the program settings for the charge controller or inverter/charger are correct, and the list includes the bulk and absorption values.
-%This will help preserve and extend the battery life.
-There are always default settings to the equipment, set by software, however those settings are not $100\%$ correct because there are difference among models of equipment and among manufacturer's.
-The ideal is to read the data-sheet from the manufacturers and perform a manual adjust.
-%
-%There are the possibility to combine batteries in a bank, with parallel and series connections, all depending the sizing of the project:
-%
-%\begin{itemize}
-%\item Batteries connected in parallel are seen by the controller as one large battery of the combined Ah capacity of all the batteries.
-For example, two 12 V and 220 Ah batteries in parallel are seen as one 12 V and 440 Ah battery;
-%\item In the other hand, although the batteries connected in series are also seen as a single battery, the result is different: two 12 V and 220 Ah batteries in series are seen as one 24 V and 220 Ah battery;
-%\item In addition, a mixed bank arrangement can be useful: a bank with two 12 V and 220 Ah batteries in series connected in parallel with a similar arrange will produce an equivalent battery of 24 V and 440 Ah.
-%\end{itemize}
-%-----------------------------------------------
-\subsection{The inverter model}
-%-----------------------------------------------
-%As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. 
-%An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
-The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage, % (127 V or 220 V, for example), 
-and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by \eqref{eq:efficinv} \cite{Hansen}:
-%
-%The inverter is characterized by a power dependent efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
-\begin{equation}
-\label{eq:efficinv}
-\eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}},
-\end{equation}
-
-\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be obtained from the inverter's data-sheet.
-
-%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
-%
-%--------------------------------------------------
+The case studies are not theoretical and were deployed in 2018, with feedback information collected from monitoring systems and through interview with the dwellers.
+%The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
+\section{State-of-art in automated verification of Electrical systems}
+This section summarizes, in a chronological way, the research done by previous studies related to the subject of this research.
+
+The conversion of traditional power grid into a smart grid, a fundamental example of a cyber-physical system, raises a number of issues that require novel methods and applications.
+In 2012, it was considered a specific Chinese Smart Grid implementation as a case study and address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+It was employed the stochastic model checking approach and present a modelling and analysis study using PRISM model checker.
+The focus was how Cyber-physical systems integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes.
+In this context, it was applied automated verification of certain quantitative properties of the system.
+%, with no interest in power generation or even solar PV systems.
+
+%In 2014, there were a research showing that power systems model information exchange and the simulation of user defined models is a challenge issue for the transmission system operator.
+The reason: the use of different simulation software with specific data format and models strongly coupled to the simulation software numerical routines.
+The researchers proposed the use of Open Source software (Modelica, JAVA and Python) for simulation and modelling as a solution to decouple these models.
+The work described the design of a simulation tool following the Free/Libre Open Source Software philosophy to simulate equation-based models and implement a standard data format for model information exchange~\cite{Gomez2014}.
+The aim was the use of Modelica to define standards and industry models, besides the interest of components in modules.
+This work did not reached the automated verification, it is just simulation, however created the base to future work of formal methods on electrical systems.
+%
+In 2015, it was showed that related to power system protection schemes, the approach of using Monte-Carlo simulation and manual interpretation of results had the limitation of the incomplete coverage of all possible operating conditions due to the time complexity of simulation~\cite{Sengupta2015}.
+It was proposed an automated simulation-based verification technique to verify the correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
+The initial focus were relay operations and test-case generation to ensure early detection of design errors.
+%The study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
+
+Other work issued in 2015 was a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with Statistical Model Checking (SMC) for Cyber-Physical Systems (CPSs) in terms of Non Functional Properties (NFP) such as time, energy, etc~\cite{Cheng2015}.
+To demonstrate the capability of Modana framework, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+The focus is in smart buildings and HVAC (Heating, ventilation, and air conditioning) systems.
+%The research did no deal with solar PV systems.
+
+Back in 2017, it was suggested the use of formal methods to verify and certifiably control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
+It was shown that formal techniques can provide compelling solutions not only when safety-critical goals are the target, but also to tackle verification and synthesis problems on populations of such devices.
+This work argued that alternative solutions based on classical analytical techniques or on approximate computations are prone to errors with global repercussions.
+Two different areas were targeted: thermal loads and electricity-generating devices interacting over a smart energy network or over a local power grid.
+The researcher discussed the aggregation of large populations of thermostatically-controlled loads and of photovoltaic panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The focus is in controlling the behavior of the components, verifying the smart grid, dealing with a 'system of systems' and with 'internet of things'.
+The author uses approximate model checking of stochastic and hybrid models.
+% Therefore, the focus is not in electricity generation or even the components of a stand-alone solar PV system.
+
+In 2018, is was proposed a methodology for the verification of the Cyber Physical Energy Systems (CPES), with the methodology applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+The approach relied on representing the unpredictable behavior of the environment in order to cover all feasible possible scenarios.
+Processed by JModelica, the simulation results covered the system's complete dynamic behavior.
+It was evident at this work the time consuming issue, with almost three days of computer effort to verify the design space of one hour from PV panels behavior.
+%The work did not include the other components of a stand-alone solar PV system.
+
+Another work issued in 2018 was the approach to modeling smart grid components using a formal specification. It was used a state-based formal specification language namely Z %(pronounced as `Zed') 
+and it was demonstrated the application of Z on four smart grid components~\cite{Akram2018}.
+The presented formal specification can be considered as first steps towards modeling of smart grid using a Software Engineering formalism.
+The starting point of this work it was that a smart home can be considered as an integrated system consists of various objects and system, that communicates and interact  with  each  other.
+The approach is base in Petri nets and from the premise that modeling of the smart home leads to clear understanding the overall behavior of the smart grid.
+
 \section{Automated Verification Using Model Checking}
@@
 %
-The model checking algorithm can be described as \cite{ClarkeHV18}:  
-%
-\begin{itemize}
-\item Given the model $M$ and a CTL (or LTL) formula $ \phi $ as input;  
-\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
-\item It returns \textit{YES} if $ \phi $ is \textit{TRUE}, or returns \textit{NO} if $ \phi $ is \textit{FALSE}.  
-\end{itemize}
+%%%%%
+%%%%%The model checking algorithm can be described as \cite{ClarkeHV18}:  (i) Given the model $M$ and a CTL (or LTL) formula $ \phi $ as input;  (ii) Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  and (iii) It returns \textit{YES} if $ \phi $ is \textit{TRUE}, or returns \textit{NO} if $ \phi $ is \textit{FALSE}.
 Specifically for the \textit{FALSE} verification result, the algorithm returns a \textit{counterexample} (i.e., a sequence of states that leads to a property violation), which is useful as diagnostic of the system to discover in which situation the model is violated; this is the most important advantage of the use of model checking~\cite{ClarkeHV18}.
-%Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
-%
-%The model checking problem can be defined as \cite{ClarkeHV18}: 
-%
-%\begin{itemize}
-%\item Let $M$ be a Kripke structure (i.e., state transition graph);
-%\item $f$ be the specification in temporal logic (a formula);
-%\item Find all states $s$ of $M$ such that $M , s \models f$
-%\end{itemize}
-%
-%Fig. \ref{fig:modelcheckstruc} shows the structure of a 
-%In a typical model checking system, a preprocessor extracts a state transition graph from a system (program or circuit).
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{modelcheckstruc}
-%\centering
-%\caption{Model Checker structure (Source: \cite{ClarkeHV18})}
-%\label{fig:modelcheckstruc}
-%\end{figure}
-%
-%Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study. 
-%
-Fig.~\ref{fig:systemverif} shows a real PV system, and Fig.~\ref{fig:systemverif2} the conversion the system to be verified by a model checking procedure.
+%%%%%
+%%%%%%%%%%%%%%%Fig.~\ref{fig:systemverif} shows a real PV system, and Fig.~\ref{fig:systemverif2} the conversion the system to be verified by a model checking procedure.
 % \textcolor{red}{Please try to adapt this figure to our context.
@@
 How can it be applied to verify PV?}.
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{system_original_blocks}
-\centering
-\caption{Real system verification (adapted from \cite{ClarkeHV18}).}
-\label{fig:systemverif}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{system_model_blocks}
-\centering
-\caption{Model checking verification \cite{ClarkeHV18}.}
-\label{fig:systemverif2}
-\end{figure}
-
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.5\textwidth]{system_original_blocks}
+%\centering
+%\caption{Real system verification (adapted from \cite{ClarkeHV18}).}
+%\label{fig:systemverif}
+%\end{figure}
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{system_model_blocks}
+%\centering
+%\caption{Model checking verification \cite{ClarkeHV18}.}
+%\label{fig:systemverif2}
+%\end{figure}
+%
 However, there is a main disadvantage of model checking: the state explosion problem.
@@
 %
-ESBMC is one of the most representatives bounded model checkers for embedded C/C++ software based on SMT solvers~\cite{esbmc2018}. %, which can use CBMC as front-end.
-%The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
-ESBMC comes as an alternative to overcome limitations of the system modeling, especially considering that the system complexity is increasing and SMT has richer theories than SAT to represent models.
-
+\subsection{CBMC}
+The C Bounded Model Checker (CBMC) is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}.
+CBMC demonstrates the violation of assertions in C programs, or proves safety of the assertions under a given bound.
+CBMC implements a bit-precise translation of an input C program, annotated
+with assertions and with loops unrolled to a given depth, into a formula. If the
+formula is satisfiable, then an execution leading to a violated assertion exists~\cite{Kroening}.
+
+CBMC's verification flow can be summarized in four stages: (i) Front-end that can read, perform parse and type checker of the C/C++ code; (ii) Intermediate Representation.
+CBMC uses  intermediate representation, converting all non-linear control flow, such as if or switch statements, loops and jumps, into equivalent guarded goto statements; aiming to reduce the verification effort; (iii) Middle end.
+CBMC performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end.
+With support to SAT and SMT solvers.
+Conversely, if the formula is unsatisfiable, no assertion can be violated within the given unwinding bounds.
 %--------------------------------------
@@
 ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+%The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
+ESBMC comes as an alternative to overcome limitations of the system modeling, especially considering that the system complexity is increasing and SMT has richer theories than SAT to represent models. 
 %
@@
 This enables ESBMC, and the respective solver, to learn from previous checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows us to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with all the design space state.
-
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%
-%%%%%ESBMC can be invoked through the command-line interface or configured through the Eclipse plug-in. Specific problems and the solver can be selected that way. 
-%
-%ESBMC aims to support all of ISO/IEC 9899:2017 C programming language standard, and detects errors in software by simulating a finite prefix of the program execution with all possible inputs.
-Classes of problems that can be detected include: user specified assertion failures, out of bounds array access, illegal pointer dereferences, double-free of malloc'd memory, misaligned memory access; integer overflows, divide by zero, memory leaks, concurrent software, deadlock, and data races (i.e.
-competing writes).
-
-%\subsection{Cyber-physical systems x Energy x ESBMC}
-%According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes.
-Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa.
-The economic and societal potential of such systems is vastly greater than what has been realized, and major investments are being made worldwide to develop the technology.
-The technology builds on the discipline of embedded systems (computers and software embedded in devices) whose principle mission is not computation, such as cars, toys, medical devices, and scientific instruments.
-CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole.
-%
-%Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}.
-For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies.
-Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation).
-%
-%Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled.
-Then a model checking will be performed to do a verification of the project in order to guarantee that the design of a stand-alone PV solution will meet the requirements, specifications and regulations.
-%
-%As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification.
-Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver.
-This work tracks the same path.
+This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows us to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with all the design space state.
+\subsection{Ultimate Automizer}
+%Ultimate Automizer is an automatic software verification tool for C programs.
+This tool is the first implementation of trace abstraction, which is an automata-theoretic approach to software verification.
+The implemented algorithm uses nested interpolants in its interprocedural program analysis.
+Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties.
+The tool implements an automata-based instance of the CEGAR scheme.
+CEGAR or Counterexample-Guides Abstraction Refinement is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check, and refinement~\cite{CEGAR}.
+%(i) precision, for the level of abstraction; (ii) feasibility check, deciding if there is a concrete error path; and (iii) a refinement procedure, which takes as input as infeasible error path and extracts a precision that suffices to instruct the exploration algorithm do not explore the same path again later~\cite{CEGAR}.
+
+In each iteration, Automizer pick a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible.
+If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace’s infeasibility.
+The predicates are a sequence of interpolants since each predicate “interpolates” between the set of reachable states and the set of states from which we cannot reach the error.
+In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed.
+It is used automata to represent sets of traces.
+The difference to a classical CEGAR-based predicate abstraction is that Automizer have to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.
 %
 %----------------------------------------
-\section{Model Checking Stand-alone Solar Photovoltaic Systems }
+\section{Automated verification of Stand-alone Solar PV Systems }
 \label{sec:Methodology}
 %----------------------------------------
-%
-%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.5\textwidth]{statetransition}
-%\centering
-%\caption{State transition diagram to the proposed automated verification.}
-%\label{fig:statetransition}
-%\end{figure}
-%
-%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.
-%
-The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
+\subsection{Stand-alone Solar PV Systems}
+PV systems are classified into distinct types~\cite{Mohanty}.
+Specifically for remote rural areas of developing countries or places where the grid extension is not feasible, the most suitable configuration is the regulated stand-alone system with battery and AC load; this configuration is the focus of case-studies of this work.
+
+The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
+It identifies the PV generator, batteries, charge controller, inverter, and AC load.
+The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
+In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
+For night hours or rainy days, we need to hold batteries, where power can be stored and used.
+The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}.
+The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
+That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+\begin{figure}[h]
+\includegraphics[width=0.6\textwidth]{blockdiagramPVS2}
+\centering
+\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
+\label{fig:blockdiagram} 
+\end{figure}
+A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves).
+However, the present work will rely on the simplified model of 1-diode.
+It was demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
+The model uses formulas from different references~\cite{Hansen}, \cite{Saloux}, and \cite{Ross}.
+
+To model the batteries, it was used the most common based on lead-acid~\cite{Copetti}.
+Related to the charge controller, it was used the 4-steps controller processes with MPPT (maximum power point tracking) to decide if the PV array must be disconnected from the system, or if the PV can be reconnected, or if the load is disconnected and when the load is reconnected~\cite{Hansen}.
+The inverter model is the simplest and is based on efficiency, i.e., the relation between the AC output power and the DC input power of the component~\cite{Hansen}.
+The AC load, from every case study, is defined by a 24 hour curve who reflects the estimated use of all electrical loads from the house.
+Load information was collected during a presential survey performed in each house.
+
+\subsection{Automated Verification Methodology}
+In order to evaluate the automated tools when verifying stand-alone solar photovoltaic systems, we created a methodology where each tool will process the ANSI-C code with constraints %($C$) 
+and properties %($P$) 
+from the PV system that are provided by the user, and the tool will automatically verify if the PV system requirements are met.
+If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation.
+However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
+
+The methodology can be described as a three stage process.
 In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
 In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to critical month method~\cite{Pinho}.
-\begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{flowchart_verification5.png}
-\centering
-\caption{Flowchart of the proposed automated verification of PV systems.}
-\label{fig:flowchartgeneral}
-\end{figure}
+%%%The equations to check the PV sizing were not presented at this paper, however the standard from Engineering Manual was the reference~\cite{Pinho}.
 %
@@
 % (as reliability, performance, or safety)
-
 %
@@
 is it SAT?}
-In a nutshell, ESBMC will process the ANSI-C code with constraints %($C$) 
-and properties %($P$) 
-from the PV system that are provided by the user, and the tool will automatically verify if the PV system requirements are met.
-If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
-However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
 %, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
@@
 If there is no property violation, then the verification algorithm continues and
-The batteries are assumed to have SOC of 100\% (Line 1), i.e., the batteries are charged. That is important because the system is said ready to use when the batteries are charged.
-
+The batteries are assumed to have initial SOC of 80\% (Line 1).
+%%100% before, i.e., the batteries are charged.
+That is important because the system is said ready to use when the batteries are charged.
 %At both case studies, it was considered 21 years of historic data from Manaus. 
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE $SOC \leftarrow 100\%$ \\
-  \COMMENT {Starting with the PV generation time}
- \\ \textit{LOOP Process}
+  \STATE $SOC \leftarrow 80\%$ \\
+%  \COMMENT {Starting with the PV generation time}
+% \\ 
+ \textit{LOOP Process}
   \FOR {$h = 1$ to $Hours \, of \, PV \, generation$}
@@
   \\
-  \COMMENT {If-then-else sequence to imitate charge controller work}
+%  \COMMENT {If-then-else sequence to imitate charge controller work}
   \IF {($battery \, is \, empty$) AND ($PV \, is \, generating$)}
@@
   \\  
-    \COMMENT {autonomy verification during discharge period}
-  \\
+%    \COMMENT {autonomy verification during discharge period}
+%  \\
   \STATE assert NOT($Battery \, empty$)  
@@
  \end{algorithm}
-%There are two premises considering the algorithm: (1) is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation from 8:00 h to 16:00 h, but without to account the battery autonomy (just considering charge and discharge process based on solar irradiation, load and battery charge), but after 16:00h is started the verification for the next hours when there is not solar photovoltaic generation.
-The process goes on until to verify all the autonomy demanded from the batteries; (2) there is an array, declared at the beginning of the C code, that defines the power demand/consumption at each hour of the day (aka load curve).
-Those are the same data used during the sizing of the project and ensure to consider the total energy (per day) supplied to the house during the verification.
-%
-%If the verification founds a situation where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
-And this information can be used by the designer to improve the system.
-%if it was a project error or if it was a combination of variables from the nature that has a low probability to occur at the field, considering the intermittent characteristic of solar PV generation.
-
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-%
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-%
-%
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-%
-%
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-%
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-%
-%----------------------------------------------
+
 \section{Experimental Evaluation} 
 \label{sec:results}
-%----------------------------------------------
-%
-%\textcolor{red}{reorganise the results as follows: experimental objectives and setup; results; and threats to validity.}
-%
-%\textcolor{red}{https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf}
-%
-
 %------------------------------------------
@@
 %------------------------------------------
-
-We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with surge of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
-
-Note that the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 5 and 6 of Algorithm~\ref{alg:verification-algorithm}).
+We have performed five case studies to evaluate the tools: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with surge of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
+
+The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 5 and 6 of Algorithm~\ref{alg:verification-algorithm}).
 Another characteristic of Manaus, based on historical weather data %\cite{Temperature},
@@
 \begin{enumerate}
-\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
-\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
+\item[RQ1] \textbf{(soundness)} Does the automated verification provide correct results?
+\item[RQ2] \textbf{(performance)} How does the  tools compare each other?
 \end{enumerate}
-All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3}.
+
+It was used two different setups of hardware and different verification engines, combined with different Solvers.
+The aim was to evaluate different environments and possible user limitation in terms of main processor and RAM memory.
+All the experiments were performed without a predefined timeout.
+
+Mostly of experiments were conducted on an otherwise idle Intel octa core Xeon CPU E5-2640 with 2.4 GHz and 264 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
+It was called high-end setup and the verification engines demanded around 90G bytes of RAM (each process).
+
+In addition, it was considered a low-end setup, using specifically the incremental option of ESBMC verification engine, where the demand of memory is very low (2G Bytes of RAM).
+The experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 32 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
+
+Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{The command-line used to perform verification: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat~\cite{Kroening}\footnote{The command-line used to perform verification: \$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{The command-line used to perform verification: \$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.
+
 % enabled with the goal of reducing memory usage; 
-We have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}. %The experiments were performed without a predefined timeout.
-
-In order to evaluate the proposed verification method and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool.
+%The experiments were performed without a predefined timeout.
+Concerning the low-end configuration: ESBMC v5.1 was used with the SMT incremental mode\footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+
+In order to evaluate the verification methods and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool.
 %Every dweller, who owns a PV system, was interviewed to get information about his/her PV system during four months of use.
@@
 %
-%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
-%\begin{enumerate}
-%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
-%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
-%
-%The description of our experimental results can be broken down into two parts: 
-(a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel.
-This verification took approximately 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level.
-Our verification engine identified those flaws (for all four houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries.
-Our verification engine took approximately 409.3 hours to find this flaw in house 1; 611.2 hours for house 2; 615.8 hours for house 3, and 620.8 hours for house 4.
-These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a month is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}, further affirming RQ1; after the sun rises, the systems returns to normal condition operation.
-
-The same five case studies were evaluated by HOMER Pro.
-The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
-All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
-%
-Despite the divergence of results for the houses 1, 2, 3 and 4 w.r.t.
-our proposed approach, it is evident that the information collected from the dwellers indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
-House 5 presented flaws from both tools; however, only our approach indicated which design error was responsible for the flaw (number of PV panels), further answering RQ2.
-%
-%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
-Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions.
-The season has impact since the case studies are from the rain forest, where clouds are always present.
-As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
-%
-%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
-Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
-All the simulations took less than 5 seconds (each) to be performed.
-%
-%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
-That verification took 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
-The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
-The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
-The proposed tool took 409.3 hours to find this error at house 1.
-This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
-Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
-
-%At the terminal, the command used to perform the verification is:
-%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
-%
-%Where:
-%
-%\begin{itemize}
-%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
-%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
-%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
-%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
-There are other options, but this parameter is necessary because the complexity of the algorithms.
-The incremental SMT solving uses few RAM memory, compared with other SMT solving.
-%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
-The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
-%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
-%\end{itemize}
-%
-%\subsection{Experimental results}
-%\label{sec:results}
-%---------------------------------------------------
-\subsection{Threats to Validity}
-%---------------------------------------------------
-We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
-
-\textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
-A careful evaluation in a PV laboratory to validate the model could add more reliability to the results produced by our method.
-
-\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario, where a solar irradiance and ambient temperature can change in fractions of minutes.
-
-\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed if other places around the world could become case studies.
-
-%-------------------------------------
-\section{Conclusion and Future Work}
-\label{sec:Conclusions}
-%-------------------------------------
-We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
+The Table~\ref{tab1} summarize the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
+
+\begin{table}
+\centering
+\caption{Summary of the case-studies comparative and the automated tools.}\label{tab1}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\hline
+\multicolumn{5}{|c|}{Model Checker (SAT/UNSAT: time and message)}\\
+\hline
+Case &  \makecell{ESBMC \\(Boolector)} & \makecell{CBMC\\(MiniSat)} & UAutomizer & \makecell{ESBMC Incremental\\(Z3)}\\
+\hline
+\hline
+House 1 &  \makecell{7.44h \\(low SOC after 16:00h)} & \makecell{Inconclusive \\(during solver)} & XX & \makecell{409.3h \\ (low SOC after 16:00h)}\\
+\hline
+House 2 &  \makecell{5.74h \\(low SOC after 16:00h)} & \makecell{Inconclusive \\(during solver)} & XX & \makecell{611.2h \\ (low SOC after 16:00h)}\\
+\hline
+House 3 & \makecell{Inconclusive \\(during solver)} & \makecell{Inconclusive \\(during solver)} & XX & \makecell{615.8h \\ (low SOC after 16:00h)}\\
+\hline
+House 4 & \makecell{5.52h \\(low SOC after 16:00h)} & \makecell{Inconclusive \\(during solver)} & XX & \makecell{620.8h \\ (low SOC after 16:00h)}\\
+\hline
+House 5 & \makecell{0.55h \\(Sizing: number of panels)} & \makecell{Inconclusive \\(during solver)} & XX & \makecell{63.3h \\ (Sizing: number of panels)}\\
+\hline
+\hline
+\end{tabular}
+\end{table}
+
+\section{Conclusions and Future Work}
+We have described and evaluated different automated verification methods to check whether a given PV system meets its specification using software model checking techniques.
 We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W.
-Although this verification method takes longer than simulation methods, it is able to find specific conditions that lead to failures in a PV system previously validated by a commercial simulation tool.
+ESBMC had the better results, in both setups (high-end and low-end configurations).
+Although the verification method takes longer than simulation methods, it is able to find specific conditions that lead to failures in a PV system previously validated by a commercial simulation tool.
 In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail.
-%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
-As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems.
-We will also consider other types of renewable energy and even hybrid ones to allow our method to design and verify typical rural electrification.
-%
-%It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results.
-The proposed tool was successful in find sizing errors and to indicate in which conditions a PV system can fails.
-% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements. 
-%
-%Plus (need to think about it): verification in every-hour of a 48h cycle?, PV model math model can be improved, charge/discharge of batteries can be improved (is a simplified model), house's power consumption is not flat or constant, the dweller can buy more home appliances, synthesis need a data base of components, to test peak (surge) consumption (above the nominal), additional models for on-grid/off-grid farm, hybrid, and on-grid with batteries).
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-%\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-%\section{}
-%Appendix two text goes here.
-% use section* for acknowledgment
-\section*{Acknowledgments}
-To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to test real PV systems.
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-%\ifCLASSOPTIONcaptionsoff
-%  \newpage
-%\fi
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-% references section
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{trindadeThesis}{}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%
-%\begin{thebibliography}{1}
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%\end{thebibliography}
-%
-%%%%%%%%%%%%%% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-\begin{IEEEbiography}
-    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alessandro3por4_2}}]{Alessandro Trindade}
-received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
-Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
-Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the Amazonas State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation.
-His interest is in renewable energy, automated verification, and model checking.
-\end{IEEEbiography}
-%
-%\begin{IEEEbiographynophoto}{Alessandro Trindade}
-%received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
-Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
-Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation (Centre of Analysis, Research and Innovation Technology Foundation).
-His interest is in renewable energy, automated verification, and model checking.
-%\end{IEEEbiographynophoto}
-%
-% if you will not have a photo at all:
-\begin{IEEEbiography}
-    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lucas3por4}}]{Lucas Cordeiro}
-received his Ph.D.
-degree in Computer Science in 2011 from the University of Southampton, UK.
-Currently, he is a Senior Lecturer in the School of Computer Science at the University of Manchester, and leads the Systems and Software Verification laboratory.
-He is also a collaborator in the Postgraduate Program in Electrical Engineering and Informatics at the Federal University of Amazonas (UFAM), Brazil.
-Prior to joining the University of Manchester, he worked as a researcher at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for 4 years as software engineer at industry.
-His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.
-\end{IEEEbiography}
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-%\begin{IEEEbiographynophoto}{Jane Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-%\vfill
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-% that's all folks
+Future work will focus in other verification engines and different solvers, besides the improvement of the algorithm in order to obtain better performance.
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+\bibliographystyle{splncs04}
+\bibliography{trindadeThesis}
+%
+
 \end{document}
+
+%\subsection{Design and Simulation of Solar PV systems}
+%The design and validation of a PV system can be done by hand or with the aid of a software tool.
+In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
+%public domain and commercial software available for the PV market. 
+%According to \cite{Brooks}, t
+%%%%%%%%%%
+%
+%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
+%to complex financial analysis and project optimization.
+At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.

### 2019-01-18 code/codePVsystem_rev9cUAH1.c
code update

@@ -15,8 +15,7 @@
 //case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
 //case study at urban area of 915W of demand and 4.88 kWh of energy
 
-//Francisco's house 501W and 3.9kWh
-#ifdef HOUSE1 
+//Francisco's house 501W and 3.9kWh HOUSE1 
   #define Phouse 501
   #define Psurge 501
   #define Econsumption 3900
@@ -31,72 +30,6 @@
   #define NPS 3
   #define VC 24  //controller voltage
   #define Vsystem 24  //DCbus
-#elif HOUSE2
-  //Aldovar's house 253W and 3.6kWh
-  #define Phouse 253
-  #define Psurge 722
-  #define Econsumption 3600
-  #define PACref 700
-  #define MAXACref 1600
-  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
-  #define NBS 2
-  #define NBP 2
-  #define capacity 220
-  #define auton 48
-  #define NPP 1  
-  #define NPS 3
-  #define VC 24  //controller voltage
-  #define Vsystem 24  //DCbus
-#elif HOUSE3
-  //Sandriane's house 263W and 2.5kWh
-  #define Phouse 263
-  #define Psurge 732
-  #define Econsumption 2500
-  #define PACref 700
-  #define MAXACref 1600
-  #define loadcurve {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113}
-  #define NBS 2
-  #define NBP 2
-  #define capacity 220
-  #define auton 48
-  #define NPP 1  
-  #define NPS 3
-  #define VC 24  //controller voltage
-  #define Vsystem 24  //DCbus
-#elif HOUSE4
-  //Marilene's house 322W and 4.3 kWh
-  #define Phouse 322
-  #define Psurge 896
-  #define Econsumption 4300
-  #define PACref 700
-  #define MAXACref 1600
-  #define loadcurve {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207}
-  #define NBS 2
-  #define NBP 2
-  #define capacity 220
-  #define auton 48
-  #define NPP 1  
[…]

### 2019-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
paper update

@@
 %
+\usepackage{xcolor}
 \usepackage{graphicx}
@@
 %
-For numerous people around the world, a better life means getting access to basic needs such as food, health services, housing and clean water.
+%%%%%%%For numerous people around the world, a better life means getting access to basic needs such as food, health services, housing and clean water.
 None of these basic needs can be provided without energy.
@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-
 Progress has been made worldwide.
@@
 \subsection{Stand-alone Solar PV Systems}
-PV systems are classified into distinct types~\cite{Mohanty}.
+%%%%%%PV systems are classified into distinct types~\cite{Mohanty}.
 Specifically for remote rural areas of developing countries or places where the grid extension is not feasible, the most suitable configuration is the regulated stand-alone system with battery and AC load; this configuration is the focus of case-studies of this work.
-
+%%%%%%
 The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
-It identifies the PV generator, batteries, charge controller, inverter, and AC load.
+%It identifies the PV generator, batteries, charge controller, inverter, and AC load.
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
@@
 Related to the charge controller, it was used the 4-steps controller processes with MPPT (maximum power point tracking) to decide if the PV array must be disconnected from the system, or if the PV can be reconnected, or if the load is disconnected and when the load is reconnected~\cite{Hansen}.
-The inverter model is the simplest and is based on efficiency, i.e., the relation between the AC output power and the DC input power of the component~\cite{Hansen}.
+The inverter model is based on efficiency, i.e., the relation between the AC output power and the DC input power of the component~\cite{Hansen}.
 The AC load, from every case study, is defined by a 24 hour curve who reflects the estimated use of all electrical loads from the house.
@@
 Algorithm~\ref{alg:verification-algorithm} describes the pseudo-code used to perform the automated verification.
-%Line 1 indicates a function call that performs the size checking of the each component of the PV system.
-%: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
-%The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation of sizing check.
-The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints a counterexample indicating a property violation.
-If there is no property violation, then the verification algorithm continues and
 The batteries are assumed to have initial SOC of 80\% (Line 1).
-%%100% before, i.e., the batteries are charged.
-That is important because the system is said ready to use when the batteries are charged.
-%At both case studies, it was considered 21 years of historic data from Manaus. 
-%According with X and Y, t
 Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using non-deterministic variables from ESBMC to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range.
-%and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
-%there is PV generation only between 8:00 h and 16:00 h every day, 
-%with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day. 
-In order to reduce the computational effort of the algorithm,
-% caused by the state explosion inherent of the technique, 
-every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation).
+In order to reduce the computational effort of the algorithm, every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, but dependent on the sun and weather conditions; and (b) one that includes all the remaining day (without PV generation).
 Therefore, our approach depends on specific data about the solar irradiation levels to define the average amount of hours of PV generation.
@@
   %%\FOR {$Autonomy = 1$ to $auton$}
-
   \STATE $SOC \leftarrow SOC - ( 24 - Hours \, of \, PV \, generation)\,h\, discharge$
@@
 
+\textcolor{red}{shall we provide further details about the case studies?}
+
 \section{Experimental Evaluation} 
@@
 %------------------------------------------
-We have performed five case studies to evaluate the tools: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with surge of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
+We have performed five case studies to evaluate the tools, as described by Table~\ref{tab2}. 
+\begin{table}
+\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\hline
+Item & House 1 & House 2 & House 3 & House 4 & House 5\\
+\hline
+\hline
+PV Panels &  \multicolumn{4}{|c|}{3x 325W: in series} & 4x 325W: 2x series and 2x parallel \\
+\hline
+Batteries & \multicolumn{4}{|c|}{\makecell{4x220Ah: 2x series and 2x parallel\\ autonomy: 48h}} & \makecell{4x 120Ah batteries in series\\ autonomy: 6h}\\
+\hline
+Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150V/35A}\\
+\hline
+Inverter & \multicolumn{4}{|c|}{700W with surge of 1,600W} & 1,200W with surge of 1,600W\\
+\hline
+Power demand & 253W & 263W & 283W & 501W & 915W\\
+\hline
+GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
+\hline
+Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
+\hline
+\hline
+\end{tabular}
+\end{table}
 
-The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 5 and 6 of Algorithm~\ref{alg:verification-algorithm}).
+The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (Lines 5 and 6 of Algorithm~\ref{alg:verification-algorithm}).
 Another characteristic of Manaus, based on historical weather data %\cite{Temperature},
-\cite{Irradiance}, is related to the fact that only during 8 hours of the day is possible to have PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
+\cite{Irradiance}, is related to the fact that only during 8 hours of the day is possible to have PV generation, from 8:00h to 16:00h.
+% (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
 
@@
 Mostly of experiments were conducted on an otherwise idle Intel octa core Xeon CPU E5-2640 with 2.4 GHz and 264 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-It was called high-end setup and the verification engines demanded around 90G bytes of RAM (each process).
+It was called high-end setup and the verification engines demanded until 90G bytes of RAM.
 
-In addition, it was considered a low-end setup, using specifically the incremental option of ESBMC verification engine, where the demand of memory is very low (2G Bytes of RAM).
-The experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 32 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
+In addition, it was considered a low-end setup, using specifically the incremental option of ESBMC verification engine, where the demand of memory is low (2G Bytes of RAM).
+The experiments were conducted on an Intel Core i7-2600 (8-cores), with 3.4 GHz and 32 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
 
@@
 
+\textcolor{red}{What are the command-lines used for all tools? Versions? Solvers? Solvers versions?}
+
 %------------------------------------------
@@
 %
-The Table~\ref{tab1} summarize the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
+Table~\ref{tab1} summarize the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
+The time expressed at the Table answer the RQ2.
+Worth to mention that using simulation tool (HOMER Pro) in all case studies, the 1,200W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
+The simulation took less than five seconds to be performed in each case study.
 
@@
 \end{table}
+
+The engines ESBMC and ESBMC Incremental accused that the 1,200W system (House 5) has sizing error related to the right number of solar panels.
+Related to the 700W systems (Houses 1-4) the verification engines ESBMC and ESBMC incremental indicate that there is a situation of low state of charge from batteries that will cause the cut of the load, just after the 16:00h of the day, when the weather condition was not enough to charge the batteries.
+
+The CBMC tool, was not successful to produce results.
+It finished the verification of all cases, but the log file indicated that the Solver did not present SAT or UNSAT answer.
+We tried the MiniSAT and even the Boolector Solvers.
+
+Related to UAutomizer, ....
+
+The flaws from 700W systems were confirmed with the dwellers who own the systems by an interview process and from a local monitoring system with the Raspberry Pi controller: at least once a month is usual the system to turn off, normally in raining or clouds days, further affirming RQ1; related to the 1,200W system, we identified that, in fact, it does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer who showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house
 

### 2019-01-19 code/codePVsystem_rev9cUAH1_with_errorfun_2.c
UAutomizer update

@@ -1,0 +1,482 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+---------------------------------------------------------------------by Alessandro Trindade, JAN-2019 UAutomizer adaption */
+//without pow, without NaN and without comments at the end of /@assert() command
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+//case study at urban area of 915W of demand and 4.88 kWh of energy
+
+//Francisco's house 501W and 3.9kWh HOUSE1 
+  #define Phouse 501
+  #define Psurge 501
+  #define Econsumption 3900
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220
+  #define auton 48
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24  //controller voltage
+  #define Vsystem 24  //DCbus
+//requirements/restrictions
+
+#define bankcapacity (capacity*NBP)
+#define SOClimit 75
+#define SOCabsorption 95
+#define SOCfull 100
+#define Vbat 12
+#define Vbulk (14.40*NBS)
+#define Vfloat (13.20*NBS)
+#define nb 1
+
+//inverter data (outlet voltage, efficiency)
+#define VoutAC 110
+#define ni 0.93 
+#define VinDC 24 
+#define VAC 127
+
+//data sheet information from the PV model Canadian 325W CS6U-325P
[…]

### 2019-01-20 Tex/LaTeX2e Style File/Trindade_Cordeiro_IEEE_SE_rev0.tex
SE paper update

--- 2018-12-28 Tex/LaTeX2e Style File/Trindade_IEEE_TC_r0.tex
@@
 \IEEEcompsocthanksitem{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}}% <-this % stops a space
-\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support.}
-\thanks{Manuscript received November 23, 2018; revised XXXXX 11, 2019.}}
+\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017 and PROTI Pesquisa 2018), for the financial support.}
+\thanks{Manuscript received January 23, 2019; revised XXXXX 11, 2019.}}
 
@@
 % The paper headers
-\markboth{IEEE Transactions on Computers,~Vol.~14, No.~8, August~2015}%
-{Trindade \MakeLowercase{\textit{et al.}}: Automated Verification of Stand-Alone Solar Photovoltaic Systems}
+\markboth{IEEE Transactions on Software Engineering,~Vol.~XX, No.~YY, August~2019}%
+{Trindade and Cordeiro: Automated Verification of Stand-Alone Solar Photovoltaic Systems}
 % The only time the second header will appear is for the odd numbered pages
@@
 %This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
-This paper makes two original contributions.
+\textit{Novelty Statement:} This paper makes two original contributions.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
 Secondly
-Firstly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT), and that was never did before.
+Firstly, we propose an automated verification method that formally checks the design of a given PV system using model checking based on Satisfiability Module Theories (SMT), and that was never did before.
 Secondly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.
@@
 %------------------------------------------
-
 We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with surge of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
@@
 All experiments were conducted on an otherwise idle Intel octa core Xeon CPU E5-2640 with 2.4 GHz and 264 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning our verification engine, ESBMC v6.0.0 was used \footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 \phantom{}-boolector}.
+Concerning our verification engine, ESBMC v6.0.0 was used \footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}.
 % enabled with the goal of reducing memory usage; 
@@
 Fig.
-\ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software.
+\ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software, specifically to house 1.
 
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{homer.png}
+\includegraphics[width=0.5\textwidth]{homer.png}
 \centering
-\caption{Homer simulation screen.}
+\caption{HOMER simulation screen (evaluation 30-days version).}
 \label{fig:homerscreen}

### 2019-01-20 Tex/LaTeX2e Style File/cover-letter-SE.tex
SE paper update

--- 2018-11-23 Tex/LaTeX2e Style File/Cover-Letter.tex
@@
 \begin{flushleft}
-      Badrul H. Chowdhury,  Ph.D. \\
+	Nenad Medvidovic \\
 	Editor-in-Chief \\
-	University of North Carolina at Charlotte \\
-	IEEE Transactions on Sustainable Energy 
+	University of Southern California\\
+	Viterbi School of Engineering, Department of Computer Science \\
+	941 Bloom Walk, SAL 338, Los Angeles, CA 90089-0781 \\
+	IEEE Transactions on Software Engineering 
     \end{flushleft}
 
-\indent Dear Badrul
+\indent Dear Nenad
 \vi
 
-Please find enclosed our manuscript entitled as ``Automated Verification of Stand-alone Solar Photovoltaic Systems'' by Alessandro Trindade and Lucas Cordeiro which we would like to submit for publication in the journal of IEEE Transactions on Sustainable Energy.
+Please find enclosed our manuscript entitled as ``Automated Verification of Stand-alone Solar Photovoltaic Systems'' by Alessandro Trindade and Lucas Cordeiro which we would like to submit for publication in the journal of IEEE Transactions on Software Engineering.
 

### 2019-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
updated abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-Around 1 billion of people do not have electrical energy nowadays on Earth.
+Currently around 1 billion of people do not have electrical energy.
 Energy poverty alleviation has become an important political issue.
 Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries.
-Particular attention is given to use renewables and stand-alone solar photovoltaic systems.
-Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-The use of automated verification in electrical systems is a fresh subject with few issued literature.
-This paper do a state-of-art review about the use of automated verification on electrical systems and perform a comparative of tolls applied to five stand-alone solar photovoltaic systems.
-Information about the use of a commercial simulator and monitoring data from the deployed systems are used to validate the research.
-Data from experimental results shows that only some flaws can be detected by automated verification and that ESBMC verification engine obtain the best results, regardless using a high-end or low-end setup.
+Particular attention is given to use renewables and stand-alone solar photovoltaic (PV) systems.
+Validation tools are available to evaluate PV designs, but they are mainly based on simulations that do not cover all aspects of the design space.
+The use of automated verification in PV systems is a recent subject with a few initiatives.
+Here we review state-of-art automated verification techniques for electrical systems and perform their comparative evaluation considering five stand-alone PV systems.
+We employ a commercial simulator and data extracted from deployed PV systems to validate our research.
+Experimental results show that our suggested verification engine obtains promising results to detect flaws that other existing approaches are unable to reveal.
 
@@
 %
-%\begin{itemize}
-%\item In modeling, a model (normally mathematical) of the system is created; 
-%\item In specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, as reliability to performance for example.
-\item Normally is expressed in temporal logic form ($CTL$);
-%\item The model checking is the verification method itself. 
-%\end{itemize}
-%
-%%%%%
-%%%%%The model checking algorithm can be described as \cite{ClarkeHV18}:  (i) Given the model $M$ and a CTL (or LTL) formula $ \phi $ as input;  (ii) Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  and (iii) It returns \textit{YES} if $ \phi $ is \textit{TRUE}, or returns \textit{NO} if $ \phi $ is \textit{FALSE}.
-Specifically for the \textit{FALSE} verification result, the algorithm returns a \textit{counterexample} (i.e., a sequence of states that leads to a property violation), which is useful as diagnostic of the system to discover in which situation the model is violated; this is the most important advantage of the use of model checking~\cite{ClarkeHV18}.
-%%%%%
-%%%%%%%%%%%%%%%Fig.~\ref{fig:systemverif} shows a real PV system, and Fig.~\ref{fig:systemverif2} the conversion the system to be verified by a model checking procedure.
-% \textcolor{red}{Please try to adapt this figure to our context.
-How can it be applied to verify PV?}.
-%Fig.~\ref{fig:systemverif} shows the process to convert a real PV system to a model to be verified by a model checking procedure.
-% \textcolor{red}{Please try to adapt this figure to our context.
-How can it be applied to verify PV?}.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.5\textwidth]{system_original_blocks}
-%\centering
-%\caption{Real system verification (adapted from \cite{ClarkeHV18}).}
-%\label{fig:systemverif}
-%\end{figure}
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{system_model_blocks}
-%\centering
-%\caption{Model checking verification \cite{ClarkeHV18}.}
-%\label{fig:systemverif2}
-%\end{figure}
 %
@@
 
-\textcolor{red}{shall we provide further details about the case studies?}
-
 \section{Experimental Evaluation} 
@@
 
-\textcolor{red}{What are the command-lines used for all tools? Versions? Solvers? Solvers versions?}
-
+%\textcolor{red}{What are the command-lines used for all tools? Versions? Solvers? Solvers versions?}
 %------------------------------------------

### 2019-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
fixed references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-%
-%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-%%%%%In 2015, 193 Member States of the United Nations agreed as part of the Sustainable Development Goals (SDG) with a specific target to 'ensure access to affordable, reliable and modern energy for all by 2030' – universal access to electricity and clean cooking~\cite{IEAeao2017}.
-Therefore electricity has a important role, based on two main issues: %that are on the agenda of all current rulers and society in general, regardless of whether it is a developed, emerging or developing country:
-%%%%%the impact on the global climate change and poverty alleviation.
-%
-%%%%%Related to climate change, the 23rd session of the Conference of the Parties (COP23) to the United Nations Framework Convention on Climate Change (UNFCCC) in 2017 was the second session after the Paris Agreement, which aims to keep the maximum global average temperature rise as close as possible to 1.5 $^{o}$C.
-%During COP23, with respect to the future market development of renewable power and solar PV (photovoltaics) in particular, it was created an alliance of nations and states committed to moving the world from burning coal to cleaner power sources was a promising sign at COP23 \cite{Jager-Waldau}.
-%%%%%Decarbonization of our energy supply is an important component to achieve the targets, because 65.3\% of the worlds current CO\textsubscript{2} emissions (from energy supple) are due to burning fossil fuels according with 2016 data: 81.1\% of our total primary energy supply depended on burning fossil fuels, namely 27.1\% coal, 31.9\% oil and 22.1\% natural gas~\cite{IEAwes2018}.
-In terms of final energy consumption electricity only accounted for 18.6\%, but was responsible for 32\% of the total CO\textsubscript{2} emissions~\cite{IEAwes2018}.
-Photovoltaics (PV) is one of the key technology options for implementing the shift to a decarbonized energy supply, because it is abundant, cannot be monopolized  and can be deployed in a modular way almost everywhere on Earth.
-%
-%Related to poverty alleviation, 
-%
-%In reality, the biggest barrier to universal energy access is not the capacity to generate electricity, but rather the ability to get energy to those who need it most.
-The concept of energy poverty and access tends to focus on very small, incremental shifts in the delivery of energy to poor people.
-The total energy demand of these shifts constitutes only a small fraction of the ‘gap’ between electricity supply in much of Africa versus more industrialised countries, or the gap between the region’s current and projected electricity supply.
-https://policy-practice.oxfamamerica.org/static/media/files/FINAL_speakingpowertotruth_SH.pdf
-%
-%%%%%Poverty, in other hand, needs to be addressed through socio-economic development.
-Poverty %is conceptualized in material terms as not having access to adequate levels of food, water, clothing, shelter, sanitation, health care and education.
-This
-%%%%%can be translated into people having insufficient income. 
-%
-%%%%%%%For numerous people around the world, a better life means getting access to basic needs such as food, health services, housing and clean water.
-None of these basic needs can be provided without energy.
-Energy is one of the most essential inputs into sustaining people‘s livelihoods.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide.
-The number of people without electricity access fell below 1 billion for the first time in 2017~\cite{IEAweo2018}.
-To provide universal electricity for all, decentralized systems, led by solar PV in off-grid and mini-grid systems, will be the least-cost solution for three-quarters of the additional connections needed, but that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion for the first time in 2017~\cite{IEAweo2018}.
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the least-cost solution for three-quarters of the additional connections needed; \textcolor{red}{This sentence is unclear...
+what is the ``role to play''?} however, that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.
 
-%With worldwide over 400GW cumulative installed photovoltaic electricity generation capacity installed by the end of 2017, photovoltaics still is a small contributor to the electricity supply with a little of 2\%, but its importance for our future energy mix is now acknowledged and with the fastest growth (32\% whem compared with 2016 numbers)~\cite{Jager-Waldau}.
-%
-In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
-However, those tools are based on running experiments in simulation models.
-Simulation %has the advantage of being cheap (if compared to test in real systems) and can be
-is employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+In order to simulate or evaluate a PV system, there are various specialized tools available in the market, e.g.
+RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.
+PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+However, those tools are based on simulation models, which are employed before the system design is concluded; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
-Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.
-Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
+Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective and faster verification in the design process of PV systems~\cite{ClarkeHV18}.
+In this study, we review verification tools for PV systems and also present five case studies, where different model checking tools are compared in terms of performance and reliability when validating stand-alone solar PV systems.
 
-In this study, an updated review about the use of verification tools in electrical systems is performed, and is presented five case studies, where different model checking tools are compared in terms of performance and reliability when validating stand-alone solar PV systems.
-In order to perform the comparation and case studies, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used.
-The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
-The model checking tools report in which conditions a system does not meet the user requirements.
-A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
-The case studies are not theoretical and were deployed in 2018, with feedback information collected from monitoring systems and through interview with the dwellers.
-%The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
+In order to compare different model checkers, we developed a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter and electrical load.
+Design requirements as battery autonomy and power demand in addition to weather conditions, as solar irradiance and ambient temperature, are translated as part of that model and automatically checked by the employed verifiers, which report under which conditions a system does not meet the user requirements.
+
+The main contribution of this approach is that it aids to detect design flaws in PV systems, thus considerably improving system reliability~\cite{Akram2018}; our case studies are empirical and they were deployed in 2018 with feedback information collected from monitoring systems via micro-controllers and by means of interviews with dwellers.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{State-of-art in automated verification of Electrical systems}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 This section summarizes, in a chronological way, the research done by previous studies related to the subject of this research.

### 2019-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion for the first time in 2017~\cite{IEAweo2018}.
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the least-cost solution for three-quarters of the additional connections needed; \textcolor{red}{This sentence is unclear...
+Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; \textcolor{red}{This sentence is unclear...
 what is the ``role to play''?} however, that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.
@@
 
-Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective and faster verification in the design process of PV systems~\cite{ClarkeHV18}.
+Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of PV systems~\cite{ClarkeHV18}.
 In this study, we review verification tools for PV systems and also present five case studies, where different model checking tools are compared in terms of performance and reliability when validating stand-alone solar PV systems.
+In order to compare different model checkers, we developed a mathematical model of each component of a stand-alone PV system, including solar panel, charge controller, batteries, inverter and electrical load.
+Design requirements as battery autonomy and power demand in addition to weather conditions, as solar irradiance and ambient temperature, are translated as part of that model and automatically checked by the employed model checkers.
 
-In order to compare different model checkers, we developed a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter and electrical load.
-Design requirements as battery autonomy and power demand in addition to weather conditions, as solar irradiance and ambient temperature, are translated as part of that model and automatically checked by the employed verifiers, which report under which conditions a system does not meet the user requirements.
-
-The main contribution of this approach is that it aids to detect design flaws in PV systems, thus considerably improving system reliability~\cite{Akram2018}; our case studies are empirical and they were deployed in 2018 with feedback information collected from monitoring systems via micro-controllers and by means of interviews with dwellers.
+The main contribution of this approach is that it automatically aids to detect design flaws in PV systems by reporting under which conditions a system does not meet the user requirements, thus considerably improving system's reliability~\cite{Akram2018}.
+Our case studies are empirical; they were deployed in 2018 with feedback information collected from monitoring systems via micro-controllers and by means of interviews with dwellers with the goal of validating our results.
 

### 2019-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 % \renewcommand\UrlFont{\color{blue}\rmfamily}
+
+\renewcommand{\baselinestretch}{0.97}
 
@@
 \email{lucas.cordeiro@manchester.ac.uk}}
-% \and ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-%\email{\{abc,lncs\}@uni-heidelberg.de}}
-%
 \maketitle              % typeset the header of the contribution
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{State-of-art in automated verification of Electrical systems}
+\section{State-of-art in Automated Verification of Electrical Systems}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-This section summarizes, in a chronological way, the research done by previous studies related to the subject of this research.
-
-The conversion of traditional power grid into a smart grid, a fundamental example of a cyber-physical system, raises a number of issues that require novel methods and applications.
-In 2012, it was considered a specific Chinese Smart Grid implementation as a case study and address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-It was employed the stochastic model checking approach and present a modelling and analysis study using PRISM model checker.
-The focus was how Cyber-physical systems integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes.
-In this context, it was applied automated verification of certain quantitative properties of the system.
+The conversion of traditional power grid into a smart grid, a fundamental example of a Cyber-Physical System (CPS), raises a number of issues that requires novel methods and applications.
+In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}.
+The focus of this study was on how CPs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system \textcolor{red}{for example?}.
 %, with no interest in power generation or even solar PV systems.
 
-%In 2014, there were a research showing that power systems model information exchange and the simulation of user defined models is a challenge issue for the transmission system operator.
-The reason: the use of different simulation software with specific data format and models strongly coupled to the simulation software numerical routines.
-The researchers proposed the use of Open Source software (Modelica, JAVA and Python) for simulation and modelling as a solution to decouple these models.
-The work described the design of a simulation tool following the Free/Libre Open Source Software philosophy to simulate equation-based models and implement a standard data format for model information exchange~\cite{Gomez2014}.
-The aim was the use of Modelica to define standards and industry models, besides the interest of components in modules.
-This work did not reached the automated verification, it is just simulation, however created the base to future work of formal methods on electrical systems.
-%
-In 2015, it was showed that related to power system protection schemes, the approach of using Monte-Carlo simulation and manual interpretation of results had the limitation of the incomplete coverage of all possible operating conditions due to the time complexity of simulation~\cite{Sengupta2015}.
-It was proposed an automated simulation-based verification technique to verify the correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
-The initial focus were relay operations and test-case generation to ensure early detection of design errors.
+In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
+The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
+The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
 %The study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
 
-Other work issued in 2015 was a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with Statistical Model Checking (SMC) for Cyber-Physical Systems (CPSs) in terms of Non Functional Properties (NFP) such as time, energy, etc~\cite{Cheng2015}.
-To demonstrate the capability of Modana framework, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
-The focus is in smart buildings and HVAC (Heating, ventilation, and air conditioning) systems.
+Other related studies from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking for CPSs in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
+In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
 %The research did no deal with solar PV systems.
 
-Back in 2017, it was suggested the use of formal methods to verify and certifiably control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
-It was shown that formal techniques can provide compelling solutions not only when safety-critical goals are the target, but also to tackle verification and synthesis problems on populations of such devices.
-This work argued that alternative solutions based on classical analytical techniques or on approximate computations are prone to errors with global repercussions.
-Two different areas were targeted: thermal loads and electricity-generating devices interacting over a smart energy network or over a local power grid.
-The researcher discussed the aggregation of large populations of thermostatically-controlled loads and of photovoltaic panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
-The focus is in controlling the behavior of the components, verifying the smart grid, dealing with a 'system of systems' and with 'internet of things'.
-The author uses approximate model checking of stochastic and hybrid models.
+In 2017, Abate suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
+He has shown that formal techniques can provide compelling solutions not only when safety-critical goals are the target, but also to tackle verification and synthesis problems on populations of such devices.
+This study also argued that alternative solutions based on classical analytical techniques or on approximate computations are prone to errors with global repercussions.
+Two different areas were identified: thermal loads and electricity-generating devices interacting over a smart energy network or over a local power grid.
+Abate discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The focus is on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
+The author also uses approximate model checking of stochastic and hybrid models.
 % Therefore, the focus is not in electricity generation or even the components of a stand-alone solar PV system.
 
-In 2018, is was proposed a methodology for the verification of the Cyber Physical Energy Systems (CPES), with the methodology applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-The approach relied on representing the unpredictable behavior of the environment in order to cover all feasible possible scenarios.
-Processed by JModelica, the simulation results covered the system's complete dynamic behavior.
-It was evident at this work the time consuming issue, with almost three days of computer effort to verify the design space of one hour from PV panels behavior.
+In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
 %The work did not include the other components of a stand-alone solar PV system.
 
-Another work issued in 2018 was the approach to modeling smart grid components using a formal specification. It was used a state-based formal specification language namely Z %(pronounced as `Zed') 
-and it was demonstrated the application of Z on four smart grid components~\cite{Akram2018}.
-The presented formal specification can be considered as first steps towards modeling of smart grid using a Software Engineering formalism.
-The starting point of this work it was that a smart home can be considered as an integrated system consists of various objects and system, that communicates and interact  with  each  other.
-The approach is base in Petri nets and from the premise that modeling of the smart home leads to clear understanding the overall behavior of the smart grid.
+Another work from 2018 was the approach to modeling smart grid components using a formal specification.
+The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
+The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods.
+The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
+This approach is base on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Automated Verification Using Model Checking}
 \label{sec:AutomatedVerification}
-%--------------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %It is necessary to keep in mind that 

### 2019-01-22 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-In 2017, Abate suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
+\textcolor{red}{We have to reduce this paragraph:} In 2017, Abate suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
 He has shown that formal techniques can provide compelling solutions not only when safety-critical goals are the target, but also to tackle verification and synthesis problems on populations of such devices.
@@
 The author also uses approximate model checking of stochastic and hybrid models.
-% Therefore, the focus is not in electricity generation or even the components of a stand-alone solar PV system.
 
@@
 
-%It is necessary to keep in mind that 
-Validation is the process of determining whether a design meets the user requirements, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}.
-If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate the verification process, thus resulting in a process known as \textit{formal verification}.
-Verification may form part of a validation process.
-%, but in general, validation cannot be formalized because it relates a system design to intent.  
-While simulation and testing explore some of the possible behaviors and scenarios of the system, leaving open the question of whether the unexplored trajectories may contain a flaw, formal verification conducts an exhaustive exploration of all possible behaviors.
-Thus, when a design is pronounced correct by a formal verification method, it implies that all behaviors have been explored, and the questions of adequate coverage or a missed behavior becomes irrelevant \cite{Clarke2012}.
-%Simulation may also be used for validation, but it is more problematic for verification.
-%In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-Testing can also be used for validation, however it is not feasible to cover all the aspects of the design space, and some times the real system must be used instead of a computing model.
- %
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
+Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
+Here we evaluate three state-of-the-art model checkers to formally verifying PV desgins w.r.t.
+user requirements.
 
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking \cite{Clarke2012}.
-%%%%%%%%Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}; one successful method in this domain is model checking \cite{Clarke2012}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{CBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% 
-%Model checking is an automatic verification technique, as defined by \cite{ClarkeHV18}.
-Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
-%
-The process of model checking can be split into three main components: modeling, specification, and verification method.
-In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in a temporal logic form as Computational Tree Logic (CTL) or Linear Temporal Logic (LTL).
-%
-%
-However, there is a main disadvantage of model checking: the state explosion problem.
-In order to tackle this problem, many different techniques were developed in the last decades.
-One of the first major advances was symbolic model checking with binary decision diagrams (BDDs).
-In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice.
-% Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes \textcolor{red}{add citation here}.
-A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level of refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
-%
-Another promising approach to overcome state explosion problem is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
-BMC is a method that checks a model up to a given path in the path length.
-BMC algorithms traverse a finite state machine for a fixed number of steps, $ k $, and checks whether a property violation occurs with this bound.
-It uses Boolean Satisfiability (SAT) or Satisfiability Module Theories (SMT) solvers to check the generated formula from BMC.
+The C Bounded Model Checker (CBMC) is considering the best-known verifier to check ANSI-C code~\cite{Kroening}. 
+CBMC checks the violation of assertions in C programs, or proves safety of the assertions under a completeness threshold.
+CBMC implements a bit-precise translation of an input C program, annotated with assertions and with loops unrolled 
+up to a given depth, into a logical formula. If the formula is satisfiable, then an execution leading to a violated assertion exists~\cite{Kroening}.
 
-SAT problem is a problem of determining whether there are certain conditions or interpretations that satisfy a given Boolean expression \cite{ClarkeHV18}. 
-SMT decides the satisfiability of a fragment of first-order formulae using a combination of different background theories and thus generalizes SAT by supporting uninterpreted functions, linear and non-linear arithmetic, bit-vectors, tuples, arrays, and other decidable first-order theories~\cite{ClarkeHV18}.
-The SAT or SMT solvers search the model for conditions (value of variables) that make the formula satisfiable.
-If a SAT or SMT solver finds a substitution for the formula/function then the substitute induces a counterexample and is said to be \textit{satisfiable}, i.e., it is satisfiable \textit{iff} the verified system contains errors.
-%
-%CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}. 
-%
-%\textcolor{red}{ESBMC does not use CBMC as its main frontend.
-Please take a look at this paper and cite it: https://ssvlab.github.io/lucasccordeiro/papers/ase2018.pdf.
-I would also suggest to remove the above sentence.}
-%
-\subsection{CBMC}
-The C Bounded Model Checker (CBMC) is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}.
-CBMC demonstrates the violation of assertions in C programs, or proves safety of the assertions under a given bound.
-CBMC implements a bit-precise translation of an input C program, annotated
-with assertions and with loops unrolled to a given depth, into a formula. If the
-formula is satisfiable, then an execution leading to a violated assertion exists~\cite{Kroening}.
+CBMC's verification flow can be summarized in four stages: 
+(i) Front-end that can read, perform parse and type checker of C code; 
+(ii) Intermediate Representation (IR): CBMC uses IR to convert all non-linear control flow, 
+such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded 
+\textit{goto} statements, thus aiming to reduce the verification effort; 
+(iii) Middle end: CBMC performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
+which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
+(iv) Back-end: With support to SAT and SMT solvers. Conversely, if the formula is unsatisfiable, no assertion can be violated within the given unwinding bounds.
 
-CBMC's verification flow can be summarized in four stages: (i) Front-end that can read, perform parse and type checker of the C/C++ code; (ii) Intermediate Representation.
-CBMC uses  intermediate representation, converting all non-linear control flow, such as if or switch statements, loops and jumps, into equivalent guarded goto statements; aiming to reduce the verification effort; (iii) Middle end.
-CBMC performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end.
-With support to SAT and SMT solvers.
-Conversely, if the formula is unsatisfiable, no assertion can be violated within the given unwinding bounds.
-%--------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{ESBMC}
-%--------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
@@
 ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C/C++ code, where the formal specification of the system to be verified is first handled; (ii) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the model simplification, thereby aiming to reduce the verification effort; and finally (iii) the SMT solving stage, where all the constraints and properties of the system to be verified are encoded into SMT and checked for satisfiability.
-%
-%%The efficient SMT based model checker, is a software verification tool for C and C++ code bases. 
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Fig. \ref{fig:esbmcarch} shows the tool architecture. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{ESBMCarch4}
-%\centering
-%\caption{ESBMC architecture (adapted from \cite{esbmc2018}).}
-%\label{fig:esbmcarch}
-%\end{figure}
-%ESBMC uses clang as front-end, a state-of-the-art compiler suite for C/C++/ObjectiveC/ObjectiveC++ widely used in industry \cite{esbmc2018}.
-% and generate an Abstract Syntax Tree (AST).
-%%%%%One legacy CBMC-based front-end that supports both C and C++ and a new clang-based front-end that currently only supports C.
-The data types and bit vectors are created in the front-end when parsing the code.
-%%%%%%%Regardless of the chosen front-end, 
-%The output is an AST (tree representation of the abstract syntactic structure of source code written in a programming language) that will be used by the GOTO converter to generate a GOTO program, which has simplified control flow and is suitable for bounded unwinding.
-The next step is the symbolic execution, when the GOTO program is executed (unrolling loops up to the bound $ k $) and converted to Static Single Assignments (SSA) form.
-SSA form enables the simplification of algorithms and reduction of computational complexity.
-%%%%%%%%%, where each variable is a target of exactly one assignment statement in the program text.
-%The feature called k-induction at Fig. \ref{fig:esbmcarch} allows the model checker to find a property violation or even to prove (partial) correctness without fully unwinding loops. 
-%%
-%%%%%%%During the symbolic execution, ESBMC aggressively tries to simplify the program \cite{Ramalho}; it propagates all constants and solves any assertions that can be statically determined.
-This is an important step for the verification, since ESBMC can fully verify programs without calling a solver, if the inputs are deterministic.
-That characteristic is useful at this work to perform the sizing check of the PV system project.
-%Following, the SSA expressions are then encoded using the chosen SMT solver supported by ESBMC. At this paper, it was used the Z3 solver \cite{DeMoura}.
-%%%%%: Boolector (default) \cite{Brummayer}, Z3 \cite{DeMoura}, MathSAT \cite{Cimatti}, Yices \cite{Dutertre} and CVC4 \cite{Barrett}. 
-%
-%Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied. 
 If the SMT formula is shown to be satisfiable (SAT), a counterexample is presented; otherwise, the formula is unsatisfiable (UNSAT), i.e., there are no errors up to the given unwinding bound.
@@
 This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows us to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with all the design space state.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Ultimate Automizer}
-%Ultimate Automizer is an automatic software verification tool for C programs.
-This tool is the first implementation of trace abstraction, which is an automata-theoretic approach to software verification.
-The implemented algorithm uses nested interpolants in its interprocedural program analysis.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties.
@@
 CEGAR or Counterexample-Guides Abstraction Refinement is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check, and refinement~\cite{CEGAR}.
-%(i) precision, for the level of abstraction; (ii) feasibility check, deciding if there is a concrete error path; and (iii) a refinement procedure, which takes as input as infeasible error path and extracts a precision that suffices to instruct the exploration algorithm do not explore the same path again later~\cite{CEGAR}.
 
@@
 The difference to a classical CEGAR-based predicate abstraction is that Automizer have to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.
-%
-%----------------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Automated verification of Stand-alone Solar PV Systems }
 \label{sec:Methodology}
-%----------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Stand-alone Solar PV Systems}
-%%%%%%PV systems are classified into distinct types~\cite{Mohanty}.
-Specifically for remote rural areas of developing countries or places where the grid extension is not feasible, the most suitable configuration is the regulated stand-alone system with battery and AC load; this configuration is the focus of case-studies of this work.
-%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.

### 2019-01-22 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The C Bounded Model Checker (CBMC) is considering the best-known verifier to check ANSI-C code~\cite{Kroening}. 
-CBMC checks the violation of assertions in C programs, or proves safety of the assertions under a completeness threshold.
-CBMC implements a bit-precise translation of an input C program, annotated with assertions and with loops unrolled 
-up to a given depth, into a logical formula. If the formula is satisfiable, then an execution leading to a violated assertion exists~\cite{Kroening}.
-
-CBMC's verification flow can be summarized in four stages: 
-(i) Front-end that can read, perform parse and type checker of C code; 
-(ii) Intermediate Representation (IR): CBMC uses IR to convert all non-linear control flow, 
-such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded 
-\textit{goto} statements, thus aiming to reduce the verification effort; 
-(iii) Middle end: CBMC performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
-which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
-(iv) Back-end: With support to SAT and SMT solvers. Conversely, if the formula is unsatisfiable, no assertion can be violated within the given unwinding bounds.
+The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
+CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
+If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
+CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
 
@@
 
-ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-%The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
-ESBMC comes as an alternative to overcome limitations of the system modeling, especially considering that the system complexity is increasing and SMT has richer theories than SAT to represent models. 
-%
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C/C++ code, where the formal specification of the system to be verified is first handled; (ii) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the model simplification, thereby aiming to reduce the verification effort; and finally (iii) the SMT solving stage, where all the constraints and properties of the system to be verified are encoded into SMT and checked for satisfiability.
-If the SMT formula is shown to be satisfiable (SAT), a counterexample is presented; otherwise, the formula is unsatisfiable (UNSAT), i.e., there are no errors up to the given unwinding bound.
-
-% incremental ESBMC text here
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}.
-An assertion, in SMT solvers, is a constraint over the variables in a formula that must hold if the formula is satisfiable~\cite{Morse2015}.
-New assertions can be added to or old assertions removed from this stack, depending on the evaluated value of variables.
-This enables ESBMC, and the respective solver, to learn from previous checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows us to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with all the design space state.
+ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
 
@@
 Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties.
-The tool implements an automata-based instance of the CEGAR scheme.
-CEGAR or Counterexample-Guides Abstraction Refinement is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check, and refinement~\cite{CEGAR}.
-
-In each iteration, Automizer pick a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible.
-If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace’s infeasibility.
-The predicates are a sequence of interpolants since each predicate “interpolates” between the set of reachable states and the set of states from which we cannot reach the error.
+The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement  (CEGAR) scheme.
+CEGAR is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check and refinement~\cite{CEGAR}.
+In each iteration, Automizer picks a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible.
+If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility.
+The predicates are a sequence of interpolants since each predicate Äú``interpolates''Äù between a set of reachable states and a set of states from which it cannot reach the error.
 In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed.
 It is used automata to represent sets of traces.
-The difference to a classical CEGAR-based predicate abstraction is that Automizer have to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.
+The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Experimental Evaluation} 
 \label{sec:results}
-%------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Description of the Case Studies}
-%------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 We have performed five case studies to evaluate the tools, as described by Table~\ref{tab2}. 
@@
 
-%------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Objectives and Setup}
-%------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Our experimental evaluation aims to answer two research questions:
@@
 
-Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{The command-line used to perform verification: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat~\cite{Kroening}\footnote{The command-line used to perform verification: \$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{The command-line used to perform verification: \$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.
+Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat~\cite{Kroening}\footnote{\$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{\$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.
 
@@
 %The experiments were performed without a predefined timeout.
-Concerning the low-end configuration: ESBMC v5.1 was used with the SMT incremental mode\footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+Concerning the low-end configuration: ESBMC v5.1 was used with the SMT incremental mode\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
 
@@
 %\textcolor{red}{What are the command-lines used for all tools? Versions? Solvers? Solvers versions?}
-%------------------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Results}
 \label{sec:results_indeed}
-%------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions and Future Work}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 We have described and evaluated different automated verification methods to check whether a given PV system meets its specification using software model checking techniques.

### 2019-02-05 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed Section 4.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
-For night hours or rainy days, we need to hold batteries, where power can be stored and used.
+For night hours or rainy days, we need to hold batteries where power can be stored and used.
 The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}.
@@
 \end{figure}
-A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves).
-However, the present work will rely on the simplified model of 1-diode.
-It was demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-The model uses formulas from different references~\cite{Hansen}, \cite{Saloux}, and \cite{Ross}.
+A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves) \textcolor{red}{add citations here}.
+However, this study will rely on the simplified model of 1-diode since prior work previously demonstrated that this model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}; the employed model uses formulas from different sources available in the literature~\cite{Hansen,Ross,Saloux}.
 
-To model the batteries, it was used the most common based on lead-acid~\cite{Copetti}.
+In order to model the batteries, it was used the most common one based on lead-acid~\cite{Copetti}.
 Related to the charge controller, it was used the 4-steps controller processes with MPPT (maximum power point tracking) to decide if the PV array must be disconnected from the system, or if the PV can be reconnected, or if the load is disconnected and when the load is reconnected~\cite{Hansen}.
 The inverter model is based on efficiency, i.e., the relation between the AC output power and the DC input power of the component~\cite{Hansen}.
-The AC load, from every case study, is defined by a 24 hour curve who reflects the estimated use of all electrical loads from the house.
+The AC load, from every case study, is defined by a 24 hour curve, which reflects the estimated use of all electrical loads from the house.
 Load information was collected during a presential survey performed in each house.

### 2019-02-05 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed Section 4.2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\subsection{Automated Verification Methodology}
-In order to evaluate the automated tools when verifying stand-alone solar photovoltaic systems, we created a methodology where each tool will process the ANSI-C code with constraints %($C$) 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Automated Verification for PV Systems}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To evaluate the automated tools when verifying stand-alone solar photovoltaic systems, we created a methodology where each tool will process the ANSI-C code with constraints %($C$) 
 and properties %($P$) 
@@
 %
-In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
+In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by the verifiers based on maximum and minimum values from the site, where the PV system will be deployed.
 %As a consequence, all the formulae of the employed mathematical models will also be updated. 
@@
 The batteries are assumed to have initial SOC of 80\% (Line 1).
-Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using non-deterministic variables from ESBMC to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range.
+Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using non-deterministic variables in order to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range.
 In order to reduce the computational effort of the algorithm, every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, but dependent on the sun and weather conditions; and (b) one that includes all the remaining day (without PV generation).

### 2019-02-05 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-We have performed five case studies to evaluate the tools, as described by Table~\ref{tab2}. 
+We have performed five case studies to evaluate the tools, as described in Table~\ref{tab2}. 
 \begin{table}
@@
 \cite{Irradiance}, is related to the fact that only during 8 hours of the day is possible to have PV generation, from 8:00h to 16:00h.
-% (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
+\textcolor{red}{why?} % (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
 
@@
 \item[RQ1] \textbf{(soundness)} Does the automated verification provide correct results?
-\item[RQ2] \textbf{(performance)} How does the  tools compare each other?
+\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other?
 \end{enumerate}
 
-It was used two different setups of hardware and different verification engines, combined with different Solvers.
+We have used two different setups of hardware and different verification engines, combined with different solvers.
 The aim was to evaluate different environments and possible user limitation in terms of main processor and RAM memory.
@@
 
-Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat~\cite{Kroening}\footnote{\$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{\$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.
+Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat \textcolor{red}{which version of minisat?}~\cite{Kroening}\footnote{\$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{\$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.
 
@@
 
-In order to evaluate the verification methods and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool.
+In order to evaluate the verification methods and its performance, we have considered five case studies and also compared their performance to the HOMER Pro tool.
 %Every dweller, who owns a PV system, was interviewed to get information about his/her PV system during four months of use.
@@
 %
-Table~\ref{tab1} summarize the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
+Table~\ref{tab1} summarizes the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
 The time expressed at the Table answer the RQ2.

### 2019-02-05 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Table~\ref{tab1} summarizes the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
-The time expressed at the Table answer the RQ2.
-Worth to mention that using simulation tool (HOMER Pro) in all case studies, the 1,200W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
-The simulation took less than five seconds to be performed in each case study.
+The times reported in Table~\ref{tab1} answer RQ2.
+Note that if we used HOMER Pro in all case studies, the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
+The simulation took less than five seconds to be performed on each case study.
 
@@
 
-The engines ESBMC and ESBMC Incremental accused that the 1,200W system (House 5) has sizing error related to the right number of solar panels.
-Related to the 700W systems (Houses 1-4) the verification engines ESBMC and ESBMC incremental indicate that there is a situation of low state of charge from batteries that will cause the cut of the load, just after the 16:00h of the day, when the weather condition was not enough to charge the batteries.
+ESBMC and ESBMC Incremental indicated that the $1,200$W system (House 5) has sizing error related to the \textcolor{red}{right?} number of solar panels.
+Related to the 700W systems (Houses 1-4), ESBMC and ESBMC incremental indicated that there is a situation of low state of charge from batteries that will cause the cut of the load, just after the 16:00h of the day, when the weather condition was not enough to charge the batteries.
 
-The CBMC tool, was not successful to produce results.
-It finished the verification of all cases, but the log file indicated that the Solver did not present SAT or UNSAT answer.
-We tried the MiniSAT and even the Boolector Solvers.
+CBMC, was not successful to produce any verification result; it finished the verification of all cases, but the log file indicated that the solver did not present SAT or UNSAT answer.
+We tried the MiniSAT and even the Boolector solvers.
 
@@
 
-The flaws from 700W systems were confirmed with the dwellers who own the systems by an interview process and from a local monitoring system with the Raspberry Pi controller: at least once a month is usual the system to turn off, normally in raining or clouds days, further affirming RQ1; related to the 1,200W system, we identified that, in fact, it does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer who showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house
+The flaws from 700W systems were confirmed with the dwellers who own the systems by an interview process and from a local monitoring system with the Raspberry Pi controller: at least once a month is usual the system to turn off, normally in rainy or clouds days, further affirming RQ1; related to the $1,200$W system, we identified that, in fact, it does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double-checked with the monitoring system from the charge controller from the manufacturer who showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house
 

### 2019-02-05 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
reviewed Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail.
-Future work will focus in other verification engines and different solvers, besides the improvement of the algorithm in order to obtain better performance.
+Future work will focus on other verification engines and different solvers, besides the improvement of the algorithm to achieve a reasonable performance.
 %

### 2019-02-14 Tex/elsevier/trindade_ren_and_sust_rev0.tex
code update to CBMC

--- 2019-01-20 Tex/LaTeX2e Style File/Trindade_Cordeiro_IEEE_SE_rev0.tex
@@
-%% bare_jrnl.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[10pt,journal,compsoc]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-%\else
-  % normal IEEE
-%  \usepackage{cite}
-%\fi
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-\usepackage{graphicx}
+\documentclass[review]{elsarticle}
+
+\usepackage{lineno,hyperref}
+\modulolinenumbers[5]
+
+\journal{Renewable \& Sustainable Energy Reviews}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+%\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%packages to makecell, algorithm, not inclueded with Elsevier
+\usepackage{makecell}
+\usepackage{algorithm,algorithmic}
+%\algsetup{linenosize=\small}
 \graphicspath{ {./images/} }
-%
-%\ifCLASSINFOpdf
-  %\usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-%  \DeclareGraphicsExtensions{.png}
-%\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-%\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
 \usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-\usepackage{algorithm,algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-%Alessandro input: makecell package to permite line break inside tables
-\usepackage{makecell}
-\usepackage{xcolor}
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-%\renewcommand{\baselinestretch}{0.975}
 
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-%\title{Building a framework to perform automated verification of solar photovoltaic off-grid systems}
+
+\begin{frontmatter}
+
+%\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
 \title{Automated Verification of Stand-alone Solar Photovoltaic Systems}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-
-\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
-\IEEEcompsocitemizethanks{
-\IEEEcompsocthanksitem{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
-\IEEEcompsocthanksitem{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}}% <-this % stops a space
-\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017 and PROTI Pesquisa 2018), for the financial support.}
-\thanks{Manuscript received January 23, 2019; revised XXXXX 11, 2019.}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-\markboth{IEEE Transactions on Software Engineering,~Vol.~XX, No.~YY, August~2019}%
-{Trindade and Cordeiro: Automated Verification of Stand-Alone Solar Photovoltaic Systems}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\IEEEtitleabstractindextext{%
+%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
+
+%% Group authors per affiliation:
+%\author{Alessandro Trindade\fnref{myfootnote}, Lucas Cordeiro}
+%\address{Radarweg 29, Amsterdam}
+
+%% or include affiliations in footnotes:
+\author[mymainaddress]{Alessandro Trindade\corref{mycorrespondingauthor}}
+\cortext[mycorrespondingauthor]{Corresponding author}
+\ead{alessandrotrindade@ufam.edu.br}
+%\ead[url]{www.elsevier.com}
+
+\author[mysecondaryaddress]{Lucas Cordeiro}
+
+\address[mymainaddress]{Federal University of Amazonas, Av. Rodrigo Octávio, 6200, Coroado I, 69077-000 Manaus-AM-Brazil}
+\address[mysecondaryaddress]{University of Manchester, School of Computer Science, Kilburn Building, Manchester M13 9PL}
+
 \begin{abstract}
@@
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Formal verification, model checking, photovoltaic power systems, power system modeling, solar power generation.
-\end{IEEEkeywords}}
-
-% make the title area
-\maketitle
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\IEEEraisesectionheading{\section{Introduction}}
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps.
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by the IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-\IEEEPARstart{T}{here} are presently 1.3 billion people with no access to electricity worldwide~\cite{Coelho}. 
+\begin{keyword}
+Formal verification \sep model checking \sep photovoltaic power systems \sep power system modeling \sep solar power generation
+%\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
+%\MSC[2010] 00-01\sep  99-00
+\end{keyword}
+
+\end{frontmatter}
+
+\linenumbers
+
+\section{Introduction}
+There are presently 1.3 billion people with no access to electricity worldwide~\cite{Coelho}. 
 %The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
@@
 %This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
-\textit{Novelty Statement:} This paper makes two original contributions.
+This paper makes two original contributions.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
 Secondly
-Firstly, we propose an automated verification method that formally checks the design of a given PV system using model checking based on Satisfiability Module Theories (SMT), and that was never did before.
+Firstly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT), and that was never did before.
 Secondly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.
@@
 \begin{figure}[h]
-\includegraphics[width=0.48\textwidth]{blockdiagramPVS2}
+\includegraphics[width=0.70\textwidth]{blockdiagramPVS2}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.20\textwidth]{equivckt1D}
+\includegraphics[width=0.50\textwidth]{equivckt1D}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{system_original_blocks}
+\includegraphics[width=0.80\textwidth]{system_original_blocks}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{system_model_blocks}
+\includegraphics[width=0.75\textwidth]{system_model_blocks}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{flowchart_verification5.png}
+\includegraphics[width=0.6\textwidth]{flowchart_verification5.png}
 \centering
@@
  \begin{algorithmic}[1]
+ \begin{small}
+
  \renewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
   \STATE $SOC \leftarrow 100\%$ \\
-  \COMMENT {Starting with the PV generation time}
- \\ \textit{LOOP Process}
+%  \COMMENT {Starting with the PV generation time}
+% \\ 
+\textit{LOOP Process}
   \FOR {$h = 1$ to $Hours \, of \, PV \, generation$}
@@
  \RETURN $(\,)$ 
+  \end{small}
  \end{algorithmic} 
@@
 %------------------------------------------
+
 We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with surge of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
@@
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{loadcurve.png}
+\includegraphics[width=0.65\textwidth]{loadcurve.png}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{homer.png}
+\includegraphics[width=0.65\textwidth]{homer.png}
 \centering
-\caption{HOMER simulation screen (evaluation 30-days version).}
+\caption{Homer simulation screen.}
 \label{fig:homerscreen}
@@
 To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to use real PV systems.
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-%\ifCLASSOPTIONcaptionsoff
-%  \newpage
-%\fi
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-% references section
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{trindadeThesis}{}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%
-%\begin{thebibliography}{1}
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%\end{thebibliography}
-%
-%%%%%%%%%%%%%% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-\begin{IEEEbiography}
-    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alessandro3por4_2}}]{Alessandro Trindade}
-received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
-Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
-Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the Amazonas State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation.
-His interest is in renewable energy, automated verification, and model checking.
-\end{IEEEbiography}
-%
-%\begin{IEEEbiographynophoto}{Alessandro Trindade}
-%received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
-Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
-Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation (Centre of Analysis, Research and Innovation Technology Foundation).
-His interest is in renewable energy, automated verification, and model checking.
-%\end{IEEEbiographynophoto}
-%
-% if you will not have a photo at all:
-\begin{IEEEbiography}
-    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lucas3por4}}]{Lucas Cordeiro}
-received his Ph.D.
-degree in Computer Science in 2011 from the University of Southampton, UK.
-Currently, he is a Senior Lecturer in the School of Computer Science at the University of Manchester, and leads the Systems and Software Verification laboratory.
-He is also a collaborator in the Postgraduate Program in Electrical Engineering and Informatics at the Federal University of Amazonas (UFAM), Brazil.
-Prior to joining the University of Manchester, he worked as a researcher at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for 4 years as software engineer at industry.
-His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.
-\end{IEEEbiography}
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-%\begin{IEEEbiographynophoto}{Jane Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-%\vfill
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-% that's all folks
+
+\section*{References}
+
+%\bibliography{mybibfile}
+\bibliography{trindadeThesis}
+
 \end{document}

### 2019-02-14 code/codePVsystem_rev9cCBMC.c

@@ -1,0 +1,444 @@
+/* --------------------------------------------------------------------------------------------------------
+  Here is the code that describes the whole PV system, focused at the charge controller and decides if the 
+  load can be met by the battery, PV panel or if is desconnected (system-off)
+---------------------------------------------------------------------by Alessandro Trindade, JAN 2019 cbmc adapted */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <assert.h>
+
+//IMPORTANT: to declare precision here to LOG of natural base and EXP
+#define precisionLN 0.0001 //0.0000000001
+#define precisionEXP 0.0001 //0.00000001 
+
+//case studies concerning the houses at Nova Esperanca (Star Energy Project): 510, 253, 263, and 283W. But with the same PV system (700W)
+//case study at urban area of 915W of demand and 4.88 kWh of energy
+
+//Francisco's house 501W and 3.9kWh
+#ifdef HOUSE1 
+  #define Phouse 501
+  #define Psurge 501
+  #define Econsumption 3900
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220
+  #define auton 16
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24  //controller voltage
+  #define Vsystem 24  //DCbus
+#elif HOUSE2
+  //Aldovar's house 253W and 3.6kWh
+  #define Phouse 253
+  #define Psurge 722
+  #define Econsumption 3600
+  #define PACref 700
+  #define MAXACref 1600
+  #define loadcurve {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136}
+  #define NBS 2
+  #define NBP 2
+  #define capacity 220
+  #define auton 16
+  #define NPP 1  
+  #define NPS 3
+  #define VC 24  //controller voltage
+  #define Vsystem 24  //DCbus
+#elif HOUSE3
[…]

### 2019-04-01 code/PVcode_rev2_house1.c
new code

@@ -1,0 +1,489 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev2 - April 2019
+ Description : New PV code (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// int nb = 1;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// int nb = 1;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
[…]

### 2019-04-01 code/PVcode_rev2_house2.c

@@ -2,7 +2,7 @@
  ============================================================================
  Name        : PVcode.c
  Author      : Alessandro
- Version     : rev2 - March 2019
+ Version     : rev2 - April 2019
  Description : New PV code (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
  //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
  ============================================================================*/
@@ -11,23 +11,58 @@
 //HOUSE1 
 // int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
 // int Phouse = 501, Psurge = 501, Econsumption = 3900;
-// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, auton = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// int nb = 1;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
 //HOUSE2 
 // int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
 // int Phouse = 253, Psurge = 722, Econsumption = 3600;
-// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, auton = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
[…]

### 2019-04-01 code/PVcode_rev2_house3.c

@@ -1,0 +1,489 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev2 - April 2019
+ Description : New PV code (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// int nb = 1;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// int nb = 1;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
[…]

### 2019-04-01 code/PVcode_rev2_house4.c

@@ -1,0 +1,489 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev2 - April 2019
+ Description : New PV code (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// int nb = 1;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// int nb = 1;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
[…]

### 2019-04-01 code/PVcode_rev2_house5.c

@@ -1,0 +1,489 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev2 - April 2019
+ Description : New PV code (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// int nb = 1;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// int nb = 1;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
[…]

### 2019-04-01 code/PVcode_rev2_old.c

@@ -1,0 +1,473 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev2 - March 2019
+ Description : New PV code (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, auton = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, auton = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, auton = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, auton = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+//HOUSE5 
[…]

### 2019-04-03 code/PVcode_rev2_house3.c
new code

@@ -112,7 +112,7 @@ float Parray, Iarray, Varray;
 double precisionLN = 0.0001;
 double precisionEXP = 0.0001;
 float Vdc,Idc, Idcmin, PinDCmin;
-int SOC = 100; //battery is charged when starts the verification
+float SOC = 100; //battery is charged when starts the verification
 
 
 /* start: C compiler */
@@ -156,8 +156,8 @@ int findEndPVGeneration(void){
 }
 
 void dischargeBattery(int hday){
-	int demand, drainedCurrent;
-	float tempf;
+	int demand;
+	float drainedCurrent, tempf;
 	//defining minimum values to met the house requirements, considering demand, output voltage of VoutAC from inverter
 	//at the inverter:
 	demand = loadcurve[hday];
@@ -165,7 +165,7 @@ void dischargeBattery(int hday){
 	//at the charge controller output (Vdc is 12*NBS and Idc must be greater than PinDC/Vdc)
 	Idcmin = PinDCmin / (Vbat*NBS);
 
-	drainedCurrent = demand / VoutAC;
+	drainedCurrent = (float)demand / (float)VoutAC;
 
 	Vdc=Vbat*NBS;
 	Idc=Idcmin;
@@ -173,7 +173,7 @@ void dischargeBattery(int hday){
 	tempf = 100*drainedCurrent*1/bankcapacity;
 		__VERIFIER_assume(tempf>=0 && tempf<=100);
 		__VERIFIER_assume(SOC>=0 && SOC<=100);
-	SOC = SOC - (int)tempf;
+	SOC = SOC - tempf;
 		if ( !(SOC>=SOClimit && SOC<=100)) { __VERIFIER_error(); }
 
 }
@@ -253,7 +253,7 @@ void PVgeneration (int, int);
 //function that generates the MPPT values (Varray and Iarray) from the PV panel,
 // considering values of solar irradiance(G) and ambient temperature
 void PVgeneration (int Gf, int AMBtemperaturef){
-	float Iphref, T, Tk, VT, a, Io, Iph, I, V, Vmax, Imax, Pmax;
+	float Iphref, T, Tk, VT, a, Io, Iph, I=0, V=0, Vmax=0, Imax=0, Pmax=0;
 	float kbq, qkb;
 	Iphref = Iscref; //mathematical approximation from the model
 	//set up of parameters

### 2019-04-03 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text and code

--- 2019-02-14 Tex/elsevier/trindade_ren_and_sust_rev0.tex
@@
 \section{Introduction}
-There are presently 1.3 billion people with no access to electricity worldwide~\cite{Coelho}. 
+There are presently 1 billion people with no access to electricity worldwide~\cite{Coelho}. 
 %The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
@@
 \label{eq:bat_Vd}
-V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \\ \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T),
+V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T),
 \end{multline}
@@
 \label{eq:Vcbat}
-V_{c} = [2+0.16SOC]+ \\ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
+V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
 \end{multline}
@@
 %------------------------------------------
-\subsection{Results}
+\subsection{Results and Discussion}
 \label{sec:results_indeed}
@@
 \section*{Acknowledgments}
-To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to use real PV systems.
-
-\section*{References}
+The authors would like to thank Coventry University for the availability of the case studies (real PV systems) to validate the tool and to support the mobility of one researcher to UK.
+
+\section*{Funding}
+This work was supported by Newton Fund [grant number 261881580] with the mobility of one researcher to UK; FAPEAM - Amazonas State Foundation for Research Support [grants from call 009/2017 and PROTI Pesquisa 2018], for the financial support related to the Virtual Machine rent (December 2018 to January 2019), for the DCTIEX II scholarship (November 2018), and for support the mobility of the researcher; and FAS - Sustainable Amazonas Foundation for the PhD scholarship (from November 2017 to March 2019).
+
+%\section*{References}
 

### 2019-04-04 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text and code

@@
 With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
+In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals.
 Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
 Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-Automated verification using model checking has proven to be an effective technique to program verification.
+Automated verification using model checking has proven to be an effective technique to any kind of program verification.
 This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
 Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected by our automated verification method.
+Different verification tools were evaluated as well.
+Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
 \end{abstract}
@@
 \section{Introduction}
-There are presently 1 billion people with no access to electricity worldwide~\cite{Coelho}. 
+Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
+The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
+Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
+Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities.
+
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
+
 %The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
@@
 Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
+However, this growth is not driven by isolated systems.
 
@@
 Using the maximum power point current (cf.
-~\eqref{eq:Imfinal}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor is determined by ~\eqref{eq:a}:
+~\eqref{eq:Imfinal}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor~\cite{Saloux} is determined by ~\eqref{eq:a}:
 \begin{equation}
@@
 
-The PV generator model is now completely determined. It requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
+The PV generator model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers in data-sheets or manuals.
 %
@@
 However, in this study, in order to simplify, the term used is controller.
-%The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-%MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power.
+The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power.
 Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
@@
 The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
+
 To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \textunderscore off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}.
@@
 %Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
+%
+%
+%--------------------------------------------------
+\section{Verification of the PV Project Sizing}
+%--------------------------------------------------
+In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a.
+sizing check).
+%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.
+
+Therefore this is a additional feature included at this paper.
+The sizing check will be performed, as proposed at the methodology, and the tool will indicate if there is an error of sizing before to perform the automated verification of the system.
+This stage ensures that the system meets the standard project steps related to the critical design month~\cite{Pinho}.
+%
+Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
+\begin{equation}
+\label{eq:Ecorrected}
+E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
+\end{equation}
+
+The total minimum number of needed solar panels ($N_{TPmin}$) is computed by ~\eqref{eq:NTPmin} and the check is performed using ~\eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from ~\eqref{eq:NTPmin}.
+\begin{equation}
+\label{eq:NTPmin}
+N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
+\end{equation}
+
+\begin{equation}
+\label{eq:NTP}
+N_{TP} \geq N_{TPmin}.
+\end{equation}
+
+Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.
+With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}), $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
+\begin{equation}
+\label{eq:NPSmin}
+N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}.
+\end{equation}
+
+\begin{equation}
+\label{eq:NPPmin}
+N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}.
+\end{equation}
+
+\begin{equation}
+\label{eq:NPS}
+N_{PS} \geq N_{PSmin}.
+\end{equation}
+
+\begin{equation}
+\label{eq:NPP}
+N_{PP} \geq N_{PPmin}.
+\end{equation}
+
+Related to the batteries, firstly must be defined the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
+\begin{equation}
+\label{eq:Cbank}
+C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}.
+\end{equation}
+%
+\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
+the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
+%
+Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}.
+Additionally, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
+\begin{equation}
+\label{eq:Nbtotal}
+N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}.
+\end{equation}
+
+\begin{equation}
+\label{eq:batcheck}
+\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total.
+\end{equation}
+
+Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem}: 
+\begin{equation}
+\label{eq:vcvsystem}
+V_{c} = V_{system}.
+\end{equation}
+
+Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
+%
+\begin{equation}
+\label{eq:iscamb}
+I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right]. 
+\end{equation}
+
+The controller must meet the maximum current from the PV array given by \eqref{eq:icmin} and \eqref{eq:icicmin}.
+\begin{equation}
+\label{eq:icmin}
+I_{c,min} = I_{sc,amb} \times N_{PP}.
+\end{equation}
+
+\begin{equation}
+\label{eq:icicmin}
+I_{c} \geq I_{c,min}.
+\end{equation}
+
+The sizing project check of the inverter is carried out by means of three equations.
+Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
+Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
+Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
+%
+\begin{equation}
+\label{eq:vindc} 
+V_{in}DC = V_{system}.
+\end{equation}
+%
+\begin{equation}
+\label{eq:voutac} 
+V_{out}AC = V_{AC}.
+\end{equation}
+%
+\begin{equation}
+\label{eq:invcheck} 
+\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
+\end{equation}
+
+Worth to mention that the charge controller, the battery, and the inverter have a nominal efficiency presented at data sheets, and those numbers are very close to 100\%.
+However, based on empirical data, those efficiencies must be corrected, according to the loading of each component.
+If field or essay data is not available, considering that the proposed tools is aimed to be used prior the deployment of the PV system at the field, it is recommended (at least) to correct the battery efficiency ($\eta_{b}$) to 85\%.
 %
@@
 %-------------------------------------
-\section{Conclusion and Future Work}
+\section{Conclusions and Future Work}
 \label{sec:Conclusions}

### 2019-04-06 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
new text

@@
 Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; \textcolor{red}{This sentence is unclear...
-what is the ``role to play''?} however, that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
 
@@
 The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}.
-The focus of this study was on how CPs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system \textcolor{red}{for example?}.
+The focus of this study was on how CPs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system, as 	probability	of	node	failure	in	the	long run, impact	of	repair	service	on	the	failure	risk, and expected energy consumption.
 %, with no interest in power generation or even solar PV systems.
@@
 
-\textcolor{red}{We have to reduce this paragraph:} In 2017, Abate suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
-He has shown that formal techniques can provide compelling solutions not only when safety-critical goals are the target, but also to tackle verification and synthesis problems on populations of such devices.
-This study also argued that alternative solutions based on classical analytical techniques or on approximate computations are prone to errors with global repercussions.
-Two different areas were identified: thermal loads and electricity-generating devices interacting over a smart energy network or over a local power grid.
-Abate discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
-The focus is on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
-The author also uses approximate model checking of stochastic and hybrid models.
+In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
+The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
+The author used approximate model checking of stochastic and hybrid models.
 
@@
 Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
-Here we evaluate three state-of-the-art model checkers to formally verifying PV desgins w.r.t.
+Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t.
 user requirements.
@@
 If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility.
-The predicates are a sequence of interpolants since each predicate Äú``interpolates''Äù between a set of reachable states and a set of states from which it cannot reach the error.
+The predicates are a sequence of interpolants since each predicate ?????
+``interpolates'' ???
+between a set of reachable states and a set of states from which it cannot reach the error.
 In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed.
@@
 \end{figure}
-A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves) \textcolor{red}{add citations here}.
+A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves)~\cite{Hansen}, \cite{Ross}, \cite{Saloux}.
 However, this study will rely on the simplified model of 1-diode since prior work previously demonstrated that this model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}; the employed model uses formulas from different sources available in the literature~\cite{Hansen,Ross,Saloux}.
@@
 
-Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat \textcolor{red}{which version of minisat?}~\cite{Kroening}\footnote{\$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{\$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.
+Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat 2.2.1~\cite{Kroening}\footnote{\$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{\$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.
 
@@
 
-ESBMC and ESBMC Incremental indicated that the $1,200$W system (House 5) has sizing error related to the \textcolor{red}{right?} number of solar panels.
+ESBMC and ESBMC Incremental indicated that the $1,200$W system (House 5) has sizing error related to the right number of solar panels.
 Related to the 700W systems (Houses 1-4), ESBMC and ESBMC incremental indicated that there is a situation of low state of charge from batteries that will cause the cut of the load, just after the 16:00h of the day, when the weather condition was not enough to charge the batteries.

### 2019-04-06 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text

@@
 Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Different verification tools were evaluated as well.
+Different verification tools were evaluated as well, in order to compare performance and soundness.
 Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
@@
 Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
-Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities.
+Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
 
@@
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
+The implementation of the proposed tool is carried out by means of an algorithm written in language C, that is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
+%three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
 %, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
@@
 %This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
-This paper makes two original contributions.
+This paper makes three original contributions.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
 Secondly
-Firstly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT), and that was never did before.
-Secondly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.
+Firstly, we propose an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system.
+Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies.
+Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation.
 
@@
 Section~\ref{sec:AutomatedVerification} presents the automated verification technique.
+Section~\ref{sec:sizingcheck} shows how to perform the sizing of a stand-alone PV system.
 The methodology is presented in section~\ref{sec:Methodology}.
@@
 
-\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
+\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
 
@@
 %--------------------------------------------------
-\section{Verification of the PV Project Sizing}
+\subsection{Availability of Stand-alone PV Systems}
+%--------------------------------------------------
+Each stand-alone PV system, like any other power systems, has a specific level of availability.
+This reliability level impacts various issues, as system performance, production, feasibility, and investment.
+The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
+The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
+
+The system availability definition depends on how critical the load application is.
+For critical loads, 99\% is considered acceptable.
+While in a ordinary house electrical load, 95\% is considered acceptable.
+As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system.
+An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
+
+With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong.
+It is important to evaluate how critical the load application is and the horizon of evaluation.
+However this analysis can be useful, for example, to improve the sized battery autonomy.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Automated Verification Using Model Checking}
+\label{sec:AutomatedVerification}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
+Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
+Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t.
+user requirements.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{CBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
+CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
+If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
+CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{ESBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{CPAchecker}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Configurable program analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
+The CPA formalism provides an interface for the definition of program analyses; consequently, the tool CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
+The comparison of different approaches in the same experimental setting is intended to be easy and the experimental results is expected to be more meaningful~\cite{Beyer2011}.
+Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consist of control-flow locations and control-flow edges.
+The CPA framework provides interfaces to SMT solvers and interpolation procedures, such that the CPA operators can be written in a concise and convenient way~\cite{Beyer2011}.
+Currently CPachecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+The CPA algorithm performs the reachability analysis, and operates on an object of the abstract data type CPA, i.e., the algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
+For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
+In software verification, its usual to take a considerable amount of effort to convert a verification idea into actual experimental results — and CPAchecker aim to accelerate this process~\cite{Beyer2011}.
+%
+%--------------------------------------------------
+\section{Stand-alone PV System Sizing and Verification}
+\label{sec:sizingcheck}
 %--------------------------------------------------
@@
 Therefore this is a additional feature included at this paper.
-The sizing check will be performed, as proposed at the methodology, and the tool will indicate if there is an error of sizing before to perform the automated verification of the system.
-This stage ensures that the system meets the standard project steps related to the critical design month~\cite{Pinho}.
+The sizing check will be performed by the proposed tool, and it will indicate if there is an error of sizing before to perform the automated verification of the system.
+This stage ensures that the system meets the standard project steps related to worst monthly average solar energy~\cite{Pinho}.
 %
@@
 
+Following, it is necessary to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, as defined by~\eqref{eq:Ep}.
+
+\begin{equation}
+\label{eq:Ep}
+E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
+\end{equation}
+
+\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV systems will be deployed, the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
+
 The total minimum number of needed solar panels ($N_{TPmin}$) is computed by ~\eqref{eq:NTPmin} and the check is performed using ~\eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from ~\eqref{eq:NTPmin}.
@@
 Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.
-With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}), $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
+With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}).
+Where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
+%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
+
 \begin{equation}
 \label{eq:NPSmin}
-N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}.
+\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}}\leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}}.
 \end{equation}
@@
 \label{eq:NPPmin}
-N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}.
+N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}}.
 \end{equation}
@@
 \noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
-the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
+$ V_{system} $ is the DC voltage of the bus, and the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
 %
@@
 \label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}.
+N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
 \end{equation}
@@
 
-Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem}: 
+Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage: 
 \begin{equation}
@@
 \label{eq:iscamb}
-I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right]. 
+I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
 \end{equation}
@@
 Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
+Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
 %
@@
 However, based on empirical data, those efficiencies must be corrected, according to the loading of each component.
-If field or essay data is not available, considering that the proposed tools is aimed to be used prior the deployment of the PV system at the field, it is recommended (at least) to correct the battery efficiency ($\eta_{b}$) to 85\%.
-%
-%--------------------------------------------------
-\section{Automated Verification Using Model Checking}
-\label{sec:AutomatedVerification}
-%--------------------------------------------------
-%It is necessary to keep in mind that 
-Validation is the process of determining whether a design meets the user requirements, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}.
-If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate the verification process, thus resulting in a process known as \textit{formal verification}.
-Verification may form part of a validation process.
-%, but in general, validation cannot be formalized because it relates a system design to intent.  
-While simulation and testing explore some of the possible behaviors and scenarios of the system, leaving open the question of whether the unexplored trajectories may contain a flaw, formal verification conducts an exhaustive exploration of all possible behaviors.
-Thus, when a design is pronounced correct by a formal verification method, it implies that all behaviors have been explored, and the questions of adequate coverage or a missed behavior becomes irrelevant \cite{Clarke2012}.
-%Simulation may also be used for validation, but it is more problematic for verification.
-%In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-Testing can also be used for validation, however it is not feasible to cover all the aspects of the design space, and some times the real system must be used instead of a computing model.
- %
-
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking \cite{Clarke2012}.
-%%%%%%%%Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}; one successful method in this domain is model checking \cite{Clarke2012}.
-
-% 
-%Model checking is an automatic verification technique, as defined by \cite{ClarkeHV18}.
-Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
-%
-The process of model checking can be split into three main components: modeling, specification, and verification method.
-In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in a temporal logic form as Computational Tree Logic (CTL) or Linear Temporal Logic (LTL).
-%
-%\begin{itemize}
-%\item In modeling, a model (normally mathematical) of the system is created; 
-%\item In specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, as reliability to performance for example.
-\item Normally is expressed in temporal logic form ($CTL$);
-%\item The model checking is the verification method itself. 
-%\end{itemize}
-%
-The model checking algorithm can be described as \cite{ClarkeHV18}:  
-%
-\begin{itemize}
-\item Given the model $M$ and a CTL (or LTL) formula $ \phi $ as input;  
-\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
-\item It returns \textit{YES} if $ \phi $ is \textit{TRUE}, or returns \textit{NO} if $ \phi $ is \textit{FALSE}.  
-\end{itemize}
-Specifically for the \textit{FALSE} verification result, the algorithm returns a \textit{counterexample} (i.e., a sequence of states that leads to a property violation), which is useful as diagnostic of the system to discover in which situation the model is violated; this is the most important advantage of the use of model checking~\cite{ClarkeHV18}.
-%Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
-%
-%The model checking problem can be defined as \cite{ClarkeHV18}: 
-%
-%\begin{itemize}
-%\item Let $M$ be a Kripke structure (i.e., state transition graph);
-%\item $f$ be the specification in temporal logic (a formula);
-%\item Find all states $s$ of $M$ such that $M , s \models f$
-%\end{itemize}
-%
-%Fig. \ref{fig:modelcheckstruc} shows the structure of a 
-%In a typical model checking system, a preprocessor extracts a state transition graph from a system (program or circuit).
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{modelcheckstruc}
-%\centering
-%\caption{Model Checker structure (Source: \cite{ClarkeHV18})}
-%\label{fig:modelcheckstruc}
-%\end{figure}
-%
-%Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study. 
-%
-Fig.~\ref{fig:systemverif} shows a real PV system, and Fig.~\ref{fig:systemverif2} the conversion the system to be verified by a model checking procedure.
-% \textcolor{red}{Please try to adapt this figure to our context.
-How can it be applied to verify PV?}.
-%Fig.~\ref{fig:systemverif} shows the process to convert a real PV system to a model to be verified by a model checking procedure.
-% \textcolor{red}{Please try to adapt this figure to our context.
-How can it be applied to verify PV?}.
-
-\begin{figure}[h]
-\includegraphics[width=0.80\textwidth]{system_original_blocks}
-\centering
-\caption{Real system verification (adapted from \cite{ClarkeHV18}).}
-\label{fig:systemverif}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.75\textwidth]{system_model_blocks}
-\centering
-\caption{Model checking verification \cite{ClarkeHV18}.}
-\label{fig:systemverif2}
-\end{figure}
-
-However, there is a main disadvantage of model checking: the state explosion problem.
-In order to tackle this problem, many different techniques were developed in the last decades.
-One of the first major advances was symbolic model checking with binary decision diagrams (BDDs).
-In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice.
-% Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes \textcolor{red}{add citation here}.
-A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level of refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}.
-%
-Another promising approach to overcome state explosion problem is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.
-BMC is a method that checks a model up to a given path in the path length.
-BMC algorithms traverse a finite state machine for a fixed number of steps, $ k $, and checks whether a property violation occurs with this bound.
-It uses Boolean Satisfiability (SAT) or Satisfiability Module Theories (SMT) solvers to check the generated formula from BMC.
-
-SAT problem is a problem of determining whether there are certain conditions or interpretations that satisfy a given Boolean expression \cite{ClarkeHV18}. 
-SMT decides the satisfiability of a fragment of first-order formulae using a combination of different background theories and thus generalizes SAT by supporting uninterpreted functions, linear and non-linear arithmetic, bit-vectors, tuples, arrays, and other decidable first-order theories~\cite{ClarkeHV18}.
-The SAT or SMT solvers search the model for conditions (value of variables) that make the formula satisfiable.
-If a SAT or SMT solver finds a substitution for the formula/function then the substitute induces a counterexample and is said to be \textit{satisfiable}, i.e., it is satisfiable \textit{iff} the verified system contains errors.
-%
-%CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}. 
-%
-%\textcolor{red}{ESBMC does not use CBMC as its main frontend.
-Please take a look at this paper and cite it: https://ssvlab.github.io/lucasccordeiro/papers/ase2018.pdf.
-I would also suggest to remove the above sentence.}
-%
-ESBMC is one of the most representatives bounded model checkers for embedded C/C++ software based on SMT solvers~\cite{esbmc2018}. %, which can use CBMC as front-end.
-%The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
-ESBMC comes as an alternative to overcome limitations of the system modeling, especially considering that the system complexity is increasing and SMT has richer theories than SAT to represent models.
-
-%--------------------------------------
-\subsection{ESBMC}
-%--------------------------------------
-ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-%
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C/C++ code, where the formal specification of the system to be verified is first handled; (ii) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the model simplification, thereby aiming to reduce the verification effort; and finally (iii) the SMT solving stage, where all the constraints and properties of the system to be verified are encoded into SMT and checked for satisfiability.
-%
-%%The efficient SMT based model checker, is a software verification tool for C and C++ code bases. 
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Fig. \ref{fig:esbmcarch} shows the tool architecture. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{ESBMCarch4}
-%\centering
-%\caption{ESBMC architecture (adapted from \cite{esbmc2018}).}
-%\label{fig:esbmcarch}
-%\end{figure}
-%ESBMC uses clang as front-end, a state-of-the-art compiler suite for C/C++/ObjectiveC/ObjectiveC++ widely used in industry \cite{esbmc2018}.
-% and generate an Abstract Syntax Tree (AST).
-%%%%%One legacy CBMC-based front-end that supports both C and C++ and a new clang-based front-end that currently only supports C.
-The data types and bit vectors are created in the front-end when parsing the code.
-%%%%%%%Regardless of the chosen front-end, 
-%The output is an AST (tree representation of the abstract syntactic structure of source code written in a programming language) that will be used by the GOTO converter to generate a GOTO program, which has simplified control flow and is suitable for bounded unwinding.
-The next step is the symbolic execution, when the GOTO program is executed (unrolling loops up to the bound $ k $) and converted to Static Single Assignments (SSA) form.
-SSA form enables the simplification of algorithms and reduction of computational complexity.
-%%%%%%%%%, where each variable is a target of exactly one assignment statement in the program text.
-%The feature called k-induction at Fig. \ref{fig:esbmcarch} allows the model checker to find a property violation or even to prove (partial) correctness without fully unwinding loops. 
-%%
-%%%%%%%During the symbolic execution, ESBMC aggressively tries to simplify the program \cite{Ramalho}; it propagates all constants and solves any assertions that can be statically determined.
-This is an important step for the verification, since ESBMC can fully verify programs without calling a solver, if the inputs are deterministic.
-That characteristic is useful at this work to perform the sizing check of the PV system project.
-%Following, the SSA expressions are then encoded using the chosen SMT solver supported by ESBMC. At this paper, it was used the Z3 solver \cite{DeMoura}.
-%%%%%: Boolector (default) \cite{Brummayer}, Z3 \cite{DeMoura}, MathSAT \cite{Cimatti}, Yices \cite{Dutertre} and CVC4 \cite{Barrett}. 
-%
-%Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied. 
-If the SMT formula is shown to be satisfiable (SAT), a counterexample is presented; otherwise, the formula is unsatisfiable (UNSAT), i.e., there are no errors up to the given unwinding bound.
-
-% incremental ESBMC text here
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}.
-An assertion, in SMT solvers, is a constraint over the variables in a formula that must hold if the formula is satisfiable~\cite{Morse2015}.
-New assertions can be added to or old assertions removed from this stack, depending on the evaluated value of variables.
-This enables ESBMC, and the respective solver, to learn from previous checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows us to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with all the design space state.
-
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%
-%%%%%ESBMC can be invoked through the command-line interface or configured through the Eclipse plug-in. Specific problems and the solver can be selected that way. 
-%
-%ESBMC aims to support all of ISO/IEC 9899:2017 C programming language standard, and detects errors in software by simulating a finite prefix of the program execution with all possible inputs.
-Classes of problems that can be detected include: user specified assertion failures, out of bounds array access, illegal pointer dereferences, double-free of malloc'd memory, misaligned memory access; integer overflows, divide by zero, memory leaks, concurrent software, deadlock, and data races (i.e.
-competing writes).
-
-%\subsection{Cyber-physical systems x Energy x ESBMC}
-%According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes.
-Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa.
-The economic and societal potential of such systems is vastly greater than what has been realized, and major investments are being made worldwide to develop the technology.
-The technology builds on the discipline of embedded systems (computers and software embedded in devices) whose principle mission is not computation, such as cars, toys, medical devices, and scientific instruments.
-CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole.
-%
-%Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}.
-For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies.
-Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation).
-%
-%Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled.
-Then a model checking will be performed to do a verification of the project in order to guarantee that the design of a stand-alone PV solution will meet the requirements, specifications and regulations.
-%
-%As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification.
-Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver.
-This work tracks the same path.
+If field or essay data is not available, considering that the proposed tools is aimed to be used prior the deployment of the PV system at the field, it is recommended (at least) to correct the battery efficiency ($\eta_{b}$) to 85\%, keeping the remaining efficiencies as expressed by the manufacturers.
 %
 %----------------------------------------
-\section{Model Checking Stand-alone Solar Photovoltaic Systems }
+\section{Proposed Automated Verification Method of PV Systems}
 \label{sec:Methodology}
@@
 In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to critical month method~\cite{Pinho}.
-The equations to check the PV sizing were not presented at this paper, however the standard from Engineering Manual was the reference~\cite{Pinho}.
+In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to worst monthly average solar energy method~\cite{Pinho}.
+The equations to check the PV sizing are present at Section~\ref{sec:sizingcheck}.
 %
@@
 is it SAT?}
-In a nutshell, ESBMC will process the ANSI-C code with constraints %($C$) 
+In a nutshell, the model checker will process the ANSI-C code with constraints %($C$) 
 and properties %($P$) 
@@
 %According with X and Y, t
-Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using non-deterministic variables from ESBMC to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range.
+Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range.
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\
+  \STATE $declare \, case \, studies \, details: \, sizing \, and \, manufacturers \, data $ \\
+  \STATE $sizing \textunderscore check()$ \\
+  \STATE $startPVgeneration \leftarrow findStartPVgeneration()$ \\
+  \STATE $endPVgeneration \leftarrow findEndPVgeneration()$ \\
   \STATE $SOC \leftarrow 100\%$ \\
+
 %  \COMMENT {Starting with the PV generation time}
 % \\ 
-\textit{LOOP Process}
-  \FOR {$h = 1$ to $Hours \, of \, PV \, generation$}
+%\textit{LOOP Process}
+ \FOR {$1st \, 24h \, loop$ to $Nth \, 24h \, loop$}
+  \FOR {$endPVgeneration+1$ to $startPVgeneration-1$}
+	  \STATE $dischargeBattery \, in \, 1h()$ \\
+%	  \STATE $autonomyCount \leftarrow autonomyCount+1$ \\
+	  \STATE $assert (SOC \geq SOC \textunderscore min)$ \\
+%	  \STATE $battery \, autonomy \, verification()$ \\
+  \ENDFOR
+  \FOR {$startPVgeneration$ to $endPVgeneration$}
     \STATE $G \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
@@
     \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting $T$ values}
-  \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ 
-  \\
+    \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ \\
     \COMMENT {If-then-else sequence to imitate charge controller work}
     \IF {($battery \, is \, empty$) AND ($PV \, is \, generating$)}
-    \STATE charge battery in 1h
-    \STATE PV feed the house
+      \STATE $chargeBattery \, in \, 1h()$ \COMMENT {PV feed the house}
     \ELSIF {($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
-    \STATE FAIL with assert macro
+      \STATE FAIL with assert macro \COMMENT {Battery is empty and there is not PV generation}
     \ELSIF {NOT($battery \, is \, empty$) AND ($PV \, is \, generating$)}
-    \STATE stop battery charge
-    \STATE PV feed the house
+      \STATE stop battery charge \COMMENT {PV feed the house}
     \ELSIF {NOT($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
-    \STATE discharge battery in 1h
-    \STATE Battery feed the house
+      \STATE $dischargeBattery \, in \, 1h()$ \COMMENT {Battery feed the house}
     \ENDIF
-  \STATE $h \leftarrow (h+1)$
+    \STATE $assert (SOC \geq SOC \textunderscore min)$ \\
+    \STATE $hour \leftarrow hour+1$ \\
    \ENDFOR
- \\ \textit{Start of battery autonomy verification:}
-%%  initialization\;
-\STATE $AutonomyCount \leftarrow 1$
- \WHILE {$AutonomyCount \leq autonomy$}
-  %%\FOR {$Autonomy = 1$ to $auton$}
-
-  \STATE $SOC \leftarrow SOC - ( 24 - Hours \, of \, PV \, generation)\,h\, discharge$
-  \STATE $AutonomyCount \leftarrow AutonomyCount+1)$
-  \\  
-    \COMMENT {autonomy verification during discharge period}
-  \\
-  \STATE assert NOT($Battery \, empty$)  
-  \\
-  \COMMENT {Perform similar \textbf{for}-LOOP as defined in line 2-21}
-  %%\ENDFOR
-  \ENDWHILE
+  \ENDFOR
  \RETURN $(\,)$ 
@@
 All experiments were conducted on an otherwise idle Intel octa core Xeon CPU E5-2640 with 2.4 GHz and 264 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning our verification engine, ESBMC v6.0.0 was used \footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}.
+Concerning the verification engine, ESBMC v6.0.0 was used \footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}.
 % enabled with the goal of reducing memory usage; 

### 2019-04-06 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text

@@
 If there is no property violation, then the verification algorithm continues and
-The batteries are assumed to have SOC of 100\% (Line 1), i.e., the batteries are charged. That is important because the system is said ready to use when the batteries are charged.
-
-%At both case studies, it was considered 21 years of historic data from Manaus. 
-%According with X and Y, t
-Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range.
+In order to reduce the computational effort of the algorithm,
+% caused by the state explosion inherent of the technique, 
+every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation), when the batteries are demanded to feed the house.
+
+Lines 1 is devoted to information from the location where the PV system will be/were deployed.
+Usually the information of annual average minimum and maximum, related to temperature ($T$) and solar irradiance ($G$), hour by hour, are obtained from specific historical weather web sites~\cite{Temperature}, ~\cite{Irradiance}.
+
+Line 2 represents all the information that comes from the PV sizing and from the equipment manufacturers data, as PV panels specification and data, batteries specification and data, inverter details and charge controller details.
+This item includes as well information from the house's load curve.
+
+The first automated verification is related to the sizing check, according described at Section ~\ref{sec:sizingcheck}.
+Then two functions, called at lines 4 and 5, are responsible for discover which hour starts the photovoltaic generation and when stops.
+Those functions get this information from the array inputted to the Algorithm with the solar irradiance values.
+
+The batteries are assumed to have SOC of 100\% (Line 6), i.e., the batteries are charged. That is important because the system is said ready to use when the batteries are charged.
+
+The first for-loop at Line 7 controls how many cycles of 24h will be performed by the Algorithm.
+And the for-loop from lines 8 to 11 is responsible to discharge the battery (according the load curve) and verify the state of charge of the battery, hour-by-hour, starting at the first hour of the day after the sun goes down until the next day before the sun goes up (when there is not PV generation).
+Following, at the next for-loop, from line 12 to 29, is performed the verification where there is solar irradiance and all the PV system works.
+The Algorithm generates information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, hour-by-hour, using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range (lines 15 and 16).
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
@@
 %with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day.
-In order to reduce the computational effort of the algorithm,
-% caused by the state explosion inherent of the technique, 
-every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation).
-Therefore, our approach depends on specific data about the solar irradiation levels to define the average amount of hours of PV generation.
-
-After that, the model from PV generator is used in the function call of Line 7, to produce the voltage and current considering the states of $G$ and $T$.
-With respect to every hour considered, the conditional \textit{if-else-endif} statements from Lines 8, 11, 13, 16 and 19, will perform the charge or discharge of batteries according to the value of different variables: if there is PV generation (which depends on $G$ and $T$), the updated state of charge from batteries, the house's load and the set-up information of the PV system.
-
-Next, representing the time of the day where PV generation is not possible anymore, starting in Line 22, the algorithm will only discharge the batteries (using the 1 hour step) until a new charging process (at the next day) starts.
-Specific \textit{assert} in Line 26 will check the state of charging from batteries, and they will violate the property if their levels reach the minimum that represents a discharged battery; therefore, the PV system is unable to supply energy to the house.
-Nevertheless, if the verification engine does not fail, then we can conclude that the PV system does not need further corrections up to the given bounds.
+
+After that, the model from PV generator is used in the function call of Line 17, to produce the voltage and current considering the states of $G$ and $T$.
+With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from Lines 18, 20, 22, 24 and 26, will imitate the charge controller work, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+
+At the end of last for-loop, the state of the batteries is verified again (Line 27) and the hour is adjusted to the next loop (Line 28).
+
+Nevertheless, if the verification engine does not fail, then we can conclude that the PV system does not need further corrections up to the given bounds $k$.
 %
@@
  \begin{algorithmic}[1]
- \begin{small}
+ \begin{scriptsize}
 
@@
  \RETURN $(\,)$ 
-  \end{small}
+  \end{scriptsize}
  \end{algorithmic} 
@@
 %------------------------------------------
-
-We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with surge of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
-
-Note that the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 5 and 6 of Algorithm~\ref{alg:verification-algorithm}).
-Another characteristic of Manaus, based on historical weather data %\cite{Temperature},
-\cite{Irradiance}, is related to the fact that only during 8 hours of the day is possible to have PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).
+%
+%We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
+We have performed five case studies to evaluate the tools, as described in Table~\ref{tab2}. 
+\begin{table}
+\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
+\begin{scriptsize}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\hline
+Item & House 1 & House 2 & House 3 & House 4 & House 5\\
+\hline
+\hline
+PV Panels &  \multicolumn{4}{|c|}{3x 325W: in series} & 4x 325W: 2x series, 2x parallel \\
+\hline
+Batteries & \multicolumn{4}{|c|}{\makecell{4x220Ah: 2x series, 2x parallel\\ autonomy: 48h}} & \makecell{4x 120Ah batteries in series\\ autonomy: 6h}\\
+\hline
+Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150V/35A}\\
+\hline
+Inverter & \multicolumn{4}{|c|}{700W with peak of 1,600W} & 1,200W with peak of 1,600W\\
+\hline
+Power demand & 253W & 263W & 283W & 501W & 915W\\
+\hline
+GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
+\hline
+Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
+\hline
+\hline
+\end{tabular}
+\end{scriptsize}
+\end{table}
 
@@
 \begin{enumerate}
-\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
-\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
+\item[RQ1] \textbf{(soundness)} Does the automated verification provide correct results?
+\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
 \end{enumerate}
 
-All experiments were conducted on an otherwise idle Intel octa core Xeon CPU E5-2640 with 2.4 GHz and 264 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits.
-Concerning the verification engine, ESBMC v6.0.0 was used \footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}.
+In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool.
+All the experiments were performed with a timeout of 14,400 seconds (4 hours).
+%Every dweller, who owns a PV system, was interviewed
+
+All verification engines experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
+The setup of HOMER Pro simulation tool: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.
+
+Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+
+Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparation~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c --unwind 100 --trace}.
+
 % enabled with the goal of reducing memory usage; 
-We have also used the SMT solver Boolector version 2.4.1~\cite{Brummayer}. %The experiments were performed without a predefined timeout.
-
-In order to evaluate the proposed verification method and its performance, we have considered five case studies and also compared its performance to the HOMER Pro tool.
-%Every dweller, who owns a PV system, was interviewed to get information about his/her PV system during four months of use.
-This information was used to know possible flaws from every system in the field.
-Experimental setup of HOMER Pro: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.
+%The experiments were performed without a predefined timeout.
+Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
+An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness.
+% enabled with the goal of reducing memory usage; 
+ %The experiments were performed without a predefined timeout.
 
@@
 %
+Table~\ref{tab1} summarizes the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
+The times reported in Table~\ref{tab1} answer RQ2.
+Note that if we used HOMER Pro in all case studies, the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
+The simulation took less than five seconds to be performed on each case study.
+
+\begin{table}
+\centering
+\caption{Summary of the case-studies comparative and the automated tools.}\label{tab1}
+\begin{scriptsize}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\hline
+\multicolumn{5}{|c|}{Model Checker (SAT/UNSAT: time and message)}\\
+\hline
+Case &  \makecell{ESBMC 6.0.0\\(Boolector 3.0.1)} & \makecell {ESBMC 6.0.0\\(Z3 4.7.1)} & \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}\\
+\hline
+\hline
+House 1 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{5m08s \\(SAT)} & \makecell{19m02s \\(SAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 2 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{4m27s \\(SAT)} & \makecell{18m59s \\(SAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 3 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{5m07s \\(SAT)} & \makecell{18m39s \\(SAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 4 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{4m37s \\(SAT)} & \makecell{18m36s \\(SAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 5 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{$\leq$ 1 sec \\(UNSAT Line 337)} & \makecell{$\leq$ 1 sec \\(UNSAT Line 337)} & \makecell{6 sec \\ (UNSAT line 337)}\\
+\hline
+\hline
+\end{tabular}
+\end{scriptsize}
+\end{table}
+
 The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel.

### 2019-04-07 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text

@@
 \subsection{Availability of Stand-alone PV Systems}
+\label{sec:availability}
 %--------------------------------------------------
@@
 \subsection{Objectives and Setup}
+\label{sec:setup}
 %------------------------------------------
@@
 %
-Table~\ref{tab1} summarizes the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
-The times reported in Table~\ref{tab1} answer RQ2.
+Table~\ref{cases} summarizes the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
+The times reported in Table~\ref{cases} answer RQ2.
+
 Note that if we used HOMER Pro in all case studies, the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
@@
 \centering
-\caption{Summary of the case-studies comparative and the automated tools.}\label{tab1}
+\caption{Summary of the case-studies comparative and the automated tools.}\label{cases}
 \begin{scriptsize}
@@
 \hline
-House 1 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{5m08s \\(SAT)} & \makecell{19m02s \\(SAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 2 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{4m27s \\(SAT)} & \makecell{18m59s \\(SAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 3 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{5m07s \\(SAT)} & \makecell{18m39s \\(SAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 4 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{4m37s \\(SAT)} & \makecell{18m36s \\(SAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 5 &  \makecell{ $\leq$ 6 min \\(Out of Memory)} & \makecell{$\leq$ 1 sec \\(UNSAT Line 337)} & \makecell{$\leq$ 1 sec \\(UNSAT Line 337)} & \makecell{6 sec \\ (UNSAT line 337)}\\
+House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{5m08s \\(UNSAT)} & \makecell{19m02s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{4m27s \\(UNSAT)} & \makecell{18m59s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{5m07s \\(UNSAT)} & \makecell{18m39s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{4m37s \\(UNSAT)} & \makecell{18m36s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{6 sec \\ (SAT line 337)}\\
 \hline
@@
 
-The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel.
-This verification took approximately 0.57 hours to be performed.
-In order to validate this possible flaw, it was surveyed the owner of the 1,200 W system; we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer who showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level.
-Our verification engine identified those flaws (for those three houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries.
-Our verification engine took approximately 5.1 hours to find this flaw in house 2; 5.8 hours for house 3, and 4.4 hours for house 4.
-These flaws were confirmed with the dwellers who own the systems by an interview process and from a local monitoring system with the Raspberry Pi controller: at least once a month is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}, further affirming RQ1; after the sun rises, the systems returns to normal condition operation.
-One more time the flaws were not caused by misuse of the system by the dwellers.
-Fig.
-\ref{fig:loadcurve} shows the monitoring result for the load curve of house 2 from June to July of 2018 (5 weeks), without undesired peaks from power demand of even unexpected energy consumption.
-The house 1 had an inconclusive result with the automated verification, because the solver did not presented any result from the SMT verification.
-
-\begin{figure}[h]
-\includegraphics[width=0.65\textwidth]{loadcurve.png}
-\centering
-\caption{Five weeks monitored load curve from House 1.}
-\label{fig:loadcurve}
-\end{figure}
-
-The same five case studies were evaluated by HOMER Pro.
+Worth to mention that a UNKNOWN result from the verification engines means that the result is not SAT or UNSAT.
+This result indicates that the verification created a out of memory or a time out situation.
+It is possible yet, that the UNKNOWN can be caused by user interruption, however this is not an option during the tests performed during the experimentation.
+
+The description of our experimental results can be broken down into three parts, one to each verification engine: ESBMC, CBMC, and CPAchecker.
+
+Related to the ESBMC, it was tried two possibilities, with the solvers Boolector and with Z3.
+The incremental option, that uses less memory, can only be performed with the solver Z3.
+Using ESBMC with the solver Boolector created a out of memory situation in all the case studies.
+And this result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes was killed.
+This resulted in a UNKNOWN return from the tool, as shown at the first column in~\ref{cases}.
+However, using the same version of the ESBMC but with the Z3 solver, the experimentation returned SAT or UNSAT to all the case studies.
+Related to the cases that use a 700 W PV system, the tool could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s.
+However the 1,200 W PV system (house 5) failed (SAT) at the line 337 of the code, indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system in order to work properly.
+This verification took less than 1s to be performed.
+
+Concerning the CBMC tool, similar results were obtained, but with some slower time.
+The experimentation returned SAT or UNSAT to all the case studies.
+Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18m36s to 19m02s.
+However the 1,200 W PV system (house 5) failed (SAT) at the line 337 of the code; with the same counterexample presented by ESBMC.
+This verification took less than 1s to be performed as well.
+
+Finally, the CPAchecker tool presented some different results.
+Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented a UNKNOWN result for all the 700W systems.
+This is because the time out set up was reached, i.e., after 4 hours of execution the tool was not possible to decide if the verification was SAT or UNSAT.
+However, when verifying the 1,200W PV system, the tool presented the same SAT message, indicating the same line (337) of the code.
+
+In order to validate the possible flaw from the house 5, presented by all verification engines, it was surveyed the owner of the 1,200 W system; we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer who showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
+The same process of validation was done to the four 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
+And even when a interruption is reported, this represents around 3.33\% of interruption in one month, what represents 96.97\% of availability of the PV system and it is in accordance to what was described in Section~\ref{sec:availability}; and that is not considered a flaw, further affirming RQ1.
+%\begin{figure}[h]
+%\includegraphics[width=0.65\textwidth]{loadcurve.png}
+%\centering
+%\caption{Five weeks monitored load curve from House 1.}
+%\label{fig:loadcurve}
+%\end{figure}
+
+The same five case studies were evaluated by HOMER Pro (RQ2).
 The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
+The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system (RQ2).
 All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
@@
 %
-Despite the divergence of results for the houses 2, 3 and 4 w.r.t.
+There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
 our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
-House 5 presented flaws from both tools; however, only our approach indicated which design error was responsible for the flaw (number of PV panels), further answering RQ2.
+House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
 %
@@
 We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
-We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W.
-Although this verification method takes longer than simulation methods, it is able to find specific conditions that lead to failures in a PV system previously validated by a commercial simulation tool.
+We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
+Although the verification method proposed takes longer than simulation methods, it is able to present details (counterexample) that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
 In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail.
+Related to the verification engines comparative, the ESBMC tool with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2G bytes when compared to 9.2G bytes of CBMC and 19.2G bytes of CPAchecker), and all the results were correct because the simulation tool presented the same results, besides the fact that interviews with the dwellers validated the possible flaws that the system could be presenting in the field.
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-All verification engines experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
+All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
 The setup of HOMER Pro simulation tool: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.
@@
 
-Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparation~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c --unwind 100 --trace}.
+Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c --unwind 100 --trace}.
 

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-However, the photocurrent delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, ~\eqref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature~\cite{Villalva}:
+However, the photo-current delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
+Therefore, ~\eqref{eq:Iph} is used to calculate the photo-current as function of irradiance and temperature~\cite{Villalva}:
 \begin{equation}
@@
 
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
 ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
@@
 The CPA framework provides interfaces to SMT solvers and interpolation procedures, such that the CPA operators can be written in a concise and convenient way~\cite{Beyer2011}.
-Currently CPachecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+Currently CPAchecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
 The CPA algorithm performs the reachability analysis, and operates on an object of the abstract data type CPA, i.e., the algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw \textcolor{red}{add a citation here}.
 Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw \textcolor{red}{add a citation here}.
-Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
+Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
 Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
@@
 
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
 ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Configurable program analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
-The CPA formalism provides an interface for the definition of program analyses; consequently, the tool CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
+The CPA formalism provides an interface for the definition of program analyses; consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
 The comparison of different approaches in the same experimental setting is intended to be easy and the experimental results is expected to be more meaningful~\cite{Beyer2011}.

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \usepackage{amsmath}
+\usepackage{xcolor}
 
@@
 The CPA formalism provides an interface for the definition of program analyses; consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-The comparison of different approaches in the same experimental setting is intended to be easy and the experimental results is expected to be more meaningful~\cite{Beyer2011}.
-Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consist of control-flow locations and control-flow edges.
+The comparison of different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
+Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
 The CPA framework provides interfaces to SMT solvers and interpolation procedures, such that the CPA operators can be written in a concise and convenient way~\cite{Beyer2011}.
-Currently CPAchecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-The CPA algorithm performs the reachability analysis, and operates on an object of the abstract data type CPA, i.e., the algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
+Currently, CPAchecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
 For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
-In software verification, its usual to take a considerable amount of effort to convert a verification idea into actual experimental results — and CPAchecker aim to accelerate this process~\cite{Beyer2011}.
+In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
 %

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Configurable program analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
-The CPA formalism provides an interface for the definition of program analyses; consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-The comparison of different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
+The CPA formalism provides an interface for the definition of program analyses.
+Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
+The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
 Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT solvers and interpolation procedures, such that the CPA operators can be written in a concise and convenient way~\cite{Beyer2011}.
-Currently, CPAchecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
+Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
 CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
 For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
-In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
+\textcolor{red}{It is unclear what a CPA is.}
+%In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
 %

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
-We have performed five case studies to evaluate the tools, as described in Table~\ref{tab2}. 
+We have performed five case studies to evaluate our approach together with the respective verification tools, as described in Table~\ref{tab2}.
+\textcolor{red}{which tools do we evaluate?
+should we add this information to the table?}
 \begin{table}

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{enumerate}
-\item[RQ1] \textbf{(soundness)} Does the automated verification provide correct results?
+\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
 \item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
@@
 
-Worth to mention that a UNKNOWN result from the verification engines means that the result is not SAT or UNSAT.
-This result indicates that the verification created a out of memory or a time out situation.
-It is possible yet, that the UNKNOWN can be caused by user interruption, however this is not an option during the tests performed during the experimentation.
+Note that an UNKNOWN result from the verification engines means that the result is not SAT or UNSAT \textcolor{red}{What does SAT or UNSAT mean?}.
+This result indicates that the verification created an out of memory or a time out situation.
+\textcolor{red}{This sentence is totally unclear...
+It is possible yet that the UNKNOWN can be caused by user interruption, however this is not an option during the tests performed during the experimentation.}
 

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Related to the ESBMC, it was tried two possibilities, with the solvers Boolector and with Z3.
-The incremental option, that uses less memory, can only be performed with the solver Z3.
-Using ESBMC with the solver Boolector created a out of memory situation in all the case studies.
-And this result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes was killed.
-This resulted in a UNKNOWN return from the tool, as shown at the first column in~\ref{cases}.
-However, using the same version of the ESBMC but with the Z3 solver, the experimentation returned SAT or UNSAT to all the case studies.
-Related to the cases that use a 700 W PV system, the tool could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s.
-However the 1,200 W PV system (house 5) failed (SAT) at the line 337 of the code, indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system in order to work properly.
-This verification took less than 1s to be performed.
+Related to ESBMC, we have tried two possibilities with the SMT solvers Boolector and with Z3.
+The incremental option, which uses less memory, can only be performed with Z3.
+Using ESBMC with Boolector led to an out of memory situation in all the case studies.
+This result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes was killed.
+This resulted in a UNKNOWN returned from the tool, as shown in the first column in Table~\ref{cases}.
+However, using the same version of ESBMC but with Z3, the experimentation returned SAT or UNSAT to all the case studies.
+Related to the cases that use a 700 W PV system, the tool \textcolor{red}{which tool?} could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s.
+However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system in order to work properly \textcolor{red}{What does work properly mean?}.
+This verification took less than 1s to be performed \textcolor{red}{why?}.
 
@@
 Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18m36s to 19m02s.
-However the 1,200 W PV system (house 5) failed (SAT) at the line 337 of the code; with the same counterexample presented by ESBMC.
-This verification took less than 1s to be performed as well.
+However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
+This verification took less than 1s to be performed as well \textcolor{red}{why?}.
 
 Finally, the CPAchecker tool presented some different results.
-Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented a UNKNOWN result for all the 700W systems.
-This is because the time out set up was reached, i.e., after 4 hours of execution the tool was not possible to decide if the verification was SAT or UNSAT.
-However, when verifying the 1,200W PV system, the tool presented the same SAT message, indicating the same line (337) of the code.
+Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700W systems.
+This is because the time out set up was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
+However, when verifying the 1,200W PV system, the tool presented the same SAT message \textcolor{red}{what is a SAT message?}, thereby indicating the same line (337) of the code.
 

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The description of our experimental results can be broken down into three parts, one to each verification engine: ESBMC, CBMC, and CPAchecker.
-
-Related to ESBMC, we have tried two possibilities with the SMT solvers Boolector and with Z3.
-The incremental option, which uses less memory, can only be performed with Z3.
+The description of our experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
+
+Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3.
+The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet.
 Using ESBMC with Boolector led to an out of memory situation in all the case studies.
-This result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes was killed.
-This resulted in a UNKNOWN returned from the tool, as shown in the first column in Table~\ref{cases}.
-However, using the same version of ESBMC but with Z3, the experimentation returned SAT or UNSAT to all the case studies.
+This result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
+However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.
 Related to the cases that use a 700 W PV system, the tool \textcolor{red}{which tool?} could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s.

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-In order to validate the possible flaw from the house 5, presented by all verification engines, it was surveyed the owner of the 1,200 W system; we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer who showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to the four 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
-And even when a interruption is reported, this represents around 3.33\% of interruption in one month, what represents 96.97\% of availability of the PV system and it is in accordance to what was described in Section~\ref{sec:availability}; and that is not considered a flaw, further affirming RQ1.
+In order to validate the possible flaw from house 5, presented by all verification engines, we have surveyed the owner of the 1,200 W system.
+We identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
+The same process of validation was done to the four \textcolor{red}{to house 4?} 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
+\textcolor{red}{I couldn't understand this sentence:} Even when an interruption is reported, this represents around 3.33\% of interruption in one month, what represents 96.97\% of availability of the PV system and it is in accordance to what was described in Section~\ref{sec:availability}; and that is not considered a flaw, further affirming RQ1.
 %\begin{figure}[h]
@@
 \begin{figure}[h]
-\includegraphics[width=0.65\textwidth]{homer.png}
+\includegraphics[width=0.8\textwidth]{homer.png}
 \centering

### 2019-04-09 Tex/elsevier/list of abbreviations.tex
new text

list of abbreviations, units and nomenclature

$a$ Ideality or quality factor
AC Alternating current
$C_{10}$ 10h of rated battery capacity
$C_{bank}$ Total capacity of the battery bank
CBMC C Bounded Model Checker
$ cos \varphi $ Power factor of the inverter
CPA Configurable Program Analysis
CPAchecker Configurable Program Analysis Checker
DC Direct current
$DOD$ Depth of discharge ($DOC=1-SOC$)
$E_{consumption}$ Energy consumption
$E_{corrected}$ Energy corrected
$E_{p}$ Energy produced by one panel
ESBMC Efficient SMT-based Bounded Model Checker
$G$ Solar irradiance
$ G_{ref} $ Solar irradiance at STC ($1000 W/m^{2}$)
$I$ Current
$I_{0}$ Reverse saturation current
$ I_{AC} $ Current that the inverter supply to the house
$I_{c,min}$ Charge controller minimum current
$ I_{DC} $ Current required by the inverter from the DC source 
$ I_{in} $ Input current
$I_{load}$ Current that feed the load
$ I_{out} $ Output current
$I_{ph}$ Photocurrent
$ I_{ph,ref} $ Photocurrent at STC
$I_{pv}$ Current from the PV system
$ I_{sc} $ Short-circuit current
$ I_{sc,amb} $ Ambient short-circuit current
$ I_{sc,ref} $ Short-circuit current at STC
$ k_{B} $ Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); 
$MAX_{AC,ref}$ Peak power that the inverter can support
$N$ Number of series-connected cells
$N_{B}total$ Sized number of batteries
$N_{BP}$ Sized number of parallel batteries
$N_{BP}min$ Total minimum number of parallel batteries
$N_{BS}$ Sized number of series batteries
$N_{BS}min$ Total minimum number of series batteries
NOCT Nominal Operating Cell Temperature
$N_{PS}$ Sized number of panels in series
$N_{PSmin}$ Total number of panels in series
$N_{PP}$ Sized number of panels in parallel
$N_{PPmin}$ Total umber of panels in parallel
$ N_{TP} $ Sized number of panels
$N_{TPmin}$ Total minimum number of needed solar panels
PV Photovoltaic
P Power
$P_{in}$ Input power
$P_{out}$ Output power
$P_{surge}$ Maximum peak power demanded by house for few seconds
$q$ Absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $)
SAT Satisfiability or Boolean satisfiability problem 
SAT When returns a failure from the verification tool
SMT Satisfiability modulo theories
$ SOC $ Battery state of charge
STC Standard Test Condition (reference state)
$T$ Temperature
$ T_{air} $ Ambient temperature
$ T_{ref}$ Temperature at STC ($=298.15 K$ or $25^{o}C$)
UNSAT Condition when verification tool succeeds (could not reach an error)
V Voltage
$ V_{AC}  $ Voltage that the inverter supply to the house
$V_{c}$ Battery charge voltage 
$V_{d}$ Battery discharge voltage
$ V_{DC} $ Input voltage to the inverter delivered by the DC source
$ V_{in} $ Input voltage
$ V_{oc} $ Open-circuit voltage
$ V_{oc,ref} $ Reference open-circuit voltage at STC
$ V_{out} $ Output voltage
$ V_{system} $ DC voltage of the bus
$V_{T}$ Thermal voltage ($ V_{T}=k_{B}T/q $)
$\Delta T$ Temperature variation ($\Delta T=T-T_{ref} $)
$ \mu_{I} $ Short-circuit current temperature coefficient ($A/K$)
$ \mu_{V} $ Open-circuit voltage temperature coefficient ($ V/K $)
$\eta_{b}$ Battery efficiency
$\eta_{c}$ Charge controller efficiency
$\eta_{i}$ Inverter efficiency
$\eta_{p}$ PV panel efficiency

### 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
removed red comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
-\title{Automated Verification of Stand-alone Solar Photovoltaic Systems}
+\title{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
@@
 
-\linenumbers
+%\linenumbers
 
@@
 To represent the system's physical characteristics, PVWatts requires values for six inputs: System DC size; Module type; Array type; System losses; Array tilt angle; Array azimuth angle.
-
+%
 %\subsection{SAM}
@@
 As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.
-
+%
 %\subsection{HOMER}
@@
 At the short-time only the commercial version will remain.
-
+%
 %The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
@@
 HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.
-
+%
 %\subsection{RETScreen}
 %As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
-
+%
 %RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options.
@@
 The software is freely distributed (but with restrictions to save work or print), and had three different versions:
-
+%
 %\begin{itemize}
@@
 %\end{itemize}
-
+%
 %As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
@@
 RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.
-
+%
 %\subsection{Hybrid2}
@@
 This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, what is a limitation.
-
+%
 %Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where 
@@
 \begin{figure}[h]
-\includegraphics[width=0.70\textwidth]{blockdiagramPVS2}
+\includegraphics[width=0.80\textwidth]{blockdiagramPVS2}
 \centering
-\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
+\caption{Block diagram for a typical stand-alone PV system (adapted from~\cite{Hansen}).}
 \label{fig:blockdiagram}
@@
 \begin{figure}[h]
-\includegraphics[width=0.50\textwidth]{equivckt1D}
+\includegraphics[width=0.40\textwidth]{equivckt1D}
 \centering
-\caption{1-diode equivalent PV cell/panel circuit model~\cite{Cubas}.}
+\caption{1-diode equivalent PV cell/panel circuit model (adapted from~\cite{Cubas}).}
 %\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
@@
 
-To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \textunderscore off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}.
-PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $.
+To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \_ off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}.
+PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \_ on} $.
 %This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
@@
 %
-In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \textunderscore off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}.
-The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \textunderscore on}$.
+In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \_ off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}.
+The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \_ on}$.
 %, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process (Source:~\cite{Hansen})}
+\caption{Summary of the controller process (adapted from~\cite{Hansen})}
 \label{table:controller}
@@
 \hline
-(1) & \makecell{If $V > V_{max \textunderscore off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
-\hline
-(2) & \makecell{If command (1) is \\done and $V < V_{max \textunderscore on}$} & \makecell{Reconnect PV array \\to the system}\\
-\hline
-(3) & \makecell{If $V < V_{min \textunderscore off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
-\hline
-(4) & \makecell{If command (3) is \\ done and $V > V_{min \textunderscore on}$} & \makecell{Reconnect the load \\to the system}\\
+(1) & \makecell{If $V > V_{max \_ off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
+\hline
+(2) & \makecell{If command (1) is \\done and $V < V_{max \_ on}$} & \makecell{Reconnect PV array \\to the system}\\
+\hline
+(3) & \makecell{If $V < V_{min \_ off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
+\hline
+(4) & \makecell{If command (3) is \\ done and $V > V_{min \_ on}$} & \makecell{Reconnect the load \\to the system}\\
 \hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw \textcolor{red}{add a citation here}.
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}.
 Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Configurable program analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
+Automatic program verification requires a choice between precision and efficiency. The
+more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was
+reflected in two major approaches to static verification: program analysis and model
+checking.
+In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
 The CPA formalism provides an interface for the definition of program analyses.
@@
 Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
+%CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
 For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
@@
   \STATE $declare \, case \, studies \, details: \, sizing \, and \, manufacturers \, data $ \\
-  \STATE $sizing \textunderscore check()$ \\
+  \STATE $sizing \_ check()$ \\
   \STATE $startPVgeneration \leftarrow findStartPVgeneration()$ \\
@@
 %	  \STATE $autonomyCount \leftarrow autonomyCount+1$ \\
-	  \STATE $assert (SOC \geq SOC \textunderscore min)$ \\
+	  \STATE $assert (SOC \geq SOC \_ min)$ \\
 %	  \STATE $battery \, autonomy \, verification()$ \\
@@
   \FOR {$startPVgeneration$ to $endPVgeneration$}
-    \STATE $G \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
-    \STATE $T \leftarrow nondet \textunderscore uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
+    \STATE $G \leftarrow nondet \_ uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
+    \STATE $T \leftarrow nondet \_ uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
     \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting $G$ values}
@@
     \ENDIF
-    \STATE $assert (SOC \geq SOC \textunderscore min)$ \\
+    \STATE $assert (SOC \geq SOC \_ min)$ \\
     \STATE $hour \leftarrow hour+1$ \\
@@
 %We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
-We have performed five case studies to evaluate our approach together with the respective verification tools, as described in Table~\ref{tab2}.
-\textcolor{red}{which tools do we evaluate?
-should we add this information to the table?}
+We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
+Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), were used to compare the approach effectiveness and efficiency.
 \begin{table}
@@
 
-Note that an UNKNOWN result from the verification engines means that the result is not SAT or UNSAT \textcolor{red}{What does SAT or UNSAT mean?}.
-This result indicates that the verification created an out of memory or a time out situation.
-\textcolor{red}{This sentence is totally unclear...
-It is possible yet that the UNKNOWN can be caused by user interruption, however this is not an option during the tests performed during the experimentation.}
+Note that an UNKNOWN result from our verification engines does not mean that a failure was found (i.e., SAT) neither that the verification is successful (i.e., UNSAT).
+An UNKNOWN result indicates that the verification engine led to  an out of memory or a time out situation.
 
@@
 However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.
-Related to the cases that use a 700 W PV system, the tool \textcolor{red}{which tool?} could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s.
-However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system in order to work properly \textcolor{red}{What does work properly mean?}.
-This verification took less than 1s to be performed \textcolor{red}{why?}.
+Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s.
+However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
+This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check and does not perform the functional verification \textcolor{red}{what is functional verification?}.
 
@@
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
-This verification took less than 1s to be performed as well \textcolor{red}{why?}.
+This verification took less than 1s to be performed as well, \textcolor{red}{for the same reason described during the results of the ESBMC engine}.
 
@@
 This is because the time out set up was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
-However, when verifying the 1,200W PV system, the tool presented the same SAT message \textcolor{red}{what is a SAT message?}, thereby indicating the same line (337) of the code.
+However, when verifying the 1,200W PV system, the tool presented a SAT message, \textcolor{red}{i.e., it was found a failure}, with the counterexample indicating the line (337) of the code, the same one appointed by the other verification engines, related to the charge controller.
 
@@
 We identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to the four \textcolor{red}{to house 4?} 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
-\textcolor{red}{I couldn't understand this sentence:} Even when an interruption is reported, this represents around 3.33\% of interruption in one month, what represents 96.97\% of availability of the PV system and it is in accordance to what was described in Section~\ref{sec:availability}; and that is not considered a flaw, further affirming RQ1.
+The same process of validation was done to \textcolor{red}{the houses 1, 2, 3 and 4, that use the} 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
+\textcolor{red}{However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), what indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.}
 %\begin{figure}[h]
@@
 \centering
-\caption{Homer simulation screen.}
+\caption{HOMER simulation screen.}
 \label{fig:homerscreen}
@@
 The authors would like to thank Coventry University for the availability of the case studies (real PV systems) to validate the tool and to support the mobility of one researcher to UK.
-
-\section*{Funding}
 This work was supported by Newton Fund [grant number 261881580] with the mobility of one researcher to UK; FAPEAM - Amazonas State Foundation for Research Support [grants from call 009/2017 and PROTI Pesquisa 2018], for the financial support related to the Virtual Machine rent (December 2018 to January 2019), for the DCTIEX II scholarship (November 2018), and for support the mobility of the researcher; and FAS - Sustainable Amazonas Foundation for the PhD scholarship (from November 2017 to March 2019).

### 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
removed red comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
-This verification took less than 1s to be performed as well, \textcolor{red}{for the same reason described during the results of the ESBMC engine}.
+This verification took less than 1s to be performed as well, for the same reason described during the results of the ESBMC engine.
 
@@
 This is because the time out set up was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
-However, when verifying the 1,200W PV system, the tool presented a SAT message, \textcolor{red}{i.e., it was found a failure}, with the counterexample indicating the line (337) of the code, the same one appointed by the other verification engines, related to the charge controller.
+However, when verifying the 1,200W PV system, the tool presented a SAT message, i.e., a failure was found, with the counterexample indicating the line (337) of the code, the same one appointed by the other verification engines, related to the charge controller.
 
@@
 We identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to \textcolor{red}{the houses 1, 2, 3 and 4, that use the} 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
+The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
 \textcolor{red}{However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), what indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.}

### 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
removed red comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
-\textcolor{red}{However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), what indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.}
+However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
 %\begin{figure}[h]

### 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text

@@
 %% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+\usepackage{numcompress}\bibliographystyle{model3-num-names}
 
@@
 %% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
+%\bibliographystyle{elsarticle-num}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{frontmatter}
+
+\section*{List of Abbreviations, Units and Nomenclature}
+\noindent $a$ Ideality or quality factor \\
+AC Alternating current \\
+$C_{10}$ 10h of rated battery capacity \\
+$C_{bank}$ Total capacity of the battery bank \\
+CBMC C Bounded Model Checker \\
+$ cos \varphi $ Power factor of the inverter \\
+CPA Configurable Program Analysis \\
+CPAchecker Configurable Program Analysis Checker \\
+DC Direct current \\
+$DOD$ Depth of discharge ($DOC=1-SOC$) \\
+$E_{consumption}$ Energy consumption \\
+$E_{corrected}$ Energy corrected \\
+$E_{p}$ Energy produced by one panel \\
+ESBMC Efficient SMT-based Bounded Model Checker \\
+$G$ Solar irradiance \\
+$ G_{ref} $ Solar irradiance at STC ($1000 W/m^{2}$) \\
+$I$ Current \\
+$I_{0}$ Reverse saturation current \\
+$ I_{AC} $ Current that the inverter supply to the house \\
+$I_{c,min}$ Charge controller minimum current \\
+$ I_{DC} $ Current required by the inverter from the DC source \\
+$ I_{in} $ Input current \\
+$I_{load}$ Current that feed the load \\
+$ I_{out} $ Output current \\
+$I_{ph}$ Photocurrent \\
+$ I_{ph,ref} $ Photocurrent at STC \\
+$I_{pv}$ Current from the PV system \\
+$ I_{sc} $ Short-circuit current \\
+$ I_{sc,amb} $ Ambient short-circuit current \\
+$ I_{sc,ref} $ Short-circuit current at STC \\
+$ k_{B} $ Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); \\
+$MAX_{AC,ref}$ Peak power that the inverter can support \\
+$N$ Number of series-connected cells \\
+$N_{B}total$ Sized number of batteries \\
+$N_{BP}$ Sized number of parallel batteries \\
+$N_{BP}min$ Total minimum number of parallel batteries \\
+$N_{BS}$ Sized number of series batteries \\
+$N_{BS}min$ Total minimum number of series batteries \\
+NOCT Nominal Operating Cell Temperature \\
+$N_{PS}$ Sized number of panels in series \\
+$N_{PSmin}$ Total number of panels in series \\
+$N_{PP}$ Sized number of panels in parallel \\
+$N_{PPmin}$ Total umber of panels in parallel \\
+$ N_{TP} $ Sized number of panels \\
+$N_{TPmin}$ Total minimum number of needed solar panels \\
+PV Photovoltaic \\
+P Power \\
+$P_{in}$ Input power \\
+$P_{out}$ Output power \\
+$P_{surge}$ Maximum peak power demanded by house for few seconds \\
+$q$ Absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $) \\
+SAT Satisfiability or Boolean satisfiability problem \\
+SAT When returns a failure from the verification tool \\
+SMT Satisfiability modulo theories \\
+$ SOC $ Battery state of charge \\
+STC Standard Test Condition (reference state) \\
+$T$ Temperature \\
+$ T_{air} $ Ambient temperature \\
+$ T_{ref}$ Temperature at STC ($=298.15 K$ or $25^{o}C$) \\
+UNSAT Condition when verification tool succeeds (could not reach an error) \\
+V Voltage \\
+$ V_{AC}  $ Voltage that the inverter supply to the house \\
+$V_{c}$ Battery charge voltage  \\
+$V_{d}$ Battery discharge voltage \\
+$ V_{DC} $ Input voltage to the inverter delivered by the DC source \\
+$ V_{in} $ Input voltage \\
+$ V_{oc} $ Open-circuit voltage \\
+$ V_{oc,ref} $ Reference open-circuit voltage at STC \\
+$ V_{out} $ Output voltage \\
+$ V_{system} $ DC voltage of the bus \\
+$V_{T}$ Thermal voltage ($ V_{T}=k_{B}T/q $) \\
+$\Delta T$ Temperature variation ($\Delta T=T-T_{ref} $) \\
+$ \mu_{I} $ Short-circuit current temperature coefficient ($A/K$) \\
+$ \mu_{V} $ Open-circuit voltage temperature coefficient ($ V/K $) \\
+$\eta_{b}$ Battery efficiency \\
+$\eta_{c}$ Charge controller efficiency \\
+$\eta_{i}$ Inverter efficiency \\
+$\eta_{p}$ PV panel efficiency \\
 
@@
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
-This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check and does not perform the functional verification \textcolor{red}{what is functional verification?}.
+This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, \textcolor{red}{which is in Line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code (much more complex)}.
 

### 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text

@@
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
-This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, \textcolor{red}{which is in Line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code (much more complex)}.
+This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in Line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code (much more complex).
 

### 2019-04-22 code/opt_PVcode_rev2.c
new code

@@ -1,0 +1,206 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode.c
+ Author      : Alessandro
+ Version     : rev2 - April 2019
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
+// int Phouse = 915, Psurge = 980, Econsumption = 4880;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+
[…]

### 2019-04-22 Tex/ASE2019/Conference-LaTeX-template_7-9-18/Trindade_ASE2019_optimization PV systems_rev0.tex
new paper

\documentclass[10pt,conference]{IEEEtran}
% \documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\bibliographystyle{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{textcomp}
\usepackage{xcolor}
\def \BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Applying automated verification to optimal sizing of stand-alone solar photovoltaic systems\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Alessandro Trindade}
\IEEEauthorblockA{\textit{Electricity Department} \\
\textit{Federal University of Amazonas}\\
Manaus, Brazil \\
alessandrotrindade@ufam.edu.br}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Lucas Cordeiro}
\IEEEauthorblockA{\textit{School of Computer Science} \\
\textit{The University of Manchester}\\
Manchester, England \\
lucas.cordeiro@@manchester.ac.uk }
}

\maketitle

\begin{abstract}
Currently around 1 billion of people do not have electrical energy. Energy poverty alleviation has become an important political issue. Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. Particular attention is given to use renewables and stand-alone solar photovoltaic (PV) systems. Validation tools are available to evaluate PV designs, but they are mainly based on simulations that do not cover all aspects of the design space. The use of automated verification in PV systems is a recent subject with a few initiatives. Here we create an algorithm and use four state-of-art automated verification techniques to optimize the sizing of a solar photovoltaic system, where commercial equipment data is part of the specification of the code. Furthermore, the technical solution is conjugated with the financial analysis of the sizing obtained. The proposal is unprecedented and interesting to streamline the design and analysis of photovoltaic solar systems projects.Experimental results show promising results, even with state explosion and time to computing issues not solved yet.
\end{abstract}

\begin{IEEEkeywords}
automated verification, model checking, optimization, electrical systems, solar photovoltaic systems
\end{IEEEkeywords}

\section{Introduction}
Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}. In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.

In order to simulate or evaluate a PV system, there are various specialized tools available in the market, e.g. RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g. PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}. However, those tools are based on simulation models, which are employed before the system design is concluded; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of PV systems~\cite{ClarkeHV18}. In this study, we review verification tools and we do a link to PV systems, what was not common in past research.

To select an optimum combination to meet sizing constraints, it is necessary to evaluate \textit{power reliability} and \textit{system cost} analysis for the recommended system. An ideal combination for any PV system is made by the best compromise between two considered objectives, which is power reliability and system cost~\cite{Alsadi2018}.

Regarding power reliability, the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that at this paper we are not considering site characteristics and neither the load changes over the time, the reliability analysis will be granted only by the critical period method of PV sizing.

In the other hand, considering the system cost analysis, it is usual to find related research done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC). Here, one more time, based on the fact that the local of deployment is not specified, this research uses an adapted LCC analysis, where only the deployment cost is considered at the model (without the maintenance or operational costs).

The main contribution of this approach is to allow that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system, and the algorithm using automated verification, and written in language C, can find the best technical and financial result.%, using non-deterministic variables and exploring the design-space
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate four state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t. user requirements.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CBMC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}. CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{ESBMC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. %ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ultimate Automizer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties. The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement (CEGAR) scheme. CEGAR is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check and refinement~\cite{CEGAR}. In each iteration, Automizer picks a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible. If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility. The predicates are a sequence of interpolants since each predicate "interpolates" between a set of reachable states and a set of states from which it cannot reach the error. In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed. It is used automata to represent sets of traces. The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CPAchecker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Automatic program verification requires a choice between precision and efficiency. The
more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was
reflected in two major approaches to static verification: program analysis and model
checking. In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$). For night hours or rainy days, we need to hold batteries where power can be stored and used. The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{blockdiagramPVS2}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
\\

The sizing check will be performed by the proposed tool, and this stage ensures that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho}. 
%
Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
\begin{equation}
\label{eq:Ecorrected}
\scriptstyle E_{corrected} = \dfrac{\scriptstyle E_{consumption}}{ \scriptstyle \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

Following, it is necessary to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, as defined by~\eqref{eq:Ep}.

\begin{equation}
\label{eq:Ep}
\scriptstyle E_{p} = \scriptstyle Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
\end{equation}

\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV systems will be deployed, the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.

The total minimum number of needed solar panels ($N_{TPmin}$) is computed by ~\eqref{eq:NTPmin}.
\begin{equation}
\label{eq:NTPmin}
\scriptstyle N_{TPmin} = \dfrac{\scriptstyle E_{corrected}}{\scriptstyle E_{p}}.
\end{equation}

Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.  Where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.

\begin{equation}
\label{eq:NPSmin}
\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}}.
\end{equation}

\begin{equation}
\label{eq:NPPmin}
\scriptstyle N_{PPmin} = \dfrac{\scriptstyle P_{total}}{\scriptstyle Number\,Panels\,Series \scriptstyle \times \scriptstyle P_{max,ref}}.
\end{equation}

Related to the batteries, firstly must be defined the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
\begin{equation}
\label{eq:Cbank}
\scriptstyle C_{bank} \scriptstyle = \dfrac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD}.
\end{equation}
%
\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% at this paper).
%
Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}. 
\begin{equation}
\label{eq:Nbtotal}
\scriptstyle N_{B}total = \scriptstyle N_{BS}min \scriptstyle \times \scriptstyle N_{BP}min = \dfrac{\scriptstyle V_{system}}{\scriptstyle V_{bat}} \scriptstyle \times \dfrac{\scriptstyle C_{bank}}{\scriptstyle 1 \,Battery \, Capacity}.
\end{equation}

Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage: 
\begin{equation}
\label{eq:vcvsystem}
\scriptstyle V_{c} = \scriptstyle V_{system}.
\end{equation}

Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
%
\begin{equation}
\label{eq:iscamb}
\scriptstyle I_{sc,amb} = \dfrac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
\end{equation}

The controller must meet the maximum current from the PV array given by \eqref{eq:icmin} and \eqref{eq:icicmin}.
\begin{equation}
\label{eq:icmin}
\scriptstyle I_{c,min} = \scriptstyle I_{sc,amb} \times \scriptstyle N_{PP}.
\end{equation}

\begin{equation}
\label{eq:icicmin}
\scriptstyle I_{c} \geq \scriptstyle I_{c,min}.
\end{equation}

The sizing project check of the inverter is carried out by means of three equations. Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$). Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}

\section{Method}
Algorithm~\ref{alg:verification-algorithm} describes the pseudo-code used to perform the optimization of stand-alone PV systems using automated verification.

 \begin{algorithm}
 \caption{Optimization algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}

 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE $initialize \, variables$ \\
  \STATE $declare \, list \, of \, PV \, panels \, data \, and \, cost $ \\
  \STATE $declare \, list \, of \, controllers \, data \, and \, cost $ \\
  \STATE $declare \, list \, of \, batteries \, data \,  and \, cost $ \\
  \STATE $declare \, list \, of \, inverters \, data \,  and \, cost $ \\
  \STATE $declare \, the \, maximum \, cost \, possible \, MaxCost $  \\
  \STATE $declare \, power \, demand, \, power \, peak, \, energy \, consumption $ \\
  \STATE $declare \, battery\,  autonomy, deep \, of \, discharge, AC \, voltage$ \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE $declare \, non-deterministic \, variable \, to \, select \, Panel \, from \, list$ \\
 	\STATE $declare \, non-deterministic \, variable \, to \, select \, Controller \, from \, list $ \\
 	\STATE $declare \, non-deterministic \, variable \, to \, select \, Battery \, from \, list $ \\
 	\STATE $declare \, non-deterministic \, variable \, to \, select \, Inverter \, from \, list $ \\ 	
 	\STATE $calculate \, E_{corrected}, \, E_{p} $ \\
	\STATE $calculate \, N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE $calculate \, C_{bank}$ \\
	\STATE $calculate \, N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{c})$ \\
 	\STATE $calculate \, I_{sc,amb}$ \\
 	\STATE $calculate \, I_{c,min}$ \\
 	\STATE $requeriment \, enforced \, by \, \textbf{assume}(I_{c})$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{in}DC)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{out}AC)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(Demand)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(P_{surge})$ \\
	\STATE $non-det \, variables \, hold \, feasible \, equipment \, and \ cost $ \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE $Violation \, check \, with \, \textbf{assert}(F_{obj} \geq HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

The algorithm starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5). Following is necessary to define user requirements (house requirements and design definitions), from Line 6 to 8.

The loop-FOR started at line 9 controls the try to get the lowest cost to the PV solution. It starts with cost of $zero$ and stops only when the algorithm finds a feasible solution which cost breaks the $assert$ of Line 28. When this happens, then the algorithm found the optimum solution and we say that the automatic verification reached a \textit{SAT} (satisfiability) condition. The algorithm uses non-deterministic variables to pick one specific data from a list of PV panels, controllers, batteries and inverters (Lines 10 to 13). That procedure ensures that the automated verification will try all the possibilities of item from each equipment, and combine them in order to mount a feasible PV solution that meet the user requirements.

Next, using the equations described at Section~\ref{sec:sizing} are calculated the sizing necessary variables (Lines 14 to 20). The directive \textit{assume} (from Line 21 to 25) ensure the compatibility of the choose item from the list of equipment: the automatic verification uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20, and more the Line 18. Therefore, the algorithm reaches the Line 27 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$.

If the algorithm do not find a feasible solution among the item of equipment that were inputted to the code, then the result is an \textit{UNSAT}, i.e., the program finish and do not find an solution. It indicates that was not possible to combine the itens of each equipment and create a feasible solution.

\section{Results and Discussion}
We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, four start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (CBMC, ESBMC, UAutomizer, and CPAchecker), were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.

\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
 & Case 1 & Case 2\\
\hline
\hline
Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3900Wh/day} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4880Wh/day}\\
\hline
CBMC 5.11 (MiniSat 2.2.1) & x1 & x2 \\
\hline
ESBMC 6.0.0 (Boolector 3.0.1) & x1 & x2 \\
\hline
UAutomizer 0.1.24 (Z3 4.8.3) & x1 & x2 \\
\hline
CPAchecker 1.8 (MathSAT 5.5.3) & x2 & x4 \\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}

% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis}{}

\vspace{12pt}

\end{document}

### 2019-04-22 Tex/ASE2019/Conference-LaTeX-template_7-9-18/conference_041818.tex
new paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} 
G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.

\bibitem{b2} 
J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.

\bibitem{b3} 
I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.

\bibitem{b4} 
K. Elissa, ``Title of paper if known,'' unpublished.

\bibitem{b5} 
R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.

\bibitem{b6} 
Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].

\bibitem{b7} 
M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.

\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-04-22 Tex/ASE2019/Conference-LaTeX-template_7-9-18/Trindade_ASE2019_optimization PV systems_rev0.tex
updated text ASE

@@
 
-The sizing check will be performed by the proposed tool, and this stage ensures that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho}. 
+The sizing check will be performed by the proposed tool, and this stage ensures that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (maximum power point tracking) charge controller, that is the most common nowadays.
 %
@@
 We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}.
-Furthermore, four start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (CBMC, ESBMC, UAutomizer, and CPAchecker), were used to compare the approach effectiveness and efficiency.
+Furthermore, four start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency.
 The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.
 
+All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
+The experiments were performed with a predefined timeout of 240 minutes.
+
+%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
 \begin{table}
@@
 \hline
-Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3900Wh/day} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4880Wh/day}\\
+Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3900Wh/day \\ Battery autonomy=48h} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4880Wh/day \\ Battery autonomy=6h}\\
 \hline
-CBMC 5.11 (MiniSat 2.2.1) & x1 & x2 \\
+CBMC 5.11 (MiniSat 2.2.1) & Out of Memory & Out of Memory \\
 \hline
-ESBMC 6.0.0 (Boolector 3.0.1) & x1 & x2 \\
+ESBMC 6.0.0 (Boolector 3.0.1) & Timeout & Timeout \\
 \hline
-UAutomizer 0.1.24 (Z3 4.8.3) & x1 & x2 \\
+UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
 \hline
-CPAchecker 1.8 (MathSAT 5.5.3) & x2 & x4 \\
+CPAchecker 1.8 (MathSAT 5.5.3) & SAT (65 minutes) & x4 \\
 \hline

### 2019-04-23 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
renamed files
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2019-04-22 Tex/ASE2019/Conference-LaTeX-template_7-9-18/Trindade_ASE2019_optimization PV systems_rev0.tex
@@
 
-\title{Applying automated verification to optimal sizing of stand-alone solar photovoltaic systems\\
+\title{Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
 % \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Alessandro Trindade}
+\author{\IEEEauthorblockN{Alessandro Trindade}
 \IEEEauthorblockA{\textit{Electricity Department} \\
@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Lucas Cordeiro}
+\IEEEauthorblockN{Lucas Cordeiro}
 \IEEEauthorblockA{\textit{School of Computer Science} \\
-\textit{The University of Manchester}\\
+\textit{University of Manchester}\\
 Manchester, England \\
@@
 \begin{abstract}
-Currently around 1 billion of people do not have electrical energy.
-Energy poverty alleviation has become an important political issue.
-Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries.
-Particular attention is given to use renewables and stand-alone solar photovoltaic (PV) systems.
-Validation tools are available to evaluate PV designs, but they are mainly based on simulations that do not cover all aspects of the design space.
-The use of automated verification in PV systems is a recent subject with a few initiatives.
-Here we create an algorithm and use four state-of-art automated verification techniques to optimize the sizing of a solar photovoltaic system, where commercial equipment data is part of the specification of the code.
-Furthermore, the technical solution is conjugated with the financial analysis of the sizing obtained.
-The proposal is unprecedented and interesting to streamline the design and analysis of photovoltaic solar systems projects.Experimental results show promising results, even with state explosion and time to computing issues not solved yet.
+Software verification has experienced significant progress over the last two decades.
+Currently, there exist various software verifies that are able to solve intricate real-world problems, e.g., to design and verify renewable and stand-alone solar photovoltaic (PV) systems.
+Currently around $1$ billion of people do not have electrical energy; energy poverty alleviation has become an important political issue. 
+%Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
+Particular attention is given to renewables and PV systems.
+Unfortunately, existing tools available to evaluate PV designs are mainly based on simulations that do not cover all aspects of the design space.
+The use of automated verification in PV systems is a recent subject with only a few initiatives. 
+Here we develop an optimization algorithm and report its preliminary results using four state-of-art software verifiers to optimize the sizing of a PV system, where commercial equipment data is part of the specification and the technical solution is conjugated with the financial analysis of the obtained sizing.
+Our proposal is unprecedented and interesting to streamline the design and analysis of PV systems. Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
 \end{abstract}

### 2019-04-23 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated keywords
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Manchester, England \\
-lucas.cordeiro@@manchester.ac.uk }
+lucas.cordeiro@manchester.ac.uk }
 }
@@
 \begin{IEEEkeywords}
-automated verification, model checking, optimization, electrical systems, solar photovoltaic systems
+automated verification, model checking, optimization, electrical systems and solar photovoltaic systems.
 \end{IEEEkeywords}
@@
 Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
 
-In order to simulate or evaluate a PV system, there are various specialized tools available in the market, e.g.
-RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.
+In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.
 PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
@@
 Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of PV systems~\cite{ClarkeHV18}.
-In this study, we review verification tools and we do a link to PV systems, what was not common in past research.
+In this study, we review verification tools and related them to design and verify PV systems, which was uncommon in prior studies~\cite{abs-1811-09438}.
 

### 2019-04-23 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textcolor{red}{What is the relation of this paper with software engineering?}
+
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
@@
 
-To select an optimum combination to meet sizing constraints, it is necessary to evaluate \textit{power reliability} and \textit{system cost} analysis for the recommended system.
-An ideal combination for any PV system is made by the best compromise between two considered objectives, which is power reliability and system cost~\cite{Alsadi2018}.
+To select an optimum combination to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system.
+An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}.
+Regarding power reliability, the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
+Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean?
+Remember that we have software engineering audience}.
 
-Regarding power reliability, the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
-Based on the fact that at this paper we are not considering site characteristics and neither the load changes over the time, the reliability analysis will be granted only by the critical period method of PV sizing.
-
-In the other hand, considering the system cost analysis, it is usual to find related research done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC).
-Here, one more time, based on the fact that the local of deployment is not specified, this research uses an adapted LCC analysis, where only the deployment cost is considered at the model (without the maintenance or operational costs).
+However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC).
+Here, one more time, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the maintenance or operational costs \textcolor{red}{cite a reference here}.
 

### 2019-04-23 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{red}{What is the relation of this paper with software engineering?}
+\textcolor{red}{What is the relation of this paper with software engineering (SE)?}
 
@@
 
-The main contribution of this approach is to allow that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system, and the algorithm using automated verification, and written in language C, can find the best technical and financial result.%, using non-deterministic variables and exploring the design-space
+The main contribution of this approach is to allow that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system, and the algorithm using automated verification, and written in language C, can find the best technical and financial result.
+
+\textcolor{red}{We need to make our contributions stronger.
+Why the SE community would be interested in this paper?
+What are the main open problems we need them to solve here?
+Remember that this is a paper for new ideas...
+we don't need to make questions but we don't need to answer all of them.}
+
+%, using non-deterministic variables and exploring the design-space
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-04-23 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Verification Using Model Checking}
+
 \label{sec:AutomatedVerification}
@@
 ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end based on clang that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; (iii) \textcolor{red}{we should describe the symbolic execution with incremental solving phase here...} and finally (iv) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
 %ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
 This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+%This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
 

### 2019-04-24 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textcolor{red}{Do we really need this section?
+Can't we just cite our technical report in arxiv?
+Remember that this is a software engineering conference.
+People are more interested in the software part.}
+
 The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
-In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
+In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$).
 For night hours or rainy days, we need to hold batteries where power can be stored and used.
@@
 
-The sizing check will be performed by the proposed tool, and this stage ensures that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (maximum power point tracking) charge controller, that is the most common nowadays.
+The sizing check will be performed by the proposed tool, and this stage ensures that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, that is the most common nowadays.
 %
-Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
+Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
 \begin{equation}
@@
 
-Following, it is necessary to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, as defined by~\eqref{eq:Ep}.
+We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, as defined by~\eqref{eq:Ep}.
 
@@
 
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV systems will be deployed, the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed by ~\eqref{eq:NTPmin}.
+\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV systems will be deployed; the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
+%
+The total minimum number of needed solar panels ($N_{TPmin}$) is computed by~\eqref{eq:NTPmin} as
 \begin{equation}
@@
 Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.  
-Where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
-
+%
 \begin{equation}
 \label{eq:NPSmin}
-\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}}.
+\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}}
 \end{equation}
@@
 \label{eq:NPPmin}
-\scriptstyle N_{PPmin} = \dfrac{\scriptstyle P_{total}}{\scriptstyle Number\,Panels\,Series \scriptstyle \times \scriptstyle P_{max,ref}}.
+\scriptstyle N_{PPmin} = \dfrac{\scriptstyle P_{total}}{\scriptstyle Number\,Panels\,Series \scriptstyle \times \scriptstyle P_{max,ref}},
 \end{equation}
 
-Related to the batteries, firstly must be defined the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
+\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
+%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
+%
+Regarding the batteries, we must first define the total capacity of the battery bank, as described by~\eqref{eq:Cbank} as
 \begin{equation}
 \label{eq:Cbank}
-\scriptstyle C_{bank} \scriptstyle = \dfrac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD}.
+\scriptstyle C_{bank} \scriptstyle = \dfrac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD},
 \end{equation}

### 2019-04-24 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\section{Method}
-Algorithm~\ref{alg:verification-algorithm} describes the pseudo-code used to perform the optimization of stand-alone PV systems using automated verification.
+%------------------------------------------------------
+\section{Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
+%------------------------------------------------------
 
+Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to optimize stand-alone PV systems using automated verification. 
+%
  \begin{algorithm}
@@
   \FOR {$HintCost=0$ to $MaxCost$}
- 	\STATE $declare \, non-deterministic \, variable \, to \, select \, Panel \, from \, list$ \\
- 	\STATE $declare \, non-deterministic \, variable \, to \, select \, Controller \, from \, list $ \\
- 	\STATE $declare \, non-deterministic \, variable \, to \, select \, Battery \, from \, list $ \\
- 	\STATE $declare \, non-deterministic \, variable \, to \, select \, Inverter \, from \, list $ \\ 	
+ 	\STATE $declare \, non-det \, variable \, to \, select \, Panel \, from \, list$ \\
+ 	\STATE $declare \, non-det \, variable \, to \, select \, Controller \, from \, list $ \\
+ 	\STATE $declare \, non-det \, variable \, to \, select \, Battery \, from \, list $ \\
+ 	\STATE $declare \, non-det \, variable \, to \, select \, Inverter \, from \, list $ \\ 	
  	\STATE $calculate \, E_{corrected}, \, E_{p} $ \\
@@
 
-The algorithm starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5).
-Following is necessary to define user requirements (house requirements and design definitions), from Line 6 to 8.
+Our algorithm starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5).
+After that, we define user requirements, i.e., house requirements and design definitions, from Lines 6 to 8.
+The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution.
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the assertion stated in Line 28; if that happens, then our algorithm has found an optimum solution, stating that the automatic verification reached a \textit{SAT} (satisfiable) condition.
+The algorithm uses non-deterministic variables to choose one specific data from a list of PV panels, controllers, batteries and inverters (Lines 10 to 13).
+That procedure ensures that the automated verification checks all possibilities of items from each equipment, and combine them to assemble a feasible PV solution, which meets the user requirements.
 
-The loop-FOR started at line 9 controls the try to get the lowest cost to the PV solution.
-It starts with cost of $zero$ and stops only when the algorithm finds a feasible solution which cost breaks the $assert$ of Line 28.
-When this happens, then the algorithm found the optimum solution and we say that the automatic verification reached a \textit{SAT} (satisfiability) condition.
-The algorithm uses non-deterministic variables to pick one specific data from a list of PV panels, controllers, batteries and inverters (Lines 10 to 13).
-That procedure ensures that the automated verification will try all the possibilities of item from each equipment, and combine them in order to mount a feasible PV solution that meet the user requirements.
+Next, we use the equations described in Section~\ref{sec:sizing} \textcolor{red}{which equations?
+please be more specific?} to calculate the sizing variables (Lines 14 to 20).
+The directive \textit{assume} (from Line 21 to 25) ensures the compatibility of the chosen items from the list of equipment: the automatic verification uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20 in addition to the Line 18.
+Therefore, our algorithm reaches Line 27 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$.
 
-Next, using the equations described at Section~\ref{sec:sizing} are calculated the sizing necessary variables (Lines 14 to 20).
-The directive \textit{assume} (from Line 21 to 25) ensure the compatibility of the choose item from the list of equipment: the automatic verification uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20, and more the Line 18.
-Therefore, the algorithm reaches the Line 27 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$.
-
-If the algorithm do not find a feasible solution among the item of equipment that were inputted to the code, then the result is an \textit{UNSAT}, i.e., the program finish and do not find an solution.
+If our algorithm does not find a feasible solution among the item of equipment that were inputted to the code, then the result is an \textit{UNSAT}, i.e., the program finishes and does not find a solution.
 It indicates that was not possible to combine the itens of each equipment and create a feasible solution.
 
+\textcolor{red}{What are the main challenges for the verification part?}
+
+%---------------------------------------------------------------------------
 \section{Results and Discussion}
+%---------------------------------------------------------------------------
+
 We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}.

### 2019-04-24 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

@@
 The use of automated verification in PV systems is a recent subject with only a few initiatives. 
-Here we develop an optimization algorithm and report its preliminary results using four state-of-art software verifiers to optimize the sizing of a PV system, where commercial equipment data is part of the specification and the technical solution is conjugated with the financial analysis of the obtained sizing.
+Here we develop an optimization algorithm and report its preliminary results using three state-of-art software verifiers to optimize the sizing of a PV system, where commercial equipment data is part of the specification and the technical solution is conjugated with the financial analysis of the obtained sizing.
 Our proposal is unprecedented and interesting to streamline the design and analysis of PV systems. Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Cyber-Physical  Systems  (CPS)  are  “engineered systems  that  are built from, and depend upon, the seamless integration of computational  and  physical  components”~\cite{NSF2015}.
+During operation, such components must frequently adapt to the executing environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
+%Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
 
-\textcolor{red}{What is the relation of this paper with software engineering (SE)?}
+While some research efforts exist to enhance and optimize the software development processes for CPS, more investigation and discussion of better and more effective models is needed [Al-Jaroodi].
+Among the opportunities for enhancements there is the developing new techniques and tools to support CPS requirements gathering and analysis.
+The developed techniques need to be able to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
+In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
+Uncertainty and variability, at the same time, can be dealed with formal verification~\cite{NESSI}.
+Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
 
@@
 
-Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of PV systems~\cite{ClarkeHV18}.
-In this study, we review verification tools and related them to design and verify PV systems, which was uncommon in prior studies~\cite{abs-1811-09438}.
+Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of systems~\cite{ClarkeHV18}.
+Therefore, in the context of this proposal, a cyber-physical system, specifically a PV system, is the target.
+We review verification tools and related them to design and to verify PV systems, which was uncommon in prior studies~\cite{abs-1811-09438}.
 
@@
 Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
-Here we evaluate four state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t.
+Here we evaluate three state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t.
 user requirements.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Ultimate Automizer}
+% \subsection{Ultimate Automizer}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties.
+%Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties.
 The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement (CEGAR) scheme.
@@
 The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.
-
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}.
-Furthermore, four start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency.
+Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency.
 The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.
@@
 \hline
-UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
-\hline
+%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
+%\hline
 CPAchecker 1.8 (MathSAT 5.5.3) & SAT (65 minutes) & x4 \\

### 2019-04-25 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

@@
 We review verification tools and related them to design and to verify PV systems, which was uncommon in prior studies~\cite{abs-1811-09438}.
-
-To select an optimum combination to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system.
-An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}.
-Regarding power reliability, the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
-Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean?
-Remember that we have software engineering audience}.
-
-However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC).
-Here, one more time, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the maintenance or operational costs \textcolor{red}{cite a reference here}.
 
@@
 \end{equation}
+% -------------------------------------------------------
+\section{Optimum sizing of PV systems}
+% -------------------------------------------------------
+To select an optimum combination of compontntes from a PV system in order to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system.
+An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}.
+
+Regarding power reliability, the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
+Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean?
+Remember that we have software engineering audience}.
+
+However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC).
+Here, one more time, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
 
@@
 	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
-	\STATE $Violation \, check \, with \, \textbf{assert}(F_{obj} \geq HintCost)$ \\
+	\STATE $Violation \, check \, with \, \textbf{assert}(F_{obj} > HintCost)$ \\
   \ENDFOR
@@
 
-Next, we use the equations described in Section~\ref{sec:sizing} \textcolor{red}{which equations?
-please be more specific?} to calculate the sizing variables (Lines 14 to 20).
+Next, we use Eq.~(\ref{eq:Ecorrected}), Eq.~(\ref{eq:Ep}), Eq.~(\ref{eq:NTPmin}), Eq.~(\ref{eq:NPSmin}), Eq.~(\ref{eq:NPPmin}), Eq.~(\ref{eq:Cbank}), Eq.~(\ref{eq:Nbtotal}), Eq.~(\ref{eq:iscamb}), and Eq.~(\ref{eq:icmin}) to calculate the sizing variables (Lines 14 to 20).
 The directive \textit{assume} (from Line 21 to 25) ensures the compatibility of the chosen items from the list of equipment: the automatic verification uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20 in addition to the Line 18.
@@
 
-\textcolor{red}{What are the main challenges for the verification part?}
+\textcolor{red}{The main challenge for the verification part is to found a feasible solution (technically speaking, regarding the constraints and user requirements) that is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is inputted to the tool}.
 

### 2019-04-26 code/opt_PVcode_case2_rev2.c
updated code changing vsystem of case 2

@@ -1,0 +1,206 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_case2.c (case 2 = 915W, 4.88 kWh/day, 48V, 6h)
+ Author      : Alessandro
+ Version     : rev2 - April 2019
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
+// int Phouse = 915, Psurge = 980, Econsumption = 4880;
[…]

### 2019-04-26 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated ASE text

@@
 PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
-However, those tools are based on simulation models, which are employed before the system design is concluded; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+However, those tools are based on simulation models; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
@@
 
-The main contribution of this approach is to allow that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system, and the algorithm using automated verification, and written in language C, can find the best technical and financial result.
+The main contribution of this approach is to allow that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system, and the algorithm using automated verification, and written in language C, can find the best compromise between those two objectives (power reliability and system cost).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\section{Automated Verification}
 \label{sec:AutomatedVerification}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\textcolor{red}{Do we really need this section?
-Can't we just cite our technical report in arxiv?
-Remember that this is a software engineering conference.
-People are more interested in the software part.}
-
 The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
@@
 \hline
-CBMC 5.11 (MiniSat 2.2.1) & Out of Memory & Out of Memory \\
+\makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{UNKNOWN \\(Out of Memory)} & \makecell{UNKNOWN \\(Out of Memory)}\\
 \hline
-ESBMC 6.0.0 (Boolector 3.0.1) & Timeout & Timeout \\
+\makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{UNKNOWN \\(Timeout)} & \makecell{UNKNOWN \\(Timeout)} \\
 \hline
@@
 %\hline
-CPAchecker 1.8 (MathSAT 5.5.3) & SAT (65 minutes) & x4 \\
+\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (66.18 min) \\ Property violation line 195: \\NTP= 4 $\times$ 320W model (2S-2P)\\NBT= 4 $\times$ 105Ah model (2S-2P)\\ Controller 15A/100V\\Inverter 700VA, 48V \\ Total Cost: US\$ 2,643.00} & \makecell {SAT (35.41 min) \\ Property violation line 195:  \\NTP= 3 $\times$ 320W model (3S)\\NBT= 2 $\times$ 105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,200VA, 48V \\ Total Cost: US\$ 2,125.00}\\
 \hline
@@
 
+More experimentation will be performed with a larger number of case studies and to compare the result with some off-the-shelf software that focus on sizing and optimization (validation of the result).
+Besides, it will be inputted a larger number of components (panels, batteries, contollers and inverters) to the database (that is limited to 12 items right now).
+That will bring more complexity to the tool, however will ensure an even better optimization.
 % argument is your BibTeX string definitions and bibliography database(s)

### 2019-04-26 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

@@
 
-While some research efforts exist to enhance and optimize the software development processes for CPS, more investigation and discussion of better and more effective models is needed [Al-Jaroodi].
+While some research efforts exist to enhance and optimize the software development processes for CPS, more investigation and discussion of better and more effective models is needed~\cite{Al-Jaroodi2016}.
 Among the opportunities for enhancements there is the developing new techniques and tools to support CPS requirements gathering and analysis.
@@
 Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of systems~\cite{ClarkeHV18}.
-Therefore, in the context of this proposal, a cyber-physical system, specifically a PV system, is the target.
-We review verification tools and related them to design and to verify PV systems, which was uncommon in prior studies~\cite{abs-1811-09438}.
+%Therefore, in the context of this proposal, a CPS, specifically a PV system, is the target.
+We review verification tools and related them to design and to PV systems verification, which was uncommon in prior studies~\cite{abs-1811-09438}.
 
-The main contribution of this approach is to allow that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system, and the algorithm using automated verification, and written in language C, can find the best compromise between those two objectives (power reliability and system cost).
-
-\textcolor{red}{We need to make our contributions stronger.
+\textcolor{red}{The main contributions of this approach is (1) to address a CPS, allowing that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system together with user requirements and environment constraints, and the algorithm using automated verification, written in language C, can find the best compromise between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; and (2), to evaluate different state-of-art software verifiers in order to obtain the better performance.
+The use of automated verication in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.}
+%
+%\textcolor{red}{We need to make our contributions stronger.
 Why the SE community would be interested in this paper?
@@
 we don't need to make questions but we don't need to answer all of them.}
-
+%
 %, using non-deterministic variables and exploring the design-space
@@
 
-Regarding power reliability, the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
+Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}.
+%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
 Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean?
@@
 However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC).
-Here, one more time, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+Here, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
 

### 2019-04-26 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{INTRODUCTION}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.
-PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
+; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
  However, those tools are based on simulation models; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
@@
 
-\textcolor{red}{The main contributions of this approach is (1) to address a CPS, allowing that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system together with user requirements and environment constraints, and the algorithm using automated verification, written in language C, can find the best compromise between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; and (2), to evaluate different state-of-art software verifiers in order to obtain the better performance.
+\textcolor{red}{The main contributions of this approach is (1) to address a CPS, allowing that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the proposed tool together with user requirements and environment constraints, and the algorithm using automated verification (written in language C), can find the best compromise between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; and (2), to evaluate different state-of-art software verifiers in order to obtain the better performance.
 The use of automated verication in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Verification}
+\section{BACKGROUND}
+\label{sec:AutomatedVerification}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Automated Verification}
 \label{sec:AutomatedVerification}
@@
 user requirements.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CBMC}
+\subsubsection{CBMC}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{ESBMC}
+\subsubsection{ESBMC}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CPAchecker}
+\subsubsection{CPAchecker}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sizing Stand-alone Solar PV Systems}
+\subsection{Sizing Stand-alone Solar PV Systems}
 \label{sec:sizing}
@@
 % -------------------------------------------------------
-\section{Optimum sizing of PV systems}
+\subsection{Optimum sizing of PV systems}
 % -------------------------------------------------------
@@
 Here, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
-
 %------------------------------------------------------
-\section{Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
+\section{APPLYING AUTOMATED VERIFICATION TO OPTIMAL SIZING OF STAND-ALONE PV SYSTEMS}
+%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
 %------------------------------------------------------
@@
 \textcolor{red}{The main challenge for the verification part is to found a feasible solution (technically speaking, regarding the constraints and user requirements) that is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is inputted to the tool}.
-
 %---------------------------------------------------------------------------
-\section{Results and Discussion}
+\section{RESULTS AND DISCUSSION}
 %---------------------------------------------------------------------------
-
 We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}.

### 2019-04-27 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
changed title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
updated abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+ \renewcommand{\baselinestretch}{0.97}
+
 \begin{document}
 
-\title{Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
+\title{Verifying Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
 % \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 Software verification has experienced significant progress over the last two decades. 
-Currently, there exist various software verifies that are able to solve intricate real-world problems, e.g., to design and verify renewable and stand-alone solar photovoltaic (PV) systems.
-Currently around $1$ billion of people do not have electrical energy; energy poverty alleviation has become an important political issue. 
+Currently, there exist various software verifies that are able to formally check real-world 
+applications from energy systems, telecommunications, digital control and medical devices.
+Our main focus here is on renewable and stand-alone solar photovoltaic (PV) systems. 
+Currently we have approximately $1$ billion of people who do not have electrical energy; 
+energy poverty alleviation has become an important political issue. 
 %Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
 Particular attention is given to renewables and PV systems. 
-Unfortunately, existing tools available to evaluate PV designs are mainly based on simulations that do not cover all aspects of the design space.
-The use of automated verification in PV systems is a recent subject with only a few initiatives. 
-Here we develop an optimization algorithm and report its preliminary results using three state-of-art software verifiers to optimize the sizing of a PV system, where commercial equipment data is part of the specification and the technical solution is conjugated with the financial analysis of the obtained sizing.
-Our proposal is unprecedented and interesting to streamline the design and analysis of PV systems. Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
+Unfortunately, state-of-the-art tools available to evaluate PV designs are mainly based on simulations, 
+which do not cover all aspects of the design-space. 
+The application of automated verification to PV systems is a very recent subject with only a few initiatives. 
+Here we develop an optimization algorithm and report preliminary results using three state-of-art software 
+verifiers with the goal of optimizing the sizing of a PV system. Commercial equipment data is part of our specification 
+and the technical solution is derived from financial analysis of the obtained sizing. Our proposal is novel and 
+unprecedented to streamline the design and analysis of PV systems. 
+Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
 \end{abstract}

### 2019-04-27 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Currently, there exist various software verifies that are able to formally check real-world 
-applications from energy systems, telecommunications, digital control and medical devices.
+applications from energy systems, telecommunications, digital control, and medical devices.
 Our main focus here is on renewable and stand-alone solar photovoltaic (PV) systems. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Cyber-Physical  Systems  (CPS)  are  “engineered systems  that  are built from, and depend upon, the seamless integration of computational  and  physical  components”~\cite{NSF2015}.
-During operation, such components must frequently adapt to the executing environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
+
+\textcolor{red}{Could you please cite this paper?}
+
+\textcolor{red}{Software Engineering Meets Control Theory: https://ieeexplore.ieee.org/document/7194659/}
+
+Cyber-Physical Systems  (CPS) are €œengineered systems, which are built from, and depend upon, 
+the seamless integration of computational  and  physical  components€~\cite{NSF2015}. 
+During operation, such components must frequently adapt to the executing environment changes 
+faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
+in a controlled and safe way, thus posing novel technical challenges for the software engineering 
+of services and applications for CPS~\cite{Metzger2014}.
 %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
 
-While some research efforts exist to enhance and optimize the software development processes for CPS, more investigation and discussion of better and more effective models is needed~\cite{Al-Jaroodi2016}.
-Among the opportunities for enhancements there is the developing new techniques and tools to support CPS requirements gathering and analysis.
-The developed techniques need to be able to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
-In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
-Uncertainty and variability, at the same time, can be dealed with formal verification~\cite{NESSI}.
+While some research efforts do exist to enhance and optimize the software development processes for CPS, 
+further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
+Among the opportunities for enhancements, there exists the need for developing new techniques and tools to support CPS 
+requirements gathering and analysis. The developed techniques need to deal with predefined requirements enforced 
+by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification 
+and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. 
+Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. 
 Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. 
-Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, the number of people without electricity access 
+fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}. 
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) 
+in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; 
+specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
 
-In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
+In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., 
+RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
 ; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
- However, those tools are based on simulation models; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+ However, those tools are based on simulations; they have the drawback of an incomplete coverage 
+ since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
@@
 
-\textcolor{red}{The main contributions of this approach is (1) to address a CPS, allowing that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the proposed tool together with user requirements and environment constraints, and the algorithm using automated verification (written in language C), can find the best compromise between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; and (2), to evaluate different state-of-art software verifiers in order to obtain the better performance.
-The use of automated verication in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.}
+\textcolor{red}{There is no connection between both paragraphs.}
+
+Our major novel contributions here are (1) to address a CPS, 
+allowing that a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) 
+can be fed to the proposed verification tool together with user requirements and environment constraints, 
+and our verification algorithm based on software model checking can find the best compromise 
+between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; 
+and (2), to evaluate different state-of-art software verifiers with the goal of obtaining the best verification performance. 
+Note that the use of automated verification in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, 
+and specifically their use in PV sizing is unprecedented.
 %

### 2019-04-27 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) 
-in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; 
+in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed \textcolor{red}{Add reference here}; 
 specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
@@
 ; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
- However, those tools are based on simulations; they have the drawback of an incomplete coverage 
+ However, those tools are based on simulation; they have the drawback of an incomplete coverage 
  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-
-Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of systems~\cite{ClarkeHV18}.
+Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}.
 %Therefore, in the context of this proposal, a CPS, specifically a PV system, is the target.
@@
 
-\textcolor{red}{There is no connection between both paragraphs.}
+\textcolor{red}{We should rewrite the following paragraph as follows.}
+
+\textcolor{red}{In summary, this paper makes the following original contributions.
+\begin{itemize}
+\item First contribution.
+\item Second contribution.
+\end{itemize}
+}
+
+\textcolor{red}{Address a CPS is not a contribution...}
 

### 2019-04-27 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textcolor{red}{Since this is a software engineering conference, the reviewers already know about this basic background. You could further reduce the following paragraph.}
+
 Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.

### 2019-04-27 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$).
-For night hours or rainy days, we need to hold batteries where power can be stored and used.
-The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}.
+For night hours or rainy days, we hold batteries where power can be stored and used.
+The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
 The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
@@
 
-The sizing check will be performed by the proposed tool, and this stage ensures that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, that is the most common nowadays.
+Here the sizing check will be automatically performed by our proposed method; 
+this stage will ensure that the system meets the standard project steps related 
+to critical period solar energy method~\cite{Pinho} and 
+adopting MPPT (Maximum Power Point Tracking) charge controller, 
+which is the most common one in practice. 
 %
-Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
 \begin{equation}
@@
 
-We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, as defined by~\eqref{eq:Ep}.
-
+We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
+%
 \begin{equation}
@@
 
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV systems will be deployed; the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
+\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
+the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
 %
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed by~\eqref{eq:NTPmin} as
+The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
+%
 \begin{equation}
@@
 
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.  
+Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
 %
@@
 \label{eq:NPSmin}
-\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}}
+\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}},
 \end{equation}
@@
 %
-Regarding the batteries, we must first define the total capacity of the battery bank, as described by~\eqref{eq:Cbank} as
+Regarding the batteries, we must first define the total capacity of the battery bank, which can be described as
 \begin{equation}
@@
 \noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% at this paper).
+$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
 %
-Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}. 
+Secondly, the total (minimum) number of batteries is computed as 
 \begin{equation}
@@
 
-Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage: 
+Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
 \begin{equation}
@@
 
-Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
+The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature \textcolor{red}{why? explain the reason here... since...} as 
 %
@@
 
-The controller must meet the maximum current from the PV array given by \eqref{eq:icmin} and \eqref{eq:icicmin}.
+The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin}.
 \begin{equation}
@@
 The sizing project check of the inverter is carried out by means of three equations.
-Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
-Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$).
-Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
+Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
+Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
+Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
 %
@@
 % -------------------------------------------------------
-To select an optimum combination of compontntes from a PV system in order to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system.
+
+To select an optimum \textcolor{red}{optimum or optimal?} combination of components from a PV system to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system.
 An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}.

### 2019-04-28 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

@@
 Particular attention is given to renewables and PV systems. 
-Unfortunately, state-of-the-art tools available to evaluate PV designs are mainly based on simulations, 
-which do not cover all aspects of the design-space. 
+Unfortunately, state-of-the-art tools available to evaluate PV designs are mainly based on simulations, which do not cover all aspects of the design-space. 
 The application of automated verification to PV systems is a very recent subject with only a few initiatives.
-Here we develop an optimization algorithm and report preliminary results using three state-of-art software 
-verifiers with the goal of optimizing the sizing of a PV system. Commercial equipment data is part of our specification 
-and the technical solution is derived from financial analysis of the obtained sizing. Our proposal is novel and 
-unprecedented to streamline the design and analysis of PV systems. 
+Here we develop an optimization algorithm and report preliminary results using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system.
+Commercial equipment data is part of our specification and the technical solution is derived from financial analysis of the obtained sizing.
+Our proposal is novel and unprecedented to streamline the design and analysis of PV systems.
 Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
@@
 
-Cyber-Physical Systems  (CPS) are €œengineered systems, which are built from, and depend upon, 
-the seamless integration of computational  and  physical  components€~\cite{NSF2015}. 
+Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
+the seamless integration of computational  and  physical  components~\cite{NSF2015}. 
 During operation, such components must frequently adapt to the executing environment changes 
 faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
-in a controlled and safe way, thus posing novel technical challenges for the software engineering 
-of services and applications for CPS~\cite{Metzger2014}.
+in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
 %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
 
-While some research efforts do exist to enhance and optimize the software development processes for CPS, 
-further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
-Among the opportunities for enhancements, there exists the need for developing new techniques and tools to support CPS 
-requirements gathering and analysis. The developed techniques need to deal with predefined requirements enforced 
-by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification 
-and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. 
+While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+Among the opportunities for enhancements, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis.
+The developed techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
+In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
 Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
@@
 
-In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., 
-RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
+In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
 ; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
- However, those tools are based on simulation; they have the drawback of an incomplete coverage 
- since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+ However, those tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}.

### 2019-04-29 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

@@
 and our verification algorithm based on software model checking can find the best compromise 
-between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; 
+between two objectives: power reliability and system cost, i.e., linking the optimal solution in technical and economical terms; 
 and (2), to evaluate different state-of-art software verifiers with the goal of obtaining the best verification performance. 
@@
 
-The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature \textcolor{red}{why? explain the reason here... since...} as 
+The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, \textcolor{red}{because the field temperature is higher that the nominal or laboratory temperature, and PV system is temperature dependent,} as
 %
@@
 % -------------------------------------------------------
-\subsection{Optimum sizing of PV systems}
+\subsection{Optimal sizing of PV systems}
 % -------------------------------------------------------
 
-To select an optimum \textcolor{red}{optimum or optimal?} combination of components from a PV system to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system.
+To select an optimal combination of components from a PV system to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system.
 An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}.
@@
 The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the assertion stated in Line 28; if that happens, then our algorithm has found an optimum solution, stating that the automatic verification reached a \textit{SAT} (satisfiable) condition.
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the assertion stated in Line 28; if that happens, then our algorithm has found an optimal solution, stating that the automatic verification reached a \textit{SAT} (satisfiable) condition.
 The algorithm uses non-deterministic variables to choose one specific data from a list of PV panels, controllers, batteries and inverters (Lines 10 to 13).

### 2019-04-29 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

@@
 Our proposal is novel and unprecedented to streamline the design and analysis of PV systems.
-Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
+Experimental results show that \textcolor{red}{using the verifier CPAchecker is possible to obtain the optimal PV system sizing of two different case studies from a list of 12 different equipment in a acceptable run-time.}
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\textcolor{red}{Could you please cite this paper?}
-
-\textcolor{red}{Software Engineering Meets Control Theory: https://ieeexplore.ieee.org/document/7194659/}
+\textcolor{red}{Software’s pervasiveness in every context of life places new challenges on Software Engineering.
+Highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.}
 
@@
 
-\textcolor{red}{We should rewrite the following paragraph as follows.}
-
 \textcolor{red}{In summary, this paper makes the following original contributions.
@@
 \item First contribution.
-\item Second contribution.
+The use of automated verification in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.
+Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed verification tool together with user requirements and environment constraints, and our verification algorithm based on software model checking can find the optimal solution in technical and economical terms.
+\item Second contribution. To evaluate different state-of-art software verifiers with the goal of obtaining the best verification performance.
 \end{itemize}
 }
-
-\textcolor{red}{Address a CPS is not a contribution...}
-
-Our major novel contributions here are (1) to address a CPS, 
-allowing that a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) 
-can be fed to the proposed verification tool together with user requirements and environment constraints, 
-and our verification algorithm based on software model checking can find the best compromise 
-between two objectives: power reliability and system cost, i.e., linking the optimal solution in technical and economical terms; 
-and (2), to evaluate different state-of-art software verifiers with the goal of obtaining the best verification performance. 
-Note that the use of automated verification in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, 
-and specifically their use in PV sizing is unprecedented.
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\textcolor{red}{Since this is a software engineering conference, the reviewers already know about this basic background. You could further reduce the following paragraph.}
-
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
+\textcolor{red}{Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
+Here we evaluate three state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t.
+user requirements.}
+%Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
 Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
@@
 ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end based on clang that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+%ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
 ESBMC's verification flow can be summarized in three stages: (i) a front-end based on clang that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; (iii) \textcolor{red}{we should describe the symbolic execution with incremental solving phase here...} and finally (iv) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Automatic program verification requires a choice between precision and efficiency. The
-more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was
-reflected in two major approaches to static verification: program analysis and model
-checking.
+%Automatic program verification requires a choice between precision and efficiency. 
+The more precise a method, the fewer false positives it will produce, but also the more expensive it is.%, and thus applicable to fewer programs. 
+Historically, this trade-off was reflected in two major approaches: program analysis and model checking.
 In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
@@
 The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
-Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+Related to the architecture, the central data structure is a set of control-flow automata (CFA).
+%, which consists of control-flow locations and control-flow edges.
 The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
@@
 Remember that we have software engineering audience}.
-
 However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC).
@@
 %------------------------------------------------------
-
 Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to optimize stand-alone PV systems using automated verification. 
@@
 The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.
-
 All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
 The experiments were performed with a predefined timeout of 240 minutes.
+
+Only CPAchecker could present the optimal sizing of the two case studies: the result came in 66 minutes and 35 minutes, respectively.
+%, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
+CBMC and ESBMC had UNKNOWN result (timeout or out of memory).
 
@@
 %\hline
-\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (66.18 min) \\ Property violation line 195: \\NTP= 4 $\times$ 320W model (2S-2P)\\NBT= 4 $\times$ 105Ah model (2S-2P)\\ Controller 15A/100V\\Inverter 700VA, 48V \\ Total Cost: US\$ 2,643.00} & \makecell {SAT (35.41 min) \\ Property violation line 195:  \\NTP= 3 $\times$ 320W model (3S)\\NBT= 2 $\times$ 105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,200VA, 48V \\ Total Cost: US\$ 2,125.00}\\
+\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (66.18 min) \\ Property violation line 195: \\NTP=4$\times$320W model (2S-2P)\\NBT=4$\times$105Ah model (2S-2P)\\ Controller 15A/100V\\Inverter 700VA, 48V \\ Total Cost=US\$ 2,643.00} & \makecell {SAT (35.41 min) \\ Property violation line 195:  \\NTP=3$\times$320W model (3S)\\NBT=2$\times$105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,200VA, 48V \\ Total Cost=US\$ 2,125.00}\\
 \hline
@@
 
-More experimentation will be performed with a larger number of case studies and to compare the result with some off-the-shelf software that focus on sizing and optimization (validation of the result).
-Besides, it will be inputted a larger number of components (panels, batteries, contollers and inverters) to the database (that is limited to 12 items right now).
-That will bring more complexity to the tool, however will ensure an even better optimization.
+More experimentation will be performed with more case studies and to compare the result with some off-the-shelf software that focus on sizing and optimization.
+Besides, it will be inputted a larger number of components (panels, batteries, controllers and inverters) to the database.
 % argument is your BibTeX string definitions and bibliography database(s)

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed title, abstract and introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\title{Verifying Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
+\title{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
 % \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 \begin{abstract}
-Software verification has experienced significant progress over the last two decades. 
-Currently, there exist various software verifies that are able to formally check real-world 
-applications from energy systems, telecommunications, digital control, and medical devices.
-Our main focus here is on renewable and stand-alone solar photovoltaic (PV) systems. 
-Currently we have approximately $1$ billion of people who do not have electrical energy; 
-energy poverty alleviation has become an important political issue. 
-%Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
-Particular attention is given to renewables and PV systems. 
-Unfortunately, state-of-the-art tools available to evaluate PV designs are mainly based on simulations, which do not cover all aspects of the design-space. 
-The application of automated verification to PV systems is a very recent subject with only a few initiatives.
-Here we develop an optimization algorithm and report preliminary results using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system.
-Commercial equipment data is part of our specification and the technical solution is derived from financial analysis of the obtained sizing.
-Our proposal is novel and unprecedented to streamline the design and analysis of PV systems.
-Experimental results show that \textcolor{red}{using the verifier CPAchecker is possible to obtain the optimal PV system sizing of two different case studies from a list of 12 different equipment in a acceptable run-time.}
+Software verification is on the core of many automated formal synthesis techniques;
+it is used to formally check whether an intricate property hols for a given software system. 
+Our main focus here is on using software verifiers to formally synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems. 
+There exist various state-of-the-art tools to evaluate PV designs but  they are mainly based on simulations, which do not cover all aspects of the design-space. 
+The application of software verification to synthesize PV systems is a very recent subject with only a few initiatives. 
+Here we develop and evaluate an automated formal synthesis algorithm and report preliminary results 
+using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system. 
+Commercial equipment data is part of our specification and the technical solution is derived 
+from financial analysis of the obtained sizing. Our proposed synthesis method is novel and 
+unprecedented to streamline the design of PV systems. 
+Experimental results show that our method allied to a software verifier (CPAchecker) 
+is able to synthesize,in an acceptable run-time, the optimal PV system sizing of two different case studies from a list of $12$ 
+different equipment.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textcolor{red}{Software’s pervasiveness in every context of life places new challenges on Software Engineering.
-Highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.}
 
@@
 %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
+Software pervasiveness in every context of life also places new challenges in Software Engineering. 
+In particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
 
@@
 
-In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
+In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
 ; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
@@
 Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}.
-%Therefore, in the context of this proposal, a CPS, specifically a PV system, is the target.
-We review verification tools and related them to design and to PV systems verification, which was uncommon in prior studies~\cite{abs-1811-09438}.
 
-\textcolor{red}{In summary, this paper makes the following original contributions.
-\begin{itemize}
-\item First contribution.
-The use of automated verification in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.
-Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed verification tool together with user requirements and environment constraints, and our verification algorithm based on software model checking can find the optimal solution in technical and economical terms.
-\item Second contribution. To evaluate different state-of-art software verifiers with the goal of obtaining the best verification performance.
-\end{itemize}
-}
+In summary, this paper makes the following original contributions for synthesizing optimal sizing of stand-alone PV systems.
+Firstly, the use of automated formal verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, 
+and specifically their use in PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) 
+can be fed to the proposed synthesis method together with user requirements and environment constraints, 
+and our synthesis algorithm based on software model checking can find the optimal solution in technical and economical terms.
+Secondly, we evaluate different state-of-art software verifiers with the goal of obtaining the best synthesis performance for PV systems.
 %

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed title, abstract and introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Software verification is on the core of many automated formal synthesis techniques;
-it is used to formally check whether an intricate property hols for a given software system. 
-Our main focus here is on using software verifiers to formally synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems. 
-There exist various state-of-the-art tools to evaluate PV designs but  they are mainly based on simulations, which do not cover all aspects of the design-space. 
+it is used to formally check whether an intricate property hols for a given system. 
+Here our main focus is to formally synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems
+using software model checking techniques. There exist various state-of-the-art tools to evaluate 
+PV designs but  they are mainly based on simulations, which do not cover all aspects of the design-space. 
 The application of software verification to synthesize PV systems is a very recent subject with only a few initiatives. 
@@
 using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system. 
-Commercial equipment data is part of our specification and the technical solution is derived 
+Commercial equipment data is provided to our synthesis engine and the candidate solution is derived 
 from financial analysis of the obtained sizing. Our proposed synthesis method is novel and 
 unprecedented to streamline the design of PV systems. 
-Experimental results show that our method allied to a software verifier (CPAchecker) 
-is able to synthesize,in an acceptable run-time, the optimal PV system sizing of two different case studies from a list of $12$ 
-different equipment.
+Experimental results show that our synthesis method based on software verification is able to synthesize, 
+in an acceptable run-time, the optimal PV system sizing of two different case studies.
 \end{abstract}

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
- \renewcommand{\baselinestretch}{0.97}
+ \renewcommand{\baselinestretch}{0.96}
 
@@
 \begin{abstract}
-Software verification is on the core of many automated formal synthesis techniques;
-it is used to formally check whether an intricate property hols for a given system. 
-Here our main focus is to formally synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems
-using software model checking techniques. There exist various state-of-the-art tools to evaluate 
-PV designs but  they are mainly based on simulations, which do not cover all aspects of the design-space. 
-The application of software verification to synthesize PV systems is a very recent subject with only a few initiatives. 
-Here we develop and evaluate an automated formal synthesis algorithm and report preliminary results 
+Currently, there exist various state-of-the-art tools to design PV but they are mainly based on simulations, which do not cover all aspects of the design-space. 
+We present a sound and automated approach to synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems.
+The application of automated formal verification to synthesize PV systems is a very recent subject with only a few initiatives. 
+Here we develop and evaluate an automated formal synthesis approach based on program synthesis and report preliminary results 
 using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system. 
@@
 unprecedented to streamline the design of PV systems. 
-Experimental results show that our synthesis method based on software verification is able to synthesize, 
-in an acceptable run-time, the optimal PV system sizing of two different case studies.
+Experimental results show that our synthesis method, based on software model checking as our verification engine, 
+is able to synthesize, in an acceptable run-time, the optimal PV system sizing of two different case studies.
 \end{abstract}
 
-\begin{IEEEkeywords}
-automated verification, model checking, optimization, electrical systems and solar photovoltaic systems.
-\end{IEEEkeywords}
+%\begin{IEEEkeywords}
+%automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
+%\end{IEEEkeywords}
 
@@
 %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
-Software pervasiveness in every context of life also places new challenges in Software Engineering. 
-In particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
+Software pervasiveness in every context of life also places new challenges. 
+In particular, highly dynamic environments, rapidly changing requirements, 
+unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
 
-While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
-Among the opportunities for enhancements, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis.
-The developed techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
-In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
-Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
+While some research efforts do exist to enhance and optimize the software development processes for CPS, 
+further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
+Among the opportunities for enhancements, there exists the need for developing new techniques and tools to support 
+CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS. 
+The developed techniques need to deal with predefined requirements enforced by the nature and inherited constraints 
+of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, 
+correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. 
 Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
@@
 
-In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
+In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
 ; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
@@
 Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}. 
+Here, we use program synthesis for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+In particular, given a correctness specification $\sigma$, our method uses that as starting point and then incrementally produce a 
+sequence of candidate solutions that satisfy $\sigma$, by integrating software model checking techniques.
 
-In summary, this paper makes the following original contributions for synthesizing optimal sizing of stand-alone PV systems.
-Firstly, the use of automated formal verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, 
+This paper makes the following original contributions.
+Firstly, the use of automated software verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, 
 and specifically their use in PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) 
@@
 and our synthesis algorithm based on software model checking can find the optimal solution in technical and economical terms.
-Secondly, we evaluate different state-of-art software verifiers with the goal of obtaining the best synthesis performance for PV systems.
-%
-%\textcolor{red}{We need to make our contributions stronger.
-Why the SE community would be interested in this paper?
-What are the main open problems we need them to solve here?
-Remember that this is a paper for new ideas...
-we don't need to make questions but we don't need to answer all of them.}
-%
-%, using non-deterministic variables and exploring the design-space
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Secondly, we evaluate different state-of-art software verifiers with the goal of obtaining the best performance for synthesizing optimal PV systems.
+
+%-----------------------------------------------------------
 \section{BACKGROUND}
 \label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Automated Verification}
-\label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textcolor{red}{Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
-Here we evaluate three state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t.
-user requirements.}
-%Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
-Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
-Here we evaluate three state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t.
-user requirements.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
-CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
-If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
-CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end based on clang that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-%ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end based on clang that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; (iii) \textcolor{red}{we should describe the symbolic execution with incremental solving phase here...} and finally (iv) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-%ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-%This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+%-----------------------------------------------------------
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Ultimate Automizer}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties.
-The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement (CEGAR) scheme.
-CEGAR is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check and refinement~\cite{CEGAR}.
-In each iteration, Automizer picks a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible.
-If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility.
-The predicates are a sequence of interpolants since each predicate "interpolates" between a set of reachable states and a set of states from which it cannot reach the error.
-In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed.
-It is used automata to represent sets of traces.
-The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.
+%-----------------------------------------------------------
+\subsection{Program Synthesis}
+\label{sec:ProgramSynthesis}
+%-----------------------------------------------------------
+
+The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
+In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$~\cite{Abateetal2017}.
+As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
+Counter-Example Guided Inductive Synthesis (CEGIS) represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is shown in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.
+
+The correctness specification $\sigma$ provided to a program synthesizer is of the form $\exists \vec{F} .
+\forall \vec{x}.
+\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free formula typically supported by SMT solvers.
+The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
+The phases {\sc Synthesize} and {\sc Verify}, in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis},  interact via a finite set of test vectors {\sc inputs} that is incrementally updated.
+Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
+If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If this is the case, then the algorithm terminates; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Automatic program verification requires a choice between precision and efficiency. 
-The more precise a method, the fewer false positives it will produce, but also the more expensive it is.%, and thus applicable to fewer programs. 
-Historically, this trade-off was reflected in two major approaches: program analysis and model checking.
-In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
-The CPA formalism provides an interface for the definition of program analyses.
-Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
-Related to the architecture, the central data structure is a set of control-flow automata (CFA).
-%, which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
-Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\columnwidth]{fig2.jpg}
+	\caption{CounterExample Guided Inductive Synthesis (CEGIS).}
+	\label{Counter-Example-Guided-Inductive-Synthesis}
+\end{figure}
+
+One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
+Given that the full set of inputs $\mathcal{D}$ is finite, this means that the refinement loop can only iterate over a finite number of times; however, $\mathcal{D}$ can represent a large number of elements for the finite set $\text{\sc inputs}$.
+In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}.
+In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig.
+\ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.
+
+Nowadays, program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based automated reasoning~\cite{Sharma14}.
+Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
 

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, \textcolor{red}{because the field temperature is higher that the nominal or laboratory temperature, and PV system is temperature dependent,} as
+The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as
 %
@@
 Remember that we have software engineering audience}.
-However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC).
+However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC).
 Here, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
 %------------------------------------------------------
-\section{APPLYING AUTOMATED VERIFICATION TO OPTIMAL SIZING OF STAND-ALONE PV SYSTEMS}
+\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
 %Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
 %------------------------------------------------------
-Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to optimize stand-alone PV systems using automated verification. 
+Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to symthesize stand-alone PV systems using software model checking. 
 %
  \begin{algorithm}
- \caption{Optimization algorithm}
+ \caption{Synthesis algorithm}
  \begin{algorithmic}[1]
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE $initialize \, variables$ \\
-  \STATE $declare \, list \, of \, PV \, panels \, data \, and \, cost $ \\
-  \STATE $declare \, list \, of \, controllers \, data \, and \, cost $ \\
-  \STATE $declare \, list \, of \, batteries \, data \,  and \, cost $ \\
-  \STATE $declare \, list \, of \, inverters \, data \,  and \, cost $ \\
-  \STATE $declare \, the \, maximum \, cost \, possible \, MaxCost $  \\
-  \STATE $declare \, power \, demand, \, power \, peak, \, energy \, consumption $ \\
-  \STATE $declare \, battery\,  autonomy, deep \, of \, discharge, AC \, voltage$ \\
+  \STATE Initialize variables \\
+  \STATE Declare list of PV panels data and cost \\
+  \STATE Declare list of controllers data and cost \\
+  \STATE Declare list of batteries data and cost \\
+  \STATE Declare list of inverters data and cost \\
+  \STATE Declare the maximum possible cost $MaxCost$  \\
+  \STATE Declare power demand, power peak, energy consumption \\
+  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
   \FOR {$HintCost=0$ to $MaxCost$}
- 	\STATE $declare \, non-det \, variable \, to \, select \, Panel \, from \, list$ \\
- 	\STATE $declare \, non-det \, variable \, to \, select \, Controller \, from \, list $ \\
- 	\STATE $declare \, non-det \, variable \, to \, select \, Battery \, from \, list $ \\
- 	\STATE $declare \, non-det \, variable \, to \, select \, Inverter \, from \, list $ \\ 	
- 	\STATE $calculate \, E_{corrected}, \, E_{p} $ \\
-	\STATE $calculate \, N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
- 	\STATE $calculate \, C_{bank}$ \\
-	\STATE $calculate \, N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
-	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{c})$ \\
- 	\STATE $calculate \, I_{sc,amb}$ \\
- 	\STATE $calculate \, I_{c,min}$ \\
- 	\STATE $requeriment \, enforced \, by \, \textbf{assume}(I_{c})$ \\
-	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{in}DC)$ \\
-	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{out}AC)$ \\
-	\STATE $requeriment \, enforced \, by \, \textbf{assume}(Demand)$ \\
-	\STATE $requeriment \, enforced \, by \, \textbf{assume}(P_{surge})$ \\
-	\STATE $non-det \, variables \, hold \, feasible \, equipment \, and \ cost $ \\
+ 	\STATE Declare nondet variable to select PV Panel from list \\
+ 	\STATE Declare nondet variable to select Controller from list \\
+ 	\STATE Declare nondet variable to select Battery from list \\
+ 	\STATE Declare nondet variable to select Inverter from list \\ 	
+ 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
+	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
+ 	\STATE Calculate $C_{bank}$ \\
+	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
+	\STATE Requeriment enforced by \textbf{assume}$(V_{c})$ \\
+ 	\STATE Calculate $I_{sc,amb}$ \\
+ 	\STATE Calculate $I_{c,min}$ \\
+ 	\STATE Requeriment enforced by \textbf{assume}$(I_{c})$ \\
+	\STATE Requeriment enforced by \textbf{assume}$(V_{in}DC)$ \\
+	\STATE Requeriment enforced by \textbf{assume}$(V_{out}AC)$ \\
+	\STATE Requeriment enforced by \textbf{assume}$(Demand)$ \\
+	\STATE Requeriment enforced by \textbf{assume}$(P_{surge})$ \\
+	\STATE non-det variables hold feasible equipment and cost  \\
 	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
-	\STATE $Violation \, check \, with \, \textbf{assert}(F_{obj} > HintCost)$ \\
+	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
   \ENDFOR
@@
 
-Our algorithm starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5).
+Our synthesis algorithm starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5).
 After that, we define user requirements, i.e., house requirements and design definitions, from Lines 6 to 8.
 The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the assertion stated in Line 28; if that happens, then our algorithm has found an optimal solution, stating that the automatic verification reached a \textit{SAT} (satisfiable) condition.
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the assertion stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the automatic verification reached a \textit{SAT} (satisfiable) condition.
 The algorithm uses non-deterministic variables to choose one specific data from a list of PV panels, controllers, batteries and inverters (Lines 10 to 13).
@@
 
-If our algorithm does not find a feasible solution among the item of equipment that were inputted to the code, then the result is an \textit{UNSAT}, i.e., the program finishes and does not find a solution.
+If our algorithm does not find a feasible solution among the item of equipment that were provided to our synthesis algorithm, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
 It indicates that was not possible to combine the itens of each equipment and create a feasible solution.
-
-\textcolor{red}{The main challenge for the verification part is to found a feasible solution (technically speaking, regarding the constraints and user requirements) that is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is inputted to the tool}.
+The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm.
+\textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?}
 %---------------------------------------------------------------------------
-\section{RESULTS AND DISCUSSION}
+\section{Results and Discussion}
 %---------------------------------------------------------------------------

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?}
+
+\textcolor{red}{Could you please reinforce here that our approach is sound and completely automated?}
+
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}.
-Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency.
+
+We have performed two case studies to evaluate our proposed synthesis approach as described in Table~\ref{tab1}.
+Furthermore, three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare our approach effectiveness and efficiency.
 The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.
 All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
-The experiments were performed with a predefined timeout of 240 minutes.
+The experiments were performed with a predefined timeout of $240$ minutes.
 
@@
 %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
-CBMC and ESBMC had UNKNOWN result (timeout or out of memory).
+CBMC and ESBMC produced UNKNOWN result (timeout or out of memory).
 
@@
 
-More experimentation will be performed with more case studies and to compare the result with some off-the-shelf software that focus on sizing and optimization.
-Besides, it will be inputted a larger number of components (panels, batteries, controllers and inverters) to the database.
+For future wore, we will perform additional experiments using other case studies and also compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization. 
+Furthermore, we will be provide a larger number of components (panels, batteries, controllers and inverters) to our database to be used by our synthesis engine.
+
+\textcolor{red}{We have to abbreviate our references.
+Take a look at https://ssvlab.github.io/lucasccordeiro/papers/icse2011.pdf, e.g., I've just put the conference acronym, remove conference place (New York), etc}
+
 % argument is your BibTeX string definitions and bibliography database(s)

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
added additional comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Counter-Example Guided Inductive Synthesis (CEGIS) represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is shown in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.
+
+\textcolor{red}{Could you please adapt this text to our context?}
 
@@
 The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm.
-\textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?}
+\textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?} \textcolor{red}{Could we synthesize the equipment that we need to meet the user requirements?}
 

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

--- 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
@@
 \begin{abstract}
-Currently, there exist various state-of-the-art tools to design PV but they are mainly based on simulations, which do not cover all aspects of the design-space. 
+Currently, there exist various state-of-the-art tools to design PV systems, but they are mainly based on simulations, which do not cover all aspects of the design-space.
 We present a sound and automated approach to synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems.
 The application of automated formal verification to synthesize PV systems is a very recent subject with only a few initiatives.
-Here we develop and evaluate an automated formal synthesis approach based on program synthesis and report preliminary results 
-using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system. 
-Commercial equipment data is provided to our synthesis engine and the candidate solution is derived 
-from financial analysis of the obtained sizing. Our proposed synthesis method is novel and 
-unprecedented to streamline the design of PV systems. 
-Experimental results show that our synthesis method, based on software model checking as our verification engine, 
-is able to synthesize, in an acceptable run-time, the optimal PV system sizing of two different case studies.
+Here we develop and evaluate an automated formal synthesis approach based on program synthesis and report preliminary results using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system.
+Commercial equipment data is provided to our synthesis engine and the candidate solution is derived from financial analysis of the obtained sizing.
+Our proposed synthesis method is novel and unprecedented to streamline the design of PV systems.
+Experimental results show that our synthesis method, based on software model checking as our verification engine, is able to synthesize, in an acceptable run-time, the optimal PV system sizing of two different case studies.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access 
-fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}. 
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) 
-in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed \textcolor{red}{Add reference here}; 
-specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}.
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
 
@@
  However, those tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}. 
+\textcolor{red}{On the other hand, optimization of PV systems is not a recent matter, since the 90's different techniques using different criteria in order to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed~\cite{Alsadi2018}.}
+
+However, formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}.
 Here, we use program synthesis for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-In particular, given a correctness specification $\sigma$, our method uses that as starting point and then incrementally produce a 
-sequence of candidate solutions that satisfy $\sigma$, by integrating software model checking techniques.
+In particular, given a correctness specification $\sigma$, our method uses that as starting point and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$, by integrating software model checking techniques.
 
 This paper makes the following original contributions.
-Firstly, the use of automated software verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, 
-and specifically their use in PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) 
-can be fed to the proposed synthesis method together with user requirements and environment constraints, 
-and our synthesis algorithm based on software model checking can find the optimal solution in technical and economical terms.
+Firstly, the use of automated software verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.
+Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on software model checking can find the optimal solution in technical and economical terms.
 Secondly, we evaluate different state-of-art software verifiers with the goal of obtaining the best performance for synthesizing optimal PV systems.
-
+%
 %-----------------------------------------------------------
@@
 %-----------------------------------------------------------
-
+%
 %-----------------------------------------------------------
@@
 %-----------------------------------------------------------
-
+%
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
@@
 Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
-
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \\
-
+%
 Here the sizing check will be automatically performed by our proposed method; 
@@
 % -------------------------------------------------------
-
+%
 To select an optimal combination of components from a PV system to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system.
@@
 The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm.
-\textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?}
-
-\textcolor{red}{Could you please reinforce here that our approach is sound and completely automated?}
-
+\textcolor{red}{Worth to mention that the process described here in completely automated and that a validation was performed by authors to ensure that the approach is sound, considering the case studies described at next section}.
 %---------------------------------------------------------------------------
@@
 
-For future wore, we will perform additional experiments using other case studies and also compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization. 
+For future work, we will perform additional experiments using other case studies and also compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization. 
 Furthermore, we will be provide a larger number of components (panels, batteries, controllers and inverters) to our database to be used by our synthesis engine.
-
-\textcolor{red}{We have to abbreviate our references.
-Take a look at https://ssvlab.github.io/lucasccordeiro/papers/icse2011.pdf, e.g., I've just put the conference acronym, remove conference place (New York), etc}
-
+%
 % argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{trindadeThesis}{}
+\bibliography{trindadeThesis_menor}{}
 

### 2019-04-30 code/opt_PVcode_case3_rev2.c
updated code case3

@@ -1,0 +1,206 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_case3.c (case 2 = 915W, 4.88 kWh/day, 24V, 12h)
+ Author      : Alessandro
+ Version     : rev2 - April 2019
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
+// int Phouse = 915, Psurge = 980, Econsumption = 4880;
[…]

### 2019-05-02 code/opt_PVcode_rev3_case1.c
updated codes rev3

@@ -1,0 +1,220 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev3_improved database.c CASE 1
+ Author      : Alessandro
+ Version     : rev2 - May 2019
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
+// int Phouse = 915, Psurge = 980, Econsumption = 4880;
[…]

### 2019-05-02 code/opt_PVcode_rev3_case2.c

@@ -1,0 +1,220 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev3_improved database.c CASE 1
+ Author      : Alessandro
+ Version     : rev2 - May 2019
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
+// int Phouse = 915, Psurge = 980, Econsumption = 4880;
[…]

### 2019-05-02 code/opt_PVcode_rev3_case3.c

@@ -1,0 +1,220 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev3_improved database.c CASE 1
+ Author      : Alessandro
+ Version     : rev2 - May 2019
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
+// int Phouse = 915, Psurge = 980, Econsumption = 4880;
[…]

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated ASE text

@@
 
-While some research efforts do exist to enhance and optimize the software development processes for CPS, 
-further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
-Among the opportunities for enhancements, there exists the need for developing new techniques and tools to support 
-CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS. 
-The developed techniques need to deal with predefined requirements enforced by the nature and inherited constraints 
-of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, 
-correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. 
+%While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS.
+The developed techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
+In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
+Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
 Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{fig2.jpg}
-	\caption{CounterExample Guided Inductive Synthesis (CEGIS).}
+	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
+	\caption{Counter-Example Guided Inductive Synthesis (CEGIS) applied to PV system sizing.}
 	\label{Counter-Example-Guided-Inductive-Synthesis}
 \end{figure}
-
+%
 One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
@@
 Nowadays, program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based automated reasoning~\cite{Sharma14}.
-Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
+%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
 %
@@
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
-In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$).
+%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$).
 For night hours or rainy days, we hold batteries where power can be stored and used.
@@
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{blockdiagramPVS2}
+\includegraphics[width=0.4\textwidth]{blockdiagramPVS2_rev}
 \centering
@@
 %
-Here the sizing check will be automatically performed by our proposed method; 
-this stage will ensure that the system meets the standard project steps related 
-to critical period solar energy method~\cite{Pinho} and 
-adopting MPPT (Maximum Power Point Tracking) charge controller, 
-which is the most common one in practice. 
+Here the sizing check will be automatically performed by our proposed method; this stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
 %
@@
 %------------------------------------------------------
-Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to symthesize stand-alone PV systems using software model checking. 
+Algorithm~\ref{alg:verification-algorithm} describes the pseudo-code used to synthesize stand-alone PV systems using software model checking. 
 %
@@
 The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the assertion stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the automatic verification reached a \textit{SAT} (satisfiable) condition.
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the automatic verification reached a \textit{SAT} (satisfiable) condition.
 The algorithm uses non-deterministic variables to choose one specific data from a list of PV panels, controllers, batteries and inverters (Lines 10 to 13).
@@
 If our algorithm does not find a feasible solution among the item of equipment that were provided to our synthesis algorithm, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
-It indicates that was not possible to combine the itens of each equipment and create a feasible solution.
+It indicates that was not possible to combine the items of each equipment and create a feasible solution.
 The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm.
@@
 %---------------------------------------------------------------------------
-
-We have performed two case studies to evaluate our proposed synthesis approach as described in Table~\ref{tab1}.
+We have performed two case studies to evaluate our proposed synthesis approach as described in Table~\ref{tab1}, and our code was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems.
 Furthermore, three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
@@
 
-Only CPAchecker could present the optimal sizing of the two case studies: the result came in 66 minutes and 35 minutes, respectively.
+Only CPAchecker could present the optimal sizing of the two case studies: the result came in 50.2 minutes and 37.2 minutes, respectively.
+The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}.
 %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
@@
 \hline
-Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3900Wh/day \\ Battery autonomy=48h} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4880Wh/day \\ Battery autonomy=6h}\\
+Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3,900Wh/day \\ Battery autonomy=48h} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4,880Wh/day \\ Battery autonomy=6h}\\
 \hline
@@
 %\hline
-\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (66.18 min) \\ Property violation line 195: \\NTP=4$\times$320W model (2S-2P)\\NBT=4$\times$105Ah model (2S-2P)\\ Controller 15A/100V\\Inverter 700VA, 48V \\ Total Cost=US\$ 2,643.00} & \makecell {SAT (35.41 min) \\ Property violation line 195:  \\NTP=3$\times$320W model (3S)\\NBT=2$\times$105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,200VA, 48V \\ Total Cost=US\$ 2,125.00}\\
+\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\ Property violation line 209: \\NTP=1$\times$330W model (1S)\\NBT=8$\times$105Ah model (2S-4P)\\ Controller 15A/75V\\Inverter 700W, 48V \\ Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\ Property violation line 209:  \\NTP=3$\times$330W model (3S)\\NBT=2$\times$105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,500VA, 24V \\ Total Cost=US\$ 2,235.57}\\
 \hline

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \IEEEauthorblockA{\textit{Electricity Department} \\
-\textit{Federal University of Amazonas}\\
-Manaus, Brazil \\
+\textit{Federal University of Amazonas}, Brazil \\
 alessandrotrindade@ufam.edu.br}
@@
 \IEEEauthorblockA{\textit{School of Computer Science} \\
-\textit{University of Manchester}\\
-Manchester, England \\
+\textit{University of Manchester}, UK \\
 lucas.cordeiro@manchester.ac.uk }
@@
 We present a sound and automated approach to synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems.
-The application of automated formal verification to synthesize PV systems is a very recent subject with only a few initiatives.
-Here we develop and evaluate an automated formal synthesis approach based on program synthesis and report preliminary results using three state-of-art software verifiers with the goal of optimizing the sizing of a PV system.
-Commercial equipment data is provided to our synthesis engine and the candidate solution is derived from financial analysis of the obtained sizing.
+The application of program synthesis to design PV systems is a very recent subject that has not been further explored.
+Here we develop and evaluate an automated formal synthesis approach based on program synthesis and report preliminary results to optimize the sizing of a PV system.
+Commercial equipment data is provided to our synthesis engine and a candidate solution is derived from financial analysis of the obtained sizing.
 Our proposed synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results show that our synthesis method, based on software model checking as our verification engine, is able to synthesize, in an acceptable run-time, the optimal PV system sizing of two different case studies.
+Experimental results show that our synthesis method, based on symbolic model checking as our main verification engine, is able to synthesize within an acceptable run-time the optimal PV system sizing of two different case studies.
 \end{abstract}

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
- \renewcommand{\baselinestretch}{0.96}
+ \renewcommand{\baselinestretch}{0.965}
 
@@
 %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
-Software pervasiveness in every context of life also places new challenges. 
-In particular, highly dynamic environments, rapidly changing requirements, 
+Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
 unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
@@
 Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}.
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
+To provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
 
@@
  However, those tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-\textcolor{red}{On the other hand, optimization of PV systems is not a recent matter, since the 90's different techniques using different criteria in order to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed~\cite{Alsadi2018}.}
+ Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.
 
-However, formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}.
+However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored yet.
+Those formal techniques can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}.
 Here, we use program synthesis for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-In particular, given a correctness specification $\sigma$, our method uses that as starting point and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$, by integrating software model checking techniques.
+Given a correctness specification $\sigma$, our method uses that as starting point and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$, by integrating symbolic model checking into our synthesis engine.
 
 This paper makes the following original contributions.
-Firstly, the use of automated software verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.
-Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on software model checking can find the optimal solution in technical and economical terms.
-Secondly, we evaluate different state-of-art software verifiers with the goal of obtaining the best performance for synthesizing optimal PV systems.
+Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.
+Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
+Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification backend for synthesizing optimal PV systems.
 %

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-Counter-Example Guided Inductive Synthesis (CEGIS) represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is shown in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.
+Counter-Example Guided Inductive Synthesis (CEGIS) represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.
 
-\textcolor{red}{Could you please adapt this text to our context?}
+The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .
+\forall \vec{x}.
+\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
+The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
+Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
 
-The correctness specification $\sigma$ provided to a program synthesizer is of the form $\exists \vec{F} .
-\forall \vec{x}.
-\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free formula typically supported by SMT solvers.
-The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-The phases {\sc Synthesize} and {\sc Verify}, in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis},  interact via a finite set of test vectors {\sc inputs} that is incrementally updated.
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated.
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
+If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If this is the case, then the algorithm terminates, i.e., we have found feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
 %
@@
 One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite, this means that the refinement loop can only iterate over a finite number of times; however, $\mathcal{D}$ can represent a large number of elements for the finite set $\text{\sc inputs}$.
-In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}.
+Given that the full set of inputs $\mathcal{D}$ is finite, this means that the refinement loop can only iterate over a finite number of times; however, $\mathcal{D}$ can represent a large number of elements for the finite set $\text{\sc inputs}$ and our synthesis engine can then conclude that no feasible equipment combination was found.
+%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}.
 In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig.
@@
 Nowadays, program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based automated reasoning~\cite{Sharma14}.
-%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
+In our particular study, we have used symbolic software verifiers based on SMT solvers to reason over QF formulas.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
 %

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
-The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
+
+The modeling of a PV system is typically based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
+The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into Direct Current (DC) electricity.
 %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$).
@@
 The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
+The PV arrays produce DC and therefore when the PV system contains an Alternating Current (AC) load, a DC/AC conversion is required.
 That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
@@
 %
-Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
 \begin{equation}
@@
 %
-Regarding the batteries, we must first define the total capacity of the battery bank, which can be described as
+Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
 \begin{equation}
@@
 
-The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin}.
+The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin} as
 \begin{equation}
 \label{eq:icmin}
-\scriptstyle I_{c,min} = \scriptstyle I_{sc,amb} \times \scriptstyle N_{PP}.
+\scriptstyle I_{c,min} = \scriptstyle I_{sc,amb} \times \scriptstyle N_{PP},
 \end{equation}
@@
 % -------------------------------------------------------
-\subsection{Optimal sizing of PV systems}
+\subsection{Optimal Sizing of PV Systems}
 % -------------------------------------------------------
@@
 However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC).
-Here, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
 %------------------------------------------------------

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %------------------------------------------------------
-Algorithm~\ref{alg:verification-algorithm} describes the pseudo-code used to synthesize stand-alone PV systems using software model checking. 
+Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code used to synthesize stand-alone PV systems using symbolic model checking. 
 %
@@
   \FOR {$HintCost=0$ to $MaxCost$}
- 	\STATE Declare nondet variable to select PV Panel from list \\
- 	\STATE Declare nondet variable to select Controller from list \\
- 	\STATE Declare nondet variable to select Battery from list \\
- 	\STATE Declare nondet variable to select Inverter from list \\ 	
+ 	\STATE Declare non-deterministic variable to select PV Panel from list \\
+ 	\STATE Declare non-deterministic variable to select Controller from list \\
+ 	\STATE Declare non-deterministic variable to select Battery from list \\
+ 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
  	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
@@
 
-Our synthesis algorithm starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5).
+Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5).
 After that, we define user requirements, i.e., house requirements and design definitions, from Lines 6 to 8.
 The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the automatic verification reached a \textit{SAT} (satisfiable) condition.
-The algorithm uses non-deterministic variables to choose one specific data from a list of PV panels, controllers, batteries and inverters (Lines 10 to 13).
-That procedure ensures that the automated verification checks all possibilities of items from each equipment, and combine them to assemble a feasible PV solution, which meets the user requirements.
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the automatic verification reached a satisfiable condition (\textit{SAT}).
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (Lines 10 to 13).
+That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.
 
-Next, we use Eq.~(\ref{eq:Ecorrected}), Eq.~(\ref{eq:Ep}), Eq.~(\ref{eq:NTPmin}), Eq.~(\ref{eq:NPSmin}), Eq.~(\ref{eq:NPPmin}), Eq.~(\ref{eq:Cbank}), Eq.~(\ref{eq:Nbtotal}), Eq.~(\ref{eq:iscamb}), and Eq.~(\ref{eq:icmin}) to calculate the sizing variables (Lines 14 to 20).
+Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (Lines 14 to 20).
 The directive \textit{assume} (from Line 21 to 25) ensures the compatibility of the chosen items from the list of equipment: the automatic verification uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20 in addition to the Line 18.
@@
 It indicates that was not possible to combine the items of each equipment and create a feasible solution.
-The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm.
-\textcolor{red}{Worth to mention that the process described here in completely automated and that a validation was performed by authors to ensure that the approach is sound, considering the case studies described at next section}.
+The main challenge for the {\sc Verify} phase is to find a feasible candidate solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm.
+Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+
 %---------------------------------------------------------------------------

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %------------------------------------------------------
-Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code used to synthesize stand-alone PV systems using symbolic model checking. 
+Algorithm~\ref{alg:verification-algorithm} describes our pseudocode to synthesize stand-alone PV systems using symbolic model checking. 
 %
@@
 The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the automatic verification reached a satisfiable condition (\textit{SAT}).
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
 Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (Lines 10 to 13).
@@
 Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (Lines 14 to 20).
-The directive \textit{assume} (from Line 21 to 25) ensures the compatibility of the chosen items from the list of equipment: the automatic verification uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20 in addition to the Line 18.
-Therefore, our algorithm reaches Line 27 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$.
+The directive \textit{assume} (from Line 21 to 25) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20 in addition to the Line 18.
+Therefore, our synthesis algorithm reaches Line 27 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$.
 
-If our algorithm does not find a feasible solution among the item of equipment that were provided to our synthesis algorithm, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
+If our algorithm does not find a feasible solution among the item of equipment that were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
 It indicates that was not possible to combine the items of each equipment and create a feasible solution.
-The main challenge for the {\sc Verify} phase is to find a feasible candidate solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm.
+The main challenge for the {\sc Verify} phase is to find a feasible candidate solution regarding the constraints and user requirements, which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our {\sc Synthesize} phase.
 Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %---------------------------------------------------------------------------
-We have performed two case studies to evaluate our proposed synthesis approach as described in Table~\ref{tab1}, and our code was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems.
-Furthermore, three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare our approach effectiveness and efficiency.
+
+We have performed two case studies to evaluate our proposed synthesis approach as described in Table~\ref{tab1}.
+Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems.
+Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used as our verification engine to compare our approach effectiveness and efficiency.
 The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.
@@
 
-Only CPAchecker could present the optimal sizing of the two case studies: the result came in 50.2 minutes and 37.2 minutes, respectively.
+Only CPAchecker was able to present the optimal sizing of the two case studies: the result came in $50.2$ minutes and $37.2$ minutes, respectively. 
 The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}.

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reduced references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 The experiments were performed with a predefined timeout of $240$ minutes.
-
+%
 Only CPAchecker was able to present the optimal sizing of the two case studies: the result came in $50.2$ minutes and $37.2$ minutes, respectively. 
@@
 CBMC and ESBMC produced UNKNOWN result (timeout or out of memory).
-
+%
 %used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
@@
 \end{table}
-
+%
 For future work, we will perform additional experiments using other case studies and also compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization. 

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated ASE text

@@
 %
-To select an optimal combination of components from a PV system to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system.
-An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}.
-
+To select an optimal combination of components from a PV system, to meet sizing constraints, 
+%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
+the ideal solution is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
 Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
@@
 Remember that we have software engineering audience}.
-However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC).
+%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC).
 Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
 %------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-
-We have performed two case studies to evaluate our proposed synthesis approach as described in Table~\ref{tab1}.
+Our experimental evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated verification approach provide correct results?, and \textit{RQ2} (performance) How do the verifiers compare to each other?
+We have performed two case studies to evaluate our proposed synthesis approach as described at the first line in Table~\ref{tab1}.
 Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems.
@@
 The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}.
+The results were tested by manual PV sizing and were sound (\textit{RQ1}).
 %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
-CBMC and ESBMC produced UNKNOWN result (timeout or out of memory).
+CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}). This answer the \textit{RQ2}.
 %
@@
 \hline
- & Case 1 & Case 2\\
+Specification & \makecell{ \textbf{Case Study 1} \\ Demand=501W \\ Peak=501W \\ Energy=3,900Wh/day\\Battery autonomy=48h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC} & \makecell{\textbf{Case Study 2}\\ Demand=915W \\ Peak=980W \\Energy=4,880Wh/day\\Battery autonomy=6h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC}\\
 \hline
 \hline
-Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3,900Wh/day \\ Battery autonomy=48h} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4,880Wh/day \\ Battery autonomy=6h}\\
+Tools & \textbf{Result} & \textbf{Result}\\
 \hline
@@
 %
-For future work, we will perform additional experiments using other case studies and also compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization. 
-Furthermore, we will be provide a larger number of components (panels, batteries, controllers and inverters) to our database to be used by our synthesis engine.
+We have reported a favorable assessment of the proposed method.
+Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, what can make the analysis more accurate; (2) improvement of the system cost analysis: to include criteria as Net Present Cost, or Levelized Cost of Energy, in order to promote the acceptability of investment (or even to include operational and maintenance costs that were not considered at this study); (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization, however the result will allow improved sizing as well; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization: this will validate the results and a simulation-verification comparative.
 %

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %---------------------------------------------------------------------------
-Our experimental evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated verification approach provide correct results?, and \textit{RQ2} (performance) How do the verifiers compare to each other?
-We have performed two case studies to evaluate our proposed synthesis approach as described at the first line in Table~\ref{tab1}.
+
+Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, and \textit{RQ2} (performance) How do the software verifiers compare to each other?
+We have performed two case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
 Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems.
 Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used as our verification engine to compare our approach effectiveness and efficiency.
+and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
 The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.
@@
 %
-Only CPAchecker was able to present the optimal sizing of the two case studies: the result came in $50.2$ minutes and $37.2$ minutes, respectively. 
+Only CPAchecker was able to present the optimal sizing of the two case studies: the result was produced in $50.2$ minutes and $37.2$ minutes, respectively. 
 The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}.
@@
 %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
-CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}). This answer the \textit{RQ2}.
+CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.
 %
@@
 We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, what can make the analysis more accurate; (2) improvement of the system cost analysis: to include criteria as Net Present Cost, or Levelized Cost of Energy, in order to promote the acceptability of investment (or even to include operational and maintenance costs that were not considered at this study); (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization, however the result will allow improved sizing as well; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization: this will validate the results and a simulation-verification comparative.
+Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: to include criteria as Net Present Cost, or Levelized Cost of Energy, in order to promote the acceptability of investment (or even to include operational and maintenance costs that were not considered here); (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization: this will validate the results and a simulation-verification comparative.
 %

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \author{\IEEEauthorblockN{Alessandro Trindade}
-\IEEEauthorblockA{\textit{Electricity Department} \\
+\IEEEauthorblockA{
 \textit{Federal University of Amazonas}, Brazil \\
@@
 \IEEEauthorblockN{Lucas Cordeiro}
-\IEEEauthorblockA{\textit{School of Computer Science} \\
+\IEEEauthorblockA{
 \textit{University of Manchester}, UK \\
@@
 
-This paper makes the following original contributions.
+Our work makes two major contributions.
 Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.
@@
 	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
-	\caption{Counter-Example Guided Inductive Synthesis (CEGIS) applied to PV system sizing.}
+	\caption{CEGIS applied to PV system sizing.}
 	\label{Counter-Example-Guided-Inductive-Synthesis}
@@
 
-Nowadays, program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based automated reasoning~\cite{Sharma14}.
-In our particular study, we have used symbolic software verifiers based on SMT solvers to reason over QF formulas.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
 %
@@
 
-The sizing project check of the inverter is carried out by means of three equations.
+The inverter sizing check is performed by means of three equations.
 Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
@@
 %
-To select an optimal combination of components from a PV system, to meet sizing constraints, 
+To select an optimal combination of components from a PV system to meet sizing constraints, 
 %we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
@@
 
-Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, and \textit{RQ2} (performance) How do the software verifiers compare to each other?
-We have performed two case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
+\textbf{Case studies and setup.} We have performed two case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
 Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems.
@@
 The experiments were performed with a predefined timeout of $240$ minutes.
-%
-Only CPAchecker was able to present the optimal sizing of the two case studies: the result was produced in $50.2$ minutes and $37.2$ minutes, respectively. 
+
+\textbf{Objectives.} Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, and \textit{RQ2} (performance) How do the software verifiers compare to each other?
+
+\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
 The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}.
@@
 \end{table}
-%
-We have reported a favorable assessment of the proposed method.
+
+\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
 Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: to include criteria as Net Present Cost, or Levelized Cost of Energy, in order to promote the acceptability of investment (or even to include operational and maintenance costs that were not considered here); (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization: this will validate the results and a simulation-verification comparative.

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-Currently, there exist various state-of-the-art tools to design PV systems, but they are mainly based on simulations, which do not cover all aspects of the design-space.
-We present a sound and automated approach to synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems.
-The application of program synthesis to design PV systems is a very recent subject that has not been further explored.
-Here we develop and evaluate an automated formal synthesis approach based on program synthesis and report preliminary results to optimize the sizing of a PV system.
-Commercial equipment data is provided to our synthesis engine and a candidate solution is derived from financial analysis of the obtained sizing.
-Our proposed synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results show that our synthesis method, based on symbolic model checking as our main verification engine, is able to synthesize within an acceptable run-time the optimal PV system sizing of two different case studies.
+Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space.
+We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis.
+In particular, our counterexample guided inductive synthesis (CEGIS) approach has two phases: we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
+The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained.
+Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
+Our synthesis method is novel and unprecedented to streamline the design of PV systems.
+Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different intricate case studies.
 \end{abstract}

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
-Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
-unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
-
+%Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
+%unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
+%
 %While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
 Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS.
-The developed techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
+Those techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
 In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
@@
 
-However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored yet.
-Those formal techniques can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}.
-Here, we use program synthesis for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-Given a correctness specification $\sigma$, our method uses that as starting point and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$, by integrating symbolic model checking into our synthesis engine.
+However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
+Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Given a correctness specification $\sigma$, our method uses that as starting point and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$.
+In particular, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
+The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.
 
 Our work makes two major contributions.
-Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.
+Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented.
 Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-Counter-Example Guided Inductive Synthesis (CEGIS) represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.
+CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.
 
@@
 If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
+If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
 %

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
   \STATE Initialize variables \\
-  \STATE Declare list of PV panels data and cost \\
-  \STATE Declare list of controllers data and cost \\
-  \STATE Declare list of batteries data and cost \\
-  \STATE Declare list of inverters data and cost \\
+  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
+%  \STATE Declare list of controllers data and cost \\
+%  \STATE Declare list of batteries data and cost \\
+%  \STATE Declare list of inverters data and cost \\
   \STATE Declare the maximum possible cost $MaxCost$  \\
@@
  	\STATE Calculate $I_{c,min}$ \\
- 	\STATE Requeriment enforced by \textbf{assume}$(I_{c})$ \\
-	\STATE Requeriment enforced by \textbf{assume}$(V_{in}DC)$ \\
-	\STATE Requeriment enforced by \textbf{assume}$(V_{out}AC)$ \\
-	\STATE Requeriment enforced by \textbf{assume}$(Demand)$ \\
-	\STATE Requeriment enforced by \textbf{assume}$(P_{surge})$ \\
-	\STATE non-det variables hold feasible equipment and cost  \\
+ 	\STATE Requeriment enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
+%	\STATE Requeriment enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
+%	\STATE Requeriment enforced by \textbf{assume}$(V_{out}AC)$ \\
+	\STATE Requeriment enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
+%	\STATE Requeriment enforced by \textbf{assume}$(P_{surge})$ \\
+	\STATE non-deterministic variables hold feasible equipment and cost  \\
 	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
@@
  \end{algorithm}
+
+ \textcolor{red}{Could you please update the lines? I've reduced the number of lines of our algorithm above.}
 

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated ASE text

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The modeling of a PV system is typically based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
+A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into Direct Current (DC) electricity.
@@
 \end{equation}
-
+%
 We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
@@
 \end{equation}
-
+%
 \noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
@@
 \end{equation}
-
+%
 Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
@@
 \end{equation}
-
+%
 \noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
@@
 \end{equation}
-
+%
 Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
@@
 \end{equation}
-
+%
 The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as
@@
 \end{equation}
-
+%
 The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin} as
@@
 \end{equation}
-
+%
 The inverter sizing check is performed by means of three equations.
@@
  \begin{scriptsize}
-
  \renewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
  \end{algorithm}
-
- \textcolor{red}{Could you please update the lines? I've reduced the number of lines of our algorithm above.}
-
-Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5).
-After that, we define user requirements, i.e., house requirements and design definitions, from Lines 6 to 8.
-The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (Lines 10 to 13).
+%
+Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Line 2).
+After that, we define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5.
+The \textit{for}-loop started at Line 6 controls the lowest cost to the PV solution.
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (Lines 7 to 10).
 That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.
 
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (Lines 14 to 20).
-The directive \textit{assume} (from Line 21 to 25) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20 in addition to the Line 18.
-Therefore, our synthesis algorithm reaches Line 27 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$.
-
+Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (Lines 11 to 17).
+The directive \textit{assume} (Lines 15, 18 and 19) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines 15, 18 and 19.
+Therefore, our synthesis algorithm reaches Line 20 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (Line 21).
 If our algorithm does not find a feasible solution among the item of equipment that were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
@@
 Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
-
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-
 \textbf{Case studies and setup.} We have performed two case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
@@
 \textbf{Results.}  CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
-The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}.
+The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}.
 The results were tested by manual PV sizing and were sound (\textit{RQ1}).
@@
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: to include criteria as Net Present Cost, or Levelized Cost of Energy, in order to promote the acceptability of investment (or even to include operational and maintenance costs that were not considered here); (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization: this will validate the results and a simulation-verification comparative.
+Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost, or Levelized Cost of Energy criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs; (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization: this will validate the results and a simulation-verification comparative.
 %

### 2019-05-04 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated ASE text

@@
 %
+
 Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Line 2).
 After that, we define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5.
+
 The \textit{for}-loop started at Line 6 controls the lowest cost to the PV solution.
 In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
+
 Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (Lines 7 to 10).
@@
 Therefore, our synthesis algorithm reaches Line 20 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (Line 21).
+
 If our algorithm does not find a feasible solution among the item of equipment that were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
 It indicates that was not possible to combine the items of each equipment and create a feasible solution.
+
 The main challenge for the {\sc Verify} phase is to find a feasible candidate solution regarding the constraints and user requirements, which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our {\sc Synthesize} phase.
@@
 %---------------------------------------------------------------------------
-\textbf{Case studies and setup.} We have performed two case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
-Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems.
+\textbf{Case studies and setup.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
+Our synthesis algorithm was feed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems.
 Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
 and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.
 All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
@@
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost, or Levelized Cost of Energy criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs; (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization: this will validate the results and a simulation-verification comparative.
+Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization of PV systems: this will validate the results obtained and it allow a simulation-verification comparative.
 %

### 2019-05-04 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
run spell checker
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
-Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification backend for synthesizing optimal PV systems.
+Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
 %
@@
 %------------------------------------------------------
-Algorithm~\ref{alg:verification-algorithm} describes our pseudocode to synthesize stand-alone PV systems using symbolic model checking. 
+Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. 
 %
@@
  	\STATE Calculate $I_{c,min}$ \\
- 	\STATE Requeriment enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
+ 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
 %	\STATE Requeriment enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
 %	\STATE Requeriment enforced by \textbf{assume}$(V_{out}AC)$ \\
-	\STATE Requeriment enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
+	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
 %	\STATE Requeriment enforced by \textbf{assume}$(P_{surge})$ \\

### 2019-05-04 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
updated ASE text double-blind

@@
 
-\title{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
+\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems\\
 % \thanks{Identify applicable funding agency here. If none, delete this.}
 }
-
-\author{\IEEEauthorblockN{Alessandro Trindade}
-\IEEEauthorblockA{
-\textit{Federal University of Amazonas}, Brazil \\
-alessandrotrindade@ufam.edu.br}
-\and
-\IEEEauthorblockN{Lucas Cordeiro}
-\IEEEauthorblockA{
-\textit{University of Manchester}, UK \\
-lucas.cordeiro@manchester.ac.uk }
-}
-
+%
+%\author{\IEEEauthorblockN{Alessandro Trindade}
+%\IEEEauthorblockA{
+%\textit{Federal University of Amazonas}, Brazil \\
+%alessandrotrindade@ufam.edu.br}
+%\and
+%\IEEEauthorblockN{Lucas Cordeiro}
+%\IEEEauthorblockA{
+%\textit{University of Manchester}, UK \\
+%lucas.cordeiro@manchester.ac.uk }
+%}
+%
 \maketitle
@@
 
-%\begin{IEEEkeywords}
-%automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
-%\end{IEEEkeywords}
+\begin{IEEEkeywords}
+automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
+\end{IEEEkeywords}
 
@@
 	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
-	\STATE Requeriment enforced by \textbf{assume}$(V_{c})$ \\
+	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
  	\STATE Calculate $I_{sc,amb}$ \\
@@
  	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
-%	\STATE Requeriment enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
-%	\STATE Requeriment enforced by \textbf{assume}$(V_{out}AC)$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
 	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
-%	\STATE Requeriment enforced by \textbf{assume}$(P_{surge})$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
 	\STATE non-deterministic variables hold feasible equipment and cost  \\

### 2019-05-04 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \textbf{Case studies and setup.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
-Our synthesis algorithm was feed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems.
+Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems.
 Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
@@
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization of PV systems: this will validate the results obtained and it allow a simulation-verification comparative.
+Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization of PV systems: this will validate the results obtained and it allows a simulation-verification comparative.
 %

### 2019-05-05 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated ASE text double-blind

@@
 \caption{Case studies and Results: optimization of PV systems.}\label{tab1}
-\begin{scriptsize}
+%\begin{scriptsize}
 \begin{tabular}{|c|c|c|}
@@
 %\hline
-\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\ Property violation line 209: \\NTP=1$\times$330W model (1S)\\NBT=8$\times$105Ah model (2S-4P)\\ Controller 15A/75V\\Inverter 700W, 48V \\ Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\ Property violation line 209:  \\NTP=3$\times$330W model (3S)\\NBT=2$\times$105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,500VA, 24V \\ Total Cost=US\$ 2,235.57}\\
+\makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\Property violation line 209\\NTP=1$\times$330W (1S)\\NBT=8$\times$105Ahm (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\Property violation line 209\\NTP=3$\times$330W (3S)\\NBT=2$\times$105Ah (2S)\\Controller 35A/145V\\Inverter 1,500VA/24V \\Total Cost=US\$ 2,235.57}\\
 \hline
@@
 \end{tabular}
-\end{scriptsize}
+%\end{scriptsize}
 \end{table}
@@
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization of PV systems: this will validate the results obtained and it allows a simulation-verification comparative.
+Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with a off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
 %
@@
 \bibliography{trindadeThesis_menor}{}
-
 \vspace{12pt}
-
 \end{document}

### 2019-05-06 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv1.tex
updated ASE text

--- 2019-05-05 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
@@
 Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems.
-Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
+Furthermore, three start-of-art verification tools, CBMC (command-line: \$ cbmc -\phantom{}-unwind 100 file.c), ESBMC (command-line: \$ esbmc file.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector), %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker (command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c) were used as our verification engine to compare our approach effectiveness and efficiency.
 All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.

### 2019-05-07 Tex/elsevier/trindade_solar_energy_rev0.tex
updated text

--- 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
@@
 \end{frontmatter}
-
-%\linenumbers
 
@@
 The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power.
+MPPT, or maximum power point tracking, is the electronic control mechanism mostly used nowadays and that maintains the PV operating at the voltage of maximum power.
 Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
@@
 The sizing check will be performed by the proposed tool, and it will indicate if there is an error of sizing before to perform the automated verification of the system.
-This stage ensures that the system meets the standard project steps related to worst monthly average solar energy~\cite{Pinho}.
+This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.
 %
@@
 
-Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage: 
+Related to the charge controller, here the model with MPPT is adopted and initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage:
 \begin{equation}
@@
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
-This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check and does not perform the functional verification \textcolor{red}{what is functional verification?}.
+This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in Line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code (much more complex).
 

### 2019-05-07 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text

@@
 
-\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems\\
-% \thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems}
 %
@@
 We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our counterexample guided inductive synthesis (CEGIS) approach has two phases: we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
 The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained.
@@
 Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS.
-Those techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
+These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
 In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
@@
 ; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
- However, those tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+ However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
  Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.
@@
 Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-Given a correctness specification $\sigma$, our method uses that as starting point and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$.
-In particular, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
+Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$.
+In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
 The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.
@@
 Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented.
-Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
+Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries)
+can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
 Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
@@
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
-In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$~\cite{Abateetal2017}.
+In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
 As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
@@
 One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite, this means that the refinement loop can only iterate over a finite number of times; however, $\mathcal{D}$ can represent a large number of elements for the finite set $\text{\sc inputs}$ and our synthesis engine can then conclude that no feasible equipment combination was found.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
+At this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.
+%however, $\mathcal{D}$ can represent a large number of elements for the finite set  and our synthesis engine can then conclude that no feasible equipment combination was found.
 %In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}.
@@
 \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.
-
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14};
+here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
 %
@@
 A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
-The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into Direct Current (DC) electricity.
+The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
 %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$).
@@
 The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an Alternating Current (AC) load, a DC/AC conversion is required.
-That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
+That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
 \begin{figure}[h]
@@
 %
-Here the sizing check will be automatically performed by our proposed method; this stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
+The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
 %
@@
 %
-To select an optimal combination of components from a PV system to meet sizing constraints, 
+%%%To select an optimal combination of components from a PV system to meet sizing constraints, 
 %we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
-the ideal solution is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
+The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
 Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
@@
 Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
-Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
 %------------------------------------------------------
@@
 
-The main challenge for the {\sc Verify} phase is to find a feasible candidate solution regarding the constraints and user requirements, which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our {\sc Synthesize} phase.
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements.
+Related to our {\sc Verify} phase the challenge is to find the lowest acquisition cost from a list of equipment and components that is provided from the {\sc Synthesize} phase.
+
 Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
@@
 %---------------------------------------------------------------------------
-\textbf{Case studies and setup.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
+\textbf{Case studies.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
 Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems.
@@
 and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
+
+\textbf{Setup.} All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
 The experiments were performed with a predefined timeout of $240$ minutes.
@@
 \end{table}
+%
 
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with a off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
+Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
 %
@@
 \bibliography{trindadeThesis_menor}{}
-\vspace{12pt}
+%\vspace{12pt}
 \end{document}

### 2019-05-07 Tex/elsevier/trindade_solar_energy_rev0.tex
updated text

@@
 
-\journal{Renewable \& Sustainable Energy Reviews}
+%\journal{Renewable \& Sustainable Energy Reviews}
 
@@
 Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-Automated verification using model checking has proven to be an effective technique to any kind of program verification.
+Automated verification using model checking has proven to be an effective technique to validate any kind of system.
 This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
@@
 \begin{keyword}
-Formal verification \sep model checking \sep photovoltaic power systems \sep power system modeling \sep solar power generation
+Formal verification \sep model checking \sep photovoltaic power systems
 %\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
@@
 Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
-The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
+%The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
 Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
@@
 
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
+In order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
 
@@
 %
-In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is created.
-The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
-The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
+In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used.
+%The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are inputted to the proposed tool and automatically verified during the formal process.
 The model checking tool reports in which conditions a system does not meet the user requirements.
@@
 %--------------------------------------------------------
-
+%
 %According to \cite{Roy}, a 
@@
 %For night hours or rainy days, one needs to hold batteries, where power can be stored and used.% \cite{Gules}. 
-
+%
 PV systems are classified into distinct types~\cite{Mohanty}.
@@
 \subsection{Design and Simulation of Solar PV systems}
-%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
+The design and validation of a PV system can be done by hand or with the aid of a software tool.
+The PV sizing can be done using different methods, and here we reference the critical period as an effective one~\cite{Pinho}.
 %
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here we evaluated the most popular tools available in the literature and summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
+This section we evaluated the most popular tools available in the literature and summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
 
@@
 %-------------------------------------------------------------------
-\subsection{PV generator model}
-\label{sec:PVmodel}
+\subsection{PV system model}
+\label{sec:PVsystemmodel}
 %-------------------------------------------------------------------
@@
 %Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
-A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves).
+Mathematical models are required in order to allow the formal specification of the PV system. At this section we will summarize the models adopted at the paper.
+
+Related to \textbf{PV modules}, a wide variety of models exists for estimation of its power output  (and $I-V$ or $P-V$ curves).
 However, the present work will rely on the simplified model of 1-diode.
@@
 
-The PV generator model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers in data-sheets or manuals.
+%The PV generator model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers in data-sheets or manuals.
 %
@@
 %------------------------------------------------------------
-\subsection{The Battery Storage Model }
-\label{sec:BATmodel}
-%------------------------------------------------------------
-
 %Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system.
@@
 
-Various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Pinho};
+Related to the \textbf{batteries}, various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Pinho};
 %, and \cite{Manwell93, Manwell94}. 
@@
 %---------------------------------------------------------
-\subsection{Charge Controller Model}
 %---------------------------------------------------------
@@
 However, in this study, in order to simplify, the term used is controller.
-The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+
+The \textbf{charge controller} or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
 MPPT, or maximum power point tracking, is the electronic control mechanism mostly used nowadays and that maintains the PV operating at the voltage of maximum power.
@@
 %-----------------------------------------------
-\subsection{The inverter model}
 %-----------------------------------------------
@@
 %An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
-The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage, % (127 V or 220 V, for example), 
+The role of the \textbf{inverter} is to keep the voltage constant on the AC side, i.e., at the rated voltage, % (127 V or 220 V, for example), 
 and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by \eqref{eq:efficinv} \cite{Hansen}:
@@
 %
-%--------------------------------------------------
-\section{Stand-alone PV System Sizing and Verification}
-\label{sec:sizingcheck}
-%--------------------------------------------------
-In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a.
-sizing check).
-%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.
-
-Therefore this is a additional feature included at this paper.
-The sizing check will be performed by the proposed tool, and it will indicate if there is an error of sizing before to perform the automated verification of the system.
-This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.
-%
-Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
-\begin{equation}
-\label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
-\end{equation}
-
-Following, it is necessary to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, as defined by~\eqref{eq:Ep}.
-
-\begin{equation}
-\label{eq:Ep}
-E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
-\end{equation}
-
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV systems will be deployed, the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed by ~\eqref{eq:NTPmin} and the check is performed using ~\eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from ~\eqref{eq:NTPmin}.
-\begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NTP}
-N_{TP} \geq N_{TPmin}.
-\end{equation}
-
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.
-With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}).
-Where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
-
-\begin{equation}
-\label{eq:NPSmin}
-\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}}\leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NPS}
-N_{PS} \geq N_{PSmin}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NPP}
-N_{PP} \geq N_{PPmin}.
-\end{equation}
-
-Related to the batteries, firstly must be defined the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
-\begin{equation}
-\label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}.
-\end{equation}
-%
-\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
-$ V_{system} $ is the DC voltage of the bus, and the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
-%
-Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}.
-Additionally, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
-\begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
-\end{equation}
-
-\begin{equation}
-\label{eq:batcheck}
-\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total.
-\end{equation}
-
-Related to the charge controller, here the model with MPPT is adopted and initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage:
-\begin{equation}
-\label{eq:vcvsystem}
-V_{c} = V_{system}.
-\end{equation}
-
-Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
-%
-\begin{equation}
-\label{eq:iscamb}
-I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
-\end{equation}
-
-The controller must meet the maximum current from the PV array given by \eqref{eq:icmin} and \eqref{eq:icicmin}.
-\begin{equation}
-\label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP}.
-\end{equation}
-
-\begin{equation}
-\label{eq:icicmin}
-I_{c} \geq I_{c,min}.
-\end{equation}
-
-The sizing project check of the inverter is carried out by means of three equations.
-Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
-Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
-Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
-%
-\begin{equation}
-\label{eq:vindc} 
-V_{in}DC = V_{system}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:voutac} 
-V_{out}AC = V_{AC}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
-\end{equation}
-
-Worth to mention that the charge controller, the battery, and the inverter have a nominal efficiency presented at data sheets, and those numbers are very close to 100\%.
-However, based on empirical data, those efficiencies must be corrected, according to the loading of each component.
-If field or essay data is not available, considering that the proposed tools is aimed to be used prior the deployment of the PV system at the field, it is recommended (at least) to correct the battery efficiency ($\eta_{b}$) to 85\%, keeping the remaining efficiencies as expressed by the manufacturers.
 %
@@
 In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to worst monthly average solar energy method~\cite{Pinho}.
-The equations to check the PV sizing are present at Section~\ref{sec:sizingcheck}.
+In Step 2, the sizing check of the PV system takes place.
+Therefore this is a additional feature included at this paper.
+The sizing check will be performed by the proposed tool, and it will indicate if there is an error of sizing before to perform the automated verification of the system.
+This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.
 %

### 2019-05-08 Tex/elsevier/trindade_solar_energy_rev0.tex
updated paper text

@@
 %Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
-Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
-However, this growth is not driven by isolated systems.
-
-In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+Only a niche market a few years ago, solar PV systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
+%However, this growth is not driven by stand-alone systems.
+
+In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 %
@@
 However, those tools are based on running experiments in simulation models.
-Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+Simulation has the advantage of being cheap (if compared to test in real systems) %and can be employed before the system design is concluded
+but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
@@
 user requirements were performed by simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
-Related to formal methods, studies were carried out toward the modeling of power smart grids~\cite{Akram2018} and solar panels~\cite{Driouich2017}; however, those studies do not perform automated verification.
-%
-In addition, recent research performed a formal study of PV farms, where the focus has been the interaction with the grid~\cite{Abate2017}; or to model a PV system and to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
-Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.
-
+Related to formal methods, in 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
+The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
+Other related study from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking the non-functional properties such as time and energy~\cite{Cheng2015}.
+In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+The focus here is on HVAC (heating, ventilation, and air conditioning) systems.
+In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
+The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
+The author used approximate model checking of stochastic and hybrid models.
+In 2018, a verification methodology was proposed with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
+Another work from 2018 was the approach to modeling smart grid components using a formal specification.
+The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
+The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods.
+This approach is based on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
+%%%%%%%%%%%%%
 %The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
 %This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
-This paper makes three original contributions.
+
+This paper makes three contributions.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
@@
 Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies.
-Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation.
+Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation.
 
@@
 %The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
-
-\textit{Outline}.
+%\textit{Outline}.
 Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
@@
 Section~\ref{sec:Conclusions} presents the conclusion and describes future work.
-
+%
 %--------------------------------------------------------
@@
 
-\subsection{Design and Simulation of Solar PV systems}
-The design and validation of a PV system can be done by hand or with the aid of a software tool.
-The PV sizing can be done using different methods, and here we reference the critical period as an effective one~\cite{Pinho}.
+\subsection{Sizing and Simulation of Solar PV systems}
+The sizing and validation of a PV system can be done by hand or with the aid of tools. Here we reference the critical period~\cite{Pinho} as an effective method to PV sizing.
 %
@@
 %Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-This section we evaluated the most popular tools available in the literature and summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
-
+
+The most popular softwares are summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
 %\subsection{PVWatts Calculator}
@@
 %Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where 
-As highlights, only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
+As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
 However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription typically range from US\$504.00 to US\$657.00.
-
+%
 \begin{table}[!t]
@@
 \end{table}
-
+%
 %-------------------------------------------------------------------
@@
 %-------------------------------------------------------------------
-\subsection{PV system model}
+\subsection{PV System Model}
 \label{sec:PVsystemmodel}
@@
 
-\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions
-(provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Villalva} that is provided by PV manufacturers ($ I_{sc,ref} $).
+\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$); %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions.
+$ I_{ph,ref} $ can be approximated to the reference short-circuit current ($ I_{sc,ref} $)\cite{Villalva}.
+% that is provided by PV manufacturers ($ I_{sc,ref} $).
 %\cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
@@
 
-\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet \cite{Ross}, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
+\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C), and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
 
@@
 \end{multline}
-
-Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period.
+%
+%Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period.
 %; however, during recharge it is much more difficult \cite{Copetti}.
@@
 
-The \textbf{charge controller} or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-MPPT, or maximum power point tracking, is the electronic control mechanism mostly used nowadays and that maintains the PV operating at the voltage of maximum power.
-Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
+The \textbf{charge controller} or controller can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+MPPT, or maximum power point tracking, is the electronic control mechanism mostly used nowadays and that maintains the PV operating at the stage of maximum power.
+%Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
 %
@@
 %--------------------------------------------------
-Each stand-alone PV system, like any other power systems, has a specific level of availability.
+%Each stand-alone PV system, like any other power systems, has a specific level of availability.
 This reliability level impacts various issues, as system performance, production, feasibility, and investment.
@@
 The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
-
 The system availability definition depends on how critical the load application is.
@@
 An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
-
-With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong.
+%
+%With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong.
 It is important to evaluate how critical the load application is and the horizon of evaluation.
@@
 The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
-Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+%Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
 %CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
@@
 %
-The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
+The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
 
@@
 
-In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
+In Step 1, the PV input data %(e.g., load power demand and load energy consumption) 
+and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
 In Step 2, the sizing check of the PV system takes place.
@@
 
-The first automated verification is related to the sizing check, according described at Section ~\ref{sec:sizingcheck}.
-Then two functions, called at lines 4 and 5, are responsible for discover which hour starts the photovoltaic generation and when stops.
+The first automated verification is related to the sizing check (line 3).
+Then two functions, called at lines 4 and 5, are responsible for discover which hour starts the PV generation and when stops.
 Those functions get this information from the array inputted to the Algorithm with the solar irradiance values.
 
-The batteries are assumed to have SOC of 100\% (Line 6), i.e., the batteries are charged. That is important because the system is said ready to use when the batteries are charged.
-
-The first for-loop at Line 7 controls how many cycles of 24h will be performed by the Algorithm.
+The batteries are assumed to be charged, i.e., with SOC of 100\% (line 6).
+
+The first for-loop at line 7 controls how many cycles of 24h will be performed by the Algorithm.
 And the for-loop from lines 8 to 11 is responsible to discharge the battery (according the load curve) and verify the state of charge of the battery, hour-by-hour, starting at the first hour of the day after the sun goes down until the next day before the sun goes up (when there is not PV generation).
@@
 
-After that, the model from PV generator is used in the function call of Line 17, to produce the voltage and current considering the states of $G$ and $T$.
-With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from Lines 18, 20, 22, 24 and 26, will imitate the charge controller work, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
-
-At the end of last for-loop, the state of the batteries is verified again (Line 27) and the hour is adjusted to the next loop (Line 28).
+After that, the model from PV generator is used in the function call of line 17, to produce the voltage and current considering the states of $G$ and $T$.
+With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller work, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+
+At the end of last for-loop, the state of the batteries is verified again (line 27) and the hour is adjusted to the next loop (line 28).
 
@@
 We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
-Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), were used to compare the approach effectiveness and efficiency.
+Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
 \begin{table}
@@
 
-In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool.
-All the experiments were performed with a timeout of 14,400 seconds (4 hours).
+%In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool.
+All the experiments were performed with a timeout of 14,400 seconds.
 %Every dweller, who owns a PV system, was interviewed
-
+%
 All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
-The setup of HOMER Pro simulation tool: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.
+The setup of HOMER Pro v3.12.0: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
+The experiments were performed with timeout of 14,400 seconds.
 
@@
 
-Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c --unwind 100 --trace}.
+Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c -\phantom{}-unwind 100 -\phantom{}-trace}.
 
@@
 %
-%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
+%\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
 %\begin{enumerate}
@@
 %
-Table~\ref{cases} summarizes the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
-The times reported in Table~\ref{cases} answer RQ2.
-
-Note that if we used HOMER Pro in all case studies, the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
+Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
+Note that an UNKNOWN result from our verification engines does not mean that a failure was found (i.e., SAT) neither that the verification is successful (i.e., UNSAT).
+An UNKNOWN result indicates that the verification engine led to  an \textit{out of memory} or a \textit{time out} situation.
+
+%HOMER Pro result: the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
 The simulation took less than five seconds to be performed on each case study.
-
+%
 \begin{table}
@@
 
-Note that an UNKNOWN result from our verification engines does not mean that a failure was found (i.e., SAT) neither that the verification is successful (i.e., UNSAT).
-An UNKNOWN result indicates that the verification engine led to  an out of memory or a time out situation.
-
 The description of our experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
@@
 Using ESBMC with Boolector led to an out of memory situation in all the case studies.
-This result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
+This result was obtained in less than six minutes of execution, i.e., the 64GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
 However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.
@@
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
-This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in Line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code (much more complex).
+This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
 
@@
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
-This verification took less than 1s to be performed as well, for the same reason described during the results of the ESBMC engine.
+This verification took less than 1s to be performed as well.
 
@@
 Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700W systems.
-This is because the time out set up was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
-However, when verifying the 1,200W PV system, the tool presented a SAT message, i.e., a failure was found, with the counterexample indicating the line (337) of the code, the same one appointed by the other verification engines, related to the charge controller.
-
-In order to validate the possible flaw from house 5, presented by all verification engines, we have surveyed the owner of the 1,200 W system.
-We identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
-However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
+This is because the \textit{time out} limit was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
+However, when verifying the 1,200W PV system, the tool presented a SAT message equal to the other engines.
+
+In order to validate the possible flaw from house 5, we have surveyed the owner of the 1,200 W system.
+We identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
+The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
+However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system %($96.67\% = 100\%-3.33\%$)
+and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
 %\begin{figure}[h]
@@
 All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
-Fig.
+%Fig.
 \ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software, specifically to house 1.
-
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{homer.png}
-\centering
-\caption{HOMER simulation screen.}
-\label{fig:homerscreen}
-\end{figure}
-%
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.8\textwidth]{homer.png}
+%\centering
+%\caption{HOMER simulation screen.}
+%\label{fig:homerscreen}
+%\end{figure}
+%
+
 There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
@@
 \textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
-A careful evaluation in a PV laboratory to validate the model could add more reliability to the results produced by our method.
-
-\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario, where a solar irradiance and ambient temperature can change in fractions of minutes.
-
-\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed if other places around the world could become case studies.
+The adoption of more complex models, or even an evaluation in a PV laboratory to validate the model could add more reliability to the results.
+
+\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.
+
+\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.
 
@@
 We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
-We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
+We have considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
 Although the verification method proposed takes longer than simulation methods, it is able to present details (counterexample) that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
 In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail.
-Related to the verification engines comparative, the ESBMC tool with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2G bytes when compared to 9.2G bytes of CBMC and 19.2G bytes of CPAchecker), and all the results were correct because the simulation tool presented the same results, besides the fact that interviews with the dwellers validated the possible flaws that the system could be presenting in the field.
+Related to the verification engines comparative, the ESBMC tool with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were correct because the simulation tool presented the same results, besides the fact that interviews with the dwellers validated the possible flaws that the system could be presenting in the field.
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
-As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems.
-We will also consider other types of renewable energy and even hybrid ones to allow our method to design and verify typical rural electrification.
+As future work, we will also consider other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
+%the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems.
+%We will also consider other types of renewable energy and even hybrid ones to allow our method to design and verify typical rural electrification.
 %
@@
 \section*{Acknowledgments}
-The authors would like to thank Coventry University for the availability of the case studies (real PV systems) to validate the tool and to support the mobility of one researcher to UK.
-This work was supported by Newton Fund [grant number 261881580] with the mobility of one researcher to UK; FAPEAM - Amazonas State Foundation for Research Support [grants from call 009/2017 and PROTI Pesquisa 2018], for the financial support related to the Virtual Machine rent (December 2018 to January 2019), for the DCTIEX II scholarship (November 2018), and for support the mobility of the researcher; and FAS - Sustainable Amazonas Foundation for the PhD scholarship (from November 2017 to March 2019).
+The authors would like to thank Coventry University for the availability of the case studies  and to support the research mobility.
+This work was supported by Newton Fund [grant number 261881580] with the research mobility; FAPEAM - Amazonas State Foundation for Research Support [grants from call 009/2017 and PROTI Pesquisa 2018], for the financial support related to the Virtual Machine (DEC-2018 to JAN-2019), for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; and FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019).
 

### 2019-05-08 Tex/elsevier/trindade_solar_energy_rev0.tex
updated paper text

@@
 \usepackage{lineno,hyperref}
-\modulolinenumbers[5]
+\modulolinenumbers[1]
+\linenumbers
 
@@
 %% Vancouver numbered
-\usepackage{numcompress}\bibliographystyle{model3-num-names}
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
 
 %% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
 
@@
 This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
+Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
 Different verification tools were evaluated as well, in order to compare performance and soundness.
@@
 \section{Introduction}
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
+Lack of access to clean and affordable energy is considered a core dimension of poverty~\citep{Hussein2012}.
+There is a close relationship between the lack of energy and the low HDI (Human Development Index)~\citep{Coelho}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\citep{IEAweo2018}.
 %The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
 Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
-Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
-
-In order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
+%Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
+
+In order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\citep{IEAweo2018}.
 
@@
 %Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
-Only a niche market a few years ago, solar PV systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
+Only a niche market a few years ago, solar PV systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\citep{EPIA}.
 %However, this growth is not driven by stand-alone systems.
 
-In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \citep{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \citep{Gow1999,Benatiallah2017}.
 %
@@
 Simulation has the advantage of being cheap (if compared to test in real systems) %and can be employed before the system design is concluded
-but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-
-Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
+but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\citep{ClarkeHV18}.
+
+Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\citep{ClarkeHV18}.  
 %with behavior that is, in principle, well determined. 
@@
 The model checking tool reports in which conditions a system does not meet the user requirements.
-A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
+A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\citep{Akram2018}.
 %Those programs are viewed as mathematical objects, and the use of 
@@
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the proposed tool is carried out by means of an algorithm written in language C, that is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
+The implementation of the proposed tool is carried out by means of an algorithm in language C, that is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\citep{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\citep{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
 %three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
@@
 In prior studies, the evaluation of PV systems w.r.t.
-user requirements were performed by simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
-Related to formal methods, in 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
-The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
-Other related study from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking the non-functional properties such as time and energy~\cite{Cheng2015}.
-In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
-The focus here is on HVAC (heating, ventilation, and air conditioning) systems.
-In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
-The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
-The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
+user requirements were performed by simulation tools using MATLAB/Simulink~\citep{Benatiallah2017, Natsheh2012}, or HOMER Pro \citep{Lamnadi2017}, where some mathematical model was adopted and the tool simulated the PV behavior over the time.
+Related to formal methods, in 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\citep{Sengupta2015}.
+The authors proposed an automated simulation-based verification technique to verify correctness of protection settings using hybrid automata-temporal-logic framework.
+In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared-smart infrastructure~\citep{Abate2017}.
+The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings and smart grids.
 The author used approximate model checking of stochastic and hybrid models.
-In 2018, a verification methodology was proposed with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+In 2018, a verification methodology was proposed with applications to PV panels and its distributed power point tracking~\citep{Driouich2018}.
 This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
+The simulation results obtained by JModelica had evident time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
 Another work from 2018 was the approach to modeling smart grid components using a formal specification.
-The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
-The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods.
-This approach is based on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
+The authors used a state-based formal specification language named Z; they demonstrated the application to four smart grid components~\citep{Akram2018}.
+This approach is based on Petri nets.
 %%%%%%%%%%%%%
@@
 
-This paper makes three contributions.
+This paper makes two main contributions.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
@@
 Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies.
-Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation.
+%Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation.
 
@@
 %The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
-%\textit{Outline}.
+\textit{Outline}.
 Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
 Section~\ref{sec:AutomatedVerification} presents the automated verification technique.
-Section~\ref{sec:sizingcheck} shows how to perform the sizing of a stand-alone PV system.
 The methodology is presented in section~\ref{sec:Methodology}.
@@
 %
-PV systems are classified into distinct types~\cite{Mohanty}.
+PV systems are classified into distinct types~\citep{Mohanty}.
 %: (1) stand-alone systems, where the energy is generated and consumed in the same place and which do not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system.
@@
 %can be split into several categories. However, 
-the most suitable configuration is the regulated stand-alone system with battery and AC load; this configuration is the focus of this study.
+the most suitable configuration is the regulated stand-alone system with battery and AC load. %; this configuration is the focus of this study.
 %, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
@@
 
-\subsection{Sizing and Simulation of Solar PV systems}
-The sizing and validation of a PV system can be done by hand or with the aid of tools. Here we reference the critical period~\cite{Pinho} as an effective method to PV sizing.
+\subsection{Sizing and Simulation of Stand-alone Solar PV systems}
+The sizing and validation of a PV system can be done by hand or with the aid of tools. Here we reference the critical period~\citep{Pinho} as an effective method to stand-alone PV sizing.
 %
@@
 
-The most popular softwares are summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
+The most popular softwares are summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\citep{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
 %\subsection{PVWatts Calculator}
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Comparative coverage of reference software}
+\caption{Comparative coverage of reference simulation software}
 \label{table:softwares}
@@
 %
-In this study, only HOMER has the minimum features for a comparative with our proposed verification approach.
-That evaluation is presented in Section~\ref{sec:results_indeed}.%All tools need some parameters inherently from manufacturer's catalog.
+In this study, HOMER was chosen to comparative with our proposed verification approach (Section~\ref{sec:results_indeed}).%All tools need some parameters inherently from manufacturer's catalog.
 %, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
@@
 A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-The PV generator (panel or array) is a semiconductor device that can convert solar energy into DC electricity.
+The PV generator is a semiconductor device that can convert solar energy into DC electricity.
 %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
-For night hours or rainy days, we need to hold batteries, where power can be stored and used.
-The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}.
+For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\citep{Hansen}.
 The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
@@
 \centering
-\caption{Block diagram for a typical stand-alone PV system (adapted from~\cite{Hansen}).}
+\caption{Block diagram for a typical stand-alone PV system (adapted from~\citep{Hansen}).}
 \label{fig:blockdiagram}
@@
 
-Related to \textbf{PV modules}, a wide variety of models exists for estimation of its power output  (and $I-V$ or $P-V$ curves).
-However, the present work will rely on the simplified model of 1-diode.
-It was demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
+\textbf{PV modules}: a wide variety of models exists. % for estimation of its power output  (and $I-V$ or $P-V$ curves). 
+However, the present work will rely on the simplified model of 1-diode, illustrated in Fig.
+\ref{fig:equivckt}.
+This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\citep{Saloux}.
 
@@
 \centering
-\caption{1-diode equivalent PV cell/panel circuit model (adapted from~\cite{Cubas}).}
+\caption{1-diode equivalent PV cell/panel circuit model (adapted from~\citep{Cubas}).}
 %\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
@@
 
-The 1-diode model, illustrated in Fig.
-\ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described by ~\eqref{eq:1diodemodel}.
+The Eq.
+\eqref{eq:1diodemodel} relates the output current, $I$, to the output voltage, $V$.
 %This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
@@
 \noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
-$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
+$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}\:J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}\:C $).
 
@@
 %
-The voltage and the current at the maximum power point tracking (MPPT), can be described by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm}  as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
+The voltage and the current at the maximum power point tracking (MPPT), can be described by Eq.
+\eqref{eq:Vmfinal}, and Eq.
+\eqref{eq:Imfinal}~\citep{Saloux}: %, and Eq.
+\eqref{eq:Pm} as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
 \begin{equation}
@@
 
-\begin{equation}
-\label{eq:Pm}
-P_{m} = V_{m} I_{m}.
-\end{equation}
-
+%\begin{equation}
+%\label{eq:Pm}
+%P_{m} = V_{m} I_{m}.
+%\end{equation}
+%
 %\begin{multline}
@@
 However, the photo-current delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, ~\eqref{eq:Iph} is used to calculate the photo-current as function of irradiance and temperature~\cite{Villalva}:
+Therefore, Eq.
+~\eqref{eq:Iph} is used to calculate the photo-current as function of irradiance and temperature~\citep{Villalva}:
 \begin{equation}
@@
 
-\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$); %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions.
-$ I_{ph,ref} $ can be approximated to the reference short-circuit current ($ I_{sc,ref} $)\cite{Villalva}.
+\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000\:W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}\:C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$); %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions.
+$ I_{ph,ref} $ can be approximated to the reference short-circuit current ($ I_{sc,ref} $)\citep{Villalva}.
 % that is provided by PV manufacturers ($ I_{sc,ref} $).
@@
 %%
-The cell temperature ($ T $) in degree Celsius is described by ~\ref{eq:Tcell}~\cite{Ross}:
+The cell temperature ($ T $) in degree Celsius is described by Eq. \ref{eq:Tcell}~\citep{Ross}:
 \begin{equation}
@@
 
-Furthermore, ~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\cite{Villalva} 
+Furthermore, Eq. ~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\citep{Villalva} 
 %In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
@@
 %The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current (cf.
-~\eqref{eq:Imfinal}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor~\cite{Saloux} is determined by ~\eqref{eq:a}:
+Using the maximum power point current, cf.
+Eq.~\eqref{eq:Imfinal}, and the saturation current in the reference temperature given by Eq.~\eqref{eq:I0}, the diode ideality factor~\citep{Saloux} is determined by Eq.~\eqref{eq:a}:
 \begin{equation}
@@
 
-Related to the \textbf{batteries}, various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Pinho};
+Related to the \textbf{batteries}, various models have been described in the literature and the most common ones are based on lead-acid batteries~\citep{Copetti,Pinho};
 %, and \cite{Manwell93, Manwell94}. 
@@
 %
-that kind of battery has relative low cost and wide availability~\cite{Copetti}. 
-%
-Here, the model adopted uses only manufacturer's data without empirical tests~\cite{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature. 
-%
-The discharge voltage equation is described by \eqref{eq:bat_Vd}.
+that kind of battery has relative low cost and wide availability~\citep{Copetti}. 
+%
+Here, the model adopted uses only manufacturer's data without empirical tests~\citep{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature. 
+%
+The discharge voltage is described by Eq. \eqref{eq:bat_Vd}.
 %The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
@@
 
-\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $%, $ T_{ref}=25^{o}C $
+\noindent where $C_{10}$ means 10 h of rated capacity (manufacturer's data-sheet), $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $%, $ T_{ref}=25^{o}C $
 ), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time.
-Mathematically, it is the ratio between the present capacity and the nominal capacity% (in $ Ah $, provided by manufacturer)
-. If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
+%Mathematically, it is the ratio between the present capacity and the nominal capacity% (in $ Ah $, provided by manufacturer)
+%If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
 %\begin{equation}
@@
 %Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
-For the charging process, however, the parameters are described by ~\eqref{eq:Vcbat} as
+For the charging process, the parameters are described by Eq.~\eqref{eq:Vcbat} as
 %
@@
 
-The \textbf{charge controller} or controller can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-MPPT, or maximum power point tracking, is the electronic control mechanism mostly used nowadays and that maintains the PV operating at the stage of maximum power.
+The \textbf{charge controller} or controller is the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+Controllers with MPPT mechanism are the mostly used nowadays,  and it maintains the PV operating at the stage of maximum power.
 %Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
@@
 
-To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \_ off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}.
+The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.
+To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \_ off}$ and when the current required by the load is less than the current delivered by the PV arrays~\citep{Hansen}.
 PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \_ on} $.
@@
 %
-In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \_ off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}.
+In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \_ off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\citep{Hansen}.
 The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \_ on}$.
@@
 %
-The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.
-
 \begin{table}[!t]
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process (adapted from~\cite{Hansen})}
+\caption{Summary of the controller process (adapted from~\citep{Hansen})}
 \label{table:controller}
@@
 %As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of controller is given by \eqref{eq:poutcont}.
+The output power ($ P_{out} $) of controller is given by Eq. \eqref{eq:poutcont}.
 \begin{equation}
@@
 
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from \eqref{eq:poutcont} we compute \eqref{eq:potcont}.
+Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Eq. \eqref{eq:poutcont} we compute Eq. \eqref{eq:potcont}.
 \begin{equation}
@@
 %An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
-The role of the \textbf{inverter} is to keep the voltage constant on the AC side, i.e., at the rated voltage, % (127 V or 220 V, for example), 
-and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by \eqref{eq:efficinv} \cite{Hansen}:
+The role of the \textbf{inverter} is to keep the voltage constant on the AC side, %, i.e., at the rated voltage, % (127 V or 220 V, for example), 
+and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by \eqref{eq:efficinv} \citep{Hansen}:
 %
@@
 
-\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be obtained from the inverter's data-sheet.
+\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be obtained from the inverter's manual.
 
@@
 This reliability level impacts various issues, as system performance, production, feasibility, and investment.
-The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
+The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\citep{Khatib2014}.
 The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
@@
 While in a ordinary house electrical load, 95\% is considered acceptable.
-As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system.
+%As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system.
 An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}.
-Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\citep{ClarkeHV18}.
+Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\citep{Clarke2012}.
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\citep{Clarke2012}.
 Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
+The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\citep{Kroening}.
 CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
-If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
+If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\citep{Kroening}.
 CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\citep{esbmc2018}, which supports the verification of LTL properties with bounded traces~\citep{DBLP:journals/sosym/MorseCN015}.
 ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\citep{Morse2015}.
 This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+This technique is called ``incremental SMT''~\citep{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Automatic program verification requires a choice between precision and efficiency. The
-more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was
-reflected in two major approaches to static verification: program analysis and model
-checking.
+Automatic program verification requires a choice between precision and efficiency.
+%The more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs.
+Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
 In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
@@
 Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
+The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\citep{Beyer2011}.
 Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
+The CPA framework provides interfaces to SMT solvers and interpolation procedures~\citep{Beyer2011}.
 %Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
@@
 In Step 1, the PV input data %(e.g., load power demand and load energy consumption) 
-and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place.
-Therefore this is a additional feature included at this paper.
-The sizing check will be performed by the proposed tool, and it will indicate if there is an error of sizing before to perform the automated verification of the system.
-This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.
+and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\citep{ANSI2018}.
+In Step 2, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
+This stage ensures that the system meets the standard project steps related to critical period method of sizing~\citep{Pinho}.
 %
@@
 and properties %($P$) 
-from the PV system that are provided by the user, and the tool will automatically verify if the PV system requirements are met.
+from the PV system, and the tool will automatically verify if the PV system requirements are met.
 If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
@@
 
-Algorithm~\ref{alg:verification-algorithm} describes the pseudo-code used to perform the automated verification.
+Algorithm~\ref{alg:verification-algorithm} describes the equivalent pseudo-code.
 %Line 1 indicates a function call that performs the size checking of the each component of the PV system.
@@
 % caused by the state explosion inherent of the technique, 
-every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation), when the batteries are demanded to feed the house.
+every 24 h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation), when the batteries are demanded to feed the house.
 
 Lines 1 is devoted to information from the location where the PV system will be/were deployed.
-Usually the information of annual average minimum and maximum, related to temperature ($T$) and solar irradiance ($G$), hour by hour, are obtained from specific historical weather web sites~\cite{Temperature}, ~\cite{Irradiance}.
-
-Line 2 represents all the information that comes from the PV sizing and from the equipment manufacturers data, as PV panels specification and data, batteries specification and data, inverter details and charge controller details.
-This item includes as well information from the house's load curve.
-
-The first automated verification is related to the sizing check (line 3).
+We use annual average minimum and maximum, related to temperature ($T$) and solar irradiance ($G$), hour by hour, from~\citep{Temperature}, and ~\citep{Irradiance}.
+
+Line 2 represents all the information that comes from the PV sizing and from the equipment manufacturers data: specification and data from PV, batteries, inverter and charge controller.
+This item includes as information from the house's load curve.
+
+The first automated verification is related to the sizing check (line 3), if an error is found then the algorithm stops.
 Then two functions, called at lines 4 and 5, are responsible for discover which hour starts the PV generation and when stops.
@@
 
-The first for-loop at line 7 controls how many cycles of 24h will be performed by the Algorithm.
-And the for-loop from lines 8 to 11 is responsible to discharge the battery (according the load curve) and verify the state of charge of the battery, hour-by-hour, starting at the first hour of the day after the sun goes down until the next day before the sun goes up (when there is not PV generation).
+The first for-loop at line 7 controls how many cycles of 24 h will be performed by the Algorithm.
+And the for-loop from lines 8 to 11 is responsible to discharge the battery (according the load curve) and verify the state of charge of the battery, hour-by-hour, starting at the first hour of the day after the sun goes down until the next day before the sun goes up (without PV generation).
 Following, at the next for-loop, from line 12 to 29, is performed the verification where there is solar irradiance and all the PV system works.
-The Algorithm generates information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, hour-by-hour, using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range (lines 15 and 16).
+The Algorithm generates information related to average temperature ($T$) and solar irradiance ($G$), hour-by-hour, using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range (lines 15 and 16).
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
@@
 
-Nevertheless, if the verification engine does not fail, then we can conclude that the PV system does not need further corrections up to the given bounds $k$.
+Nevertheless, if the verification engine does not fail, we can conclude that the PV system does not need further corrections up to the given bound $k$.
 %
@@
   \STATE $SOC \leftarrow 100\%$ \\
-
 %  \COMMENT {Starting with the PV generation time}
@@
 %if it was a project error or if it was a combination of variables from the nature that has a low probability to occur at the field, considering the intermittent characteristic of solar PV generation.
-
+%
 %\subsection{Subsection Heading Here}
@@
 %
-
 %------------------------------------------
@@
 We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
-Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
+%Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
 \begin{table}
@@
 \hline
-PV Panels &  \multicolumn{4}{|c|}{3x 325W: in series} & 4x 325W: 2x series, 2x parallel \\
-\hline
-Batteries & \multicolumn{4}{|c|}{\makecell{4x220Ah: 2x series, 2x parallel\\ autonomy: 48h}} & \makecell{4x 120Ah batteries in series\\ autonomy: 6h}\\
-\hline
-Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150V/35A}\\
-\hline
-Inverter & \multicolumn{4}{|c|}{700W with peak of 1,600W} & 1,200W with peak of 1,600W\\
-\hline
-Power demand & 253W & 263W & 283W & 501W & 915W\\
+PV Panels &  \multicolumn{4}{|c|}{3x 325 W: in series} & 4x 325 W: 2x series, 2x parallel \\
+\hline
+Batteries & \multicolumn{4}{|c|}{\makecell{4x220 Ah: 2x series, 2x parallel\\ autonomy: 48 h}} & \makecell{4x 120 Ah batteries in series\\ autonomy: 6 h}\\
+\hline
+Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
+\hline
+Inverter & \multicolumn{4}{|c|}{700 W, peak of 1,600 W} & 1,200 W, peak of 1,600 W\\
+\hline
+Power demand & 253 W & 263 W & 283 W & 501 W & 915 W\\
 \hline
@@
 \end{table}
-
 %------------------------------------------
@@
 
-Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
-
-Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c -\phantom{}-unwind 100 -\phantom{}-trace}.
+Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\citep{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled; % with the goal of reducing memory usage; we have also used
+with SMT solver Z3 version 4.7.1~\citep{DeMoura}.
+
+Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\citep{Kroening}\footnote{Command-line: \$ cbmc filename.c -\phantom{}-unwind 100 -\phantom{}-trace}.
 
@@
 %The experiments were performed without a predefined timeout.
-Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
+Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\citep{mathsat5}.
 An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness.
@@
 Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
-Note that an UNKNOWN result from our verification engines does not mean that a failure was found (i.e., SAT) neither that the verification is successful (i.e., UNSAT).
-An UNKNOWN result indicates that the verification engine led to  an \textit{out of memory} or a \textit{time out} situation.
+Note that an UNKNOWN result from our verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
 
@@
 \hline
-House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{5m08s \\(UNSAT)} & \makecell{19m02s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{4m27s \\(UNSAT)} & \makecell{18m59s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{5m07s \\(UNSAT)} & \makecell{18m39s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{4m37s \\(UNSAT)} & \makecell{18m36s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 08 s \\(UNSAT)} & \makecell{19 m 02 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 27 s \\(UNSAT)} & \makecell{18 m 59 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 07 s \\(UNSAT)} & \makecell{18 m 39 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 37 s \\(UNSAT)} & \makecell{18 m 36 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
 \hline
@@
 Using ESBMC with Boolector led to an out of memory situation in all the case studies.
-This result was obtained in less than six minutes of execution, i.e., the 64GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
+This result was obtained in less than six minutes of execution, i.e., the 64 GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
 However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.
-Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s.
+Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s.
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
-This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
+This verification took less than 1 s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
 
@@
 The experimentation returned SAT or UNSAT to all the case studies.
-Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18m36s to 19m02s.
+Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s.
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
-This verification took less than 1s to be performed as well.
+This verification took less than 1 s to be performed as well.
 
 Finally, the CPAchecker tool presented some different results.
-Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700W systems.
+Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700 W systems.
 This is because the \textit{time out} limit was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
-However, when verifying the 1,200W PV system, the tool presented a SAT message equal to the other engines.
+However, when verifying the 1,200 W PV system, the tool presented a SAT message equal to the other engines.
 
@@
 We identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
-However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system %($96.67\% = 100\%-3.33\%$)
+The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
+However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system %($96.67\% = 100\%-3.33\%$)
 and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
@@
 We have considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-Although the verification method proposed takes longer than simulation methods, it is able to present details (counterexample) that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
-In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail.
-Related to the verification engines comparative, the ESBMC tool with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were correct because the simulation tool presented the same results, besides the fact that interviews with the dwellers validated the possible flaws that the system could be presenting in the field.
+Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
+In particular, the proposed method was successful in finding sizing errors and indicating in details.
+Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
@@
 \section*{Acknowledgments}
-The authors would like to thank Coventry University for the availability of the case studies  and to support the research mobility.
-This work was supported by Newton Fund [grant number 261881580] with the research mobility; FAPEAM - Amazonas State Foundation for Research Support [grants from call 009/2017 and PROTI Pesquisa 2018], for the financial support related to the Virtual Machine (DEC-2018 to JAN-2019), for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; and FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019).
+The authors would like to thank: (i) Coventry University for the case studies and for the research mobility; (ii) Newton Fund [grant number 261881580] for the research mobility support; (iii) FAPEAM - Amazonas State Foundation for Research Support [grants 009/2017 and PROTI-Pesquisa 2018], for the Virtual Machine rent (DEC-2018 to JAN-2019), for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; and (iv) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019).
 

### 2019-05-10 code/opt_PVcode_rev4_case1.c
updated optmization code with 40 equipment

@@ -1,0 +1,238 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev4_improved database.c CASE 1
+ Author      : Alessandro Trindade
+ Version     : rev4 - May 2019: 40 equipment, lowerbound defined by SW
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
[…]

### 2019-05-10 code/opt_PVcode_rev4_case2.c

@@ -1,0 +1,237 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev4_improved database.c CASE 1
+ Author      : Alessandro Trindade
+ Version     : rev4 - May 2019
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
[…]

### 2019-05-10 code/opt_PVcode_rev4_case3.c

@@ -1,0 +1,238 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev3_improved database.c CASE 3
+ Author      : Alessandro Trindade
+ Version     : rev4 - May 2019
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
[…]

### 2019-05-17 Tex/Old text/thesis_rev0.tex
Thesis text organization

--- 2018-08-06 Tex/Old text/paper_old_rev0.tex
@@
-\documentclass[10pt,a4paper]{article}
-\usepackage[utf8]{inputenc}
+\documentclass[12pt,a4paper]{ltxdoc}
+\usepackage{lmodern}			% Usa a fonte Latin Modern			
+\usepackage[T1]{fontenc}		% seleção de códigos de fonte.
+\usepackage[utf8]{inputenc}		% determina a codificação utilizada (conversão automática dos acentos)
+\usepackage{hyperref}  			% controla a formação do índice
+\usepackage{parskip}			% espaçamento entre os parágrafos
+\usepackage{microtype} 			% para melhorias de justificação
+\usepackage{morefloats}			% permite mais floats
+\usepackage{setspace}
+%\singlespacing
+\onehalfspacing
+%\doublespacing
+%\setstretch{1.1}
+
+%\documentclass[10pt,a4paper]{article}
+%\usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
@@
 \usepackage{makecell}
-\usepackage{cite}
+\usepackage[alf]{abntex2cite}	% citacoes
 \graphicspath{ {./images/} }
 
-\title{Building a framework to perform automated verification of solar photovoltaic off-grid systems}
-\author{Alessandro Trindade \thanks{Federal University of Amazonas, Av.
-Rodrigo Octavio 3000, Coroado, Faculdade de Tecnologia, Campus Universitário, Manaus-AM, Brazil, alessandrotrindade@ufam.edu.br} \and Lucas Cordeiro \thanks{Department of Computer Science, University of Oxford, UK}}
+\title{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation}
+\author{Alessandro Bezerra Trindade \thanks{Federal University of Amazonas, Av.
+Rodrigo Octavio 3000, Coroado, Faculdade de Tecnologia, Campus Universitário, Manaus-AM, Brazil, alessandrotrindade@ufam.edu.br}}
 \date{}
@@
 \begin{abstract}
-The deployment of renewable energy in off-grid systems is growing in both developed and developing countries.
-With declining costs and increasing performance, off-grid renewable energy systems could become an important growth market for the future deployment of renewables according to International Renewable Energy Agency.
-The impact of off-grid renewable energy systems will not only be measured in terms of their usage or reduced costs for electricity consumption in rural areas, but also in the context of their effect on the lives of more than 1.3 billion people who today do not have access to electricity.
-Electrification of rural areas can improve the standard of education, health conditions, and living of this population.
-In addition, depending on the geography of the country, using renewable energy sources in off-grid mode is a feasible solution if compared to grid extension.
-Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to analyze, and evaluate rural electrification projects.
-This paper aims to build the framework to apply automated verification methods to mathematical models of a complete system of rural electrification with solar photovoltaic energy to validate its design from a formal verification perspective.
+xxxx
 
@@
 
+\begin{abstract}
+xxxx
+
+Palavras-chave:  ab c 
+\end{abstract}
+
 \section{Introduction}
+Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
+
+In order to simulate or evaluate a PV system, there are various specialized tools available in the market, e.g.
+RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.
+PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+However, those tools are based on simulation models, which are employed before the system design is concluded; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+
+Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of PV systems~\cite{ClarkeHV18}.
+
+///////////
+
 According to \cite{Coelho} there are presently 1.3 billion people with no access to electricity worldwide.
@@
 
+\subsection{Problem's Definition}
+
 In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
@@
 
+\subsection{Objectives}
 Bringing this idea to the field of solar photovoltaic systems, instead of finding a bug or a software inconsistence, the present work aim to verify a complete PV system project, informing in which condition the project do not meet user requirements or will fail.
@@
 
+The CBMC, it is notable its prominence through international awards received in competitions.
+In the works related to the CBMC, much of the research is focused on the improvement of the tool (as software and hardware verifier) and its performance in the competitions, without addressing, however, the question of PV system validation, as can be seen in \cite{Kroening}.
+For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.
+
+ESBMC was developed to perform bounded model checks on both sequential and concurrent programs using a range of SMT solvers, and has a proven track of bug finding in real-world applications \cite{Cordeiro}, \cite{Ramalho}.
+The tool also implements a technique to prove the correctness of (some) unbounded programs, the k-induction algorithm; this approach has been applied to a large number of benchmarks and has produced more correct results than similar competing tools \cite{GadelhaSBMF}, \cite{GadelhaK}.
+\cite{Trindade} show that is possible to perform the partitioning of hardware-software (optimization) using ESBMC as well.
+\cite{Bessa} show that is possible to use ESBMC to check the stability of digital control systems with uncertainty.
+In addition, \cite{Abateetal2017} show the approach to synthesize safe digital feedback controllers for physical plants represented as linear, time invariant models.
+However, the use of ESBMC to verify PV systems is unprecedented.
+
+Concerning modeling and simulation of electrical energy systems, \cite{Kremers} used an agent-base model approach to evaluate the effect of loads (refrigerators mainly), shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study.
+However, that is a software development approach for the simulation of complex systems, without the formalism of automated verification.
+
+In the other hand, the use of formal verification related to modeling and validation or even simulation of power systems or power networks is a young theme of research.
+According \cite{Abateetal2014}, where articles from seminars were issued at this thematic, the actual focus is on optimization and control of microgrids, HVAC systems (diagnostics and maintenance), models of generic wind turbine generation, modeling of transmission networks, and verification of smart grids.
+In addition, according with \cite{Abate2017}, recent research has attempted to formalize and implement a formal study of large population of PV panels (very common in European Union).
+The focus have been the modeling of the dynamics of PV panels and their interaction with the power grid.
+Those models do not use battery array, for example.
+
+Therefore, the present work unites the versatility and power of the formal models, applied to a formal verification tool, with individual PV systems (off-grid), which is the most indicated and common option to solve the problem of energy in developing countries.
+Especially those that have isolated communities, either for long distances of the great centers, or for being riverside.
+This work includes, based on its off-grid characteristic, batteries and charge controllers, differently of on-grid systems of related work.
+
+\subsection{Contributions}
+This paper makes two main contributions.
+% Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
+Secondly
+Firstly, we propose an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system.
+Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies.
+%Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation.
+
+Our work makes two major contributions.
+Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented.
+Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries)
+can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
+Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
+
+\subsection{Related Work}
+The conversion of traditional power grid into a smart grid, a fundamental example of a Cyber-Physical System (CPS), raises a number of issues that requires novel methods and applications.
+In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}.
+The focus of this study was on how CPs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system, as 	probability	of	node	failure	in	the	long run, impact	of	repair	service	on	the	failure	risk, and expected energy consumption.
+%, with no interest in power generation or even solar PV systems.
+
+In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
+The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
+The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
+%The study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
+
+Other related studies from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking for CPSs in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
+In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
+%The research did no deal with solar PV systems.
+
+In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
+The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
+The author used approximate model checking of stochastic and hybrid models.
+
+In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
+%The work did not include the other components of a stand-alone solar PV system.
+
+Another work from 2018 was the approach to modeling smart grid components using a formal specification.
+The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
+The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods.
+The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
+This approach is base on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
+
+\subsection{Thesis Organization}
 The remainder of this paper is organized as follows: Sect.
@@
 
-\section{Solar Photovoltaic System }
+\section{Background}
+\subsection{Solar Photovoltaic System }
 According to \cite{Roy}, a PV system is designed to give the electric supply to a load.
@@
 
-\subsection{Unregulated standalone PV system with DC load }
+\subsubsection{Unregulated standalone PV system with DC load }
 Usually this type of system is for low power applications, as defined by \cite{Roy}.
@@
 
-\subsection{Regulated standalone PV system with DC load}
+\subsubsection{Regulated standalone PV system with DC load}
 It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:regSPV1}.
@@
 
-\subsection{Regulated standalone system with battery and DC load}
+\subsubsection{Regulated standalone system with battery and DC load}
 Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}.
@@
 
-\subsection{Regulated standalone system with battery, AC load}
+\subsubsection{Regulated standalone system with battery, AC load}
 This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}.
@@
 
-\section{Design and Validation of a Solar photovoltaic system}
+\subsection{Design and Validation of a Solar photovoltaic system}
 The design and validation of a SPV system can be done by hand or with the aid of a software tool.
@@
 
-\subsection{PVWatts Calculator}
+\subsubsection{PVWatts Calculator}
 According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
@@
 
-\subsection{SAM}
+\subsubsection{SAM}
 SAM or System Advisor Model is a software from the U.S.
@@
 
-\subsection{HOMER}
+\subsubsection{HOMER}
 As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
@@
 
-\subsection{RETScreen}
+\subsubsection{RETScreen}
 As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
@@
 
-\subsection{Hybrid2}
+\subsubsection{Hybrid2}
 The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
@@
 
-\subsection{Paper Proposal x Reference Tools}
+\subsubsection{Paper Proposal x Reference Tools}
 Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER and RETScreen remain for comparative.
@@
 
-\section{Component models for stand-alone PV system }
+\subsection{Component models for stand-alone PV system }
 The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load.
@@
 
-\subsection{PV generator (cell, module, array) }
+\subsubsection{PV generator (cell, module, array) }
 A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. In the present modeling, the focus is only on cell/module/array.
@@
 
-\subsection{Proposed PV Panel Model}
+\subsubsection{Proposed PV Panel Model}
 With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1d1rmodel}.
@@
 
-\subsection{The Battery Storage Model }
+\subsubsection{The Battery Storage Model }
 Because of the fluctuating nature of the output delivered by the PV arrays, batteries are necessary in a PV system.
@@
 
-\subsection{Controller Model}
+\subsubsection{Controller Model}
 Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
@@
 
-\subsection{The inverter model}
+\subsubsection{The inverter model}
 As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
@@
 
-\section{Automated verification }
+\subsection{Automated Verification }
 It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.
@@
 
-\subsection{ESBMC }
+\subsubsection{ESBMC }
 According \cite{GadelhaSBMF}, ESBMC is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs.
@@
 
-\subsection{Cyber-physical systems x Energy x ESBMC}
+\subsubsection{Cyber-physical systems x Energy x ESBMC}
 According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes.
@@
 
-\section{Related work}
-The CBMC, it is notable its prominence through international awards received in competitions.
-In the works related to the CBMC, much of the research is focused on the improvement of the tool (as software and hardware verifier) and its performance in the competitions, without addressing, however, the question of PV system validation, as can be seen in \cite{Kroening}.
-For example, in \cite{Schrammel2017}, CBMC received an extension to perform verification of embedded software.
-
-ESBMC was developed to perform bounded model checks on both sequential and concurrent programs using a range of SMT solvers, and has a proven track of bug finding in real-world applications \cite{Cordeiro}, \cite{Ramalho}.
-The tool also implements a technique to prove the correctness of (some) unbounded programs, the k-induction algorithm; this approach has been applied to a large number of benchmarks and has produced more correct results than similar competing tools \cite{GadelhaSBMF}, \cite{GadelhaK}.
-\cite{Trindade} show that is possible to perform the partitioning of hardware-software (optimization) using ESBMC as well.
-\cite{Bessa} show that is possible to use ESBMC to check the stability of digital control systems with uncertainty.
-In addition, \cite{Abateetal2017} show the approach to synthesize safe digital feedback controllers for physical plants represented as linear, time invariant models.
-However, the use of ESBMC to verify PV systems is unprecedented.
-
-Concerning modeling and simulation of electrical energy systems, \cite{Kremers} used an agent-base model approach to evaluate the effect of loads (refrigerators mainly), shedding, grids, wind power generation, and smart grids, in a dynamic integral multi-scale case study.
-However, that is a software development approach for the simulation of complex systems, without the formalism of automated verification.
-
-In the other hand, the use of formal verification related to modeling and validation or even simulation of power systems or power networks is a young theme of research.
-According \cite{Abateetal2014}, where articles from seminars were issued at this thematic, the actual focus is on optimization and control of microgrids, HVAC systems (diagnostics and maintenance), models of generic wind turbine generation, modeling of transmission networks, and verification of smart grids.
-In addition, according with \cite{Abate2017}, recent research has attempted to formalize and implement a formal study of large population of PV panels (very common in European Union).
-The focus have been the modeling of the dynamics of PV panels and their interaction with the power grid.
-Those models do not use battery array, for example.
-
-Therefore, the present work unites the versatility and power of the formal models, applied to a formal verification tool, with individual PV systems (off-grid), which is the most indicated and common option to solve the problem of energy in developing countries.
-Especially those that have isolated communities, either for long distances of the great centers, or for being riverside.
-This work includes, based on its off-grid characteristic, batteries and charge controllers, differently of on-grid systems of related work.
+\section{Results}
 
@@
 
-\section{Nomenclature }
+%\section{Nomenclature }
 
@@
 \bibliography{trindadeThesis}{}
-\bibliographystyle{ieeetr}
-%\bibliographystyle{plain}
+%\bibliographystyle{ieeetr}
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
 %\printbibliography

### 2019-05-27 Tex/elsevier/trindade_appliedenergy_rev0.tex
new code optimization and paper

--- 2019-05-07 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
@@
-\documentclass[10pt,conference]{IEEEtran}
-% \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\bibliographystyle{IEEEtran}
-\usepackage{cite}
+\documentclass[review]{elsarticle}
+
+\usepackage{lineno,hyperref}
+%\modulolinenumbers[5]
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{xcolor}
-\def \BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 
- \renewcommand{\baselinestretch}{0.965}
+\journal{Applied Energy}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+%\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems}
+\begin{frontmatter}
+
+%\title{Innovative techno-economic optimization of stand-alone solar photovoltaic systems using automated formal synthesis} 
+\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
 %
-%\author{\IEEEauthorblockN{Alessandro Trindade}
-%\IEEEauthorblockA{
-%\textit{Federal University of Amazonas}, Brazil \\
-%alessandrotrindade@ufam.edu.br}
-%\and
-%\IEEEauthorblockN{Lucas Cordeiro}
-%\IEEEauthorblockA{
-%\textit{University of Manchester}, UK \\
-%lucas.cordeiro@manchester.ac.uk }
-%}
+%\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
+%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
 %
-\maketitle
+%% Group authors per affiliation:
+\author[mymainaddress]{Alessandro Trindade\corref{mycorrespondingauthor}}
+\cortext[mycorrespondingauthor]{Corresponding author}
+\ead{alessandrotrindade@ufam.edu.br}
+%\ead[url]{www.elsevier.com}
+
+\author[mysecondaryaddress]{Lucas Cordeiro}
+
+\address[mymainaddress]{Federal University of Amazonas, Av. Rodrigo Octávio, 6200, Coroado I, 69077-000 Manaus-AM-Brazil}
+\address[mysecondaryaddress]{University of Manchester, School of Computer Science, Kilburn Building, Manchester M13 9PL}
 
@@
 
-\begin{IEEEkeywords}
-automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
-\end{IEEEkeywords}
+\begin{keyword}
+automated verification \sep model checking \sep program synthesis \sep electrical systems \sep solar photovoltaic systems
+\end{keyword}
+
+\end{frontmatter}
+
+%\linenumbers
 
@@
 Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+
 \begin{equation}
 \label{eq:Ecorrected}
-\scriptstyle E_{corrected} = \dfrac{\scriptstyle E_{consumption}}{ \scriptstyle \eta_{b} \eta_{c} \eta_{i} }.
+E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
 \end{equation}
+
 %
@@
 %
+
 \begin{equation}
 \label{eq:Ep}
-\scriptstyle E_{p} = \scriptstyle Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
+E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
 \end{equation}
-%
+
 \noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
@@
 The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
-%
+
 \begin{equation}
 \label{eq:NTPmin}
-\scriptstyle N_{TPmin} = \dfrac{\scriptstyle E_{corrected}}{\scriptstyle E_{p}}.
+N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
 \end{equation}
-%
+
 Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
-%
+
 \begin{equation}
 \label{eq:NPSmin}
-\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}},
+\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
 \end{equation}
-%
+
 \begin{equation}
 \label{eq:NPPmin}
-\scriptstyle N_{PPmin} = \dfrac{\scriptstyle P_{total}}{\scriptstyle Number\,Panels\,Series \scriptstyle \times \scriptstyle P_{max,ref}},
+N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
 \end{equation}
-%
+
 \noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
@@
 Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
+
 \begin{equation}
 \label{eq:Cbank}
-\scriptstyle C_{bank} \scriptstyle = \dfrac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD},
+C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
 \end{equation}
-%
+
 \noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
@@
 Secondly, the total (minimum) number of batteries is computed as
+
 \begin{equation}
 \label{eq:Nbtotal}
-\scriptstyle N_{B}total = \scriptstyle N_{BS}min \scriptstyle \times \scriptstyle N_{BP}min = \dfrac{\scriptstyle V_{system}}{\scriptstyle V_{bat}} \scriptstyle \times \dfrac{\scriptstyle C_{bank}}{\scriptstyle 1 \,Battery \, Capacity}.
+N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
 \end{equation}
-%
+
 Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
@@
 \label{eq:vcvsystem}
-\scriptstyle V_{c} = \scriptstyle V_{system}.
+V_{c} = V_{system}.
 \end{equation}
-%
+
 The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as
-%
+
 \begin{equation}
 \label{eq:iscamb}
-\scriptstyle I_{sc,amb} = \dfrac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
+I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
 \end{equation}
-%
+
 The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin} as
+
 \begin{equation}
 \label{eq:icmin}
-\scriptstyle I_{c,min} = \scriptstyle I_{sc,amb} \times \scriptstyle N_{PP},
+I_{c,min} = I_{sc,amb} \times N_{PP},
 \end{equation}
-%
+
 \begin{equation}
 \label{eq:icicmin}
-\scriptstyle I_{c} \geq \scriptstyle I_{c,min}.
+I_{c} \geq I_{c,min}.
 \end{equation}
-%
+
 The inverter sizing check is performed by means of three equations.
@@
 \label{eq:vindc} 
-\scriptstyle V_{in}DC = \scriptstyle V_{system}.
+V_{in}DC = V_{system}.
 \end{equation}
-%
+
 \begin{equation}
 \label{eq:voutac} 
-\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
+V_{out}AC = V_{AC}.
 \end{equation}
-%
+
 \begin{equation}
 \label{eq:invcheck} 
-\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
+\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
 \end{equation}
+
 % -------------------------------------------------------
@@
  \begin{algorithmic}[1]
- \begin{scriptsize}
  \renewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
  \RETURN $(\,)$ 
-  \end{scriptsize}
  \end{algorithmic} 
@@
 % argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{trindadeThesis_menor}{}
+\section*{References}
+\bibliography{trindadeThesis}{}
 %\vspace{12pt}

### 2019-05-27 code/opt_PVcode_rev51_case2.c

@@ -1,0 +1,262 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev5_improved database.c CASE 1
+ Author      : Alessandro Trindade
+ Version     : rev5 - May 2019 : 40 equipment, lowerbound defined by SW, better HintCost
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2019-05-27 code/opt_PVcode_rev51_case3.c

@@ -1,0 +1,262 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev5_improved database.c CASE 3
+ Author      : Alessandro Trindade
+ Version     : rev5 - May 2019 : 40 equipment, lowerbound defined by SW, better HintCost
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2019-05-28 code/opt_PVcode_rev51_house2.c
new code optimization and paper

@@ -1,0 +1,266 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev5_improved database.c CASE HOUSE2
+ Author      : Alessandro Trindade
+ Version     : rev5 - May 2019: 40 equipment, lowerbound defined by SW, better HintCost
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2019-05-28 code/opt_PVcode_rev51_house3.c

@@ -1,0 +1,266 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev5_improved database.c CASE HOUSE3
+ Author      : Alessandro Trindade
+ Version     : rev5 - May 2019: 40 equipment, lowerbound defined by SW, better HintCost
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2019-05-28 code/opt_PVcode_rev51_house4.c

@@ -1,0 +1,266 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev5_improved database.c CASE HOUSE4
+ Author      : Alessandro Trindade
+ Version     : rev5 - May 2019: 40 equipment, lowerbound defined by SW, better HintCost
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2019-05-28 code/opt_PVcode_rev51_house5.c

@@ -1,0 +1,266 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev5_improved database.c CASE HOUSE5
+ Author      : Alessandro Trindade
+ Version     : rev5 - May 2019: 40 equipment, lowerbound defined by SW, better HintCost
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2019-05-30 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy text

@@
 \begin{abstract}
-Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space.
-We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
-The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained.
-Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
+Currently, there exist various methods and tools to size solar photovoltaic systems.
+The tools are mainly based on simulations, which do not cover all aspects of the design-space.
+We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based in technical issues, but that may not achieve the lowest cost; the optimal solution is then verified iteratively with a lower bound via symbolic model checking, if the verification step do not fail, the lower bound is adjusted and thefails, a counterexample is provided with the optimal sizing, linking the technical response of the first phase with cost analysis of the second phase.
+is obtainedto the synthesis engine and the process iterates until an optimal sizing is obtained.
+Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
 Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different intricate case studies.
+Experimental results using seven case studies show that our synthesis method is able to output within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
 \end{abstract}
@@
 in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
-%Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
-%Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
-%unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
-%
-%While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI}.
+Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
+
+While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
 Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS.
@@
 
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
-; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
+; and even general purpose simulation tools, e.g., PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
@@
 Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented.
-Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries)
+Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries)
 can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
 Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
+
+\textit{Outline}.
+Section~\ref{sec:Background} gives the background about related works, program synthesis, design sizing and validation of PV systems, and the mathematical modeling.
+Section~\ref{sec:Method} presents the automated formal synthesis proposed by this work.
+Section~\ref{sec:Results} is devoted to the experimentation, results and discussions.
+Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
 %
@@
 \section{BACKGROUND}
-\label{sec:AutomatedVerification}
+\label{sec:Background}
 %-----------------------------------------------------------
 %
+\subsection{State-of-art in Automated Verification of Electrical Systems}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The conversion of traditional power grid into a smart grid, a fundamental example of a CPS, raises a number of issues that requires novel methods and applications.
+In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}.
+The focus of this study was on how CPS integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system, as 	probability	of	node	failure	in	the	long run, impact	of	repair	service	on	the	failure	risk, and expected energy consumption, with no interest in power generation or even solar PV systems.
+
+In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
+The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
+The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
+The study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
+
+Other related studies from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
+In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
+The research did no deal with solar PV systems.
+
+In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
+The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
+The author used approximate model checking of stochastic and hybrid models.
+
+In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
+The work did not include the other components of a stand-alone solar PV system.
+
+Another work from 2018 was the approach to modeling smart grid components using a formal specification.
+The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
+The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods.
+The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
+This approach is base on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
 %-----------------------------------------------------------
@@
 As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.
+CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
+A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
@@
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{blockdiagramPVS2_rev}
+\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
 \centering
@@
 %------------------------------------------------------
-\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
+\section{METHOD}
+\label{sec:Method}
+
+\subsection{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
 %Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
@@
 Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+
+\subsection{Assumptions and Premises}
+
 %---------------------------------------------------------------------------
-\section{Results and Discussion}
+\section{RESULTS AND DISCUSSION}
+\label{sec:Results}
 %---------------------------------------------------------------------------
@@
 Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
+
+\section{CONCLUSIONS}
+Conclusions here
+\label{sec:Conclusion}
 %
 % argument is your BibTeX string definitions and bibliography database(s)
-\section*{References}
+%\section*{REFERENCES}
 \bibliography{trindadeThesis}{}

### 2019-05-31 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy text

@@
 \begin{abstract}
-Currently, there exist various methods and tools to size solar photovoltaic systems.
+There exist various methods and tools to size solar photovoltaic systems.
 The tools are mainly based on simulations, which do not cover all aspects of the design-space.
 We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based in technical issues, but that may not achieve the lowest cost; the optimal solution is then verified iteratively with a lower bound via symbolic model checking, if the verification step do not fail, the lower bound is adjusted and thefails, a counterexample is provided with the optimal sizing, linking the technical response of the first phase with cost analysis of the second phase.
-is obtainedto the synthesis engine and the process iterates until an optimal sizing is obtained.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based in power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
+If the verification step do not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, linking the technical response of the first phase with cost analysis of the second phase.
 Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
@@
 However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
- Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.
+ Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed.
+An ideal combination of any PV system is made by the best compromise between two considered objectives, which is power reliability and system cost~\cite{Alsadi2018}.
 
@@
 Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$.
+Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
 In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
-The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.
+The candidate solution is then verified via symbolic model checking with a lower bound that serve as the minimum cost of reference; if the verification do not fails, the lower bound is adjusted.
+And if it fails then a counterexample is provided with the optimal sizing that meet power reliability and system cost.
 
@@
 
-% -------------------------------------------------------
-\subsection{Optimal Sizing of PV Systems}
-% -------------------------------------------------------
+\subsection{PV systems Optimization Criteria}
+In order to select an optimal combination to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the system.
+An ideal combination for any PV system is made by the best compromise between those two objectives.
+
 %
@@
 %we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
-The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
-Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
+%The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
+%Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
 %the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
@@
 Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+\subsection{Stand-alone PV System Optimization Technique}
+To recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables.
+
 %------------------------------------------------------

### 2019-05-31 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 
+During the PV system design, one of the most important aspects to ensure power system security is to analyze power supply availability.
+The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
+A reliable power is a generation system that has sufficient power to feed load demand in a period.
+
+There are different methods to express system reliability, the most popular are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
+In both methods, if the probability is zero, then the load will always be fulfilled; while in the opposite (probability of one) then the load will never be fulfilled.
+
+LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
+And we say that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
+On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
+The main approaches to LPSP demand chronological simulation or probabilistic technique.
+In both, time series data is necessary, and dynamic behavior analysis.
+Data is not always available and dynamic analysis is complex, and this is a drawback.
+
+Related to economic analysis, there are several methods available.
+The aim is to determine wheter the project has or has not acceptable investment, and the usual is to perform economic analysis after reliability analysis in order to propose a system with high reliability and lowest cost~\cite{Alsadi2018}.
+Frequently are used the Net Present Cost (NPC), the Levelized Cost of Energy (LCOE), or the Life Cycle Cost (LCC).
+
+NPC is the total present value of a time series.
+The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an interest rate of internal rate of return (IRR).[90]
+
+LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost is considered [91].
+LCOE method is useful in comparing different generation technologies with different operating characteristics [6].
+
+LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value [92].
+Eq.~\ref{eq:LCC} is used to calculate LCC of a PV system,
+
+\begin{equation}
+\label{eq:LCC}
+LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
+\end{equation}
+
+\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs in present worth.
+
 %
@@
 Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
-Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
 \subsection{Stand-alone PV System Optimization Technique}
 To recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables.
+As number of optimization variables increases, the computation effort will exponentially increase [6].
+Hence, to obtain the best PV system design as well as simplified sizing process, past work introduced three main techniques for system sizing calculation [???], namely intuitive, numerical, and analytical methods.
+
+Intuitive method is simple, easy to be implemented, and can be used to give rough suggestion for preliminary design.
+The sizing rules are based on designer's experience, using lowest performance either in a time period data or by directly using average value (daily, monthly, or annual) of solar irradiance.
+This method do not the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
+
+Numerical method the design is simulated for each time step within a period.
+State of charge of batteries is calculated and investigated.
+It is very accurate, however is complex, demanding more time for calculation.
+
+Analytical methods is used to obtain a close relation of correlation in a form of equation between capacities and reliabilities.
+The sizing task become much simpler, however the relation cannot be applied at different sites, because is specific to one specific place of deployment of the PV system, demanding adaptation if another site is analyzed.
 
@@
 \subsection{Assumptions and Premises}
+Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}.
+The usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
+However, based on the fact that here we are neither considering site characteristics nor the load changes over time, which demands historical data, the reliability analysis will be developed only by the critical period method of PV sizing.
 
@@
 %---------------------------------------------------------------------------
-\textbf{Case studies.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
-Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems.
+\textbf{Case studies.} We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
+Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
 Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},

### 2019-06-01 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 To recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables.
-As number of optimization variables increases, the computation effort will exponentially increase [6].
-Hence, to obtain the best PV system design as well as simplified sizing process, past work introduced three main techniques for system sizing calculation [???], namely intuitive, numerical, and analytical methods.
+As number of optimization variables increases, the computation effort will increase as well.
+Hence, to obtain the best PV system design as well as simplified sizing process, past work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Alsadi2018}[6].
 
@@
 
-Analytical methods is used to obtain a close relation of correlation in a form of equation between capacities and reliabilities.
+Analytical methods is used to obtain a close relation or correlation in a form of equation between capacities and reliabilities.
 The sizing task become much simpler, however the relation cannot be applied at different sites, because is specific to one specific place of deployment of the PV system, demanding adaptation if another site is analyzed.
@@
 \subsection{Assumptions and Premises}
+Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was inputted to the code in order to allow the choice of the every item of PV sizing.
+Data sheet from each item is necessary to collect the technical data.
+And the price of each item was collected using the internet (in US dollars).
+
 Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}.
@@
 However, based on the fact that here we are neither considering site characteristics nor the load changes over time, which demands historical data, the reliability analysis will be developed only by the critical period method of PV sizing.
+
+Regarding the financial analysis:
+\begin{itemize}
+	\item LCOE lifetime considered: 20 years;
+	\item Battery lifetime: 4 years for lead-acid batteries. Therefore will be performed three battery bank replacements;
+	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost [Agrener2013];
+	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013].
+Includes circuit breakers, surge protection devices, electrical grounding, DC fuses, main switchboard, string boxes;
+	\item Value of the discount rate or interest rate: 10\%, what is a good rate considering financial investments in developing countries;
+	\item Operation and maintenance costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of USD [Agrener2013].
+\end{itemize}
+
+Regarding the PV system optimization technique, it will be adopted at this work the intuitive method, because is used the average value daily of solar irradiance at the mathematical model, without consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions.
+Therefore all the computation effort will be at the automated synthesis algorithm.
+
+Regarding all case studies, it was assumed that the minimum state of charge of batteries is 75\% (DOD maximum of 25\%), the voltage of the system is set in 24 V DC, and the AC voltage from the inverter is 120 V.
 
@@
 \begin{table}
-\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
-%\begin{scriptsize}
-\begin{tabular}{|c|c|c|}
+\caption{Case studies and results: optimization of PV systems.}\label{tab1}
+\begin{scriptsize}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
 \hline
-Specification & \makecell{ \textbf{Case Study 1} \\ Demand=501W \\ Peak=501W \\ Energy=3,900Wh/day\\Battery autonomy=48h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC} & \makecell{\textbf{Case Study 2}\\ Demand=915W \\ Peak=980W \\Energy=4,880Wh/day\\Battery autonomy=6h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC}\\
+Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro \\
 \hline
 \hline
-Tools & \textbf{Result} & \textbf{Result}\\
+Specification & Result & Result & Result & Result \\
 \hline
-\makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{UNKNOWN \\(Out of Memory)} & \makecell{UNKNOWN \\(Out of Memory)}\\
+\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (50.2 min) \\NTP=1$\times$330W (1S)\\NBT=8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\Cost=US\$ 1,902.60} & XYZ \\
 \hline
-\makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{UNKNOWN \\(Timeout)} & \makecell{UNKNOWN \\(Timeout)} \\
+\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (37.2 min) \\NTP=3$\times$330W (3S)\\NBT=2$\times$105Ah (2S)\\Controller 35A/145V\\Inverter 1,500VA/24V \\Cost=US\$ 2,235.57} & XYZ \\
 \hline
-%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
-%\hline
-\makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\Property violation line 209\\NTP=1$\times$330W (1S)\\NBT=8$\times$105Ahm (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\Property violation line 209\\NTP=3$\times$330W (3S)\\NBT=2$\times$105Ah (2S)\\Controller 35A/145V\\Inverter 1,500VA/24V \\Total Cost=US\$ 2,235.57}\\
+\makecell{\textbf{Case Study 3}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & SAT & XYZ \\
+\hline
+\makecell{\textbf{Case Study 4}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & SAT & XYZ \\
+\hline
+\makecell{\textbf{Case Study 5}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & SAT & XYZ \\
+\hline
+\makecell{\textbf{Case Study 6}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & SAT & XYZ \\
+\hline
+\makecell{\textbf{Case Study 7}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & TO & TO & XYZ \\
 \hline
@@
 \end{tabular}
-%\end{scriptsize}
+\\Legend: OM (out of memory), TO (timeout), IF (internal failure), E (energy).
+\end{scriptsize}
 \end{table}
+
 %

### 2019-06-01 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
-; and even general purpose simulation tools, e.g., PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g., PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+
 Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed.
@@
 This approach is base on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Automated Verification Using Model Checking}
+\label{sec:AutomatedVerification}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
+Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
+Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t.
+user requirements.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{CBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
+CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
+If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
+CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{ESBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{CPAchecker}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Automatic program verification requires a choice between precision and efficiency.
+The more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs.
+Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
+In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
+The CPA formalism provides an interface for the definition of program analyses.
+Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
+The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\citep{Beyer2011}.
+Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+The CPA framework provides interfaces to SMT solvers and interpolation procedures~\citep{Beyer2011}.
+Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+%CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
+For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
+\textcolor{red}{It is unclear what a CPA is.}
+%In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
 %-----------------------------------------------------------
@@
 	\centering
-	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
+	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
 	\caption{CEGIS applied to PV system sizing.}
@@
 Eq.~\ref{eq:LCC} is used to calculate LCC of a PV system,
-
 \begin{equation}
@@
 \end{equation}
-
 \noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs in present worth.
@@
 	\STATE non-deterministic variables hold feasible equipment and cost  \\
-	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
+	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
 	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
@@
 \subsection{Assumptions and Premises}
-Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was inputted to the code in order to allow the choice of the every item of PV sizing.
-Data sheet from each item is necessary to collect the technical data.
+Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was inputted to the code in order to allow the choice of every item of PV sizing.
+Data sheet from each item is necessary to collect the technical information.
 And the price of each item was collected using the internet (in US dollars).
 
-Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}.
+With respect to power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}.
 The usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
@@
 
-Regarding the financial analysis:
+Regarding financial analysis:
 \begin{itemize}
@@
 
-Regarding the PV system optimization technique, it will be adopted at this work the intuitive method, because is used the average value daily of solar irradiance at the mathematical model, without consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions.
+On the subject of PV system optimization technique, it will be adopted at this work the intuitive method, because is used the average value daily of solar irradiance at the mathematical model, without consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions.
 Therefore all the computation effort will be at the automated synthesis algorithm.
 
-Regarding all case studies, it was assumed that the minimum state of charge of batteries is 75\% (DOD maximum of 25\%), the voltage of the system is set in 24 V DC, and the AC voltage from the inverter is 120 V.
+Regarding all case studies, it was defined that the minimum state of charge of batteries is 75\% (DOD maximum of 25\%), the voltage of the system is set in 24 V DC, and the AC voltage from the inverter is 120 V.
+
+Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
+Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
+Therefore, at this work, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
+Worth to mention that HOMER Pro is available only for Microsoft Windows and the annual standard subscription costs US\$ 504.00.
 
@@
 %---------------------------------------------------------------------------
-\textbf{Case studies.} We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
-Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
-Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+\textbf{Case studies.} We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (Specification).
+
+\begin{table}
+\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
+\begin{scriptsize}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\hline
+Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro \\
+\hline
+\hline
+Specification & Result & Result & Result & Result \\
+\hline
+\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (146.13 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC:US\$ 1,902.60} & XYZ \\
+\hline
+\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (105.06 min) \\NTP:3$\times$275W (3S)\\NBT:2$\times$80Ah (2S)\\Controller 30A/100V\\Inverter 1,200W/24V \\LCC:US\$ 1,323.00} & XYZ \\
+\hline
+\makecell{\textbf{Case Study 3}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (131.38 min) \\NTP:3$\times$330W (3S)\\NBT:2$\times$80Ah (2S)\\Controller 35A/145V\\Inverter 1,200W/24V \\LCC:US\$ 1,441.40} & XYZ \\
+\hline
+\makecell{\textbf{Case Study 4}\\Demand:253W\\Peak:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (145.57 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 280W/24V \\LCC:US\$ 1,927.15} & XYZ \\
+\hline
+\makecell{\textbf{Case Study 5}\\Demand:263W\\Peak:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (133.90 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC:US\$ 1,389.85} & XYZ \\
+\hline
+\makecell{\textbf{Case Study 6}\\Demand:322W\\Peak:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (234.00 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC:US\$ 2,375.65} & XYZ \\
+\hline
+\makecell{\textbf{Case Study 7}\\Demand:1,800W\\Peak:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO & TO & XYZ \\
+\hline
+\hline
+\end{tabular}
+\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
+\end{scriptsize}
+\end{table}
+
+\textbf{Verification Tools.} Three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
 and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
+Simulation tool HOMER Pro version 3.13.1 was used as well.
 
-\textbf{Setup.} All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
+\textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
+Related to HOMER Pro, it was used an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
 The experiments were performed with a predefined timeout of $240$ minutes.
@@
 CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.
-%
+
 %used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
-\begin{table}
-\caption{Case studies and results: optimization of PV systems.}\label{tab1}
-\begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\hline
-Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro \\
-\hline
-\hline
-Specification & Result & Result & Result & Result \\
-\hline
-\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (50.2 min) \\NTP=1$\times$330W (1S)\\NBT=8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\Cost=US\$ 1,902.60} & XYZ \\
-\hline
-\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (37.2 min) \\NTP=3$\times$330W (3S)\\NBT=2$\times$105Ah (2S)\\Controller 35A/145V\\Inverter 1,500VA/24V \\Cost=US\$ 2,235.57} & XYZ \\
-\hline
-\makecell{\textbf{Case Study 3}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & SAT & XYZ \\
-\hline
-\makecell{\textbf{Case Study 4}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & SAT & XYZ \\
-\hline
-\makecell{\textbf{Case Study 5}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & SAT & XYZ \\
-\hline
-\makecell{\textbf{Case Study 6}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & SAT & XYZ \\
-\hline
-\makecell{\textbf{Case Study 7}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & TO & TO & XYZ \\
-\hline
-\hline
-\end{tabular}
-\\Legend: OM (out of memory), TO (timeout), IF (internal failure), E (energy).
-\end{scriptsize}
-\end{table}
-
-%
-
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
+Nevertheless, we have also identified two threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) ????
 

### 2019-06-03 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text and code

@@
 NPC is the total present value of a time series.
-The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an interest rate of internal rate of return (IRR).[90]
+The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an interest rate of internal rate of return (IRR)~\cite{Park2004}.
 
-LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost is considered [91].
-LCOE method is useful in comparing different generation technologies with different operating characteristics [6].
+LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost is considered~\cite{Kamel2005}.
+LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
 
-LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value [92].
+LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
 Eq.~\ref{eq:LCC} is used to calculate LCC of a PV system,
@@
 	\item Battery lifetime: 4 years for lead-acid batteries. Therefore will be performed three battery bank replacements;
-	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost [Agrener2013];
-	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013].
+	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost~\cite{Agrener2013};
+%	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013].
 Includes circuit breakers, surge protection devices, electrical grounding, DC fuses, main switchboard, string boxes;
 	\item Value of the discount rate or interest rate: 10\%, what is a good rate considering financial investments in developing countries;
-	\item Operation and maintenance costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of USD [Agrener2013].
+	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
 \end{itemize}

### 2019-06-03 code/opt_PVcode_rev6_case1_old.c

@@ -1,6 +1,6 @@
 /*
  ============================================================================
- Name        : opt_PVcode_rev5_improved database.c CASE 1
+ Name        : opt_PVcode_rev4_improved database.c CASE 1
  Author      : Alessandro Trindade
  Version     : rev5 - May 2019: 40 equipment, lowerbound defined by SW, better HintCost
  Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
@@ -42,7 +42,7 @@ float Tref = 298.15; //reference temperature is 25oC or 298.15K
 int Phouse = 501, Psurge = 501, Econsumption = 3900;
 
 //must define
-int MaxCost=10000; //10 million maximum cost just to control the loop of main function
+float LimLoop=10000; //50 thousand USD maximum cost just to control the loop of main function
 int Vsystem = 24;  //12V, 24V, 36V or 48V: DC Bus voltage definition
 int autonomy = 48; //autonomy in hours
 int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
@@ -136,15 +136,13 @@ int FHintCost(void){
 		if ((int)InverterData[cont][5] < lowervalue) lowervalue=(int)InverterData[cont][5];
 	}
 	cost = cost+lowervalue;
-	cost = cost + cost*0.05; //installation cost of 5%
-	cost = cost + 20*289.64; //O&M cost of 289.64 in 20 years
 	return(cost);
 }
 
 /*--------------------------------
             Auxiliary function
 ----------------------------------*/
-int Faux (int cost){
+int Faux (int costL, int costH){
 	int NTP, NPP, NPS, NBtotal, NBS, NBP, NPPmin, ICmin;
 	float Ecorrected, Ep, NTPmin, NPSmin1, NPSmin2, Cbank, Iscamb, NBSmin, NBPmin, Fobj;
 	unsigned char PanelChoice, BatteryChoice, ControllerChoice, InverterChoice;
@@ -176,6 +174,7 @@ int Faux (int cost){
 	float Vmref = PanelData[PanelChoice][10];
 	float VmpNOCT = PanelData[PanelChoice][11];
 	float PanelCost = PanelData[PanelChoice][12];
[…]

### 2019-06-03 code/opt_PVcode_rev6_case7.c

@@ -1,6 +1,6 @@
 /*
  ============================================================================
- Name        : opt_PVcode_rev5_improved database.c CASE 1
+ Name        : opt_PVcode_rev5_improved database.c CASE HOUSE5
  Author      : Alessandro Trindade
  Version     : rev5 - May 2019: 40 equipment, lowerbound defined by SW, better HintCost
  Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
@@ -39,7 +39,7 @@ int Gref = 1000; //reference irradiance is 1000 W/m²
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
 
 //data from the house
-int Phouse = 501, Psurge = 501, Econsumption = 3900;
+int Phouse = 1800, Psurge = 2900, Econsumption = 14000;
 
 //must define
 int MaxCost=10000; //10 million maximum cost just to control the loop of main function
@@ -125,7 +125,7 @@ int FHintCost(void){
 	for (cont=1; cont <= 9; cont++) {
 		if ((int)BatteryData[cont][5] < lowervalue) lowervalue=(int)BatteryData[cont][5];
 	}
-	cost = cost+lowervalue;
+	cost = cost+lowervalue+lowervalue*3; //Cbatrep 3x in 20 years
 	lowervalue=(int)ControllerData[0][5];
 	for (cont=1; cont <= 9; cont++) {
 		if ((int)ControllerData[cont][5] < lowervalue) lowervalue=(int)ControllerData[cont][5];

### 2019-06-05 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text and code

@@
 \begin{itemize}
-	\item LCOE lifetime considered: 20 years;
-	\item Battery lifetime: 4 years for lead-acid batteries. Therefore will be performed three battery bank replacements;
+	\item LCC lifetime considered: 20 years;
 	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost~\cite{Agrener2013};
@@
 	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
+This cost includes the battery lifetime (4 years for lead-acid batteries).
+Therefore will be performed three battery bank replacements during the LCC analysis.
 \end{itemize}
@@
 \hline
-\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (146.13 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC:US\$ 1,902.60} & XYZ \\
+\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC:US\$ 7,790.53} & XYZ \\
 \hline
-\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (105.06 min) \\NTP:3$\times$275W (3S)\\NBT:2$\times$80Ah (2S)\\Controller 30A/100V\\Inverter 1,200W/24V \\LCC:US\$ 1,323.00} & XYZ \\
+\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (105.06 min) \\NTP:2$\times$320W (2S)\\NBT:2$\times$80Ah (2S)\\Controller 40A/100V DC\\Inverter 1,200W/24V \\LCC:US\$ 7,133.39} & XYZ \\
 \hline

### 2019-06-05 code/opt_PVcode_rev61_case1.c

@@ -107,6 +107,7 @@ float InverterData [10][6] =   {{0.93, 48, 110, 700, 1600, 400.00},
 
 //global variables
 float SOC = 100; //battery is charged when starts the verification
+float LCC;
 
 extern void __VERIFIER_error() __attribute__ ((__noreturn__));
 extern void __VERIFIER_assume(int expression);
@@ -136,8 +137,6 @@ int FHintCost(void){
 		if ((int)InverterData[cont][5] < lowervalue) lowervalue=(int)InverterData[cont][5];
 	}
 	cost = cost+lowervalue;
-	cost = cost + cost*0.05; //installation cost of 5%
-	cost = cost + 20*289.64; //O&M cost of 289.64 in 20 years
 	return(cost);
 }
 
@@ -250,8 +249,8 @@ int Faux (int cost){
 
 	// Function objective: minimum acquisition cost
 	Fobj= NTP*PanelCost + NBtotal*BatteryCost + ControllerCost + InverterCost;
-	Fobj= Fobj+Fobj*0.05+3*(NBtotal*BatteryCost)+20*289.64; //cost = equipment + 5% of installation + 3*batrep + O&M cost
-	__VERIFIER_assume ( ( Fobj >= (cost-800) ) );
+	LCC= Fobj+Fobj*0.05+20*289.64; //cost = equipment + 5% of installation + 3*batrep + O&M cost [out: 3*(NBtotal*BatteryCost)+]
+	__VERIFIER_assume ( ( Fobj >= (cost-500) ) );
 
 	//minimize cost of the solution, considering all the equipment that can be used and was declared at the code
 	if (!(Fobj > cost)) { __VERIFIER_error(); }
@@ -261,8 +260,8 @@ int Faux (int cost){
 /* ----------- MAIN FUNCTION --------- */
 int main() {
 	int HintCost;
-	HintCost = FHintCost()+800;
-	for (; HintCost <= MaxCost; HintCost=HintCost+800){
+	HintCost = FHintCost()+500;
+	for (; HintCost <= MaxCost; HintCost=HintCost+500){
 		Faux(HintCost);
 	}
 	return 0;

### 2019-06-05 code/opt_PVcode_rev61_case2.c

@@ -8,26 +8,28 @@
  ============================================================================*/
 
 //case studies
-//HOUSE1 
+//CASE1 
 // int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
 // int Phouse = 501, Psurge = 501, Econsumption = 3900;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE2 
+//CASE4 
 // int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
 // int Phouse = 253, Psurge = 722, Econsumption = 3600;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE3 
+//CASE5 
 // int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
 // int Phouse = 263, Psurge = 732, Econsumption = 2500;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE4 
+//CASE6 
 // int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
 // int Phouse = 322, Psurge = 896, Econsumption = 4300;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE5 
+//CASE2 = CASE 3 (but autonomy is 12h in CASE 3)
 // int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
 // int Phouse = 915, Psurge = 980, Econsumption = 4880;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//CASE 7 
+// int Phouse = 1800, Psurge = 2900, Econsumption = 14000; //autonomy 48h
 
 //data from Manaus
 int minSolarIrrad [24] = {0,0,0,0,0,0,25,135,274,422,509,537,503,505,430,281,80,10,0,0,0,0,0,0};
[…]

### 2019-06-05 code/opt_PVcode_rev61_case3.c

@@ -8,26 +8,28 @@
  ============================================================================*/
 
 //case studies
-//HOUSE1 
+//CASE1 
 // int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
 // int Phouse = 501, Psurge = 501, Econsumption = 3900;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE2 
+//CASE4 
 // int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
 // int Phouse = 253, Psurge = 722, Econsumption = 3600;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE3 
+//CASE5 
 // int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
 // int Phouse = 263, Psurge = 732, Econsumption = 2500;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE4 
+//CASE6 
 // int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
 // int Phouse = 322, Psurge = 896, Econsumption = 4300;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE5 
+//CASE2 = CASE 3 (but autonomy is 12h in CASE 3)
 // int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
 // int Phouse = 915, Psurge = 980, Econsumption = 4880;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//CASE 7 
+// int Phouse = 1800, Psurge = 2900, Econsumption = 14000; //autonomy 48h
 
 //data from Manaus
 int minSolarIrrad [24] = {0,0,0,0,0,0,25,135,274,422,509,537,503,505,430,281,80,10,0,0,0,0,0,0};
[…]

### 2019-06-05 code/opt_PVcode_rev61_case4.c

@@ -8,26 +8,28 @@
  ============================================================================*/
 
 //case studies
-//HOUSE1 
+//CASE1 
 // int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
 // int Phouse = 501, Psurge = 501, Econsumption = 3900;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE2 
+//CASE4 
 // int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
 // int Phouse = 253, Psurge = 722, Econsumption = 3600;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE3 
+//CASE5 
 // int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
 // int Phouse = 263, Psurge = 732, Econsumption = 2500;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE4 
+//CASE6 
 // int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
 // int Phouse = 322, Psurge = 896, Econsumption = 4300;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE5 
+//CASE2 = CASE 3 (but autonomy is 12h in CASE 3)
 // int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
 // int Phouse = 915, Psurge = 980, Econsumption = 4880;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//CASE 7 
+// int Phouse = 1800, Psurge = 2900, Econsumption = 14000; //autonomy 48h
 
 //data from Manaus
 int minSolarIrrad [24] = {0,0,0,0,0,0,25,135,274,422,509,537,503,505,430,281,80,10,0,0,0,0,0,0};
[…]

### 2019-06-05 code/opt_PVcode_rev61_case5.c

@@ -8,26 +8,28 @@
  ============================================================================*/
 
 //case studies
-//HOUSE1 
+//CASE1 
 // int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
 // int Phouse = 501, Psurge = 501, Econsumption = 3900;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE2 
+//CASE4 
 // int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
 // int Phouse = 253, Psurge = 722, Econsumption = 3600;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE3 
+//CASE5 
 // int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
 // int Phouse = 263, Psurge = 732, Econsumption = 2500;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE4 
+//CASE6 
 // int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
 // int Phouse = 322, Psurge = 896, Econsumption = 4300;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE5 
+//CASE2 = CASE 3 (but autonomy is 12h in CASE 3)
 // int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
 // int Phouse = 915, Psurge = 980, Econsumption = 4880;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//CASE 7 
+// int Phouse = 1800, Psurge = 2900, Econsumption = 14000; //autonomy 48h
 
 //data from Manaus
 int minSolarIrrad [24] = {0,0,0,0,0,0,25,135,274,422,509,537,503,505,430,281,80,10,0,0,0,0,0,0};
[…]

### 2019-06-05 code/opt_PVcode_rev61_case6.c

@@ -8,26 +8,28 @@
  ============================================================================*/
 
 //case studies
-//HOUSE1 
+//CASE1 
 // int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
 // int Phouse = 501, Psurge = 501, Econsumption = 3900;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE2 
+//CASE4 
 // int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
 // int Phouse = 253, Psurge = 722, Econsumption = 3600;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE3 
+//CASE5 
 // int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
 // int Phouse = 263, Psurge = 732, Econsumption = 2500;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE4 
+//CASE6 
 // int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
 // int Phouse = 322, Psurge = 896, Econsumption = 4300;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
-//HOUSE5 
+//CASE2 = CASE 3 (but autonomy is 12h in CASE 3)
 // int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
 // int Phouse = 915, Psurge = 980, Econsumption = 4880;
 // int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//CASE 7 
+// int Phouse = 1800, Psurge = 2900, Econsumption = 14000; //autonomy 48h
 
 //data from Manaus
 int minSolarIrrad [24] = {0,0,0,0,0,0,25,135,274,422,509,537,503,505,430,281,80,10,0,0,0,0,0,0};
[…]

### 2019-06-05 code/opt_PVcode_rev61_case7.c

@@ -1,8 +1,8 @@
 /*
  ============================================================================
- Name        : opt_PVcode_rev5_improved database.c CASE 1
+ Name        : opt_PVcode_rev61_improved database.c CASE HOUSE5
  Author      : Alessandro Trindade
- Version     : rev5 - May 2019: 40 equipment, lowerbound defined by SW, better HintCost
+ Version     : rev61 - Jun 2019: 40 equipment, lowerbound defined by SW, better HintCost
  Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
  //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
  ============================================================================*/
@@ -39,7 +39,7 @@ int Gref = 1000; //reference irradiance is 1000 W/m²
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
 
 //data from the house
-int Phouse = 501, Psurge = 501, Econsumption = 3900;
+int Phouse = 1800, Psurge = 2900, Econsumption = 14000;
 
 //must define
 int MaxCost=10000; //10 million maximum cost just to control the loop of main function
@@ -125,7 +125,7 @@ int FHintCost(void){
 	for (cont=1; cont <= 9; cont++) {
 		if ((int)BatteryData[cont][5] < lowervalue) lowervalue=(int)BatteryData[cont][5];
 	}
-	cost = cost+lowervalue;
+	cost = cost+lowervalue+lowervalue*3; //Cbatrep 3x in 20 years
 	lowervalue=(int)ControllerData[0][5];
 	for (cont=1; cont <= 9; cont++) {
 		if ((int)ControllerData[cont][5] < lowervalue) lowervalue=(int)ControllerData[cont][5];
@@ -136,8 +136,6 @@ int FHintCost(void){
 		if ((int)InverterData[cont][5] < lowervalue) lowervalue=(int)InverterData[cont][5];
 	}
 	cost = cost+lowervalue;
-	cost = cost + cost*0.05; //installation cost of 5%
-	cost = cost + 20*289.64; //O&M cost of 289.64 in 20 years
 	return(cost);
 }
 
@@ -250,8 +248,7 @@ int Faux (int cost){
 
 	// Function objective: minimum acquisition cost
[…]

### 2019-06-05 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 \hline
-\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC:US\$ 7,790.53} & XYZ \\
+\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & XYZ \\
 \hline
-\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (105.06 min) \\NTP:2$\times$320W (2S)\\NBT:2$\times$80Ah (2S)\\Controller 40A/100V DC\\Inverter 1,200W/24V \\LCC:US\$ 7,133.39} & XYZ \\
+\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (105.06 min) \\NTP:2$\times$320W (2S)\\NBT:2$\times$80Ah (2S)\\Controller 40A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,133.39} & XYZ \\
 \hline
-\makecell{\textbf{Case Study 3}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (131.38 min) \\NTP:3$\times$330W (3S)\\NBT:2$\times$80Ah (2S)\\Controller 35A/145V\\Inverter 1,200W/24V \\LCC:US\$ 1,441.40} & XYZ \\
+\makecell{\textbf{Case Study 3}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & XYZ \\
 \hline
-\makecell{\textbf{Case Study 4}\\Demand:253W\\Peak:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (145.57 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 280W/24V \\LCC:US\$ 1,927.15} & XYZ \\
+\makecell{\textbf{Case Study 4}\\Demand:253W\\Peak:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & XYZ \\
 \hline
-\makecell{\textbf{Case Study 5}\\Demand:263W\\Peak:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (133.90 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC:US\$ 1,389.85} & XYZ \\
+\makecell{\textbf{Case Study 5}\\Demand:263W\\Peak:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & XYZ \\
 \hline
-\makecell{\textbf{Case Study 6}\\Demand:322W\\Peak:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (234.00 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC:US\$ 2,375.65} & XYZ \\
+\makecell{\textbf{Case Study 6}\\Demand:322W\\Peak:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & XYZ \\
 \hline

### 2019-06-06 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems.
-The tools are mainly based on simulations, which do not cover all aspects of the design-space.
+There exist various methods and tools to size solar photovoltaic systems, however the tools are mainly based on simulations, which do not cover all aspects of the design-space.
 We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
@@
 Our work makes two major contributions.
-Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented.
+\textbf{Firstly}, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented.
 Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries)
 can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
-Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
+\textbf{Secondly}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
 
@@
 The sizing rules are based on designer's experience, using lowest performance either in a time period data or by directly using average value (daily, monthly, or annual) of solar irradiance.
-This method do not the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
+This method do not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
 
@@
 Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was inputted to the code in order to allow the choice of every item of PV sizing.
-Data sheet from each item is necessary to collect the technical information.
-And the price of each item was collected using the internet (in US dollars).
+Data sheet from each item was necessary to collect the technical information.
+Moreover, the price of each item was collected using the internet (in US dollars).
 
@@
 
-\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
-The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}.
-The results were tested by manual PV sizing and were sound (\textit{RQ1}).
+\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing in six of seven case studies: the result was produced in time that varied from $105.06$ to $235.75$ minutes.
+Only case 7 presented a \textit{timeout} result.
+The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}.
+%The results were tested by manual PV sizing and were sound (\textit{RQ1}).
 %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
-CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.
+
+CBMC and ESBMC were not capable to produce some conclusive results.
+Situations of \textit{internal failure} or \textit{timeout} or \textit{out of memory} occurred; this partially answers the \textit{RQ2}.
+Worth to mention that the internal failure presented by the ESBMC verifier was a Z3 solver issue (a bug), and this will demand an updated version of the ESBMC.
+
+Related to the HOMER Pro, xxx
 
@@
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified two threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) ????
+Nevertheless, we have also identified two threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) the cost analysis is well tailored to the Amazon region of Brazil, however a broad analysis from other isolated areas must be performed in order to make the optimization general in terms of applicability.
 

### 2019-06-08 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
+If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify} with a lower bound (that is incremented during every iteration), in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again; however, in our variant CEGIS method, if the {\sc verify} phase is not successful, then a new candidate is generated by {\sc synthesize} and the lower bound in incremented in order to pursuit the lowest cost.
 %
@@
 %
+
 One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
 Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
-At this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.
+%In a nutshell, at this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.
 %however, $\mathcal{D}$ can represent a large number of elements for the finite set  and our synthesis engine can then conclude that no feasible equipment combination was found.
@@
 \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.
+
 Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14};

### 2019-06-11 Tex/elsevier/trindade_appliedenergy_rev0.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems, however the tools are mainly based on simulations, which do not cover all aspects of the design-space.
+There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space.
 We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.

### 2019-06-11 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed asbtract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based in power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
-If the verification step do not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, linking the technical response of the first phase with cost analysis of the second phase.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
+If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
 Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
 Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to output within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
+Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
 \end{abstract}

### 2019-06-11 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
@@
 faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
-in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
-Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI}.
-Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
+in a controlled and safe way, thus posing novel technical challenges for the software engineering 
+of services and applications for CPS~\cite{Metzger2014}. Important quality aspects for CPS include scalability, 
+e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI} \textcolor}{red}{only scalability?}.
+Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, 
+rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
 
-While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
-Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS.
-These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
-In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
+While some research efforts do exist to enhance and optimize the software development 
+processes for CPS, further investigation and discussion of better and more effective models 
+are still needed in practice~\cite{Al-Jaroodi2016}. Among the opportunities for enhancements 
+in the software development processes for CPS, there exists the need for developing new techniques 
+and tools to support CPS requirements gathering and analysis with the goal of synthesizing 
+correct-by-construction implementations of CPS. These techniques need to deal with 
+predefined requirements enforced by the nature and inherited constraints of the target CPS. 
+In addition, they should be able to provide verification and validation mechanisms 
+for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. 
 Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. 
@@
 
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}.
-To provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
+Lack of access to clean and affordable energy is considered a core 
+dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; 
+in particular, the number of people without electricity access fell below $1$ 
+billion threshold for the first time in 2017~\cite{IEAweo2018}. In order to provide 
+universal electricity for all, decentralized systems led by solar photovoltaic (PV) 
+in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters 
+of the additional connections needed~\cite{Hussein2012}; 
+specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
 
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g., PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
-However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+In order to simulate or evaluate a PV system, there exist various specialized tools, 
+e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; 
+and even general purpose simulation tools, e.g., PSpice \textcolor{red}{add citation}, Saber \textcolor{red}{add citation} 
+or MATLAB/Simulink package~\cite{Gow1999,Benatiallah2017}. However, these tools are based on simulation; 
+they have the drawback of an incomplete coverage  since verification of all possible 
+combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
-Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed.
-An ideal combination of any PV system is made by the best compromise between two considered objectives, which is power reliability and system cost~\cite{Alsadi2018}.
+Optimization of PV systems is not a recent topic; since the 90's different techniques 
+using a wide variety of criteria to find ultimate combinations for design parameters, 
+based on intuitive, numerical and analytical methods were developed and evaluated. 
+An ideal combination of any PV system is made by the best compromise between 
+two considered objectives, which is power reliability and system cost~\cite{Alsadi2018}.
 
-However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
-Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
-In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
-The candidate solution is then verified via symbolic model checking with a lower bound that serve as the minimum cost of reference; if the verification do not fails, the lower bound is adjusted.
-And if it fails then a counterexample is provided with the optimal sizing that meet power reliability and system cost.
+However, formal methods based on \textit{symbolic model checking} and its application 
+to synthesize PV systems have not been further explored, which can offer a great potential 
+to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. 
+Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing 
+optimal sizing of stand-alone PV systems using commercial equipment data. 
+Given a correctness specification $\sigma$, our method uses that as starting point 
+and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
+related to power reliability. In particular, on each iteration, we synthesize sizing of 
+stand-alone PV systems but that may not achieve the lowest cost. The candidate solution 
+is then verified via symbolic model checking with a lower bound that serves as the minimum 
+cost of reference; if the verification step does not fail, the lower bound is adjusted. 
+If it fails then a counterexample is provided with an optimal sizing that meets 
+power reliability and system cost.
 
-Our work makes two major contributions.
-\textbf{Firstly}, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented.
-Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries)
-can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
-\textbf{Secondly}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
+Our work makes two major contributions. \textbf{Firstly}, the use of automated 
+symbolic verification in electrical systems was uncommon in recent 
+prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
+PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
+charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
+method together with user requirements and environment constraints, 
+and our synthesis algorithm based on symbolic model checking 
+can find the optimal solution in technical and economical terms. 
+\textbf{Secondly}, we evaluate different state-of-art symbolic software 
+verifiers with the goal of obtaining the best performance in our verification 
+back-end for synthesizing optimal PV systems.
 
-\textit{Outline}.
-Section~\ref{sec:Background} gives the background about related works, program synthesis, design sizing and validation of PV systems, and the mathematical modeling.
-Section~\ref{sec:Method} presents the automated formal synthesis proposed by this work.
-Section~\ref{sec:Results} is devoted to the experimentation, results and discussions.
-Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
+\textit{Outline}. Section~\ref{sec:Background} gives the background about related studies, 
+program synthesis, design sizing and validation of PV systems, and the mathematical modeling. 
+Section~\ref{sec:Method} presents the automated formal synthesis proposed 
+by this underlying work. Section~\ref{sec:Results} is devoted to the experimentation, 
+results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
 %

### 2019-06-12 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 of services and applications for CPS~\cite{Metzger2014}. Important quality aspects for CPS include scalability, 
-e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI} \textcolor}{red}{only scalability?}.
+e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI} \textcolor{red}{only scalability?}.
 Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, 
@@
 %-----------------------------------------------------------
-%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{State-of-art in Automated Verification of Electrical Systems}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The conversion of traditional power grid into a smart grid, a fundamental example of a CPS, raises a number of issues that requires novel methods and applications.
-In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}.
-The focus of this study was on how CPS integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system, as 	probability	of	node	failure	in	the	long run, impact	of	repair	service	on	the	failure	risk, and expected energy consumption, with no interest in power generation or even solar PV systems.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
-The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
+The conversion of traditional power grid into a smart grid, a fundamental example of a CPS, 
+raises a number of issues that requires novel methods and applications. 
+In 2012, a Chinese smart grid implementation was considered as case study 
+to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}. 
+The authors employed a stochastic model checking approach and presented 
+a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}. 
+The focus of this study was on how CPSs integrate information and 
+communication technology functions to the physical elements 
+of a system for monitoring and controlling purposes; here the authors 
+employed automated verification of certain quantitative properties of the system, 
+as probability of	 node failure in the long run, impact of repair service on the failure risk, 
+and expected energy consumption, with no interest in power generation or even solar PV systems.
+
+In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes 
+presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}. 
+The authors proposed an automated simulation-based verification technique to verify correctness 
+of protection settings efficiently using hybrid automata-temporal-logic framework. 
 The initial focus was on relay operations and test-case generation to ensure early detection of design errors. 
-The study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
+However, this study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
 
-Other related studies from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
-In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+Other related studies from 2015 include a framework named Modana to achieve an integrated process 
+from modeling with SysML/MARTE to analysis with statistical model checking for CPS 
+in terms of non-functional properties such as time and energy~\cite{Cheng2015}. 
+In order to demonstrate Modana's capability, the authors modelled energy-aware buildings 
+as a case study, and discussed the analysis on energy consumption in different scenarios. 
 The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems. 
-The research did no deal with solar PV systems.
+This research, however, did no address the design and verification of solar PV systems.
 
-In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
-The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
-The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
-The author used approximate model checking of stochastic and hybrid models.
+In 2017, a researcher suggested the application of formal methods to verify and control 
+the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}. 
+The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, 
+and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, 
+and respectively of frequency stabilization and grid robustness. The focus was on controlling the behavior of components, 
+thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''. 
+The author, however, used approximate model checking of stochastic and hybrid models.
 
-In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
-The work did not include the other components of a stand-alone solar PV system.
+In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) 
+with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}. 
+This approach relied on representing unpredictable behavior of the environment to cover all possible 
+feasible scenarios. The simulation results obtained by JModelica covered the system's complete dynamic behavior; 
+however, it was evident the time consuming issue with almost three days of computer effort 
+to verify the design space of one operation hour of the PV panels behavior. 
+This related study did not include other components of a stand-alone solar PV system.
 
-Another work from 2018 was the approach to modeling smart grid components using a formal specification.
-The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
-The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods.
-The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
-This approach is base on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
+Another work from 2018 was the approach to model smart grid components using a formal specification. 
+The authors used a state-based formal specification language named Z; 
+they demonstrated the application of Z to four smart grid components~\cite{Akram2018}. 
+The presented formal specification can be considered as a first step towards modeling 
+of smart grid using formal methods. The starting point of this study was that a smart home 
+can be considered as an integrated system consisting of various objects and system, 
+which communicates and interacts with each other. This approach is based 
+on Petri nets and under the assumption that modeling the smart home 
+leads to clear understanding of the overall behavior of the smart grid.
 

### 2019-06-12 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed Sections 3 and 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %------------------------------------------------------
-\section{METHOD}
+\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
 \label{sec:Method}
+%------------------------------------------------------
 
-\subsection{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
-%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
-%------------------------------------------------------
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. 
@@
 \subsection{Assumptions and Premises}
-Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was inputted to the code in order to allow the choice of every item of PV sizing.
+Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to the code in order to allow the choice of every item of PV sizing.
 Data sheet from each item was necessary to collect the technical information.
-Moreover, the price of each item was collected using the internet (in US dollars).
+Moreover, the price of each item was collected using the internet (in US dollars) \textcolor{red}{add references here?}.
 
-With respect to power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}.
+With respect to power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing} \textcolor{red}{Could you check in the journal guidelines whether we should refer as ``section~\ref{sec:sizing}'' or ``Section~\ref{sec:sizing}''.
+Then update the entire manuscript with this standard}.
 The usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
@@
 
-On the subject of PV system optimization technique, it will be adopted at this work the intuitive method, because is used the average value daily of solar irradiance at the mathematical model, without consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions.
-Therefore all the computation effort will be at the automated synthesis algorithm.
+On the subject of PV system optimization technique, we will adopt here the intuitive method since the average value daily of solar irradiance is used at the mathematical model, without considering the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions.
+Therefore, all the computational effort will be concentrated in our automated synthesis algorithm.
 
-Regarding all case studies, it was defined that the minimum state of charge of batteries is 75\% (DOD maximum of 25\%), the voltage of the system is set in 24 V DC, and the AC voltage from the inverter is 120 V.
+Regarding all case studies, it was defined that the minimum state of charge of batteries is 75\% (DOD maximum of 25\%), the voltage of the system is set in 24 V DC, and the AC voltage from the inverter is 120 V \textcolor{red}{why do we define these parameters?
+Give a rationale here}.
 
@@
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-Therefore, at this work, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
-Worth to mention that HOMER Pro is available only for Microsoft Windows and the annual standard subscription costs US\$ 504.00.
+Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
+Note that that HOMER Pro is available only for Microsoft Windows and the annual standard subscription costs US\$ $504.00$ \textcolor{red}{cite reference}.
 
 %---------------------------------------------------------------------------
-\section{RESULTS AND DISCUSSION}
+\section{Experimental Evaluation}
 \label{sec:Results}
 %---------------------------------------------------------------------------
-\textbf{Case studies.} We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (Specification).
+
+%---------------------------------------------------------------------------
+\subsection{Case studies} 
+%---------------------------------------------------------------------------
+
+We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (Specification) \textcolor{red}{why did you choose these case studies?}.
 
@@
 
-\textbf{Verification Tools.} Three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+%---------------------------------------------------------------------------
+\subsection{Verification Tools} 
+%---------------------------------------------------------------------------
+
+Three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
 and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
@@
 
-\textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
+%---------------------------------------------------------------------------
+\subsection{Setup} 
+%---------------------------------------------------------------------------
+
+All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
 Related to HOMER Pro, it was used an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
@@
 
-\textbf{Objectives.} Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, and \textit{RQ2} (performance) How do the software verifiers compare to each other?
+%---------------------------------------------------------------------------
+\subsection{Objectives} 
+%---------------------------------------------------------------------------
 
-\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing in six of seven case studies: the result was produced in time that varied from $105.06$ to $235.75$ minutes.
+Our evaluation aims to answer two research questions:
+
+\begin{enumerate}
+
+\item[RQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
+
+\item[RQ2] \textbf{(performance)} how do the software verifiers compare to each other?
+
+\end{enumerate}
+
+%---------------------------------------------------------------------------
+\subsection{Results}  
+%---------------------------------------------------------------------------
+
+CPAchecker was able to synthesize the optimal sizing in six of seven case studies: the result was produced in time that varied from $105.06$ to $235.75$ minutes.
 Only case 7 presented a \textit{timeout} result.

### 2019-06-12 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \subsection{PV systems Optimization Criteria}
-In order to select an optimal combination to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the system.
-An ideal combination for any PV system is made by the best compromise between those two objectives.
+In order to select an optimal combination to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the underlying system.
+An ideal combination for any PV system is made by the best compromise between these two objectives.
 
-During the PV system design, one of the most important aspects to ensure power system security is to analyze power supply availability.
+During the PV system design, one of the most important aspects to ensure power system security \textcolor{red}{what do you define as ``power system security''?
+Should it be ``safety''?} is to analyze power supply availability.
 The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
@@
 
-There are different methods to express system reliability, the most popular are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
-In both methods, if the probability is zero, then the load will always be fulfilled; while in the opposite (probability of one) then the load will never be fulfilled.
+There are different methods to express system reliability, the most popular ones are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
+In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
 
 LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
-And we say that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
+On one hand, we say that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
 On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
 The main approaches to LPSP demand chronological simulation or probabilistic technique.
-In both, time series data is necessary, and dynamic behavior analysis.
-Data is not always available and dynamic analysis is complex, and this is a drawback.
+\textcolor{red}{this sentence is unclar...
+In both, time series data is necessary, and dynamic behavior analysis}.
+Data is not always available and dynamic analysis is complex, and this is a drawback \textcolor{red}{add citation}.
 
-Related to economic analysis, there are several methods available.
-The aim is to determine wheter the project has or has not acceptable investment, and the usual is to perform economic analysis after reliability analysis in order to propose a system with high reliability and lowest cost~\cite{Alsadi2018}.
-Frequently are used the Net Present Cost (NPC), the Levelized Cost of Energy (LCOE), or the Life Cycle Cost (LCC).
+Related to economic analysis, there exist various methods available.
+The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
+The common methods include: Net Present Cost (NPC) \textcolor{red}{add citation}, the Levelized Cost of Energy (LCOE) \textcolor{red}{add citation}, or the Life Cycle Cost (LCC) \textcolor{red}{add citation}.
 
@@
 
-LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost is considered~\cite{Kamel2005}.
+LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
 LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
@@
 Eq.~\ref{eq:LCC} is used to calculate LCC of a PV system,
+%
 \begin{equation}
@@
 Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+
+%----------------------------------------------------------------------------------------------
 \subsection{Stand-alone PV System Optimization Technique}
-To recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables.
+%----------------------------------------------------------------------------------------------
+
+In order to recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables.
 As number of optimization variables increases, the computation effort will increase as well.
-Hence, to obtain the best PV system design as well as simplified sizing process, past work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Alsadi2018}[6].
+Hence, to obtain the best PV system design as well as simplified sizing process, prior work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Alsadi2018} \textcolor{red}{why [6]?}.
 
@@
 The sizing rules are based on designer's experience, using lowest performance either in a time period data or by directly using average value (daily, monthly, or annual) of solar irradiance.
-This method do not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
+This method does not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
 
-Numerical method the design is simulated for each time step within a period.
+For numerical method, the design is simulated for each time step within a period.
 State of charge of batteries is calculated and investigated.
-It is very accurate, however is complex, demanding more time for calculation.
+It is very accurate, however is complex, demanding more time for calculation \textcolor{red}{add citation}.
 
 Analytical methods is used to obtain a close relation or correlation in a form of equation between capacities and reliabilities.
-The sizing task become much simpler, however the relation cannot be applied at different sites, because is specific to one specific place of deployment of the PV system, demanding adaptation if another site is analyzed.
+The sizing task becomes much simpler \textcolor{red}{than what?}, however the relation cannot be applied to different sites, because it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
 

### 2019-06-13 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; 
-and even general purpose simulation tools, e.g., PSpice \textcolor{red}{add citation}, Saber \textcolor{red}{add citation} 
-or MATLAB/Simulink package~\cite{Gow1999,Benatiallah2017}. However, these tools are based on simulation; 
+and even general purpose simulation tools, e.g., \textcolor{red} {PSpice~\cite{Gow1999},  
+or MATLAB/Simulink package~\cite{Benatiallah2017}}. However, these tools are based on simulation; 
 they have the drawback of an incomplete coverage  since verification of all possible 
@@
 
-During the PV system design, one of the most important aspects to ensure power system security \textcolor{red}{what do you define as ``power system security''?
-Should it be ``safety''?} is to analyze power supply availability.
+During the PV system design, one of the most important aspects to ensure power system \textcolor{red}{reliability is to analyze power supply availability}.
 The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
@@
 On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
-The main approaches to LPSP demand chronological simulation or probabilistic technique.
-\textcolor{red}{this sentence is unclar...
-In both, time series data is necessary, and dynamic behavior analysis}.
-Data is not always available and dynamic analysis is complex, and this is a drawback \textcolor{red}{add citation}.
+\textcolor{red}{The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance}.
+However, data is not always available and dynamic analysis is complex, and this is a drawback \textcolor{red}{to LOLP and LPSP~\cite{Alsadi2018}}.
 
@@
 The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
-The common methods include: Net Present Cost (NPC) \textcolor{red}{add citation}, the Levelized Cost of Energy (LCOE) \textcolor{red}{add citation}, or the Life Cycle Cost (LCC) \textcolor{red}{add citation}.
+The common methods include: Net Present Cost (NPC) \textcolor{red}{~\cite{Park2004}}, the Levelized Cost of Energy (LCOE) \textcolor{red}{~\cite{Zhou2010}}, or the Life Cycle Cost (LCC) \textcolor{red}{~\cite{Applasamy2011}}.
 
@@
 %The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
-%Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
+%Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
 %the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
@@
 %----------------------------------------------------------------------------------------------
-
 In order to recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables.
 As number of optimization variables increases, the computation effort will increase as well.
-Hence, to obtain the best PV system design as well as simplified sizing process, prior work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Alsadi2018} \textcolor{red}{why [6]?}.
+Hence, to obtain the best PV system design as well as simplified sizing process, prior work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Alsadi2018} \textcolor{red}{why [6]?
+Alessandro: Não entendi o 6 aqui}.
 
@@
 State of charge of batteries is calculated and investigated.
-It is very accurate, however is complex, demanding more time for calculation \textcolor{red}{add citation}.
+It is very accurate, however is complex, demanding more time for calculation \textcolor{red}{~\cite{Park2004}}.
 
 Analytical methods is used to obtain a close relation or correlation in a form of equation between capacities and reliabilities.
-The sizing task becomes much simpler \textcolor{red}{than what?}, however the relation cannot be applied to different sites, because it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
+The sizing task becomes much simpler \textcolor{red}{than numerical technique}, however the relation cannot be applied to different sites, because it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
 
@@
 Data sheet from each item was necessary to collect the technical information.
-Moreover, the price of each item was collected using the internet (in US dollars) \textcolor{red}{add references here?}.
+Moreover, the price of each item \textcolor{red}{was obtained from available quotation of the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars) MUDEI O TEXTO POIS A CONSULTA NA WEB P/ OBTER PREÇO DEMANDOU VÁRIOS SITES}.
 
-With respect to power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing} \textcolor{red}{Could you check in the journal guidelines whether we should refer as ``section~\ref{sec:sizing}'' or ``Section~\ref{sec:sizing}''.
-Then update the entire manuscript with this standard}.
+With respect to power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in \textcolor{red}{Section~\ref{sec:sizing}}.
 The usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
@@
 
-Regarding all case studies, it was defined that the minimum state of charge of batteries is 75\% (DOD maximum of 25\%), the voltage of the system is set in 24 V DC, and the AC voltage from the inverter is 120 V \textcolor{red}{why do we define these parameters?
-Give a rationale here}.
+Regarding all case studies, it was defined that the minimum state of charge of batteries is 75\% \textcolor{red}{(with DOD maximum of 25\%, what is common to lead-acid batteries), the voltage of the system is set in 24 V DC (the most common as well, but the value can be adjusted to 12 or 48 V at the code), and the AC voltage from the inverter is 127 V (Brazil standard)}.
 
@@
 Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
-Note that that HOMER Pro is available only for Microsoft Windows and the annual standard subscription costs US\$ $504.00$ \textcolor{red}{cite reference}.
+Note that that HOMER Pro is available only for Microsoft Windows and the annual standard subscription costs US\$ $504.00$ \textcolor{red}{~\cite{HOMER}}.
 
@@
 
-We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (Specification) \textcolor{red}{why did you choose these case studies?}.
+We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification).
+\textcolor{red}{These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{Agrener2013}}.
 

### 2019-06-14 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
-in a controlled and safe way, thus posing novel technical challenges for the software engineering 
-of services and applications for CPS~\cite{Metzger2014}. Important quality aspects for CPS include scalability, 
-e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI} \textcolor{red}{only scalability?}.
-Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, 
-rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
+in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. 
+%Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI} \textcolor{red}{only scalability?}.
+Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
 
@@
 are still needed in practice~\cite{Al-Jaroodi2016}. Among the opportunities for enhancements 
-in the software development processes for CPS, there exists the need for developing new techniques 
-and tools to support CPS requirements gathering and analysis with the goal of synthesizing 
-correct-by-construction implementations of CPS. These techniques need to deal with 
-predefined requirements enforced by the nature and inherited constraints of the target CPS. 
-In addition, they should be able to provide verification and validation mechanisms 
-for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. 
+in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS.
+These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
+In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
 Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
@@
 As number of optimization variables increases, the computation effort will increase as well.
-Hence, to obtain the best PV system design as well as simplified sizing process, prior work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Alsadi2018} \textcolor{red}{why [6]?
-Alessandro: Não entendi o 6 aqui}.
+Hence, to obtain the best PV system design as well as simplified sizing process, prior work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical \textcolor{red}{methods~\cite{Zhou2010}}.
 
@@
 Data sheet from each item was necessary to collect the technical information.
-Moreover, the price of each item \textcolor{red}{was obtained from available quotation of the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars) MUDEI O TEXTO POIS A CONSULTA NA WEB P/ OBTER PREÇO DEMANDOU VÁRIOS SITES}.
+Moreover, the price of each item \textcolor{red}{was obtained from available quotation of the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
+MUDEI O TEXTO POIS A CONSULTA NA WEB P/ OBTER PREÇO DEMANDOU VÁRIOS SITES}
 
@@
 	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
-This cost includes the battery lifetime (4 years for lead-acid batteries).
+This cost includes the battery replacement based on its lifetime (4 years for lead-acid batteries).
 Therefore will be performed three battery bank replacements during the LCC analysis.
@@
 We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification).
-\textcolor{red}{These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{Agrener2013}}.
+\textcolor{red}{These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}}.
 

### 2019-06-14 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space.
-We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
-If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
-Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
+There exist various methods and tools to size solar photovoltaic systems; 
+however, the tools are mainly based on simulations, which do not cover all aspects 
+of the design-space. We present a sound and automated approach to obtain 
+optimal sizing of stand-alone PV systems using program synthesis. In particular, 
+our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: 
+first we synthesize the sizing of stand-alone PV systems based on power reliability, 
+but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively 
+with a lower bound via symbolic bounded model checking. If the verification step does not fail, 
+the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, 
+thereby linking the technical response of the first phase with cost analysis of the second phase. 
+Commercial equipment data from different manufacturers are provided to our synthesis engine 
+and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis 
+method is novel and unprecedented to streamline the design of PV systems. Experimental results 
+using seven case studies show that our synthesis method is able to produce within an acceptable 
+run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows 
+the effectiveness of our approach.
 \end{abstract}

### 2019-06-14 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2019-06-14 Tex/elsevier/trindade_appliedenergy_rev0.tex
@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space.
-We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
-If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
-Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
+There exist various methods and tools to size solar photovoltaic systems; 
+however, the tools are mainly based on simulations, which do not cover all aspects 
+of the design-space. We present a sound and automated approach to obtain 
+optimal sizing of stand-alone PV systems using program synthesis. In particular, 
+our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: 
+first we synthesize the sizing of stand-alone PV systems based on power reliability, 
+but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively 
+with a lower bound via symbolic model checking. If the verification step does not fail, 
+the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, 
+thereby linking the technical response of the first phase with cost analysis of the second phase. 
+Commercial equipment data from different manufacturers are provided to our synthesis engine 
+and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis 
+method is novel and unprecedented to streamline the design of PV systems. Experimental results 
+using seven case studies show that our synthesis method is able to produce within an acceptable 
+run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows 
+the effectiveness of our approach.
 \end{abstract}
@@
 the seamless integration of computational and physical  components~\cite{NSF2015}. 
-During operation, such components must frequently adapt to the executing environment changes 
+During operation, such components must frequently adapt to the operating environment changes 
 faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
-in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. 
-%Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI} \textcolor{red}{only scalability?}.
-Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
+in a controlled and safe way, thus posing novel technical challenges for the software engineering 
+of services and applications for CPS~\cite{Metzger2014}. Software pervasiveness in CPS places 
+new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
+unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
 
@@
 are still needed in practice~\cite{Al-Jaroodi2016}. Among the opportunities for enhancements 
-in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS.
-These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
-In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
-Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
-Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
+in the software development processes for CPS, there exists the need for developing new techniques 
+and tools to support CPS requirements gathering and analysis with the goal of synthesizing 
+\textit{correct-by-construction} implementations of CPS. These techniques need to deal with 
+predefined requirements enforced by the nature and inherited constraints of the target CPS. 
+In addition, they should be able to provide verification and validation mechanisms for completeness, 
+correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, 
+can be dealt with formal verification~\cite{NESSI}. Energy production, distribution, and 
+optimization are all CPS problems~\cite{UC}.
 
@@
 
-Optimization of PV systems is not a recent topic; since the 90's different techniques 
+Optimization of PV systems is not a recent topic; since the $90$'s different techniques 
 using a wide variety of criteria to find ultimate combinations for design parameters, 
-based on intuitive, numerical and analytical methods were developed and evaluated. 
+based on intuitive, numerical and analytical methods were developed and evaluated \textcolor{red}{add citation}. 
 An ideal combination of any PV system is made by the best compromise between 
-two considered objectives, which is power reliability and system cost~\cite{Alsadi2018}.
+two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
 
 However, formal methods based on \textit{symbolic model checking} and its application 
-to synthesize PV systems have not been further explored, which can offer a great potential 
-to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. 
-Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing 
+to synthesize PV systems have not been further explored in literature, which could offer 
+a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. 
+Here, we use a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing 
 optimal sizing of stand-alone PV systems using commercial equipment data. 
@@
 and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
-related to power reliability. In particular, on each iteration, we synthesize sizing of 
+related to power reliability. In particular, in each iteration, we synthesize sizing of 
 stand-alone PV systems but that may not achieve the lowest cost. The candidate solution 
@@
 
-Our work makes two major contributions. \textbf{Firstly}, the use of automated 
-symbolic verification in electrical systems was uncommon in recent 
+Our work makes two major contributions. Firstly, the use of automated 
+symbolic verification methods in electrical systems was uncommon in recent 
 prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
@@
 \textit{Outline}. Section~\ref{sec:Background} gives the background about related studies, 
-program synthesis, design sizing and validation of PV systems, and the mathematical modeling. 
+program synthesis, sizing design and validation of PV systems, and the mathematical modeling. 
 Section~\ref{sec:Method} presents the automated formal synthesis proposed 
-by this underlying work. Section~\ref{sec:Results} is devoted to the experimentation, 
+in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, 
 results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.

### 2019-06-14 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 raises a number of issues that requires novel methods and applications. 
-In 2012, a Chinese smart grid implementation was considered as case study 
+In $2012$, a Chinese smart grid implementation was considered as case study 
 to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}. 
 The authors employed a stochastic model checking approach and presented 
-a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}. 
+a modelling and analysis study using PRISM, which is
+a probabilistic model checker~\cite{KwiatkowskaNP11}. 
 The focus of this study was on how CPSs integrate information and 
 communication technology functions to the physical elements 
-of a system for monitoring and controlling purposes; here the authors 
+of a system for monitoring and controlling purposes; here, the authors 
 employed automated verification of certain quantitative properties of the system, 
 as probability of	 node failure in the long run, impact of repair service on the failure risk, 
-and expected energy consumption, with no interest in power generation or even solar PV systems.
+and expected energy consumption, without any interest in power generation or even solar PV systems.
 
-In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes 
+In $2015$, an automated approach for applying Monte-Carlo simulation to power system protection schemes 
 presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}. 
@@
 
-Other related studies from 2015 include a framework named Modana to achieve an integrated process 
-from modeling with SysML/MARTE to analysis with statistical model checking for CPS 
+Other related studies from $2015$ include a framework named Modana to achieve an integrated process 
+from modeling with SysML/MARTE to analysis using statistical model checking for CPS 
 in terms of non-functional properties such as time and energy~\cite{Cheng2015}. 
@@
 
-In 2017, a researcher suggested the application of formal methods to verify and control 
-the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}. 
+In $2017$, a researcher suggested the application of formal methods to verify and control 
+the behavior of computational devices, interacting over a shared and smart infrastructure~\cite{Abate2017}. 
 The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, 
@@
 and respectively of frequency stabilization and grid robustness. The focus was on controlling the behavior of components, 
-thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''. 
+thereby verifying the given smart grid as a ``system of systems'' within the context of ``internet of things''. 
 The author, however, used approximate model checking of stochastic and hybrid models.
 
-In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) 
+In $2018$, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) 
 with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}. 
@@
 
-Another work from 2018 was the approach to model smart grid components using a formal specification. 
+Another work from $2018$ was the approach to model smart grid components using a formal specification. 
 The authors used a state-based formal specification language named Z; 
@@
 The presented formal specification can be considered as a first step towards modeling 
-of smart grid using formal methods. The starting point of this study was that a smart home 
+of smart grids using formal methods. The starting point of this study was that a smart home 
 can be considered as an integrated system consisting of various objects and system, 
 which communicates and interacts with each other. This approach is based 
-on Petri nets and under the assumption that modeling the smart home 
+on Petri nets and is under the assumption that modeling the smart home 
 leads to clear understanding of the overall behavior of the smart grid.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Automated Verification Using Model Checking}
 \label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
-Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
-Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t.
-user requirements.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Although simulation and testing explore possible behaviors and scenarios of a given system, 
+they leave open the question of whether unexplored trajectories may contain a flaw. 
+Formal verification conducts an exhaustive exploration of all possible behaviors; 
+when a design is said to be ``correct'' by a formal verification method, it implies that all 
+behaviors have been explored, and questions regarding adequate coverage or missed behavior 
+becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
+applies mathematical reasoning to obtain guarantees about the correctness of a system; 
+one successful method in this domain is model checking~\cite{Clarke2012}. 
+Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
-CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
-If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
-CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The C Bounded Model Checker (CBMC) falsifies assertions in C programs 
+or proves that they are safe if a completeness threshold is given~\cite{Kroening}. 
+CBMC implements a bit-precise translation of a C program, annotated with assertions 
+and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, 
+then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification 
+flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; 
+it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, 
+into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
+(ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
+which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
+(iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded 
+mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL 
+properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification 
+flow can be summarized in three stages: (i) a front-end that can read and compile C code, 
+where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, 
+control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; 
+and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into 
+SMT and checked for satisfiability. ESBMC exploits the standardized input language of SMT solvers 
+(SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called 
+\textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, 
+to learn from previous checks, thus optimizing the search procedure and potentially eliminating 
+a large amount of formula state space to be searched, because it solves and disregards data 
+during the process, incrementally. This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} 
+and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and 
+the computing platform does not have large amount of memory to deal with the entire design space state.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Automatic program verification requires a choice between precision and efficiency. 
-The more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs.
-Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
-In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
-The CPA formalism provides an interface for the definition of program analyses.
-Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\citep{Beyer2011}.
-Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT solvers and interpolation procedures~\citep{Beyer2011}.
-Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-%CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
-For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
-\textcolor{red}{It is unclear what a CPA is.}
-%In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
+The more precise a method, the fewer false positives it will produce, but also the 
+more expensive it is, and thus applicable to fewer programs. 
+Historically, this trade-off was reflected in two major approaches to static verification: 
+program analysis and model checking. In order to experiment with the trade-off, 
+and in order to be able to set the dial between the two extreme points, 
+Configurable Program Analysis (CPA) provides a conceptual basis for expressing 
+different verification approaches in the same formal setting. The CPA formalism 
+provides an interface for the definition of program analyses. Consequently, CPAchecker 
+provides an implementation framework that allows the seamless integration of program 
+analyses that are expressed in the CPA framework. The comparison among different 
+approaches in the same experimental setting is intended to be easy and the experimental 
+results are expected to be more meaningful~\citep{Beyer2011}. Related to the architecture, 
+the central data structure is a set of control-flow automata (CFA), which consists of control-flow 
+locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and 
+interpolation procedures~\citep{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
+and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+
 %-----------------------------------------------------------
@@
 %-----------------------------------------------------------
-%
-The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
-In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
-As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
 
-The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .
-\forall \vec{x}.
-\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
-The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+The basic idea of program synthesis is to automatically construct a program 
+$P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis 
+is automatically performed by engines that use a correctness specification $\sigma$, 
+as starting point, and then incrementally produce a sequence of candidate solutions 
+that partially satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program 
+$p$ is iteratively refined, in order to match $\sigma$ more closely. CEGIS represents 
+one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, 
+whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} 
+and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
 
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated.
-Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify} with a lower bound (that is incremented during every iteration), in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again; however, in our variant CEGIS method, if the {\sc verify} phase is not successful, then a new candidate is generated by {\sc synthesize} and the lower bound in incremented in order to pursuit the lowest cost.
+The correctness specification $\sigma$ provided to our program synthesizer 
+is of the form $\exists \vec{F} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{F})$, 
+where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, 
+and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers. 
+The ground terms are interpreted over some finite domain $\mathcal{D}$, 
+where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part. 
+Examples of specification used by our method include house demand, 
+energy, and battery autonomy; we also provide a list of equipment specification 
+and price from different manufacturers and models.
+
+ \textcolor{red}{this text needs to be updated since we do not use this test vector {\sc inputs} in our algorithm, right?}
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} 
+interact via a finite set of test vectors {\sc inputs}, which is incrementally updated. 
+Given the correctness specification $\sigma$, the {\sc Synthesize} procedure 
+tries to find an existential witness $\vec{F}$ satisfying the specification 
+$\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). 
+If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution 
+(i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify} 
+with a lower bound (that is incremented during every iteration), in order to check whether it is a proper solution 
+({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). 
+If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment 
+with the lowest cost; otherwise, in the CEGIS traditional method, additional information is 
+provided to the phase {\sc synthesize}, in the form of a new counterexample that is added 
+to the {\sc inputs} set and the loop iterates again; however, in our variant CEGIS method, 
+if the {\sc verify} phase is not successful, then a new candidate is generated by {\sc synthesize} 
+and the lower bound in incremented in order to pursuit the lowest cost.
 %
@@
 
-One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
-%In a nutshell, at this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.
-%however, $\mathcal{D}$ can represent a large number of elements for the finite set  and our synthesis engine can then conclude that no feasible equipment combination was found.
-%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}.
-In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig.
-\ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.
+ \textcolor{red}{this text needs to be updated since we do not use this test vector {\sc inputs} in our algorithm, right?}
+One may notice that each iteration of the CEGIS loop adds a new input to the finite set 
+$\text{\sc inputs}$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ 
+is finite because we use bit-vector expressions, this means that the refinement loop can 
+only iterate over a finite number of times; however, {\sc synthesize} may conclude that 
+no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ 
+exists and our synthesis engine can then conclude that no feasible equipment combination was found.
 
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14};
-here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
-%
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce 
+solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-06-14 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.  
-%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$).
-For night hours or rainy days, we hold batteries where power can be stored and used.
-The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
-That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage 
+form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system 
+contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior 
+of AC electrical load from the house that will be fed by the system.
+%
 \begin{figure}[h]
@@
 \end{figure}
-\\
+
+The sizing check stage will ensure that the system meets the standard project steps related 
+to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller,
+which is the most common one in practice. Firstly, we need to correct the energy consumption estimated to the load 
+($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
+controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
 %
-The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
-%
-Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
-
 \begin{equation}
@@
 
-%
 We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
 %
-
 \begin{equation}
@@
 the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
+The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
 %
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
-
 \begin{equation}
@@
 Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
-
+%
 \begin{equation}
@@
 \end{equation}
-
-\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
 %
+\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ 
+is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and 
+$V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering 
+the maximum and minimum operational temperature, respectively; 
+$P_{total}$ is the total power demanded from the PV system and 
+$P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
 Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
-
+%
 \begin{equation}
@@
 
-The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as
-
+The short circuit reference information from the manufacturer's solar panel must be corrected 
+to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, 
+and PV system is temperature dependent, as 
+%
 \begin{equation}
@@
 
-The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin} as
-
+The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin} as
+%
 \begin{equation}
@@
 
-The inverter sizing check is performed by means of three equations.
-Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
-Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
+The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that 
+the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the 
+output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that 
+the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), 
+where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; 
+$MAX_{AC,ref}$ is the peak power that the inverter can support.
 %
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{PV systems Optimization Criteria}
-In order to select an optimal combination to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the underlying system.
-An ideal combination for any PV system is made by the best compromise between these two objectives.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-During the PV system design, one of the most important aspects to ensure power system \textcolor{red}{reliability is to analyze power supply availability}.
-The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
-A reliable power is a generation system that has sufficient power to feed load demand in a period.
+In order to select an optimal combination to meet sizing constraints, 
+it is necessary to evaluate power reliability and system cost analysis for the underlying system. 
+An ideal combination of any PV system is made by the best compromise between these two objectives.
 
-There are different methods to express system reliability, the most popular ones are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
+During the PV system design, one of the most important aspects to ensure power system reliability 
+is to analyze power supply availability \textcolor{red}{add citation here}. The reason is because solar 
+energy production is intermittent and, therefore, the energy generated usually will not match 
+with the load demand. A reliable power is a generation system that has sufficient power 
+to feed load demand in a period.
+
+There exist different methods to express system reliability, where the most popular ones 
+are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}. 
 In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
@@
 LOLP is the probability for the case when a load demand exceeds the generation power by the PV system. 
-On one hand, we say that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
-On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
-\textcolor{red}{The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance}.
-However, data is not always available and dynamic analysis is complex, and this is a drawback \textcolor{red}{to LOLP and LPSP~\cite{Alsadi2018}}.
+On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill
+the demanded load within a time span. On the other hand, LPSP is defined as the probability of the case 
+when system generates insufficient power to satisfy the load demand. The main approaches to LPSP demand 
+simulation or probabilistic treatment of time series data to predict dynamic changing on system performance. 
+However, data is not always available and dynamic analysis is complex; 
+and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
 
-Related to economic analysis, there exist various methods available.
-The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
-The common methods include: Net Present Cost (NPC) \textcolor{red}{~\cite{Park2004}}, the Levelized Cost of Energy (LCOE) \textcolor{red}{~\cite{Zhou2010}}, or the Life Cycle Cost (LCC) \textcolor{red}{~\cite{Applasamy2011}}.
+Related to economic analysis, there exist various methods available. The main objective is to determine whether 
+the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis 
+with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}. The common methods include: 
+Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, 
+or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
 
-NPC is the total present value of a time series.
-The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an interest rate of internal rate of return (IRR)~\cite{Park2004}.
+NPC is the total present value of a time series. \textcolor{red}{this sentence is unclear or maybe I'm not familiar with this term... 
+The net present worth is found by discounting all cash inflows and outflows}, 
+including cost of installation, replacement and maintenance of the PV system, 
+at an interest rate of internal rate of return (IRR)~\cite{Park2004}.
 
-LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
-LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
+LCOE is defined as the average cost per kWh of useful electrical energy produced 
+by the PV system when a lifetime, investment cost, replacement, operation and maintenance, 
+and capital cost are considered~\cite{Kamel2005}. LCOE method is useful in comparing 
+different generation technologies with different operating characteristics~\cite{Zhou2010}.
 
-LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
-Eq.~\ref{eq:LCC} is used to calculate LCC of a PV system,
+LCC is the estimation of sum of installation cost, operating and maintenance of a PV system 
+for a period of time, and expressed in today's value~\cite{Applasamy2011}. Eq.~\eqref{eq:LCC} 
+is used to calculate LCC of a PV system,
 %
@@
 \end{equation}
-\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs in present worth.
-
-%
-%%%To select an optimal combination of components from a PV system to meet sizing constraints, 
-%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
-%The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
-%Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
-%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
-Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean?
-Remember that we have software engineering audience}.
-%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC).
-Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, 
+$C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, 
+$C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs 
+in present worth.
 
@@
 %----------------------------------------------------------------------------------------------
-In order to recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables.
-As number of optimization variables increases, the computation effort will increase as well.
-Hence, to obtain the best PV system design as well as simplified sizing process, prior work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical \textcolor{red}{methods~\cite{Zhou2010}}.
 
-Intuitive method is simple, easy to be implemented, and can be used to give rough suggestion for preliminary design.
-The sizing rules are based on designer's experience, using lowest performance either in a time period data or by directly using average value (daily, monthly, or annual) of solar irradiance.
-This method does not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
+In order to recommend an optimal configuration for PV systems, 
+the designer has to evaluate the design based on optimization variables. 
+As the number of optimization variables increases, the computational effort 
+will increase as well. Hence, to obtain the best PV system design as well as 
+simplified sizing process, prior work introduced three main techniques 
+for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
+
+Intuitive method is simple, easy to be implemented, and can be used to give 
+rough suggestion for preliminary design. The sizing rules are based on designer's experience, 
+using lowest performance either in a time period data or by directly using average value 
+(daily, monthly, or annual) of solar irradiance. This method does not consider the battery's 
+state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
 
 For numerical method, the design is simulated for each time step within a period. 
-State of charge of batteries is calculated and investigated.
-It is very accurate, however is complex, demanding more time for calculation \textcolor{red}{~\cite{Park2004}}.
+State of charge of batteries is calculated and investigated. It is very accurate, 
+however is complex, demanding more time for calculation~\cite{Park2004}.
 
-Analytical methods is used to obtain a close relation or correlation in a form of equation between capacities and reliabilities.
-The sizing task becomes much simpler \textcolor{red}{than numerical technique}, however the relation cannot be applied to different sites, because it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
+Analytical methods is used to obtain a close relation or correlation in a form 
+of equation between capacities and reliabilities. The sizing task becomes much simpler 
+than numerical technique; however, the relation cannot be applied to different sites
+since it is specific to one place of deployment of the PV system, 
+thereby demanding adaptation if another site is analyzed.
 
@@
 
-Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Line 2).
-After that, we define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5.
+Our synthesis algorithm will synthesize constant values; 
+it starts with the input of manufacturers data and prices of PV panels, batteries, 
+charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
+house requirements and design definitions, from lines $4$ and $5$.
 
-The \textit{for}-loop started at Line 6 controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
+The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. 
+In particular, it starts with cost $0$ and stops only when the algorithm finds a 
+feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
+if that happens, then our algorithm has found an optimal solution, thereby stating 
+that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
+The $MaxCost$ value at line $6$ is just a very high value put as a limit 
+to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
 
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (Lines 7 to 10).
-That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
+from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
+That procedure ensures that our synthesis engine checks all combinations of items 
+from each equipment, and combine them to assemble a feasible (candidate) PV solution, 
+which meets the user requirements.
 
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (Lines 11 to 17).
-The directive \textit{assume} (Lines 15, 18 and 19) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines 15, 18 and 19.
-Therefore, our synthesis algorithm reaches Line 20 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (Line 21).
+Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, 
+Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
+Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} t
+o calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
+ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
+uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$. 
+Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
+and the cost of that solution is calculated in $F_{obj}$ (line $21$).
 
-If our algorithm does not find a feasible solution among the item of equipment that were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
-It indicates that was not possible to combine the items of each equipment and create a feasible solution.
+If our algorithm does not find a feasible solution among the item of equipment that 
+were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
+the program finishes and does not find a solution, which indicates that it 
+was not possible to combine the items of each equipment in order to create a feasible solution.
 
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements.
-Related to our {\sc Verify} phase the challenge is to find the lowest acquisition cost from a list of equipment and components that is provided from the {\sc Synthesize} phase.
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
+solution regarding the constraints and user requirements. Related to our {\sc Verify} 
+phase the challenge is to find the lowest acquisition cost from a list of equipment and 
+components that is provided from the {\sc Synthesize} phase.
 
-Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+Note that the process described here in completely automated and that a validation is performed 
+by our {\sc Verify} phase to ensure that the approach is sound.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Assumptions and Premises}
-Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to the code in order to allow the choice of every item of PV sizing.
-Data sheet from each item was necessary to collect the technical information.
-Moreover, the price of each item \textcolor{red}{was obtained from available quotation of the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-MUDEI O TEXTO POIS A CONSULTA NA WEB P/ OBTER PREÇO DEMANDOU VÁRIOS SITES}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-With respect to power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in \textcolor{red}{Section~\ref{sec:sizing}}.
-The usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
-However, based on the fact that here we are neither considering site characteristics nor the load changes over time, which demands historical data, the reliability analysis will be developed only by the critical period method of PV sizing.
+Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, 
+a list of forty equipment from ten different manufacturers was provided 
+to the synthesis engine in order to allow the choice of every item 
+of PV sizing. Data sheet from each item was necessary to collect 
+technical information. Moreover, the price of each item was obtained 
+from available quotations in the market, and if the currency was not in US dollars, 
+then it was used the exchange rate of the day to convert it to US dollars.
+
+With respect to power reliability, this work will rely on the critical period solar 
+energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
+The usual way is to use loss of load probability (LOLP) or loss of power 
+supply probability (LPSP). However, based on the fact that here we 
+are neither considering site characteristics nor the load changes over time, 
+which demands historical data, the reliability analysis will be developed only 
+by the critical period method of PV sizing.
 
@@
 \begin{itemize}
-	\item LCC lifetime considered: 20 years;
-	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost~\cite{Agrener2013};
-%	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013].
-Includes circuit breakers, surge protection devices, electrical grounding, DC fuses, main switchboard, string boxes;
-	\item Value of the discount rate or interest rate: 10\%, what is a good rate considering financial investments in developing countries;
+	\item LCC lifetime considered: $20$ years;
+	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
+	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
 	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
-This cost includes the battery replacement based on its lifetime (4 years for lead-acid batteries).
-Therefore will be performed three battery bank replacements during the LCC analysis.
+This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries).
+Therefore, it will be performed three battery bank replacements during the LCC analysis.
 \end{itemize}
 
-On the subject of PV system optimization technique, we will adopt here the intuitive method since the average value daily of solar irradiance is used at the mathematical model, without considering the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions.
-Therefore, all the computational effort will be concentrated in our automated synthesis algorithm.
+On the subject of PV system optimization technique, we will adopt here the intuitive method 
+since the average value daily of solar irradiance is used in the mathematical model, 
+without considering the battery's state of charge, or even the random nature 
+of solar irradiation and meteorological conditions. Therefore, all the computational 
+effort will be concentrated in our automated synthesis algorithm.
 
-Regarding all case studies, it was defined that the minimum state of charge of batteries is 75\% \textcolor{red}{(with DOD maximum of 25\%, what is common to lead-acid batteries), the voltage of the system is set in 24 V DC (the most common as well, but the value can be adjusted to 12 or 48 V at the code), and the AC voltage from the inverter is 127 V (Brazil standard)}.
+Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% 
+(with DOD maximum of 25\%, which is common to lead-acid batteries), the voltage of the system 
+is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), 
+and the AC voltage from the inverter is $127$ V (Brazilian standard).
 
-Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
-Note that that HOMER Pro is available only for Microsoft Windows and the annual standard subscription costs US\$ $504.00$ \textcolor{red}{~\cite{HOMER}}.
+Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 
+perform off-grid system with battery backup analysis. 
+Additionally, HOMER and RETScreen include economical analysis 
+or even optimization-sensitive analysis. Therefore, in this study, 
+HOMER Pro will be the simulation tool used to compare with our automated synthesis method. 
+Note that that HOMER Pro is available only for Microsoft Windows and 
+its annual standard subscription costs US\$ $504.00$ ~\cite{HOMER}.
 

### 2019-06-14 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification).
-\textcolor{red}{These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}}.
-
+We have performed seven stand-alone PV system case studies 
+to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification). 
+These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}. 
+%
 \begin{table}

### 2019-06-14 Tex/elsevier/trindade_appliedenergy_rev0.tex
minor changes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; 
-and even general purpose simulation tools, e.g., \textcolor{red} {PSpice~\cite{Gow1999},  
-or MATLAB/Simulink package~\cite{Benatiallah2017}}. However, these tools are based on simulation; 
+and even general purpose simulation tools, e.g.,  PSpice~\cite{Gow1999},  
+or MATLAB/Simulink package~\cite{Benatiallah2017}. However, these tools are based on simulation; 
 they have the drawback of an incomplete coverage  since verification of all possible 

### 2019-06-15 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 using a wide variety of criteria to find ultimate combinations for design parameters, 
-based on intuitive, numerical and analytical methods were developed and evaluated \textcolor{red}{add citation}. 
+based on intuitive, numerical and analytical methods were developed and evaluated \textcolor{red}{~\cite{Applasamy2011}}. 
 An ideal combination of any PV system is made by the best compromise between 
@@
 In order to select an optimal combination to meet sizing constraints, 
-it is necessary to evaluate power reliability and system cost analysis for the underlying system. 
-An ideal combination of any PV system is made by the best compromise between these two objectives.
+it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives.
 
-During the PV system design, one of the most important aspects to ensure power system reliability 
-is to analyze power supply availability \textcolor{red}{add citation here}. The reason is because solar 
-energy production is intermittent and, therefore, the energy generated usually will not match 
-with the load demand. A reliable power is a generation system that has sufficient power 
-to feed load demand in a period.
+During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability \textcolor{red}{~\cite{Alsadi2018}}.
+The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
+A reliable power is a generation system that has sufficient power to feed load demand in a period.
 
@@
 LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
-On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill
-the demanded load within a time span. On the other hand, LPSP is defined as the probability of the case 
-when system generates insufficient power to satisfy the load demand. The main approaches to LPSP demand 
-simulation or probabilistic treatment of time series data to predict dynamic changing on system performance. 
-However, data is not always available and dynamic analysis is complex; 
-and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
+On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
+On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
+The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance.
+However, data is not always available and dynamic analysis is complex; and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
 
@@
 
-NPC is the total present value of a time series. \textcolor{red}{this sentence is unclear or maybe I'm not familiar with this term... 
+\textcolor{red}{The NPC or life-cycle cost is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
 The net present worth is found by discounting all cash inflows and outflows},
 including cost of installation, replacement and maintenance of the PV system, 
-at an interest rate of internal rate of return (IRR)~\cite{Park2004}.
+at an internal rate of return (IRR)~\cite{Park2004}.  IRR is used to evaluate the attractiveness of a project or investment.
 

### 2019-06-17 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 
-The basic idea of program synthesis is to automatically construct a program 
-$P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis 
-is automatically performed by engines that use a correctness specification $\sigma$, 
-as starting point, and then incrementally produce a sequence of candidate solutions 
-that partially satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program 
-$p$ is iteratively refined, in order to match $\sigma$ more closely. CEGIS represents 
-one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, 
-whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} 
-and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
+In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
+As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
+CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
 
-The correctness specification $\sigma$ provided to our program synthesizer 
-is of the form $\exists \vec{F} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{F})$, 
-where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, 
-and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers. 
-The ground terms are interpreted over some finite domain $\mathcal{D}$, 
-where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part. 
-Examples of specification used by our method include house demand, 
-energy, and battery autonomy; we also provide a list of equipment specification 
-and price from different manufacturers and models.
-
- \textcolor{red}{this text needs to be updated since we do not use this test vector {\sc inputs} in our algorithm, right?}
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} 
-interact via a finite set of test vectors {\sc inputs}, which is incrementally updated. 
-Given the correctness specification $\sigma$, the {\sc Synthesize} procedure 
-tries to find an existential witness $\vec{F}$ satisfying the specification 
-$\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). 
-If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution 
-(i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify} 
-with a lower bound (that is incremented during every iteration), in order to check whether it is a proper solution 
-({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). 
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment 
-with the lowest cost; otherwise, in the CEGIS traditional method, additional information is 
-provided to the phase {\sc synthesize}, in the form of a new counterexample that is added 
-to the {\sc inputs} set and the loop iterates again; however, in our variant CEGIS method, 
-if the {\sc verify} phase is not successful, then a new candidate is generated by {\sc synthesize} 
-and the lower bound in incremented in order to pursuit the lowest cost.
-%
 \begin{figure}[h]
@@
 \end{figure}
-%
 
- \textcolor{red}{this text needs to be updated since we do not use this test vector {\sc inputs} in our algorithm, right?}
-One may notice that each iteration of the CEGIS loop adds a new input to the finite set 
-$\text{\sc inputs}$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ 
-is finite because we use bit-vector expressions, this means that the refinement loop can 
-only iterate over a finite number of times; however, {\sc synthesize} may conclude that 
-no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ 
-exists and our synthesis engine can then conclude that no feasible equipment combination was found.
+The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .
+\forall \vec{x}.
+\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
+The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
+Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
 
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce 
-solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
+\textcolor{red}{In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
+Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
+If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.}
+
+One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
+
+\textcolor{red}{However, in our variant CEGIS method proposed at this paper, there are four particular differences related to traditional CEGIS: (1) there is not test vectors and every candidate is generated during the run-time at the {\sc Synthesize} phase and sent to {\sc Verify} phase; (2) if the {\sc Verify} phase is not successful, then a new candidate is generated by {\sc Synthesize} and (3) the lower bound of {\sc Verify} phase is incremented in order to pursuit the lowest cost; (4) therefore, there is not the refinement from the {\sc Verify} back to {\sc Synthesize} phase (a new counterexample is not added to the {\sc inputs} set) because a FAIL during {\sc Verify} just discard the candidate, that can be feasible in the next iteration with a new lower bound.}
+
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
 

### 2019-06-18 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed CEGIS
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{red}{However, in our variant CEGIS method proposed at this paper, there are four particular differences related to traditional CEGIS: (1) there is not test vectors and every candidate is generated during the run-time at the {\sc Synthesize} phase and sent to {\sc Verify} phase; (2) if the {\sc Verify} phase is not successful, then a new candidate is generated by {\sc Synthesize} and (3) the lower bound of {\sc Verify} phase is incremented in order to pursuit the lowest cost; (4) therefore, there is not the refinement from the {\sc Verify} back to {\sc Synthesize} phase (a new counterexample is not added to the {\sc inputs} set) because a FAIL during {\sc Verify} just discard the candidate, that can be feasible in the next iteration with a new lower bound.}
+However, in our variant CEGIS method proposed here, there are four particular differences related to the traditional CEGIS: 
+(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
+(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
+(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
+a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard 
+a given candidate that could be feasible in the next iteration with a new lower bound.
 

### 2019-06-18 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 using a wide variety of criteria to find ultimate combinations for design parameters, 
-based on intuitive, numerical and analytical methods were developed and evaluated \textcolor{red}{~\cite{Applasamy2011}}. 
+based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}. 
 An ideal combination of any PV system is made by the best compromise between 
@@
 
-\textcolor{red}{The NPC or life-cycle cost is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
-The net present worth is found by discounting all cash inflows and outflows},
+The NPC or life-cycle cost is the present value of all the costs over the project lifetime, 
+minus the present value of all the revenues that it earns over the project lifetime. 
+The net present worth is found by discounting all cash inflows and outflows, 
 including cost of installation, replacement and maintenance of the PV system, 

### 2019-06-22 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; 
-however, the tools are mainly based on simulations, which do not cover all aspects 
-of the design-space. We present a sound and automated approach to obtain 
-optimal sizing of stand-alone PV systems using program synthesis. In particular, 
-our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: 
-first we synthesize the sizing of stand-alone PV systems based on power reliability, 
-but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively 
-with a lower bound via symbolic model checking. If the verification step does not fail, 
-the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, 
-thereby linking the technical response of the first phase with cost analysis of the second phase. 
-Commercial equipment data from different manufacturers are provided to our synthesis engine 
-and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis 
-method is novel and unprecedented to streamline the design of PV systems. Experimental results 
-using seven case studies show that our synthesis method is able to produce within an acceptable 
-run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows 
-the effectiveness of our approach.
+There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space.
+We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
+If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
+Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
+Our synthesis method is novel and unprecedented to streamline the design of PV systems.
+Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
+During operation, such components must frequently adapt to the operating environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
+Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
 
-Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, 
-the seamless integration of computational and physical  components~\cite{NSF2015}. 
-During operation, such components must frequently adapt to the operating environment changes 
-faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
-in a controlled and safe way, thus posing novel technical challenges for the software engineering 
-of services and applications for CPS~\cite{Metzger2014}. Software pervasiveness in CPS places 
-new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
-unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
+While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing \textit{correct-by-construction} implementations of CPS.
+These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
+In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
+Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
+Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
 
-While some research efforts do exist to enhance and optimize the software development 
-processes for CPS, further investigation and discussion of better and more effective models 
-are still needed in practice~\cite{Al-Jaroodi2016}. Among the opportunities for enhancements 
-in the software development processes for CPS, there exists the need for developing new techniques 
-and tools to support CPS requirements gathering and analysis with the goal of synthesizing 
-\textit{correct-by-construction} implementations of CPS. These techniques need to deal with 
-predefined requirements enforced by the nature and inherited constraints of the target CPS. 
-In addition, they should be able to provide verification and validation mechanisms for completeness, 
-correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, 
-can be dealt with formal verification~\cite{NESSI}. Energy production, distribution, and 
-optimization are all CPS problems~\cite{UC}.
+Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}.
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
 
-Lack of access to clean and affordable energy is considered a core 
-dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; 
-in particular, the number of people without electricity access fell below $1$ 
-billion threshold for the first time in 2017~\cite{IEAweo2018}. In order to provide 
-universal electricity for all, decentralized systems led by solar photovoltaic (PV) 
-in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters 
-of the additional connections needed~\cite{Hussein2012}; 
-specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
+In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and  Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.,  PSpice~\cite{Gow1999}, or MATLAB/Simulink package~\cite{Benatiallah2017}.
+However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
-In order to simulate or evaluate a PV system, there exist various specialized tools, 
-e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; 
-and even general purpose simulation tools, e.g.,  PSpice~\cite{Gow1999},  
-or MATLAB/Simulink package~\cite{Benatiallah2017}. However, these tools are based on simulation; 
-they have the drawback of an incomplete coverage  since verification of all possible 
-combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-
-Optimization of PV systems is not a recent topic; since the $90$'s different techniques 
-using a wide variety of criteria to find ultimate combinations for design parameters, 
-based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}. 
-An ideal combination of any PV system is made by the best compromise between 
-two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
+Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
+An ideal combination of any PV system is made by the best compromise between two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
 
@@
 
-\textcolor{red}{In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
 If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.}
+If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
 
@@
 
-During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability \textcolor{red}{~\cite{Alsadi2018}}.
+During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
 The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
@@
 
-Related to economic analysis, there exist various methods available. The main objective is to determine whether 
-the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis 
-with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}. The common methods include: 
-Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, 
-or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
+Related to economic analysis, there exist various methods available.
+The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
+The common methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
 
-The NPC or life-cycle cost is the present value of all the costs over the project lifetime, 
-minus the present value of all the revenues that it earns over the project lifetime. 
-The net present worth is found by discounting all cash inflows and outflows, 
-including cost of installation, replacement and maintenance of the PV system, 
-at an internal rate of return (IRR)~\cite{Park2004}.  IRR is used to evaluate the attractiveness of a project or investment.
+The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
+The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
+IRR is used to evaluate the attractiveness of a project or investment.
 
-LCOE is defined as the average cost per kWh of useful electrical energy produced 
-by the PV system when a lifetime, investment cost, replacement, operation and maintenance, 
-and capital cost are considered~\cite{Kamel2005}. LCOE method is useful in comparing 
-different generation technologies with different operating characteristics~\cite{Zhou2010}.
+LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
+LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
 
-LCC is the estimation of sum of installation cost, operating and maintenance of a PV system 
-for a period of time, and expressed in today's value~\cite{Applasamy2011}. Eq.~\eqref{eq:LCC} 
-is used to calculate LCC of a PV system,
+LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
+Eq.~\eqref{eq:LCC} is used to calculate LCC of a PV system,
 %
@@
 \end{equation}
-\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, 
-$C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, 
-$C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs 
+\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs
 in present worth.
@@
 	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
-	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
-This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries).
-Therefore, it will be performed three battery bank replacements during the LCC analysis.
+	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
+This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every 10 years).
+Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
 \end{itemize}
@@
 
-Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% 
-(with DOD maximum of 25\%, which is common to lead-acid batteries), the voltage of the system 
-is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), 
-and the AC voltage from the inverter is $127$ V (Brazilian standard).
+Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of 25\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
 
-Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 
-perform off-grid system with battery backup analysis. 
-Additionally, HOMER and RETScreen include economical analysis 
-or even optimization-sensitive analysis. Therefore, in this study, 
-HOMER Pro will be the simulation tool used to compare with our automated synthesis method. 
-Note that that HOMER Pro is available only for Microsoft Windows and 
-its annual standard subscription costs US\$ $504.00$ ~\cite{HOMER}.
+Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
+Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
+Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
+Related to HOMER Pro:
+
+\begin{itemize}
+	\item HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER};
+	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
+	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
+However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
+	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the 365 days of the year;
+	\item HOMER Pro do not have a explicit equipment called charge controller.
+It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
+During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
+	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
+With that in mind, it was included a generic flat plate PV of 1kW and generic lead-acid batteries of 1kW as well (and with capacity of 83.4 Ah according with HOMER Pro modeling).
+HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
+\end{itemize}
 
@@
 
-We have performed seven stand-alone PV system case studies 
-to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification). 
+We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification).
 These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
@@
 \hline
-Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro \\
+Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro 3.13.1\\
 \hline
@@
 \hline
-\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & XYZ \\
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
 \hline
-\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (105.06 min) \\NTP:2$\times$320W (2S)\\NBT:2$\times$80Ah (2S)\\Controller 40A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,133.39} & XYZ \\
+\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
 \hline
-\makecell{\textbf{Case Study 3}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & XYZ \\
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
 \hline
-\makecell{\textbf{Case Study 4}\\Demand:253W\\Peak:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & XYZ \\
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
 \hline
-\makecell{\textbf{Case Study 5}\\Demand:263W\\Peak:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & XYZ \\
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
 \hline
-\makecell{\textbf{Case Study 6}\\Demand:322W\\Peak:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & XYZ \\
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
 \hline
-\makecell{\textbf{Case Study 7}\\Demand:1,800W\\Peak:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO & TO & XYZ \\
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
 \hline

### 2019-06-22 code/opt_PVcode_rev61_case3_48h.c

@@ -1,0 +1,270 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev5_improved database.c CASE 3 with 48h autonomy
+ Author      : Alessandro Trindade
+ Version     : rev5 - JUN 2019: 40 equipment, lowerbound defined by SW, better HintCost
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//CASE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//CASE4 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//CASE5 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//CASE6 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//CASE2 = CASE 3 (but autonomy is 12h in CASE 3)
[…]

### 2019-06-24 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
+	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
+By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\citep{Khatib2014}.
+For critical loads, 99\% is considered acceptable.
+While in a ordinary house electrical load, 95\% is considered acceptable.
 	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
@@
 %---------------------------------------------------------------------------
-\subsection{Verification Tools} 
+\subsection{Tools} 
 %---------------------------------------------------------------------------
@@
 
-Related to the HOMER Pro, xxx
+Related to the HOMER Pro, it was capable to evaluate all the seven case studies, and within a time shorten than 30 seconds. However, HOMER Pro some drawbacks:
+
+Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, it is easy to notice that mostly of the results were very similar, in terms of technical solution and cost, with exception of case 2 and case 7.
+In case 2, the costs presented by
+
+(1) ele não inclui o controlador de carga explicitamente no design.
+Ele usa duas possibilidade via software para simular carga e descarga da bateria, portanto não diz que marca e modelo o usuário deve adotar; (2) ele precisa começar com alguma opção de bateria com Ah e não vai testando outras opções, portanto não dá a opção de outras baterias, apenas a ligação série e paralela da bateria que foi escolhida pelo usuário; (3) ele não dá a solução de total de painéis solares e o tipo do painel solar, apenas dá o total de potência que ele deve entregar (não diz quantos e nem se em série ou paralelo).
 
@@
 Conclusions here
+
+As future work, the authors plan to improve the power reliability analysis and to address the restriction to only allow automated synthesis of riverside communities in Amazon (Brazil).
+
 \label{sec:Conclusion}

### 2019-06-24 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

--- 2019-06-22 Tex/elsevier/trindade_appliedenergy_rev0.tex
@@
 raises a number of issues that requires novel methods and applications.
-In $2012$, a Chinese smart grid implementation was considered as case study 
-to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}. 
-The authors employed a stochastic model checking approach and presented 
-a modelling and analysis study using PRISM, which is
-a probabilistic model checker~\cite{KwiatkowskaNP11}. 
-The focus of this study was on how CPSs integrate information and 
-communication technology functions to the physical elements 
-of a system for monitoring and controlling purposes; here, the authors 
-employed automated verification of certain quantitative properties of the system, 
-as probability of	 node failure in the long run, impact of repair service on the failure risk, 
-and expected energy consumption, without any interest in power generation or even solar PV systems.
+In $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
+The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here, the authors employed automated verification of certain quantitative properties of the system, as probability of	 node failure in the long run, impact of repair service on the failure risk, and expected energy consumption, without any interest in power generation or even solar PV systems.
 
-In $2015$, an automated approach for applying Monte-Carlo simulation to power system protection schemes 
-presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}. 
-The authors proposed an automated simulation-based verification technique to verify correctness 
-of protection settings efficiently using hybrid automata-temporal-logic framework. 
+In $2015$, an automated approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
+The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
 The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
@@
 
-Other related studies from $2015$ include a framework named Modana to achieve an integrated process 
-from modeling with SysML/MARTE to analysis using statistical model checking for CPS 
-in terms of non-functional properties such as time and energy~\cite{Cheng2015}. 
-In order to demonstrate Modana's capability, the authors modelled energy-aware buildings 
-as a case study, and discussed the analysis on energy consumption in different scenarios. 
+Other related studies from $2015$ include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis using statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
+In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
 The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
@@
 
-In $2017$, a researcher suggested the application of formal methods to verify and control 
-the behavior of computational devices, interacting over a shared and smart infrastructure~\cite{Abate2017}. 
-The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, 
-and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, 
-and respectively of frequency stabilization and grid robustness. The focus was on controlling the behavior of components, 
-thereby verifying the given smart grid as a ``system of systems'' within the context of ``internet of things''. 
+In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices, interacting over a shared and smart infrastructure~\cite{Abate2017}.
+The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The focus was on controlling the behavior of components, thereby verifying the given smart grid as a "system of systems" within the context of "internet of things".
 The author, however, used approximate model checking of stochastic and hybrid models.
 
-In $2018$, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) 
-with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}. 
-This approach relied on representing unpredictable behavior of the environment to cover all possible 
-feasible scenarios. The simulation results obtained by JModelica covered the system's complete dynamic behavior; 
-however, it was evident the time consuming issue with almost three days of computer effort 
-to verify the design space of one operation hour of the PV panels behavior. 
+In $2018$, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
 This related study did not include other components of a stand-alone solar PV system.
@@
 Another work from $2018$ was the approach to model smart grid components using a formal specification.
-The authors used a state-based formal specification language named Z; 
-they demonstrated the application of Z to four smart grid components~\cite{Akram2018}. 
-The presented formal specification can be considered as a first step towards modeling 
-of smart grids using formal methods. The starting point of this study was that a smart home 
-can be considered as an integrated system consisting of various objects and system, 
-which communicates and interacts with each other. This approach is based 
-on Petri nets and is under the assumption that modeling the smart home 
-leads to clear understanding of the overall behavior of the smart grid.
+The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
+The presented formal specification can be considered as a first step towards modeling of smart grids using formal methods.
+The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
+This approach is based on Petri nets and is under the assumption that modeling the smart home leads to clear understanding of the overall behavior of the smart grid.
 
@@
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
+It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
 %
@@
 During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
+	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
+By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\citep{Khatib2014}.
+For critical loads, 99\% is considered acceptable.
+While in a ordinary house electrical load, 95\% is considered acceptable;
+	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
 	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of 1kW and generic lead-acid batteries of 1kW as well (and with capacity of 83.4 Ah according with HOMER Pro modeling).
+With that in mind, it was included a generic flat plate PV of 1 kW and generic lead-acid batteries of 1 kW as well (and with capacity of 83.4 Ah according with HOMER Pro modeling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
@@
 %---------------------------------------------------------------------------
+At this section will be presented the case studies used to evaluate the results and to compare with the simulation tool, the version and command line of each verifier adopted, the computing setup, the objectives of the experimental phase, and the results itself.
 
@@
 
-CPAchecker was able to synthesize the optimal sizing in six of seven case studies: the result was produced in time that varied from $105.06$ to $235.75$ minutes.
-Only case 7 presented a \textit{timeout} result.
+CPAchecker was able to synthesize the optimal sizing in six of seven case studies: the result was produced in time that varied from $134.71$ to $235.75$ minutes.
+Only case 7 presented a \textit{timeout} result, i.e., it was not solved.
 The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}.
@@
 
-Related to the HOMER Pro, xxx
+Related to the HOMER Pro, it was capable to evaluate six case studies, and within a time shorter than 30 seconds, much faster than our automated synthesis tool (\textit{RQ2}).
+Case 3 was not possible to be simulated because Homer Pro do not have the feature of adjust the battery autonomy: the tool always try to feed with electricity the load during 365 days/year.
+Worth to mention others HOMER Pro drawbacks:
+\begin{itemize}
+	\item There is not an explicit charge controller as an equipment of the system.
+HOMER Pro includes automatically a controller just to simulate the charge/discharge of batteries and to meet the load requirement, however without cost or even with electrical characteristics as maximum current and voltage that are common during PV sizing;
+	\item The tool demands to include some battery specification to start the optimization, however it does not change the electrical specifications during the simulation, and the result are multiples of the original battery type suggested by the user.
+As example, it was started with a 83.4 Ah lead-acid battery and during the simulation, HOMER Pro did not try other capacities or types;
+	\item HOMER Pro does not presents the optimal solution in terms of arrays connections of PV panels, just the total in terms of power, i.e., it does not presents models and the power of each PV panel, neither the total of panels in series or parallel.
+\end{itemize}
+
+Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, it is easy to notice that mostly of the results were very similar, in terms of technical solution and cost, with exception of case 2 and case 7.
+In case 2, the costs presented by HOMER Pro were 54\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by our automated synthesis tool were underestimated to that specific load.
+The size of the PV panels were bigger in HOMER Pro than with CPAchecker, and that discrepancy is not easy to address without some real systems.
+The authors had four PV systems deployed and monitored since June 2019 at a riverside community in Amazon State in Brazil, with similar demand presented by cases 1, 4, 5, and 6, always with a 3$\times$325W (3S) panels and 4$\times$225Ah (2S-2P) lead-acid batteries.
+That solutions is more close to the result presented by CPAchecker than HOMER Pro, and that answer partially \textit{RQ1}.
 
@@
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified two threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) the cost analysis is well tailored to the Amazon region of Brazil, however a broad analysis from other isolated areas must be performed in order to make the optimization general in terms of applicability.
+Nevertheless, we have also identified three threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) the cost analysis is well tailored to the Amazon region of Brazil, however a broad analysis from other isolated areas must be performed in order to make the optimization general in terms of applicability; (3) to deploy at the field some PV systems sized using the synthesized results in order to validate it.
 
 \section{CONCLUSIONS}
-Conclusions here
 \label{sec:Conclusion}
+We have described and evaluated an automated synthesis method to obtain the optimal size of PV system using software model checking techniques.
+We have considered seven case studies from PV systems in two different sites of Amazon State in Brazil, ranging from $253$ W to $1,586$ W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+Our automated synthesis tool presented detailed optimal solution to six cases adopted at this paper, with specifications, models and the arrangement in terms of series-parallel connections, covering the charge controller that was not presented by HOMER Pro.
+In a nutshell, our automated synthesis tool took more time to find the optimal solution than 	HOMER Pro, however the presented solution was more complete and detailed, very useful to a user to get a list of equipment and go to shopping.
+
+As future work, the authors plan to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in Amazon (Brazil), and to validate some cases with deployed PV systems at isolated communities.
+
+\section*{Acknowledgments}
+The authors would like to thank: (i) Coventry University for some case studies and for the research mobility; (ii) Newton Fund [grant number 261881580] for the research mobility support; (iii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa 2018], for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; and (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019).
 %

### 2019-06-24 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded 
-mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL 
-properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification 
-flow can be summarized in three stages: (i) a front-end that can read and compile C code, 
-where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, 
-control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; 
-and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into 
-SMT and checked for satisfiability. ESBMC exploits the standardized input language of SMT solvers 
-(SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called 
-\textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, 
-to learn from previous checks, thus optimizing the search procedure and potentially eliminating 
-a large amount of formula state space to be searched, because it solves and disregards data 
-during the process, incrementally. This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} 
-and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and 
-the computing platform does not have large amount of memory to deal with the entire design space state.
+ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
 
@@
 \hline
-Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro 3.13.1\\
+Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
 \hline
@@
 \hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
 \hline
-\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
+\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
 \hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
 \hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
 \hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
 \hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
 \hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
 \hline
@@
 
-Three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-Simulation tool HOMER Pro version 3.13.1 was used as well.
+Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
+Worth to mention that "incremental" ESBMC with solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
+Simulation tool HOMER Pro version 3.13.1 was used during comparative.
 
@@
 Related to the HOMER Pro, it was capable to evaluate six case studies, and within a time shorter than 30 seconds, much faster than our automated synthesis tool (\textit{RQ2}).
-Case 3 was not possible to be simulated because Homer Pro do not have the feature of adjust the battery autonomy: the tool always try to feed with electricity the load during 365 days/year.
+Case 3 was not possible to be simulated because HOMER Pro do not have the feature of adjust the battery autonomy: the tool always try to feed with electricity the load during 365 days/year.
 Worth to mention others HOMER Pro drawbacks:
@@
 In case 2, the costs presented by HOMER Pro were 54\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by our automated synthesis tool were underestimated to that specific load.
-The size of the PV panels were bigger in HOMER Pro than with CPAchecker, and that discrepancy is not easy to address without some real systems.
-The authors had four PV systems deployed and monitored since June 2019 at a riverside community in Amazon State in Brazil, with similar demand presented by cases 1, 4, 5, and 6, always with a 3$\times$325W (3S) panels and 4$\times$225Ah (2S-2P) lead-acid batteries.
+In general, the size of the PV panels were bigger in HOMER Pro than with CPAchecker, and that discrepancy is not easy to address without some real systems.
+Even considering that PVs and inverters were kept at the same cost in both methodologies (simulation and formal synthesis), HOMER Pro have more parameters to be set and a different mathematical model adopted.
+Just to compare the results with the real world, the authors had four PV systems deployed and monitored since June 2019 at a riverside community in Amazon State in Brazil, with similar demand presented by cases 1, 4, 5, and 6, always with a 3$\times$325 W (3S) panels and 4$\times$220 Ah (2S-2P) lead-acid batteries.
 That solutions is more close to the result presented by CPAchecker than HOMER Pro, and that answer partially \textit{RQ1}.
@@
 \section*{Acknowledgments}
-The authors would like to thank: (i) Coventry University for some case studies and for the research mobility; (ii) Newton Fund [grant number 261881580] for the research mobility support; (iii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa 2018], for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; and (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019).
+The authors would like to thank: (i) Newton Fund [grant number 261881580] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa 2018], for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; and (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019).
 %

### 2019-06-25 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 \section*{Acknowledgments}
-The authors would like to thank: (i) Newton Fund [grant number 261881580] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa 2018], for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; and (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019).
+The authors would like to thank: (i) Newton Fund [grant number 261881580] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa 2018], for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019); and (iv) University of Sheffield's Research England QR GCRF Institutional Allocation for the HOMER Pro license.
+
 %

### 2019-06-25 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed Sections 4 and 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %---------------------------------------------------------------------------
-At this section will be presented the case studies used to evaluate the results and to compare with the simulation tool, the version and command line of each verifier adopted, the computing setup, the objectives of the experimental phase, and the results itself.
+
+This section presents the case studies used to evaluate our proposed approach. 
+We also compare our approach with a simulation tool, named HOME Pro. 
+The version and command-line of each verifier adopted, 
+the computing setup, the objectives of the experimental phase, 
+and the results itself are also described.
 
@@
 
-We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification).
-These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+We have performed seven stand-alone PV system case studies to evaluate 
+our proposed synthesis approach, as described in the first column of 
+Table~\ref{tab1} (named Specification). These case studies were defined 
+based on usual electrical load found in riverside communities of the 
+Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}. 
 %
@@
 Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-Worth to mention that "incremental" ESBMC with solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
-Simulation tool HOMER Pro version 3.13.1 was used during comparative.
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used 
+as our verification engine to compare our approach effectiveness 
+and efficiency. Note that ``incremental'' ESBMC with the SMT solver 
+Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3}
+as an alternative to use less computing memory. 
+The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
 
@@
 
-All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
-Related to HOMER Pro, it was used an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
-The experiments were performed with a predefined timeout of $240$ minutes.
+All experiments regarding the verification tools were conducted 
+on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
+$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
+Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
+with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
+Our experiments were performed with a predefined timeout of $240$ minutes.
 
@@
 
-Our evaluation aims to answer two research questions:
+Our evaluation aims to answer two experimental questions:
 
@@
 
-\item[RQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
+\item[EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
 
-\item[RQ2] \textbf{(performance)} how do the software verifiers compare to each other?
+\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?
 
@@
 
-CPAchecker was able to synthesize the optimal sizing in six of seven case studies: the result was produced in time that varied from $134.71$ to $235.75$ minutes.
-Only case 7 presented a \textit{timeout} result, i.e., it was not solved.
-The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}.
+CPAchecker was able to synthesize the optimal sizing in 
+six out of seven case studies: the result was produced 
+within the time limit, which varied from $134.71$ to 
+$235.75$ minutes. Only case study $7$ led to a \textit{timeout} 
+result, i.e., it was not solved within $240$ minutes.
+\textcolor{red}{if we allow CPAchecker to run without time limits, what would be the synthesis time for case study 7?}
+
+The violation (SAT result) indicated in Table~\ref{tab1} 
+is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
 %The results were tested by manual PV sizing and were sound (\textit{RQ1}).
@@
 
-CBMC and ESBMC were not capable to produce some conclusive results.
-Situations of \textit{internal failure} or \textit{timeout} or \textit{out of memory} occurred; this partially answers the \textit{RQ2}.
-Worth to mention that the internal failure presented by the ESBMC verifier was a Z3 solver issue (a bug), and this will demand an updated version of the ESBMC.
+CBMC and ESBMC were unable to produce any conclusive result. 
+Situations of \textit{internal failure}, \textit{timeout}, 
+or \textit{out of memory} occurred; this partially answers 
+the \textit{EQ2}. Note tha the internal failure presented 
+by ESBMC was a Z3 solver issue (a bug), and this will demand 
+an updated version of ESBMC.
 
-Related to the HOMER Pro, it was capable to evaluate six case studies, and within a time shorter than 30 seconds, much faster than our automated synthesis tool (\textit{RQ2}).
-Case 3 was not possible to be simulated because HOMER Pro do not have the feature of adjust the battery autonomy: the tool always try to feed with electricity the load during 365 days/year.
-Worth to mention others HOMER Pro drawbacks:
+Related to HOMER Pro, it was able to evaluate six case studies, 
+and within a time shorter than $30$ seconds, which was much faster 
+than our automated synthesis tool (cf.~\textit{EQ2}). 
+Case study $3$ was not possible to be simulated since 
+HOMER Pro does not have the feature of adjust the battery autonomy, i.e., 
+the tool always tries to feed with electricity the load during $365$ days/year. 
+We have also noted others HOMER Pro drawbacks:
 \begin{itemize}
-	\item There is not an explicit charge controller as an equipment of the system.
-HOMER Pro includes automatically a controller just to simulate the charge/discharge of batteries and to meet the load requirement, however without cost or even with electrical characteristics as maximum current and voltage that are common during PV sizing;
-	\item The tool demands to include some battery specification to start the optimization, however it does not change the electrical specifications during the simulation, and the result are multiples of the original battery type suggested by the user.
-As example, it was started with a 83.4 Ah lead-acid battery and during the simulation, HOMER Pro did not try other capacities or types;
-	\item HOMER Pro does not presents the optimal solution in terms of arrays connections of PV panels, just the total in terms of power, i.e., it does not presents models and the power of each PV panel, neither the total of panels in series or parallel.
+\item There exists no explicit charge controller as a system equipment. 
+HOMER Pro includes automatically a controller just to simulate the 
+charge/discharge of batteries and to meet the load requirement; 
+however, without costs or even with electrical characteristics 
+as maximum current and voltage, which are common during PV sizing;
+\item HOME Pro demands to include some battery specification 
+to initiate the optimization; however, it does not change the 
+electrical specifications during the simulation; and the result 
+are multiples of the original battery type suggested by the user. 
+As example, it was started with a $83.4$ Ah lead-acid battery 
+and during the simulation, HOMER Pro did not try to use 
+other capacities or types;
+\item HOMER Pro does not present the optimal solution 
+in terms of arrays connections of PV panels, just the total 
+in terms of power, i.e., it does not present models and 
+the power of each PV panel, neither the total of panels in series or parallel. 
 \end{itemize}
 
-Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, it is easy to notice that mostly of the results were very similar, in terms of technical solution and cost, with exception of case 2 and case 7.
-In case 2, the costs presented by HOMER Pro were 54\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by our automated synthesis tool were underestimated to that specific load.
-In general, the size of the PV panels were bigger in HOMER Pro than with CPAchecker, and that discrepancy is not easy to address without some real systems.
-Even considering that PVs and inverters were kept at the same cost in both methodologies (simulation and formal synthesis), HOMER Pro have more parameters to be set and a different mathematical model adopted.
-Just to compare the results with the real world, the authors had four PV systems deployed and monitored since June 2019 at a riverside community in Amazon State in Brazil, with similar demand presented by cases 1, 4, 5, and 6, always with a 3$\times$325 W (3S) panels and 4$\times$220 Ah (2S-2P) lead-acid batteries.
-That solutions is more close to the result presented by CPAchecker than HOMER Pro, and that answer partially \textit{RQ1}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Comparison between Formal Synthsis and HOME Pro}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Comparing the results between the formal synthesis 
+with CPAchecker and HOMER Pro, we observed that 
+most results were quite similar, in terms of technical 
+solution and cost, except for case studies $2$ and $7$. 
+In case study $2$, the costs presented by HOMER Pro were 
+$54$\% higher than the automated synthesis tool, probably 
+because the operation and maintenance costs assumed by our 
+automated synthesis tool were underestimated to that specific load.
+
+In general, the size of the PV panels were bigger 
+in HOMER Pro than with our formal synthesis approach, and that 
+discrepancy is not easy to address without some real systems. 
+Even considering that PVs and inverters were kept at the same cost 
+in both methodologies (simulation and formal synthesis), 
+HOMER Pro have more parameters to be set and a different 
+mathematical model adopted. Just to compare the results with 
+the real-world, the authors had four PV systems deployed and 
+monitored since June $2019$ in a riverside community at the 
+Amazonas State in Brazil, with similar demand presented 
+by case studies $1$, $4$, $5$, and $6$, always with a $3$$\times$$325$ W ($3$S) 
+panels and $4$$\times$$220$ Ah ($2$S-$2$P) lead-acid batteries. 
+Thse solutions are more close to the result presented by 
+our formal synthesis approach than HOMER Pro, and that partially 
+answers \textit{RQ1}.
+
+\textcolor{red}{In general, I don't think we have strong results here.
+Could you please provide a concrete example of the results provided by both tools and then show that our approach gives a more complete solution of the PV design?}
 
 %used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
-\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified three threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) the cost analysis is well tailored to the Amazon region of Brazil, however a broad analysis from other isolated areas must be performed in order to make the optimization general in terms of applicability; (3) to deploy at the field some PV systems sized using the synthesized results in order to validate it.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Threats to validity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We have reported a favorable assessment of our formal synthesis method. 
+Nevertheless, we have also identified three threats to the validity 
+of our experimental results, which can be further assessed and 
+constitute future work: (1) improvement of the power reliability 
+analysis: to include loss of load probability or loss of power 
+supply probability, which can make the analysis more accurate; 
+(2) the cost analysis is well tailored to the Amazon region of Brazil; 
+however, a broad analysis from other isolated areas must be 
+performed in order to make the optimization general in terms 
+of applicability; (3) to deploy at the field some PV systems 
+sized using our synthesized results in order to validate it.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{CONCLUSIONS}
 \label{sec:Conclusion}
-We have described and evaluated an automated synthesis method to obtain the optimal size of PV system using software model checking techniques.
-We have considered seven case studies from PV systems in two different sites of Amazon State in Brazil, ranging from $253$ W to $1,586$ W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
-Our automated synthesis tool presented detailed optimal solution to six cases adopted at this paper, with specifications, models and the arrangement in terms of series-parallel connections, covering the charge controller that was not presented by HOMER Pro.
-In a nutshell, our automated synthesis tool took more time to find the optimal solution than 	HOMER Pro, however the presented solution was more complete and detailed, very useful to a user to get a list of equipment and go to shopping.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-As future work, the authors plan to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in Amazon (Brazil), and to validate some cases with deployed PV systems at isolated communities.
+We have described and evaluated an automated synthesis method 
+to obtain the optimal size of PV system using software model 
+checking techniques. We have considered seven case studies 
+from PV systems in two different sites of the Amazonas State 
+in Brazil, ranging from $253$\,W to $1,586$\,W peak; and 
+three state-of-art verification engines were considered 
+(ESBMC, CBMC, and CPAchecker), in addition to a specialized 
+off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+
+Our automated synthesis tool presented detailed optimal solution 
+to six case studies adopted in this paper, with specifications, 
+models, and the arrangement in terms of series-parallel connections, 
+thereby covering the charge controller, which was not presented by HOMER Pro. 
+In a nutshell, our automated synthesis tool took more time 
+to find the optimal solution than HOMER Pro; however, the presented 
+solution was more complete and detailed, which is very useful 
+to a user to get a list of equipment and go to shopping.
+
+As future work, the authors plan to improve the power reliability analysis, 
+to address the restriction to only allow automated synthesis of 
+riverside communities in the Amazonas state (Brazil), and to 
+validate some cases with deployed PV systems in isolated communities.
 

### 2019-06-25 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
-	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the 365 days of the year;
+	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
 	\item HOMER Pro do not have a explicit equipment called charge controller.
@@
 	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of 1 kW and generic lead-acid batteries of 1 kW as well (and with capacity of 83.4 Ah according with HOMER Pro modeling).
+With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
@@
 Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used 
-as our verification engine to compare our approach effectiveness 
-and efficiency. Note that ``incremental'' ESBMC with the SMT solver 
-Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3}
-as an alternative to use less computing memory. 
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
+Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
 The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
@@
 
-CPAchecker was able to synthesize the optimal sizing in 
-six out of seven case studies: the result was produced 
-within the time limit, which varied from $134.71$ to 
-$235.75$ minutes. Only case study $7$ led to a \textit{timeout} 
-result, i.e., it was not solved within $240$ minutes.
-\textcolor{red}{if we allow CPAchecker to run without time limits, what would be the synthesis time for case study 7?}
-
-The violation (SAT result) indicated in Table~\ref{tab1} 
-is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
+CPAchecker was able to synthesize the optimal sizing in six out of seven case studies: the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
+Only case study $7$ led to a \textit{timeout} result, i.e., it was not solved within $240$ minutes.
+\textcolor{red}{Removing timeout limitation from CPAchecker, the verifier was able to solve the optimization in minutes}.
+The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
 %The results were tested by manual PV sizing and were sound (\textit{RQ1}).
@@
 CBMC and ESBMC were unable to produce any conclusive result.
-Situations of \textit{internal failure}, \textit{timeout}, 
-or \textit{out of memory} occurred; this partially answers 
-the \textit{EQ2}. Note tha the internal failure presented 
-by ESBMC was a Z3 solver issue (a bug), and this will demand 
-an updated version of ESBMC.
+Situations of \textit{internal failure}, \textit{timeout}, or \textit{out of memory} occurred; this partially answers the \textit{EQ2}.
+Note that the internal failure presented by ESBMC was a Z3 solver issue (a bug), and this will demand an updated version of ESBMC.
+\textcolor{red}{Removing the timeout from ESBMC with Boolector solver, the verifier was able to obtain the automated synthesis in $73.18$ hours for the case $2$ for example}.
 
-Related to HOMER Pro, it was able to evaluate six case studies, 
-and within a time shorter than $30$ seconds, which was much faster 
-than our automated synthesis tool (cf.~\textit{EQ2}). 
-Case study $3$ was not possible to be simulated since 
-HOMER Pro does not have the feature of adjust the battery autonomy, i.e., 
-the tool always tries to feed with electricity the load during $365$ days/year. 
+Related to HOMER Pro, it was able to evaluate six case studies, and within a time shorter than $30$ seconds, which was much faster than our automated synthesis tool (cf.~\textit{EQ2}).
+Case study $3$ was not possible to be simulated since HOMER Pro does not have the feature of adjust the battery autonomy, i.e., the tool always tries to feed with electricity the load during $365$ days/year.
 We have also noted others HOMER Pro drawbacks:
+
 \begin{itemize}
 \item There exists no explicit charge controller as a system equipment.
-HOMER Pro includes automatically a controller just to simulate the 
-charge/discharge of batteries and to meet the load requirement; 
-however, without costs or even with electrical characteristics 
-as maximum current and voltage, which are common during PV sizing;
-\item HOME Pro demands to include some battery specification 
-to initiate the optimization; however, it does not change the 
-electrical specifications during the simulation; and the result 
-are multiples of the original battery type suggested by the user. 
-As example, it was started with a $83.4$ Ah lead-acid battery 
-and during the simulation, HOMER Pro did not try to use 
-other capacities or types;
-\item HOMER Pro does not present the optimal solution 
-in terms of arrays connections of PV panels, just the total 
-in terms of power, i.e., it does not present models and 
-the power of each PV panel, neither the total of panels in series or parallel. 
+HOMER Pro includes automatically a controller just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics as maximum current and voltage, which are common during PV sizing;
+\item HOME Pro demands to include some battery specification to initiate the optimization; however, it does not change the electrical specifications during the simulation; and the result are multiples of the original battery type suggested by the user.
+As example, it was started with a $83.4$ Ah lead-acid battery and during the simulation, HOMER Pro did not try to use other capacities or types;
+\item HOMER Pro does not present the optimal solution in terms of arrays connections of PV panels, just the total in terms of power, i.e., it does not present models and the power of each PV panel, neither the total of panels in series or parallel.
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison between Formal Synthsis and HOME Pro}
+\subsection{Comparison between Formal Synthesis and HOME Pro}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Comparing the results between the formal synthesis 
-with CPAchecker and HOMER Pro, we observed that 
-most results were quite similar, in terms of technical 
-solution and cost, except for case studies $2$ and $7$. 
-In case study $2$, the costs presented by HOMER Pro were 
-$54$\% higher than the automated synthesis tool, probably 
-because the operation and maintenance costs assumed by our 
-automated synthesis tool were underestimated to that specific load.
+Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we observed that most results were quite similar, in terms of technical solution and cost (Table~\ref{tab1}).
 
-In general, the size of the PV panels were bigger 
-in HOMER Pro than with our formal synthesis approach, and that 
-discrepancy is not easy to address without some real systems. 
-Even considering that PVs and inverters were kept at the same cost 
-in both methodologies (simulation and formal synthesis), 
-HOMER Pro have more parameters to be set and a different 
-mathematical model adopted. Just to compare the results with 
-the real-world, the authors had four PV systems deployed and 
-monitored since June $2019$ in a riverside community at the 
-Amazonas State in Brazil, with similar demand presented 
-by case studies $1$, $4$, $5$, and $6$, always with a $3$$\times$$325$ W ($3$S) 
-panels and $4$$\times$$220$ Ah ($2$S-$2$P) lead-acid batteries. 
-Thse solutions are more close to the result presented by 
-our formal synthesis approach than HOMER Pro, and that partially 
-answers \textit{RQ1}.
+Particularly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from 0.23\% to 17.4\%.
+Even adopting same price per kW to the PV panels, inverters, and batteries, HOMER Pro do not use costs related to charge controllers that were included at CPAchecker modelling.
+The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well at this discrepancy, however it is not significant.
 
-\textcolor{red}{In general, I don't think we have strong results here.
-Could you please provide a concrete example of the results provided by both tools and then show that our approach gives a more complete solution of the PV design?}
+However, there was a huge divergence in case study $2$, where the costs presented by HOMER Pro were 54\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by our automated synthesis tool were underestimated to that specific load.
 
+In general, the size of the PV panels and battery bank were bigger in HOMER Pro than with our formal synthesis approach, and that discrepancy is not easy to address without some real systems validation.
+The mathematical models are different and particular parameters can be tuned as well in each approach, and that can justify the difference that was present in all the cases.
+As comparative, lets take case $1$: the optimal solution provided by HOMER Pro demands $7$ $\times$ more PV panels that the solution presented by CPAchecker, and do not shows the arrangement of arrays (number of series and parallel PV panels); the battery bank presented by HOMER Pro provides $500.4$ Ah of capacity ($6 \times 83.4$), while CPAchecker presented a optimal solution with $420$ Ah of total capacity ($4 \times 105$).
+Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2019$ in a riverside community at the Amazonas State in Brazil, with similar demand presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+These solutions are more close to the result presented by our formal synthesis approach than HOMER Pro, showing that our solution is sound \textit{RQ1}.
+
+Related to the inverters, HOMER Pro suggests a value in kW very close to the peak of every case, and it is just a reference value and not a commercial value of inverter.
+CPAchecker, in other hand, presents inverters that are commercial and can be found off-the-shelf.
+Therefore is a PRO to the formal synthesis method.
+
+Concerning to charge controllers, as told in previous section, HOMER Pro do not include it as an explicit equipment at its model, only CPAchecker presents a commercial controller and includes it during the cost analysis.
+Therefore, the formal synthesis method presents more reliable results.
+
+Case $7$ was not solved by CPAchecker within the limit of time established during the experimental phase.
+And case $3$ was not possible to simulate in HOMER Pro, by its restriction to not allow to set battery autonomy.
+Resting both without parameters to comparative.
+
+Summarizing, CPAchecker is capable to present a solution that is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
+Our automated synthesis method can show all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, like the model of the component, nominal current and voltage.
+By the way, even the name of the manufacturer can be presented (at Table~\ref{tab1} it was removed to avoid some advertising).
 %used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.

### 2019-06-26 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed experimental evaluation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2019-06-25 Tex/elsevier/trindade_appliedenergy_rev0.tex
@@
 
-CPAchecker was able to synthesize the optimal sizing in 
-six out of seven case studies: the result was produced 
-within the time limit, which varied from $134.71$ to 
-$235.75$ minutes. Only case study $7$ led to a \textit{timeout} 
-result, i.e., it was not solved within $240$ minutes.
-\textcolor{red}{if we allow CPAchecker to run without time limits, what would be the synthesis time for case study 7?}
-
+CPAchecker was able to synthesize the optimal sizing in six 
+out of seven case studies: the result was produced within 
+the time limit, which varied from $134.71$ to $235.75$ minutes. 
+Only case study $7$ led to a \textit{timeout} result, i.e., 
+it was not solved within $240$ minutes. However, if we remove 
+this timeout limitation from CPAchecker, the verifier is 
+able to solve the optimization in \textcolor{red}{XXXX} minutes. 
 The violation (SAT result) indicated in Table~\ref{tab1} 
@@
 
-CBMC and ESBMC were unable to produce any conclusive result. 
+CBMC and ESBMC are unable to produce any conclusive result. 
 Situations of \textit{internal failure}, \textit{timeout}, 
 or \textit{out of memory} occurred; this partially answers 
-the \textit{EQ2}. Note tha the internal failure presented 
-by ESBMC was a Z3 solver issue (a bug), and this will demand 
-an updated version of ESBMC.
+the \textit{EQ2}. Note that the internal failure presented 
+by ESBMC was a Z3 solver issue (a bug); this will demand 
+an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
+if we remove the timeout from ESBMC with the SMT solver Boolector, 
+then the verifier is able to obtain the automated synthesis 
+in $73.18$ hours for the case study $2$. \textcolor{red}{What about CBMC? Is it able to compute any result?}
 
 Related to HOMER Pro, it was able to evaluate six case studies, 
-and within a time shorter than $30$ seconds, which was much faster 
-than our automated synthesis tool (cf.~\textit{EQ2}). 
-Case study $3$ was not possible to be simulated since 
-HOMER Pro does not have the feature of adjust the battery autonomy, i.e., 
-the tool always tries to feed with electricity the load during $365$ days/year. 
-We have also noted others HOMER Pro drawbacks:
+and within a time shorter than $30$ seconds, which was much 
+faster than our automated synthesis tool (cf.~\textit{EQ2}). 
+Case study $3$ was not possible to be simulated since HOMER Pro 
+does not have the feature of adjusting the battery autonomy, i.e., 
+the tool always tries to feed with electricity the given load 
+during $365$ days/year. We have also noted other HOMER Pro drawbacks:
+
 \begin{itemize}
-\item There exists no explicit charge controller as a system equipment. 
-HOMER Pro includes automatically a controller just to simulate the 
-charge/discharge of batteries and to meet the load requirement; 
-however, without costs or even with electrical characteristics 
+\item There exists no explicit charge controller 
+as a system equipment. HOMER Pro includes automatically 
+a controller just to simulate the charge/discharge 
+of batteries and to meet the load requirement; however, 
+without costs or even with electrical characteristics 
 as maximum current and voltage, which are common during PV sizing;
 \item HOME Pro demands to include some battery specification 
-to initiate the optimization; however, it does not change the 
-electrical specifications during the simulation; and the result 
-are multiples of the original battery type suggested by the user. 
-As example, it was started with a $83.4$ Ah lead-acid battery 
-and during the simulation, HOMER Pro did not try to use 
-other capacities or types;
+to initiate the optimization; however, it does not change 
+the electrical specifications during the simulation; 
+the presented results are multiples of the original 
+battery type suggested by the user. As example, it was 
+started with a $83.4$ Ah lead-acid battery and during 
+the simulation, HOMER Pro did not try to use other capacities or types;
 \item HOMER Pro does not present the optimal solution 
-in terms of arrays connections of PV panels, just the total 
-in terms of power, i.e., it does not present models and 
-the power of each PV panel, neither the total of panels in series or parallel. 
+in terms of connections of arrays of PV panels, just the 
+total in terms of power, i.e., it does not present neither models 
+and the power of each PV panel nor the total of panels in series or parallel. 
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison between Formal Synthsis and HOME Pro}
+\subsection{Comparison between Formal Synthesis and HOME Pro}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Comparing the results between the formal synthesis 
-with CPAchecker and HOMER Pro, we observed that 
-most results were quite similar, in terms of technical 
-solution and cost, except for case studies $2$ and $7$. 
-In case study $2$, the costs presented by HOMER Pro were 
-$54$\% higher than the automated synthesis tool, probably 
-because the operation and maintenance costs assumed by our 
-automated synthesis tool were underestimated to that specific load.
+Comparing the results between the formal synthesis with CPAchecker 
+and HOMER Pro, we observed that most results are quite similar, 
+in terms of technical solution and cost (cf. Table~\ref{tab1}).
 
-In general, the size of the PV panels were bigger 
-in HOMER Pro than with our formal synthesis approach, and that 
-discrepancy is not easy to address without some real systems. 
-Even considering that PVs and inverters were kept at the same cost 
-in both methodologies (simulation and formal synthesis), 
-HOMER Pro have more parameters to be set and a different 
-mathematical model adopted. Just to compare the results with 
-the real-world, the authors had four PV systems deployed and 
-monitored since June $2019$ in a riverside community at the 
-Amazonas State in Brazil, with similar demand presented 
-by case studies $1$, $4$, $5$, and $6$, always with a $3$$\times$$325$ W ($3$S) 
-panels and $4$$\times$$220$ Ah ($2$S-$2$P) lead-acid batteries. 
-Thse solutions are more close to the result presented by 
-our formal synthesis approach than HOMER Pro, and that partially 
-answers \textit{RQ1}.
+Particularly related to LCC, the cost was very close in cases 
+$1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
+Even adopting the same price per kW to the PV panels, 
+inverters, and batteries, HOMER Pro does not use costs 
+related to charge controllers, which were introduced into the 
+CPAchecker modeling. The premise used in CPAchecker to adopt 
+a fixed annual cost for operation and maintenance can produce 
+some impact as well at this discrepancy; however, it is not significant
+since \textcolor{red}{explain here...}.
 
-\textcolor{red}{In general, I don't think we have strong results here.
-Could you please provide a concrete example of the results provided by both tools and then show that our approach gives a more complete solution of the PV design?}
+However, there exists a huge divergence in case study $2$, 
+where the costs presented by HOMER Pro were $54$\% higher 
+than our automated synthesis tool, probably because the 
+operation and maintenance costs assumed by our automated 
+synthesis tool were underestimated to that specific load.
 
+In general, the size of the PV panels and battery bank were 
+bigger in HOMER Pro than with our formal synthesis approach, 
+and that discrepancy is not easy to address without some real 
+systems validation. The mathematical models are different and 
+particular parameters can be tuned as well in each approach, 
+and that can justify the difference, which was presented in all 
+the case studies. As comparative, let's consider case study $1$: 
+the optimal solution provided by HOMER Pro demands $7$ $\times$ 
+more PV panels than the solution presented by our synthesis tool, 
+and HOME Pro does not show the arrangement of arrays 
+(i.e., the number of series and parallel PV panels); 
+the battery bank presented by HOMER Pro provides $500.4$ Ah 
+of capacity ($6 \times 83.4$), while our synthesis tool 
+presented an optimal solution with $420$ Ah of total capacity 
+($4 \times 105$).
+
+Just to compare the results obtained from the optimization 
+with the real-world, the authors had four PV systems deployed 
+and monitored since June $2019$ in a riverside community 
+in the Amazonas State in Brazil, with similar demands 
+presented by case studies $1$, $4$, $5$, and $6$, 
+always with a $3$ $\times$ $325$ W ($3$S) panels and 
+$4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) 
+lead-acid batteries. These solutions are more close 
+to the result presented by our formal synthesis 
+approach than HOMER Pro, thereby showing that our 
+solution is sound, which answers \textit{EQ1}.
+
+Related to the inverters, HOMER Pro suggests a value in 
+kW very close to the peak of every case study, and it 
+is just a reference value and not a commercial value of 
+the employed inverter. Our synthesis tool, however, 
+presents inverters that are commercial and can be found 
+off-the-shelf. Therefore is a PRO to the formal synthesis method.
+
+Concerning to charge controllers, as we reported in 
+the previous section, HOMER Pro does not include it 
+as an explicit equipment in its mathmetical model, 
+only our synthesis tool presents a commercial controller 
+and includes it during the cost analysis. Therefore, 
+the formal synthesis method presents more reliable results than
+HOME Pro.
+
+Case study $7$ was not solved by our synthesis tool 
+within the time limit established during the experimental 
+phase. Case study $3$ was not possible to simulate in HOMER Pro, 
+because its restriction does not allow one to set the battery autonomy, 
+thus resting both without parameters to comparative.
+
+Summarizing, our synthesis tool is capable to present a 
+solution, which is far detailed and close to the commercial 
+reality than the solution presented by HOMER Pro. 
+In particular, our automated synthesis method 
+can provide all the details of every component of 
+a PV system solution, with complete electrical details 
+from data sheet of manufacturers, including 
+the model of the component, nominal current and voltage. 
+In this respect, even the name of the manufacturer 
+can be presented (in Table~\ref{tab1} it was removed 
+to avoid some advertising).
 %used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.

### 2019-06-26 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 this timeout limitation from CPAchecker, the verifier is 
-able to solve the optimization in \textcolor{red}{XXXX} minutes. 
+able to solve the optimization in \textcolor{red}{$XXXX$} minutes. 
 The violation (SAT result) indicated in Table~\ref{tab1} 
@@
 then the verifier is able to obtain the automated synthesis 
-in $73.18$ hours for the case study $2$. \textcolor{red}{What about CBMC? Is it able to compute any result?}
+in $73.18$ hours for the case study $2$. \textcolor{red}{Similarly, if the timeout of CBMC is removed, the time to obtain the optimal solution to case $2$ with this verifier is of $XX$ hours.}
 
@@
 some impact as well at this discrepancy; however, it is not significant
-since \textcolor{red}{explain here...}.
+since \textcolor{red}{the annual cost considered is too small when compared to the resulting LCC value.}.
 

### 2019-06-27 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 then the verifier is able to obtain the automated synthesis 
-in $73.18$ hours for the case study $2$. \textcolor{red}{Similarly, if the timeout of CBMC is removed, the time to obtain the optimal solution to case $2$ with this verifier is of $XX$ hours.}
+in $73.18$ hours for the case study $2$. \textcolor{red}{CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.}
 
@@
 some impact as well at this discrepancy; however, it is not significant
-since \textcolor{red}{the annual cost considered is too small when compared to the resulting LCC value.}.
+since \textcolor{red}{the annual cost considered is too small when compared to the resulting LCC value.}
 

### 2019-06-27 Tex/Old text/chapters/appendix.tex
thesis structure

appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix.

### 2019-06-27 Tex/Old text/chapters/chapter02.tex
thesis structure

chapter02 text here lkgf go kdgndfgn g f dgdgs hd hd gh dgh

### 2019-06-27 Tex/Old text/chapters/chapter03.tex
thesis structure

chapter03 here amamas asd asd as das das d af dsgf dfg  tre tre t ret ret er ter te rt ert ert er tre t

### 2019-06-27 Tex/Old text/chapters/chapter04.tex
thesis structure

chapter04 here  dgfrty tyuj gfhj cb cvb cvb cvb cvb

### 2019-06-27 Tex/Old text/chapters/introduction.tex
thesis structure

introduction text here kadhew nrjrenasmnfs,mgfs gfsdf gdsf dfsg dsgh bv dzfg df gdf gdf gdf gdf gd fg dfg dfg

### 2019-06-27 Tex/Old text/main.tex
thesis structure

\documentclass[12pt,twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{caption}
\usepackage{subcaption}
\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm,bindingoffset=6mm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{Thesis Title}
\fancyfoot{}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[LO,CE]{Chapter \thechapter}
\fancyfoot[CO,RE]{Author Name}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

%\usepackage[style=authoryear,sorting=none]{biblatex}
%\addbibresource{references.bib}

\title{Thesis Title}
\author{Alessandro Trindade}
\date{Day Month Year}

\begin{document}

\input{titlepage}

\input{abstract}

\chapter*{Dedication}
To mum and dad

\chapter*{Declaration}
I declare that..

\chapter*{Acknowledgements}
I want to thank...

\tableofcontents

\listoffigures

\listoftables

\chapter{Introduction}
\input{chapters/introduction}

\chapter{Chapter Two Title}
\input{chapters/chapter02}

\chapter{Chapter Three Title}
\input{chapters/chapter03}

\chapter{Chapter Four Title}
\input{chapters/chapter04}

\chapter{Conclusion}
\input{chapters/conclusion}

\appendix
\chapter{Appendix Title}
\input{chapters/appendix}

%\printbibliography
\bibliography{trindadeThesis}{}

\end{document}

### 2019-06-27 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
+Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach.
 \end{abstract}

### 2019-06-29 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}.
 In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
@@
 
-\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
+\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; 
 $ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
@@
 	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
-This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every 10 years).
+This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
 Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
@@
 
-Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of 25\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
+Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
 
@@
 this timeout limitation from CPAchecker, the verifier is 
-able to solve the optimization in \textcolor{red}{$XXXX$} minutes. 
+able to solve the optimization in $44.97$ hours. 
 The violation (SAT result) indicated in Table~\ref{tab1} 
@@
 then the verifier is able to obtain the automated synthesis 
-in $73.18$ hours for the case study $2$. \textcolor{red}{CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.}
+in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.
 
@@
 some impact as well at this discrepancy; however, it is not significant
-since \textcolor{red}{the annual cost considered is too small when compared to the resulting LCC value.}
+since this annual cost is too small when compared to the resulting LCC value.
 
@@
 with the real-world, the authors had four PV systems deployed 
-and monitored since June $2019$ in a riverside community 
+and monitored since June $2018$ in a riverside community 
 in the Amazonas State in Brazil, with similar demands 
@@
 the previous section, HOMER Pro does not include it 
-as an explicit equipment in its mathmetical model, 
+as an explicit equipment in its mathematical model, 
 only our synthesis tool presents a commercial controller 
@@
 of our experimental results, which can be further assessed and 
-constitute future work: (1) improvement of the power reliability 
+constitute future work: ($1$) improvement of the power reliability 
 analysis: to include loss of load probability or loss of power 
 supply probability, which can make the analysis more accurate; 
-(2) the cost analysis is well tailored to the Amazon region of Brazil; 
+($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
 however, a broad analysis from other isolated areas must be 
 performed in order to make the optimization general in terms 
-of applicability; (3) to deploy at the field some PV systems 
+of applicability; ($3$) to deploy at the field some PV systems 
 sized using our synthesized results in order to validate it.
@@
 \section*{Acknowledgments}
-The authors would like to thank: (i) Newton Fund [grant number 261881580] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa 2018], for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019); and (iv) University of Sheffield's Research England QR GCRF Institutional Allocation for the HOMER Pro license.
+The authors would like to thank: (i) Newton Fund [grant number $261881580$] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa $2018$], for the DCTIEX II scholarship (NOV-$2018$), and for support the research mobility to UK; (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and (iv) University of Sheffield's Research England QR GCRF Institutional Allocation for the HOMER Pro license.
 

### 2019-07-01 Tex/Old text/abstract.tex
thesis updated text

\thispagestyle{plain}
\begin{center}
    \Large
    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}

    \vspace{0.4cm}
    \large
    Optimal Sizing and Project Validation

    \vspace{0.4cm}
    \textbf{Alessandro Trindade}

    \vspace{0.9cm}
    \textbf{Abstract}
\end{center}
verif:
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to validate any kind of system. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated as well, in order to compare performance and soundness. Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.

synthesis:
There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking. If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase. Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach.

\textit{Keywords}: Formal verification; automated verification; model checking; program synthesis; electrical systems; solar photovoltaic systems

### 2019-07-01 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
-chapter02 text here lkgf go kdgndfgn g f dgdgs hd hd gh dgh
+chapter02 text here
+
+////////////////// Begin old stuff
+
+\subsection{Solar Photovoltaic System }
+According to \cite{Roy}, a PV system is designed to give the electric supply to a load.
+This load can be either Alternate Current (AC) type or Direct Current (DC) type.
+Electric supply can be needed either in daytime or evening time (in particular cases, in both times).
+The most basic PV system can give supply only in daytime.
+For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.
+
+PV systems are broadly classified into three distinct types, as described by \cite{Mohanty}:
+
+\begin{itemize}
+\item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
+Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants;
+\item Grid-connected systems, where the solar PV system is connected to the grid.
+The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards.
+Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode;
+\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
+In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
+\end{itemize}
+
+Specifically concerning isolated communities, depending on the type of load, cost, resources availability, and requirements of the load, standalone systems can be split into several categories, which are described in this section.
+As the goal of this Thesis is just the solutions aimed to isolated/ off-grid application, therefore it is not considered the on-grid or hybrid configurations.
+
+There is a resource, called maximum power point tracking (MPPT), which is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}.
+That resource is found at modern PV systems and is strongly indicated due to its advantages.
+
+\subsubsection{Unregulated standalone PV system with DC load }
+Usually this type of system is for low power applications, as defined by \cite{Roy}.
+The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:unregSPV}.
+At night hours, the system will not provide any supply because of the absence of the battery.
+
+\begin{figure}[h]
+\includegraphics[width=0.6\textwidth]{unregulatedSPV.png}
+\centering
+\caption{Unregulated standalone SPV system with DC load (Source: \cite{Roy})}
+\label{fig:unregSPV}
+\end{figure}
+
+\subsubsection{Regulated standalone PV system with DC load}
+It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:regSPV1}.
+Usually system with MPPT should have battery; otherwise, extra power will be waste.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{regulatedSPV1.png}
+\centering
+\caption{Regulated standalone SPV system with DC load (Source: \cite{Roy})}
+\label{fig:regSPV1}
+\end{figure}
+
+\subsubsection{Regulated standalone system with battery and DC load}
+Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}.
+Battery is used to store the extra power of PV system.
+A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
+Extra charging and deep discharging can reduce the battery life \cite{Kim}.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{regulatedSPV2.png}
+\centering
+\caption{Regulated standalone SPV system with battery DC load (Source: \cite{Roy})}
+\label{fig:regSPV2}
+\end{figure}
+
+According to \cite{Pinho}, PV systems that are used to feed loads with low variation on the consumption can be sized to operate without the controller.
+That is called of self-regulated standalone PV system with battery.
+However, the voltage from the PV panel must be compatible with the batteries voltage.
+Normally, the bank of batteries are oversized related to the PV panel and to the load.
+The drawback is the operation of the batteries, normally overloaded or with excessive discharges (that can damage the batteries).
+
+\subsubsection{Regulated standalone system with battery, AC load}
+This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}.
+This solution has an increase of cost because has more equipments.
+However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
+That configuration is the focus of the present thesis since it is the most common nowadays all over the world, when off-grid or isolated regions is the target.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{regulatedSPV3.png}
+\centering
+\caption{Regulated standalone system with battery, AC load (Source: \cite{Roy})}
+\label{fig:regSPV3}
+\end{figure}
+
+\subsection{Design and Validation of a Solar photovoltaic system}
+The design and validation of a SPV system can be done by hand or with the aid of a software tool.
+
+In order to address different aspects of project system and systems design, there is a myriad of public domain and commercial software available for the SPV market.
+According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
+Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
+
+Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
+In this study, the most popular tools are presented:
+
+\begin{itemize}
+\item PVWatts 
+\item SAM
+\item Homer
+\item RETScreen
+\item Hybrid2
+\end{itemize}
+
+\subsubsection{PVWatts Calculator}
+According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
+According to \cite{NRELDobos}, to use the calculator, it is necessary to provide information about the system's location, basic design parameters, and system economics.
+PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity monetary value.
+This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules.
+The production estimates that PVWatts computation do not account for many factors that are important in the design of a photovoltaic system, therefore it is necessary support of an energy expert.
+The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year.
+To represent the system's physical characteristics, PVWatts requires values for six inputs: System DC size; Module type; Array type; System losses; Array tilt angle; Array azimuth angle.
+
+\subsubsection{SAM}
+SAM or System Advisor Model is a software from the U.S.
+Department of Energy and National Renewable Energy Laboratory.
+According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications, and (also) to provide information for readers who do not plan to use the model, but want to learn about its capabilities.
+SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: Project managers and engineers; Financial and policy analysts; Technology developers; and Researchers.
+SAM makes performance predictions and cost of energy estimates for grid-connected power projects based on installation and operating costs and system design parameters that you specify as inputs to the model.
+Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement.
+SAM is an electric power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet electric load.
+It does not model thermal energy systems that meet a thermal process load.
+As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.
+
+\subsubsection{HOMER}
+As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
+HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources.
+HOMER Legacy is the original HOMER software version created at the National Renewable Energy Laboratory (NREL).
+HOMER Legacy is a free computer model that simplifies the task of evaluating design options for both off-grid and grid-connected power systems for remote, stand-alone, and distributed generation applications.
+HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options.
+Since 2016 Homer Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available.
+At the short-time only the commercial version will remain.
+
+The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
+HOMER Pro put together three tools in one product: optimization, simulation, and sensitivity analysis.
+HOMER Pro provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use.
+It is adaptable to a wide variety of projects.
+For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project.
+For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations.
+Chronological simulation is essential for modeling variable resources, such as solar and wind power and for combined heat and power applications, where the thermal load is variable.
+HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.
+
+\subsubsection{RETScreen}
+As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
+
+RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options.
+The software can be used to evaluate benefits from both clean energy production from power generation projects and savings through energy efficiency projects, accounting for project costs, greenhouse gas emission reductions, and financial risk.
+The software is freely distributed (but with restrictions to save work or print), and had three different versions:
+
+\begin{itemize}
+\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
+\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
+\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
+However, this version works is only Windows-based.
+This version has a complete paid version, in an annual subscription way.
+\end{itemize}
+
+As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
+It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
+RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.
+
+\subsubsection{Hybrid2}
+The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
+Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
+Variations in wind speed and in load within each time step are factored into the performance predictions.
+The code does not consider short-term system fluctuations caused by system dynamics or component transients.
+This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, what is a limitation.
+
+Table \ref{table:softwares} summarizes the tools described in this paper.
+Where just Hybrid2 do not have technical support; only HOMER, RETScreen and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER and RETScreen are complete, including economical analysis or even optimization-sensitive analysis.
+However, only paid version of those softwares have all the features, and they run only at Windows-based operational systems.
+
+\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Comparative coverage of reference softwares}
+\label{table:softwares}
+\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+\begin{tabular}{c | c | c | c | c | c}
+\hline
+\hline
+Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen } & \rotatebox{90}{Hybrid2}\\
+\hline
+Support & X & X & X & X &  \\
+Off-grid systems &   &   & X & X & X\\
+Hybrid systems &  &  & X & X & X\\
+Photovoltaics & X & X & X & X & X\\
+Batteries &  &  & X & X & X\\
+Main technical (T) or economical (E) & T & T & E & E & T \\
+Optimization &  &  & X & X &  \\
+Sensitive analysis &  &  & X & X & \\
+\hline
+\hline
+\end{tabular}
+\end{table}
+
+\subsubsection{Paper Proposal x Reference Tools}
+Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER and RETScreen remain for comparative.
+All tools need some parameters inherently from manufacturer's catalog, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries.
+After that, the potential solution is analyzed in another tool to validate or even optimize the solution.
+Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution.
+
+\subsection{Component models for stand-alone PV system }
+The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load.
+The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}.
+The modular structure facilitates the modeling of the other system structures and replacing of elements as, for instance, a DC load instead of an AC load.
+
+\begin{figure}[h]
+\includegraphics[width=0.95\textwidth]{blockdiagramPVS}
+\centering
+\caption{Block diagram for the stand-alone PV system (Source: \cite{Hansen})}
+\label{fig:blockdiagram}
+\end{figure}
+
+In the literature, there are several mathematical models available for each component of stand-alone PV systems. In this section, the mathematical model for each component of PV system is presented.
+
+\subsubsection{PV generator (cell, module, array) }
+A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. In the present modeling, the focus is only on cell/module/array.
+
+The basic element of a PV System is the PV cell, also called a Solar Cell.
+A PV / Solar Cell is a semiconductor device that can convert solar energy into DC electricity.
+The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
+When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}.
+If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
+
+To increase their utility, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module).
+For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
+In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}.
+The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.
+
+\begin{figure}[h]
+\includegraphics[width=0.95\textwidth]{celmodarray}
+\centering
+\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
+\label{fig:celmodarray}
+\end{figure}
+
+The PV modules are generally rated under standard test conditions (STC), which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
+The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
+However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
+
+These uncertainties lead to either over- or underestimation of energy yield from PV modules.
+An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
+The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}.
+Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
+However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage.
+Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
+
+Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
+
+The performance of photovoltaic systems (solar cell/panels), that is, the output current/voltage curve ($I-V$ curve), is usually studied using an equivalent circuit model.
+This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}.
+Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig.
+\ref{fig:equivckt}.
+
+\begin{figure}[h]
+\includegraphics[width=0.95\textwidth]{equivckt}
+\centering
+\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
+\label{fig:equivckt}
+\end{figure}
+
+The 1-diode model, whose equation to relate the output current, $I$, to the output voltage, $V$, is described in Equation \ref{eq:1diodemodel}.
+
+\begin{equation}
+\label{eq:1diodemodel}
+I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right] 
+\end{equation}
+
+Where:
+\begin{itemize}
+\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
+\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
+\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed;
+	\begin{itemize}
+	\item $ N=1 $ in a single cell configuration. 	
+	\end{itemize}	  
+\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; 
+	\begin{itemize}
+	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
+	\end{itemize}
+\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
+	\begin{itemize}
+	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
+	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
+	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
+	\end{itemize}	 
+\end{itemize}
+
+This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.
+
+The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}.
+
+\begin{equation}
+\label{eq:1d1rmodel}
+I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
+\end{equation}
+
+Where $R_{s}$ is the series resistor.
+
+At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
+
+The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}.
+
+\begin{equation}
+\label{eq:1d2rmodel}
+I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
+\end{equation}
+
+Where $R_{sh}$ is the shunt resistor.
+
+At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
+
+And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}.
+
+\begin{equation}
+\label{eq:2d2rmodel}
+I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
+\end{equation}
+
+This model has six unknown parameters with two exponential terms. 
+Briefly, both single and double diode models require the knowledge of all unknown parameters, which is usually not provided by manufacturers.
+Nevertheless, the current-voltage equation is a transcendental expression \cite{Jakhrani}.
+
+However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel.
+
+For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
+The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
+However, due to implicit nature and nonlinearity of PV cell or module characteristics, it is hard to find out the analytical solution of all unknown parameters, as described by \cite{Hasan}.
+Thus, numerical methods such as Newton-Raphson method or Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}.
+This happens because numerical methods give approximate solution of the nonlinear problems without searching for exact solutions.
+However, numerical methods are time consuming and need long term time series data, which is not available in developing countries.
+\cite{Jakhrani} did a mixed methodology using analytical and numerical steps together.
+\cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation (essays).
+And \cite{Tian} did a mix of analytical and experimental methodology to get the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use experimental technique.
+
+Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves).
+However, the present work will rely on the simplified model of 1-diode, that was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested.
+In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation.
+
+\subsubsection{Proposed PV Panel Model}
+With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1d1rmodel}.
+
+A single-diode without series and shunt resistances is considered. Equation 1 is used to write down expressions for currents and voltages at each key point shown in Fig. \ref{fig:ivcurve}.
+
+\begin{figure}[h]
+\includegraphics[width=0.90\textwidth]{ivcurve}
+\centering
+\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
+\label{fig:ivcurve}
+\end{figure}
+
+Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
+
+\begin{equation}
+\label{eq:Isc}
+I_{sc}=I_{ph}\vert_{V=0}
+\end{equation}
+
+\begin{equation}
+\label{eq:Voc}
+V_{oc}=\dfrac{aNk_{B}T}{q}ln\left( 1+\dfrac{I_{sc}}{I_{0}} \right) 
+\end{equation}
+
+\begin{equation}
+\label{eq:exp}
+exp\left( \dfrac{qV_{oc}}{aNk_{B}T} \right) = \left(1+\dfrac{qV_{m}}{aNk_{B}T} \right) exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) 
+\end{equation}
+
+\begin{equation}
+\label{eq:Im}
+I_{m} =I_{ph}-I_{0}\left[ exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) -1 \right] 
+\end{equation}
+
+Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way.
+A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}.
+These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig.
+\ref{fig:ivcurve}, where the transition is a compromise between both behaviors.
+It is interesting to observe that the maximum power point corresponds to a trade-off condition, where the current is still high enough before it starts decreasing with increasing the output voltage (Fig.
+\ref{fig:ivcurve}).
+
+Based on this, the tangent of the I-V curve can be used to evaluate the transition between current- to voltage-source controlled regions; this operation yields Equation \ref{eq:didv}.
+
+\begin{equation}
+\label{eq:didv}
+\dfrac{dI}{dV}=-\dfrac{qI_{0}}{aNk_{B}T}exp \left( \dfrac{qV}{aNk_{B}T}  \right) 
+\end{equation}
+
+The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell.
+Therefore, the Equation \ref{eq:Vmderiv} is generated.
+
+\begin{equation}
+\label{eq:Vmderiv}
+V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
+\end{equation}
+
+It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point.
+The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change on $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}.
+Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation 10 can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
+
+\begin{equation}
+\label{eq:dIdV_Vm}
+\dfrac{dI}{dV}\vert_{V_{m}} \cong -\dfrac{0-I_{sc}}{V_{oc}-0}=\dfrac{I_{sc}}{V_{oc}}
+\end{equation}
+
+Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, the voltage and the current at the maximum power point and consequently the maximum output power, are expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm} ($ P_{m}=V_{m}I_{m} $).
+These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
+
+\begin{equation}
+\label{eq:Vmfinal}
+V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) 
+\end{equation}
+
+\begin{equation}
+\label{eq:Imfinal}
+I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  
+\end{equation}
+
+\begin{equation}
+\label{eq:Pm}
+P_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
+\end{equation}
+
+However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
+Therefore, Equation \ref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.
+
+\begin{equation}
+\label{eq:Iph}
+I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right] 
+\end{equation}
+
+Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $.
+
+In Equation \ref{eq:Iph}, $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) and corresponds to the photocurrent obtained from a given PV cell working at (STC or standard test conditions) reference conditions (provided by PV manufacturers).
+$ I_{ph,ref} $ can also be approximated to the reference short-circuit current that is provided by PV manufacturers ($ I_{sc,ref} $) as shown by \cite{Jakhrani}.
+
+The cell temperature ($ T $) can be obtained from \cite{Ross} and is shown in Equation \ref{eq:Tcell}.
+
+\begin{equation}
+\label{eq:Tcell}
+T = T_{air} + \dfrac{NOCT-20}{800}G
+\end{equation}
+
+Where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
+
+Furthermore, \cite{Villalva} have proposed a relationship, which allows the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature.
+In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
+
+\begin{equation}
+\label{eq:I0}
+I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1}
+\end{equation}
+
+Where $ V_{oc,ref} $ is the reference open-circuit voltage, and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
+
+The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state.
+Using the maximum power point current equation (Equation \ref{eq:Pm}) and the saturation current in the reference temperature given by Equation \ref{eq:I0}, the diode quality coefficient is determined by Equation \ref{eq:a}.
+
+\begin{equation}
+\label{eq:a}
+a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) }
+\end{equation}
+
+Where $ V_{mref} $, $ V_{oc,ref} $, $ I_{m,ref} $, and $ I_{sc,ref} $ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers.
+
+The model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
+
+If the PV cells are in parallel, then there is a parallel array.
+Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
+
+\begin{equation}
+\label{eq:Iarray}
+I_{array} = (N_{cells in parallel})(I_{one cell})
+\end{equation}
+
+Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
+
+In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
+
+\begin{equation}
+\label{eq:Varray}
+V_{array} = (N_{cells in series})(V_{one panel})
+\end{equation}
+
+Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
+
+Besides the model verification, there is the prior stage of project sizing check, which is simple, based on manufacturer's data and information from the sizing and the site.
+
+First is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$).
+That is done by Equation \ref{eq:Ecorrected}, according \cite{Pinho}.
+Where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
+
+\begin{equation}
+\label{eq:Ecorrected}
+E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }
+\end{equation}
+
+The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by Equation \ref{eq:NTPmin}, and the check is done with the Equation \ref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from Equation \ref{eq:NTPmin}.
+
+\begin{equation}
+\label{eq:NTPmin}
+N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}
+\end{equation}
+
+\begin{equation}
+\label{eq:NTP}
+N_{TP} \geq N_{TPmin}
+\end{equation}
+
+Particularly, the total number of panels is series ($ N_{PSmin} $) and parallel ($ N_{PPmin} $) are given by the Equations \ref{eq:NPSmin} and \ref{eq:NPPmin}, respectively.
+With the check did by Equations \ref{eq:NPS} and \ref{eq:NPP}.
+$ V_{system} $ is the DC voltage of the bus, and is a design decision (normally 12, 24 or 48 V).
+
+\begin{equation}
+\label{eq:NPSmin}
+N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}
+\end{equation}
+
+\begin{equation}
+\label{eq:NPPmin}
+N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}
+\end{equation}
+
+\begin{equation}
+\label{eq:NPS}
+N_{PS} \geq N_{PSmin}
+\end{equation}
+
+\begin{equation}
+\label{eq:NPP}
+N_{PP} \geq N_{PPmin}
+\end{equation}
+
+\subsubsection{The Battery Storage Model }
+Because of the fluctuating nature of the output delivered by the PV arrays, batteries are necessary in a PV system.
+Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery.
+During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.
+
+Several models have been presented in the literature. However, regardless of the model, normally the following parameters are required:
+
+\begin{itemize}
+\item Nominal capacity ($ q_{m} $), is the number of Ampère-hours ($ Ah $) that can maximally be extracted from the battery, under predetermined discharge conditions.
+\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $.
+Obviously $ 0<SOC<1 $.
+If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
+\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged).
+It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
+\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
+\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
+\end{itemize}
+
+The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
+The battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
+LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.
+
+In general, the battery models view the battery as a voltage source $ E $ in series with an internal resistance $ R_{0} $, as shown in Fig. \ref{fig:batteryckt}.
+
+\begin{figure}[h]
+\includegraphics[width=0.7\textwidth]{batteryckt}
+\centering
+\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
+\label{fig:batteryckt}
+\end{figure}
+
+The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.
+
+Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
+
+The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.
+
+The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
+However, it uses some data extracted from tested batteries in laboratory.
+Therefore is not suitable to this study.
+
+Most of the created models were used to simulate and optimize PV storage system based on lead-acid batteries.
+That kind of battery is the most common used batteries in PV application, owing to their relative low cost and wide availability \cite{Copetti}.
+
+Here, the model adopted is the based on \cite{Copetti}, who uses manufacturer's data and allows finding relations among voltage, current, state of charge and temperature.
+
+The discharge voltage equation is shown in Equation \ref{eq:bat_Vd}.
+The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
+
+\begin{equation}
+\label{eq:bat_Vd}
+V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T)
+\end{equation}
+
+Where $ C_{10} $ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $ \Delta T $ is temperature variation ($ \Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $, $ SOC $ indicates how much electric charge is stored in the cell at given time, defined by Equation \ref{eq:SOCbat}.
+
+\begin{equation}
+\label{eq:SOCbat}
+SOC = \left( 1 - \dfrac{Q}{C} \right) 
+\end{equation}
+
+Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
+
+The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the farction of discharge, i.e., $ DOC=1-SOC $.
+
+The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
+This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
+
+\begin{equation}
+\label{eq:CC10}
+\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 \Delta T)
+\end{equation}
+
+Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
+
+For the charging process, however, the parameters are presented in Equation \ref{eq:Vcbat}.
+
+\begin{equation}
+\label{eq:Vcbat}
+V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T)
+\end{equation}
+
+SOC can be calculated easily at any point during the discharge period; however, during recharge it is much more difficult \cite{Copetti}.
+
+Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell.
+The efficiency drops to zero at full charge and the function that represents the charge efficiency ($ \eta_{c} $) variation with state of charge and current rate is given in Equation \ref{eq:efficcharge}.
+
+\begin{equation}
+\label{eq:efficcharge}
+\eta_{c} = 1 - exp \left[ \dfrac{20.73}{\dfrac{I}{I_{10}}+0.55} (SOC-1) \right] 
+\end{equation}
+
+\cite{Copetti} show that, during overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (Equation \ref{eq:Vec}).
+It was created a function for the gassing voltage as well, as shown in Equation \ref{eq:Vg}.
+In addition, the overcharge phenomenon can be represented by Equation \ref{eq:Voverc}.
+
+\begin{equation}
+\label{eq:Vec}
+V_{ec} = \left[ 2.45 + 2.011 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
+\end{equation}
+
+\begin{equation}
+\label{eq:Vg}
+V_{g} = \left[ 2.24 + 1.97 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
+\end{equation}
+
+\begin{equation}
+\label{eq:Voverc}
+V_{c} = V_{g} + (V_{ec} - V_{g}) \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
+\end{equation}
+
+Where $ Ah_{restored} $ represents the Ampère-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
+
+The function assumes that 95\% of the capacity was already restored at the start of overcharge.
+
+The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by Equation \ref{eq:tau}.
+
+\begin{equation}
+\label{eq:tau}
+\tau = \dfrac{17.3}{1+852 \left( \dfrac{I}{C_{10}} \right) ^{1.67} }
+\end{equation}
+
+Therefore, to model the voltage ($ V_{c} $) evolution of the battery, equation \ref{eq:Vcbat} can be used up the start of gassing ($ V_{c} \leq V_{g} $).
+And during overcharging ($ V_{c} > V_{g} $), Equation \ref{eq:Voverc} can be used until a constant final voltage ($ V_{ec} $) is reached.
+
+The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
+
+\begin{equation}
+\label{eq:stor}
+Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
+\end{equation}
+
+Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
+
+As an example of this formula application, as shown by \cite{Abdulateef}, considering that an off-grid PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
+
+Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$.
+Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$).
+If a single battery of 12 V and 350 Ah is considered, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
+
+At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature.
+The equations are used to update the $SOC$ of the batteries, and have the number of hours ($ Num_{h} $) as a variable.
+There is a factor (1.15) which is present at the charging equation, and is necessary to express that during the charging process is usual to reach 115\% of the battery capacity
+
+\begin{equation}
+\label{eq:charge}
+SOC_{charge} = SOC_{previous} + \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
+\end{equation}
+
+\begin{equation}
+\label{eq:discharge}
+SOC_{discharge} = SOC_{previous} - \dfrac{100*I_{drained}*Num_{h}}{capacity}
+\end{equation}
+
+Besides the model verification, there is also the prior stage of project sizing check, as did to the solar panel.
+First is necessary to define the total capacity of the battery bank, as shown by Equation \ref{eq:Cbank}.
+
+\begin{equation}
+\label{eq:Cbank}
+C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}
+\end{equation}
+
+The variable $ autonomy $ is a design definition and normally has a value ranging from 6 to 48h. The other variables were discussed previously.
+
+Following, is done the total (minimum) number of batteries, as show by Equation \ref{eq:Nbtotal}.
+Moreover, the Equation \ref{eq:batcheck} perform the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that were established to the project.
+
+\begin{equation}
+\label{eq:Nbtotal}
+N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}
+\end{equation}
+
+\begin{equation}
+\label{eq:batcheck}
+\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total
+\end{equation}
+
+\subsubsection{Controller Model}
+Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
+However, in this study, in order to simplify, the term used is controller.
+
+The controller is a set of items (DC-DC converter, a MPPT and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+According to \cite{Pinho}, controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.
+
+As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components.
+The use of battery as a storage form implies thus the presence of a charge controller.
+
+In general, there are two main operating modes for the controller: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
+
+In \cite{Mellit} was established that the controller allows the management of energy between the load and the battery.
+The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
+The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
+
+According \cite{Hansen}, to protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and when the current required by the load is less than the current delivered by the PV arrays.
+PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $.
+This can be done by using a switch with a hysteresis cycle, as illustrated in Fig.
+\ref{fig:controllerover}.
+
+\begin{figure}[h]
+\includegraphics[width=0.7\textwidth]{controllerover}
+\centering
+\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
+\label{fig:controllerover}
+\end{figure}
+
+To protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold i and when the current required by the load is larger than the current delivered by the PV arrays \cite{Hansen}.
+The load is reconnected to the system, when the terminal voltage is above a certain value i, using a switch with a hysteresis cycle, as shown in Fig.
+\ref{fig:controllerdisc}.
+
+\begin{figure}[h]
+\includegraphics[width=0.7\textwidth]{controllerdisc}
+\centering
+\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
+\label{fig:controllerdisc}
+\end{figure}
+
+According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.).
+
+The steps in the modeling of the controller process are summarized in Table \ref{table:controller}.
+
+\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Summary of the controller process (Source: \cite{Hansen})}
+\label{table:controller}
+\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+\begin{tabular}{c | c | c }
+\hline
+\hline
+Step  & Constraint & Command\\
+\hline
+\hline
+(1) & \makecell{If $V > V_{max \textunderscore off}$ and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array from the system}\\
+\hline
+(2) & \makecell{If command (1) is done and $V < V_{max \textunderscore on}$} & \makecell{Reconnect PV array to the system}\\
+\hline
+(3) & \makecell{If $V < V_{min \textunderscore off}$ and $I_{load} > I_{pv}$} & \makecell{Disconnect the load from the system}\\
+\hline
+(4) & \makecell{If command (3) is done and $V > V_{min \textunderscore on}$} & \makecell{Reconnect the load to the system}\\
+\hline
+\hline
+\end{tabular}
+\end{table}
+
+Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage.
+
+As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load.
+The output power ($ P_{out} $) of DC-DC converter is given by Equation \ref{eq:poutcont}.
+
+\begin{equation}
+\label{eq:poutcont}
+P_{in = P_{out}}
+\end{equation}
+
+Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Equation \ref{eq:poutcont} is possible to reach Equation \ref{eq:potcont}.
+
+\begin{equation}
+\label{eq:potcont}
+V_{in} I_{in} \eta_{c} = V_{out} I_{out}
+\end{equation}
+
+Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the current output of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $-I_{out}$ is the output current from the converter, when all the other values are known.
+
+The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}).
+
+A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
+In addition, there is the Cuk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.
+
+For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.
+
+\begin{equation}
+\label{eq:voutvin}
+\dfrac{V_{out}}{V_{in}} = \dfrac{D}{D-1}
+\end{equation}
+
+Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
+
+The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
+
+Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.
+
+As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
+
+One more time, some steps must be done to check the sizing project of the controller, prior the verification phase.
+Initially the controller must meet the voltage requirement of the PV system, as shown by Equation \ref{eq:vcvsystem}.
+
+\begin{equation}
+\label{eq:vcvsystem}
+V_{c} = V_{system}
+\end{equation}
+
+Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as shown by Equation \ref{eq:iscamb}.
+
+\begin{equation}
+\label{eq:iscamb}
+I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right] 
+\end{equation}
+
+The controller must meet the maximum current from the PV array (Equations \ref{eq:icmin} and \ref{eq:icicmin}).
+
+\begin{equation}
+\label{eq:icmin}
+I_{c,min} = I_{sc,amb} \times N_{PP}
+\end{equation}
+
+\begin{equation}
+\label{eq:icicmin}
+I_{c} \geq I_{c,min}
+\end{equation}
+
+The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
+In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
+
+\begin{equation}
+\label{eq:numberofcmin}
+number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} =  \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
+\end{equation}
+
+\begin{equation}
+\label{eq:numberofc}
+N_{controller} \geq number_{controllers}
+\end{equation}
+
+\subsubsection{The inverter model}
+As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
+An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output.
+The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage (127 V or 220 V, for example), and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency \cite{Hansen}.
+
+The inverter is characterized by a power dependent efficiency $ \eta_{i} $ given by \cite{Hansen} as shown by Equation \ref{eq:efficinv}.
+
+\begin{equation}
+\label{eq:efficinv}
+\eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}}
+\end{equation}
+
+Where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be found from the inverter's data-sheet.
+
+Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
+
+The sizing project check of the inverter is done through three Equations.
+Equation \ref{eq:vindc} ensure that the input voltage of the controller meet the voltage of the system.
+Equation \ref{eq:voutac} ensures that the output voltage of the controller meet the AC voltage of the load.
+Moreover, Equation \ref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
+
+\begin{equation}
+\label{eq:vindc} 
+V_{in}DC = V_{system}
+\end{equation}
+
+\begin{equation}
+\label{eq:voutac} 
+V_{out}AC = V_{AC}
+\end{equation}
+
+\begin{equation}
+\label{eq:invcheck} 
+\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right] 
+\end{equation}
+
+\subsection{Automated Verification }
+It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.
+
+If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, resulting in a process known as formal verification.
+Verification may form part of a validation process, but in general, validation cannot be formalized because it relates a system design to intent.
+
+Simulation may also be used for validation, but it is more problematic for verification.
+In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
+
+Testing can also be used for validation, but for the same reasons, it too is problematic for verification.
+
+According \cite{Clarke2008}, verification procedure is an intelligent exhaustive search of the state space of the design.
+In addition, according to \cite{Forejt2011}, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system.
+One successful method in this domain is model checking.
+
+Model checking is an automatic verification technique, as defined by \cite{Clarke2008}.
+Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
+
+The process of model checking can be divided in three components: modeling, specification, and verification method.
+
+\begin{itemize}
+\item In modeling, a model (normally mathematical) of the system is created; 
+\item In specification, normally a list of properties to be satisfied by the system is stablished, i.e., the requirements, as reliability to performance for example.
+\item Normally is expressed in temporal logic form ($CTL$);
+\item The model checking is the verification method itself. 
+\end{itemize}
+
+The model checking algorithm can be described as:
+
+\begin{itemize}
+\item Given the model $ 'M' $ and a $CTL$ formula $ \phi $ as input;  
+\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
+\item It returns $YES$ if $ \phi $ is $TRUE$, or returns $NO$ if $ \phi $ is $FALSE$.
+
+\end{itemize}
+Specifically at the $FALSE$ situation, the algorithm returns a counterexample that is useful as diagnostic of the system, in order to discover in which situation the model is violated.
+\cite{Clarke2008} consider that the most important advantage of the use of model checking.
+
+Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
+However, there is a main disadvantage of model checking: the state explosion problem.
+
+The model checking problem can be defined as shown in \cite{Clarke2008}:
+
+\begin{itemize}
+\item Let $M$ be a Kripke structure (i.e., state transition graph);
+\item $f$ be the specification in temporal logic (a formula);
+\item Find all states $s$ of $M$ such that $M , s \models f$
+\end{itemize}
+
+Fig. \ref{fig:modelcheckstruc} shows the structure of a typical model checking system. A preprocessor extracts a state transition graph from a system (program or circuit).
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{modelcheckstruc}
+\centering
+\caption{Model Checker structure (Source: \cite{Clarke2008})}
+\label{fig:modelcheckstruc}
+\end{figure}
+
+Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study.
+
+The Fig. \ref{fig:systemverif} shows the process to convert a real system to a model in order to be verified by a model checking.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{systemverif}
+\centering
+\caption{From real system verification to model checking (adapted from \cite{Clarke2008})}
+\label{fig:systemverif}
+\end{figure}
+
+In order to solve the problem of state explosion, many different techniques were developed at the last decades. One of the promising is the Bounded Model Checking (BMC).
+
+BMC is a method that checks the model up to a given path in the path length.
+BMC algorithms traverses a finite state machine for a fixed number of steps, , and checks whether violation occurs with this bound.
+It uses fast SAT solvers, where SAT means satisfiability.
+SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression.
+SAT solvers are used in BMC, such that if there are some Boolean function, the solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
+If SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
+
+CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++, as can be seen in \cite{Kroening}.
+
+ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.  
+The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
+
+/////////////// end OLD STUFF

### 2019-07-01 Tex/Old text/chapters/introduction.tex
thesis updated text

@@
 introduction text here kadhew nrjrenasmnfs,mgfs gfsdf gdsf dfsg dsgh bv dzfg df gdf gdf gdf gdf gd fg dfg dfg
+
+Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV).
+Only a niche market a few years ago, PV are now becoming a mainstream electricity provider, changing the way the world is powered.
+Based in data from \cite{EPIA}, there was an increase of approximately 30\% from 2013 to 2014 in terms of new installations of PV.
+The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}.
+The renewable energy leads to an advance all over the world by protecting the environment: it is clean (low greenhouse gases emissions), operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}.
+Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
+The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
+
+In order to validate or even simulate a potential PV solution, there are a myriad of tools.
+However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.
+
+According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
+In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
+SPV systems can be classified into grid-connected and stand-alone systems.
+At this proposal, only off-grid or stand-alone systems will be considered.
+The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
+
+The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy.
+Apart from PV modules; the PV systems consist of battery bank, controller, and inverter, plus the load.
+Moreover, the optimum sizing of these devices is important for reliable operation.
+Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}.
+
+\subsection{Problem's Definition}
+
+In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
+According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
+Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
+
+Manufacturers and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
+
+Changing the subject to the design of complex systems, more time is spent on verification than on construction, as shown in \cite{Baier}.
+Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
+Programs, and more generally computer systems, may be viewed as mathematical objects with behavior that is, in principle, well determined.
+This makes it possible to specify programs using mathematical logic, which constitutes the intended (correct) behavior.
+Then, one can try to give a formal proof or otherwise establish that the program meets its specification, as defined by \cite{Trindade}.
+
+This area of research is referred as formal methods as defined in \cite{Clarkeetal}. Their aim is to establish system correctness with mathematical rigor.
+
+In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of bugs in order to ensure the correctness of the system.
+
+Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner.
+Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
+Algorithms can verify the system model through systematically explore all their states.
+
+\subsection{Objectives}
+Objectives here
+
+\subsection{Contributions}
+Contributions text subsection here
+
+\subsection{Related Work}
+
+\subsection{Thesis Organization}
+Text here

### 2019-07-01 Tex/Old text/main.tex
thesis updated text

@@
 \documentclass[12pt,twoside]{report}
-\usepackage[utf8]{inputenc}
+%\documentclass[12pt,a4paper]{ltxdoc}
+%\documentclass[12pt,a4paper]{article}
+\usepackage{lmodern}			% Usa a fonte Latin Modern			
+\usepackage[T1]{fontenc}		% seleção de códigos de fonte.
+\usepackage[utf8]{inputenc}		% determina a codificação utilizada (conversão automática dos acentos)
+\usepackage{hyperref}  			% controla a formação do índice
+\usepackage{parskip}			% espaçamento entre os parágrafos
+\usepackage{microtype} 			% para melhorias de justificação
+\usepackage{morefloats}			% permite mais floats
+\usepackage{setspace}
+%\singlespacing
+\onehalfspacing
+%\doublespacing
+%\setstretch{1.1}
+
+%\documentclass[10pt,a4paper]{article}
+%\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
 \usepackage{graphicx}
+%Alessandro input: makecell package to permite line break inside tables
+\usepackage{makecell}
+\usepackage[alf]{abntex2cite}	% citacoes
+
+%\documentclass[12pt,twoside]{report}
+%\usepackage[utf8]{inputenc}
+%\usepackage{graphicx}
 \graphicspath{ {images/} }
-\usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{caption}
+%\usepackage{subcaption}
 \usepackage[a4paper,width=150mm,top=25mm,bottom=25mm,bindingoffset=6mm]{geometry}
@@
 \fancyhead{}
-\fancyhead[RO,LE]{Thesis Title}
+\fancyhead[RO,LE]{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
 \fancyfoot{}
@@
 \fancyfoot[LO,CE]{Chapter \thechapter}
-\fancyfoot[CO,RE]{Author Name}
+\fancyfoot[CO,RE]{Alessandro Trindade}
 \renewcommand{\headrulewidth}{0.4pt}
@@
 
-\title{Thesis Title}
+\title{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation}
 \author{Alessandro Trindade}
-\date{Day Month Year}
+\date{31 July 2019}
 
@@
 
-\chapter*{Dedication}
-To mum and dad
-
-\chapter*{Declaration}
-I declare that..
-
+%\chapter*{Dedication}
+%To mum and dad
+%
+%\chapter*{Declaration}
+%I declare that..
+%
 \chapter*{Acknowledgements}
@@
 
-\chapter{Chapter Two Title}
+\chapter{Background}
 \input{chapters/chapter02}
 
-\chapter{Chapter Three Title}
+\chapter{Methodology}
 \input{chapters/chapter03}
 
-\chapter{Chapter Four Title}
+\chapter{Experimental Evaluation}
 \input{chapters/chapter04}
 
-\chapter{Conclusion}
+\chapter{Conclusion and Future Work}
 \input{chapters/conclusion}

### 2019-07-01 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 That configuration is the focus of the present thesis since it is the most common nowadays all over the world, when off-grid or isolated regions is the target.
+\textcolor{red} { Alternative???
+Specifically for remote rural areas of developing countries or places where the grid extension is not feasible,}
+%stand-alone systems are one the most used solutions, and 
+% depending on the type of load, cost, resources availability, and requirements of the load, 
+%stand-alone systems 
+%can be split into several categories. However, 
+the most suitable configuration is the regulated stand-alone system with battery and AC load.
 
@@
 
-/////////////// end OLD STUFF
+///////begin-verification 
+\subsection{Sizing and Simulation of Stand-alone Solar PV systems}
+The sizing and validation of a PV system can be done by hand or with the aid of tools. Here we reference the critical period~\cite{Pinho} as an effective method to stand-alone PV sizing.
+%
+%In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
+%public domain and commercial software available for the PV market. 
+%According to \cite{Brooks}, t
+%%%%%%%%%%The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
+% to complex financial analysis and project optimization. 
+%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
+%
+%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
+
+The most popular softwares are summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
+%\subsection{PVWatts Calculator}
+%According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
+According to \cite{NRELDobos}, to use the calculator, it is necessary to provide information about the system's location, basic design parameters, and system economics.
+PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity monetary value.
+This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules.
+The production estimates that PVWatts computation do not account for many factors that are important in the design of a photovoltaic system, therefore it is necessary support of an energy expert.
+The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year.
+To represent the system's physical characteristics, PVWatts requires values for six inputs: System DC size; Module type; Array type; System losses; Array tilt angle; Array azimuth angle.
+%
+%\subsection{SAM}
+%SAM or System Advisor Model is a software from the U.S.
+Department of Energy and National Renewable Energy Laboratory.
+According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications, and (also) to provide information for readers who do not plan to use the model, but want to learn about its capabilities.
+SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: Project managers and engineers; Financial and policy analysts; Technology developers; and Researchers.
+SAM makes performance predictions and cost of energy estimates for grid-connected power projects based on installation and operating costs and system design parameters that you specify as inputs to the model.
+Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement.
+SAM is an electric power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet electric load.
+It does not model thermal energy systems that meet a thermal process load.
+As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.
+%
+%\subsection{HOMER}
+%As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
+HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources.
+HOMER Legacy is the original HOMER software version created at the National Renewable Energy Laboratory (NREL).
+HOMER Legacy is a free computer model that simplifies the task of evaluating design options for both off-grid and grid-connected power systems for remote, stand-alone, and distributed generation applications.
+HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options.
+Since 2016 HOMER Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available.
+At the short-time only the commercial version will remain.
+%
+%The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
+HOMER Pro put together three tools in one product: optimization, simulation, and sensitivity analysis.
+HOMER Pro provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use.
+It is adaptable to a wide variety of projects.
+For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project.
+For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations.
+Chronological simulation is essential for modeling variable resources, such as solar and wind power and for combined heat and power applications, where the thermal load is variable.
+HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.
+%
+%\subsection{RETScreen}
+%As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
+%
+%RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options.
+The software can be used to evaluate benefits from both clean energy production from power generation projects and savings through energy efficiency projects, accounting for project costs, greenhouse gas emission reductions, and financial risk.
+The software is freely distributed (but with restrictions to save work or print), and had three different versions:
+%
+%\begin{itemize}
+%\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
+%\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
+%\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
+However, this version works is only Windows-based.
+This version has a complete paid version, in an annual subscription way.
+%\end{itemize}
+%
+%As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
+It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
+RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.
+%
+%\subsection{Hybrid2}
+%The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
+Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
+Variations in wind speed and in load within each time step are factored into the performance predictions.
+The code does not consider short-term system fluctuations caused by system dynamics or component transients.
+This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, what is a limitation.
+%
+%Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where 
+As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
+Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
+However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription typically range from US\$504.00 to US\$657.00.
+%
+\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Comparative coverage of reference simulation software}
+\label{table:softwares}
+\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+\begin{tabular}{c | c | c | c | c | c}
+\hline
+\hline
+Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen} & \rotatebox{90}{Hybrid2}\\
+\hline
+\hline
+Support & X & X & X & X &  \\
+\hline
+Off-grid systems &   &   & X & X & X\\
+\hline
+Hybrid systems &  &  & X & X & X\\
+\hline
+Photovoltaics & X & X & X & X & X\\
+\hline
+Batteries &  &  & X &  & X\\
+\hline
+\makecell{Main technical (T) \\ or economical(E)} & T & T & E & E & T \\
+\hline
+Optimization &  &  & X & X &  \\
+\hline
+Sensitive analysis &  &  & X & X & \\
+\hline
+\hline
+\end{tabular}
+\end{table}
+%
+%-------------------------------------------------------------------
+%\subsection{Paper Proposal x Reference Tools}
+%-------------------------------------------------------------------
+%
+In this study, HOMER was chosen to comparative with our proposed verification approach (Section~\ref{sec:results_indeed}).%All tools need some parameters inherently from manufacturer's catalog.
+%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
+%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
+%Thus, the main challenge here is to demonstrate the application of software model checking to formally verify a stand-alone PV solution, thus proving that this approach is more effective and complete than other state-of-the-art tool such as HOMER Pro.
+The comparative evaluation between HOMER Pro and our approach is presented in Section~\ref{sec:results_indeed}.
+%
+%-------------------------------------------------------------------
+\subsection{Component models for a stand-alone PV system }
+%-------------------------------------------------------------------
+%The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
+%The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
+It identifies the PV generator, batteries, charge controller, inverter, and AC load.
+A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
+The PV generator is a semiconductor device that can convert solar energy into DC electricity.
+%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
+For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\cite{Hansen}.
+The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
+The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+%
+%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
+%
+\begin{figure}[h]
+\includegraphics[width=0.80\textwidth]{blockdiagramPVS2}
+\centering
+\caption{Block diagram for a typical stand-alone PV system (adapted from~\cite{Hansen}).}
+\label{fig:blockdiagram}
+\end{figure}
+%
+%In the literature, there are several mathematical models available for each component of PV systems. At the next section, the mathematical model for each component is presented. 
+%-------------------------------------------------------------------
+\subsection{PV System Model}
+\label{sec:PVsystemmodel}
+%-------------------------------------------------------------------
+%A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
+%In the present modeling, the focus is only on cell/module/array.
+%
+%%%%%%The basic element of a PV system is a PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
+%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
+When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}.
+If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
+%%%%%To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
+%%%%%package called panel or module. 
+%For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
+In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}.
+The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{celmodarray}
+%\centering
+%\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
+%\label{fig:celmodarray}
+%\end{figure}
+%
+%%%%%The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on meteorological conditions.
+%the meteorological conditions of the area to be serviced by PV solution. %However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
+%, which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
+The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
+However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
+%
+%These uncertainties lead to either over- or underestimation of energy yield from PV modules.
+An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
+The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
+%
+%Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
+However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage.
+Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
+% 
+%Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
+Mathematical models are required in order to allow the formal specification of the PV system. At this section we will summarize the models adopted at the paper.
+
+\textbf{PV modules}: a wide variety of models exists. % for estimation of its power output  (and $I-V$ or $P-V$ curves). 
+However, the present work will rely on the simplified model of 1-diode, illustrated in Fig.
+\ref{fig:equivckt}.
+This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
+
+%The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
+%is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
+%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
+\begin{figure}[h]
+\includegraphics[width=0.40\textwidth]{equivckt1D}
+\centering
+\caption{1-diode equivalent PV cell/panel circuit model (adapted from~\cite{Cubas}).}
+%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
+\label{fig:equivckt}
+\end{figure}
+
+The Eq.
+\eqref{eq:1diodemodel} relates the output current, $I$, to the output voltage, $V$.
+%This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
+%In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
+\begin{equation}
+\label{eq:1diodemodel}
+I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right], 
+\end{equation}
+
+\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
+$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}\:J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}\:C $).
+
+%\begin{itemize}
+%\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
+%\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
+%\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed; $ N=1 $ in a single cell configuration.
+%	\begin{itemize}
+%	\item $ N=1 $ in a single cell configuration. 	
+%	\end{itemize}	  
+%\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes.
+%	\begin{itemize}
+%	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
+%	\end{itemize}
+%\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
+%	\begin{itemize}
+%	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
+%	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
+%	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
+%	\end{itemize}	 
+%\end{itemize}
+%
+%This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.
+%
+%The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}. 
+%
+%\begin{equation}
+%\label{eq:1d1rmodel}
+%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
+%\end{equation}
+%
+%Where $R_{s}$ is the series resistor.
+%
+%At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
+%
+%The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}. 
+%
+%\begin{equation}
+%\label{eq:1d2rmodel}
+%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
+%\end{equation}
+%
+%Where $R_{sh}$ is the shunt resistor.
+%
+%At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
+%
+%And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}. 
+%
+%\begin{multline}
+%\label{eq:2d2rmodel}
+%I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - \\ %I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
+%\end{multline}
+%
+%This model has six unknown parameters with two exponential terms. 
+%Briefly, both single and double diode models require the knowledge of all unknown parameters, which is usually not provided by manufacturers.
+Nevertheless, the current-voltage equation is a transcendental expression \cite{Jakhrani}.
+%
+%However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel. 
+%
+%For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
+The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
+However, due to implicit nature and nonlinearity of PV cell or module characteristics, it is hard to find out the analytical solution of all unknown parameters, as described by \cite{Hasan}.
+Thus, numerical methods such as Newton-Raphson method or Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}.
+This happens because numerical methods give approximate solution of the nonlinear problems without searching for exact solutions.
+However, numerical methods are time consuming and need long term time series data, which is not available in developing countries.
+\cite{Jakhrani} did a mixed methodology using analytical and numerical steps together.
+\cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation (essays).
+And \cite{Tian} did a mix of analytical and experimental methodology to get the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use experimental technique.
+%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
+%The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
+In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
+ %
+%\subsection{PV Panel Model}
+%With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
+%
+%A single-diode without series and shunt resistances is considered. 
+%%%%%%%Eq.~\eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
+% shown in Fig. \ref{fig:ivcurve}.
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{ivcurve}
+%\centering
+%\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
+%\label{fig:ivcurve}
+%\end{figure}
+%
+%Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
+%\begin{equation}
+%\label{eq:Isc}
+%I_{sc}=I_{ph}\vert_{V=0}
+%\end{equation}
+%
+%\begin{equation}
+%\label{eq:Voc}
+%V_{oc}=\dfrac{aNk_{B}T}{q}ln\left( 1+\dfrac{I_{sc}}{I_{0}} \right) 
+%\end{equation}
+%
+%\begin{equation}
+%\label{eq:exp}
+%exp\left( \dfrac{qV_{oc}}{aNk_{B}T} \right) = \left(1+\dfrac{qV_{m}}{aNk_{B}T} \right) exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) 
+%\end{equation}
+%
+%\begin{equation}
+%\label{eq:Im}
+%I_{m} =I_{ph}-I_{0}\left[ exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) -1 \right] 
+%\end{equation}
+%
+%Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way. 
+%
+%A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}. 
+%These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig.
+\ref{fig:ivcurve}, where the transition is a compromise between both behaviors.
+It is interesting to observe that the maximum power point corresponds to a trade-off condition, where the current is still high enough before it starts decreasing with increasing the output voltage (Fig.
+\ref{fig:ivcurve}).
+%
+%Based on this, the tangent of the I-V curve can be used to evaluate the transition between current- to voltage-source controlled regions; this operation yields Equation \ref{eq:didv}.
+%
+%\begin{equation}
+%\label{eq:didv}
+%\dfrac{dI}{dV}=-\dfrac{qI_{0}}{aNk_{B}T}exp \left( \dfrac{qV}{aNk_{B}T}  \right) 
+%\end{equation}
+%
+%The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell.
+Therefore, the Equation \ref{eq:Vmderiv} is generated.
+%
+%\begin{equation}
+%\label{eq:Vmderiv}
+%V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
+%\end{equation}
+%
+%It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point.
+The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change on $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}.
+Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation \ref{eq:Vmderiv} can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
+%
+%\begin{equation}
+%\label{eq:dIdV_Vm}
+%\dfrac{dI}{dV}\vert_{V_{m}} \cong -\dfrac{0-I_{sc}}{V_{oc}-0}=\dfrac{I_{sc}}{V_{oc}}
+%\end{equation}
+%
+%Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, 
+%
+The voltage and the current at the maximum power point tracking (MPPT), can be described by Eq.
+\eqref{eq:Vmfinal}, and Eq.
+\eqref{eq:Imfinal}~\cite{Saloux}: %, and Eq.
+\eqref{eq:Pm} as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
+\begin{equation}
+\label{eq:Vmfinal}
+V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right). 
+\end{equation}
+
+\begin{equation}
+\label{eq:Imfinal}
+I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right).  
+\end{equation}
+
+%\begin{equation}
+%\label{eq:Pm}
+%P_{m} = V_{m} I_{m}.
+%\end{equation}
+%
+%\begin{multline}
+%\label{eq:Pm}
+%P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
+%\end{multline}
+%
+However, the photo-current delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
+Therefore, Eq.
+~\eqref{eq:Iph} is used to calculate the photo-current as function of irradiance and temperature~\cite{Villalva}:
+\begin{equation}
+\label{eq:Iph}
+I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right], 
+\end{equation}
+
+\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000\:W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}\:C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$); %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions.
+$ I_{ph,ref} $ can be approximated to the reference short-circuit current ($ I_{sc,ref} $)\cite{Villalva}.
+% that is provided by PV manufacturers ($ I_{sc,ref} $).
+%\cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
+%%
+The cell temperature ($ T $) in degree Celsius is described by Eq. \ref{eq:Tcell}~\cite{Ross}:
+\begin{equation}
+\label{eq:Tcell}
+T = T_{air} + \dfrac{NOCT-20}{800}G,
+\end{equation}
+
+\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C), and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
+
+Furthermore, Eq. ~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\cite{Villalva} 
+%In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
+
+\begin{equation}
+\label{eq:I0}
+I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1},
+\end{equation}
+
+\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
+
+%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
+Using the maximum power point current, cf.
+Eq.~\eqref{eq:Imfinal}, and the saturation current in the reference temperature given by Eq.~\eqref{eq:I0}, the diode ideality factor~\cite{Saloux} is determined by Eq.~\eqref{eq:a}:
+\begin{equation}
+\label{eq:a}
+a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) },
+\end{equation}
+
+\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions.
+%, usually provided by manufacturers; t
+
+%The PV generator model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers in data-sheets or manuals.
+%
+%If the PV cells are in parallel, then there is a parallel array.
+Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
+%
+%\begin{equation}
+%\label{eq:Iarray}
+%I_{array} = (N_{cells in parallel})(I_{one cell})
+%\end{equation}
+%
+%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
+%
+%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
+%
+%\begin{equation}
+%\label{eq:Varray}
+%V_{array} = (N_{cells in series})(V_{one panel})
+%\end{equation}
+%
+%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
+%------------------------------------------------------------
+%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system.
+Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery.
+During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.
+
+Related to the \textbf{batteries}, various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Pinho};
+%, and \cite{Manwell93, Manwell94}. 
+%However, regardless of the model, normally the following parameters are required: 
+%
+%\begin{itemize}
+%\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
+%, under predetermined discharge conditions.
+%\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
+%Obviously $ 0<SOC<1 $. 
+%If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
+%\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
+%It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
+%\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
+%\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
+%\end{itemize}
+%
+%The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
+The battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
+LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.
+%
+%In general, the battery models view the battery as a voltage source $ E $ in series with an internal resistance $ R_{0} $, as shown in Fig. \ref{fig:batteryckt}. 
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{batteryckt}
+%\centering
+%\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
+%\label{fig:batteryckt}
+%\end{figure}
+%
+%The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.  
+%
+%Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
+%
+%The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.  
+%
+%The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
+However, it uses some data extracted from tested batteries in laboratory.
+Therefore is not suitable to this study.
+%
+that kind of battery has relative low cost and wide availability~\cite{Copetti}. 
+%
+Here, the model adopted uses only manufacturer's data without empirical tests~\cite{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature. 
+%
+The discharge voltage is described by Eq. \eqref{eq:bat_Vd}.
+%The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
+%
+\begin{multline}
+\label{eq:bat_Vd}
+V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T),
+\end{multline}
+
+\noindent where $C_{10}$ means 10 h of rated capacity (manufacturer's data-sheet), $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $%, $ T_{ref}=25^{o}C $
+), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time.
+%Mathematically, it is the ratio between the present capacity and the nominal capacity% (in $ Ah $, provided by manufacturer)
+%If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
+%\begin{equation}
+%\label{eq:SOCbat}
+%SOC = \left( 1 - \dfrac{Q}{C} \right) 
+%\end{equation}
+%
+%Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
+%
+%The ratio between $ Q $ and $ C $ represents t
+The depth of discharge ($DOD$) or the fraction of discharge, is $DOC=1-SOC$.
+
+%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
+This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
+%
+%\begin{equation}
+%\label{eq:CC10}
+%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
+%\end{equation}
+%
+%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
+For the charging process, the parameters are described by Eq.~\eqref{eq:Vcbat} as
+%
+\begin{multline}
+\label{eq:Vcbat}
+V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
+\end{multline}
+%
+%Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period.
+%; however, during recharge it is much more difficult \cite{Copetti}.
+%Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell.
+The efficiency drops to zero at full charge and the function that represents the charge efficiency ($ \eta_{c} $) variation with state of charge and current rate is given in Equation \ref{eq:efficcharge}.
+%\begin{equation}
+%\label{eq:efficcharge}
+%\eta_{c} = 1 - exp \left[ \dfrac{20.73}{\dfrac{I}{I_{10}}+0.55} (SOC-1) \right] 
+%\end{equation}
+%
+%\cite{Copetti} show that, 
+%During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (\ref{eq:Vec}).
+It was created a function for the gassing voltage as well, as shown in (\ref{eq:Vg}).
+In addition, the overcharge phenomenon can be represented by (\ref{eq:Voverc}).
+%\begin{equation}
+%\label{eq:Vec}
+%V_{ec} = \left[ 2.45 + 2.011 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
+%\end{equation}
+%
+%\begin{equation}
+%\label{eq:Vg}
+%V_{g} = \left[ 2.24 + 1.97 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
+%\end{equation}
+%
+%\begin{multline}
+%\label{eq:Voverc}
+%V_{c} = V_{g} + (V_{ec} - V_{g}) \\ \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
+%\end{multline}
+%
+%Where $ Ah_{restored} $ represents the Ampere-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
+%
+%The function assumes that 95\% of the capacity was already restored at the start of overcharge.
+%
+%The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by (\ref{eq:tau}).
+%\begin{equation}
+%\label{eq:tau}
+%\tau = \dfrac{17.3}{1+852 \left( \dfrac{I}{C_{10}} \right) ^{1.67} }
+%\end{equation}
+%
+%Therefore, to model the voltage ($ V_{c} $) evolution of the battery, (\ref{eq:Vcbat}) can be used up the start of gassing ($ V_{c} \leq V_{g} $).
+And during overcharging ($ V_{c} > V_{g} $), (\ref{eq:Voverc}) can be used until a constant final voltage ($ V_{ec} $) is reached.
+%
+%The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
+%
+%\begin{equation}
+%\label{eq:stor}
+%Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
+%\end{equation}
+%
+%Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
+%
+%As an example of this formula application, as shown by \cite{Abdulateef}, considering that a stand-alone PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
+%
+%Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$.
+Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$).
+If a single battery of 12 V and 350 Ah is considered, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
+%
+%At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature.
+The equations are used to update the $SOC$ of the batteries, and have the number of hours ($ Num_{h} $) as a variable.
+There is a factor (1.15) which is present at the charging equation, and is necessary to express that during the charging process is usual to reach 115\% of the battery capacity
+%
+%\begin{multline}
+%\label{eq:charge}
+%SOC_{charge} = SOC_{previous} + \\ \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
+%\end{multline}
+%
+%\begin{multline}
+%\label{eq:discharge}
+%SOC_{discharge} = SOC_{previous} - \\ \dfrac{100*I_{drained}*Num_{h}}{capacity}
+%\end{multline}
+%
+%
+%---------------------------------------------------------
+%---------------------------------------------------------
+%Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
+However, in this study, in order to simplify, the term used is controller.
+
+The \textbf{charge controller} or controller is the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+Controllers with MPPT mechanism are the mostly used nowadays,  and it maintains the PV operating at the stage of maximum power.
+%Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
+%
+%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
+%
+%
+%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components.
+The use of battery as a storage form implies thus the presence of a charge controller.
+%
+%%%%%%%%%%In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
+%
+%The controller allows the management of energy between the load and the battery \cite{Mellit}. 
+%The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
+The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
+
+The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.
+To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \_ off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}.
+PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \_ on} $.
+%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{controllerover}
+%\centering
+%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
+%\label{fig:controllerover}
+%\end{figure}
+%
+In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \_ off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}.
+The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \_ on}$.
+%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.4\textwidth]{controllerdisc}
+%\centering
+%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
+%\label{fig:controllerdisc}
+%\end{figure}
+%
+%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
+%
+\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Summary of the controller process (adapted from~\cite{Hansen})}
+\label{table:controller}
+\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+\begin{tabular}{c | c | c }
+\hline
+\hline
+Step  & Constraint & Command\\
+\hline
+\hline
+(1) & \makecell{If $V > V_{max \_ off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
+\hline
+(2) & \makecell{If command (1) is \\done and $V < V_{max \_ on}$} & \makecell{Reconnect PV array \\to the system}\\
+\hline
+(3) & \makecell{If $V < V_{min \_ off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
+\hline
+(4) & \makecell{If command (3) is \\ done and $V > V_{min \_ on}$} & \makecell{Reconnect the load \\to the system}\\
+\hline
+\hline
+\end{tabular}
+\end{table}
+
+%Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage. 
+%
+%As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
+The output power ($ P_{out} $) of controller is given by Eq. \eqref{eq:poutcont}.
+\begin{equation}
+\label{eq:poutcont}
+P_{in} \eta_{c} = P_{out}.
+\end{equation}
+
+Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Eq. \eqref{eq:poutcont} we compute Eq. \eqref{eq:potcont}.
+\begin{equation}
+\label{eq:potcont}
+V_{in} I_{in} \eta_{c} = V_{out} I_{out},
+\end{equation}
+
+\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
+
+%The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}). 
+% 
+%A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
+In addition, there is the Cuk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.
+%
+%For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.
+%
+%\begin{equation}
+%\label{eq:voutvin}
+%\dfrac{V_{out}}{V_{in}} = \dfrac{D}{D-1}
+%\end{equation}
+%
+%Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
+% 
+%The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
+%  
+%Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.
+% 
+%As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
+
+%The number of controllers required for the stand-alone PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
+In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
+%\begin{multline}
+%\label{eq:numberofcmin}
+%number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \\ \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
+%\end{multline}
+%
+%\begin{equation}
+%\label{eq:numberofc}
+%N_{controller} \geq number_{controllers}
+%\end{equation}
+%
+%\subsection{Joint work: charge controller and batteries}
+%When batteries are charged, they go through three main different states - bulk, absorption and float, with impact to the inverter and to power supplied to the house.
+%, and it is necessary to understand those three states in order to comprehend the joint work of the controller with the battery. With impact to the inverter and to power supplied to the house. 
+%
+%All the explanation at this section is related to $SOC$ and to the voltage at the DC-bus (controller output, which will be bigger than $V_{system}$) where the batteries are connected, all ruled by the charge controller.
+Moreover, it is important to mention that smart chargers, the most usual nowadays, will detect voltage and resistance from the battery prior to charging.
+%
+%Bulk - is the first stage of charging. Bulk begins when the sun comes out.
+%, or other source of electrical generation is turned on. 
+%This stage occurs when the batteries are at a lower $SOC$, generally anything not smaller than $75\%$ to $80\%$ (defined during system sizing).
+This stage is typically where the highest voltage and current the charger is rated for will actually be used.
+The bulk stage basically allows the PV panel to put as much current into the batteries as possible.
+For a typical 12 V battery, the charging voltage going into a battery will reach 14.16 V to 14.40 V at this stage, and there is no risk of overcharging in this stage because the battery hasn't even reached full yet.
+%
+%Absorption - once the batteries reach the programmed absorb voltage, usually somewhere between 14.16 and 14.40 V, the batteries will go into the absorption stage.
+Typically, when a battery reaches this stage its $SOC$ is around $85-95\%$.
+During this stage, the batteries are kept at the programmed voltage, and the current going into the batteries reduces as the batteries become more full.
+The absorption stage ends after the programmed time is reached or the number of Ampere going into the battery falls below a preset number.
+The lower current going into the battery safely brings up the charge on the battery without overheating it.
+%Usually, this stage takes more time than the bulk stage.
+%
+%Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage that a 12 V battery can hold, and begin the float stage.
+The float stage brings the battery all the way through and maintains $SOC$ at $100\%$.
+The current will also decrease to a point where it's considered just a pulse.
+It's essentially the float stage where there is charge going into the battery at all times, but only at a safe rate to ensure a full state of charge and nothing more.
+%Most smart chargers do not turn off at this point, however it is completely safe to leave a battery in float mode for months to even years at a time.
+%
+%Battery charging technology relies on smart micro-controlled devices.
+Therefore it is extremely important that the program settings for the charge controller or inverter/charger are correct, and the list includes the bulk and absorption values.
+%This will help preserve and extend the battery life.
+There are always default settings to the equipment, set by software, however those settings are not $100\%$ correct because there are difference among models of equipment and among manufacturer's.
+The ideal is to read the data-sheet from the manufacturers and perform a manual adjust.
+%
+%There are the possibility to combine batteries in a bank, with parallel and series connections, all depending the sizing of the project:
+%
+%\begin{itemize}
+%\item Batteries connected in parallel are seen by the controller as one large battery of the combined Ah capacity of all the batteries.
+For example, two 12 V and 220 Ah batteries in parallel are seen as one 12 V and 440 Ah battery;
+%\item In the other hand, although the batteries connected in series are also seen as a single battery, the result is different: two 12 V and 220 Ah batteries in series are seen as one 24 V and 220 Ah battery;
+%\item In addition, a mixed bank arrangement can be useful: a bank with two 12 V and 220 Ah batteries in series connected in parallel with a similar arrange will produce an equivalent battery of 24 V and 440 Ah.
+%\end{itemize}
+%-----------------------------------------------
+%-----------------------------------------------
+%As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. 
+%An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
+The role of the \textbf{inverter} is to keep the voltage constant on the AC side, %, i.e., at the rated voltage, % (127 V or 220 V, for example), 
+and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by \eqref{eq:efficinv} \cite{Hansen}:
+%
+%The inverter is characterized by a power dependent efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
+\begin{equation}
+\label{eq:efficinv}
+\eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}},
+\end{equation}
+
+\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be obtained from the inverter's manual.
+
+%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
+%
+%
+%--------------------------------------------------
+\subsection{Availability of Stand-alone PV Systems}
+\label{sec:availability}
+%--------------------------------------------------
+%Each stand-alone PV system, like any other power systems, has a specific level of availability.
+This reliability level impacts various issues, as system performance, production, feasibility, and investment.
+The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
+The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
+The system availability definition depends on how critical the load application is.
+For critical loads, 99\% is considered acceptable.
+While in a ordinary house electrical load, 95\% is considered acceptable.
+%As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system.
+An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
+%
+%With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong.
+It is important to evaluate how critical the load application is and the horizon of evaluation.
+However this analysis can be useful, for example, to improve the sized battery autonomy.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Automated Verification Using Model Checking}
+\label{sec:AutomatedVerification}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}.
+Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
+Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t.
+user requirements.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{CBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
+CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
+If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
+CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{ESBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{CPAchecker}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Automatic program verification requires a choice between precision and efficiency.
+%The more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs.
+Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
+In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
+The CPA formalism provides an interface for the definition of program analyses.
+Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
+The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
+Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
+%Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+%CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
+For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
+\textcolor{red}{It is unclear what a CPA is.}
+%In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
+
+//////Begin optimization
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Automated Verification Using Model Checking}
+\label{sec:AutomatedVerification}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Although simulation and testing explore possible behaviors and scenarios of a given system, 
+they leave open the question of whether unexplored trajectories may contain a flaw. 
+Formal verification conducts an exhaustive exploration of all possible behaviors; 
+when a design is said to be ``correct'' by a formal verification method, it implies that all 
+behaviors have been explored, and questions regarding adequate coverage or missed behavior 
+becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
+applies mathematical reasoning to obtain guarantees about the correctness of a system; 
+one successful method in this domain is model checking~\cite{Clarke2012}. 
+Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{CBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The C Bounded Model Checker (CBMC) falsifies assertions in C programs 
+or proves that they are safe if a completeness threshold is given~\cite{Kroening}. 
+CBMC implements a bit-precise translation of a C program, annotated with assertions 
+and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, 
+then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification 
+flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; 
+it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, 
+into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
+(ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
+which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
+(iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{ESBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{CPAchecker}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Automatic program verification requires a choice between precision and efficiency. 
+The more precise a method, the fewer false positives it will produce, but also the 
+more expensive it is, and thus applicable to fewer programs. 
+Historically, this trade-off was reflected in two major approaches to static verification: 
+program analysis and model checking. In order to experiment with the trade-off, 
+and in order to be able to set the dial between the two extreme points, 
+Configurable Program Analysis (CPA) provides a conceptual basis for expressing 
+different verification approaches in the same formal setting. The CPA formalism 
+provides an interface for the definition of program analyses. Consequently, CPAchecker 
+provides an implementation framework that allows the seamless integration of program 
+analyses that are expressed in the CPA framework. The comparison among different 
+approaches in the same experimental setting is intended to be easy and the experimental 
+results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, 
+the central data structure is a set of control-flow automata (CFA), which consists of control-flow 
+locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and 
+interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
+and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+
+%-----------------------------------------------------------
+\subsection{Program Synthesis}
+\label{sec:ProgramSynthesis}
+%-----------------------------------------------------------
+
+The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
+In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
+As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
+CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
+	\caption{CEGIS applied to PV system sizing.}
+	\label{Counter-Example-Guided-Inductive-Synthesis}
+\end{figure}
+
+The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .
+\forall \vec{x}.
+\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
+The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
+Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
+Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
+If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
+
+One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
+
+However, in our variant CEGIS method proposed here, there are four particular differences related to the traditional CEGIS: 
+(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
+(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
+(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
+a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard 
+a given candidate that could be feasible in the next iteration with a new lower bound.
+
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Sizing Stand-alone Solar PV Systems}
+\label{sec:sizing}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
+The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.  
+For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage 
+form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system 
+contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior 
+of AC electrical load from the house that will be fed by the system.
+%
+\begin{figure}[h]
+\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
+\centering
+\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
+\label{fig:blockdiagram} 
+\end{figure}
+
+The sizing check stage will ensure that the system meets the standard project steps related 
+to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller,
+which is the most common one in practice. Firstly, we need to correct the energy consumption estimated to the load 
+($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
+controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+%
+\begin{equation}
+\label{eq:Ecorrected}
+E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
+\end{equation}
+
+We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
+%
+\begin{equation}
+\label{eq:Ep}
+E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
+\end{equation}
+
+\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
+the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
+The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
+%
+\begin{equation}
+\label{eq:NTPmin}
+N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
+\end{equation}
+
+Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
+%
+\begin{equation}
+\label{eq:NPSmin}
+\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
+\end{equation}
+%
+\begin{equation}
+\label{eq:NPPmin}
+N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
+\end{equation}
+%
+\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ 
+is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and 
+$V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering 
+the maximum and minimum operational temperature, respectively; 
+$P_{total}$ is the total power demanded from the PV system and 
+$P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
+Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
+%
+\begin{equation}
+\label{eq:Cbank}
+C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
+\end{equation}
+
+\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; 
+$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
+%
+Secondly, the total (minimum) number of batteries is computed as
+
+\begin{equation}
+\label{eq:Nbtotal}
+N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
+\end{equation}
+
+Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
+\begin{equation}
+\label{eq:vcvsystem}
+V_{c} = V_{system}.
+\end{equation}
+
+The short circuit reference information from the manufacturer's solar panel must be corrected 
+to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, 
+and PV system is temperature dependent, as 
+%
+\begin{equation}
+\label{eq:iscamb}
+I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
+\end{equation}
+
+The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin} as
+%
+\begin{equation}
+\label{eq:icmin}
+I_{c,min} = I_{sc,amb} \times N_{PP},
+\end{equation}
+%
+\begin{equation}
+\label{eq:icicmin}
+I_{c} \geq I_{c,min}.
+\end{equation}
+
+The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that 
+the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the 
+output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that 
+the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), 
+where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; 
+$MAX_{AC,ref}$ is the peak power that the inverter can support.
+%
+\begin{equation}
+\label{eq:vindc} 
+V_{in}DC = V_{system}.
+\end{equation}
+%
+\begin{equation}
+\label{eq:voutac} 
+V_{out}AC = V_{AC}.
+\end{equation}
+%
+\begin{equation}
+\label{eq:invcheck} 
+\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{PV systems Optimization Criteria}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to select an optimal combination to meet sizing constraints, 
+it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives.
+
+During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
+The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
+A reliable power is a generation system that has sufficient power to feed load demand in a period.
+
+There exist different methods to express system reliability, where the most popular ones 
+are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
+In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
+
+LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
+On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
+On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
+The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance.
+However, data is not always available and dynamic analysis is complex; and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
+
+Related to economic analysis, there exist various methods available.
+The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
+The common methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
+
+The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
+The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
+IRR is used to evaluate the attractiveness of a project or investment.
+
+LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
+LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
+
+LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
+Eq.~\eqref{eq:LCC} is used to calculate LCC of a PV system,
+%
+\begin{equation}
+\label{eq:LCC}
+LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
+\end{equation}
+\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs
+in present worth.
+
+%----------------------------------------------------------------------------------------------
+\subsection{Stand-alone PV System Optimization Technique}
+%----------------------------------------------------------------------------------------------
+
+In order to recommend an optimal configuration for PV systems, 
+the designer has to evaluate the design based on optimization variables. 
+As the number of optimization variables increases, the computational effort 
+will increase as well. Hence, to obtain the best PV system design as well as 
+simplified sizing process, prior work introduced three main techniques 
+for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
+
+Intuitive method is simple, easy to be implemented, and can be used to give 
+rough suggestion for preliminary design. The sizing rules are based on designer's experience, 
+using lowest performance either in a time period data or by directly using average value 
+(daily, monthly, or annual) of solar irradiance. This method does not consider the battery's 
+state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
+
+For numerical method, the design is simulated for each time step within a period. 
+State of charge of batteries is calculated and investigated. It is very accurate, 
+however is complex, demanding more time for calculation~\cite{Park2004}.
+
+Analytical methods is used to obtain a close relation or correlation in a form 
+of equation between capacities and reliabilities. The sizing task becomes much simpler 
+than numerical technique; however, the relation cannot be applied to different sites
+since it is specific to one place of deployment of the PV system, 
+thereby demanding adaptation if another site is analyzed.

### 2019-07-01 Tex/Old text/chapters/chapter03.tex
thesis updated text

@@
-chapter03 here amamas asd asd as das das d af dsgf dfg  tre tre t ret ret er ter te rt ert ert er tre t
+The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
+
+\begin{figure}[h]
+\includegraphics[width=0.6\textwidth]{flowchart_verification5.png}
+\centering
+\caption{Flowchart of the proposed automated verification of PV systems.}
+\label{fig:flowchartgeneral}
+\end{figure}
+
+In Step 1, the PV input data %(e.g., load power demand and load energy consumption) 
+and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
+In Step 2, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
+This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.
+%
+In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
+%As a consequence, all the formulae of the employed mathematical models will also be updated. 
+In addition, depending on one of the desired properties of the system such as battery autonomy, energy availability, or even system power supply, our verification engine is able to indicate a failure if those properties are not met; in this particular case, it provides a diagnostic counterexample that shows in which conditions the property violation occurred.
+%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
+% (as reliability, performance, or safety)
+
+%
+%\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above.
+For example, what does a failure mean?
+is it SAT?}
+In a nutshell, the model checker will process the ANSI-C code with constraints %($C$) 
+and properties %($P$) 
+from the PV system, and the tool will automatically verify if the PV system requirements are met.
+If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
+However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
+%, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
+%
+%
+%---------------------------------------------------------------------
+% \subsection{The case studies and the Algorithm}
+%---------------------------------------------------------------------
+%
+% 
+%and as backup at night 
+%
+%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
+%
+%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
+%
+%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).
+
+Algorithm~\ref{alg:verification-algorithm} describes the equivalent pseudo-code.
+%Line 1 indicates a function call that performs the size checking of the each component of the PV system.
+%: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
+%The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation of sizing check.
+The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints a counterexample indicating a property violation.
+If there is no property violation, then the verification algorithm continues and
+In order to reduce the computational effort of the algorithm,
+% caused by the state explosion inherent of the technique, 
+every 24 h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation), when the batteries are demanded to feed the house.
+
+Lines 1 is devoted to information from the location where the PV system will be/were deployed.
+We use annual average minimum and maximum, related to temperature ($T$) and solar irradiance ($G$), hour by hour, from~\cite{Temperature}, and ~\cite{Irradiance}.
+
+Line 2 represents all the information that comes from the PV sizing and from the equipment manufacturers data: specification and data from PV, batteries, inverter and charge controller.
+This item includes as information from the house's load curve.
+
+The first automated verification is related to the sizing check (line 3), if an error is found then the algorithm stops.
+Then two functions, called at lines 4 and 5, are responsible for discover which hour starts the PV generation and when stops.
+Those functions get this information from the array inputted to the Algorithm with the solar irradiance values.
+
+The batteries are assumed to be charged, i.e., with SOC of 100\% (line 6).
+
+The first for-loop at line 7 controls how many cycles of 24 h will be performed by the Algorithm.
+And the for-loop from lines 8 to 11 is responsible to discharge the battery (according the load curve) and verify the state of charge of the battery, hour-by-hour, starting at the first hour of the day after the sun goes down until the next day before the sun goes up (without PV generation).
+Following, at the next for-loop, from line 12 to 29, is performed the verification where there is solar irradiance and all the PV system works.
+The Algorithm generates information related to average temperature ($T$) and solar irradiance ($G$), hour-by-hour, using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range (lines 15 and 16).
+%and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
+%there is PV generation only between 8:00 h and 16:00 h every day, 
+%with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day.
+
+After that, the model from PV generator is used in the function call of line 17, to produce the voltage and current considering the states of $G$ and $T$.
+With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller work, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+
+At the end of last for-loop, the state of the batteries is verified again (line 27) and the hour is adjusted to the next loop (line 28).
+
+Nevertheless, if the verification engine does not fail, we can conclude that the PV system does not need further corrections up to the given bound $k$.
+%
+%\textcolor{red}{this sentence is unclear...
+After this process is started the battery autonomy verification, from line 31}.
+\textcolor{red}{this sentence is unclear...
+Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.} \textcolor{red}{what do you mean by The formal verification is guaranteed?...
+The formal verification is guaranteed by  macro to specific variables of the model, according lines 27 and 35.}
+% and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
+%Within this 8h-period, $G$ and $T$ are automated verified with different values every one hour.
+%, and change their value every 1 h according with the algorithm created using the technique.
+ \begin{algorithm}
+ \caption{Model checking algorithm for stand-alone PV}
+ \begin{algorithmic}[1]
+ \begin{scriptsize}
+ \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+ \renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\
+  \STATE $declare \, case \, studies \, details: \, sizing \, and \, manufacturers \, data $ \\
+  \STATE $sizing \_ check()$ \\
+  \STATE $startPVgeneration \leftarrow findStartPVgeneration()$ \\
+  \STATE $endPVgeneration \leftarrow findEndPVgeneration()$ \\
+  \STATE $SOC \leftarrow 100\%$ \\
+%  \COMMENT {Starting with the PV generation time}
+% \\ 
+%\textit{LOOP Process}
+ \FOR {$1st \, 24h \, loop$ to $Nth \, 24h \, loop$}
+  \FOR {$endPVgeneration+1$ to $startPVgeneration-1$}
+	  \STATE $dischargeBattery \, in \, 1h()$ \\
+%	  \STATE $autonomyCount \leftarrow autonomyCount+1$ \\
+	  \STATE $assert (SOC \geq SOC \_ min)$ \\
+%	  \STATE $battery \, autonomy \, verification()$ \\
+  \ENDFOR
+  \FOR {$startPVgeneration$ to $endPVgeneration$}
+    \STATE $G \leftarrow nondet \_ uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
+    \STATE $T \leftarrow nondet \_ uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
+    \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting $G$ values}
+    \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting $T$ values}
+    \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ \\
+    \COMMENT {If-then-else sequence to imitate charge controller work}
+    \IF {($battery \, is \, empty$) AND ($PV \, is \, generating$)}
+      \STATE $chargeBattery \, in \, 1h()$ \COMMENT {PV feed the house}
+    \ELSIF {($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
+      \STATE FAIL with assert macro \COMMENT {Battery is empty and there is not PV generation}
+    \ELSIF {NOT($battery \, is \, empty$) AND ($PV \, is \, generating$)}
+      \STATE stop battery charge \COMMENT {PV feed the house}
+    \ELSIF {NOT($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
+      \STATE $dischargeBattery \, in \, 1h()$ \COMMENT {Battery feed the house}
+    \ENDIF
+    \STATE $assert (SOC \geq SOC \_ min)$ \\
+    \STATE $hour \leftarrow hour+1$ \\
+   \ENDFOR
+  \ENDFOR
+ \RETURN $(\,)$ 
+  \end{scriptsize}
+ \end{algorithmic} 
+ \label{alg:verification-algorithm}
+ \end{algorithm}
+
+ /////////////
+ Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
+It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
+%
+ \begin{algorithm}
+ \caption{Synthesis algorithm}
+ \begin{algorithmic}[1]
+ \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+ \renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \STATE Initialize variables \\
+  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
+%  \STATE Declare list of controllers data and cost \\
+%  \STATE Declare list of batteries data and cost \\
+%  \STATE Declare list of inverters data and cost \\
+  \STATE Declare the maximum possible cost $MaxCost$  \\
+  \STATE Declare power demand, power peak, energy consumption \\
+  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
+  \FOR {$HintCost=0$ to $MaxCost$}
+ 	\STATE Declare non-deterministic variable to select PV Panel from list \\
+ 	\STATE Declare non-deterministic variable to select Controller from list \\
+ 	\STATE Declare non-deterministic variable to select Battery from list \\
+ 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
+ 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
+	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
+ 	\STATE Calculate $C_{bank}$ \\
+	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
+	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
+ 	\STATE Calculate $I_{sc,amb}$ \\
+ 	\STATE Calculate $I_{c,min}$ \\
+ 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
+	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
+	\STATE non-deterministic variables hold feasible equipment and cost  \\
+	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
+	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
+  \ENDFOR
+ \RETURN $(\,)$ 
+ \end{algorithmic} 
+ \label{alg:opt-algorithm}
+ \end{algorithm}
+%
+
+Our synthesis algorithm will synthesize constant values; 
+it starts with the input of manufacturers data and prices of PV panels, batteries, 
+charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
+house requirements and design definitions, from lines $4$ and $5$.
+
+The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. 
+In particular, it starts with cost $0$ and stops only when the algorithm finds a 
+feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
+if that happens, then our algorithm has found an optimal solution, thereby stating 
+that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
+The $MaxCost$ value at line $6$ is just a very high value put as a limit 
+to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
+
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
+from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
+That procedure ensures that our synthesis engine checks all combinations of items 
+from each equipment, and combine them to assemble a feasible (candidate) PV solution, 
+which meets the user requirements.
+
+Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, 
+Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
+Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} t
+o calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
+ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
+uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$. 
+Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
+and the cost of that solution is calculated in $F_{obj}$ (line $21$).
+
+If our algorithm does not find a feasible solution among the item of equipment that 
+were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
+the program finishes and does not find a solution, which indicates that it 
+was not possible to combine the items of each equipment in order to create a feasible solution.
+
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
+solution regarding the constraints and user requirements. Related to our {\sc Verify} 
+phase the challenge is to find the lowest acquisition cost from a list of equipment and 
+components that is provided from the {\sc Synthesize} phase.
+
+Note that the process described here in completely automated and that a validation is performed 
+by our {\sc Verify} phase to ensure that the approach is sound.

### 2019-07-01 Tex/Old text/chapters/conclusion.tex
thesis updated text

--- 2019-05-08 Tex/elsevier/trindade_solar_energy_rev0.tex
@@
-\documentclass[review]{elsarticle}
-
-\usepackage{lineno,hyperref}
-\modulolinenumbers[1]
-\linenumbers
-
-%\journal{Renewable \& Sustainable Energy Reviews}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-%\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%packages to makecell, algorithm, not inclueded with Elsevier
-\usepackage{makecell}
-\usepackage{algorithm,algorithmic}
-%\algsetup{linenosize=\small}
-\graphicspath{ {./images/} }
-\usepackage{amsmath}
-\usepackage{xcolor}
-
-\begin{document}
-
-\begin{frontmatter}
-
-%\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
-\title{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}
-%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
-
-%% Group authors per affiliation:
-%\author{Alessandro Trindade\fnref{myfootnote}, Lucas Cordeiro}
-%\address{Radarweg 29, Amsterdam}
-
-%% or include affiliations in footnotes:
-\author[mymainaddress]{Alessandro Trindade\corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Corresponding author}
-\ead{alessandrotrindade@ufam.edu.br}
-%\ead[url]{www.elsevier.com}
-
-\author[mysecondaryaddress]{Lucas Cordeiro}
-
-\address[mymainaddress]{Federal University of Amazonas, Av. Rodrigo Octávio, 6200, Coroado I, 69077-000 Manaus-AM-Brazil}
-\address[mysecondaryaddress]{University of Manchester, School of Computer Science, Kilburn Building, Manchester M13 9PL}
-
-\begin{abstract}
-With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
-In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals.
-Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
-Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-Automated verification using model checking has proven to be an effective technique to validate any kind of system.
-This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Different verification tools were evaluated as well, in order to compare performance and soundness.
-Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
-\end{abstract}
-
-\begin{keyword}
-Formal verification \sep model checking \sep photovoltaic power systems
-%\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
-%\MSC[2010] 00-01\sep  99-00
-\end{keyword}
-
-\end{frontmatter}
-
-\section{Introduction}
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\citep{Hussein2012}.
-There is a close relationship between the lack of energy and the low HDI (Human Development Index)~\citep{Coelho}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\citep{IEAweo2018}.
-%The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
-Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
-%Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
-
-In order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\citep{IEAweo2018}.
-
-%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
-%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
-%
-%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
-Only a niche market a few years ago, solar PV systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\citep{EPIA}.
-%However, this growth is not driven by stand-alone systems.
-
-In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \citep{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \citep{Gow1999,Benatiallah2017}.
-%
-%However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
-%
-%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
-In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
-SPV...
-%
-%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
-Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-%
-%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
-%
-%PV systems can be classified into grid-connected and stand-alone systems.
-At this proposal, only off-grid or stand-alone systems will be considered.
-The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-However, those tools are based on running experiments in simulation models.
-Simulation has the advantage of being cheap (if compared to test in real systems) %and can be employed before the system design is concluded
-but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\citep{ClarkeHV18}.
-
-Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\citep{ClarkeHV18}.  
-%with behavior that is, in principle, well determined. 
-Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
-%User or project requirements can be added during the creation of the formal model to be verified.
-%, as defined by \cite{Trindade}.
-%
-%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
-% Their aim is to establish system correctness with mathematical rigor. 
-%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
-% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
-%
-%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
-%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
-%Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
-%
-%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
-%
-In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used.
-%The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
-The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are inputted to the proposed tool and automatically verified during the formal process.
-The model checking tool reports in which conditions a system does not meet the user requirements.
-A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\citep{Akram2018}.
-%Those programs are viewed as mathematical objects, and the use of 
-%Bringing this technique to solar PV systems, i
-%Instead of finding a bug or a software inconsistence, t
-%Here it will be verified a stand-alone PV system, with all their components modeled mathematically,   
-%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the proposed tool is carried out by means of an algorithm in language C, that is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\citep{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\citep{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
-%three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
-%, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
-
-In prior studies, the evaluation of PV systems w.r.t.
-user requirements were performed by simulation tools using MATLAB/Simulink~\citep{Benatiallah2017, Natsheh2012}, or HOMER Pro \citep{Lamnadi2017}, where some mathematical model was adopted and the tool simulated the PV behavior over the time.
-Related to formal methods, in 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\citep{Sengupta2015}.
-The authors proposed an automated simulation-based verification technique to verify correctness of protection settings using hybrid automata-temporal-logic framework.
-In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared-smart infrastructure~\citep{Abate2017}.
-The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings and smart grids.
-The author used approximate model checking of stochastic and hybrid models.
-In 2018, a verification methodology was proposed with applications to PV panels and its distributed power point tracking~\citep{Driouich2018}.
-This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica had evident time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
-Another work from 2018 was the approach to modeling smart grid components using a formal specification.
-The authors used a state-based formal specification language named Z; they demonstrated the application to four smart grid components~\citep{Akram2018}.
-This approach is based on Petri nets.
-%%%%%%%%%%%%%
-%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
-%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
-
-This paper makes two main contributions.
-% Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
-Secondly
-Firstly, we propose an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system.
-Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies.
-%Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation.
-
-%\textcolor{red}{This introduction is missing the description of the vision, approach and results.
-In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
-%
-%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
-\textit{Outline}.
-Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
-Section~\ref{sec:AutomatedVerification} presents the automated verification technique.
-The methodology is presented in section~\ref{sec:Methodology}.
-Section~\ref{sec:results} is devoted to the results.
-Section~\ref{sec:Conclusions} presents the conclusion and describes future work.
-%
-%--------------------------------------------------------
-\section{Solar Photovoltaic System }
-\label{sec:SolarPhotovoltaicSystem}
-%--------------------------------------------------------
-%
-%According to \cite{Roy}, a 
-%A PV system is designed to give the electric supply to a load.
-This load can be either Alternate Current (AC) or Direct Current (DC) type.
-Electric supply can be needed either in daytime or evening time.
-%(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
-%For night hours or rainy days, one needs to hold batteries, where power can be stored and used.% \cite{Gules}. 
-%
-PV systems are classified into distinct types~\citep{Mohanty}.
-%: (1) stand-alone systems, where the energy is generated and consumed in the same place and which do not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system.
-%, where another source(s) of energy can work together with the solar PV.
-% system to provide the required demand.
-%, such as wind, biomass or diesel, 
-%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
-%
-%\begin{itemize}
-%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
-Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants;
-%\item Grid-connected systems, where the solar PV system is connected to the grid.
-The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards.
-Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode;
-%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
-In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
-%\end{itemize}
-Specifically for remote rural areas of developing countries or places where the grid extension is not feasible, 
-%stand-alone systems are one the most used solutions, and 
-% depending on the type of load, cost, resources availability, and requirements of the load, 
-%stand-alone systems 
-%can be split into several categories. However, 
-the most suitable configuration is the regulated stand-alone system with battery and AC load. %; this configuration is the focus of this study.
-%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
-%PV array, battery, MPPT and AC load.
-Battery is used to store the extra power of PV system.
-A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
-Extra charging and deep discharging can reduce the battery life \cite{Kim}.
-Because of the AC load, an inverter (DC to AC converter) is required.
-%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
-%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.
-
-%\subsection{Unregulated stand-alone PV system with DC load }
-%Usually this type of system is for low power applications, as defined by \cite{Roy}.
-The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:standaloneSPV} letter (a).
-At night hours, the system will not provide any supply because of the absence of the battery.
-
-%\begin{figure}[h]
-%\includegraphics[width=0.5\textwidth]{reg_unreg4.png}
-%\centering
-%\caption{PV stand-alone systems: (a) regulated stand-alone SPV system with DC load; (b) regulated stand-alone SPV system with DC load; (c) regulated stand-alone SPV system with battery DC load; and (d) regulated stand-alone system with battery and AC load  (Source: \cite{Roy}).}
-%\label{fig:standaloneSPV}
-%\end{figure}
-
-%\subsection{Regulated stand-alone PV system with DC load}
-%It is similar to unregulated stand-alone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:standaloneSPV} letter (b).
-Usually system with MPPT should have battery; otherwise, extra power will be waste.
-
-%\subsection{Regulated stand-alone system with battery and DC load}
-%Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:standaloneSPV} letter (c).
-Battery is used to store the extra power of PV system.
-A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
-Extra charging and deep discharging can reduce the battery life \cite{Kim}.
-
-%According to \cite{Pinho}, PV systems that are used to feed loads with low variation on the consumption can be sized to operate without the controller.
-That is called of self-regulated stand-alone PV system with battery.
-However, the voltage from the PV panel must be compatible with the batteries voltage.
-Normally, the bank of batteries are oversized related to the PV panel and to the load.
-The drawback is the operation of the batteries, normally overloaded or with excessive discharges (that can damage the batteries).
-
-%\subsection{Regulated stand-alone system with battery and AC load}
-%This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:standaloneSPV} letter (d).
-This solution has an increase of cost because has more equipments.
-However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-That configuration is the focus of the present work since it is the most common nowadays all over the world, when off-grid or isolated regions is the target.
-
-\subsection{Sizing and Simulation of Stand-alone Solar PV systems}
-The sizing and validation of a PV system can be done by hand or with the aid of tools. Here we reference the critical period~\citep{Pinho} as an effective method to stand-alone PV sizing.
-%
-%In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
-%public domain and commercial software available for the PV market. 
-%According to \cite{Brooks}, t
-%%%%%%%%%%The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
-% to complex financial analysis and project optimization. 
-%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-%
-%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-
-The most popular softwares are summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\citep{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
-%\subsection{PVWatts Calculator}
-%According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
-According to \cite{NRELDobos}, to use the calculator, it is necessary to provide information about the system's location, basic design parameters, and system economics.
-PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity monetary value.
-This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules.
-The production estimates that PVWatts computation do not account for many factors that are important in the design of a photovoltaic system, therefore it is necessary support of an energy expert.
-The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year.
-To represent the system's physical characteristics, PVWatts requires values for six inputs: System DC size; Module type; Array type; System losses; Array tilt angle; Array azimuth angle.
-%
-%\subsection{SAM}
-%SAM or System Advisor Model is a software from the U.S.
-Department of Energy and National Renewable Energy Laboratory.
-According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications, and (also) to provide information for readers who do not plan to use the model, but want to learn about its capabilities.
-SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: Project managers and engineers; Financial and policy analysts; Technology developers; and Researchers.
-SAM makes performance predictions and cost of energy estimates for grid-connected power projects based on installation and operating costs and system design parameters that you specify as inputs to the model.
-Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement.
-SAM is an electric power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet electric load.
-It does not model thermal energy systems that meet a thermal process load.
-As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.
-%
-%\subsection{HOMER}
-%As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
-HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources.
-HOMER Legacy is the original HOMER software version created at the National Renewable Energy Laboratory (NREL).
-HOMER Legacy is a free computer model that simplifies the task of evaluating design options for both off-grid and grid-connected power systems for remote, stand-alone, and distributed generation applications.
-HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options.
-Since 2016 HOMER Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available.
-At the short-time only the commercial version will remain.
-%
-%The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
-HOMER Pro put together three tools in one product: optimization, simulation, and sensitivity analysis.
-HOMER Pro provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use.
-It is adaptable to a wide variety of projects.
-For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project.
-For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations.
-Chronological simulation is essential for modeling variable resources, such as solar and wind power and for combined heat and power applications, where the thermal load is variable.
-HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.
-%
-%\subsection{RETScreen}
-%As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
-%
-%RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options.
-The software can be used to evaluate benefits from both clean energy production from power generation projects and savings through energy efficiency projects, accounting for project costs, greenhouse gas emission reductions, and financial risk.
-The software is freely distributed (but with restrictions to save work or print), and had three different versions:
-%
-%\begin{itemize}
-%\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
-%\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
-%\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
-However, this version works is only Windows-based.
-This version has a complete paid version, in an annual subscription way.
-%\end{itemize}
-%
-%As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
-It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
-RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.
-%
-%\subsection{Hybrid2}
-%The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
-Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
-Variations in wind speed and in load within each time step are factored into the performance predictions.
-The code does not consider short-term system fluctuations caused by system dynamics or component transients.
-This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, what is a limitation.
-%
-%Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where 
-As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription typically range from US\$504.00 to US\$657.00.
-%
-\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Comparative coverage of reference simulation software}
-\label{table:softwares}
-\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-\begin{tabular}{c | c | c | c | c | c}
-\hline
-\hline
-Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen} & \rotatebox{90}{Hybrid2}\\
-\hline
-\hline
-Support & X & X & X & X &  \\
-\hline
-Off-grid systems &   &   & X & X & X\\
-\hline
-Hybrid systems &  &  & X & X & X\\
-\hline
-Photovoltaics & X & X & X & X & X\\
-\hline
-Batteries &  &  & X &  & X\\
-\hline
-\makecell{Main technical (T) \\ or economical(E)} & T & T & E & E & T \\
-\hline
-Optimization &  &  & X & X &  \\
-\hline
-Sensitive analysis &  &  & X & X & \\
-\hline
-\hline
-\end{tabular}
-\end{table}
-%
-%-------------------------------------------------------------------
-%\subsection{Paper Proposal x Reference Tools}
-%-------------------------------------------------------------------
-%
-In this study, HOMER was chosen to comparative with our proposed verification approach (Section~\ref{sec:results_indeed}).%All tools need some parameters inherently from manufacturer's catalog.
-%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
-%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-%Thus, the main challenge here is to demonstrate the application of software model checking to formally verify a stand-alone PV solution, thus proving that this approach is more effective and complete than other state-of-the-art tool such as HOMER Pro.
-The comparative evaluation between HOMER Pro and our approach is presented in Section~\ref{sec:results_indeed}.
-%
-%-------------------------------------------------------------------
-\subsection{Component models for a stand-alone PV system }
-%-------------------------------------------------------------------
-%The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
-%The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
-It identifies the PV generator, batteries, charge controller, inverter, and AC load.
-A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-The PV generator is a semiconductor device that can convert solar energy into DC electricity.
-%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
-For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\citep{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
-The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
-%
-%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
-%
-\begin{figure}[h]
-\includegraphics[width=0.80\textwidth]{blockdiagramPVS2}
-\centering
-\caption{Block diagram for a typical stand-alone PV system (adapted from~\citep{Hansen}).}
-\label{fig:blockdiagram}
-\end{figure}
-%
-%In the literature, there are several mathematical models available for each component of PV systems. At the next section, the mathematical model for each component is presented. 
-%-------------------------------------------------------------------
-\subsection{PV System Model}
-\label{sec:PVsystemmodel}
-%-------------------------------------------------------------------
-%A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
-%In the present modeling, the focus is only on cell/module/array.
-%
-%%%%%%The basic element of a PV system is a PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
-%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
-When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}.
-If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
-%%%%%To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
-%%%%%package called panel or module. 
-%For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
-In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}.
-The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{celmodarray}
-%\centering
-%\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
-%\label{fig:celmodarray}
-%\end{figure}
-%
-%%%%%The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on meteorological conditions.
-%the meteorological conditions of the area to be serviced by PV solution. %However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
-%, which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
-The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
-However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
-%
-%These uncertainties lead to either over- or underestimation of energy yield from PV modules.
-An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
-The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
-%
-%Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
-However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage.
-Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
-% 
-%Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
-Mathematical models are required in order to allow the formal specification of the PV system. At this section we will summarize the models adopted at the paper.
-
-\textbf{PV modules}: a wide variety of models exists. % for estimation of its power output  (and $I-V$ or $P-V$ curves). 
-However, the present work will rely on the simplified model of 1-diode, illustrated in Fig.
-\ref{fig:equivckt}.
-This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\citep{Saloux}.
-
-%The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-%is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
-%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
-\begin{figure}[h]
-\includegraphics[width=0.40\textwidth]{equivckt1D}
-\centering
-\caption{1-diode equivalent PV cell/panel circuit model (adapted from~\citep{Cubas}).}
-%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
-\label{fig:equivckt}
-\end{figure}
-
-The Eq.
-\eqref{eq:1diodemodel} relates the output current, $I$, to the output voltage, $V$.
-%This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-%In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
-\begin{equation}
-\label{eq:1diodemodel}
-I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right], 
-\end{equation}
-
-\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
-$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}\:J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}\:C $).
-
-%\begin{itemize}
-%\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
-%\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
-%\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed; $ N=1 $ in a single cell configuration.
-%	\begin{itemize}
-%	\item $ N=1 $ in a single cell configuration. 	
-%	\end{itemize}	  
-%\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes.
-%	\begin{itemize}
-%	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
-%	\end{itemize}
-%\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
-%	\begin{itemize}
-%	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
-%	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
-%	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
-%	\end{itemize}	 
-%\end{itemize}
-%
-%This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.
-%
-%The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}. 
-%
-%\begin{equation}
-%\label{eq:1d1rmodel}
-%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
-%\end{equation}
-%
-%Where $R_{s}$ is the series resistor.
-%
-%At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
-%
-%The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}. 
-%
-%\begin{equation}
-%\label{eq:1d2rmodel}
-%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-%\end{equation}
-%
-%Where $R_{sh}$ is the shunt resistor.
-%
-%At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
-%
-%And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}. 
-%
-%\begin{multline}
-%\label{eq:2d2rmodel}
-%I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - \\ %I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-%\end{multline}
-%
-%This model has six unknown parameters with two exponential terms. 
-%Briefly, both single and double diode models require the knowledge of all unknown parameters, which is usually not provided by manufacturers.
-Nevertheless, the current-voltage equation is a transcendental expression \cite{Jakhrani}.
-%
-%However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel. 
-%
-%For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
-The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
-However, due to implicit nature and nonlinearity of PV cell or module characteristics, it is hard to find out the analytical solution of all unknown parameters, as described by \cite{Hasan}.
-Thus, numerical methods such as Newton-Raphson method or Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}.
-This happens because numerical methods give approximate solution of the nonlinear problems without searching for exact solutions.
-However, numerical methods are time consuming and need long term time series data, which is not available in developing countries.
-\cite{Jakhrani} did a mixed methodology using analytical and numerical steps together.
-\cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation (essays).
-And \cite{Tian} did a mix of analytical and experimental methodology to get the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use experimental technique.
-%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
-%The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
- %
-%\subsection{PV Panel Model}
-%With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
-%
-%A single-diode without series and shunt resistances is considered. 
-%%%%%%%Eq.~\eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
-% shown in Fig. \ref{fig:ivcurve}.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{ivcurve}
-%\centering
-%\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
-%\label{fig:ivcurve}
-%\end{figure}
-%
-%Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
-%\begin{equation}
-%\label{eq:Isc}
-%I_{sc}=I_{ph}\vert_{V=0}
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Voc}
-%V_{oc}=\dfrac{aNk_{B}T}{q}ln\left( 1+\dfrac{I_{sc}}{I_{0}} \right) 
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:exp}
-%exp\left( \dfrac{qV_{oc}}{aNk_{B}T} \right) = \left(1+\dfrac{qV_{m}}{aNk_{B}T} \right) exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) 
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Im}
-%I_{m} =I_{ph}-I_{0}\left[ exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) -1 \right] 
-%\end{equation}
-%
-%Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way. 
-%
-%A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}. 
-%These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig.
-\ref{fig:ivcurve}, where the transition is a compromise between both behaviors.
-It is interesting to observe that the maximum power point corresponds to a trade-off condition, where the current is still high enough before it starts decreasing with increasing the output voltage (Fig.
-\ref{fig:ivcurve}).
-%
-%Based on this, the tangent of the I-V curve can be used to evaluate the transition between current- to voltage-source controlled regions; this operation yields Equation \ref{eq:didv}.
-%
-%\begin{equation}
-%\label{eq:didv}
-%\dfrac{dI}{dV}=-\dfrac{qI_{0}}{aNk_{B}T}exp \left( \dfrac{qV}{aNk_{B}T}  \right) 
-%\end{equation}
-%
-%The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell.
-Therefore, the Equation \ref{eq:Vmderiv} is generated.
-%
-%\begin{equation}
-%\label{eq:Vmderiv}
-%V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
-%\end{equation}
-%
-%It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point.
-The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change on $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}.
-Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation \ref{eq:Vmderiv} can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
-%
-%\begin{equation}
-%\label{eq:dIdV_Vm}
-%\dfrac{dI}{dV}\vert_{V_{m}} \cong -\dfrac{0-I_{sc}}{V_{oc}-0}=\dfrac{I_{sc}}{V_{oc}}
-%\end{equation}
-%
-%Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, 
-%
-The voltage and the current at the maximum power point tracking (MPPT), can be described by Eq.
-\eqref{eq:Vmfinal}, and Eq.
-\eqref{eq:Imfinal}~\citep{Saloux}: %, and Eq.
-\eqref{eq:Pm} as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
-\begin{equation}
-\label{eq:Vmfinal}
-V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right). 
-\end{equation}
-
-\begin{equation}
-\label{eq:Imfinal}
-I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right).  
-\end{equation}
-
-%\begin{equation}
-%\label{eq:Pm}
-%P_{m} = V_{m} I_{m}.
-%\end{equation}
-%
-%\begin{multline}
-%\label{eq:Pm}
-%P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
-%\end{multline}
-%
-However, the photo-current delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, Eq.
-~\eqref{eq:Iph} is used to calculate the photo-current as function of irradiance and temperature~\citep{Villalva}:
-\begin{equation}
-\label{eq:Iph}
-I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right], 
-\end{equation}
-
-\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000\:W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}\:C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$); %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions.
-$ I_{ph,ref} $ can be approximated to the reference short-circuit current ($ I_{sc,ref} $)\citep{Villalva}.
-% that is provided by PV manufacturers ($ I_{sc,ref} $).
-%\cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
-%%
-The cell temperature ($ T $) in degree Celsius is described by Eq. \ref{eq:Tcell}~\citep{Ross}:
-\begin{equation}
-\label{eq:Tcell}
-T = T_{air} + \dfrac{NOCT-20}{800}G,
-\end{equation}
-
-\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C), and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
-
-Furthermore, Eq. ~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\citep{Villalva} 
-%In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
-
-\begin{equation}
-\label{eq:I0}
-I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1},
-\end{equation}
-
-\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
-
-%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current, cf.
-Eq.~\eqref{eq:Imfinal}, and the saturation current in the reference temperature given by Eq.~\eqref{eq:I0}, the diode ideality factor~\citep{Saloux} is determined by Eq.~\eqref{eq:a}:
-\begin{equation}
-\label{eq:a}
-a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) },
-\end{equation}
-
-\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions.
-%, usually provided by manufacturers; t
-
-%The PV generator model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers in data-sheets or manuals.
-%
-%If the PV cells are in parallel, then there is a parallel array.
-Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
-%
-%\begin{equation}
-%\label{eq:Iarray}
-%I_{array} = (N_{cells in parallel})(I_{one cell})
-%\end{equation}
-%
-%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
-%
-%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
-%
-%\begin{equation}
-%\label{eq:Varray}
-%V_{array} = (N_{cells in series})(V_{one panel})
-%\end{equation}
-%
-%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
-%------------------------------------------------------------
-%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system.
-Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery.
-During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.
-
-Related to the \textbf{batteries}, various models have been described in the literature and the most common ones are based on lead-acid batteries~\citep{Copetti,Pinho};
-%, and \cite{Manwell93, Manwell94}. 
-%However, regardless of the model, normally the following parameters are required: 
-%
-%\begin{itemize}
-%\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
-%, under predetermined discharge conditions.
-%\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
-%Obviously $ 0<SOC<1 $. 
-%If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
-%\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
-%It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
-%\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
-%\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
-%\end{itemize}
-%
-%The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
-The battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
-LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.
-%
-%In general, the battery models view the battery as a voltage source $ E $ in series with an internal resistance $ R_{0} $, as shown in Fig. \ref{fig:batteryckt}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{batteryckt}
-%\centering
-%\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
-%\label{fig:batteryckt}
-%\end{figure}
-%
-%The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.  
-%
-%Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
-%
-%The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.  
-%
-%The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
-However, it uses some data extracted from tested batteries in laboratory.
-Therefore is not suitable to this study.
-%
-that kind of battery has relative low cost and wide availability~\citep{Copetti}. 
-%
-Here, the model adopted uses only manufacturer's data without empirical tests~\citep{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature. 
-%
-The discharge voltage is described by Eq. \eqref{eq:bat_Vd}.
-%The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
-%
-\begin{multline}
-\label{eq:bat_Vd}
-V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T),
-\end{multline}
-
-\noindent where $C_{10}$ means 10 h of rated capacity (manufacturer's data-sheet), $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $%, $ T_{ref}=25^{o}C $
-), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time.
-%Mathematically, it is the ratio between the present capacity and the nominal capacity% (in $ Ah $, provided by manufacturer)
-%If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
-%\begin{equation}
-%\label{eq:SOCbat}
-%SOC = \left( 1 - \dfrac{Q}{C} \right) 
-%\end{equation}
-%
-%Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
-%
-%The ratio between $ Q $ and $ C $ represents t
-The depth of discharge ($DOD$) or the fraction of discharge, is $DOC=1-SOC$.
-
-%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
-This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
-%
-%\begin{equation}
-%\label{eq:CC10}
-%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
-%\end{equation}
-%
-%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
-For the charging process, the parameters are described by Eq.~\eqref{eq:Vcbat} as
-%
-\begin{multline}
-\label{eq:Vcbat}
-V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
-\end{multline}
-%
-%Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period.
-%; however, during recharge it is much more difficult \cite{Copetti}.
-%Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell.
-The efficiency drops to zero at full charge and the function that represents the charge efficiency ($ \eta_{c} $) variation with state of charge and current rate is given in Equation \ref{eq:efficcharge}.
-%\begin{equation}
-%\label{eq:efficcharge}
-%\eta_{c} = 1 - exp \left[ \dfrac{20.73}{\dfrac{I}{I_{10}}+0.55} (SOC-1) \right] 
-%\end{equation}
-%
-%\cite{Copetti} show that, 
-%During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (\ref{eq:Vec}).
-It was created a function for the gassing voltage as well, as shown in (\ref{eq:Vg}).
-In addition, the overcharge phenomenon can be represented by (\ref{eq:Voverc}).
-%\begin{equation}
-%\label{eq:Vec}
-%V_{ec} = \left[ 2.45 + 2.011 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Vg}
-%V_{g} = \left[ 2.24 + 1.97 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-%\end{equation}
-%
-%\begin{multline}
-%\label{eq:Voverc}
-%V_{c} = V_{g} + (V_{ec} - V_{g}) \\ \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
-%\end{multline}
-%
-%Where $ Ah_{restored} $ represents the Ampere-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
-%
-%The function assumes that 95\% of the capacity was already restored at the start of overcharge.
-%
-%The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by (\ref{eq:tau}).
-%\begin{equation}
-%\label{eq:tau}
-%\tau = \dfrac{17.3}{1+852 \left( \dfrac{I}{C_{10}} \right) ^{1.67} }
-%\end{equation}
-%
-%Therefore, to model the voltage ($ V_{c} $) evolution of the battery, (\ref{eq:Vcbat}) can be used up the start of gassing ($ V_{c} \leq V_{g} $).
-And during overcharging ($ V_{c} > V_{g} $), (\ref{eq:Voverc}) can be used until a constant final voltage ($ V_{ec} $) is reached.
-%
-%The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
-%
-%\begin{equation}
-%\label{eq:stor}
-%Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
-%\end{equation}
-%
-%Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
-%
-%As an example of this formula application, as shown by \cite{Abdulateef}, considering that a stand-alone PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
-%
-%Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$.
-Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$).
-If a single battery of 12 V and 350 Ah is considered, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
-%
-%At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature.
-The equations are used to update the $SOC$ of the batteries, and have the number of hours ($ Num_{h} $) as a variable.
-There is a factor (1.15) which is present at the charging equation, and is necessary to express that during the charging process is usual to reach 115\% of the battery capacity
-%
-%\begin{multline}
-%\label{eq:charge}
-%SOC_{charge} = SOC_{previous} + \\ \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
-%\end{multline}
-%
-%\begin{multline}
-%\label{eq:discharge}
-%SOC_{discharge} = SOC_{previous} - \\ \dfrac{100*I_{drained}*Num_{h}}{capacity}
-%\end{multline}
-%
-%
-%---------------------------------------------------------
-%---------------------------------------------------------
-%Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
-However, in this study, in order to simplify, the term used is controller.
-
-The \textbf{charge controller} or controller is the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-Controllers with MPPT mechanism are the mostly used nowadays,  and it maintains the PV operating at the stage of maximum power.
-%Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
-%
-%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
-%
-%
-%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components.
-The use of battery as a storage form implies thus the presence of a charge controller.
-%
-%%%%%%%%%%In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
-%
-%The controller allows the management of energy between the load and the battery \cite{Mellit}. 
-%The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
-The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
-
-The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.
-To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \_ off}$ and when the current required by the load is less than the current delivered by the PV arrays~\citep{Hansen}.
-PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \_ on} $.
-%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{controllerover}
-%\centering
-%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
-%\label{fig:controllerover}
-%\end{figure}
-%
-In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \_ off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\citep{Hansen}.
-The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \_ on}$.
-%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{controllerdisc}
-%\centering
-%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
-%\label{fig:controllerdisc}
-%\end{figure}
-%
-%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
-%
-\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process (adapted from~\citep{Hansen})}
-\label{table:controller}
-\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-\begin{tabular}{c | c | c }
-\hline
-\hline
-Step  & Constraint & Command\\
-\hline
-\hline
-(1) & \makecell{If $V > V_{max \_ off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
-\hline
-(2) & \makecell{If command (1) is \\done and $V < V_{max \_ on}$} & \makecell{Reconnect PV array \\to the system}\\
-\hline
-(3) & \makecell{If $V < V_{min \_ off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
-\hline
-(4) & \makecell{If command (3) is \\ done and $V > V_{min \_ on}$} & \makecell{Reconnect the load \\to the system}\\
-\hline
-\hline
-\end{tabular}
-\end{table}
-
-%Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage. 
-%
-%As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of controller is given by Eq. \eqref{eq:poutcont}.
-\begin{equation}
-\label{eq:poutcont}
-P_{in} \eta_{c} = P_{out}.
-\end{equation}
-
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Eq. \eqref{eq:poutcont} we compute Eq. \eqref{eq:potcont}.
-\begin{equation}
-\label{eq:potcont}
-V_{in} I_{in} \eta_{c} = V_{out} I_{out},
-\end{equation}
-
-\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
-
-%The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}). 
-% 
-%A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
-In addition, there is the Cuk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.
-%
-%For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.
-%
-%\begin{equation}
-%\label{eq:voutvin}
-%\dfrac{V_{out}}{V_{in}} = \dfrac{D}{D-1}
-%\end{equation}
-%
-%Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
-% 
-%The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
-%  
-%Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.
-% 
-%As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
-
-%The number of controllers required for the stand-alone PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
-In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
-%\begin{multline}
-%\label{eq:numberofcmin}
-%number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \\ \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
-%\end{multline}
-%
-%\begin{equation}
-%\label{eq:numberofc}
-%N_{controller} \geq number_{controllers}
-%\end{equation}
-%
-%\subsection{Joint work: charge controller and batteries}
-%When batteries are charged, they go through three main different states - bulk, absorption and float, with impact to the inverter and to power supplied to the house.
-%, and it is necessary to understand those three states in order to comprehend the joint work of the controller with the battery. With impact to the inverter and to power supplied to the house. 
-%
-%All the explanation at this section is related to $SOC$ and to the voltage at the DC-bus (controller output, which will be bigger than $V_{system}$) where the batteries are connected, all ruled by the charge controller.
-Moreover, it is important to mention that smart chargers, the most usual nowadays, will detect voltage and resistance from the battery prior to charging.
-%
-%Bulk - is the first stage of charging. Bulk begins when the sun comes out.
-%, or other source of electrical generation is turned on. 
-%This stage occurs when the batteries are at a lower $SOC$, generally anything not smaller than $75\%$ to $80\%$ (defined during system sizing).
-This stage is typically where the highest voltage and current the charger is rated for will actually be used.
-The bulk stage basically allows the PV panel to put as much current into the batteries as possible.
-For a typical 12 V battery, the charging voltage going into a battery will reach 14.16 V to 14.40 V at this stage, and there is no risk of overcharging in this stage because the battery hasn't even reached full yet.
-%
-%Absorption - once the batteries reach the programmed absorb voltage, usually somewhere between 14.16 and 14.40 V, the batteries will go into the absorption stage.
-Typically, when a battery reaches this stage its $SOC$ is around $85-95\%$.
-During this stage, the batteries are kept at the programmed voltage, and the current going into the batteries reduces as the batteries become more full.
-The absorption stage ends after the programmed time is reached or the number of Ampere going into the battery falls below a preset number.
-The lower current going into the battery safely brings up the charge on the battery without overheating it.
-%Usually, this stage takes more time than the bulk stage.
-%
-%Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage that a 12 V battery can hold, and begin the float stage.
-The float stage brings the battery all the way through and maintains $SOC$ at $100\%$.
-The current will also decrease to a point where it's considered just a pulse.
-It's essentially the float stage where there is charge going into the battery at all times, but only at a safe rate to ensure a full state of charge and nothing more.
-%Most smart chargers do not turn off at this point, however it is completely safe to leave a battery in float mode for months to even years at a time.
-%
-%Battery charging technology relies on smart micro-controlled devices.
-Therefore it is extremely important that the program settings for the charge controller or inverter/charger are correct, and the list includes the bulk and absorption values.
-%This will help preserve and extend the battery life.
-There are always default settings to the equipment, set by software, however those settings are not $100\%$ correct because there are difference among models of equipment and among manufacturer's.
-The ideal is to read the data-sheet from the manufacturers and perform a manual adjust.
-%
-%There are the possibility to combine batteries in a bank, with parallel and series connections, all depending the sizing of the project:
-%
-%\begin{itemize}
-%\item Batteries connected in parallel are seen by the controller as one large battery of the combined Ah capacity of all the batteries.
-For example, two 12 V and 220 Ah batteries in parallel are seen as one 12 V and 440 Ah battery;
-%\item In the other hand, although the batteries connected in series are also seen as a single battery, the result is different: two 12 V and 220 Ah batteries in series are seen as one 24 V and 220 Ah battery;
-%\item In addition, a mixed bank arrangement can be useful: a bank with two 12 V and 220 Ah batteries in series connected in parallel with a similar arrange will produce an equivalent battery of 24 V and 440 Ah.
-%\end{itemize}
-%-----------------------------------------------
-%-----------------------------------------------
-%As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. 
-%An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
-The role of the \textbf{inverter} is to keep the voltage constant on the AC side, %, i.e., at the rated voltage, % (127 V or 220 V, for example), 
-and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by \eqref{eq:efficinv} \citep{Hansen}:
-%
-%The inverter is characterized by a power dependent efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
-\begin{equation}
-\label{eq:efficinv}
-\eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}},
-\end{equation}
-
-\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be obtained from the inverter's manual.
-
-%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
-%
-%
-%--------------------------------------------------
-\subsection{Availability of Stand-alone PV Systems}
-\label{sec:availability}
-%--------------------------------------------------
-%Each stand-alone PV system, like any other power systems, has a specific level of availability.
-This reliability level impacts various issues, as system performance, production, feasibility, and investment.
-The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\citep{Khatib2014}.
-The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
-The system availability definition depends on how critical the load application is.
-For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable.
-%As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system.
-An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
-%
-%With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong.
-It is important to evaluate how critical the load application is and the horizon of evaluation.
-However this analysis can be useful, for example, to improve the sized battery autonomy.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Verification Using Model Checking}
-\label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\citep{ClarkeHV18}.
-Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\citep{Clarke2012}.
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\citep{Clarke2012}.
-Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t.
-user requirements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\citep{Kroening}.
-CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
-If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\citep{Kroening}.
-CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\citep{esbmc2018}, which supports the verification of LTL properties with bounded traces~\citep{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\citep{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\citep{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Automatic program verification requires a choice between precision and efficiency.
-%The more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs.
-Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
-In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
-The CPA formalism provides an interface for the definition of program analyses.
-Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\citep{Beyer2011}.
-Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT solvers and interpolation procedures~\citep{Beyer2011}.
-%Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-%CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
-For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
-\textcolor{red}{It is unclear what a CPA is.}
-%In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
-%
-%
-%----------------------------------------
-\section{Proposed Automated Verification Method of PV Systems}
-\label{sec:Methodology}
-%----------------------------------------
-%
-%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.5\textwidth]{statetransition}
-%\centering
-%\caption{State transition diagram to the proposed automated verification.}
-%\label{fig:statetransition}
-%\end{figure}
-%
-%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.
-%
-The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
-
-\begin{figure}[h]
-\includegraphics[width=0.6\textwidth]{flowchart_verification5.png}
-\centering
-\caption{Flowchart of the proposed automated verification of PV systems.}
-\label{fig:flowchartgeneral}
-\end{figure}
-
-In Step 1, the PV input data %(e.g., load power demand and load energy consumption) 
-and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\citep{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
-This stage ensures that the system meets the standard project steps related to critical period method of sizing~\citep{Pinho}.
-%
-In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
-%As a consequence, all the formulae of the employed mathematical models will also be updated. 
-In addition, depending on one of the desired properties of the system such as battery autonomy, energy availability, or even system power supply, our verification engine is able to indicate a failure if those properties are not met; in this particular case, it provides a diagnostic counterexample that shows in which conditions the property violation occurred.
-%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
-% (as reliability, performance, or safety)
-
-%
-%\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above.
-For example, what does a failure mean?
-is it SAT?}
-In a nutshell, the model checker will process the ANSI-C code with constraints %($C$) 
-and properties %($P$) 
-from the PV system, and the tool will automatically verify if the PV system requirements are met.
-If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
-However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
-%, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
-%
-%
-%---------------------------------------------------------------------
-% \subsection{The case studies and the Algorithm}
-%---------------------------------------------------------------------
-%
-% 
-%and as backup at night 
-%
-%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
-%
-%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
-%
-%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).
-
-Algorithm~\ref{alg:verification-algorithm} describes the equivalent pseudo-code.
-%Line 1 indicates a function call that performs the size checking of the each component of the PV system.
-%: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
-%The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation of sizing check.
-The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints a counterexample indicating a property violation.
-If there is no property violation, then the verification algorithm continues and
-In order to reduce the computational effort of the algorithm,
-% caused by the state explosion inherent of the technique, 
-every 24 h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation), when the batteries are demanded to feed the house.
-
-Lines 1 is devoted to information from the location where the PV system will be/were deployed.
-We use annual average minimum and maximum, related to temperature ($T$) and solar irradiance ($G$), hour by hour, from~\citep{Temperature}, and ~\citep{Irradiance}.
-
-Line 2 represents all the information that comes from the PV sizing and from the equipment manufacturers data: specification and data from PV, batteries, inverter and charge controller.
-This item includes as information from the house's load curve.
-
-The first automated verification is related to the sizing check (line 3), if an error is found then the algorithm stops.
-Then two functions, called at lines 4 and 5, are responsible for discover which hour starts the PV generation and when stops.
-Those functions get this information from the array inputted to the Algorithm with the solar irradiance values.
-
-The batteries are assumed to be charged, i.e., with SOC of 100\% (line 6).
-
-The first for-loop at line 7 controls how many cycles of 24 h will be performed by the Algorithm.
-And the for-loop from lines 8 to 11 is responsible to discharge the battery (according the load curve) and verify the state of charge of the battery, hour-by-hour, starting at the first hour of the day after the sun goes down until the next day before the sun goes up (without PV generation).
-Following, at the next for-loop, from line 12 to 29, is performed the verification where there is solar irradiance and all the PV system works.
-The Algorithm generates information related to average temperature ($T$) and solar irradiance ($G$), hour-by-hour, using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range (lines 15 and 16).
-%and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
-%there is PV generation only between 8:00 h and 16:00 h every day, 
-%with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day.
-
-After that, the model from PV generator is used in the function call of line 17, to produce the voltage and current considering the states of $G$ and $T$.
-With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller work, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
-
-At the end of last for-loop, the state of the batteries is verified again (line 27) and the hour is adjusted to the next loop (line 28).
-
-Nevertheless, if the verification engine does not fail, we can conclude that the PV system does not need further corrections up to the given bound $k$.
-%
-%\textcolor{red}{this sentence is unclear...
-After this process is started the battery autonomy verification, from line 31}.
-\textcolor{red}{this sentence is unclear...
-Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.} \textcolor{red}{what do you mean by The formal verification is guaranteed?...
-The formal verification is guaranteed by  macro to specific variables of the model, according lines 27 and 35.}
-% and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
-%Within this 8h-period, $G$ and $T$ are automated verified with different values every one hour.
-%, and change their value every 1 h according with the algorithm created using the technique.
- \begin{algorithm}
- \caption{Model checking algorithm for stand-alone PV}
- \begin{algorithmic}[1]
- \begin{scriptsize}
- \renewcommand{\algorithmicrequire}{\textbf{Input:}}
- \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\
-  \STATE $declare \, case \, studies \, details: \, sizing \, and \, manufacturers \, data $ \\
-  \STATE $sizing \_ check()$ \\
-  \STATE $startPVgeneration \leftarrow findStartPVgeneration()$ \\
-  \STATE $endPVgeneration \leftarrow findEndPVgeneration()$ \\
-  \STATE $SOC \leftarrow 100\%$ \\
-%  \COMMENT {Starting with the PV generation time}
-% \\ 
-%\textit{LOOP Process}
- \FOR {$1st \, 24h \, loop$ to $Nth \, 24h \, loop$}
-  \FOR {$endPVgeneration+1$ to $startPVgeneration-1$}
-	  \STATE $dischargeBattery \, in \, 1h()$ \\
-%	  \STATE $autonomyCount \leftarrow autonomyCount+1$ \\
-	  \STATE $assert (SOC \geq SOC \_ min)$ \\
-%	  \STATE $battery \, autonomy \, verification()$ \\
-  \ENDFOR
-  \FOR {$startPVgeneration$ to $endPVgeneration$}
-    \STATE $G \leftarrow nondet \_ uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
-    \STATE $T \leftarrow nondet \_ uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
-    \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting $G$ values}
-    \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting $T$ values}
-    \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ \\
-    \COMMENT {If-then-else sequence to imitate charge controller work}
-    \IF {($battery \, is \, empty$) AND ($PV \, is \, generating$)}
-      \STATE $chargeBattery \, in \, 1h()$ \COMMENT {PV feed the house}
-    \ELSIF {($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
-      \STATE FAIL with assert macro \COMMENT {Battery is empty and there is not PV generation}
-    \ELSIF {NOT($battery \, is \, empty$) AND ($PV \, is \, generating$)}
-      \STATE stop battery charge \COMMENT {PV feed the house}
-    \ELSIF {NOT($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
-      \STATE $dischargeBattery \, in \, 1h()$ \COMMENT {Battery feed the house}
-    \ENDIF
-    \STATE $assert (SOC \geq SOC \_ min)$ \\
-    \STATE $hour \leftarrow hour+1$ \\
-   \ENDFOR
-  \ENDFOR
- \RETURN $(\,)$ 
-  \end{scriptsize}
- \end{algorithmic} 
- \label{alg:verification-algorithm}
- \end{algorithm}
-%There are two premises considering the algorithm: (1) is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation from 8:00 h to 16:00 h, but without to account the battery autonomy (just considering charge and discharge process based on solar irradiation, load and battery charge), but after 16:00h is started the verification for the next hours when there is not solar photovoltaic generation.
-The process goes on until to verify all the autonomy demanded from the batteries; (2) there is an array, declared at the beginning of the C code, that defines the power demand/consumption at each hour of the day (aka load curve).
-Those are the same data used during the sizing of the project and ensure to consider the total energy (per day) supplied to the house during the verification.
-%
-%If the verification founds a situation where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
-And this information can be used by the designer to improve the system.
-%if it was a project error or if it was a combination of variables from the nature that has a low probability to occur at the field, considering the intermittent characteristic of solar PV generation.
-%
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-%
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-%
-%
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-%
-%
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-%
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-%
-%----------------------------------------------
-\section{Experimental Evaluation} 
-\label{sec:results}
-%----------------------------------------------
-%
-%\textcolor{red}{reorganise the results as follows: experimental objectives and setup; results; and threats to validity.}
-%
-%\textcolor{red}{https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf}
-%
-%------------------------------------------
-\subsection{Description of the Case Studies}
-%------------------------------------------
-%
-%We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
-We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
-%Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
-\begin{table}
-\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
-\begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\hline
-Item & House 1 & House 2 & House 3 & House 4 & House 5\\
-\hline
-\hline
-PV Panels &  \multicolumn{4}{|c|}{3x 325 W: in series} & 4x 325 W: 2x series, 2x parallel \\
-\hline
-Batteries & \multicolumn{4}{|c|}{\makecell{4x220 Ah: 2x series, 2x parallel\\ autonomy: 48 h}} & \makecell{4x 120 Ah batteries in series\\ autonomy: 6 h}\\
-\hline
-Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
-\hline
-Inverter & \multicolumn{4}{|c|}{700 W, peak of 1,600 W} & 1,200 W, peak of 1,600 W\\
-\hline
-Power demand & 253 W & 263 W & 283 W & 501 W & 915 W\\
-\hline
-GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
-\hline
-Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
-\hline
-\hline
-\end{tabular}
-\end{scriptsize}
-\end{table}
-%------------------------------------------
-\subsection{Objectives and Setup}
-\label{sec:setup}
-%------------------------------------------
-Our experimental evaluation aims to answer two research questions:
-%
-\begin{enumerate}
-\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
-\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
-\end{enumerate}
-
-%In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool.
-All the experiments were performed with a timeout of 14,400 seconds.
-%Every dweller, who owns a PV system, was interviewed
-%
-All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
-The setup of HOMER Pro v3.12.0: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
-The experiments were performed with timeout of 14,400 seconds.
-
-Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\citep{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled; % with the goal of reducing memory usage; we have also used
-with SMT solver Z3 version 4.7.1~\citep{DeMoura}.
-
-Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\citep{Kroening}\footnote{Command-line: \$ cbmc filename.c -\phantom{}-unwind 100 -\phantom{}-trace}.
-
-% enabled with the goal of reducing memory usage; 
-%The experiments were performed without a predefined timeout.
-Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\citep{mathsat5}.
-An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness.
-% enabled with the goal of reducing memory usage; 
- %The experiments were performed without a predefined timeout.
-
-%------------------------------------------
-\subsection{Results and Discussion}
-\label{sec:results_indeed}
-%------------------------------------------
-%
-%\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
-%\begin{enumerate}
-%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
-%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
-%
-Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
-Note that an UNKNOWN result from our verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
-
-%HOMER Pro result: the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
-The simulation took less than five seconds to be performed on each case study.
-%
-\begin{table}
-\centering
-\caption{Summary of the case-studies comparative and the automated tools.}\label{cases}
-\begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\hline
-\multicolumn{5}{|c|}{Model Checker (SAT/UNSAT: time and message)}\\
-\hline
-Case &  \makecell{ESBMC 6.0.0\\(Boolector 3.0.1)} & \makecell {ESBMC 6.0.0\\(Z3 4.7.1)} & \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}\\
-\hline
-\hline
-House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 08 s \\(UNSAT)} & \makecell{19 m 02 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 27 s \\(UNSAT)} & \makecell{18 m 59 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 07 s \\(UNSAT)} & \makecell{18 m 39 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 37 s \\(UNSAT)} & \makecell{18 m 36 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{6 sec \\ (SAT line 337)}\\
-\hline
-\hline
-\end{tabular}
-\end{scriptsize}
-\end{table}
-
-The description of our experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
-
-Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3.
-The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet.
-Using ESBMC with Boolector led to an out of memory situation in all the case studies.
-This result was obtained in less than six minutes of execution, i.e., the 64 GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
-However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.
-Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s.
-However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
-This verification took less than 1 s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
-
-Concerning the CBMC tool, similar results were obtained, but with some slower time.
-The experimentation returned SAT or UNSAT to all the case studies.
-Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s.
-However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
-This verification took less than 1 s to be performed as well.
-
-Finally, the CPAchecker tool presented some different results.
-Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700 W systems.
-This is because the \textit{time out} limit was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
-However, when verifying the 1,200 W PV system, the tool presented a SAT message equal to the other engines.
-
-In order to validate the possible flaw from house 5, we have surveyed the owner of the 1,200 W system.
-We identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
-However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system %($96.67\% = 100\%-3.33\%$)
-and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
-%\begin{figure}[h]
-%\includegraphics[width=0.65\textwidth]{loadcurve.png}
-%\centering
-%\caption{Five weeks monitored load curve from House 1.}
-%\label{fig:loadcurve}
-%\end{figure}
-
-The same five case studies were evaluated by HOMER Pro (RQ2).
-The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system (RQ2).
-All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
-%Fig.
-\ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software, specifically to house 1.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.8\textwidth]{homer.png}
-%\centering
-%\caption{HOMER simulation screen.}
-%\label{fig:homerscreen}
-%\end{figure}
-%
-
-There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
-our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
-House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
-%
-%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
-Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions.
-The season has impact since the case studies are from the rain forest, where clouds are always present.
-As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
-%
-%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
-Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
-All the simulations took less than 5 seconds (each) to be performed.
-%
-%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
-That verification took 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
-The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
-The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
-The proposed tool took 409.3 hours to find this error at house 1.
-This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
-Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
-
-%At the terminal, the command used to perform the verification is:
-%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
-%
-%Where:
-%
-%\begin{itemize}
-%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
-%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
-%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
-%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
-There are other options, but this parameter is necessary because the complexity of the algorithms.
-The incremental SMT solving uses few RAM memory, compared with other SMT solving.
-%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
-The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
-%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
-%\end{itemize}
-%
-%\subsection{Experimental results}
-%\label{sec:results}
-%---------------------------------------------------
-\subsection{Threats to Validity}
-%---------------------------------------------------
-We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
-
-\textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
-The adoption of more complex models, or even an evaluation in a PV laboratory to validate the model could add more reliability to the results.
-
-\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.
-
-\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.
-
-%-------------------------------------
-\section{Conclusions and Future Work}
-\label{sec:Conclusions}
-%-------------------------------------
 We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
@@
 As future work, we will also consider other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
-%the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems.
-%We will also consider other types of renewable energy and even hybrid ones to allow our method to design and verify typical rural electrification.
-%
-%It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results.
-The proposed tool was successful in find sizing errors and to indicate in which conditions a PV system can fails.
-% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements. 
-%
-%Plus (need to think about it): verification in every-hour of a 48h cycle?, PV model math model can be improved, charge/discharge of batteries can be improved (is a simplified model), house's power consumption is not flat or constant, the dweller can buy more home appliances, synthesis need a data base of components, to test peak (surge) consumption (above the nominal), additional models for on-grid/off-grid farm, hybrid, and on-grid with batteries).
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-%\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-%\section{}
-%Appendix two text goes here.
-% use section* for acknowledgment
-\section*{Acknowledgments}
-The authors would like to thank: (i) Coventry University for the case studies and for the research mobility; (ii) Newton Fund [grant number 261881580] for the research mobility support; (iii) FAPEAM - Amazonas State Foundation for Research Support [grants 009/2017 and PROTI-Pesquisa 2018], for the Virtual Machine rent (DEC-2018 to JAN-2019), for the DCTIEX II scholarship (NOV-2018), and for support the research mobility to UK; and (iv) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-2017 to MAR-2019).
 
-%\section*{References}
+///////////////////////
 
-%\bibliography{mybibfile}
-\bibliography{trindadeThesis}
+We have described and evaluated an automated synthesis method 
+to obtain the optimal size of PV system using software model 
+checking techniques. We have considered seven case studies 
+from PV systems in two different sites of the Amazonas State 
+in Brazil, ranging from $253$\,W to $1,586$\,W peak; and 
+three state-of-art verification engines were considered 
+(ESBMC, CBMC, and CPAchecker), in addition to a specialized 
+off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
 
-\end{document}
+Our automated synthesis tool presented detailed optimal solution 
+to six case studies adopted in this paper, with specifications, 
+models, and the arrangement in terms of series-parallel connections, 
+thereby covering the charge controller, which was not presented by HOMER Pro. 
+In a nutshell, our automated synthesis tool took more time 
+to find the optimal solution than HOMER Pro; however, the presented 
+solution was more complete and detailed, which is very useful 
+to a user to get a list of equipment and go to shopping.
+
+As future work, the authors plan to improve the power reliability analysis, 
+to address the restriction to only allow automated synthesis of 
+riverside communities in the Amazonas state (Brazil), and to 
+validate some cases with deployed PV systems in isolated communities.

### 2019-07-01 Tex/Old text/chapters/introduction.tex
thesis updated text

@@
-introduction text here kadhew nrjrenasmnfs,mgfs gfsdf gdsf dfsg dsgh bv dzfg df gdf gdf gdf gdf gd fg dfg dfg
+%%automated verification
+Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+There is a close relationship between the lack of energy and the low HDI (Human Development Index)~\cite{Coelho}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
+%The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
+Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
+%Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
+
+In order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
+
+%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
+%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
+%
+%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
+Only a niche market a few years ago, solar PV systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
+%However, this growth is not driven by stand-alone systems.
+
+In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+%
+%However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
+%
+%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
+In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
+SPV...
+%
+%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
+According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
+Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
+%
+%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
+%
+%PV systems can be classified into grid-connected and stand-alone systems.
+At this proposal, only off-grid or stand-alone systems will be considered.
+The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
+However, those tools are based on running experiments in simulation models.
+Simulation has the advantage of being cheap (if compared to test in real systems) %and can be employed before the system design is concluded
+but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+
+Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
+%with behavior that is, in principle, well determined. 
+Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
+%User or project requirements can be added during the creation of the formal model to be verified.
+%, as defined by \cite{Trindade}.
+%
+%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
+% Their aim is to establish system correctness with mathematical rigor. 
+%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
+% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
+%
+%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
+%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
+%Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
+%
+%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
+%
+
+//automated synthesis
+Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
+During operation, such components must frequently adapt to the operating environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
+Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
+
+While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing \textit{correct-by-construction} implementations of CPS.
+These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
+In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
+Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
+Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
+
+Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}.
+In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
+
+In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and  Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.,  PSpice~\cite{Gow1999}, or MATLAB/Simulink package~\cite{Benatiallah2017}.
+However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+
+Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
+An ideal combination of any PV system is made by the best compromise between two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
+
+However, formal methods based on \textit{symbolic model checking} and its application 
+to synthesize PV systems have not been further explored in literature, which could offer 
+a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
+
+//old material
 
@@
 \subsection{Objectives}
-Objectives here
+In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used.
+%The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are inputted to the proposed tool and automatically verified during the formal process.
+The model checking tool reports in which conditions a system does not meet the user requirements.
+A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
+%Those programs are viewed as mathematical objects, and the use of 
+%Bringing this technique to solar PV systems, i
+%Instead of finding a bug or a software inconsistence, t
+%Here it will be verified a stand-alone PV system, with all their components modeled mathematically,   
+%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
+The implementation of the proposed tool is carried out by means of an algorithm in language C, that is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
+%three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
+%, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
+
+///////////
+Here, we use a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing 
+optimal sizing of stand-alone PV systems using commercial equipment data. 
+Given a correctness specification $\sigma$, our method uses that as starting point 
+and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
+related to power reliability. In particular, in each iteration, we synthesize sizing of 
+stand-alone PV systems but that may not achieve the lowest cost. The candidate solution 
+is then verified via symbolic model checking with a lower bound that serves as the minimum 
+cost of reference; if the verification step does not fail, the lower bound is adjusted. 
+If it fails then a counterexample is provided with an optimal sizing that meets 
+power reliability and system cost.
 
 \subsection{Contributions}
-Contributions text subsection here
+This paper makes two main contributions.
+% Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
+Secondly
+Firstly, we propose an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system.
+Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies.
+%Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation.
+
+%\textcolor{red}{This introduction is missing the description of the vision, approach and results.
+In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
+%
+%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
+
+/////////////////
+Our work makes two major contributions. Firstly, the use of automated 
+symbolic verification methods in electrical systems was uncommon in recent 
+prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
+PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
+charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
+method together with user requirements and environment constraints, 
+and our synthesis algorithm based on symbolic model checking 
+can find the optimal solution in technical and economical terms. 
+\textbf{Secondly}, we evaluate different state-of-art symbolic software 
+verifiers with the goal of obtaining the best performance in our verification 
+back-end for synthesizing optimal PV systems.
 
@@
 
+The conversion of traditional power grid into a smart grid, a fundamental example of a CPS, 
+raises a number of issues that requires novel methods and applications.
+In $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
+The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here, the authors employed automated verification of certain quantitative properties of the system, as probability of	 node failure in the long run, impact of repair service on the failure risk, and expected energy consumption, without any interest in power generation or even solar PV systems.
+
+In $2015$, an automated approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
+The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
+The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
+However, this study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
+
+Other related studies from $2015$ include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis using statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
+In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
+This research, however, did no address the design and verification of solar PV systems.
+
+In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices, interacting over a shared and smart infrastructure~\cite{Abate2017}.
+The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The focus was on controlling the behavior of components, thereby verifying the given smart grid as a "system of systems" within the context of "internet of things".
+The author, however, used approximate model checking of stochastic and hybrid models.
+
+In $2018$, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
+This related study did not include other components of a stand-alone solar PV system.
+
+Another work from $2018$ was the approach to model smart grid components using a formal specification.
+The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
+The presented formal specification can be considered as a first step towards modeling of smart grids using formal methods.
+The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
+This approach is based on Petri nets and is under the assumption that modeling the smart home leads to clear understanding of the overall behavior of the smart grid.
+
 \subsection{Thesis Organization}
-Text here
+Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
+Section~\ref{sec:AutomatedVerification} presents the automated verification technique.
+The methodology is presented in section~\ref{sec:Methodology}.
+Section~\ref{sec:results} is devoted to the results.
+Section~\ref{sec:Conclusions} presents the conclusion and describes future work.
+
+Section~\ref{sec:Background} gives the background about related studies, 
+program synthesis, sizing design and validation of PV systems, and the mathematical modeling. 
+Section~\ref{sec:Method} presents the automated formal synthesis proposed 
+in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, 
+results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.

### 2019-07-01 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 
-\subsection{Solar Photovoltaic System }
+\section{Solar Photovoltaic System }
 According to \cite{Roy}, a PV system is designed to give the electric supply to a load.
@@
 
-\subsubsection{Unregulated standalone PV system with DC load }
+\subsection{Unregulated standalone PV system with DC load }
 Usually this type of system is for low power applications, as defined by \cite{Roy}.
@@
 
-\subsubsection{Regulated standalone PV system with DC load}
+\subsection{Regulated standalone PV system with DC load}
 It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:regSPV1}.
@@
 
-\subsubsection{Regulated standalone system with battery and DC load}
+\subsection{Regulated standalone system with battery and DC load}
 Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}.
@@
 
-\subsubsection{Regulated standalone system with battery, AC load}
+\subsection{Regulated standalone system with battery, AC load}
 This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}.
@@
 
-\subsection{Automated Verification }
-It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.
-
-If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, resulting in a process known as formal verification.
-Verification may form part of a validation process, but in general, validation cannot be formalized because it relates a system design to intent.
-
-Simulation may also be used for validation, but it is more problematic for verification.
-In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-
-Testing can also be used for validation, but for the same reasons, it too is problematic for verification.
-
-According \cite{Clarke2008}, verification procedure is an intelligent exhaustive search of the state space of the design.
-In addition, according to \cite{Forejt2011}, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system.
-One successful method in this domain is model checking.
-
-Model checking is an automatic verification technique, as defined by \cite{Clarke2008}.
-Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
-
-The process of model checking can be divided in three components: modeling, specification, and verification method.
-
-\begin{itemize}
-\item In modeling, a model (normally mathematical) of the system is created; 
-\item In specification, normally a list of properties to be satisfied by the system is stablished, i.e., the requirements, as reliability to performance for example.
-\item Normally is expressed in temporal logic form ($CTL$);
-\item The model checking is the verification method itself. 
-\end{itemize}
-
-The model checking algorithm can be described as:
-
-\begin{itemize}
-\item Given the model $ 'M' $ and a $CTL$ formula $ \phi $ as input;  
-\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
-\item It returns $YES$ if $ \phi $ is $TRUE$, or returns $NO$ if $ \phi $ is $FALSE$.
-
-\end{itemize}
-Specifically at the $FALSE$ situation, the algorithm returns a counterexample that is useful as diagnostic of the system, in order to discover in which situation the model is violated.
-\cite{Clarke2008} consider that the most important advantage of the use of model checking.
-
-Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
-However, there is a main disadvantage of model checking: the state explosion problem.
-
-The model checking problem can be defined as shown in \cite{Clarke2008}:
-
-\begin{itemize}
-\item Let $M$ be a Kripke structure (i.e., state transition graph);
-\item $f$ be the specification in temporal logic (a formula);
-\item Find all states $s$ of $M$ such that $M , s \models f$
-\end{itemize}
-
-Fig. \ref{fig:modelcheckstruc} shows the structure of a typical model checking system. A preprocessor extracts a state transition graph from a system (program or circuit).
-
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{modelcheckstruc}
-\centering
-\caption{Model Checker structure (Source: \cite{Clarke2008})}
-\label{fig:modelcheckstruc}
-\end{figure}
-
-Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study.
-
-The Fig. \ref{fig:systemverif} shows the process to convert a real system to a model in order to be verified by a model checking.
-
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{systemverif}
-\centering
-\caption{From real system verification to model checking (adapted from \cite{Clarke2008})}
-\label{fig:systemverif}
-\end{figure}
-
-In order to solve the problem of state explosion, many different techniques were developed at the last decades. One of the promising is the Bounded Model Checking (BMC).
-
-BMC is a method that checks the model up to a given path in the path length.
-BMC algorithms traverses a finite state machine for a fixed number of steps, , and checks whether violation occurs with this bound.
-It uses fast SAT solvers, where SAT means satisfiability.
-SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression.
-SAT solvers are used in BMC, such that if there are some Boolean function, the solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
-If SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
-
-CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++, as can be seen in \cite{Kroening}.
-
-ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.  
-The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
-
 ///////begin-verification 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+/////////////
+%\section{Automated Verification }
+It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.
+
+If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, resulting in a process known as formal verification.
+Verification may form part of a validation process, but in general, validation cannot be formalized because it relates a system design to intent.
+
+Simulation may also be used for validation, but it is more problematic for verification.
+In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
+
+Testing can also be used for validation, but for the same reasons, it too is problematic for verification.
+
+According \cite{Clarke2008}, verification procedure is an intelligent exhaustive search of the state space of the design.
+In addition, according to \cite{Forejt2011}, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system.
+One successful method in this domain is model checking.
+
+Model checking is an automatic verification technique, as defined by \cite{Clarke2008}.
+Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
+
+The process of model checking can be divided in three components: modeling, specification, and verification method.
+
+\begin{itemize}
+\item In modeling, a model (normally mathematical) of the system is created; 
+\item In specification, normally a list of properties to be satisfied by the system is stablished, i.e., the requirements, as reliability to performance for example.
+\item Normally is expressed in temporal logic form ($CTL$);
+\item The model checking is the verification method itself. 
+\end{itemize}
+
+The model checking algorithm can be described as:
+
+\begin{itemize}
+\item Given the model $ 'M' $ and a $CTL$ formula $ \phi $ as input;  
+\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
+\item It returns $YES$ if $ \phi $ is $TRUE$, or returns $NO$ if $ \phi $ is $FALSE$.
+
+\end{itemize}
+Specifically at the $FALSE$ situation, the algorithm returns a counterexample that is useful as diagnostic of the system, in order to discover in which situation the model is violated.
+\cite{Clarke2008} consider that the most important advantage of the use of model checking.
+
+Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
+However, there is a main disadvantage of model checking: the state explosion problem.
+
+The model checking problem can be defined as shown in \cite{Clarke2008}:
+
+\begin{itemize}
+\item Let $M$ be a Kripke structure (i.e., state transition graph);
+\item $f$ be the specification in temporal logic (a formula);
+\item Find all states $s$ of $M$ such that $M , s \models f$
+\end{itemize}
+
+Fig. \ref{fig:modelcheckstruc} shows the structure of a typical model checking system. A preprocessor extracts a state transition graph from a system (program or circuit).
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{modelcheckstruc}
+\centering
+\caption{Model Checker structure (Source: \cite{Clarke2008})}
+\label{fig:modelcheckstruc}
+\end{figure}
+
+Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study.
+
+The Fig. \ref{fig:systemverif} shows the process to convert a real system to a model in order to be verified by a model checking.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{systemverif}
+\centering
+\caption{From real system verification to model checking (adapted from \cite{Clarke2008})}
+\label{fig:systemverif}
+\end{figure}
+
+In order to solve the problem of state explosion, many different techniques were developed at the last decades. One of the promising is the Bounded Model Checking (BMC).
+
+BMC is a method that checks the model up to a given path in the path length.
+BMC algorithms traverses a finite state machine for a fixed number of steps, , and checks whether violation occurs with this bound.
+It uses fast SAT solvers, where SAT means satisfiability.
+SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression.
+SAT solvers are used in BMC, such that if there are some Boolean function, the solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
+If SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
+
+CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++, as can be seen in \cite{Kroening}.
+
+ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.  
+The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
+
+//////////////////
+
 Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}.

### 2019-07-01 Tex/Old text/chapters/chapter03.tex
thesis updated text

@@
+\section{Automated Verification}
 The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
@@
  /////////////
+ \section{Optimization}
  Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
@@
 by our {\sc Verify} phase to ensure that the approach is sound.
+
+\section{Assumptions and Premises}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, 
+a list of forty equipment from ten different manufacturers was provided 
+to the synthesis engine in order to allow the choice of every item 
+of PV sizing. Data sheet from each item was necessary to collect 
+technical information. Moreover, the price of each item was obtained 
+from available quotations in the market, and if the currency was not in US dollars, 
+then it was used the exchange rate of the day to convert it to US dollars.
+
+With respect to power reliability, this work will rely on the critical period solar 
+energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
+The usual way is to use loss of load probability (LOLP) or loss of power 
+supply probability (LPSP). However, based on the fact that here we 
+are neither considering site characteristics nor the load changes over time, 
+which demands historical data, the reliability analysis will be developed only 
+by the critical period method of PV sizing.
+
+Regarding financial analysis:
+\begin{itemize}
+	\item LCC lifetime considered: $20$ years;
+	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
+	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
+	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
+This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
+Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
+\end{itemize}
+
+On the subject of PV system optimization technique, we will adopt here the intuitive method 
+since the average value daily of solar irradiance is used in the mathematical model, 
+without considering the battery's state of charge, or even the random nature 
+of solar irradiation and meteorological conditions. Therefore, all the computational 
+effort will be concentrated in our automated synthesis algorithm.
+
+Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
+
+Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
+Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
+Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
+Related to HOMER Pro:
+
+\begin{itemize}
+	\item HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER};
+	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
+	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
+However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
+	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
+	\item HOMER Pro do not have a explicit equipment called charge controller.
+It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
+During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
+	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
+By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
+For critical loads, 99\% is considered acceptable.
+While in a ordinary house electrical load, 95\% is considered acceptable;
+	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
+	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
+With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
+HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
+\end{itemize}

### 2019-07-01 Tex/Old text/chapters/chapter04.tex
thesis updated text

@@
-chapter04 here  dgfrty tyuj gfhj cb cvb cvb cvb cvb
+\section{Automated Verification}
+-----------------------------------------
+\subsection{Description of the Case Studies}
+%------------------------------------------
+%
+%We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
+We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
+%Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
+\begin{table}
+\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
+\begin{scriptsize}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\hline
+Item & House 1 & House 2 & House 3 & House 4 & House 5\\
+\hline
+\hline
+PV Panels &  \multicolumn{4}{|c|}{3x 325 W: in series} & 4x 325 W: 2x series, 2x parallel \\
+\hline
+Batteries & \multicolumn{4}{|c|}{\makecell{4x220 Ah: 2x series, 2x parallel\\ autonomy: 48 h}} & \makecell{4x 120 Ah batteries in series\\ autonomy: 6 h}\\
+\hline
+Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
+\hline
+Inverter & \multicolumn{4}{|c|}{700 W, peak of 1,600 W} & 1,200 W, peak of 1,600 W\\
+\hline
+Power demand & 253 W & 263 W & 283 W & 501 W & 915 W\\
+\hline
+GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
+\hline
+Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
+\hline
+\hline
+\end{tabular}
+\end{scriptsize}
+\end{table}
+%------------------------------------------
+\subsection{Objectives and Setup}
+\label{sec:setup}
+%------------------------------------------
+Our experimental evaluation aims to answer two research questions:
+%
+\begin{enumerate}
+\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
+\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
+\end{enumerate}
+
+%In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool.
+All the experiments were performed with a timeout of 14,400 seconds.
+%Every dweller, who owns a PV system, was interviewed
+%
+All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
+The setup of HOMER Pro v3.12.0: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
+The experiments were performed with timeout of 14,400 seconds.
+
+Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled; % with the goal of reducing memory usage; we have also used
+with SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+
+Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c -\phantom{}-unwind 100 -\phantom{}-trace}.
+
+% enabled with the goal of reducing memory usage; 
+%The experiments were performed without a predefined timeout.
+Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
+An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness.
+% enabled with the goal of reducing memory usage; 
+ %The experiments were performed without a predefined timeout.
+
+%------------------------------------------
+\subsection{Results and Discussion}
+\label{sec:results_indeed}
+%------------------------------------------
+%
+%\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
+%\begin{enumerate}
+%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
+%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
+%
+Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
+Note that an UNKNOWN result from our verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
+
+%HOMER Pro result: the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
+The simulation took less than five seconds to be performed on each case study.
+%
+\begin{table}
+\centering
+\caption{Summary of the case-studies comparative and the automated tools.}\label{cases}
+\begin{scriptsize}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\hline
+\multicolumn{5}{|c|}{Model Checker (SAT/UNSAT: time and message)}\\
+\hline
+Case &  \makecell{ESBMC 6.0.0\\(Boolector 3.0.1)} & \makecell {ESBMC 6.0.0\\(Z3 4.7.1)} & \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}\\
+\hline
+\hline
+House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 08 s \\(UNSAT)} & \makecell{19 m 02 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 27 s \\(UNSAT)} & \makecell{18 m 59 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 07 s \\(UNSAT)} & \makecell{18 m 39 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 37 s \\(UNSAT)} & \makecell{18 m 36 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+\hline
+House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{6 sec \\ (SAT line 337)}\\
+\hline
+\hline
+\end{tabular}
+\end{scriptsize}
+\end{table}
+
+The description of our experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
+
+Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3.
+The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet.
+Using ESBMC with Boolector led to an out of memory situation in all the case studies.
+This result was obtained in less than six minutes of execution, i.e., the 64 GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
+However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.
+Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s.
+However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
+This verification took less than 1 s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
+
+Concerning the CBMC tool, similar results were obtained, but with some slower time.
+The experimentation returned SAT or UNSAT to all the case studies.
+Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s.
+However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
+This verification took less than 1 s to be performed as well.
+
+Finally, the CPAchecker tool presented some different results.
+Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700 W systems.
+This is because the \textit{time out} limit was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
+However, when verifying the 1,200 W PV system, the tool presented a SAT message equal to the other engines.
+
+In order to validate the possible flaw from house 5, we have surveyed the owner of the 1,200 W system.
+We identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
+The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
+However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system %($96.67\% = 100\%-3.33\%$)
+and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
+%\begin{figure}[h]
+%\includegraphics[width=0.65\textwidth]{loadcurve.png}
+%\centering
+%\caption{Five weeks monitored load curve from House 1.}
+%\label{fig:loadcurve}
+%\end{figure}
+
+The same five case studies were evaluated by HOMER Pro (RQ2).
+The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues.
+The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system (RQ2).
+All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
+%Fig.
+\ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software, specifically to house 1.
+%
+%\begin{figure}[h]
+%\includegraphics[width=0.8\textwidth]{homer.png}
+%\centering
+%\caption{HOMER simulation screen.}
+%\label{fig:homerscreen}
+%\end{figure}
+%
+
+There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
+our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
+House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
+%
+%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
+Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions.
+The season has impact since the case studies are from the rain forest, where clouds are always present.
+As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
+%
+%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
+Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
+The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
+All the simulations took less than 5 seconds (each) to be performed.
+%
+%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
+The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
+That verification took 63.3 hours to be performed.
+Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
+That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
+The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
+The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
+The proposed tool took 409.3 hours to find this error at house 1.
+This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
+Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
+
+%At the terminal, the command used to perform the verification is:
+%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
+%
+%Where:
+%
+%\begin{itemize}
+%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
+%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
+%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
+%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
+There are other options, but this parameter is necessary because the complexity of the algorithms.
+The incremental SMT solving uses few RAM memory, compared with other SMT solving.
+%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
+The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
+%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
+%\end{itemize}
+%
+%\subsection{Experimental results}
+%\label{sec:results}
+%---------------------------------------------------
+\subsection{Threats to Validity}
+%---------------------------------------------------
+We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
+Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
+
+\textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
+The adoption of more complex models, or even an evaluation in a PV laboratory to validate the model could add more reliability to the results.
+
+\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.
+
+\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.
+
+\section{Optimization}
+This section presents the case studies used to evaluate our proposed approach. 
+We also compare our approach with a simulation tool, named HOME Pro. 
+The version and command-line of each verifier adopted, 
+the computing setup, the objectives of the experimental phase, 
+and the results itself are also described.
+
+%---------------------------------------------------------------------------
+\subsection{Case studies} 
+%---------------------------------------------------------------------------
+
+We have performed seven stand-alone PV system case studies to evaluate 
+our proposed synthesis approach, as described in the first column of 
+Table~\ref{tab1} (named Specification). These case studies were defined 
+based on usual electrical load found in riverside communities of the 
+Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}. 
+%
+\begin{table}
+\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
+\begin{scriptsize}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\hline
+Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
+\hline
+\hline
+Specification & Result & Result & Result & Result \\
+\hline
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\hline
+\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
+\hline
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
+\hline
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
+\hline
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
+\hline
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
+\hline
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+\hline
+\hline
+\end{tabular}
+\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
+\end{scriptsize}
+\end{table}
+
+%---------------------------------------------------------------------------
+\subsection{Tools} 
+%---------------------------------------------------------------------------
+
+Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
+Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
+The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
+
+%---------------------------------------------------------------------------
+\subsection{Setup} 
+%---------------------------------------------------------------------------
+
+All experiments regarding the verification tools were conducted 
+on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
+$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
+Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
+with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
+Our experiments were performed with a predefined timeout of $240$ minutes.
+
+%---------------------------------------------------------------------------
+\subsection{Objectives} 
+%---------------------------------------------------------------------------
+
+Our evaluation aims to answer two experimental questions:
+
+\begin{enumerate}
+
+\item[EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
+
+\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?
+
+\end{enumerate}
+
+%---------------------------------------------------------------------------
+\subsection{Results}  
+%---------------------------------------------------------------------------
+
+CPAchecker was able to synthesize the optimal sizing in six 
+out of seven case studies: the result was produced within 
+the time limit, which varied from $134.71$ to $235.75$ minutes. 
+Only case study $7$ led to a \textit{timeout} result, i.e., 
+it was not solved within $240$ minutes. However, if we remove 
+this timeout limitation from CPAchecker, the verifier is 
+able to solve the optimization in $44.97$ hours. 
+The violation (SAT result) indicated in Table~\ref{tab1} 
+is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
+%The results were tested by manual PV sizing and were sound (\textit{RQ1}).
+%, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
+
+CBMC and ESBMC are unable to produce any conclusive result. 
+Situations of \textit{internal failure}, \textit{timeout}, 
+or \textit{out of memory} occurred; this partially answers 
+the \textit{EQ2}. Note that the internal failure presented 
+by ESBMC was a Z3 solver issue (a bug); this will demand 
+an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
+if we remove the timeout from ESBMC with the SMT solver Boolector, 
+then the verifier is able to obtain the automated synthesis 
+in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.
+
+Related to HOMER Pro, it was able to evaluate six case studies, 
+and within a time shorter than $30$ seconds, which was much 
+faster than our automated synthesis tool (cf.~\textit{EQ2}). 
+Case study $3$ was not possible to be simulated since HOMER Pro 
+does not have the feature of adjusting the battery autonomy, i.e., 
+the tool always tries to feed with electricity the given load 
+during $365$ days/year. We have also noted other HOMER Pro drawbacks:
+
+\begin{itemize}
+\item There exists no explicit charge controller 
+as a system equipment. HOMER Pro includes automatically 
+a controller just to simulate the charge/discharge 
+of batteries and to meet the load requirement; however, 
+without costs or even with electrical characteristics 
+as maximum current and voltage, which are common during PV sizing;
+\item HOME Pro demands to include some battery specification 
+to initiate the optimization; however, it does not change 
+the electrical specifications during the simulation; 
+the presented results are multiples of the original 
+battery type suggested by the user. As example, it was 
+started with a $83.4$ Ah lead-acid battery and during 
+the simulation, HOMER Pro did not try to use other capacities or types;
+\item HOMER Pro does not present the optimal solution 
+in terms of connections of arrays of PV panels, just the 
+total in terms of power, i.e., it does not present neither models 
+and the power of each PV panel nor the total of panels in series or parallel. 
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Comparison between Formal Synthesis and HOME Pro}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Comparing the results between the formal synthesis with CPAchecker 
+and HOMER Pro, we observed that most results are quite similar, 
+in terms of technical solution and cost (cf. Table~\ref{tab1}).
+
+Particularly related to LCC, the cost was very close in cases 
+$1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
+Even adopting the same price per kW to the PV panels, 
+inverters, and batteries, HOMER Pro does not use costs 
+related to charge controllers, which were introduced into the 
+CPAchecker modeling. The premise used in CPAchecker to adopt 
+a fixed annual cost for operation and maintenance can produce 
+some impact as well at this discrepancy; however, it is not significant
+since this annual cost is too small when compared to the resulting LCC value.
+
+However, there exists a huge divergence in case study $2$, 
+where the costs presented by HOMER Pro were $54$\% higher 
+than our automated synthesis tool, probably because the 
+operation and maintenance costs assumed by our automated 
+synthesis tool were underestimated to that specific load.
+
+In general, the size of the PV panels and battery bank were 
+bigger in HOMER Pro than with our formal synthesis approach, 
+and that discrepancy is not easy to address without some real 
+systems validation. The mathematical models are different and 
+particular parameters can be tuned as well in each approach, 
+and that can justify the difference, which was presented in all 
+the case studies. As comparative, let's consider case study $1$: 
+the optimal solution provided by HOMER Pro demands $7$ $\times$ 
+more PV panels than the solution presented by our synthesis tool, 
+and HOME Pro does not show the arrangement of arrays 
+(i.e., the number of series and parallel PV panels); 
+the battery bank presented by HOMER Pro provides $500.4$ Ah 
+of capacity ($6 \times 83.4$), while our synthesis tool 
+presented an optimal solution with $420$ Ah of total capacity 
+($4 \times 105$).
+
+Just to compare the results obtained from the optimization 
+with the real-world, the authors had four PV systems deployed 
+and monitored since June $2018$ in a riverside community 
+in the Amazonas State in Brazil, with similar demands 
+presented by case studies $1$, $4$, $5$, and $6$, 
+always with a $3$ $\times$ $325$ W ($3$S) panels and 
+$4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) 
+lead-acid batteries. These solutions are more close 
+to the result presented by our formal synthesis 
+approach than HOMER Pro, thereby showing that our 
+solution is sound, which answers \textit{EQ1}.
+
+Related to the inverters, HOMER Pro suggests a value in 
+kW very close to the peak of every case study, and it 
+is just a reference value and not a commercial value of 
+the employed inverter. Our synthesis tool, however, 
+presents inverters that are commercial and can be found 
+off-the-shelf. Therefore is a PRO to the formal synthesis method.
+
+Concerning to charge controllers, as we reported in 
+the previous section, HOMER Pro does not include it 
+as an explicit equipment in its mathematical model, 
+only our synthesis tool presents a commercial controller 
+and includes it during the cost analysis. Therefore, 
+the formal synthesis method presents more reliable results than
+HOME Pro.
+
+Case study $7$ was not solved by our synthesis tool 
+within the time limit established during the experimental 
+phase. Case study $3$ was not possible to simulate in HOMER Pro, 
+because its restriction does not allow one to set the battery autonomy, 
+thus resting both without parameters to comparative.
+
+Summarizing, our synthesis tool is capable to present a 
+solution, which is far detailed and close to the commercial 
+reality than the solution presented by HOMER Pro. 
+In particular, our automated synthesis method 
+can provide all the details of every component of 
+a PV system solution, with complete electrical details 
+from data sheet of manufacturers, including 
+the model of the component, nominal current and voltage. 
+In this respect, even the name of the manufacturer 
+can be presented (in Table~\ref{tab1} it was removed 
+to avoid some advertising).
+%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Threats to validity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We have reported a favorable assessment of our formal synthesis method. 
+Nevertheless, we have also identified three threats to the validity 
+of our experimental results, which can be further assessed and 
+constitute future work: ($1$) improvement of the power reliability 
+analysis: to include loss of load probability or loss of power 
+supply probability, which can make the analysis more accurate; 
+($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
+however, a broad analysis from other isolated areas must be 
+performed in order to make the optimization general in terms 
+of applicability; ($3$) to deploy at the field some PV systems 
+sized using our synthesized results in order to validate it.

### 2019-07-01 Tex/Old text/chapters/introduction.tex
thesis updated text

@@
 
-\subsection{Problem's Definition}
+\section{Problem's Definition}
 
@@
 
-\subsection{Objectives}
+\section{Objectives}
 In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used.
@@
 
-\subsection{Contributions}
+\section{Contributions}
 This paper makes two main contributions.
@@
 
-\subsection{Related Work}
+\section{Related Work}
 
@@
 
-\subsection{Thesis Organization}
+\section{Thesis Organization}
 Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.

### 2019-07-02 Tex/Old text/fichacatalog.tex
thesis updated text

--- 2019-07-01 Tex/Old text/abstract.tex
@@
 \begin{center}
-    \Large
-    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
-
-    \vspace{0.4cm}
-    \large
-    Optimal Sizing and Project Validation
-
-    \vspace{0.4cm}
-    \textbf{Alessandro Trindade}
-
+%    \Large
+%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
+%    
+%    \vspace{0.4cm}
+%    \large
+%    Optimal Sizing and Project Validation
+%    
+%    \vspace{0.4cm}
+%    \textbf{Alessandro Trindade}
+%    
     \vspace{0.9cm}
-    \textbf{Abstract}
+    \textbf{Ficha Catalográfica}
 \end{center}
-verif:
-With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
-In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals.
-Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
-Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-Automated verification using model checking has proven to be an effective technique to validate any kind of system.
-This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Different verification tools were evaluated as well, in order to compare performance and soundness.
-Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
-
-synthesis:
-There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space.
-We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
-If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
-Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach.
-
-\textit{Keywords}: Formal verification; automated verification; model checking; program synthesis; electrical systems; solar photovoltaic systems
+\thispagestyle{plain}
+Ficha catalog aqui

### 2019-07-02 Tex/Old text/main.tex
thesis updated text

@@
 \usepackage{graphicx}
+\usepackage{algorithm,algorithmic}
+\usepackage{xcolor}
 %Alessandro input: makecell package to permite line break inside tables
@@
 \pagestyle{fancy}
-\fancyhead{}
-\fancyhead[RO,LE]{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
-\fancyfoot{}
-\fancyfoot[LE,RO]{\thepage}
-\fancyfoot[LO,CE]{Chapter \thechapter}
-\fancyfoot[CO,RE]{Alessandro Trindade}
+%
 \renewcommand{\headrulewidth}{0.4pt}
@@
 
+\input{2ndcover}
+\thispagestyle{empty}
+\pagenumbering{gobble}
+
+\input{fichacatalog}
+%\thispagestyle{empty}
+\newpage
+
 \input{abstract}
+\pagestyle{empty}
+%\thispagestyle{empty}
+
+\input{resumo}
+%\thispagestyle{empty}
 
@@
 \chapter*{Acknowledgements}
-I want to thank...
+It is not possible to get here without the help of several people. I hope I have not forgotten any and do no wrong.
+
+I would like to thank God (for the gift of life); Solange and Louise (without the patience and support of my family I could not be here); my parents and grandparents; Lucas (for having believed in me and for the patience); the Electricity Department at UFAM (for the support); Professors Feitosa and Barreto from IComp (support and advice); secretary people from IComp (for the support); the financial support from FAPEAM, British Council/Newton Fund and Fundação Amazonas Sustentável; and Coventry University team (Elena, Kojo, and for the opportunity to use field deployed photovoltaic solar systems).
+
+\pagestyle{empty}
 
@@
 \chapter{Introduction}
+\pagenumbering{arabic}
+\pagestyle{fancy}
+\fancyhead{}
+\fancyhead[RO,LE]{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
+\fancyfoot{}
+\fancyfoot[LE,RO]{\thepage}
+\fancyfoot[CO,CE]{Chapter \thechapter}
+\fancyfoot[LO,RE]{A. B. Trindade}
+\renewcommand{\headrulewidth}{0.4pt}
+\renewcommand{\footrulewidth}{0.4pt}
 \input{chapters/introduction}
@@
 
-\chapter{Experimental Evaluation}
+\chapter{Results}
 \input{chapters/chapter04}
@@
 \chapter{Conclusion and Future Work}
+\fancyfoot[CO,CE]{Conclusion and Future Work}
 \input{chapters/conclusion}
@@
 \chapter{Appendix Title}
+\fancyfoot[CO,CE]{Appendix}
 \input{chapters/appendix}
 
+\fancyfoot[CO,CE]{Bibliography}
 %\printbibliography

### 2019-07-03 Tex/Old text/abbreviations.tex
thesis updated text

--- 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
@@
-\documentclass[review]{elsarticle}
+\thispagestyle{plain}
+\begin{center}
+%    \Large
+%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
+%    
+%    \vspace{0.4cm}
+%    \large
+%    Optimal Sizing and Project Validation
+%    
+%    \vspace{0.4cm}
+%    \textbf{Alessandro Trindade}
+%    
+    \vspace{0.9cm}
+    \textbf{List of Abbreviations, Units and NomenclatureList of Abbreviations, Units and Nomenclature}
+\end{center}
 
-\usepackage{lineno,hyperref}
-\modulolinenumbers[5]
-
-\journal{Renewable \& Sustainable Energy Reviews}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-%\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%packages to makecell, algorithm, not inclueded with Elsevier
-\usepackage{makecell}
-\usepackage{algorithm,algorithmic}
-%\algsetup{linenosize=\small}
-\graphicspath{ {./images/} }
-\usepackage{amsmath}
-\usepackage{xcolor}
-
-\begin{document}
-
-\begin{frontmatter}
-
-%\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
-\title{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}
-%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
-
-%% Group authors per affiliation:
-%\author{Alessandro Trindade\fnref{myfootnote}, Lucas Cordeiro}
-%\address{Radarweg 29, Amsterdam}
-
-%% or include affiliations in footnotes:
-\author[mymainaddress]{Alessandro Trindade\corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Corresponding author}
-\ead{alessandrotrindade@ufam.edu.br}
-%\ead[url]{www.elsevier.com}
-
-\author[mysecondaryaddress]{Lucas Cordeiro}
-
-\address[mymainaddress]{Federal University of Amazonas, Av. Rodrigo Octávio, 6200, Coroado I, 69077-000 Manaus-AM-Brazil}
-\address[mysecondaryaddress]{University of Manchester, School of Computer Science, Kilburn Building, Manchester M13 9PL}
-
-\begin{abstract}
-With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
-In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals.
-Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
-Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-Automated verification using model checking has proven to be an effective technique to any kind of program verification.
-This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Different verification tools were evaluated as well, in order to compare performance and soundness.
-Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
-\end{abstract}
-
-\begin{keyword}
-Formal verification \sep model checking \sep photovoltaic power systems \sep power system modeling \sep solar power generation
-%\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
-%\MSC[2010] 00-01\sep  99-00
-\end{keyword}
-
-\end{frontmatter}
-
-\section*{List of Abbreviations, Units and Nomenclature}
 \noindent $a$ Ideality or quality factor \\
@@
 $\eta_{p}$ PV panel efficiency \\
-
-%\linenumbers
-
-\section{Introduction}
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
-The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
-Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
-Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
-
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
-
-%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
-%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
-%
-%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
-Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
-However, this growth is not driven by isolated systems.
-
-In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
-%
-%However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
-%
-%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
-In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
-SPV...
-%
-%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
-Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-%
-%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
-%
-%PV systems can be classified into grid-connected and stand-alone systems.
-At this proposal, only off-grid or stand-alone systems will be considered.
-The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-However, those tools are based on running experiments in simulation models.
-Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-
-Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
-%with behavior that is, in principle, well determined. 
-Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
-%User or project requirements can be added during the creation of the formal model to be verified.
-%, as defined by \cite{Trindade}.
-%
-%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
-% Their aim is to establish system correctness with mathematical rigor. 
-%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
-% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
-%
-%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
-%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
-%Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
-%
-%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
-%
-In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is created.
-The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
-The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process.
-The model checking tool reports in which conditions a system does not meet the user requirements.
-A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}.
-%Those programs are viewed as mathematical objects, and the use of 
-%Bringing this technique to solar PV systems, i
-%Instead of finding a bug or a software inconsistence, t
-%Here it will be verified a stand-alone PV system, with all their components modeled mathematically,   
-%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the proposed tool is carried out by means of an algorithm written in language C, that is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
-%three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
-%, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
-
-In prior studies, the evaluation of PV systems w.r.t.
-user requirements were performed by simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}.
-Related to formal methods, studies were carried out toward the modeling of power smart grids~\cite{Akram2018} and solar panels~\cite{Driouich2017}; however, those studies do not perform automated verification.
-%
-In addition, recent research performed a formal study of PV farms, where the focus has been the interaction with the grid~\cite{Abate2017}; or to model a PV system and to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}.
-Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.
-
-%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool.
-%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
-This paper makes three original contributions.
-% Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
-Secondly
-Firstly, we propose an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system.
-Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies.
-Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation.
-
-%\textcolor{red}{This introduction is missing the description of the vision, approach and results.
-In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
-%
-%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
-
-\textit{Outline}.
-Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
-Section~\ref{sec:AutomatedVerification} presents the automated verification technique.
-Section~\ref{sec:sizingcheck} shows how to perform the sizing of a stand-alone PV system.
-The methodology is presented in section~\ref{sec:Methodology}.
-Section~\ref{sec:results} is devoted to the results.
-Section~\ref{sec:Conclusions} presents the conclusion and describes future work.
-
-%--------------------------------------------------------
-\section{Solar Photovoltaic System }
-\label{sec:SolarPhotovoltaicSystem}
-%--------------------------------------------------------
-
-%According to \cite{Roy}, a 
-%A PV system is designed to give the electric supply to a load.
-This load can be either Alternate Current (AC) or Direct Current (DC) type.
-Electric supply can be needed either in daytime or evening time.
-%(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
-%For night hours or rainy days, one needs to hold batteries, where power can be stored and used.% \cite{Gules}.
-
-PV systems are classified into distinct types~\cite{Mohanty}.
-%: (1) stand-alone systems, where the energy is generated and consumed in the same place and which do not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system.
-%, where another source(s) of energy can work together with the solar PV.
-% system to provide the required demand.
-%, such as wind, biomass or diesel, 
-%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
-%
-%\begin{itemize}
-%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
-Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants;
-%\item Grid-connected systems, where the solar PV system is connected to the grid.
-The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards.
-Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode;
-%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
-In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
-%\end{itemize}
-Specifically for remote rural areas of developing countries or places where the grid extension is not feasible, 
-%stand-alone systems are one the most used solutions, and 
-% depending on the type of load, cost, resources availability, and requirements of the load, 
-%stand-alone systems 
-%can be split into several categories. However, 
-the most suitable configuration is the regulated stand-alone system with battery and AC load; this configuration is the focus of this study.
-%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
-%PV array, battery, MPPT and AC load.
-Battery is used to store the extra power of PV system.
-A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
-Extra charging and deep discharging can reduce the battery life \cite{Kim}.
-Because of the AC load, an inverter (DC to AC converter) is required.
-%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
-%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.
-
-%\subsection{Unregulated stand-alone PV system with DC load }
-%Usually this type of system is for low power applications, as defined by \cite{Roy}.
-The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:standaloneSPV} letter (a).
-At night hours, the system will not provide any supply because of the absence of the battery.
-
-%\begin{figure}[h]
-%\includegraphics[width=0.5\textwidth]{reg_unreg4.png}
-%\centering
-%\caption{PV stand-alone systems: (a) regulated stand-alone SPV system with DC load; (b) regulated stand-alone SPV system with DC load; (c) regulated stand-alone SPV system with battery DC load; and (d) regulated stand-alone system with battery and AC load  (Source: \cite{Roy}).}
-%\label{fig:standaloneSPV}
-%\end{figure}
-
-%\subsection{Regulated stand-alone PV system with DC load}
-%It is similar to unregulated stand-alone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:standaloneSPV} letter (b).
-Usually system with MPPT should have battery; otherwise, extra power will be waste.
-
-%\subsection{Regulated stand-alone system with battery and DC load}
-%Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:standaloneSPV} letter (c).
-Battery is used to store the extra power of PV system.
-A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
-Extra charging and deep discharging can reduce the battery life \cite{Kim}.
-
-%According to \cite{Pinho}, PV systems that are used to feed loads with low variation on the consumption can be sized to operate without the controller.
-That is called of self-regulated stand-alone PV system with battery.
-However, the voltage from the PV panel must be compatible with the batteries voltage.
-Normally, the bank of batteries are oversized related to the PV panel and to the load.
-The drawback is the operation of the batteries, normally overloaded or with excessive discharges (that can damage the batteries).
-
-%\subsection{Regulated stand-alone system with battery and AC load}
-%This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:standaloneSPV} letter (d).
-This solution has an increase of cost because has more equipments.
-However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-That configuration is the focus of the present work since it is the most common nowadays all over the world, when off-grid or isolated regions is the target.
-
-\subsection{Design and Simulation of Solar PV systems}
-%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
-%
-%In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
-%public domain and commercial software available for the PV market. 
-%According to \cite{Brooks}, t
-%%%%%%%%%%The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
-% to complex financial analysis and project optimization. 
-%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-%
-%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-Here we evaluated the most popular tools available in the literature and summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
-
-%\subsection{PVWatts Calculator}
-%According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
-According to \cite{NRELDobos}, to use the calculator, it is necessary to provide information about the system's location, basic design parameters, and system economics.
-PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity monetary value.
-This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules.
-The production estimates that PVWatts computation do not account for many factors that are important in the design of a photovoltaic system, therefore it is necessary support of an energy expert.
-The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year.
-To represent the system's physical characteristics, PVWatts requires values for six inputs: System DC size; Module type; Array type; System losses; Array tilt angle; Array azimuth angle.
-%
-%\subsection{SAM}
-%SAM or System Advisor Model is a software from the U.S.
-Department of Energy and National Renewable Energy Laboratory.
-According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications, and (also) to provide information for readers who do not plan to use the model, but want to learn about its capabilities.
-SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: Project managers and engineers; Financial and policy analysts; Technology developers; and Researchers.
-SAM makes performance predictions and cost of energy estimates for grid-connected power projects based on installation and operating costs and system design parameters that you specify as inputs to the model.
-Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement.
-SAM is an electric power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet electric load.
-It does not model thermal energy systems that meet a thermal process load.
-As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.
-%
-%\subsection{HOMER}
-%As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
-HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources.
-HOMER Legacy is the original HOMER software version created at the National Renewable Energy Laboratory (NREL).
-HOMER Legacy is a free computer model that simplifies the task of evaluating design options for both off-grid and grid-connected power systems for remote, stand-alone, and distributed generation applications.
-HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options.
-Since 2016 HOMER Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available.
-At the short-time only the commercial version will remain.
-%
-%The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
-HOMER Pro put together three tools in one product: optimization, simulation, and sensitivity analysis.
-HOMER Pro provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use.
-It is adaptable to a wide variety of projects.
-For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project.
-For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations.
-Chronological simulation is essential for modeling variable resources, such as solar and wind power and for combined heat and power applications, where the thermal load is variable.
-HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.
-%
-%\subsection{RETScreen}
-%As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
-%
-%RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options.
-The software can be used to evaluate benefits from both clean energy production from power generation projects and savings through energy efficiency projects, accounting for project costs, greenhouse gas emission reductions, and financial risk.
-The software is freely distributed (but with restrictions to save work or print), and had three different versions:
-%
-%\begin{itemize}
-%\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
-%\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
-%\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
-However, this version works is only Windows-based.
-This version has a complete paid version, in an annual subscription way.
-%\end{itemize}
-%
-%As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
-It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
-RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.
-%
-%\subsection{Hybrid2}
-%The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
-Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
-Variations in wind speed and in load within each time step are factored into the performance predictions.
-The code does not consider short-term system fluctuations caused by system dynamics or component transients.
-This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, what is a limitation.
-%
-%Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where 
-As highlights, only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription typically range from US\$504.00 to US\$657.00.
-
-\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Comparative coverage of reference software}
-\label{table:softwares}
-\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-\begin{tabular}{c | c | c | c | c | c}
-\hline
-\hline
-Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen} & \rotatebox{90}{Hybrid2}\\
-\hline
-\hline
-Support & X & X & X & X &  \\
-\hline
-Off-grid systems &   &   & X & X & X\\
-\hline
-Hybrid systems &  &  & X & X & X\\
-\hline
-Photovoltaics & X & X & X & X & X\\
-\hline
-Batteries &  &  & X &  & X\\
-\hline
-\makecell{Main technical (T) \\ or economical(E)} & T & T & E & E & T \\
-\hline
-Optimization &  &  & X & X &  \\
-\hline
-Sensitive analysis &  &  & X & X & \\
-\hline
-\hline
-\end{tabular}
-\end{table}
-
-%-------------------------------------------------------------------
-%\subsection{Paper Proposal x Reference Tools}
-%-------------------------------------------------------------------
-%
-In this study, only HOMER has the minimum features for a comparative with our proposed verification approach.
-That evaluation is presented in Section~\ref{sec:results_indeed}.%All tools need some parameters inherently from manufacturer's catalog.
-%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
-%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-%Thus, the main challenge here is to demonstrate the application of software model checking to formally verify a stand-alone PV solution, thus proving that this approach is more effective and complete than other state-of-the-art tool such as HOMER Pro.
-The comparative evaluation between HOMER Pro and our approach is presented in Section~\ref{sec:results_indeed}.
-%
-%-------------------------------------------------------------------
-\subsection{Component models for a stand-alone PV system }
-%-------------------------------------------------------------------
-%The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
-%The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
-It identifies the PV generator, batteries, charge controller, inverter, and AC load.
-A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-The PV generator (panel or array) is a semiconductor device that can convert solar energy into DC electricity.
-%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
-For night hours or rainy days, we need to hold batteries, where power can be stored and used.
-The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
-The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
-%
-%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
-%
-\begin{figure}[h]
-\includegraphics[width=0.80\textwidth]{blockdiagramPVS2}
-\centering
-\caption{Block diagram for a typical stand-alone PV system (adapted from~\cite{Hansen}).}
-\label{fig:blockdiagram}
-\end{figure}
-%
-%In the literature, there are several mathematical models available for each component of PV systems. At the next section, the mathematical model for each component is presented. 
-%-------------------------------------------------------------------
-\subsection{PV generator model}
-\label{sec:PVmodel}
-%-------------------------------------------------------------------
-%A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
-%In the present modeling, the focus is only on cell/module/array.
-%
-%%%%%%The basic element of a PV system is a PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
-%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
-When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}.
-If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
-%%%%%To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
-%%%%%package called panel or module. 
-%For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
-In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}.
-The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{celmodarray}
-%\centering
-%\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
-%\label{fig:celmodarray}
-%\end{figure}
-%
-%%%%%The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on meteorological conditions.
-%the meteorological conditions of the area to be serviced by PV solution. %However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
-%, which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
-The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
-However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
-%
-%These uncertainties lead to either over- or underestimation of energy yield from PV modules.
-An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
-The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
-%
-%Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
-However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage.
-Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
-% 
-%Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
-A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves).
-However, the present work will rely on the simplified model of 1-diode.
-It was demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-
-%The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-%is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
-%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
-\begin{figure}[h]
-\includegraphics[width=0.40\textwidth]{equivckt1D}
-\centering
-\caption{1-diode equivalent PV cell/panel circuit model (adapted from~\cite{Cubas}).}
-%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
-\label{fig:equivckt}
-\end{figure}
-
-The 1-diode model, illustrated in Fig.
-\ref{fig:equivckt}, whose equation relates the output current, $I$, to the output voltage, $V$, is described by ~\eqref{eq:1diodemodel}.
-%This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-%In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
-\begin{equation}
-\label{eq:1diodemodel}
-I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right], 
-\end{equation}
-
-\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
-$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).
-
-%\begin{itemize}
-%\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
-%\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
-%\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed; $ N=1 $ in a single cell configuration.
-%	\begin{itemize}
-%	\item $ N=1 $ in a single cell configuration. 	
-%	\end{itemize}	  
-%\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes.
-%	\begin{itemize}
-%	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
-%	\end{itemize}
-%\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
-%	\begin{itemize}
-%	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
-%	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
-%	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
-%	\end{itemize}	 
-%\end{itemize}
-%
-%This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.
-%
-%The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}. 
-%
-%\begin{equation}
-%\label{eq:1d1rmodel}
-%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
-%\end{equation}
-%
-%Where $R_{s}$ is the series resistor.
-%
-%At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
-%
-%The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}. 
-%
-%\begin{equation}
-%\label{eq:1d2rmodel}
-%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-%\end{equation}
-%
-%Where $R_{sh}$ is the shunt resistor.
-%
-%At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
-%
-%And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}. 
-%
-%\begin{multline}
-%\label{eq:2d2rmodel}
-%I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - \\ %I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-%\end{multline}
-%
-%This model has six unknown parameters with two exponential terms. 
-%Briefly, both single and double diode models require the knowledge of all unknown parameters, which is usually not provided by manufacturers.
-Nevertheless, the current-voltage equation is a transcendental expression \cite{Jakhrani}.
-%
-%However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel. 
-%
-%For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
-The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
-However, due to implicit nature and nonlinearity of PV cell or module characteristics, it is hard to find out the analytical solution of all unknown parameters, as described by \cite{Hasan}.
-Thus, numerical methods such as Newton-Raphson method or Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}.
-This happens because numerical methods give approximate solution of the nonlinear problems without searching for exact solutions.
-However, numerical methods are time consuming and need long term time series data, which is not available in developing countries.
-\cite{Jakhrani} did a mixed methodology using analytical and numerical steps together.
-\cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation (essays).
-And \cite{Tian} did a mix of analytical and experimental methodology to get the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use experimental technique.
-%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
-%The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
- %
-%\subsection{PV Panel Model}
-%With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
-%
-%A single-diode without series and shunt resistances is considered. 
-%%%%%%%Eq.~\eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
-% shown in Fig. \ref{fig:ivcurve}.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{ivcurve}
-%\centering
-%\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
-%\label{fig:ivcurve}
-%\end{figure}
-%
-%Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
-%\begin{equation}
-%\label{eq:Isc}
-%I_{sc}=I_{ph}\vert_{V=0}
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Voc}
-%V_{oc}=\dfrac{aNk_{B}T}{q}ln\left( 1+\dfrac{I_{sc}}{I_{0}} \right) 
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:exp}
-%exp\left( \dfrac{qV_{oc}}{aNk_{B}T} \right) = \left(1+\dfrac{qV_{m}}{aNk_{B}T} \right) exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) 
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Im}
-%I_{m} =I_{ph}-I_{0}\left[ exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) -1 \right] 
-%\end{equation}
-%
-%Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way. 
-%
-%A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}. 
-%These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig.
-\ref{fig:ivcurve}, where the transition is a compromise between both behaviors.
-It is interesting to observe that the maximum power point corresponds to a trade-off condition, where the current is still high enough before it starts decreasing with increasing the output voltage (Fig.
-\ref{fig:ivcurve}).
-%
-%Based on this, the tangent of the I-V curve can be used to evaluate the transition between current- to voltage-source controlled regions; this operation yields Equation \ref{eq:didv}.
-%
-%\begin{equation}
-%\label{eq:didv}
-%\dfrac{dI}{dV}=-\dfrac{qI_{0}}{aNk_{B}T}exp \left( \dfrac{qV}{aNk_{B}T}  \right) 
-%\end{equation}
-%
-%The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell.
-Therefore, the Equation \ref{eq:Vmderiv} is generated.
-%
-%\begin{equation}
-%\label{eq:Vmderiv}
-%V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
-%\end{equation}
-%
-%It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point.
-The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change on $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}.
-Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation \ref{eq:Vmderiv} can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
-%
-%\begin{equation}
-%\label{eq:dIdV_Vm}
-%\dfrac{dI}{dV}\vert_{V_{m}} \cong -\dfrac{0-I_{sc}}{V_{oc}-0}=\dfrac{I_{sc}}{V_{oc}}
-%\end{equation}
-%
-%Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, 
-%
-The voltage and the current at the maximum power point tracking (MPPT), can be described by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm}  as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
-\begin{equation}
-\label{eq:Vmfinal}
-V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right). 
-\end{equation}
-
-\begin{equation}
-\label{eq:Imfinal}
-I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right).  
-\end{equation}
-
-\begin{equation}
-\label{eq:Pm}
-P_{m} = V_{m} I_{m}.
-\end{equation}
-
-%\begin{multline}
-%\label{eq:Pm}
-%P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
-%\end{multline}
-%
-However, the photo-current delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, ~\eqref{eq:Iph} is used to calculate the photo-current as function of irradiance and temperature~\cite{Villalva}:
-\begin{equation}
-\label{eq:Iph}
-I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right], 
-\end{equation}
-
-\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions
-(provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Villalva} that is provided by PV manufacturers ($ I_{sc,ref} $).
-%\cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
-%%
-The cell temperature ($ T $) in degree Celsius is described by ~\ref{eq:Tcell}~\cite{Ross}:
-\begin{equation}
-\label{eq:Tcell}
-T = T_{air} + \dfrac{NOCT-20}{800}G,
-\end{equation}
-
-\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet \cite{Ross}, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
-
-Furthermore, ~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\cite{Villalva} 
-%In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
-
-\begin{equation}
-\label{eq:I0}
-I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1},
-\end{equation}
-
-\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
-
-%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current (cf.
-~\eqref{eq:Imfinal}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor~\cite{Saloux} is determined by ~\eqref{eq:a}:
-\begin{equation}
-\label{eq:a}
-a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) },
-\end{equation}
-
-\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions.
-%, usually provided by manufacturers; t
-
-The PV generator model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers in data-sheets or manuals.
-%
-%If the PV cells are in parallel, then there is a parallel array.
-Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
-%
-%\begin{equation}
-%\label{eq:Iarray}
-%I_{array} = (N_{cells in parallel})(I_{one cell})
-%\end{equation}
-%
-%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
-%
-%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
-%
-%\begin{equation}
-%\label{eq:Varray}
-%V_{array} = (N_{cells in series})(V_{one panel})
-%\end{equation}
-%
-%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
-%------------------------------------------------------------
-\subsection{The Battery Storage Model }
-\label{sec:BATmodel}
-%------------------------------------------------------------
-
-%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system.
-Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery.
-During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.
-
-Various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Pinho};
-%, and \cite{Manwell93, Manwell94}. 
-%However, regardless of the model, normally the following parameters are required: 
-%
-%\begin{itemize}
-%\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
-%, under predetermined discharge conditions.
-%\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
-%Obviously $ 0<SOC<1 $. 
-%If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
-%\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
-%It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
-%\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
-%\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
-%\end{itemize}
-%
-%The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
-The battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
-LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.
-%
-%In general, the battery models view the battery as a voltage source $ E $ in series with an internal resistance $ R_{0} $, as shown in Fig. \ref{fig:batteryckt}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{batteryckt}
-%\centering
-%\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
-%\label{fig:batteryckt}
-%\end{figure}
-%
-%The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.  
-%
-%Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
-%
-%The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.  
-%
-%The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
-However, it uses some data extracted from tested batteries in laboratory.
-Therefore is not suitable to this study.
-%
-that kind of battery has relative low cost and wide availability~\cite{Copetti}. 
-%
-Here, the model adopted uses only manufacturer's data without empirical tests~\cite{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature. 
-%
-The discharge voltage equation is described by \eqref{eq:bat_Vd}.
-%The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
-%
-\begin{multline}
-\label{eq:bat_Vd}
-V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T),
-\end{multline}
-
-\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $%, $ T_{ref}=25^{o}C $
-), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time.
-Mathematically, it is the ratio between the present capacity and the nominal capacity% (in $ Ah $, provided by manufacturer)
-. If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
-%\begin{equation}
-%\label{eq:SOCbat}
-%SOC = \left( 1 - \dfrac{Q}{C} \right) 
-%\end{equation}
-%
-%Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
-%
-%The ratio between $ Q $ and $ C $ represents t
-The depth of discharge ($DOD$) or the fraction of discharge, is $DOC=1-SOC$.
-
-%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
-This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
-%
-%\begin{equation}
-%\label{eq:CC10}
-%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
-%\end{equation}
-%
-%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
-For the charging process, however, the parameters are described by ~\eqref{eq:Vcbat} as
-%
-\begin{multline}
-\label{eq:Vcbat}
-V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
-\end{multline}
-
-Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period.
-%; however, during recharge it is much more difficult \cite{Copetti}.
-%Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell.
-The efficiency drops to zero at full charge and the function that represents the charge efficiency ($ \eta_{c} $) variation with state of charge and current rate is given in Equation \ref{eq:efficcharge}.
-%\begin{equation}
-%\label{eq:efficcharge}
-%\eta_{c} = 1 - exp \left[ \dfrac{20.73}{\dfrac{I}{I_{10}}+0.55} (SOC-1) \right] 
-%\end{equation}
-%
-%\cite{Copetti} show that, 
-%During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (\ref{eq:Vec}).
-It was created a function for the gassing voltage as well, as shown in (\ref{eq:Vg}).
-In addition, the overcharge phenomenon can be represented by (\ref{eq:Voverc}).
-%\begin{equation}
-%\label{eq:Vec}
-%V_{ec} = \left[ 2.45 + 2.011 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Vg}
-%V_{g} = \left[ 2.24 + 1.97 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-%\end{equation}
-%
-%\begin{multline}
-%\label{eq:Voverc}
-%V_{c} = V_{g} + (V_{ec} - V_{g}) \\ \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
-%\end{multline}
-%
-%Where $ Ah_{restored} $ represents the Ampere-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
-%
-%The function assumes that 95\% of the capacity was already restored at the start of overcharge.
-%
-%The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by (\ref{eq:tau}).
-%\begin{equation}
-%\label{eq:tau}
-%\tau = \dfrac{17.3}{1+852 \left( \dfrac{I}{C_{10}} \right) ^{1.67} }
-%\end{equation}
-%
-%Therefore, to model the voltage ($ V_{c} $) evolution of the battery, (\ref{eq:Vcbat}) can be used up the start of gassing ($ V_{c} \leq V_{g} $).
-And during overcharging ($ V_{c} > V_{g} $), (\ref{eq:Voverc}) can be used until a constant final voltage ($ V_{ec} $) is reached.
-%
-%The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
-%
-%\begin{equation}
-%\label{eq:stor}
-%Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
-%\end{equation}
-%
-%Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
-%
-%As an example of this formula application, as shown by \cite{Abdulateef}, considering that a stand-alone PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
-%
-%Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$.
-Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$).
-If a single battery of 12 V and 350 Ah is considered, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
-%
-%At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature.
-The equations are used to update the $SOC$ of the batteries, and have the number of hours ($ Num_{h} $) as a variable.
-There is a factor (1.15) which is present at the charging equation, and is necessary to express that during the charging process is usual to reach 115\% of the battery capacity
-%
-%\begin{multline}
-%\label{eq:charge}
-%SOC_{charge} = SOC_{previous} + \\ \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
-%\end{multline}
-%
-%\begin{multline}
-%\label{eq:discharge}
-%SOC_{discharge} = SOC_{previous} - \\ \dfrac{100*I_{drained}*Num_{h}}{capacity}
-%\end{multline}
-%
-%
-%---------------------------------------------------------
-\subsection{Charge Controller Model}
-%---------------------------------------------------------
-%Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
-However, in this study, in order to simplify, the term used is controller.
-The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power.
-Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
-%
-%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
-%
-%
-%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components.
-The use of battery as a storage form implies thus the presence of a charge controller.
-%
-%%%%%%%%%%In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
-%
-%The controller allows the management of energy between the load and the battery \cite{Mellit}. 
-%The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
-The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
-
-To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \_ off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}.
-PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \_ on} $.
-%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{controllerover}
-%\centering
-%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
-%\label{fig:controllerover}
-%\end{figure}
-%
-In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \_ off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}.
-The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \_ on}$.
-%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{controllerdisc}
-%\centering
-%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
-%\label{fig:controllerdisc}
-%\end{figure}
-%
-%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
-%
-The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.
-
-\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process (adapted from~\cite{Hansen})}
-\label{table:controller}
-\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-\begin{tabular}{c | c | c }
-\hline
-\hline
-Step  & Constraint & Command\\
-\hline
-\hline
-(1) & \makecell{If $V > V_{max \_ off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
-\hline
-(2) & \makecell{If command (1) is \\done and $V < V_{max \_ on}$} & \makecell{Reconnect PV array \\to the system}\\
-\hline
-(3) & \makecell{If $V < V_{min \_ off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
-\hline
-(4) & \makecell{If command (3) is \\ done and $V > V_{min \_ on}$} & \makecell{Reconnect the load \\to the system}\\
-\hline
-\hline
-\end{tabular}
-\end{table}
-
-%Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage. 
-%
-%As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of controller is given by \eqref{eq:poutcont}.
-\begin{equation}
-\label{eq:poutcont}
-P_{in} \eta_{c} = P_{out}.
-\end{equation}
-
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from \eqref{eq:poutcont} we compute \eqref{eq:potcont}.
-\begin{equation}
-\label{eq:potcont}
-V_{in} I_{in} \eta_{c} = V_{out} I_{out},
-\end{equation}
-
-\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
-
-%The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}). 
-% 
-%A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
-In addition, there is the Cuk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.
-%
-%For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.
-%
-%\begin{equation}
-%\label{eq:voutvin}
-%\dfrac{V_{out}}{V_{in}} = \dfrac{D}{D-1}
-%\end{equation}
-%
-%Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
-% 
-%The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
-%  
-%Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.
-% 
-%As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
-
-%The number of controllers required for the stand-alone PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
-In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
-%\begin{multline}
-%\label{eq:numberofcmin}
-%number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \\ \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
-%\end{multline}
-%
-%\begin{equation}
-%\label{eq:numberofc}
-%N_{controller} \geq number_{controllers}
-%\end{equation}
-%
-%\subsection{Joint work: charge controller and batteries}
-%When batteries are charged, they go through three main different states - bulk, absorption and float, with impact to the inverter and to power supplied to the house.
-%, and it is necessary to understand those three states in order to comprehend the joint work of the controller with the battery. With impact to the inverter and to power supplied to the house. 
-%
-%All the explanation at this section is related to $SOC$ and to the voltage at the DC-bus (controller output, which will be bigger than $V_{system}$) where the batteries are connected, all ruled by the charge controller.
-Moreover, it is important to mention that smart chargers, the most usual nowadays, will detect voltage and resistance from the battery prior to charging.
-%
-%Bulk - is the first stage of charging. Bulk begins when the sun comes out.
-%, or other source of electrical generation is turned on. 
-%This stage occurs when the batteries are at a lower $SOC$, generally anything not smaller than $75\%$ to $80\%$ (defined during system sizing).
-This stage is typically where the highest voltage and current the charger is rated for will actually be used.
-The bulk stage basically allows the PV panel to put as much current into the batteries as possible.
-For a typical 12 V battery, the charging voltage going into a battery will reach 14.16 V to 14.40 V at this stage, and there is no risk of overcharging in this stage because the battery hasn't even reached full yet.
-%
-%Absorption - once the batteries reach the programmed absorb voltage, usually somewhere between 14.16 and 14.40 V, the batteries will go into the absorption stage.
-Typically, when a battery reaches this stage its $SOC$ is around $85-95\%$.
-During this stage, the batteries are kept at the programmed voltage, and the current going into the batteries reduces as the batteries become more full.
-The absorption stage ends after the programmed time is reached or the number of Ampere going into the battery falls below a preset number.
-The lower current going into the battery safely brings up the charge on the battery without overheating it.
-%Usually, this stage takes more time than the bulk stage.
-%
-%Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage that a 12 V battery can hold, and begin the float stage.
-The float stage brings the battery all the way through and maintains $SOC$ at $100\%$.
-The current will also decrease to a point where it's considered just a pulse.
-It's essentially the float stage where there is charge going into the battery at all times, but only at a safe rate to ensure a full state of charge and nothing more.
-%Most smart chargers do not turn off at this point, however it is completely safe to leave a battery in float mode for months to even years at a time.
-%
-%Battery charging technology relies on smart micro-controlled devices.
-Therefore it is extremely important that the program settings for the charge controller or inverter/charger are correct, and the list includes the bulk and absorption values.
-%This will help preserve and extend the battery life.
-There are always default settings to the equipment, set by software, however those settings are not $100\%$ correct because there are difference among models of equipment and among manufacturer's.
-The ideal is to read the data-sheet from the manufacturers and perform a manual adjust.
-%
-%There are the possibility to combine batteries in a bank, with parallel and series connections, all depending the sizing of the project:
-%
-%\begin{itemize}
-%\item Batteries connected in parallel are seen by the controller as one large battery of the combined Ah capacity of all the batteries.
-For example, two 12 V and 220 Ah batteries in parallel are seen as one 12 V and 440 Ah battery;
-%\item In the other hand, although the batteries connected in series are also seen as a single battery, the result is different: two 12 V and 220 Ah batteries in series are seen as one 24 V and 220 Ah battery;
-%\item In addition, a mixed bank arrangement can be useful: a bank with two 12 V and 220 Ah batteries in series connected in parallel with a similar arrange will produce an equivalent battery of 24 V and 440 Ah.
-%\end{itemize}
-%-----------------------------------------------
-\subsection{The inverter model}
-%-----------------------------------------------
-%As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. 
-%An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
-The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage, % (127 V or 220 V, for example), 
-and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by \eqref{eq:efficinv} \cite{Hansen}:
-%
-%The inverter is characterized by a power dependent efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
-\begin{equation}
-\label{eq:efficinv}
-\eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}},
-\end{equation}
-
-\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be obtained from the inverter's data-sheet.
-
-%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
-%
-%
-%--------------------------------------------------
-\subsection{Availability of Stand-alone PV Systems}
-\label{sec:availability}
-%--------------------------------------------------
-Each stand-alone PV system, like any other power systems, has a specific level of availability.
-This reliability level impacts various issues, as system performance, production, feasibility, and investment.
-The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
-The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
-
-The system availability definition depends on how critical the load application is.
-For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable.
-As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system.
-An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
-
-With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong.
-It is important to evaluate how critical the load application is and the horizon of evaluation.
-However this analysis can be useful, for example, to improve the sized battery autonomy.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Verification Using Model Checking}
-\label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}.
-Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
-Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t.
-user requirements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
-CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
-If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
-CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Automatic program verification requires a choice between precision and efficiency. The
-more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was
-reflected in two major approaches to static verification: program analysis and model
-checking.
-In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
-The CPA formalism provides an interface for the definition of program analyses.
-Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
-Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
-Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-%CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
-For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
-\textcolor{red}{It is unclear what a CPA is.}
-%In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
-%
-%--------------------------------------------------
-\section{Stand-alone PV System Sizing and Verification}
-\label{sec:sizingcheck}
-%--------------------------------------------------
-In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a.
-sizing check).
-%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.
-
-Therefore this is a additional feature included at this paper.
-The sizing check will be performed by the proposed tool, and it will indicate if there is an error of sizing before to perform the automated verification of the system.
-This stage ensures that the system meets the standard project steps related to worst monthly average solar energy~\cite{Pinho}.
-%
-Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
-\begin{equation}
-\label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
-\end{equation}
-
-Following, it is necessary to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, as defined by~\eqref{eq:Ep}.
-
-\begin{equation}
-\label{eq:Ep}
-E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
-\end{equation}
-
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV systems will be deployed, the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed by ~\eqref{eq:NTPmin} and the check is performed using ~\eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from ~\eqref{eq:NTPmin}.
-\begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NTP}
-N_{TP} \geq N_{TPmin}.
-\end{equation}
-
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively.
-With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}).
-Where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
-
-\begin{equation}
-\label{eq:NPSmin}
-\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}}\leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NPS}
-N_{PS} \geq N_{PSmin}.
-\end{equation}
-
-\begin{equation}
-\label{eq:NPP}
-N_{PP} \geq N_{PPmin}.
-\end{equation}
-
-Related to the batteries, firstly must be defined the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
-\begin{equation}
-\label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}.
-\end{equation}
-%
-\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
-$ V_{system} $ is the DC voltage of the bus, and the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
-%
-Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}.
-Additionally, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
-\begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
-\end{equation}
-
-\begin{equation}
-\label{eq:batcheck}
-\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total.
-\end{equation}
-
-Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage: 
-\begin{equation}
-\label{eq:vcvsystem}
-V_{c} = V_{system}.
-\end{equation}
-
-Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
-%
-\begin{equation}
-\label{eq:iscamb}
-I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
-\end{equation}
-
-The controller must meet the maximum current from the PV array given by \eqref{eq:icmin} and \eqref{eq:icicmin}.
-\begin{equation}
-\label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP}.
-\end{equation}
-
-\begin{equation}
-\label{eq:icicmin}
-I_{c} \geq I_{c,min}.
-\end{equation}
-
-The sizing project check of the inverter is carried out by means of three equations.
-Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
-Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
-Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
-%
-\begin{equation}
-\label{eq:vindc} 
-V_{in}DC = V_{system}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:voutac} 
-V_{out}AC = V_{AC}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
-\end{equation}
-
-Worth to mention that the charge controller, the battery, and the inverter have a nominal efficiency presented at data sheets, and those numbers are very close to 100\%.
-However, based on empirical data, those efficiencies must be corrected, according to the loading of each component.
-If field or essay data is not available, considering that the proposed tools is aimed to be used prior the deployment of the PV system at the field, it is recommended (at least) to correct the battery efficiency ($\eta_{b}$) to 85\%, keeping the remaining efficiencies as expressed by the manufacturers.
-%
-%----------------------------------------
-\section{Proposed Automated Verification Method of PV Systems}
-\label{sec:Methodology}
-%----------------------------------------
-%
-%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.5\textwidth]{statetransition}
-%\centering
-%\caption{State transition diagram to the proposed automated verification.}
-%\label{fig:statetransition}
-%\end{figure}
-%
-%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.
-%
-The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
-
-\begin{figure}[h]
-\includegraphics[width=0.6\textwidth]{flowchart_verification5.png}
-\centering
-\caption{Flowchart of the proposed automated verification of PV systems.}
-\label{fig:flowchartgeneral}
-\end{figure}
-
-In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place to make sure that the components were selected according to worst monthly average solar energy method~\cite{Pinho}.
-The equations to check the PV sizing are present at Section~\ref{sec:sizingcheck}.
-%
-In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
-%As a consequence, all the formulae of the employed mathematical models will also be updated. 
-In addition, depending on one of the desired properties of the system such as battery autonomy, energy availability, or even system power supply, our verification engine is able to indicate a failure if those properties are not met; in this particular case, it provides a diagnostic counterexample that shows in which conditions the property violation occurred.
-%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
-% (as reliability, performance, or safety)
-
-%
-%\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above.
-For example, what does a failure mean?
-is it SAT?}
-In a nutshell, the model checker will process the ANSI-C code with constraints %($C$) 
-and properties %($P$) 
-from the PV system that are provided by the user, and the tool will automatically verify if the PV system requirements are met.
-If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
-However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
-%, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
-%
-%
-%---------------------------------------------------------------------
-% \subsection{The case studies and the Algorithm}
-%---------------------------------------------------------------------
-%
-% 
-%and as backup at night 
-%
-%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
-%
-%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
-%
-%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).
-
-Algorithm~\ref{alg:verification-algorithm} describes the pseudo-code used to perform the automated verification.
-%Line 1 indicates a function call that performs the size checking of the each component of the PV system.
-%: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
-%The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation of sizing check.
-The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints a counterexample indicating a property violation.
-If there is no property violation, then the verification algorithm continues and
-In order to reduce the computational effort of the algorithm,
-% caused by the state explosion inherent of the technique, 
-every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation), when the batteries are demanded to feed the house.
-
-Lines 1 is devoted to information from the location where the PV system will be/were deployed.
-Usually the information of annual average minimum and maximum, related to temperature ($T$) and solar irradiance ($G$), hour by hour, are obtained from specific historical weather web sites~\cite{Temperature}, ~\cite{Irradiance}.
-
-Line 2 represents all the information that comes from the PV sizing and from the equipment manufacturers data, as PV panels specification and data, batteries specification and data, inverter details and charge controller details.
-This item includes as well information from the house's load curve.
-
-The first automated verification is related to the sizing check, according described at Section ~\ref{sec:sizingcheck}.
-Then two functions, called at lines 4 and 5, are responsible for discover which hour starts the photovoltaic generation and when stops.
-Those functions get this information from the array inputted to the Algorithm with the solar irradiance values.
-
-The batteries are assumed to have SOC of 100\% (Line 6), i.e., the batteries are charged. That is important because the system is said ready to use when the batteries are charged.
-
-The first for-loop at Line 7 controls how many cycles of 24h will be performed by the Algorithm.
-And the for-loop from lines 8 to 11 is responsible to discharge the battery (according the load curve) and verify the state of charge of the battery, hour-by-hour, starting at the first hour of the day after the sun goes down until the next day before the sun goes up (when there is not PV generation).
-Following, at the next for-loop, from line 12 to 29, is performed the verification where there is solar irradiance and all the PV system works.
-The Algorithm generates information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, hour-by-hour, using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range (lines 15 and 16).
-%and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
-%there is PV generation only between 8:00 h and 16:00 h every day, 
-%with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day.
-
-After that, the model from PV generator is used in the function call of Line 17, to produce the voltage and current considering the states of $G$ and $T$.
-With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from Lines 18, 20, 22, 24 and 26, will imitate the charge controller work, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
-
-At the end of last for-loop, the state of the batteries is verified again (Line 27) and the hour is adjusted to the next loop (Line 28).
-
-Nevertheless, if the verification engine does not fail, then we can conclude that the PV system does not need further corrections up to the given bounds $k$.
-%
-%\textcolor{red}{this sentence is unclear...
-After this process is started the battery autonomy verification, from line 31}.
-\textcolor{red}{this sentence is unclear...
-Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.} \textcolor{red}{what do you mean by The formal verification is guaranteed?...
-The formal verification is guaranteed by  macro to specific variables of the model, according lines 27 and 35.}
-% and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
-%Within this 8h-period, $G$ and $T$ are automated verified with different values every one hour.
-%, and change their value every 1 h according with the algorithm created using the technique.
- \begin{algorithm}
- \caption{Model checking algorithm for stand-alone PV}
- \begin{algorithmic}[1]
- \begin{scriptsize}
-
- \renewcommand{\algorithmicrequire}{\textbf{Input:}}
- \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\
-  \STATE $declare \, case \, studies \, details: \, sizing \, and \, manufacturers \, data $ \\
-  \STATE $sizing \_ check()$ \\
-  \STATE $startPVgeneration \leftarrow findStartPVgeneration()$ \\
-  \STATE $endPVgeneration \leftarrow findEndPVgeneration()$ \\
-  \STATE $SOC \leftarrow 100\%$ \\
-
-%  \COMMENT {Starting with the PV generation time}
-% \\ 
-%\textit{LOOP Process}
- \FOR {$1st \, 24h \, loop$ to $Nth \, 24h \, loop$}
-  \FOR {$endPVgeneration+1$ to $startPVgeneration-1$}
-	  \STATE $dischargeBattery \, in \, 1h()$ \\
-%	  \STATE $autonomyCount \leftarrow autonomyCount+1$ \\
-	  \STATE $assert (SOC \geq SOC \_ min)$ \\
-%	  \STATE $battery \, autonomy \, verification()$ \\
-  \ENDFOR
-  \FOR {$startPVgeneration$ to $endPVgeneration$}
-    \STATE $G \leftarrow nondet \_ uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
-    \STATE $T \leftarrow nondet \_ uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
-    \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting $G$ values}
-    \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting $T$ values}
-    \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ \\
-    \COMMENT {If-then-else sequence to imitate charge controller work}
-    \IF {($battery \, is \, empty$) AND ($PV \, is \, generating$)}
-      \STATE $chargeBattery \, in \, 1h()$ \COMMENT {PV feed the house}
-    \ELSIF {($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
-      \STATE FAIL with assert macro \COMMENT {Battery is empty and there is not PV generation}
-    \ELSIF {NOT($battery \, is \, empty$) AND ($PV \, is \, generating$)}
-      \STATE stop battery charge \COMMENT {PV feed the house}
-    \ELSIF {NOT($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
-      \STATE $dischargeBattery \, in \, 1h()$ \COMMENT {Battery feed the house}
-    \ENDIF
-    \STATE $assert (SOC \geq SOC \_ min)$ \\
-    \STATE $hour \leftarrow hour+1$ \\
-   \ENDFOR
-  \ENDFOR
- \RETURN $(\,)$ 
-  \end{scriptsize}
- \end{algorithmic} 
- \label{alg:verification-algorithm}
- \end{algorithm}
-%There are two premises considering the algorithm: (1) is considered a $SOC$ of 80\% at 8:00 h, and is made the automated evaluation from 8:00 h to 16:00 h, but without to account the battery autonomy (just considering charge and discharge process based on solar irradiation, load and battery charge), but after 16:00h is started the verification for the next hours when there is not solar photovoltaic generation.
-The process goes on until to verify all the autonomy demanded from the batteries; (2) there is an array, declared at the beginning of the C code, that defines the power demand/consumption at each hour of the day (aka load curve).
-Those are the same data used during the sizing of the project and ensure to consider the total energy (per day) supplied to the house during the verification.
-%
-%If the verification founds a situation where the electrical demand of the house is not met, then the algorithm presents a counterexample of this combination.
-And this information can be used by the designer to improve the system.
-%if it was a project error or if it was a combination of variables from the nature that has a low probability to occur at the field, considering the intermittent characteristic of solar PV generation.
-
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-%
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-%
-%
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-%
-%
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-%
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-%
-%----------------------------------------------
-\section{Experimental Evaluation} 
-\label{sec:results}
-%----------------------------------------------
-%
-%\textcolor{red}{reorganise the results as follows: experimental objectives and setup; results; and threats to validity.}
-%
-%\textcolor{red}{https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf}
-%
-
-%------------------------------------------
-\subsection{Description of the Case Studies}
-%------------------------------------------
-%
-%We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
-We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
-Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), were used to compare the approach effectiveness and efficiency.
-\begin{table}
-\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
-\begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\hline
-Item & House 1 & House 2 & House 3 & House 4 & House 5\\
-\hline
-\hline
-PV Panels &  \multicolumn{4}{|c|}{3x 325W: in series} & 4x 325W: 2x series, 2x parallel \\
-\hline
-Batteries & \multicolumn{4}{|c|}{\makecell{4x220Ah: 2x series, 2x parallel\\ autonomy: 48h}} & \makecell{4x 120Ah batteries in series\\ autonomy: 6h}\\
-\hline
-Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150V/35A}\\
-\hline
-Inverter & \multicolumn{4}{|c|}{700W with peak of 1,600W} & 1,200W with peak of 1,600W\\
-\hline
-Power demand & 253W & 263W & 283W & 501W & 915W\\
-\hline
-GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
-\hline
-Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
-\hline
-\hline
-\end{tabular}
-\end{scriptsize}
-\end{table}
-
-%------------------------------------------
-\subsection{Objectives and Setup}
-\label{sec:setup}
-%------------------------------------------
-Our experimental evaluation aims to answer two research questions:
-%
-\begin{enumerate}
-\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
-\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
-\end{enumerate}
-
-In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool.
-All the experiments were performed with a timeout of 14,400 seconds (4 hours).
-%Every dweller, who owns a PV system, was interviewed
-
-All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
-The setup of HOMER Pro simulation tool: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Microsoft Windows 10; we have used HOMER Pro v3.12.0.
-
-Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
-
-Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c --unwind 100 --trace}.
-
-% enabled with the goal of reducing memory usage; 
-%The experiments were performed without a predefined timeout.
-Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
-An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness.
-% enabled with the goal of reducing memory usage; 
- %The experiments were performed without a predefined timeout.
-
-%------------------------------------------
-\subsection{Results and Discussion}
-\label{sec:results_indeed}
-%------------------------------------------
-%
-%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
-%\begin{enumerate}
-%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
-%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
-%
-Table~\ref{cases} summarizes the results concerning the use of the automated verification tools applied to the five case-studies of a solar PV system.
-The times reported in Table~\ref{cases} answer RQ2.
-
-Note that if we used HOMER Pro in all case studies, the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
-The simulation took less than five seconds to be performed on each case study.
-
-\begin{table}
-\centering
-\caption{Summary of the case-studies comparative and the automated tools.}\label{cases}
-\begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\hline
-\multicolumn{5}{|c|}{Model Checker (SAT/UNSAT: time and message)}\\
-\hline
-Case &  \makecell{ESBMC 6.0.0\\(Boolector 3.0.1)} & \makecell {ESBMC 6.0.0\\(Z3 4.7.1)} & \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}\\
-\hline
-\hline
-House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{5m08s \\(UNSAT)} & \makecell{19m02s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{4m27s \\(UNSAT)} & \makecell{18m59s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{5m07s \\(UNSAT)} & \makecell{18m39s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{4m37s \\(UNSAT)} & \makecell{18m36s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{6 sec \\ (SAT line 337)}\\
-\hline
-\hline
-\end{tabular}
-\end{scriptsize}
-\end{table}
-
-Note that an UNKNOWN result from our verification engines does not mean that a failure was found (i.e., SAT) neither that the verification is successful (i.e., UNSAT).
-An UNKNOWN result indicates that the verification engine led to  an out of memory or a time out situation.
-
-The description of our experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
-
-Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3.
-The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet.
-Using ESBMC with Boolector led to an out of memory situation in all the case studies.
-This result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
-However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.
-Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s.
-However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
-This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in Line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code (much more complex).
-
-Concerning the CBMC tool, similar results were obtained, but with some slower time.
-The experimentation returned SAT or UNSAT to all the case studies.
-Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18m36s to 19m02s.
-However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
-This verification took less than 1s to be performed as well, for the same reason described during the results of the ESBMC engine.
-
-Finally, the CPAchecker tool presented some different results.
-Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700W systems.
-This is because the time out set up was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
-However, when verifying the 1,200W PV system, the tool presented a SAT message, i.e., a failure was found, with the counterexample indicating the line (337) of the code, the same one appointed by the other verification engines, related to the charge controller.
-
-In order to validate the possible flaw from house 5, presented by all verification engines, we have surveyed the owner of the 1,200 W system.
-We identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}.
-However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
-%\begin{figure}[h]
-%\includegraphics[width=0.65\textwidth]{loadcurve.png}
-%\centering
-%\caption{Five weeks monitored load curve from House 1.}
-%\label{fig:loadcurve}
-%\end{figure}
-
-The same five case studies were evaluated by HOMER Pro (RQ2).
-The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system (RQ2).
-All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
-Fig.
-\ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software, specifically to house 1.
-
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{homer.png}
-\centering
-\caption{HOMER simulation screen.}
-\label{fig:homerscreen}
-\end{figure}
-%
-There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
-our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
-House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
-%
-%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
-Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions.
-The season has impact since the case studies are from the rain forest, where clouds are always present.
-As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
-%
-%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
-Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
-All the simulations took less than 5 seconds (each) to be performed.
-%
-%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
-That verification took 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
-The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
-The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
-The proposed tool took 409.3 hours to find this error at house 1.
-This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
-Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
-
-%At the terminal, the command used to perform the verification is:
-%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
-%
-%Where:
-%
-%\begin{itemize}
-%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
-%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
-%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
-%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
-There are other options, but this parameter is necessary because the complexity of the algorithms.
-The incremental SMT solving uses few RAM memory, compared with other SMT solving.
-%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
-The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
-%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
-%\end{itemize}
-%
-%\subsection{Experimental results}
-%\label{sec:results}
-%---------------------------------------------------
-\subsection{Threats to Validity}
-%---------------------------------------------------
-We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
-
-\textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
-A careful evaluation in a PV laboratory to validate the model could add more reliability to the results produced by our method.
-
-\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario, where a solar irradiance and ambient temperature can change in fractions of minutes.
-
-\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed if other places around the world could become case studies.
-
-%-------------------------------------
-\section{Conclusions and Future Work}
-\label{sec:Conclusions}
-%-------------------------------------
-We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
-We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-Although the verification method proposed takes longer than simulation methods, it is able to present details (counterexample) that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
-In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail.
-Related to the verification engines comparative, the ESBMC tool with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2G bytes when compared to 9.2G bytes of CBMC and 19.2G bytes of CPAchecker), and all the results were correct because the simulation tool presented the same results, besides the fact that interviews with the dwellers validated the possible flaws that the system could be presenting in the field.
-%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
-As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems.
-We will also consider other types of renewable energy and even hybrid ones to allow our method to design and verify typical rural electrification.
-%
-%It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results.
-The proposed tool was successful in find sizing errors and to indicate in which conditions a PV system can fails.
-% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements. 
-%
-%Plus (need to think about it): verification in every-hour of a 48h cycle?, PV model math model can be improved, charge/discharge of batteries can be improved (is a simplified model), house's power consumption is not flat or constant, the dweller can buy more home appliances, synthesis need a data base of components, to test peak (surge) consumption (above the nominal), additional models for on-grid/off-grid farm, hybrid, and on-grid with batteries).
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-%\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-%\section{}
-%Appendix two text goes here.
-% use section* for acknowledgment
-\section*{Acknowledgments}
-The authors would like to thank Coventry University for the availability of the case studies (real PV systems) to validate the tool and to support the mobility of one researcher to UK.
-This work was supported by Newton Fund [grant number 261881580] with the mobility of one researcher to UK; FAPEAM - Amazonas State Foundation for Research Support [grants from call 009/2017 and PROTI Pesquisa 2018], for the financial support related to the Virtual Machine rent (December 2018 to January 2019), for the DCTIEX II scholarship (November 2018), and for support the mobility of the researcher; and FAS - Sustainable Amazonas Foundation for the PhD scholarship (from November 2017 to March 2019).
-
-%\section*{References}
-
-%\bibliography{mybibfile}
-\bibliography{trindadeThesis}
-
-\end{document}

### 2019-07-03 Tex/Old text/chapters/appendix.tex
thesis updated text

@@
-appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix.
+\textbf{List of Publications}
+
+Journals-------------------
+Automated Formal Verification of Stand-alone Solar Photovoltaic Systems, 8-May submitted, in review Elsevier Solar Energy (IF 4.374, A1 interdisciplinar, A1 eng.
+IV ) https://www.journals.elsevier.com/solar-energy
+
+An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative, 29-June submitted, Elsevier Applied Solar (IF 7.900, A1 interdisciplinar, A2 Eng.
+IV, B1 ciência da computação) https://www.journals.elsevier.com/applied-energy
+
+Congress--------------------
+Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems - submitted 06-MAY-2019 - New Ideas papers - ASE 2019 The IEEE/ACM Automated Software Engineering (ASE 2019) Conference

### 2019-07-03 Tex/Old text/chapters/chapter04.tex
thesis updated text

@@
-\section{Automated Verification}
+\section{Intro to Automated Verification Experimental Evaluation}
+
+Intro text here
+
 -----------------------------------------
-\subsection{Description of the Case Studies}
+\section{Description of the Case Studies}
 %------------------------------------------
@@
 %------------------------------------------
-\subsection{Objectives and Setup}
+\section{Objectives and Setup}
 \label{sec:setup}
@@
 %------------------------------------------
-\subsection{Results and Discussion}
+\section{Results and Discussion}
 \label{sec:results_indeed}
@@
 %---------------------------------------------------
-\subsection{Threats to Validity}
+\section{Threats to Validity}
 %---------------------------------------------------
@@
 
-\section{Optimization}
-This section presents the case studies used to evaluate our proposed approach. 
-We also compare our approach with a simulation tool, named HOME Pro. 
-The version and command-line of each verifier adopted, 
-the computing setup, the objectives of the experimental phase, 
-and the results itself are also described.
-
-%---------------------------------------------------------------------------
-\subsection{Case studies} 
-%---------------------------------------------------------------------------
-
-We have performed seven stand-alone PV system case studies to evaluate 
-our proposed synthesis approach, as described in the first column of 
-Table~\ref{tab1} (named Specification). These case studies were defined 
-based on usual electrical load found in riverside communities of the 
-Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}. 
-%
-\begin{table}
-\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
-\begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\hline
-Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
-\hline
-\hline
-Specification & Result & Result & Result & Result \\
-\hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
-\hline
-\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
-\hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
-\hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
-\hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
-\hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
-\hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
-\hline
-\hline
-\end{tabular}
-\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
-\end{scriptsize}
-\end{table}
-
-%---------------------------------------------------------------------------
-\subsection{Tools} 
-%---------------------------------------------------------------------------
-
-Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
-The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
-
-%---------------------------------------------------------------------------
-\subsection{Setup} 
-%---------------------------------------------------------------------------
-
-All experiments regarding the verification tools were conducted 
-on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
-$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
-Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
-with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
-Our experiments were performed with a predefined timeout of $240$ minutes.
-
-%---------------------------------------------------------------------------
-\subsection{Objectives} 
-%---------------------------------------------------------------------------
-
-Our evaluation aims to answer two experimental questions:
-
-\begin{enumerate}
-
-\item[EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
-
-\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?
-
-\end{enumerate}
-
-%---------------------------------------------------------------------------
-\subsection{Results}  
-%---------------------------------------------------------------------------
-
-CPAchecker was able to synthesize the optimal sizing in six 
-out of seven case studies: the result was produced within 
-the time limit, which varied from $134.71$ to $235.75$ minutes. 
-Only case study $7$ led to a \textit{timeout} result, i.e., 
-it was not solved within $240$ minutes. However, if we remove 
-this timeout limitation from CPAchecker, the verifier is 
-able to solve the optimization in $44.97$ hours. 
-The violation (SAT result) indicated in Table~\ref{tab1} 
-is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
-%The results were tested by manual PV sizing and were sound (\textit{RQ1}).
-%, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
-
-CBMC and ESBMC are unable to produce any conclusive result. 
-Situations of \textit{internal failure}, \textit{timeout}, 
-or \textit{out of memory} occurred; this partially answers 
-the \textit{EQ2}. Note that the internal failure presented 
-by ESBMC was a Z3 solver issue (a bug); this will demand 
-an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
-if we remove the timeout from ESBMC with the SMT solver Boolector, 
-then the verifier is able to obtain the automated synthesis 
-in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.
-
-Related to HOMER Pro, it was able to evaluate six case studies, 
-and within a time shorter than $30$ seconds, which was much 
-faster than our automated synthesis tool (cf.~\textit{EQ2}). 
-Case study $3$ was not possible to be simulated since HOMER Pro 
-does not have the feature of adjusting the battery autonomy, i.e., 
-the tool always tries to feed with electricity the given load 
-during $365$ days/year. We have also noted other HOMER Pro drawbacks:
-
-\begin{itemize}
-\item There exists no explicit charge controller 
-as a system equipment. HOMER Pro includes automatically 
-a controller just to simulate the charge/discharge 
-of batteries and to meet the load requirement; however, 
-without costs or even with electrical characteristics 
-as maximum current and voltage, which are common during PV sizing;
-\item HOME Pro demands to include some battery specification 
-to initiate the optimization; however, it does not change 
-the electrical specifications during the simulation; 
-the presented results are multiples of the original 
-battery type suggested by the user. As example, it was 
-started with a $83.4$ Ah lead-acid battery and during 
-the simulation, HOMER Pro did not try to use other capacities or types;
-\item HOMER Pro does not present the optimal solution 
-in terms of connections of arrays of PV panels, just the 
-total in terms of power, i.e., it does not present neither models 
-and the power of each PV panel nor the total of panels in series or parallel. 
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison between Formal Synthesis and HOME Pro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Comparing the results between the formal synthesis with CPAchecker 
-and HOMER Pro, we observed that most results are quite similar, 
-in terms of technical solution and cost (cf. Table~\ref{tab1}).
-
-Particularly related to LCC, the cost was very close in cases 
-$1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
-Even adopting the same price per kW to the PV panels, 
-inverters, and batteries, HOMER Pro does not use costs 
-related to charge controllers, which were introduced into the 
-CPAchecker modeling. The premise used in CPAchecker to adopt 
-a fixed annual cost for operation and maintenance can produce 
-some impact as well at this discrepancy; however, it is not significant
-since this annual cost is too small when compared to the resulting LCC value.
-
-However, there exists a huge divergence in case study $2$, 
-where the costs presented by HOMER Pro were $54$\% higher 
-than our automated synthesis tool, probably because the 
-operation and maintenance costs assumed by our automated 
-synthesis tool were underestimated to that specific load.
-
-In general, the size of the PV panels and battery bank were 
-bigger in HOMER Pro than with our formal synthesis approach, 
-and that discrepancy is not easy to address without some real 
-systems validation. The mathematical models are different and 
-particular parameters can be tuned as well in each approach, 
-and that can justify the difference, which was presented in all 
-the case studies. As comparative, let's consider case study $1$: 
-the optimal solution provided by HOMER Pro demands $7$ $\times$ 
-more PV panels than the solution presented by our synthesis tool, 
-and HOME Pro does not show the arrangement of arrays 
-(i.e., the number of series and parallel PV panels); 
-the battery bank presented by HOMER Pro provides $500.4$ Ah 
-of capacity ($6 \times 83.4$), while our synthesis tool 
-presented an optimal solution with $420$ Ah of total capacity 
-($4 \times 105$).
-
-Just to compare the results obtained from the optimization 
-with the real-world, the authors had four PV systems deployed 
-and monitored since June $2018$ in a riverside community 
-in the Amazonas State in Brazil, with similar demands 
-presented by case studies $1$, $4$, $5$, and $6$, 
-always with a $3$ $\times$ $325$ W ($3$S) panels and 
-$4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) 
-lead-acid batteries. These solutions are more close 
-to the result presented by our formal synthesis 
-approach than HOMER Pro, thereby showing that our 
-solution is sound, which answers \textit{EQ1}.
-
-Related to the inverters, HOMER Pro suggests a value in 
-kW very close to the peak of every case study, and it 
-is just a reference value and not a commercial value of 
-the employed inverter. Our synthesis tool, however, 
-presents inverters that are commercial and can be found 
-off-the-shelf. Therefore is a PRO to the formal synthesis method.
-
-Concerning to charge controllers, as we reported in 
-the previous section, HOMER Pro does not include it 
-as an explicit equipment in its mathematical model, 
-only our synthesis tool presents a commercial controller 
-and includes it during the cost analysis. Therefore, 
-the formal synthesis method presents more reliable results than
-HOME Pro.
-
-Case study $7$ was not solved by our synthesis tool 
-within the time limit established during the experimental 
-phase. Case study $3$ was not possible to simulate in HOMER Pro, 
-because its restriction does not allow one to set the battery autonomy, 
-thus resting both without parameters to comparative.
-
-Summarizing, our synthesis tool is capable to present a 
-solution, which is far detailed and close to the commercial 
-reality than the solution presented by HOMER Pro. 
-In particular, our automated synthesis method 
-can provide all the details of every component of 
-a PV system solution, with complete electrical details 
-from data sheet of manufacturers, including 
-the model of the component, nominal current and voltage. 
-In this respect, even the name of the manufacturer 
-can be presented (in Table~\ref{tab1} it was removed 
-to avoid some advertising).
-%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Threats to validity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We have reported a favorable assessment of our formal synthesis method. 
-Nevertheless, we have also identified three threats to the validity 
-of our experimental results, which can be further assessed and 
-constitute future work: ($1$) improvement of the power reliability 
-analysis: to include loss of load probability or loss of power 
-supply probability, which can make the analysis more accurate; 
-($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
-however, a broad analysis from other isolated areas must be 
-performed in order to make the optimization general in terms 
-of applicability; ($3$) to deploy at the field some PV systems 
-sized using our synthesized results in order to validate it.
+\section{Conclusion}

### 2019-07-03 Tex/Old text/chapters/chapter05.tex
thesis updated text

--- 2019-06-29 Tex/elsevier/trindade_appliedenergy_rev0.tex
@@
-\documentclass[review]{elsarticle}
-
-\usepackage{lineno,hyperref}
-%\modulolinenumbers[5]
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithm,algorithmic}
-\usepackage{graphicx}
-\usepackage{makecell}
-\usepackage{textcomp}
-\usepackage{xcolor}
-
-\journal{Applied Energy}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\begin{frontmatter}
-
-%\title{Innovative techno-economic optimization of stand-alone solar photovoltaic systems using automated formal synthesis} 
-\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
-%
-%\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
-%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
-%
-%% Group authors per affiliation:
-\author[mymainaddress]{Alessandro Trindade\corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Corresponding author}
-\ead{alessandrotrindade@ufam.edu.br}
-%\ead[url]{www.elsevier.com}
-
-\author[mysecondaryaddress]{Lucas Cordeiro}
-
-\address[mymainaddress]{Federal University of Amazonas, Av. Rodrigo Octávio, 6200, Coroado I, 69077-000 Manaus-AM-Brazil}
-\address[mysecondaryaddress]{University of Manchester, School of Computer Science, Kilburn Building, Manchester M13 9PL}
-
-\begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space.
-We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
-If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
-Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach.
-\end{abstract}
-
-\begin{keyword}
-automated verification \sep model checking \sep program synthesis \sep electrical systems \sep solar photovoltaic systems
-\end{keyword}
-
-\end{frontmatter}
-
-%\linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
-During operation, such components must frequently adapt to the operating environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
-Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
-
-While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
-Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing \textit{correct-by-construction} implementations of CPS.
-These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
-In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
-Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
-Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
-
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}.
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
-
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and  Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.,  PSpice~\cite{Gow1999}, or MATLAB/Simulink package~\cite{Benatiallah2017}.
-However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-
-Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
-An ideal combination of any PV system is made by the best compromise between two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
-
-However, formal methods based on \textit{symbolic model checking} and its application 
-to synthesize PV systems have not been further explored in literature, which could offer 
-a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. 
-Here, we use a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing 
-optimal sizing of stand-alone PV systems using commercial equipment data. 
-Given a correctness specification $\sigma$, our method uses that as starting point 
-and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
-related to power reliability. In particular, in each iteration, we synthesize sizing of 
-stand-alone PV systems but that may not achieve the lowest cost. The candidate solution 
-is then verified via symbolic model checking with a lower bound that serves as the minimum 
-cost of reference; if the verification step does not fail, the lower bound is adjusted. 
-If it fails then a counterexample is provided with an optimal sizing that meets 
-power reliability and system cost.
-
-Our work makes two major contributions. Firstly, the use of automated 
-symbolic verification methods in electrical systems was uncommon in recent 
-prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
-PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
-charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
-method together with user requirements and environment constraints, 
-and our synthesis algorithm based on symbolic model checking 
-can find the optimal solution in technical and economical terms. 
-\textbf{Secondly}, we evaluate different state-of-art symbolic software 
-verifiers with the goal of obtaining the best performance in our verification 
-back-end for synthesizing optimal PV systems.
-
-\textit{Outline}. Section~\ref{sec:Background} gives the background about related studies, 
-program synthesis, sizing design and validation of PV systems, and the mathematical modeling. 
-Section~\ref{sec:Method} presents the automated formal synthesis proposed 
-in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, 
-results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
-%
-%-----------------------------------------------------------
-\section{BACKGROUND}
-\label{sec:Background}
-%-----------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{State-of-art in Automated Verification of Electrical Systems}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The conversion of traditional power grid into a smart grid, a fundamental example of a CPS, 
-raises a number of issues that requires novel methods and applications.
-In $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
-The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here, the authors employed automated verification of certain quantitative properties of the system, as probability of	 node failure in the long run, impact of repair service on the failure risk, and expected energy consumption, without any interest in power generation or even solar PV systems.
-
-In $2015$, an automated approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
-The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
-The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
-However, this study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
-
-Other related studies from $2015$ include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis using statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
-In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
-The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
-This research, however, did no address the design and verification of solar PV systems.
-
-In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices, interacting over a shared and smart infrastructure~\cite{Abate2017}.
-The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
-The focus was on controlling the behavior of components, thereby verifying the given smart grid as a "system of systems" within the context of "internet of things".
-The author, however, used approximate model checking of stochastic and hybrid models.
-
-In $2018$, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
-This related study did not include other components of a stand-alone solar PV system.
-
-Another work from $2018$ was the approach to model smart grid components using a formal specification.
-The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
-The presented formal specification can be considered as a first step towards modeling of smart grids using formal methods.
-The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
-This approach is based on Petri nets and is under the assumption that modeling the smart home leads to clear understanding of the overall behavior of the smart grid.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Automated Verification Using Model Checking}
-\label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Although simulation and testing explore possible behaviors and scenarios of a given system, 
-they leave open the question of whether unexplored trajectories may contain a flaw. 
-Formal verification conducts an exhaustive exploration of all possible behaviors; 
-when a design is said to be ``correct'' by a formal verification method, it implies that all 
-behaviors have been explored, and questions regarding adequate coverage or missed behavior 
-becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
-applies mathematical reasoning to obtain guarantees about the correctness of a system; 
-one successful method in this domain is model checking~\cite{Clarke2012}. 
-Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs 
-or proves that they are safe if a completeness threshold is given~\cite{Kroening}. 
-CBMC implements a bit-precise translation of a C program, annotated with assertions 
-and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, 
-then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification 
-flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; 
-it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, 
-into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
-(ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
-which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
-(iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Automatic program verification requires a choice between precision and efficiency. 
-The more precise a method, the fewer false positives it will produce, but also the 
-more expensive it is, and thus applicable to fewer programs. 
-Historically, this trade-off was reflected in two major approaches to static verification: 
-program analysis and model checking. In order to experiment with the trade-off, 
-and in order to be able to set the dial between the two extreme points, 
-Configurable Program Analysis (CPA) provides a conceptual basis for expressing 
-different verification approaches in the same formal setting. The CPA formalism 
-provides an interface for the definition of program analyses. Consequently, CPAchecker 
-provides an implementation framework that allows the seamless integration of program 
-analyses that are expressed in the CPA framework. The comparison among different 
-approaches in the same experimental setting is intended to be easy and the experimental 
-results are expected to be more meaningful~\citep{Beyer2011}. Related to the architecture, 
-the central data structure is a set of control-flow automata (CFA), which consists of control-flow 
-locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and 
-interpolation procedures~\citep{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
-and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-
-%-----------------------------------------------------------
-\subsection{Program Synthesis}
-\label{sec:ProgramSynthesis}
-%-----------------------------------------------------------
-
-The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
-In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
-As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
-	\caption{CEGIS applied to PV system sizing.}
-	\label{Counter-Example-Guided-Inductive-Synthesis}
-\end{figure}
-
-The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .
-\forall \vec{x}.
-\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
-The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
-
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
-Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
-
-One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
-
-However, in our variant CEGIS method proposed here, there are four particular differences related to the traditional CEGIS: 
-(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
-(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
-(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
-(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
-a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard 
-a given candidate that could be feasible in the next iteration with a new lower bound.
-
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sizing Stand-alone Solar PV Systems}
-\label{sec:sizing}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
-The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.  
-For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage 
-form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system 
-contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior 
-of AC electrical load from the house that will be fed by the system.
-%
-\begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
-\centering
-\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
-\label{fig:blockdiagram} 
-\end{figure}
-
-The sizing check stage will ensure that the system meets the standard project steps related 
-to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller,
-which is the most common one in practice. Firstly, we need to correct the energy consumption estimated to the load 
-($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
-controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
-%
-\begin{equation}
-\label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
-\end{equation}
-
-We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
-%
-\begin{equation}
-\label{eq:Ep}
-E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
-\end{equation}
-
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
-the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
-%
-\begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
-\end{equation}
-
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
-%
-\begin{equation}
-\label{eq:NPSmin}
-\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
-\end{equation}
-%
-\begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
-\end{equation}
-%
-\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ 
-is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and 
-$V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering 
-the maximum and minimum operational temperature, respectively; 
-$P_{total}$ is the total power demanded from the PV system and 
-$P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
-%
-\begin{equation}
-\label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
-\end{equation}
-
-\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-%
-Secondly, the total (minimum) number of batteries is computed as
-
-\begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
-\end{equation}
-
-Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
-\begin{equation}
-\label{eq:vcvsystem}
-V_{c} = V_{system}.
-\end{equation}
-
-The short circuit reference information from the manufacturer's solar panel must be corrected 
-to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, 
-and PV system is temperature dependent, as 
-%
-\begin{equation}
-\label{eq:iscamb}
-I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
-\end{equation}
-
-The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin} as
-%
-\begin{equation}
-\label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP},
-\end{equation}
-%
-\begin{equation}
-\label{eq:icicmin}
-I_{c} \geq I_{c,min}.
-\end{equation}
-
-The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that 
-the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the 
-output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that 
-the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), 
-where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; 
-$MAX_{AC,ref}$ is the peak power that the inverter can support.
-%
-\begin{equation}
-\label{eq:vindc} 
-V_{in}DC = V_{system}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:voutac} 
-V_{out}AC = V_{AC}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{PV systems Optimization Criteria}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In order to select an optimal combination to meet sizing constraints, 
-it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives.
-
-During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
-The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
-A reliable power is a generation system that has sufficient power to feed load demand in a period.
-
-There exist different methods to express system reliability, where the most popular ones 
-are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
-In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
-
-LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
-On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
-On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
-The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance.
-However, data is not always available and dynamic analysis is complex; and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
-
-Related to economic analysis, there exist various methods available.
-The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
-The common methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
-
-The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
-The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
-IRR is used to evaluate the attractiveness of a project or investment.
-
-LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
-LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
-
-LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
-Eq.~\eqref{eq:LCC} is used to calculate LCC of a PV system,
-%
-\begin{equation}
-\label{eq:LCC}
-LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
-\end{equation}
-\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs
-in present worth.
-
-%----------------------------------------------------------------------------------------------
-\subsection{Stand-alone PV System Optimization Technique}
-%----------------------------------------------------------------------------------------------
-
-In order to recommend an optimal configuration for PV systems, 
-the designer has to evaluate the design based on optimization variables. 
-As the number of optimization variables increases, the computational effort 
-will increase as well. Hence, to obtain the best PV system design as well as 
-simplified sizing process, prior work introduced three main techniques 
-for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
-
-Intuitive method is simple, easy to be implemented, and can be used to give 
-rough suggestion for preliminary design. The sizing rules are based on designer's experience, 
-using lowest performance either in a time period data or by directly using average value 
-(daily, monthly, or annual) of solar irradiance. This method does not consider the battery's 
-state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
-
-For numerical method, the design is simulated for each time step within a period. 
-State of charge of batteries is calculated and investigated. It is very accurate, 
-however is complex, demanding more time for calculation~\cite{Park2004}.
-
-Analytical methods is used to obtain a close relation or correlation in a form 
-of equation between capacities and reliabilities. The sizing task becomes much simpler 
-than numerical technique; however, the relation cannot be applied to different sites
-since it is specific to one place of deployment of the PV system, 
-thereby demanding adaptation if another site is analyzed.
-
-%------------------------------------------------------
-\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
-\label{sec:Method}
-%------------------------------------------------------
-
-Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
-It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
-%
- \begin{algorithm}
- \caption{Synthesis algorithm}
- \begin{algorithmic}[1]
- \renewcommand{\algorithmicrequire}{\textbf{Input:}}
- \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE Initialize variables \\
-  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
-%  \STATE Declare list of controllers data and cost \\
-%  \STATE Declare list of batteries data and cost \\
-%  \STATE Declare list of inverters data and cost \\
-  \STATE Declare the maximum possible cost $MaxCost$  \\
-  \STATE Declare power demand, power peak, energy consumption \\
-  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
-  \FOR {$HintCost=0$ to $MaxCost$}
- 	\STATE Declare non-deterministic variable to select PV Panel from list \\
- 	\STATE Declare non-deterministic variable to select Controller from list \\
- 	\STATE Declare non-deterministic variable to select Battery from list \\
- 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
- 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
-	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
- 	\STATE Calculate $C_{bank}$ \\
-	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
-	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
- 	\STATE Calculate $I_{sc,amb}$ \\
- 	\STATE Calculate $I_{c,min}$ \\
- 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
-	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
-	\STATE non-deterministic variables hold feasible equipment and cost  \\
-	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
-	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
-  \ENDFOR
- \RETURN $(\,)$ 
- \end{algorithmic} 
- \label{alg:verification-algorithm}
- \end{algorithm}
-%
-
-Our synthesis algorithm will synthesize constant values; 
-it starts with the input of manufacturers data and prices of PV panels, batteries, 
-charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
-house requirements and design definitions, from lines $4$ and $5$.
-
-The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. 
-In particular, it starts with cost $0$ and stops only when the algorithm finds a 
-feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
-if that happens, then our algorithm has found an optimal solution, thereby stating 
-that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
-The $MaxCost$ value at line $6$ is just a very high value put as a limit 
-to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
-
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
-from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
-That procedure ensures that our synthesis engine checks all combinations of items 
-from each equipment, and combine them to assemble a feasible (candidate) PV solution, 
-which meets the user requirements.
-
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, 
-Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
-Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} t
-o calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
-ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
-uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$. 
-Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
-and the cost of that solution is calculated in $F_{obj}$ (line $21$).
-
-If our algorithm does not find a feasible solution among the item of equipment that 
-were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
-the program finishes and does not find a solution, which indicates that it 
-was not possible to combine the items of each equipment in order to create a feasible solution.
-
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
-solution regarding the constraints and user requirements. Related to our {\sc Verify} 
-phase the challenge is to find the lowest acquisition cost from a list of equipment and 
-components that is provided from the {\sc Synthesize} phase.
-
-Note that the process described here in completely automated and that a validation is performed 
-by our {\sc Verify} phase to ensure that the approach is sound.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Assumptions and Premises}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, 
-a list of forty equipment from ten different manufacturers was provided 
-to the synthesis engine in order to allow the choice of every item 
-of PV sizing. Data sheet from each item was necessary to collect 
-technical information. Moreover, the price of each item was obtained 
-from available quotations in the market, and if the currency was not in US dollars, 
-then it was used the exchange rate of the day to convert it to US dollars.
-
-With respect to power reliability, this work will rely on the critical period solar 
-energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
-The usual way is to use loss of load probability (LOLP) or loss of power 
-supply probability (LPSP). However, based on the fact that here we 
-are neither considering site characteristics nor the load changes over time, 
-which demands historical data, the reliability analysis will be developed only 
-by the critical period method of PV sizing.
-
-Regarding financial analysis:
-\begin{itemize}
-	\item LCC lifetime considered: $20$ years;
-	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
-	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
-	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
-This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
-Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
-\end{itemize}
-
-On the subject of PV system optimization technique, we will adopt here the intuitive method 
-since the average value daily of solar irradiance is used in the mathematical model, 
-without considering the battery's state of charge, or even the random nature 
-of solar irradiation and meteorological conditions. Therefore, all the computational 
-effort will be concentrated in our automated synthesis algorithm.
-
-Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
-
-Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
-Related to HOMER Pro:
-
-\begin{itemize}
-	\item HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER};
-	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
-	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
-However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
-	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
-	\item HOMER Pro do not have a explicit equipment called charge controller.
-It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
-During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
-	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
-By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\citep{Khatib2014}.
-For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable;
-	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
-	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
-HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
-\end{itemize}
-
-%---------------------------------------------------------------------------
-\section{Experimental Evaluation}
-\label{sec:Results}
-%---------------------------------------------------------------------------
-
+\section{Intro to Automated Formal Synthesis Optimization}
 This section presents the case studies used to evaluate our proposed approach. 
@@
 %---------------------------------------------------------------------------
-\subsection{Case studies} 
+\section{Optimization Case studies} 
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-\subsection{Tools} 
+\section{Tools} 
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-\subsection{Setup} 
+\section{Setup} 
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-\subsection{Objectives} 
+\section{Objectives} 
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-\subsection{Results}  
+\
+section{Results}  
 %---------------------------------------------------------------------------
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison between Formal Synthesis and HOME Pro}
+\section{Comparison between Formal Synthesis and HOME Pro}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Threats to validity}
+\section{Threats to validity}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CONCLUSIONS}
-\label{sec:Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We have described and evaluated an automated synthesis method 
-to obtain the optimal size of PV system using software model 
-checking techniques. We have considered seven case studies 
-from PV systems in two different sites of the Amazonas State 
-in Brazil, ranging from $253$\,W to $1,586$\,W peak; and 
-three state-of-art verification engines were considered 
-(ESBMC, CBMC, and CPAchecker), in addition to a specialized 
-off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
-
-Our automated synthesis tool presented detailed optimal solution 
-to six case studies adopted in this paper, with specifications, 
-models, and the arrangement in terms of series-parallel connections, 
-thereby covering the charge controller, which was not presented by HOMER Pro. 
-In a nutshell, our automated synthesis tool took more time 
-to find the optimal solution than HOMER Pro; however, the presented 
-solution was more complete and detailed, which is very useful 
-to a user to get a list of equipment and go to shopping.
-
-As future work, the authors plan to improve the power reliability analysis, 
-to address the restriction to only allow automated synthesis of 
-riverside communities in the Amazonas state (Brazil), and to 
-validate some cases with deployed PV systems in isolated communities.
-
-\section*{Acknowledgments}
-The authors would like to thank: (i) Newton Fund [grant number $261881580$] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa $2018$], for the DCTIEX II scholarship (NOV-$2018$), and for support the research mobility to UK; (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and (iv) University of Sheffield's Research England QR GCRF Institutional Allocation for the HOMER Pro license.
-
-%
-% argument is your BibTeX string definitions and bibliography database(s)
-%\section*{REFERENCES}
-\bibliography{trindadeThesis}{}
-%\vspace{12pt}
-\end{document}
+\section{Conclusion}

### 2019-07-03 Tex/Old text/chapters/conclusion.tex
thesis updated text

@@
+\section{Main Contributions}
+
 We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
@@
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.
-As future work, we will also consider other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
 
@@
 
-As future work, the authors plan to improve the power reliability analysis, 
+\section{Future Work Directions}
+create a research group in automated verification applied to electrical systems
+improve mathematical models
+
+Automated verification: As future work, we will also consider other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
+
+Synthesis: As future work, the authors plan to improve the power reliability analysis, 
 to address the restriction to only allow automated synthesis of 
@@
 validate some cases with deployed PV systems in isolated communities.
+
+\section{Concluding Remarks}

### 2019-07-03 Tex/Old text/main.tex
thesis updated text

--- 2019-07-01 Tex/Old text/main.tex
@@
 \chapter*{Acknowledgements}
-I want to thank...
+(It is not possible to get here without the help of several people. I hope I have not forgotten any and do no wrong).
+
+I would like to thank God (for the gift of life); Solange and Louise (without the patience and support of my family I could not be here); my parents and grandparents; Lucas (for having believed in me and for the patience); the Electricity Department at UFAM (for the support); Professors Feitosa, Marco Cristo and Barreto from IComp (support and advice); IT support team from IComp (Virtual Machine maintenance); secretary people from IComp (for the administrative support); the financial support from FAPEAM, British Council/Newton Fund and Fundação Amazonas Sustentável; Davide Poggio from University of Sheffield for the HOMER Pro license (Research England QR GCRF Institutional Allocation); and Coventry University team (Elena, Kojo, and Ross for the opportunity to use field deployed photovoltaic solar systems).
+
+\pagestyle{empty}
 
@@
 \listoftables
+\newpage 
+\input{abbreviations}
 
 \chapter{Introduction}
+\pagenumbering{arabic}
+\pagestyle{fancy}
+\fancyhead{}
+\fancyhead[RO,LE]{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
+\fancyfoot{}
+\fancyfoot[LE,RO]{\thepage}
+\fancyfoot[CO,CE]{Chapter \thechapter}
+\fancyfoot[LO,RE]{A. B. Trindade}
+\renewcommand{\headrulewidth}{0.4pt}
+\renewcommand{\footrulewidth}{0.4pt}
 \input{chapters/introduction}
@@
 
-\chapter{Experimental Evaluation}
+\chapter{Automated Formal Verification of Stand-Alone Solar PV Systems}
 \input{chapters/chapter04}
 
-\chapter{Conclusion and Future Work}
+\chapter{Automated Formal Synthesis Optimization Method for Sizing of Stand-Alone Solar PV Systems}
+\input{chapters/chapter05}
+
+\chapter{Conclusions}
+\fancyfoot[CO,CE]{Conclusions}
 \input{chapters/conclusion}
@@
 \appendix
-\chapter{Appendix Title}
+\chapter{List of Publications}
+\fancyfoot[CO,CE]{Appendix}
 \input{chapters/appendix}
 
+\fancyfoot[CO,CE]{References}
 %\printbibliography
+\renewcommand\bibname{References}
 \bibliography{trindadeThesis}{}

### 2019-07-03 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
-chapter02 text here
-
-////////////////// Begin old stuff
+In this chapter some concepts related to the intersection of the two areas of this research are presented: the computer science applied to an electrical engineering problem, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.
+
+First, the concept of formal verification is introduced as background to understanding how a methodology that performs (mainly) bug detection can be used to validate a design sizing or to obtain an optimal solution of PV systems.
+
+And secondly, how a solar PV system can be modelled in order to be verified/optimized by the formal verification methodology.
+
+\section{Formal Methods and Formal Verification}
+Formal methods are system design techniques that use rigorously specified mathematical models to build software and hardware systems.
+In contrast to other design systems, formal methods use mathematical proof as a complement to system testing in order to ensure correct behavior.
+As systems become more complicated, and safety becomes a more important issue, the formal approach to system design offers another level of insurance.
+
+Formal methods differ from other design systems through the use of formal verification schemes, the basic principles of the system must be proven correct before they are accepted [Bowen93].
+Traditional system design has used extensive testing to verify behavior, but testing is capable of only finite conclusions.
+Dijkstra and others have demonstrated that tests can only show the situations where a system won't fail, but cannot say anything about the behavior of the system outside of the testing scenarios [Bentley89].
+In contrast, once a theorem is proven true it remains true.
+
+It is very important to note that formal verification does not obviate the need for testing [Bowen95].
+Formal verification cannot fix bad assumptions in the design, but it can help identify errors in reasoning which would otherwise be left unverified.
+In several cases, engineers have reported finding flaws in systems once they reviewed their designs formally [Kling95].
+
+Roughly speaking, formal design can be seen as a three step process, following the outline given here:
+
+Formal Specification: During the formal specification phase, the engineer rigorously defines a system using a modeling language.
+Modeling languages are fixed grammars which allow users to model complex structures out of predefined types.
+This process of formal specification is similar to the process of converting a word problem into algebraic notation.
+In many ways, this step of the formal design process is similar to the formal software engineering technique developed by Rumbaugh, Booch and others.
+At the minimum, both techniques help engineers to clearly define their problems, goals and solutions.
+However, formal modeling languages are more rigorously defined: in a formal grammar, there is a distinction between WFFs (well-formed formulas) and non-WFFs (syntactically incorrect statements).
+Even at this stage, the distinction between WFF and non-WFF can help to specify the design.
+Several engineers who have used formal specifications say that the clarity that this stage produces is a benefit in itself [Kling95].
+
+Verification: As stated above, formal methods differ from other specification systems by their heavy emphasis on provability and correctness.
+By building a system using a formal specification, the designer is actually developing a set of theorems about his system.
+By proving these theorems correct, the formal
+Verification is a difficult process, largely because even the simplest system has several dozen theorems, each of which has to be proven.
+Even a traditional mathematical proof is a complex affair, Wiles' proof of Fermat's Last Theorem, for example, took several years after its announcement to be completed.
+Given the demands of complexity and Moore's law, almost all formal systems use an automated theorem proving tool of some form.
+These tools can prove simple theorems, verify the semantics of theorems, and provide assistance for verifying more complicated proofs.
+
+Implementation: Once the model has been specified and verified, it is implemented by converting the specification into code.
+As the difference between software and hardware design grows narrower, formal methods for developing embedded systems have been developed.
+LARCH, for example, has a VHDL implementation.
+Similarly, hardware systems such as the VIPER and AAMP5 processors have been developed using formal approaches.
+An alternative to this approach is the lightweight approach to formal design.
+In a lightweight design, formal methods are applied sparingly to a system.
+This approach offers the benefits of formal specification, but also avoids some of the difficulties.
+
+Formal methods are viewed with a certain degree of suspicion.
+While formal methods research has been progressing since 1960's, formal methods are only being slowly accepted by engineers.
+There are several reasons for this, but most of the problems seem to be a result of misapplication.
+Most formal systems are extremely descriptive and all-encompassing, modeling languages have generally been judged by their capacity to model anything.
+Unfortunately, these same qualities make formal methods very difficult to use, especially for engineers untrained in the type theory needed for most formal systems.[Bowen93]
+
+Conversely, it is apparent that some form of formal specification is necessary: complex systems require formal models.
+In addition,the mathematics required for formal methods is becoming a more prominent fixture of engineering curricula, engineering schools in Europe are already requiring courses in VDM, Z and similar formal specifications.
+Ultimately, formal methods will acquire some form of acceptance, but compromises will be made in both directions: formal methods will become simpler and formal methods training will become more common.
+
+Key Concepts
+Provability And Automated Verification
+Formal methods are distinguished from other specification systems by their emphasis on correctness and proof, which is ultimately another measure of system integrity.
+Proof is a complement, not a substitute, for testing.
+Testing is an important part of guaranteeing any system's fitness, but it is finite.
+Testing cannot demonstrate that a system operates properly; it can only demonstrate that the system works for the tested cases.
+Because testing cannot demonstrate that the system should work outside the tested cases, formal proof is necessary.
+
+Formally proving computer systems is not a new idea.
+Knuth and Dijkstra have written extensively on the topic, although their methods of proof are based on the traditional mathematical methods.
+In pure sciences, proofs are verified through extensive peer review before publication.
+Such techniques are time-intensive and less than perfect; it isn't unusual for a published proof to contain a flaw.
+Given the cost and time requirements of systems engineering, traditional proving techniques are not really applicable.
+
+Because of the costs of hand verification, most formal methods use automated theorem proving systems to verify their designs.
+Automated theorem provers are best described as mathematical CAD tools: they can prove simple propositions and automatically and provide assistance for verifying more complex theorems.
+
+Benefits Of Formal Models
+Formal methods offer additional benefits outside of provability, and these benefits do deserve some mention.
+However, most of these benefits are available from other systems, and usually without the steep learning curve that formal methods require.
+
+Discipline: By virtue of their rigor, formal systems require an engineer to think out his design in a more thorough fashion.
+In particular, a formal proof of correctness is going to require a rigorous specification of goals, not just operation.
+This thorough approach can help identify faulty reasoning far earlier than in traditional design.[Bowen95]
+The discipline involved in formal specification has proved useful even on already existing systems.
+Engineers using the PVS system, for example, reported identifying several microcode errors in one of their microprocessor designs.[Miller95]
+
+Precision: Traditionally, disciplines have moved into jargons and formal notation as the weaknesses of natural language descriptions become more glaringly obvious.
+There is no reason that systems engineering should differ, and there are several formal methods which are used almost exclusively for notation.[Bowen93]
+For engineers designing safety-critical systems, the benefits of formal methods lie in their clarity.
+Unlike many other design approaches, the formal verification requires very clearly defined goals and approaches.
+In a safety critical system, ambiguity can be extremely dangerous, and one of the primary benefits of the formal approach is the elimination of ambiguity.[Kling94].
+Weaknesses Of Formal Methods
+: Bowen points out that formal methods are generally viewed with suspicion by the professional engineering community, and the propensity of tentative case studies and advocacy papers for the formal approach would seem to support his thesis [Bowen93].
+There are several reasons why formal methods are not used as much as they might be, most stemming from overreaching on the part of formal methods advocates.
+Expense:Because of the rigor involved, formal methods are always going to be more expensive than traditional approaches to engineering.
+However, given that software cost estimation is more of an art than a science, it is debatable exactly how much more expensive formal verification is.
+In general, formal methods involve a large initial cost followed by less consumption as the project progresses; this is a reverse from the normal cost model for software development.[Bowen93]
+Limits Of Computational Models:While not a universal problem, most formal methods introduce some form of computational model, usually hamstringing the operations allowed in order to make the notation elegant and the system provable.
+Unfortunately, these design limitations are usually considered intolerable from a developer's perspective.
+An excellent example comes from SML.
+Statements of proof in SML depend on a purely functional programming model: all data is passed through the parameter/return mechanism of a function, no side effect alterations, modifications of global variables or the like is allowed [Paulson96].
+Handling side effects and other aberrancies are a requirement for any system involving input, network operations or other systems which require interrupts, meaning that SML's model is, to some extent, broken.
+
+Usability:Traditionally, formal methods have been judged on the richness of their descriptive model.
+That is, 'good' formal methods have described a wide variety of systems, and 'bad' formal methods have been limited in their descriptive capacities.
+While an all-encompassing formal description is attractive from a theoretical perspective, it invariably involved developing an incredibly complex and nuanced description language, which returns to the difficulties of natural language.
+Case studies of full formal methods often acknowledge the need for a less all-encompassing approach.[Miller95]
+Arguably, many of these failures can be attributed to overreaching on the part of formal methods advocates. This reasoning has led to the lightweight approach to formal specification.
+The Lightweight Approach
+The flaws in formal specifications have been heavily focused on in the past few years, leading to several alternate approaches.
+The traditional view of formal methods as all-encompassing highly abstracted schemes has led to formal methods being all-encompassing, extremely rigorous, and very expensive.
+While theoretically appealing, formal methods have generally been ignored by engineers in the field.
+The lightweight approach to formal design recognizes that formal methods are not a panacea: there are areas where formal methods are useful, and areas where a formal specification will accomplish nothing.
+In a lightweight design, formal methods are used in specific locations, and different formal methods may be used in different subsystems, ideally playing to the strengths of each method [Easterbrook 98].
+In such a system, Petri Nets might be used to describe the communications protocol, and a LARCH system might be used to model the data storage.
+For other parts of the system, formal specifications might be avoided entirely: for example, the user interface may be refined using a rapid prototyping system and client interviews.
+
+The lightweight approach is a traditional engineering compromise, and there is a tradeoff.
+As formal methods become more common, engineers will have to learn type theory, modern algebra and proof techniques.
+Ultimately, engineers will have to think more like mathematicians.
+%(source https://users.ece.cmu.edu/koopman/des_s99/formal_methods 03JUL2019)
 
@@
 thereby demanding adaptation if another site is analyzed.
+
+\section{Summary}

### 2019-07-04 Tex/Old text/chapters/chapter02.tex
thesis updated text

--- 2019-07-01 Tex/Old text/chapters/chapter02.tex
@@
-chapter02 text here
-
-////////////////// Begin old stuff
+In this chapter some concepts related to the intersection of the two areas of this research are presented: the computer science applied to an electrical engineering problem, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.
+
+First, the concept of formal verification is introduced as background to understanding how a methodology that performs (mainly) bug detection can be used to validate a design sizing or to obtain an optimal solution of PV systems.
+
+And secondly, how a solar PV system can be modelled in order to be verified/optimized by the formal verification methodology.
+
+\section{Formal Methods, Formal Design and Formal Verification}
+Formal methods are system design techniques that use rigorously specified mathematical models to validate systems, most notably (and known for) software and hardware systems~\cite{Collins98}.
+In contrast to other design systems, formal methods use mathematical proof as a complement to system testing in order to ensure correct behavior.
+With increasing scale and complexity, and safety becomes a more important issue, the formal approach to system design offers another level of insurance.
+
+Formal methods differ from other design systems through the use of formal verification schemes, the basic principles of the system must be proven correct before they are accepted~\cite{Bowen93}.
+Traditional system design has used extensive testing to verify behavior, but testing is capable of only finite conclusions.
+Dijkstra and others have demonstrated that tests can only show the situations where a system won't fail, but cannot say anything about the behavior of the system outside of the testing scenarios~\cite{Bentley99}.
+In contrast, once a theorem is proven true it remains true.
+
+It is very important to note that formal verification does not avoid the need for testing~\cite{Bowen95}.
+Formal verification cannot fix bad assumptions in the design, but it can help identify errors in reasoning which would otherwise be left unverified.
+In several cases, engineers have reported finding flaws in systems once they reviewed their designs formally~\cite{Kling95}.
+
+A formal design can be summarized as a three step process, as described below~\cite{Collins98}:
+
+\begin{itemize}
+\item Formal Specification: During the formal specification phase, the engineer rigorously defines a system using a modelling language.
+Modeling languages are fixed grammars which allow users to model complex structures out of predefined types (are rigorously defined).
+This process of formal specification is similar to the process of converting a word problem into algebraic notation and help engineers to clearly define their problems, goals and solutions.
+Several engineers who have used formal specifications say that the clarity that this stage produces is a benefit in itself~\cite{Kling95}.
+\item Verification: As stated above, formal methods differ from other specification systems by their heavy emphasis on provability and correctness.
+By building a system using a formal specification, the designer is actually developing a set of theorems about his system.
+By proving these theorems correct, the formal verification ensures that the modelled system has an intended behavior.
+Verification is a difficult process, largely because even the simplest system has several dozen theorems, each of which has to be proven.
+Given the demands of complexity and Moore's law, almost all formal systems use an automated theorem proving tool of some form.
+That is the origin of 'automated verification' definition.
+These tools can prove simple theorems, verify the semantics of theorems, and provide assistance for verifying more complicated proofs and with feedback about the trace of the error (in order to correct the system and the specification of it).
+\item Implementation: Once the model has been specified and verified, it is implemented by converting the specification into code.
+
+\end{itemize}
+
+%Formal methods are viewed with a certain degree of suspicion.
+While formal methods research has been progressing since 1960's, formal methods are only being slowly accepted by engineers.
+There are several reasons for this, but most of the problems seem to be a result of misapplication.
+Most formal systems are extremely descriptive and all-encompassing, modeling languages have generally been judged by their capacity to model anything.
+Unfortunately, these same qualities make formal methods very difficult to use, especially for engineers untrained in the type theory needed for most formal systems.[Bowen93]
+%
+%Conversely, it is apparent that some form of formal specification is necessary: complex systems require formal models.
+In addition,the mathematics required for formal methods is becoming a more prominent fixture of engineering curricula, engineering schools in Europe are already requiring courses in VDM, Z and similar formal specifications.
+Ultimately, formal methods will acquire some form of acceptance, but compromises will be made in both directions: formal methods will become simpler and formal methods training will become more common.
+%
+%Key Concepts
+%Provability And Automated Verification
+%Formal methods are distinguished from other specification systems by their emphasis on correctness and proof, which is ultimately another measure of system integrity.
+Proof is a complement, not a substitute, for testing.
+Testing is an important part of guaranteeing any system's fitness, but it is finite.
+Testing cannot demonstrate that a system operates properly; it can only demonstrate that the system works for the tested cases.
+Because testing cannot demonstrate that the system should work outside the tested cases, formal proof is necessary.
+%
+%Formally proving computer systems is not a new idea.
+Knuth and Dijkstra have written extensively on the topic, although their methods of proof are based on the traditional mathematical methods.
+In pure sciences, proofs are verified through extensive peer review before publication.
+Such techniques are time-intensive and less than perfect; it isn't unusual for a published proof to contain a flaw.
+Given the cost and time requirements of systems engineering, traditional proving techniques are not really applicable.
+%
+%Because of the costs of hand verification, most formal methods use automated theorem proving systems to verify their designs.
+Automated theorem provers are best described as mathematical CAD tools: they can prove simple propositions and automatically and provide assistance for verifying more complex theorems.
+%
+%Benefits Of Formal Models
+%Formal methods offer additional benefits outside of provability, and these benefits do deserve some mention.
+However, most of these benefits are available from other systems, and usually without the steep learning curve that formal methods require.
+%
+%Discipline: By virtue of their rigor, formal systems require an engineer to think out his design in a more thorough fashion.
+In particular, a formal proof of correctness is going to require a rigorous specification of goals, not just operation.
+This thorough approach can help identify faulty reasoning far earlier than in traditional design.[Bowen95]
+%The discipline involved in formal specification has proved useful even on already existing systems.
+Engineers using the PVS system, for example, reported identifying several microcode errors in one of their microprocessor designs.[Miller95]
+%
+%Precision: Traditionally, disciplines have moved into jargons and formal notation as the weaknesses of natural language descriptions become more glaringly obvious.
+There is no reason that systems engineering should differ, and there are several formal methods which are used almost exclusively for notation.[Bowen93]
+%For engineers designing safety-critical systems, the benefits of formal methods lie in their clarity.
+Unlike many other design approaches, the formal verification requires very clearly defined goals and approaches.
+In a safety critical system, ambiguity can be extremely dangerous, and one of the primary benefits of the formal approach is the elimination of ambiguity.[Kling94].
+%
+%Weaknesses Of Formal Methods
+%: Bowen points out that formal methods are generally viewed with suspicion by the professional engineering community, and the propensity of tentative case studies and advocacy papers for the formal approach would seem to support his thesis [Bowen93].
+There are several reasons why formal methods are not used as much as they might be, most stemming from overreaching on the part of formal methods advocates.
+%Expense:Because of the rigor involved, formal methods are always going to be more expensive than traditional approaches to engineering.
+However, given that software cost estimation is more of an art than a science, it is debatable exactly how much more expensive formal verification is.
+In general, formal methods involve a large initial cost followed by less consumption as the project progresses; this is a reverse from the normal cost model for software development.[Bowen93]
+%
+%Limits Of Computational Models:While not a universal problem, most formal methods introduce some form of computational model, usually hamstringing the operations allowed in order to make the notation elegant and the system provable.
+Unfortunately, these design limitations are usually considered intolerable from a developer's perspective.
+%An excellent example comes from SML.
+Statements of proof in SML depend on a purely functional programming model: all data is passed through the parameter/return mechanism of a function, no side effect alterations, modifications of global variables or the like is allowed [Paulson96].
+Handling side effects and other aberrancies are a requirement for any system involving input, network operations or other systems which require interrupts, meaning that SML's model is, to some extent, broken.
+%
+%Usability:Traditionally, formal methods have been judged on the richness of their descriptive model.
+That is, 'good' formal methods have described a wide variety of systems, and 'bad' formal methods have been limited in their descriptive capacities.
+While an all-encompassing formal description is attractive from a theoretical perspective, it invariably involved developing an incredibly complex and nuanced description language, which returns to the difficulties of natural language.
+Case studies of full formal methods often acknowledge the need for a less all-encompassing approach.[Miller95]
+%Arguably, many of these failures can be attributed to overreaching on the part of formal methods advocates. This reasoning has led to the lightweight approach to formal specification.
+%
+%The Lightweight Approach
+%The flaws in formal specifications have been heavily focused on in the past few years, leading to several alternate approaches.
+The traditional view of formal methods as all-encompassing highly abstracted schemes has led to formal methods being all-encompassing, extremely rigorous, and very expensive.
+While theoretically appealing, formal methods have generally been ignored by engineers in the field.
+%The lightweight approach to formal design recognizes that formal methods are not a panacea: there are areas where formal methods are useful, and areas where a formal specification will accomplish nothing.
+In a lightweight design, formal methods are used in specific locations, and different formal methods may be used in different subsystems, ideally playing to the strengths of each method [Easterbrook 98].
+In such a system, Petri Nets might be used to describe the communications protocol, and a LARCH system might be used to model the data storage.
+For other parts of the system, formal specifications might be avoided entirely: for example, the user interface may be refined using a rapid prototyping system and client interviews.
+%
+%The lightweight approach is a traditional engineering compromise, and there is a tradeoff.
+As formal methods become more common, engineers will have to learn type theory, modern algebra and proof techniques.
+Ultimately, engineers will have to think more like mathematicians.
+
+\section{Project Validation, Automated Verification and Synthesis Using Model Checking}
+\label{sec:AutomatedVerification}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+/////////////
+%\section{Automated Verification }
+It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.
+
+If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, resulting in a process known as formal verification.
+Verification may form part of a validation process, but in general, validation cannot be formalized because it relates a system design to intent.
+
+Simulation may also be used for validation, but it is more problematic for verification.
+In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
+
+Testing can also be used for validation, but for the same reasons, it too is problematic for verification.
+
+According \cite{Clarke2008}, verification procedure is an intelligent exhaustive search of the state space of the design.
+In addition, according to \cite{Forejt2011}, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system.
+One successful method in this domain is model checking.
+
+\subsection{Model Checking}
+
+Model checking is an automatic verification technique, as defined by \cite{Clarke2008}.
+Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
+
+The process of model checking can be divided in three components: modeling, specification, and verification method.
+
+\begin{itemize}
+\item In modeling, a model (normally mathematical) of the system is created; 
+\item In specification, normally a list of properties to be satisfied by the system is stablished, i.e., the requirements, as reliability to performance for example.
+\item Normally is expressed in temporal logic form ($CTL$);
+\item The model checking is the verification method itself. 
+\end{itemize}
+
+The model checking algorithm can be described as:
+
+\begin{itemize}
+\item Given the model $ 'M' $ and a $CTL$ formula $ \phi $ as input;  
+\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
+\item It returns $YES$ if $ \phi $ is $TRUE$, or returns $NO$ if $ \phi $ is $FALSE$.
+
+\end{itemize}
+Specifically at the $FALSE$ situation, the algorithm returns a counterexample that is useful as diagnostic of the system, in order to discover in which situation the model is violated.
+\cite{Clarke2008} consider that the most important advantage of the use of model checking.
+
+Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
+However, there is a main disadvantage of model checking: the state explosion problem.
+
+The model checking problem can be defined as shown in \cite{Clarke2008}:
+
+\begin{itemize}
+\item Let $M$ be a Kripke structure (i.e., state transition graph);
+\item $f$ be the specification in temporal logic (a formula);
+\item Find all states $s$ of $M$ such that $M , s \models f$
+\end{itemize}
+
+Fig. \ref{fig:modelcheckstruc} shows the structure of a typical model checking system. A preprocessor extracts a state transition graph from a system (program or circuit).
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{modelcheckstruc}
+\centering
+\caption{Model Checker structure (Source: \cite{Clarke2008})}
+\label{fig:modelcheckstruc}
+\end{figure}
+
+Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study.
+
+The Fig. \ref{fig:systemverif} shows the process to convert a real system to a model in order to be verified by a model checking.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{systemverif}
+\centering
+\caption{From real system verification to model checking (adapted from \cite{Clarke2008})}
+\label{fig:systemverif}
+\end{figure}
+
+In order to solve the problem of state explosion, many different techniques were developed at the last decades. One of the promising is the Bounded Model Checking (BMC).
+
+BMC is a method that checks the model up to a given path in the path length.
+BMC algorithms traverses a finite state machine for a fixed number of steps, , and checks whether violation occurs with this bound.
+It uses fast SAT solvers, where SAT means satisfiability.
+SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression.
+SAT solvers are used in BMC, such that if there are some Boolean function, the solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
+If SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
+
+CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++, as can be seen in \cite{Kroening}.
+
+ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.  
+The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
+
+//////////////////
+
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}.
+Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
+
+Here we evaluate three state-of-the-art model checkers to formally verifying and synthesize PV designs w.r.t. user requirements.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{CBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
+CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
+If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
+CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{ESBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{CPAchecker}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Automatic program verification requires a choice between precision and efficiency.
+%The more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs.
+Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
+In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
+The CPA formalism provides an interface for the definition of program analyses.
+Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
+The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
+Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
+%Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+%CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
+For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
+\textcolor{red}{It is unclear what a CPA is.}
+%In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
+
+//////Begin optimization
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Automated Verification Using Model Checking}
+\label{sec:AutomatedVerification}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Although simulation and testing explore possible behaviors and scenarios of a given system, 
+they leave open the question of whether unexplored trajectories may contain a flaw. 
+Formal verification conducts an exhaustive exploration of all possible behaviors; 
+when a design is said to be ``correct'' by a formal verification method, it implies that all 
+behaviors have been explored, and questions regarding adequate coverage or missed behavior 
+becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
+applies mathematical reasoning to obtain guarantees about the correctness of a system; 
+one successful method in this domain is model checking~\cite{Clarke2012}. 
+Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{CBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The C Bounded Model Checker (CBMC) falsifies assertions in C programs 
+or proves that they are safe if a completeness threshold is given~\cite{Kroening}. 
+CBMC implements a bit-precise translation of a C program, annotated with assertions 
+and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, 
+then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification 
+flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; 
+it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, 
+into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
+(ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
+which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
+(iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{ESBMC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{CPAchecker}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Automatic program verification requires a choice between precision and efficiency. 
+The more precise a method, the fewer false positives it will produce, but also the 
+more expensive it is, and thus applicable to fewer programs. 
+Historically, this trade-off was reflected in two major approaches to static verification: 
+program analysis and model checking. In order to experiment with the trade-off, 
+and in order to be able to set the dial between the two extreme points, 
+Configurable Program Analysis (CPA) provides a conceptual basis for expressing 
+different verification approaches in the same formal setting. The CPA formalism 
+provides an interface for the definition of program analyses. Consequently, CPAchecker 
+provides an implementation framework that allows the seamless integration of program 
+analyses that are expressed in the CPA framework. The comparison among different 
+approaches in the same experimental setting is intended to be easy and the experimental 
+results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, 
+the central data structure is a set of control-flow automata (CFA), which consists of control-flow 
+locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and 
+interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
+and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+
+%-----------------------------------------------------------
+\subsection{Program Synthesis}
+\label{sec:ProgramSynthesis}
+%-----------------------------------------------------------
+
+The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
+In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
+As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
+CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
+	\caption{CEGIS applied to PV system sizing.}
+	\label{Counter-Example-Guided-Inductive-Synthesis}
+\end{figure}
+
+The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .
+\forall \vec{x}.
+\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
+The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
+Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
+Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
+If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
+
+One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
+
+However, in our variant CEGIS method proposed here, there are four particular differences related to the traditional CEGIS: 
+(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
+(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
+(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
+a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard 
+a given candidate that could be feasible in the next iteration with a new lower bound.
+
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
 
@@
 \centering
-\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
+\caption{Schematic diagram of the battery. Source: \cite{Hansen}}
 \label{fig:batteryckt}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Verification Using Model Checking}
-\label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-/////////////
-%\section{Automated Verification }
-It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.
-
-If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, resulting in a process known as formal verification.
-Verification may form part of a validation process, but in general, validation cannot be formalized because it relates a system design to intent.
-
-Simulation may also be used for validation, but it is more problematic for verification.
-In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-
-Testing can also be used for validation, but for the same reasons, it too is problematic for verification.
-
-According \cite{Clarke2008}, verification procedure is an intelligent exhaustive search of the state space of the design.
-In addition, according to \cite{Forejt2011}, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system.
-One successful method in this domain is model checking.
-
-Model checking is an automatic verification technique, as defined by \cite{Clarke2008}.
-Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
-
-The process of model checking can be divided in three components: modeling, specification, and verification method.
-
-\begin{itemize}
-\item In modeling, a model (normally mathematical) of the system is created; 
-\item In specification, normally a list of properties to be satisfied by the system is stablished, i.e., the requirements, as reliability to performance for example.
-\item Normally is expressed in temporal logic form ($CTL$);
-\item The model checking is the verification method itself. 
-\end{itemize}
-
-The model checking algorithm can be described as:
-
-\begin{itemize}
-\item Given the model $ 'M' $ and a $CTL$ formula $ \phi $ as input;  
-\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
-\item It returns $YES$ if $ \phi $ is $TRUE$, or returns $NO$ if $ \phi $ is $FALSE$.
-
-\end{itemize}
-Specifically at the $FALSE$ situation, the algorithm returns a counterexample that is useful as diagnostic of the system, in order to discover in which situation the model is violated.
-\cite{Clarke2008} consider that the most important advantage of the use of model checking.
-
-Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
-However, there is a main disadvantage of model checking: the state explosion problem.
-
-The model checking problem can be defined as shown in \cite{Clarke2008}:
-
-\begin{itemize}
-\item Let $M$ be a Kripke structure (i.e., state transition graph);
-\item $f$ be the specification in temporal logic (a formula);
-\item Find all states $s$ of $M$ such that $M , s \models f$
-\end{itemize}
-
-Fig. \ref{fig:modelcheckstruc} shows the structure of a typical model checking system. A preprocessor extracts a state transition graph from a system (program or circuit).
-
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{modelcheckstruc}
-\centering
-\caption{Model Checker structure (Source: \cite{Clarke2008})}
-\label{fig:modelcheckstruc}
-\end{figure}
-
-Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study.
-
-The Fig. \ref{fig:systemverif} shows the process to convert a real system to a model in order to be verified by a model checking.
-
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{systemverif}
-\centering
-\caption{From real system verification to model checking (adapted from \cite{Clarke2008})}
-\label{fig:systemverif}
-\end{figure}
-
-In order to solve the problem of state explosion, many different techniques were developed at the last decades. One of the promising is the Bounded Model Checking (BMC).
-
-BMC is a method that checks the model up to a given path in the path length.
-BMC algorithms traverses a finite state machine for a fixed number of steps, , and checks whether violation occurs with this bound.
-It uses fast SAT solvers, where SAT means satisfiability.
-SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression.
-SAT solvers are used in BMC, such that if there are some Boolean function, the solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
-If SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
-
-CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++, as can be seen in \cite{Kroening}.
-
-ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.  
-The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
-
-//////////////////
-
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}.
-Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
-Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t.
-user requirements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
-CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
-If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
-CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Automatic program verification requires a choice between precision and efficiency.
-%The more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs.
-Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
-In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
-The CPA formalism provides an interface for the definition of program analyses.
-Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
-Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
-%Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-%CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
-For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs.
-\textcolor{red}{It is unclear what a CPA is.}
-%In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
-
-//////Begin optimization
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Automated Verification Using Model Checking}
-\label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Although simulation and testing explore possible behaviors and scenarios of a given system, 
-they leave open the question of whether unexplored trajectories may contain a flaw. 
-Formal verification conducts an exhaustive exploration of all possible behaviors; 
-when a design is said to be ``correct'' by a formal verification method, it implies that all 
-behaviors have been explored, and questions regarding adequate coverage or missed behavior 
-becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
-applies mathematical reasoning to obtain guarantees about the correctness of a system; 
-one successful method in this domain is model checking~\cite{Clarke2012}. 
-Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs 
-or proves that they are safe if a completeness threshold is given~\cite{Kroening}. 
-CBMC implements a bit-precise translation of a C program, annotated with assertions 
-and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, 
-then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification 
-flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; 
-it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, 
-into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
-(ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
-which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
-(iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Automatic program verification requires a choice between precision and efficiency. 
-The more precise a method, the fewer false positives it will produce, but also the 
-more expensive it is, and thus applicable to fewer programs. 
-Historically, this trade-off was reflected in two major approaches to static verification: 
-program analysis and model checking. In order to experiment with the trade-off, 
-and in order to be able to set the dial between the two extreme points, 
-Configurable Program Analysis (CPA) provides a conceptual basis for expressing 
-different verification approaches in the same formal setting. The CPA formalism 
-provides an interface for the definition of program analyses. Consequently, CPAchecker 
-provides an implementation framework that allows the seamless integration of program 
-analyses that are expressed in the CPA framework. The comparison among different 
-approaches in the same experimental setting is intended to be easy and the experimental 
-results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, 
-the central data structure is a set of control-flow automata (CFA), which consists of control-flow 
-locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and 
-interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
-and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-
-%-----------------------------------------------------------
-\subsection{Program Synthesis}
-\label{sec:ProgramSynthesis}
-%-----------------------------------------------------------
-
-The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
-In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
-As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
-	\caption{CEGIS applied to PV system sizing.}
-	\label{Counter-Example-Guided-Inductive-Synthesis}
-\end{figure}
-
-The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .
-\forall \vec{x}.
-\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
-The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
-
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
-Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
-
-One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
-
-However, in our variant CEGIS method proposed here, there are four particular differences related to the traditional CEGIS: 
-(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
-(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
-(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
-(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
-a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard 
-a given candidate that could be feasible in the next iteration with a new lower bound.
-
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
 

### 2019-07-04 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 
-And secondly, how a solar PV system can be modelled in order to be verified/optimized by the formal verification methodology.
+And secondly, how a solar PV system can be modelled in order to be validated or optimized by the formal verification methodology.
 
 \section{Formal Methods, Formal Design and Formal Verification}
+
 Formal methods are system design techniques that use rigorously specified mathematical models to validate systems, most notably (and known for) software and hardware systems~\cite{Collins98}.
@@
 In contrast, once a theorem is proven true it remains true.
+
+Prior the 80's, mainly deductive verification was used as formal method, with the use of axioms and proving rules to demonstrate the correctness of the system.
+The original focus was to verify critical systems based on the premise that 'if system is important, must spend the enough time to verify it'~\cite{Lowry1998}.
+Worth to mention that back in time, formal methods were initially performed by hand.
 
@@
 Verification is a difficult process, largely because even the simplest system has several dozen theorems, each of which has to be proven.
-Given the demands of complexity and Moore's law, almost all formal systems use an automated theorem proving tool of some form.
+Given the demands of complexity and Moore's law, almost all formal systems use an automated theorem proving tool of some form~\cite{Collins98}.
 That is the origin of 'automated verification' definition.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-/////////////
+
 %\section{Automated Verification }
@@
 \centering
-\caption{Model Checker structure (Source: \cite{Clarke2008})}
+\caption{Model Checker structure. Source: \cite{Clarke2008}.}
 \label{fig:modelcheckstruc}
@@
 \centering
-\caption{From real system verification to model checking (adapted from \cite{Clarke2008})}
+\caption{From real system verification to model checking. Source: adapted from \cite{Clarke2008}.}
 \label{fig:systemverif}
@@
 It uses fast SAT solvers, where SAT means satisfiability.
+
 SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression.
@@
 
-CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++, as can be seen in \cite{Kroening}.
-
-ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.  
+%%CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++, as can be seen in \cite{Kroening}. 
+%
+%ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.  
 The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
 
-//////////////////
-
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}.
+%Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}.
 Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
@@
 
-Here we evaluate three state-of-the-art model checkers to formally verifying and synthesize PV designs w.r.t. user requirements.
+At this work will be evaluated three state-of-the-art model checkers to formally verifying and synthesize PV designs w.r.t. user requirements.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
@@
 If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
-CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+
+CBMC's verification flow can be summarized in three stages:
+
+\begin{itemize}
+\item Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort;
+\item Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
+\item Back-end: supports SAT and SMT solvers to discharge verification conditions.
+\end{itemize}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+
+ESBMC's verification flow can be summarized in three stages:
+
+\begin{itemize}
+\item A front-end that can read and compile C code, where the system formal specification is first handled; 
+\item Preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally 
+\item The SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+\end{itemize}
+
 ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
@@
 This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
-%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Automatic program verification requires a choice between precision and efficiency.
-%The more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs.
+The more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs.
+
 Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
 In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
+
 The CPA formalism provides an interface for the definition of program analyses.
@@
 Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+
 The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
-%Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
 %CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing.
@@
 //////Begin optimization
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Automated Verification Using Model Checking}
-\label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Although simulation and testing explore possible behaviors and scenarios of a given system, 
-they leave open the question of whether unexplored trajectories may contain a flaw. 
-Formal verification conducts an exhaustive exploration of all possible behaviors; 
-when a design is said to be ``correct'' by a formal verification method, it implies that all 
-behaviors have been explored, and questions regarding adequate coverage or missed behavior 
-becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
-applies mathematical reasoning to obtain guarantees about the correctness of a system; 
-one successful method in this domain is model checking~\cite{Clarke2012}. 
-Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs 
-or proves that they are safe if a completeness threshold is given~\cite{Kroening}. 
-CBMC implements a bit-precise translation of a C program, annotated with assertions 
-and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, 
-then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification 
-flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; 
-it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, 
-into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
-(ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
-which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
-(iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Automatic program verification requires a choice between precision and efficiency. 
-The more precise a method, the fewer false positives it will produce, but also the 
-more expensive it is, and thus applicable to fewer programs. 
-Historically, this trade-off was reflected in two major approaches to static verification: 
-program analysis and model checking. In order to experiment with the trade-off, 
-and in order to be able to set the dial between the two extreme points, 
-Configurable Program Analysis (CPA) provides a conceptual basis for expressing 
-different verification approaches in the same formal setting. The CPA formalism 
-provides an interface for the definition of program analyses. Consequently, CPAchecker 
-provides an implementation framework that allows the seamless integration of program 
-analyses that are expressed in the CPA framework. The comparison among different 
-approaches in the same experimental setting is intended to be easy and the experimental 
-results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, 
-the central data structure is a set of control-flow automata (CFA), which consists of control-flow 
-locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and 
-interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
-and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-
 %-----------------------------------------------------------
-\subsection{Program Synthesis}
+\subsection{CEGIS and Program Synthesis}
 \label{sec:ProgramSynthesis}
@@
 Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
-
-However, in our variant CEGIS method proposed here, there are four particular differences related to the traditional CEGIS: 
-(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
-(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
-(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
-(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
-a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard 
-a given candidate that could be feasible in the next iteration with a new lower bound.
-
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
 
@@
 \centering
-\caption{Unregulated standalone SPV system with DC load (Source: \cite{Roy})}
+\caption{Unregulated standalone SPV system with DC load. Source: \cite{Roy}.}
 \label{fig:unregSPV}
@@
 \centering
-\caption{Regulated standalone SPV system with DC load (Source: \cite{Roy})}
+\caption{Regulated standalone SPV system with DC load. Source: \cite{Roy}.}
 \label{fig:regSPV1}
@@
 \centering
-\caption{Regulated standalone SPV system with battery DC load (Source: \cite{Roy})}
+\caption{Regulated standalone SPV system with battery DC load. Source: \cite{Roy}.}
 \label{fig:regSPV2}
@@
 \centering
-\caption{Regulated standalone system with battery, AC load (Source: \cite{Roy})}
+\caption{Regulated standalone system with battery, AC load. Source: \cite{Roy}.}
 \label{fig:regSPV3}
@@
 \centering
-\caption{Block diagram for the stand-alone PV system (Source: \cite{Hansen})}
+\caption{Block diagram for the stand-alone PV system. Source: \cite{Hansen}.}
 \label{fig:blockdiagram}
@@
 \centering
-\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
+\caption{PV cell, module and array. Source: \cite{SamlexSolar}.}
 \label{fig:celmodarray}
@@
 \centering
-\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
+\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor. Source: \cite{Cubas}.}
 \label{fig:equivckt}
@@
 \centering
-\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
+\caption{$ I-V $ characteristic curve of an ideal PV cell. Source: \cite{Saloux}.}
 \label{fig:ivcurve}
@@
 \centering
-\caption{Schematic diagram of the battery. Source: \cite{Hansen}}
+\caption{Schematic diagram of the battery. Source: \cite{Hansen}.}
 \label{fig:batteryckt}
@@
 \centering
-\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
+\caption{Operating principle of an overcharge protector. Source: \cite{Hansen}.}
 \label{fig:controllerover}
@@
 \centering
-\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
+\caption{Operating principle of a discharge protector. Source: \cite{Hansen}.}
 \label{fig:controllerdisc}
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process (Source: \cite{Hansen})}
+\caption{Summary of the controller process. Source: \cite{Hansen}.}
 \label{table:controller}

### 2019-07-04 Tex/Old text/chapters/chapter03.tex
thesis updated text

@@
+\section{Intro}
+
+Introduction text here
+
 \section{Automated Verification}
@@
  \section{Optimization}
+
+\subsection{Variant CEGIS} 
+Related to the CEGIS presented in chapter Background, it was created a variant CEGIS method at this work. There are four particular differences related to the traditional CEGIS:
+
+\begin{itemize}
+\item There exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+\item If the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} 
+\item The lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
+\item As a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate that could be feasible in the next iteration with a new lower bound.
+\end{itemize}
+
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
+
 Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
@@
 \end{itemize}
+
+\section{Conclusion}

### 2019-07-04 Tex/Old text/chapters/introduction.tex
thesis updated text

@@
 \section{Thesis Organization}
-Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling.
-Section~\ref{sec:AutomatedVerification} presents the automated verification technique.
-The methodology is presented in section~\ref{sec:Methodology}.
-Section~\ref{sec:results} is devoted to the results.
-Section~\ref{sec:Conclusions} presents the conclusion and describes future work.
-
-Section~\ref{sec:Background} gives the background about related studies, 
-program synthesis, sizing design and validation of PV systems, and the mathematical modeling. 
-Section~\ref{sec:Method} presents the automated formal synthesis proposed 
-in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, 
-results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
+% ~\nameref or \autoref{
+Chapter \nameref{chap:background} gives the theoretical basis on formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.
+Chapter~\nameref{chap:methodology} presents the automated verification  and the automated synthesis techniques.
+The results related to the experimental use of automated verification are in \autoref{chap:automatedverification}.
+While \autoref{chap:automatedsynthesis} is devoted to the experimentation,
+results and discussions of the automated synthesis technique. Chapter \nameref{chap:conclusions} presents the main contributions, future work directions and concluding remarks.

### 2019-07-06 Tex/elsevier/trindade_appliedenergy_rev1.tex
applied energy upadted text

--- 2019-06-29 Tex/elsevier/trindade_appliedenergy_rev0.tex
@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space.
-We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
+There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
+\textcolor{red}{We present a sound, automated and pioneer approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with focus on the computer optimization method and not in criteria or objectives that were the focus of improvement in past works}.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound \textcolor{red}{cost} via symbolic model checking.
 If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
@@
 Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach.
+Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, \textcolor{red}{beyond that a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach}.
 \end{abstract}
@@
 
-However, formal methods based on \textit{symbolic model checking} and its application 
+\textcolor{red}{At the present work, the focus is not a novelty in the criteria or the optimization objectives.
+Our aim and novelty is to show a most effective approach on the pursuit of the optimal solution, using formal methods.}
+
+Formal methods based on \textit{symbolic model checking} and its application 
 to synthesize PV systems have not been further explored in literature, which could offer 
@@
 
-Our work makes two major contributions. Firstly, the use of automated 
+Our work makes two major contributions. \textbf{Firstly}, the use of automated 
 symbolic verification methods in electrical systems was uncommon in recent 
 prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
-PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
+optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
 charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
@@
 verifiers with the goal of obtaining the best performance in our verification 
-back-end for synthesizing optimal PV systems.
+back-end for synthesizing optimal PV systems, \textcolor{red}{being the first work that performs this type of comparative.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textcolor{red} {Here we discuss only the use of use of formal methods on electrical systems in general, because there is not the use of it or even synthesis program to obtain the optimization of PV sizing.}
 
@@
 This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design-space of one operation hour of the PV panels behavior.
 This related study did not include other components of a stand-alone solar PV system.
@@
 %------------------------------------------------------
-\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
+\section{SYNTHESIZING OPTIMAL SIZING OF STAND-ALONE SOLAR PHOTOVOLTAIC SYSTEMS}
 \label{sec:Method}
@@
 %---------------------------------------------------------------------------
-\section{Experimental Evaluation}
+\section{EXPERIMENTAL EVALUATION}
 \label{sec:Results}
@@
 to obtain the optimal size of PV system using software model 
-checking techniques. We have considered seven case studies 
+checking techniques.
+\textcolor{red}{The focus was on the method to obtain the optimal solution, based on formal methods that can cover the design-space better than simulation tools}.
+We have considered seven case studies
 from PV systems in two different sites of the Amazonas State 

### 2019-07-08 Tex/elsevier/trindade_appliedenergy_rev1.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
-\textcolor{red}{We present a sound, automated and pioneer approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with focus on the computer optimization method and not in criteria or objectives that were the focus of improvement in past works}.
+\textcolor{red}{We present a novel sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last two decades}.
 In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound \textcolor{red}{cost} via symbolic model checking.
@@
 Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, \textcolor{red}{beyond that a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach}.
+Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing.
+\textcolor{red}{We also present a comparative with a specialized simulation tool over real PV systems to show the effectiveness of our approach, which is able to provide more accurate results of optimal sizing of stand-alone PV systems than that existing simulation tool}.
 \end{abstract}

### 2019-07-08 Tex/elsevier/trindade_appliedenergy_rev1.tex
reviewed Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textcolor{red} {Here we discuss only the use of use of formal methods on electrical systems in general, because there is not the use of it or even synthesis program to obtain the optimization of PV sizing.}
+
+\textcolor{red} {Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.}
 

### 2019-07-08 Tex/elsevier/trindade_appliedenergy_rev1.tex
reviewed Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{red}{At the present work, the focus is not a novelty in the criteria or the optimization objectives.
-Our aim and novelty is to show a most effective approach on the pursuit of the optimal solution, using formal methods.}
+\textcolor{red}{In this study, our focus is not on a novel criteria or optimization objectives.
+Instead, our novelty relies on an effective approach on the pursuit of the optimal solution using formal methods, which outperforms existing state-of-the-art simulation tools.}
 
@@
 
-Our work makes two major contributions. \textbf{Firstly}, the use of automated 
+%------------------------------------------------------
+\subsection{Contributions}
+%------------------------------------------------------
+
+Our work makes three major contributions. \textbf{First}, the use of automated 
 symbolic verification methods in electrical systems was uncommon in recent 
@@
 can find the optimal solution in technical and economical terms. 
-\textbf{Secondly}, we evaluate different state-of-art symbolic software 
+\textbf{Second}, we evaluate different state-of-art symbolic software 
 verifiers with the goal of obtaining the best performance in our verification 
 back-end for synthesizing optimal PV systems, \textcolor{red}{being the first work that performs this type of comparative.}
+\textcolor{red}{\textbf{Third}, our experimental results show that our synthesis method is an effective and efficient approach 
+on the pursuit of the optimal solution of PV system design using formal methods, which outperforms 
+existing state-of-the-art simulation tools.}
 
-\textit{Outline}. Section~\ref{sec:Background} gives the background about related studies, 
+\noindent \textit{Outline}. Section~\ref{sec:Background} gives the background about related studies, 
 program synthesis, sizing design and validation of PV systems, and the mathematical modeling. 

### 2019-07-08 Tex/elsevier/trindade_appliedenergy_rev1.tex
reviewed Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
-\textcolor{red}{We present a novel sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last two decades}.
+There exist various methods and tools to size solar photovoltaic systems; however, these existing tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
+\textcolor{red}{Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last two decades}.
 In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound \textcolor{red}{cost} via symbolic model checking.
@@
 
-\textcolor{red}{In this study, our focus is not on a novel criteria or optimization objectives.
-Instead, our novelty relies on an effective approach on the pursuit of the optimal solution using formal methods, which outperforms existing state-of-the-art simulation tools.}
+\textcolor{red}{Note that in this study, our focus is not on a novel criteria or even optimization objectives.
+Instead, our novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tools.}
 
@@
 \textcolor{red}{\textbf{Third}, our experimental results show that our synthesis method is an effective and efficient approach 
-on the pursuit of the optimal solution of PV system design using formal methods, which outperforms 
-existing state-of-the-art simulation tools.}
+on the pursuit of the optimal solution of PV systems using formal methods, which outperforms 
+existing state-of-the-art simulation tools. As a result, our study marks the first application of a sound
+and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.
+Thus, we considerably advance the state-of-the-art in applied energy over the last two decades 
+with the goal of optimally designing PV systems.}
 

### 2019-07-08 Tex/elsevier/trindade_appliedenergy_rev1.tex
applied energy upadted text

@@
 There exist various methods and tools to size solar photovoltaic systems; however, these existing tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
-\textcolor{red}{Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last two decades}.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound \textcolor{red}{cost} via symbolic model checking.
+Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last two decades.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound cost via symbolic model checking.
 If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
@@
 Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing.
-\textcolor{red}{We also present a comparative with a specialized simulation tool over real PV systems to show the effectiveness of our approach, which is able to provide more accurate results of optimal sizing of stand-alone PV systems than that existing simulation tool}.
+We also present a comparative with a specialized simulation tool over real PV systems to show the effectiveness of our approach, which is able to provide more accurate results of optimal sizing of stand-alone PV systems than that existing simulation tool.
 \end{abstract}
@@
 
-\textcolor{red}{Note that in this study, our focus is not on a novel criteria or even optimization objectives.
-Instead, our novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tools.}
+Note that in this study, our focus is not on a novel criteria or even optimization objectives.
+Instead, our novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tools.
 
@@
 verifiers with the goal of obtaining the best performance in our verification 
-back-end for synthesizing optimal PV systems, \textcolor{red}{being the first work that performs this type of comparative.}
-\textcolor{red}{\textbf{Third}, our experimental results show that our synthesis method is an effective and efficient approach 
+back-end for synthesizing optimal PV systems, being the first work that performs this type of comparative.
+\textbf{Third}, our experimental results show that our synthesis method is an effective and efficient approach 
 on the pursuit of the optimal solution of PV systems using formal methods, which outperforms 
-existing state-of-the-art simulation tools. As a result, our study marks the first application of a sound
+existing state-of-the-art simulation tool. As a result, our study marks the first application of a sound
 and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.
 Thus, we considerably advance the state-of-the-art in applied energy over the last two decades 
-with the goal of optimally designing PV systems.}
+with the goal of optimally designing PV systems.
 
@@
 
-\textcolor{red} {Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.}
+Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.
 
@@
 checking techniques.
-\textcolor{red}{The focus was on the method to obtain the optimal solution, based on formal methods that can cover the design-space better than simulation tools}.
+The focus was on the method to obtain the optimal solution, based on formal methods that can cover the design-space better than simulation tools.
 We have considered seven case studies

### 2019-07-08 Tex/Old text/abstract.tex
thesis updated text

@@
 \begin{center}
-    \Large
-    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
-
-    \vspace{0.4cm}
-    \large
-    Optimal Sizing and Project Validation
-
-    \vspace{0.4cm}
-    \textbf{Alessandro Trindade}
-
+%    \Large
+%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
+%    
+%    \vspace{0.4cm}
+%    \large
+%    Optimal Sizing and Project Validation
+%    
+%    \vspace{0.4cm}
+%    \textbf{Alessandro Trindade}
+%    
     \vspace{0.9cm}
@@
 \end{center}
-verif:
 With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
@@
 Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
-Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-Automated verification using model checking has proven to be an effective technique to validate any kind of system.
-This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
+Tools to evaluate or to size electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space.
+In the other hand, the use of formal methods to model and validate any kind the systems is growing with time, mainly to find bugs in complex hardware and software systems: their aim is to establish system correctness with mathematical rigor.
+The use of formal methods in electrical systems is a recent subject, with research being published only in the last four years.
+Moreover, the use of automated synthesis in order to obtain optimal sizing of solar photovoltaic systems was never done before.
+This Thesis marks two mains achievements: (1) the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load; and (2) a sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis, where every component and function of a solar photovoltaic system is described, including its properties, and the behavioral model that represents the optimal sizing can be synthesized automatically.
+Related to formal verification, case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
 Different verification tools were evaluated as well, in order to compare performance and soundness.
-Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
-
-synthesis:
-There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space.
-We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
+Data from practical applications show the effectiveness of the proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
+Moreover, related to the use of program synthesis, it is proposed a variant of counterexample guided inductive synthesis (CEGIS) approach, with two well-defined phases: first it synthesizes the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
 If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
-Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach.
+Commercial equipment data from different manufacturers are provided to the synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
+The proposed synthesis method is novel and unprecedented to streamline the design of photovoltaic systems.
+Experimental results using seven case studies show that the proposed synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of approach.
 

### 2019-07-08 Tex/Old text/resumo.tex
thesis updated text

--- 2019-07-02 Tex/Old text/fichacatalog.tex
@@
     \vspace{0.9cm}
-    \textbf{Ficha Catalográfica}
+    \textbf{Resumo}
 \end{center}
-\thispagestyle{plain}
-Ficha catalog aqui
+Com custos decrescentes e com melhoria de desempenho, a implantação de sistemas de energia renovável está crescendo cada vez mais rapidamente no mundo.
+Em 2017, pela primeira vez, o número de pessoas sem acesso à eletricidade ficou abaixo de 1 bilhão, mas os dados quanto a universalização do acesso a energia ficaram aquém das metas globais.
+Particular atenção é dada aos sistemas isolados solares fotovoltaicos em áreas rurais ou onde a extensão da rede é inviável.
+Ferramentas para avaliar ou dimensionar projetos de eletrificação estão disponíveis, mas elas são baseadas em simulações que não cobrem todos os aspectos do espaço de projeto.
+Por outro lado, o uso de métodos formais para modelar e validar qualquer tipo de sistema está crescendo com o tempo, principalmente para encontrar bugs em sistemas complexos de \textit{hardware} e \textit{software}: seu objetivo é estabelecer a corretude do sistema com rigor matemático.
+O uso de métodos formais em sistemas elétricos é um assunto recente, com pesquisas sendo publicadas apenas nos últimos quatro anos.
+Além disso, o uso de síntese automatizada para obter um ótimo dimensionamento de sistemas solares fotovoltaicos nunca foi feito antes.
+Esta tese marca duas conquistas principais: (1) a primeira aplicação de modelagem de software para verificar o projeto de um sistema isolado solar fotovoltaico, incluindo painel solar, controlador de carga, bateria, inversor e carga elétrica; e (2) uma abordagem confiável e automatizada para obter o dimensionamento ótimo de sistemas fotovoltaicos usando a síntese de programas, onde cada componente e função de um sistema solar fotovoltaico é descrito, incluindo suas propriedades, e o modelo comportamental que representa o dimensionamento ótimo é sintetizado automaticamente.
+Relacionado a verificação formal, estudos de caso de sistemas fotovoltaicos reais instalados em cinco localidades diferentes foram usados para avaliar a abordagem proposta e para compará-la com ferramenta de simulação especializada.
+Diferentes ferramentas de verificação são avaliadas também, a fim de comparar o desempenho e a confiabilidade dos resultados.
+Dados de aplicações práticas mostram a eficácia da abordagem proposta, onde condições específicas que levam a falhas em um sistema solar fotovoltaico são detalhadas apenas pelo método de verificação automatizado.
+Além disso, em relação ao uso da síntese de programas, propõe-se a variante do método de síntese indutiva guiada por contraexemplos (CEGIS), com duas fases bem definidas: primeiro ele sintetiza o dimensionamento de sistemas fotovoltaicos baseados em confiabilidade de energia, mas que pode não alcançar o menor custo; segundo, a solução proposta é então verificada iterativamente com um limite inferior via verificação de modelo simbólico.
+Se a etapa de verificação não falhar, o limite inferior será ajustado; e se falhar, o contraexemplo é fornecido com o dimensionamento ótimo, vinculando assim a resposta técnica da primeira fase à análise de custo da segunda fase.
+Os dados de equipamentos comerciais de diferentes fabricantes são fornecidos ao mecanismo de síntese e as soluções candidatas são derivadas da análise financeira do dimensionamento obtido.
+O método de síntese proposto é novo e sem precedentes para simplificar o projeto de sistemas fotovoltaicos.
+Resultados experimentais usando sete estudos de caso mostram que o método de síntese é capaz de produzir em um tempo de execução aceitável o dimensionamento ótimo do sistema fotovoltaico, e um comparativo com uma ferramenta de simulação especializada e sistemas fotovoltaicos reais mostra a eficácia da abordagem adotada.
+
+\textit{Palavras-chave}: Verificação formal; verificação automatizada; verificação de modelos; síntese de programa; sistemas elétricos; sistema solar fotovoltaico

### 2019-07-09 Tex/Old text/chapters/introduction.tex
thesis updated text

@@
 %%automated verification
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-There is a close relationship between the lack of energy and the low HDI (Human Development Index)~\cite{Coelho}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
-%The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
-Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
-%Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
-
-In order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
-
-%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
-%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
-%
-%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
-Only a niche market a few years ago, solar PV systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
-%However, this growth is not driven by stand-alone systems.
-
-In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
-%
-%However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
-%
-%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
-In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
-SPV...
-%
-%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
-Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-%
-%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
-%
-%PV systems can be classified into grid-connected and stand-alone systems.
-At this proposal, only off-grid or stand-alone systems will be considered.
-The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-However, those tools are based on running experiments in simulation models.
-Simulation has the advantage of being cheap (if compared to test in real systems) %and can be employed before the system design is concluded
-but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-
-Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
-%with behavior that is, in principle, well determined. 
-Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
-%User or project requirements can be added during the creation of the formal model to be verified.
-%, as defined by \cite{Trindade}.
-%
-%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
-% Their aim is to establish system correctness with mathematical rigor. 
-%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
-% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
-%
-%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
-%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
-%Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
-%
-%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
-%
-
-//automated synthesis
 Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}.
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
+The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
+Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
+Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
+Therefore, increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
 
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and  Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.,  PSpice~\cite{Gow1999}, or MATLAB/Simulink package~\cite{Benatiallah2017}.
-However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development~\cite{Yatimi}.
+The renewable energy leads to an advance all over the world by protecting the environment: it is clean (low greenhouse gases emissions), operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}.
+Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
 
-Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
+Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV).
+According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
+In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
+
+Only a niche market a few years ago, solar PV systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
+However, this growth is not driven by stand-alone systems.
+
+In other hand, aiming to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
+
+The PV cell in a solar PV system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy.
+Apart from PV modules; the PV systems consist of battery bank, controller, and inverter, plus the load.
+%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
+%
+%However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
+%
+%The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
+
+The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
+
+Moreover, the optimum sizing of these devices is important for reliable operation.
+Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}.
+
+\section{Problem's Definition}
+
+In order to address different aspects of a solar PV project, there is a myriad of public domain and commercial software available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization).
+Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
+%
+Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
+%
+%PV systems can be classified into grid-connected and stand-alone systems.
+At this proposal, only off-grid or stand-alone systems will be considered.
+The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
+However, those tools are based on running experiments in simulation models.
+Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded, but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+
+Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}, with behavior that is, in principle, well determined.
+Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
+User or project requirements can be added during the creation of the formal model to be verified~\cite{Trindade}.
+%
+This area of research is referred as formal methods~\cite{Clarkeetal}. Their aim is to establish system correctness with mathematical rigor. 
+In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of flaws in order to ensure the correctness of the system.
+
+Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner.
+Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
+Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
+%
+%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
+%
+
+%automated synthesis
+In the other hand, optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
 An ideal combination of any PV system is made by the best compromise between two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
@@
 
-//old material
+\section{Objectives}
+This Thesis has the novelty of applying automated verification method to solar PV systems.
+The result is the development of two software: one to perform automated verification and validate the solar PV systems behavior; and other to produce the optimal sizing of solar PV systems through automated synthesis program.
 
-Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV).
-Only a niche market a few years ago, PV are now becoming a mainstream electricity provider, changing the way the world is powered.
-Based in data from \cite{EPIA}, there was an increase of approximately 30\% from 2013 to 2014 in terms of new installations of PV.
-The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}.
-The renewable energy leads to an advance all over the world by protecting the environment: it is clean (low greenhouse gases emissions), operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}.
-Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
-The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
-
-In order to validate or even simulate a potential PV solution, there are a myriad of tools.
-However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.
-
-According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
-In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
-SPV systems can be classified into grid-connected and stand-alone systems.
-At this proposal, only off-grid or stand-alone systems will be considered.
-The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-
-The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy.
-Apart from PV modules; the PV systems consist of battery bank, controller, and inverter, plus the load.
-Moreover, the optimum sizing of these devices is important for reliable operation.
-Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}.
-
-\section{Problem's Definition}
-
-In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
-Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-
-Manufacturers and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
-
-Changing the subject to the design of complex systems, more time is spent on verification than on construction, as shown in \cite{Baier}.
-Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process.
-Programs, and more generally computer systems, may be viewed as mathematical objects with behavior that is, in principle, well determined.
-This makes it possible to specify programs using mathematical logic, which constitutes the intended (correct) behavior.
-Then, one can try to give a formal proof or otherwise establish that the program meets its specification, as defined by \cite{Trindade}.
-
-This area of research is referred as formal methods as defined in \cite{Clarkeetal}. Their aim is to establish system correctness with mathematical rigor.
-
-In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of bugs in order to ensure the correctness of the system.
-
-Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner.
-Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
-Algorithms can verify the system model through systematically explore all their states.
-
-\section{Objectives}
-In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used.
-%The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+Related to \textbf{automated verification}, in this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used.
+The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
 The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are inputted to the proposed tool and automatically verified during the formal process.
@@
 
-///////////
-Here, we use a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing 
-optimal sizing of stand-alone PV systems using commercial equipment data. 
+Related to \textbf{automated synthesis} method and the optimal sizing of stand-alone PV systems, this Thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data to deliver commercial list of items.
 Given a correctness specification $\sigma$, our method uses that as starting point 
@@
 power reliability and system cost.
+Note that in this study, the focus is not on a novel criteria or even optimization objectives.
+Instead, the novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
 
 \section{Contributions}
-This paper makes two main contributions.
+Associated to \textbf{automated verification}, this Thesis makes three main contributions.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
 Secondly
-Firstly, we propose an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system.
-Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies.
-%Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation.
-
-%\textcolor{red}{This introduction is missing the description of the vision, approach and results.
-In particular, try to match each paragraph to: problem, vision, approach, results and contributions.}
+\textbf{Firstly}, it is proposed an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system.
+\textbf{Secondly}, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies. 
+\textbf{Thirdly}, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation. 
 %
@@
 
-/////////////////
-Our work makes two major contributions. Firstly, the use of automated 
-symbolic verification methods in electrical systems was uncommon in recent 
-prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
-PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
-charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
-method together with user requirements and environment constraints, 
-and our synthesis algorithm based on symbolic model checking 
-can find the optimal solution in technical and economical terms. 
-\textbf{Secondly}, we evaluate different state-of-art symbolic software 
-verifiers with the goal of obtaining the best performance in our verification 
-back-end for synthesizing optimal PV systems.
+And linked to \textbf{automated synthesis}, this work makes three major contributions. 
+\textbf{First}, the use of automated symbolic verification methods in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented.
+Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
+\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems, being the first work that performs this type of comparative.
+\textbf{Third}, the experimental results show that our synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
+As a result, this Thesis marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.
+Thus, there is considerably advance the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.
 
 \section{Related Work}
+
+Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.
 

### 2019-07-09 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 
-It is very important to note that formal verification does not avoid the need for testing~\cite{Bowen95}.
-Formal verification cannot fix bad assumptions in the design, but it can help identify errors in reasoning which would otherwise be left unverified.
+Worth to mention that formal verification does not avoid the need for testing~\cite{Bowen95}.
+Formal verification can not fix bad assumptions in the design, but it can help identify errors in reasoning which would otherwise be left unverified.
 In several cases, engineers have reported finding flaws in systems once they reviewed their designs formally~\cite{Kling95}.

### 2019-07-09 Tex/Old text/chapters/introduction.tex
thesis updated text

@@
 
-The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.
+The increase in a number of PV systems installed all over the world brings the need for proper modeling of those equipment and simulation tools for researcher and practitioners involved in their application.
 
@@
 
-Related to \textbf{automated synthesis} method and the optimal sizing of stand-alone PV systems, this Thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data to deliver commercial list of items.
-Given a correctness specification $\sigma$, our method uses that as starting point 
+Related to \textbf{automated synthesis} method and the optimal sizing of stand-alone PV systems, this Thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input.
+Given a correctness specification $\sigma$, the proposed method uses that as starting point 
 and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
@@
 \textbf{First}, the use of automated symbolic verification methods in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented.
-Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
-\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems, being the first work that performs this type of comparative.
-\textbf{Third}, the experimental results show that our synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
+Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with user requirements and environment constraints, and the proposed synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
+\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in the verification back-end for synthesizing optimal PV systems, being the first work that performs this type of comparative.
+\textbf{Third}, the experimental results show that the proposed synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
 As a result, this Thesis marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.

### 2019-07-11 Tex/elsevier/REPLY_original.tex
solar energy revised text

\documentclass[11pt]{article}

\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{url}
%\usepackage{mathtools}
\usepackage{enumerate}
\usepackage[nodayofweek]{datetime}
\usepackage[caption=false]{subfig}
%\mathtoolsset{showonlyrefs}
\usepackage[linesnumbered,lined,ruled,boxed]{algorithm2e}
\SetKw{KwBy}{by}
\usepackage{xcolor}
%\input{rgbcolors}
%\usepackage{color}
\usepackage{natbib}
% \usepackage[style=authoryear-comp,dashed=false]{biblatex}
% \bibliography{piecewise_lyapunov}
\newtheorem{myassumption}{Assumption}
\newcommand{\mstitle}{A Survey on Automated Symbolic Verification and its Application for Synthesizing Cyber-Physical Systems}
\newcommand{\refnumber}{CPS-2018-5006}
\newenvironment{resposta}{~~~\begin{quote}\color{blue}\textbf{Response:}}{\end{quote}}
\newcommand{\comment}[1]{}
%\definecolor{DarkGreen}{rgb}{0.2, 0.4, 0.2}
\usepackage{amsmath}
\usepackage{listings}
\lstset{language=C,basicstyle=\small\ttfamily}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows, calc,patterns,decorations.pathmorphing,decorations.markings}

\newcommand{\param}[2]{\ensuremath{\langle{#1},{#2}\rangle}\xspace}
\textwidth 15cm
\setlength{\textheight}{1.1\textheight}
\newcommand\hi{\hspace*{\parindent}}
\newcommand\vi{\vspace{\baselineskip}}
\newcommand\lac{{\mbox{{\Huge\bf L}\hspace{-0.65em}
\raisebox{-1.2ex}{\Huge\bf A}\hspace{-1.1em}
\raisebox{-0.6ex}{\Huge\bf C~}}}}
\newcommand{\fwlfunction}[1]{\mathcal{FWL}[#1]}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Manuscript Reference Number: \refnumber}
\rhead{Page \thepage\ of \pageref{LastPage}}
\lfoot{}
\rfoot{}

%\pagestyle{headings}
\pagenumbering{roman}
\begin{document}
\setcounter{page}{1}
\thispagestyle{empty}

\hoffset -1.5cm \voffset .5cm

\sf

\vspace*{-2.5cm} \hspace*{-0.1cm} {\small
{\mbox{\begin{minipage}{2cm}
\centerline{\includegraphics[width=2.5cm]{manchester.png}}
\end{minipage}}} \hspace*{0.1cm}
\begin{minipage}{11.0cm}{\large \textbf{UNIVERSITY OF MANCHESTER}}\\
{\sc School of Computer Science}
\end{minipage}
} \vspace*{0mm}

\hspace*{-.7cm} {\rule[-1ex]{15cm}{0.03cm}}

\begin{flushright}
\begin{minipage}{7.0cm}\small
{\bf Please Reply to:}\\
Dr. Lucas Cordeiro\\
University of Manchester\\
School of Computer Science\\
Kilburn Building, Manchester, M13 9PL\\
{\em lucas.cordeiro@manchester.ac.uk}
\end{minipage}
\end{flushright}

\vi
\hspace*{\fill}{\small Manchester, \today.}
\vi

\begin{flushleft}
    Professor Dr. Shiyan Hu and Albert Zomaya\\
    Editors-in-chief\\
	IET Cyber-Physical Systems: Theory \& Applications
    \end{flushleft}
\vi

\begin{flushleft}
\textbf{REF.:} \refnumber
    \end{flushleft}
\vi \vi

\indent Dear Shiyan Hu and Albert Zomaya,
\vi

We thank you for asking us to comply with your Referees' reports. 
We are submitting a revised version of our manuscript entitled ``{\em \mstitle},'' by Lucas C. Cordeiro, Eddie B. de Lima Filho, and Iury V. Bessa. This revised version carefully addresses each comment provided by the reviewers, as suggested in your original decision letter. 
In particular, our reply letter describes all modifications we made to our manuscript and the respective responses to the comments raised by the reviewers.

%\vi

%Thank you very much in advance.

\vi\vi

\indent
Sincerely,\\

\begin{quote}
\begin{quote}
\begin{flushright}

\vi
\vi

Lucas C. Cordeiro~~~~~~~
\end{flushright}
\end{quote}
\end{quote}

\hoffset -1.5cm \voffset .5cm

% =============================================
\newpage
\subsection*{Authors'  Response to the Review Comments on manuscript ``{\mstitle}'' -- Manuscript Reference Number: \refnumber}

\vi

The authors would like to thank the anonymous reviewers for their valuable and constructive comments and suggestions, which helped us significantly improve the quality of our manuscript.

According to the editors-in-chief and reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in blue color, along with the original text. Our responses  to all comments (also in blue color) are given in the sequel, with clear indications about how and where they were addressed along our manuscript.

We hope those modifications in our manuscript and also our responses are sufficient to make our work suitable for publication in {\bf IET Cyber-Physical Systems: Theory \& Applications}.

\newpage

\subsection*{Reviewer \#1 comments followed by the authors' answers:}

\begin{quote}
The paper is a survey on verification and synthesis of embedded and cyber-physical systems. More in detail, the authors consider symbolic model checking (mostly bounded-model checking) and synthesis, and other techniques are also mentioned.

Unfortunately, I don't think that the current version meets the standards for publication.

\begin{resposta} 
We thank this reviewer for the valuable and honest comments about our manuscript. In this revised version, we have carefully addressed each of the reviewers' comments, with the goal of making our manuscript suitable for publication in {\bf IET Cyber-Physical Systems: Theory \& Applications}. In this respect, we have significantly extended our manuscript, in order to describe various model checkers that are not only state-of-the-art, but also contributed to the development of the embedded \& cyber-physical systems (ECPS) field ({\it cf.} Sections 3, 4.5, 7.1 and 7.2). Give that this is a broad research area, we might have forgotten to cite some other relevant work; however, given the current knowledge in system verification, we believe we have covered the most relevant and significant related studies. We have also covered a variety of studies strictly related to verification and synthesis of CPS and hybrid systems ({\it cf.} Section 3) and introduced an illustrative example of a real-world three-tanks system modeled by hybrid-automata ({\it cf.} Section 2, by using computation three logic and linear-time temporal logic), while pointed out the main current challenges to formally verify and synthesize control software for ECPSs ({\it cf.} Sections 6 and 7). In Section 9, we highlighted the main limitations of our survey, in terms of systematic literature review.
\end{resposta}

The two main weaknesses are:

(1) The paper is not specific: a number of sections in the paper and a number of references are not related to ECPS, but only to software verification or to verification in general. For instance, the authors mention Hybrid Systems (HS) and techniques for HS in section 2, but HS are not mentioned after this point.

\begin{resposta}
Indeed, our goal was to tackle literature related to symbolic model checking and program synthesis, while pointing out promising approaches related to ECPSs. As a consequence, we first addressed classical and state-of-the-art techniques, in order to give a broad view, and then restricted to studies specifically related to ECPSs or with potential to be applied to them. Nonetheless, such a strategy may have given the impression that our manuscript's central subject was not ECPS, which we tried to mitigate with the current revised version and its new text, such as current Section 3, as it stands now, and the hybrid-system (HS) example in Section 2. Generally, ECPSs are systems that present both continuous and discrete dynamics, as HSs, and, due to this reason, the main approach to formally verify and synthesize controllers for ECPSs is modeling them through HSs. Section 2 is dedicated to establish a suitable modeling approach for application of formal verification and synthesis techniques: the chosen adequate models are hybrid automata (HA). Thus, it was important to discuss the literature related to representation of hybrid system in this section, in order to achieve the concept notion of hybrid automata and their use for ECPS modeling. In the remaining sections, there is no need for particularly tackling HSs, given that the manuscript is focused on discussing verification and synthesis methodologies for ECPSs, which are usually represented by HA. The goal of the discussion regarding HSs was clarified along the revised Section 2. Furthermore, an example of HA for an ECPS, known as Sim3Tanks, was presented for discussion along the remaining manuscript, in order to illustrate the application of symbolic verification and synthesis.
\end{resposta}

(2) The paper is not structured: for instance, section 3 is a generic introduction to software verification, and a discussion about specific techniques for ECPS verification is only present in section 6. In general, It is not clear how the authors chose their references.
\begin{resposta} 
Indeed, our intention was to provide a broad review regarding symbolic verification and its application to synthesis, while highlighting specific techniques applied to ECPSs, which may have led to this comment. One may notice that we did not mean to focus on a specific set of references, but instead unveil ECPS development and then propose and devise future paths for system design and verification, which are safe and secure by construction ({\it cf.} Section 7). In order to provide more structure and focus on ECPS verification, we have added the second before last paragraph of the introduction and also modified the last one of it, a new Section 3 was added, in order to provide focus on cyber-physical systems, and, finally, the former Section 3 was modified and now constitutes Section 4, which now acts as a discussion text towards the authors' vision for ECPS verification. Additionally, we have substantially expanded the description of symbolic verification tools throughout our manuscript, in order to emphasize their strengthens and weaknesses, when verifying ECPSs, and also their potential to fulfill current technical gaps. Section 6, which is now section 7 and already contained discussion regarding ECPS verification, as mentioned by the reviewer, was also further extended, with more technical information.  
\end{resposta}

(3) More in detail, for 1): section 3 should have a different title, as it is not specific to ECPS. This section should probably be replaced by a section containing specific approaches for ECPS verification. Section 4 should contain more technical details about the approaches presented. Section 5 and section 6 are phrased like a research agenda for ECPS, rather than as a survey (even if some paragraphs under future trends are effectively surveying state of the art).
\begin{resposta} 
	As mentioned in previous responses, we added a new section 3, which now presents material strictly related to ECPS verification, while also tackling aggregate effects, which deserve special attention. That was done as a response to the reviewer's comment, in order to be compliant with its first part. In addition, former section 3 is now section 4, presents a new title, and also includes more material, while bearing the authors' vision regarding future trends in ECPs verification. Former Section 4 is now section 5 and contains more technical material regarding DSVerifier, DSSynth, and Scratch, which indeed improved its efficacy in conveying the proposed material. Former Sections 5 and 6, which are now 6 and 7, respectively, intended to both highlight current challenges, while proposing feasible solutions, and present research towards them, which belong to the state of the art group. Anyway, they are important, since they reveal trends and propose approaches based on real research. In order to expand Section 6, complete its content, and avoid impression of a mere research agenda, while preserving its structure (both trends and state of the art), we have added material related to initial and promising research regarding both ECPS verification and synthesis, which provides more survey structure and is now mixed with insightful research directions. Section 7, in turn, aims to present research problems, where we have also improved literature review, in order to show their relevance.
\end{resposta}

(4) For 2): the authors should specify how they have selected their references. This could be done by adopting a systematic approach, or by defining a taxonomy, or by some other structured approach (e.g., using a running ECPS example).
\begin{resposta} 
	As our article's title suggests, we intended to provide a survey on symbolic verification and its application to ECPS. As a consequence, we addressed a large part of the current existing literature on that matter. Even so, we tried to narrow to ECPS verification, aggregate effects, ECPS synthesis, and open research problems on those areas, while focusing on symbolic model checking; in particular, bounded model checking, \textit{k}-induction, interpolants, symbolic execution, and abstraction. Anyway, we have adopted automated search through popular digital libraries, whose relevant results were filtered according to peer-reviewed conferences and journals in that target area. In addition, we included a few studies outside this group, whose content was highly correlated with our results. Our methodology for reference selection has also employed a broader scheme, which included the strategy mentioned above, as a constructive block, and is described as follows. Firstly, we began with HSs, explained their link with ECPSs, and them expanded by tackling ECPS verification with aggregate effects. Then, we took the cue created by existing approaches, in order to provide a link with symbolic model checking. Later, we moved to ECPS synthesis and merged both regarding challenges and trends. A more detailed description of our literature review can be found in the recently added Section 9.
\end{resposta}

(5) Currently, the paper mentions some techniques, but ignore other approaches. As a concrete example: the authors focus mainly on bounded model checking techniques and tools, but only one tool is described in some detail (ESBMC) in section 6, while others are only mentioned (e.g., CBMC) and this choice is not motivated. Similarly, other software verification techniques (e.g., those based on separation logic) are not considered nor compared for the verification of C code. 
\begin{resposta} 
	As previously explained, bounded model checking (BMC) and its companion techniques ({\it e.g.}, $k$-induction) are envisioned as a promising approach towards ECPS synthesis and verification, as long as merged with system and behavior models, which may have led to this condition. In order to mitigate that, we have focused on symbolic verification methods, and in particular BMC, in some specific parts of the text, and then further described eight additional software verifiers: CPAchecker (Section 6.1), Lazy-CSeq (Section 6.2), Astree (Sections 3.7 and 6.4), Polyspace (Sections 3.7 and 6.4), Frama-C (Sections 3.7 and 6.4), Infer (Section 6.1), SMV (Section 3), NuSMV (Section 3), KLEE (section 4.6). Each verifier is described as follows:

	\textbf{CPAchecker}. Beyer, Dangl, and Wendler described a software verification-framework called CPAchecker, which automatically generates invariants through a combination of data-flow-based invariant generator and dynamic precision adjustment, with the goal of injecting (inductive) invariants into the \textit{k}-induction algorithm. Even though the combination between \textit{k}-induction and continuously-refined invariants significantly enhances verification results, there is still room for improvements, particularly for learning from counterexamples, in order to improve bug finding capabilities.

	\textbf{Lazy-Cseq}. Lazy-CSeq is a code-to-code transformation tool based on Lazy Sequentialization techniques, initially introduced by La Torre {\it et al.} for non-deterministically sequentializing concurrent C programs, which re-uses existing BMC tools as backends, in order to find code violations. Its main idea is to pre-process a concurrent program and convert it into a non-deterministic sequential one, with the goal of simplifying verification tasks.

	\textbf{Astree, Polyspace, and Frama-C}. Astr\'ee, PolySpace, and Frama-C are the most successful implementations of the abstract interpretation technique; in particular, Astr\'ee and PolySpace have been successfully used to prove absence of run-time errors, in real-world flight control software. Although those software verifiers scale relatively well for large code bases, their main drawback is that they usually provide false alarms, due to over-approximation of possible program executions.

	\textbf{Separation logic and Infer}. Another interesting direction for future research consists in investigating the application of separation logic, in order to reason about ECPS. The key idea of separation logic is to perform a local reasoning based on specifications and proofs of a given program component, by considering only the portion of memory used by that same component, and not the entire program global state; thus, this allows modular reasoning among different program components, with the goal of scaling formal verification to larger software systems. Infer represents one of the most successful implementations of that approach; it is an open-source static code analysis tool used for verifying the Facebook code base, was employed on many mobile apps ({\it e.g.}, WhatsApp), and was adopted by many companies ({\it e.g.}, Mozilla and Spotify).

	\textbf{SMV and NuSMV}. SMV and NuSMV are two representative symbolic verifiers based on binary decision diagrams (BDDs); actually, the latter is a re-implementation and extension of SMV, which also supports BMC using SAT solvers. In NuSMV, system properties can be expressed in a wide range of temporal properties, such as CTL, as done for system Sim3Tanks in Section 2, real-time CTL, LTL, and property specification language (PSL).

	\textbf{KLEE}. Path-based symbolic execution tools, as KLEE, employ several optimizations to prune the number of paths being explored, thereby caching previous queries and checking whether branch path constraints are satisfiable, before exploring them. One notable advantage of symbolic executors, over BMC tools, is that the former can be used for coverage test generation.
\end{resposta}

(6) Additional comments (mostly typos/rephrasing):
\begin{itemize}
	\item p.1 "mainly when his contact with patients..." $\rightarrow$ rephrase as it is not clear.
	\begin{resposta} 
	We have replaced ``mainly when his contact with patients...'' by ``mainly when their contact with patients...'', in which the personal (possessive) pronoun ``their'' refers to ``human specialists''.
        \end{resposta}
	\item p.2 "Correctness is asserted wrt [...] safety or reachability": what about liveness properties?
	\begin{resposta}
	We have rewritten the first paragraph of Section ``modeling Cyber-Physical Systems for Verification and Control Synthesis Purpose'' to state about safety and liveness properties as follows: Correctness is asserted with respect to a given specification, which may be related to safety or liveness. A safety specification is related to a set of undesirable (reachable) states that must be avoided or simply ensures that ``something bad never happens'', while a liveness one refers to a desired (reachable) state that must eventually be achieved or simply ensures that ``something good will eventually happen''. In both cases, a model is needed for an ECPS, in order to compute that no error state is reachable or that a desirable state is eventually reached.  Therefore, an algorithmic (decision) procedure ({\it cf.} Definition 2) can be devised from this model, in to decide about its correctness and reliability; this decision procedure output is simply ``yes'', if a specification holds, or, otherwise, ``no''.
	\end{resposta}
	\item p.3 Rephrase "to decide if a number of steps $\forall$..."
	\begin{resposta}
	We have rephrased this sentence as follows: ``Given a class of ECPSs $\Omega$ and a set $\Phi$ of desired properties, a class of verification problems $\gamma$ is called decidable if an algorithmic procedure can decide whether there exists a finite number of steps $\mathcal{O} \in \Omega$ that satisfies every property $\mathcal{L}\in \Phi$''.
	\end{resposta}
	\item p.4 I don't understand how (2) encodes a loop, shouldn't you have an additional predicate loop($s_k$,$s_l$) with $k \geq l$ ?
	\begin{resposta}
	The property $\phi$ is already encoded within a loop. When passing from $\psi_{k} = I\left(s_{0}\right) \wedge \bigwedge^{k-1}_{i=0} R\left(s_{i},s_{i+1}\right) \wedge \neg \phi_{k}$ to $\psi_{k} = I\left(s_{0}\right) \wedge \bigwedge^{k-1}_{i=0} R\left(s_{i},s_{i+1}\right) \wedge \left(\bigvee^{k}_{i=0} \neg \phi_{i}\right)$, both equations unroll the transition system $R$, but the latter means that property $\phi$ is checked at every loop iteration, {\it i.e.}, at every system unrolling up to the iteration bound (depth) $k$. As a consequence, there is no need for adding that predicate  loop($s_k$,$s_l$). We have completely revised Section 4.1 ``Bounded Model Checking (BMC)'', in order to make our BMC formulation clearer for readers.
	\end{resposta}
	\item p.5 "x tends to infinity after 128 executions" $\rightarrow$ please explain
	\begin{resposta}
	We have rewritten it as ``If we consider the IEEE floating-point standard (IEEE 754), then invariant $x>0$ initially holds; however, after $128$ loop iterations (lines 4-6 of Figure 4), $x$ tends to infinity, thereby leading to values outside the range of representable \texttt{float} numbers''.
	\end{resposta}
	\item p.6 "and If no such inductive..." $\rightarrow$ if lowercase
         \begin{resposta} 
	Implemented as suggested.
        \end{resposta}
	\item p.6 (same paragraph as above) "the instance  $x>1 (a=1, b=0)$..." $\rightarrow$ are a and b defined?
	\begin{resposta}
	There was a typo in this particular sentence. The variables ``a'' and ``b'' are not used in the example provided in Figure 6. We have fixed it in the revised version of our manuscript. 
	\end{resposta}
	\item p.6, second column: "there is no satisfying assignment to A /\ B*" $\rightarrow$ what is B*?
	\begin{resposta}
	We have fixed this typo. The footnote indicated by ``*'' should be after ``.'' and not after ``B''.
	\end{resposta}
	\item p.6 "another viable, elegant, and more viable..." $\rightarrow$ viable repeated
         \begin{resposta} 
	 We have replaced ``another viable, elegant, and more viable...'' by ``Another viable and more elegant strategy...''
        \end{resposta}
	\item p.7 "An possible approach" $\rightarrow$ A possible approach
	\begin{resposta} 
	Implemented as suggested.
        \end{resposta}
	\item p.8/9 section 5 contains mainly challenges for verification, synthesis is only mentioned in the last paragraph
	\begin{resposta} 
	We have added three additional challenges related to synthesis, as follows:

        \begin{enumerate}
	  \item  \textcolor{blue}{Parametrize search-space exploration;}
	  \item  \textcolor{blue}{Improve learning processes via counterexamples;}
	  \item  \textcolor{blue}{Use of incremental SAT/SMT solving process.}
       \end{enumerate}

        These additional synthesis challenges are described in further details, at the end of Section 6, as follows:

The first aspect is related to word lengths and representations of variables in an employed (embedded) hardware, where an ECPS is built upon. Here, floating-point representations can provide better approximation of real numbers, when compared with fixed-point ones with the same number of bits, which typically varies from $16$ to $64$ bits, in popular hardware architectures used for ECPSs. Multiple-precision floating-point arithmetic can further represent real numbers, whose precision digits are bounded by the available memory of a system, and practical software packages do exist to implement that type of arithmetic ({\it e.g.}, MPFR\footnote{https://www.mpfr.org/} and MPFI\footnote{https://directory.fsf.org/wiki/MPFI}). Nonetheless, using floating-point arithmetic in software synthesizers usually leads to higher verification time and memory consumption, as previously observed by Duggirala and Viswanathan [1]. In order to synthesize a given ECPS, typical synthesizers need to parameterize search-space exploration via multiple choices of word-length and variable representations, in order to produce a candidate solution that considers time and memory limits.

The second aspect deals with the way software synthesizers can learn from counterexamples produced during a verification phase, in order to quickly propose a candidate solution that meets a given specification. Here, critical aspects for any CEGIS approach, such as counterexample selection, are still poorly understood by the research community, thereby resulting in completely ad-hoc designs. Further investigation of those aspects would allow software synthesizers to come up with efficient synthesis approaches, for instance, through the use of an additional processing step before counterexample input, so that reliable implementations of communication and control software in ECPSs could be learned, in order to quickly achieve a correct-by-construction design. Machine learning techniques, such as reinforcement learning and decision tree learning, could be used, in order to achieve that goal and then speed up synthesis processes.

Lastly, the third aspect is related to the ability of SAT/SMT solvers to incrementally solve propositional or fragment of first-order logic formulae. In particular, incremental SAT solving allows software synthesizers to deal with sufficiently large logical formulae, incrementally, by learning from previous checks, {\it i.e.}, check VCs in iteration $k + 1$ based on the work done for iteration $k$, thus optimizing search procedures and potentially eliminating a large amount of formula state-space to be tackled. Some prior studies~[2,3] show that incremental learning can cut run-times by one order of magnitude, in comparison with standard non-incremental approaches over a large set of industrial embedded benchmarks (mainly from the automotive industry); however, we have not seen much effort, in the research community, regarding use of incremental SAT/SMT solving to efficiently synthesize control software for ECPS, through incremental learning (from previous checks).

[1] Duggirala, P.S., Viswanathan, M. Analyzing real time linear control systems using software verification. In: IEEE Real-Time Systems Symposium, 2015. pp. 216--226.

[2] Schrammel, P., Kroening, D., Brain, M., Martins, R., Teige, T., Bienmüller, T.: Incremental bounded model checking for embedded software, Formal Aspects of Computing, 2017, 29, (5), pp. 911--931

[3] E\'en, N., S\"orensson, N.: An extensible sat-solver. In: 6th International Conference on Theory and Applications of Satisfiability Testing. vol. 2919 of LNCS, 2003. pp. 502--518

        \end{resposta}

	\item p.9 Section 6, RP2, RP4 RP5 are not specific to ECPS (for instance section 6.2 on page 10 is not mentioning ECPS by generic Linux distributions).
	\begin{resposta} 
	We have rewritten RP2, in order to make its relation stronger to ECPSs, as follows: ``exploitation of SMT techniques to leverage (bounded) model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving, when verifying ECPS implementations that require multi-core processors with scalable shared memory''. We have also added additional statements to Section 7.2, in order to emphasize the importance of multi-threaded software verification, in the context of ECPS implementations.

	Regarding RP4, we have rewritten the first paragraph of Section 7.4, by describing three additional (real-world) examples of ECPS [1,2,3] that have been tackled in literature, with the goal of incorporating knowledge about system purpose and associated features into symbolic verification methods.

	Regarding RP5, we have also rewritten the first paragraph of Section 7.5, in order to emphasize the relation of this RP with ECPSs, as follows: ``Although existing symbolic verification tools were extended to support Java, C/C++, and some variants, new application interfaces and programming languages are often developed, which require suitable software verification tools for specific frameworks and embedded platforms, in order to building ECPSs. Indeed, it would be interesting if a new programming language model could be loaded, which, along with symbolic verification core algorithms, were able to check different programs and frameworks.''. We have also introduced new content to the second paragraph of Section 7.5, in order to illustrate some real cases being addressed by this RP, as follows: ``In this respect, Clang even provides a static analyzer (called CSA), which is an open-source project built on top of Clang that can perform context-sensitive inter-procedural analysis for programs written in the languages supported by Clang. It is designed to be fast, so that it can provide results for common mistakes ({\it e.g.}, division by zero or null pointer dereferencing), even in complex programs.''.

	[1] Peter Schrammel, Daniel Kroening, Martin Brain, Ruben Martins, Tino Teige, Tom Bienmüller: Incremental bounded model checking for embedded software. Formal Asp. Comput. 29(5): 911--931 (2017)

	[2] Lennon Chaves, Iury Bessa, Hussama Ismail, Adriano Bruno dos Santos Frutuoso, Lucas C. Cordeiro, Eddie Batista de Lima Filho: DSVerifier-Aided Verification Applied to Attitude Control Software in Unmanned Aerial Vehicles. IEEE Trans. Reliability 67(4): 1420--1441 (2018)

	[3] Jeremy Morse, Lucas C. Cordeiro, Denis A. Nicole, Bernd Fischer: Model checking LTL properties over ANSI-C programs with bounded traces. Software and System Modeling 14(1): 65-81 (2015)
	\end{resposta}
	\item Several references need to be fixed, e.g. [3] has an unbalanced open bracket near (, 2008, but many others have similar problems.
\end{itemize}

\begin{resposta} 
	We thank the comment provided by this reviewer. We have carefully revised our reference list and fixed the mentioned problem and many others.
\end{resposta}

\end{quote}

\newpage

\subsection*{Reviewer \#2 comments followed by the authors' answers:}

\begin{quote}
Embedded \& cyber-physical systems (ECPSs) develop rapidly and are applied in wider fields. With the increasing complexity of the systems and higher requirements of reliability on them, new challenges arose for verification and synthesis of ECPSs. This paper is a survey that reviews the related work and discusses recent advances on symbolic model checking techniques and their applications to control synthesis. Additionally, challenges, problems, and recent advances to ensure correctness and timeliness regarding ECPSs are discussed. Reliability issues, in the development of ECPSs, are then considered, as a prominent verification and synthesis application for achieving correct-by-construction systems.

In the first part of the article, the authors introduce the significance and challenges of ECPS, and then conclude the technologies of verification and synthesis in detail. In the latter part of the article, the authors introduce the verification and synthesis challenges for ECPSs and define seven major research problems in detail. Finally, the authors put forward the new application of software verification and synthesis, where not only code correctness will be addressed, but also full system reliability.

It can be seen that great efforts have been made in this paper. It summarizes the application and challenges of ECPSs and the development of verification and synthesis technologies comprehensively. The definition and technologies are presented friendly to understand. The research questions proposed by authors are reasonable. Interesting conclusions have been drawn on new applications of verification and synthesis for Asps. From the point of writing, the author arranges the content appropriately.

	\begin{resposta} 
		We thank the kind comment provided by this reviewer. Indeed, it summarizes what was intended to be done with this manuscript. In addition, we should highlight that, initially, our main focus was on symbolic verification techniques based on SAT and SMT solvers, which we believe is a promising approach for ECPS verification and synthesis, given they are constantly presenting size and complexity increase. In the revised version of our manuscript, we have also covered other verification techniques and tools, as suggested by the other reviewers. As examples, we have revised Section 4.5, named as ``Abstraction'', with the goal of covering abstract interpretation, which is a useful static analysis approach to formally verify large code bases. We have also introduced a completely new section 4.6, named as``Path-based symbolic execution'', in order to address another important verification techniques successfully employed for coverage test generation. Finally, we have also introduced, in Section 7.1, separation logic, which has been successfully employed to verify the Facebook's code base and many mobile apps ({\it e.g.}, WhatsApp), in addition to being adopted by many companies ({\it e.g.}, Mozilla and Spotify).		
		We hope that our revised version now fairly covers the most significant and recent related studies in the field of ECPS synthesis and verification.
	\end{resposta}

However, some minor issues still need to be improved:

	(7) The method of survey and the scope the bibliography should be explained.

	\begin{resposta} 
	We have written a new section called ``Limitations of this Survey'', in order to describe the method we have employed to search for publications via digital libraries, along with its limitations. 	
	\end{resposta}

	(8) I suggest that the limitation of this work should be discussed in Section 8.
	\begin{resposta} 
	The main limitations that we can identify for our work are related to the systematic review process. In particular, we have systematically carried out a literature review about symbolic verification and synthesis techniques for ECPSs, while also outlined our vision for future research; however, one of the major problems with systematic literature review is to find all relevant studies related to a given research area. In Section 9, we describe each limitation of our systematic review, related to the \textit{searching}, \textit{screening}, and \textit{synthesis} phases. Here, we have also described ways to alleviate those limitations and to remove any bias introduced into each stage of this systematic review process.
	\end{resposta}

	(9) There are a few typos and grammar errors in this paper.
	\begin{resposta} 
		We have carefully revised our manuscript; all typos and grammar errors, which we have identified during this first round of reviews, haven been fixed.
	\end{resposta}

\end{quote}

\newpage

\subsection*{Reviewer \#3 comments followed by the authors' answers:}

\begin{quote}
	(10) This is a survey paper that discusses symbolic verification approaches to verify and synthesize embedded and cyber-physical systems (ECPS). The paper is very well-written and it covers important papers and advancements in this field. ECPS is a very important area and by its own nature, it is extremely challenging to verify these systems - in particular to develop verification techniques that are both, precise and scalable. I liked the way, the relevant research work is organized and presented. Moreover, it also describes the challenges along with the current state of open problems. This should be helpful not only to researchers who are new to this field but also to more experienced researchers since the paper can form a concise source of information and the state-of-the-art for this vast and growing field.

	The only concern I have about the paper is regarding the reference formats. Not only that some details are missing from several references but also that formats are inconsistent which should be unacceptable particularly for a survey paper (and even otherwise). These issues should be fixed if the paper is accepted.

	\begin{resposta} 
		We thank the comment provided by this reviewer. We have carefully revised and standardize all the entries. 
	\end{resposta}

\end{quote}

\label{LastPage}

% \printbibliography

\end{document}

### 2019-07-11 Tex/elsevier/reply Solar Energy JULY 2019.tex
solar energy revised text

--- 2019-07-11 Tex/elsevier/REPLY_original.tex
@@
 \newtheorem{myassumption}{Assumption}
-\newcommand{\mstitle}{A Survey on Automated Symbolic Verification and its Application for Synthesizing Cyber-Physical Systems}
-\newcommand{\refnumber}{CPS-2018-5006}
+\newcommand{\mstitle}{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}
+\newcommand{\refnumber}{SE-D-19-01248}
 \newenvironment{resposta}{~~~\begin{quote}\color{blue}\textbf{Response:}}{\end{quote}}
@@
 {\mbox{\begin{minipage}{2cm}
-\centerline{\includegraphics[width=2.5cm]{manchester.png}}
+\centerline{\includegraphics[width=1.5cm]{ufam_logo.png}}
 \end{minipage}}} \hspace*{0.1cm}
-\begin{minipage}{11.0cm}{\large \textbf{UNIVERSITY OF MANCHESTER}}\\
-{\sc School of Computer Science}
+\begin{minipage}{11.0cm}{\large \textbf{Federal University of Amazonas}}\\
+{\sc Faculty of Technology}\\
+{\sc Department of Electricity}
 \end{minipage}
@@
 {\bf Please Reply to:}\\
-Dr. Lucas Cordeiro\\
-University of Manchester\\
-School of Computer Science\\
-Kilburn Building, Manchester, M13 9PL\\
-{\em lucas.cordeiro@manchester.ac.uk}
+Assistant Professor Alessandro Trindade\\
+Universidade Federal do Amazonas\\
+Departamento de Eletricidade\\
+Av. Gal. Rodrigo Otávio, 3000, Japiim, Campus Universitário\\
+ZIP 69077-000, Manaus - AM, Brazil\\
+{\em alessandrotrindade@ufam.edu.br}
 \end{minipage}
@@
 \vi
-\hspace*{\fill}{\small Manchester, \today.}
+\hspace*{\fill}{\small Manaus, \today.}
 \vi
@@
 \begin{flushleft}
-    Professor Dr. Shiyan Hu and Albert Zomaya\\
-    Editors-in-chief\\
-	IET Cyber-Physical Systems: Theory \& Applications
+    Mario A Medina, PhD, PE\\
+    Associate Editor\\
+	Solar Energy
     \end{flushleft}
@@
 
-\indent Dear Shiyan Hu and Albert Zomaya,
+\indent Dear Associate Editor,
 \vi
 
-We thank you for asking us to comply with your Referees' reports. 
-We are submitting a revised version of our manuscript entitled ``{\em \mstitle},'' by Lucas C.
-Cordeiro, Eddie B.
-de Lima Filho, and Iury V.
-Bessa.
+We thank you for asking us to comply with your Reviewers' reports. 
+We are submitting a revised version of our manuscript entitled ``{\em \mstitle},'' by Alessandro Trindade, and Lucas Cordeiro.
 This revised version carefully addresses each comment provided by the reviewers, as suggested in your original decision letter.
@@
 
-Lucas C. Cordeiro~~~~~~~
+Alessandro B. Trindade~~~~~~~
 \end{flushright}
@@
 
-According to the editors-in-chief and reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in blue color, along with the original text.
-Our responses  to all comments (also in blue color) are given in the sequel, with clear indications about how and where they were addressed along our manuscript.
+According to the associate editor and reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text.
+The revision included the Abstract, Introduction, and Results sections.
 
-We hope those modifications in our manuscript and also our responses are sufficient to make our work suitable for publication in {\bf IET Cyber-Physical Systems: Theory \& Applications}.
+Our responses  to all comments (in blue color) are given in the sequel, with clear indications about how and where they were addressed along our manuscript.
+
+We hope those modifications in our manuscript and also our responses are sufficient to make our work suitable for publication in {\bf Solar Energy}.
+
+\newpage
+\subsection*{Reviewer \#2 comments followed by the authors' answers:}
+
+\begin{quote}
+
+In the manuscript, the authors report about the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
+They show, case studies, from real photovoltaic systems deployed in five different places, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
+Also, the authors reported the evaluated different verification tools, in order to compare performance and soundness.
+Data from practical applications show the effectiveness of their approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
+
+I have specifics questions and suggestions in order to improvement the manuscript.
+
+1.-To clarify the figure 2, i recommend write "current" inside the figure, don't put just I.
+
+\begin{resposta}
+
+\end{resposta}
+
+2.-This software model checking has performance in comparison the other commercials software,how is this performance?, Could you give the areas where your software performs better than commercial software?
+
+\begin{resposta}
+
+\end{resposta}
+
+3.-In text reference at figure 1 the authors do not describe all symbols drawn into image, for instances, what is means G, T.
+I suspect that in section 4 they define which are the variables (Irradiation and temperature).
+I suggest you define those symbols in the text that that figure describes.
+
+\begin{resposta}
+
+\end{resposta}
+
+4.- Are the verification results carried out affected by the different characteristics of the computers?
+
+\begin{resposta}
+
+\end{resposta}
+
+\end{quote}
+\newpage
+
+\subsection*{Reviewer \#4 comments followed by the authors' answers:}
+
+\begin{quote}
+
+The topic itself is interest for the PV application. However some section including abstract and result must be rewritten to be enhanced, here are the comments:
+
+-       The manuscript illustrated the main drawback from other existed work that they are based on simulation and the proposed approach is claimed to do evaluation based real PV system as illustrated in the abstract, however the evolution is based on simulation model, mathematical, and information from website data such as Weather base and Energy Plus.
+The author should present real data measurement for more accurate results then compared and the main difference should be clarified.
+
+\begin{resposta}
+
+\end{resposta}
+
+-       Section 5 "Experimental Evolution" It can be changed to Verification result, otherwise the author should clarify the real measurements of the system.
+
+\begin{resposta}
+
+\end{resposta}
+
+-       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? waveforms such as: Input power, VMPP, IMPP, AC load
+
+\begin{resposta}
+
+\end{resposta}
+\end{quote}
 
@@
 
+------------------------------Lucas:
 \subsection*{Reviewer \#1 comments followed by the authors' answers:}

### 2019-07-11 Tex/elsevier/trindade_solar_energy_rev1.tex
solar energy revised text

--- 2019-05-08 Tex/elsevier/trindade_solar_energy_rev0.tex
@@
 \usepackage{lineno,hyperref}
-\modulolinenumbers[1]
-\linenumbers
+%\modulolinenumbers[1]
+%\linenumbers
 
@@
 %----------------------------------------------
-\section{Experimental Evaluation} 
+\section{\textcolor{red}{Verification and Simulation Results}} 
 \label{sec:results}
@@
 %------------------------------------------
-Our experimental evaluation aims to answer two research questions:
+Our \textcolor{red}{Verification and Simulation Results} aims to answer two research questions:
 %
@@
 
+\textcolor{red}{Note that the results presented here depend on the computer’s processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved.
+Additionally, any change from HOMER Pro to another tool can influence the measured time of the algorithms.}
+
 %------------------------------------------
@@
 
-The description of our experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
+The description of our results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
 

### 2019-07-11 Tex/elsevier/reply Solar Energy JULY 2019.tex
solar energy revised text

@@
 \begin{resposta} 
+We thank the kind comment provided by this reviewer.
+Indeed, it summarizes what was intended to be done with this manuscript.
+In addition, we should highlight that the main focus was at the validation process of the PV system, instead of the mathematical modelling that was investigated in prior studies over the last two decades.
+This information was carefully included at the revised Abstract, Introduction and at the Conclusion sections.
+
+Regarding the Figure 2, we did as highlighted by the reviewer. Moreover, we did the same to voltage V in order to keep the same standard.
 
@@
 \begin{resposta} 
-
+Indeed, we miss this information at paragraph that describes the Figure.
+We thank you so much for this observation.
+Therefore we revised the text and described every symbol.
+The final version of the paragraphs were: "A stand-alone PV system is illustrated in Fig.1.
+The PV generator is a semiconductor device that can convert solar energy into DC electricity, with high dependence of two weather variables from the site where the system is deployed: solar irradiance $G$ and temperature $T$.
+For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller.
+The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
+The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.".
 \end{resposta}
@@
 \begin{resposta} 
-
+Indeed, we did not inform the impact the changing of computer setup or related issues.
+We thank you so much for this observation.
+Therefore we revised the text and included the following paragraph: "Note that the results presented here depend on the computer's processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved.
+Additionally, any change from HOMER Pro to another simulation tool can influence the measured time to obtain results.".
 \end{resposta}

### 2019-07-11 Tex/elsevier/trindade_solar_energy_rev1.tex
solar energy revised text

@@
 Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-Automated verification using model checking has proven to be an effective technique to validate any kind of system.
+Automated verification using model checking has proven to be an effective technique to validate \textcolor{red}{complex systems}.
 This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Different verification tools were evaluated as well, in order to compare performance and soundness.
-Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
+\textcolor{red}{Therefore the focus is in the solar photovoltaic project validation, as intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior.
+Case studies, ranging from 700 W to 1,200 W}, were used to evaluate this proposed approach and to compare that with specialized simulation tool.
+Different verification tools were evaluated as well, in order to compare performance and soundness among automated tools.
+\textcolor{red}{The results reported by the automated verification and by the simulation tools were compared with data collected from dwellers of the deployed cases, showing the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.}
 \end{abstract}
@@
 %, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.
+
+\textcolor{red}{Note that in this study, our focus is not on a novel mathematical modelling of PV systems.
+Instead, our novelty relies on an effective approach to perform validation of PV systems using formal methods, in a process that is intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior.}
 
@@
 A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-The PV generator is a semiconductor device that can convert solar energy into DC electricity.
-%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
+The PV generator is a semiconductor device that can convert solar energy into DC electricity\textcolor{red}{, with high dependence of two weather variables from the site where the system is deployed: solar irradiance $G$ and temperature $T$}.
 For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\citep{Hansen}.
@@
 The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+\textcolor{red}{At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.}
 %
@@
 
-\textcolor{red}{Note that the results presented here depend on the computer’s processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved.
-Additionally, any change from HOMER Pro to another tool can influence the measured time of the algorithms.}
+\textcolor{red}{Note that the results presented here depend on the computer's processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved.
+Additionally, any change from HOMER Pro to another simulation tool can influence the measured time to obtain results.}
 
@@
 We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. 
-We have considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
+\textcolor{red}{The focus was on the method to validate PV systems projects, based on formal methods that can cover the design-space better than simulation tools. 
+We have considered five case studies, ranging from $700$ W to $1,200$ W; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro).
+The results from automated verification and simulation tools were confronted with information collected from dwelles of the sites where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
 In particular, the proposed method was successful in finding sizing errors and indicating in details.

### 2019-07-11 Tex/elsevier/reply Solar Energy JULY 2019.tex
solar energy revised text

@@
 Indeed, it summarizes what was intended to be done with this manuscript.
-In addition, we should highlight that the main focus was at the validation process of the PV system, instead of the mathematical modelling that was investigated in prior studies over the last two decades.
-This information was carefully included at the revised Abstract, Introduction and at the Conclusion sections.
+In addition, we should highlight that the main focus was at the validation process of the solar PV system, instead of the mathematical modelling that was investigated in prior studies over the last two decades.
+This information was carefully included at the revised Abstract, Introduction and at the Conclusion sections, because we concluded that was not clear in the previous version of the paper.
 
@@
 \begin{resposta} 
+Here it is worth to mention that our options about specialized off-the-shelf tools were reduced.
+As informed at Section 2.1 of the paper, only Hybrid2 and HOMER Pro perform off-grid with battery analysis of PV systems.
+Hybrid2 is not supported anymore, being in disuse.
+This information was updated to the paper.
+Therefore, at this particular kind of system (stand-alone solar PV systems), only HOMER Pro could be used for comparative.
+Nevertheless, some general use simulation could be used, with the same mathematical model adopted by the automated verification tool.
+Because of that, we included a mention to that issue in the section 5.4 (Threats to Validity).
+
+Model checking and software simulation are two different techniques that uses mathematical models.
+However how they work is completely different.
+Simulation depends on the choice of input variables (and their values) in order to obtain the output.
+In the other hand, model checking performs an automatic output search that causes the system to fails (a not expected behavior of the system) and presents the input that causes it.
+Therefore with model checking we can prove the absence of system flaws.
+This information was included at the revised text as well.
+
+Model checking explores more efficiently the design-space because the specification of the system is based on formal notation (that is converted to Boolean algebra) and the evaluation of variables is made automatically based on constraints (basically system information and electrical load demand transformed in software code) and properties (use defined demands, weather variables that the use do not have precise forecasting).
+This resulting mathematical model pass through a exploration of its possible states in order to find a configuration where occurs or not a fail.
+Logically, depending on the number of variables, the number of states explode and is time-consuming during computing of the result.
+
+However, the authors showed in 2016\footnote{Trindade, A.B.
+and Cordeiro, Applying SMT-based verification to hardware/software partitioning in embedded systems.
+Des Autom Embed Syst (2016) 20: 1.
+https://doi.org/10.1007/s10617-015-9163-z} that model checking can present better performance than simulation software when performing hardware-software partitioning in specifically amount of instances.
 
@@
 \begin{resposta} 
+We appreciate the comments and we realized that our text was not clear.
+As told for the Reviewer \#2, we should highlight that our main focus was at the validation process of the solar PV system, instead of the mathematical modelling that was investigated in prior studies over the last two decades.
+Moreover, we compare the results of using automated verification with simulation tool; real PV systems were just to check the validation results presented by the two tools.
+Because the automated verification and simulation tools are intended to be used during the project, before the buying or deployment of equipment.
+This information was carefully included at the revised Abstract, Introduction and at the Conclusion sections, because we concluded that was not clear in the previous version of the paper.
 
+The authors have real load curve, and information collected from monitoring system of four (in five) PV systems/cases, however based on the fact that the automated verification is mathematical and not visual (curves/plots), seems that is not a adequate way of comparative.
+
+The information from temperature and solar irradiance from every site, used to the simulation and formal verification tools, come from historical data collected from real stations that are available in Weather Base and Energy Plus web sites.
+Considering that the idea of the work is to show the effectiveness of the proposal just after the design phase, before deployment, seems that is plausible that procedure.
+Worth to mention that the sites from four case studies (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closet site with historic data).
 \end{resposta}
@@
 \begin{resposta} 
-
+We thank the reviewer for this comment.
+We did as suggested and changed the section title to "Verification and Simulation Results", because the results were related to verification and simulation tools only.
+The data collected from dwellers with real PV systems were used just to confirm flaws and complains about the equipment deployed at the field.
+The idea was not to present wave forms because how automated verification works it is different of simulation or testing.
 \end{resposta}
@@
 \begin{resposta} 
+As explained at the first question, here the authors failed in explain better the study. We appreciate one more time the comment and the opportunity to correct this issue.
 
+At the paper, we compare model checking with simulation tool.
+However how they work is completely different.
+Simulation depends on the choice of input variables (and their values) in order to obtain the output.
+In the other hand, model checking performs an automatic output search that causes the system to fails (a not expected behavior of the system) and presents the input that causes it.
+Therefore with model checking we can prove the absence of system flaws.
+
+When we work with waveform we are performing testing of simulation, and that is different of automated verification that is a mathematical prove (of correctness or flaw).
+Based on the fact that the authors have the five cases deployed at the field, and with monitoring system in four those PV systems, it is possible to add waveforms to the work.
+However, the use of this resource seems that is not a adequate way of comparative.
+However, we included details about the estimated load curve of each case study at the revised paper (section 4) that is represented by a vector with 24 elements (one to each hour of the day).
 \end{resposta}
-\end{quote}
-
-\newpage
-
-------------------------------Lucas:
-\subsection*{Reviewer \#1 comments followed by the authors' answers:}
-
-\begin{quote}
-The paper is a survey on verification and synthesis of embedded and cyber-physical systems.
-More in detail, the authors consider symbolic model checking (mostly bounded-model checking) and synthesis, and other techniques are also mentioned.
-
-Unfortunately, I don't think that the current version meets the standards for publication.
-
-\begin{resposta} 
-We thank this reviewer for the valuable and honest comments about our manuscript.
-In this revised version, we have carefully addressed each of the reviewers' comments, with the goal of making our manuscript suitable for publication in {\bf IET Cyber-Physical Systems: Theory \& Applications}.
-In this respect, we have significantly extended our manuscript, in order to describe various model checkers that are not only state-of-the-art, but also contributed to the development of the embedded \& cyber-physical systems (ECPS) field ({\it cf.} Sections 3, 4.5, 7.1 and 7.2).
-Give that this is a broad research area, we might have forgotten to cite some other relevant work; however, given the current knowledge in system verification, we believe we have covered the most relevant and significant related studies.
-We have also covered a variety of studies strictly related to verification and synthesis of CPS and hybrid systems ({\it cf.} Section 3) and introduced an illustrative example of a real-world three-tanks system modeled by hybrid-automata ({\it cf.} Section 2, by using computation three logic and linear-time temporal logic), while pointed out the main current challenges to formally verify and synthesize control software for ECPSs ({\it cf.} Sections 6 and 7).
-In Section 9, we highlighted the main limitations of our survey, in terms of systematic literature review.
-\end{resposta}
-
-The two main weaknesses are:
-
-(1) The paper is not specific: a number of sections in the paper and a number of references are not related to ECPS, but only to software verification or to verification in general.
-For instance, the authors mention Hybrid Systems (HS) and techniques for HS in section 2, but HS are not mentioned after this point.
-
-\begin{resposta}
-Indeed, our goal was to tackle literature related to symbolic model checking and program synthesis, while pointing out promising approaches related to ECPSs.
-As a consequence, we first addressed classical and state-of-the-art techniques, in order to give a broad view, and then restricted to studies specifically related to ECPSs or with potential to be applied to them.
-Nonetheless, such a strategy may have given the impression that our manuscript's central subject was not ECPS, which we tried to mitigate with the current revised version and its new text, such as current Section 3, as it stands now, and the hybrid-system (HS) example in Section 2.
-Generally, ECPSs are systems that present both continuous and discrete dynamics, as HSs, and, due to this reason, the main approach to formally verify and synthesize controllers for ECPSs is modeling them through HSs.
-Section 2 is dedicated to establish a suitable modeling approach for application of formal verification and synthesis techniques: the chosen adequate models are hybrid automata (HA).
-Thus, it was important to discuss the literature related to representation of hybrid system in this section, in order to achieve the concept notion of hybrid automata and their use for ECPS modeling.
-In the remaining sections, there is no need for particularly tackling HSs, given that the manuscript is focused on discussing verification and synthesis methodologies for ECPSs, which are usually represented by HA.
-The goal of the discussion regarding HSs was clarified along the revised Section 2.
-Furthermore, an example of HA for an ECPS, known as Sim3Tanks, was presented for discussion along the remaining manuscript, in order to illustrate the application of symbolic verification and synthesis.
-\end{resposta}
-
-(2) The paper is not structured: for instance, section 3 is a generic introduction to software verification, and a discussion about specific techniques for ECPS verification is only present in section 6.
-In general, It is not clear how the authors chose their references.
-\begin{resposta} 
-Indeed, our intention was to provide a broad review regarding symbolic verification and its application to synthesis, while highlighting specific techniques applied to ECPSs, which may have led to this comment.
-One may notice that we did not mean to focus on a specific set of references, but instead unveil ECPS development and then propose and devise future paths for system design and verification, which are safe and secure by construction ({\it cf.} Section 7).
-In order to provide more structure and focus on ECPS verification, we have added the second before last paragraph of the introduction and also modified the last one of it, a new Section 3 was added, in order to provide focus on cyber-physical systems, and, finally, the former Section 3 was modified and now constitutes Section 4, which now acts as a discussion text towards the authors' vision for ECPS verification.
-Additionally, we have substantially expanded the description of symbolic verification tools throughout our manuscript, in order to emphasize their strengthens and weaknesses, when verifying ECPSs, and also their potential to fulfill current technical gaps.
-Section 6, which is now section 7 and already contained discussion regarding ECPS verification, as mentioned by the reviewer, was also further extended, with more technical information.
-\end{resposta}
-
-(3) More in detail, for 1): section 3 should have a different title, as it is not specific to ECPS.
-This section should probably be replaced by a section containing specific approaches for ECPS verification.
-Section 4 should contain more technical details about the approaches presented.
-Section 5 and section 6 are phrased like a research agenda for ECPS, rather than as a survey (even if some paragraphs under future trends are effectively surveying state of the art).
-\begin{resposta} 
-	As mentioned in previous responses, we added a new section 3, which now presents material strictly related to ECPS verification, while also tackling aggregate effects, which deserve special attention.
-That was done as a response to the reviewer's comment, in order to be compliant with its first part.
-In addition, former section 3 is now section 4, presents a new title, and also includes more material, while bearing the authors' vision regarding future trends in ECPs verification.
-Former Section 4 is now section 5 and contains more technical material regarding DSVerifier, DSSynth, and Scratch, which indeed improved its efficacy in conveying the proposed material.
-Former Sections 5 and 6, which are now 6 and 7, respectively, intended to both highlight current challenges, while proposing feasible solutions, and present research towards them, which belong to the state of the art group.
-Anyway, they are important, since they reveal trends and propose approaches based on real research.
-In order to expand Section 6, complete its content, and avoid impression of a mere research agenda, while preserving its structure (both trends and state of the art), we have added material related to initial and promising research regarding both ECPS verification and synthesis, which provides more survey structure and is now mixed with insightful research directions.
-Section 7, in turn, aims to present research problems, where we have also improved literature review, in order to show their relevance.
-\end{resposta}
-
-(4) For 2): the authors should specify how they have selected their references.
-This could be done by adopting a systematic approach, or by defining a taxonomy, or by some other structured approach (e.g., using a running ECPS example).
-\begin{resposta} 
-	As our article's title suggests, we intended to provide a survey on symbolic verification and its application to ECPS.
-As a consequence, we addressed a large part of the current existing literature on that matter.
-Even so, we tried to narrow to ECPS verification, aggregate effects, ECPS synthesis, and open research problems on those areas, while focusing on symbolic model checking; in particular, bounded model checking, \textit{k}-induction, interpolants, symbolic execution, and abstraction.
-Anyway, we have adopted automated search through popular digital libraries, whose relevant results were filtered according to peer-reviewed conferences and journals in that target area.
-In addition, we included a few studies outside this group, whose content was highly correlated with our results.
-Our methodology for reference selection has also employed a broader scheme, which included the strategy mentioned above, as a constructive block, and is described as follows.
-Firstly, we began with HSs, explained their link with ECPSs, and them expanded by tackling ECPS verification with aggregate effects.
-Then, we took the cue created by existing approaches, in order to provide a link with symbolic model checking.
-Later, we moved to ECPS synthesis and merged both regarding challenges and trends.
-A more detailed description of our literature review can be found in the recently added Section 9.
-\end{resposta}
-
-(5) Currently, the paper mentions some techniques, but ignore other approaches.
-As a concrete example: the authors focus mainly on bounded model checking techniques and tools, but only one tool is described in some detail (ESBMC) in section 6, while others are only mentioned (e.g., CBMC) and this choice is not motivated.
-Similarly, other software verification techniques (e.g., those based on separation logic) are not considered nor compared for the verification of C code.
-\begin{resposta} 
-	As previously explained, bounded model checking (BMC) and its companion techniques ({\it e.g.}, $k$-induction) are envisioned as a promising approach towards ECPS synthesis and verification, as long as merged with system and behavior models, which may have led to this condition.
-In order to mitigate that, we have focused on symbolic verification methods, and in particular BMC, in some specific parts of the text, and then further described eight additional software verifiers: CPAchecker (Section 6.1), Lazy-CSeq (Section 6.2), Astree (Sections 3.7 and 6.4), Polyspace (Sections 3.7 and 6.4), Frama-C (Sections 3.7 and 6.4), Infer (Section 6.1), SMV (Section 3), NuSMV (Section 3), KLEE (section 4.6).
-Each verifier is described as follows:
-
-	\textbf{CPAchecker}.
-Beyer, Dangl, and Wendler described a software verification-framework called CPAchecker, which automatically generates invariants through a combination of data-flow-based invariant generator and dynamic precision adjustment, with the goal of injecting (inductive) invariants into the \textit{k}-induction algorithm.
-Even though the combination between \textit{k}-induction and continuously-refined invariants significantly enhances verification results, there is still room for improvements, particularly for learning from counterexamples, in order to improve bug finding capabilities.
-
-	\textbf{Lazy-Cseq}.
-Lazy-CSeq is a code-to-code transformation tool based on Lazy Sequentialization techniques, initially introduced by La Torre {\it et al.} for non-deterministically sequentializing concurrent C programs, which re-uses existing BMC tools as backends, in order to find code violations.
-Its main idea is to pre-process a concurrent program and convert it into a non-deterministic sequential one, with the goal of simplifying verification tasks.
-
-	\textbf{Astree, Polyspace, and Frama-C}.
-Astr\'ee, PolySpace, and Frama-C are the most successful implementations of the abstract interpretation technique; in particular, Astr\'ee and PolySpace have been successfully used to prove absence of run-time errors, in real-world flight control software.
-Although those software verifiers scale relatively well for large code bases, their main drawback is that they usually provide false alarms, due to over-approximation of possible program executions.
-
-	\textbf{Separation logic and Infer}.
-Another interesting direction for future research consists in investigating the application of separation logic, in order to reason about ECPS.
-The key idea of separation logic is to perform a local reasoning based on specifications and proofs of a given program component, by considering only the portion of memory used by that same component, and not the entire program global state; thus, this allows modular reasoning among different program components, with the goal of scaling formal verification to larger software systems.
-Infer represents one of the most successful implementations of that approach; it is an open-source static code analysis tool used for verifying the Facebook code base, was employed on many mobile apps ({\it e.g.}, WhatsApp), and was adopted by many companies ({\it e.g.}, Mozilla and Spotify).
-
-	\textbf{SMV and NuSMV}.
-SMV and NuSMV are two representative symbolic verifiers based on binary decision diagrams (BDDs); actually, the latter is a re-implementation and extension of SMV, which also supports BMC using SAT solvers.
-In NuSMV, system properties can be expressed in a wide range of temporal properties, such as CTL, as done for system Sim3Tanks in Section 2, real-time CTL, LTL, and property specification language (PSL).
-
-	\textbf{KLEE}.
-Path-based symbolic execution tools, as KLEE, employ several optimizations to prune the number of paths being explored, thereby caching previous queries and checking whether branch path constraints are satisfiable, before exploring them.
-One notable advantage of symbolic executors, over BMC tools, is that the former can be used for coverage test generation.
-\end{resposta}
-
-(6) Additional comments (mostly typos/rephrasing):
-\begin{itemize}
-	\item p.1 "mainly when his contact with patients..." $\rightarrow$ rephrase as it is not clear.
-	\begin{resposta} 
-	We have replaced ``mainly when his contact with patients...'' by ``mainly when their contact with patients...'', in which the personal (possessive) pronoun ``their'' refers to ``human specialists''.
-        \end{resposta}
-	\item p.2 "Correctness is asserted wrt [...] safety or reachability": what about liveness properties?
-	\begin{resposta}
-	We have rewritten the first paragraph of Section ``modeling Cyber-Physical Systems for Verification and Control Synthesis Purpose'' to state about safety and liveness properties as follows: Correctness is asserted with respect to a given specification, which may be related to safety or liveness.
-A safety specification is related to a set of undesirable (reachable) states that must be avoided or simply ensures that ``something bad never happens'', while a liveness one refers to a desired (reachable) state that must eventually be achieved or simply ensures that ``something good will eventually happen''.
-In both cases, a model is needed for an ECPS, in order to compute that no error state is reachable or that a desirable state is eventually reached.
-Therefore, an algorithmic (decision) procedure ({\it cf.} Definition 2) can be devised from this model, in to decide about its correctness and reliability; this decision procedure output is simply ``yes'', if a specification holds, or, otherwise, ``no''.
-	\end{resposta}
-	\item p.3 Rephrase "to decide if a number of steps $\forall$..."
-	\begin{resposta}
-	We have rephrased this sentence as follows: ``Given a class of ECPSs $\Omega$ and a set $\Phi$ of desired properties, a class of verification problems $\gamma$ is called decidable if an algorithmic procedure can decide whether there exists a finite number of steps $\mathcal{O} \in \Omega$ that satisfies every property $\mathcal{L}\in \Phi$''.
-	\end{resposta}
-	\item p.4 I don't understand how (2) encodes a loop, shouldn't you have an additional predicate loop($s_k$,$s_l$) with $k \geq l$ ?
-	\begin{resposta}
-	The property $\phi$ is already encoded within a loop.
-When passing from $\psi_{k} = I\left(s_{0}\right) \wedge \bigwedge^{k-1}_{i=0} R\left(s_{i},s_{i+1}\right) \wedge \neg \phi_{k}$ to $\psi_{k} = I\left(s_{0}\right) \wedge \bigwedge^{k-1}_{i=0} R\left(s_{i},s_{i+1}\right) \wedge \left(\bigvee^{k}_{i=0} \neg \phi_{i}\right)$, both equations unroll the transition system $R$, but the latter means that property $\phi$ is checked at every loop iteration, {\it i.e.}, at every system unrolling up to the iteration bound (depth) $k$.
-As a consequence, there is no need for adding that predicate  loop($s_k$,$s_l$).
-We have completely revised Section 4.1 ``Bounded Model Checking (BMC)'', in order to make our BMC formulation clearer for readers.
-	\end{resposta}
-	\item p.5 "x tends to infinity after 128 executions" $\rightarrow$ please explain
-	\begin{resposta}
-	We have rewritten it as ``If we consider the IEEE floating-point standard (IEEE 754), then invariant $x>0$ initially holds; however, after $128$ loop iterations (lines 4-6 of Figure 4), $x$ tends to infinity, thereby leading to values outside the range of representable \texttt{float} numbers''.
-	\end{resposta}
-	\item p.6 "and If no such inductive..." $\rightarrow$ if lowercase
-         \begin{resposta} 
-	Implemented as suggested.
-        \end{resposta}
-	\item p.6 (same paragraph as above) "the instance  $x>1 (a=1, b=0)$..." $\rightarrow$ are a and b defined?
-	\begin{resposta}
-	There was a typo in this particular sentence. The variables ``a'' and ``b'' are not used in the example provided in Figure 6. We have fixed it in the revised version of our manuscript. 
-	\end{resposta}
-	\item p.6, second column: "there is no satisfying assignment to A /\ B*" $\rightarrow$ what is B*?
-	\begin{resposta}
-	We have fixed this typo. The footnote indicated by ``*'' should be after ``.'' and not after ``B''.
-	\end{resposta}
-	\item p.6 "another viable, elegant, and more viable..." $\rightarrow$ viable repeated
-         \begin{resposta} 
-	 We have replaced ``another viable, elegant, and more viable...'' by ``Another viable and more elegant strategy...''
-        \end{resposta}
-	\item p.7 "An possible approach" $\rightarrow$ A possible approach
-	\begin{resposta} 
-	Implemented as suggested.
-        \end{resposta}
-	\item p.8/9 section 5 contains mainly challenges for verification, synthesis is only mentioned in the last paragraph
-	\begin{resposta} 
-	We have added three additional challenges related to synthesis, as follows:
-
-        \begin{enumerate}
-	  \item  \textcolor{blue}{Parametrize search-space exploration;}
-	  \item  \textcolor{blue}{Improve learning processes via counterexamples;}
-	  \item  \textcolor{blue}{Use of incremental SAT/SMT solving process.}
-       \end{enumerate}
-
-        These additional synthesis challenges are described in further details, at the end of Section 6, as follows:
-
-The first aspect is related to word lengths and representations of variables in an employed (embedded) hardware, where an ECPS is built upon.
-Here, floating-point representations can provide better approximation of real numbers, when compared with fixed-point ones with the same number of bits, which typically varies from $16$ to $64$ bits, in popular hardware architectures used for ECPSs.
-Multiple-precision floating-point arithmetic can further represent real numbers, whose precision digits are bounded by the available memory of a system, and practical software packages do exist to implement that type of arithmetic ({\it e.g.}, MPFR\footnote{https://www.mpfr.org/} and MPFI\footnote{https://directory.fsf.org/wiki/MPFI}).
-Nonetheless, using floating-point arithmetic in software synthesizers usually leads to higher verification time and memory consumption, as previously observed by Duggirala and Viswanathan [1].
-In order to synthesize a given ECPS, typical synthesizers need to parameterize search-space exploration via multiple choices of word-length and variable representations, in order to produce a candidate solution that considers time and memory limits.
-
-The second aspect deals with the way software synthesizers can learn from counterexamples produced during a verification phase, in order to quickly propose a candidate solution that meets a given specification.
-Here, critical aspects for any CEGIS approach, such as counterexample selection, are still poorly understood by the research community, thereby resulting in completely ad-hoc designs.
-Further investigation of those aspects would allow software synthesizers to come up with efficient synthesis approaches, for instance, through the use of an additional processing step before counterexample input, so that reliable implementations of communication and control software in ECPSs could be learned, in order to quickly achieve a correct-by-construction design.
-Machine learning techniques, such as reinforcement learning and decision tree learning, could be used, in order to achieve that goal and then speed up synthesis processes.
-
-Lastly, the third aspect is related to the ability of SAT/SMT solvers to incrementally solve propositional or fragment of first-order logic formulae.
-In particular, incremental SAT solving allows software synthesizers to deal with sufficiently large logical formulae, incrementally, by learning from previous checks, {\it i.e.}, check VCs in iteration $k + 1$ based on the work done for iteration $k$, thus optimizing search procedures and potentially eliminating a large amount of formula state-space to be tackled.
-Some prior studies~[2,3] show that incremental learning can cut run-times by one order of magnitude, in comparison with standard non-incremental approaches over a large set of industrial embedded benchmarks (mainly from the automotive industry); however, we have not seen much effort, in the research community, regarding use of incremental SAT/SMT solving to efficiently synthesize control software for ECPS, through incremental learning (from previous checks).
-
-[1] Duggirala, P.S., Viswanathan, M. Analyzing real time linear control systems using software verification. In: IEEE Real-Time Systems Symposium, 2015. pp. 216--226.
-
-[2] Schrammel, P., Kroening, D., Brain, M., Martins, R., Teige, T., Bienmüller, T.: Incremental bounded model checking for embedded software, Formal Aspects of Computing, 2017, 29, (5), pp. 911--931
-
-[3] E\'en, N., S\"orensson, N.: An extensible sat-solver. In: 6th International Conference on Theory and Applications of Satisfiability Testing. vol. 2919 of LNCS, 2003. pp. 502--518
-
-        \end{resposta}
-
-	\item p.9 Section 6, RP2, RP4 RP5 are not specific to ECPS (for instance section 6.2 on page 10 is not mentioning ECPS by generic Linux distributions).
-	\begin{resposta} 
-	We have rewritten RP2, in order to make its relation stronger to ECPSs, as follows: ``exploitation of SMT techniques to leverage (bounded) model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving, when verifying ECPS implementations that require multi-core processors with scalable shared memory''.
-We have also added additional statements to Section 7.2, in order to emphasize the importance of multi-threaded software verification, in the context of ECPS implementations.
-
-	Regarding RP4, we have rewritten the first paragraph of Section 7.4, by describing three additional (real-world) examples of ECPS [1,2,3] that have been tackled in literature, with the goal of incorporating knowledge about system purpose and associated features into symbolic verification methods.
-
-	Regarding RP5, we have also rewritten the first paragraph of Section 7.5, in order to emphasize the relation of this RP with ECPSs, as follows: ``Although existing symbolic verification tools were extended to support Java, C/C++, and some variants, new application interfaces and programming languages are often developed, which require suitable software verification tools for specific frameworks and embedded platforms, in order to building ECPSs.
-Indeed, it would be interesting if a new programming language model could be loaded, which, along with symbolic verification core algorithms, were able to check different programs and frameworks.''.
-We have also introduced new content to the second paragraph of Section 7.5, in order to illustrate some real cases being addressed by this RP, as follows: ``In this respect, Clang even provides a static analyzer (called CSA), which is an open-source project built on top of Clang that can perform context-sensitive inter-procedural analysis for programs written in the languages supported by Clang.
-It is designed to be fast, so that it can provide results for common mistakes ({\it e.g.}, division by zero or null pointer dereferencing), even in complex programs.''.
-
-	[1] Peter Schrammel, Daniel Kroening, Martin Brain, Ruben Martins, Tino Teige, Tom Bienmüller: Incremental bounded model checking for embedded software. Formal Asp. Comput. 29(5): 911--931 (2017)
-
-	[2] Lennon Chaves, Iury Bessa, Hussama Ismail, Adriano Bruno dos Santos Frutuoso, Lucas C.
-Cordeiro, Eddie Batista de Lima Filho: DSVerifier-Aided Verification Applied to Attitude Control Software in Unmanned Aerial Vehicles.
-IEEE Trans.
-Reliability 67(4): 1420--1441 (2018)
-
-	[3] Jeremy Morse, Lucas C. Cordeiro, Denis A. Nicole, Bernd Fischer: Model checking LTL properties over ANSI-C programs with bounded traces. Software and System Modeling 14(1): 65-81 (2015)
-	\end{resposta}
-	\item Several references need to be fixed, e.g. [3] has an unbalanced open bracket near (, 2008, but many others have similar problems.
-\end{itemize}
-
-\begin{resposta} 
-	We thank the comment provided by this reviewer. We have carefully revised our reference list and fixed the mentioned problem and many others.
-\end{resposta}
-
-\end{quote}
-
-\newpage
-
-\subsection*{Reviewer \#2 comments followed by the authors' answers:}
-
-\begin{quote}
-Embedded \& cyber-physical systems (ECPSs) develop rapidly and are applied in wider fields.
-With the increasing complexity of the systems and higher requirements of reliability on them, new challenges arose for verification and synthesis of ECPSs.
-This paper is a survey that reviews the related work and discusses recent advances on symbolic model checking techniques and their applications to control synthesis.
-Additionally, challenges, problems, and recent advances to ensure correctness and timeliness regarding ECPSs are discussed.
-Reliability issues, in the development of ECPSs, are then considered, as a prominent verification and synthesis application for achieving correct-by-construction systems.
-
-In the first part of the article, the authors introduce the significance and challenges of ECPS, and then conclude the technologies of verification and synthesis in detail.
-In the latter part of the article, the authors introduce the verification and synthesis challenges for ECPSs and define seven major research problems in detail.
-Finally, the authors put forward the new application of software verification and synthesis, where not only code correctness will be addressed, but also full system reliability.
-
-It can be seen that great efforts have been made in this paper.
-It summarizes the application and challenges of ECPSs and the development of verification and synthesis technologies comprehensively.
-The definition and technologies are presented friendly to understand.
-The research questions proposed by authors are reasonable.
-Interesting conclusions have been drawn on new applications of verification and synthesis for Asps.
-From the point of writing, the author arranges the content appropriately.
-
-	\begin{resposta} 
-		We thank the kind comment provided by this reviewer.
-Indeed, it summarizes what was intended to be done with this manuscript.
-In addition, we should highlight that, initially, our main focus was on symbolic verification techniques based on SAT and SMT solvers, which we believe is a promising approach for ECPS verification and synthesis, given they are constantly presenting size and complexity increase.
-In the revised version of our manuscript, we have also covered other verification techniques and tools, as suggested by the other reviewers.
-As examples, we have revised Section 4.5, named as ``Abstraction'', with the goal of covering abstract interpretation, which is a useful static analysis approach to formally verify large code bases.
-We have also introduced a completely new section 4.6, named as``Path-based symbolic execution'', in order to address another important verification techniques successfully employed for coverage test generation.
-Finally, we have also introduced, in Section 7.1, separation logic, which has been successfully employed to verify the Facebook's code base and many mobile apps ({\it e.g.}, WhatsApp), in addition to being adopted by many companies ({\it e.g.}, Mozilla and Spotify).
-		We hope that our revised version now fairly covers the most significant and recent related studies in the field of ECPS synthesis and verification.
-	\end{resposta}
-
-However, some minor issues still need to be improved:
-
-	(7) The method of survey and the scope the bibliography should be explained.
-
-	\begin{resposta} 
-	We have written a new section called ``Limitations of this Survey'', in order to describe the method we have employed to search for publications via digital libraries, along with its limitations. 	
-	\end{resposta}
-
-	(8) I suggest that the limitation of this work should be discussed in Section 8.
-	\begin{resposta} 
-	The main limitations that we can identify for our work are related to the systematic review process.
-In particular, we have systematically carried out a literature review about symbolic verification and synthesis techniques for ECPSs, while also outlined our vision for future research; however, one of the major problems with systematic literature review is to find all relevant studies related to a given research area.
-In Section 9, we describe each limitation of our systematic review, related to the \textit{searching}, \textit{screening}, and \textit{synthesis} phases.
-Here, we have also described ways to alleviate those limitations and to remove any bias introduced into each stage of this systematic review process.
-	\end{resposta}
-
-	(9) There are a few typos and grammar errors in this paper.
-	\begin{resposta} 
-		We have carefully revised our manuscript; all typos and grammar errors, which we have identified during this first round of reviews, haven been fixed.
-	\end{resposta}
-
-\end{quote}
-
-\newpage
-
-\subsection*{Reviewer \#3 comments followed by the authors' answers:}
-
-\begin{quote}
-	(10) This is a survey paper that discusses symbolic verification approaches to verify and synthesize embedded and cyber-physical systems (ECPS).
-The paper is very well-written and it covers important papers and advancements in this field.
-ECPS is a very important area and by its own nature, it is extremely challenging to verify these systems - in particular to develop verification techniques that are both, precise and scalable.
-I liked the way, the relevant research work is organized and presented.
-Moreover, it also describes the challenges along with the current state of open problems.
-This should be helpful not only to researchers who are new to this field but also to more experienced researchers since the paper can form a concise source of information and the state-of-the-art for this vast and growing field.
-
-	The only concern I have about the paper is regarding the reference formats.
-Not only that some details are missing from several references but also that formats are inconsistent which should be unacceptable particularly for a survey paper (and even otherwise).
-These issues should be fixed if the paper is accepted.
-
-	\begin{resposta} 
-		We thank the comment provided by this reviewer. We have carefully revised and standardize all the entries. 
-	\end{resposta}
-
 \end{quote}
@@
 % \printbibliography
-
 \end{document}

### 2019-07-11 Tex/elsevier/trindade_solar_energy_rev1.tex
solar energy revised text

@@
 Instead, our novelty relies on an effective approach to perform validation of PV systems using formal methods, in a process that is intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior.}
+
+\textcolor{red}{Here we compare model checking with simulation tool.
+However how they work is completely different.
+Simulation depends on the choice of input variables (and their values) in order to obtain the output.
+In the other hand, model checking performs an automatic output search that causes the system to fails (a not expected behavior of the system) and presents the input that causes it.
+Therefore only with model checking we can prove the absence of system flaws.}
 
@@
 %Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where 
-As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
+As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis.
+\textcolor{red}{Hybrid2 is not supported anymore, being in disuse.} %all the tools perform solar photovoltaic analysis;
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
@@
 \centering
-\caption{Block diagram for a typical stand-alone PV system (adapted from~\citep{Hansen}).}
+\caption{\textcolor{red}{Block diagram for a typical stand-alone PV system, adapted from~\citep{Hansen}}.}
 \label{fig:blockdiagram}
@@
 \centering
-\caption{1-diode equivalent PV cell/panel circuit model (adapted from~\citep{Cubas}).}
+\caption{\textcolor{red}{1-diode equivalent PV cell/panel circuit model, adapted from~\citep{Cubas}.}}
 %\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
@@
 %
-%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.
+\textcolor{red}{It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.}
+
 %
@@
 
-In Step 1, the PV input data %(e.g., load power demand and load energy consumption) 
+In Step 1, the PV input data \textcolor{red}{(e.g., load power demand and load energy consumption)} 
 and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\citep{ANSI2018}.
@@
 This item includes as information from the house's load curve.
+
+\textcolor{red}{Those estimated load curves are converted as vectors with 24 positions, one to each house of the day (in Watts): 
+House 1: [118, 118, 118, 46, 46, 46, 95, 95, 170, 170, 296, 242, 242, 95, 95, 95, 95, 95, 342, 288, 288, 288, 288, 118]; 
+House 2: [136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136]; 
+House 3: [113, 113, 113, 113, 113, 113, 67, 67, 217, 97, 97, 97, 97, 97, 97, 97, 97, 97, 263, 113, 113, 113, 113, 113]; 
+House 4: [207, 207, 207, 135, 135, 135, 66, 66, 161, 161, 233, 253, 248, 66, 66, 66, 66, 66, 302, 317, 322, 302, 302, 207]; 
+House 5: [45, 16, 16, 16, 16, 16, 0, 0, 0, 72, 72, 222, 150, 150, 0, 0, 72, 72, 814, 814, 814, 742, 742, 16].}
 
@@
 We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
-%Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
+\textcolor{red}{Power peak, power surge and energy consumption were estimated based on visiting and survey applied in each house (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
+
 \begin{table}
@@
 \hline
-PV Panels &  \multicolumn{4}{|c|}{3x 325 W: in series} & 4x 325 W: 2x series, 2x parallel \\
-\hline
-Batteries & \multicolumn{4}{|c|}{\makecell{4x220 Ah: 2x series, 2x parallel\\ autonomy: 48 h}} & \makecell{4x 120 Ah batteries in series\\ autonomy: 6 h}\\
+PV Panels &  \multicolumn{4}{|c|}{3$\times$325 W: (3S)} & 4$\times$325 W: (2S-2P) \\
+\hline
+Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah (4S)\\ autonomy: 6 h}\\
 \hline
@@
 \hline
-Inverter & \multicolumn{4}{|c|}{700 W, peak of 1,600 W} & 1,200 W, peak of 1,600 W\\
-\hline
-Power demand & 253 W & 263 W & 283 W & 501 W & 915 W\\
+Inverter & \multicolumn{4}{|c|}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
+\hline
+\textcolor{red}{Power peak (W)}& 342  & 253  & 263 & 322 & 814 \\
+\hline
+\textcolor{red}{Power surge (W)}& 342 & 722 & 732 & 896 & 980\\
+\hline
+\makecell{Consumption \\ kWh/day}& \textcolor{red}{3.9} & \textcolor{red}{3.6} & \textcolor{red}{2.5} & \textcolor{red}{4.3} & \textcolor{red}{4.88} \\
 \hline
@@
 \end{tabular}
+\textcolor{red}{Legend: (S): Series; (P): Parallel.}
 \end{scriptsize}
@@
 %------------------------------------------
-Our \textcolor{red}{Verification and Simulation Results} aims to answer two research questions:
+\textcolor{red}{We aim} to answer two research questions:
 %
@@
 We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
+Nevertheless, we have also identified \textcolor{red}{four} threats to the validity of our results that can further be assessed.
 
@@
 \textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.
+
+\textcolor{red}{
+\textit{Simulation Tool:} Only HOMER Pro was used.
+The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification can change the comparative.}
 
@@
 In particular, the proposed method was successful in finding sizing errors and indicating in details.
-Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
+Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2 GB when compared to 9.2 GB of CBMC and 19.2 GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 

### 2019-07-12 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised reply letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{flushleft}
-    Mario A Medina, PhD, PE\\
+    Mario A. Medina, PhD, PE\\
     Associate Editor\\
@@
 
-\indent Dear Associate Editor,
+\indent Dear Mario,
 \vi
 
-We thank you for asking us to comply with your Reviewers' reports. 
-We are submitting a revised version of our manuscript entitled ``{\em \mstitle},'' by Alessandro Trindade, and Lucas Cordeiro.
-This revised version carefully addresses each comment provided by the reviewers, as suggested in your original decision letter.
-In particular, our reply letter describes all modifications we made to our manuscript and the respective responses to the comments raised by the reviewers.
+We thank you for asking us to comply with your reviewers' reports. 
+We are submitting a revised version of our manuscript entitled 
+``{\em \mstitle}'' by Alessandro Trindade and Lucas Cordeiro. 
+This revised version carefully addresses each comment provided 
+by the reviewers, as suggested in your original decision letter. 
+In particular, our reply letter describes all modifications we made 
+to our manuscript and the respective responses to the comments 
+raised by the reviewers.
 

### 2019-07-12 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (1)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta} 
-We thank the kind comment provided by this reviewer.
-Indeed, it summarizes what was intended to be done with this manuscript.
-In addition, we should highlight that the main focus was at the validation process of the solar PV system, instead of the mathematical modelling that was investigated in prior studies over the last two decades.
-This information was carefully included at the revised Abstract, Introduction and at the Conclusion sections, because we concluded that was not clear in the previous version of the paper.
-
-Regarding the Figure 2, we did as highlighted by the reviewer. Moreover, we did the same to voltage V in order to keep the same standard.
+We thank the reviewer fot this insightful comment.
+Indeed, it summarizes what was intended to be studied in this manuscript.
+Additionally, we emphasize that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated by prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction and conclusion sections since we concluded that it was unclear in the previous version of our manuscript.
+Regarding Figure 2, we fixed it as indicated by the reviewer.
+Moreover, we applied the same procedure to voltage V, in order to keep consistency throughout our manuscript.
 

### 2019-07-13 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 In contrast to other design systems, formal methods use mathematical proof as a complement to system testing in order to ensure correct behavior.
-With increasing scale and complexity, and safety becomes a more important issue, the formal approach to system design offers another level of insurance.
+With increasing scale and complexity, and safety becomes a more important issue, the formal approach to system design offers better level of insurance.
 
@@
 The original focus was to verify critical systems based on the premise that 'if system is important, must spend the enough time to verify it'~\cite{Lowry1998}.
-Worth to mention that back in time, formal methods were initially performed by hand.
+Back in time, formal methods were initially performed by hand.
 
@@
 
-If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification, resulting in a process known as formal verification.
-Verification may form part of a validation process, but in general, validation cannot be formalized because it relates a system design to intent.
+If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate verification.
 
@@
 In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-
 Testing can also be used for validation, but for the same reasons, it too is problematic for verification.
@@
 
-//////Begin optimization
 %-----------------------------------------------------------
@@
 As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
+
 CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
@@
 	\centering
-	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
-	\caption{CEGIS applied to PV system sizing.}
+	\includegraphics[width=0.75\columnwidth]{fig2_orig}
+	\caption{Counterexample Guided Inductive Synthesis (CEGIS).}
 	\label{Counter-Example-Guided-Inductive-Synthesis}
@@
 The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
-
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
+
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
 If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
-
-One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
+If this is the case, then the algorithm terminates, i.e., we have found a feasible solution; otherwise, in the CEGIS method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
+
+One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible solution was found.
 
@@
 Photovoltaics & X & X & X & X & X\\
-Batteries &  &  & X & X & X\\
+Batteries &  &  & X &  & X\\
 Main technical (T) or economical (E) & T & T & E & E & T \\
@@
 
-\subsubsection{Paper Proposal x Reference Tools}
-Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER and RETScreen remain for comparative.
+\subsubsection{Thesis Proposal x Reference Tools}
+Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER remain for comparative.
 All tools need some parameters inherently from manufacturer's catalog, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries.
@@
 
-\subsection{Component models for stand-alone PV system }
+\subsection{Component models for stand-alone PV systems}
 The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load.
@@
 
-///////begin-verification 
-\subsection{Sizing and Simulation of Stand-alone Solar PV systems}
-The sizing and validation of a PV system can be done by hand or with the aid of tools. Here we reference the critical period~\cite{Pinho} as an effective method to stand-alone PV sizing.
-%
-%In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
-%public domain and commercial software available for the PV market. 
-%According to \cite{Brooks}, t
-%%%%%%%%%%The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
-% to complex financial analysis and project optimization. 
-%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-%
-%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-
-The most popular softwares are summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
-%\subsection{PVWatts Calculator}
-%According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
-According to \cite{NRELDobos}, to use the calculator, it is necessary to provide information about the system's location, basic design parameters, and system economics.
-PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity monetary value.
-This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules.
-The production estimates that PVWatts computation do not account for many factors that are important in the design of a photovoltaic system, therefore it is necessary support of an energy expert.
-The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year.
-To represent the system's physical characteristics, PVWatts requires values for six inputs: System DC size; Module type; Array type; System losses; Array tilt angle; Array azimuth angle.
-%
-%\subsection{SAM}
-%SAM or System Advisor Model is a software from the U.S.
-Department of Energy and National Renewable Energy Laboratory.
-According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications, and (also) to provide information for readers who do not plan to use the model, but want to learn about its capabilities.
-SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: Project managers and engineers; Financial and policy analysts; Technology developers; and Researchers.
-SAM makes performance predictions and cost of energy estimates for grid-connected power projects based on installation and operating costs and system design parameters that you specify as inputs to the model.
-Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement.
-SAM is an electric power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet electric load.
-It does not model thermal energy systems that meet a thermal process load.
-As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.
-%
-%\subsection{HOMER}
-%As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
-HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources.
-HOMER Legacy is the original HOMER software version created at the National Renewable Energy Laboratory (NREL).
-HOMER Legacy is a free computer model that simplifies the task of evaluating design options for both off-grid and grid-connected power systems for remote, stand-alone, and distributed generation applications.
-HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options.
-Since 2016 HOMER Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available.
-At the short-time only the commercial version will remain.
-%
-%The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
-HOMER Pro put together three tools in one product: optimization, simulation, and sensitivity analysis.
-HOMER Pro provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use.
-It is adaptable to a wide variety of projects.
-For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project.
-For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations.
-Chronological simulation is essential for modeling variable resources, such as solar and wind power and for combined heat and power applications, where the thermal load is variable.
-HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.
-%
-%\subsection{RETScreen}
-%As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
-%
-%RETScreen models various types of renewable energy technologies (RETs), allowing for comparisons between technology options.
-The software can be used to evaluate benefits from both clean energy production from power generation projects and savings through energy efficiency projects, accounting for project costs, greenhouse gas emission reductions, and financial risk.
-The software is freely distributed (but with restrictions to save work or print), and had three different versions:
-%
-%\begin{itemize}
-%\item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
-%\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
-%\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
-However, this version works is only Windows-based.
-This version has a complete paid version, in an annual subscription way.
-%\end{itemize}
-%
-%As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
-It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
-RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.
-%
-%\subsection{Hybrid2}
-%The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
-Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
-Variations in wind speed and in load within each time step are factored into the performance predictions.
-The code does not consider short-term system fluctuations caused by system dynamics or component transients.
-This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, what is a limitation.
-%
-%Table~\ref{table:softwares} summarizes the off-the-shelf tools employed here, where 
-As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-However, commercial version of those tools, called RETScreen Expert and HOMER Pro, are available only for Microsoft Windows and the annual subscription typically range from US\$504.00 to US\$657.00.
-%
-\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Comparative coverage of reference simulation software}
-\label{table:softwares}
-\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-\begin{tabular}{c | c | c | c | c | c}
-\hline
-\hline
-Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen} & \rotatebox{90}{Hybrid2}\\
-\hline
-\hline
-Support & X & X & X & X &  \\
-\hline
-Off-grid systems &   &   & X & X & X\\
-\hline
-Hybrid systems &  &  & X & X & X\\
-\hline
-Photovoltaics & X & X & X & X & X\\
-\hline
-Batteries &  &  & X &  & X\\
-\hline
-\makecell{Main technical (T) \\ or economical(E)} & T & T & E & E & T \\
-\hline
-Optimization &  &  & X & X &  \\
-\hline
-Sensitive analysis &  &  & X & X & \\
-\hline
-\hline
-\end{tabular}
-\end{table}
-%
-%-------------------------------------------------------------------
-%\subsection{Paper Proposal x Reference Tools}
-%-------------------------------------------------------------------
-%
-In this study, HOMER was chosen to comparative with our proposed verification approach (Section~\ref{sec:results_indeed}).%All tools need some parameters inherently from manufacturer's catalog.
-%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
-%After that, the potential solution is analyzed in another tool to simulate or even optimize the proposed solution. Therefore, that is 
-%Thus, the main challenge here is to demonstrate the application of software model checking to formally verify a stand-alone PV solution, thus proving that this approach is more effective and complete than other state-of-the-art tool such as HOMER Pro.
-The comparative evaluation between HOMER Pro and our approach is presented in Section~\ref{sec:results_indeed}.
-%
-%-------------------------------------------------------------------
-\subsection{Component models for a stand-alone PV system }
-%-------------------------------------------------------------------
-%The main purpose of this section is to describe the models for the elements of a stand-alone PV system: PV generator, battery, controller, inverter, and load. 
-%The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}.
-It identifies the PV generator, batteries, charge controller, inverter, and AC load.
-A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-The PV generator is a semiconductor device that can convert solar energy into DC electricity.
-%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$).
-For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
-The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
-%
-%The modular structure facilitates the modeling of the other system structures and replacement of elements, such as a DC load instead of an AC load. 
-%
-\begin{figure}[h]
-\includegraphics[width=0.80\textwidth]{blockdiagramPVS2}
-\centering
-\caption{Block diagram for a typical stand-alone PV system (adapted from~\cite{Hansen}).}
-\label{fig:blockdiagram}
-\end{figure}
-%
-%In the literature, there are several mathematical models available for each component of PV systems. At the next section, the mathematical model for each component is presented. 
 %-------------------------------------------------------------------
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sizing Stand-alone Solar PV Systems}
-\label{sec:sizing}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
-The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.  
-For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage 
-form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system 
-contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior 
-of AC electrical load from the house that will be fed by the system.
-%
-\begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
-\centering
-\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
-\label{fig:blockdiagram} 
-\end{figure}
+////sizing check
 

### 2019-07-13 Tex/Old text/chapters/chapter03.tex
thesis updated text

@@
 \subsection{Variant CEGIS}
-Related to the CEGIS presented in chapter Background, it was created a variant CEGIS method at this work. There are four particular differences related to the traditional CEGIS:
+
+In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS. This variant was created during this Thesis.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
+	\caption{CEGIS applied to PV system sizing.}
+	\label{CEGISalt}
+\end{figure}
+
+Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+
+-----------
+
+There are four particular differences related to the traditional CEGIS described in Figure XX:
 

### 2019-07-13 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 \subsection{Component models for stand-alone PV systems}
+\label{model}
+
 The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load.
@@
 	\begin{itemize}
-	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
+	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); 
 	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
@@
 \subsubsection{Proposed PV Panel Model}
-With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1d1rmodel}.
-
-A single-diode without series and shunt resistances is considered. Equation 1 is used to write down expressions for currents and voltages at each key point shown in Fig. \ref{fig:ivcurve}.
+With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation~\ref{eq:1diodemodel}.
+
+A single-diode without series and shunt resistances is considered.
+Equation~\ref{eq:1diodemodel} is used to write down expressions for currents and voltages at each key point shown in Fig.
+\ref{fig:ivcurve}.
 
@@
 Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, the voltage and the current at the maximum power point and consequently the maximum output power, are expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm} ($ P_{m}=V_{m}I_{m} $).
-These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
+These equations are used to calculate the key cell parameters at the maximum power point (MPPT) as function cell temperature and parameters from the manufacturer's data-sheet.
 
@@
 
-The model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
+The model is now completely determined, i.e., with all the variables defined.
+This model requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
 
@@
 
-Besides the model verification, there is the prior stage of project sizing check, which is simple, based on manufacturer's data and information from the sizing and the site.
-
-First is necessary to correct the energy consumption that was estimated to the load ($E_{consumption}$).
-That is done by Equation \ref{eq:Ecorrected}, according \cite{Pinho}.
-Where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered.
-
-\begin{equation}
-\label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }
-\end{equation}
-
-The total minimum number of solar panels necessary($ N_{TPmin} $) is calculated by Equation \ref{eq:NTPmin}, and the check is done with the Equation \ref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from Equation \ref{eq:NTPmin}.
-
-\begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}
-\end{equation}
-
-\begin{equation}
-\label{eq:NTP}
-N_{TP} \geq N_{TPmin}
-\end{equation}
-
-Particularly, the total number of panels is series ($ N_{PSmin} $) and parallel ($ N_{PPmin} $) are given by the Equations \ref{eq:NPSmin} and \ref{eq:NPPmin}, respectively.
-With the check did by Equations \ref{eq:NPS} and \ref{eq:NPP}.
-$ V_{system} $ is the DC voltage of the bus, and is a design decision (normally 12, 24 or 48 V).
-
-\begin{equation}
-\label{eq:NPSmin}
-N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}
-\end{equation}
-
-\begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}
-\end{equation}
-
-\begin{equation}
-\label{eq:NPS}
-N_{PS} \geq N_{PSmin}
-\end{equation}
-
-\begin{equation}
-\label{eq:NPP}
-N_{PP} \geq N_{PPmin}
-\end{equation}
-
-\subsubsection{The Battery Storage Model }
+\subsubsection{Battery Storage Model }
 Because of the fluctuating nature of the output delivered by the PV arrays, batteries are necessary in a PV system.
@@
 
-Besides the model verification, there is also the prior stage of project sizing check, as did to the solar panel.
-First is necessary to define the total capacity of the battery bank, as shown by Equation \ref{eq:Cbank}.
-
-\begin{equation}
-\label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}
-\end{equation}
-
-The variable $ autonomy $ is a design definition and normally has a value ranging from 6 to 48h. The other variables were discussed previously.
-
-Following, is done the total (minimum) number of batteries, as show by Equation \ref{eq:Nbtotal}.
-Moreover, the Equation \ref{eq:batcheck} perform the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that were established to the project.
-
-\begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}
-\end{equation}
-
-\begin{equation}
-\label{eq:batcheck}
-\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total
-\end{equation}
-
 \subsubsection{Controller Model}
@@
 According to \cite{Pinho}, controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.
+
+Controllers with MPPT mechanism are the mostly used nowadays,  and it maintains the PV operating at the stage of maximum power.
 
@@
 
-Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the current output of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $-I_{out}$ is the output current from the converter, when all the other values are known.
+Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the current output of PV array, $ V_{out}$ is the  DC bus voltage, and $I_{out}$ is the output current from the converter, when all the other values are known.
+
+Worth to mention that $ V_{out}$, depending on the PV panel generation and on the batteries charge, it can be the voltage that charges the battery $V_{b}$ (which is bigger than the nominal voltage of the batteries), the voltage that is feed by the batteries (the same $V_{b}$ but with levels that can be lower than it, or even the voltage that comes from the PV panels and depends on the MPPT system employed by the controller.
 
@@
 As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
-
-One more time, some steps must be done to check the sizing project of the controller, prior the verification phase.
-Initially the controller must meet the voltage requirement of the PV system, as shown by Equation \ref{eq:vcvsystem}.
-
-\begin{equation}
-\label{eq:vcvsystem}
-V_{c} = V_{system}
-\end{equation}
-
-Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as shown by Equation \ref{eq:iscamb}.
-
-\begin{equation}
-\label{eq:iscamb}
-I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right] 
-\end{equation}
-
-The controller must meet the maximum current from the PV array (Equations \ref{eq:icmin} and \ref{eq:icicmin}).
-
-\begin{equation}
-\label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP}
-\end{equation}
-
-\begin{equation}
-\label{eq:icicmin}
-I_{c} \geq I_{c,min}
-\end{equation}
-
-The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
-In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
-
-\begin{equation}
-\label{eq:numberofcmin}
-number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} =  \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
-\end{equation}
-
-\begin{equation}
-\label{eq:numberofc}
-N_{controller} \geq number_{controllers}
-\end{equation}
 
@@
 
-The sizing project check of the inverter is done through three Equations.
-Equation \ref{eq:vindc} ensure that the input voltage of the controller meet the voltage of the system.
-Equation \ref{eq:voutac} ensures that the output voltage of the controller meet the AC voltage of the load.
-Moreover, Equation \ref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
-
-\begin{equation}
-\label{eq:vindc} 
-V_{in}DC = V_{system}
-\end{equation}
-
-\begin{equation}
-\label{eq:voutac} 
-V_{out}AC = V_{AC}
-\end{equation}
-
-\begin{equation}
-\label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right] 
-\end{equation}
-
-%-------------------------------------------------------------------
-\subsection{PV System Model}
-\label{sec:PVsystemmodel}
-%-------------------------------------------------------------------
-%A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. 
-%In the present modeling, the focus is only on cell/module/array.
-%
-%%%%%%The basic element of a PV system is a PV cell, also called a solar cell. A solar cell is a semiconductor device that can convert solar energy into DC electricity. 
-%The semiconductor materials (usually silicon), which are specially treated to form an electric field, positive on one side (backside) and negative on the other (towards the sun).
-When solar energy (photons) hits the solar cell, electrons are knocked loose from the atoms in the semiconductor material, creating electron-hole pairs \cite{Lorenzo}.
-If electrical conductors are attached to the positive and negative sides, forming an electrical circuit, the electrons are captured in the form of electric current $ I_{ph} $ (photocurrent).
-%%%%%To increase their utility, a number of individual PV cells are interconnected together in a %sealed, weatherproof 
-%%%%%package called panel or module. 
-%For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
-In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}.
-The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{celmodarray}
-%\centering
-%\caption{PV cell, module and array (Source: \cite{SamlexSolar})}
-%\label{fig:celmodarray}
-%\end{figure}
-%
-%%%%%The PV modules are generally rated under standard test conditions (STC), and the parameters required for the input of the PV modules are relying on meteorological conditions.
-%the meteorological conditions of the area to be serviced by PV solution. %However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
-%, which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
-The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
-However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
-%
-%These uncertainties lead to either over- or underestimation of energy yield from PV modules.
-An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
-The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Yatimi}, \cite{Saloux}, \cite{Mellit}.
-%
-%Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
-However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage.
-Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
-% 
-%Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
-Mathematical models are required in order to allow the formal specification of the PV system. At this section we will summarize the models adopted at the paper.
-
-\textbf{PV modules}: a wide variety of models exists. % for estimation of its power output  (and $I-V$ or $P-V$ curves). 
-However, the present work will rely on the simplified model of 1-diode, illustrated in Fig.
-\ref{fig:equivckt}.
-This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-
-%The performance of PV systems %, %that is, the output current/voltage curve ($I-V$ curve), 
-%is usually studied using an equivalent circuit model~\cite{Yatimi}, which consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model~\cite{Cubas}.
-%Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig. \ref{fig:equivckt}. 
-\begin{figure}[h]
-\includegraphics[width=0.40\textwidth]{equivckt1D}
-\centering
-\caption{1-diode equivalent PV cell/panel circuit model (adapted from~\cite{Cubas}).}
-%\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
-\label{fig:equivckt}
-\end{figure}
-
-The Eq.
-\eqref{eq:1diodemodel} relates the output current, $I$, to the output voltage, $V$.
-%This model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-%In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
-\begin{equation}
-\label{eq:1diodemodel}
-I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right], 
-\end{equation}
-
-\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
-$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}\:J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}\:C $).
-
-%\begin{itemize}
-%\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
-%\item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
-%\item $ N $ is the number of series-connected cells in the photovoltaic system to be analyzed; $ N=1 $ in a single cell configuration.
-%	\begin{itemize}
-%	\item $ N=1 $ in a single cell configuration. 	
-%	\end{itemize}	  
-%\item $ a $ is the ideality factor (or quality factor) that takes into account the deviation of the diodes from the Shockley diffusion theory; $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes.
-%	\begin{itemize}
-%	\item $a=1$ for ideal diodes and between $ 1 $ and $ 2 $ for real diodes. 	
-%	\end{itemize}
-%\item $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $);
-%	\begin{itemize}
-%	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J $); 
-%	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
-%	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
-%	\end{itemize}	 
-%\end{itemize}
-%
-%This model has only three unknown parameters ($ I_{ph}$, $I_{0}$, and $a $), and it assumes that the series resistance is $ zero $ and shunt resistance is $ infinite $ and, thus, both of these parameters are ignored.
-%
-%The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}. 
-%
-%\begin{equation}
-%\label{eq:1d1rmodel}
-%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
-%\end{equation}
-%
-%Where $R_{s}$ is the series resistor.
-%
-%At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
-%
-%The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}. 
-%
-%\begin{equation}
-%\label{eq:1d2rmodel}
-%I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-%\end{equation}
-%
-%Where $R_{sh}$ is the shunt resistor.
-%
-%At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
-%
-%And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}. 
-%
-%\begin{multline}
-%\label{eq:2d2rmodel}
-%I =I_{ph}-I_{01}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{1}V_{T}} \right) -1 \right] - \\ %I_{02}\left[ exp \left( \dfrac{V+IR_{s}}{Na_{2}V_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-%\end{multline}
-%
-%This model has six unknown parameters with two exponential terms. 
-%Briefly, both single and double diode models require the knowledge of all unknown parameters, which is usually not provided by manufacturers.
-Nevertheless, the current-voltage equation is a transcendental expression \cite{Jakhrani}.
-%
-%However, regardless of the adopted model, the parameters of the equations must be estimated to adapt the corresponding model to the real behavior of the solar cell/panel. 
-%
-%For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
-The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
-However, due to implicit nature and nonlinearity of PV cell or module characteristics, it is hard to find out the analytical solution of all unknown parameters, as described by \cite{Hasan}.
-Thus, numerical methods such as Newton-Raphson method or Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}.
-This happens because numerical methods give approximate solution of the nonlinear problems without searching for exact solutions.
-However, numerical methods are time consuming and need long term time series data, which is not available in developing countries.
-\cite{Jakhrani} did a mixed methodology using analytical and numerical steps together.
-\cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation (essays).
-And \cite{Tian} did a mix of analytical and experimental methodology to get the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use experimental technique.
-%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
-%The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing~\cite{Cubas}.
- %
-%\subsection{PV Panel Model}
-%With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation \ref{eq:1diodemodel}.
-%
-%A single-diode without series and shunt resistances is considered. 
-%%%%%%%Eq.~\eqref{eq:1diodemodel} is used to express currents and voltages at each key point of the characteristic curve from a PV cell \cite{Villalva}.
-% shown in Fig. \ref{fig:ivcurve}.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{ivcurve}
-%\centering
-%\caption{$ I-V $ characteristic curve of an ideal PV cell (Source: \cite{Saloux})}
-%\label{fig:ivcurve}
-%\end{figure}
-%
-%Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
-%\begin{equation}
-%\label{eq:Isc}
-%I_{sc}=I_{ph}\vert_{V=0}
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Voc}
-%V_{oc}=\dfrac{aNk_{B}T}{q}ln\left( 1+\dfrac{I_{sc}}{I_{0}} \right) 
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:exp}
-%exp\left( \dfrac{qV_{oc}}{aNk_{B}T} \right) = \left(1+\dfrac{qV_{m}}{aNk_{B}T} \right) exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) 
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Im}
-%I_{m} =I_{ph}-I_{0}\left[ exp \left( \dfrac{qV_{m}}{aNk_{B}T} \right) -1 \right] 
-%\end{equation}
-%
-%Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way. 
-%
-%A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}. 
-%These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig.
-\ref{fig:ivcurve}, where the transition is a compromise between both behaviors.
-It is interesting to observe that the maximum power point corresponds to a trade-off condition, where the current is still high enough before it starts decreasing with increasing the output voltage (Fig.
-\ref{fig:ivcurve}).
-%
-%Based on this, the tangent of the I-V curve can be used to evaluate the transition between current- to voltage-source controlled regions; this operation yields Equation \ref{eq:didv}.
-%
-%\begin{equation}
-%\label{eq:didv}
-%\dfrac{dI}{dV}=-\dfrac{qI_{0}}{aNk_{B}T}exp \left( \dfrac{qV}{aNk_{B}T}  \right) 
-%\end{equation}
-%
-%The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell.
-Therefore, the Equation \ref{eq:Vmderiv} is generated.
-%
-%\begin{equation}
-%\label{eq:Vmderiv}
-%V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
-%\end{equation}
-%
-%It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point.
-The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change on $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}.
-Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation \ref{eq:Vmderiv} can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
-%
-%\begin{equation}
-%\label{eq:dIdV_Vm}
-%\dfrac{dI}{dV}\vert_{V_{m}} \cong -\dfrac{0-I_{sc}}{V_{oc}-0}=\dfrac{I_{sc}}{V_{oc}}
-%\end{equation}
-%
-%Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, 
-%
-The voltage and the current at the maximum power point tracking (MPPT), can be described by Eq.
-\eqref{eq:Vmfinal}, and Eq.
-\eqref{eq:Imfinal}~\cite{Saloux}: %, and Eq.
-\eqref{eq:Pm} as follows~\cite{Saloux}: %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
-\begin{equation}
-\label{eq:Vmfinal}
-V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right). 
-\end{equation}
-
-\begin{equation}
-\label{eq:Imfinal}
-I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right).  
-\end{equation}
-
-%\begin{equation}
-%\label{eq:Pm}
-%P_{m} = V_{m} I_{m}.
-%\end{equation}
-%
-%\begin{multline}
-%\label{eq:Pm}
-%P_{m} = V_{m} I_{m} = \left[ \dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) \right] \times \\ \left[ I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  \right]
-%\end{multline}
-%
-However, the photo-current delivered by the constant current source ($I_{ph}$) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, Eq.
-~\eqref{eq:Iph} is used to calculate the photo-current as function of irradiance and temperature~\cite{Villalva}:
-\begin{equation}
-\label{eq:Iph}
-I_{ph}=\dfrac{G}{G_{ref}} \left[ I_{ph,ref} + \mu_{I} \left( T-T_{ref} \right)    \right], 
-\end{equation}
-
-\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000\:W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}\:C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$); %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions.
-$ I_{ph,ref} $ can be approximated to the reference short-circuit current ($ I_{sc,ref} $)\cite{Villalva}.
-% that is provided by PV manufacturers ($ I_{sc,ref} $).
-%\cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
-%%
-The cell temperature ($ T $) in degree Celsius is described by Eq. \ref{eq:Tcell}~\cite{Ross}:
-\begin{equation}
-\label{eq:Tcell}
-T = T_{air} + \dfrac{NOCT-20}{800}G,
-\end{equation}
-
-\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C), and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
-
-Furthermore, Eq. ~\eqref{eq:I0} permits the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature as~\cite{Villalva} 
-%In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
-
-\begin{equation}
-\label{eq:I0}
-I_{0} = \dfrac{I_{sc,ref} + \mu_{I}(T - T_{ref})}{exp \left[ \dfrac{q(V_{oc,ref} + \mu_{V} (T - T_{ref}))}{aNk_{B}T}    \right] -1},
-\end{equation}
-
-\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
-
-%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
-Using the maximum power point current, cf.
-Eq.~\eqref{eq:Imfinal}, and the saturation current in the reference temperature given by Eq.~\eqref{eq:I0}, the diode ideality factor~\cite{Saloux} is determined by Eq.~\eqref{eq:a}:
-\begin{equation}
-\label{eq:a}
-a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) },
-\end{equation}
-
-\noindent where $V_{mref}$, $V_{oc,ref}$, $I_{m,ref}$, and $I_{sc,ref}$ are key cell values obtained under both actual cell temperature and solar irradiance conditions.
-%, usually provided by manufacturers; t
-
-%The PV generator model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers in data-sheets or manuals.
-%
-%If the PV cells are in parallel, then there is a parallel array.
-Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
-%
-%\begin{equation}
-%\label{eq:Iarray}
-%I_{array} = (N_{cells in parallel})(I_{one cell})
-%\end{equation}
-%
-%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
-%
-%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
-%
-%\begin{equation}
-%\label{eq:Varray}
-%V_{array} = (N_{cells in series})(V_{one panel})
-%\end{equation}
-%
-%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
-%------------------------------------------------------------
-%Because of the fluctuating nature of the output delivered by the PV arrays, batteries are nece\sqrt{•}ry in a PV system.
-Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery.
-During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.
-
-Related to the \textbf{batteries}, various models have been described in the literature and the most common ones are based on lead-acid batteries~\cite{Copetti,Pinho};
-%, and \cite{Manwell93, Manwell94}. 
-%However, regardless of the model, normally the following parameters are required: 
-%
-%\begin{itemize}
-%\item Nominal capacity ($ q_{max} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery
-%, under predetermined discharge conditions.
-%\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. 
-%Obviously $ 0<SOC<1 $. 
-%If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
-%\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). 
-%It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
-%\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
-%\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
-%\end{itemize}
-%
-%The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
-The battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
-LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.
-%
-%In general, the battery models view the battery as a voltage source $ E $ in series with an internal resistance $ R_{0} $, as shown in Fig. \ref{fig:batteryckt}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{batteryckt}
-%\centering
-%\caption{Schematic diagram of the battery (Source: \cite{Hansen})}
-%\label{fig:batteryckt}
-%\end{figure}
-%
-%The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.  
-%
-%Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
-%
-%The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.  
-%
-%The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
-However, it uses some data extracted from tested batteries in laboratory.
-Therefore is not suitable to this study.
-%
-that kind of battery has relative low cost and wide availability~\cite{Copetti}. 
-%
-Here, the model adopted uses only manufacturer's data without empirical tests~\cite{Copetti}. % and allows finding relations among voltage, current, state of charge and temperature. 
-%
-The discharge voltage is described by Eq. \eqref{eq:bat_Vd}.
-%The first term represents the voltage variation with the state of charge ($ SOC $), i.e., the electrolyte concentration, and the second is the variation due to internal resistance variation.
-%
-\begin{multline}
-\label{eq:bat_Vd}
-V_{d} = \left[ 2.085-0.12(1-SOC) \right] - \dfrac{I}{C_{10}} \left( \dfrac{4}{1+I^{1.3}} + \dfrac{0.27}{SOC^{1.5}}+0.02 \right) (1-0.007 \Delta T),
-\end{multline}
-
-\noindent where $C_{10}$ means 10 h of rated capacity (manufacturer's data-sheet), $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $%, $ T_{ref}=25^{o}C $
-), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time.
-%Mathematically, it is the ratio between the present capacity and the nominal capacity% (in $ Ah $, provided by manufacturer)
-%If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
-%\begin{equation}
-%\label{eq:SOCbat}
-%SOC = \left( 1 - \dfrac{Q}{C} \right) 
-%\end{equation}
-%
-%Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
-%
-%The ratio between $ Q $ and $ C $ represents t
-The depth of discharge ($DOD$) or the fraction of discharge, is $DOC=1-SOC$.
-
-%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
-This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
-%
-%\begin{equation}
-%\label{eq:CC10}
-%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
-%\end{equation}
-%
-%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
-For the charging process, the parameters are described by Eq.~\eqref{eq:Vcbat} as
-%
-\begin{multline}
-\label{eq:Vcbat}
-V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
-\end{multline}
-%
-%Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period.
-%; however, during recharge it is much more difficult \cite{Copetti}.
-%Generally, the efficient region is where $ SOC $ is below $ 0.7 $ and $ V_{c} $ is less than $2.3 V$ per cell.
-The efficiency drops to zero at full charge and the function that represents the charge efficiency ($ \eta_{c} $) variation with state of charge and current rate is given in Equation \ref{eq:efficcharge}.
-%\begin{equation}
-%\label{eq:efficcharge}
-%\eta_{c} = 1 - exp \left[ \dfrac{20.73}{\dfrac{I}{I_{10}}+0.55} (SOC-1) \right] 
-%\end{equation}
-%
-%\cite{Copetti} show that, 
-%During overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (\ref{eq:Vec}).
-It was created a function for the gassing voltage as well, as shown in (\ref{eq:Vg}).
-In addition, the overcharge phenomenon can be represented by (\ref{eq:Voverc}).
-%\begin{equation}
-%\label{eq:Vec}
-%V_{ec} = \left[ 2.45 + 2.011 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-%\end{equation}
-%
-%\begin{equation}
-%\label{eq:Vg}
-%V_{g} = \left[ 2.24 + 1.97 ln \left( 1+\dfrac{I}{C_{10}} \right)  \right] (1-0.002 \Delta T)
-%\end{equation}
-%
-%\begin{multline}
-%\label{eq:Voverc}
-%V_{c} = V_{g} + (V_{ec} - V_{g}) \\ \left[ 1- exp \left( \dfrac{Ah_{restored}-0.95C}{I\tau}  \right)    \right] 
-%\end{multline}
-%
-%Where $ Ah_{restored} $ represents the Ampere-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
-%
-%The function assumes that 95\% of the capacity was already restored at the start of overcharge.
-%
-%The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by (\ref{eq:tau}).
-%\begin{equation}
-%\label{eq:tau}
-%\tau = \dfrac{17.3}{1+852 \left( \dfrac{I}{C_{10}} \right) ^{1.67} }
-%\end{equation}
-%
-%Therefore, to model the voltage ($ V_{c} $) evolution of the battery, (\ref{eq:Vcbat}) can be used up the start of gassing ($ V_{c} \leq V_{g} $).
-And during overcharging ($ V_{c} > V_{g} $), (\ref{eq:Voverc}) can be used until a constant final voltage ($ V_{ec} $) is reached.
-%
-%The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
-%
-%\begin{equation}
-%\label{eq:stor}
-%Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
-%\end{equation}
-%
-%Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
-%
-%As an example of this formula application, as shown by \cite{Abdulateef}, considering that a stand-alone PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
-%
-%Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$.
-Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$).
-If a single battery of 12 V and 350 Ah is considered, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
-%
-%At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature.
-The equations are used to update the $SOC$ of the batteries, and have the number of hours ($ Num_{h} $) as a variable.
-There is a factor (1.15) which is present at the charging equation, and is necessary to express that during the charging process is usual to reach 115\% of the battery capacity
-%
-%\begin{multline}
-%\label{eq:charge}
-%SOC_{charge} = SOC_{previous} + \\ \dfrac{100*Pm*Num_{h}}{V_{system}*capacity*N_{BP}*1.15}
-%\end{multline}
-%
-%\begin{multline}
-%\label{eq:discharge}
-%SOC_{discharge} = SOC_{previous} - \\ \dfrac{100*I_{drained}*Num_{h}}{capacity}
-%\end{multline}
-%
-%
-%---------------------------------------------------------
-%---------------------------------------------------------
-%Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
-However, in this study, in order to simplify, the term used is controller.
-
-The \textbf{charge controller} or controller is the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-Controllers with MPPT mechanism are the mostly used nowadays,  and it maintains the PV operating at the stage of maximum power.
-%Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime.
-%
-%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
-%
-%
-%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components.
-The use of battery as a storage form implies thus the presence of a charge controller.
-%
-%%%%%%%%%%In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
-%
-%The controller allows the management of energy between the load and the battery \cite{Mellit}. 
-%The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
-The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
-
-The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.
-To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \_ off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}.
-PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \_ on} $.
-%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{controllerover}
-%\centering
-%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
-%\label{fig:controllerover}
-%\end{figure}
-%
-In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \_ off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}.
-The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \_ on}$.
-%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.4\textwidth]{controllerdisc}
-%\centering
-%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
-%\label{fig:controllerdisc}
-%\end{figure}
-%
-%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
-%
-\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process (adapted from~\cite{Hansen})}
-\label{table:controller}
-\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-\begin{tabular}{c | c | c }
-\hline
-\hline
-Step  & Constraint & Command\\
-\hline
-\hline
-(1) & \makecell{If $V > V_{max \_ off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
-\hline
-(2) & \makecell{If command (1) is \\done and $V < V_{max \_ on}$} & \makecell{Reconnect PV array \\to the system}\\
-\hline
-(3) & \makecell{If $V < V_{min \_ off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
-\hline
-(4) & \makecell{If command (3) is \\ done and $V > V_{min \_ on}$} & \makecell{Reconnect the load \\to the system}\\
-\hline
-\hline
-\end{tabular}
-\end{table}
-
-%Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage. 
-%
-%As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load. 
-The output power ($ P_{out} $) of controller is given by Eq. \eqref{eq:poutcont}.
-\begin{equation}
-\label{eq:poutcont}
-P_{in} \eta_{c} = P_{out}.
-\end{equation}
-
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Eq. \eqref{eq:poutcont} we compute Eq. \eqref{eq:potcont}.
-\begin{equation}
-\label{eq:potcont}
-V_{in} I_{in} \eta_{c} = V_{out} I_{out},
-\end{equation}
-
-\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.
-
-%The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}). 
-% 
-%A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
-In addition, there is the Cuk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.
-%
-%For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.
-%
-%\begin{equation}
-%\label{eq:voutvin}
-%\dfrac{V_{out}}{V_{in}} = \dfrac{D}{D-1}
-%\end{equation}
-%
-%Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
-% 
-%The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
-%  
-%Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.
-% 
-%As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
-
-%The number of controllers required for the stand-alone PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
-In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
-%\begin{multline}
-%\label{eq:numberofcmin}
-%number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \\ \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
-%\end{multline}
-%
-%\begin{equation}
-%\label{eq:numberofc}
-%N_{controller} \geq number_{controllers}
-%\end{equation}
-%
-%\subsection{Joint work: charge controller and batteries}
-%When batteries are charged, they go through three main different states - bulk, absorption and float, with impact to the inverter and to power supplied to the house.
-%, and it is necessary to understand those three states in order to comprehend the joint work of the controller with the battery. With impact to the inverter and to power supplied to the house. 
-%
-%All the explanation at this section is related to $SOC$ and to the voltage at the DC-bus (controller output, which will be bigger than $V_{system}$) where the batteries are connected, all ruled by the charge controller.
-Moreover, it is important to mention that smart chargers, the most usual nowadays, will detect voltage and resistance from the battery prior to charging.
-%
-%Bulk - is the first stage of charging. Bulk begins when the sun comes out.
-%, or other source of electrical generation is turned on. 
-%This stage occurs when the batteries are at a lower $SOC$, generally anything not smaller than $75\%$ to $80\%$ (defined during system sizing).
-This stage is typically where the highest voltage and current the charger is rated for will actually be used.
-The bulk stage basically allows the PV panel to put as much current into the batteries as possible.
-For a typical 12 V battery, the charging voltage going into a battery will reach 14.16 V to 14.40 V at this stage, and there is no risk of overcharging in this stage because the battery hasn't even reached full yet.
-%
-%Absorption - once the batteries reach the programmed absorb voltage, usually somewhere between 14.16 and 14.40 V, the batteries will go into the absorption stage.
-Typically, when a battery reaches this stage its $SOC$ is around $85-95\%$.
-During this stage, the batteries are kept at the programmed voltage, and the current going into the batteries reduces as the batteries become more full.
-The absorption stage ends after the programmed time is reached or the number of Ampere going into the battery falls below a preset number.
-The lower current going into the battery safely brings up the charge on the battery without overheating it.
-%Usually, this stage takes more time than the bulk stage.
-%
-%Float - upon the completion of the absorption stage, the charge controller will  drop down the voltage and maintain at a steady 13.20 V to 13.38 V (manufacturer's defined value), which is the maximum voltage that a 12 V battery can hold, and begin the float stage.
-The float stage brings the battery all the way through and maintains $SOC$ at $100\%$.
-The current will also decrease to a point where it's considered just a pulse.
-It's essentially the float stage where there is charge going into the battery at all times, but only at a safe rate to ensure a full state of charge and nothing more.
-%Most smart chargers do not turn off at this point, however it is completely safe to leave a battery in float mode for months to even years at a time.
-%
-%Battery charging technology relies on smart micro-controlled devices.
-Therefore it is extremely important that the program settings for the charge controller or inverter/charger are correct, and the list includes the bulk and absorption values.
-%This will help preserve and extend the battery life.
-There are always default settings to the equipment, set by software, however those settings are not $100\%$ correct because there are difference among models of equipment and among manufacturer's.
-The ideal is to read the data-sheet from the manufacturers and perform a manual adjust.
-%
-%There are the possibility to combine batteries in a bank, with parallel and series connections, all depending the sizing of the project:
-%
-%\begin{itemize}
-%\item Batteries connected in parallel are seen by the controller as one large battery of the combined Ah capacity of all the batteries.
-For example, two 12 V and 220 Ah batteries in parallel are seen as one 12 V and 440 Ah battery;
-%\item In the other hand, although the batteries connected in series are also seen as a single battery, the result is different: two 12 V and 220 Ah batteries in series are seen as one 24 V and 220 Ah battery;
-%\item In addition, a mixed bank arrangement can be useful: a bank with two 12 V and 220 Ah batteries in series connected in parallel with a similar arrange will produce an equivalent battery of 24 V and 440 Ah.
-%\end{itemize}
-%-----------------------------------------------
-%-----------------------------------------------
-%As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. 
-%An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output. 
-The role of the \textbf{inverter} is to keep the voltage constant on the AC side, %, i.e., at the rated voltage, % (127 V or 220 V, for example), 
-and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency $ \eta_{i} $ as described by \eqref{eq:efficinv} \cite{Hansen}:
-%
-%The inverter is characterized by a power dependent efficiency $ \eta_{i} $ as shown by (\ref{eq:efficinv}) \cite{Hansen}.
-\begin{equation}
-\label{eq:efficinv}
-\eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}},
-\end{equation}
-
-\noindent where $ I_{DC} $ is the current required by the inverter from the DC source to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be obtained from the inverter's manual.
-
-%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
-%
 %
@@
 %--------------------------------------------------
-%Each stand-alone PV system, like any other power systems, has a specific level of availability.
+
+Each stand-alone PV system, like any other power systems, has a specific level of availability.
 This reliability level impacts various issues, as system performance, production, feasibility, and investment.
+
 The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
@@
 While in a ordinary house electrical load, 95\% is considered acceptable.
-%As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system.
+
+As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system.
 An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
-%
-%With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong.
+
+With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong.
 It is important to evaluate how critical the load application is and the horizon of evaluation.
 However this analysis can be useful, for example, to improve the sized battery autonomy.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-////sizing check
-
-The sizing check stage will ensure that the system meets the standard project steps related 
+
+\subsection{Sizing Stand-alone Solar Photovoltaic Systems}
+
+The mathematical model presented at section~\ref{model} is important for the project validation, however if it is included an approach to perform the sizing of stand-alone PV systems, than the proposed tools at this Thesis can perform the system validation (the intended behavior), and moreover to obtain the optimal project sizing.
+
+The sizing check stage can ensure that the system meets the standard project steps related 
 to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller,
@@
 %
-Secondly, the total (minimum) number of batteries is computed as
+Secondly, the total number of batteries is computed as
 
@@
 N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
+\end{equation}
+
+Moreover, the Equation \ref{eq:batcheck} perform the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted by the project.
+
+\begin{equation}
+\label{eq:batcheck}
+\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total
 \end{equation}
@@
 I_{c} \geq I_{c,min}.
+\end{equation}
+
+The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
+In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
+
+\begin{equation}
+\label{eq:numberofcmin}
+number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} =  \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
+\end{equation}
+
+\begin{equation}
+\label{eq:numberofc}
+N_{controller} \geq number_{controllers}
 \end{equation}
@@
 
+\textcolor{red}{Number of inverters???? XXXXXXXXXXX}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{PV systems Optimization Criteria}
+\subsection{PV Systems Optimization Criteria}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (2)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta} 
-Here it is worth to mention that our options about specialized off-the-shelf tools were reduced.
-As informed at Section 2.1 of the paper, only Hybrid2 and HOMER Pro perform off-grid with battery analysis of PV systems.
-Hybrid2 is not supported anymore, being in disuse.
-This information was updated to the paper.
-Therefore, at this particular kind of system (stand-alone solar PV systems), only HOMER Pro could be used for comparative.
-Nevertheless, some general use simulation could be used, with the same mathematical model adopted by the automated verification tool.
-Because of that, we included a mention to that issue in the section 5.4 (Threats to Validity).
+Note that our options about specialized off-the-shelf tools to design stand-alone solar PV systems are very limited in literature, which motivated us to perform further studies in this area.
+In particular, as described in Section 2.1, only Hybrid2 and HOMER Pro perform off-grid with battery analysis of PV systems.
+Hybrid2 is not supported anymore, thereby being in disuse.
+We have updated this information in our manuscript.
+Therefore, in this particular research field (stand-alone solar PV systems), only HOMER Pro could be used for comparative purposes.
+However, in our experiments we could some general simulation tools with the same mathematical model adopted by the automated verification tool.
+However, this would represent an unfair comparison since we would need to tweak the simulation tools to prepare them for comparison purposes.
+We have described this limitation in Section 5.4 (``Threats to Validity'') in order to state that additional comparisons could be carried out with general simulation tools if they employ similar mathematical models as the ones described here.
 
-Model checking and software simulation are two different techniques that uses mathematical models.
-However how they work is completely different.
-Simulation depends on the choice of input variables (and their values) in order to obtain the output.
-In the other hand, model checking performs an automatic output search that causes the system to fails (a not expected behavior of the system) and presents the input that causes it.
-Therefore with model checking we can prove the absence of system flaws.
-This information was included at the revised text as well.
+Note that model checking and software simulations are two different techniques that use mathematical models.
+However, the way they work is completely different.
+On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
+On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
+In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation.
+Therefore, we can prove the absence of system flaws using model checking.
+This information was included in the revised version of our manuscript in Section X \textcolor{red}{could you please describe the section here?}.
 
-Model checking explores more efficiently the design-space because the specification of the system is based on formal notation (that is converted to Boolean algebra) and the evaluation of variables is made automatically based on constraints (basically system information and electrical load demand transformed in software code) and properties (use defined demands, weather variables that the use do not have precise forecasting).
-This resulting mathematical model pass through a exploration of its possible states in order to find a configuration where occurs or not a fail.
-Logically, depending on the number of variables, the number of states explode and is time-consuming during computing of the result.
+Importantly, model checking explores more efficiently the design-space because the system specification is based on a formal notation, which gets converted into Boolean algebra; the evaluation of variables is made automatically by a Boolean Satisfiability (SAT) solver based on the system's constraints, i.e., system information and electrical load demand transformed into properties (e.g., use defined demands and non-deterministic weather variables that do not have precise forecasting).
+This resulting mathematical model is submitted to full exploration of all possible states to find a configuration, where an error might occur or not.
+Logically, depending on the number of variables, state-explosion can occur and the model checking process might be time-consuming to transverse the entire state-space.
 
-However, the authors showed in 2016\footnote{Trindade, A.B.
-and Cordeiro, Applying SMT-based verification to hardware/software partitioning in embedded systems.
-Des Autom Embed Syst (2016) 20: 1.
-https://doi.org/10.1007/s10617-015-9163-z} that model checking can present better performance than simulation software when performing hardware-software partitioning in specifically amount of instances.
+However, the authors demonstrated in $2016$ [1] that model checking can present better performance than software simulation if one performs hardware-software partitioning in specifically amount of instances.
+
+[1] Trindade, A.B. and Cordeiro, Applying SMT-based verification to hardware/software partitioning in embedded systems. Des Autom Embed Syst (2016) 20: 1. https://doi.org/10.1007/s10617-015-9163-z
 

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (3)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta} 
-Indeed, we miss this information at paragraph that describes the Figure.
+Indeed, we have missed this particular information in the paragraph that describes the mentioned figure.
 We thank you so much for this observation.
-Therefore we revised the text and described every symbol.
-The final version of the paragraphs were: "A stand-alone PV system is illustrated in Fig.1.
+We have revised our manuscript to describe every employed symbol.
+The revised version of these paragraphs \textcolor{red}{in Section X} are now described as: ``A stand-alone PV system is illustrated in Fig.1.
 The PV generator is a semiconductor device that can convert solar energy into DC electricity, with high dependence of two weather variables from the site where the system is deployed: solar irradiance $G$ and temperature $T$.
@@
 The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
-At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.".
+At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.''.
 \end{resposta}

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (4)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta} 
-Indeed, we did not inform the impact the changing of computer setup or related issues.
-We thank you so much for this observation.
-Therefore we revised the text and included the following paragraph: "Note that the results presented here depend on the computer's processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved.
-Additionally, any change from HOMER Pro to another simulation tool can influence the measured time to obtain results.".
+Indeed, we did not inform the impact of changing the computer setup or related issues.
+We thank the reviewer for this observation.
+We have revised our manuscript to include the following paragraph: ``Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved \textcolor{red}{what do you mean by the algorithm to be solved?}.
+Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.".
 \end{resposta}

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (5)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-1.-To clarify the figure 2, i recommend write "current" inside the figure, don't put just I.
+(1) To clarify the figure 2, i recommend write "current" inside the figure, don't put just I.
 
@@
 
-2.-This software model checking has performance in comparison the other commercials software,how is this performance?, Could you give the areas where your software performs better than commercial software?
+(2) This software model checking has performance in comparison the other commercials software,how is this performance?, Could you give the areas where your software performs better than commercial software?
 
@@
 
-3.-In text reference at figure 1 the authors do not describe all symbols drawn into image, for instances, what is means G, T.
+(3) In text reference at figure 1 the authors do not describe all symbols drawn into image, for instances, what is means G, T.
 I suspect that in section 4 they define which are the variables (Irradiation and temperature).
@@
 
-4.- Are the verification results carried out affected by the different characteristics of the computers?
+(4) Are the verification results carried out affected by the different characteristics of the computers?
 
@@
 
-The topic itself is interest for the PV application. However some section including abstract and result must be rewritten to be enhanced, here are the comments:
+(5) The topic itself is interest for the PV application. However some section including abstract and result must be rewritten to be enhanced, here are the comments:
 
@@
 \begin{resposta} 
-We appreciate the comments and we realized that our text was not clear.
-As told for the Reviewer \#2, we should highlight that our main focus was at the validation process of the solar PV system, instead of the mathematical modelling that was investigated in prior studies over the last two decades.
-Moreover, we compare the results of using automated verification with simulation tool; real PV systems were just to check the validation results presented by the two tools.
-Because the automated verification and simulation tools are intended to be used during the project, before the buying or deployment of equipment.
-This information was carefully included at the revised Abstract, Introduction and at the Conclusion sections, because we concluded that was not clear in the previous version of the paper.
+We appreciate these comments; we actually realized that our manuscript was unclear.
+We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modelling, which was already investigated in prior studies over the last two decades.
+Moreover, we compare the results of using automated verification with simulation; real PV systems were employed just to validate the results presented by both approaches (model checking and simulation).
+Note that the automated verification and simulation tools are intended to be used during the design of the PV system, i.e., before actually buying or deploying the equipment.
+This information was carefully included in the revised abstract, introduction and conclusion sections since we concluded that it was unclear in the previous version of our manuscript.
 
-The authors have real load curve, and information collected from monitoring system of four (in five) PV systems/cases, however based on the fact that the automated verification is mathematical and not visual (curves/plots), seems that is not a adequate way of comparative.
+The authors hold real load curve and information collected from monitoring system of four (in five) PV systems/cases \textcolor{red}{could you please identify them here?
+which one does not have such a information?}; however, based on the fact that the automated verification is mathematical and not visual (curves/plots), it seems that our comparison is not an adequate way \textcolor{red}{why not?
+explain the reason here}.
 
-The information from temperature and solar irradiance from every site, used to the simulation and formal verification tools, come from historical data collected from real stations that are available in Weather Base and Energy Plus web sites.
-Considering that the idea of the work is to show the effectiveness of the proposal just after the design phase, before deployment, seems that is plausible that procedure.
-Worth to mention that the sites from four case studies (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closet site with historic data).
+The information from temperature and solar irradiance from every site, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites \textcolor{red}{shall we provide the website here?}.
+Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure \textcolor{red}{to....}.
+Note that the sites from four case studies (i.e., the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest site with historical data) \textcolor{red}{what are the consequences?
+shall we state this limitation in the threats to validity section?}.
 \end{resposta}
 
--       Section 5 "Experimental Evolution" It can be changed to Verification result, otherwise the author should clarify the real measurements of the system.
+(6)      Section 5 "Experimental Evolution" It can be changed to Verification result, otherwise the author should clarify the real measurements of the system.
 
@@
 
--       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? waveforms such as: Input power, VMPP, IMPP, AC load
+(7)       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? waveforms such as: Input power, VMPP, IMPP, AC load
 

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (6)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We thank the reviewer for this comment.
-We did as suggested and changed the section title to "Verification and Simulation Results", because the results were related to verification and simulation tools only.
-The data collected from dwellers with real PV systems were used just to confirm flaws and complains about the equipment deployed at the field.
-The idea was not to present wave forms because how automated verification works it is different of simulation or testing.
+We did as suggested, i.e., we changed the section title to ``Verification and Simulation Results" since the results are related to both verification and simulation tools.
+The data collected from dwellers with real PV systems were used just to confirm flaws and complains about the equipment deployed in the field.
+The idea was not to present wave forms because how automated verification works is different from that of simulation or testing \textcolor{red}{why is it different?
+explain here...
+please do not point to the answer of another reviewer}.
 \end{resposta}

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (7)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta}
-As explained at the first question, here the authors failed in explain better the study. We appreciate one more time the comment and the opportunity to correct this issue.
 
-At the paper, we compare model checking with simulation tool.
-However how they work is completely different.
-Simulation depends on the choice of input variables (and their values) in order to obtain the output.
-In the other hand, model checking performs an automatic output search that causes the system to fails (a not expected behavior of the system) and presents the input that causes it.
-Therefore with model checking we can prove the absence of system flaws.
+We agree with the reviewer that we could further improve the explanation of our study.
+In our manuscript, we compare model checking with software simulation.
+However, the way they work is completely different.
+On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
+On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
+In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation.
+Therefore, we can prove the absence of system flaws using model checking.
+This information was included in the revised version of our manuscript in Section X \textcolor{red}{could you please describe the section here?}.
 
-When we work with waveform we are performing testing of simulation, and that is different of automated verification that is a mathematical prove (of correctness or flaw).
-Based on the fact that the authors have the five cases deployed at the field, and with monitoring system in four those PV systems, it is possible to add waveforms to the work.
-However, the use of this resource seems that is not a adequate way of comparative.
-However, we included details about the estimated load curve of each case study at the revised paper (section 4) that is represented by a vector with 24 elements (one to each hour of the day).
+When we work with waveform, we are performing testing of simulation \textcolor{red}{``testing of simulation'' sounds weird.
+Could you please explain it further here?}, and that is different of automated verification, which is a mathematical proof (of correctness or flaw).
+Based on the fact that the authors have the five cases deployed in field and with monitoring system in four those PV systems, it is possible to add waveforms to the work.
+However, the use of this resource seems that is not an adequate way of comparative \textcolor{red}{why not?
+could you please explain here?}.
+However, we included details about the estimated load curve of each case study in the revised version of our manuscript (cf.
+Section $4$), which is represented by a vector with $24$ elements (one to each hour of the day).
 \end{resposta}

### 2019-07-15 Tex/elsevier/reply Solar Energy JULY 2019.tex
solar energy revised text and reply letter

@@
 According to the associate editor and reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text.
-The revision included the Abstract, Introduction, and Results sections.
+The revision included the Abstract, Introduction, Methodology, and Results sections.
 
@@
 Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in Section X \textcolor{red}{could you please describe the section here?}.
+This information was included in the revised version of our manuscript in \textcolor{red}{Section 1 (Introduction).}
 
@@
 We have revised our manuscript to describe every employed symbol.
-The revised version of these paragraphs \textcolor{red}{in Section X} are now described as: ``A stand-alone PV system is illustrated in Fig.1.
+The revised version of these paragraphs \textcolor{red}{in Section "2.2 Component models for a stand-alone PV system"} are now described as: ``A stand-alone PV system is illustrated in Fig.1.
 The PV generator is a semiconductor device that can convert solar energy into DC electricity, with high dependence of two weather variables from the site where the system is deployed: solar irradiance $G$ and temperature $T$.
@@
 We thank the reviewer for this observation.
-We have revised our manuscript to include the following paragraph: ``Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved \textcolor{red}{what do you mean by the algorithm to be solved?}.
-Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.".
+We have revised our manuscript to include the following paragraph in Section "5.2 Objectives and Setup": "Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the \textcolor{red}{coded problem (software created by authors) to be solved.
+Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results}.".
 \end{resposta}
@@
 
-The authors hold real load curve and information collected from monitoring system of four (in five) PV systems/cases \textcolor{red}{could you please identify them here?
-which one does not have such a information?}; however, based on the fact that the automated verification is mathematical and not visual (curves/plots), it seems that our comparison is not an adequate way \textcolor{red}{why not?
-explain the reason here}.
+The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed  \textcolor{red}{at House 1, House 2, House 3 and House 4}; however, based on the fact that the automated verification is mathematical and not visual,  \textcolor{red}{(automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS analysis of coded system, with the counterexample detailing the status of the variables that cause a FAIL in the analysis), so it seems that this comparison is not adequate}.
 
-The information from temperature and solar irradiance from every site, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites \textcolor{red}{shall we provide the website here?}.
-Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure \textcolor{red}{to....}.
-Note that the sites from four case studies (i.e., the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest site with historical data) \textcolor{red}{what are the consequences?
-shall we state this limitation in the threats to validity section?}.
+The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, \textcolor{red}{as presented at Section "References"}.
+Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure \textcolor{red}{and not using weather base stations in each place.
+Even because the fact that House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data).
+Because of that, we decide to include this issue at the Section "5.4 Threats to Validity".
+We thank you for that specifically comment}.
 \end{resposta}
@@
 We did as suggested, i.e., we changed the section title to ``Verification and Simulation Results" since the results are related to both verification and simulation tools.
-The data collected from dwellers with real PV systems were used just to confirm flaws and complains about the equipment deployed in the field.
-The idea was not to present wave forms because how automated verification works is different from that of simulation or testing \textcolor{red}{why is it different?
-explain here...
-please do not point to the answer of another reviewer}.
+The data collected from dwellers with real PV systems were used just to confirm (or not) flaws and complains about the equipment deployed in the field.
+
+The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed  \textcolor{red}{at House 1, House 2, House 3 and House 4}; however, based on the fact that the automated verification is mathematical and not visual,  \textcolor{red}{(automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS analysis of coded system, with the counterexample detailing the status of the variables that cause a FAIL in the analysis, as described in Section 4 of the paper), so it seems that this comparison is not adequate}.
+
+Note that model checking and software simulations are two different techniques that use mathematical models.
+However, the way they work is completely different.
+On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
+On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
+In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation.
+Therefore, we can prove the absence of system flaws using model checking.
+This information was included in the revised version of our manuscript in \textcolor{red}{Section 1 (Introduction).}
 \end{resposta}
@@
 Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in Section X \textcolor{red}{could you please describe the section here?}.
+This information was included in the revised version of our manuscript in Section \textcolor{red}{"1 Introduction"}.
 
-When we work with waveform, we are performing testing of simulation \textcolor{red}{``testing of simulation'' sounds weird.
-Could you please explain it further here?}, and that is different of automated verification, which is a mathematical proof (of correctness or flaw).
-Based on the fact that the authors have the five cases deployed in field and with monitoring system in four those PV systems, it is possible to add waveforms to the work.
-However, the use of this resource seems that is not an adequate way of comparative \textcolor{red}{why not?
-could you please explain here?}.
-However, we included details about the estimated load curve of each case study in the revised version of our manuscript (cf.
-Section $4$), which is represented by a vector with $24$ elements (one to each hour of the day).
+When we work with waveform, we are performing \textcolor{red}{testing or simulation}, and that is different of automated verification.
+\textcolor{red}{We consider that this demand (number 7 in this Reply Letter) is related to the experimental question done by the same reviewer at item number (6).
+Therefore we expect that the explanations done at item 6, with the consequent updated paper can cover any further issue about it}.
 \end{resposta}

### 2019-07-15 Tex/elsevier/trindade_solar_energy_rev1.tex
solar energy revised text and reply letter

@@
 \textcolor{red}{Therefore the focus is in the solar photovoltaic project validation, as intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior.
-Case studies, ranging from 700 W to 1,200 W}, were used to evaluate this proposed approach and to compare that with specialized simulation tool.
+Case studies, ranging from 253 W to 814 W}, were used to evaluate this proposed approach and to compare that with specialized simulation tool.
 Different verification tools were evaluated as well, in order to compare performance and soundness among automated tools.
@@
 However how they work is completely different.
-Simulation depends on the choice of input variables (and their values) in order to obtain the output.
-In the other hand, model checking performs an automatic output search that causes the system to fails (a not expected behavior of the system) and presents the input that causes it.
-Therefore only with model checking we can prove the absence of system flaws.}
+On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
+On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
+In the latter case, if the property is violated (an unexpected behavior of the system), then the model checker presents the input that causes such a violation.
+Therefore, we can prove the absence of system flaws using model checking.}
 
@@
 Line 2 represents all the information that comes from the PV sizing and from the equipment manufacturers data: specification and data from PV, batteries, inverter and charge controller.
-This item includes as information from the house's load curve.
-
-\textcolor{red}{Those estimated load curves are converted as vectors with 24 positions, one to each house of the day (in Watts): 
+This item includes as well information from the house's load curve.
+
+\textcolor{red}{At this work, we estimated load curves based on survey and visiting performed in June of 2017, and the the estimated load curve was converted as vectors with 24 positions, one to each house of the day (in Watts):
 House 1: [118, 118, 118, 46, 46, 46, 95, 95, 170, 170, 296, 242, 242, 95, 95, 95, 95, 95, 342, 288, 288, 288, 288, 118]; 
@@
 
-\textcolor{red}{Note that the results presented here depend on the computer's processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved.
-Additionally, any change from HOMER Pro to another simulation tool can influence the measured time to obtain results.}
+\textcolor{red}{Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the coded problem (software created by authors) to be solved.
+Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.}
 
@@
 We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, we have also identified \textcolor{red}{four} threats to the validity of our results that can further be assessed.
+Nevertheless, we have also identified \textcolor{red}{five} threats to the validity of our results that can further be assessed.
 
@@
 The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification can change the comparative.}
+
+\textcolor{red}{
+\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from data bases available online.
+However, considering that riverside communities do not have weather stations, the data used at this work come from the closest municipality (Manaus in all case studies), where stations collect regularly those data.
+Therefore, the most accurate should be the use of weather stations in each location to obtain the data.}
 
@@
 \textcolor{red}{The focus was on the method to validate PV systems projects, based on formal methods that can cover the design-space better than simulation tools. 
-We have considered five case studies, ranging from $700$ W to $1,200$ W; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro).
+We have considered five case studies, ranging from \textcolor{red}{$253$ W to $814$ W}; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro).
 The results from automated verification and simulation tools were confronted with information collected from dwelles of the sites where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
@@
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
-As future work, we will also consider other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
+As future work, we will \textcolor{red} {expand the number of case studies (preferentially in different countries), and also consider} other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
 %the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems.

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (1)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Indeed, it summarizes what was intended to be studied in this manuscript.
-Additionally, we emphasize that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated by prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction and conclusion sections since we concluded that it was unclear in the previous version of our manuscript.
-Regarding Figure 2, we fixed it as indicated by the reviewer.
+Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.
+Regarding Figure 2, we fixed it as recommended by the reviewer.
 Moreover, we applied the same procedure to voltage V, in order to keep consistency throughout our manuscript.

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (2)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Hybrid2 is not supported anymore, thereby being in disuse.
-We have updated this information in our manuscript.
+We have updated this information in our manuscript \textcolor{red}{Which section?}.
 Therefore, in this particular research field (stand-alone solar PV systems), only HOMER Pro could be used for comparative purposes.
-However, in our experiments we could some general simulation tools with the same mathematical model adopted by the automated verification tool.
-However, this would represent an unfair comparison since we would need to tweak the simulation tools to prepare them for comparison purposes.
+However, in our experiments we could some general simulation tools with the same mathematical model adopted by our automated verification tool.
+However, this would represent an unfair comparison since we would need to tweak the simulation tools to prepare them for comparison purposes, which could introduce errors.
 We have described this limitation in Section 5.4 (``Threats to Validity'') in order to state that additional comparisons could be carried out with general simulation tools if they employ similar mathematical models as the ones described here.
@@
 Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in \textcolor{red}{Section 1 (Introduction).}
+This information was included in the revised version of our manuscript in Section 1 (Introduction).
 
-Importantly, model checking explores more efficiently the design-space because the system specification is based on a formal notation, which gets converted into Boolean algebra; the evaluation of variables is made automatically by a Boolean Satisfiability (SAT) solver based on the system's constraints, i.e., system information and electrical load demand transformed into properties (e.g., use defined demands and non-deterministic weather variables that do not have precise forecasting).
+Importantly, model checking explores more efficiently the design-space because the system specification is based on a formal notation, which gets converted into Boolean algebra; the evaluation of variables is made automatically by a Boolean Satisfiability (SAT) solver based on the system's constraints, i.e., system information and electrical load demand transformed into properties (e.g., use defined demands and non-deterministic variables to model the respective weather that does not have precise forecasting).
 This resulting mathematical model is submitted to full exploration of all possible states to find a configuration, where an error might occur or not.

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (3)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We have revised our manuscript to describe every employed symbol.
-The revised version of these paragraphs \textcolor{red}{in Section "2.2 Component models for a stand-alone PV system"} are now described as: ``A stand-alone PV system is illustrated in Fig.1.
-The PV generator is a semiconductor device that can convert solar energy into DC electricity, with high dependence of two weather variables from the site where the system is deployed: solar irradiance $G$ and temperature $T$.
+The revised version of these paragraphs in Section ``2.2 Component models for a stand-alone PV system'' are now described as: ``A stand-alone PV system is illustrated in Fig.1.
+The PV generator is a semiconductor device that can convert solar energy into DC electricity, with high dependence on two weather variables from the site, where the system is deployed: solar irradiance $G$ and temperature $T$.
 For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller.

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (4)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We thank the reviewer for this observation.
-We have revised our manuscript to include the following paragraph in Section "5.2 Objectives and Setup": "Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the \textcolor{red}{coded problem (software created by authors) to be solved.
-Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results}.".
+We have revised our manuscript to include the following paragraph in Section "5.2 Objectives and Setup": ``Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the implemented model (software created by the authors) to be solved.
+Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.''.
 \end{resposta}

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (5)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta} 
-We appreciate these comments; we actually realized that our manuscript was unclear.
+We appreciate these comments; we actually realized that the contributions of our manuscript were unclear.
 We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modelling, which was already investigated in prior studies over the last two decades.
@@
 Note that the automated verification and simulation tools are intended to be used during the design of the PV system, i.e., before actually buying or deploying the equipment.
-This information was carefully included in the revised abstract, introduction and conclusion sections since we concluded that it was unclear in the previous version of our manuscript.
+This information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.
 
-The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed  \textcolor{red}{at House 1, House 2, House 3 and House 4}; however, based on the fact that the automated verification is mathematical and not visual,  \textcolor{red}{(automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS analysis of coded system, with the counterexample detailing the status of the variables that cause a FAIL in the analysis), so it seems that this comparison is not adequate}.
+The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result), we understand that this comparison is not appropriate.
 
-The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, \textcolor{red}{as presented at Section "References"}.
-Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure \textcolor{red}{and not using weather base stations in each place.
-Even because the fact that House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data).
-Because of that, we decide to include this issue at the Section "5.4 Threats to Validity".
-We thank you for that specifically comment}.
+The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, as presented in our "References" section \textcolor{red}{could you please indicate the references here?
+for example, [3, 7, 10]}.
+Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure for not using weather base stations in each place since House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data).
+Because of that, we decided to add this discussion in Section ``5.4 Threats to Validity''.
+We thank you for that specific comment.
 \end{resposta}

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (6)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We thank the reviewer for this comment.
-We did as suggested, i.e., we changed the section title to ``Verification and Simulation Results" since the results are related to both verification and simulation tools.
+We implemented as suggested, i.e., we changed the section title to ``Verification and Simulation Results" since the results are related to both verification and simulation tools.
 The data collected from dwellers with real PV systems were used just to confirm (or not) flaws and complains about the equipment deployed in the field.
 
-The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed  \textcolor{red}{at House 1, House 2, House 3 and House 4}; however, based on the fact that the automated verification is mathematical and not visual,  \textcolor{red}{(automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS analysis of coded system, with the counterexample detailing the status of the variables that cause a FAIL in the analysis, as described in Section 4 of the paper), so it seems that this comparison is not adequate}.
+The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result, as described in Section 4 of our manuscript), so we understand that this comparison is not appropriate.
 
@@
 Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in \textcolor{red}{Section 1 (Introduction).}
+This information was included in the revised version of our manuscript in Section 1 (Introduction).
 \end{resposta}

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (7)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in Section \textcolor{red}{"1 Introduction"}.
+This information was included in the revised version of our manuscript in Section 1 (Introduction).
 
-When we work with waveform, we are performing \textcolor{red}{testing or simulation}, and that is different of automated verification.
-\textcolor{red}{We consider that this demand (number 7 in this Reply Letter) is related to the experimental question done by the same reviewer at item number (6).
-Therefore we expect that the explanations done at item 6, with the consequent updated paper can cover any further issue about it}.
+When we work with waveform, we are performing testing or simulation, and that is different of automated verification.
+We consider that this comment (number $7$ in this Reply Letter) is related to the experimental question done by the same reviewer in (6).
+As a result, we expect that the explanations given in (6), together with the consequent updated manuscript, can cover any further concerns about this particular issue.
 \end{resposta}

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
-In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals.
-Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
-Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-Automated verification using model checking has proven to be an effective technique to validate \textcolor{red}{complex systems}.
-This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-\textcolor{red}{Therefore the focus is in the solar photovoltaic project validation, as intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior.
-Case studies, ranging from 253 W to 814 W}, were used to evaluate this proposed approach and to compare that with specialized simulation tool.
-Different verification tools were evaluated as well, in order to compare performance and soundness among automated tools.
-\textcolor{red}{The results reported by the automated verification and by the simulation tools were compared with data collected from dwellers of the deployed cases, showing the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.}
+\textcolor{red}{With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
+In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals.
+Particular attention is given to stand-alone solar photovoltaic (PV) systems in rural areas or where grid extension is unfeasible.
+Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space.
+Automated verification using model checking has proven to be an effective technique to validate complex (state transition) systems.
+This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load.
+Our main focus is on the solar PV project validation to be carried out just after the system sizing, i.e., prior to buying the equipment and deploying it in the field, as a safe approach to ensure the intended behavior.
+Case studies, ranging from $253$ W to $814$ W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
+Different verification tools were evaluated to compare performance and soundness among automated verifiers.
+The experimental results reported by our automated verification method and by the simulation tools were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar PV system are only detailed by the automated verification method.}
 \end{abstract}
@@
 \begin{keyword}
-Formal verification \sep model checking \sep photovoltaic power systems
+Formal verification \sep model checking \sep photovoltaic power systems.
 %\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load.
-Our main focus is on the solar PV project validation to be carried out just after the system sizing, i.e., prior to buying the equipment and deploying it in the field, as a safe approach to ensure the intended behavior.
+Our main focus is on the solar PV project validation to be carried out just after the system sizing, i.e., prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior.
 Case studies, ranging from $253$ W to $814$ W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
@@
 \textcolor{red}{Note that in this study, our focus is not on a novel mathematical modelling of PV systems.
-Instead, our novelty relies on an effective approach to perform validation of PV systems using formal methods, in a process that is intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior.}
-
-\textcolor{red}{Here we compare model checking with simulation tool.
+Instead, our novelty relies on an effective approach to perform validation of PV systems using software model checking, in a process that is intended to be done just after the system sizing, prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior.}
+
+\textcolor{red}{Here we compare model checking with simulation tools.
 However how they work is completely different.

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis.
-\textcolor{red}{Hybrid2 is not supported anymore, being in disuse.} %all the tools perform solar photovoltaic analysis;
+\textcolor{red}{Hybrid2 is not supported anymore, being in disuse.} \textcolor{green}{how did you conclude that?
+explain here...} %all the tools perform solar photovoltaic analysis;
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
@@
 A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-The PV generator is a semiconductor device that can convert solar energy into DC electricity\textcolor{red}{, with high dependence of two weather variables from the site where the system is deployed: solar irradiance $G$ and temperature $T$}.
+The PV generator is a semiconductor device that can convert solar energy into DC electricity\textcolor{red}{, with high dependence on two weather variables from the site, where the system is deployed: solar irradiance $G$ and temperature $T$}.
 For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\citep{Hansen}.
@@
 The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
-\textcolor{red}{At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.}
+\textcolor{red}{In this pictured modular structure, every element produces/consumes current $I$ and voltage $V$, as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct, and $ac$ is alternating signals.}
 %

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-\textcolor{red}{It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.}
+\textcolor{red}{Note that the steps described here are carried out shortly after the design of the solar PV system, as soon as the equipment and its specifications are defined, i.e., before buying and deploying them, as a safe approach to ensure that the project will succeed.}
 
@@
 
-\textcolor{red}{At this work, we estimated load curves based on survey and visiting performed in June of 2017, and the the estimated load curve was converted as vectors with 24 positions, one to each house of the day (in Watts):
-House 1: [118, 118, 118, 46, 46, 46, 95, 95, 170, 170, 296, 242, 242, 95, 95, 95, 95, 95, 342, 288, 288, 288, 288, 118]; 
-House 2: [136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136]; 
-House 3: [113, 113, 113, 113, 113, 113, 67, 67, 217, 97, 97, 97, 97, 97, 97, 97, 97, 97, 263, 113, 113, 113, 113, 113]; 
-House 4: [207, 207, 207, 135, 135, 135, 66, 66, 161, 161, 233, 253, 248, 66, 66, 66, 66, 66, 302, 317, 322, 302, 302, 207]; 
-House 5: [45, 16, 16, 16, 16, 16, 0, 0, 0, 72, 72, 222, 150, 150, 0, 0, 72, 72, 814, 814, 814, 742, 742, 16].}
+\textcolor{red}{In our study, we estimated load curves based on survey and visiting performed in June of 2017, and the the estimated load curve was converted as vectors with 24 positions, one to each house of the day (in Watts):}
+%
+\begin{itemize} 
+\item \textcolor{red}{House 1: [118, 118, 118, 46, 46, 46, 95, 95, 170, 170, 296, 242, 242, 95, 95, 95, 95, 95, 342, 288, 288, 288, 288, 118];} 
+\item \textcolor{red}{House 2: [136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136];} 
+\item \textcolor{red}{House 3: [113, 113, 113, 113, 113, 113, 67, 67, 217, 97, 97, 97, 97, 97, 97, 97, 97, 97, 263, 113, 113, 113, 113, 113];}
+\item \textcolor{red}{House 4: [207, 207, 207, 135, 135, 135, 66, 66, 161, 161, 233, 253, 248, 66, 66, 66, 66, 66, 302, 317, 322, 302, 302, 207];} 
+\item \textcolor{red}{House 5: [45, 16, 16, 16, 16, 16, 0, 0, 0, 72, 72, 222, 150, 150, 0, 0, 72, 72, 814, 814, 814, 742, 742, 16].}
+\end{itemize}
 

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
-\textcolor{red}{Power peak, power surge and energy consumption were estimated based on visiting and survey applied in each house (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
+\textcolor{red}{Power peak, power surge, and energy consumption were estimated based on visiting and survey applied to each house (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
 
@@
 
-\textcolor{red}{Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the coded problem (software created by authors) to be solved.
+\textcolor{red}{Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the implemented model (software created by authors) to be solved.
 Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.}
@@
 \textit{Simulation Tool:} Only HOMER Pro was used.
-The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification can change the comparative.}
+The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparative.}
 
 \textcolor{red}{
-\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from data bases available online.
-However, considering that riverside communities do not have weather stations, the data used at this work come from the closest municipality (Manaus in all case studies), where stations collect regularly those data.
+\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online \textcolor{green}{cite them here?}.
+However, considering that riverside communities do not have weather stations, the data used in our study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data.
 Therefore, the most accurate should be the use of weather stations in each location to obtain the data.}

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 6
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. 
-\textcolor{red}{The focus was on the method to validate PV systems projects, based on formal methods that can cover the design-space better than simulation tools. 
+\textcolor{red}{Our main focus was on the method to validate PV system projects, based on software model checking, which can cover the design-space better than simulation tools. 
 We have considered five case studies, ranging from \textcolor{red}{$253$ W to $814$ W}; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro).
-The results from automated verification and simulation tools were confronted with information collected from dwelles of the sites where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
+The experimental results from automated verification and simulation tools were compared with information collected from dwelles of the sites, where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
 In particular, the proposed method was successful in finding sizing errors and indicating in details.

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
solar energy revised text and reply letter

@@
 Regarding Figure 2, we fixed it as recommended by the reviewer.
-Moreover, we applied the same procedure to voltage V, in order to keep consistency throughout our manuscript.
+Moreover, we applied the same procedure to voltage $V$, in order to keep consistency throughout our manuscript.
 
@@
 Hybrid2 is not supported anymore, thereby being in disuse.
-We have updated this information in our manuscript \textcolor{red}{Which section?}.
+We have updated this information in our manuscript (Section 2.1 as well).
 Therefore, in this particular research field (stand-alone solar PV systems), only HOMER Pro could be used for comparative purposes.
-However, in our experiments we could some general simulation tools with the same mathematical model adopted by our automated verification tool.
+However, in our experiments we could use some general simulation tools with the same mathematical model adopted by our automated verification tool.
 However, this would represent an unfair comparison since we would need to tweak the simulation tools to prepare them for comparison purposes, which could introduce errors.
 We have described this limitation in Section 5.4 (``Threats to Validity'') in order to state that additional comparisons could be carried out with general simulation tools if they employ similar mathematical models as the ones described here.
+Moreover, we mentioned the possibility to include this general purpose software tool comparative as future work (Section 6).
 
@@
 
-The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, as presented in our "References" section \textcolor{red}{could you please indicate the references here?
-for example, [3, 7, 10]}.
+The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, as presented in our "References" section: (Weatherbase, 2018) and (EnergyPlus, 2018).
 Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure for not using weather base stations in each place since House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data).

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
solar energy revised text and reply letter

@@
 Our main focus is on the solar PV project validation to be carried out just after the system sizing, i.e., prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior.
-Case studies, ranging from $253$ W to $814$ W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
+Case studies, ranging from $253$ W to $814$ W, were used to evaluate this proposed approach and to compare that with specialized simulation tool.
 Different verification tools were evaluated to compare performance and soundness among automated verifiers.
-The experimental results reported by our automated verification method and by the simulation tools were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar PV system are only detailed by the automated verification method.}
+The experimental results reported by our automated verification method and by the simulation tool were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar PV system are only detailed by the automated verification method.}
 \end{abstract}
@@
 As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis.
-\textcolor{red}{Hybrid2 is not supported anymore, being in disuse.} \textcolor{green}{how did you conclude that?
-explain here...} %all the tools perform solar photovoltaic analysis;
+\textcolor{red}{Hybrid2 is not supported anymore, being in disuse since that not work on Windows platforms later than Windows XP~\citep{UMASS, Pinho}.} %all the tools perform solar photovoltaic analysis;
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
@@
 We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
-\textcolor{red}{Power peak, power surge, and energy consumption were estimated based on visiting and survey applied to each house (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
+\textcolor{red}{Power peak, power surge, and energy consumption were estimated based on visiting and survey applied to each house in June 2017 (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
 
@@
 \hline
-Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah (4S)\\ autonomy: 6 h}\\
+Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah: (4S)\\ autonomy: 6 h}\\
 \hline
@@
 \hline
-\makecell{Consumption \\ kWh/day}& \textcolor{red}{3.9} & \textcolor{red}{3.6} & \textcolor{red}{2.5} & \textcolor{red}{4.3} & \textcolor{red}{4.88} \\
+\makecell{\textcolor{red}{Consumption}\\ \textcolor{red}{(kWh/day)}}& \textcolor{red}{3.9} & \textcolor{red}{3.6} & \textcolor{red}{2.5} & \textcolor{red}{4.3} & \textcolor{red}{4.88} \\
 \hline
@@
 \textcolor{red}{
-\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online \textcolor{green}{cite them here?}.
+\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online~\citep{Temperature, Irradiance}.
 However, considering that riverside communities do not have weather stations, the data used in our study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data.
-Therefore, the most accurate should be the use of weather stations in each location to obtain the data.}
+Therefore, the most accurate should be the use of weather stations in each location.}
 
@@
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
-As future work, we will \textcolor{red} {expand the number of case studies (preferentially in different countries), and also consider} other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
+As future work, we will \textcolor{red} {expand the number of case studies (preferentially in different countries), develop the code of a general purpose simulation tool to include in the comparative, and also consider} other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
 %the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems.

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1_unmarked.tex
solar energy revised text and reply letter

--- 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
@@
 \begin{abstract}
-\textcolor{red}{With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
+With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
+In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals.
+Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
+Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space.
+Automated verification using model checking has proven to be an effective technique to validate complex (state transition) systems.
+This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load.
+Our main focus is on the project validation to be carried out just after the system sizing, i.e., prior to buying equipment and deployment, as a safe approach to ensure the intended behavior.
+Five case studies were used to evaluate this proposed approach and to compare that with specialized simulation tool.
+Different verification tools were evaluated to compare performance and soundness among automated verifiers.
+The experimental results reported by our automated verification method and by the simulation tool were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar photovoltaic system are only detailed by the automated verification method.
+%With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
 In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals.
@@
 
-\textcolor{red}{Note that in this study, our focus is not on a novel mathematical modelling of PV systems.
-Instead, our novelty relies on an effective approach to perform validation of PV systems using software model checking, in a process that is intended to be done just after the system sizing, prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior.}
-
-\textcolor{red}{Here we compare model checking with simulation tools.
+Note that in this study, our focus is not on a novel mathematical modelling of PV systems.
+Instead, our novelty relies on an effective approach to perform validation of PV systems using software model checking, in a process that is intended to be done just after the system sizing, prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior.
+
+Here we compare model checking with simulation tools.
 However how they work is completely different.
@@
 In the latter case, if the property is violated (an unexpected behavior of the system), then the model checker presents the input that causes such a violation.
-Therefore, we can prove the absence of system flaws using model checking.}
+Therefore, we can prove the absence of system flaws using model checking.
 
@@
 As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis.
-\textcolor{red}{Hybrid2 is not supported anymore, being in disuse since that not work on Windows platforms later than Windows XP~\citep{UMASS, Pinho}.} %all the tools perform solar photovoltaic analysis;
+Hybrid2 is not supported anymore, being in disuse since that not work on Windows platforms later than Windows XP~\citep{UMASS, Pinho}.
+%all the tools perform solar photovoltaic analysis;
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
@@
 A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-The PV generator is a semiconductor device that can convert solar energy into DC electricity\textcolor{red}{, with high dependence on two weather variables from the site, where the system is deployed: solar irradiance $G$ and temperature $T$}.
+The PV generator is a semiconductor device that can convert solar energy into DC electricity, with high dependence on two weather variables from the site, where the system is deployed: solar irradiance $G$ and temperature $T$.
 For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\citep{Hansen}.
@@
 The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
-\textcolor{red}{In this pictured modular structure, every element produces/consumes current $I$ and voltage $V$, as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct, and $ac$ is alternating signals.}
+In this pictured modular structure, every element produces/consumes current $I$ and voltage $V$, as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct, and $ac$ is alternating signals.
 %
@@
 \centering
-\caption{\textcolor{red}{Block diagram for a typical stand-alone PV system, adapted from~\citep{Hansen}}.}
+\caption{Block diagram for a typical stand-alone PV system, adapted from~\citep{Hansen}.}
 \label{fig:blockdiagram}
@@
 \centering
-\caption{\textcolor{red}{1-diode equivalent PV cell/panel circuit model, adapted from~\citep{Cubas}.}}
+\caption{1-diode equivalent PV cell/panel circuit model, adapted from~\citep{Cubas}.}
 %\caption{Four different equivalent circuit models: (a) 1-diode; (b) 1-diode/1-resistor; (c) 1-diode/2-resistor; (d) 2-diode/2-resistor (Source: \cite{Cubas})}
@@
 %
-\textcolor{red}{Note that the steps described here are carried out shortly after the design of the solar PV system, as soon as the equipment and its specifications are defined, i.e., before buying and deploying them, as a safe approach to ensure that the project will succeed.}
+Note that the steps described here are carried out shortly after the design of the solar PV system, as soon as the equipment and its specifications are defined, i.e., before buying and deploying them, as a safe approach to ensure that the project will succeed.
 
@@
 
-In Step 1, the PV input data \textcolor{red}{(e.g., load power demand and load energy consumption)} 
+In Step 1, the PV input data (e.g., load power demand and load energy consumption) 
 and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\citep{ANSI2018}.
@@
 
-\textcolor{red}{In our study, we estimated load curves based on survey and visiting performed in June of 2017, and the the estimated load curve was converted as vectors with 24 positions, one to each house of the day (in Watts):}
+In our study, we estimated load curves based on survey and visiting performed in June of 2017, and the the estimated load curve was converted as vectors with 24 positions, one to each house of the day (in Watts):
 %
 \begin{itemize} 
-\item \textcolor{red}{House 1: [118, 118, 118, 46, 46, 46, 95, 95, 170, 170, 296, 242, 242, 95, 95, 95, 95, 95, 342, 288, 288, 288, 288, 118];} 
-\item \textcolor{red}{House 2: [136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136];} 
-\item \textcolor{red}{House 3: [113, 113, 113, 113, 113, 113, 67, 67, 217, 97, 97, 97, 97, 97, 97, 97, 97, 97, 263, 113, 113, 113, 113, 113];}
-\item \textcolor{red}{House 4: [207, 207, 207, 135, 135, 135, 66, 66, 161, 161, 233, 253, 248, 66, 66, 66, 66, 66, 302, 317, 322, 302, 302, 207];} 
-\item \textcolor{red}{House 5: [45, 16, 16, 16, 16, 16, 0, 0, 0, 72, 72, 222, 150, 150, 0, 0, 72, 72, 814, 814, 814, 742, 742, 16].}
+\item House 1: [118, 118, 118, 46, 46, 46, 95, 95, 170, 170, 296, 242, 242, 95, 95, 95, 95, 95, 342, 288, 288, 288, 288, 118];
+\item House 2: [136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136]; 
+\item House 3: [113, 113, 113, 113, 113, 113, 67, 67, 217, 97, 97, 97, 97, 97, 97, 97, 97, 97, 263, 113, 113, 113, 113, 113];
+\item House 4: [207, 207, 207, 135, 135, 135, 66, 66, 161, 161, 233, 253, 248, 66, 66, 66, 66, 66, 302, 317, 322, 302, 302, 207]; 
+\item House 5: [45, 16, 16, 16, 16, 16, 0, 0, 0, 72, 72, 222, 150, 150, 0, 0, 72, 72, 814, 814, 814, 742, 742, 16].
 \end{itemize}
@@
 %----------------------------------------------
-\section{\textcolor{red}{Verification and Simulation Results}} 
+\section{Verification and Simulation Results} 
 \label{sec:results}
@@
 We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
-\textcolor{red}{Power peak, power surge, and energy consumption were estimated based on visiting and survey applied to each house in June 2017 (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
+Power peak, power surge, and energy consumption were estimated based on visiting and survey applied to each house in June 2017 (before the electrification).
+%Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
 
@@
 \hline
-\textcolor{red}{Power peak (W)}& 342  & 253  & 263 & 322 & 814 \\
-\hline
-\textcolor{red}{Power surge (W)}& 342 & 722 & 732 & 896 & 980\\
-\hline
-\makecell{\textcolor{red}{Consumption}\\ \textcolor{red}{(kWh/day)}}& \textcolor{red}{3.9} & \textcolor{red}{3.6} & \textcolor{red}{2.5} & \textcolor{red}{4.3} & \textcolor{red}{4.88} \\
+Power peak (W)& 342  & 253  & 263 & 322 & 814 \\
+\hline
+Power surge (W)& 342 & 722 & 732 & 896 & 980\\
+\hline
+\makecell{Consumption\\(kWh/day)}& 3.9 & 3.6 & 2.5 & 4.3 & 4.88 \\
 \hline
@@
 \end{tabular}
-\textcolor{red}{Legend: (S): Series; (P): Parallel.}
+Legend: (S): Series; (P): Parallel.
 \end{scriptsize}
@@
 %------------------------------------------
-\textcolor{red}{We aim} to answer two research questions:
+We aim to answer two research questions:
 %
@@
 
-\textcolor{red}{Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the implemented model (software created by authors) to be solved.
-Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.}
+Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the implemented model (software created by authors) to be solved.
+Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.
 
@@
 We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, we have also identified \textcolor{red}{five} threats to the validity of our results that can further be assessed.
+Nevertheless, we have also identified five threats to the validity of our results that can further be assessed.
 
@@
 
-\textcolor{red}{
 \textit{Simulation Tool:} Only HOMER Pro was used.
-The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparative.}
-
-\textcolor{red}{
+The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparative.
+
 \textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online~\citep{Temperature, Irradiance}.
 However, considering that riverside communities do not have weather stations, the data used in our study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data.
-Therefore, the most accurate should be the use of weather stations in each location.}
+Therefore, the most accurate should be the use of weather stations in each location.
 
@@
 We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. 
-\textcolor{red}{Our main focus was on the method to validate PV system projects, based on software model checking, which can cover the design-space better than simulation tools. 
-We have considered five case studies, ranging from \textcolor{red}{$253$ W to $814$ W}; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro).
-The experimental results from automated verification and simulation tools were compared with information collected from dwelles of the sites, where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
+Our main focus was on the method to validate PV system projects, based on software model checking, which can cover the design-space better than simulation tools. 
+We have considered five case studies, ranging from $253$ W to $814$ W; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro).
+The experimental results from automated verification and simulation tools were compared with information collected from dwelles of the sites, where the real PV systems were deployed.
+Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
 In particular, the proposed method was successful in finding sizing errors and indicating in details.
@@
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
-As future work, we will \textcolor{red} {expand the number of case studies (preferentially in different countries), develop the code of a general purpose simulation tool to include in the comparative, and also consider} other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
+As future work, we will expand the number of case studies (preferentially in different countries), develop the code of a general purpose simulation tool to include in the comparative, and also consider other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
 %the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems.

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
solar energy revised text

@@
 \usepackage{lineno,hyperref}
-%\modulolinenumbers[1]
-%\linenumbers
+\modulolinenumbers[1]
+\linenumbers
 
@@
 \textcolor{red}{With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
+In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals.
+Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
+Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space.
+Automated verification using model checking has proven to be an effective technique to validate complex (state transition) systems.
+This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load.
+Our main focus is on the project validation to be carried out just after the system sizing, i.e., prior to buying equipment and deployment, as a safe approach to ensure the intended behavior.
+Five case studies were used to evaluate this proposed approach and to compare that with specialized simulation tool.
+Different verification tools were evaluated to compare performance and soundness among automated verifiers.
+The results reported by our automated verification method and by the simulation tool were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar photovoltaic system are only detailed by the automated verification method.}
+%With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
 In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals.

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1_unmarked.tex
solar energy revised text

@@
 Different verification tools were evaluated to compare performance and soundness among automated verifiers.
-The experimental results reported by our automated verification method and by the simulation tool were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar photovoltaic system are only detailed by the automated verification method.
+The results reported by our automated verification method and by the simulation tool were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar photovoltaic system are only detailed by the automated verification method.
 %With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{red}{Note that in this study, our focus is not on a novel mathematical modelling of PV systems.
+\textcolor{red}{Note that in this study, our focus is not on a novel mathematical modeling of PV systems.
 Instead, our novelty relies on an effective approach to perform validation of PV systems using software model checking, in a process that is intended to be done just after the system sizing, prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior.}
@@
 
-The most popular softwares are summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\citep{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
+The most popular software tools are summarized in Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\citep{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.
 %\subsection{PVWatts Calculator}
@@
 
-\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
+\noindent where $I_{ph}$ is the photo-current delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration);
 $a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}\:J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}\:C $).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\citep{esbmc2018}, which supports the verification of LTL properties with bounded traces~\citep{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\citep{esbmc2018}, which supports the verification of Linear-time Temporal Logic (LTL) properties with bounded traces~\citep{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) pre-processing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
 ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\citep{Morse2015}.
@@
 We have considered five case studies, ranging from \textcolor{red}{$253$ W to $814$ W}; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro).
-The experimental results from automated verification and simulation tools were compared with information collected from dwelles of the sites, where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
+The experimental results from automated verification and simulation tools were compared with information collected from dwellers of the sites, where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
 In particular, the proposed method was successful in finding sizing errors and indicating in details.

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta} 
-We thank the reviewer fot this insightful comment.
+We thank the reviewer for this insightful comment.
 Indeed, it summarizes what was intended to be studied in this manuscript.
-Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.
+Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modeling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.
 Regarding Figure 2, we fixed it as recommended by the reviewer.
@@
 We appreciate these comments; we actually realized that the contributions of our manuscript were unclear.
-We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modelling, which was already investigated in prior studies over the last two decades.
+We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modeling, which was already investigated in prior studies over the last two decades.
 Moreover, we compare the results of using automated verification with simulation; real PV systems were employed just to validate the results presented by both approaches (model checking and simulation).
@@
 
-The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result), we understand that this comparison is not appropriate.
+The authors hold real load curve and information collected from monitoring system using Raspberry Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result), we understand that this comparison is not appropriate.
 
@@
 
-The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result, as described in Section 4 of our manuscript), so we understand that this comparison is not appropriate.
+The authors hold real load curve and information collected from monitoring system using Raspberry Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result, as described in Section 4 of our manuscript), so we understand that this comparison is not appropriate.
 
@@
 
-(7)       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? waveforms such as: Input power, VMPP, IMPP, AC load
+(7)       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? wave-forms such as: Input power, VMPP, IMPP, AC load
 

### 2019-07-16 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 
+Worth to mention that, specifically to PV systems used in Brazil, there is a Normative Resolution issued by the Brazil National Electric Energy Agency (Aneel) that establishes the minimum of 48 hours of battery autonomy to stand-alone solar PV systems (RN 493/2012), among others definitions related to this matter.
+
 \subsubsection{Controller Model}
@@
 
-%
 %--------------------------------------------------
@@
 
-\textcolor{red}{Number of inverters???? XXXXXXXXXXX}
+Some models of inverters allow parallel operation of more than one unit, besides the integration in order to create bi-phase and three-phase circuits.
+It is advised the use of pure sine wave inverter, especially for cases where are used electronic loads sensitive to harmonic distortion waves.
+
+Moreover, it is important to verify the compatibility between charge controller and inverter, because there are some models that do not accept to work with brands of different manufacturers.
 
@@
 \section{Summary}
+
+At this Section, all the background and theoretical base needed to understand the concepts, techniques, tools, and criteria used during the following Sections were presented.
+
+A historical explanation about the origin of the formal methods until to reach modern model checkers was presented.
+It was highlighted the importance of computers evolution in order to allow the automation of formal verification.
+If we were stuck in time, probably the formal verification was being made by hand until nowadays.
+
+Is was pointed out the importance of mathematical rigor to the models and representation of systems, and that automated verification can be applied to any kind of systems (from simple ones to the complex ones)
+
+State-of-art automated verification tools were described with relation to their characteristics and techniques.
+Simulation tools were described as well and the reason why HOMER Pro was the one chosen to the comparative.
+
+It was explained how to validate a system, comparing test, simulation and automated verification techniques.
+It was possible to demonstrate that only automated verification can prove the absence of system flaws.
+
+The method of critical period solar energy method was presented as the chosen one for sizing solar PV systems.
+Following, the criteria and techniques for optimal sizing of PV systems were highlighted as well.

### 2019-07-17 Tex/Old text/chapters/chapter03.tex
thesis updated text

@@
-\section{Intro}
+%\section{Introduction}
+%
+In this Chapter, the adopted methodologies to perform formal verification and optimal sizing of stand-alone solar PV systems using formal methods, more specifically model checking, will be detailed.
+Besides that, all the assumptions and premises adopted are presented as well with direct impact in the results and conclusions of this work.
 
-Introduction text here
+It is important to emphasize that the whole explanation about the theoretical basis of the two subjects discussed here are present in the previous chapter.
+In addition, the author suggests that previous reading be done to facilitate understanding.
 
-\section{Automated Verification}
+\section{Automated Verification of Solar PV Systems}
 The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
@@
 
-In Step 1, the PV input data %(e.g., load power demand and load energy consumption) 
-and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
-In Step 2, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
+In \textbf{Step 1}, the PV input data %(e.g., load power demand and load energy consumption) 
+and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}. In
+
+\textbf{Step 2}, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
 This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.
-%
-In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
+
+In \textbf{Step 3}, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
 %As a consequence, all the formulae of the employed mathematical models will also be updated. 
@@
 is it SAT?}
-In a nutshell, the model checker will process the ANSI-C code with constraints %($C$) 
-and properties %($P$) 
-from the PV system, and the tool will automatically verify if the PV system requirements are met.
+In a nutshell, the model checker will process the ANSI-C code with constraints ($C$) and properties ($P$) from the PV system, and the tool will automatically verify if the PV system requirements are met.
 If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
@@
 We use annual average minimum and maximum, related to temperature ($T$) and solar irradiance ($G$), hour by hour, from~\cite{Temperature}, and ~\cite{Irradiance}.
+
+Premise 1:
 
@@
 
- /////////////
- \section{Optimization}
+ \section{Optimal Sizing of Solar PV Systems}
 
-\subsection{Variant CEGIS}
+\subsection{Variant of CEGIS}
 
-In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS. This variant was created during this Thesis.
+In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section \textcolor{red}{XXX}. This variant was created during this Thesis.
 
@@
 
-\section{Assumptions and Premises}
+\subsection{Optimization Assumptions and Premises}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A premise is a stated reason or evidence that supports the conclusion. 
+An assumption is an unstated premise that supports the conclusion. 
+Both premise and assumption are unquestionable facts but the assumption, unlike the premise, is not explicitly stated and needs to be deciphered.
 

### 2019-07-18 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{systemverif}
+\includegraphics[width=0.8\textwidth]{systemverif3}
 \centering
@@
 However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-That configuration is the focus of the present thesis since it is the most common nowadays all over the world, when off-grid or isolated regions is the target.
-\textcolor{red} { Alternative???
-Specifically for remote rural areas of developing countries or places where the grid extension is not feasible,}
+That configuration is the focus of the present Thesis since it is the most common nowadays specifically for remote rural areas of developing countries or places where the grid extension is not feasible.
 %stand-alone systems are one the most used solutions, and 
@@
 %can be split into several categories. However, 
-the most suitable configuration is the regulated stand-alone system with battery and AC load.
+%the most suitable configuration is the regulated stand-alone system with battery and AC load.
 
@@
 \begin{figure}[h]
-\includegraphics[width=0.90\textwidth]{ivcurve}
+\includegraphics[width=0.7\textwidth]{ivcurve}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{batteryckt}
+\includegraphics[width=0.5\textwidth]{batteryckt}
 \centering
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Summary of the controller process. Source: \cite{Hansen}.}
+\caption{Summary of the controller process. Source: adapted from~\cite{Hansen}}
 \label{table:controller}
@@
 \hline
-(1) & \makecell{If $V > V_{max \textunderscore off}$ and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array from the system}\\
+(1) & \makecell{If $V > V_{max \_ off}$ \\and $I_{load} < I_{pv}$} & \makecell{Disconnect PV array \\from the system}\\
 \hline
-(2) & \makecell{If command (1) is done and $V < V_{max \textunderscore on}$} & \makecell{Reconnect PV array to the system}\\
+(2) & \makecell{If command (1) is \\done and $V < V_{max \_ on}$} & \makecell{Reconnect PV array \\to the system}\\
 \hline
-(3) & \makecell{If $V < V_{min \textunderscore off}$ and $I_{load} > I_{pv}$} & \makecell{Disconnect the load from the system}\\
+(3) & \makecell{If $V < V_{min \_ off}$ and \\ $I_{load} > I_{pv}$} & \makecell{Disconnect the load \\from the system}\\
 \hline
-(4) & \makecell{If command (3) is done and $V > V_{min \textunderscore on}$} & \makecell{Reconnect the load to the system}\\
+(4) & \makecell{If command (3) is \\ done and $V > V_{min \_ on}$} & \makecell{Reconnect the load \\to the system}\\
 \hline

### 2019-07-18 Tex/Old text/chapters/chapter03.tex
thesis updated text

@@
 \section{Automated Verification of Solar PV Systems}
+
+The Fig. \ref{fig:systemverif3} shows the process to convert a real solar PV system to a model in order to be verified by a model checking.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{systemverif4}
+\centering
+\caption{From real solar PV system verification to model checking. Source: adapted from \cite{Clarke2008}.}
+\label{fig:systemverif3}
+\end{figure}
+
 The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.

### 2019-07-19 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 \subsubsection{Controller Model}
+\label{sec:controller}
 Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.

### 2019-07-19 Tex/Old text/chapters/chapter03.tex
thesis updated text

@@
 
-The Fig. \ref{fig:systemverif3} shows the process to convert a real solar PV system to a model in order to be verified by a model checking.
+Fig.~\ref{fig:validation} illustrates how a stand-alone solar PV project can be validated, passing through the traditional techniques, as manual, simulation, testing, and including the proposed automatic verification that is detailed in this Section.
+Note that, in one hand, the input information is the same for all the techniques, with the difference that in automated validation it is possible to define the bound $k$ to restrict the space-design search.
+However, in the other hand, the outputs are not equal, as the design-space coverage and the information presented as result.
+
+\begin{figure}[h]
+\includegraphics[width=1.0\textwidth]{PVprojectvalidation}
+\centering
+\caption{Comparative of project validation methods}
+\label{fig:validation}
+\end{figure}
+
+Starting at his point, it will be showed how is done the automated verification.
+
+The process begins with the conversion of the real PV system into a model.
+The Fig.
+\ref{fig:systemverif4} shows the process to convert a real solar PV system to a model in order to be verified by a model checking.
+
+This illustration is a adaption from the general process of real system conversion depicted in Fig.~\ref{fig:systemverif}, detailing the inputs, outputs, and requirements of a real solar PV system.
+
+Worth to mention that the model checking process is the same independently of the system that is validated, and the important is to chose a accurate model, to define the requirements/constraints, and to get correct information from the system components, in order to get sound and effective validation,
 
@@
 \caption{From real solar PV system verification to model checking. Source: adapted from \cite{Clarke2008}.}
-\label{fig:systemverif3}
+\label{fig:systemverif4}
 \end{figure}
 
-The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
+Moreover, the proposed flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
+Those three steps are the high level description of how the automated verification, applied to solar PV systems, works.
 
@@
 In \textbf{Step 1}, the PV input data %(e.g., load power demand and load energy consumption) 
-and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}. In
+and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
 
-\textbf{Step 2}, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
+\textbf{Assumption:} All the PV system model, user requirements, assumptions, and technical information from the PV system equipment is written as an ANSI-C code.
+
+In \textbf{Step 2}, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
 This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.
+
+\textbf{Assumption:} before the automated verification, who performs the verification of the intended system behavior, is performed the sizing checking of the system.
+Moreover, if there is some error, the process stops, showing where is the sizing error.
+
+\textbf{Assumption:} Sizing check is performed using critical period criteria.
 
@@
 However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
+
+\textbf{Assumption:} Use of bound $k$ to restrict the design-space and improve performance.
+
 %, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
@@
 
+\textbf{Assumption:} day is divided in two parts (when there is and there is not PV generation, based in historical data from the location).
+Considering average temperature and solar irradiance (for every hour of the day) and the annual solar insolation (per day).
+
 Lines 1 is devoted to information from the location where the PV system will be/were deployed.
@@
 
-Premise 1:
+\textbf{Premise:} The availability of temperature, solar irradiance, and solar insolation data from the location where the solar PV system will be used.
 
@@
 This item includes as information from the house's load curve.
+
+\textbf{Premise:} Availability of data sheet from every element of the solar PV system to be validated.
+
+\textbf{Premise:} It is necessary the detailed sized project of the PV system in order to perform the validation (list of equipment and configuration, as voltage, current and how they are connected).
+
+\textbf{Assumption:} Load curve from every house must be estimated or measured.
+Moreover, the time step is of 1 hour, and it is not considered seasonality, i.e., the load curve is the same for the entire year.
 
@@
 The batteries are assumed to be charged, i.e., with SOC of 100\% (line 6).
+
+\textbf{Assumption:} Batteries are considered charged at the beginning of the project validation.
 
@@
 After that, the model from PV generator is used in the function call of line 17, to produce the voltage and current considering the states of $G$ and $T$.
-With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller work, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller work as depicted in Table~\ref{table:controller} of Section~\ref{sec:controller}, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
 
@@
  \begin{algorithm}
- \caption{Model checking algorithm for stand-alone PV}
+ \caption{Model checking algorithm for validation of stand-alone PV systems}
  \begin{algorithmic}[1]
@@
 
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual, and simulation), and including the proposed automatic synthesis that is detailed in this Section.
+
+One more time, as depicted in automated verification process, the input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search.
+And the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.
+
+\begin{figure}[h]
+\includegraphics[width=1.0\textwidth]{optimalsizingprocess}
+\centering
+\caption{Comparative of optimal sizing methods}
+\label{fig:optimization}
+\end{figure}
+
 \subsection{Variant of CEGIS}
 
-In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section \textcolor{red}{XXX}. This variant was created during this Thesis.
+In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section ~\ref{sec:ProgramSynthesis}, Fig.~\ref{Counter-Example-Guided-Inductive-Synthesis}.
+This variant was created during this Thesis and it will be detailed in this Section.
 
@@
 
-Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+Examples of specification used by the proposed method include solar insolation (site dependent), house power demand, house consumption energy, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+Design assumptions are considered project specification as well.
+The assumptions regarding the optimal sizing are listed in Section~\ref{sec:OptAssumptions}.
 
------------
-
-There are four particular differences related to the traditional CEGIS described in Figure XX:
+There are four particular differences related to the traditional CEGIS described in Figure ~\ref{Counter-Example-Guided-Inductive-Synthesis} when compared to the variant CEGIS used in the proposed approach:
 
@@
 \subsection{Optimization Assumptions and Premises}
+\label{sec:OptAssumptions}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-07-20 Tex/Old text/chapters/chapter03.tex
thesis updated text

@@
 In this Chapter, the adopted methodologies to perform formal verification and optimal sizing of stand-alone solar PV systems using formal methods, more specifically model checking, will be detailed.
-Besides that, all the assumptions and premises adopted are presented as well with direct impact in the results and conclusions of this work.
+Diagrams, flowcharts, and algorithms support and explain the solutions.
+
+Besides that, all the assumptions and premises adopted are presented.
+Both support the results/conclusions, with direct impact on it.
+Usually, a premise is an unquestionable fact, however assumptions can be questionable.
+Unlike the premise, assumptions are not explicitly stated and need to be deciphered.
+With that in mind, a detailed explanation of assumptions is performed for all over this Chapter.
 
@@
 Fig.~\ref{fig:validation} illustrates how a stand-alone solar PV project can be validated, passing through the traditional techniques, as manual, simulation, testing, and including the proposed automatic verification that is detailed in this Section.
+
 Note that, in one hand, the input information is the same for all the techniques, with the difference that in automated validation it is possible to define the bound $k$ to restrict the space-design search.
+Among the inputs it is possible to list: location weather data (temperature, solar irradiance, and solar insolation); system sizing information regarding specifications and configuration of PV panels, charge controller, inverter, batteries, DC bus  voltage; and requirements (battery autonomy, electric load demand, electric peak power demand, energy consumption, load curve, and AC voltage).
+
 However, in the other hand, the outputs are not equal, as the design-space coverage and the information presented as result.
+Regarding the design-space, it was shown in  chapter \nameref{chap:background} that the most complete coverage is performed by automated verification, event using the bound $k$ to restrict the search, because is not necessary to unbound completely the system in order to found a design flaw.
+Moreover, testing and simulation depends on the test vector used as input to evaluate the system.
+
+About the results presented by the methods, a project validation done 'by hand' is just a piece of paper produced; simulation software produce fail, success information and can additionally to present the optimized design if the evaluated has some flaw, with graphics and reports; testing (using laboratory or field) is done using measurement equipment and/or data from monitoring systems.
+Automated verification, proposed at this Thesis, presents fail, success information as well, however the output is not graphical (as will be shown in the  \autoref{chap:automatedverification}), summarized by reports with details about the variables and states of the project that causes a project flaw (in the case where is detected a design fail).
 
 \begin{figure}[h]
-\includegraphics[width=1.0\textwidth]{PVprojectvalidation}
+\includegraphics[width=1.0\textwidth]{PVprojectvalidation2}
 \centering
@@
 
-Starting at his point, it will be showed how is done the automated verification.
+Starting at his point, it will be showed how is done the proposed automated verification of stand-alone solar PV systems.
 
@@
 The Fig.
-\ref{fig:systemverif4} shows the process to convert a real solar PV system to a model in order to be verified by a model checking.
+\ref{fig:systemverif4} shows how a real solar PV system is equivalent and converted to a model in order to be verified by a model checking.
 
@@
 The first automated verification is related to the sizing check (line 3), if an error is found then the algorithm stops.
-Then two functions, called at lines 4 and 5, are responsible for discover which hour starts the PV generation and when stops.
+In order to perform the sizing check, the algorithm uses Equations \eqref{eq:NTPmin}, \eqref{eq:NPSmin}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
+
+Then, if there is not a sizing design flaw, two functions, called at lines 4 and 5, are responsible for discover which hour starts the PV generation and when stops.
 Those functions get this information from the array inputted to the Algorithm with the solar irradiance values.
@@
 
+%\subsubsection{Assumptions and Premises} 
+%
+
 \section{Optimal Sizing of Solar PV Systems}
@@
 \begin{figure}[h]
-\includegraphics[width=1.0\textwidth]{optimalsizingprocess}
+\includegraphics[width=1.0\textwidth]{optimalsizingprocess2}
 \centering
@@
 Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
-Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} t
-o calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
+Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
 ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
 uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$.
+Line $15$ is specific to the charge controller voltage check.
+Line $18$ checks the inverter check $I_{c}$, charge controller DC input voltage $V_{in}DC$, and charge controller AC output voltage $V_{in}DC$ check.
+Line $19$ ensures the power demand and the surge power of inverter.
 Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
-and the cost of that solution is calculated in $F_{obj}$ (line $21$).
+and the cost of that solution is calculated in $F_{obj}$ (line $21$). This cost is the equivalent of ~\ref{eq:LCC} described in Section ~\ref{sec:optcriteria}.
 
@@
 
-Note that the process described here in completely automated and that a validation is performed 
+Note that the process described here is completely automated and that a validation is performed 
 by our {\sc Verify} phase to ensure that the approach is sound.
@@
 
-A premise is a stated reason or evidence that supports the conclusion. 
-An assumption is an unstated premise that supports the conclusion. 
-Both premise and assumption are unquestionable facts but the assumption, unlike the premise, is not explicitly stated and needs to be deciphered.
+Here some premise are presented and some adopted assumptions are explained for the optimal sizing method, regarding the automated synthesis and simulation software.
 
@@
 \begin{itemize}
-	\item HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER};
 	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
@@
 \section{Conclusion}
+
+This Chapter showed in details how the automated verification method and the automated synthesis method, two state-of-art tools used in computer science, were adapted in order to be used in stand-alone solar PV systems to validate their behavior or the obtain the optimal project sizing.
+Moreover, is was possible to picture how the proposed methods are compared with the traditional ones used for the same purpose.
+
+Detailed diagrams, flowcharts and algorithms with pseudo-code were presented with the aim to support the proposed work and to facilitate the understanding.
+And even more so, the assumptions adopted for the automated verification and simulation software were listed, because those assumptions have impact at the results there will be presented at the next two Chapters.

### 2019-07-20 Tex/Old text/chapters/chapter03.tex
thesis updated text

@@
 
-\textbf{Assumption:} All the PV system model, user requirements, assumptions, and technical information from the PV system equipment is written as an ANSI-C code.
-
 In \textbf{Step 2}, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
@@
 However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
-
-\textbf{Assumption:} Use of bound $k$ to restrict the design-space and improve performance.
 
@@
 
-Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, 
+Regarding the line $2$ of Algorithm~\ref{alg:opt-algorithm}, 
 a list of forty equipment from ten different manufacturers was provided 
@@
 
-Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
+Regarding batteries, the voltage of the system (DC bus) is set in $24$ V DC (but the value can be adjusted to $12$ or $48$ V at the code).
 
-Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
 Related to HOMER Pro:
@@
 
+\section{General Assumptions}
+
+Here is listed the assumptions adopted for both methods developed on this Thesis.
+
+Regarding the code in ANSI-C created to perform both methods, automated verification and automated synthesis, it was written in order to be the same independently of the verifier used.
+This means that:
+
+\begin{itemize}
+\item There is not the use of '\# include' preprocessor directive, so common in the C language, which allows the use of language C libraries, including the mathematical one;
+\item Because of absence of '\# include' directive, it was necessary to create specific mathematical functions at the proposed code in order to calculate the exponential 'exp(x)' or $e^{x}$, and natural logarithm 'log(x)' functions, used for the solar PV model;
+\item There is not the presence of '\# define' preprocessor directive. Therefore were used global variables to replace it;
+\item The macro 'assert (expression);' must be replaced by 'if (!expression) \{ \_ \_ VERIFIER\_ error();\}'
+\item The macro 'assume (expression);' must be replaced by '\_ \_ VERIFIER\_ assume(expression)';
+\item It is not possible to use the \# if, \# else, \# elif, \# endif or \# ifdef, \# ifndef commands.
+\end{itemize}
+
+Regarding the automated verification and automated synthesis methods:
+
+\begin{itemize}
+\item It was used a value of bound $k$ to restrict the design-space and improve performance. The chose of value was empirical, after some tests with the code;
+\item All the PV system model, user requirements, assumptions, and technical information from the PV system equipment are written as an ANSI-C code.
+\end{itemize}
+
+Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
+Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis, however RETScreen do not have stand-alone solar PV system analysis capacity.
+Therefore, in this study, HOMER Pro will be the only simulation tool used to compare with our automated synthesis method.
+
+Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\%, i.e., with DOD maximum of $25$\%, which is common to lead-acid batteries (adopted as standard here), and the AC voltage from the inverter is $127$ V (Brazilian standard).
+
 \section{Conclusion}

### 2019-07-20 Tex/Old text/chapters/chapter05.tex
thesis updated text

@@
-\section{Intro to Automated Formal Synthesis Optimization}
+%\section{Intro to Automated Formal Synthesis Optimization}
 This section presents the case studies used to evaluate our proposed approach. 
@@
 Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
-%
+
 \begin{table}
@@
 %---------------------------------------------------------------------------
-\section{Tools} 
-%---------------------------------------------------------------------------
-
-Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
-The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
-
-%---------------------------------------------------------------------------
-\section{Setup} 
-%---------------------------------------------------------------------------
-
-All experiments regarding the verification tools were conducted 
-on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
-$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
-Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
-with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
-Our experiments were performed with a predefined timeout of $240$ minutes.
-
-%---------------------------------------------------------------------------
-\section{Objectives} 
+\section{Objectives and Setup} 
 %---------------------------------------------------------------------------
@@
 
+All experiments regarding the verification tools were conducted 
+on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
+$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
+Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
+with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
+Our experiments were performed with a predefined timeout of $240$ minutes.
+
+Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
+Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
+The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
+
+\section{Verifiers and HOMER Pro Environments}
+
+The environment and captured screens are the same as presented in Section~\ref{sec:verifenviron} for the verifiers and in Section~\ref{sec:homerenviron} for the HOMER Pro tools.
+
 %---------------------------------------------------------------------------
-\
-section{Results}  
+\section{Results}  
 %---------------------------------------------------------------------------

### 2019-07-21 Tex/Old text/chapters/chapter04.tex
thesis updated text

@@
-\section{Intro to Automated Verification Experimental Evaluation}
+This Chapter is devoted to the results of using automated verification to validate the intended behavior of stand-alone solar PV systems.
+Moreover, there is the comparative with a specialized simulation tool, and even the use of different verifiers who perform the automated verification in order to evaluate performance.
 
-Intro text here
-
------------------------------------------
 \section{Description of the Case Studies}
@@
 %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
+These case studies were defined 
+based on usual electrical load found in riverside communities of the 
+Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+
 \begin{table}
@@
 \end{table}
+
 %------------------------------------------
@@
 All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
-The setup of HOMER Pro v3.12.0: Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
-The experiments were performed with timeout of 14,400 seconds.
+The setup of HOMER Pro v3.13.1 was an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
+The experiments were performed with timeout of 240 minutes.
 
@@
 Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
-An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness.
+An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness in the results (so it is not reported here).
 % enabled with the goal of reducing memory usage; 
  %The experiments were performed without a predefined timeout.
+
+\section{Verifiers Environment}
+\label{sec:verifenviron}
+
+Screens and comments about the verifiers.
+
+\subsubsection{CBMC}
+
+\subsubsection{ESBMC}
+
+\subsubsection{CPAchecker}
+
+\section{HOMER Pro Environment}
+\label{sec:homerenviron}
+
+Screens and comments about the simulation tool.
 

### 2019-07-21 Tex/Old text/chapters/chapter05.tex
thesis updated text

@@
 %\section{Intro to Automated Formal Synthesis Optimization}
-This section presents the case studies used to evaluate our proposed approach. 
-We also compare our approach with a simulation tool, named HOME Pro. 
+This Chapter presents the case studies used to evaluate the proposed approach of optimal sizing of stand-alone solar PV systems using automated synthesis. 
+Moreover, the approach is compared with a simulation tool, named HOME Pro. 
 The version and command-line of each verifier adopted, 
@@
 with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
-Our experiments were performed with a predefined timeout of $240$ minutes.
+The experiments were performed with a predefined timeout of $240$ minutes.
 
-Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
+Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with solver Boolector 3.0.1~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engine to compare the proposed approach effectiveness and efficiency.
+Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
 The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.

### 2019-07-22 Tex/Old text/chapters/chapter04.tex
thesis updated text

@@
 Moreover, there is the comparative with a specialized simulation tool, and even the use of different verifiers who perform the automated verification in order to evaluate performance.
+Tables, commented reports, and graphical outputs are presented to aid the understanding.
 
@@
 %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
-These case studies were defined 
-based on usual electrical load found in riverside communities of the 
-Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
 
@@
 \hline
-PV Panels &  \multicolumn{4}{|c|}{3x 325 W: in series} & 4x 325 W: 2x series, 2x parallel \\
+PV Panels &  \multicolumn{4}{|c|}{3$\times$325 W: (3S)} & 4$\times$325 W: (2S-2P) \\
 \hline
-Batteries & \multicolumn{4}{|c|}{\makecell{4x220 Ah: 2x series, 2x parallel\\ autonomy: 48 h}} & \makecell{4x 120 Ah batteries in series\\ autonomy: 6 h}\\
+Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah: (4S)\\ autonomy: 6 h}\\
 \hline
@@
 \hline
-Inverter & \multicolumn{4}{|c|}{700 W, peak of 1,600 W} & 1,200 W, peak of 1,600 W\\
+Inverter & \multicolumn{4}{|c|}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
 \hline
-Power demand & 253 W & 263 W & 283 W & 501 W & 915 W\\
+Power peak (W)& 342  & 253  & 263 & 322 & 814 \\
+\hline
+Power surge (W)& 342 & 722 & 732 & 896 & 980\\
+\hline
+Load curve (W) & \multicolumn{5}{|l|}{\makecell{House 1: 118-118-118-46-46-46-95-95-170-170-296-242-242-95-95-95-95-95-342-288-288-288-288-118\\House 2: 136-136-136-136-136-136-67-67-184-184-184-184-184-67-67-67-67-67-253-253-253-253-253-136\\House 3: 113-113-113-113-113-113-67-67-217-97-97-97-97-97-97-97-97-97-263-113-113-113-113-113\\House 4: 207-207-207-135-135-135-66-66-161-161-233-253-248-66-66-66-66-66-302-317-322-302-302-207\\House 5: 45-16-16-16-16-16-0-0-0-72-72-222-150-150-0-0-72-72-814-814-814-742-742-16}}\\
+\hline
+\makecell{Consumption\\ (kWh/day)}& 3.9 & 3.6 & 2.5 & 4.3 & 4.88\\
 \hline
@@
 \end{tabular}
+Legend: (S): Series; (P): Parallel.
 \end{scriptsize}
@@
 
-\section{Verifiers Environment}
-\label{sec:verifenviron}
-
-Screens and comments about the verifiers.
-
-\subsubsection{CBMC}
-
-\subsubsection{ESBMC}
-
-\subsubsection{CPAchecker}
-
-\section{HOMER Pro Environment}
-\label{sec:homerenviron}
-
-Screens and comments about the simulation tool.
+%\section{Verifiers Environment}
+%\label{sec:verifenviron}
 
@@
 %------------------------------------------
-%
+
+This Section presents the results, with commented outputs produced by every tool, mainly related to the reports (CBMC and ESBMC) and some graphical resources (CPAchecker and ESBMC).
+
 %\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
@@
 
+\subsection{ESBMC}
 Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3.
 The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet.
+
 Using ESBMC with Boolector led to an out of memory situation in all the case studies.
 This result was obtained in less than six minutes of execution, i.e., the 64 GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
+
 However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.
-Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s.
+
+Related to the cases that use a 700 W PV system (house 1, house 2, house 3, and house 4), ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s.
+Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool, with the absence of fail at the end of analysis.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{esbmcverifh1.png}
+\centering
+\caption{Report generated by ESBMC (with Z3 solver) after validation of House 1.}
+\label{fig:esbmcverifhouse1}
+\end{figure}
+
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
+Fig.~\ref{fig:esbmcverifhouse5} shows the report issued by the tool, with red highlights for the result, showing the incompatibility of the sized charge controller and the minimum necessary.
 This verification took less than 1 s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
 
-Concerning the CBMC tool, similar results were obtained, but with some slower time.
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{esbmcverifh5.png}
+\centering
+\caption{Report generated by ESBMC (with Z3 solver) after validation of House 5.}
+\label{fig:esbmcverifhouse5}
+\end{figure}
+
+%At the terminal, the command used to perform the verification is:
+%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
+%
+%Where:
+%
+%\begin{itemize}
+%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
+%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
+%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
+%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
+There are other options, but this parameter is necessary because the complexity of the algorithms.
+The incremental SMT solving uses few RAM memory, compared with other SMT solving.
+%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
+The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
+%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
+%\end{itemize}
+%
+
+\subsection{CBMC}
+
+Concerning the CBMC tool, similar results were obtained, but with some slower time than ESBMC.
 The experimentation returned SAT or UNSAT to all the case studies.
-Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s.
+Related to the 700 W PV systems (house 1, house 2, house 3, and house 4), the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s.
+
+Fig.
+\ref{fig:cbmcverifhouse1} shows part of report produced by CBMC when validating the house 1.
+The file produced by CBMC is 160 lines long and 12.4 kB of size.
+The author highlighted the result, which shows that was not found design flaws within the bound $k$ of 100.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{cbmcverifh1.png}
+\centering
+\caption{Report generated by CBMC after validation of House 1.}
+\label{fig:cbmcverifhouse1}
+\end{figure}
+
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
 This verification took less than 1 s to be performed as well.
+Fig.~\ref{fig:cbmcverifhouse5} shows the (edited) report produced, with the highlights about the flaw found: the minimum controller current needed to the PV systems is not compatible with the chosen controller of the sized system.
+
+\begin{figure}[h]
+\includegraphics[width=0.7\textwidth]{cbmcverifh5.png}
+\centering
+\caption{Report generated by CBMC after validation of House 5.}
+\label{fig:cbmcverifhouse5}
+\end{figure}
+
+\subsection{CPAchecker}
 
@@
 
-In order to validate the possible flaw from house 5, we have surveyed the owner of the 1,200 W system.
-We identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
-However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system %($96.67\% = 100\%-3.33\%$)
-and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
-%\begin{figure}[h]
-%\includegraphics[width=0.65\textwidth]{loadcurve.png}
-%\centering
-%\caption{Five weeks monitored load curve from House 1.}
-%\label{fig:loadcurve}
-%\end{figure}
+\subsection{HOMER Pro Environment}
+\label{sec:homerenviron}
 
+Screens and comments about the simulation tool.
 The same five case studies were evaluated by HOMER Pro (RQ2).
@@
 
-%At the terminal, the command used to perform the verification is:
-%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
-%
-%Where:
-%
-%\begin{itemize}
-%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
-%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
-%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
-%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
-There are other options, but this parameter is necessary because the complexity of the algorithms.
-The incremental SMT solving uses few RAM memory, compared with other SMT solving.
-%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
-The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
-%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
-%\end{itemize}
-%
+\subsection{Comparing Automated Verification and Simulation Results with Real PV Systems}
+
+In order to validate the possible flaw from house 5, we have surveyed the owner of the 1,200 W system.
+We identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
+The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
+However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system %($96.67\% = 100\%-3.33\%$)
+and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
+%\begin{figure}[h]
+%\includegraphics[width=0.65\textwidth]{loadcurve.png}
+%\centering
+%\caption{Five weeks monitored load curve from House 1.}
+%\label{fig:loadcurve}
+%\end{figure}
+
 %\subsection{Experimental results}

### 2019-07-22 Tex/Old text/chapters/chapter04.tex
thesis updated text

@@
 These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+
+Worth to mention that the load curve represents a array of 24 integer numbers for every hour of the day (instant power in Watts) and it was estimated after visiting and survey applied in June of 2017, before the houses were electrified.
 
@@
 %In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool.
-All the experiments were performed with a timeout of 14,400 seconds.
+All the experiments were performed with a time out of 14,400 seconds.
 %Every dweller, who owns a PV system, was interviewed
@@
 The setup of HOMER Pro v3.13.1 was an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
-The experiments were performed with timeout of 240 minutes.
+The experiments were performed with time out of 240 minutes.
 
-Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled; % with the goal of reducing memory usage; we have also used
-with SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled; with SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+% with the goal of reducing memory usage.
 
@@
 
-% enabled with the goal of reducing memory usage; 
-%The experiments were performed without a predefined timeout.
 Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
 An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness in the results (so it is not reported here).
-% enabled with the goal of reducing memory usage; 
- %The experiments were performed without a predefined timeout.
 
@@
 
-However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.
+However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned was conclusive (SAT or UNSAT) to all the case studies.
 
 Related to the cases that use a 700 W PV system (house 1, house 2, house 3, and house 4), ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s.
-Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool, with the absence of fail at the end of analysis.
+Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for the house 1, with the absence of fail at the end of analysis.
+The file produced by ESBMC is 160 lines long and 12.4 kB of size.
+The author highlighted the result, which shows that was not found design flaws (SAT result or SUCCESS) within the bound $k$ of 100.
 
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{esbmcverifh1.png}
+\includegraphics[width=0.65\textwidth]{esbmcverifh1.png}
 \centering
@@
 However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
+
 Fig.~\ref{fig:esbmcverifhouse5} shows the report issued by the tool, with red highlights for the result, showing the incompatibility of the sized charge controller and the minimum necessary.
+The report generated by ESBMC was a text file of 14.1 kB of size and 353 lines of length.
 This verification took less than 1 s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
@@
 
-Concerning the CBMC tool, similar results were obtained, but with some slower time than ESBMC.
-The experimentation returned SAT or UNSAT to all the case studies.
+Concerning the CBMC tool, similar results were obtained, but with some slower time than ESBMC. The experimentation returned SAT or UNSAT to all the case studies, i.e., it was conclusive to all houses.
+
 Related to the 700 W PV systems (house 1, house 2, house 3, and house 4), the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s.
@@
 \ref{fig:cbmcverifhouse1} shows part of report produced by CBMC when validating the house 1.
-The file produced by CBMC is 160 lines long and 12.4 kB of size.
+The file produced by CBMC is 270,512 lines long and 39 MB of size.
 The author highlighted the result, which shows that was not found design flaws within the bound $k$ of 100.
@@
 Fig.~\ref{fig:cbmcverifhouse5} shows the (edited) report produced, with the highlights about the flaw found: the minimum controller current needed to the PV systems is not compatible with the chosen controller of the sized system.
+The report file generated contained 217 lines and was 13 kB long.
 
@@
 This is because the \textit{time out} limit was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
+
+Figure here CPA house 1
+
 However, when verifying the 1,200 W PV system, the tool presented a SAT message equal to the other engines.
+
+Figure here CPA house 5
 
@@
 Screens and comments about the simulation tool.
+1) If you want to simulate a particular capacity for PV and battery, you can use the search space instead of HOMER Optimizer for sizing.
+You can either aggregate all the 3 PV panels together as a single PV component or add 3 PV components to represent the series configuration.
+For the batteries, you will have to find the equivalent capacity of the series and parallel configuration since HOMER considers only one battery component per simulation even if you add multiple battery components in the schematic.
+2) You cannot set the autonomy of the batteries as HOMER controller will decide when it is economical to discharge the batteries during the simulation year.
+
 The same five case studies were evaluated by HOMER Pro (RQ2).
 The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system (RQ2).
 All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
-%Fig.
-\ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software, specifically to house 1.
-%
-%\begin{figure}[h]
-%\includegraphics[width=0.8\textwidth]{homer.png}
-%\centering
-%\caption{HOMER simulation screen.}
-%\label{fig:homerscreen}
-%\end{figure}
-%
+Fig.
+\ref{fig:homerscreen1} shows one of the screens presented by HOMER Pro software, specifically to house 1.
 
-There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
-our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
-House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{homer.png}
+\centering
+\caption{HOMER simulation screen.}
+\label{fig:homerscreen1}
+\end{figure}
+
+The case study that was not possible to simulate was the 1,200 W (house 5).
+The reason is based on the fact that HOMER Pro do not allow to set up a battery autonomy; therefore, it was was not possible to obtain any indication about the failures of this specifically PV system with simulation (RQ2).
+
 %
@@
 
+There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
+our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
+House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
+
 In order to validate the possible flaw from house 5, we have surveyed the owner of the 1,200 W system.
@@
 The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
-However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system %($96.67\% = 100\%-3.33\%$)
+However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$)
 and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
+
 %\begin{figure}[h]
@@
 %\end{figure}
-
+%
 %\subsection{Experimental results}
@@
 %---------------------------------------------------
+
 We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
@@
 
-\textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
+\textit{Model precision:} each component of the PV system is mathematically modeled, and the precision of the proposed method depends on the precision of that particular model. 
 The adoption of more complex models, or even an evaluation in a PV laboratory to validate the model could add more reliability to the results.
@@
 \section{Conclusion}
+
+At this Chapter it was performed the comparative among verifiers with the proposed automated verification using model checking, which showed that 'incremental' ESBMC had the best overall performance.
+CBMC presented the same results, however with a worse time to result, and CPAchecker was not conclusive (house 1, house 2, house 3, and house 4) because the \textit{time out} was not enough to obtain some result.
+
+A comparative with a specialized simulation tool was performed as well, however some limitations of the tool, mainly related to not allow battery autonomy setup, restricted the comparative between automated verification tools versus simulation tools.
+
+Based on the fact that all case studies were deployed at the field, with regular visiting to perform interview with the dwellers, and with monitoring system in some of the houses (house 1, house 2, house 3, and house 4), it was possible to compare the computer obtained results with the real world employment of the stand-alone solar PV systems.
+The final conclusion was that the proposed tool is sound and with an acceptable performance.

### 2019-07-23 Tex/Old text/chapters/chapter04.tex
thesis updated text

@@
 %------------------------------------------
-Our experimental evaluation aims to answer two research questions:
+
+The experimental evaluation aims to answer two research questions:
 %
 \begin{enumerate}
-\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
+\item[RQ1] \textbf{(soundness)} Does the automated verification approach provide correct results?
 \item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
@@
 Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
-Note that an UNKNOWN result from our verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
+Note that an UNKNOWN result from the proposed verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
 
@@
 
-The description of our experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
+The description of the experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
 
@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{esbmcverifh5.png}
+\includegraphics[width=0.65\textwidth]{esbmcverifh5.png}
 \centering
@@
 There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
-our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
+of proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that the proposed approach provides the correct evaluation of the PV system, thus answering RQ2.
 House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
 
-In order to validate the possible flaw from house 5, we have surveyed the owner of the 1,200 W system.
-We identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
+In order to validate the possible flaw from house 5, it was surveyed the owner of the 1,200 W system.
+It was identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
 The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
@@
 
-We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
+At this Chapter, it was reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
+Nevertheless, we have also identified five threats to the validity of the results that can further be assessed.
 
-\textit{Model precision:} each component of the PV system is mathematically modeled, and the precision of the proposed method depends on the precision of that particular model. 
+\textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
 The adoption of more complex models, or even an evaluation in a PV laboratory to validate the model could add more reliability to the results.
 
-\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.
+\textit{Time step:} The run-time complexity of the proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.
 
-\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.
+\textit{Case studies:} The case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.
+
+\textit{Simulation Tool:} Only HOMER Pro was used.
+The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparative.
+
+\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online~\cite{Temperature, Irradiance}.
+However, considering that riverside communities do not have weather stations, the data used in the present study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data.
+Therefore, the most accurate should be the use of weather stations in each location.
 

### 2019-07-23 Tex/Old text/chapters/chapter05.tex
thesis updated text

@@
 
-We have performed seven stand-alone PV system case studies to evaluate 
-our proposed synthesis approach, as described in the first column of 
-Table~\ref{tab1} (named Specification). These case studies were defined 
-based on usual electrical load found in riverside communities of the 
-Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+It was performed seven stand-alone PV system case studies to evaluate the proposed synthesis approach:
+
+\begin{itemize}
+\item Case Study 1: Power peak: 342 W, power surge: 342 W, energy consumption: 3,900 Wh/day, battery autonomy: 48 h;
+\item Case Study 2: Power peak: 814 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 48 h;
+\item Case Study 3: Power peak: 815 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 12 h;
+\item Case Study 4: Power peak: 253 W, power surge: 722 W, energy consumption: 3,600 Wh/day, battery autonomy: 48 h;
+\item Case Study 5: Power peak: 263 W, power surge: 732 W, energy consumption: 2,500 Wh/day, battery autonomy: 48 h;
+\item Case Study 6: Power peak: 322 W, power surge: 896 W, energy consumption: 4,300 Wh/day, battery autonomy: 48 h;
+\item Case Study 7: Power peak: 1,586 W, power surge: 2,900 W, energy consumtion: 14,000 Wh/day, battery autonomy: 48h.
+\end{itemize}
+
+These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+With exception of case 7 that was idealized as a small town solution to support few lamps and an 12 kBTUs air-conditioner.
+
+%---------------------------------------------------------------------------
+\section{Objectives and Setup} 
+%---------------------------------------------------------------------------
+
+The evaluation aims to answer two experimental questions:
+
+\begin{enumerate}
+
+\item[EQ1] \textbf{(soundness)} does the proposed automated synthesis approach provide correct results?
+
+\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?
+
+\end{enumerate}
+
+All experiments regarding the verification tools were conducted 
+on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
+$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
+Related to HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), 
+with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
+The experiments were performed with a predefined time out of $240$ minutes.
+
+Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with solver Boolector 3.0.1~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engine to compare the proposed approach effectiveness and efficiency.
+Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
+The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
+
+\section{Verifiers and HOMER Pro Environments}
+
+The environment and captured screens are the same as presented in Section~\ref{sec:verifenviron} for the verifiers and in Section~\ref{sec:homerenviron} for the HOMER Pro tools.
+
+%---------------------------------------------------------------------------
+\section{Results}  
+\label{sec:synthesisresults}
+%---------------------------------------------------------------------------
+
+The results are presented at Table~\ref{tab1}.
 
@@
 \end{tabular}
-\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
+\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
 \end{scriptsize}
 \end{table}
-
-%---------------------------------------------------------------------------
-\section{Objectives and Setup} 
-%---------------------------------------------------------------------------
-
-Our evaluation aims to answer two experimental questions:
-
-\begin{enumerate}
-
-\item[EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
-
-\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?
-
-\end{enumerate}
-
-All experiments regarding the verification tools were conducted 
-on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
-$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
-Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
-with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
-The experiments were performed with a predefined timeout of $240$ minutes.
-
-Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with solver Boolector 3.0.1~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engine to compare the proposed approach effectiveness and efficiency.
-Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
-The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
-
-\section{Verifiers and HOMER Pro Environments}
-
-The environment and captured screens are the same as presented in Section~\ref{sec:verifenviron} for the verifiers and in Section~\ref{sec:homerenviron} for the HOMER Pro tools.
-
-%---------------------------------------------------------------------------
-\section{Results}  
-%---------------------------------------------------------------------------
 
@@
 the time limit, which varied from $134.71$ to $235.75$ minutes. 
-Only case study $7$ led to a \textit{timeout} result, i.e., 
-it was not solved within $240$ minutes. However, if we remove 
-this timeout limitation from CPAchecker, the verifier is 
+Only case study $7$ led to a \textit{time out} result, i.e., 
+it was not solved within $240$ minutes. However, if it is remove 
+this time out limitation from CPAchecker, the verifier is 
 able to solve the optimization in $44.97$ hours. 
@@
 CBMC and ESBMC are unable to produce any conclusive result. 
-Situations of \textit{internal failure}, \textit{timeout}, 
+Situations of \textit{internal failure}, \textit{time out}, 
 or \textit{out of memory} occurred; this partially answers 
@@
 an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
-if we remove the timeout from ESBMC with the SMT solver Boolector, 
+if it is removed the time out from ESBMC with the SMT solver Boolector, 
 then the verifier is able to obtain the automated synthesis 
@@
 and within a time shorter than $30$ seconds, which was much 
-faster than our automated synthesis tool (cf.~\textit{EQ2}). 
+faster than the proposed automated synthesis tool (cf.~\textit{EQ2}). 
 Case study $3$ was not possible to be simulated since HOMER Pro 
@@
 the tool always tries to feed with electricity the given load 
-during $365$ days/year. We have also noted other HOMER Pro drawbacks:
+during $365$ days/year.
+
+It was also noted other HOMER Pro drawbacks:
 
@@
 Comparing the results between the formal synthesis with CPAchecker 
-and HOMER Pro, we observed that most results are quite similar, 
+and HOMER Pro, it was observed that most results are quite similar, 
 in terms of technical solution and cost (cf. Table~\ref{tab1}).
@@
 where the costs presented by HOMER Pro were $54$\% higher 
-than our automated synthesis tool, probably because the 
-operation and maintenance costs assumed by our automated 
+than the automated synthesis tool, probably because the 
+operation and maintenance costs assumed by the automated 
 synthesis tool were underestimated to that specific load.
@@
 In general, the size of the PV panels and battery bank were 
-bigger in HOMER Pro than with our formal synthesis approach, 
+bigger in HOMER Pro than with the formal synthesis approach, 
 and that discrepancy is not easy to address without some real 
@@
 the optimal solution provided by HOMER Pro demands $7$ $\times$ 
-more PV panels than the solution presented by our synthesis tool, 
+more PV panels than the solution presented by the synthesis tool, 
 and HOME Pro does not show the arrangement of arrays 
@@
 the battery bank presented by HOMER Pro provides $500.4$ Ah 
-of capacity ($6 \times 83.4$), while our synthesis tool 
+of capacity ($6 \times 83.4$), while the synthesis tool 
 presented an optimal solution with $420$ Ah of total capacity 
@@
 lead-acid batteries. These solutions are more close 
-to the result presented by our formal synthesis 
-approach than HOMER Pro, thereby showing that our 
+to the result presented by the proposed formal synthesis 
+approach than HOMER Pro, thereby showing that the 
 solution is sound, which answers \textit{EQ1}.
@@
 is just a reference value and not a commercial value of 
-the employed inverter. Our synthesis tool, however, 
+the employed inverter. The proposed synthesis tool, however, 
 presents inverters that are commercial and can be found 
@@
 
-Concerning to charge controllers, as we reported in 
-the previous section, HOMER Pro does not include it 
+Concerning to charge controllers, as it was reported in 
+the section~\ref{sec:synthesisresults}, HOMER Pro does not include it 
 as an explicit equipment in its mathematical model, 
-only our synthesis tool presents a commercial controller 
+only the synthesis tool presents a commercial controller 
 and includes it during the cost analysis. Therefore, 
@@
 
-Case study $7$ was not solved by our synthesis tool 
+Case study $7$ was not solved by the synthesis tool 
 within the time limit established during the experimental 
@@
 
-Summarizing, our synthesis tool is capable to present a 
+Summarizing, the synthesis tool is capable to present a 
 solution, which is far detailed and close to the commercial 
 reality than the solution presented by HOMER Pro. 
-In particular, our automated synthesis method 
+In particular, the automated synthesis method 
 can provide all the details of every component of 
@@
 
-We have reported a favorable assessment of our formal synthesis method. 
-Nevertheless, we have also identified three threats to the validity 
-of our experimental results, which can be further assessed and 
-constitute future work: ($1$) improvement of the power reliability 
+At this Section, it was reported a favorable assessment of proposed formal synthesis method. 
+Nevertheless, it was also identified three threats to the validity 
+of the experimental results, which can be further assessed and 
+constitute future work:
+
+\begin{itemize}
+\item ($1$) improvement of the power reliability 
 analysis: to include loss of load probability or loss of power 
 supply probability, which can make the analysis more accurate; 
-($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
+\item ($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
 however, a broad analysis from other isolated areas must be 
 performed in order to make the optimization general in terms 
-of applicability; ($3$) to deploy at the field some PV systems 
-sized using our synthesized results in order to validate it.
+of applicability; 
+\item ($3$) to deploy at the field some PV systems 
+sized using the synthesized results in order to validate it.
+\end{itemize}
 

### 2019-07-23 Tex/Old text/chapters/conclusion.tex
thesis updated text

--- 2019-07-01 Tex/Old text/chapters/conclusion.tex
@@
-We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
-We have considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
+At this final chapter, the conclusions about the research done during the Doctoral process are presented.
+Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable source) closes the work.
+
+\section{Main Contributions}
+
+This Thesis contributions can be split in two, each one concerning the tools created with the use of model checking to solar PV systems.
+
+It was described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
+It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
 Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
@@
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.
-As future work, we will also consider other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
 
-///////////////////////
+It was described and evaluated as well, an automated synthesis method to obtain the optimal size of PV system using software model checking techniques.
+It was considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+The automated synthesis tool presented detailed optimal solution to six case studies adopted in this paper, with specifications, models, and the arrangement in terms of series-parallel connections, thereby covering the charge controller, which was not presented by HOMER Pro.
+In a nutshell, our automated synthesis tool took more time to find the optimal solution than HOMER Pro; however, the presented solution was more complete and detailed, which is very useful to a user to get a list of equipment and go to shopping.
 
-We have described and evaluated an automated synthesis method 
-to obtain the optimal size of PV system using software model 
-checking techniques. We have considered seven case studies 
-from PV systems in two different sites of the Amazonas State 
-in Brazil, ranging from $253$\,W to $1,586$\,W peak; and 
-three state-of-art verification engines were considered 
-(ESBMC, CBMC, and CPAchecker), in addition to a specialized 
-off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+\section{Future Work Directions}
 
-Our automated synthesis tool presented detailed optimal solution 
-to six case studies adopted in this paper, with specifications, 
-models, and the arrangement in terms of series-parallel connections, 
-thereby covering the charge controller, which was not presented by HOMER Pro. 
-In a nutshell, our automated synthesis tool took more time 
-to find the optimal solution than HOMER Pro; however, the presented 
-solution was more complete and detailed, which is very useful 
-to a user to get a list of equipment and go to shopping.
+As the focus here was stand-alone solar PV systems, one future work will be also consider other types of renewable energy and even hybrid ones to allow the method to verify and to obtain the optimal sizing of typical rural electrification systems.
 
-As future work, the authors plan to improve the power reliability analysis, 
-to address the restriction to only allow automated synthesis of 
-riverside communities in the Amazonas state (Brazil), and to 
-validate some cases with deployed PV systems in isolated communities.
+Related to automated sizing, the author plan to improve the power reliability analysis, 
+to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil), and to validate some cases with deployed PV systems in isolated communities.
+
+It is planned to develop the code of a general purpose simulation tool, using the same mathematical model employed for the model checking methods of this work, to include it in the comparative in order to cover all the possibilities to validate or optimize solar PV systems.
+
+One future long term direction is to foster the creation of a research group in automated verification and synthesis applied to electrical systems improve mathematical models; and a international network of researchers in model checking applied to electrical systems.
+
+\section{Concluding Remarks}
+
+The automated verification and automates synthesis methods demonstrate the effectiveness and the potential of use in stand-alone solar PV systems.
+Some issues must be addressed in order to improve the tools, as performance and the human-computer interaction, however the work has potential and it is promising.
+
+About license and the use of tools that the author employed at this work, must be noticed that HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; the verifiers, as CPAchecker, ESBMC and CBMC, and their solvers, they are  based on open source software license and usually allows the users to freely use, modify, and distribute licensed product.
+Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is a advantage when compared to commercial tools); therefore, some of the licenses do not allow the software to be used in a commercial context.
+
+Based on the fact that the tools detailed here have not similarity in past work in the world, can be concluded that it was produced original research that expands the boundaries of knowledge, putting cutting-edge computer science methodologies to solve typical electrical engineering problems and to improve the design of systems.

### 2019-07-23 Tex/Old text/chapters/appendix.tex
thesis updated text

--- 2019-06-27 Tex/Old text/chapters/appendix.tex
@@
-appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix.
+%\textbf{List of Publications}
+%
+Here there are a list of papers that were written during the Thesis elaboration and the status of every submission until the date of this document.
+
+\section{Journals}
+
+Automated Formal Verification of Stand-alone Solar Photovoltaic Systems, 8-May submitted, in review by Elsevier Solar Energy (Impact Factor 4.374, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV ) https://www.journals.elsevier.com/solar-energy
+
+An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative, 29-June submitted, Elsevier Applied Solar (Impact Factor 7.9, CAPES A1 Interdisciplinary, CAPES A2 Engineering IV, CAPES B1 Computer Science) https://www.journals.elsevier.com/applied-energy
+
+\section{Congress}
+
+Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems - submitted 06-MAY-2019 - New Ideas papers - ASE 2019 The IEEE/ACM Automated Software Engineering (ASE 2019) Conference

### 2019-07-23 Tex/Old text/chapters/chapter04.tex
thesis updated text

@@
 %------------------------------------------
-%
+
 %We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
@@
 
-Worth to mention that the load curve represents a array of 24 integer numbers for every hour of the day (instant power in Watts) and it was estimated after visiting and survey applied in June of 2017, before the houses were electrified.
+Worth to mention that the load curve represents a array of $24$ integer numbers for every hour of the day (instant power in Watts) and it was estimated after visiting and survey applied in June of $2017$, before the houses were electrified.
 
@@
 \subsection{ESBMC}
+
 Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3.
@@
 Using ESBMC with Boolector led to an out of memory situation in all the case studies.
-This result was obtained in less than six minutes of execution, i.e., the 64 GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
+This result was obtained in less than six minutes of execution, i.e., the $64$ GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
 
@@
 
-Related to the cases that use a 700 W PV system (house 1, house 2, house 3, and house 4), ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s.
-Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for the house 1, with the absence of fail at the end of analysis.
-The file produced by ESBMC is 160 lines long and 12.4 kB of size.
-The author highlighted the result, which shows that was not found design flaws (SAT result or SUCCESS) within the bound $k$ of 100.
+Related to the cases that use a $700$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC could not reach an error in all the four houses and the execution time took from $04$ m $27$ s to $05$ m $08$ s.
+Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for the house $1$, with the absence of fail at the end of analysis.
+The file produced by ESBMC is $160$ lines long and $12.4$ kB of size.
+The author highlighted the result, which shows that was not found design flaws (SAT result or SUCCESS) within the bound $k$ of $100$.
 
@@
 
-However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
+However the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
 
 Fig.~\ref{fig:esbmcverifhouse5} shows the report issued by the tool, with red highlights for the result, showing the incompatibility of the sized charge controller and the minimum necessary.
-The report generated by ESBMC was a text file of 14.1 kB of size and 353 lines of length.
-This verification took less than 1 s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
+The report generated by ESBMC was a text file of $14.1$ kB of size and $353$ lines of length.
+This verification took less than $1$ s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line $3$ of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
 
 \begin{figure}[h]
-\includegraphics[width=0.65\textwidth]{esbmcverifh5.png}
+\includegraphics[width=0.5\textwidth]{esbmcverifh5.png}
 \centering
@@
 
-Related to the 700 W PV systems (house 1, house 2, house 3, and house 4), the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s.
+Related to the 700 W PV systems (house $1$, house $2$, house $3$, and house $4$), the tool could not reach an error in all the four houses and the execution time took from $18$ m $36$ s to $19$ m $02$ s.
 
@@
 \ref{fig:cbmcverifhouse1} shows part of report produced by CBMC when validating the house 1.
-The file produced by CBMC is 270,512 lines long and 39 MB of size.
-The author highlighted the result, which shows that was not found design flaws within the bound $k$ of 100.
+The file produced by CBMC is $270,512$ lines long and $39$ MB of size.
+The author highlighted the result, which shows that was not found design flaws within the bound $k$ of $100$.
 
@@
 
-However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
-This verification took less than 1 s to be performed as well.
+However the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code; with the same counterexample presented by ESBMC.
+This verification took less than $1$ s to be performed as well.
 Fig.~\ref{fig:cbmcverifhouse5} shows the (edited) report produced, with the highlights about the flaw found: the minimum controller current needed to the PV systems is not compatible with the chosen controller of the sized system.
-The report file generated contained 217 lines and was 13 kB long.
+The report file generated contains $217$ lines and it was $13$ kB of size.
 
@@
 Finally, the CPAchecker tool presented some different results.
-Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700 W systems.
-This is because the \textit{time out} limit was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
+Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the $700$ W systems (house $1$, house $2$, house $3$, and house $4$).
 
-Figure here CPA house 1
+This is because the \textit{time out} limit was reached, i.e., after $4$ hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
+This is shown in Fig.~\ref{fig:cpavalidh1} is shown one of the text reports issued by CPAchecker.
+Differently of ESBMC and CBMC, CPAchecker produces a lot of different reports, notable for log, statistical, and counterexample files (which is graphical and not in text format).
 
-However, when verifying the 1,200 W PV system, the tool presented a SAT message equal to the other engines.
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{CPA_verif_h1.png}
+\centering
+\caption{CPAchecker time out result for house 1 validation (file CPALog.txt).}
+\label{fig:cpavalidh1}
+\end{figure}
 
-Figure here CPA house 5
+However, when validating the $1,200$ W PV system (house $5$), the tool presented a SAT message equal to the other engines, but with a execution time of $6$ seconds.
+Fig.~\ref{fig:cpavalidh5} show the result, with highlights to the line that causes the fail ($IC_{min}$) and part of the CFA (control-flow automata, represented as a control-flow graph) diagram pointing to this fail.
+
+\begin{figure}[h]
+\includegraphics[width=1.0\textwidth]{CPA_verif_h5.png}
+\centering
+\caption{CPAchecker time out result for house 5 validation (file Counterexample.html).}
+\label{fig:cpavalidh5}
+\end{figure}
 
@@
 
-Screens and comments about the simulation tool.
+\textcolor{red}{Screens and comments about the simulation tool.}
+
 1) If you want to simulate a particular capacity for PV and battery, you can use the search space instead of HOMER Optimizer for sizing.
@@
 The same five case studies were evaluated by HOMER Pro (RQ2).
-The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues.
-All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
+The simulation results showed that the project restrictions were met by four $700$ W PV systems (houses $1$, $2$, $3$ and $4$), without any indication of sizing error or even performance related issues.
+All the simulations took less than $5$ seconds (each) to be performed by HOMER Pro.
 Fig.
-\ref{fig:homerscreen1} shows one of the screens presented by HOMER Pro software, specifically to house 1.
+\ref{fig:homerscreen1} shows one of the screens presented by HOMER Pro software, specifically to house $1$.
 
@@
 
-The case study that was not possible to simulate was the 1,200 W (house 5).
+The case study that was not possible to simulate was the $1,200$ W (house $5$).
 The reason is based on the fact that HOMER Pro do not allow to set up a battery autonomy; therefore, it was was not possible to obtain any indication about the failures of this specifically PV system with simulation (RQ2).
@@
 
-There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
+There were no divergence of results for the houses $1$, $2$, $3$ and $4$ w.r.t.
 of proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that the proposed approach provides the correct evaluation of the PV system, thus answering RQ2.
-House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
+House $5$ presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
 
-In order to validate the possible flaw from house 5, it was surveyed the owner of the 1,200 W system.
+In order to validate the possible flaw from house $5$, it was surveyed the owner of the $1,200$ W system.
 It was identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
-However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$)
-and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
+
+The same process of validation was done to the houses $1$, $2$, $3$ and $4$, which use the $700$ W PV systems: from July of $2018$ to March $2019$, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
+
+However, even when one interruption is reported in a month, this represents around $3.33$\% of interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
 
@@
 At this Chapter it was performed the comparative among verifiers with the proposed automated verification using model checking, which showed that 'incremental' ESBMC had the best overall performance.
-CBMC presented the same results, however with a worse time to result, and CPAchecker was not conclusive (house 1, house 2, house 3, and house 4) because the \textit{time out} was not enough to obtain some result.
+CBMC presented the same results, however with a worse time to result, and CPAchecker was not conclusive (house $1$, house $2$, house $3$, and house $4$) because the \textit{time out} was not enough to obtain some result.
 
@@
 
-Based on the fact that all case studies were deployed at the field, with regular visiting to perform interview with the dwellers, and with monitoring system in some of the houses (house 1, house 2, house 3, and house 4), it was possible to compare the computer obtained results with the real world employment of the stand-alone solar PV systems.
+Based on the fact that all case studies were deployed at the field, with regular visiting to perform interview with the dwellers, and with monitoring system in some of the houses (house $1$, house $2$, house $3$, and house $4$), it was possible to compare the computer obtained results with the real world employment of the stand-alone solar PV systems.
 The final conclusion was that the proposed tool is sound and with an acceptable performance.

### 2019-07-23 Tex/Old text/chapters/conclusion.tex
thesis updated text

@@
 The automated synthesis tool presented detailed optimal solution to six case studies adopted in this paper, with specifications, models, and the arrangement in terms of series-parallel connections, thereby covering the charge controller, which was not presented by HOMER Pro.
-In a nutshell, our automated synthesis tool took more time to find the optimal solution than HOMER Pro; however, the presented solution was more complete and detailed, which is very useful to a user to get a list of equipment and go to shopping.
+In a nutshell, the proposed automated synthesis tool took more time to find the optimal solution than HOMER Pro; however, the presented solution was more complete and detailed, which is very useful to a user to get a list of equipment and go to shopping.
 

### 2019-07-24 Tex/Old text/chapters/appendix.tex
thesis updated text

--- 2019-06-27 Tex/Old text/chapters/appendix.tex
@@
-appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix.
+%\textbf{List of Publications}
+%
+Here there are a list of papers that were written during the Thesis elaboration and the status of every submission until the date of this document.
+
+\section{Journals}
+
+Trindade, A., Cordeiro, L.
+\textbf{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}, submitted: 8-May-2019 , status: in review (2nr round, since 16-July-2019) by Elsevier Solar Energy (Impact Factor 4.374, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV ) \url{https://www.journals.elsevier.com/solar-energy}
+
+Trindade, A., Cordeiro, L.
+\textbf{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}, submitted: 29-June-2019, resubmitted: 09-July-2019, status: under review by Elsevier Applied Solar (Impact Factor 7.9, CAPES A1 Interdisciplinary, CAPES A2 Engineering IV, CAPES B1 Computer Science) \url{https://www.journals.elsevier.com/applied-energy}
+
+\section{Congress}
+
+Trindade, A., Cordeiro, L.
+\textbf{Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems}, submitted: 06-MAY-2019, status: under review by The IEEE/ACM Automated Software Engineering (ASE 2019) Conference (New Ideas Papers) \url{https://2019.ase-conferences.org/track/ase-2019-papers}

### 2019-07-24 Tex/Old text/chapters/chapter02.tex
thesis updated text

@@
 This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
 
@@
 \subsection{PV Systems Optimization Criteria}
+\label{sec:optcriteria}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-07-24 Tex/Old text/chapters/conclusion.tex
thesis updated text

@@
 It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool.
-In particular, the proposed method was successful in finding sizing errors and indicating in details.
-Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
+Although the verification method proposed takes longer than simulation methods, it is able to avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.
+Moreover, it was not necessary to 'adapt' the tool, since the specialized simulation tool (HOMER Pro) had to be adjusted in order to not perform the optimization of the system.
+In addition, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature.
+
+Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

### 2019-07-29 Tex/Old text/chapters/introduction.tex
started revising Chapter 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+%-------------------------------------------------
 \section{Problem's Definition}
+%-------------------------------------------------
 
@@
 %
-Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
+Manufactures and integrators have yet their proprietary software to perform various system sizing \textcolor{red}{add citation}, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
 %
@@
 The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-However, those tools are based on running experiments in simulation models.
+However, those tools are based on running experiments in simulation models \textcolor{red}{which tools?}.
 Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded, but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
-Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}, with behavior that is, in principle, well determined.
+Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}, including for example CPS~\cite{Abateetal2017,AbateBCCDKK17,Bessa,ChavesBCKF17}, with behavior that is, in principle, well determined.
 Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.

### 2019-07-29 Tex/Old text/chapters/introduction.tex
revised Chapter 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
-Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
+Furthermore, there exists a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
 Therefore, increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
@@
 
-In order to address different aspects of a solar PV project, there is a myriad of public domain and commercial software available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+In order to address different aspects of a solar PV project, there exists a myriad of public domain and commercial software available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization).
@@
 %
-Manufactures and integrators have yet their proprietary software to perform various system sizing \textcolor{red}{add citation}, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.
+Manufactures and integrators have yet their proprietary software to perform various system sizing \textcolor{red}{add citation}, with the drawback of including just their own products among the possibilities of choice, which restricts their solution.
 %
@@
 
-Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}, including for example CPS~\cite{Abateetal2017,AbateBCCDKK17,Bessa,ChavesBCKF17}, with behavior that is, in principle, well determined.
-Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification.
-User or project requirements can be added during the creation of the formal model to be verified~\cite{Trindade}.
+Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}, including for example applications to CPS~\cite{Abateetal2017,AbateBCCDKK17,Bessa,ChavesBCKF17}, with behavior that is, in principle, well determined.
+Any system type can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification~\cite{DBLP:journals/sttt/GadelhaIC17}.
+User or project requirements can be added during the creation of the formal model to be verified~\cite{Trindade,TrindadeDJISC17}.
 %
-This area of research is referred as formal methods~\cite{Clarkeetal}. Their aim is to establish system correctness with mathematical rigor. 
-In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of flaws in order to ensure the correctness of the system.
+This research area is referred as formal methods~\cite{Clarkeetal}, which aim to establish system correctness with mathematical rigor. 
+In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of flaws in order to ensure the correctness of the system, including programming languages such as C/C++ and Java~\cite{esbmc2018,RamalhoFSMC013,CordeiroKKST18}.
 
 Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner.
-Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}.
+Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade,TrindadeDJISC17}.
 Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
@@
 %automated synthesis
-In the other hand, optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
-An ideal combination of any PV system is made by the best compromise between two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
+However, optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
+An ideal combination of any PV system is made by the best compromise between two considered objectives, which is \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.
 
@@
 
+%----------------------------------------------
 \section{Objectives}
+%----------------------------------------------
+
+\textcolor{red}{I think we're giving too much emphasis in tool development here. You should focus your description on research objectives!}
+
 This Thesis has the novelty of applying automated verification method to solar PV systems.
-The result is the development of two software: one to perform automated verification and validate the solar PV systems behavior; and other to produce the optimal sizing of solar PV systems through automated synthesis program.
+The result is the development of two software: one to perform automated verification and validate the solar PV systems behavior; and another one to produce the optimal sizing of solar PV systems through automated synthesis program.
 
@@
 The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
-The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are inputted to the proposed tool and automatically verified during the formal process.
+The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are provided to the proposed tool and automatically verified during the formal process.
 The model checking tool reports in which conditions a system does not meet the user requirements.
@@
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-The implementation of the proposed tool is carried out by means of an algorithm in language C, that is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
+The implementation of the proposed tool is carried out by means of an algorithm implemented using the C programming language, which is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
 %three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
@@
 
+%----------------------------------------------
 \section{Contributions}
+%----------------------------------------------
+
 Associated to \textbf{automated verification}, this Thesis makes three main contributions.
@@
 
+%---------------------------------------------- 
 \section{Related Work}
+%----------------------------------------------
 
@@
 
+%----------------------------------------------
 \section{Thesis Organization}
+%----------------------------------------------
+
 % ~\nameref or \autoref{

### 2019-07-29 Tex/Old text/chapters/introduction.tex
revised Chapter 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %----------------------------------------------
+\section{Outline of the Solution}
+%----------------------------------------------
+
+\textcolor{red}{you should briefly describe here the outline of your solution. As example, take a look at \url{https://ssvlab.github.io/lucasccordeiro/papers/phd\_thesis\_cordeiro.pdf.}}
+
+%----------------------------------------------
 \section{Contributions}
@@
 Secondly
-\textbf{Firstly}, it is proposed an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system.
+\textbf{Firstly}, we propose an algorithm written in the C programming language, which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system.
 \textbf{Secondly}, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies. 
-\textbf{Thirdly}, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation. 
+\textbf{Thirdly}, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation. 
 %
@@
 \textbf{First}, the use of automated symbolic verification methods in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented.
-Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with user requirements and environment constraints, and the proposed synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
-\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in the verification back-end for synthesizing optimal PV systems, being the first work that performs this type of comparative.
+Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with the user requirements and environment constraints, and the proposed synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
+\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in the verification back-end for synthesizing optimal PV systems, thereby being the first work that performs this type of evaluation.
 \textbf{Third}, the experimental results show that the proposed synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
 As a result, this Thesis marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.
-Thus, there is considerably advance the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.
+Thus, this research considerably advances the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.
 
@@
 The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
-The focus was on controlling the behavior of components, thereby verifying the given smart grid as a "system of systems" within the context of "internet of things".
+The focus was on controlling the behavior of components, thereby verifying the given smart grid as a ``system of systems'' within the context of "internet of things".
 The author, however, used approximate model checking of stochastic and hybrid models.
@@
 
+\textcolor{red}{you should add some paragraphs here to describe the difference of your work to other available in the literature.}
+
 %----------------------------------------------
@@
 Chapter~\nameref{chap:methodology} presents the automated verification  and the automated synthesis techniques.
-The results related to the experimental use of automated verification are in \autoref{chap:automatedverification}.
-While \autoref{chap:automatedsynthesis} is devoted to the experimentation,
+The results related to the experimental use of automated verification are in \autoref{chap:automatedverification}, while \autoref{chap:automatedsynthesis} is devoted to the experimentation,
 results and discussions of the automated synthesis technique. Chapter \nameref{chap:conclusions} presents the main contributions, future work directions and concluding remarks.

### 2019-07-29 Tex/Old text/chapters/chapter02.tex
revised Chapter 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Formal Methods, Formal Design and Formal Verification}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Project Validation, Automated Verification and Synthesis Using Model Checking}
@@
 
-The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C~\cite{esbmc2018}, C++~\cite{RamalhoFSMC013}, Qt~\cite{MonteiroGCF17}, and CUDA~\cite{PereiraASMMFC17} programs, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Regulated standalone system with battery and DC load}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Regulated standalone system with battery, AC load}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Design and Validation of a Solar photovoltaic system}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The design and validation of a SPV system can be done by hand or with the aid of a software tool.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{PVWatts Calculator}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{SAM}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 SAM or System Advisor Model is a software from the U.S.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{HOMER}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{RETScreen}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Hybrid2}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Thesis Proposal x Reference Tools}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER remain for comparative.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Component models for stand-alone PV systems}
 \label{model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{PV generator (cell, module, array) }
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. In the present modeling, the focus is only on cell/module/array.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Proposed PV Panel Model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation~\ref{eq:1diodemodel}.
@@
 
-Where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
+\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
 
@@
 
-Where $ V_{oc,ref} $ is the reference open-circuit voltage, and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
+\noindent where $ V_{oc,ref} $ is the reference open-circuit voltage, and $ \mu_{V} $ is an open-circuit voltage temperature coefficient ($ V/K $).
 
@@
 
-Where $ V_{mref} $, $ V_{oc,ref} $, $ I_{m,ref} $, and $ I_{sc,ref} $ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers.
+\noindent where $ V_{mref} $, $ V_{oc,ref} $, $ I_{m,ref} $, and $ I_{sc,ref} $ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers.
 
@@
 
-Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
+\noindent where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
 
@@
 
-Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
-
+\noindent where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Battery Storage Model }
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Because of the fluctuating nature of the output delivered by the PV arrays, batteries are necessary in a PV system.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Controller Model}
 \label{sec:controller}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Sizing Stand-alone Solar Photovoltaic Systems}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-07-29 Tex/Old text/chapters/introduction.tex
revised Chapter 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%automated verification
-Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
+Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015,ChavesIBCF19}.
 During operation, such components must frequently adapt to the operating environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.

### 2019-08-15 Tex/elsevier/reply Solar Energy AUG 2019.tex
Solar Energy journal reply R2

--- 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
@@
 \newcommand{\mstitle}{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}
-\newcommand{\refnumber}{SE-D-19-01248}
+\newcommand{\refnumber}{SE-D-19-01248R1}
 \newenvironment{resposta}{~~~\begin{quote}\color{blue}\textbf{Response:}}{\end{quote}}
@@
 According to the associate editor and reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text.
-The revision included the Abstract, Introduction, Methodology, and Results sections.
 
@@
 \newpage
-\subsection*{Reviewer \#2 comments followed by the authors' answers:}
+\subsection*{Reviewers' comments:}
 
 \begin{quote}
+Mandatory Editorial Changes: your highlights are incomplete sentences.
 
-In the manuscript, the authors report about the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-They show, case studies, from real photovoltaic systems deployed in five different places, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Also, the authors reported the evaluated different verification tools, in order to compare performance and soundness.
-Data from practical applications show the effectiveness of their approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
+Please follow the Guide for Authors to construct the Highlights.
+Your Highlights do not comply with the requirements stated in the Guide for Authors.  Failure to comply with this requirement will result in the rejection of your paper.
 
-I have specifics questions and suggestions in order to improvement the manuscript.
+1.     Highlights must be complete sentences with a maximum of 85 characters, not words, including spaces, per highlight.
+A complete sentence is a sentence that conveys and idea, contains a subject and a verb predicate, projects a full thought, and is able to stand alone.
+Please visit www.elsevier.com/authors/journal-authors/highlights for more details and to see examples of highlights.
 
-(1) To clarify the figure 2, i recommend write "current" inside the figure, don't put just I.
+To understand the concept of a complete sentences, please visit:
+
+http://faculty.washington.edu/ezent/imsc.htm
+\end{quote}
 
 \begin{resposta} 
-We thank the reviewer for this insightful comment.
-Indeed, it summarizes what was intended to be studied in this manuscript.
+We thank the reviewer for this insightful comment and suggestion.
+Indeed, we had to rewrite the highlights doc fileit summarizes what was intended to be studied in this manuscript.
 Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modeling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.
@@
 
-(2) This software model checking has performance in comparison the other commercials software,how is this performance?, Could you give the areas where your software performs better than commercial software?
-
-\begin{resposta} 
-Note that our options about specialized off-the-shelf tools to design stand-alone solar PV systems are very limited in literature, which motivated us to perform further studies in this area.
-In particular, as described in Section 2.1, only Hybrid2 and HOMER Pro perform off-grid with battery analysis of PV systems.
-Hybrid2 is not supported anymore, thereby being in disuse.
-We have updated this information in our manuscript (Section 2.1 as well).
-Therefore, in this particular research field (stand-alone solar PV systems), only HOMER Pro could be used for comparative purposes.
-However, in our experiments we could use some general simulation tools with the same mathematical model adopted by our automated verification tool.
-However, this would represent an unfair comparison since we would need to tweak the simulation tools to prepare them for comparison purposes, which could introduce errors.
-We have described this limitation in Section 5.4 (``Threats to Validity'') in order to state that additional comparisons could be carried out with general simulation tools if they employ similar mathematical models as the ones described here.
-Moreover, we mentioned the possibility to include this general purpose software tool comparative as future work (Section 6).
-
-Note that model checking and software simulations are two different techniques that use mathematical models.
-However, the way they work is completely different.
-On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
-On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
-In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation.
-Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in Section 1 (Introduction).
-
-Importantly, model checking explores more efficiently the design-space because the system specification is based on a formal notation, which gets converted into Boolean algebra; the evaluation of variables is made automatically by a Boolean Satisfiability (SAT) solver based on the system's constraints, i.e., system information and electrical load demand transformed into properties (e.g., use defined demands and non-deterministic variables to model the respective weather that does not have precise forecasting).
-This resulting mathematical model is submitted to full exploration of all possible states to find a configuration, where an error might occur or not.
-Logically, depending on the number of variables, state-explosion can occur and the model checking process might be time-consuming to transverse the entire state-space.
-
-However, the authors demonstrated in $2016$ [1] that model checking can present better performance than software simulation if one performs hardware-software partitioning in specifically amount of instances.
-
-[1] Trindade, A.B. and Cordeiro, Applying SMT-based verification to hardware/software partitioning in embedded systems. Des Autom Embed Syst (2016) 20: 1. https://doi.org/10.1007/s10617-015-9163-z
-
-\end{resposta}
-
-(3) In text reference at figure 1 the authors do not describe all symbols drawn into image, for instances, what is means G, T.
-I suspect that in section 4 they define which are the variables (Irradiation and temperature).
-I suggest you define those symbols in the text that that figure describes.
-
-\begin{resposta} 
-Indeed, we have missed this particular information in the paragraph that describes the mentioned figure.
-We thank you so much for this observation.
-We have revised our manuscript to describe every employed symbol.
-The revised version of these paragraphs in Section ``2.2 Component models for a stand-alone PV system'' are now described as: ``A stand-alone PV system is illustrated in Fig.1.
-The PV generator is a semiconductor device that can convert solar energy into DC electricity, with high dependence on two weather variables from the site, where the system is deployed: solar irradiance $G$ and temperature $T$.
-For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
-The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
-At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.''.
-\end{resposta}
-
-(4) Are the verification results carried out affected by the different characteristics of the computers?
-
-\begin{resposta} 
-Indeed, we did not inform the impact of changing the computer setup or related issues.
-We thank the reviewer for this observation.
-We have revised our manuscript to include the following paragraph in Section "5.2 Objectives and Setup": ``Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the implemented model (software created by the authors) to be solved.
-Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.''.
-\end{resposta}
-
-\end{quote}
-\newpage
-
-\subsection*{Reviewer \#4 comments followed by the authors' answers:}
-
-\begin{quote}
-
-(5) The topic itself is interest for the PV application. However some section including abstract and result must be rewritten to be enhanced, here are the comments:
-
--       The manuscript illustrated the main drawback from other existed work that they are based on simulation and the proposed approach is claimed to do evaluation based real PV system as illustrated in the abstract, however the evolution is based on simulation model, mathematical, and information from website data such as Weather base and Energy Plus.
-The author should present real data measurement for more accurate results then compared and the main difference should be clarified.
-
-\begin{resposta} 
-We appreciate these comments; we actually realized that the contributions of our manuscript were unclear.
-We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modeling, which was already investigated in prior studies over the last two decades.
-Moreover, we compare the results of using automated verification with simulation; real PV systems were employed just to validate the results presented by both approaches (model checking and simulation).
-Note that the automated verification and simulation tools are intended to be used during the design of the PV system, i.e., before actually buying or deploying the equipment.
-This information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.
-
-The authors hold real load curve and information collected from monitoring system using Raspberry Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result), we understand that this comparison is not appropriate.
-
-The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, as presented in our "References" section: (Weatherbase, 2018) and (EnergyPlus, 2018).
-Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure for not using weather base stations in each place since House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data).
-Because of that, we decided to add this discussion in Section ``5.4 Threats to Validity''.
-We thank you for that specific comment.
-\end{resposta}
-
-(6)      Section 5 "Experimental Evolution" It can be changed to Verification result, otherwise the author should clarify the real measurements of the system.
-
-\begin{resposta} 
-We thank the reviewer for this comment.
-We implemented as suggested, i.e., we changed the section title to ``Verification and Simulation Results" since the results are related to both verification and simulation tools.
-The data collected from dwellers with real PV systems were used just to confirm (or not) flaws and complains about the equipment deployed in the field.
-
-The authors hold real load curve and information collected from monitoring system using Raspberry Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result, as described in Section 4 of our manuscript), so we understand that this comparison is not appropriate.
-
-Note that model checking and software simulations are two different techniques that use mathematical models.
-However, the way they work is completely different.
-On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
-On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
-In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation.
-Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in Section 1 (Introduction).
-\end{resposta}
-
-(7)       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? wave-forms such as: Input power, VMPP, IMPP, AC load
-
-\begin{resposta}
-
-We agree with the reviewer that we could further improve the explanation of our study.
-In our manuscript, we compare model checking with software simulation.
-However, the way they work is completely different.
-On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
-On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
-In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation.
-Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in Section 1 (Introduction).
-
-When we work with waveform, we are performing testing or simulation, and that is different of automated verification.
-We consider that this comment (number $7$ in this Reply Letter) is related to the experimental question done by the same reviewer in (6).
-As a result, we expect that the explanations given in (6), together with the consequent updated manuscript, can cover any further concerns about this particular issue.
-\end{resposta}
-\end{quote}
-
 \label{LastPage}

### 2019-08-16 Tex/elsevier/reply Solar Energy AUG 2019.tex
Solar Energy journal reply R2

@@
 We thank you for asking us to comply with your reviewers' reports. 
-We are submitting a revised version of our manuscript entitled 
+We are submitting a revised version of our highlights file from the entitled paper  
 ``{\em \mstitle}'' by Alessandro Trindade and Lucas Cordeiro. 
-This revised version carefully addresses each comment provided 
+This revised version carefully addresses the comment provided 
 by the reviewers, as suggested in your original decision letter. 
 In particular, our reply letter describes all modifications we made 
-to our manuscript and the respective responses to the comments 
-raised by the reviewers.
+to our highlights file and the respective response to the comments 
+raised by the reviewer.
 
@@
 
-The authors would like to thank the anonymous reviewers for their valuable and constructive comments and suggestions, which helped us significantly improve the quality of our manuscript.
+The authors would like to thank the anonymous reviewers for their valuable and constructive comments and suggestions related to the highlights file, which helped us significantly improve the quality of our material.
 
-According to the associate editor and reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text.
+According to the associate editor and reviewers' comments, our highlights file has been carefully modified and rewritten.
 
-Our responses  to all comments (in blue color) are given in the sequel, with clear indications about how and where they were addressed along our manuscript.
+Our responses  to all comments (in blue color) are given in the sequel, with clear indications about how and where they were addressed.
 
-We hope those modifications in our manuscript and also our responses are sufficient to make our work suitable for publication in {\bf Solar Energy}.
+We hope those modifications in our highlights file and also our responses are sufficient to make our work suitable for publication in {\bf Solar Energy}.
 
@@
 \begin{resposta} 
-We thank the reviewer for this insightful comment and suggestion.
-Indeed, we had to rewrite the highlights doc fileit summarizes what was intended to be studied in this manuscript.
-Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modeling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.
-Regarding Figure 2, we fixed it as recommended by the reviewer.
-Moreover, we applied the same procedure to voltage $V$, in order to keep consistency throughout our manuscript.
+We thank the reviewers for this insightful comment and suggestion. Indeed, we had to rewrite the highlights doc file to comply with the correct expectation from {\bf Solar Energy} journal.
+
+Now our new highlights files states:
+\begin{itemize}
+\item Verification can be effective to validate stand-alone solar photovoltaic systems
+\item Automated verification method can detect design errors better than simulation
+\item ESBMC can produce better performance and soundness among automated verifiers
+\end{itemize}
+
+Compared with the original and not suitable:
+\begin{itemize}
+\item Approach detect design errors which are not easily detected by other approaches
+\item Algorithm that implements the automated verification method 
+\item Formal checking of the sizing and the operation of a given stand-alone PV system
+\item Comparative of three state-of-the-art model checkers in five real case studies
+\end{itemize}
 

### 2019-08-18 Tex/acmart-master/sample-sigconf.tex
ICSE paper

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,review]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
%\AtBeginDocument{%
%  \providecommand\BibTeX{{%
%    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%\setcopyright{acmcopyright}
%\copyrightyear{2018}
%\acmYear{2018}
%\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
%\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
%  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%  June 03--05, 2018, Woodstock, NY}
%\acmPrice{15.00}
%\acmISBN{978-1-4503-9999-9/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Test}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Valerie Beranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
%\begin{teaserfigure}
%  \includegraphics[width=\textwidth]{sampleteaser}
%  \caption{Seattle Mariners at Spring Training, 2010.}
%  \Description{Enjoying the baseball game from the third-base
%  seats. Ichiro Suzuki preparing to bat.}
%  \label{fig:teaser}
%\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigconf]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for all short- and
full-length articles, and optional for two-page abstracts.

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=\linewidth]{sample-franklin}
%  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
%    Ewing, Inc. [Public domain], via Wikimedia
%    Commons. (\url{https://goo.gl/VLCRBB}).}
%  \Description{The 1907 Franklin Model D roadster.}
%\end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
{\bfseries also} include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed {\itshape below} the figure.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of BibTeX for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the BibTeX file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, an article in a proceedings (of a conference,
  symposium, workshop for example) (paginated proceedings article)
  \cite{Andler79}, a proceedings article with all possible elements
  \cite{Smith10}, an example of an enumerated proceedings article
  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
  doctoral dissertation \cite{Clarkson85}, a master's thesis:
  \cite{anisi03}, an online document / world wide web resource
  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
  (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2019-08-19 Tex/acmart-master/paper_ICSE_rev0.tex
ICSE paper

--- 2019-05-07 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
@@
-\documentclass[10pt,conference]{IEEEtran}
-% \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\bibliographystyle{IEEEtran}
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
+%%
+%% This is file `sample-sigconf.tex',
+%% generated with the docstrip utility.
+%%
+%% The original source files were:
+%%
+%% samples.dtx  (with options: `sigconf')
+%% 
+%% IMPORTANT NOTICE:
+%% 
+%% For the copyright see the source file.
+%% 
+%% Any modified versions of this file must be renamed
+%% with new filenames distinct from sample-sigconf.tex.
+%% 
+%% For distribution of the original source see the terms
+%% for copying and modification in the file samples.dtx.
+%% 
+%% This generated file may be distributed as long as the
+%% original source files, as listed above, are part of the
+%% same distribution. (The sources need not necessarily be
+%% in the same archive or directory.)
+%%
+%% The first command in your LaTeX source must be the \documentclass command.
+\documentclass[sigconf,review]{acmart}
 \usepackage{algorithm,algorithmic}
-\usepackage{graphicx}
 \usepackage{makecell}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\def \BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 
- \renewcommand{\baselinestretch}{0.965}
+%%
+%% \BibTeX command to typeset BibTeX logo in the docs
+%\AtBeginDocument{%
+%  \providecommand\BibTeX{{%
+%    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
 
+%% Rights management information.  This information is sent to you
+%% when you complete the rights form.  These commands have SAMPLE
+%% values in them; it is your responsibility as an author to replace
+%% the commands and values with those provided to you when you
+%% complete the rights form.
+%\setcopyright{acmcopyright}
+%\copyrightyear{2018}
+%\acmYear{2018}
+%\acmDOI{10.1145/1122445.1122456}
+
+%% These commands are for a PROCEEDINGS abstract or paper.
+%\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
+%  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
+%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
+%  June 03--05, 2018, Woodstock, NY}
+%\acmPrice{15.00}
+%\acmISBN{978-1-4503-9999-9/18/06}
+
+%%
+%% Submission ID.
+%% Use this when submitting an article to a sponsored event. You'll
+%% receive a unique submission ID from the organizers
+%% of the event, and this ID should be used as the parameter to this command.
+%%\acmSubmissionID{123-A56-BU3}
+
+%%
+%% The majority of ACM publications use numbered citations and
+%% references.  The command \citestyle{authoryear} switches to the
+%% "author year" style.
+%%
+%% If you are preparing content for an event
+%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
+%% citations and references.
+%% Uncommenting
+%% the next command will enable that style.
+%%\citestyle{acmauthoryear}
+
+%%
+%% end of the preamble, start of the body of the document source.
 \begin{document}
 
+%%
+%% The "title" command has an optional parameter,
+%% allowing the author to define a "short title" to be used in page headers.
 \title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems}
-%
-%\author{\IEEEauthorblockN{Alessandro Trindade}
-%\IEEEauthorblockA{
-%\textit{Federal University of Amazonas}, Brazil \\
-%alessandrotrindade@ufam.edu.br}
-%\and
-%\IEEEauthorblockN{Lucas Cordeiro}
-%\IEEEauthorblockA{
-%\textit{University of Manchester}, UK \\
-%lucas.cordeiro@manchester.ac.uk }
-%}
-%
-\maketitle
 
+%%
+%% The "author" command and its associated commands are used to define
+%% the authors and their affiliations.
+%% Of note is the shared affiliation of the first two authors, and the
+%% "authornote" and "authornotemark" commands
+%% used to denote shared contribution to the research.
+\author{Alessandro Trindade}
+%\authornote{Both authors contributed equally to this research.}
+\email{alessandrotrindade@ufam.edu.br}
+\affiliation{%
+  \institution{Federal University of Amazonas}
+  \streetaddress{Av. Rodrigo Otavio 3000, Campus Universitario}
+  \city{Manaus}
+  \country{Brazil}
+  \postcode{69077-000}
+}
+
+\author{Lucas Cordeiro}
+\email{lucas.cordeiro@manchester.ac.uk}
+\affiliation{%
+  \institution{The University of Oxford}
+  \city{Manchester}
+  \country{UK}
+}
+
+%%
+%% By default, the full list of authors will be used in the page
+%% headers. Often, this list is too long, and will overlap
+%% other information printed in the page headers. This command allows
+%% the author to define a more concise list
+%% of authors' names for this purpose.
+\renewcommand{\shortauthors}{Trindade and Cordeiro.}
+
+%%
+%% The abstract is a short summary of the work to be presented in the
+%% article.
 \begin{abstract}
@@
 
-\begin{IEEEkeywords}
-automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
-\end{IEEEkeywords}
+%%
+%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+%% Please copy and paste the code instead of the example below.
+%%
+\begin{CCSXML}
+<ccs2012>
+ <concept>
+  <concept_id>10010520.10010553.10010562</concept_id>
+  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+  <concept_significance>500</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010575.10010755</concept_id>
+  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+  <concept_significance>300</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010553.10010554</concept_id>
+  <concept_desc>Computer systems organization~Robotics</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10003033.10003083.10003095</concept_id>
+  <concept_desc>Networks~Network reliability</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Computer systems organization~Embedded systems}
+\ccsdesc[300]{Computer systems organization~Redundancy}
+\ccsdesc{Computer systems organization~Robotics}
+\ccsdesc[100]{Networks~Network reliability}
+
+%%
+%% Keywords. The author(s) should pick words that accurately describe
+%% the work being presented. Separate the keywords with commas.
+\keywords{automated verification, model checking, program synthesis, cyber-physical systems , solar photovoltaic systems.}
+
+%% A "teaser" image appears between the author and affiliation
+%% information and the body of the document, and typically spans the
+%% page.
+%\begin{teaserfigure}
+%  \includegraphics[width=\textwidth]{sampleteaser}
+%  \caption{Seattle Mariners at Spring Training, 2010.}
+%  \Description{Enjoying the baseball game from the third-base
+%  seats. Ichiro Suzuki preparing to bat.}
+%  \label{fig:teaser}
+%\end{teaserfigure}
+
+%%
+%% This command processes the author and affiliation and title
+%% information and builds the first part of the formatted document.
+\maketitle
 
@@
 Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
-%
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{trindadeThesis_menor}{}
-%\vspace{12pt}
+
+\section{Authors and Affiliations}
+
+Each author must be defined separately for accurate metadata
+identification. Multiple authors may share one affiliation. Authors'
+names should not be abbreviated; use full first names wherever
+possible. Include authors' e-mail addresses whenever possible.
+
+Grouping authors' names or e-mail addresses, or providing an ``e-mail
+alias,'' as shown below, is not acceptable:
+\begin{verbatim}
+  \author{Brooke Aster, David Mehldau}
+  \email{dave,judy,steve@university.edu}
+  \email{firstname.lastname@phillips.org}
+\end{verbatim}
+
+The \verb|authornote| and \verb|authornotemark| commands allow a note
+to apply to multiple authors --- for example, if the first two authors
+of an article contributed equally to the work.
+
+If your author list is lengthy, you must define a shortened version of
+the list of authors to be used in the page headers, to prevent
+overlapping text. The following command should be placed just after
+the last \verb|\author{}| definition:
+\begin{verbatim}
+  \renewcommand{\shortauthors}{McCartney, et al.}
+\end{verbatim}
+Omitting this command will force the use of a concatenated list of all
+of the authors' names, which may result in overlapping text in the
+page headers.
+
+The article template's documentation, available at
+\url{https://www.acm.org/publications/proceedings-template}, has a
+complete explanation of these commands and tips for their effective
+use.
+
+\section{Rights Information}
+
+Authors of any work published by ACM will need to complete a rights
+form. Depending on the kind of work, and the rights management choice
+made by the author, this may be copyright transfer, permission,
+license, or an OA (open access) agreement.
+
+Regardless of the rights management choice, the author will receive a
+copy of the completed rights form once it has been submitted. This
+form contains \LaTeX\ commands that must be copied into the source
+document. When the document source is compiled, these commands and
+their parameters add formatted text to several areas of the final
+document:
+\begin{itemize}
+\item the ``ACM Reference Format'' text on the first page.
+\item the ``rights management'' text on the first page.
+\item the conference information in the page header(s).
+\end{itemize}
+
+Rights information is unique to the work; if you are preparing several
+works for an event, make sure to use the correct set of commands with
+each of the works.
+
+\section{CCS Concepts and User-Defined Keywords}
+
+Two elements of the ``acmart'' document class provide powerful
+taxonomic tools for you to help readers find your work in an online
+search.
+
+The ACM Computing Classification System ---
+\url{https://www.acm.org/publications/class-2012} --- is a set of
+classifiers and concepts that describe the computing
+discipline. Authors can select entries from this classification
+system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
+commands to be included in the \LaTeX\ source.
+
+User-defined keywords are a comma-separated list of words and phrases
+of the authors' choosing, providing a more flexible way of describing
+the research being presented.
+
+CCS concepts and user-defined keywords are required for all short- and
+full-length articles, and optional for two-page abstracts.
+
+\section{Sectioning Commands}
+
+Your work should use standard \LaTeX\ sectioning commands:
+\verb|section|, \verb|subsection|, \verb|subsubsection|, and
+\verb|paragraph|. They should be numbered; do not remove the numbering
+from the commands.
+
+Simulating a sectioning command by setting the first word or words of
+a paragraph in boldface or italicized text is {\bfseries not allowed.}
+
+\section{Tables}
+
+The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
+package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
+high-quality tables.
+
+Table captions are placed {\itshape above} the table.
+
+Because tables cannot be split across pages, the best placement for
+them is typically the top of the page nearest their initial cite.  To
+ensure this proper ``floating'' placement of tables, use the
+environment \textbf{table} to enclose the table's contents and the
+table caption.  The contents of the table itself must go in the
+\textbf{tabular} environment, to be aligned properly in rows and
+columns, with the desired horizontal and vertical rules.  Again,
+detailed instructions on \textbf{tabular} material are found in the
+\textit{\LaTeX\ User's Guide}.
+
+Immediately following this sentence is the point at which
+Table~\ref{tab:freq} is included in the input file; compare the
+placement of the table here with the table in the printed output of
+this document.
+
+\begin{table}
+  \caption{Frequency of Special Characters}
+  \label{tab:freq}
+  \begin{tabular}{ccl}
+    \toprule
+    Non-English or Math&Frequency&Comments\\
+    \midrule
+    \O & 1 in 1,000& For Swedish names\\
+    $\pi$ & 1 in 5& Common in math\\
+    \$ & 4 in 5 & Used in business\\
+    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+  \bottomrule
+\end{tabular}
+\end{table}
+
+To set a wider table, which takes up the whole width of the page's
+live area, use the environment \textbf{table*} to enclose the table's
+contents and the table caption.  As with a single-column table, this
+wide table will ``float'' to a location deemed more
+desirable. Immediately following this sentence is the point at which
+Table~\ref{tab:commands} is included in the input file; again, it is
+instructive to compare the placement of the table here with the table
+in the printed output of this document.
+
+\begin{table*}
+  \caption{Some Typical Commands}
+  \label{tab:commands}
+  \begin{tabular}{ccl}
+    \toprule
+    Command &A Number & Comments\\
+    \midrule
+    \texttt{{\char'134}author} & 100& Author \\
+    \texttt{{\char'134}table}& 300 & For tables\\
+    \texttt{{\char'134}table*}& 400& For wider tables\\
+    \bottomrule
+  \end{tabular}
+\end{table*}
+
+\section{Math Equations}
+You may want to display math equations in three distinct styles:
+inline, numbered or non-numbered display.  Each of the three are
+discussed in the next sections.
+
+\subsection{Inline (In-text) Equations}
+A formula that appears in the running text is called an inline or
+in-text formula.  It is produced by the \textbf{math} environment,
+which can be invoked with the usual
+\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
+the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
+and structures, from $\alpha$ to $\omega$, available in
+\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
+examples of in-text equations in context. Notice how this equation:
+\begin{math}
+  \lim_{n\rightarrow \infty}x=0
+\end{math},
+set here in in-line math style, looks slightly different when
+set in display style.  (See next section).
+
+\subsection{Display Equations}
+A numbered display equation---one set off by vertical space from the
+text and centered horizontally---is produced by the \textbf{equation}
+environment. An unnumbered display equation is produced by the
+\textbf{displaymath} environment.
+
+Again, in either environment, you can use any of the symbols and
+structures available in \LaTeX\@; this section will just give a couple
+of examples of display equations in context.  First, consider the
+equation, shown as an inline equation above:
+\begin{equation}
+  \lim_{n\rightarrow \infty}x=0
+\end{equation}
+Notice how it is formatted somewhat differently in
+the \textbf{displaymath}
+environment.  Now, we'll enter an unnumbered equation:
+\begin{displaymath}
+  \sum_{i=0}^{\infty} x + 1
+\end{displaymath}
+and follow it with another numbered equation:
+\begin{equation}
+  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
+\end{equation}
+just to demonstrate \LaTeX's able handling of numbering.
+
+\section{Figures}
+
+The ``\verb|figure|'' environment should be used for figures. One or
+more images can be placed within a figure. If your figure contains
+third-party material, you must clearly identify it as such, as shown
+in the example below.
+%\begin{figure}[h]
+%  \centering
+%  \includegraphics[width=\linewidth]{sample-franklin}
+%  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
+%    Ewing, Inc. [Public domain], via Wikimedia
+%    Commons. (\url{https://goo.gl/VLCRBB}).}
+%  \Description{The 1907 Franklin Model D roadster.}
+%\end{figure}
+
+Your figures should contain a caption which describes the figure to
+the reader. Figure captions go below the figure. Your figures should
+{\bfseries also} include a description suitable for screen readers, to
+assist the visually-challenged to better understand your work.
+
+Figure captions are placed {\itshape below} the figure.
+
+\section{Citations and Bibliographies}
+
+The use of BibTeX for the preparation and formatting of one's
+references is strongly recommended. Authors' names should be complete
+--- use full first names (``Donald E. Knuth'') not initials
+(``D. E. Knuth'') --- and the salient identifying features of a
+reference should be included: title, year, volume, number, pages,
+article DOI, etc.
+
+The bibliography is included in your source document with these two
+commands, placed just before the \verb|\end{document}| command:
+\begin{verbatim}
+  \bibliographystyle{ACM-Reference-Format}
+  \bibliography{bibfile}
+\end{verbatim}
+where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
+suffix, of the BibTeX file.
+
+Citations and references are numbered by default. A small number of
+ACM publications have citations and references formatted in the
+``author year'' style; for these exceptions, please include this
+command in the {\bfseries preamble} (before
+``\verb|\begin{document}|'') of your \LaTeX\ source:
+\begin{verbatim}
+  \citestyle{acmauthoryear}
+\end{verbatim}
+
+  Some examples.  A paginated journal article \cite{Abril07}, an
+  enumerated journal article \cite{Cohen07}, a reference to an entire
+  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
+  monograph/whole book in a series (see 2a in spec. document)
+  \cite{Harel79}, a divisible-book such as an anthology or compilation
+  \cite{Editor00} followed by the same example, however we only output
+  the series if the volume number is given \cite{Editor00a} (so
+  Editor00a's series should NOT be present since it has no vol. no.),
+  a chapter in a divisible book \cite{Spector90}, a chapter in a
+  divisible book in a series \cite{Douglass98}, a multi-volume work as
+  book \cite{Knuth97}, an article in a proceedings (of a conference,
+  symposium, workshop for example) (paginated proceedings article)
+  \cite{Andler79}, a proceedings article with all possible elements
+  \cite{Smith10}, an example of an enumerated proceedings article
+  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
+  doctoral dissertation \cite{Clarkson85}, a master's thesis:
+  \cite{anisi03}, an online document / world wide web resource
+  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
+  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
+  (Case 3) a patent \cite{JoeScientist001}, work accepted for
+  publication \cite{rous08}, 'YYYYb'-test for prolific author
+  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
+  contain 'duplicate' DOI and URLs (some SIAM articles)
+  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
+  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
+  couple of citations with DOIs:
+  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
+  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
+  \cite{R} and \cite{UMassCitations}.
+
+\section{Acknowledgments}
+
+Identification of funding sources and other support, and thanks to
+individuals and groups that assisted in the research and the
+preparation of the work should be included in an acknowledgment
+section, which is placed just before the reference section in your
+document.
+
+This section has a special environment:
+\begin{verbatim}
+  \begin{acks}
+  ...
+  \end{acks}
+\end{verbatim}
+so that the information contained therein can be more easily collected
+during the article metadata extraction phase, and to ensure
+consistency in the spelling of the section heading.
+
+Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
+
+%%
+%% The acknowledgments section is defined using the "acks" environment
+%% (and NOT an unnumbered section). This ensures the proper
+%% identification of the section in the article metadata, and the
+%% consistent spelling of the heading.
+\begin{acks}
+To Robert, for the bagels and explaining CMYK and color spaces.
+\end{acks}
+
+%%
+%% The next two lines define the bibliography style to be used, and
+%% the bibliography file.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{trindadeThesis}
+
+%%
+%% If your work has an appendix, this is the place to put it.
+
 \end{document}
+%\endinput
+%%
+%% End of file `sample-sigconf.tex'.

### 2019-08-19 Tex/acmart-master/paper_ICSE_rev0.tex
ICSE paper

@@
 <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+<concept_id>10011007.10010940.10010992.10010998.10003791</concept_id>
+<concept_desc>Software and its engineering~Model checking</concept_desc>
 <concept_significance>500</concept_significance>
@@
 <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+<concept_id>10011007.10011074.10011099.10011692</concept_id>
+<concept_desc>Software and its engineering~Formal software verification</concept_desc>
 <concept_significance>300</concept_significance>
@@
 <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
+<concept_id>10010583.10010662.10010663.10010666</concept_id>
+<concept_desc>Hardware~Renewable energy</concept_desc>
+<concept_significance>300</concept_significance>
 </concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Software and its engineering~Model checking}
+\ccsdesc[300]{Software and its engineering~Formal software verification}
+\ccsdesc[300]{Hardware~Renewable energy}
 

### 2019-08-21 Tex/acmart-master/paper_ICSE_rev0.tex
ICSE paper

--- 2019-05-07 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
@@
-\documentclass[10pt,conference]{IEEEtran}
-% \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\bibliographystyle{IEEEtran}
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
+%%
+%% This is file `sample-sigconf.tex',
+%% generated with the docstrip utility.
+%%
+%% The original source files were:
+%%
+%% samples.dtx  (with options: `sigconf')
+%% 
+%% IMPORTANT NOTICE:
+%% 
+%% For the copyright see the source file.
+%% 
+%% Any modified versions of this file must be renamed
+%% with new filenames distinct from sample-sigconf.tex.
+%% 
+%% For distribution of the original source see the terms
+%% for copying and modification in the file samples.dtx.
+%% 
+%% This generated file may be distributed as long as the
+%% original source files, as listed above, are part of the
+%% same distribution. (The sources need not necessarily be
+%% in the same archive or directory.)
+%%
+%% The first command in your LaTeX source must be the \documentclass command.
+\documentclass[sigconf,review]{acmart}
 \usepackage{algorithm,algorithmic}
-\usepackage{graphicx}
 \usepackage{makecell}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\def \BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 
- \renewcommand{\baselinestretch}{0.965}
+%%
+%% \BibTeX command to typeset BibTeX logo in the docs
+%\AtBeginDocument{%
+%  \providecommand\BibTeX{{%
+%    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
 
+%% Rights management information.  This information is sent to you
+%% when you complete the rights form.  These commands have SAMPLE
+%% values in them; it is your responsibility as an author to replace
+%% the commands and values with those provided to you when you
+%% complete the rights form.
+%\setcopyright{acmcopyright}
+%\copyrightyear{2018}
+%\acmYear{2018}
+%\acmDOI{10.1145/1122445.1122456}
+
+%% These commands are for a PROCEEDINGS abstract or paper.
+\acmConference[ICSE 2020]{Seoul: 42nd International Conference on Software Engineering}{May 23--29, 2020}{Seoul, South Korea}
+%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
+%  June 03--05, 2018, Woodstock, NY}
+%\acmPrice{15.00}
+%\acmISBN{978-1-4503-9999-9/18/06}
+
+%%
+%% Submission ID.
+%% Use this when submitting an article to a sponsored event. You'll
+%% receive a unique submission ID from the organizers
+%% of the event, and this ID should be used as the parameter to this command.
+%%\acmSubmissionID{123-A56-BU3}
+
+%%
+%% The majority of ACM publications use numbered citations and
+%% references.  The command \citestyle{authoryear} switches to the
+%% "author year" style.
+%%
+%% If you are preparing content for an event
+%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
+%% citations and references.
+%% Uncommenting
+%% the next command will enable that style.
+%%\citestyle{acmauthoryear}
+
+%%
+%% end of the preamble, start of the body of the document source.
 \begin{document}
 
+%%
+%% The "title" command has an optional parameter,
+%% allowing the author to define a "short title" to be used in page headers.
 \title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems}
-%
-%\author{\IEEEauthorblockN{Alessandro Trindade}
-%\IEEEauthorblockA{
-%\textit{Federal University of Amazonas}, Brazil \\
-%alessandrotrindade@ufam.edu.br}
-%\and
-%\IEEEauthorblockN{Lucas Cordeiro}
-%\IEEEauthorblockA{
-%\textit{University of Manchester}, UK \\
-%lucas.cordeiro@manchester.ac.uk }
-%}
-%
-\maketitle
 
+%%
+%% The "author" command and its associated commands are used to define
+%% the authors and their affiliations.
+%% Of note is the shared affiliation of the first two authors, and the
+%% "authornote" and "authornotemark" commands
+%% used to denote shared contribution to the research.
+\author{Alessandro Trindade}
+%\authornote{Both authors contributed equally to this research.}
+\email{alessandrotrindade@ufam.edu.br}
+\affiliation{%
+  \institution{Federal University of Amazonas}
+  \streetaddress{Av. Rodrigo Otavio 3000, Campus Universitario}
+  \city{Manaus}
+  \country{Brazil}
+  \postcode{69077-000}
+}
+
+\author{Lucas Cordeiro}
+\email{lucas.cordeiro@manchester.ac.uk}
+\affiliation{%
+  \institution{The University of Manchester}
+  \city{Manchester}
+  \country{UK}
+}
+
+%%
+%% By default, the full list of authors will be used in the page
+%% headers. Often, this list is too long, and will overlap
+%% other information printed in the page headers. This command allows
+%% the author to define a more concise list
+%% of authors' names for this purpose.
+\renewcommand{\shortauthors}{Trindade and Cordeiro.}
+
+%%
+%% The abstract is a short summary of the work to be presented in the
+%% article.
 \begin{abstract}
@@
 In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
-The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained.
+The optimal solution is then verified via symbolic model checking; if the verification step fails, a bound is increased and the process iterates until an optimal sizing is obtained.
 Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
@@
 
-\begin{IEEEkeywords}
-automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
-\end{IEEEkeywords}
+%%
+%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+%% Please copy and paste the code instead of the example below.
+%%
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10011007.10010940.10010992.10010998.10003791</concept_id>
+<concept_desc>Software and its engineering~Model checking</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011074.10011099.10011692</concept_id>
+<concept_desc>Software and its engineering~Formal software verification</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10010583.10010662.10010663.10010666</concept_id>
+<concept_desc>Hardware~Renewable energy</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Software and its engineering~Model checking}
+\ccsdesc[300]{Software and its engineering~Formal software verification}
+\ccsdesc[300]{Hardware~Renewable energy}
+
+%%
+%% Keywords. The author(s) should pick words that accurately describe
+%% the work being presented. Separate the keywords with commas.
+\keywords{automated verification, model checking, program synthesis, cyber-physical systems , solar photovoltaic systems.}
+
+%% A "teaser" image appears between the author and affiliation
+%% information and the body of the document, and typically spans the
+%% page.
+%\begin{teaserfigure}
+%  \includegraphics[width=\textwidth]{sampleteaser}
+%  \caption{Seattle Mariners at Spring Training, 2010.}
+%  \Description{Enjoying the baseball game from the third-base
+%  seats. Ichiro Suzuki preparing to bat.}
+%  \label{fig:teaser}
+%\end{teaserfigure}
+
+%%
+%% This command processes the author and affiliation and title
+%% information and builds the first part of the formatted document.
+\maketitle
 
@@
 Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
-%
+
 %-----------------------------------------------------------
@@
 %-----------------------------------------------------------
-%
+
 %-----------------------------------------------------------
@@
 %-----------------------------------------------------------
-%
+
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
@@
 If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
-%
+
 \begin{figure}[h]
@@
 \end{figure}
-%
+
 One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
@@
 here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
-%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
@@
 That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+
 \begin{figure}[h]
@@
 \end{figure}
-\\
+
 %
 The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
-%
+
 Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+
 \begin{equation}
 \label{eq:Ecorrected}
-\scriptstyle E_{corrected} = \dfrac{\scriptstyle E_{consumption}}{ \scriptstyle \eta_{b} \eta_{c} \eta_{i} }.
+E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
 \end{equation}
-%
+
 We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
-%
+
 \begin{equation}
 \label{eq:Ep}
-\scriptstyle E_{p} = \scriptstyle Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
+E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
 \end{equation}
-%
+
 \noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
 the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-%
+
 The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
-%
+
 \begin{equation}
 \label{eq:NTPmin}
-\scriptstyle N_{TPmin} = \dfrac{\scriptstyle E_{corrected}}{\scriptstyle E_{p}}.
+N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
 \end{equation}
@@
 Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
-%
+
 \begin{equation}
 \label{eq:NPSmin}
-\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}},
+\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
 \end{equation}
-%
+
 \begin{equation}
 \label{eq:NPPmin}
-\scriptstyle N_{PPmin} = \dfrac{\scriptstyle P_{total}}{\scriptstyle Number\,Panels\,Series \scriptstyle \times \scriptstyle P_{max,ref}},
+N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
 \end{equation}
-%
+
 \noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
 %, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
-%
+
 Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
+
 \begin{equation}
 \label{eq:Cbank}
-\scriptstyle C_{bank} \scriptstyle = \dfrac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD},
+C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
 \end{equation}
-%
+
 \noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
 $ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-%
+
 Secondly, the total (minimum) number of batteries is computed as
+
 \begin{equation}
 \label{eq:Nbtotal}
-\scriptstyle N_{B}total = \scriptstyle N_{BS}min \scriptstyle \times \scriptstyle N_{BP}min = \dfrac{\scriptstyle V_{system}}{\scriptstyle V_{bat}} \scriptstyle \times \dfrac{\scriptstyle C_{bank}}{\scriptstyle 1 \,Battery \, Capacity}.
+N_{B}total = N_{BS}min \times N_{BP}min.
 \end{equation}
-%
+
+\begin{equation}
+\label{eq:Nbtotal2}
+N_{B}total = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
+\end{equation}
+
 Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage:
+
 \begin{equation}
 \label{eq:vcvsystem}
-\scriptstyle V_{c} = \scriptstyle V_{system}.
+V_{c} = V_{system}.
 \end{equation}
-%
+
 The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as
-%
+
 \begin{equation}
 \label{eq:iscamb}
-\scriptstyle I_{sc,amb} = \dfrac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
+I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
 \end{equation}
-%
+
 The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin} as
+
 \begin{equation}
 \label{eq:icmin}
-\scriptstyle I_{c,min} = \scriptstyle I_{sc,amb} \times \scriptstyle N_{PP},
+I_{c,min} = I_{sc,amb} \times N_{PP},
 \end{equation}
-%
+
 \begin{equation}
 \label{eq:icicmin}
-\scriptstyle I_{c} \geq \scriptstyle I_{c,min}.
+I_{c} \geq I_{c,min}.
 \end{equation}
-%
+
 The inverter sizing check is performed by means of three equations.
@@
 Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
-%
+
 \begin{equation}
 \label{eq:vindc} 
-\scriptstyle V_{in}DC = \scriptstyle V_{system}.
+V_{in}DC = V_{system}.
 \end{equation}
-%
+
 \begin{equation}
 \label{eq:voutac} 
-\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
+V_{out}AC = V_{AC}.
 \end{equation}
-%
+
 \begin{equation}
 \label{eq:invcheck} 
-\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
+\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
 \end{equation}
+
 % -------------------------------------------------------
@@
 % -------------------------------------------------------
-%
+
 %%%To select an optimal combination of components from a PV system to meet sizing constraints, 
@@
 Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+
 %------------------------------------------------------
@@
 %------------------------------------------------------
+
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
-%
+
  \begin{algorithm}
@@
  \begin{algorithmic}[1]
- \begin{scriptsize}
+% \begin{scriptsize}
  \renewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
  \RETURN $(\,)$ 
-  \end{scriptsize}
+%  \end{scriptsize}
  \end{algorithmic} 
@@
  \end{algorithm}
-%
 
@@
 Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
+
 \textbf{Case studies.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
@@
 %used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
-\begin{table}
+
+\begin{table*}
 \caption{Case studies and Results: optimization of PV systems.}\label{tab1}
@@
 %\end{scriptsize}
-\end{table}
+\end{table*}
 %
@@
 Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
-%
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{trindadeThesis_menor}{}
-%\vspace{12pt}
+
+%%
+%% The acknowledgments section is defined using the "acks" environment
+%% (and NOT an unnumbered section). This ensures the proper
+%% identification of the section in the article metadata, and the
+%% consistent spelling of the heading.
+\begin{acks}
+The authors would like to thank: (i) Newton Fund [grant number $261881580$] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa $2018$], for the DCTIEX II scholarship (NOV-$2018$), and for support the research mobility to UK; and (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$).
+\end{acks}
+
+%%
+%% The next two lines define the bibliography style to be used, and
+%% the bibliography file.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{trindadeThesis}
+
+%%
+%% If your work has an appendix, this is the place to put it.
+
 \end{document}
+%\endinput
+%%
+%% End of file `sample-sigconf.tex'.

### 2019-08-22 Tex/acmart-master/paper_ICSE_rev0.tex
ICSE paper

@@
 \begin{abstract}
-Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space.
+Currently, there exist various state-of-the-art tools to size solar photovoltaic systems, but they are mainly based on simulations and do not cover all aspects of the design-space.
 We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
-The optimal solution is then verified via symbolic model checking; if the verification step fails, a bound is increased and the process iterates until an optimal sizing is obtained.
-Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
+The focus is in a new computer optimization method and not in criteria or objectives for optimization which were investigated in prior studies over the last two decades.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first, starting from user requirements and a list of commercial equipment, we synthesize a feasible sizing solution of a given stand-alone PV system; secondly, the optimal solution is then verified via symbolic model checking to check if the cost is the lowest among the feasible solutions; if the verification step fails, a bound is adjusted and the process iterates until an optimal sizing is obtained.
+Therefore, candidate solutions are derived from financial analysis of the obtained sizing.
 Our synthesis method is novel and unprecedented to streamline the design of PV systems.
@@
 Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
-Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
+
+Worth to mention that energy production, distribution, and optimization are all CPS problems~\cite{UC}.
 
@@
 
-However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
+Note that in this study, our focus is not on a novel criteria or even optimization objectives.
+Instead, our novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods
+
+However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, its can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
 Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
@@
 \sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
-The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
+The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vector part.
 Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
 
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated.
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vector {\sc inputs} that is incrementally updated.
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
@@
 
+%---------------------------------------------------------------------------
+\section{Conclusions and Future Work}
+%---------------------------------------------------------------------------
+
+We have described and evaluated an automated synthesis method 
+to obtain the optimal size of PV system using software model 
+checking techniques.
+The focus was on the method to obtain the optimal solution, based on formal methods that can cover the design-space better than simulation tools.
+We have considered seven case studies
+from PV systems in two different sites of the Amazonas State 
+in Brazil, ranging from $253$\,W to $1,586$\,W peak; and 
+three state-of-art verification engines were considered 
+(ESBMC, CBMC, and CPAchecker), in addition to a specialized 
+off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+
+Our automated synthesis tool presented detailed optimal solution 
+to six case studies adopted in this paper, with specifications, 
+models, and the arrangement in terms of series-parallel connections, 
+thereby covering the charge controller, which was not presented by HOMER Pro. 
+In a nutshell, our automated synthesis tool took more time 
+to find the optimal solution than HOMER Pro; however, the presented 
+solution was more complete and detailed, which is very useful 
+to a user to get a list of equipment and go to shopping.
+
+As future work, the authors plan to improve the power reliability analysis, 
+to address the restriction to only allow automated synthesis of 
+riverside communities in the Amazonas state (Brazil), and to 
+validate some cases with deployed PV systems in isolated communities.
+
+Use of simulation to compare the tools!!!!!!!!!!!!!!!!
+
 %%

### 2019-08-22 Tex/acmart-master/paper_ICSE_rev0.tex
ICSE paper

@@
 \begin{abstract}
-Currently, there exist various state-of-the-art tools to size solar photovoltaic systems, but they are mainly based on simulations and do not cover all aspects of the design-space.
+Considering the last two decades, most of the effort related to optimal sizing of stand-alone solar photovoltaic systems was toward optimization criteria and/or objectives.
+Very few was devoted to the computing method of optimization.
+There exist various state-of-the-art tools to size solar photovoltaic systems, but they are mainly based on simulations and do not cover all aspects of the design-space.
 We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis.
-The focus is in a new computer optimization method and not in criteria or objectives for optimization which were investigated in prior studies over the last two decades.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first, starting from user requirements and a list of commercial equipment, we synthesize a feasible sizing solution of a given stand-alone PV system; secondly, the optimal solution is then verified via symbolic model checking to check if the cost is the lowest among the feasible solutions; if the verification step fails, a bound is adjusted and the process iterates until an optimal sizing is obtained.
+The focus is in a new computer optimization method.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first, starting from user requirements and a list of commercial equipment, we synthesize a feasible sizing solution of a given stand-alone PV system; secondly, the optimal solution is then verified via symbolic model checking to guarantee that the cost is the lowest among the feasible solutions; if the verification step fails, a bound is adjusted and the process iterates until an optimal sizing is obtained.
 Therefore, candidate solutions are derived from financial analysis of the obtained sizing.
@@
 %While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+
 Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS.
@@
 Worth to mention that energy production, distribution, and optimization are all CPS problems~\cite{UC}.
-
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
@@
  However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+
 Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.
@@
 However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, its can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
-Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Here, we use counterexample guided inductive synthesis (CEGIS) variation for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
 Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$.
 In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
-The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.
+The optimal solution is then verified via symbolic model checking; if the verification step succed, the method returns to the synthesis phase and a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.
 
@@
 Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented.
-Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries)
-can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
+Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
 Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
+
+As a result, our study marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.
+Thus, we considerably advance the state-of-the-art in applied energy over the last two decades
+with the goal of optimally designing PV systems.
 
@@
 
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
+A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
@@
 The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}.
+
 Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
@@
 Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+
 Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
@@
 
-\textbf{Case studies.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
+At this section, the case studies, the setup of experimentation, the verifiers, the objectives, and the results are presented.
+
+\subsection{Case studies}
+
+We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach, based on the electrical load of usual riverside communities of Amazonas State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+
 Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems.
@@
 
-\textbf{Setup.} All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
+\subsection{Setup}
+
+All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
 The experiments were performed with a predefined timeout of $240$ minutes.
 
-\textbf{Objectives.} Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, and \textit{RQ2} (performance) How do the software verifiers compare to each other?
+\subsection{Objectives}
 
-\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
+Our evaluation aims to answer two research questions:
+
+\textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, and
+
+\textit{RQ2} (performance) How do the software verifiers compare to each other?
+
+\subsection{Results}
+
+CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively.
+
 The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}.
+
 The results were tested by manual PV sizing and were sound (\textit{RQ1}).
@@
 \end{table*}
-%
 
-\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
+\subsection{Threats to validity}
+
+We have reported a favorable assessment of the proposed method.
+Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work:
+
+(1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate;
+
+(2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper;
+
+(3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and
+
+(4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
 
@@
 The focus was on the method to obtain the optimal solution, based on formal methods that can cover the design-space better than simulation tools.
-We have considered seven case studies
-from PV systems in two different sites of the Amazonas State 
-in Brazil, ranging from $253$\,W to $1,586$\,W peak; and 
-three state-of-art verification engines were considered 
-(ESBMC, CBMC, and CPAchecker), in addition to a specialized 
-off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+We have considered two case studies and three state-of-art verification engines were considered
+(ESBMC, CBMC, and CPAchecker) in order to compare the results.
 
-Our automated synthesis tool presented detailed optimal solution 
-to six case studies adopted in this paper, with specifications, 
+Our automated synthesis tool presented detailed optimal solution, with specifications, 
 models, and the arrangement in terms of series-parallel connections, 
-thereby covering the charge controller, which was not presented by HOMER Pro. 
-In a nutshell, our automated synthesis tool took more time 
-to find the optimal solution than HOMER Pro; however, the presented 
-solution was more complete and detailed, which is very useful 
+The presented solution was more complete and detailed, which is very useful 
 to a user to get a list of equipment and go to shopping.
 
-As future work, the authors plan to improve the power reliability analysis, 
+As future work, the authors plan to use specialized off-the-shelf simulation tool for comparation, to improve the power reliability analysis, 
 to address the restriction to only allow automated synthesis of 
@@
 validate some cases with deployed PV systems in isolated communities.
-
-Use of simulation to compare the tools!!!!!!!!!!!!!!!!
 

### 2019-08-22 Tex/acmart-master/paper_ICSE_rev0.tex
ICSE paper

@@
 The focus is in a new computer optimization method.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first, starting from user requirements and a list of commercial equipment, we synthesize a feasible sizing solution of a given stand-alone PV system; secondly, the optimal solution is then verified via symbolic model checking to guarantee that the cost is the lowest among the feasible solutions; if the verification step fails, a bound is adjusted and the process iterates until an optimal sizing is obtained.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first, starting from design requirements and a list of commercial equipment, we synthesize a feasible sizing solution of a given stand-alone PV system; secondly, the optimal solution is then verified via symbolic model checking to guarantee that the cost is the lowest among the feasible solutions; if the verification step does not fails, a bound is adjusted and the process iterates until an optimal sizing is obtained.
 Therefore, candidate solutions are derived from financial analysis of the obtained sizing.
 Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different intricate case studies.
+Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different case studies very common in rural areas.
 \end{abstract}
@@
 In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
-The optimal solution is then verified via symbolic model checking; if the verification step succed, the method returns to the synthesis phase and a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.
+The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is generated with the optimal cost for the feasible solution found at the synthesis phase.
+If the verification succeeds, the  method returns to the synthesis engine, with a new bound of search (new possible optimal cost) and the process iterates until an optimal sizing is obtained from financial analysis.
+
+The proposed method differs from traditional CEGIS because the counterexample is not used from the formal verification to create a set of input values for the synthesis phase.
+Moreover, the set of feasible PV sizing solutions from the synthesis phase can be tested more than once at the verification phase, depending on the bound used in each iteration.
 
@@
 %-----------------------------------------------------------
+
+Program synthesis addresses an age-old issue in computer science: can a computer program itself?
+The aim is to avoid errors inputted by programmers during coding (bugs) and to improve productivity.
+Moreover, to compound this risk, today’s highly asynchronous, heterogeneous, and distributed systems are even more prone to programming errors.
+And if we could just tell the computer what it should do — provide it with a specification of what we want — and let it do the legwork of figuring out how to do it?
+This is the promise of program synthesis: given a specification, automatically generate a program that satisfies it~\cite{ACMSigplan}.
+
+Before the computer can automatically generate a program, we need to give it a specification of what the program should do.
+The specification needs to describe the program’s desired behavior in enough detail to ensure the program does what we want, but ideally, it should be much simpler than the program itself, since otherwise we may as well just write the program~\cite{ACMSigplan}.
+In recent years, synthesis has been used for digital control systems design as well, however without application to solar PV systems~\cite{Abateetal2017, Abate2017}.
 
@@
 	\centering
-	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
+	\includegraphics[width=0.85\columnwidth]{fig2_rev2.jpg}
 	\caption{CEGIS applied to PV system sizing.}

### 2019-09-03 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

--- 2019-07-08 Tex/elsevier/trindade_appliedenergy_rev1.tex
@@
-\documentclass[review]{elsarticle}
-
-\usepackage{lineno,hyperref}
-%\modulolinenumbers[5]
+%% bare_jrnl.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% see http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[journal]{IEEEtran}
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[journal]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+%\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+%\usepackage{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
+%
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a larger sans serif font
+% than the serif footnote size font used in traditional IEEE formatting
+% and thus the need to invoke different subfig.sty package options depending
+% on whether compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
+% Axel Sommerfeldt. This package may be useful when used in conjunction with 
+% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
+% submissions have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.4.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/pkg/endfloat
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{graphicx}
+\graphicspath{ {./images/} }
 \usepackage{makecell}
@@
 
-\journal{Applied Energy}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
 
 \begin{document}
-
-\begin{frontmatter}
-
-%\title{Innovative techno-economic optimization of stand-alone solar photovoltaic systems using automated formal synthesis} 
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
 \title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
 %
-%\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
-%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
-%
-%% Group authors per affiliation:
-\author[mymainaddress]{Alessandro Trindade\corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Corresponding author}
-\ead{alessandrotrindade@ufam.edu.br}
-%\ead[url]{www.elsevier.com}
-
-\author[mysecondaryaddress]{Lucas Cordeiro}
-
-\address[mymainaddress]{Federal University of Amazonas, Av. Rodrigo Octávio, 6200, Coroado I, 69077-000 Manaus-AM-Brazil}
-\address[mysecondaryaddress]{University of Manchester, School of Computer Science, Kilburn Building, Manchester M13 9PL}
-
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
+
+\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
+\thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
+\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
+\thanks{Manuscript received September XY, 2019; revised XXXXX 11, 2019.}}
+
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+% 
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+\markboth{IEEE Transactions on Sustainable Energy,~Vol.~XX, No.~YY, September~2019}%
+{Trindade and Cordeiro: An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark.
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% make the title area
+\maketitle
+
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
 \begin{abstract}
@@
 
-\begin{keyword}
-automated verification \sep model checking \sep program synthesis \sep electrical systems \sep solar photovoltaic systems
-\end{keyword}
-
-\end{frontmatter}
-
-%\linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+Automated verification, model checking, program synthesis, electrical systems, solar photovoltaic systems.
+\end{IEEEkeywords}
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
+\section{Introduction}
+% The very first letter is a 2 line initial drop letter followed
+% by the rest of the first word in caps.
+% 
+% form to use if the first word consists of a single letter:
+% \IEEEPARstart{A}{demo} file is ....
+% 
+% form to use if you need the single drop letter followed by
+% normal text (unknown if ever used by the IEEE):
+% \IEEEPARstart{A}{}demo file is ....
+% 
+% Some journals put the first two words in caps:
+% \IEEEPARstart{T}{his demo} file is ....
+% 
+% Here we have the typical use of a "T" for an initial drop letter
+% and "HIS" in caps to complete the first word.
+%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
+%
+\IEEEPARstart{C}{yber}-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
 During operation, such components must frequently adapt to the operating environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
@@
 results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
-%
-%-----------------------------------------------------------
-\section{BACKGROUND}
+
+\section{Background}
 \label{sec:Background}
@@
 approaches in the same experimental setting is intended to be easy and the experimental 
-results are expected to be more meaningful~\citep{Beyer2011}. Related to the architecture, 
+results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, 
 the central data structure is a set of control-flow automata (CFA), which consists of control-flow 
 locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and 
-interpolation procedures~\citep{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
+interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
 and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
@@
 	\centering
-	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
+	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
 	\caption{CEGIS applied to PV system sizing.}
@@
 %------------------------------------------------------
-\section{SYNTHESIZING OPTIMAL SIZING OF STAND-ALONE SOLAR PHOTOVOLTAIC SYSTEMS}
+\section{Synthesizing optimal sizing of stand-alone solar PV systems}
 \label{sec:Method}
@@
 	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
-	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
+	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
 This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
@@
 	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
-By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\citep{Khatib2014}.
+By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
 For critical loads, 99\% is considered acceptable.
@@
 %---------------------------------------------------------------------------
-\section{EXPERIMENTAL EVALUATION}
+\section{Experimental evaluation}
 \label{sec:Results}
@@
 Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
-%
-\begin{table}
+
+\begin{table}[!t]
 \caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CONCLUSIONS}
+\section{Conclusion}
 \label{sec:Conclusion}
@@
 
-\section*{Acknowledgments}
+% An example of a floating figure using the graphicx package.
+% Note that \label must occur AFTER (or within) \caption.
+% For figures, \caption should occur after the \includegraphics.
+% Note that IEEEtran v1.7 and later has special internal code that
+% is designed to preserve the operation of \label within \caption
+% even when the captionsoff option is in effect. However, because
+% of issues like this, it may be the safest practice to put all your
+% \label just after \caption rather than within \caption{}.
+%
+% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
+% option should be used if it is desired that the figures are to be
+% displayed while in draft mode.
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=2.5in]{myfigure}
+% where an .eps filename suffix will be assumed under latex, 
+% and a .pdf suffix will be assumed for pdflatex; or what has been declared
+% via \DeclareGraphicsExtensions.
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure}
+
+% Note that the IEEE typically puts floats only at the top, even when this
+% results in a large percentage of a column being occupied by floats.
+
+% An example of a double column floating figure using two subfigures.
+% (The subfig.sty package must be loaded for this to work.)
+% The subfigure \label commands are set within each subfloat command,
+% and the \label for the overall figure must come after \caption.
+% \hfil is used as a separator to get equal spacing.
+% Watch out that the combined width of all the subfigures on a 
+% line do not exceed the text width or a line break will occur.
+%
+%\begin{figure*}[!t]
+%\centering
+%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
+%\label{fig_first_case}}
+%\hfil
+%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
+%\label{fig_second_case}}
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure*}
+%
+% Note that often IEEE papers with subfigures do not employ subfigure
+% captions (using the optional argument to \subfloat[]), but instead will
+% reference/describe all of them (a), (b), etc., within the main caption.
+% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
+% labels, the optional argument to \subfloat must be present. If a
+% subcaption is not desired, just leave its contents blank,
+% e.g., \subfloat[].
+
+% An example of a floating table. Note that, for IEEE style tables, the
+% \caption command should come BEFORE the table and, given that table
+% captions serve much like titles, are usually capitalized except for words
+% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
+% and up, which are usually not capitalized unless they are the first or
+% last word of the caption. Table text will default to \footnotesize as
+% the IEEE normally uses this smaller font for tables.
+% The \label must come after \caption as always.
+%
+%\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+%\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+%\caption{An Example of a Table}
+%\label{table_example}
+%\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+%\begin{tabular}{|c||c|}
+%\hline
+%One & Two\\
+%\hline
+%Three & Four\\
+%\hline
+%\end{tabular}
+%\end{table}
+
+% Note that the IEEE does not put floats in the very first column
+% - or typically anywhere on the first page for that matter. Also,
+% in-text middle ("here") positioning is typically not used, but it
+% is allowed and encouraged for Computer Society conferences (but
+% not Computer Society journals). Most IEEE journals/conferences use
+% top floats exclusively. 
+% Note that, LaTeX2e, unlike IEEE journals/conferences, places
+% footnotes above bottom floats. This can be corrected via the
+% \fnbelowfloat command of the stfloats package.
+
+% if have a single appendix:
+%\appendix[Proof of the Zonklar Equations]
+% or
+%\appendix  % for no appendix heading
+% do not use \section anymore after \appendix, only \section*
+% is possibly needed
+
+% use appendices with more than one appendix
+% then use \section to start each appendix
+% you must declare a \section before using any
+% \subsection or using \label (\appendices by itself
+% starts a section numbered zero.)
+%
+
+% use section* for acknowledgment
+\section*{Acknowledgment}
+
 The authors would like to thank: (i) Newton Fund [grant number $261881580$] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa $2018$], for the DCTIEX II scholarship (NOV-$2018$), and for support the research mobility to UK; (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and (iv) University of Sheffield's Research England QR GCRF Institutional Allocation for the HOMER Pro license.
 
-%
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
-%\section*{REFERENCES}
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
 \bibliography{trindadeThesis}{}
-%\vspace{12pt}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+%
+%\begin{thebibliography}{1}
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%\end{thebibliography}
+%
+%%%%%%%%%%%%%% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+\begin{IEEEbiography}
+    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alessandro3por4_2}}]{Alessandro Trindade}
+received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
+Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
+Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the Amazonas State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation.
+His interest is in renewable energy, automated verification, and model checking.
+\end{IEEEbiography}
+%
+%\begin{IEEEbiographynophoto}{Alessandro Trindade}
+%received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
+Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
+Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation (Centre of Analysis, Research and Innovation Technology Foundation).
+His interest is in renewable energy, automated verification, and model checking.
+%\end{IEEEbiographynophoto}
+%
+% if you will not have a photo at all:
+\begin{IEEEbiography}
+    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lucas3por4}}]{Lucas Cordeiro}
+received his Ph.D.
+degree in Computer Science in 2011 from the University of Southampton, UK.
+Currently, he is a Senior Lecturer in the School of Computer Science at the University of Manchester, and leads the Systems and Software Verification laboratory.
+He is also a collaborator in the Postgraduate Program in Electrical Engineering and Informatics at the Federal University of Amazonas (UFAM), Brazil.
+Prior to joining the University of Manchester, he worked as a researcher at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for 4 years as software engineer at industry.
+His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.
+\end{IEEEbiography}
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
+% that's all folks
 \end{document}

### 2019-09-10 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 % Do not put math or special symbols in the title.
-\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
+%\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
+\title{Optimal Sizing of Stand-alone Solar Photovoltaic Systems Through Automated Formal Synthesis Method}
 %
@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; however, these existing tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
-Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last two decades.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound cost via symbolic model checking.
+There exist various methods and tools to size solar photovoltaic systems; however, the existing tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
+Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last decades.
+In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound cost via symbolic model checking.
 If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
-Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing.
-We also present a comparative with a specialized simulation tool over real PV systems to show the effectiveness of our approach, which is able to provide more accurate results of optimal sizing of stand-alone PV systems than that existing simulation tool.
+Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis.
+Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal system sizing.
+We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which is able to provide more detailed and accurate solution than the existing simulation tool.
 \end{abstract}

### 2019-09-10 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 %\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
-\title{Optimal Sizing of Stand-alone Solar Photovoltaic Systems Through Automated Formal Synthesis Method}
+\title{Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method}
 %
@@
 %
-\IEEEPARstart{C}{yber}-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
+%\IEEEPARstart{C}{yber}-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
 During operation, such components must frequently adapt to the operating environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
 Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
-
-While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+%
+%While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
 Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing \textit{correct-by-construction} implementations of CPS.
@@
 
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+\IEEEPARstart{L}{ack} of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
 Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}.
@@
 one successful method in this domain is model checking~\cite{Clarke2012}. 
-Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs 
-or proves that they are safe if a completeness threshold is given~\cite{Kroening}. 
-CBMC implements a bit-precise translation of a C program, annotated with assertions 
-and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, 
-then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification 
-flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; 
-it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, 
-into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
-(ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
-which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
-(iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+Here we use one state-of-the-art model checker to formally verifying PV designs w.r.t. user requirements. XXXXXXXXmention that received Golden Medal SV-CompXXXX
 
@@
 \begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|}
 \hline
 \hline
-Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
+Tools & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
 \hline
 \hline
-Specification & Result & Result & Result & Result \\
+Specification & Result & Result \\
 \hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
 \hline
-\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
+\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
 \hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
 \hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} &  \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
 \hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
 \hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
 \hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
 \hline
@@
 %---------------------------------------------------------------------------
-\subsection{Tools} 
+\subsection{Comparative Tools} 
 %---------------------------------------------------------------------------
 
-Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
+The start-of-art verification tool, CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
 The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
@@
 %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
-
-CBMC and ESBMC are unable to produce any conclusive result. 
-Situations of \textit{internal failure}, \textit{timeout}, 
-or \textit{out of memory} occurred; this partially answers 
-the \textit{EQ2}. Note that the internal failure presented 
-by ESBMC was a Z3 solver issue (a bug); this will demand 
-an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
-if we remove the timeout from ESBMC with the SMT solver Boolector, 
-then the verifier is able to obtain the automated synthesis 
-in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.
 
@@
 to avoid some advertising).
-%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
 
@@
 from PV systems in two different sites of the Amazonas State 
-in Brazil, ranging from $253$\,W to $1,586$\,W peak; and 
-three state-of-art verification engines were considered 
-(ESBMC, CBMC, and CPAchecker), in addition to a specialized 
+in Brazil, ranging from $253$\,W to $1,586$\,W peak; one 
+state-of-art verification engine was considered 
+(CPAchecker), in addition to a specialized 
 off-the-shelf simulation tool (HOMER Pro) in order to compare the results.

### 2019-09-11 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 
+Formal methods could offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
+Related to past studies where formal methods are applied to the energy area, in $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+In $2015$, automated simulation-based verification technique was applied to verify correctness of power system protection settings ~\cite{Sengupta2015}.
+In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices, interacting over a smart grid  infrastructure~\cite{Abate2017}.
+Finally, in $2018$, a verification methodology was applied to PV panels (not a complete PV system) and its distributed power point tracking~\cite{Driouich2018}.
+However, past studies did not deal with electricity generation or even solar PV systems optimization.
+Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored in literature.
+
+Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
+In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
+The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted.
+If it fails then a counterexample is provided with an optimal sizing that meets power reliability and system cost.
 Note that in this study, our focus is not on a novel criteria or even optimization objectives.
-Instead, our novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tools.
-
-Formal methods based on \textit{symbolic model checking} and its application 
-to synthesize PV systems have not been further explored in literature, which could offer 
-a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. 
-Here, we use a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing 
-optimal sizing of stand-alone PV systems using commercial equipment data. 
-Given a correctness specification $\sigma$, our method uses that as starting point 
-and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
-related to power reliability. In particular, in each iteration, we synthesize sizing of 
-stand-alone PV systems but that may not achieve the lowest cost. The candidate solution 
-is then verified via symbolic model checking with a lower bound that serves as the minimum 
-cost of reference; if the verification step does not fail, the lower bound is adjusted. 
-If it fails then a counterexample is provided with an optimal sizing that meets 
-power reliability and system cost.
-
-%------------------------------------------------------
-\subsection{Contributions}
-%------------------------------------------------------
-
-Our work makes three major contributions. \textbf{First}, the use of automated 
-symbolic verification methods in electrical systems was uncommon in recent 
-prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
-optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
-charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
-method together with user requirements and environment constraints, 
-and our synthesis algorithm based on symbolic model checking 
-can find the optimal solution in technical and economical terms. 
-\textbf{Second}, we evaluate different state-of-art symbolic software 
-verifiers with the goal of obtaining the best performance in our verification 
-back-end for synthesizing optimal PV systems, being the first work that performs this type of comparative.
-\textbf{Third}, our experimental results show that our synthesis method is an effective and efficient approach 
-on the pursuit of the optimal solution of PV systems using formal methods, which outperforms 
-existing state-of-the-art simulation tool. As a result, our study marks the first application of a sound
-and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.
-Thus, we considerably advance the state-of-the-art in applied energy over the last two decades 
-with the goal of optimally designing PV systems.
-
-\noindent \textit{Outline}. Section~\ref{sec:Background} gives the background about related studies, 
-program synthesis, sizing design and validation of PV systems, and the mathematical modeling. 
-Section~\ref{sec:Method} presents the automated formal synthesis proposed 
-in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, 
-results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
+Instead, our novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods.
+%, which outperforms existing state-of-the-art simulation tool.
+
+%Our work makes two major contributions.
+\textbf{First}, the use of automated symbolic verification methods in electrical systems was rare in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented.
+Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
+\textbf{Second}, %our experimental results show that our synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
+As a result,
+\textit{Contribution}.
+Our study marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems, which outperforms existing state-of-the-art simulation tool used in a comparative with seven case studies.
+Thus, we considerably advance the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.
+
+\textit{Outline}.
+Section~\ref{sec:Background} gives the background about program synthesis, design sizing and validation of PV systems, and the mathematical modeling.
+Section~\ref{sec:Method} presents the automated formal synthesis proposed in this underlying study.
+Section~\ref{sec:Results} is devoted to the experimentation, results and discussions.
+Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
 
@@
 %-----------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{State-of-art in Automated Verification of Electrical Systems}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.
-
-The conversion of traditional power grid into a smart grid, a fundamental example of a CPS, 
-raises a number of issues that requires novel methods and applications.
-In $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
-The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here, the authors employed automated verification of certain quantitative properties of the system, as probability of	 node failure in the long run, impact of repair service on the failure risk, and expected energy consumption, without any interest in power generation or even solar PV systems.
-
-In $2015$, an automated approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
-The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
-The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
-However, this study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
-
-Other related studies from $2015$ include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis using statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
-In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
-The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
-This research, however, did no address the design and verification of solar PV systems.
-
-In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices, interacting over a shared and smart infrastructure~\cite{Abate2017}.
-The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
-The focus was on controlling the behavior of components, thereby verifying the given smart grid as a "system of systems" within the context of "internet of things".
-The author, however, used approximate model checking of stochastic and hybrid models.
-
-In $2018$, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design-space of one operation hour of the PV panels behavior.
-This related study did not include other components of a stand-alone solar PV system.
-
-Another work from $2018$ was the approach to model smart grid components using a formal specification.
-The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
-The presented formal specification can be considered as a first step towards modeling of smart grids using formal methods.
-The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
-This approach is based on Petri nets and is under the assumption that modeling the smart home leads to clear understanding of the overall behavior of the smart grid.
+Here we explain how to size a stand-alone solar PV system with their respective mathematical model, and what type of criteria or technique is possible to apply for the optimal sizing of PV systems.
+Furthermore, we present the theory about program synthesis,
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Sizing Stand-alone Solar PV Systems}
+\label{sec:sizing}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A PV system is illustrated in Fig.\ref{fig:blockdiagram}.
+It identifies the PV generator, batteries, charge controller, inverter, and AC load.
+The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
+For night hours or rainy days, we hold batteries where power can be stored and used.
+The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
+The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
+That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+
+\begin{figure}[h]
+\includegraphics[width=0.4\textwidth]{blockdiagramPVS2_rev}
+\centering
+\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
+\label{fig:blockdiagram} 
+\end{figure}
+
+The sizing check stage will ensure that the system meets the standard project steps related 
+to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice, among other sizing techniques and possibilities.
+
+Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+
+\begin{equation}
+\label{eq:Ecorrected}
+E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
+\end{equation}
+
+We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
+
+\begin{equation}
+\label{eq:Ep}
+E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
+\end{equation}
+
+\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
+the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
+The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
+
+\begin{equation}
+\label{eq:NTPmin}
+N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
+\end{equation}
+
+Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
+
+\begin{equation}
+\label{eq:NPSmin}
+\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
+\end{equation}
+
+\begin{equation}
+\label{eq:NPPmin}
+N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
+\end{equation}
+
+\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ 
+is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and 
+$V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering 
+the maximum and minimum operational temperature, respectively; 
+$P_{total}$ is the total power demanded from the PV system and 
+$P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
+Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
+
+\begin{equation}
+\label{eq:Cbank}
+C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
+\end{equation}
+
+\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; 
+$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
+
+Secondly, the total (minimum) number of batteries is computed as
+
+\begin{equation}
+\label{eq:Nbtotal}
+N_{B}total = N_{BS}min \times N_{BP}min
+\end{equation}
+
+\begin{equation}
+\label{eq:Nbtotal2}
+N_{B}total = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
+\end{equation}
+
+Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage:
+
+\begin{equation}
+\label{eq:vcvsystem}
+V_{c} = V_{system}.
+\end{equation}
+
+The short circuit reference information from the manufacturer's solar panel must be corrected 
+to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, 
+and PV system is temperature dependent, as
+
+\begin{equation}
+\label{eq:iscamb}
+I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
+\end{equation}
+
+The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin} as
+
+\begin{equation}
+\label{eq:icmin}
+I_{c,min} = I_{sc,amb} \times N_{PP},
+\end{equation}
+
+\begin{equation}
+\label{eq:icicmin}
+I_{c} \geq I_{c,min}.
+\end{equation}
+
+The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that 
+the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the 
+output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that 
+the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), 
+where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; 
+$MAX_{AC,ref}$ is the peak power that the inverter can support.
+
+\begin{equation}
+\label{eq:vindc} 
+V_{in}DC = V_{system}.
+\end{equation}
+
+\begin{equation}
+\label{eq:voutac} 
+V_{out}AC = V_{AC}.
+\end{equation}
+
+\begin{equation}
+\label{eq:invcheck} 
+\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{PV systems Optimization Criteria}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to select an optimal combination to meet sizing constraints, 
+it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives.
+
+During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
+The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
+A reliable power is a generation system that has sufficient power to feed load demand in a period.
+
+There exist different methods to express system reliability, where the most popular ones 
+are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
+In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
+
+LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
+On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
+On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
+The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance.
+However, data is not always available and dynamic analysis is complex; and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
+
+Related to economic analysis, there exist various methods available.
+The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
+The common methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
+
+The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
+The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
+IRR is used to evaluate the attractiveness of a project or investment.
+
+LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
+LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
+
+LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
+Eq.~\eqref{eq:LCC} is used to calculate LCC of a PV system,
+
+\begin{equation}
+\label{eq:LCC}
+\begin{aligned}
+LCC = & C_{PV} + C_{bat} + C_{charger} + C_{inv} + \\
+      & C_{installation} + C_{batrep} + C_{PWO\&M},
+\end{aligned}
+\end{equation}
+
+\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs
+in present worth.
+
+%----------------------------------------------------------------------------------------------
+\subsection{Stand-alone PV System Optimization Technique}
+%----------------------------------------------------------------------------------------------
+
+In order to recommend an optimal configuration for PV systems, 
+the designer has to evaluate the design based on optimization variables. 
+As the number of optimization variables increases, the computational effort 
+will increase as well. Hence, to obtain the best PV system design as well as 
+simplified sizing process, prior work introduced three main techniques 
+for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
+
+Intuitive method is simple, easy to be implemented, and can be used to give 
+rough suggestion for preliminary design. The sizing rules are based on designer's experience, 
+using lowest performance either in a time period data or by directly using average value 
+(daily, monthly, or annual) of solar irradiance. This method does not consider the battery's 
+state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
+
+For numerical method, the design is simulated for each time step within a period. 
+State of charge of batteries is calculated and investigated. It is very accurate, 
+however is complex, demanding more time for calculation~\cite{Park2004}.
+
+Analytical methods is used to obtain a close relation or correlation in a form 
+of equation between capacities and reliabilities. The sizing task becomes much simpler 
+than numerical technique; however, the relation cannot be applied to different sites
+since it is specific to one place of deployment of the PV system, 
+thereby demanding adaptation if another site is analyzed.
 
@@
 one successful method in this domain is model checking~\cite{Clarke2012}. 
-Here we use one state-of-the-art model checker to formally verifying PV designs w.r.t. user requirements. XXXXXXXXmention that received Golden Medal SV-CompXXXX
+Here we use one state-of-the-art model checker, who was awarded with the Golden Medal at the annual competition in software verification~\cite{LMU2019}, to formally verifying PV designs w.r.t.
+user requirements.
 
@@
 %-----------------------------------------------------------
-\subsection{Program Synthesis}
+\subsection{Program Synthesis Technique}
 \label{sec:ProgramSynthesis}
@@
 
-The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
+Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}.
+Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do.
+The specification needs to describe the program’s desired behavior (in enough detail) in order to ensure that the program does what it is intended.
+
+Therefore, the basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
 In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
 As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization, and  whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
 
@@
 Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sizing Stand-alone Solar PV Systems}
-\label{sec:sizing}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
-The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.  
-For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage 
-form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system 
-contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior 
-of AC electrical load from the house that will be fed by the system.
-%
-\begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
-\centering
-\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
-\label{fig:blockdiagram} 
-\end{figure}
-
-The sizing check stage will ensure that the system meets the standard project steps related 
-to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller,
-which is the most common one in practice. Firstly, we need to correct the energy consumption estimated to the load 
-($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
-controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
-%
-\begin{equation}
-\label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
-\end{equation}
-
-We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
-%
-\begin{equation}
-\label{eq:Ep}
-E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
-\end{equation}
-
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
-the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
-%
-\begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
-\end{equation}
-
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
-%
-\begin{equation}
-\label{eq:NPSmin}
-\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
-\end{equation}
-%
-\begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
-\end{equation}
-%
-\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ 
-is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and 
-$V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering 
-the maximum and minimum operational temperature, respectively; 
-$P_{total}$ is the total power demanded from the PV system and 
-$P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
-%
-\begin{equation}
-\label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
-\end{equation}
-
-\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-%
-Secondly, the total (minimum) number of batteries is computed as
-
-\begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
-\end{equation}
-
-Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
-\begin{equation}
-\label{eq:vcvsystem}
-V_{c} = V_{system}.
-\end{equation}
-
-The short circuit reference information from the manufacturer's solar panel must be corrected 
-to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, 
-and PV system is temperature dependent, as 
-%
-\begin{equation}
-\label{eq:iscamb}
-I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
-\end{equation}
-
-The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin} as
-%
-\begin{equation}
-\label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP},
-\end{equation}
-%
-\begin{equation}
-\label{eq:icicmin}
-I_{c} \geq I_{c,min}.
-\end{equation}
-
-The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that 
-the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the 
-output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that 
-the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), 
-where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; 
-$MAX_{AC,ref}$ is the peak power that the inverter can support.
-%
-\begin{equation}
-\label{eq:vindc} 
-V_{in}DC = V_{system}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:voutac} 
-V_{out}AC = V_{AC}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{PV systems Optimization Criteria}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In order to select an optimal combination to meet sizing constraints, 
-it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives.
-
-During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
-The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
-A reliable power is a generation system that has sufficient power to feed load demand in a period.
-
-There exist different methods to express system reliability, where the most popular ones 
-are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
-In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
-
-LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
-On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
-On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
-The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance.
-However, data is not always available and dynamic analysis is complex; and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
-
-Related to economic analysis, there exist various methods available.
-The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
-The common methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
-
-The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
-The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
-IRR is used to evaluate the attractiveness of a project or investment.
-
-LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
-LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
-
-LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
-Eq.~\eqref{eq:LCC} is used to calculate LCC of a PV system,
-%
-\begin{equation}
-\label{eq:LCC}
-LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
-\end{equation}
-\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs
-in present worth.
-
-%----------------------------------------------------------------------------------------------
-\subsection{Stand-alone PV System Optimization Technique}
-%----------------------------------------------------------------------------------------------
-
-In order to recommend an optimal configuration for PV systems, 
-the designer has to evaluate the design based on optimization variables. 
-As the number of optimization variables increases, the computational effort 
-will increase as well. Hence, to obtain the best PV system design as well as 
-simplified sizing process, prior work introduced three main techniques 
-for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
-
-Intuitive method is simple, easy to be implemented, and can be used to give 
-rough suggestion for preliminary design. The sizing rules are based on designer's experience, 
-using lowest performance either in a time period data or by directly using average value 
-(daily, monthly, or annual) of solar irradiance. This method does not consider the battery's 
-state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
-
-For numerical method, the design is simulated for each time step within a period. 
-State of charge of batteries is calculated and investigated. It is very accurate, 
-however is complex, demanding more time for calculation~\cite{Park2004}.
-
-Analytical methods is used to obtain a close relation or correlation in a form 
-of equation between capacities and reliabilities. The sizing task becomes much simpler 
-than numerical technique; however, the relation cannot be applied to different sites
-since it is specific to one place of deployment of the PV system, 
-thereby demanding adaptation if another site is analyzed.
 

### 2019-09-12 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 
-\section{Background}
+\section{Sizing and Optimization of PV Systems}
 \label{sec:Background}
 %-----------------------------------------------------------
-Here we explain how to size a stand-alone solar PV system with their respective mathematical model, and what type of criteria or technique is possible to apply for the optimal sizing of PV systems.
-Furthermore, we present the theory about program synthesis,
+
+Here we explain the adopted method to size stand-alone solar PV systems, and what type of criteria and technique is possible to apply for the optimal sizing.
 
@@
 
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-It identifies the PV generator, batteries, charge controller, inverter, and AC load.
+A PV system block diagram is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. 
@@
 The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
-That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required.
+The AC load dictates the behavior of AC electrical load from the house.
+% that will be fed by the PV system.
 
@@
 
-The sizing check stage will ensure that the system meets the standard project steps related 
-to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice, among other sizing techniques and possibilities.
-
+%The sizing check stage will ensure that the system meets the standard project steps related  to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice, among other sizing techniques and possibilities.
+Among the techniques that can be used for the sizing of PV systems, it was adopted here the critical period solar energy method~\cite{Pinho}, with the use of MPPT (Maximum Power Point Tracking) charge controller (which is the most common nowadays).
 Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{PV systems Optimization Criteria}
+\subsection{PV Systems Optimization Criteria}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-In order to select an optimal combination to meet sizing constraints, 
-it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives.
+In order to select an optimal combination to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the underlying system.
+An ideal combination of any PV system is made by the best compromise between these two objectives.
 
@@
 %----------------------------------------------------------------------------------------------
-\subsection{Stand-alone PV System Optimization Technique}
+\subsection{PV Systems Optimization Techniques}
 %----------------------------------------------------------------------------------------------
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%------------------------------------------------------
+\section{Automated Formal Synthesis Method}
+\label{sec:Method}
+%------------------------------------------------------
+
+In this section we present the theory and the methodology created to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.
+
 \subsection{Automated Verification Using Model Checking}
@@
 
-%------------------------------------------------------
-\section{Synthesizing optimal sizing of stand-alone solar PV systems}
-\label{sec:Method}
-%------------------------------------------------------
-
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
 It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
-%
+
  \begin{algorithm}
@@
 %---------------------------------------------------------------------------
-\section{Experimental evaluation}
+\section{Case Studies and Analysis}
 \label{sec:Results}
@@
 This section presents the case studies used to evaluate our proposed approach.
-We also compare our approach with a simulation tool, named HOME Pro. 
-The version and command-line of each verifier adopted, 
-the computing setup, the objectives of the experimental phase, 
-and the results itself are also described.
+We also compare our approach with a specialized simulation tool (HOME Pro).
+The computing setup, the objectives of the experimental phase, and the results itself are also described.
 
@@
 
-We have performed seven stand-alone PV system case studies to evaluate 
-our proposed synthesis approach, as described in the first column of 
-Table~\ref{tab1} (named Specification). These case studies were defined 
-based on usual electrical load found in riverside communities of the 
-Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (named Specification).
+These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil.
+For all cases, a estimated load curve (kWh) was defined based on the electronics consumers found of each house.
 
@@
 %---------------------------------------------------------------------------
-\subsection{Comparative Tools} 
-%---------------------------------------------------------------------------
-
-The start-of-art verification tool, CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
-
-%---------------------------------------------------------------------------
 \subsection{Setup} 
 %---------------------------------------------------------------------------
+
+The start-of-art verification tool, CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} was used as our verification engine to compare our approach effectiveness and efficiency.
+The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
 
@@
 
-\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?
+\item[EQ2] \textbf{(performance)} how does our formal synthesis tools compares to a specialized simulation tool?
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison between Formal Synthesis and HOME Pro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Comparing the results between the formal synthesis with CPAchecker 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
+\section{Conclusion and Future Work}
 \label{sec:Conclusion}

### 2019-09-12 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 \textit{Outline}.
-Section~\ref{sec:Background} gives the background about program synthesis, design sizing and validation of PV systems, and the mathematical modeling.
+Section~\ref{sec:Background} gives the background about sizing and optimization of PV systems.
 Section~\ref{sec:Method} presents the automated formal synthesis proposed in this underlying study.
-Section~\ref{sec:Results} is devoted to the experimentation, results and discussions.
+Section~\ref{sec:Results} is devoted to the experimentation, results and analysis.
 Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
@@
 
-Here we explain the adopted method to size stand-alone solar PV systems, and what type of criteria and technique is possible to apply for the optimal sizing.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sizing Stand-alone Solar PV Systems}
-\label{sec:sizing}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A PV system block diagram is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
+A stand-alone PV system block diagram is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
@@
 
-%The sizing check stage will ensure that the system meets the standard project steps related  to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice, among other sizing techniques and possibilities.
-Among the techniques that can be used for the sizing of PV systems, it was adopted here the critical period solar energy method~\cite{Pinho}, with the use of MPPT (Maximum Power Point Tracking) charge controller (which is the most common nowadays).
+In this section we explain the adopted method to size stand-alone solar PV systems, and what criteria and technique is possible to apply for the optimal sizing.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Sizing Stand-alone Solar PV Systems}
+\label{sec:sizing}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+At this work, was adopted the critical period solar energy method~\cite{Pinho}, and MPPT (Maximum Power Point Tracking) charge controller (which is the most common nowadays).
 Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{PV Systems Optimization Criteria}
+\subsection{PV Systems Optimization: Criteria and Techniques}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-In order to select an optimal combination to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the underlying system.
-An ideal combination of any PV system is made by the best compromise between these two objectives.
+In order to select an optimal PV system to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the underlying system.
+An ideal combination of any PV system is made by the best compromise between these two objectives or \textbf{criteria}.
 
@@
 
-%----------------------------------------------------------------------------------------------
-\subsection{PV Systems Optimization Techniques}
-%----------------------------------------------------------------------------------------------
-
-In order to recommend an optimal configuration for PV systems, 
+Parallel to criteria, in order to recommend an optimal configuration for PV systems, 
 the designer has to evaluate the design based on optimization variables. 
@@
 will increase as well. Hence, to obtain the best PV system design as well as 
-simplified sizing process, prior work introduced three main techniques 
+simplified sizing process, prior work introduced three main \textbf{techniques} 
 for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
@@
 one successful method in this domain is model checking~\cite{Clarke2012}.
-Here we use one state-of-the-art model checker, who was awarded with the Golden Medal at the annual competition in software verification~\cite{LMU2019}, to formally verifying PV designs w.r.t.
-user requirements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to perform the automated formal synthesis, we will use a state-of-the-art model checker, who was awarded with the Golden Medal at the annual competition in software verification~\cite{LMU2019}, the \textbf{CPAchecker}.
 
@@
 different verification approaches in the same formal setting. The CPA formalism 
-provides an interface for the definition of program analyses. Consequently, CPAchecker 
-provides an implementation framework that allows the seamless integration of program 
-analyses that are expressed in the CPA framework. The comparison among different 
+provides an interface for the definition of program analyses.
+Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
+The comparison among different
 approaches in the same experimental setting is intended to be easy and the experimental 

### 2019-09-18 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; however, the existing tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
-Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last decades.
+There exist various methods and computer tools to size solar photovoltaic systems; however, those tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
+In prior studies related to optimal sizing of photovoltaic systems, the focus was always on criteria or objectives.
+Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using an unprecedented program synthesis.
 In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound cost via symbolic model checking.

### 2019-09-18 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 A stand-alone PV system block diagram is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
-The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.
+The PV generator (a panel or an array) is a semiconductor device that can convert solar energy into DC electricity.
 For night hours or rainy days, we hold batteries where power can be stored and used.
@@
 The short circuit reference information from the manufacturer's solar panel must be corrected 
-to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, 
-and PV system is temperature dependent, as
+to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as
 
@@
 A reliable power is a generation system that has sufficient power to feed load demand in a period.
-
-There exist different methods to express system reliability, where the most popular ones 
-are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
+There exist different methods to express system reliability, where the most popular ones are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
 In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
-
 LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
@@
 The common methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
-
 The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
@@
 IRR is used to evaluate the attractiveness of a project or investment.
-
 LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
 LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
-
 LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
@@
 for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
-
-Intuitive method is simple, easy to be implemented, and can be used to give 
-rough suggestion for preliminary design. The sizing rules are based on designer's experience, 
-using lowest performance either in a time period data or by directly using average value 
-(daily, monthly, or annual) of solar irradiance. This method does not consider the battery's 
-state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
-
+Intuitive method is simple, easy to be implemented, and can be used to give rough suggestion for preliminary design.
+The sizing rules are based on designer's experience, using lowest performance either in a time period data or by directly using average value (daily, monthly, or annual) of solar irradiance.
+This method does not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
 For numerical method, the design is simulated for each time step within a period.
-State of charge of batteries is calculated and investigated. It is very accurate, 
-however is complex, demanding more time for calculation~\cite{Park2004}.
-
-Analytical methods is used to obtain a close relation or correlation in a form 
-of equation between capacities and reliabilities. The sizing task becomes much simpler 
-than numerical technique; however, the relation cannot be applied to different sites
-since it is specific to one place of deployment of the PV system, 
+State of charge of batteries is calculated and investigated.
+It is very accurate, however is complex, demanding more time for calculation~\cite{Park2004}.
+Analytical methods is used to obtain a close relation or correlation in a form of equation between capacities and reliabilities.
+The sizing task becomes much simpler than numerical technique; however, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system,
 thereby demanding adaptation if another site is analyzed.
@@
 Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-The comparison among different
-approaches in the same experimental setting is intended to be easy and the experimental 
-results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, 
-the central data structure is a set of control-flow automata (CFA), which consists of control-flow 
-locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and 
-interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
-and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
+Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}.
+Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.
 
@@
 Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do.
-The specification needs to describe the program’s desired behavior (in enough detail) in order to ensure that the program does what it is intended.
+The specification needs to describe the program’s desired behavior in order to ensure that the program does what it is intended.
 
@@
 As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization, and  whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization, and  whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur} from model checking.
 
@@
 a list of forty equipment from ten different manufacturers was provided 
-to the synthesis engine in order to allow the choice of every item 
+to our synthesis engine in order to allow the choice of every item 
 of PV sizing. Data sheet from each item was necessary to collect 
@@
 	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
-	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
+	\item Operation and maintenance annual costs: based on PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
 This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
@@
 	\item HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER};
-	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
-	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
+	\item HOMER Pro do not have the LCC cost in its reports. It has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative;
+	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected from online databases.
 However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
-	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
 	\item HOMER Pro do not have a explicit equipment called charge controller.
@@
 We also compare our approach with a specialized simulation tool (HOME Pro).
-The computing setup, the objectives of the experimental phase, and the results itself are also described.
+The computing setup, the objectives of the experimental phase, and the results are also described.
 
@@
 \end{tabular}
-\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
+\\Caption: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
 \end{scriptsize}
@@
 %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
-
-Related to HOMER Pro, it was able to evaluate six case studies, 
-and within a time shorter than $30$ seconds, which was much 
-faster than our automated synthesis tool (cf.~\textit{EQ2}). 
-Case study $3$ was not possible to be simulated since HOMER Pro 
-does not have the feature of adjusting the battery autonomy, i.e., 
-the tool always tries to feed with electricity the given load 
-during $365$ days/year. We have also noted other HOMER Pro drawbacks:
-
-\begin{itemize}
-\item There exists no explicit charge controller 
-as a system equipment. HOMER Pro includes automatically 
-a controller just to simulate the charge/discharge 
-of batteries and to meet the load requirement; however, 
-without costs or even with electrical characteristics 
-as maximum current and voltage, which are common during PV sizing;
-\item HOME Pro demands to include some battery specification 
-to initiate the optimization; however, it does not change 
-the electrical specifications during the simulation; 
-the presented results are multiples of the original 
-battery type suggested by the user. As example, it was 
-started with a $83.4$ Ah lead-acid battery and during 
-the simulation, HOMER Pro did not try to use other capacities or types;
-\item HOMER Pro does not present the optimal solution 
-in terms of connections of arrays of PV panels, just the 
-total in terms of power, i.e., it does not present neither models 
-and the power of each PV panel nor the total of panels in series or parallel. 
-\end{itemize}
-
-Comparing the results between the formal synthesis with CPAchecker 
-and HOMER Pro, we observed that most results are quite similar, 
-in terms of technical solution and cost (cf. Table~\ref{tab1}).
-
+As interesting feature of the automated synthesis, every optimal sizing is presented as a detailed list of equipment with brand (in Table~\ref{tab1} it was removed 
+to avoid some advertising) and model taken from the list inputted to the algorithm, moreover the number of series and parallel solar panels and batteries are presented.
+
+Related to HOMER Pro, it was able to evaluate six case studies, and within a time shorter than $30$ seconds, which was much faster than our automated synthesis tool  (cf.~\textit{EQ2}).
+Case study $3$ was not possible to be simulated since HOMER Pro does not have the feature of adjusting the battery autonomy (the tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year).
+Other HOMER Pro drawbacks, when compared to our automated synthesis method: (a) There exists no explicit charge controller as a system equipment.
+HOMER includes automatically a controller just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics as maximum current and voltage, which are common during PV sizing; (b) HOMER demands to include some battery specification to initiate the optimization; however, it does not change the electrical specifications during the simulation; the presented results are multiples of the original battery type suggested by the user.
+As example, it was started with a $83.4$ Ah lead-acid battery and during the simulation, HOMER Pro did not try to use other capacities or types; (c) HOMER does not present the optimal solution in terms of connections of arrays of PV panels, just the total in terms of power, i.e., it does not present neither models and the power of each PV panel nor the total of panels in series or parallel; (d) Battery autonomy is not an parameter that the user can set when using HOMER.
+
+Comparing the results between the formal synthesis with CPAchecker and HOMER Pro  (cf.~\textit{EQ2}), we observed that most results are quite similar, in terms of technical solution and cost (cf.
+Table~\ref{tab1}).
 Particularly related to LCC, the cost was very close in cases
@@
 
-However, there exists a huge divergence in case study $2$, 
-where the costs presented by HOMER Pro were $54$\% higher 
-than our automated synthesis tool, probably because the 
-operation and maintenance costs assumed by our automated 
-synthesis tool were underestimated to that specific load.
+However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our automated synthesis tool, probably because the operation and maintenance costs assumed by our automated synthesis tool were underestimated to that specific load.
 
@@
 and monitored since June $2018$ in a riverside community 
-in the Amazonas State in Brazil, with similar demands 
+in the Amazonas State in Brazil (coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W), with similar power demands 
 presented by case studies $1$, $4$, $5$, and $6$, 
@@
 thus resting both without parameters to comparative.
-
-Summarizing, our synthesis tool is capable to present a 
-solution, which is far detailed and close to the commercial 
-reality than the solution presented by HOMER Pro. 
-In particular, our automated synthesis method 
-can provide all the details of every component of 
-a PV system solution, with complete electrical details 
-from data sheet of manufacturers, including 
-the model of the component, nominal current and voltage. 
-In this respect, even the name of the manufacturer 
-can be presented (in Table~\ref{tab1} it was removed 
-to avoid some advertising).
 
@@
 
-We have described and evaluated an automated synthesis method 
-to obtain the optimal size of PV system using software model 
-checking techniques.
+We have described and evaluated an automated synthesis method to obtain the optimal size of PV system using software model checking techniques.
 The focus was on the method to obtain the optimal solution, based on formal methods that can cover the design-space better than simulation tools.
-We have considered seven case studies
-from PV systems in two different sites of the Amazonas State 
-in Brazil, ranging from $253$\,W to $1,586$\,W peak; one 
-state-of-art verification engine was considered 
-(CPAchecker), in addition to a specialized 
-off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
-
-Our automated synthesis tool presented detailed optimal solution 
-to six case studies adopted in this paper, with specifications, 
-models, and the arrangement in terms of series-parallel connections, 
-thereby covering the charge controller, which was not presented by HOMER Pro. 
-In a nutshell, our automated synthesis tool took more time 
-to find the optimal solution than HOMER Pro; however, the presented 
-solution was more complete and detailed, which is very useful 
-to a user to get a list of equipment and go to shopping.
-
-As future work, the authors plan to improve the power reliability analysis, 
-to address the restriction to only allow automated synthesis of 
-riverside communities in the Amazonas state (Brazil), and to 
-validate some cases with deployed PV systems in isolated communities.
+We have considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; one state-of-art verification engine was considered (CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+
+Summarizing, our synthesis tool is capable to present a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
+In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current and voltage.
+In this respect, even the name of the manufacturer can be presented.
+Covering the charge controller, which was not presented by HOMER Pro.
+In a nutshell, our automated synthesis tool took more time to find the optimal solution than HOMER Pro; however, the presented solution was more complete and detailed, which is very useful to a user to get a list of equipment and go to shopping.
+
+As future work, the authors plan to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil), and to validate some cases with the deployment of real PV systems in isolated communities.
 
@@
 
-The authors would like to thank: (i) Newton Fund [grant number $261881580$] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa $2018$], for the DCTIEX II scholarship (NOV-$2018$), and for support the research mobility to UK; (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and (iv) University of Sheffield's Research England QR GCRF Institutional Allocation for the HOMER Pro license.
+The authors would like to thank: (i) Newton Fund [grant $261881580$] for the mobility support; (ii) FAPEAM - Amazonas Foundation for Research [PROTI-Pesquisa $2018$], for the mobility support to UK (NOV-$2018$); (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and (iv) University of Sheffield's QR GCRF Institutional Allocation for the HOMER Pro license.
 

### 2019-09-18 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 
-Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
+Related to off-the-shelf simulation tools only HOMER Pro perform off-grid system with battery backup analysis and includes economical analysis.
 Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
-Related to HOMER Pro:
-
-\begin{itemize}
-	\item HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER};
-	\item HOMER Pro do not have the LCC cost in its reports. It has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative;
-	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected from online databases.
-However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
-	\item HOMER Pro do not have a explicit equipment called charge controller.
+Related to HOMER Pro: (a) is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; (b) it does not have the LCC cost in its reports.
+It has NPC and LCOE.
+Therefore NPC was used to obtain LCC in order to allow the comparative; (c) the optimization analysis of HOMER allows to define a load curve and temperature according of data collected from online databases.
+However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools; (d) it does not have a explicit equipment called charge controller.
 It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
-During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
-	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
+During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER}; (e) It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
 By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
 For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable;
-	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
-	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
+While in a ordinary house electrical load, 95\% is considered acceptable; (f) it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; (g) the premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER will search for the optimized power of each component.
 With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
-\end{itemize}
 
@@
 
+Worth to mention the adaption created for the CEGIS synthesis method and implemented by the algorithm of our proposed formal synthesis tool, allowing the optimization of stand-alone PV systems with the  best compromise between power reliability and system cost analysis.
+
 As future work, the authors plan to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil), and to validate some cases with the deployment of real PV systems in isolated communities.

### 2019-09-20 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual, and simulation), and including the proposed automatic synthesis that is detailed in this Section.
+The input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search.
+And the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.
+
+\begin{figure}[h]
+\includegraphics[width=0.5\textwidth]{optimalsizingprocess2}
+\centering
+\caption{Comparative of optimal sizing methods}
+\label{fig:optimization}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Automated Verification Using Model Checking}
@@
 Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+
+However, there is a main disadvantage of model checking: the state explosion problem~\cite{Clarke2012}.
+In order to solve this issue, many different techniques were developed at the last decades.
+One of the promising is the Bounded Model Checking (BMC).
+BMC algorithms traverses a finite state machine for a fixed number of steps, $k$, and checks whether violation occurs with this bound.
+
 The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}.
 Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.
-
+The use of SMT by CPAchecker, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
+
+%CPAchecker algorithms can traverse a finite state machine for a fixed number of steps, $k$, and checks whether violation occurs with this bound; therefore is not necessary to search for 
+%
+%BMC techniques are only able to falsify properties up to the given depth k;
+%
+%Verification of safety properties: can we find a bad state in k steps?
+%
+%Model checking tools face a combinatorial blow up of the state-space, commonly known as the state explosion problem, that must be addressed to solve most real-world problems.
+There are several approaches to combat this problem.
+%
 %-----------------------------------------------------------

### 2019-09-22 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-There exist various methods and computer tools to size solar photovoltaic systems; however, those tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
+There exist various methods and computer tools to size solar photovoltaic systems; however, these tools rely on simulations, which do not cover all aspects of the design space during the search for the optimal solution.
 In prior studies related to optimal sizing of photovoltaic systems, the focus was always on criteria or objectives.
-Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using an unprecedented program synthesis.
+Here, we present a new sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using an unprecedented program synthesis.
 In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound cost via symbolic model checking.
 If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal system sizing.
-We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which is able to provide more detailed and accurate solution than the existing simulation tool.
+We provide commercial equipment data from different manufacturers to our synthesis engine and derive candidate solutions from financial analysis.
+Experimental results using seven case studies show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
+We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which can provide a more detailed and accurate solution than that existing simulation tool.
 \end{abstract}
@@
 \centering
-\caption{Comparative of optimal sizing methods}
+\caption{Comparative of optimal sizing methods. \textcolor{red}{could you please convert this figure into greyscale?}}
 \label{fig:optimization}

### 2019-09-22 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}.
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
-
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.,  PSpice~\cite{Gow1999}, or MATLAB/Simulink package~\cite{Benatiallah2017}.
-However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-
-Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
-An ideal combination of any PV system is made by the best compromise between two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
-
-Formal methods could offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
-Related to past studies where formal methods are applied to the energy area, in $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-In $2015$, automated simulation-based verification technique was applied to verify correctness of power system protection settings ~\cite{Sengupta2015}.
+Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for three-quarters of the additional connections needed to provide universal electricity~\cite{Hussein2012}; specifically, grid extension are the standard in urban areas~\cite{IEAweo2018}.
+
+To simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general-purpose simulation tools, e.g., PSpice~\cite{Gow1999}, or MATLAB/Simulink package~\cite{Benatiallah2017}.
+However, these tools rely on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+
+Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods were developed and evaluated~\cite{Applasamy2011}.
+An ideal combination of any PV system consists of the best compromise between two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
+
+Formal methods could offer great potential to obtain a more effective design process for PV systems~\cite{ClarkeHV18}.
+In $2012$, a Chinese smart grid implementation considered a case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
 In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices, interacting over a smart grid infrastructure~\cite{Abate2017}.
 Finally, in $2018$, a verification methodology was applied to PV panels (not a complete PV system) and its distributed power point tracking~\cite{Driouich2018}.
-However, past studies did not deal with electricity generation or even solar PV systems optimization.
-Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored in literature.
+However, prior studies did not deal with electricity generation or even solar PV systems optimization.
+Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in literature.
 
 Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
-In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
+Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
+In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
 The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted.
-If it fails then a counterexample is provided with an optimal sizing that meets power reliability and system cost.
-Note that in this study, our focus is not on a novel criteria or even optimization objectives.
-Instead, our novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods.
-%, which outperforms existing state-of-the-art simulation tool.
+If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost.
+Note that in this study, our focus is not on new criteria or even optimization objectives.
+Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.
 
@@
 \textit{Contribution}.
-Our study marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems, which outperforms existing state-of-the-art simulation tool used in a comparative with seven case studies.
-Thus, we considerably advance the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.
+Our study marks the first application of a sound and automated formal synthesis approach that can provide accurate results of optimal sizing of stand-alone PV systems, which outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies.
+\textcolor{red}{could you please summarise the main results here?
+Why are they good?} Thus, over the last two decades, we considerably advance the state-of-the-art in applied energy to optimally design PV systems.
 
@@
 Section~\ref{sec:Method} presents the automated formal synthesis proposed in this underlying study.
-Section~\ref{sec:Results} is devoted to the experimentation, results and analysis.
-Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
+Section~\ref{sec:Results} is devoted to the experimental evaluation, while Section~\ref{sec:Conclusion} presents the conclusions and describes future work.
 

### 2019-09-22 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+%-----------------------------------------------------------
 \section{Sizing and Optimization of PV Systems}
@@
 
-A stand-alone PV system block diagram is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
+Fig.\ref{fig:blockdiagram} illustrates a stand-alone PV system block diagram.
 The PV generator (a panel or an array) is a semiconductor device that can convert solar energy into DC electricity.
@@
 The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required.
-The AC load dictates the behavior of AC electrical load from the house.
-% that will be fed by the PV system.
-
+The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required.
+The AC load dictates the behavior of the AC electrical load from the house.
+%
 \begin{figure}[h]
@@
 
-In this section we explain the adopted method to size stand-alone solar PV systems, and what criteria and technique is possible to apply for the optimal sizing.
+In this section, we explain the adopted method to size stand-alone solar PV systems, and what criteria and technique are possible to apply for the optimal sizing.
 
@@
 
-At this work, was adopted the critical period solar energy method~\cite{Pinho}, and MPPT (Maximum Power Point Tracking) charge controller (which is the most common nowadays).
-Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+We adopted a critical period solar energy method~\cite{Pinho}; in particular, maximum power point tracking (MPPT) charge controller, which is the most common nowadays.
+First, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
 
@@
 
-We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
+We also need to estimate the energy that each panel produces, called $E_{p}$, in Wh, defined as
 
@@
 
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
+\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where we deploy the PV system; 
 the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
+We compute the total minimum number of needed solar panels ($N_{TPmin}$) as
 
@@
 
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
+Notably, we give the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) by
 
@@
 $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
-
+Regarding batteries, we must first define the total capacity of the battery bank as
+%
 \begin{equation}
@@
 
-\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-
-Secondly, the total (minimum) number of batteries is computed as
-
+\noindent where the variable $autonomy$ is a design definition and typically has a value ranging from $6$ to $48$h; $ V_{system} $ 
+is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
+%
+Second, we compute the total (minimum) number of batteries as 
+%
 \begin{equation}
@@
 
-The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that 
+The inverter sizing check is performed using three equations. Eq.~\eqref{eq:vindc} ensures that 
 the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the 
@@
 
-In order to select an optimal PV system to meet sizing constraints, it is necessary to evaluate power reliability and system cost analysis for the underlying system.
-An ideal combination of any PV system is made by the best compromise between these two objectives or \textbf{criteria}.
+We need to evaluate \textit{power reliability} and \textit{system cost analysis} for the underlying system to select an optimal PV system to meet sizing constraints.
+An ideal combination of any PV system consists of the best compromise between these two objectives or criteria.
 
 During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
-The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
+The reason is that solar energy production is intermittent and, therefore, the energy generated usually does not match with the load demand.
 A reliable power is a generation system that has sufficient power to feed load demand in a period.
 There exist different methods to express system reliability, where the most popular ones are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
-In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
+In both methods, if the probability is zero, then the load is always fulfilled; otherwise (i.e., probability of one) the load is never fulfilled.
 LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
-On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
-On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
+On the one hand,  we have a reliable PV system when it can generate sufficient power to fulfill the demanded load within a period.
+On the other hand, LPSP is defined as the probability of the case when the system generates insufficient power to satisfy the load demand.
 The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance.
@@
 
-Related to economic analysis, there exist various methods available.
-The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
-The common methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
+There exist various methods available related to economic analysis.
+The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis to propose a system with high reliability and lowest cost~\cite{Alsadi2018}.
+The conventional methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
 The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
-The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
+We find the present net worth by discounting all cash inflows and outflows, including the cost of installation, replacement, and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
 IRR is used to evaluate the attractiveness of a project or investment.
-LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
+We define LCOE as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
 LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
-LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
+LCC is the estimation of the sum of installation cost, operating and maintenance of a PV system for some time, and expressed in today's value~\cite{Applasamy2011}.
 Eq.~\eqref{eq:LCC} is used to calculate LCC of a PV system,
-
+%
 \begin{equation}
@@
 
-Parallel to criteria, in order to recommend an optimal configuration for PV systems, 
-the designer has to evaluate the design based on optimization variables. 
-As the number of optimization variables increases, the computational effort 
-will increase as well. Hence, to obtain the best PV system design as well as 
-simplified sizing process, prior work introduced three main \textbf{techniques} 
-for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
-Intuitive method is simple, easy to be implemented, and can be used to give rough suggestion for preliminary design.
-The sizing rules are based on designer's experience, using lowest performance either in a time period data or by directly using average value (daily, monthly, or annual) of solar irradiance.
+Parallel to criteria, the designer has to evaluate the design based on optimization variables to recommend an optimal configuration for PV systems.
+As the number of optimization variables increases, the computational effort increases as well.
+Hence, to obtain the best PV system design as well as a simplified sizing process, prior work introduced three primary techniques for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
+The intuitive method is simple, easy to be implemented, and can be used to give rough suggestions for preliminary design.
+The sizing rules rely on the designer's experience, using the lowest performance either in a time data or by directly using average value (daily, monthly, or annual) of solar irradiance.
 This method does not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
-For numerical method, the design is simulated for each time step within a period.
-State of charge of batteries is calculated and investigated.
-It is very accurate, however is complex, demanding more time for calculation~\cite{Park2004}.
-Analytical methods is used to obtain a close relation or correlation in a form of equation between capacities and reliabilities.
-The sizing task becomes much simpler than numerical technique; however, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system,
-thereby demanding adaptation if another site is analyzed.
+For the numerical method, the design simulates for each time step within a period to calculate and investigate the state of charge of batteries.
+The numerical method is very accurate; however, it is complex, demanding more time for calculation~\cite{Park2004}.
+Analytical methods are used to obtain a close relation or correlation in the form of an equation between capacities and reliabilities.
+The sizing task becomes much more straightforward than numerical technique; however, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
 

### 2019-09-22 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-In this section we present the theory and the methodology created to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.
-
-Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual, and simulation), and including the proposed automatic synthesis that is detailed in this Section.
-The input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search.
-And the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.
+In this section, we present the theory and methodology created to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual and simulation), and including the proposed automatic synthesis proposed here.
+The input information is the same for all the methods, with the difference that in automated validation, it is possible to define the bound $k$ to restrict the design-space search.
+\textcolor{red}{this sentence is unclear...
+Moreover, the outputs are not equal, as the design-space coverage and the, mainly, the final resulting}.
 
@@
 
-Although simulation and testing explore possible behaviors and scenarios of a given system, 
-they leave open the question of whether unexplored trajectories may contain a flaw. 
-Formal verification conducts an exhaustive exploration of all possible behaviors; 
-when a design is said to be ``correct'' by a formal verification method, it implies that all 
-behaviors have been explored, and questions regarding adequate coverage or missed behavior 
-becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
-applies mathematical reasoning to obtain guarantees about the correctness of a system; 
-one successful method in this domain is model checking~\cite{Clarke2012}.
-
-In order to perform the automated formal synthesis, we will use a state-of-the-art model checker, who was awarded with the Golden Medal at the annual competition in software verification~\cite{LMU2019}, the \textbf{CPAchecker}.
-
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
+Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies all behaviors explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
+
+To perform the automated formal synthesis, we use a state-of-the-art model checker, awarded with the golden medal at the annual competition in software verification: \textbf{CPAchecker}~\cite{LMU2019}.
 Automatic program verification requires a choice between precision and efficiency.
-The more precise a method, the fewer false positives it will produce, but also the 
-more expensive it is, and thus applicable to fewer programs. 
-Historically, this trade-off was reflected in two major approaches to static verification: 
-program analysis and model checking. In order to experiment with the trade-off, 
-and in order to be able to set the dial between the two extreme points, 
-Configurable Program Analysis (CPA) provides a conceptual basis for expressing 
-different verification approaches in the same formal setting. The CPA formalism 
-provides an interface for the definition of program analyses.
-Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
-Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-
-However, there is a main disadvantage of model checking: the state explosion problem~\cite{Clarke2012}.
+The more precise a method, the fewer false positives it produces, but also the more expensive it is, and thus applicable to fewer programs.
+Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
+To experiment with the trade-off and to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
+The CPA formalism provides an interface for the definition of program analysis.
+Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analysis expressed in the CPA framework.
+In terms of the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}.
+Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.
+
+%However, there exists a main disadvantage of model checking: the state explosion problem~\cite{Clarke2012}.
 In order to solve this issue, many different techniques were developed at the last decades.
@@
 
-The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}.
+%The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}.
 Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.
@@
 
-%CPAchecker algorithms can traverse a finite state machine for a fixed number of steps, $k$, and checks whether violation occurs with this bound; therefore is not necessary to search for 
-%
-%BMC techniques are only able to falsify properties up to the given depth k;
-%
-%Verification of safety properties: can we find a bad state in k steps?
-%
-%Model checking tools face a combinatorial blow up of the state-space, commonly known as the state explosion problem, that must be addressed to solve most real-world problems.
-There are several approaches to combat this problem.
 %
@@
 Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do.
-The specification needs to describe the program’s desired behavior in order to ensure that the program does what it is intended.
-
-Therefore, the basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
+The specification needs to describe the program's desired behavior to ensure that the program does what it intends.
+
+The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
 In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
-As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization, and  whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur} from model checking.
-
+As a result, a given candidate program $p$ is iteratively refined, to match $\sigma$ more closely.
+CEGIS represents one of the most popular approaches to program synthesis currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization.
+Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture.
+Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur} from model checking.
+%
 \begin{figure}[h]
@@
 The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+Examples of specifications used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specifications and prices from different manufacturers and models.
 

### 2019-09-24 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
updated conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textit{Outline}.
+%\textit{Outline}.
 Section~\ref{sec:Background} gives the background about sizing and optimization of PV systems.
@@
 
-We have described and evaluated an automated synthesis method to obtain the optimal size of PV system using software model checking techniques.
-The focus was on the method to obtain the optimal solution, based on formal methods that can cover the design-space better than simulation tools.
-We have considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; one state-of-art verification engine was considered (CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
-
-Summarizing, our synthesis tool is capable to present a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
-In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current and voltage.
-In this respect, even the name of the manufacturer can be presented.
-Covering the charge controller, which was not presented by HOMER Pro.
-In a nutshell, our automated synthesis tool took more time to find the optimal solution than HOMER Pro; however, the presented solution was more complete and detailed, which is very useful to a user to get a list of equipment and go to shopping.
-
-Worth to mention the adaption created for the CEGIS synthesis method and implemented by the algorithm of our proposed formal synthesis tool, allowing the optimization of stand-alone PV systems with the  best compromise between power reliability and system cost analysis.
-
-As future work, the authors plan to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil), and to validate some cases with the deployment of real PV systems in isolated communities.
+We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking techniques.
+The focus was on the synthesis method to obtain the optimal solution based on formal methods, which can cover the entire design-space as opposed to simulation tools.
+We have considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; one state-of-art verification engine was considered (CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
+
+In summary, our synthesis tool is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
+In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage (or even the manufacturer name); we also cover the charge controller, which is unavailable in HOMER Pro.
+Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro; however, the presented solution is sound and complete; it also provides a list of equipment to be bought from manufacturers.
+\textcolor{red}{what is the scientific contribution?}
+
+Note further that we extended the CEGIS synthesis method and implemented this extension within our proposed formal synthesis tool, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
+
+For future work, we plan to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil) and to validate some cases with the deployment of real PV systems in isolated communities.
 

### 2019-09-24 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
updated Section IV.E
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-We have reported a favorable assessment of our formal synthesis method. 
-Nevertheless, we have also identified three threats to the validity 
-of our experimental results, which can be further assessed and 
+We have reported a favorable assessment of our formal synthesis method to obtain the optimal size of the PV system. 
+Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and 
 constitute future work: ($1$) improvement of the power reliability 
 analysis: to include loss of load probability or loss of power 
-supply probability, which can make the analysis more accurate; 
-($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
+supply probability, which can make the analysis more accurate \textcolor{red}{how much? can you quantify?}; 
+($2$) the cost analysis is well-tailored to the Amazon region of Brazil; 
 however, a broad analysis from other isolated areas must be 
-performed in order to make the optimization general in terms 
-of applicability; ($3$) to deploy at the field some PV systems 
-sized using our synthesized results in order to validate it.
+performed to make the optimization general in terms 
+of applicability \textcolor{red}{cite example of areas?}; ($3$) to deploy at the field some PV systems 
+sized using our synthesized results to validate it \textcolor{red}{why is it important?}.
 

### 2019-09-24 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
updated Section IV.D
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-CPAchecker was able to synthesize the optimal sizing in six 
-out of seven case studies: the result was produced within 
-the time limit, which varied from $134.71$ to $235.75$ minutes. 
-Only case study $7$ led to a \textit{timeout} result, i.e., 
-it was not solved within $240$ minutes. However, if we remove 
-this timeout limitation from CPAchecker, the verifier is 
-able to solve the optimization in $44.97$ hours. 
-The violation (SAT result) indicated in Table~\ref{tab1} 
-is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
-%The results were tested by manual PV sizing and were sound (\textit{RQ1}).
-%, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
-As interesting feature of the automated synthesis, every optimal sizing is presented as a detailed list of equipment with brand (in Table~\ref{tab1} it was removed 
-to avoid some advertising) and model taken from the list inputted to the algorithm, moreover the number of series and parallel solar panels and batteries are presented.
+CPAchecker was able to synthesize the optimal sizing in six out of seven case studies: the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
+Only case study $7$ led to a \textit{timeout} result, i.e., it was not solved within $240$ minutes.
+However, if we remove this timeout limitation from CPAchecker, the verifier can solve the optimization in $44.97$ hours.
+The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
+As an interesting feature of the automated synthesis, we present every optimal sizing as a detailed list of equipment with brand (in Table~\ref{tab1} it was removed to avoid some advertising) and model taken from the list provided to the algorithm.
+Moreover, we present the number of series and parallel solar panels and batteries.
 
 Related to HOMER Pro, it was able to evaluate six case studies, and within a time shorter than $30$ seconds, which was much faster than our automated synthesis tool (cf.~\textit{EQ2}).
-Case study $3$ was not possible to be simulated since HOMER Pro does not have the feature of adjusting the battery autonomy (the tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year).
+We were unable to simulate case study $3$ since HOMER Pro does not have the feature of adjusting the battery autonomy (the tool always meets the user requirement, i.e., the load curve during the $365$ days of the year).
 Other HOMER Pro drawbacks, when compared to our automated synthesis method: (a) There exists no explicit charge controller as a system equipment.
-HOMER includes automatically a controller just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics as maximum current and voltage, which are common during PV sizing; (b) HOMER demands to include some battery specification to initiate the optimization; however, it does not change the electrical specifications during the simulation; the presented results are multiples of the original battery type suggested by the user.
-As example, it was started with a $83.4$ Ah lead-acid battery and during the simulation, HOMER Pro did not try to use other capacities or types; (c) HOMER does not present the optimal solution in terms of connections of arrays of PV panels, just the total in terms of power, i.e., it does not present neither models and the power of each PV panel nor the total of panels in series or parallel; (d) Battery autonomy is not an parameter that the user can set when using HOMER.
+HOMER includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics as maximum current and voltage, which are common during PV sizing; (b) HOMER demands to include some battery specification to initiate the optimization; however, it does not change the electrical specifications during the simulation; the presented results are multiples of the original battery type suggested by the user.
+As example, it was started with a $83.4$ Ah lead-acid battery, and during the simulation, HOMER Pro did not try to use other capacities or types; (c) HOMER does not present the optimal solution in terms of connections of arrays of PV panels, just the total in terms of power, i.e., it does present neither models and the power of each PV panel nor the total of panels in series or parallel; (d) Battery autonomy is not a parameter that the user can set when using HOMER.
 

### 2019-09-24 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
updated Section IV.D
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Comparing the results between the formal synthesis with CPAchecker and HOMER Pro  (cf.~\textit{EQ2}), we observed that most results are quite similar, in terms of technical solution and cost (cf.
-Table~\ref{tab1}).
-Particularly related to LCC, the cost was very close in cases
-$1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
+Comparing the results between the formal synthesis with CPAchecker and HOMER Pro (cf.~\textit{EQ2}), 
+we observed that most results are quite similar, in terms of technical solution and cost (cf. Table~\ref{tab1}). 
+Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
 Even adopting the same price per kW to the PV panels, 
 inverters, and batteries, HOMER Pro does not use costs 
-related to charge controllers, which were introduced into the 
+related to charge controllers, which we introduced into the 
 CPAchecker modeling. The premise used in CPAchecker to adopt 
@@
 since this annual cost is too small when compared to the resulting LCC value.
-
-However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our automated synthesis tool, probably because the operation and maintenance costs assumed by our automated synthesis tool were underestimated to that specific load.
+However, there exists a considerable divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our automated synthesis tool, probably because we underestimated the operation and maintenance costs assumed by our automated synthesis tool to that specific load.
 

### 2019-09-24 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 Our study marks the first application of a sound and automated formal synthesis approach that can provide accurate results of optimal sizing of stand-alone PV systems, which outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies.
-\textcolor{red}{could you please summarise the main results here?
-Why are they good?} Thus, over the last two decades, we considerably advance the state-of-the-art in applied energy to optimally design PV systems.
+\textcolor{red}{The methodological research with automated synthesis produces more detailed and complete optimization when compared with the simulation tool, besides the fact that the sizing is closer to real PV systems deployed at isolated communities in Amazon area of Brazil.} Thus, over the last two decades, we considerably advance the state-of-the-art in applied energy to optimally design PV systems.
 
@@
 In this section, we present the theory and methodology created to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.
-Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual and simulation), and including the proposed automatic synthesis proposed here.
-The input information is the same for all the methods, with the difference that in automated validation, it is possible to define the bound $k$ to restrict the design-space search.
-\textcolor{red}{this sentence is unclear...
-Moreover, the outputs are not equal, as the design-space coverage and the, mainly, the final resulting}.
+
+\textcolor{red}{Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, showing the traditional techniques (manual and simulation), and including the proposed automatic synthesis.
+Worth to mention that the input information is the same for all the methods (weather data, detailed equipment and price information, design requirements, as load curve and power demand, and design assumptions), with the difference that in automated synthesis is possible to define the bound $k$ to restrict the design-space search.
+Related to the output presented by the techniques, all produce a successful or fail result considering a feasible technical solution that has the lowest cost.
+However when done by simulation we get a report or graphical result; in the other hand, the automated synthesis technique, that is a mathematical reasoning of a model, presents a counter-example with the optimal solution stored in variables.
+Furthermore, as it will be showed in this section, the design-space coverage during the optimal sizing search is more complete when using automated synthesis.}
 
 \begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{optimalsizingprocess2}
+\includegraphics[width=0.5\textwidth]{optimalsizingprocess3}
 \centering
-\caption{Comparative of optimal sizing methods. \textcolor{red}{could you please convert this figure into greyscale?}}
+\caption{Comparative of optimal sizing methods.}
 \label{fig:optimization}
@@
 \begin{table}[!t]
-\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
+\caption{Case studies and results: optimization of PV systems.}\label{tab1}
 \begin{scriptsize}
@@
 analysis: to include loss of load probability or loss of power 
-supply probability, which can make the analysis more accurate \textcolor{red}{how much? can you quantify?}; 
+supply probability, which can make the analysis more \textcolor{red}{precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, 
+based on historical data}; 
 ($2$) the cost analysis is well-tailored to the Amazon region of Brazil; 
@@
 performed to make the optimization general in terms 
-of applicability \textcolor{red}{cite example of areas?}; ($3$) to deploy at the field some PV systems 
-sized using our synthesized results to validate it \textcolor{red}{why is it important?}.
+of applicability \textcolor{red}{in other isolated areas of the world, as India and China, for example}; ($3$) to deploy at the field some PV systems 
+sized using our synthesized results to validate it\textcolor{red}{, because a comparative with a real system may be more reliable than comparing with a simulation tool}.
 
@@
 We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking techniques.
-The focus was on the synthesis method to obtain the optimal solution based on formal methods, which can cover the entire design-space as opposed to simulation tools.
+The focus was on the synthesis method to obtain the optimal solution based on formal methods, which can cover better the design-space as opposed to simulation tools.
 We have considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; one state-of-art verification engine was considered (CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
 
+\textcolor{red}{The paper produced a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.} 
 In summary, our synthesis tool is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
-In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage (or even the manufacturer name); we also cover the charge controller, which is unavailable in HOMER Pro.
+In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current, and voltage; we also cover the charge controller, which is unavailable in HOMER Pro.
 Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro; however, the presented solution is sound and complete; it also provides a list of equipment to be bought from manufacturers.
-\textcolor{red}{what is the scientific contribution?}
-
-Note further that we extended the CEGIS synthesis method and implemented this extension within our proposed formal synthesis tool, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
+\textcolor{red}{Moreover, we extended the CEGIS synthesis method and implemented this extension within our proposed formal synthesis tool, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.}
 

### 2019-09-25 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Our study marks the first application of a sound and automated formal synthesis approach that can provide accurate results of optimal sizing of stand-alone PV systems, which outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies.
-\textcolor{red}{The methodological research with automated synthesis produces more detailed and complete optimization when compared with the simulation tool, besides the fact that the sizing is closer to real PV systems deployed at isolated communities in Amazon area of Brazil.} Thus, over the last two decades, we considerably advance the state-of-the-art in applied energy to optimally design PV systems.
+In particular, the methodological research with automated synthesis produces more detailed and complete optimization when compared with the simulation tool, besides the fact that the sizing is closer to real PV systems deployed at isolated communities in the Amazon area of Brazil.
+Considering other studies carried out in the last two decades, we considerably advance the state-of-the-art in applied energy to optimally design PV systems.
 

### 2019-09-25 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-In this section, we present the theory and methodology created to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.
-
-\textcolor{red}{Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, showing the traditional techniques (manual and simulation), and including the proposed automatic synthesis.
-Worth to mention that the input information is the same for all the methods (weather data, detailed equipment and price information, design requirements, as load curve and power demand, and design assumptions), with the difference that in automated synthesis is possible to define the bound $k$ to restrict the design-space search.
-Related to the output presented by the techniques, all produce a successful or fail result considering a feasible technical solution that has the lowest cost.
-However when done by simulation we get a report or graphical result; in the other hand, the automated synthesis technique, that is a mathematical reasoning of a model, presents a counter-example with the optimal solution stored in variables.
-Furthermore, as it will be showed in this section, the design-space coverage during the optimal sizing search is more complete when using automated synthesis.}
-
+In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.
+In particular, Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis.
+Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions) except for the automated synthesis where we also define the bound $k$ to restrict the design-space search.
+Related to the output presented by both techniques, all of them produce a successful or fail result considering a feasible technical solution with the lowest cost.
+On the one hand, when done by simulation we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
+Furthermore, as described in this section, the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
+%
 \begin{figure}[h]

### 2019-09-25 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 analysis: to include loss of load probability or loss of power 
-supply probability, which can make the analysis more \textcolor{red}{precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, 
-based on historical data}; 
+supply probability, which can make the analysis more precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, 
+based on historical data; 
 ($2$) the cost analysis is well-tailored to the Amazon region of Brazil; 
@@
 performed to make the optimization general in terms 
-of applicability \textcolor{red}{in other isolated areas of the world, as India and China, for example}; ($3$) to deploy at the field some PV systems 
-sized using our synthesized results to validate it\textcolor{red}{, because a comparative with a real system may be more reliable than comparing with a simulation tool}.
+of applicability in other isolated areas of the world, such as India and China; ($3$) to deploy at the field some PV systems 
+sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
 

### 2019-09-25 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{red}{The paper produced a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.} 
+The paper produced a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
 In summary, our synthesis tool is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
@@
 Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro; however, the presented solution is sound and complete; it also provides a list of equipment to be bought from manufacturers.
-\textcolor{red}{Moreover, we extended the CEGIS synthesis method and implemented this extension within our proposed formal synthesis tool, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.}
+Moreover, we extended the CEGIS synthesis method and implemented this extension within our proposed formal synthesis tool, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
 

### 2019-09-25 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-This section presents the case studies used to evaluate our proposed approach.
+This section describes our case studies, experimental setup,  objectives, and results to evaluate our proposed synthesis approach.
 We also compare our approach with a specialized simulation tool (HOME Pro).
-The computing setup, the objectives of the experimental phase, and the results are also described.
 
@@
 
-We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (named Specification).
-These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil.
-For all cases, a estimated load curve (kWh) was defined based on the electronics consumers found of each house.
+We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (\textit{Specification}).
+These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil \textcolor{red}{add citation, e.g., project website?
+can you also briefly explain this project?
+we should also mention it in the beginning of our article}.
+For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.
 
@@
 
-The start-of-art verification tool, CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} was used as our verification engine to compare our approach effectiveness and efficiency.
+The start-of-art verification tool CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} was used as our verification engine to compare our approach effectiveness and efficiency.
 The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
@@
 $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
-Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
+For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
 with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
@@
 
-\item[EQ2] \textbf{(performance)} how does our formal synthesis tools compares to a specialized simulation tool?
+\item[EQ2] \textbf{(performance)} how does our formal synthesis tool compare to a specialized simulation tool?
 
@@
 
-In general, the size of the PV panels and battery bank were 
-bigger in HOMER Pro than with our formal synthesis approach, 
-and that discrepancy is not easy to address without some real 
-systems validation. The mathematical models are different and 
-particular parameters can be tuned as well in each approach, 
-and that can justify the difference, which was presented in all 
-the case studies. As comparative, let's consider case study $1$: 
-the optimal solution provided by HOMER Pro demands $7$ $\times$ 
-more PV panels than the solution presented by our synthesis tool, 
-and HOME Pro does not show the arrangement of arrays 
-(i.e., the number of series and parallel PV panels); 
-the battery bank presented by HOMER Pro provides $500.4$ Ah 
-of capacity ($6 \times 83.4$), while our synthesis tool 
-presented an optimal solution with $420$ Ah of total capacity 
-($4 \times 105$).
+In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach,  and that discrepancy is not easy to address without some real systems validation \textcolor{red}{why is it not easy?}.
+The mathematical models are different, and particular parameters can be tuned as well in each approach, and that can justify the difference presented in all the case studies.
+As comparative, consider case study $1$: the optimal solution provided by HOMER Pro demands $7$ $\times$ more PV panels than the solution presented by our synthesis tool, and HOME Pro does not show the arrangement of arrays (i.e., the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides $500.4$ Ah of capacity ($6 \times 83.4$), while our synthesis tool presented an optimal solution with $420$ Ah of total capacity ($4 \times 105$).
 

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Just to compare the results obtained from the optimization 
-with the real-world, the authors had four PV systems deployed 
-and monitored since June $2018$ in a riverside community 
-in the Amazonas State in Brazil (coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W), with similar power demands 
-presented by case studies $1$, $4$, $5$, and $6$, 
-always with a $3$ $\times$ $325$ W ($3$S) panels and 
-$4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) 
-lead-acid batteries. These solutions are more close 
-to the result presented by our formal synthesis 
-approach than HOMER Pro, thereby showing that our 
-solution is sound, which answers \textit{EQ1}.
-
-Related to the inverters, HOMER Pro suggests a value in 
-kW very close to the peak of every case study, and it 
-is just a reference value and not a commercial value of 
-the employed inverter. Our synthesis tool, however, 
-presents inverters that are commercial and can be found 
-off-the-shelf. Therefore is a PRO to the formal synthesis method.
-
-Concerning to charge controllers, as we reported in 
-the previous section, HOMER Pro does not include it 
-as an explicit equipment in its mathematical model, 
-only our synthesis tool presents a commercial controller 
-and includes it during the cost analysis. Therefore, 
-the formal synthesis method presents more reliable results than
-HOME Pro.
-
-Case study $7$ was not solved by our synthesis tool 
-within the time limit established during the experimental 
-phase. Case study $3$ was not possible to simulate in HOMER Pro, 
-because its restriction does not allow one to set the battery autonomy, 
-thus resting both without parameters to comparative.
+To compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil (coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W), with similar power demands presented by case studies $1$, $4$, $5$, and $6$,
+always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+These solutions are closer to the result presented by our formal synthesis approach than HOMER Pro, thereby showing that our solution is sound, which answers \textit{EQ1}.
+
+Related to the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter.
+Our synthesis tool, however,
+presents inverters that are commercial and can be found off-the-shelf; therefore, our approach is a PRO to the formal synthesis method.
+
+Concerning the charge controllers, as we reported in the previous section, HOMER Pro does not include it as an explicit equipment in its mathematical model; only our synthesis tool presents a commercial controller and includes it during the cost analysis.
+Therefore, the formal synthesis method presents more reliable results than HOME Pro.
+
+Our synthesis tool did not solve the case study $7$  within the time limit established during the experimental phase.
+Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters for comparison.
 

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
-
-However, in our variant CEGIS method proposed here, there are four particular differences related to the traditional CEGIS: 
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists, and our synthesis engine can then conclude that no feasible equipment combination was found.
+
+However, in our variant CEGIS method proposed here, there exist four distinct differences related to the traditional CEGIS: 
 (1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
@@
 (4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
-a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard 
-a given candidate that could be feasible in the next iteration with a new lower bound.
-
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
+a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
+
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here, we have used symbolic software verifiers based on SMT solvers.
 
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
-It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
-
+We adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
+%
  \begin{algorithm}
@@
 %
-
-Our synthesis algorithm will synthesize constant values; 
-it starts with the input of manufacturers data and prices of PV panels, batteries, 
-charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
-house requirements and design definitions, from lines $4$ and $5$.
+Our synthesis algorithm will synthesize constant values.
+It starts with the input of manufacturers' data and prices of PV panels, batteries, charge controllers, and inverters (line $2$).
+After that, we define user requirements, i.e., house requirements and design definitions, from lines $4$ and $5$.
 
 The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a 
-feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
-if that happens, then our algorithm has found an optimal solution, thereby stating 
-that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
-The $MaxCost$ value at line $6$ is just a very high value put as a limit 
-to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
-
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
-from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
-That procedure ensures that our synthesis engine checks all combinations of items 
-from each equipment, and combine them to assemble a feasible (candidate) PV solution, 
-which meets the user requirements.
-
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, 
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $22$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+The $MaxCost$ value at line $6$ is just a very high value put as a limit to the \textit{for}-loop, which never will be reached because the optimal solution will be found first \textcolor{red}{Is there some formal guarantee?}.
+
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (lines $7$ to $10$).
+That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.
+
+Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep},Eq.~\eqref{eq:NTPmin}, 
 Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
-Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} t
-o calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
-ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
-uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$. 
-Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
-and the cost of that solution is calculated in $F_{obj}$ (line $21$).
-
-If our algorithm does not find a feasible solution among the item of equipment that 
-were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
-the program finishes and does not find a solution, which indicates that it 
-was not possible to combine the items of each equipment in order to create a feasible solution.
-
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
-solution regarding the constraints and user requirements. Related to our {\sc Verify} 
-phase the challenge is to find the lowest acquisition cost from a list of equipment and 
-components that is provided from the {\sc Synthesize} phase.
-
-Note that the process described here in completely automated and that a validation is performed 
-by our {\sc Verify} phase to ensure that the approach is sound.
+Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
+ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$.
+Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, and we calcuate the cost of that solution in $F_{obj}$ (line $21$).
+
+If our algorithm does not find a feasible solution among the item of equipment that we provide to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution, which indicates that it was not possible to combine the items of each equipment in order to create a feasible solution.
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements.
+Related to our {\sc Verify} phase, the challenge is to find the lowest acquisition cost from a list of equipment and components that are provided from the {\sc Synthesize} phase.
+Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
 
@@
 
-Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, 
-a list of forty equipment from ten different manufacturers was provided 
-to our synthesis engine in order to allow the choice of every item 
-of PV sizing. Data sheet from each item was necessary to collect 
-technical information. Moreover, the price of each item was obtained 
-from available quotations in the market, and if the currency was not in US dollars, 
-then it was used the exchange rate of the day to convert it to US dollars.
+Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to our synthesis engine in order to allow the choice of every item of PV sizing.
+Data sheet from each item was necessary to collect technical information.
+Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
 

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 As a result,
-\textit{Contribution}.
+In summary, this paper makes the following original contributions.
+
+\begin{itemize}
+\item Our study marks the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems. 
+\item We propose a variant CEGIS method that consists of four distinct differences related to the traditional CEGIS: \textcolor{red}{explain here}
+\item Experimental results show that our proposed formal synthesis approach outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies.
+The median runtime for our case studies is X\,s, \textcolor{red}{is it good or bad?
+try to emphasize our main achievements gere}.
+\end{itemize}
+
+%\textit{Contribution}.
 Our study marks the first application of a sound and automated formal synthesis approach that can provide accurate results of optimal sizing of stand-alone PV systems, which outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies.

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 \item Our study marks the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems. 
-\item We propose a variant CEGIS method that consists of four distinct differences related to the traditional CEGIS: \textcolor{red}{explain here}
-\item Experimental results show that our proposed formal synthesis approach outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies.
-The median runtime for our case studies is X\,s, \textcolor{red}{is it good or bad?
-try to emphasize our main achievements gere}.
+\item \textcolor{red}{We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental iterative loop until the optimal cost solution of the system is reached.}
+\item Experimental results show that our proposed formal synthesis approach qualitatively outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies.
+\textcolor{red}{Our solution is far detailed and close to the commercial reality (real PV systems) than the solution presented by simulation}.
 \end{itemize}
@@
   \FOR {$HintCost=0$ to $MaxCost$}
- 	\STATE Declare non-deterministic variable to select PV Panel from list \\
- 	\STATE Declare non-deterministic variable to select Controller from list \\
- 	\STATE Declare non-deterministic variable to select Battery from list \\
- 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
+ 	\STATE Non-deterministic variable selects PV Panel from list \\
+ 	\STATE Non-deterministic variable selects Controller from list \\
+ 	\STATE Non-deterministic variable selects Battery from list \\
+ 	\STATE Non-deterministic variable selects Inverter from list \\ 	
  	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
@@
 %	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
-	\STATE non-deterministic variables hold feasible equipment and cost  \\
+	\STATE Variables hold feasible PV system candidate and cost  \\
 	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
@@
 
-The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $22$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value at line $6$ is just a very high value put as a limit to the \textit{for}-loop, which never will be reached because the optimal solution will be found first \textcolor{red}{Is there some formal guarantee?}.
+\textcolor{red}{The \textit{for}-loop on line 6 ensures the search for the lowest cost to the PV solution.
+The $MaxCost$ value is a very high value put as a limit to the loop, which never will be reached because the optimal solution will be found first.
+The formal guarantee of this statement is based on the fact that the cost is verified just after a feasible technical candidate if found on {\sc Synthesize} phase}.
+In particular, the loop starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $22$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
 
@@
 We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (\textit{Specification}).
-These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil \textcolor{red}{add citation, e.g., project website?
-can you also briefly explain this project?
-we should also mention it in the beginning of our article}.
+These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil.
+\textcolor{red}{This project, finished in March'2019, visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers\footnote{http://star-energy.coventry.ac.uk/}}.
 For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
minor fixes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
-\title{Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method}
+\title{Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis}
 %
@@
 \item Our study marks the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems. 
-\item \textcolor{red}{We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental iterative loop until the optimal cost solution of the system is reached.}
+\item We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop until we reach the optimal cost solution of the system.
 \item Experimental results show that our proposed formal synthesis approach qualitatively outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies.
-\textcolor{red}{Our solution is far detailed and close to the commercial reality (real PV systems) than the solution presented by simulation}.
+Our solution is far detailed and closer to the commercial reality (real PV systems) than the solution presented by simulation.
 \end{itemize}
@@
 
-\textcolor{red}{The \textit{for}-loop on line 6 ensures the search for the lowest cost to the PV solution.
+The \textit{for}-loop on line 6 ensures the search for the lowest cost to the PV solution.
 The $MaxCost$ value is a very high value put as a limit to the loop, which never will be reached because the optimal solution will be found first.
-The formal guarantee of this statement is based on the fact that the cost is verified just after a feasible technical candidate if found on {\sc Synthesize} phase}.
+The formal guarantee of this statement is based on the fact that the cost is verified just after a feasible technical candidate if found on {\sc Synthesize} phase.
 In particular, the loop starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $22$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
@@
 These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil.
-\textcolor{red}{This project, finished in March'2019, visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers\footnote{http://star-energy.coventry.ac.uk/}}.
-For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.
+This project finished in March 2019, where we visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers.\footnote{http://star-energy.coventry.ac.uk/} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.
 
@@
 He is also a collaborator in the Postgraduate Program in Electrical Engineering and Informatics at the Federal University of Amazonas (UFAM), Brazil.
-Prior to joining the University of Manchester, he worked as a researcher at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for 4 years as software engineer at industry.
+Before joining the University of Manchester, he worked as a researcher at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for four years as a software engineer in industry.
 His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
minor fixes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+\renewcommand{\baselinestretch}{0.97}
+
 \begin{document}
@@
 However, these tools rely on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-
+%
 Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods were developed and evaluated~\cite{Applasamy2011}.
-An ideal combination of any PV system consists of the best compromise between two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
+An ideal combination of any PV system consists of the best compromise between two objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
 
@@
 Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.
-
+%
 %Our work makes two major contributions.
@@
 The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required.
-The AC load dictates the behavior of the AC electrical load from the house.
+The AC load dictates the AC electrical load behavior from the house.
 %
@@
 Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture.
-Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur} from model checking.
+Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+%from model checking.
 %
@@
 
-However, in our variant CEGIS method proposed here, there exist four distinct differences related to the traditional CEGIS: 
+In our variant CEGIS method, there exist four distinct differences related to the traditional CEGIS: 
 (1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
@@
 The usual way is to use loss of load probability (LOLP) or loss of power 
-supply probability (LPSP). However, based on the fact that here we 
-are neither considering site characteristics nor the load changes over time, 
+supply probability (LPSP). However, we are neither considering site characteristics nor the load changes over time, 
 which demands historical data, the reliability analysis will be developed only 
 by the critical period method of PV sizing.
-
+%
 Regarding financial analysis:

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
minor fixes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
     [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alessandro3por4_2}}]{Alessandro Trindade}
-received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
-Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
-Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the Amazonas State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation.
+received his B.Sc.
+and M.Sc.
+in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
+Currently, he is pursuing his Ph.D.
+in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
+Before joining UFAM, he worked four years as a Consultant of renewable energy to the Amazonas State Electric Utility and the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation.
 His interest is in renewable energy, automated verification, and model checking.

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 
-In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach,  and that discrepancy is not easy to address without some real systems validation \textcolor{red}{why is it not easy?}.
-The mathematical models are different, and particular parameters can be tuned as well in each approach, and that can justify the difference presented in all the case studies.
+In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach, and determining which one is the correct depends on a comparison with field-deployed solar systems.
+The mathematical models are different in our model and the simulation tool, and particular parameters can be tuned.
+This may explain the difference presented in all case studies.
 As comparative, consider case study $1$: the optimal solution provided by HOMER Pro demands $7$ $\times$ more PV panels than the solution presented by our synthesis tool, and HOME Pro does not show the arrangement of arrays (i.e., the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides $500.4$ Ah of capacity ($6 \times 83.4$), while our synthesis tool presented an optimal solution with $420$ Ah of total capacity ($4 \times 105$).

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0 (copy).tex
IEEE Trans on Sustainable Energy paper

--- 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
@@
 
-The authors would like to thank: (i) Newton Fund [grant $261881580$] for the mobility support; (ii) FAPEAM - Amazonas Foundation for Research [PROTI-Pesquisa $2018$], for the mobility support to UK (NOV-$2018$); (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and (iv) University of Sheffield's QR GCRF Institutional Allocation for the HOMER Pro license.
+The authors would like to thank to University of Sheffield's QR GCRF for HOMER license.
+
+The authors would like to thank: (i) Newton Fund [grant $261881580$] for the mobility support; (ii) FAPEAM - Amazonas Foundation for Research [PROTI-Pesquisa $2018$], for the mobility support to UK (NOV-$2018$); (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and
 

### 2019-09-28 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
IEEE Trans on Sustainable Energy paper

@@
 \thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
+\thanks{The work of A. Trindade was supported in part by Newton Fund under Grant $261881580$, and in part by FAPEAM- Amazonas Foundation for Research under Grant PROTI-Pesquisa $2018$.}
 \thanks{Manuscript received September XY, 2019; revised XXXXX 11, 2019.}}
@@
 \begin{abstract}
-There exist various methods and computer tools to size solar photovoltaic systems; however, these tools rely on simulations, which do not cover all aspects of the design space during the search for the optimal solution.
-In prior studies related to optimal sizing of photovoltaic systems, the focus was always on criteria or objectives.
-Here, we present a new sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using an unprecedented program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound cost via symbolic model checking.
-If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-We provide commercial equipment data from different manufacturers to our synthesis engine and derive candidate solutions from financial analysis.
-Experimental results using seven case studies show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
-We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which can provide a more detailed and accurate solution than that existing simulation tool.
+There exist various methods and tools to size solar photovoltaic systems; however, these tools rely on simulations, which do not cover all aspects of the design space during the search for optimal solution.
+In prior studies in optimal sizing, the focus was always on criteria or objectives.
+Here, we present a new sound and automated approach to obtain optimal sizing  using an unprecedented program synthesis.
+Our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases linking the technical and cost analysis: first we synthesize a feasible candidate based on power reliability, but that may not achieve the lowest cost; second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
+If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample provides the optimal solution.
+Experimental results using seven case studies and commercial equipment data show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
+We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which can provide a more detailed and accurate solution than that simulation tool.
 \end{abstract}
@@
 
-To simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general-purpose simulation tools, e.g., PSpice~\cite{Gow1999}, or MATLAB/Simulink package~\cite{Benatiallah2017}.
+%To simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general-purpose simulation tools, e.g., PSpice~\cite{Gow1999}, or MATLAB/Simulink package~\cite{Benatiallah2017}.
 However, these tools rely on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 %
+To simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}; and even general-purpose simulation tools, as  MATLAB~\cite{Benatiallah2017}.
+However, these tools rely on simulation, with the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+
 Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods were developed and evaluated~\cite{Applasamy2011}.
@@
 In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices, interacting over a smart grid infrastructure~\cite{Abate2017}.
-Finally, in $2018$, a verification methodology was applied to PV panels (not a complete PV system) and its distributed power point tracking~\cite{Driouich2018}.
+In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
+Finally, in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
 However, prior studies did not deal with electricity generation or even solar PV systems optimization.
@@
 Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.
-%
+
 %Our work makes two major contributions.
@@
 As a result,
-In summary, this paper makes the following original contributions.
-
-\begin{itemize}
-\item Our study marks the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems. 
-\item We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop until we reach the optimal cost solution of the system.
-\item Experimental results show that our proposed formal synthesis approach qualitatively outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies.
+In summary, this paper makes the following original contributions: (i) It is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems; (ii) We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop to reach the optimal cost solution of the system; and (iii)  Experimental results with seven case studies show that formal synthesis approach qualitatively outperforms an existing state-of-the-art simulation tool.
 Our solution is far detailed and closer to the commercial reality (real PV systems) than the solution presented by simulation.
-\end{itemize}
 
@@
 	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
-	\caption{CEGIS applied to PV system sizing.}
+	\caption{CEGIS adapted to PV system sizing.}
 	\label{Counter-Example-Guided-Inductive-Synthesis}
@@
 
-The authors would like to thank: (i) Newton Fund [grant $261881580$] for the mobility support; (ii) FAPEAM - Amazonas Foundation for Research [PROTI-Pesquisa $2018$], for the mobility support to UK (NOV-$2018$); (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and (iv) University of Sheffield's QR GCRF Institutional Allocation for the HOMER Pro license.
+The authors would like to thank to University of Sheffield's QR GCRF for HOMER Pro license.
 
@@
 % or if you just want to reserve a space for a photo:
-\begin{IEEEbiography}
-    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alessandro3por4_2}}]{Alessandro Trindade}
-received his B.Sc.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{IEEEbiography}
+%    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{alessandro3por4_2}}]{Alessandro Trindade}
+%received his B.Sc.
 and M.Sc.
@@
 His interest is in renewable energy, automated verification, and model checking.
-\end{IEEEbiography}
-%
-%\begin{IEEEbiographynophoto}{Alessandro Trindade}
-%received his BSc and MSc in Electrical Engineering from the Federal University of Amazonas (UFAM) in 1995 and 2015, respectively.
-Currently, he is pursuing his PhD in the Postgraduate Program in Informatics (PPGI) at UFAM, and holds an Assistant Professor position in the Electricity Department from UFAM.
-Prior to joining UFAM, he worked 4 years as Consultant of renewable energy to the State Electric Utility and to the Inter-American Institute for Cooperation on Agriculture (IICA); he also worked for 12 years as R\&D and project manager at a non-profit foundation (Centre of Analysis, Research and Innovation Technology Foundation).
-His interest is in renewable energy, automated verification, and model checking.
-%\end{IEEEbiographynophoto}
-%
-% if you will not have a photo at all:
-\begin{IEEEbiography}
-    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lucas3por4}}]{Lucas Cordeiro}
-received his Ph.D.
+%\end{IEEEbiography}
+%\begin{IEEEbiography}
+%    [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lucas3por4}}]{Lucas Cordeiro}
+%received his Ph.D.
 degree in Computer Science in 2011 from the University of Southampton, UK.
@@
 His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.
-\end{IEEEbiography}
+%\end{IEEEbiography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % You can push biographies down or up by placing

### 2019-10-08 Tex/Old text/abstract.tex
Thesis update

@@
 This Thesis marks two mains achievements: (1) the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load; and (2) a sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis, where every component and function of a solar photovoltaic system is described, including its properties, and the behavioral model that represents the optimal sizing can be synthesized automatically.
-Related to formal verification, case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Different verification tools were evaluated as well, in order to compare performance and soundness.
-Data from practical applications show the effectiveness of the proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
-Moreover, related to the use of program synthesis, it is proposed a variant of counterexample guided inductive synthesis (CEGIS) approach, with two well-defined phases: first it synthesizes the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
+Related to formal verification, case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, are used to evaluate the proposed approach and to compare that with specialized simulation tool.
+Different verification tools are evaluated as well, in order to compare performance and soundness.
+Data from practical applications show the effectiveness of our proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
+Moreover, related to the use of program synthesis, we propose a variant of counterexample guided inductive synthesis (CEGIS) approach, with two well-defined phases: first it synthesizes the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
 If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.

### 2019-10-08 Tex/Old text/resumo.tex
Thesis update

@@
 Esta tese marca duas conquistas principais: (1) a primeira aplicação de modelagem de software para verificar o projeto de um sistema isolado solar fotovoltaico, incluindo painel solar, controlador de carga, bateria, inversor e carga elétrica; e (2) uma abordagem confiável e automatizada para obter o dimensionamento ótimo de sistemas fotovoltaicos usando a síntese de programas, onde cada componente e função de um sistema solar fotovoltaico é descrito, incluindo suas propriedades, e o modelo comportamental que representa o dimensionamento ótimo é sintetizado automaticamente.
-Relacionado a verificação formal, estudos de caso de sistemas fotovoltaicos reais instalados em cinco localidades diferentes foram usados para avaliar a abordagem proposta e para compará-la com ferramenta de simulação especializada.
+Relacionado a verificação formal, estudos de caso de sistemas fotovoltaicos reais instalados em cinco localidades diferentes são usados para avaliar a abordagem proposta e para compará-la com ferramenta de simulação especializada.
 Diferentes ferramentas de verificação são avaliadas também, a fim de comparar o desempenho e a confiabilidade dos resultados.
 Dados de aplicações práticas mostram a eficácia da abordagem proposta, onde condições específicas que levam a falhas em um sistema solar fotovoltaico são detalhadas apenas pelo método de verificação automatizado.
-Além disso, em relação ao uso da síntese de programas, propõe-se a variante do método de síntese indutiva guiada por contraexemplos (CEGIS), com duas fases bem definidas: primeiro ele sintetiza o dimensionamento de sistemas fotovoltaicos baseados em confiabilidade de energia, mas que pode não alcançar o menor custo; segundo, a solução proposta é então verificada iterativamente com um limite inferior via verificação de modelo simbólico.
+Além disso, em relação ao uso da síntese de programas, propõe-se uma variante do método de síntese indutiva guiada por contraexemplos (CEGIS), com duas fases bem definidas: primeiro ele sintetiza o dimensionamento de sistemas fotovoltaicos baseados em confiabilidade de energia, mas que pode não alcançar o menor custo; segundo, a solução proposta é então verificada iterativamente com um limite inferior via verificação de modelo simbólico.
 Se a etapa de verificação não falhar, o limite inferior será ajustado; e se falhar, o contraexemplo é fornecido com o dimensionamento ótimo, vinculando assim a resposta técnica da primeira fase à análise de custo da segunda fase.
@@
 O método de síntese proposto é novo e sem precedentes para simplificar o projeto de sistemas fotovoltaicos.
-Resultados experimentais usando sete estudos de caso mostram que o método de síntese é capaz de produzir em um tempo de execução aceitável o dimensionamento ótimo do sistema fotovoltaico, e um comparativo com uma ferramenta de simulação especializada e sistemas fotovoltaicos reais mostra a eficácia da abordagem adotada.
+Resultados experimentais usando sete estudos de caso mostram que o nosso método de síntese é capaz de produzir em um tempo de execução aceitável o dimensionamento ótimo do sistema fotovoltaico, e um comparativo com uma ferramenta de simulação especializada e sistemas fotovoltaicos reais mostra a eficácia da abordagem adotada.
 

### 2019-10-09 Tex/Old text/abstract.tex
Thesis update

@@
 Data from practical applications show the effectiveness of our proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
-Moreover, related to the use of program synthesis, we propose a variant of counterexample guided inductive synthesis (CEGIS) approach, with two well-defined phases: first it synthesizes the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking.
-If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-Commercial equipment data from different manufacturers are provided to the synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
+Moreover, related to the use of program synthesis, we propose a variant of counterexample guided inductive synthesis (CEGIS) approach, with two phases linking the technical and cost analysis: first we synthesize a feasible candidate based on power reliability, but that may not achieve the lowest cost; second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
+If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample provides the optimal solution.
 The proposed synthesis method is novel and unprecedented to streamline the design of photovoltaic systems.
-Experimental results using seven case studies show that the proposed synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of approach.
+Experimental results using seven case studies and commercial equipment data show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
+We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which can provide a more detailed and accurate solution than that simulation tool.
 

### 2019-10-09 Tex/Old text/chapters/chapter02.tex
Thesis update chapter 2 k missing
Thesis update

@@
 
-And secondly, how a solar PV system can be modelled in order to be validated or optimized by the formal verification methodology.
+And secondly, how a solar PV system can be modeled in order to be validated or optimized by the formal verification methodology.
 
@@
 \begin{itemize}
-\item Formal Specification: During the formal specification phase, the engineer rigorously defines a system using a modelling language.
+\item Formal Specification: During the formal specification phase, the engineer rigorously defines a system using a modeling language.
 Modeling languages are fixed grammars which allow users to model complex structures out of predefined types (are rigorously defined).
@@
 By building a system using a formal specification, the designer is actually developing a set of theorems about his system.
-By proving these theorems correct, the formal verification ensures that the modelled system has an intended behavior.
+By proving these theorems correct, the formal verification ensures that the modeled system has an intended behavior.
 Verification is a difficult process, largely because even the simplest system has several dozen theorems, each of which has to be proven.
@@
 BMC is a method that checks the model up to a given path in the path length.
-BMC algorithms traverses a finite state machine for a fixed number of steps, , and checks whether violation occurs with this bound.
+BMC algorithms traverses a finite state machine for a fixed number of steps, $k$, and checks whether violation occurs with this bound.
 It uses fast SAT solvers, where SAT means satisfiability.

### 2019-10-09 Tex/Old text/chapters/introduction.tex
Thesis update

@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
+Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
 The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
@@
 %
-Manufactures and integrators have yet their proprietary software to perform various system sizing \textcolor{red}{add citation}, with the drawback of including just their own products among the possibilities of choice, which restricts their solution.
+Manufactures and integrators have yet their proprietary software to perform various system sizing\textcolor{red}{~\cite{Zhou2010}}, with the drawback of including just their own products among the possibilities of choice, which restricts their solution.
 %
@@
 The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-However, those tools are based on running experiments in simulation models \textcolor{red}{which tools?}.
+However, \textcolor{red}{public domain and commercial software or even proprietary tools are based on running experiments in simulation models}.
 Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded, but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
@@
 
-\textcolor{red}{I think we're giving too much emphasis in tool development here. You should focus your description on research objectives!}
+\textcolor{red}{The main objective of this thesis is thus to propose and evaluate the use of formal methods in solar PV systems, using a computer science method to solve a specific issues of the electrical engineering area.
+In particular, we focus on automated verification by model checking, on stand-alone solar PV systems that is most adequate to rural areas of developing countries, on the need to validate and optimize those systems, on evaluating different state-of-art symbolic software verifiers (and solvers) with the goal of obtaining the best performance in our verification back-end, on applications written in ANSI-C that are platform-independent; and we do not perform code modification on the verifiers or solvers, we use it as available by their developers.
+We further evaluate our proposed solution by comparative with commercial simulation tool and by data collected from real PV systems deployed at riverside communities.}
+%More specifically we will:
+%The thesis produces a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
 
-This Thesis has the novelty of applying automated verification method to solar PV systems.
+This PhD thesis has the novelty of applying automated verification method to solar PV systems.
 The result is the development of two software: one to perform automated verification and validate the solar PV systems behavior; and another one to produce the optimal sizing of solar PV systems through automated synthesis program.
@@
 
+Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system (if a sized system must evaluated if meets the user demands) and optimal sizing (if there is just the demands and not the size of the PV system).
+We thus develop algorithms and the corresponding tools and evaluate them using comparative with simulation tool and real data from deployed PV systems.
+
+XXXThe tools are built using a number of advanced (and complex) techniques, including symbolic execution engines, satisfiability modulo theories
+solvers, context-bounded analysis, and partial order reduction. We use off-the-shelf
+software wherever possible and focus our effort on a comprehensive and implemented
+SMT-based model checking procedure to verify embedded software or more precisely, fi-
+nite approximations of embedded software. In particular, we reuse the C/C++ front-end
+from the CProver framework3 and use existing SMT solvers
+
 %----------------------------------------------
@@
 
-Associated to \textbf{automated verification}, this Thesis makes three main contributions.
+Associated to \textbf{automated verification}, this thesis makes three main contributions.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
@@
 
-And linked to \textbf{automated synthesis}, this work makes three major contributions. 
-\textbf{First}, the use of automated symbolic verification methods in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented.
+And linked to \textbf{automated synthesis}, our work makes more three original contributions: \textbf{First}, it is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems;
+\textbf{Secondly}, we propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop to reach the optimal cost solution of the system; and
+\textbf{Thirdly}, experimental results with seven case studies show that formal synthesis approach qualitatively outperforms an existing state-of-the-art simulation tool.
+Our solution is far detailed and closer to the commercial reality (real PV systems) than the solution presented by simulation.
+
+%three major contributions. 
+%\textbf{First}, the use of automated symbolic verification methods in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented.
 Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with the user requirements and environment constraints, and the proposed synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
-\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in the verification back-end for synthesizing optimal PV systems, thereby being the first work that performs this type of evaluation.
-\textbf{Third}, the experimental results show that the proposed synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
-As a result, this Thesis marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.
+%\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in the verification back-end for synthesizing optimal PV systems, thereby being the first work that performs this type of evaluation.
+%\textbf{Third}, the experimental results show that the proposed synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
+As a result, this thesis marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.
 Thus, this research considerably advances the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.
@@
 In $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
+The authors employed a stochastic model checking approach and presented a modeling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
 The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here, the authors employed automated verification of certain quantitative properties of the system, as probability of	 node failure in the long run, impact of repair service on the failure risk, and expected energy consumption, without any interest in power generation or even solar PV systems.
@@
 Other related studies from $2015$ include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis using statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
-In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+In order to demonstrate Modana's capability, the authors modeled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
 The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
@@
 
-\textcolor{red}{you should add some paragraphs here to describe the difference of your work to other available in the literature.}
+\textcolor{red}{However, prior studies did not deal with formal verification of a complete stand-alone PV system (with batteries, charge controller, and power inverter) or even solar PV systems optimization.
+Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in literature.
+And it is exactly in those gaps that this thesis focuses.}
 
@@
 %----------------------------------------------
+
+\textcolor{red}{This introduction has outlined the context, motivation, and problem addressed by this thesis, and the objectives, solution and contributions of the research.
+The remainder of the chapters of this thesis are organized as follows:}
 

### 2019-10-09 Tex/Old text/chapters/introduction.tex
Thesis update

@@
 %----------------------------------------------
+%\textcolor{red}{you should briefly describe here the outline of your solution. As example, take a look at \url{https://ssvlab.github.io/lucasccordeiro/papers/phd\_thesis\_cordeiro.pdf.}}
 
-\textcolor{red}{you should briefly describe here the outline of your solution. As example, take a look at \url{https://ssvlab.github.io/lucasccordeiro/papers/phd\_thesis\_cordeiro.pdf.}}
+\textcolor{red}{Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system (when a sized system must be evaluated in order to define if it meets the design requirements and user needs) and optimal sizing (when there are just the requirements and not the size of the PV system).
+We thus develop algorithms and the corresponding tools, moreover we evaluate them using comparative process in several case studies with simulation tool and real data from deployed PV systems.}
 
-Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system (if a sized system must evaluated if meets the user demands) and optimal sizing (if there is just the demands and not the size of the PV system).
-We thus develop algorithms and the corresponding tools and evaluate them using comparative with simulation tool and real data from deployed PV systems.
+\textcolor{red}{Fig.\ref{fig:validation_outline} outlines the proposed solution to perform the validation of stand-alone solar PV systems via automated verification.
+And Fig.\ref{fig:optimization_outline} illustrates the proposed solution to obtain the optimal sizing of stand-alone solar PV systems via automated synthesis.
+We describe here only a summary of each phase of our proposed approach, with highlights to the input parameters, the outputs and to the design-space coverage during the search for the validation or the optimal size of solar PV system; more details are presented in the next chapters.}
 
-XXXThe tools are built using a number of advanced (and complex) techniques, including symbolic execution engines, satisfiability modulo theories
-solvers, context-bounded analysis, and partial order reduction. We use off-the-shelf
-software wherever possible and focus our effort on a comprehensive and implemented
-SMT-based model checking procedure to verify embedded software or more precisely, fi-
-nite approximations of embedded software. In particular, we reuse the C/C++ front-end
-from the CProver framework3 and use existing SMT solvers
+\begin{figure}[h]
+\includegraphics[width=0.85\textwidth]{verification_outline.png}
+\centering
+\caption{Proposed validation of PV systems via automated verification.}
+\label{fig:validation_outline} 
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=0.85\textwidth]{optimization_outline.png}
+\centering
+\caption{Proposed optimal sizing of PV systems via automated synthesis.}
+\label{fig:optimization_outline} 
+\end{figure}
 

### 2019-10-11 Tex/Old text/abstract.tex
Thesis update

@@
 Moreover, the use of automated synthesis in order to obtain optimal sizing of solar photovoltaic systems was never done before.
-This Thesis marks two mains achievements: (1) the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load; and (2) a sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis, where every component and function of a solar photovoltaic system is described, including its properties, and the behavioral model that represents the optimal sizing can be synthesized automatically.
+This PhD thesis marks two mains achievements: (1) the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load; and (2) a sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis, where every component and function of a solar photovoltaic system is described, including its properties, and the behavioral model that represents the optimal sizing can be synthesized automatically.
 Related to formal verification, case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, are used to evaluate the proposed approach and to compare that with specialized simulation tool.

### 2019-10-11 Tex/Old text/chapters/introduction.tex
Thesis update

@@
 
-Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV).
+Among the options of renewable sources, there are hydro, wind, and solar PV.
 According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
-In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials.
+In solar PV systems, solar radiations are captured from the sun and turned into electricity using solar PV cells made of silicon and other materials.
 
@@
 
-\textcolor{red}{Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system (when a sized system must be evaluated in order to define if it meets the design requirements and user needs) and optimal sizing (when there are just the requirements and not the size of the PV system).
-We thus develop algorithms and the corresponding tools, moreover we evaluate them using comparative process in several case studies with simulation tool and real data from deployed PV systems.}
+\textcolor{red}{Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system and optimal sizing.
+Validation when a sized system must be evaluated in order to define if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or then the user tries to obtain a better solution that he or she has.
+We thus develop algorithms and the corresponding tools, moreover we evaluate them using comparative process in several case studies with specialized simulation tool and real data from deployed PV systems.}
 
@@
 And Fig.\ref{fig:optimization_outline} illustrates the proposed solution to obtain the optimal sizing of stand-alone solar PV systems via automated synthesis.
-We describe here only a summary of each phase of our proposed approach, with highlights to the input parameters, the outputs and to the design-space coverage during the search for the validation or the optimal size of solar PV system; more details are presented in the next chapters.}
+We pictured here only a summary of each phase of our proposed approach, with highlights to the input parameters, the outputs for the validation or the optimal size of solar PV system; more details are presented in the next chapters.
+Moreover, the illustrations show the methodological approach related to comparative result analysis, employing our approaches, commercial software tool and data from real PV systems deployed at the field.}
 
 \begin{figure}[h]
-\includegraphics[width=0.85\textwidth]{verification_outline.png}
+\includegraphics[width=0.85\textwidth]{verification_outline2.png}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.85\textwidth]{optimization_outline.png}
+\includegraphics[width=0.85\textwidth]{optimization_outline2.png}
 \centering
@@
 \end{figure}
+
+Worth to mention that is out of our scope to perform code modification on the verifiers or the solvers used during the automated verification or automated synthesis steps of our approach.
 

### 2019-10-15 Tex/Old text/chapters/chapter02.tex
Thesis update

@@
-In this chapter some concepts related to the intersection of the two areas of this research are presented: the computer science applied to an electrical engineering problem, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.
-
-First, the concept of formal verification is introduced as background to understanding how a methodology that performs (mainly) bug detection can be used to validate a design sizing or to obtain an optimal solution of PV systems.
+In this chapter we present some concepts related to the intersection of the two areas: the computer science applied to an electrical engineering problem, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.
+
+First, we introduce the concept of formal verification as background to understanding how a methodology that performs (mainly) bug detection can be used to validate a design sizing or to obtain an optimal solution of PV systems.
 
@@
 
-Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study.
+Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. In other words, the problem is not dealing with an abstraction of the actual system under study.
 
@@
 
-At this work will be evaluated three state-of-the-art model checkers to formally verifying and synthesize PV designs w.r.t. user requirements.
+At this work we will evaluated three state-of-the-art model checkers to formally verifying and synthesize PV designs w.r.t.
+user requirements.
+Moreover, different solvers will be evaluated as well, according with the feature of each model checker.
 
@@
 
+Particularly, CBMC comes with a built-in solver for bit-vector formulas that is based on MiniSat. We used this solver during the experimentation in this PhD thesis~\cite{Kroening}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+ESBMC in 'incremental SMT' uses only Z3 solver~\cite{DeMoura}.
 
@@
 
+Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}.
+Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do.
+The specification needs to describe the program's desired behavior to ensure that the program does what it intends.
+
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
@@
 \section{Solar Photovoltaic System }
+
 According to \cite{Roy}, a PV system is designed to give the electric supply to a load.

### 2019-10-15 Tex/Old text/chapters/chapter03.tex
revised Chapter 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
Thesis update

@@
+%\textcolor{red}{This title ``Methodology'' is too generic!!! methodology of what?}
+%
 %\section{Introduction}
 %
-In this Chapter, the adopted methodologies to perform formal verification and optimal sizing of stand-alone solar PV systems using formal methods, more specifically model checking, will be detailed.
+In this Chapter, we detail the adopted methodologies to perform formal verification and optimal sizing of stand-alone solar PV systems using formal methods, more specifically model checking.
 Diagrams, flowcharts, and algorithms support and explain the solutions.
 
-Besides that, all the assumptions and premises adopted are presented.
+Besides that, we present all the assumptions and premises adopted.
 Both support the results/conclusions, with direct impact on it.
@@
 Unlike the premise, assumptions are not explicitly stated and need to be deciphered.
-With that in mind, a detailed explanation of assumptions is performed for all over this Chapter.
+With that in mind, we perform a detailed explanation of assumptions all over this Chapter.
 
 It is important to emphasize that the whole explanation about the theoretical basis of the two subjects discussed here are present in the previous chapter.
-In addition, the author suggests that previous reading be done to facilitate understanding.
+In addition, we do suggest that previous reading must be done to facilitate the understanding.
 

### 2019-10-17 Tex/Old text/main.tex
thesis updated text
revised Chapter 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
Thesis update
updated thesis title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \documentclass[12pt,twoside]{report}
+\usepackage{titlesec}         %para 4 níveis de subsection com numeração
+\setcounter{secnumdepth}{4}   %para 4 níveis de subsection com numeração
+\setcounter{tocdepth}{4}      %pata 4 níveis no TOC com numeração aparecendo
 %\documentclass[12pt,a4paper]{ltxdoc}
@@
 \usepackage[utf8]{inputenc}		% determina a codificação utilizada (conversão automática dos acentos)
-\usepackage{hyperref}  			% controla a formação do índice
+\usepackage[breaklinks]{hyperref}
 \usepackage{parskip}			% espaçamento entre os parágrafos
@@
 %\documentclass[10pt,a4paper]{article}
-%\usepackage[utf8]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
@@
 
-\title{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation}
+\title{Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation}
 \author{Alessandro Trindade}
@@
 %\thispagestyle{empty}
+\newpage
 
@@
 \fancyhead{}
-\fancyhead[RO,LE]{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
+\fancyhead[RO,LE]{Automated Verification of Stand-alone Solar Photovoltaic Systems}
 \fancyfoot{}
@@
 \chapter{Background}
+\label{chap:background}
 \input{chapters/chapter02}
 
-\chapter{Methodology}
+\chapter{Automated Verification and Synthesis Methodologies}
+\label{chap:methodology}
 \input{chapters/chapter03}
@@
 \chapter{Automated Formal Verification of Stand-Alone Solar PV Systems}
+\label{chap:automatedverification}
 \input{chapters/chapter04}
@@
 \chapter{Automated Formal Synthesis Optimization Method for Sizing of Stand-Alone Solar PV Systems}
+\label{chap:automatedsynthesis}
 \input{chapters/chapter05}
@@
 \chapter{Conclusions}
+\label{chap:conclusions}
 \fancyfoot[CO,CE]{Conclusions}
@@
 \chapter{List of Publications}
+\label{chap:publications}
 \fancyfoot[CO,CE]{Appendix}
@@
 \renewcommand\bibname{References}
+\bibliographystyle{abntex2-num}
 \bibliography{trindadeThesis}{}

### 2019-10-20 Tex/Old text/chapters/appendix.tex
Thesis update

--- 2019-07-03 Tex/Old text/chapters/appendix.tex
@@
-\textbf{List of Publications}
+%\textbf{List of Publications}
+%
+\section{List of Publications}
+Here there are a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.
 
-Journals-------------------
-Automated Formal Verification of Stand-alone Solar Photovoltaic Systems, 8-May submitted, in review Elsevier Solar Energy (IF 4.374, A1 interdisciplinar, A1 eng.
-IV ) https://www.journals.elsevier.com/solar-energy
+\subsection{Journals}
 
-An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative, 29-June submitted, Elsevier Applied Solar (IF 7.900, A1 interdisciplinar, A2 Eng.
-IV, B1 ciência da computação) https://www.journals.elsevier.com/applied-energy
+Trindade, A., Cordeiro, L.
+\textbf{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}, submitted: 8 May 2019, status: accepted 26 September 2019; published on-line on 15 October 2019) by Elsevier Solar Energy (Impact Factor 4.674, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV) \url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X1930965X}
 
-Congress--------------------
-Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems - submitted 06-MAY-2019 - New Ideas papers - ASE 2019 The IEEE/ACM Automated Software Engineering (ASE 2019) Conference
+Trindade, A., Cordeiro, L.
+\textbf{Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis}, submitted: 28 September 2019, status: under review by IEEE Transactions on Sustainable Energy (Impact Factor 7.65, CAPES A1 Engineering IV), \url{https://www.journals.elsevier.com/applied-energy}
+
+Trindade, A., Degelo, R., Santos Junior, E., Ismail, H., Silva, H., and Cordeiro, L.
+\textbf{Multi-core model checking and maximum satisfiability applied to hardware-software partitioning}, Online publication date: 15 November 2017, by International Journal of Embedded Systems (IJES), CAPES B2 Computing Engineering index.
+DOI:   \url {https://doi.org/10.1504/IJES.2017.10008947}.
+
+\subsection{Congress}
+Trindade, A., Cordeiro, L.
+\textbf{Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems}, submitted: 06 May 2019, status: rejected by The IEEE/ACM Automated Software Engineering (ASE 2019) Conference (New Ideas Papers) in \url{https://2019.ase-conferences.org/track/ase-2019-papers}.
+This paper is now the base of a new paper, for the 32nd International Conference on Computer-Aided Verification (CAV) 2020 with deadline in 23 January 2020 in \url{http://i-cav.org/2020/call-for-papers/}.
+
+\section{Tools Description and How to Use it}
+
+In this section, we describe the two tools created during the PhD process to implement and test the two scientific methodologies of the thesis.
+
+\subsection{Tools}
+
+\subsection{How to use it}

### 2019-10-20 Tex/Old text/chapters/chapter03.tex
Thesis update

@@
 %
-In this Chapter, we detail the adopted methodologies to perform formal verification and optimal sizing of stand-alone solar PV systems using formal methods, more specifically model checking.
+In this Chapter, we detail the adopted methodology to perform formal verification of stand-alone solar PV systems using formal methods, more specifically model checking.
 Diagrams, flowcharts, and algorithms support and explain the solutions.
@@
 
-It is important to emphasize that the whole explanation about the theoretical basis of the two subjects discussed here are present in the previous chapter.
+It is important to emphasize that the whole explanation about the theoretical basis of the subject discussed here is present in the previous chapter, ~\nameref{chap:background}.
 In addition, we do suggest that previous reading must be done to facilitate the understanding.
@@
 
-\section{Optimal Sizing of Solar PV Systems}
+\section{General Assumptions}
+\label{sec:assumptions}
 
-Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual, and simulation), and including the proposed automatic synthesis that is detailed in this Section.
-
-One more time, as depicted in automated verification process, the input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search.
-And the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.
-
-\begin{figure}[h]
-\includegraphics[width=1.0\textwidth]{optimalsizingprocess2}
-\centering
-\caption{Comparative of optimal sizing methods}
-\label{fig:optimization}
-\end{figure}
-
-\subsection{Variant of CEGIS}
-
-In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section ~\ref{sec:ProgramSynthesis}, Fig.~\ref{Counter-Example-Guided-Inductive-Synthesis}.
-This variant was created during this Thesis and it will be detailed in this Section.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
-	\caption{CEGIS applied to PV system sizing.}
-	\label{CEGISalt}
-\end{figure}
-
-Examples of specification used by the proposed method include solar insolation (site dependent), house power demand, house consumption energy, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
-Design assumptions are considered project specification as well.
-The assumptions regarding the optimal sizing are listed in Section~\ref{sec:OptAssumptions}.
-
-There are four particular differences related to the traditional CEGIS described in Figure ~\ref{Counter-Example-Guided-Inductive-Synthesis} when compared to the variant CEGIS used in the proposed approach:
-
-\begin{itemize}
-\item There exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
-\item If the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} 
-\item The lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
-\item As a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate that could be feasible in the next iteration with a new lower bound.
-\end{itemize}
-
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
-
-Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
-It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
-%
- \begin{algorithm}
- \caption{Synthesis algorithm}
- \begin{algorithmic}[1]
- \renewcommand{\algorithmicrequire}{\textbf{Input:}}
- \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE Initialize variables \\
-  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
-%  \STATE Declare list of controllers data and cost \\
-%  \STATE Declare list of batteries data and cost \\
-%  \STATE Declare list of inverters data and cost \\
-  \STATE Declare the maximum possible cost $MaxCost$  \\
-  \STATE Declare power demand, power peak, energy consumption \\
-  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
-  \FOR {$HintCost=0$ to $MaxCost$}
- 	\STATE Declare non-deterministic variable to select PV Panel from list \\
- 	\STATE Declare non-deterministic variable to select Controller from list \\
- 	\STATE Declare non-deterministic variable to select Battery from list \\
- 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
- 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
-	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
- 	\STATE Calculate $C_{bank}$ \\
-	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
-	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
- 	\STATE Calculate $I_{sc,amb}$ \\
- 	\STATE Calculate $I_{c,min}$ \\
- 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
-	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
-	\STATE non-deterministic variables hold feasible equipment and cost  \\
-	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
-	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
-  \ENDFOR
- \RETURN $(\,)$ 
- \end{algorithmic} 
- \label{alg:opt-algorithm}
- \end{algorithm}
-%
-
-Our synthesis algorithm will synthesize constant values; 
-it starts with the input of manufacturers data and prices of PV panels, batteries, 
-charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
-house requirements and design definitions, from lines $4$ and $5$.
-
-The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. 
-In particular, it starts with cost $0$ and stops only when the algorithm finds a 
-feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
-if that happens, then our algorithm has found an optimal solution, thereby stating 
-that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
-The $MaxCost$ value at line $6$ is just a very high value put as a limit 
-to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
-
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
-from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
-That procedure ensures that our synthesis engine checks all combinations of items 
-from each equipment, and combine them to assemble a feasible (candidate) PV solution, 
-which meets the user requirements.
-
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, 
-Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
-Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
-ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
-uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$.
-Line $15$ is specific to the charge controller voltage check.
-Line $18$ checks the inverter check $I_{c}$, charge controller DC input voltage $V_{in}DC$, and charge controller AC output voltage $V_{in}DC$ check.
-Line $19$ ensures the power demand and the surge power of inverter.
-Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
-and the cost of that solution is calculated in $F_{obj}$ (line $21$). This cost is the equivalent of ~\ref{eq:LCC} described in Section ~\ref{sec:optcriteria}.
-
-If our algorithm does not find a feasible solution among the item of equipment that 
-were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
-the program finishes and does not find a solution, which indicates that it 
-was not possible to combine the items of each equipment in order to create a feasible solution.
-
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
-solution regarding the constraints and user requirements. Related to our {\sc Verify} 
-phase the challenge is to find the lowest acquisition cost from a list of equipment and 
-components that is provided from the {\sc Synthesize} phase.
-
-Note that the process described here is completely automated and that a validation is performed 
-by our {\sc Verify} phase to ensure that the approach is sound.
-
-\subsection{Optimization Assumptions and Premises}
-\label{sec:OptAssumptions}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Here some premise are presented and some adopted assumptions are explained for the optimal sizing method, regarding the automated synthesis and simulation software.
-
-Regarding the line $2$ of Algorithm~\ref{alg:opt-algorithm}, 
-a list of forty equipment from ten different manufacturers was provided 
-to the synthesis engine in order to allow the choice of every item 
-of PV sizing. Data sheet from each item was necessary to collect 
-technical information. Moreover, the price of each item was obtained 
-from available quotations in the market, and if the currency was not in US dollars, 
-then it was used the exchange rate of the day to convert it to US dollars.
-
-With respect to power reliability, this work will rely on the critical period solar 
-energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
-The usual way is to use loss of load probability (LOLP) or loss of power 
-supply probability (LPSP). However, based on the fact that here we 
-are neither considering site characteristics nor the load changes over time, 
-which demands historical data, the reliability analysis will be developed only 
-by the critical period method of PV sizing.
-
-Regarding financial analysis:
-\begin{itemize}
-	\item LCC lifetime considered: $20$ years;
-	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
-	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
-	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
-This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
-Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
-\end{itemize}
-
-On the subject of PV system optimization technique, we will adopt here the intuitive method 
-since the average value daily of solar irradiance is used in the mathematical model, 
-without considering the battery's state of charge, or even the random nature 
-of solar irradiation and meteorological conditions. Therefore, all the computational 
-effort will be concentrated in our automated synthesis algorithm.
-
-Regarding batteries, the voltage of the system (DC bus) is set in $24$ V DC (but the value can be adjusted to $12$ or $48$ V at the code).
-
-Related to HOMER Pro:
-
-\begin{itemize}
-	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
-	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
-However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
-	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
-	\item HOMER Pro do not have a explicit equipment called charge controller.
-It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
-During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
-	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
-By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
-For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable;
-	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
-	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
-HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
-\end{itemize}
-
-\section{General Assumptions}
-
-Here is listed the assumptions adopted for both methods developed on this Thesis.
+Here is listed the assumptions adopted for scientific methods of automated verification developed on this Thesis.
 
@@
 
-Regarding the automated verification and automated synthesis methods:
+Regarding the automated verification scientific method:
 
@@
 Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis, however RETScreen do not have stand-alone solar PV system analysis capacity.
-Therefore, in this study, HOMER Pro will be the only simulation tool used to compare with our automated synthesis method.
+Therefore, in this study, HOMER Pro will be the only simulation tool used to compare with our method.
 
@@
 
-This Chapter showed in details how the automated verification method and the automated synthesis method, two state-of-art tools used in computer science, were adapted in order to be used in stand-alone solar PV systems to validate their behavior or the obtain the optimal project sizing.
-Moreover, is was possible to picture how the proposed methods are compared with the traditional ones used for the same purpose.
+This Chapter showed in details how the state-of-art computer science method of automated verification was adapted in order to be used in stand-alone solar PV systems to validate their behavior.
+Moreover, is was possible to picture the comparative of how the proposed method and the traditional one of simulation work differently.
 
 Detailed diagrams, flowcharts and algorithms with pseudo-code were presented with the aim to support the proposed work and to facilitate the understanding.
-And even more so, the assumptions adopted for the automated verification and simulation software were listed, because those assumptions have impact at the results there will be presented at the next two Chapters.
+And even more so, the assumptions adopted for the automated verification and simulation software were listed, because those assumptions have impact at the results there will be presented at \autoref{chap:automatedverification}.

### 2019-10-20 Tex/Old text/chapters/chapter04.tex
Thesis update

--- 2019-07-22 Tex/Old text/chapters/chapter04.tex
@@
-This Chapter is devoted to the results of using automated verification to validate the intended behavior of stand-alone solar PV systems.
-Moreover, there is the comparative with a specialized simulation tool, and even the use of different verifiers who perform the automated verification in order to evaluate performance.
-Tables, commented reports, and graphical outputs are presented to aid the understanding.
+In this Chapter, we detail the adopted methodology to perform optimal sizing of stand-alone solar PV systems, more specifically using model checking.
+Diagrams, flowcharts, and algorithms support and explain the solutions.
 
-\section{Description of the Case Studies}
-%------------------------------------------
-%
-%We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
-We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
-%Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
-These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+Besides that, we present all the assumptions and premises adopted. This chapter supports as well the results/conclusions, with direct impact on it.
 
-Worth to mention that the load curve represents a array of 24 integer numbers for every hour of the day (instant power in Watts) and it was estimated after visiting and survey applied in June of 2017, before the houses were electrified.
+It is important to emphasize that the whole explanation about the theoretical basis of the subject discussed here is present in the previous chapter.
+In addition, we do suggest that previous reading must be done to facilitate the understanding.
 
-\begin{table}
-\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
-\begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\hline
-Item & House 1 & House 2 & House 3 & House 4 & House 5\\
-\hline
-\hline
-PV Panels &  \multicolumn{4}{|c|}{3$\times$325 W: (3S)} & 4$\times$325 W: (2S-2P) \\
-\hline
-Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah: (4S)\\ autonomy: 6 h}\\
-\hline
-Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
-\hline
-Inverter & \multicolumn{4}{|c|}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
-\hline
-Power peak (W)& 342  & 253  & 263 & 322 & 814 \\
-\hline
-Power surge (W)& 342 & 722 & 732 & 896 & 980\\
-\hline
-Load curve (W) & \multicolumn{5}{|l|}{\makecell{House 1: 118-118-118-46-46-46-95-95-170-170-296-242-242-95-95-95-95-95-342-288-288-288-288-118\\House 2: 136-136-136-136-136-136-67-67-184-184-184-184-184-67-67-67-67-67-253-253-253-253-253-136\\House 3: 113-113-113-113-113-113-67-67-217-97-97-97-97-97-97-97-97-97-263-113-113-113-113-113\\House 4: 207-207-207-135-135-135-66-66-161-161-233-253-248-66-66-66-66-66-302-317-322-302-302-207\\House 5: 45-16-16-16-16-16-0-0-0-72-72-222-150-150-0-0-72-72-814-814-814-742-742-16}}\\
-\hline
-\makecell{Consumption\\ (kWh/day)}& 3.9 & 3.6 & 2.5 & 4.3 & 4.88\\
-\hline
-GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
-\hline
-Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
-\hline
-\hline
-\end{tabular}
-Legend: (S): Series; (P): Parallel.
-\end{scriptsize}
-\end{table}
+\section{Optimal Sizing of Solar PV Systems}
 
-%------------------------------------------
-\section{Objectives and Setup}
-\label{sec:setup}
-%------------------------------------------
-Our experimental evaluation aims to answer two research questions:
-%
-\begin{enumerate}
-\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
-\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
-\end{enumerate}
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual, and simulation), and including the proposed automatic synthesis that is detailed in this Section.
 
-%In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool.
-All the experiments were performed with a time out of 14,400 seconds.
-%Every dweller, who owns a PV system, was interviewed
-%
-All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
-The setup of HOMER Pro v3.13.1 was an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
-The experiments were performed with time out of 240 minutes.
-
-Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled; with SMT solver Z3 version 4.7.1~\cite{DeMoura}.
-% with the goal of reducing memory usage.
-
-Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c -\phantom{}-unwind 100 -\phantom{}-trace}.
-
-Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
-An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness in the results (so it is not reported here).
-
-%\section{Verifiers Environment}
-%\label{sec:verifenviron}
-
-%------------------------------------------
-\section{Results and Discussion}
-\label{sec:results_indeed}
-%------------------------------------------
-
-This Section presents the results, with commented outputs produced by every tool, mainly related to the reports (CBMC and ESBMC) and some graphical resources (CPAchecker and ESBMC).
-
-%\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
-%\begin{enumerate}
-%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
-%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
-%
-Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
-Note that an UNKNOWN result from our verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
-
-%HOMER Pro result: the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
-The simulation took less than five seconds to be performed on each case study.
-%
-\begin{table}
-\centering
-\caption{Summary of the case-studies comparative and the automated tools.}\label{cases}
-\begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\hline
-\multicolumn{5}{|c|}{Model Checker (SAT/UNSAT: time and message)}\\
-\hline
-Case &  \makecell{ESBMC 6.0.0\\(Boolector 3.0.1)} & \makecell {ESBMC 6.0.0\\(Z3 4.7.1)} & \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}\\
-\hline
-\hline
-House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 08 s \\(UNSAT)} & \makecell{19 m 02 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 27 s \\(UNSAT)} & \makecell{18 m 59 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 07 s \\(UNSAT)} & \makecell{18 m 39 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 37 s \\(UNSAT)} & \makecell{18 m 36 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
-\hline
-House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{6 sec \\ (SAT line 337)}\\
-\hline
-\hline
-\end{tabular}
-\end{scriptsize}
-\end{table}
-
-The description of our experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
-
-\subsection{ESBMC}
-Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3.
-The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet.
-
-Using ESBMC with Boolector led to an out of memory situation in all the case studies.
-This result was obtained in less than six minutes of execution, i.e., the 64 GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
-
-However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned was conclusive (SAT or UNSAT) to all the case studies.
-
-Related to the cases that use a 700 W PV system (house 1, house 2, house 3, and house 4), ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s.
-Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for the house 1, with the absence of fail at the end of analysis.
-The file produced by ESBMC is 160 lines long and 12.4 kB of size.
-The author highlighted the result, which shows that was not found design flaws (SAT result or SUCCESS) within the bound $k$ of 100.
+One more time, as depicted in automated verification process, the input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search.
+And the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.
 
 \begin{figure}[h]
-\includegraphics[width=0.65\textwidth]{esbmcverifh1.png}
+\includegraphics[width=1.0\textwidth]{optimalsizingprocess2}
 \centering
-\caption{Report generated by ESBMC (with Z3 solver) after validation of House 1.}
-\label{fig:esbmcverifhouse1}
+\caption{Comparative of optimal sizing methods}
+\label{fig:optimization}
 \end{figure}
 
-However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
+\subsection{Variant of CEGIS}
 
-Fig.~\ref{fig:esbmcverifhouse5} shows the report issued by the tool, with red highlights for the result, showing the incompatibility of the sized charge controller and the minimum necessary.
-The report generated by ESBMC was a text file of 14.1 kB of size and 353 lines of length.
-This verification took less than 1 s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
+In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section ~\ref{sec:ProgramSynthesis}, Fig.~\ref{Counter-Example-Guided-Inductive-Synthesis}.
+This variant was created during this Thesis and it will be detailed in this Section.
 
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{esbmcverifh5.png}
 	\centering
-\caption{Report generated by ESBMC (with Z3 solver) after validation of House 5.}
-\label{fig:esbmcverifhouse5}
+	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
+	\caption{CEGIS applied to PV system sizing.}
+	\label{CEGISalt}
 \end{figure}
 
-%At the terminal, the command used to perform the verification is:
-%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
+Examples of specification used by the proposed method include solar insolation (site dependent), house power demand, house consumption energy, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+Design assumptions are considered project specification as well.
+The assumptions regarding the optimal sizing are listed in Section~\ref{sec:OptAssumptions}.
+
+There are four particular differences related to the traditional CEGIS described in Figure ~\ref{Counter-Example-Guided-Inductive-Synthesis} when compared to the variant CEGIS used in the proposed approach:
+
+\begin{itemize}
+\item There exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+\item If the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} 
+\item The lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
+\item As a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate that could be feasible in the next iteration with a new lower bound.
+\end{itemize}
+
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
+
+Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
+It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
 %
-%Where:
-%
-%\begin{itemize}
-%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
-%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
-%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
-%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
-There are other options, but this parameter is necessary because the complexity of the algorithms.
-The incremental SMT solving uses few RAM memory, compared with other SMT solving.
-%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
-The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
-%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
-%\end{itemize}
+ \begin{algorithm}
+ \caption{Synthesis algorithm}
+ \begin{algorithmic}[1]
+ \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+ \renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \STATE Initialize variables \\
+  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
+%  \STATE Declare list of controllers data and cost \\
+%  \STATE Declare list of batteries data and cost \\
+%  \STATE Declare list of inverters data and cost \\
+  \STATE Declare the maximum possible cost $MaxCost$  \\
+  \STATE Declare power demand, power peak, energy consumption \\
+  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
+  \FOR {$HintCost=0$ to $MaxCost$}
+ 	\STATE Declare non-deterministic variable to select PV Panel from list \\
+ 	\STATE Declare non-deterministic variable to select Controller from list \\
+ 	\STATE Declare non-deterministic variable to select Battery from list \\
+ 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
+ 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
+	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
+ 	\STATE Calculate $C_{bank}$ \\
+	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
+	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
+ 	\STATE Calculate $I_{sc,amb}$ \\
+ 	\STATE Calculate $I_{c,min}$ \\
+ 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
+	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
+	\STATE non-deterministic variables hold feasible equipment and cost  \\
+	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
+	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
+  \ENDFOR
+ \RETURN $(\,)$ 
+ \end{algorithmic} 
+ \label{alg:opt-algorithm}
+ \end{algorithm}
 %
 
-\subsection{CBMC}
+Our synthesis algorithm will synthesize constant values; 
+it starts with the input of manufacturers data and prices of PV panels, batteries, 
+charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
+house requirements and design definitions, from lines $4$ and $5$.
 
-Concerning the CBMC tool, similar results were obtained, but with some slower time than ESBMC. The experimentation returned SAT or UNSAT to all the case studies, i.e., it was conclusive to all houses.
+The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. 
+In particular, it starts with cost $0$ and stops only when the algorithm finds a 
+feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
+if that happens, then our algorithm has found an optimal solution, thereby stating 
+that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
+The $MaxCost$ value at line $6$ is just a very high value put as a limit 
+to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
 
-Related to the 700 W PV systems (house 1, house 2, house 3, and house 4), the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s.
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
+from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
+That procedure ensures that our synthesis engine checks all combinations of items 
+from each equipment, and combine them to assemble a feasible (candidate) PV solution, 
+which meets the user requirements.
 
-Fig.
-\ref{fig:cbmcverifhouse1} shows part of report produced by CBMC when validating the house 1.
-The file produced by CBMC is 270,512 lines long and 39 MB of size.
-The author highlighted the result, which shows that was not found design flaws within the bound $k$ of 100.
+Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, 
+Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
+Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
+ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
+uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$.
+Line $15$ is specific to the charge controller voltage check.
+Line $18$ checks the inverter check $I_{c}$, charge controller DC input voltage $V_{in}DC$, and charge controller AC output voltage $V_{in}DC$ check.
+Line $19$ ensures the power demand and the surge power of inverter.
+Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
+and the cost of that solution is calculated in $F_{obj}$ (line $21$). This cost is the equivalent of ~\ref{eq:LCC} described in Section ~\ref{sec:optcriteria}.
 
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{cbmcverifh1.png}
-\centering
-\caption{Report generated by CBMC after validation of House 1.}
-\label{fig:cbmcverifhouse1}
-\end{figure}
+If our algorithm does not find a feasible solution among the item of equipment that 
+were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
+the program finishes and does not find a solution, which indicates that it 
+was not possible to combine the items of each equipment in order to create a feasible solution.
 
-However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC.
-This verification took less than 1 s to be performed as well.
-Fig.~\ref{fig:cbmcverifhouse5} shows the (edited) report produced, with the highlights about the flaw found: the minimum controller current needed to the PV systems is not compatible with the chosen controller of the sized system.
-The report file generated contained 217 lines and was 13 kB long.
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
+solution regarding the constraints and user requirements. Related to our {\sc Verify} 
+phase the challenge is to find the lowest acquisition cost from a list of equipment and 
+components that is provided from the {\sc Synthesize} phase.
 
-\begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{cbmcverifh5.png}
-\centering
-\caption{Report generated by CBMC after validation of House 5.}
-\label{fig:cbmcverifhouse5}
-\end{figure}
+Note that the process described here is completely automated and that a validation is performed 
+by our {\sc Verify} phase to ensure that the approach is sound.
 
-\subsection{CPAchecker}
+\subsection{Optimization Assumptions and Premises}
+\label{sec:OptAssumptions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Finally, the CPAchecker tool presented some different results.
-Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700 W systems.
-This is because the \textit{time out} limit was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
+Here some premise are presented and some adopted assumptions are explained for the optimal sizing method, regarding the automated synthesis and simulation software.
 
-Figure here CPA house 1
+Regarding the line $2$ of Algorithm~\ref{alg:opt-algorithm}, 
+a list of forty equipment from ten different manufacturers was provided 
+to the synthesis engine in order to allow the choice of every item 
+of PV sizing. Data sheet from each item was necessary to collect 
+technical information. Moreover, the price of each item was obtained 
+from available quotations in the market, and if the currency was not in US dollars, 
+then it was used the exchange rate of the day to convert it to US dollars.
 
-However, when verifying the 1,200 W PV system, the tool presented a SAT message equal to the other engines.
+With respect to power reliability, this work will rely on the critical period solar 
+energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
+The usual way is to use loss of load probability (LOLP) or loss of power 
+supply probability (LPSP). However, based on the fact that here we 
+are neither considering site characteristics nor the load changes over time, 
+which demands historical data, the reliability analysis will be developed only 
+by the critical period method of PV sizing.
 
-Figure here CPA house 5
+Regarding financial analysis:
+\begin{itemize}
+	\item LCC lifetime considered: $20$ years;
+	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
+	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
+	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
+This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
+Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
+\end{itemize}
 
-\subsection{HOMER Pro Environment}
-\label{sec:homerenviron}
+On the subject of PV system optimization technique, we will adopt here the intuitive method 
+since the average value daily of solar irradiance is used in the mathematical model, 
+without considering the battery's state of charge, or even the random nature 
+of solar irradiation and meteorological conditions. Therefore, all the computational 
+effort will be concentrated in our automated synthesis algorithm.
 
-Screens and comments about the simulation tool.
-1) If you want to simulate a particular capacity for PV and battery, you can use the search space instead of HOMER Optimizer for sizing.
-You can either aggregate all the 3 PV panels together as a single PV component or add 3 PV components to represent the series configuration.
-For the batteries, you will have to find the equivalent capacity of the series and parallel configuration since HOMER considers only one battery component per simulation even if you add multiple battery components in the schematic.
-2) You cannot set the autonomy of the batteries as HOMER controller will decide when it is economical to discharge the batteries during the simulation year.
+Regarding batteries, the voltage of the system (DC bus) is set in $24$ V DC (but the value can be adjusted to $12$ or $48$ V at the code).
 
-The same five case studies were evaluated by HOMER Pro (RQ2).
-The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues.
-All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
-Fig.
-\ref{fig:homerscreen1} shows one of the screens presented by HOMER Pro software, specifically to house 1.
+Related to HOMER Pro:
 
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{homer.png}
-\centering
-\caption{HOMER simulation screen.}
-\label{fig:homerscreen1}
-\end{figure}
+\begin{itemize}
+	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
+	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
+However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
+	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
+	\item HOMER Pro do not have a explicit equipment called charge controller.
+It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
+During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
+	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
+By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
+For critical loads, 99\% is considered acceptable.
+While in a ordinary house electrical load, 95\% is considered acceptable;
+	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
+	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
+With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
+HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
+\end{itemize}
 
-The case study that was not possible to simulate was the 1,200 W (house 5).
-The reason is based on the fact that HOMER Pro do not allow to set up a battery autonomy; therefore, it was was not possible to obtain any indication about the failures of this specifically PV system with simulation (RQ2).
+\section{General Assumptions}
 
-%
-%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
-Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions.
-The season has impact since the case studies are from the rain forest, where clouds are always present.
-As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
-%
-%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
-Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
-All the simulations took less than 5 seconds (each) to be performed.
-%
-%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
-That verification took 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
-The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
-The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
-The proposed tool took 409.3 hours to find this error at house 1.
-This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
-Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
-
-\subsection{Comparing Automated Verification and Simulation Results with Real PV Systems}
-
-There were no divergence of results for the houses 1, 2, 3 and 4 w.r.t.
-our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2.
-House 5 presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
-
-In order to validate the possible flaw from house 5, we have surveyed the owner of the 1,200 W system.
-We identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
-The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
-However, even when one interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), which indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$)
-and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
-
-%\begin{figure}[h]
-%\includegraphics[width=0.65\textwidth]{loadcurve.png}
-%\centering
-%\caption{Five weeks monitored load curve from House 1.}
-%\label{fig:loadcurve}
-%\end{figure}
-%
-%\subsection{Experimental results}
-%\label{sec:results}
-%---------------------------------------------------
-\section{Threats to Validity}
-%---------------------------------------------------
-
-We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
-
-\textit{Model precision:} each component of the PV system is mathematically modeled, and the precision of the proposed method depends on the precision of that particular model. 
-The adoption of more complex models, or even an evaluation in a PV laboratory to validate the model could add more reliability to the results.
-
-\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.
-
-\textit{Case studies:} Our case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.
+The general assumptions for the scientific method of automated synthesis are the same presented at Chapter~\nameref{chap:methodology1}, related to the code in ANSI-C, to the bound $k$, to simulation tool comparative, and to the battery state of charge.
 
@@
 
-At this Chapter it was performed the comparative among verifiers with the proposed automated verification using model checking, which showed that 'incremental' ESBMC had the best overall performance.
-CBMC presented the same results, however with a worse time to result, and CPAchecker was not conclusive (house 1, house 2, house 3, and house 4) because the \textit{time out} was not enough to obtain some result.
+In this Chapter we showed in details how the state-of-art computer science method of automated synthesis method was adapted in order to be used in stand-alone solar PV systems to obtain the optimal project sizing.
+Moreover, is was possible to picture how the proposed method compares with the traditional use of simulation tool for the same purpose.
 
-A comparative with a specialized simulation tool was performed as well, however some limitations of the tool, mainly related to not allow battery autonomy setup, restricted the comparative between automated verification tools versus simulation tools.
-
-Based on the fact that all case studies were deployed at the field, with regular visiting to perform interview with the dwellers, and with monitoring system in some of the houses (house 1, house 2, house 3, and house 4), it was possible to compare the computer obtained results with the real world employment of the stand-alone solar PV systems.
-The final conclusion was that the proposed tool is sound and with an acceptable performance.
+Detailed diagrams, flowcharts and algorithms with pseudo-code were presented with the aim to support the proposed work and to facilitate the understanding.
+And even more so, the assumptions adopted for the automated verification and simulation software were listed, because those assumptions have impact at the results there will be presented at  \autoref{chap:automatedsynthesis}.

### 2019-10-20 Tex/Old text/chapters/chapter05.tex
Thesis update

--- 2019-07-20 Tex/Old text/chapters/chapter05.tex
@@
-%\section{Intro to Automated Formal Synthesis Optimization}
-This section presents the case studies used to evaluate our proposed approach. 
-We also compare our approach with a simulation tool, named HOME Pro. 
-The version and command-line of each verifier adopted, 
-the computing setup, the objectives of the experimental phase, 
-and the results itself are also described.
+This Chapter is devoted to the results of using automated verification to validate the intended behavior of stand-alone solar PV systems.
+Moreover, there is the comparative with a specialized simulation tool, and even the use of different verifiers who perform the automated verification in order to evaluate performance.
+Tables, commented reports, and graphical outputs are presented to aid the understanding.
 
-%---------------------------------------------------------------------------
-\section{Optimization Case studies} 
-%---------------------------------------------------------------------------
+\section{Description of the Case Studies}
+%------------------------------------------
 
-We have performed seven stand-alone PV system case studies to evaluate 
-our proposed synthesis approach, as described in the first column of 
-Table~\ref{tab1} (named Specification). These case studies were defined 
-based on usual electrical load found in riverside communities of the 
-Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+%We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
+It was performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
+%Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
+These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+
+Worth to mention that the load curve represents a array of $24$ integer numbers for every hour of the day (instant power in Watts) and it was estimated after visiting and survey applied in June of $2017$, before the houses were electrified.
 
 \begin{table}
-\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
+\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
+\begin{scriptsize}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\hline
+Item & House 1 & House 2 & House 3 & House 4 & House 5\\
+\hline
+\hline
+PV Panels &  \multicolumn{4}{|c|}{3$\times$325 W: (3S)} & 4$\times$325 W: (2S-2P) \\
+\hline
+Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah: (4S)\\ autonomy: 6 h}\\
+\hline
+Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
+\hline
+Inverter & \multicolumn{4}{|c|}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
+\hline
+Power peak (W)& 342  & 253  & 263 & 322 & 814 \\
+\hline
+Power surge (W)& 342 & 722 & 732 & 896 & 980\\
+\hline
+Load curve (W) & \multicolumn{5}{|l|}{\makecell{House 1: 118-118-118-46-46-46-95-95-170-170-296-242-242-95-95-95-95-95-342-288-288-288-288-118\\House 2: 136-136-136-136-136-136-67-67-184-184-184-184-184-67-67-67-67-67-253-253-253-253-253-136\\House 3: 113-113-113-113-113-113-67-67-217-97-97-97-97-97-97-97-97-97-263-113-113-113-113-113\\House 4: 207-207-207-135-135-135-66-66-161-161-233-253-248-66-66-66-66-66-302-317-322-302-302-207\\House 5: 45-16-16-16-16-16-0-0-0-72-72-222-150-150-0-0-72-72-814-814-814-742-742-16}}\\
+\hline
+\makecell{Consumption\\ (kWh/day)}& 3.9 & 3.6 & 2.5 & 4.3 & 4.88\\
+\hline
+GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
+\hline
+Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
+\hline
+\hline
+\end{tabular}
+Legend: (S): Series; (P): Parallel.
+\end{scriptsize}
+\end{table}
+
+%------------------------------------------
+\section{Objectives and Setup}
+\label{sec:setup}
+%------------------------------------------
+
+The experimental evaluation aims to answer two research questions:
+%
+\begin{enumerate}
+\item[RQ1] \textbf{(soundness)} Does the automated verification approach provide correct results?
+\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
+\end{enumerate}
+
+%In order to evaluate the proposed verification method and its performance, we have considered five case studies, three verification engines in different configurations, and also compared the results to the HOMER Pro tool.
+All the experiments were performed with a time out of 14,400 seconds.
+%Every dweller, who owns a PV system, was interviewed
+%
+All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
+The setup of HOMER Pro v3.13.1 was an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
+The experiments were performed with time out of 240 minutes.
+
+Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the 'incremental SMT' mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled; with SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+% with the goal of reducing memory usage.
+
+Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c -\phantom{}-unwind 100 -\phantom{}-trace}.
+
+Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
+An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness in the results (so it is not reported here).
+
+%\section{Verifiers Environment}
+%\label{sec:verifenviron}
+
+%------------------------------------------
+\section{Results and Discussion}
+\label{sec:results_indeed}
+%------------------------------------------
+
+This Section presents the results, with commented outputs produced by every tool, mainly related to the reports (CBMC and ESBMC) and some graphical resources (CPAchecker and ESBMC).
+
+%\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
+%\begin{enumerate}
+%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
+%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
+%
+Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
+Note that an UNKNOWN result from the proposed verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
+
+%HOMER Pro result: the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation.
+The simulation took less than five seconds to be performed on each case study.
+%
+\begin{table}
+\centering
+\caption{Summary of the case-studies comparative and the automated tools.}\label{cases}
 \begin{scriptsize}
@@
 \hline
-Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
+\multicolumn{5}{|c|}{Model Checker (SAT/UNSAT: time and message)}\\
+\hline
+Case &  \makecell{ESBMC 6.0.0\\(Boolector 3.0.1)} & \makecell {ESBMC 6.0.0\\(Z3 4.7.1)} & \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}\\
 \hline
 \hline
-Specification & Result & Result & Result & Result \\
+House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 08 s \\(UNSAT)} & \makecell{19 m 02 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
 \hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 27 s \\(UNSAT)} & \makecell{18 m 59 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
 \hline
-\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
+House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 07 s \\(UNSAT)} & \makecell{18 m 39 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
 \hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
+House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 37 s \\(UNSAT)} & \makecell{18 m 36 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
 \hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
-\hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
-\hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
-\hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{6 sec \\ (SAT line 337)}\\
 \hline
@@
 \end{tabular}
-\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
 \end{scriptsize}
@@
 
-%---------------------------------------------------------------------------
-\section{Objectives and Setup} 
-%---------------------------------------------------------------------------
+The description of the experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
 
-Our evaluation aims to answer two experimental questions:
+\subsection{ESBMC}
 
-\begin{enumerate}
+Related to ESBMC, it was tried two possibilities: one with Boolector and another one with Z3.
+The 'incremental SMT' option, which uses less memory, can be performed with Z3 only since ESBMC does not support the 'incremental' mode with solver Boolector yet.
 
-\item[EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
+Using ESBMC with Boolector led to an out of memory situation in all the case studies.
+This result was obtained in less than six minutes of execution, i.e., the $64$ GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
 
-\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?
+However, running the same version of ESBMC but using 'incremental SMT' solving with Z3, the experimentation returned was conclusive (SAT or UNSAT) to all the case studies.
 
-\end{enumerate}
+Related to the cases that use a $700$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC could not reach an error in all the four houses and the execution time took from $04$ m $27$ s to $05$ m $08$ s.
+Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for the house $1$, with the absence of fail at the end of analysis.
+The file produced by ESBMC is $160$ lines long and $12.4$ kB of size.
+The author highlighted the result, which shows that was not found design flaws (SAT result or SUCCESS) within the bound $k$ of $100$.
 
-All experiments regarding the verification tools were conducted 
-on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
-$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
-Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
-with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
-Our experiments were performed with a predefined timeout of $240$ minutes.
+\begin{figure}[h]
+\includegraphics[width=0.65\textwidth]{esbmcverifh1.png}
+\centering
+\caption{Report generated by ESBMC (with Z3 solver) after validation of House 1.}
+\label{fig:esbmcverifhouse1}
+\end{figure}
 
-Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
-The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
+However the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
 
-\section{Verifiers and HOMER Pro Environments}
+Fig.~\ref{fig:esbmcverifhouse5} shows the report issued by the tool, with red highlights for the result, showing the incompatibility of the sized charge controller and the minimum necessary.
+The report generated by ESBMC was a text file of $14.1$ kB of size and $353$ lines of length.
+This verification took less than $1$ s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line $3$ of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
 
-The environment and captured screens are the same as presented in Section~\ref{sec:verifenviron} for the verifiers and in Section~\ref{sec:homerenviron} for the HOMER Pro tools.
+\begin{figure}[h]
+\includegraphics[width=0.5\textwidth]{esbmcverifh5.png}
+\centering
+\caption{Report generated by ESBMC (with Z3 solver) after validation of House 5.}
+\label{fig:esbmcverifhouse5}
+\end{figure}
 
-%---------------------------------------------------------------------------
-\section{Results}  
-%---------------------------------------------------------------------------
+%At the terminal, the command used to perform the verification is:
+%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
+%
+%Where:
+%
+%\begin{itemize}
+%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
+%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
+%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
+%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
+There are other options, but this parameter is necessary because the complexity of the algorithms.
+The incremental SMT solving uses few RAM memory, compared with other SMT solving.
+%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
+The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
+%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
+%\end{itemize}
+%
 
-CPAchecker was able to synthesize the optimal sizing in six 
-out of seven case studies: the result was produced within 
-the time limit, which varied from $134.71$ to $235.75$ minutes. 
-Only case study $7$ led to a \textit{timeout} result, i.e., 
-it was not solved within $240$ minutes. However, if we remove 
-this timeout limitation from CPAchecker, the verifier is 
-able to solve the optimization in $44.97$ hours. 
-The violation (SAT result) indicated in Table~\ref{tab1} 
-is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
-%The results were tested by manual PV sizing and were sound (\textit{RQ1}).
-%, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
+\subsection{CBMC}
 
-CBMC and ESBMC are unable to produce any conclusive result. 
-Situations of \textit{internal failure}, \textit{timeout}, 
-or \textit{out of memory} occurred; this partially answers 
-the \textit{EQ2}. Note that the internal failure presented 
-by ESBMC was a Z3 solver issue (a bug); this will demand 
-an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
-if we remove the timeout from ESBMC with the SMT solver Boolector, 
-then the verifier is able to obtain the automated synthesis 
-in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.
+Concerning the CBMC tool, similar results were obtained, but with some slower time than ESBMC. The experimentation returned SAT or UNSAT to all the case studies, i.e., it was conclusive to all houses.
 
-Related to HOMER Pro, it was able to evaluate six case studies, 
-and within a time shorter than $30$ seconds, which was much 
-faster than our automated synthesis tool (cf.~\textit{EQ2}). 
-Case study $3$ was not possible to be simulated since HOMER Pro 
-does not have the feature of adjusting the battery autonomy, i.e., 
-the tool always tries to feed with electricity the given load 
-during $365$ days/year. We have also noted other HOMER Pro drawbacks:
+Related to the 700 W PV systems (house $1$, house $2$, house $3$, and house $4$), the tool could not reach an error in all the four houses and the execution time took from $18$ m $36$ s to $19$ m $02$ s.
 
-\begin{itemize}
-\item There exists no explicit charge controller 
-as a system equipment. HOMER Pro includes automatically 
-a controller just to simulate the charge/discharge 
-of batteries and to meet the load requirement; however, 
-without costs or even with electrical characteristics 
-as maximum current and voltage, which are common during PV sizing;
-\item HOME Pro demands to include some battery specification 
-to initiate the optimization; however, it does not change 
-the electrical specifications during the simulation; 
-the presented results are multiples of the original 
-battery type suggested by the user. As example, it was 
-started with a $83.4$ Ah lead-acid battery and during 
-the simulation, HOMER Pro did not try to use other capacities or types;
-\item HOMER Pro does not present the optimal solution 
-in terms of connections of arrays of PV panels, just the 
-total in terms of power, i.e., it does not present neither models 
-and the power of each PV panel nor the total of panels in series or parallel. 
-\end{itemize}
+Fig.
+\ref{fig:cbmcverifhouse1} shows part of report produced by CBMC when validating the house 1.
+The file produced by CBMC is $270,512$ lines long and $39$ MB of size.
+The author highlighted the result, which shows that was not found design flaws within the bound $k$ of $100$.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparison between Formal Synthesis and HOME Pro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{cbmcverifh1.png}
+\centering
+\caption{Report generated by CBMC after validation of House 1.}
+\label{fig:cbmcverifhouse1}
+\end{figure}
 
-Comparing the results between the formal synthesis with CPAchecker 
-and HOMER Pro, we observed that most results are quite similar, 
-in terms of technical solution and cost (cf. Table~\ref{tab1}).
+However the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code; with the same counterexample presented by ESBMC.
+This verification took less than $1$ s to be performed as well.
+Fig.~\ref{fig:cbmcverifhouse5} shows the (edited) report produced, with the highlights about the flaw found: the minimum controller current needed to the PV systems is not compatible with the chosen controller of the sized system.
+The report file generated contains $217$ lines and it was $13$ kB of size.
 
-Particularly related to LCC, the cost was very close in cases 
-$1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
-Even adopting the same price per kW to the PV panels, 
-inverters, and batteries, HOMER Pro does not use costs 
-related to charge controllers, which were introduced into the 
-CPAchecker modeling. The premise used in CPAchecker to adopt 
-a fixed annual cost for operation and maintenance can produce 
-some impact as well at this discrepancy; however, it is not significant
-since this annual cost is too small when compared to the resulting LCC value.
+\begin{figure}[h]
+\includegraphics[width=0.7\textwidth]{cbmcverifh5.png}
+\centering
+\caption{Report generated by CBMC after validation of House 5.}
+\label{fig:cbmcverifhouse5}
+\end{figure}
 
-However, there exists a huge divergence in case study $2$, 
-where the costs presented by HOMER Pro were $54$\% higher 
-than our automated synthesis tool, probably because the 
-operation and maintenance costs assumed by our automated 
-synthesis tool were underestimated to that specific load.
+\subsection{CPAchecker}
 
-In general, the size of the PV panels and battery bank were 
-bigger in HOMER Pro than with our formal synthesis approach, 
-and that discrepancy is not easy to address without some real 
-systems validation. The mathematical models are different and 
-particular parameters can be tuned as well in each approach, 
-and that can justify the difference, which was presented in all 
-the case studies. As comparative, let's consider case study $1$: 
-the optimal solution provided by HOMER Pro demands $7$ $\times$ 
-more PV panels than the solution presented by our synthesis tool, 
-and HOME Pro does not show the arrangement of arrays 
-(i.e., the number of series and parallel PV panels); 
-the battery bank presented by HOMER Pro provides $500.4$ Ah 
-of capacity ($6 \times 83.4$), while our synthesis tool 
-presented an optimal solution with $420$ Ah of total capacity 
-($4 \times 105$).
+Finally, the CPAchecker tool presented some different results.
+Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the $700$ W systems (house $1$, house $2$, house $3$, and house $4$).
 
-Just to compare the results obtained from the optimization 
-with the real-world, the authors had four PV systems deployed 
-and monitored since June $2018$ in a riverside community 
-in the Amazonas State in Brazil, with similar demands 
-presented by case studies $1$, $4$, $5$, and $6$, 
-always with a $3$ $\times$ $325$ W ($3$S) panels and 
-$4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) 
-lead-acid batteries. These solutions are more close 
-to the result presented by our formal synthesis 
-approach than HOMER Pro, thereby showing that our 
-solution is sound, which answers \textit{EQ1}.
+This is because the \textit{time out} limit was reached, i.e., after $4$ hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
+This is shown in Fig.~\ref{fig:cpavalidh1} is shown one of the text reports issued by CPAchecker.
+Differently of ESBMC and CBMC, CPAchecker produces a lot of different reports, notable for log, statistical, and counterexample files (which is graphical and not in text format).
 
-Related to the inverters, HOMER Pro suggests a value in 
-kW very close to the peak of every case study, and it 
-is just a reference value and not a commercial value of 
-the employed inverter. Our synthesis tool, however, 
-presents inverters that are commercial and can be found 
-off-the-shelf. Therefore is a PRO to the formal synthesis method.
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{CPA_verif_h1.png}
+\centering
+\caption{CPAchecker time out result for house 1 validation (file CPALog.txt).}
+\label{fig:cpavalidh1}
+\end{figure}
 
-Concerning to charge controllers, as we reported in 
-the previous section, HOMER Pro does not include it 
-as an explicit equipment in its mathematical model, 
-only our synthesis tool presents a commercial controller 
-and includes it during the cost analysis. Therefore, 
-the formal synthesis method presents more reliable results than
-HOME Pro.
+However, when validating the $1,200$ W PV system (house $5$), the tool presented a SAT message equal to the other engines, but with a execution time of $6$ seconds.
+Fig.~\ref{fig:cpavalidh5} show the result, with highlights to the line that causes the fail ($IC_{min}$) and part of the CFA (control-flow automata, represented as a control-flow graph) diagram pointing to this fail.
 
-Case study $7$ was not solved by our synthesis tool 
-within the time limit established during the experimental 
-phase. Case study $3$ was not possible to simulate in HOMER Pro, 
-because its restriction does not allow one to set the battery autonomy, 
-thus resting both without parameters to comparative.
+\begin{figure}[h]
+\includegraphics[width=1.0\textwidth]{CPA_verif_h5.png}
+\centering
+\caption{CPAchecker time out result for house 5 validation (file Counterexample.html).}
+\label{fig:cpavalidh5}
+\end{figure}
 
-Summarizing, our synthesis tool is capable to present a 
-solution, which is far detailed and close to the commercial 
-reality than the solution presented by HOMER Pro. 
-In particular, our automated synthesis method 
-can provide all the details of every component of 
-a PV system solution, with complete electrical details 
-from data sheet of manufacturers, including 
-the model of the component, nominal current and voltage. 
-In this respect, even the name of the manufacturer 
-can be presented (in Table~\ref{tab1} it was removed 
-to avoid some advertising).
-%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+\subsection{HOMER Pro Specialized Simulation Tool}
+\label{sec:homerenviron}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Threats to validity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+HOMER Pro is a powerful specialized electrical systems simulator, however even with the simulation characteristic, it in fact performs optimization when a given design is inputted to the schematic of the tool.
+This means that HOMER does not maintain the characteristic of the system under evaluation.
+It starts with the inputted information, however it uses the optimization default set up to increase or decrease the characteristic of each component until the load be meet by the electric generation system, and with the lowest cost.
 
-We have reported a favorable assessment of our formal synthesis method. 
-Nevertheless, we have also identified three threats to the validity 
-of our experimental results, which can be further assessed and 
-constitute future work: ($1$) improvement of the power reliability 
-analysis: to include loss of load probability or loss of power 
-supply probability, which can make the analysis more accurate; 
-($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
-however, a broad analysis from other isolated areas must be 
-performed in order to make the optimization general in terms 
-of applicability; ($3$) to deploy at the field some PV systems 
-sized using our synthesized results in order to validate it.
+Therefore, in order to perform a limited simulation and not exceed the values of each component (for example, the total power of the PV array under evaluation), it is necessary use the 'search space' instead of 'HOMER Optimizer' for sizing.
+That is done at the menu of each component inputted in the schematic of the tool.
+
+Related to PV panels and batteries: If you want to simulate a particular capacity for PV and battery, you can use the 'search space' instead of 'HOMER Optimizer' for sizing.
+You can either aggregate all the PV panels together as a single PV component (in this case, the search space must vary from 0 to 1, i.e., from the option without PV panels until reach the power inputted to the component in the HOMER schematic) or add each PV components to represent the series configuration.
+For the batteries, you will have to find the equivalent capacity of the series and parallel configuration since HOMER considers only one battery component per simulation even if you add multiple battery components in the schematic.
+
+Other drawback of HOMER Pro is the fact that the user cannot set the autonomy of the batteries as HOMER controller will decide when it is economical to discharge the batteries during the simulation year.
+Therefore, any simulation regarding battery autonomy is not possible to be evaluated.
+
+Therefore, related to the comparative proposed, four $700$ W PV systems (houses $1$, $2$, $3$ and $4$) were evaluated by HOMER Pro (RQ2).
+The simulation results showed that for everyone of the sized systems, HOMER Pro concluded that it was not found feasible solution with the components inputted in the schematic.
+Fig.
+\ref{fig:homersimuh2no} shows one of the screens presented by HOMER Pro software, specifically to house $2$.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{homersimuh2no.png}
+\centering
+\caption{HOMER simulation screen presented for house 2 with no feasible solution found.}
+\label{fig:homersimuh2no}
+\end{figure}
+
+Moreover, in order to evaluate what was the problem associated with the lack of feasible solution, it was performed some empirical changes to the evaluated project.
+Fig.~\ref{fig:homersimuh2yes} shows that a configuration with higher battery capacity (3 strings of 2 batteries each, 2S-3P, of 220 Ah; instead of 2 strings of 2 batteries each as the original sized system) can solve the problem of house 2.
+The same happened to the other tree houses of $700 W$, when improved battery capacity is presented by HOMER Pro as a optimal solution.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{homersimuh2yes.png}
+\centering
+\caption{HOMER simulation screen presented for house 2 with feasible solution.}
+\label{fig:homersimuh2yes}
+\end{figure}
+
+The case study that was not possible to simulate was the $1,200$ W (house $5$).
+The reason is based on the fact that HOMER Pro do not allow to set up a battery autonomy (because it always size and optimize the electrical system in order to meet the load requirements for a entire year of simulation); therefore, it was was not possible to obtain any indication about the failures of this specifically PV system with simulation (RQ2).
+
+%
+%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
+Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions.
+The season has impact since the case studies are from the rain forest, where clouds are always present.
+As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
+%
+%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
+Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
+The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
+All the simulations took less than 5 seconds (each) to be performed.
+%
+%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
+The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
+That verification took 63.3 hours to be performed.
+Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
+That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
+The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
+The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
+The proposed tool took 409.3 hours to find this error at house 1.
+This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
+Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
+
+\subsection{Comparing Automated Verification and Simulation Results with Real PV Systems}
+
+There were divergence of results for the houses $1$, $2$, $3$ and $4$ w.r.t.
+of proposed approach: the automated evaluation shows that there is not project flaws, but simulation demanded to improve batteries capacity (adding one more string of batteries to the system).
+
+In order to evaluate which validation is correct, it was necessary to access the access interviews performed with the dwellers of deployed systems.
+From July of $2018$ to March $2019$, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
+
+However, even when one interruption is reported in a month, this represents around $3.33$\% of interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
+Therefore, the proposed approach using automated verification provides the correct evaluation of the PV system, thus answering RQ2.
+
+House $5$ presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
+
+In order to validate the possible flaw identified by the automated verification from house $5$, it was surveyed the owner of the $1,200$ W system.
+It was identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
+
+%\begin{figure}[h]
+%\includegraphics[width=0.65\textwidth]{loadcurve.png}
+%\centering
+%\caption{Five weeks monitored load curve from House 1.}
+%\label{fig:loadcurve}
+%\end{figure}
+%
+%\subsection{Experimental results}
+%\label{sec:results}
+%---------------------------------------------------
+\section{Threats to Validity}
+%---------------------------------------------------
+
+At this Chapter, it was reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
+Nevertheless, it was also identified five threats to the validity of the results that can further be assessed.
+
+\textit{Model precision:} each component of the PV system is mathematically modeled. %, and the precision of the proposed method depends on the precision of that particular model. 
+The adoption of more complex models, or even an evaluation in a PV laboratory to validate the model could add more reliability to the results.
+
+\textit{Time step:} The run-time complexity of the proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.
+
+\textit{Case studies:} The case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.
+
+\textit{Simulation Tool:} Only HOMER Pro was used.
+The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparative.
+
+\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online~\cite{Temperature, Irradiance}.
+However, considering that riverside communities do not have weather stations, the data used in the present study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data.
+Therefore, the most accurate should be the use of weather stations in each location.
 
 \section{Conclusion}
+
+At this Chapter it was performed the comparative among verifiers with the proposed automated verification using model checking, which showed that 'incremental' ESBMC had the best overall performance.
+CBMC presented the same results, however with a worse time to result, and CPAchecker was not conclusive (house $1$, house $2$, house $3$, and house $4$) because the \textit{time out} was not enough to obtain some result.
+
+A comparative with a specialized simulation tool was performed as well, however some limitations of the tool, mainly related to not allow battery autonomy setup or the oversize of the batteries bank by HOMER Pro, restricted the comparative between automated verification tools versus simulation tools.
+
+Based on the fact that all case studies were deployed at the field, with regular visiting to perform interview with the dwellers, and with monitoring system in some of the houses (house $1$, house $2$, house $3$, and house $4$), it was possible to compare the computational validation (by simulation or automated verification) with the real world employment of the stand-alone solar PV systems.
+The final conclusion was that the proposed tool is sound and with an acceptable performance.

### 2019-10-20 Tex/Old text/chapters/chapter06.tex
Thesis update

--- 2019-07-08 Tex/elsevier/trindade_appliedenergy_rev1.tex
@@
-\documentclass[review]{elsarticle}
-
-\usepackage{lineno,hyperref}
-%\modulolinenumbers[5]
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithm,algorithmic}
-\usepackage{graphicx}
-\usepackage{makecell}
-\usepackage{textcomp}
-\usepackage{xcolor}
-
-\journal{Applied Energy}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\begin{frontmatter}
-
-%\title{Innovative techno-economic optimization of stand-alone solar photovoltaic systems using automated formal synthesis} 
-\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
-%
-%\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
-%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
-%
-%% Group authors per affiliation:
-\author[mymainaddress]{Alessandro Trindade\corref{mycorrespondingauthor}}
-\cortext[mycorrespondingauthor]{Corresponding author}
-\ead{alessandrotrindade@ufam.edu.br}
-%\ead[url]{www.elsevier.com}
-
-\author[mysecondaryaddress]{Lucas Cordeiro}
-
-\address[mymainaddress]{Federal University of Amazonas, Av. Rodrigo Octávio, 6200, Coroado I, 69077-000 Manaus-AM-Brazil}
-\address[mysecondaryaddress]{University of Manchester, School of Computer Science, Kilburn Building, Manchester M13 9PL}
-
-\begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution.
-\textcolor{red}{We present a novel sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last two decades}.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound \textcolor{red}{cost} via symbolic model checking.
-If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase.
-Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
-Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing.
-\textcolor{red}{We also present a comparative with a specialized simulation tool over real PV systems to show the effectiveness of our approach, which is able to provide more accurate results of optimal sizing of stand-alone PV systems than that existing simulation tool}.
-\end{abstract}
-
-\begin{keyword}
-automated verification \sep model checking \sep program synthesis \sep electrical systems \sep solar photovoltaic systems
-\end{keyword}
-
-\end{frontmatter}
-
-%\linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical  components~\cite{NSF2015}.
-During operation, such components must frequently adapt to the operating environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
-Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
-
-While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
-Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing \textit{correct-by-construction} implementations of CPS.
-These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
-In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
-Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
-Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
-
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}.
-In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
-
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and  Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g.,  PSpice~\cite{Gow1999}, or MATLAB/Simulink package~\cite{Benatiallah2017}.
-However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-
-Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
-An ideal combination of any PV system is made by the best compromise between two considered objectives, which is power \textit{reliability} and \textit{system cost}~\cite{Alsadi2018}.
-
-\textcolor{red}{In this study, our focus is not on a novel criteria or optimization objectives.
-Instead, our novelty relies on an effective approach on the pursuit of the optimal solution using formal methods, which outperforms existing state-of-the-art simulation tools.}
-
-Formal methods based on \textit{symbolic model checking} and its application 
-to synthesize PV systems have not been further explored in literature, which could offer 
-a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. 
-Here, we use a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing 
-optimal sizing of stand-alone PV systems using commercial equipment data. 
-Given a correctness specification $\sigma$, our method uses that as starting point 
-and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
-related to power reliability. In particular, in each iteration, we synthesize sizing of 
-stand-alone PV systems but that may not achieve the lowest cost. The candidate solution 
-is then verified via symbolic model checking with a lower bound that serves as the minimum 
-cost of reference; if the verification step does not fail, the lower bound is adjusted. 
-If it fails then a counterexample is provided with an optimal sizing that meets 
-power reliability and system cost.
-
-%------------------------------------------------------
-\subsection{Contributions}
-%------------------------------------------------------
-
-Our work makes three major contributions. \textbf{First}, the use of automated 
-symbolic verification methods in electrical systems was uncommon in recent 
-prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
-optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
-charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
-method together with user requirements and environment constraints, 
-and our synthesis algorithm based on symbolic model checking 
-can find the optimal solution in technical and economical terms. 
-\textbf{Second}, we evaluate different state-of-art symbolic software 
-verifiers with the goal of obtaining the best performance in our verification 
-back-end for synthesizing optimal PV systems, \textcolor{red}{being the first work that performs this type of comparative.}
-\textcolor{red}{\textbf{Third}, our experimental results show that our synthesis method is an effective and efficient approach 
-on the pursuit of the optimal solution of PV system design using formal methods, which outperforms 
-existing state-of-the-art simulation tools.}
-
-\noindent \textit{Outline}. Section~\ref{sec:Background} gives the background about related studies, 
-program synthesis, sizing design and validation of PV systems, and the mathematical modeling. 
-Section~\ref{sec:Method} presents the automated formal synthesis proposed 
-in this underlying study. Section~\ref{sec:Results} is devoted to the experimentation, 
-results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
-%
-%-----------------------------------------------------------
-\section{BACKGROUND}
-\label{sec:Background}
-%-----------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{State-of-art in Automated Verification of Electrical Systems}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\textcolor{red} {Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.}
-
-The conversion of traditional power grid into a smart grid, a fundamental example of a CPS, 
-raises a number of issues that requires novel methods and applications.
-In $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
-The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here, the authors employed automated verification of certain quantitative properties of the system, as probability of	 node failure in the long run, impact of repair service on the failure risk, and expected energy consumption, without any interest in power generation or even solar PV systems.
-
-In $2015$, an automated approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
-The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
-The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
-However, this study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
-
-Other related studies from $2015$ include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis using statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
-In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
-The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
-This research, however, did no address the design and verification of solar PV systems.
-
-In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices, interacting over a shared and smart infrastructure~\cite{Abate2017}.
-The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
-The focus was on controlling the behavior of components, thereby verifying the given smart grid as a "system of systems" within the context of "internet of things".
-The author, however, used approximate model checking of stochastic and hybrid models.
-
-In $2018$, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design-space of one operation hour of the PV panels behavior.
-This related study did not include other components of a stand-alone solar PV system.
-
-Another work from $2018$ was the approach to model smart grid components using a formal specification.
-The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
-The presented formal specification can be considered as a first step towards modeling of smart grids using formal methods.
-The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
-This approach is based on Petri nets and is under the assumption that modeling the smart home leads to clear understanding of the overall behavior of the smart grid.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Automated Verification Using Model Checking}
-\label{sec:AutomatedVerification}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Although simulation and testing explore possible behaviors and scenarios of a given system, 
-they leave open the question of whether unexplored trajectories may contain a flaw. 
-Formal verification conducts an exhaustive exploration of all possible behaviors; 
-when a design is said to be ``correct'' by a formal verification method, it implies that all 
-behaviors have been explored, and questions regarding adequate coverage or missed behavior 
-becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that 
-applies mathematical reasoning to obtain guarantees about the correctness of a system; 
-one successful method in this domain is model checking~\cite{Clarke2012}. 
-Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The C Bounded Model Checker (CBMC) falsifies assertions in C programs 
-or proves that they are safe if a completeness threshold is given~\cite{Kroening}. 
-CBMC implements a bit-precise translation of a C program, annotated with assertions 
-and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, 
-then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification 
-flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; 
-it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, 
-into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
-(ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, 
-which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
-(iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{ESBMC}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{CPAchecker}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Automatic program verification requires a choice between precision and efficiency. 
-The more precise a method, the fewer false positives it will produce, but also the 
-more expensive it is, and thus applicable to fewer programs. 
-Historically, this trade-off was reflected in two major approaches to static verification: 
-program analysis and model checking. In order to experiment with the trade-off, 
-and in order to be able to set the dial between the two extreme points, 
-Configurable Program Analysis (CPA) provides a conceptual basis for expressing 
-different verification approaches in the same formal setting. The CPA formalism 
-provides an interface for the definition of program analyses. Consequently, CPAchecker 
-provides an implementation framework that allows the seamless integration of program 
-analyses that are expressed in the CPA framework. The comparison among different 
-approaches in the same experimental setting is intended to be easy and the experimental 
-results are expected to be more meaningful~\citep{Beyer2011}. Related to the architecture, 
-the central data structure is a set of control-flow automata (CFA), which consists of control-flow 
-locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and 
-interpolation procedures~\citep{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; 
-and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.
-
-%-----------------------------------------------------------
-\subsection{Program Synthesis}
-\label{sec:ProgramSynthesis}
-%-----------------------------------------------------------
-
-The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
-In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
-As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
-	\caption{CEGIS applied to PV system sizing.}
-	\label{Counter-Example-Guided-Inductive-Synthesis}
-\end{figure}
-
-The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .
-\forall \vec{x}.
-\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
-The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
-
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
-Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
-
-One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
-
-However, in our variant CEGIS method proposed here, there are four particular differences related to the traditional CEGIS: 
-(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
-(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
-(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
-(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
-a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard 
-a given candidate that could be feasible in the next iteration with a new lower bound.
-
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sizing Stand-alone Solar PV Systems}
-\label{sec:sizing}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
-The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity.  
-For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage 
-form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system 
-contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior 
-of AC electrical load from the house that will be fed by the system.
-%
-\begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
-\centering
-\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
-\label{fig:blockdiagram} 
-\end{figure}
-
-The sizing check stage will ensure that the system meets the standard project steps related 
-to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller,
-which is the most common one in practice. Firstly, we need to correct the energy consumption estimated to the load 
-($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
-controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
-%
-\begin{equation}
-\label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
-\end{equation}
-
-We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
-%
-\begin{equation}
-\label{eq:Ep}
-E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
-\end{equation}
-
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
-the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
-%
-\begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
-\end{equation}
-
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
-%
-\begin{equation}
-\label{eq:NPSmin}
-\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
-\end{equation}
-%
-\begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
-\end{equation}
-%
-\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ 
-is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and 
-$V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering 
-the maximum and minimum operational temperature, respectively; 
-$P_{total}$ is the total power demanded from the PV system and 
-$P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
-%
-\begin{equation}
-\label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
-\end{equation}
-
-\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-%
-Secondly, the total (minimum) number of batteries is computed as
-
-\begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
-\end{equation}
-
-Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
-\begin{equation}
-\label{eq:vcvsystem}
-V_{c} = V_{system}.
-\end{equation}
-
-The short circuit reference information from the manufacturer's solar panel must be corrected 
-to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, 
-and PV system is temperature dependent, as 
-%
-\begin{equation}
-\label{eq:iscamb}
-I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
-\end{equation}
-
-The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin} as
-%
-\begin{equation}
-\label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP},
-\end{equation}
-%
-\begin{equation}
-\label{eq:icicmin}
-I_{c} \geq I_{c,min}.
-\end{equation}
-
-The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that 
-the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the 
-output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that 
-the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), 
-where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; 
-$MAX_{AC,ref}$ is the peak power that the inverter can support.
-%
-\begin{equation}
-\label{eq:vindc} 
-V_{in}DC = V_{system}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:voutac} 
-V_{out}AC = V_{AC}.
-\end{equation}
-%
-\begin{equation}
-\label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{PV systems Optimization Criteria}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In order to select an optimal combination to meet sizing constraints, 
-it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives.
-
-During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
-The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
-A reliable power is a generation system that has sufficient power to feed load demand in a period.
-
-There exist different methods to express system reliability, where the most popular ones 
-are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
-In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
-
-LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
-On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
-On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
-The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance.
-However, data is not always available and dynamic analysis is complex; and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
-
-Related to economic analysis, there exist various methods available.
-The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
-The common methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
-
-The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
-The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
-IRR is used to evaluate the attractiveness of a project or investment.
-
-LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
-LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
-
-LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
-Eq.~\eqref{eq:LCC} is used to calculate LCC of a PV system,
-%
-\begin{equation}
-\label{eq:LCC}
-LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
-\end{equation}
-\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs
-in present worth.
-
-%----------------------------------------------------------------------------------------------
-\subsection{Stand-alone PV System Optimization Technique}
-%----------------------------------------------------------------------------------------------
-
-In order to recommend an optimal configuration for PV systems, 
-the designer has to evaluate the design based on optimization variables. 
-As the number of optimization variables increases, the computational effort 
-will increase as well. Hence, to obtain the best PV system design as well as 
-simplified sizing process, prior work introduced three main techniques 
-for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
-
-Intuitive method is simple, easy to be implemented, and can be used to give 
-rough suggestion for preliminary design. The sizing rules are based on designer's experience, 
-using lowest performance either in a time period data or by directly using average value 
-(daily, monthly, or annual) of solar irradiance. This method does not consider the battery's 
-state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
-
-For numerical method, the design is simulated for each time step within a period. 
-State of charge of batteries is calculated and investigated. It is very accurate, 
-however is complex, demanding more time for calculation~\cite{Park2004}.
-
-Analytical methods is used to obtain a close relation or correlation in a form 
-of equation between capacities and reliabilities. The sizing task becomes much simpler 
-than numerical technique; however, the relation cannot be applied to different sites
-since it is specific to one place of deployment of the PV system, 
-thereby demanding adaptation if another site is analyzed.
-
-%------------------------------------------------------
-\section{SYNTHESIZING OPTIMAL SIZING OF STAND-ALONE SOLAR PHOTOVOLTAIC SYSTEMS}
-\label{sec:Method}
-%------------------------------------------------------
-
-Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
-It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
-%
- \begin{algorithm}
- \caption{Synthesis algorithm}
- \begin{algorithmic}[1]
- \renewcommand{\algorithmicrequire}{\textbf{Input:}}
- \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \STATE Initialize variables \\
-  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
-%  \STATE Declare list of controllers data and cost \\
-%  \STATE Declare list of batteries data and cost \\
-%  \STATE Declare list of inverters data and cost \\
-  \STATE Declare the maximum possible cost $MaxCost$  \\
-  \STATE Declare power demand, power peak, energy consumption \\
-  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
-  \FOR {$HintCost=0$ to $MaxCost$}
- 	\STATE Declare non-deterministic variable to select PV Panel from list \\
- 	\STATE Declare non-deterministic variable to select Controller from list \\
- 	\STATE Declare non-deterministic variable to select Battery from list \\
- 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
- 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
-	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
- 	\STATE Calculate $C_{bank}$ \\
-	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
-	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
- 	\STATE Calculate $I_{sc,amb}$ \\
- 	\STATE Calculate $I_{c,min}$ \\
- 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
-	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
-	\STATE non-deterministic variables hold feasible equipment and cost  \\
-	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
-	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
-  \ENDFOR
- \RETURN $(\,)$ 
- \end{algorithmic} 
- \label{alg:verification-algorithm}
- \end{algorithm}
-%
-
-Our synthesis algorithm will synthesize constant values; 
-it starts with the input of manufacturers data and prices of PV panels, batteries, 
-charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
-house requirements and design definitions, from lines $4$ and $5$.
-
-The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. 
-In particular, it starts with cost $0$ and stops only when the algorithm finds a 
-feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
-if that happens, then our algorithm has found an optimal solution, thereby stating 
-that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
-The $MaxCost$ value at line $6$ is just a very high value put as a limit 
-to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
-
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
-from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
-That procedure ensures that our synthesis engine checks all combinations of items 
-from each equipment, and combine them to assemble a feasible (candidate) PV solution, 
-which meets the user requirements.
-
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, 
-Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
-Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} t
-o calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
-ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
-uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$. 
-Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
-and the cost of that solution is calculated in $F_{obj}$ (line $21$).
-
-If our algorithm does not find a feasible solution among the item of equipment that 
-were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
-the program finishes and does not find a solution, which indicates that it 
-was not possible to combine the items of each equipment in order to create a feasible solution.
-
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
-solution regarding the constraints and user requirements. Related to our {\sc Verify} 
-phase the challenge is to find the lowest acquisition cost from a list of equipment and 
-components that is provided from the {\sc Synthesize} phase.
-
-Note that the process described here in completely automated and that a validation is performed 
-by our {\sc Verify} phase to ensure that the approach is sound.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Assumptions and Premises}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, 
-a list of forty equipment from ten different manufacturers was provided 
-to the synthesis engine in order to allow the choice of every item 
-of PV sizing. Data sheet from each item was necessary to collect 
-technical information. Moreover, the price of each item was obtained 
-from available quotations in the market, and if the currency was not in US dollars, 
-then it was used the exchange rate of the day to convert it to US dollars.
-
-With respect to power reliability, this work will rely on the critical period solar 
-energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
-The usual way is to use loss of load probability (LOLP) or loss of power 
-supply probability (LPSP). However, based on the fact that here we 
-are neither considering site characteristics nor the load changes over time, 
-which demands historical data, the reliability analysis will be developed only 
-by the critical period method of PV sizing.
-
-Regarding financial analysis:
-\begin{itemize}
-	\item LCC lifetime considered: $20$ years;
-	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
-	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
-	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
-This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
-Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
-\end{itemize}
-
-On the subject of PV system optimization technique, we will adopt here the intuitive method 
-since the average value daily of solar irradiance is used in the mathematical model, 
-without considering the battery's state of charge, or even the random nature 
-of solar irradiation and meteorological conditions. Therefore, all the computational 
-effort will be concentrated in our automated synthesis algorithm.
-
-Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
-
-Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis.
-Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
-Related to HOMER Pro:
-
-\begin{itemize}
-	\item HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER};
-	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
-	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
-However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
-	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
-	\item HOMER Pro do not have a explicit equipment called charge controller.
-It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
-During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
-	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
-By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\citep{Khatib2014}.
-For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable;
-	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
-	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
-HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
-\end{itemize}
-
-%---------------------------------------------------------------------------
-\section{EXPERIMENTAL EVALUATION}
-\label{sec:Results}
-%---------------------------------------------------------------------------
-
-This section presents the case studies used to evaluate our proposed approach. 
-We also compare our approach with a simulation tool, named HOME Pro. 
+%\section{Intro to Automated Formal Synthesis Optimization}
+This Chapter presents the case studies used to evaluate the proposed approach of optimal sizing of stand-alone solar PV systems using automated synthesis. 
+Moreover, the approach is compared with a simulation tool, named HOME Pro. 
 The version and command-line of each verifier adopted, 
@@
 %---------------------------------------------------------------------------
-\subsection{Case studies} 
+\section{Optimization Case studies} 
 %---------------------------------------------------------------------------
 
-We have performed seven stand-alone PV system case studies to evaluate 
-our proposed synthesis approach, as described in the first column of 
-Table~\ref{tab1} (named Specification). These case studies were defined 
-based on usual electrical load found in riverside communities of the 
-Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}. 
-%
+It was performed seven stand-alone PV system case studies to evaluate the proposed synthesis approach:
+
+\begin{itemize}
+\item Case Study 1: Power peak: 342 W, power surge: 342 W, energy consumption: 3,900 Wh/day, battery autonomy: 48 h;
+\item Case Study 2: Power peak: 814 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 48 h;
+\item Case Study 3: Power peak: 815 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 12 h;
+\item Case Study 4: Power peak: 253 W, power surge: 722 W, energy consumption: 3,600 Wh/day, battery autonomy: 48 h;
+\item Case Study 5: Power peak: 263 W, power surge: 732 W, energy consumption: 2,500 Wh/day, battery autonomy: 48 h;
+\item Case Study 6: Power peak: 322 W, power surge: 896 W, energy consumption: 4,300 Wh/day, battery autonomy: 48 h;
+\item Case Study 7: Power peak: 1,586 W, power surge: 2,900 W, energy consumtion: 14,000 Wh/day, battery autonomy: 48h.
+\end{itemize}
+
+These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+With exception of case 7 that was idealized as a small town solution to support few lamps and an 12 kBTUs air-conditioner.
+
+%---------------------------------------------------------------------------
+\section{Objectives and Setup} 
+%---------------------------------------------------------------------------
+
+The evaluation aims to answer two experimental questions:
+
+\begin{enumerate}
+
+\item[EQ1] \textbf{(soundness)} does the proposed automated synthesis approach provide correct results?
+
+\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?
+
+\end{enumerate}
+
+All experiments regarding the verification tools were conducted 
+on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
+$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
+Related to HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), 
+with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
+The experiments were performed with a predefined time out of $240$ minutes.
+
+Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with solver Boolector 3.0.1~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engine to compare the proposed approach effectiveness and efficiency.
+Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
+The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
+
+%---------------------------------------------------------------------------
+\section{Results}  
+\label{sec:synthesisresults}
+%---------------------------------------------------------------------------
+
+The results are presented at Table~\ref{tab1}.
+
 \begin{table}
@@
 \end{tabular}
-\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
+\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
 \end{scriptsize}
@@
 
-%---------------------------------------------------------------------------
-\subsection{Tools} 
-%---------------------------------------------------------------------------
+CPAchecker was able to synthesize the optimal sizing in six 
+out of seven case studies (cases $1$ to $6$): the result was produced within 
+the time limit, which varied from $134.71$ to $235.75$ minutes.
+Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing in the left size as the integer $8$ to the solar panel (which is the model RSM36-6-150P from manufacturer Risen), battery $0$ that means the model 12MF80 of 80 Ah from Moura, charge controller $1$ that means the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ means the model IP350-11 from Epever (750 W).
+The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, presented at the counter-example as well, shows how many and how the panels and batteries are connected.
 
-Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-Note that ``incremental'' ESBMC with the SMT solver Z3 was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
-The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
-
-%---------------------------------------------------------------------------
-\subsection{Setup} 
-%---------------------------------------------------------------------------
-
-All experiments regarding the verification tools were conducted 
-on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
-$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
-Related to HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
-with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
-Our experiments were performed with a predefined timeout of $240$ minutes.
-
-%---------------------------------------------------------------------------
-\subsection{Objectives} 
-%---------------------------------------------------------------------------
-
-Our evaluation aims to answer two experimental questions:
-
-\begin{enumerate}
-
-\item[EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
-
-\item[EQ2] \textbf{(performance)} how do the software verifiers compare to each other?
-
-\end{enumerate}
-
-%---------------------------------------------------------------------------
-\subsection{Results}  
-%---------------------------------------------------------------------------
-
-CPAchecker was able to synthesize the optimal sizing in six 
-out of seven case studies: the result was produced within 
-the time limit, which varied from $134.71$ to $235.75$ minutes. 
-Only case study $7$ led to a \textit{timeout} result, i.e., 
-it was not solved within $240$ minutes. However, if we remove 
-this timeout limitation from CPAchecker, the verifier is 
+Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., 
+it was not solved within $240$ minutes. However, if it is removed 
+this time out limitation from CPAchecker, the verifier is 
 able to solve the optimization in $44.97$ hours. 
@@
 
+\begin{figure}[h]
+\includegraphics[width=1.0\textwidth]{CPA_opt_c4.png}
+\centering
+\caption{Counter-example generated by CPAchecker after validation of case 4 (file Counterexample.html).}
+\label{fig:CPAoptc1}
+\end{figure}
+
 CBMC and ESBMC are unable to produce any conclusive result. 
-Situations of \textit{internal failure}, \textit{timeout}, 
+Situations of \textit{internal failure}, \textit{time out}, 
 or \textit{out of memory} occurred; this partially answers 
@@
 an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
-if we remove the timeout from ESBMC with the SMT solver Boolector, 
+if it is removed the \textit{time out} from ESBMC with the SMT solver Boolector, 
 then the verifier is able to obtain the automated synthesis 
-in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the memory out issue.
+in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the \textit{memory out} issue.
 
-Related to HOMER Pro, it was able to evaluate six case studies, 
-and within a time shorter than $30$ seconds, which was much 
-faster than our automated synthesis tool (cf.~\textit{EQ2}). 
+Related to HOMER Pro, it was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much 
+faster than the proposed automated synthesis tool (cf.~\textit{EQ2}). 
 Case study $3$ was not possible to be simulated since HOMER Pro 
@@
 the tool always tries to feed with electricity the given load 
-during $365$ days/year. We have also noted other HOMER Pro drawbacks:
+during $365$ days/year.
+
+Fig.~\ref{fig:homeroptc4} illustrates parts of the 9-page PDF report presented by HOMER Pro, specifically for the case 4.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{homeroptc4.png}
+\centering
+\caption{Optimization report (partial) from HOMER Pro (case 4).}
+\label{fig:homeroptc4}
+\end{figure}
+
+It was also noted other HOMER Pro drawbacks:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison between Formal Synthesis and HOME Pro}
+\section{Comparison between Formal Synthesis and HOMER Pro}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Threats to validity}
+\section{Threats to validity}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-We have reported a favorable assessment of our formal synthesis method. 
-Nevertheless, we have also identified three threats to the validity 
-of our experimental results, which can be further assessed and 
-constitute future work: ($1$) improvement of the power reliability 
+At this Section, it was reported a favorable assessment of proposed formal synthesis method. 
+Nevertheless, it was also identified three threats to the validity 
+of the experimental results, which can be further assessed and 
+constitute future work:
+
+\begin{itemize}
+\item ($1$) improvement of the power reliability 
 analysis: to include loss of load probability or loss of power 
 supply probability, which can make the analysis more accurate; 
-($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
+\item ($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
 however, a broad analysis from other isolated areas must be 
 performed in order to make the optimization general in terms 
-of applicability; ($3$) to deploy at the field some PV systems 
-sized using our synthesized results in order to validate it.
+of applicability; 
+\item ($3$) to deploy at the field some PV systems 
+sized using the synthesized results in order to validate it.
+\end{itemize}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CONCLUSIONS}
-\label{sec:Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
 
-We have described and evaluated an automated synthesis method 
-to obtain the optimal size of PV system using software model 
-checking techniques.
-\textcolor{red}{The focus was on the method to obtain the optimal solution, based on formal methods that can cover the design-space better than simulation tools}.
-We have considered seven case studies
-from PV systems in two different sites of the Amazonas State 
-in Brazil, ranging from $253$\,W to $1,586$\,W peak; and 
-three state-of-art verification engines were considered 
-(ESBMC, CBMC, and CPAchecker), in addition to a specialized 
-off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+At this Chapter it was performed the comparative among verifiers with the proposed automated synthesis using model checking, in order to obtain the optimal sizing of stand-alone solar PV systems, which showed that CPAchecker had the best overall performance.
+CBMC and ESBMC were not conclusive for all the cases, reaching the \textit{time out} stipulated ($240$ minutes) or by \textit{out of memory} issue.
+CPAchecker was not possible to present a conclusive result just in case $7$ (\textit{time out}).
 
-Our automated synthesis tool presented detailed optimal solution 
-to six case studies adopted in this paper, with specifications, 
-models, and the arrangement in terms of series-parallel connections, 
-thereby covering the charge controller, which was not presented by HOMER Pro. 
-In a nutshell, our automated synthesis tool took more time 
-to find the optimal solution than HOMER Pro; however, the presented 
-solution was more complete and detailed, which is very useful 
-to a user to get a list of equipment and go to shopping.
+A comparative with a specialized simulation tool was performed as well, however in just $5$ case studies (case $1$, case $2$, case $4$, case $5$, and case $6$) it was possible comparative for the presented result.
+Some limitations of the simulation tool, mainly related to not allow battery autonomy setup, and the $time out$ or $out of memory$ messages presented by the verifiers, restricted the comparative between automated verification tools versus simulation tools.
+However, when the comparative was possible, it was noticed that the LCC was very close, and that HOMER Pro overestimated the sizing.
 
-As future work, the authors plan to improve the power reliability analysis, 
-to address the restriction to only allow automated synthesis of 
-riverside communities in the Amazonas state (Brazil), and to 
-validate some cases with deployed PV systems in isolated communities.
-
-\section*{Acknowledgments}
-The authors would like to thank: (i) Newton Fund [grant number $261881580$] for the research mobility support; (ii) FAPEAM - Amazonas State Foundation for Research Support [PROTI-Pesquisa $2018$], for the DCTIEX II scholarship (NOV-$2018$), and for support the research mobility to UK; (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and (iv) University of Sheffield's Research England QR GCRF Institutional Allocation for the HOMER Pro license.
-
-%
-% argument is your BibTeX string definitions and bibliography database(s)
-%\section*{REFERENCES}
-\bibliography{trindadeThesis}{}
-%\vspace{12pt}
-\end{document}
+Based on the fact that mostly case studies were deployed at the field (case $1$, case $4$, case $5$, and case $6$), with regular visiting to perform interview with the dwellers, and with monitoring system in those houses, it was possible to compare the computer obtained results with the real world employment of the stand-alone solar PV systems.
+The final conclusion was that the proposed tool is sound, with an acceptable performance, and with a better quality of the presented output.

### 2019-10-24 Tex/Old text/chapters/chapteroptimization.tex
Thesis update

--- 2019-10-20 Tex/Old text/chapters/chapter06.tex
@@
-%\section{Intro to Automated Formal Synthesis Optimization}
-This Chapter presents the case studies used to evaluate the proposed approach of optimal sizing of stand-alone solar PV systems using automated synthesis. 
+In this Chapter, we detail the adopted methodology to perform optimal sizing of stand-alone solar PV systems, more specifically using model checking.
+Diagrams, flowcharts, and algorithms support and explain the solutions.
+
+Besides that, we present all the assumptions and premises adopted.
+We present as well the case studies used to evaluate the proposed approach of optimal sizing of stand-alone solar PV systems using automated synthesis.
 Moreover, the approach is compared with a simulation tool, named HOME Pro.
-The version and command-line of each verifier adopted, 
-the computing setup, the objectives of the experimental phase, 
-and the results itself are also described.
+The version and command-line of each verifier adopted, the computing setup, the objectives of the experimental phase, and the results itself are also described.
+
+It is important to emphasize that the whole explanation about the theoretical basis of the subject discussed here is present in the Chapter~\nameref{chap:background}.
+We do suggest that this previous Chapter reading must be done to facilitate the understanding.
+
+\section{Optimal Sizing of Solar PV Systems}
+
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual, and simulation), and including the proposed automatic synthesis that is detailed in this Section.
+
+One more time, as depicted in automated verification process, the input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search.
+And the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.
+
+\begin{figure}[h]
+\includegraphics[width=1.0\textwidth]{optimalsizingprocess2g}
+\centering
+\caption{Comparative of optimal sizing methods}
+\label{fig:optimization}
+\end{figure}
+
+\subsection{Variant of CEGIS}
+
+In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section ~\ref{sec:ProgramSynthesis}, Fig.~\ref{Counter-Example-Guided-Inductive-Synthesis}.
+This variant was created during this Thesis and it will be detailed in this Section.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
+	\caption{CEGIS applied to PV system sizing.}
+	\label{CEGISalt}
+\end{figure}
+
+Examples of specification used by the proposed method include solar insolation (site dependent), house power demand, house consumption energy, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+Design assumptions are considered project specification as well.
+The assumptions regarding the optimal sizing are listed in Section~\ref{sec:OptAssumptions}.
+
+There are four particular differences related to the traditional CEGIS described in Figure ~\ref{Counter-Example-Guided-Inductive-Synthesis} when compared to the variant CEGIS used in the proposed approach:
+
+\begin{itemize}
+\item There exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+\item If the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} 
+\item The lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
+\item As a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate that could be feasible in the next iteration with a new lower bound.
+\end{itemize}
+
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
+
+Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
+It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
+%
+ \begin{algorithm}
+ \caption{Synthesis algorithm}
+ \begin{algorithmic}[1]
+ \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+ \renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \STATE Initialize variables \\
+  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
+%  \STATE Declare list of controllers data and cost \\
+%  \STATE Declare list of batteries data and cost \\
+%  \STATE Declare list of inverters data and cost \\
+  \STATE Declare the maximum possible cost $MaxCost$  \\
+  \STATE Declare power demand, power peak, energy consumption \\
+  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
+  \FOR {$HintCost=0$ to $MaxCost$}
+ 	\STATE Declare non-deterministic variable to select PV Panel from list \\
+ 	\STATE Declare non-deterministic variable to select Controller from list \\
+ 	\STATE Declare non-deterministic variable to select Battery from list \\
+ 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
+ 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
+	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
+ 	\STATE Calculate $C_{bank}$ \\
+	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
+	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
+ 	\STATE Calculate $I_{sc,amb}$ \\
+ 	\STATE Calculate $I_{c,min}$ \\
+ 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
+	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
+%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
+	\STATE non-deterministic variables hold feasible equipment and cost  \\
+	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
+	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
+  \ENDFOR
+ \RETURN $(\,)$ 
+ \end{algorithmic} 
+ \label{alg:opt-algorithm}
+ \end{algorithm}
+%
+
+Our synthesis algorithm will synthesize constant values; 
+it starts with the input of manufacturers data and prices of PV panels, batteries, 
+charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
+house requirements and design definitions, from lines $4$ and $5$.
+
+The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. 
+In particular, it starts with cost $0$ and stops only when the algorithm finds a 
+feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
+if that happens, then our algorithm has found an optimal solution, thereby stating 
+that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
+The $MaxCost$ value at line $6$ is just a very high value put as a limit 
+to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
+
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
+from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
+That procedure ensures that our synthesis engine checks all combinations of items 
+from each equipment, and combine them to assemble a feasible (candidate) PV solution, 
+which meets the user requirements.
+
+Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, 
+Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
+Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
+ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
+uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$.
+Line $15$ is specific to the charge controller voltage check.
+Line $18$ checks the inverter check $I_{c}$, charge controller DC input voltage $V_{in}DC$, and charge controller AC output voltage $V_{in}DC$ check.
+Line $19$ ensures the power demand and the surge power of inverter.
+Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
+and the cost of that solution is calculated in $F_{obj}$ (line $21$). This cost is the equivalent of ~\ref{eq:LCC} described in Section ~\ref{sec:optcriteria}.
+
+If our algorithm does not find a feasible solution among the item of equipment that 
+were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
+the program finishes and does not find a solution, which indicates that it 
+was not possible to combine the items of each equipment in order to create a feasible solution.
+
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
+solution regarding the constraints and user requirements. Related to our {\sc Verify} 
+phase the challenge is to find the lowest acquisition cost from a list of equipment and 
+components that is provided from the {\sc Synthesize} phase.
+
+Note that the process described here is completely automated and that a validation is performed 
+by our {\sc Verify} phase to ensure that the approach is sound.
+
+\subsection{Optimization Assumptions and Premises}
+\label{sec:OptAssumptions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Here some premise are presented and some adopted assumptions are explained for the optimal sizing method, regarding the automated synthesis and simulation software.
+
+Regarding the line $2$ of Algorithm~\ref{alg:opt-algorithm}, 
+a list of forty equipment from ten different manufacturers was provided 
+to the synthesis engine in order to allow the choice of every item 
+of PV sizing. Data sheet from each item was necessary to collect 
+technical information. Moreover, the price of each item was obtained 
+from available quotations in the market, and if the currency was not in US dollars, 
+then it was used the exchange rate of the day to convert it to US dollars.
+
+With respect to power reliability, this work will rely on the critical period solar 
+energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
+The usual way is to use loss of load probability (LOLP) or loss of power 
+supply probability (LPSP). However, based on the fact that here we 
+are neither considering site characteristics nor the load changes over time, 
+which demands historical data, the reliability analysis will be developed only 
+by the critical period method of PV sizing.
+
+Regarding financial analysis:
+\begin{itemize}
+	\item LCC lifetime considered: $20$ years;
+	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
+	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
+	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
+This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
+Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
+\end{itemize}
+
+On the subject of PV system optimization technique, we will adopt here the intuitive method 
+since the average value daily of solar irradiance is used in the mathematical model, 
+without considering the battery's state of charge, or even the random nature 
+of solar irradiation and meteorological conditions. Therefore, all the computational 
+effort will be concentrated in our automated synthesis algorithm.
+
+Regarding batteries, the voltage of the system (DC bus) is set in $24$ V DC (but the value can be adjusted to $12$ or $48$ V at the code).
+
+Related to HOMER Pro:
+
+\begin{itemize}
+	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
+	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
+However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
+	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
+	\item HOMER Pro do not have a explicit equipment called charge controller.
+It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
+During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
+	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
+By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
+For critical loads, 99\% is considered acceptable.
+While in a ordinary house electrical load, 95\% is considered acceptable;
+	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
+	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
+With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
+HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
+\end{itemize}
+
+\section{General Assumptions}
+
+The general assumptions for the scientific method of automated synthesis are the same presented at Chapter~\nameref{chap:methodology1}, related to the code in ANSI-C, to the bound $k$, to simulation tool comparative, and to the battery state of charge.
 
@@
 
-At this Chapter it was performed the comparative among verifiers with the proposed automated synthesis using model checking, in order to obtain the optimal sizing of stand-alone solar PV systems, which showed that CPAchecker had the best overall performance.
+In this Chapter we showed in details how the state-of-art computer science method of automated synthesis method was adapted in order to be used in stand-alone solar PV systems to obtain the optimal project sizing.
+Moreover, is was possible to picture how the proposed method compares with the traditional use of simulation tool for the same purpose.
+
+Detailed diagrams, flowcharts and algorithms with pseudo-code were presented with the aim to support the proposed work and to facilitate the understanding.
+And even more so, the assumptions adopted for the automated verification and simulation software were listed.
+
+It was performed the comparative among verifiers with the proposed automated synthesis using model checking, in order to obtain the optimal sizing of stand-alone solar PV systems, which showed that CPAchecker had the best overall performance.
 CBMC and ESBMC were not conclusive for all the cases, reaching the \textit{time out} stipulated ($240$ minutes) or by \textit{out of memory} issue.

### 2019-10-24 Tex/Old text/chapters/chapterverification.tex
Thesis update

--- 2019-10-20 Tex/Old text/chapters/chapter05.tex
@@
-This Chapter is devoted to the results of using automated verification to validate the intended behavior of stand-alone solar PV systems.
+In this Chapter, we detail the adopted methodology to perform formal verification of stand-alone solar PV systems using formal methods, more specifically model checking.
+Diagrams, flowcharts, and algorithms support and explain the solutions.
+The experimentation, case studies, and results are present as well.
 Moreover, there is the comparative with a specialized simulation tool, and even the use of different verifiers who perform the automated verification in order to evaluate performance.
 Tables, commented reports, and graphical outputs are presented to aid the understanding.
+
+Besides that, we present all the assumptions and premises adopted.
+Both support the results/conclusions, with direct impact on it.
+Usually, a premise is an unquestionable fact, however assumptions can be questionable.
+Unlike the premise, assumptions are not explicitly stated and need to be deciphered.
+With that in mind, we perform a detailed explanation of assumptions all over this Chapter.
+
+It is important to emphasize that the whole explanation about the theoretical basis of the subject discussed here is present in the previous chapter, ~\nameref{chap:background}.
+In addition, we do suggest that previous reading must be done to facilitate the understanding.
+
+\section{Automated Verification of Solar PV Systems}
+
+Fig.~\ref{fig:validation} illustrates how a stand-alone solar PV project can be validated, passing through the traditional techniques, as manual, simulation, testing, and including the proposed automatic verification that is detailed in this Section.
+
+Note that, in one hand, the input information is the same for all the techniques, with the difference that in automated validation it is possible to define the bound $k$ to restrict the space-design search.
+Among the inputs it is possible to list: location weather data (temperature, solar irradiance, and solar insolation); system sizing information regarding specifications and configuration of PV panels, charge controller, inverter, batteries, DC bus  voltage; and requirements (battery autonomy, electric load demand, electric peak power demand, energy consumption, load curve, and AC voltage).
+
+However, in the other hand, the outputs are not equal, as the design-space coverage and the information presented as result.
+Regarding the design-space, it was shown in  chapter \nameref{chap:background} that the most complete coverage is performed by automated verification, event using the bound $k$ to restrict the search, because is not necessary to unbound completely the system in order to found a design flaw.
+Moreover, testing and simulation depends on the test vector used as input to evaluate the system.
+
+About the results presented by the methods, a project validation done 'by hand' is just a piece of paper produced; simulation software produce fail, success information and can additionally to present the optimized design if the evaluated has some flaw, with graphics and reports; testing (using laboratory or field) is done using measurement equipment and/or data from monitoring systems.
+Automated verification, proposed at this Thesis, presents fail, success information as well, however the output is not graphical (as will be shown in the  \autoref{chap:automatedverification}), summarized by reports with details about the variables and states of the project that causes a project flaw (in the case where is detected a design fail).
+
+\begin{figure}[h]
+\includegraphics[width=1.0\textwidth]{PVprojectvalidation2g}
+\centering
+\caption{Comparative of project validation methods}
+\label{fig:validation}
+\end{figure}
+
+Starting at his point, it will be showed how is done the proposed automated verification of stand-alone solar PV systems.
+
+The process begins with the conversion of the real PV system into a model.
+The Fig.
+\ref{fig:systemverif4} shows how a real solar PV system is equivalent and converted to a model in order to be verified by a model checking.
+
+This illustration is a adaption from the general process of real system conversion depicted in Fig.~\ref{fig:systemverif}, detailing the inputs, outputs, and requirements of a real solar PV system.
+
+Worth to mention that the model checking process is the same independently of the system that is validated, and the important is to chose a accurate model, to define the requirements/constraints, and to get correct information from the system components, in order to get sound and effective validation,
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{systemverif4}
+\centering
+\caption{From real solar PV system verification to model checking. Source: adapted from \cite{Clarke2008}.}
+\label{fig:systemverif4}
+\end{figure}
+
+Moreover, the proposed flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
+Those three steps are the high level description of how the automated verification, applied to solar PV systems, works.
+
+\begin{figure}[h]
+\includegraphics[width=0.6\textwidth]{flowchart_verification5.png}
+\centering
+\caption{Flowchart of the proposed automated verification of PV systems.}
+\label{fig:flowchartgeneral}
+\end{figure}
+
+In \textbf{Step 1}, the PV input data %(e.g., load power demand and load energy consumption) 
+and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.
+
+In \textbf{Step 2}, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
+This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.
+
+\textbf{Assumption:} before the automated verification, who performs the verification of the intended system behavior, is performed the sizing checking of the system.
+Moreover, if there is some error, the process stops, showing where is the sizing error.
+
+\textbf{Assumption:} Sizing check is performed using critical period criteria.
+
+In \textbf{Step 3}, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
+%As a consequence, all the formulae of the employed mathematical models will also be updated. 
+In addition, depending on one of the desired properties of the system such as battery autonomy, energy availability, or even system power supply, our verification engine is able to indicate a failure if those properties are not met; in this particular case, it provides a diagnostic counterexample that shows in which conditions the property violation occurred.
+%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
+% (as reliability, performance, or safety)
+
+%
+%\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above.
+For example, what does a failure mean?
+is it SAT?}
+In a nutshell, the model checker will process the ANSI-C code with constraints ($C$) and properties ($P$) from the PV system, and the tool will automatically verify if the PV system requirements are met.
+If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
+However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
+
+%, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
+%
+%
+%---------------------------------------------------------------------
+% \subsection{The case studies and the Algorithm}
+%---------------------------------------------------------------------
+%
+% 
+%and as backup at night 
+%
+%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
+%
+%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
+%
+%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).
+
+Algorithm~\ref{alg:verification-algorithm} describes the equivalent pseudo-code.
+%Line 1 indicates a function call that performs the size checking of the each component of the PV system.
+%: using Equations \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
+%The verification is carried out by the \textit{assert} macro from the ANSI-C programming language to encode each equation of sizing check.
+The argument to the \textit{assert} statement must be \textit{true} if the system specification is met; otherwise, the program aborts and prints a counterexample indicating a property violation.
+If there is no property violation, then the verification algorithm continues and
+In order to reduce the computational effort of the algorithm,
+% caused by the state explosion inherent of the technique, 
+every 24 h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation), when the batteries are demanded to feed the house.
+
+\textbf{Assumption:} day is divided in two parts (when there is and there is not PV generation, based in historical data from the location).
+Considering average temperature and solar irradiance (for every hour of the day) and the annual solar insolation (per day).
+
+Lines 1 is devoted to information from the location where the PV system will be/were deployed.
+We use annual average minimum and maximum, related to temperature ($T$) and solar irradiance ($G$), hour by hour, from~\cite{Temperature}, and ~\cite{Irradiance}.
+
+\textbf{Premise:} The availability of temperature, solar irradiance, and solar insolation data from the location where the solar PV system will be used.
+
+Line 2 represents all the information that comes from the PV sizing and from the equipment manufacturers data: specification and data from PV, batteries, inverter and charge controller.
+This item includes as information from the house's load curve.
+
+\textbf{Premise:} Availability of data sheet from every element of the solar PV system to be validated.
+
+\textbf{Premise:} It is necessary the detailed sized project of the PV system in order to perform the validation (list of equipment and configuration, as voltage, current and how they are connected).
+
+\textbf{Assumption:} Load curve from every house must be estimated or measured.
+Moreover, the time step is of 1 hour, and it is not considered seasonality, i.e., the load curve is the same for the entire year.
+
+The first automated verification is related to the sizing check (line 3), if an error is found then the algorithm stops.
+In order to perform the sizing check, the algorithm uses Equations \eqref{eq:NTPmin}, \eqref{eq:NPSmin}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
+
+Then, if there is not a sizing design flaw, two functions, called at lines 4 and 5, are responsible for discover which hour starts the PV generation and when stops.
+Those functions get this information from the array inputted to the Algorithm with the solar irradiance values.
+
+The batteries are assumed to be charged, i.e., with SOC of 100\% (line 6).
+
+\textbf{Assumption:} Batteries are considered charged at the beginning of the project validation.
+
+The first for-loop at line 7 controls how many cycles of 24 h will be performed by the Algorithm.
+And the for-loop from lines 8 to 11 is responsible to discharge the battery (according the load curve) and verify the state of charge of the battery, hour-by-hour, starting at the first hour of the day after the sun goes down until the next day before the sun goes up (without PV generation).
+Following, at the next for-loop, from line 12 to 29, is performed the verification where there is solar irradiance and all the PV system works.
+The Algorithm generates information related to average temperature ($T$) and solar irradiance ($G$), hour-by-hour, using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range (lines 15 and 16).
+%and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
+%there is PV generation only between 8:00 h and 16:00 h every day, 
+%with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day.
+
+After that, the model from PV generator is used in the function call of line 17, to produce the voltage and current considering the states of $G$ and $T$.
+With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller work as depicted in Table~\ref{table:controller} of Section~\ref{sec:controller}, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+
+At the end of last for-loop, the state of the batteries is verified again (line 27) and the hour is adjusted to the next loop (line 28).
+
+Nevertheless, if the verification engine does not fail, we can conclude that the PV system does not need further corrections up to the given bound $k$.
+%
+%\textcolor{red}{this sentence is unclear...
+After this process is started the battery autonomy verification, from line 31}.
+\textcolor{red}{this sentence is unclear...
+Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.} \textcolor{red}{what do you mean by The formal verification is guaranteed?...
+The formal verification is guaranteed by  macro to specific variables of the model, according lines 27 and 35.}
+% and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries.
+%Within this 8h-period, $G$ and $T$ are automated verified with different values every one hour.
+%, and change their value every 1 h according with the algorithm created using the technique.
+ \begin{algorithm}
+ \caption{Model checking algorithm for validation of stand-alone PV systems}
+ \begin{algorithmic}[1]
+ \begin{scriptsize}
+ \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+ \renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\
+  \STATE $declare \, case \, studies \, details: \, sizing \, and \, manufacturers \, data $ \\
+  \STATE $sizing \_ check()$ \\
+  \STATE $startPVgeneration \leftarrow findStartPVgeneration()$ \\
+  \STATE $endPVgeneration \leftarrow findEndPVgeneration()$ \\
+  \STATE $SOC \leftarrow 100\%$ \\
+%  \COMMENT {Starting with the PV generation time}
+% \\ 
+%\textit{LOOP Process}
+ \FOR {$1st \, 24h \, loop$ to $Nth \, 24h \, loop$}
+  \FOR {$endPVgeneration+1$ to $startPVgeneration-1$}
+	  \STATE $dischargeBattery \, in \, 1h()$ \\
+%	  \STATE $autonomyCount \leftarrow autonomyCount+1$ \\
+	  \STATE $assert (SOC \geq SOC \_ min)$ \\
+%	  \STATE $battery \, autonomy \, verification()$ \\
+  \ENDFOR
+  \FOR {$startPVgeneration$ to $endPVgeneration$}
+    \STATE $G \leftarrow nondet \_ uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
+    \STATE $T \leftarrow nondet \_ uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
+    \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting $G$ values}
+    \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting $T$ values}
+    \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ \\
+    \COMMENT {If-then-else sequence to imitate charge controller work}
+    \IF {($battery \, is \, empty$) AND ($PV \, is \, generating$)}
+      \STATE $chargeBattery \, in \, 1h()$ \COMMENT {PV feed the house}
+    \ELSIF {($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
+      \STATE FAIL with assert macro \COMMENT {Battery is empty and there is not PV generation}
+    \ELSIF {NOT($battery \, is \, empty$) AND ($PV \, is \, generating$)}
+      \STATE stop battery charge \COMMENT {PV feed the house}
+    \ELSIF {NOT($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
+      \STATE $dischargeBattery \, in \, 1h()$ \COMMENT {Battery feed the house}
+    \ENDIF
+    \STATE $assert (SOC \geq SOC \_ min)$ \\
+    \STATE $hour \leftarrow hour+1$ \\
+   \ENDFOR
+  \ENDFOR
+ \RETURN $(\,)$ 
+  \end{scriptsize}
+ \end{algorithmic} 
+ \label{alg:verification-algorithm}
+ \end{algorithm}
+
+%\subsubsection{Assumptions and Premises} 
+%
+
+\section{General Assumptions}
+\label{sec:assumptions}
+
+Here is listed the assumptions adopted for scientific methods of automated verification developed on this Thesis.
+
+Regarding the code in ANSI-C created to perform both methods, automated verification and automated synthesis, it was written in order to be the same independently of the verifier used.
+This means that:
+
+\begin{itemize}
+\item There is not the use of '\# include' preprocessor directive, so common in the C language, which allows the use of language C libraries, including the mathematical one;
+\item Because of absence of '\# include' directive, it was necessary to create specific mathematical functions at the proposed code in order to calculate the exponential 'exp(x)' or $e^{x}$, and natural logarithm 'log(x)' functions, used for the solar PV model;
+\item There is not the presence of '\# define' preprocessor directive. Therefore were used global variables to replace it;
+\item The macro 'assert (expression);' must be replaced by 'if (!expression) \{ \_ \_ VERIFIER\_ error();\}'
+\item The macro 'assume (expression);' must be replaced by '\_ \_ VERIFIER\_ assume(expression)';
+\item It is not possible to use the \# if, \# else, \# elif, \# endif or \# ifdef, \# ifndef commands.
+\end{itemize}
+
+Regarding the automated verification scientific method:
+
+\begin{itemize}
+\item It was used a value of bound $k$ to restrict the design-space and improve performance. The chose of value was empirical, after some tests with the code;
+\item All the PV system model, user requirements, assumptions, and technical information from the PV system equipment are written as an ANSI-C code.
+\end{itemize}
+
+Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
+Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis, however RETScreen do not have stand-alone solar PV system analysis capacity.
+Therefore, in this study, HOMER Pro will be the only simulation tool used to compare with our method.
+
+Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\%, i.e., with DOD maximum of $25$\%, which is common to lead-acid batteries (adopted as standard here), and the AC voltage from the inverter is $127$ V (Brazilian standard).
 
@@
 
-At this Chapter it was performed the comparative among verifiers with the proposed automated verification using model checking, which showed that 'incremental' ESBMC had the best overall performance.
+This Chapter showed in details how the state-of-art computer science method of automated verification was adapted in order to be used in stand-alone solar PV systems to validate their behavior.
+Moreover, is was possible to picture the comparative of how the proposed method and the traditional one of simulation work differently.
+
+Detailed diagrams, flowcharts and algorithms with pseudo-code were presented with the aim to support the proposed work and to facilitate the understanding.
+And even more so, the assumptions adopted for the automated verification and simulation software were listed.
+
+Furthermore, at this Chapter it was performed the comparative among verifiers with the proposed automated verification using model checking, which showed that 'incremental' ESBMC had the best overall performance.
 CBMC presented the same results, however with a worse time to result, and CPAchecker was not conclusive (house $1$, house $2$, house $3$, and house $4$) because the \textit{time out} was not enough to obtain some result.

### 2019-10-24 Tex/Old text/chapters/introduction.tex
Thesis update

@@
 % ~\nameref or \autoref{
-Chapter \nameref{chap:background} gives the theoretical basis on formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.
-Chapter~\nameref{chap:methodology} presents the automated verification  and the automated synthesis techniques.
-The results related to the experimental use of automated verification are in \autoref{chap:automatedverification}, while \autoref{chap:automatedsynthesis} is devoted to the experimentation,
-results and discussions of the automated synthesis technique. Chapter \nameref{chap:conclusions} presents the main contributions, future work directions and concluding remarks.
+Chapter '~\nameref{chap:background}' gives the theoretical basis on formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.
+Chapter '~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new technique.
+Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science applied to solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collect during fieldwork.
+Chapter '~\nameref{chap:conclusions}' presents the main contributions, future work directions and concluding remarks.

### 2019-10-25 Tex/Old text/chapters/chapter02.tex
Thesis update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{PV generator (cell, module, array) }
+\subsubsection{PV generator (cell, module, string, and array) }
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
-In addition, to achieve the desired voltage and current, modules are wired in series and parallel into what is called a PV Array, as shown in Fig.\ref{fig:celmodarray}.
+In addition, to achieve the desired voltage and current, modules are wired in series (strings) and parallel into what is called a PV array, as shown in Fig.\ref{fig:celmodarray}.
 The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.
@@
 \begin{figure}[h]
-\includegraphics[width=0.95\textwidth]{celmodarray}
-\centering
-\caption{PV cell, module and array. Source: \cite{SamlexSolar}.}
+\includegraphics[width=0.95\textwidth]{PVarray}
+\centering
+\caption{PV cell, module, string and array. Source: \cite{SamlexSolar}.}
 \label{fig:celmodarray}

### 2019-10-25 Tex/Old text/chapters/chapteroptimization.tex
Thesis update

@@
 It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
-%
+
  \begin{algorithm}
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
+  \REQUIRE weather data (temperature, solar irradiance), list of equipment (data sheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis)
+ \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available
   \STATE Initialize variables \\

### 2019-10-25 Tex/Old text/chapters/chapterverification.tex
Thesis update

@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
+ \REQUIRE mathematical model (PV, batteries, inverter, charge controller), weather data (temperature, solar irradiance), system sizing details, design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (system availability, battery state of charge, 1-hour step of validation)
+ \ENSURE design sizing check; FAIL with counter-example to improve the design; SUCCESS, saying that the project has no flaws
   \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\

### 2019-10-25 Tex/Old text/chapters/conclusion.tex
Thesis update

@@
-At this final chapter, the conclusions about the research done during the Doctoral process are presented.
+At this final chapter, we present the conclusions about the research done during the Doctoral process.
 Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable source) closes the work.
@@
 
-This Thesis contributions can be split in two, each one concerning the tools created with the use of model checking to solar PV systems.
+This Thesis contributions can be split in two, each one concerning the techniques proposed with the use of model checking to solar PV systems, and the tools created to validate it.
 
@@
 
-One future long term direction is to foster the creation of a research group in automated verification and synthesis applied to electrical systems improve mathematical models; and a international network of researchers in model checking applied to electrical systems.
+One future long term direction is to foster the creation of a research group in automated verification and synthesis applied to electrical systems; and a international network of researchers in model checking applied to electrical systems.
 
@@
 Based on the fact that the tools detailed here have not similarity in past work in the world, can be concluded that it was produced original research that expands the boundaries of knowledge, putting cutting-edge computer science methodologies to solve typical electrical engineering problems and to improve the design of systems.
+
+And last, but not least important to report, besides the fact that the goal of a PhD is to make a contribution to the body of human research, one of the great things about PhD is you will be able to conduct your own research.
+In that direction, we can say that with the technique proposed here (formal methods using automated verification and model checking) to energy sector, there is a vast field of future applications and developments, using different renewable sources, as biomass, wind, or even hybrid, with different mathematical models and requirements; and even smart grids, or electrical systems in general.
+Few research has been made until now, and the scenario is auspicious from now on.

### 2019-10-26 Tex/Old text/chapters/appendix.tex
Thesis update

@@
 %
-\section{List of Publications}
 Here there are a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.
 
-\subsection{Journals}
+\section{Journals}
 
@@
 
-\subsection{Congress}
+\section{Congress}
+
 Trindade, A., Cordeiro, L.
@@
 This paper is now the base of a new paper, for the 32nd International Conference on Computer-Aided Verification (CAV) 2020 with deadline in 23 January 2020 in \url{http://i-cav.org/2020/call-for-papers/}.
-
-\section{Tools Description and How to Use it}
-
-In this section, we describe the two tools created during the PhD process to implement and test the two scientific methodologies of the thesis.
-
-\subsection{Tools}
-
-\subsection{How to use it}

### 2019-10-26 Tex/Old text/chapters/appendixB.tex
Thesis update

%\textbf{List of Publications}
%
Here we describe the two tools created during the PhD process to implement and validate the two scientific methodologies of the thesis.

\section{Tools}

\section{How to use it}

### 2019-10-26 Tex/Old text/chapters/conclusion.tex
Thesis update

@@
-At this final chapter, we present the conclusions about the research done during the Doctoral process.
-Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable source) closes the work.
+At this final chapter, we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were applied to solar PV systems.
+Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources) closes the work.
 
@@
 
-This Thesis contributions can be split in two, each one concerning the techniques proposed with the use of model checking to solar PV systems, and the tools created to validate it.
+Our contributions can be split in two, each one concerning the scientific methods proposed with the use of model checking to solar PV systems, and the tools created to validate it.
 
-It was described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques.
-It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-Although the verification method proposed takes longer than simulation methods, it is able to avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.
+Related to the first contributions, depicted with details in ~\autoref{chap:automatedverification}, it was described and evaluated an automated verification method to validate over the time a given stand-alone PV system design, and see if it meets its user and electrical requirements using software model checking techniques.
+There are a lot of possibilities to perform that validation, as testing, laboratory measuring, or even simulation (used before field deployment, as our proposal); however, we showed, supported by an algorithm that uses our approach, moreover supported by case studies, by monitoring data from field, and from interview if the owners, that our approach is feasible and effective.
+
+It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W (inverter specification); and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
+Although the verification method that we proposed takes longer than simulation methods, it is able to avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.
+This result was validated by the sized systems deployed at the field.
+
 Moreover, it was not necessary to 'adapt' the tool, since the specialized simulation tool (HOMER Pro) had to be adjusted in order to not perform the optimization of the system.
@@
 
+%In a nutshell, our proposed PV system validation method, who check the size of inputted PV system, and verifies it over the time, was feasible and effective, supported by a algorithm written to implement the method, by a comparative with a commercial simulation tool, and by real data collect at the field.
+%
 Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
@@
 
-It was described and evaluated as well, an automated synthesis method to obtain the optimal size of PV system using software model checking techniques.
-It was considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
-The automated synthesis tool presented detailed optimal solution to six case studies adopted in this paper, with specifications, models, and the arrangement in terms of series-parallel connections, thereby covering the charge controller, which was not presented by HOMER Pro.
-In a nutshell, the proposed automated synthesis tool took more time to find the optimal solution than HOMER Pro; however, the presented solution was more complete and detailed, which is very useful to a user to get a list of equipment and go to shopping.
+Furthermore, we have also contributions from the method depicted in ~\autoref{chap:automatedsynthesis}.
+We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking techniques.
+The focus was on the synthesis method to obtain the optimal solution based on formal methods, which can cover better the design-space as opposed to simulation tools.
+Our thesis produced a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
+
+We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase, and a refinement from the iterative search from the {\sc Verify} phase, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
+Our algorithm, that implements the method, uses a data base of commercial equipment from the marketing, including the price.
+In order to validate the method, it was considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+In terms of performance and better results, CPAchecker was the winner and used for the comparative with the simulation tool.
+
+In summary, our synthesis proposal is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
+In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current, and voltage; we also cover the charge controller, which is unavailable in HOMER Pro.
+Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro; however, the presented solution is sound and complete; it also provides a list of equipment to be bought from manufacturers.
+%Moreover, we extended the CEGIS synthesis method and implemented this extension within our proposed formal synthesis tool, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
 
@@
 And last, but not least important to report, besides the fact that the goal of a PhD is to make a contribution to the body of human research, one of the great things about PhD is you will be able to conduct your own research.
-In that direction, we can say that with the technique proposed here (formal methods using automated verification and model checking) to energy sector, there is a vast field of future applications and developments, using different renewable sources, as biomass, wind, or even hybrid, with different mathematical models and requirements; and even smart grids, or electrical systems in general.
+In that direction, we can say that with the technique proposed here (formal methods using automated verification and model checking) to energy sector, there is a vast field of future applications and developments, using different renewable sources, as biomass, as wind, or even hybrid, with different mathematical models and requirements; and including smart grids, or electrical systems in general.
 Few research has been made until now, and the scenario is auspicious from now on.

### 2019-10-26 Tex/Old text/chapters/introduction.tex
Thesis update

@@
 Chapter '~\nameref{chap:background}' gives the theoretical basis on formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.
+
 Chapter '~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new technique.
+
 Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science applied to solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collect during fieldwork.
+
 Chapter '~\nameref{chap:conclusions}' presents the main contributions, future work directions and concluding remarks.
+
+~\autoref{chap:publications} presents a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.
+
+~\autoref{chap:tools} depicts the tools created during the PhD process to implement and validate the two scientific methods of the thesis (and how to use it).

### 2019-10-26 Tex/Old text/chapters/appendixB.tex
Thesis update

@@
-%\textbf{List of Publications}
-%
 Here we describe the two tools created during the PhD process to implement and validate the two scientific methodologies of the thesis.
@@
 
+During the PhD process, the techniques from computer science and proposed to tackle issues related to solar photovoltaic systems became algorithms and codes.
+Those codes became tools, and the tools were used during comparative with simulation tool in order to validate the technique.
+
+In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation.
+
+We wrote the tools in Language C, without the use of '\# include', or '\# define'.
+Based on the fact that there is no use of compiler library, it was necessary to write some functions which perform specific calculations according to the adopted mathematical models (logarithm of natural order and exponential).
+
+\subsubsection{Automated Verification Tool (PV System validation)}
+
+The code can be divided in four blocks:
+
+\begin{itemize}
+\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and data sheet information from each equipment of the PV system that will be verified.
+
+\item \textbf{Block 2}: support functions (logarithm of natural order, exponential)
+
+\item \textbf{Block 3}: PV system specific functions (charge battery, discharge battery, PV panel generation, sizing check)
+
+\item \textbf{Block 4}: main code with charge, discharge battery control, based on PV generation from solar panels and the state of charge form batteries, having the commitment to deliver the power and energy that the house demands, according with the restrictions form the sized system.
+\end{itemize}
+
+\subsubsection{Automated Synthesis Tool (PV System Optimal Sizing)}
+
+The code can be divided in three blocks:
+
+\begin{itemize}
+\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and data sheet information from each equipment of the PV system that will be verified.
+
+\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions)
+
+\item \textbf{Block 3}: main code with the iterative control of the verify phase
+\end{itemize}
+
 \section{How to use it}
+The only block that demands user intervention from user in order to input data is the block 1 of both tools.
+
+Regarding the automated verification tool, it is necessary to input the following data (editing and modifying the code):
+
+\begin{itemize}
+\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location
+\item Minimum and maximum temperature (average for every month of the year)
+\item Local insolation (average number of sun hours by day at the location)
+\item Number of solar panels in series
+\item Number of solar panels in parallel
+\item Number of series-connected cells from each solar panel
+\item Nominal Operating Cell Temperature
+\item Reference solar irradiance
+\item Reference temperature
+\item Short-circuit current temperature coefficient
+\item Open-circuit voltage temperature coefficient
+\item Reference short-circuit current
+\item Reference open-circuit voltage
+\item Reference maximum current, voltage, and power
+\item Minimum MPPT voltage
+\item Operation current
+\item Solar panel efficiency
+\item Panel area in square meters
+\item DC-bus voltage
+\item Individual battery voltage
+\item Battery bank capacity
+\item State of charge limit
+\item Number of batteries in series
+\item Number of batteries in parallel
+\item Autonomy of the batteries
+\item Efficiency from batteries
+\item Float, absorption and bulk battery voltages
+\item Charge controller efficiency
+\item Charge controller current
+\item Charge controller maximum voltage
+\item Inverter output voltage
+\item Inverter AC reference power
+\item Inverter maximum (surge) AC power reference
+\item AC voltage (outlet standard)
+\item Power demand from the house
+\item Surge demand from the house
+\item Energy consumption from the house
+\end{itemize}
+
+And regarding the automated synthesis tool, it is necessary the following data (editing and modifying the code):
+
+\begin{itemize}
+\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location
+\item Minimum and maximum temperature (average for every month of the year)
+\item Local insolation (average number of sun hours by day at the location)
+\item DC-bus voltage
+\item Autonomy of the batteries
+\item State of charge limit
+\item Individual battery voltage
+\item Reference solar irradiance
+\item Reference temperature
+\item For every item of solar PV panel list, as a matrix (area, efficiency, number of series-connected cells, Nominal Operating Cell Temperature, short-circuit current temperature coefficient, open-circuit voltage temperature coefficient, reference short-circuit current, reference open-circuit voltage, reference maximum power, reference maximum current, reference maximum voltage, maximum voltage on NOCT, cost in US dollars)
+\item For every item of batteries list, as a matrix (efficiency, voltage, capacity $C_{20}$), bulk voltage, float voltage, cost in US dollars)
+\item For every item of charge controller list, as a matrix (efficiency, nominal current, voltage  output, minimum MPPT voltage, maximum current, cost in US dollars)
+\item For every item of inverter list, as a matrix (efficiency, input DC voltage, output AC voltage, reference AC power, reference maximum AC power, cost in US dollars)
+\item AC voltage (outlet standard)
+\item Power demand from the house
+\item Surge demand from the house
+\item Energy consumption from the house
+\end{itemize}
+
+\section{Automated Verification with Incremental ESBMC}
+Here 123
+
+\section{Automated Synthesis with CPAchecker}
+Here 4321

### 2019-10-27 Tex/Old text/chapters/appendixB.tex
Thesis update

@@
-Here we describe the two tools created during the PhD process to implement and validate the two scientific methodologies of the thesis.
+Here we describe the two tools created with the target to implement and validate the two scientific methodologies of the thesis.
 
@@
 During the PhD process, the techniques from computer science and proposed to tackle issues related to solar photovoltaic systems became algorithms and codes.
-Those codes became tools, and the tools were used during comparative with simulation tool in order to validate the technique.
+Those codes became tools, and the tools were used during comparative with simulation tool in order to validate the techniques.
 
-In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation.
+In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since that we aimed to evaluate different .
 
@@
 
-\subsubsection{Automated Verification Tool (PV System validation)}
+\subsection{Automated Verification Tool (PV System validation)}
+\label{sec:automatedverification}
 
@@
 
-\subsubsection{Automated Synthesis Tool (PV System Optimal Sizing)}
+\subsection{Automated Synthesis Tool (PV System Optimal Sizing)}
+\label{sec:automatedsynthesis}
 
@@
 
-\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions)
+\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking)
 
@@
 \section{How to use it}
+
 The only block that demands user intervention from user in order to input data is the block 1 of both tools.
+If it is aimed to change the mathematical model adopted, so coding must be done in block 3 of automated verification tool and in block 2 of automated synthesis tool.
 
@@
 
-\section{Automated Verification with Incremental ESBMC}
-Here 123
+\subsection{Automated Verification with Incremental ESBMC}
 
-\section{Automated Synthesis with CPAchecker}
-Here 4321
+Here we describe specifically how to use the code explained in previous section (\ref{sec:automatedverification}) using the incremental ESBMC with Z3 solver, that presented the better performance during the comparative with other verifiers.
+However, in \ref{sec:setup} it was showed how to use the code with other verifiers.
+
+ESBMC can be downloaded from its GitHub in \url{https://github.com/esbmc/esbmc}. Installation commands can be found in \url{https://ssvlab.github.io/esbmc/documentation.html}.
+
+Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3.
+
+Where:
+\begin{itemize}
+\item -no-bounds-check: says to the verifier to not perform array bound check (the aim is not to check array bound violation);
+\item -\phantom{}-no-pointer-check: says to the verifier to not check if there is pointer violation;
+\item -\phantom{}-unwind 100: it limits the bound of search (100 in this case);
+\item -\phantom{}-smt-during-symex: enable incremental SMT solving;
+\item -\phantom{}-smt-symex-guard: call the solver during symbolic execution;
+\item -\phantom{}-z3: uses Z3 as solver.
+\end{itemize}
+
+Some results issued by the ESBMC verifier were depicted in \ref{sec:ESBMCverification} when performing the case studies.
+
+\subsection{Automated Synthesis with CPAchecker}
+
+Here we describe specifically how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, that presented the better performance during the comparative with other verifiers.
+However, in \ref{sec:synthesissetup} it was showed how to use the code with other verifiers.
+
+The CPAchecker can be downloaded from its web site in \url{https://cpachecker.sosy-lab.org/}. There are versions available to Linux and MS-Windows operational systems.
+
+Install a Java Runtime Environment which is at least Java 8 compatible (e.g., Oracle JRE, OpenJDK). Cf. the web site \url{http://java.oracle.com/}.
+
+The command-line in Linux is: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c.
+
+Worth to mention that the default heap size is 1200m (or 1.2 GB of RAM), however it is indicated to specify a large value with '-heap' if you have more RAM memory available.
+In our case, we adjusted the heap to 64000m (64 GB).
+
+Other important issue is the time-out of the execution process: the parameter 'limits.time.cpu' at the file 'resource-limits.properties' in folder 'config/includes' must be edited according the desired value.
+In our case, 'limits.time.cpu = 14400s', i.e., 14400 seconds or 240 minutes or 4 hours.
+
+Some results, reports and graphics, issued by the CPAchecker verifier were depicted in \ref{sec:synthesisresults}.

### 2019-10-28 Tex/Old text/chapters/chapter02.tex
Thesis update

@@
-In this chapter we present some concepts related to the intersection of the two areas: the computer science applied to an electrical engineering problem, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.
+In this chapter we present some concepts related to the intersection of the two areas:  computer science methods used to solve electrical engineering problems, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.
 
@@
 
-Is was pointed out the importance of mathematical rigor to the models and representation of systems, and that automated verification can be applied to any kind of systems (from simple ones to the complex ones)
+Is was pointed out the importance of mathematical rigor to the models and representation of systems, and that automated verification method can be applied to any kind of systems (from simple ones to the complex ones)
 

### 2019-10-28 Tex/Old text/chapters/conclusion.tex
Thesis update

@@
-At this final chapter, we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were applied to solar PV systems.
+At this final chapter, we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were used to tackle solar PV systems issues, as validation over time and sizing optimization.
 Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources) closes the work.
@@
 
-One future long term direction is to foster the creation of a research group in automated verification and synthesis applied to electrical systems; and a international network of researchers in model checking applied to electrical systems.
+One future long term direction is to foster the creation of a research group in automated verification and synthesis applied to electrical systems.
 

### 2019-10-28 Tex/Old text/chapters/introduction.tex
Thesis update

@@
 
-Chapter '~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new technique.
+Chapter '~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new method of PV systems validation.
 
-Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science applied to solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collect during fieldwork.
+Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science and its application to obtain the optimal sizing of stand-alone solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collect from fieldwork.
 

### 2019-10-28 Tex/Old text/chapters/appendix.tex
Added citations
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Trindade, A., Cordeiro, L.
-\textbf{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}, submitted: 8 May 2019, status: accepted 26 September 2019; published on-line on 15 October 2019) by Elsevier Solar Energy (Impact Factor 4.674, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV) \url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X1930965X}
+\textbf{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}, submitted: 8 May 2019, status: accepted 26 September 2019; published on-line on 15 October 2019) by Elsevier Solar Energy (Impact Factor 4.674, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV) \url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X1930965X}~\cite{TrindadeCordeiro19}.
 
 Trindade, A., Cordeiro, L.
-\textbf{Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis}, submitted: 28 September 2019, status: under review by IEEE Transactions on Sustainable Energy (Impact Factor 7.65, CAPES A1 Engineering IV), \url{https://www.journals.elsevier.com/applied-energy}
+\textbf{Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis}, submitted: 28 September 2019, status: under review by IEEE Transactions on Sustainable Energy (Impact Factor 7.65, CAPES A1 Engineering IV), \url{https://www.journals.elsevier.com/applied-energy}~\cite{abs-1909-13139}.
 
@@
 \textbf{Multi-core model checking and maximum satisfiability applied to hardware-software partitioning}, Online publication date: 15 November 2017, by International Journal of Embedded Systems (IJES), CAPES B2 Computing Engineering index.
-DOI:   \url {https://doi.org/10.1504/IJES.2017.10008947}.
+DOI:   \url {https://doi.org/10.1504/IJES.2017.10008947}~\cite{TrindadeDJISC17}.
 

### 2019-10-28 Tex/Old text/chapters/appendixB.tex
Thesis update

@@
 \begin{itemize}
-\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and data sheet information from each equipment of the PV system that will be verified.
+\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and data sheet information from each equipment of the PV system that will be verified;
 
-\item \textbf{Block 2}: support functions (logarithm of natural order, exponential)
+\item \textbf{Block 2}: support functions (logarithm of natural order, exponential);
 
-\item \textbf{Block 3}: PV system specific functions (charge battery, discharge battery, PV panel generation, sizing check)
+\item \textbf{Block 3}: PV system specific functions (charge battery, discharge battery, PV panel generation, sizing check);
 
@@
 \begin{itemize}
-\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and data sheet information from each equipment of the PV system that will be verified.
+\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and data sheet information from each equipment of the PV system that will be verified;
 
-\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking)
+\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);
 
-\item \textbf{Block 3}: main code with the iterative control of the verify phase
+\item \textbf{Block 3}: main code with the iterative control of the verify phase.
 \end{itemize}
@@
 \begin{itemize}
-\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location
-\item Minimum and maximum temperature (average for every month of the year)
-\item Local insolation (average number of sun hours by day at the location)
-\item Number of solar panels in series
-\item Number of solar panels in parallel
-\item Number of series-connected cells from each solar panel
-\item Nominal Operating Cell Temperature
-\item Reference solar irradiance
-\item Reference temperature
-\item Short-circuit current temperature coefficient
-\item Open-circuit voltage temperature coefficient
-\item Reference short-circuit current
-\item Reference open-circuit voltage
-\item Reference maximum current, voltage, and power
-\item Minimum MPPT voltage
-\item Operation current
-\item Solar panel efficiency
-\item Panel area in square meters
-\item DC-bus voltage
-\item Individual battery voltage
-\item Battery bank capacity
-\item State of charge limit
-\item Number of batteries in series
-\item Number of batteries in parallel
-\item Autonomy of the batteries
-\item Efficiency from batteries
-\item Float, absorption and bulk battery voltages
-\item Charge controller efficiency
-\item Charge controller current
-\item Charge controller maximum voltage
-\item Inverter output voltage
-\item Inverter AC reference power
-\item Inverter maximum (surge) AC power reference
-\item AC voltage (outlet standard)
-\item Power demand from the house
-\item Surge demand from the house
-\item Energy consumption from the house
+\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
+\item Minimum and maximum temperature (average for every month of the year);
+\item Local insolation (average number of sun hours by day at the location);
+\item Number of solar panels in series;
+\item Number of solar panels in parallel;
+\item Number of series-connected cells from each solar panel;
+\item Nominal Operating Cell Temperature;
+\item Reference solar irradiance;
+\item Reference temperature;
+\item Short-circuit current temperature coefficient;
+\item Open-circuit voltage temperature coefficient;
+\item Reference short-circuit current;
+\item Reference open-circuit voltage;
+\item Reference maximum current, voltage, and power;
+\item Minimum MPPT voltage;
+\item Operation current;
+\item Solar panel efficiency;
+\item Panel area in square meters;
+\item DC-bus voltage;
+\item Individual battery voltage;
+\item Battery bank capacity;
+\item State of charge limit;
+\item Number of batteries in series;
+\item Number of batteries in parallel;
+\item Autonomy of the batteries;
+\item Efficiency from batteries;
+\item Float, absorption and bulk battery voltages;
+\item Charge controller efficiency;
+\item Charge controller current;
+\item Charge controller maximum voltage;
+\item Inverter output voltage;
+\item Inverter AC reference power;
+\item Inverter maximum (surge) AC power reference;
+\item AC voltage (outlet standard);
+\item Power demand from the house;
+\item Surge demand from the house;
+\item Energy consumption from the house.
 \end{itemize}
@@
 \begin{itemize}
-\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location
-\item Minimum and maximum temperature (average for every month of the year)
-\item Local insolation (average number of sun hours by day at the location)
-\item DC-bus voltage
-\item Autonomy of the batteries
-\item State of charge limit
-\item Individual battery voltage
-\item Reference solar irradiance
-\item Reference temperature
-\item For every item of solar PV panel list, as a matrix (area, efficiency, number of series-connected cells, Nominal Operating Cell Temperature, short-circuit current temperature coefficient, open-circuit voltage temperature coefficient, reference short-circuit current, reference open-circuit voltage, reference maximum power, reference maximum current, reference maximum voltage, maximum voltage on NOCT, cost in US dollars)
-\item For every item of batteries list, as a matrix (efficiency, voltage, capacity $C_{20}$), bulk voltage, float voltage, cost in US dollars)
-\item For every item of charge controller list, as a matrix (efficiency, nominal current, voltage  output, minimum MPPT voltage, maximum current, cost in US dollars)
-\item For every item of inverter list, as a matrix (efficiency, input DC voltage, output AC voltage, reference AC power, reference maximum AC power, cost in US dollars)
-\item AC voltage (outlet standard)
-\item Power demand from the house
-\item Surge demand from the house
-\item Energy consumption from the house
+\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
+\item Minimum and maximum temperature (average for every month of the year);
+\item Local insolation (average number of sun hours by day at the location);
+\item DC-bus voltage;
+\item Autonomy of the batteries;
+\item State of charge limit;
+\item Individual battery voltage;
+\item Reference solar irradiance;
+\item Reference temperature;
+\item For every item of solar PV panel list, as a matrix (area, efficiency, number of series-connected cells, Nominal Operating Cell Temperature, short-circuit current temperature coefficient, open-circuit voltage temperature coefficient, reference short-circuit current, reference open-circuit voltage, reference maximum power, reference maximum current, reference maximum voltage, maximum voltage on NOCT, cost in US dollars);
+\item For every item of batteries list, as a matrix (efficiency, voltage, capacity $C_{20}$), bulk voltage, float voltage, cost in US dollars);
+\item For every item of charge controller list, as a matrix (efficiency, nominal current, voltage  output, minimum MPPT voltage, maximum current, cost in US dollars);
+\item For every item of inverter list, as a matrix (efficiency, input DC voltage, output AC voltage, reference AC power, reference maximum AC power, cost in US dollars);
+\item AC voltage (outlet standard);
+\item Power demand from the house;
+\item Surge demand from the house;
+\item Energy consumption from the house.
 \end{itemize}
@@
 
-ESBMC can be downloaded from its GitHub in \url{https://github.com/esbmc/esbmc}. Installation commands can be found in \url{https://ssvlab.github.io/esbmc/documentation.html}.
+ESBMC can be downloaded from its GitHub in \url{https://github.com/esbmc/esbmc}.
+Installation commands can be found in \url{https://ssvlab.github.io/esbmc/documentation.html}.
+There is just the Linux version of the verifier.
 
-Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3.
+\bigskip
+\fbox{\parbox{\textwidth}{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3.}}
+\bigskip
 
@@
 
-The command-line in Linux is: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c.
+\bigskip
+\fbox{\parbox{\textwidth}{The command-line in Linux is: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c.}} 
+\bigskip
 

### 2019-10-28 Tex/Old text/chapters/conclusion.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
-At this final chapter, we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were used to tackle solar PV systems issues, as validation over time and sizing optimization.
+Here we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were used to tackle solar PV systems issues, as validation over time and sizing optimization.
 Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources) closes the work.

### 2019-10-28 Tex/Old text/chapters/conclusion.tex
revised conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Here we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were used to tackle solar PV systems issues, as validation over time and sizing optimization.
-Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources) closes the work.
+Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources), concludes the work.
 
+%----------------------------------------------
 \section{Main Contributions}
+%----------------------------------------------
 
@@
 
-Related to the first contributions, depicted with details in ~\autoref{chap:automatedverification}, it was described and evaluated an automated verification method to validate over the time a given stand-alone PV system design, and see if it meets its user and electrical requirements using software model checking techniques.
-There are a lot of possibilities to perform that validation, as testing, laboratory measuring, or even simulation (used before field deployment, as our proposal); however, we showed, supported by an algorithm that uses our approach, moreover supported by case studies, by monitoring data from field, and from interview if the owners, that our approach is feasible and effective.
+Concerning the first contribution presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method to validate a given stand-alone PV system design and check whether it meets its user and electrical requirements using software model checking techniques.
+There exist various possibilities to perform that validation, such as testing, laboratory measuring, or even simulation (used before field deployment, as our proposal).
+\textcolor{red}{this sentence is unclear....} However, we showed, supported by an algorithm that uses our approach, moreover supported by case studies, by monitoring data from field, and from an interview with the owners, that our approach is feasible and effective.
 
-It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W (inverter specification); and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-Although the verification method that we proposed takes longer than simulation methods, it is able to avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.
-This result was validated by the sized systems deployed at the field.
+It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W (inverter specification), and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
+Although the verification method that we proposed takes longer than simulation methods, it can avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.
+This result was validated by the sized systems deployed in the field.
 
-Moreover, it was not necessary to 'adapt' the tool, since the specialized simulation tool (HOMER Pro) had to be adjusted in order to not perform the optimization of the system.
-In addition, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature.
+Moreover, it was not necessary to ``adapt'' the tool, since the specialized simulation tool (HOMER Pro) had to be adjusted in order not to perform the optimization of the system.
+\textcolor{red}{this sentence is unclear...} Besides, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature.
 
@@
 %
-Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
+\textcolor{red}{this sentence needs to be rewritten... when you use better, less, etc, you need to use ``than'' and add the second sentence for the comparison.}
+Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presented in the field.
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.
 
-Furthermore, we have also contributions from the method depicted in ~\autoref{chap:automatedsynthesis}.
+Furthermore, we have also contributions from the method described in ~\autoref{chap:automatedsynthesis}.
 We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking techniques.
@@
 
+\textcolor{red}{These sentences are too long and difficult to understand.}
 We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase, and a refinement from the iterative search from the {\sc Verify} phase, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
-Our algorithm, that implements the method, uses a data base of commercial equipment from the marketing, including the price.
-In order to validate the method, it was considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results.
+Our algorithm that implements this method uses a database of commercial equipment from the marketing, including the price.
+In order to validate our proposed method, we considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
 In terms of performance and better results, CPAchecker was the winner and used for the comparative with the simulation tool.
@@
 In summary, our synthesis proposal is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
-In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current, and voltage; we also cover the charge controller, which is unavailable in HOMER Pro.
+In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the component model, nominal current, and voltage.
+We also cover the charge controller, which is unavailable in HOMER Pro.
 Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro; however, the presented solution is sound and complete; it also provides a list of equipment to be bought from manufacturers.
@@
 
+%----------------------------------------------
 \section{Future Work Directions}
+%----------------------------------------------
 
-As the focus here was stand-alone solar PV systems, one future work will be also consider other types of renewable energy and even hybrid ones to allow the method to verify and to obtain the optimal sizing of typical rural electrification systems.
+As the focus here was stand-alone solar PV systems, one future work will also consider other types of renewable energy and even hybrid ones to allow the method to verify and to obtain the optimal sizing of typical rural electrification systems.
 
-Related to automated sizing, the author plan to improve the power reliability analysis, 
-to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil), and to validate some cases with deployed PV systems in isolated communities.
+Related to automated sizing, the author plans to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil), and to validate some cases with deployed PV systems in isolated communities.
 
-It is planned to develop the code of a general purpose simulation tool, using the same mathematical model employed for the model checking methods of this work, to include it in the comparative in order to cover all the possibilities to validate or optimize solar PV systems.
+\textcolor{red}{This sentence is too long and difficult to understand.}
+It is planned to develop the code of a general-purpose simulation tool, using the same mathematical model employed for the model checking methods of this work, to include it in the comparative in order to cover all the possibilities to validate or optimize solar PV systems.
 
@@
 
+%----------------------------------------------
 \section{Concluding Remarks}
+%----------------------------------------------
 
+\textcolor{red}{This sentence is too long and difficult to understand.}
 The automated verification and automates synthesis methods demonstrate the effectiveness and the potential of use in stand-alone solar PV systems.
-Some issues must be addressed in order to improve the tools, as performance and the human-computer interaction, however the work has potential and it is promising.
+Some issues must be addressed in order to improve the tools, as performance and the human-computer interaction.
+However, the work has potential, and it is promising \textcolor{red}{how is it promising?}.
 
-About license and the use of tools that the author employed at this work, must be noticed that HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; the verifiers, as CPAchecker, ESBMC and CBMC, and their solvers, they are  based on open source software license and usually allows the users to freely use, modify, and distribute licensed product.
-Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is a advantage when compared to commercial tools); therefore, some of the licenses do not allow the software to be used in a commercial context.
+\textcolor{red}{This sentence is too long and difficult to understand.}
+About license and the use of tools that the author employed at this work, must be noticed that HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; the verifiers, as CPAchecker, ESBMC and CBMC, and their solvers, they are based on open-source software license and usually allows the users to use, modify, and distribute licensed product freely.
+Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is an advantage when compared to commercial tools); therefore, some of the licenses do not allow the software to be used in a commercial context.
 
@@
 
-And last, but not least important to report, besides the fact that the goal of a PhD is to make a contribution to the body of human research, one of the great things about PhD is you will be able to conduct your own research.
-In that direction, we can say that with the technique proposed here (formal methods using automated verification and model checking) to energy sector, there is a vast field of future applications and developments, using different renewable sources, as biomass, as wind, or even hybrid, with different mathematical models and requirements; and including smart grids, or electrical systems in general.
-Few research has been made until now, and the scenario is auspicious from now on.
+\textcolor{red}{this sentence is tool informal with the use of ``you''.}
+And last, but not least significant to report, besides the fact that the goal of a PhD is to contribute to the body of human research, one of the great things about PhD is you will be able to conduct your research.
+In that direction, we can say that with the technique proposed here (formal methods using automated verification and model checking) to energy sector, there exists a vast field of future applications and developments, using different renewable sources, as biomass, wind, or even hybrid, with different mathematical models and requirements; and including smart grids, or electrical systems in general.
+Few research has been done until now, and the scenario is auspicious from now on.

### 2019-10-28 Tex/Old text/chapters/conclusion.tex
Thesis update

@@
 
-Concerning the first contribution presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method to validate a given stand-alone PV system design and check whether it meets its user and electrical requirements using software model checking techniques.
-There exist various possibilities to perform that validation, such as testing, laboratory measuring, or even simulation (used before field deployment, as our proposal).
-\textcolor{red}{this sentence is unclear....} However, we showed, supported by an algorithm that uses our approach, moreover supported by case studies, by monitoring data from field, and from an interview with the owners, that our approach is feasible and effective.
+Concerning the first contribution presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method to validate a given stand-alone PV system.
+\textcolor{red}{Our method, using model checking, can performance size check and verify, over time, if a PV system meets electrical requirements.
+We showed that there exist various possibilities to perform that validation, such as testing, laboratory measuring, or even simulation.
+However, we developed an algorithm and a tool using model checking that was feasible and effective.
+Our results were supported by case studies, by monitoring data from field, and from an interview with PV owners.}
 
@@
 
-Moreover, it was not necessary to ``adapt'' the tool, since the specialized simulation tool (HOMER Pro) had to be adjusted in order not to perform the optimization of the system.
-\textcolor{red}{this sentence is unclear...} Besides, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature.
+\textcolor{red}{Moreover, considering that HOMER Pro always perform size optimization during the simulation process, the user always have to 'adapt' this simulation tool in order to avoid the optimization and to validate the PV system as inputted in it.
+That adaptation is not necessary using our approach, because optimization is another method different of verification.
+Besides, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature, i.e., the user can not specify the battery autonomy.}
 
@@
 %
-\textcolor{red}{this sentence needs to be rewritten... when you use better, less, etc, you need to use ``than'' and add the second sentence for the comparison.}
-Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presented in the field.
+\textcolor{red}{Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance than CBMC (around four times faster), used less RAM memory than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presented in the field.}
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.
@@
 
-\textcolor{red}{These sentences are too long and difficult to understand.}
-We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase, and a refinement from the iterative search from the {\sc Verify} phase, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
-Our algorithm that implements this method uses a database of commercial equipment from the marketing, including the price.
-In order to validate our proposed method, we considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
+\textcolor{red}{We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase, and a refinement from the iterative search from the {\sc Verify} phase.
+With this approach, we obtain optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
+Our algorithm, that implements this method, uses a database of commercial equipment from the marketing, including the price.
+Furthermore, in order to validate our method, we considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
+In addition, we used again the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
 In terms of performance and better results, CPAchecker was the winner and used for the comparative with the simulation tool.
+}
 
@@
 
-\textcolor{red}{This sentence is too long and difficult to understand.}
-It is planned to develop the code of a general-purpose simulation tool, using the same mathematical model employed for the model checking methods of this work, to include it in the comparative in order to cover all the possibilities to validate or optimize solar PV systems.
+\textcolor{red}{It is planned to develop the code of a general-purpose simulation tool, as MATLAB for example, using the same mathematical model employed in our two methods.
+Thus a broader comparison can be made, in order to cover all the possibilities to validate or optimize solar PV systems.}
 
@@
 
-\textcolor{red}{This sentence is too long and difficult to understand.}
-The automated verification and automates synthesis methods demonstrate the effectiveness and the potential of use in stand-alone solar PV systems.
-Some issues must be addressed in order to improve the tools, as performance and the human-computer interaction.
-However, the work has potential, and it is promising \textcolor{red}{how is it promising?}.
+\textcolor{red}{The automated verification and automates synthesis methods demonstrate the effectiveness and the potential of use in stand-alone solar PV systems.
+Some issues must be addressed in order to improve the tools, as performance and the human-computer interaction.}.
 
-\textcolor{red}{This sentence is too long and difficult to understand.}
-About license and the use of tools that the author employed at this work, must be noticed that HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; the verifiers, as CPAchecker, ESBMC and CBMC, and their solvers, they are based on open-source software license and usually allows the users to use, modify, and distribute licensed product freely.
-Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is an advantage when compared to commercial tools); therefore, some of the licenses do not allow the software to be used in a commercial context.
+\textcolor{red}{About license and the use of tools mentioned in this thesis, must be noticed that HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}.
+Related to the verifiers, as CPAchecker, ESBMC and CBMC, and their solvers, they are based on open-source software license and usually allows the users to use, modify, and distribute licensed product freely.
+Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is an advantage when compared to commercial tools).}
 
@@
 
-\textcolor{red}{this sentence is tool informal with the use of ``you''.}
-And last, but not least significant to report, besides the fact that the goal of a PhD is to contribute to the body of human research, one of the great things about PhD is you will be able to conduct your research.
-In that direction, we can say that with the technique proposed here (formal methods using automated verification and model checking) to energy sector, there exists a vast field of future applications and developments, using different renewable sources, as biomass, wind, or even hybrid, with different mathematical models and requirements; and including smart grids, or electrical systems in general.
-Few research has been done until now, and the scenario is auspicious from now on.
+\textcolor{red}{And last, but not least significant to report, one of the great things about PhD is that the student will be able to conduct its research in the future.
+In that direction, we can say that with the methods proposed here and targeted to tackle the energy sector, there exists a vast field of future applications and developments, using different renewable sources.
+We can mention here biomass, wind, or even hybrid generation, with different mathematical models and requirements; and including smart grids, or electrical systems in general.
+Few research has been done until now, and the scenario is auspicious to do it.}
+%besides the fact that the goal of a PhD is to contribute to the body of human research,

### 2019-10-29 Tex/Old text/chapters/conclusion.tex
revised conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
-Here we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were used to tackle solar PV systems issues, as validation over time and sizing optimization.
-Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources), concludes the work.
+Here we present the conclusions about our research and the results obtained during the Doctoral process.
+In particular, we described two scientific methods (or techniques) from computer science, which were used to tackle solar PV systems issues, as validation over time and sizing optimization.
+A list of future contributions concludes the work; this list might foster the creation of a research group that investigates model checking techniques to electrical systems (and not only renewable sources as we have done here).
 
@@
 
-Our contributions can be split in two, each one concerning the scientific methods proposed with the use of model checking to solar PV systems, and the tools created to validate it.
+We split our contributions into two, each one concerning the scientific methods proposed with the use of model checking to solar PV systems, and the tools created to validate it.
 
 Concerning the first contribution presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method to validate a given stand-alone PV system.
-\textcolor{red}{Our method, using model checking, can performance size check and verify, over time, if a PV system meets electrical requirements.
+Our method, using model checking, can performance size check and verify, over time, whether a PV system meets electrical requirements.
 We showed that there exist various possibilities to perform that validation, such as testing, laboratory measuring, or even simulation.
 However, we developed an algorithm and a tool using model checking that was feasible and effective.
-Our results were supported by case studies, by monitoring data from field, and from an interview with PV owners.}
+Our results were supported by case studies, by monitoring data from the field, and an interview with PV owners.
 
-It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W (inverter specification), and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
+We have considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W (inverter specification), and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
 Although the verification method that we proposed takes longer than simulation methods, it can avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.
-This result was validated by the sized systems deployed in the field.
+We validate these results by the sized systems deployed in the field.
 
-\textcolor{red}{Moreover, considering that HOMER Pro always perform size optimization during the simulation process, the user always have to 'adapt' this simulation tool in order to avoid the optimization and to validate the PV system as inputted in it.
-That adaptation is not necessary using our approach, because optimization is another method different of verification.
-Besides, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature, i.e., the user can not specify the battery autonomy.}
+Moreover, considering that HOMER Pro always performs size optimization during the simulation process, the user always has to ``adopt'' this simulation tool in order to avoid the optimization and to validate the PV system as inputted in it.
+That adaptation is not necessary using our approach, because optimization is another method different to verification.
+Besides, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature, i.e., the user can not specify the battery autonomy.
 
@@
 %
-\textcolor{red}{Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance than CBMC (around four times faster), used less RAM memory than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presented in the field.}
+Concerning the verification engines comparative, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented the better performance than CBMC (around four times faster), used less RAM than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker).
+All our experimental results are sound since the PV owners and the monitoring system validated the possible flaws that the system could present in the field.
 %New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.
 
-Furthermore, we have also contributions from the method described in ~\autoref{chap:automatedsynthesis}.
+Furthermore, we have also contributions from the method described in~\autoref{chap:automatedsynthesis}.
 We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking techniques.
@@
 
-\textcolor{red}{We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase, and a refinement from the iterative search from the {\sc Verify} phase.
-With this approach, we obtain optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
-Our algorithm, that implements this method, uses a database of commercial equipment from the marketing, including the price.
+We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase and refinement from the iterative search from the {\sc Verify} phase.
+With this approach, we obtain the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
+Our algorithm that implements this method uses a database of commercial equipment from the marketing, including the price.
 Furthermore, in order to validate our method, we considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-In addition, we used again the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
+Besides, we used again the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
 In terms of performance and better results, CPAchecker was the winner and used for the comparative with the simulation tool.
-}
 
@@
 
-As the focus here was stand-alone solar PV systems, one future work will also consider other types of renewable energy and even hybrid ones to allow the method to verify and to obtain the optimal sizing of typical rural electrification systems.
+As the focus here was stand-alone solar PV systems, one future work will consider other types of renewable energy and even hybrid ones to allow the method to verify and to obtain the optimal sizing of typical rural electrification systems.
 
@@
 
-\textcolor{red}{It is planned to develop the code of a general-purpose simulation tool, as MATLAB for example, using the same mathematical model employed in our two methods.
-Thus a broader comparison can be made, in order to cover all the possibilities to validate or optimize solar PV systems.}
+We plan to develop the code of a general-purpose simulation tool, like MATLAB, for example, using the same mathematical model employed in our two methods.
+Thus a broader comparison can be made in order to cover all the possibilities to validate or optimize solar PV systems.
 
@@
 
-\textcolor{red}{The automated verification and automates synthesis methods demonstrate the effectiveness and the potential of use in stand-alone solar PV systems.
-Some issues must be addressed in order to improve the tools, as performance and the human-computer interaction.}.
+The automated verification and automates synthesis methods demonstrate the effectiveness and the potential of use in stand-alone solar PV systems.
+We must address some issues in order to improve the tools, as performance and the human-computer interaction.
 
-\textcolor{red}{About license and the use of tools mentioned in this thesis, must be noticed that HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}.
+About license and the use of tools mentioned in this thesis, note that HOMER Pro is available only for Microsoft Windows, and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}.
 Related to the verifiers, as CPAchecker, ESBMC and CBMC, and their solvers, they are based on open-source software license and usually allows the users to use, modify, and distribute licensed product freely.
-Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is an advantage when compared to commercial tools).}
+Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is an advantage when compared to commercial tools).
 
-Based on the fact that the tools detailed here have not similarity in past work in the world, can be concluded that it was produced original research that expands the boundaries of knowledge, putting cutting-edge computer science methodologies to solve typical electrical engineering problems and to improve the design of systems.
+The tools we described here have no similarity to any other pior work.
+We can conclude that we have have produced original research that expands the boundaries of knowledge.
+In particular, we have proposed cutting-edge computer science methodologies to solve typical electrical engineering problems and to improve the design of systems.
 
-\textcolor{red}{And last, but not least significant to report, one of the great things about PhD is that the student will be able to conduct its research in the future.
+Moreover, last, but not least significant to report, one of the great things about Ph.D.
+is that the student will be able to conduct its research in the future.
 In that direction, we can say that with the methods proposed here and targeted to tackle the energy sector, there exists a vast field of future applications and developments, using different renewable sources.
 We can mention here biomass, wind, or even hybrid generation, with different mathematical models and requirements; and including smart grids, or electrical systems in general.
-Few research has been done until now, and the scenario is auspicious to do it.}
+Few research has been done until now, and the scenario is auspicious to do it.
 %besides the fact that the goal of a PhD is to contribute to the body of human research,

### 2019-10-29 Tex/Old text/chapters/appendixB.tex
revised appendix B
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+%---------------------------------------
 \section{Tools}
+%---------------------------------------
 
-During the PhD process, the techniques from computer science and proposed to tackle issues related to solar photovoltaic systems became algorithms and codes.
-Those codes became tools, and the tools were used during comparative with simulation tool in order to validate the techniques.
+During the Ph.D.
+process, the techniques from computer science proposed to tackle issues related to solar photovoltaic systems became algorithms and programs.
+Those programs became tools, and the tools were used during comparative with simulation tools in order to validate the techniques.
 
-In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since that we aimed to evaluate different .
+\textcolor{red}{the second part of this sentence is unclear...} In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since we aimed to evaluate different.
 
-We wrote the tools in Language C, without the use of '\# include', or '\# define'.
-Based on the fact that there is no use of compiler library, it was necessary to write some functions which perform specific calculations according to the adopted mathematical models (logarithm of natural order and exponential).
+We wrote the tools in the C programming language, without the use of '\# include', or '\# define'.
+Based on the fact that there exists no use of compiler library, it was necessary to write some functions, which perform specific calculations according to the adopted mathematical models (e.g., logarithm of natural order and exponential).
 
+%---------------------------------------
 \subsection{Automated Verification Tool (PV System validation)}
 \label{sec:automatedverification}
+%---------------------------------------
 
-The code can be divided in four blocks:
+We split the code into four blocks:
 
 \begin{itemize}
-\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and data sheet information from each equipment of the PV system that will be verified;
+\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and datasheet information from each equipment of the PV system that will be verified;
 
-\item \textbf{Block 2}: support functions (logarithm of natural order, exponential);
+\item \textbf{Block 2}: support functions (e.g., logarithm of natural order, exponential);
 
@@
 
-\item \textbf{Block 4}: main code with charge, discharge battery control, based on PV generation from solar panels and the state of charge form batteries, having the commitment to deliver the power and energy that the house demands, according with the restrictions form the sized system.
+\item \textbf{Block 4}: main code with charge, discharge battery control, based on PV generation from solar panels and the state of charge form batteries, committing to deliver the power and energy that the house demands, according with the restrictions form the sized system.
 \end{itemize}
 
+%---------------------------------------
 \subsection{Automated Synthesis Tool (PV System Optimal Sizing)}
 \label{sec:automatedsynthesis}
+%---------------------------------------
 
-The code can be divided in three blocks:
+We split the code into three blocks:
 
 \begin{itemize}
-\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and data sheet information from each equipment of the PV system that will be verified;
+\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and datasheet information from each equipment of the PV system that will be verified;
 
-\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);
+\item \textbf{Block 2}: support functions (start value with the lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);
 
@@
 
+%---------------------------------------
 \section{How to use it}
+%---------------------------------------
 
-The only block that demands user intervention from user in order to input data is the block 1 of both tools.
-If it is aimed to change the mathematical model adopted, so coding must be done in block 3 of automated verification tool and in block 2 of automated synthesis tool.
+The only block that demands user intervention to input data is block 1 of both tools \textcolor{red}{where can I see block 1?
+which tools?}.
+If it is aimed to change the mathematical model adopted, so coding must be done in block 3 of the automated verification tool and block 2 of the automated synthesis tool.
 
@@
 \item Efficiency from batteries;
-\item Float, absorption and bulk battery voltages;
+\item Float, absorption, and bulk battery voltages;
 \item Charge controller efficiency;
@@
 
-And regarding the automated synthesis tool, it is necessary the following data (editing and modifying the code):
+Moreover, regarding the automated synthesis tool, it is necessary to add the following data (editing and modifying the code):
 
@@
 
+%---------------------------------------
 \subsection{Automated Verification with Incremental ESBMC}
+%---------------------------------------
 
-Here we describe specifically how to use the code explained in previous section (\ref{sec:automatedverification}) using the incremental ESBMC with Z3 solver, that presented the better performance during the comparative with other verifiers.
+Here we describe precisely how to use the code explained in the previous section (\ref{sec:automatedverification}) using the incremental ESBMC with the Z3 SMT solver that presented the better performance during the comparative than other verifiers.
 However, in \ref{sec:setup} it was showed how to use the code with other verifiers.
@@
 
-Some results issued by the ESBMC verifier were depicted in \ref{sec:ESBMCverification} when performing the case studies.
+Some results issued by the ESBMC verifier were shown in \ref{sec:ESBMCverification} when performing the case studies.
 
+%---------------------------------------
 \subsection{Automated Synthesis with CPAchecker}
+%---------------------------------------
 
-Here we describe specifically how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, that presented the better performance during the comparative with other verifiers.
+Here we describe precisely how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, which presented better performance during the comparative than other verifiers.
 However, in \ref{sec:synthesissetup} it was showed how to use the code with other verifiers.
@@
 
-Install a Java Runtime Environment which is at least Java 8 compatible (e.g., Oracle JRE, OpenJDK). Cf. the web site \url{http://java.oracle.com/}.
+Install a Java Runtime Environment, which is at least Java 8 compatible (e.g., Oracle JRE, OpenJDK). Cf. the web site \url{http://java.oracle.com/}.
 
@@
 
-Worth to mention that the default heap size is 1200m (or 1.2 GB of RAM), however it is indicated to specify a large value with '-heap' if you have more RAM memory available.
+Note that the default heap size is 1200m (or 1.2 GB of RAM).
+However, it is indicated to specify a significant value with '-heap' if you have more RAM available.
 In our case, we adjusted the heap to 64000m (64 GB).
 
-Other important issue is the time-out of the execution process: the parameter 'limits.time.cpu' at the file 'resource-limits.properties' in folder 'config/includes' must be edited according the desired value.
+Another important issue is the time-out of the execution process: the parameter 'limits.time.cpu' at the file 'resource-limits.properties' in folder 'config/includes' must be edited according to the desired value.
 In our case, 'limits.time.cpu = 14400s', i.e., 14400 seconds or 240 minutes or 4 hours.
 
-Some results, reports and graphics, issued by the CPAchecker verifier were depicted in \ref{sec:synthesisresults}.
+Some results, reports, and graphics, issued by the CPAchecker verifier were depicted in \ref{sec:synthesisresults}.

### 2019-10-29 Tex/Old text/abstract.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2019-10-09 Tex/Old text/abstract.tex
@@
 \end{center}
-With declining costs and increasing performance, the deployment of renewable energy systems is growing faster.
+With declining costs and increasing performance, the deployment of renewable energy systems is now growing faster than in the previous decade.
 In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals.
 Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
-Tools to evaluate or to size electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space.
-In the other hand, the use of formal methods to model and validate any kind the systems is growing with time, mainly to find bugs in complex hardware and software systems: their aim is to establish system correctness with mathematical rigor.
-The use of formal methods in electrical systems is a recent subject, with research being published only in the last four years.
-Moreover, the use of automated synthesis in order to obtain optimal sizing of solar photovoltaic systems was never done before.
-This Thesis marks two mains achievements: (1) the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load; and (2) a sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis, where every component and function of a solar photovoltaic system is described, including its properties, and the behavioral model that represents the optimal sizing can be synthesized automatically.
+Tools to evaluate or to size electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
+However, the use of formal methods to model and validate any system is growing with time, mainly to find bugs in sophisticated hardware and software systems: they aim to establish system correctness with mathematical rigor.
+The use of formal methods in electrical systems is a new subject, with research being published only in the last four years.
+Moreover, the use of automated synthesis in order to obtain the optimal sizing of solar photovoltaic systems was never done before.
+This PhD thesis marks two mains achievements.
+First, the application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load.
+Second, a sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis.
+Here every component and function of a solar photovoltaic system is described, including its properties and the behavioral model that represents the optimal sizing.
 Related to formal verification, case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, are used to evaluate the proposed approach and to compare that with specialized simulation tool.
-Different verification tools are evaluated as well, in order to compare performance and soundness.
+Different verification tools are evaluated as well in order to compare performance and soundness.
 Data from practical applications show the effectiveness of our proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
-Moreover, related to the use of program synthesis, we propose a variant of counterexample guided inductive synthesis (CEGIS) approach, with two phases linking the technical and cost analysis: first we synthesize a feasible candidate based on power reliability, but that may not achieve the lowest cost; second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
-If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample provides the optimal solution.
+Moreover, concerning the use of program synthesis, we propose a variant of counterexample guided inductive synthesis (CEGIS) approach.
+This variant has two phases linking the technical and cost analysis.
+First, we synthesize a feasible candidate based on power reliability, but that may not achieve the lowest cost.
+Second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
+If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution.
 The proposed synthesis method is novel and unprecedented to streamline the design of photovoltaic systems.
-Experimental results using seven case studies and commercial equipment data show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
+Experimental results using seven case studies and financial equipment data show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
 We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which can provide a more detailed and accurate solution than that simulation tool.
 
-\textit{Keywords}: Formal verification; automated verification; model checking; program synthesis; electrical systems; solar photovoltaic systems
+\textit{Keywords}: Formal verification; automated verification; model checking; program synthesis; electrical systems; and solar photovoltaic systems.

### 2019-10-29 Tex/Old text/chapters/introduction.tex
Revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%automated verification
+\textcolor{red}{What is the relation between CPS and PV? We should make it clear already in the beginning...}
 Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19}.
-During operation, such components must frequently adapt to the operating environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
+During operation, such components must frequently adapt to the operating environment changes (dynamics of the physical processes) faced at run-time.
+They must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
 Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
@@
 While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
-Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing \textit{correct-by-construction} implementations of CPS.
-These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
-In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
+Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis to synthesize \textit{correct-by-construction} implementations of CPS.
+These techniques need to deal with predefined requirements enforced by nature and inherited constraints of the target CPS.
+Besides, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
 Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
@@
 The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
-Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}.
+Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million people until 2023~\cite{EPE2018}.
 Furthermore, there exists a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
@@
 The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development~\cite{Yatimi}.
-The renewable energy leads to an advance all over the world by protecting the environment: it is clean (low greenhouse gases emissions), operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}.
+The renewable energy leads to an advance all over the world by protecting the environment: it is clean (low greenhouse gas emissions), operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible~\cite{Noroozian}.
 Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
 
-Among the options of renewable sources, there are hydro, wind, and solar PV.
-According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
+Among the options of renewable sources, there exist hydro, wind, and solar PV.
+According to~\cite{SEIA} and~\cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
 In solar PV systems, solar radiations are captured from the sun and turned into electricity using solar PV cells made of silicon and other materials.
@@
 
-In other hand, aiming to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.
+However, in order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed.
+Grid extension will be the standard, especially in urban areas~\cite{IEAweo2018}.
 
-The PV cell in a solar PV system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy.
-Apart from PV modules; the PV systems consist of battery bank, controller, and inverter, plus the load.
+The PV cell in a solar PV system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts solar radiation into electrical energy.
+Apart from PV modules, the PV systems consist of a battery bank, controller, and inverter, plus the load.
 %The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
@@
 
-The increase in a number of PV systems installed all over the world brings the need for proper modeling of those equipment and simulation tools for researcher and practitioners involved in their application.
+The increase in the number of PV systems installed all over the world brings the need for proper modeling of those equipment and simulation tools for researchers and practitioners involved in their application.
 
-Moreover, the optimum sizing of these devices is important for reliable operation.
-Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}.
+Moreover, the optimum sizing of these devices is essential for reliable operation.
+Therefore, these systems need to be appropriately designed according to the site, the land area available, load requirement, load pattern, environmental conditions, and economics in order to utilize available resources efficiently and economically~\cite{Rawat}.
 
@@
 
-In order to address different aspects of a solar PV project, there exists a myriad of public domain and commercial software available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization).
-Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
+In order to address different aspects of a solar PV project, there exists a myriad of public domain and commercial software available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general-purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+According to~\cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation to site survey and system design tools, to sophisticated financial analysis software (with optimization).
+Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
 %
-Manufactures and integrators have yet their proprietary software to perform various system sizing\textcolor{red}{~\cite{Zhou2010}}, with the drawback of including just their own products among the possibilities of choice, which restricts their solution.
+Manufactures and integrators have yet their proprietary software to perform various system sizing~\cite{Zhou2010}, with the drawback of including just their products among the possibilities of choice, which restricts their solution.
 %
@@
 The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-However, \textcolor{red}{public domain and commercial software or even proprietary tools are based on running experiments in simulation models}.
-Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded, but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+However, public domain and commercial software or even proprietary tools are based on running experiments in simulation models.
+Simulation has the advantage of being cheap (if compared to testing in real systems) and can be employed before the system design is concluded.
+However, it has the drawback of an incomplete coverage since the verification of all possible combinations, and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
-Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}, including for example applications to CPS~\cite{Abateetal2017,AbateBCCDKK17,Bessa,ChavesBCKF17}, with behavior that is, in principle, well determined.
+Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}, including, for example, applications to CPS~\cite{Abateetal2017,AbateBCCDKK17,Bessa,ChavesBCKF17}, with behavior that is, in principle, well determined.
 Any system type can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification~\cite{DBLP:journals/sttt/GadelhaIC17}.
@@
 %
-This research area is referred as formal methods~\cite{Clarkeetal}, which aim to establish system correctness with mathematical rigor. 
-In the recent decades, research in formal methods has led to the development of very promising verification techniques that facilitate the early detection of flaws in order to ensure the correctness of the system, including programming languages such as C/C++ and Java~\cite{esbmc2018,RamalhoFSMC013,CordeiroKKST18}.
+This research area is referred to as formal methods~\cite{Clarkeetal}, which aim to establish system correctness with mathematical rigor. 
+In recent decades, research in formal methods has led to the development of up-and-coming verification techniques that facilitate the early detection of flaws in order to ensure the correctness of the system, including programming languages such as C/C++ and Java~\cite{esbmc2018,RamalhoFSMC013,CordeiroKKST18}.
 
-Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner.
-Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade,TrindadeDJISC17}.
-Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
+Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise, and unambiguous manner.
+Thus, such problems as incompleteness, ambiguities, and inconsistencies, which generally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade,TrindadeDJISC17}.
+Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the given system meets the requirements.
 %
@@
 %automated synthesis
-However, optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were developed and evaluated~\cite{Applasamy2011}.
+However, optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods were developed and evaluated~\cite{Applasamy2011}.
 An ideal combination of any PV system is made by the best compromise between two considered objectives, which is \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.
 
-However, formal methods based on \textit{symbolic model checking} and its application 
-to synthesize PV systems have not been further explored in literature, which could offer 
-a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
+However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored in literature, which could offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
 
@@
 
-\textcolor{red}{The main objective of this thesis is thus to propose and evaluate the use of formal methods in solar PV systems, using a computer science method to solve a specific issues of the electrical engineering area.
-In particular, we focus on automated verification by model checking, on stand-alone solar PV systems that is most adequate to rural areas of developing countries, on the need to validate and optimize those systems, on evaluating different state-of-art symbolic software verifiers (and solvers) with the goal of obtaining the best performance in our verification back-end, on applications written in ANSI-C that are platform-independent; and we do not perform code modification on the verifiers or solvers, we use it as available by their developers.
-We further evaluate our proposed solution by comparative with commercial simulation tool and by data collected from real PV systems deployed at riverside communities.}
+The main objective of this thesis is thus to propose and evaluate the use of formal methods in solar PV systems, using a computer science method to solve specific issues of the electrical engineering area.
+\textcolor{red}{This sentence is too long and unclear...} In particular, we focus on automated verification by model checking, on stand-alone solar PV systems that is most adequate to rural areas of developing countries, on the need to validate and optimize those systems, on evaluating different state-of-art symbolic software verifiers (and solvers) with the goal of obtaining the best performance in our verification back-end, on applications written in ANSI-C that are platform-independent; and we do not perform code modification on the verifiers or solvers, we use it as available by their developers.
+We further evaluate our proposed solution by comparative with commercial simulation tool and by data collected from real PV systems deployed at riverside communities.
 %More specifically we will:
@@
 
-This PhD thesis has the novelty of applying automated verification method to solar PV systems.
-The result is the development of two software: one to perform automated verification and validate the solar PV systems behavior; and another one to produce the optimal sizing of solar PV systems through automated synthesis program.
+\textcolor{red}{A PhD thesis is not simply the application of methods and development of tools. Please rephrase this sentence.}
+This Ph.D.
+thesis has the novelty of applying automated verification method to solar PV systems.
+The result is the development of two software: one to perform automated verification and validate the solar PV systems behavior, and another one to produce the optimal sizing of solar PV systems through automated synthesis program.
 
-Related to \textbf{automated verification}, in this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used.
+In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used for formal verification.
 The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
@@
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
+\textcolor{red}{This paragraph is too long and unclear...}
 The implementation of the proposed tool is carried out by means of an algorithm implemented using the C programming language, which is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
@@
 
-Related to \textbf{automated synthesis} method and the optimal sizing of stand-alone PV systems, this Thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input.
-Given a correctness specification $\sigma$, the proposed method uses that as starting point 
-and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
-related to power reliability. In particular, in each iteration, we synthesize sizing of 
-stand-alone PV systems but that may not achieve the lowest cost. The candidate solution 
-is then verified via symbolic model checking with a lower bound that serves as the minimum 
-cost of reference; if the verification step does not fail, the lower bound is adjusted. 
-If it fails then a counterexample is provided with an optimal sizing that meets 
-power reliability and system cost.
-Note that in this study, the focus is not on a novel criteria or even optimization objectives.
-Instead, the novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
+Related to \textbf{automated synthesis} method and the optimal sizing of stand-alone PV systems, this thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input.
+Given a correctness specification $\sigma$, the proposed method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
+In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
+The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted.
+If it fails, then a counterexample is provided with an optimal sizing that meets power reliability and system cost.
+Note that in this study, the focus is not on new criteria or even optimization objectives.
+Instead, the novelty relies on a practical approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
 
@@
 
-\textcolor{red}{Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system and optimal sizing.
+Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system and optimal sizing.
 Validation when a sized system must be evaluated in order to define if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or then the user tries to obtain a better solution that he or she has.
-We thus develop algorithms and the corresponding tools, moreover we evaluate them using comparative process in several case studies with specialized simulation tool and real data from deployed PV systems.}
+We thus develop algorithms and the corresponding tools; moreover, we evaluate them using a comparative process \textcolor{red}{what do you mean by a ``comparative process''?} in several case studies with specialized simulation tools and real data from deployed PV systems.
 
-\textcolor{red}{Fig.\ref{fig:validation_outline} outlines the proposed solution to perform the validation of stand-alone solar PV systems via automated verification.
-And Fig.\ref{fig:optimization_outline} illustrates the proposed solution to obtain the optimal sizing of stand-alone solar PV systems via automated synthesis.
-We pictured here only a summary of each phase of our proposed approach, with highlights to the input parameters, the outputs for the validation or the optimal size of solar PV system; more details are presented in the next chapters.
-Moreover, the illustrations show the methodological approach related to comparative result analysis, employing our approaches, commercial software tool and data from real PV systems deployed at the field.}
+Fig.\ref{fig:validation_outline} outlines the proposed solution to perform the validation of stand-alone solar PV systems via automated verification.
+Fig.\ref{fig:optimization_outline} illustrates the proposed solution to obtain the optimal sizing of stand-alone solar PV systems via automated synthesis.
+We pictured here only a summary of each phase of our proposed approach, with highlights to the input parameters, the outputs for the validation, or the optimal size of the solar PV system; more details are presented in the next chapters.
+Moreover, the illustrations show the methodological approach related to comparative result analysis, employing our approaches, commercial software tool, and data from real PV systems deployed in the field.
 
@@
 
-Worth to mention that is out of our scope to perform code modification on the verifiers or the solvers used during the automated verification or automated synthesis steps of our approach.
+Note that it is out of our scope to perform code modification on the verifiers or the solvers used during the automated verification or automated synthesis steps of our approach.
+\textcolor{red}{why is it out of scope?
+You need to explain here.}
 
@@
 
-Associated to \textbf{automated verification}, this thesis makes three main contributions.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
 Secondly
-\textbf{Firstly}, we propose an algorithm written in the C programming language, which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system.
-\textbf{Secondly}, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies. 
-\textbf{Thirdly}, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation. 
+
+\textcolor{red}{The beginning of this sentence is weird...}
+Associated with \textbf{automated verification}, this thesis makes three main contributions. 
+\textbf{First}, we propose an algorithm written in the C programming language, which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system.
+\textbf{Second}, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies. 
+\textbf{Third}, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation. 
 %
@@
 
+\textcolor{red}{The second and third contributions are long and tough to read. I don't understand them.}
 And linked to \textbf{automated synthesis}, our work makes more three original contributions: \textbf{First}, it is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems;
@@
 
-The conversion of traditional power grid into a smart grid, a fundamental example of a CPS, 
-raises a number of issues that requires novel methods and applications.
+The conversion of the traditional power grid into a smart grid, a fundamental example of a CPS, raises many issues that require novel methods and applications.
 In $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
 The authors employed a stochastic model checking approach and presented a modeling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
-The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here, the authors employed automated verification of certain quantitative properties of the system, as probability of	 node failure in the long run, impact of repair service on the failure risk, and expected energy consumption, without any interest in power generation or even solar PV systems.
+\textcolor{red}{This sentence is too long...} The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here, the authors employed automated verification of certain quantitative properties of the system, as probability of node failure in the long run, impact of repair service on the failure risk, and expected energy consumption, without any interest in power generation or even solar PV systems.
 
 In $2015$, an automated approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
-The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
-The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
+The authors proposed an automated simulation-based verification technique to verify the correctness of protection settings efficiently using a hybrid automata-temporal-logic framework.
+The initial focus was on relay operations and test-case generation to ensure the early detection of design errors.
 However, this study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
@@
 Other related studies from $2015$ include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis using statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
-In order to demonstrate Modana's capability, the authors modeled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+In order to demonstrate Modana's capability, the authors modeled energy-aware buildings as a case study and discussed the analysis of energy consumption in different scenarios.
 The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
-This research, however, did no address the design and verification of solar PV systems.
+This research, however, did not address the design and verification of solar PV systems.
 
 In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices, interacting over a shared and smart infrastructure~\cite{Abate2017}.
-The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The author discussed the aggregation of large populations of thermostatically-controlled loads and PV panels, and the similar problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
 The focus was on controlling the behavior of components, thereby verifying the given smart grid as a ``system of systems'' within the context of "internet of things".
-The author, however, used approximate model checking of stochastic and hybrid models.
+The author, however, used an approximate model checking of stochastic and hybrid models.
 
-In $2018$, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
+In $2018$, a verification methodology was proposed for the Cyber-Physical Energy Systems (CPES) with applications to PV panels and its distributed powerpoint tracking~\cite{Driouich2018}.
+This approach relied on representing the unpredictable behavior of the environment to cover all possible feasible scenarios.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time-consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
 This related study did not include other components of a stand-alone solar PV system.
@@
 The presented formal specification can be considered as a first step towards modeling of smart grids using formal methods.
-The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
-This approach is based on Petri nets and is under the assumption that modeling the smart home leads to clear understanding of the overall behavior of the smart grid.
+The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and systems, which communicates and interacts with each other.
+This approach is based on Petri nets and is under the assumption that modeling the smart home leads to a clear understanding of the overall behavior of the smart grid.
 
-\textcolor{red}{However, prior studies did not deal with formal verification of a complete stand-alone PV system (with batteries, charge controller, and power inverter) or even solar PV systems optimization.
+However, prior studies did not deal with formal verification of a complete stand-alone PV system (with batteries, charge controller, and power inverter) or even solar PV systems optimization.
 Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in literature.
-And it is exactly in those gaps that this thesis focuses.}
+Moreover, it is precisely in those gaps that this thesis focuses on.
 
@@
 
-\textcolor{red}{This introduction has outlined the context, motivation, and problem addressed by this thesis, and the objectives, solution and contributions of the research.
-The remainder of the chapters of this thesis are organized as follows:}
+This introduction has outlined the context, motivation, and problem addressed by this thesis and the objectives, solution, and contributions of the research.
+The remainder of the chapters of this thesis are organized as follows:
 
-% ~\nameref or \autoref{
 Chapter '~\nameref{chap:background}' gives the theoretical basis on formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.
@@
 
-Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science and its application to obtain the optimal sizing of stand-alone solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collect from fieldwork.
+Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science and its application to obtain the optimal sizing of stand-alone solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collected from fieldwork.
 
@@
 
+\textcolor{red}{This sentence is unclear...}
 ~\autoref{chap:publications} presents a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.

### 2019-10-29 Tex/Old text/chapters/introduction.tex
added citation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \textcolor{red}{What is the relation between CPS and PV? We should make it clear already in the beginning...}
-Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19}.
+Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19,iet-cps.2018.5006}.
 During operation, such components must frequently adapt to the operating environment changes (dynamics of the physical processes) faced at run-time.

### 2019-10-29 Tex/Old text/abstract.tex
Thesis update

@@
 Moreover, the use of automated synthesis in order to obtain the optimal sizing of solar photovoltaic systems was never done before.
-This PhD thesis marks two mains achievements.
+This Ph.D.
+thesis marks two mains achievements.
 First, the application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load.
 Second, a sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis.
-Here every component and function of a solar photovoltaic system is described, including its properties and the behavioral model that represents the optimal sizing.
-Related to formal verification, case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, are used to evaluate the proposed approach and to compare that with specialized simulation tool.
+Related to formal verification, we used case studies from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, in order to evaluate the proposed approach and to compare that with specialized simulation tool.
 Different verification tools are evaluated as well in order to compare performance and soundness.
@@
 The proposed synthesis method is novel and unprecedented to streamline the design of photovoltaic systems.
-Experimental results using seven case studies and financial equipment data show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
+Experimental results using seven case studies show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
 We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which can provide a more detailed and accurate solution than that simulation tool.

### 2019-10-29 Tex/Old text/chapters/appendixB.tex
Thesis update

@@
 
-\textcolor{red}{the second part of this sentence is unclear...} In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since we aimed to evaluate different.
+One premise of our tools was to be written as an ANSI C program, and to follow the requirements established for the International Competition on Software Verification (SV-COMP) \footnote{https://sv-comp.sosy-lab.org/}.
+That allow us to write a code that could be executed into three different verifiers without adaptation, and even in the future other verifiers can be used as well.
+%
+%\textcolor{red}{the second part of this sentence is unclear...} In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since we aimed to evaluate different.
 
-We wrote the tools in the C programming language, without the use of '\# include', or '\# define'.
-Based on the fact that there exists no use of compiler library, it was necessary to write some functions, which perform specific calculations according to the adopted mathematical models (e.g., logarithm of natural order and exponential).
+Therefore, we wrote the code without the use of '\# include', or '\# define'.
+Moreover, based on the fact that there exists no use of compiler library, it was necessary to write some functions, which perform specific calculations according to the adopted mathematical models (e.g., logarithm of natural order and exponential).
 
@@
 
-The only block that demands user intervention to input data is block 1 of both tools \textcolor{red}{where can I see block 1?
-which tools?}.
+The only block that demands user intervention to input data is the block 1 listed in~\ref{sec:automatedverification} and \ref{sec:automatedsynthesis} from the automated verification and synthesis tools respectively.
 If it is aimed to change the mathematical model adopted, so coding must be done in block 3 of the automated verification tool and block 2 of the automated synthesis tool.

### 2019-10-29 Tex/Old text/chapters/introduction.tex
Thesis update

--- 2019-10-29 Tex/Old text/chapters/introduction.tex
@@
-%%automated verification
-\textcolor{red}{What is the relation between CPS and PV? We should make it clear already in the beginning...}
-Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19}.
+%\textcolor{red}{What is the relation between CPS and PV? We should make it clear already in the beginning...}
+\textcolor{red}{Energy production, distribution, and optimization are all Cyber-Physical Systems (CPS) problems~\cite{UC}}.
+CPS are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19,iet-cps.2018.5006}.
 During operation, such components must frequently adapt to the operating environment changes (dynamics of the physical processes) faced at run-time.
@@
 Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
-Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
 
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+\textcolor{red}{Moving into the myriad of CPS systems, in this thesis we focus specifically on energy.} Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
 Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
@@
 
-The main objective of this thesis is thus to propose and evaluate the use of formal methods in solar PV systems, using a computer science method to solve specific issues of the electrical engineering area.
-\textcolor{red}{This sentence is too long and unclear...} In particular, we focus on automated verification by model checking, on stand-alone solar PV systems that is most adequate to rural areas of developing countries, on the need to validate and optimize those systems, on evaluating different state-of-art symbolic software verifiers (and solvers) with the goal of obtaining the best performance in our verification back-end, on applications written in ANSI-C that are platform-independent; and we do not perform code modification on the verifiers or solvers, we use it as available by their developers.
-We further evaluate our proposed solution by comparative with commercial simulation tool and by data collected from real PV systems deployed at riverside communities.
+\textcolor{red}{The main objective of this thesis is thus to create a new approach of formal methods and evaluate it as an alternative to solve research issues from solar PV systems.
+We therefore foster the use of specific computer science techniques to tackle specific issues of PV systems, as design validation and sizing optimization.
+In particular, we focus on automated verification and automated synthesis.
+Secondarily, we focus on: evaluating different state-of-art symbolic software verifiers (and solvers) with the goal of obtaining the best performance in our verification back-end; on applications written in ANSI-C that are platform-independent.
+%; and we do not perform code modification on the verifiers or solvers, we use it as available by their developers.
+We further evaluate our proposed solution by comparative with commercial simulation tool and by data collected from real PV systems deployed at riverside communities.}
+
 %More specifically we will:
@@
 
-\textcolor{red}{A PhD thesis is not simply the application of methods and development of tools. Please rephrase this sentence.}
-This Ph.D.
-thesis has the novelty of applying automated verification method to solar PV systems.
-The result is the development of two software: one to perform automated verification and validate the solar PV systems behavior, and another one to produce the optimal sizing of solar PV systems through automated synthesis program.
+\textcolor{red}{This Ph.D.
+thesis has the novelty of create an automated verification approach to solar PV systems.
+The research led to the creation of two software to carry out computational experiments and to compare with commercial tools and real data from systems installed in the field.
+One software to perform automated verification and validate the solar PV systems behavior, and another one to produce the optimal sizing of solar PV systems through automated synthesis program.}
 
@@
 %Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
-\textcolor{red}{This paragraph is too long and unclear...}
-The implementation of the proposed tool is carried out by means of an algorithm implemented using the C programming language, which is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
+
+\textcolor{red}{The implementation of the proposed method is carried out by means of an algorithm implemented using the C programming language.
+We performed computing experimentation in three state-of-the-art model checkers to formally verify PV designs, aiming to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).}
 %three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
@@
 Validation when a sized system must be evaluated in order to define if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or then the user tries to obtain a better solution that he or she has.
-We thus develop algorithms and the corresponding tools; moreover, we evaluate them using a comparative process \textcolor{red}{what do you mean by a ``comparative process''?} in several case studies with specialized simulation tools and real data from deployed PV systems.
+\textcolor{red}{We thus develop algorithms and the corresponding tools; moreover, we evaluate them with several case studies, in a comparative with specialized simulation tools, supported by real data from deployed PV systems.}
 
@@
 Note that it is out of our scope to perform code modification on the verifiers or the solvers used during the automated verification or automated synthesis steps of our approach.
-\textcolor{red}{why is it out of scope?
-You need to explain here.}
+\textcolor{red}{This thesis intend to create front-end applications to the verifiers and solvers (that it will be the back-end).
+That decision is based on the fact that we can be verifier-independent, and evaluate different back-ends, now and in the future, always searching for the best performance and soundness.}
 
@@
 
-\textcolor{red}{The beginning of this sentence is weird...}
-Associated with \textbf{automated verification}, this thesis makes three main contributions. 
+\textcolor{red}{Related with the proposed \textbf{automated verification} method, this thesis makes three main contributions.}
 \textbf{First}, we propose an algorithm written in the C programming language, which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system.
@@
 
-\textcolor{red}{The second and third contributions are long and tough to read. I don't understand them.}
 And linked to \textbf{automated synthesis}, our work makes more three original contributions: \textbf{First}, it is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems;
-\textbf{Secondly}, we propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop to reach the optimal cost solution of the system; and
-\textbf{Thirdly}, experimental results with seven case studies show that formal synthesis approach qualitatively outperforms an existing state-of-the-art simulation tool.
-Our solution is far detailed and closer to the commercial reality (real PV systems) than the solution presented by simulation.
+\textcolor{red}{\textbf{Secondly}, we propose a variant CEGIS method of synthesis with striking differences of how the {\sc Synthesize} and {\sc Verify} phases from original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and }
+\textcolor{red}{\textbf{Thirdly}, experimental results with seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tool: our solution is far detailed and closer to real PV systems than the solution presented by simulation.}
 
@@
 The authors employed a stochastic model checking approach and presented a modeling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
-\textcolor{red}{This sentence is too long...} The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here, the authors employed automated verification of certain quantitative properties of the system, as probability of node failure in the long run, impact of repair service on the failure risk, and expected energy consumption, without any interest in power generation or even solar PV systems.
+\textcolor{red}{The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes.
+The authors did not focus on power generation or even solar PV systems.}
 
@@
 
-\textcolor{red}{This sentence is unclear...}
-~\autoref{chap:publications} presents a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.
+\textcolor{red}{~\autoref{chap:publications} presents a list of papers that we submitted to international journals and conference related to the use of automated verification method.
+It covers the years from 2015 to 2019, related to the Ph.D.
+process.}
 

### 2019-10-30 Tex/Old text/chapters/introduction.tex
Thesis update

@@
 %\textcolor{red}{What is the relation between CPS and PV? We should make it clear already in the beginning...}
-\textcolor{red}{Energy production, distribution, and optimization are all Cyber-Physical Systems (CPS) problems~\cite{UC}}.
+Energy production, distribution, and optimization are all Cyber-Physical Systems (CPS) problems~\cite{UC}.
 CPS are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19,iet-cps.2018.5006}.
@@
 
-\textcolor{red}{Moving into the myriad of CPS systems, in this thesis we focus specifically on energy.} Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+Among the myriad of CPS systems, in this thesis we focus specifically on energy generation by stand-alone solar PV systems.
+Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
 Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
@@
 
-\textcolor{red}{The main objective of this thesis is thus to create a new approach of formal methods and evaluate it as an alternative to solve research issues from solar PV systems.
+The main objective of this thesis is thus to create a new approach of formal methods and evaluate it as an alternative to solve research issues from solar PV systems.
 We therefore foster the use of specific computer science techniques to tackle specific issues of PV systems, as design validation and sizing optimization.
@@
 %; and we do not perform code modification on the verifiers or solvers, we use it as available by their developers.
-We further evaluate our proposed solution by comparative with commercial simulation tool and by data collected from real PV systems deployed at riverside communities.}
+We further evaluate our proposed solution by comparative with commercial simulation tool and by data collected from real PV systems deployed at riverside communities.
 
@@
 
-\textcolor{red}{This Ph.D.
+This Ph.D.
 thesis has the novelty of create an automated verification approach to solar PV systems.
 The research led to the creation of two software to carry out computational experiments and to compare with commercial tools and real data from systems installed in the field.
-One software to perform automated verification and validate the solar PV systems behavior, and another one to produce the optimal sizing of solar PV systems through automated synthesis program.}
+One software to perform automated verification and validate the solar PV systems behavior, and another one to produce the optimal sizing of solar PV systems through automated synthesis program.
 
@@
 
-\textcolor{red}{The implementation of the proposed method is carried out by means of an algorithm implemented using the C programming language.
-We performed computing experimentation in three state-of-the-art model checkers to formally verify PV designs, aiming to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).}
+The implementation of the proposed method is carried out by means of an algorithm implemented using the C programming language.
+We performed computing experimentation in three state-of-the-art model checkers to formally verify PV designs, aiming to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
 %three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
@@
 Validation when a sized system must be evaluated in order to define if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or then the user tries to obtain a better solution that he or she has.
-\textcolor{red}{We thus develop algorithms and the corresponding tools; moreover, we evaluate them with several case studies, in a comparative with specialized simulation tools, supported by real data from deployed PV systems.}
+We thus develop algorithms and the corresponding tools; moreover, we evaluate them with several case studies, in a comparative with specialized simulation tools, supported by real data from deployed PV systems.
 
@@
 Note that it is out of our scope to perform code modification on the verifiers or the solvers used during the automated verification or automated synthesis steps of our approach.
-\textcolor{red}{This thesis intend to create front-end applications to the verifiers and solvers (that it will be the back-end).
-That decision is based on the fact that we can be verifier-independent, and evaluate different back-ends, now and in the future, always searching for the best performance and soundness.}
+This thesis intend to create front-end applications to the verifiers and solvers (that it will be the back-end).
+That decision is based on the fact that we can be verifier-independent, and evaluate different back-ends, now and in the future, always searching for the best performance and soundness.
 
@@
 
-\textcolor{red}{Related with the proposed \textbf{automated verification} method, this thesis makes three main contributions.}
+Related with the proposed \textbf{automated verification} method, this thesis makes three main contributions. 
 \textbf{First}, we propose an algorithm written in the C programming language, which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system.
@@
 And linked to \textbf{automated synthesis}, our work makes more three original contributions: \textbf{First}, it is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems;
-\textcolor{red}{\textbf{Secondly}, we propose a variant CEGIS method of synthesis with striking differences of how the {\sc Synthesize} and {\sc Verify} phases from original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and }
-\textcolor{red}{\textbf{Thirdly}, experimental results with seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tool: our solution is far detailed and closer to real PV systems than the solution presented by simulation.}
+\textbf{Secondly}, we propose a variant CEGIS method of synthesis with striking differences of how the {\sc Synthesize} and {\sc Verify} phases from original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and
+\textbf{Thirdly}, experimental results with seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tool: our solution is far detailed and closer to real PV systems than the solution presented by simulation.
 
@@
 The authors employed a stochastic model checking approach and presented a modeling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
-\textcolor{red}{The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes.
-The authors did not focus on power generation or even solar PV systems.}
+The focus of this study was on how CPSs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes.
+The authors did not focus on power generation or even solar PV systems.
 
@@
 
-\textcolor{red}{~\autoref{chap:publications} presents a list of papers that we submitted to international journals and conference related to the use of automated verification method.
+~\autoref{chap:publications} presents a list of papers that we submitted to international journals and conference related to the use of automated verification method.
 It covers the years from 2015 to 2019, related to the Ph.D.
-process.}
+process.
 

### 2019-11-29 Tex/Old text/chapters/introduction.tex
Thesis update

@@
 ~\autoref{chap:tools} depicts the tools created during the PhD process to implement and validate the two scientific methods of the thesis (and how to use it).
+
+It is worth mentioning that we decided, in agreement and with the consent of the coordination of the postgraduate program, that this document would be written in active voice and entirely in English.
+The choice of the passive voice comes from the choice of the English language, which in the studied thesis always always presented in active voice.
+On the other hand, the choice of language comes from the possibility that the research may lead to further developments and activities, without the need for translation.

### 2019-12-04 Tex/Old text/fichacatalog.tex
thesis updated text
Thesis update

@@
 \thispagestyle{plain}
-\begin{center}
+%\begin{center}
 %    \Large
@@
 %    
-    \vspace{0.9cm}
-    \textbf{Ficha Catalográfica}
+%    \vspace{0.9cm}
+%    \textbf{Ficha Catalográfica elaborada por Suely O. Moraes - CRB 11/365}
+%\end{center}
+%
+%
+\thispagestyle{empty}
+\null\vfill
+
+\begin{center}
+Ficha Catalográfica elaborada por Suely Oliveira Moraes – CRB 11/365
+\begin{tabular}{|p{14.5cm}|}%{p{12cm}}
+\hline
+\begin{small}
+\begin{verbatim}
+       Trindade, Alessandro Bezerra.
+T833a     Automated verification of stand-alone solar photovoltaic 
+       systems: optimal sizing and project validation / Alessandro 
+       Bezerra Trindade. Manaus: UFAM, 2019.
+
+         121 fl.: il.: 21 cm
+
+         Orientador: Prof. PhD. Lucas Carvalho Cordeiro
+
+         Tese (Doutorado em Informática) - Universidade Federal do
+       Amazonas, Programa de Pós-Graduação em Informática.
+
+         1. Verificação formal. 2. Model checking. 3. Sistemas solares
+       fotovoltaicos I. Cordeiro, Lucas Carvalho (Orient.) II. 
+       Universidade Federal do Amazonas. III. Título.
+
+                                               CDU 004.02:621.31(043.2)
+\end{verbatim}
+\end{small}
+\\ \hline
+\end{tabular}
 \end{center}
+
 \thispagestyle{plain}
-Ficha catalog aqui

### 2019-12-05 Tex/Old text/resumo.tex
Thesis update

@@
 Além disso, o uso de síntese automatizada para obter um ótimo dimensionamento de sistemas solares fotovoltaicos nunca foi feito antes.
-Esta tese marca duas conquistas principais: (1) a primeira aplicação de modelagem de software para verificar o projeto de um sistema isolado solar fotovoltaico, incluindo painel solar, controlador de carga, bateria, inversor e carga elétrica; e (2) uma abordagem confiável e automatizada para obter o dimensionamento ótimo de sistemas fotovoltaicos usando a síntese de programas, onde cada componente e função de um sistema solar fotovoltaico é descrito, incluindo suas propriedades, e o modelo comportamental que representa o dimensionamento ótimo é sintetizado automaticamente.
+Esta tese marca duas conquistas principais: (1) a primeira aplicação de verificação de modelos de software para verificar o projeto de um sistema isolado solar fotovoltaico, incluindo painel solar, controlador de carga, bateria, inversor e carga elétrica; e (2) uma abordagem confiável e automatizada para obter o dimensionamento ótimo de sistemas fotovoltaicos usando a síntese de programas, onde cada componente e função de um sistema solar fotovoltaico é descrito, incluindo suas propriedades, e o modelo comportamental que representa o dimensionamento ótimo é sintetizado automaticamente.
 Relacionado a verificação formal, estudos de caso de sistemas fotovoltaicos reais instalados em cinco localidades diferentes são usados para avaliar a abordagem proposta e para compará-la com ferramenta de simulação especializada.

### 2019-12-28 Tex/Old text/abstract.tex
Thesis update

@@
 \end{center}
-With declining costs and increasing performance, the deployment of renewable energy systems is now growing faster than in the previous decade.
-In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals.
+With decreasing costs and increasing performance, the deployment of renewable energy systems is now growing faster now than in the past decade.
+In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends in energy access still fall short of global goals.
 Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
 Tools to evaluate or to size electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-However, the use of formal methods to model and validate any system is growing with time, mainly to find bugs in sophisticated hardware and software systems: they aim to establish system correctness with mathematical rigor.
-The use of formal methods in electrical systems is a new subject, with research being published only in the last four years.
-Moreover, the use of automated synthesis in order to obtain the optimal sizing of solar photovoltaic systems was never done before.
-This Ph.D.
-thesis marks two mains achievements.
-First, the application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load.
-Second, a sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis.
-Related to formal verification, we used case studies from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, in order to evaluate the proposed approach and to compare that with specialized simulation tool.
-Different verification tools are evaluated as well in order to compare performance and soundness.
-Data from practical applications show the effectiveness of our proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
-Moreover, concerning the use of program synthesis, we propose a variant of counterexample guided inductive synthesis (CEGIS) approach.
-This variant has two phases linking the technical and cost analysis.
-First, we synthesize a feasible candidate based on power reliability, but that may not achieve the lowest cost.
+However, the use of formal methods to model and validate any system has grown with time, mainly to find bugs in sophisticated hardware and software systems: they aim to establish system correctness with mathematical rigor.
+The use of formal methods in electrical systems is a new subject, with published research spanning only in the last four years.
+Moreover, the use of automated synthesis in order to obtain the optimal sizing of solar photovoltaic systems has never been done before.
+This thesis marks the achievement of two major goals: first, the application of software model checking to verify formally the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load; second, a sound and automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis.
+For the  formal verification, we used case studies from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, in order to evaluate the proposed approach and to compare it with a specialized simulation tool.
+Different verification tools are evaluated also, in order to compare performance and soundness.
+Data from practical applications show the effectiveness of our proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are detailed only by the automated verification method.
+In addition, for the use of program synthesis, we propose a variant of the counterexample guided inductive synthesis (CEGIS) approach.
+This variant has two phases linking the technical and the cost analysis.
+First, we synthesize a feasible candidate based on power reliability, but which may not attain the lowest cost.
 Second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
 If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution.
-The proposed synthesis method is novel and unprecedented to streamline the design of photovoltaic systems.
-Experimental results using seven case studies show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
-We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which can provide a more detailed and accurate solution than that simulation tool.
+The proposed synthesis method is novel and unprecedented as it streamlines the design of photovoltaic systems.
+Experimental results using seven case studies demonstrate that our synthesis method can produce optimal system sizing within an acceptable run-time.
+We also present a comparison with a specialized simulation tool over real photovoltaic systems in order to show the effectiveness of our approach, which can provide a more detailed and accurate solution than the simulation tool.
 

### 2019-12-28 Tex/Old text/chapters/introduction.tex
Thesis update

--- 2019-10-30 Tex/Old text/chapters/introduction.tex
@@
 Energy production, distribution, and optimization are all Cyber-Physical Systems (CPS) problems~\cite{UC}.
-CPS are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19,iet-cps.2018.5006}.
-During operation, such components must frequently adapt to the operating environment changes (dynamics of the physical processes) faced at run-time.
+CPS are engineered systems, which are built from, and depend on, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19,iet-cps.2018.5006}.
+During operation, these components must frequently adapt to the operating environment changes (dynamics of the physical processes) faced at run-time.
 They must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
-Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
+Software pervasiveness in CPS places new challenges and demands new paradigms for software design, particularly in the face of highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
 
-While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
-Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis to synthesize \textit{correct-by-construction} implementations of CPS.
-These techniques need to deal with predefined requirements enforced by nature and inherited constraints of the target CPS.
-Besides, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
-Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
+While some existing research efforts do aim enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+Among the opportunities for enhancements in the development processes for CPS software, there exists the need to develop new techniques and tools to support CPS requirement gathering and analysis to synthesize \textit{correct-by-construction} implementations of CPS.
+These techniques have to deal with predefined requirements enforced by nature and inherited constraints of the target CPS.
+In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
+Uncertainty and variability, at the same time, can be dealt with by formal verification~\cite{NESSI}.
 
-Among the myriad of CPS systems, in this thesis we focus specifically on energy generation by stand-alone solar PV systems.
+Among the many CPS systems, in this thesis we will focus specifically on energy generation by stand-alone solar PV systems.
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
+Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below the 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
 The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
-Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million people until 2023~\cite{EPE2018}.
-Furthermore, there exists a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
-Therefore, increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
+Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}.
+Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
+It follows that, increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
 
-The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development~\cite{Yatimi}.
-The renewable energy leads to an advance all over the world by protecting the environment: it is clean (low greenhouse gas emissions), operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible~\cite{Noroozian}.
-Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
+The use of the power generation technology with a renewable energy source is developing rapidly due to the industrial development~\cite{Yatimi}.
+Renewable energy leads to advances all over the world by protecting the environment: it is clean (low greenhouse gas emissions), operates silently, long-lasting, low maintenance costs, zero fuel costs and an  inexhaustible supply~\cite{Noroozian}.
+Renewable energy, and particularly power generated from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
 
-Among the options of renewable sources, there exist hydro, wind, and solar PV.
+Renewable sources of energy include hydro, wind, and solar PV.
 According to~\cite{SEIA} and~\cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
-In solar PV systems, solar radiations are captured from the sun and turned into electricity using solar PV cells made of silicon and other materials.
+In solar PV systems, solar radiation is captured from the sun and turned into electricity using solar PV cells made of silicon and other materials.
 
-Only a niche market a few years ago, solar PV systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.
-However, this growth is not driven by stand-alone systems.
+Nothing more than a niche market only a few years ago, solar PV systems have become a mainstream electricity provider, with an  approximate 50\% increase in new PV installations from 2016 to 2017~\cite{EPIA}, although this growth is not driven by stand-alone systems.
 
@@
 
-The PV cell in a solar PV system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts solar radiation into electrical energy.
-Apart from PV modules, the PV systems consist of a battery bank, controller, and inverter, plus the load.
+The PV cell in a solar PV system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts solar radiation directly into electrical energy.
+Apart from the PV modules, the PV systems consist of a battery bank, controller, and inverter, plus the load.
 %The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
@@
 
-The increase in the number of PV systems installed all over the world brings the need for proper modeling of those equipment and simulation tools for researchers and practitioners involved in their application.
+The increase in the number of PV systems installed all over the world underscores the need for proper modeling of the equipment and simulation tools for researchers and practitioners involved in their application.
 
 Moreover, the optimum sizing of these devices is essential for reliable operation.
-Therefore, these systems need to be appropriately designed according to the site, the land area available, load requirement, load pattern, environmental conditions, and economics in order to utilize available resources efficiently and economically~\cite{Rawat}.
+Therefore, these systems need to be designed in accordance with the site, the land area available, load requirement, load pattern, environmental conditions, and economics in order to utilize available resources efficiently and economically~\cite{Rawat}.
 
 %-------------------------------------------------
-\section{Problem's Definition}
+\section{The Problem}
 %-------------------------------------------------
 
-In order to address different aspects of a solar PV project, there exists a myriad of public domain and commercial software available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general-purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
-According to~\cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation to site survey and system design tools, to sophisticated financial analysis software (with optimization).
+In order to address different aspects of a solar PV project, there is a variety of public domain and commercial software solutions  available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general-purpose simulation tools such as PSpice, and the MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+According to~\cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation to site survey and system design tools, and to sophisticated financial analysis software (with optimization).
 Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
 %
-Manufactures and integrators have yet their proprietary software to perform various system sizing~\cite{Zhou2010}, with the drawback of including just their products among the possibilities of choice, which restricts their solution.
+Manufacturers and integrators also have their own proprietary software to perform system sizing~\cite{Zhou2010}, with the drawback of indicating only their own products among the possibilities of choice, which restricts their solution.
 %
@@
 The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.
-However, public domain and commercial software or even proprietary tools are based on running experiments in simulation models.
+However, public domain and commercial software and even proprietary tools are based on running experiments in simulation models.
 Simulation has the advantage of being cheap (if compared to testing in real systems) and can be employed before the system design is concluded.
-However, it has the drawback of an incomplete coverage since the verification of all possible combinations, and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+However, it has the drawback of an incomplete coverage since the verification of all possible combinations, and of potential system failures is unfeasible~\cite{ClarkeHV18}.
 
-Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}, including, for example, applications to CPS~\cite{Abateetal2017,AbateBCCDKK17,Bessa,ChavesBCKF17}, with behavior that is, in principle, well determined.
-Any system type can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification~\cite{DBLP:journals/sttt/GadelhaIC17}.
+Formal methods based on model checking offer a great potential to obtain a faster and more effective verification in the design process~\cite{ClarkeHV18}, including, for example, applications to CPS~\cite{Abateetal2017,AbateBCCDKK17,Bessa,ChavesBCKF17}, with behavior that is, in principle, well determined.
+Any system type can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; one can then try to produce a formal proof or otherwise establish that the program meets its specification~\cite{DBLP:journals/sttt/GadelhaIC17}.
 User or project requirements can be added during the creation of the formal model to be verified~\cite{Trindade,TrindadeDJISC17}.
@@
 
-Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise, and unambiguous manner.
-Thus, such problems as incompleteness, ambiguities, and inconsistencies, which generally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade,TrindadeDJISC17}.
+Model-based verification techniques are based on models that describe possible system behavior in a mathematically precise, and unambiguous manner.
+Thus, problems such as incompleteness, ambiguities, and inconsistencies, which are generally discovered only in the later stages of the design, can be detected in advance, as described by \cite{Trindade,TrindadeDJISC17}.
 Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the given system meets the requirements.
@@
 %automated synthesis
-However, optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods were developed and evaluated~\cite{Applasamy2011}.
-An ideal combination of any PV system is made by the best compromise between two considered objectives, which is \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.
+Optimization of PV systems is not a recent topic; since the $1990$s different techniques have been developed and evaluated using a wide variety of criteria to find the ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods~\cite{Applasamy2011}.
+The ideal combination for  any PV system is made by the best compromise between two considered objectives, which are \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.
 
-However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored in literature, which could offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
+However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored in the literature, which could offer a great opportunity to obtain a more effective design process for PV systems~\cite{ClarkeHV18}.
 
@@
 
-The main objective of this thesis is thus to create a new approach of formal methods and evaluate it as an alternative to solve research issues from solar PV systems.
+The main objective of this dissertation is thus to create a new approach of formal methods and evaluate it as a solution to research issues pertaining to solar PV systems.
+We therefore adopt specific computer science techniques to tackle specific issues of PV systems, such as design validation and sizing optimization.
+In particular, we focus on automated verification and automated synthesis.
+Secondarily, we focus on: evaluating different state-of-the-art symbolic software verifiers (and solvers) with the goal of obtaining the best performance in our verification back-end;  applications written in ANSI-C that are platform-independent.
+We further evaluate our proposed solution comparing it with commercial simulation tools and using data collected from real PV systems deployed in riverside communities.
+%The main objective of this thesis is thus to create a new approach of formal methods and evaluate it as an alternative to solve research issues from solar PV systems.
 We therefore foster the use of specific computer science techniques to tackle specific issues of PV systems, as design validation and sizing optimization.
@@
 %; and we do not perform code modification on the verifiers or solvers, we use it as available by their developers.
-We further evaluate our proposed solution by comparative with commercial simulation tool and by data collected from real PV systems deployed at riverside communities.
+%We further evaluate our proposed solution by comparative with commercial simulation tool and by data collected from real PV systems deployed at riverside communities.
 
@@
 %The thesis produces a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
+The originality of this thesis lies in the creation of an automated verification approach to solar PV systems.
+The research led to the creation of two software solutions to carry out computational experiments and to compare with commercial tools and real data from systems installed in the field.
+One software solution to perform automated verification and validate the solar PV systems behavior, the other to produce the optimal sizing of solar PV systems through an automated synthesis program.
 
-This Ph.D.
+%This Ph.D.
 thesis has the novelty of create an automated verification approach to solar PV systems.
@@
 One software to perform automated verification and validate the solar PV systems behavior, and another one to produce the optimal sizing of solar PV systems through automated synthesis program.
-
-In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is used for formal verification.
-The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
-The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are provided to the proposed tool and automatically verified during the formal process.
+In this study, a mathematical model of each component of a stand-alone PV system: the solar panel, charge controller, batteries, inverter, and electrical load, is used for formal verification.
+The behavior of each system component can be analyzed and observed with the support of the formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+The project requirements, such as battery autonomy and power demand, as well as the weather conditions, such as solar irradiance and ambient temperature, are provided for the proposed tool and automatically verified during the formal process.
 The model checking tool reports in which conditions a system does not meet the user requirements.
@@
 
-The implementation of the proposed method is carried out by means of an algorithm implemented using the C programming language.
+The proposed method is applied by means of an algorithm implemented using the C programming language.
 We performed computing experimentation in three state-of-the-art model checkers to formally verify PV designs, aiming to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
@@
 
-Related to \textbf{automated synthesis} method and the optimal sizing of stand-alone PV systems, this thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input.
-Given a correctness specification $\sigma$, the proposed method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
-In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
+With respect to the \textbf{automated synthesis} method and optimal sizing of stand-alone PV systems, this thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input.
+Given a correctness specification $\sigma$, the proposed method uses $\sigma$ as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$ with respect to power reliability.
+In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, which may not attain the lowest cost.
 The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted.
-If it fails, then a counterexample is provided with an optimal sizing that meets power reliability and system cost.
+If it fails, then a counterexample is provided with an optimal sizing that meets power reliability and system cost requirements.
 Note that in this study, the focus is not on new criteria or even optimization objectives.
-Instead, the novelty relies on a practical approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.
+Instead, the novelty lies in the practical approach to the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tools.
 
 %----------------------------------------------
-\section{Outline of the Solution}
+\section{The Solution: an Outline}
 %----------------------------------------------
@@
 Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system and optimal sizing.
+Validation when a sized system must be evaluated in order to decide if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or when the user tries to obtain a better solution that he or she has.
+We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in a comparison with specialized simulation tools, supported by real data from deployed PV systems.
+
+%Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system and optimal sizing.
 Validation when a sized system must be evaluated in order to define if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or then the user tries to obtain a better solution that he or she has.
 We thus develop algorithms and the corresponding tools; moreover, we evaluate them with several case studies, in a comparative with specialized simulation tools, supported by real data from deployed PV systems.
-
 Fig.\ref{fig:validation_outline} outlines the proposed solution to perform the validation of stand-alone solar PV systems via automated verification.
 Fig.\ref{fig:optimization_outline} illustrates the proposed solution to obtain the optimal sizing of stand-alone solar PV systems via automated synthesis.
-We pictured here only a summary of each phase of our proposed approach, with highlights to the input parameters, the outputs for the validation, or the optimal size of the solar PV system; more details are presented in the next chapters.
-Moreover, the illustrations show the methodological approach related to comparative result analysis, employing our approaches, commercial software tool, and data from real PV systems deployed in the field.
+We pictured here only a summary of each phase of our proposed approach, highlighting the input parameters, the outputs for the validation, or the optimal size of the solar PV system; more details will be presented in the next chapters.
+Moreover, the illustrations show the methodological approach with respect to comparative result analysis, employing our approaches, the commercial software tool, and data from real PV systems deployed in the field.
 
@@
 Note that it is out of our scope to perform code modification on the verifiers or the solvers used during the automated verification or automated synthesis steps of our approach.
-This thesis intend to create front-end applications to the verifiers and solvers (that it will be the back-end).
+Here we intend to create front-end applications for the verifiers and solvers (which are the back-end).
 That decision is based on the fact that we can be verifier-independent, and evaluate different back-ends, now and in the future, always searching for the best performance and soundness.
@@
 
+With respect to the proposed \textbf{automated verification} method, this thesis makes three main contributions: \textbf{first}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; \textbf{second}, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies; \textbf{third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.
+
+In the area of \textbf{automated synthesis}, our study makes a further three original contributions: \textbf{first}, it is the first application of a sound and automated formal synthesis approach which can provide accurate results for optimal sizing of stand-alone PV systems; \textbf{second}, we propose a variant CEGIS method of synthesis with striking differences of how the Synthesize and Verify phases from the original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and \textbf{third}, experimental results in seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tools: our solution is far more detailed and closer to real PV systems than solutions presented by simulation.
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
 Secondly
-
-Related with the proposed \textbf{automated verification} method, this thesis makes three main contributions. 
-\textbf{First}, we propose an algorithm written in the C programming language, which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system.
+%
+%With respect to the proposed \textbf{automated verification} method, this thesis makes three main contributions. 
+%\textbf{First}, we propose an algorithm written in the C programming language, which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system.
 \textbf{Second}, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies.
@@
 %The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
-
-And linked to \textbf{automated synthesis}, our work makes more three original contributions: \textbf{First}, it is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems;
-\textbf{Secondly}, we propose a variant CEGIS method of synthesis with striking differences of how the {\sc Synthesize} and {\sc Verify} phases from original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and
-\textbf{Thirdly}, experimental results with seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tool: our solution is far detailed and closer to real PV systems than the solution presented by simulation.
-
+%
+%And linked to \textbf{automated synthesis}, our work makes more three original contributions: \textbf{First}, it is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems; \textbf{Secondly}, we propose a variant CEGIS method of synthesis with striking differences of how the {\sc Synthesize} and {\sc Verify} phases from original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and \textbf{Thirdly}, experimental results with seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tool: our solution is far detailed and closer to real PV systems than the solution presented by simulation.
+%
 %three major contributions. 
@@
 
-Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.
+In this section we discuss only the use of formal methods in electrical systems in general since optimization of PV sizing is currently not obtained by formal methods or even program synthesis.
+%Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.
 
 The conversion of the traditional power grid into a smart grid, a fundamental example of a CPS, raises many issues that require novel methods and applications.
-In $2012$, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+In $2012$, a Chinese smart grid implementation was considered as a case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
 The authors employed a stochastic model checking approach and presented a modeling and analysis study using PRISM, which is a probabilistic model checker~\cite{KwiatkowskaNP11}.
@@
 This approach relied on representing the unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time-consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, almost three days of computer effort to verify the design space of a single operational hour of the PV panels’ behavior made it clear that time was an issue.
+This related study did not include any  other components of a stand-alone solar PV system.
+%however, it was evident the time-consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
 This related study did not include other components of a stand-alone solar PV system.
 
-Another work from $2018$ was the approach to model smart grid components using a formal specification.
+Another study from $2018$ presented an approach to modeling smart grid components using a formal specification.
 The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
-The presented formal specification can be considered as a first step towards modeling of smart grids using formal methods.
-The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and systems, which communicates and interacts with each other.
-This approach is based on Petri nets and is under the assumption that modeling the smart home leads to a clear understanding of the overall behavior of the smart grid.
+The formal specification presented can be considered a first step towards modeling smart grids using formal methods.
+The starting point of this study was that a smart home can be considered an integrated system consisting of various objects and systems, which communicate and interact with each other.
+This approach is based on Petri nets and works under the assumption that modeling smart homes leads to a clear understanding of the overall behavior of the smart grids.
 
 However, prior studies did not deal with formal verification of a complete stand-alone PV system (with batteries, charge controller, and power inverter) or even solar PV systems optimization.
-Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in literature.
-Moreover, it is precisely in those gaps that this thesis focuses on.
+Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in the literature.
+Moreover, it is precisely on these gaps that this thesis is focused.
 
@@
 This introduction has outlined the context, motivation, and problem addressed by this thesis and the objectives, solution, and contributions of the research.
-The remainder of the chapters of this thesis are organized as follows:
+The remaining chapters are organized as follows:
 
-Chapter '~\nameref{chap:background}' gives the theoretical basis on formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.
+Chapter '~\nameref{chap:background}' presents the theoretical basis of formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.
 
@@
 
-Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science and its application to obtain the optimal sizing of stand-alone solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collected from fieldwork.
+Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science and its application to obtain the optimal sizing of stand-alone solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with a  simulation tool and from data collected from fieldwork.
 
-Chapter '~\nameref{chap:conclusions}' presents the main contributions, future work directions and concluding remarks.
+In the '~\nameref{chap:conclusions}' we present the main contributions, future work directions and concluding remarks.
 
-~\autoref{chap:publications} presents a list of papers that we submitted to international journals and conference related to the use of automated verification method.
-It covers the years from 2015 to 2019, related to the Ph.D.
+~\autoref{chap:publications} presents a list of papers that we submitted to international journals and conferences on the topic of the automated verification method.
+It covers the years 2015-2019, restricted to the Ph.D.
 process.
 
-~\autoref{chap:tools} depicts the tools created during the PhD process to implement and validate the two scientific methods of the thesis (and how to use it).
+~\autoref{chap:tools} depicts the tools created during the Ph.D process to implement and validate the two scientific methods of the thesis (and instructions for their use).
+
+It is worth mentioning that we decided, with the consent of the coordination of the graduate program, that this document would be written in the active voice and entirely in English.
+The choice of the active voice comes from the choice of the English language, which in the thesis studied was always presented in the active voice.
+The decision to use the English language stems from the possibility that the research may lead to further developments and activities, without the need for translation.

### 2019-12-28 Tex/Old text/main.tex
Thesis update

@@
 \author{Alessandro Trindade}
-\date{31 July 2019}
+\date{29 November 2019}
 
@@
 \chapter*{Acknowledgements}
-(It is not possible to get here without the help of several people. I hope I have not forgotten any and do no wrong).
+(It is not possible to arrive at this point without the help of several people. I hope I have not forgotten anyone and do wrong to none).
 
-I would like to thank God (for the gift of life); Solange and Louise (without the patience and support of my family I could not be here); my parents and grandparents; Lucas (for having believed in me and for the patience); the Electricity Department at UFAM (for the support); Professors Feitosa, Marco Cristo and Barreto from IComp (support and advice); IT support team from IComp (Virtual Machine maintenance); secretary people from IComp (for the administrative support); the financial support from FAPEAM, British Council/Newton Fund and Fundação Amazonas Sustentável; Davide Poggio from University of Sheffield for the HOMER Pro license (Research England QR GCRF Institutional Allocation); and Coventry University team (Elena, Kojo, and Ross for the opportunity to use field deployed photovoltaic solar systems).
+I would like to thank God (for the gift of life); Solange and Louise (without the patience and support of my family I could not be here); my parents and grandparents; Lucas (for having believed in me and for his patience); the Electricity Department at UFAM (for the support); Professors Feitosa, Marco Cristo and Barreto from IComp (support and advice); IT support team from IComp (Virtual Machine maintenance); the IComp administrative team (for their administrative support); the financial support from FAPEAM, the British Council/Newton Fund and Fundação Amazonas Sustentável; Davide Poggio from the University of Sheffield for the HOMER Pro license (Research England QR GCRF Institutional Allocation); and the Coventry University team (Elena, Kojo, and Ross for the opportunity to use field deployed photovoltaic solar systems).
 
@@
 
-\chapter{Automated Verification and Synthesis Methodologies}
-\label{chap:methodology}
-\input{chapters/chapter03}
+%\chapter{Automated Verification Methodology}
+%\label{chap:methodology1}
+%\input{chapters/chapter03}
+%
+%\chapter{Automated Synthesis Methodology}
+%\label{chap:methodology2}
+%\input{chapters/chapter04}
 
@@
 \label{chap:automatedverification}
-\input{chapters/chapter04}
+\input{chapters/chapterverification}
 
-\chapter{Automated Formal Synthesis Optimization Method for Sizing of Stand-Alone Solar PV Systems}
+\chapter{Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis}
 \label{chap:automatedsynthesis}
-\input{chapters/chapter05}
+\input{chapters/chapteroptimization}
 
@@
 \label{chap:publications}
-\fancyfoot[CO,CE]{Appendix}
+\fancyfoot[CO,CE]{Appendix A}
 \input{chapters/appendix}
+\chapter{Tools Description and How to Use it}
+\label{chap:tools}
+\fancyfoot[CO,CE]{Appendix B}
+\input{chapters/appendixB}
 
@@
 \renewcommand\bibname{References}
-\bibliographystyle{abntex2-num}
+%\bibliographystyle{abntex2-num}
 \bibliography{trindadeThesis}{}

### 2019-12-28 Tex/Old text/resumo.tex
Thesis update

--- 2019-10-08 Tex/Old text/resumo.tex
@@
 Com custos decrescentes e com melhoria de desempenho, a implantação de sistemas de energia renovável está crescendo cada vez mais rapidamente no mundo.
-Em 2017, pela primeira vez, o número de pessoas sem acesso à eletricidade ficou abaixo de 1 bilhão, mas os dados quanto a universalização do acesso a energia ficaram aquém das metas globais.
+Em 2017, pela primeira vez, o número de pessoas sem acesso a eletricidade ficou abaixo de 1 bilhão, mas os dados quanto à universalização do acesso a energia ficaram aquém das metas globais.
 Particular atenção é dada aos sistemas isolados solares fotovoltaicos em áreas rurais ou onde a extensão da rede é inviável.
@@
 O uso de métodos formais em sistemas elétricos é um assunto recente, com pesquisas sendo publicadas apenas nos últimos quatro anos.
-Além disso, o uso de síntese automatizada para obter um ótimo dimensionamento de sistemas solares fotovoltaicos nunca foi feito antes.
-Esta tese marca duas conquistas principais: (1) a primeira aplicação de modelagem de software para verificar o projeto de um sistema isolado solar fotovoltaico, incluindo painel solar, controlador de carga, bateria, inversor e carga elétrica; e (2) uma abordagem confiável e automatizada para obter o dimensionamento ótimo de sistemas fotovoltaicos usando a síntese de programas, onde cada componente e função de um sistema solar fotovoltaico é descrito, incluindo suas propriedades, e o modelo comportamental que representa o dimensionamento ótimo é sintetizado automaticamente.
-Relacionado a verificação formal, estudos de caso de sistemas fotovoltaicos reais instalados em cinco localidades diferentes são usados para avaliar a abordagem proposta e para compará-la com ferramenta de simulação especializada.
+Além disso, a síntese automatizada nunca foi usada antes para obter um ótimo dimensionamento de sistemas solares fotovoltaicos nunca foi feito antes.
+Esta tese marca duas conquistas principais: (1) a primeira aplicação de verificação de modelos de software para verificar o projeto de um sistema isolado solar fotovoltaico, incluindo painel solar, controlador de carga, bateria, inversor e carga elétrica; e (2) uma abordagem confiável e automatizada para obter o dimensionamento ótimo de sistemas fotovoltaicos usando a síntese de programas onde cada componente e função de um sistema solar fotovoltaico é descrito, incluindo suas propriedades, e o modelo comportamental que representa o dimensionamento ótimo é sintetizado automaticamente.
+Relacionado à verificação formal, estudos de caso de sistemas fotovoltaicos reais instalados em cinco localidades diferentes são usados para avaliar a abordagem proposta e para compará-la com ferramenta de simulação especializada.
 Diferentes ferramentas de verificação são avaliadas também, a fim de comparar o desempenho e a confiabilidade dos resultados.
 Dados de aplicações práticas mostram a eficácia da abordagem proposta, onde condições específicas que levam a falhas em um sistema solar fotovoltaico são detalhadas apenas pelo método de verificação automatizado.
-Além disso, em relação ao uso da síntese de programas, propõe-se uma variante do método de síntese indutiva guiada por contraexemplos (CEGIS), com duas fases bem definidas: primeiro ele sintetiza o dimensionamento de sistemas fotovoltaicos baseados em confiabilidade de energia, mas que pode não alcançar o menor custo; segundo, a solução proposta é então verificada iterativamente com um limite inferior via verificação de modelo simbólico.
+Além disso, em relação ao uso da síntese de programas, propõe-se uma variante do método de síntese indutiva guiada por contraexemplos (CEGIS), com duas fases bem definidas: primeiro, ele sintetiza o dimensionamento de sistemas fotovoltaicos baseados em confiabilidade de energia, mas que pode não alcançar o menor custo; segundo, a solução proposta é então verificada iterativamente com um limite inferior via verificação de modelo simbólico.
 Se a etapa de verificação não falhar, o limite inferior será ajustado; e se falhar, o contraexemplo é fornecido com o dimensionamento ótimo, vinculando assim a resposta técnica da primeira fase à análise de custo da segunda fase.

### 2019-12-29 Tex/Old text/chapters/chapter02.tex
Thesis update

@@
-In this chapter we present some concepts related to the intersection of the two areas:  computer science methods used to solve electrical engineering problems, i.e., the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.
+In this chapter we present some concepts related to the intersection of the two areas:  computer science methods used to solve electrical engineering problems; in this case, the use of formal verification methodology to perform automated verification and optimal sizing of stand-alone solar PV systems.
 
@@
 
-And secondly, how a solar PV system can be modeled in order to be validated or optimized by the formal verification methodology.
+And secondly, how a solar PV system can be modeled in order to be validated or optimized by formal verification methodology.
 
@@
 In contrast to other design systems, formal methods use mathematical proof as a complement to system testing in order to ensure correct behavior.
-With increasing scale and complexity, and safety becomes a more important issue, the formal approach to system design offers better level of insurance.
-
-Formal methods differ from other design systems through the use of formal verification schemes, the basic principles of the system must be proven correct before they are accepted~\cite{Bowen93}.
+With increasing scale and complexity, when safety becomes a more important issue, the formal approach to system design offers a better level of insurance.
+
+Formal methods differ from other design systems through the use of formal verification schemes; the basic principles of the system must be proven correct before they are accepted~\cite{Bowen93}.
 Traditional system design has used extensive testing to verify behavior, but testing is capable of only finite conclusions.
-Dijkstra and others have demonstrated that tests can only show the situations where a system won't fail, but cannot say anything about the behavior of the system outside of the testing scenarios~\cite{Bentley99}.
-In contrast, once a theorem is proven true it remains true.
-
-Prior the 80's, mainly deductive verification was used as formal method, with the use of axioms and proving rules to demonstrate the correctness of the system.
-The original focus was to verify critical systems based on the premise that 'if system is important, must spend the enough time to verify it'~\cite{Lowry1998}.
-Back in time, formal methods were initially performed by hand.
-
-Worth to mention that formal verification does not avoid the need for testing~\cite{Bowen95}.
-Formal verification can not fix bad assumptions in the design, but it can help identify errors in reasoning which would otherwise be left unverified.
-In several cases, engineers have reported finding flaws in systems once they reviewed their designs formally~\cite{Kling95}.
+Dijkstra and others have demonstrated that tests can only show the situations where a system will not fail, but can say nothing about the behavior of the system outside of the testing scenarios~\cite{Bentley99}.
+In contrast, a theorem once proven true remains true.
+
+Prior to the 1980s, mainly deductive verification was used as the formal method, with the use of axioms and proving rules to demonstrate the correctness of the system.
+The original focus was to verify critical systems based on the premise that if the system is important, time must be spent to verify it~\cite{Lowry1998}.
+Originally, formal methods were performed by hand.
+
+It is worth pointing out that formal verification does not avoid the need for testing~\cite{Bowen95}.
+Formal verification can not correct bad assumptions in the design, but it can help to identify errors in reasoning which would otherwise be left unverified.
+In several cases, engineers have reported finding flaws in systems following a formal review of their designs~\cite{Kling95}.
 
@@
 \item Formal Specification: During the formal specification phase, the engineer rigorously defines a system using a modeling language.
-Modeling languages are fixed grammars which allow users to model complex structures out of predefined types (are rigorously defined).
-This process of formal specification is similar to the process of converting a word problem into algebraic notation and help engineers to clearly define their problems, goals and solutions.
-Several engineers who have used formal specifications say that the clarity that this stage produces is a benefit in itself~\cite{Kling95}.
+Modeling languages are fixed grammars which allow users to model complex structures from predefined types (that are rigorously defined).
+This process of formal specification is similar to the process of converting a word problem into algebraic notation and helps engineers to clearly define their problems, goals and solutions.
+Several engineers who have used formal specifications claim that the clarity that this stage produces is a benefit in itself~\cite{Kling95}.
 \item Verification: As stated above, formal methods differ from other specification systems by their heavy emphasis on provability and correctness.
-By building a system using a formal specification, the designer is actually developing a set of theorems about his system.
+In building a system using formal specification, the designer is actually developing a set of theorems about his system.
 By proving these theorems correct, the formal verification ensures that the modeled system has an intended behavior.
@@
 That is the origin of 'automated verification' definition.
-These tools can prove simple theorems, verify the semantics of theorems, and provide assistance for verifying more complicated proofs and with feedback about the trace of the error (in order to correct the system and the specification of it).
+These tools can prove simple theorems, verify the semantics of theorems, and provide assistance for verifying more complicated proofs, with feedback about the trace of the error (in order to correct the system and the specification of it).
 \item Implementation: Once the model has been specified and verified, it is implemented by converting the specification into code.
@@
 
-Simulation may also be used for validation, but it is more problematic for verification.
+Simulation may also be used for validation, but it raises more problems for verification.
 In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs.
-Testing can also be used for validation, but for the same reasons, it too is problematic for verification.
-
-According \cite{Clarke2008}, verification procedure is an intelligent exhaustive search of the state space of the design.
+Testing can also be used for validation, but for the same reasons, it too raises problems for verification.
+
+According to \cite{Clarke2008}, verification procedure is an intelligent exhaustive search of the state space of the design.
 In addition, according to \cite{Forejt2011}, formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system.
@@
 Model checking is an automatic verification technique, as defined by \cite{Clarke2008}.
-Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system.
+Model checking was originally developed for reasoning about finite state of concurrent systems, though nowadays it is mainly used for hardware and software verification, but can be applied to any kind of system.
 
@@
 \item In modeling, a model (normally mathematical) of the system is created; 
-\item In specification, normally a list of properties to be satisfied by the system is stablished, i.e., the requirements, as reliability to performance for example.
-\item Normally is expressed in temporal logic form ($CTL$);
+\item In specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, such as reliability to performance, for example; 
+\item Normally it is expressed in temporal logic form ($CTL$); 
 \item The model checking is the verification method itself. 
@@
 \item Given the model $ 'M' $ and a $CTL$ formula $ \phi $ as input;  
-\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
+\item The moodel checking algorithm provides all the states of model $ M $ which satisfy $ \phi $;  
 \item It returns $YES$ if $ \phi $ is $TRUE$, or returns $NO$ if $ \phi $ is $FALSE$.
@@
 \end{itemize}
-Specifically at the $FALSE$ situation, the algorithm returns a counterexample that is useful as diagnostic of the system, in order to discover in which situation the model is violated.
-\cite{Clarke2008} consider that the most important advantage of the use of model checking.
-
-Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving).
-However, there is a main disadvantage of model checking: the state explosion problem.
+Specifically, in the case of $ \phi $ being $FALSE$, the algorithm returns a counterexample that is useful as a system diagnostic, in order to discover in which situation the model has been violated.
+\cite{Clarke2008} considers this to be the most important advantage of model checking.
+
+Model checking presents several other advantages: proofs are not needed (the algorithm is not a deductive procedure); there is no problem with partial specifications of the system, logics can easily express many concurrency properties; it is fast (compared to other rigorous methods such as interactive theorem proving).
+However, there is one major disadvantage in model checking: the state explosion problem.
 
@@
 \begin{itemize}
-\item Let $M$ be a Kripke structure (i.e., state transition graph);
+\item Let $M$ be a Kripke structure (i.e., a state transition graph);
 \item $f$ be the specification in temporal logic (a formula);
@@
 
-Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. In other words, the problem is not dealing with an abstraction of the actual system under study.
-
-The Fig. \ref{fig:systemverif} shows the process to convert a real system to a model in order to be verified by a model checking.
+Here it is worth mentioning that the term "model" is not used here with its dictionary definition. In other words, the problem is not dealing with an abstraction of the actual system under study.
+
+The Fig. \ref{fig:systemverif} shows the process of converting a real system to a model in order to be verified by model checking.
 
@@
 
-In order to solve the problem of state explosion, many different techniques were developed at the last decades. One of the promising is the Bounded Model Checking (BMC).
-
-BMC is a method that checks the model up to a given path in the path length.
-BMC algorithms traverses a finite state machine for a fixed number of steps, $k$, and checks whether violation occurs with this bound.
+In order to solve the problem of state explosion, many different techniques have been developed over the last decades. One of the most promising is Bounded Model Checking (BMC).
+
+BMC is a method that checks the model up to a given point in the path length.
+The BMC algorithms traverse a finite state machine for a fixed number of steps, $k$, and check whether violation occurs within this bound.
 It uses fast SAT solvers, where SAT means satisfiability.
 
-SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretation that satisfy a given Boolean expression.
-SAT solvers are used in BMC, such that if there are some Boolean function, the solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
-If SAT Solver find a substitution for the formula/function then the substitute induces a counterexample.
+A SAT problem, as defined by \cite{Clarke2008}, is a problem of determining if there are certain conditions or interpretations that satisfy a given Boolean expression.
+SAT solvers are used in BMC, such that if there is some Boolean function, the solver would search the model for conditions (value of variables) that would make the formula $TRUE$.
+If the SAT Solver finds a substitution for the formula/function then the substitute induces a counterexample.
 
@@
 %ESBMC is a context-bounded model checker for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver, which can use CBMC as front-end.  
-The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
+The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the system's modeling, especially considering that the complexity of these is increasing and the SMT method has a higher level and richer theories than the SAT to represent the models.
 
@@
 
-At this work we will evaluated three state-of-the-art model checkers to formally verifying and synthesize PV designs w.r.t.
+In this study we will evaluate three state-of-the-art model checkers to formally verifying and synthesize PV designs w.r.t.
 user requirements.
-Moreover, different solvers will be evaluated as well, according with the feature of each model checker.
+In addition, other solvers will be evaluated, according to the feature of each model checker.
 
@@
 
-Particularly, CBMC comes with a built-in solver for bit-vector formulas that is based on MiniSat. We used this solver during the experimentation in this PhD thesis~\cite{Kroening}.
+Specifically, CBMC comes with a built-in solver for bit-vector formulas that is based on MiniSat. We used this solver during the experimentation in this Ph.D thesis~\cite{Kroening}.
 
@@
 \begin{itemize}
-\item A front-end that can read and compile C code, where the system formal specification is first handled; 
-\item Preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally 
+\item A front-end that can read and compile C code, where the system's formal specification is first handled; 
+\item Preprocessing steps deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally 
 \item The SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
@@
 This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
-ESBMC in 'incremental SMT' uses only Z3 solver~\cite{DeMoura}.
+This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have a large amount of memory to deal with the entire design space state.
+ESBMC in 'incremental SMT' uses only the Z3 solver~\cite{DeMoura}.
 
@@
 
-The CPA formalism provides an interface for the definition of program analyses.
+CPA formalism provides an interface for the definition of program analyses.
 Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework.
 The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}.
-Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+As to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
 
@@
 Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do.
-The specification needs to describe the program's desired behavior to ensure that the program does what it intends.
+The specification needs to describe the program's desired behavior to ensure that the program does what it is intended.
 
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
-In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
+In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$ as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
 As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
 
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+CEGIS represents one of the most popular approaches to program synthesis that are currently in use for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
 
@@
 
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the  CEGIS method's {\sc Synthesize} and {\sc Verify} phases interact via a finite set of test vector {\sc inputs}, which is incrementally updated.
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible solution; otherwise, in the CEGIS method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
+If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., a feasible combination of equipment) for the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If this is the case, then the algorithm terminates, i.e., we have found a feasible solution; otherwise, in the CEGIS method, additional information is provided for the {\sc Synthesize} phase, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
 
 One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible solution was found.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times.
+However, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible solution was found.
 
@@
 
-According to \cite{Roy}, a PV system is designed to give the electric supply to a load.
-This load can be either Alternate Current (AC) type or Direct Current (DC) type.
-Electric supply can be needed either in daytime or evening time (in particular cases, in both times).
-The most basic PV system can give supply only in daytime.
-For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.
+According to \cite{Roy}, a PV system is designed to supply electrical loads.
+This load can be of the Alternating Current (AC) type or the Direct Current (DC) type.
+The supply electricity can be needed either in daytime or nighttime (in particular cases, in both).
+The most basic PV system can supply only in daytime.
+For the night hours or rainy days, batteries are needed, where power can be stored and used \cite{Gules}.
 
@@
 \item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
-Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants;
+Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting systems, solar lanterns, and solar power plants;
 \item Grid-connected systems, where the solar PV system is connected to the grid.
-The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards.
+The grid-connected system can be either a grid-tied system, which can only feed power into the grid, with the result that this system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards.
 Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode;
-\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
-In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
+\item Solar PV hybrid systems: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
+In this type of system, the main objective is to bring more reliability into the overall system at an affordable cost by adding one or more energy sources.
 \end{itemize}
 
-Specifically concerning isolated communities, depending on the type of load, cost, resources availability, and requirements of the load, standalone systems can be split into several categories, which are described in this section.
-As the goal of this Thesis is just the solutions aimed to isolated/ off-grid application, therefore it is not considered the on-grid or hybrid configurations.
-
-There is a resource, called maximum power point tracking (MPPT), which is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}.
-That resource is found at modern PV systems and is strongly indicated due to its advantages.
+In the specific case of isolated communities, depending on the type of load, cost, resources availability, and the load requirements, standalone systems can be split into several categories, as described below.
+Since the goal of this Thesis is to present solutions only to isolated/ off-grid applications, on-grid or hybrid configurations are not discussed here.
+
+There is a resource, called maximum power point tracking (MPPT), which is an electronic control mechanism that maintains the PV operating at a voltage that corresponds to maximum power voltage, which maximizes the transfer of power while avoiding loss of PV cells \cite{Pinho}.
+This resource is found in modern PV systems and is strongly indicated due to its advantages.
 

### 2019-12-29 Tex/Old text/chapters/chapter02.tex
Thesis update

@@
 
-\section{Solar Photovoltaic System }
+\section{Solar Photovoltaic Systems}
 
@@
 
-\subsection{Unregulated standalone PV system with DC load }
+\subsection{Unregulated standalone PV systems with DC load }
 Usually this type of system is for low power applications, as defined by \cite{Roy}.
-The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:unregSPV}.
-At night hours, the system will not provide any supply because of the absence of the battery.
+The PV system is directly connected to the load without any MPPT controller, as shown in Fig.\ref{fig:unregSPV}.
+At night, the system will not provide any supply because of the absence of a battery.
 
@@
 
-\subsection{Regulated standalone PV system with DC load}
-It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:regSPV1}.
-Usually system with MPPT should have battery; otherwise, extra power will be waste.
+\subsection{Regulated standalone PV systems with DC load}
+Similar to the unregulated standalone system with DC load, the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated in Fig.\ref{fig:regSPV1}.
+Usually systems with MPPT should have a battery; otherwise, the extra power will be wasted.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Regulated standalone system with battery and DC load}
+\subsection{Regulated standalone systems with battery and DC load}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}.
-Battery is used to store the extra power of PV system.
+The battery is used to store the extra power from the PV system.
 A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
@@
 \centering
-\caption{Regulated standalone SPV system with battery DC load. Source: \cite{Roy}.}
+\caption{Regulated standalone SPV system with battery and DC load. Source: \cite{Roy}.}
 \label{fig:regSPV2}
@@
 
-According to \cite{Pinho}, PV systems that are used to feed loads with low variation on the consumption can be sized to operate without the controller.
-That is called of self-regulated standalone PV system with battery.
-However, the voltage from the PV panel must be compatible with the batteries voltage.
-Normally, the bank of batteries are oversized related to the PV panel and to the load.
+According to \cite{Pinho}, PV systems that are used to feed loads with low variation of consumption can be sized to operate without the controller.
+This is known as a self-regulated standalone PV system with battery.
+However, PV panel voltage must be compatible with the battery voltage.
+Normally, the bank of batteries is oversized in relation to the PV panel and to the load.
 The drawback is the operation of the batteries, normally overloaded or with excessive discharges (that can damage the batteries).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Regulated standalone system with battery, AC load}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}.
-This solution has an increase of cost because has more equipments.
-However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
-That configuration is the focus of the present Thesis since it is the most common nowadays specifically for remote rural areas of developing countries or places where the grid extension is not feasible.
+\subsection{Regulated standalone systems with battery, AC load}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This system is similar to the previous one, but the AC load draws the power from the PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}.
+This solution has an cost increase because it has more equipment.
+However, AC availability has the advantage of permitting the use of a higher number of AC appliances in homes or consumer units.
+This configuration is this thesis since it is currently the most common system used specifically for remote rural areas of developing countries or areas where the grid extension is not feasible.
 %stand-alone systems are one the most used solutions, and 
@@
 
-In order to address different aspects of project system and systems design, there is a myriad of public domain and commercial software available for the SPV market.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization).
-Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-
-Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.
-In this study, the most popular tools are presented:
+In order to address different aspects of a project system and system's design, a lot of public domain and commercial software is available for the SPV market.
+According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, and to complex financial analysis software (with optimization).
+Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
+
+Manufacturers and integrators also have their own proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback of just including´ their own products among the possibilities of choice.
+In this study, the most widely used tools are presented:
 
@@
 
-According to \cite{Freeman} and \cite{NRELDobos}, it is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
-According to \cite{NRELDobos}, to use the calculator, it is necessary to provide information about the system's location, basic design parameters, and system economics.
-PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity monetary value.
+According to \cite{Freeman} and \cite{NRELDobos}, this is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
+According to \cite{NRELDobos}, using the calculator, requires information about the system's location, basic design parameters, and system economics.
+PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity's monetary value.
 This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules.
-The production estimates that PVWatts computation do not account for many factors that are important in the design of a photovoltaic system, therefore it is necessary support of an energy expert.
+The production estimates that PVWatts computation does not account for many factors that are important in the design of a photovoltaic system, which makes it necessary to have the support of an energy expert.
 The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year.
@@
 
-SAM or System Advisor Model is a software from the U.S.
+SAM or System Advisor Model is a software solution produced by the U.S.
 Department of Energy and National Renewable Energy Laboratory.
 According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications, and (also) to provide information for readers who do not plan to use the model, but want to learn about its capabilities.
-SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: Project managers and engineers; Financial and policy analysts; Technology developers; and Researchers.
-SAM makes performance predictions and cost of energy estimates for grid-connected power projects based on installation and operating costs and system design parameters that you specify as inputs to the model.
+SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: project managers and engineers; financial and policy analysts; technology developers; and researchers.
+SAM makes performance predictions and energy cost estimates for grid-connected power projects based on installation and operating costs and system design parameters that user specifies as inputs to the model.
 Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement.
-SAM is an electric power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet electric load.
+SAM is an electrical power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet the electric load.
 It does not model thermal energy systems that meet a thermal process load.
@@
 
-As defined in \cite{HOMER}, actually is a set of two tools: HOMER Legacy and HOMER Pro.
+As defined in \cite{HOMER}, this is actually a set of two tools: HOMER Legacy and HOMER Pro.
 HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources.
@@
 HOMER's optimization and sensitivity analysis algorithms allow the user to evaluate the economic and technical feasibility of a large number of technology options.
-Since 2016 Homer Legacy can be found at HOMER web site, but only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has not support available.
-At the short-time only the commercial version will remain.
-
-The commercial version (paid), called HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
-HOMER Pro put together three tools in one product: optimization, simulation, and sensitivity analysis.
-HOMER Pro provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use.
-It is adaptable to a wide variety of projects.
+Since 2016 Homer Legacy can be found at the HOMER web site, but it is only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has no support available.
+For a short-time only the commercial version will remain.
+
+The commercial version (paid), known as HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
+HOMER Pro puts together three tools in one product: optimization, simulation, and sensitivity analysis.
+It provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use and is adaptable to a wide variety of projects.
 For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project.
@@
 \item RETScreen 4 (discontinued, requires Microsoft Excel to run); 
-\item RETScreen Software Suit, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
-\item And the actual (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
-However, this version works is only Windows-based.
-This version has a complete paid version, in an annual subscription way.
+\item RETScreen Software Suite, which includes the RETScreen 4 and a Windows-based graphical software that allows project owners to verify the ongoing energy performance of their facilities (discontinued in 2013);
+\item And the current (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
+This version is only Windows-based and has a complete paid version, via annual subscription way.
 \end{itemize}
 
-As described by \cite{Pradhan}, RETScreen performs a five-step standard analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
+As described by \cite{Pradhan}, RETScreen performs a standard five-step analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
 It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
@@
 
-The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool to perform detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
+The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool that executes detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
 Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
@@
 The code does not consider short-term system fluctuations caused by system dynamics or component transients.
-This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, what is a limitation.
+This program is not supported anymore and according to \cite{UMASS}, probably after the user performs the free download of the tool, it will not work on Windows platforms later than Windows XP, which is a limitation.
 
 Table \ref{table:softwares} summarizes the tools described in this paper.
-Where just Hybrid2 do not have technical support; only HOMER, RETScreen and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; and that only HOMER and RETScreen are complete, including economical analysis or even optimization-sensitive analysis.
-However, only paid version of those softwares have all the features, and they run only at Windows-based operational systems.
+Where just Hybrid2 is mentioned, no technical support is available; only HOMER, RETScreen and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; only HOMER and RETScreen are complete, including economic analysis and even optimization-sensitive analysis.
+However, only the paid version of these software packages have all the features, and they run only on Windows-based operating systems.
 
@@
 
-Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER remain for comparative.
-All tools need some parameters inherently from manufacturer's catalog, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries.
-After that, the potential solution is analyzed in another tool to validate or even optimize the solution.
-Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution.
+Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER remains for comparison.
+All tools need some parameters inherently from the manufacturer's catalog, so the project starts with manufacturer's and integrator's tool to define the basic items of the project: panels, inverters, controllers, and batteries.
+The potential solution is then analyzed by another tool to validate or even optimize the solution.
+The challenge of this study therefore is to prove that it is possible to use automated verification to validate an off-grid PV solution.
 
@@
 
-The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load.
+The main purpose of this section is to describe the models for the elements of a standalone PV system: the PV generator, battery, controller, inverter, and load.
 The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}.
-The modular structure facilitates the modeling of the other system structures and replacing of elements as, for instance, a DC load instead of an AC load.
+The modular structure facilitates the modeling of the other system structures and the replacement of elements such as a DC load instead of an AC load.
 
@@
 
-A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. In the present modeling, the focus is only on cell/module/array.
+A photovoltaic PV generator is the whole assembly of solar cells, connections, protective parts, and supports. In the present modeling, the focus is only on the cell/module/array.
 
@@
 The PV modules are generally rated under standard test conditions (STC), which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
-The parameters required for the input of the PV modules are relying on the meteorological conditions of the area to be serviced by photovoltaic solution.
+The parameters required for the input of the PV modules are dependent on the meteorological conditions of the area to be serviced by photovoltaic solution.
 However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
@@
 These uncertainties lead to either over- or underestimation of energy yield from PV modules.
-An overestimation up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
-The growing demand of photovoltaics technologies led to research in the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}.
+An overestimation of up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
+The growing demand for photovoltaics technologies has led to research into the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}.
 Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
@@
 
-Modeling provides the ways to understand the current, voltage, and power relationships of PV systems.
+Modeling provides the means to understand the current, voltage, and power relationships of PV systems.
 
@@
 This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}.
-Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown by Fig.
+Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown in Fig.
 \ref{fig:equivckt}.
@@
 	\item $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); 
-	\item $ T $ the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
-	\item $ q $ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
+	\item $ T $ is the temperature of the p-n junction (or cell temperature) expressed in Kelvin; 
+	\item $ q $ is the absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $).	
 	\end{itemize}	 
@@
 
-The 1-diode/1-resistor model, is described by Equation \ref{eq:1d1rmodel}.
+The 1-diode/1-resistor model, is described in Equation \ref{eq:1d1rmodel}.
 
@@
 
-At this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
-
-The 1-diode/2-resistor model, is described by Equation \ref{eq:1d2rmodel}.
+In this model, there are four unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, and $ a $), and it assumes shunt resistance as $ infinite $.
+
+The 1-diode/2-resistor model, is described in Equation \ref{eq:1d2rmodel}.
 
@@
 
-At this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
-
-And the 2-diode/2-resistor model, is described by Equation \ref{eq:2d2rmodel}.
+In this model, there are five unknown parameters ($ I_{ph}$, $I_{0}$, $ R_{s} $, $ R_{sh} $, and $ a $).
+
+And the 2-diode/2-resistor model, is described in Equation \ref{eq:2d2rmodel}.
 
@@
 
-For that reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters and walked through three different paths.
+For this reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters, proceeding along three different paths.
 The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
-However, due to implicit nature and nonlinearity of PV cell or module characteristics, it is hard to find out the analytical solution of all unknown parameters, as described by \cite{Hasan}.
-Thus, numerical methods such as Newton-Raphson method or Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}.
-This happens because numerical methods give approximate solution of the nonlinear problems without searching for exact solutions.
+However, due to the implicit nature and nonlinearity of PV cell or module characteristics, it is hard to discover the analytical solution of all unknown parameters, as described in \cite{Hasan}.
+Thus, numerical methods such as the Newton-Raphson method or the Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}.
+This happens because numerical methods give approximate solutions to the nonlinear problems without searching for exact solutions.
 However, numerical methods are time consuming and need long term time series data, which is not available in developing countries.
-\cite{Jakhrani} did a mixed methodology using analytical and numerical steps together.
+\cite{Jakhrani} used mixed methodology bringing analytical and numerical steps together.
 \cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation (essays).
-And \cite{Tian} did a mix of analytical and experimental methodology to get the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use experimental technique.
-
-Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves).
-However, the present work will rely on the simplified model of 1-diode, that was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested.
+And \cite{Tian} used a mix of analytical and experimental methodology to establish the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use the experimental technique.
+
+Therefore, a wide variety of models exists for estimation of the power output of PV modules (and $I-V$ or $P-V$ curves).
+However, this study will rely on the simplified 1-diode model, that was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested.
 In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Proposed PV Panel Model}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-With the proposed model, an explicit set of equations is derivate from the ideal PV model given by Equation~\ref{eq:1diodemodel}.
+\subsubsection{The Proposed PV Panel Model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+With the proposed model, an explicit set of equations is derived from the ideal PV model given by Equation~\ref{eq:1diodemodel}.
 
@@
 
-Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown from Equations \ref{eq:Isc} to \ref{eq:Im}.
+Hence, the short-circuit current, the open-circuit voltage, the maximum power voltage and current are written as defined by \cite{Saloux} and shown in Equations \ref{eq:Isc} to \ref{eq:Im}.
 
@@
 
-Equation \ref{eq:exp} is not explicit with the PV key parameters, therefore need to be rewritten in a different way.
-A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and voltage-source at the open-circuit point \cite{Saloux}.
+Equation \ref{eq:exp} is not explicit with regard to the key PV  parameters, it therefore needs to be rewritten in a different way.
+A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and a voltage-source at the open-circuit point \cite{Saloux}.
 These two regions are characterized by two asymptotes of the $ I-V $ curve in Fig.
 \ref{fig:ivcurve}, where the transition is a compromise between both behaviors.
-It is interesting to observe that the maximum power point corresponds to a trade-off condition, where the current is still high enough before it starts decreasing with increasing the output voltage (Fig.
+It is interesting to observe that the maximum power point corresponds to a trade-off condition, where the current is still high enough before it starts decreasing with the increase in the output voltage (Fig.
 \ref{fig:ivcurve}).
@@
 
-The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell.
-Therefore, the Equation \ref{eq:Vmderiv} is generated.
+The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell, thus generating the Equation \ref{eq:Vmderiv}.
 
@@
 It is evident that Equation \ref{eq:Vmderiv} requires an expression of the derivative of the current with voltage evaluated at the maximum power point.
-The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change on $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}.
-Consequently, considering the asymptotic behavior of the $I-V$ curve at short- and open-circuit conditions, the derivative required by Equation 10 can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
+The fact that the maximum power corresponds to an extreme, the variation of the maximum output power with voltage is relatively small, i.e., a change in $ V_{m} $ has a relatively small effect on the maximum power of the cell \cite{Saloux}.
+Consequently, considering the asymptotic behavior of the $I-V$ curve in short- and open-circuit conditions, the derivative required by Equation 10 can be calculated as shown in Equation \ref{eq:dIdV_Vm}.
 
@@
 Replacing the Equation \ref{eq:dIdV_Vm} into Equations \ref{eq:Vmderiv} and \ref{eq:Im}, the voltage and the current at the maximum power point and consequently the maximum output power, are expressed by Equations \ref{eq:Vmfinal}, \ref{eq:Imfinal}, and \ref{eq:Pm} ($ P_{m}=V_{m}I_{m} $).
-These equations are used to calculate the key cell parameters at the maximum power point (MPPT) as function cell temperature and parameters from the manufacturer's data-sheet.
+These equations are used to calculate the key cell parameters at the maximum power point (MPPT) as a function of cell temperature and parameters from the manufacturer's data-sheet.
 
@@
 
-However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) are not given by PV manufacturers.
-Therefore, Equation \ref{eq:Iph} is used to calculate the photocurrent as function of irradiance and temperature \cite{Villalva}.
+However, the photocurrent delivered by the constant current source ($ I_{ph} $) or even the reverse saturation current ($ I_{0} $) is not given by PV manufacturers.
+Therefore, Equation \ref{eq:Iph} is used to calculate the photocurrent as a function of irradiance and temperature \cite{Villalva}.
 
@@
 
-Where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $.
+\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $, and the temperature $ T_{ref}=298.15 K (=25^{o}C) $.
 
@@
 
-\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.
+\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found on the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) at the location of the PV system.
 
 Furthermore, \cite{Villalva} have proposed a relationship, which allows the saturation current ($ I_{0} $) to be expressed as a function of the cell temperature.
-In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient as well as the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
+In this study, this relation is explicitly written based on cell open-circuit conditions using the short-circuit current temperature coefficient in addition to the open-circuit voltage temperature coefficient (Equation \ref{eq:I0}).
 
@@
 
-\noindent where $ V_{mref} $, $ V_{oc,ref} $, $ I_{m,ref} $, and $ I_{sc,ref} $ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by manufacturers.
+\noindent where $ V_{mref} $, $ V_{oc,ref} $, $ I_{m,ref} $, and $ I_{sc,ref} $ are key cell values obtained under both actual cell temperature and solar irradiance conditions, usually provided by the manufacturers.
 
@@
 If the PV cells are in parallel, then there is a parallel array.
-Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
+There will therefore be a change in the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
 
@@
 
-In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
+In addition, if the panels are in series, the current does not change but the total voltage is the sum of the voltage of each individual panel.
 
@@
 
-Because of the fluctuating nature of the output delivered by the PV arrays, batteries are necessary in a PV system.
-Thus, during the hours of sunshine, the PV system feeds directly the load and the excess electrical energy is stored in the battery.
+Because of the fluctuating nature of the output delivered by the PV arrays, batteries are an essential part of a PV system.
+Thus, during the hours of sunshine, the PV system feeds the load directly and excess electrical energy is stored in the battery.
 During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.
 
-Several models have been presented in the literature. However, regardless of the model, normally the following parameters are required:
+Several models have been presented in the literature. However, regardless of the model, normally the following parameters are normally required:
 
 \begin{itemize}
-\item Nominal capacity ($ q_{m} $), is the number of Ampère-hours ($ Ah $) that can maximally be extracted from the battery, under predetermined discharge conditions.
+\item Nominal capacity ($ q_{m} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery, under predetermined discharge conditions.
 \item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $.
@@
 The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
-The battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
+Battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
 LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.
@@
 
-The battery model, which describes the relationship between the voltage, current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.
-
-The Kinetic Battery Model (KiBaM) of Manwell and McGowen \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
-However, it uses some data extracted from tested batteries in laboratory.
-Therefore is not suitable to this study.
-
-Most of the created models were used to simulate and optimize PV storage system based on lead-acid batteries.
-That kind of battery is the most common used batteries in PV application, owing to their relative low cost and wide availability \cite{Copetti}.
+The battery model, which describes the relationship between the voltage, the current and the state of charge, can be found in \cite{Copetti}, \cite{Manwell93}, and \cite{Manwell94}.
+
+Manwell and McGowen's Kinetic Battery Model (KiBaM)  \cite{Manwell93} was developed at the University of Massachusetts to predict the performance of the battery, based on manufacturer's data.
+However, it uses some data extracted from batteries tested in laboratory.
+It is therefore not suitable for this study.
+
+Most of the models created were used to simulate and optimize PV storage systems based on lead-acid batteries, the most commonly used batteries in PV applications, owing to their relative low cost and wide availability \cite{Copetti}.
 
@@
 
-Where $ C_{10} $ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $ \Delta T $ is temperature variation ($ \Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $, $ SOC $ indicates how much electric charge is stored in the cell at given time, defined by Equation \ref{eq:SOCbat}.
+\noindent where $ C_{10} $ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $ \Delta T $ is temperature variation ($ \Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $, $ SOC $ indicates how much electric charge is stored in the cell at any given time, defined by Equation \ref{eq:SOCbat}.
 
@@
 
-Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
-
-The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the farction of discharge, i.e., $ DOC=1-SOC $.
-
-The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
-This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
+\noindent where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
+
+The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the fraction of discharge, i.e., $ DOC=1-SOC $.
+
+The efficiency of the battery discharge is assumed to be 100\%, according to \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}.
+This equation, known as capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
 
@@
 
-\cite{Copetti} show that, during overcharge, gassing occur and tests demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decreasing of the temperature (Equation \ref{eq:Vec}).
-It was created a function for the gassing voltage as well, as shown in Equation \ref{eq:Vg}.
+\cite{Copetti} show that, during overcharge, gassing occurs and tests have demonstrated that the final charge voltage ($ V_{ec} $) increases with the current intensity and with the decrease in temperature (Equation \ref{eq:Vec}).
+A function was created for the gassing voltage also, as shown in Equation \ref{eq:Vg}.
 In addition, the overcharge phenomenon can be represented by Equation \ref{eq:Voverc}.
@@
 
-Where $ Ah_{restored} $ represents the Ampère-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
-
-The function assumes that 95\% of the capacity was already restored at the start of overcharge.
-
-The time constant of the phenomenon ($ \tau $) is reversely proportional to the charge intensity and can be written by Equation \ref{eq:tau}.
+\noindent where $ Ah_{restored} $ represents the Ampere-hour stored in the battery with regard to the battery capacity ($ C $) during this hour.
+
+The function assumes that 95\% of the capacity has already been restored at the start of overcharge.
+
+The time constant of the phenomenon ($ \tau $) is inversely proportional to the charge intensity and can be written as Equation \ref{eq:tau}.
 
@@
 
-Therefore, to model the voltage ($ V_{c} $) evolution of the battery, equation \ref{eq:Vcbat} can be used up the start of gassing ($ V_{c} \leq V_{g} $).
-And during overcharging ($ V_{c} > V_{g} $), Equation \ref{eq:Voverc} can be used until a constant final voltage ($ V_{ec} $) is reached.
-
-The storage capacity of the battery can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
+Equation \ref{eq:Vcbat} can therefore be used to model the voltage ($ V_{c} $) evolution of the battery, at the start of gassing ($ V_{c} \leq V_{g} $).
+During overcharging ($ V_{c} > V_{g} $), Equation \ref{eq:Voverc} can be used until a constant final voltage ($ V_{ec} $) is reached.
+
+The battery's storage capacity can be calculated using Equation \ref{eq:stor}, as defined in \cite{Wenham}.
 
@@
 
-Where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
-
-As an example of this formula application, as shown by \cite{Abdulateef}, considering that an off-grid PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of discharge for the battery $DOD$ of $0.8$ and battery efficiency $80\%$.
-
-Then the storage capacity using Equation \ref{eq:stor} becomes $56.3 kWh$.
+\noindent where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
+
+As an example of this formula's application, as shown in \cite{Abdulateef}, considering that an off-grid PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of battery discharge $DOD$ of $0.8$ and battery efficiency at $80\%$.
+
+Using Equation \ref{eq:stor}, the storage capacity then becomes $56.3 kWh$.
 Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$).
-If a single battery of 12 V and 350 Ah is considered, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
-
-At this research, it was considered a simplified model for charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) of the batteries, even considering that the process is not linear and depends on the temperature.
+If a single battery is 12 V and 350 Ah, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
+
+In this study, a simplified model for battery charging (Equation \ref{eq:charge}) and discharging (Equation \ref{eq:discharge}) was considered, even recognizing that the process is not linear and is temperature-dependent.
 The equations are used to update the $SOC$ of the batteries, and have the number of hours ($ Num_{h} $) as a variable.
-There is a factor (1.15) which is present at the charging equation, and is necessary to express that during the charging process is usual to reach 115\% of the battery capacity
+There is a factor (1.15) which is present in the charging equation, and is necessary to express that during the charging process it is usual to reach 115\% of the battery capacity.
 
@@
 
-Worth to mention that, specifically to PV systems used in Brazil, there is a Normative Resolution issued by the Brazil National Electric Energy Agency (Aneel) that establishes the minimum of 48 hours of battery autonomy to stand-alone solar PV systems (RN 493/2012), among others definitions related to this matter.
+It is worth mentioning that, specifically for PV systems used in Brazil, a Regulation (RN 493/2012), issued by the Brazilian Electricity Regulatory Agency (Aneel) establishes a minimum of 48 hours of battery autonomy for stand-alone solar PV systems, among others related definitions.
 

### 2019-12-30 Tex/Old text/chapters/chapter02.tex
Thesis update

@@
 
-Manufacturers and integrators also have their own proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback of just including´ their own products among the possibilities of choice.
+Manufacturers and integrators also have their own proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback of just including their own products among the possibilities of choice.
 In this study, the most widely used tools are presented:
@@
 
-Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
+The controller is named differently by different authors: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}.
 However, in this study, in order to simplify, the term used is controller.
 
-The controller is a set of items (DC-DC converter, a MPPT and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+The controller is a set of items (DC-DC converter, a MPPT and switches) and can be defined as the responsible for managing the energy flow to the PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
 According to \cite{Pinho}, controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.
 
-Controllers with MPPT mechanism are the mostly used nowadays,  and it maintains the PV operating at the stage of maximum power.
+Currently, controllers with MPPT mechanisms are the most widely used nowadays,  and they maintain the PV operating at the stage of maximum power.
 
 As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components.
-The use of battery as a storage form implies thus the presence of a charge controller.
+The use of a battery as a storage form thus implies the presence of a charge controller.
 
@@
 
-In \cite{Mellit} was established that the controller allows the management of energy between the load and the battery.
-The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
-The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).
-
-According \cite{Hansen}, to protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and when the current required by the load is less than the current delivered by the PV arrays.
+\cite{Mellit} established that the controller allows the management of energy between the load and the battery.
+The input signals for the regulator model are the battery current ($ I_{br} $), the PV generator's voltage ($ V_{PV} $), the PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
+The outputs are battery current ($ I_{rb} $) and used current ($ I_{u} $).
+
+According to \cite{Hansen}, in order to protect the battery against an excessive charge, the PV arrays are disconnected from the system, whenever the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and whenever the current required by the load is less than the current delivered by the PV arrays.
 PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $.
@@
 
-To protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold i and when the current required by the load is larger than the current delivered by the PV arrays \cite{Hansen}.
-The load is reconnected to the system, when the terminal voltage is above a certain value i, using a switch with a hysteresis cycle, as shown in Fig.
+To protect the battery against excessive discharge, the load is disconnected whenever the terminal voltage falls below a certain threshold $i$ and when the current required by the load is larger than the current delivered by the PV arrays \cite{Hansen}.
+The load is reconnected to the system, when the terminal voltage is above a certain value $i$, using a switch with a hysteresis cycle, as shown in Fig.
 \ref{fig:controllerdisc}.
@@
 
-Regarding the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage.
-
-As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by PV array to the voltage required by the load.
-The output power ($ P_{out} $) of DC-DC converter is given by Equation \ref{eq:poutcont}.
+As to the DC-DC converter, the most basic idea is that the power is converted while altering the current and voltage.
+
+As shown in \cite{Abdulateef}, the DC-DC converter is used to increase the efficiency of the PV system by matching the voltage generated by the PV array to the voltage required by the load.
+The output power ($ P_{out} $) of the DC-DC converter is given by Equation \ref{eq:poutcont}.
 
@@
 
-Assuming that the efficiency of the controller ($ \eta_{c} $) is a manufacturer's data, from Equation \ref{eq:poutcont} is possible to reach Equation \ref{eq:potcont}.
+Assuming that the efficiency of the controller ($ \eta_{c} $) is data provided by the manufacturer, from Equation \ref{eq:poutcont} it is possible to reach Equation \ref{eq:potcont}.
 
@@
 
-Where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the current output of PV array, $ V_{out}$ is the  DC bus voltage, and $I_{out}$ is the output current from the converter, when all the other values are known.
-
-Worth to mention that $ V_{out}$, depending on the PV panel generation and on the batteries charge, it can be the voltage that charges the battery $V_{b}$ (which is bigger than the nominal voltage of the batteries), the voltage that is feed by the batteries (the same $V_{b}$ but with levels that can be lower than it, or even the voltage that comes from the PV panels and depends on the MPPT system employed by the controller.
-
-The output voltage is related to the input voltage as a function of duty cycle of the switch (\cite{Abdulateef}).
+\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the current output of the PV array, $ V_{out}$ is the  DC bus voltage, and $I_{out}$ is the output current from the converter, when all the other values are known.
+
+It is worth mentioning that, depending on the PV panel generation and on the batteries charge, $ V_{out}$ can be the voltage that charges the battery $V_{b}$ (which is greater than the nominal voltage of the batteries), the voltage that is feed by the batteries (the same $V_{b}$ but with levels that can be lower), or even the voltage that comes from the PV panels and depends on the MPPT system employed by the controller.
+
+The output voltage is related to the input voltage as a function of the duty cycle of the switch (\cite{Abdulateef}).
 
@@
 
-For the Cuk converter, the relationship is expressed by \ref{eq:voutvin} as show in \cite{Abdulateef}.
+For the Cuk converter, the relationship is expressed by Equation  \ref{eq:voutvin} as shown in \cite{Abdulateef}.
 
@@
 
-Where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
+\noindent where $D$ is the duty cycle or ratio of the circuit converter, i.e., it is defined as the ratio of the on time of the switch to the total switching period.
 
@@
 
-Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown by \cite{Haque}.
-
-As the MPPT definition and the equations to get the maximum power from the PV panels was described at the end of the PV panel modeling, the important here is to notice that the Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
+Various types of MPPT schemes are proposed by researchers, namely open circuit, short circuit, perturb and observe (P\& O)/hill climbing, incremental conductance, and so forth, as shown in  \cite{Haque}.
+
+As the MPPT definition and the equations to get the maximum power from the PV panels were described at the end of the PV panel modeling, what is important here is that Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
 
 \subsubsection{The inverter model}
-As shown by \cite{Mellit}, the PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
-An inverter is a converter, where the power flows from DC to AC side, i.e., having a DC voltage as input; it produces AC voltage, as output.
-The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage (127 V or 220 V, for example), and to convert the input power $ P_{in} $ into the output power $ P_{out} $ with the best possible efficiency \cite{Hansen}.
-
-The inverter is characterized by a power dependent efficiency $ \eta_{i} $ given by \cite{Hansen} as shown by Equation \ref{eq:efficinv}.
+As shown by \cite{Mellit}, PV arrays produce DC and therefore when the PV system contains an AC load, DC/AC conversion is required.
+An inverter is a converter, where the power flows from the DC to the AC side, having DC voltage as input and producing AC voltage as output.
+The role of the inverter is to keep the voltage constant on the AC side, i.e., at the rated voltage (127 V or 220 V, for example), and to convert input power $ P_{in} $ into  output power $ P_{out} $ with the best possible efficiency \cite{Hansen}.
+
+The inverter is characterized by a power dependent efficiency $ \eta_{i} $ given by \cite{Hansen} as shown by Equation in  \ref{eq:efficinv}.
 
@@
 
-Where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be found from the inverter's data-sheet.
-
-Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model).
+\noindent where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be found from the inverter's data-sheet.
+
+Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feeds the inverter (which is obtained by this study model).
 
@@
 
-Each stand-alone PV system, like any other power systems, has a specific level of availability.
-This reliability level impacts various issues, as system performance, production, feasibility, and investment.
-
-The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
+Each stand-alone PV system, like any other power system, has a specific level of availability.
+This reliability level impacts various issues: system performance, production, feasibility, and investment.
+
+The availability of a stand-alone PV system can be defined as the percentage of time during which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
 The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
-The system availability definition depends on how critical the load application is.
-For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable.
+The definition of system availability depends on how critical the load application is.
+For critical loads, 99\% is considered acceptable, while in an ordinary house electrical load, 95\% is considered acceptable.
 
@@
 
-With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong.
-It is important to evaluate how critical the load application is and the horizon of evaluation.
-However this analysis can be useful, for example, to improve the sized battery autonomy.
+With that in mind, it is important to mention that even if formal verification or a simulation shows that a PV system fails, this  does not mean that the sizing is wrong.
+It is important to evaluate how critical the load application is and the evaluation period.
+However, this analysis can be useful, for example, to improve sized battery autonomy.
 
@@
 
-The mathematical model presented at section~\ref{model} is important for the project validation, however if it is included an approach to perform the sizing of stand-alone PV systems, than the proposed tools at this Thesis can perform the system validation (the intended behavior), and moreover to obtain the optimal project sizing.
+The mathematical model presented in section~\ref{model} is important for project validation; however if an approach is used to perform the sizing of stand-alone PV systems, then the tool proposed in this thesis can perform system validation (the intended behavior), and moreover obtain optimal project sizing.
 
 The sizing check stage can ensure that the system meets the standard project steps related 
-to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller,
-which is the most common one in practice. Firstly, we need to correct the energy consumption estimated to the load 
+to the critical period method for solar energy system sizing~\cite{Pinho} and adopting a MPPT (Maximum Power Point Tracking) charge controller,
+which is the most common one in use. Firstly, we need to correct the energy consumption estimated for the load 
 ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
@@
 
-We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
+We also need to estimate the energy that can be produced by each panel, called $E_{p}$, in Watt-hour ($Wh$), defined as
 %
@@
 \noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
-the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
+the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents PV panel efficiency.
+The total minimum number of solar panels needed ($N_{TPmin}$) is computed as
 %
@@
 
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
+Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) is respectively given by
 %
@@
 $P_{total}$ is the total power demanded from the PV system and 
-$P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
+$P_{max,ref}$ is the power supplied by one PV panel in $Watts$.
+As for batteries, we must first define the total capacity of the battery bank, which can be described as
 %
@@
 
-\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-%
-Secondly, the total number of batteries is computed as
+\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$ hours; 
+$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery depth of discharge (considered the maximum of 25\% here).
+%
+Second, the total number of batteries is computed as
 
@@
 
-Moreover, the Equation \ref{eq:batcheck} perform the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted by the project.
+Equation \ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted by the project.
 
@@
 
-Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
+The charge controller must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem}.
+
 \begin{equation}
@@
 The short circuit reference information from the manufacturer's solar panel must be corrected 
-to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, 
-and PV system is temperature dependent, as 
+to the cell temperature because field temperature is higher than  nominal or laboratory temperature, 
+and the PV system is temperature dependent, as shown by Equation~\eqref{eq:iscamb}. 
 %
@@
 
-The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin} as
+The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin}.
 %
@@
 The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
-In addition, the final sizing check is did by Equation \ref{eq:numberofc}, who validate the number of controllers adopted.
+In addition, the final sizing check is performed by Equation \ref{eq:numberofc}, which validates the number of controllers adopted.
 
@@
 
-Some models of inverters allow parallel operation of more than one unit, besides the integration in order to create bi-phase and three-phase circuits.
-It is advised the use of pure sine wave inverter, especially for cases where are used electronic loads sensitive to harmonic distortion waves.
-
-Moreover, it is important to verify the compatibility between charge controller and inverter, because there are some models that do not accept to work with brands of different manufacturers.
+Some inverter models allow parallel operation of more than one unit, besides the integration in order to create bi-phase and three-phase circuits.
+It is advisable to use pure sine wave inverters, especially for electronic loads sensitive to harmonic distortion waves.
+
+Moreover, it is important to verify the compatibility between charge controller and inverter, because there are some models that are not compatible with equipment from other manufacturers.
 
@@
 In order to select an optimal combination to meet sizing constraints, 
-it is necessary to evaluate power reliability and system cost analysis for the underlying system. An ideal combination of any PV system is made by the best compromise between these two objectives.
-
-During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
-The reason is because solar energy production is intermittent and, therefore, the energy generated usually will not match with the load demand.
-A reliable power is a generation system that has sufficient power to feed load demand in a period.
-
-There exist different methods to express system reliability, where the most popular ones 
+it is necessary to evaluate power reliability and analyze system cost for the underlying system. A PV system is best produced when there is an ideal compromise between these two objectives.
+
+During the PV system design, one of the most important aspects in ensuring power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
+The reason is that solar energy production is intermittent and, therefore, the energy generated will usually not match the load demand.
+Reliable power is a generation system that has sufficient power to feed load demand in a period.
+
+There are different methods of expressing system reliability, where the most popular ones 
 are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
@@
 
-LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
+LOLP is the probability for the case when load demand exceeds the power generation of the PV system.
 On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
-On the other hand, LPSP is defined as the probability of the case when system generates insufficient power to satisfy the load demand.
-The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance.
-However, data is not always available and dynamic analysis is complex; and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
-
-Related to economic analysis, there exist various methods available.
-The main objective is to determine whether the project has an acceptable investment; the usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability and lowest cost~\cite{Alsadi2018}.
-The common methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
+On the other, LPSP is defined as the probability of the system generating insufficient power to satisfy the load demand.
+The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing in system performance.
+However, data is not always available and dynamic analysis is complex; and this is a drawback of both LOLP and LPSP~\cite{Alsadi2018}.
+
+Various methods of economic analysis are available.
+Their main objective is to determine whether the project is an acceptable investment.
+The usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability at the lowest cost~\cite{Alsadi2018}.
+The most commonly used methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
 
@@
 
-LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
-LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
-
-LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}.
+LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
+The LCOE method is useful in comparing different generations of technology with different operating characteristics~\cite{Zhou2010}.
+
+LCC is the estimation of the current value of the sum of the installation cost, the operation and maintenance of a PV system for a period of time~\cite{Applasamy2011}.
 Eq.~\eqref{eq:LCC} is used to calculate LCC of a PV system,
@@
 \end{equation}
-\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs
-in present worth.
+
+\noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current prices.
 
@@
 
-In order to recommend an optimal configuration for PV systems, 
+In order to recommend an optimal configuration for a PV system, 
 the designer has to evaluate the design based on optimization variables. 
-As the number of optimization variables increases, the computational effort 
-will increase as well. Hence, to obtain the best PV system design as well as 
-simplified sizing process, prior work introduced three main techniques 
-for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
-
-Intuitive method is simple, easy to be implemented, and can be used to give 
-rough suggestion for preliminary design. The sizing rules are based on designer's experience, 
-using lowest performance either in a time period data or by directly using average value 
-(daily, monthly, or annual) of solar irradiance. This method does not consider the battery's 
-state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
-
-For numerical method, the design is simulated for each time step within a period. 
-State of charge of batteries is calculated and investigated. It is very accurate, 
-however is complex, demanding more time for calculation~\cite{Park2004}.
-
-Analytical methods is used to obtain a close relation or correlation in a form 
-of equation between capacities and reliabilities. The sizing task becomes much simpler 
-than numerical technique; however, the relation cannot be applied to different sites
-since it is specific to one place of deployment of the PV system, 
-thereby demanding adaptation if another site is analyzed.
+As the number of optimization variables increases, the computational effort will increase accordingly.
+Hence, to obtain the best PV system design as well as a simplified sizing process, three main techniques have been presented in the literature for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Zhou2010}.
+
+The intuitive method is simple, easily implemented, and can be used to give a rough suggestion for the preliminary design.
+The sizing rules are based on the designer's experience, using lowest performance data for a time period or by directly using average value (daily, monthly, or annual) of solar irradiance.
+This method does not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
+
+in the numerical method, the design is simulated for each time step within a period.
+Battery state of charge is calculated and investigated.
+Although very accurate, it is also complex, demanding more calculation time~\cite{Park2004}.
+
+Analytical methods are used to obtain a close relation or correlation in the form of an equation between capacities and reliabilities.
+The sizing task becomes much simpler than in the numerical technique; however, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
 
@@
 
-At this Section, all the background and theoretical base needed to understand the concepts, techniques, tools, and criteria used during the following Sections were presented.
-
-A historical explanation about the origin of the formal methods until to reach modern model checkers was presented.
-It was highlighted the importance of computers evolution in order to allow the automation of formal verification.
-If we were stuck in time, probably the formal verification was being made by hand until nowadays.
-
-Is was pointed out the importance of mathematical rigor to the models and representation of systems, and that automated verification method can be applied to any kind of systems (from simple ones to the complex ones)
-
-State-of-art automated verification tools were described with relation to their characteristics and techniques.
-Simulation tools were described as well and the reason why HOMER Pro was the one chosen to the comparative.
-
-It was explained how to validate a system, comparing test, simulation and automated verification techniques.
+In this Section, all the background and theoretical base needed to understand the concepts, techniques, tools, and criteria used during the following Sections were presented.
+
+A historical explanation was presented of the origin of formal methods, culminating with modern model checkers.
+The evolution of the computers was highlighted as essential to the automation of formal verification.
+If we were stuck in time, formal verification would probably still be being done by hand.
+
+The importance of mathematical rigor to the models and representation of systems was emphasized, and that the automated verification method can be applied to any kind of system (from the most simple to the most complex).
+
+State-of-the-art automated verification tools were described with respect to their characteristics and techniques.
+Simulation tools were also described and the reason why HOMER Pro was the chosen for the comparison was explained.
+
+System validation methods were explained, comparing test, simulation and automated verification techniques.
 It was possible to demonstrate that only automated verification can prove the absence of system flaws.
 
-The method of critical period solar energy method was presented as the chosen one for sizing solar PV systems.
-Following, the criteria and techniques for optimal sizing of PV systems were highlighted as well.
+The method of critical period solar energy sizing was presented as the one chosen for sizing solar PV systems.
+Following that, the criteria and techniques for optimal sizing of PV systems were also described.

### 2019-12-31 Tex/Old text/abstract.tex
Thesis update

@@
 \end{center}
-With decreasing costs and increasing performance, the deployment of renewable energy systems is now growing faster now than in the past decade.
+With decreasing costs and increasing performance, the deployment of renewable energy systems is growing faster now than in the past decade.
 In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends in energy access still fall short of global goals.
@@
 However, the use of formal methods to model and validate any system has grown with time, mainly to find bugs in sophisticated hardware and software systems: they aim to establish system correctness with mathematical rigor.
-The use of formal methods in electrical systems is a new subject, with published research spanning only in the last four years.
-Moreover, the use of automated synthesis in order to obtain the optimal sizing of solar photovoltaic systems has never been done before.
-This thesis marks the achievement of two major goals: first, the application of software model checking to verify formally the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load; second, a sound and automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis.
-For the  formal verification, we used case studies from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, in order to evaluate the proposed approach and to compare it with a specialized simulation tool.
+The use of formal methods in electrical systems is a new subject, with published research spanning only the last four years.
+Moreover, the use of automated synthesis in order to obtain optimal sizing of solar photovoltaic systems has never been done before.
+This thesis marks the achievement of two major goals: first, the application of software model checking to verify formally the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load; second, a sound, automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis.
+For the formal verification, we used case studies from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1.200 W, in order to evaluate the proposed approach and to compare  it with a specialized simulation tool.
 Different verification tools are evaluated also, in order to compare performance and soundness.
@@
 
-\textit{Keywords}: Formal verification; automated verification; model checking; program synthesis; electrical systems; and solar photovoltaic systems.
+\textit{Keywords}: Formal verification; automated verification; model checking; program synthesis; electrical systems; solar photovoltaic systems.

### 2019-12-31 Tex/Old text/chapters/chapteroptimization.tex
Thesis update

@@
 %---------------------------------------------------------------------------
-\section{Optimization Case studies} 
+\section{Description of the case studies} 
 %---------------------------------------------------------------------------
@@
 
-These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{TrindadeCordeiro19, Agrener2013}.
 With exception of case 7 that was idealized as a small town solution to support few lamps and an 12 kBTUs air-conditioner.
@@
 \section{Objectives and Setup}
+\label{sec:synthesissetup} 
 %---------------------------------------------------------------------------
@@
 Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., 
-it was not solved within $240$ minutes. However, if it is removed 
-this time out limitation from CPAchecker, the verifier is 
+it was not solved within $240$ minutes. This is depicted in Fig.~\ref{fig:cpaoptcase7}. However, if it is removed this time out limitation from CPAchecker, the verifier is 
 able to solve the optimization in $44.97$ hours. 
@@
 \label{fig:CPAoptc1}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=1.0\textwidth]{CPAchecker_timeout_case7.png}
+\centering
+\caption{CPAchecker time out result for case 7 optimization (file CPALog.txt).}
+\label{fig:cpaoptcase7}
 \end{figure}

### 2019-12-31 Tex/Old text/chapters/chapterverification.tex
Thesis update

@@
 Moreover, the proposed flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
-Those three steps are the high level description of how the automated verification, applied to solar PV systems, works.
+Those three steps are the high level description of how the automated verification method can be used to validate solar PV systems.
 
@@
 %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
-These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}.
+These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{TrindadeCordeiro19, Agrener2013}.
 
@@
 \subsection{ESBMC}
+\label{sec:ESBMCverification}
 
@@
 \subsection{CPAchecker}
+%\label{sec:CPAresult1}
 

### 2019-12-31 Tex/Old text/chapters/introduction.tex
Thesis update

@@
 
-The main objective of this dissertation is thus to create a new approach of formal methods and evaluate it as a solution to research issues pertaining to solar PV systems.
+The main objective of this thesis is thus to create a new approach of formal methods and evaluate it as a solution to research issues pertaining to solar PV systems.
 We therefore adopt specific computer science techniques to tackle specific issues of PV systems, such as design validation and sizing optimization.

### 2019-12-31 Tex/Old text/resumo.tex
Thesis update

@@
 O uso de métodos formais em sistemas elétricos é um assunto recente, com pesquisas sendo publicadas apenas nos últimos quatro anos.
+Além disso, a síntese automatizada nunca foi usada antes para obter um ótimo dimensionamento de sistemas solares fotovoltaicos .
+Esta tese marca duas conquistas principais: (1) a primeira aplicação de verificação de modelos de \textit{software} para verificar o projeto de um sistema isolado solar fotovoltaico, incluindo painel solar, controlador de carga, bateria, inversor e carga elétrica; e (2) uma abordagem confiável e automatizada para obter o dimensionamento ótimo de sistemas fotovoltaicos usando a síntese de programas onde cada componente e função de um sistema solar fotovoltaico é descrito, incluindo suas propriedades, e o modelo comportamental que representa o dimensionamento ótimo é sintetizado automaticamente.
+Relacionado à verificação formal, estudos de caso de sistemas fotovoltaicos reais instalados em cinco localidades diferentes são usados para avaliar a abordagem proposta e para compará-la com ferramenta de simulação especializada.
+Diferentes ferramentas de verificação são avaliadas também, a fim de comparar o desempenho e a confiabilidade dos resultados.
+Dados de aplicações práticas mostram a eficácia da abordagem proposta, onde condições específicas que levam a falhas em um sistema solar fotovoltaico são detalhadas apenas pelo método de verificação automatizado.
+Além disso, em relação ao uso da síntese de programas, propõe-se uma variante do método de síntese indutiva guiada por contraexemplos (CEGIS), com duas fases bem definidas: primeiro, ele sintetiza o dimensionamento de sistemas fotovoltaicos baseados em confiabilidade de energia, mas que pode não alcançar o menor custo; segundo, a solução proposta é então verificada iterativamente com um limite inferior via verificação de modelo simbólico.
+Se a etapa de verificação não falhar, o limite inferior será ajustado; e se falhar, o contraexemplo é fornecido com o dimensionamento ótimo, vinculando assim a resposta técnica da primeira fase à análise de custo da segunda fase.
+Os dados de equipamentos comerciais de diferentes fabricantes são fornecidos ao mecanismo de síntese e as soluções candidatas são derivadas da análise financeira do dimensionamento obtido.
+O método de síntese proposto é novo e sem precedentes para simplificar o projeto de sistemas fotovoltaicos.
+Resultados experimentais usando sete estudos de caso mostram que o nosso método de síntese é capaz de produzir em um tempo de execução aceitável o dimensionamento ótimo do sistema fotovoltaico, e um comparativo com uma ferramenta de simulação especializada e sistemas fotovoltaicos reais mostra a eficácia da abordagem adotada.
+%Com custos decrescentes e com melhoria de desempenho, a implantação de sistemas de energia renovável está crescendo cada vez mais rapidamente no mundo.
+Em 2017, pela primeira vez, o número de pessoas sem acesso a eletricidade ficou abaixo de 1 bilhão, mas os dados quanto à universalização do acesso a energia ficaram aquém das metas globais.
+Particular atenção é dada aos sistemas isolados solares fotovoltaicos em áreas rurais ou onde a extensão da rede é inviável.
+Ferramentas para avaliar ou dimensionar projetos de eletrificação estão disponíveis, mas elas são baseadas em simulações que não cobrem todos os aspectos do espaço de projeto.
+Por outro lado, o uso de métodos formais para modelar e validar qualquer tipo de sistema está crescendo com o tempo, principalmente para encontrar bugs em sistemas complexos de \textit{hardware} e \textit{software}: seu objetivo é estabelecer a corretude do sistema com rigor matemático.
+O uso de métodos formais em sistemas elétricos é um assunto recente, com pesquisas sendo publicadas apenas nos últimos quatro anos.
 Além disso, a síntese automatizada nunca foi usada antes para obter um ótimo dimensionamento de sistemas solares fotovoltaicos nunca foi feito antes.

### 2020-01-01 Tex/Old text/chapters/chapterverification.tex
Thesis update

@@
-In this Chapter, we detail the adopted methodology to perform formal verification of stand-alone solar PV systems using formal methods, more specifically model checking.
+In this Chapter, we detail the methodology adopted to perform formal verification of stand-alone solar PV systems using formal methods, more specifically model checking.
 Diagrams, flowcharts, and algorithms support and explain the solutions.
-The experimentation, case studies, and results are present as well.
-Moreover, there is the comparative with a specialized simulation tool, and even the use of different verifiers who perform the automated verification in order to evaluate performance.
-Tables, commented reports, and graphical outputs are presented to aid the understanding.
+The experimentation, case studies, and results are also presented.
+In addition, the Chapter contains a comparison with a specialized simulation tool, and also the use of different verifiers that evaluate performance by means of automated verification.
+Tables, commented reports, and graphic outputs are presented to aid  understanding.
 
-Besides that, we present all the assumptions and premises adopted.
-Both support the results/conclusions, with direct impact on it.
-Usually, a premise is an unquestionable fact, however assumptions can be questionable.
-Unlike the premise, assumptions are not explicitly stated and need to be deciphered.
-With that in mind, we perform a detailed explanation of assumptions all over this Chapter.
+Additionally, we present all assumptions and premises adopted, all of which support the results/conclusions, with direct impact on them.
+Usually, a premise is an unquestionable fact, however assumptions can be questioned.
+Unlike premises, assumptions are not explicit and need to be deciphered.
+With that in mind, we perform a detailed explanation of all assumptions over the course of the Chapter.
 
-It is important to emphasize that the whole explanation about the theoretical basis of the subject discussed here is present in the previous chapter, ~\nameref{chap:background}.
-In addition, we do suggest that previous reading must be done to facilitate the understanding.
+It is important to emphasize that the theoretical basis of the subject presented in this chapter was discussed in Chapter 1, ~\nameref{chap:background}.
+In addition, knowledge of the literature is essentila to aid understanding.
 
@@
 
-Fig.~\ref{fig:validation} illustrates how a stand-alone solar PV project can be validated, passing through the traditional techniques, as manual, simulation, testing, and including the proposed automatic verification that is detailed in this Section.
+Fig.~\ref{fig:validation} illustrates how a stand-alone solar PV project can be validated, starting with the traditional techniques - manual, simulation, testing, only then including the proposed automatic verification that is detailed in this Section.
 
-Note that, in one hand, the input information is the same for all the techniques, with the difference that in automated validation it is possible to define the bound $k$ to restrict the space-design search.
-Among the inputs it is possible to list: location weather data (temperature, solar irradiance, and solar insolation); system sizing information regarding specifications and configuration of PV panels, charge controller, inverter, batteries, DC bus  voltage; and requirements (battery autonomy, electric load demand, electric peak power demand, energy consumption, load curve, and AC voltage).
+Note that, on the one hand, although the input information is the same for all the techniques, automated validation is different in that it is possible to define the bound $k$ to restrict the space-design search.
+Among the possible inputs are: weather data at the location (temperature, solar irradiance, and solar insolation); system sizing information regarding specifications and configuration of PV panels, charge controller, inverter, batteries, DC bus  voltage; and requirements (battery autonomy, electric load demand, electric peak power demand, energy consumption, load curve, and AC voltage).
 
-However, in the other hand, the outputs are not equal, as the design-space coverage and the information presented as result.
-Regarding the design-space, it was shown in  chapter \nameref{chap:background} that the most complete coverage is performed by automated verification, event using the bound $k$ to restrict the search, because is not necessary to unbound completely the system in order to found a design flaw.
-Moreover, testing and simulation depends on the test vector used as input to evaluate the system.
+In contrast, the outputs are not equal - design-space coverage and the information presented as result.
+Design-space coverage was shown in chapter \nameref{chap:background} to be the most complete when performed by automated verification, event using the bound $k$ to restrict the search, it not being necessary to unbound the system completely in order to discover a design flaw.
+Moreover, testing and simulation depend on the test vector used as input to evaluate the system.
 
-About the results presented by the methods, a project validation done 'by hand' is just a piece of paper produced; simulation software produce fail, success information and can additionally to present the optimized design if the evaluated has some flaw, with graphics and reports; testing (using laboratory or field) is done using measurement equipment and/or data from monitoring systems.
-Automated verification, proposed at this Thesis, presents fail, success information as well, however the output is not graphical (as will be shown in the  \autoref{chap:automatedverification}), summarized by reports with details about the variables and states of the project that causes a project flaw (in the case where is detected a design fail).
+With respect to the results presented, a project validated manually is just a piece of paper; simulation software produces success - fail information and can additionally present the optimized design if the system evaluated has some flaw, with graphics and reports; testing (whether laboratory or field) uses  measurement equipment and/or data from monitoring systems.
+Automated verification, as proposed in this thesis, presents success-fail information also, however the output is not graphic  (as will be shown in the  \autoref{chap:automatedverification}), is summarized in reports with details about the variables and states of the project that cause a project flaw (in this case,  where a design flaw is detected).
 
@@
 \centering
-\caption{Comparative of project validation methods}
+\caption{Project validation methods compared}
 \label{fig:validation}
@@
 
-Starting at his point, it will be showed how is done the proposed automated verification of stand-alone solar PV systems.
+Starting at his point, it will be shown how the proposed automated verification of stand-alone solar PV systems functions.
 
-The process begins with the conversion of the real PV system into a model.
-The Fig.
-\ref{fig:systemverif4} shows how a real solar PV system is equivalent and converted to a model in order to be verified by a model checking.
+The process begins with the conversion of a real PV system into a model.
+Fig.
+\ref{fig:systemverif4} shows how a real solar PV system is equivalent and converted to a model in order to be verified by model checking.
 
-This illustration is a adaption from the general process of real system conversion depicted in Fig.~\ref{fig:systemverif}, detailing the inputs, outputs, and requirements of a real solar PV system.
+Fig.~\ref{fig:systemverif} is an adaptation of the general process of real system conversion detailing the inputs, outputs, and requirements of a real solar PV system.
 
-Worth to mention that the model checking process is the same independently of the system that is validated, and the important is to chose a accurate model, to define the requirements/constraints, and to get correct information from the system components, in order to get sound and effective validation,
+It is important to bear in mind that the model checking process is the same whatever the system that is being validated; what is  important is to choose an accurate model, define the requirements/constraints, and get correct information from the system components, in order to achieve sound and effective validation.
 
@@
 
-Moreover, the proposed flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
-Those three steps are the high level description of how the automated verification method can be used to validate solar PV systems.
+The flowchart proposed for the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
+The three steps are the high level description of how the automated verification method can be used to validate solar PV systems.
 
@@
 
-In \textbf{Step 2}, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system.
-This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.
+In \textbf{Step 2}, the sizing check of the PV system takes place: indicating if there is a sizing error before performing the automated verification of the system.
+This stage ensures that the system follows the standard project steps of the critical period method of sizing~\cite{Pinho}.
 
-\textbf{Assumption:} before the automated verification, who performs the verification of the intended system behavior, is performed the sizing checking of the system.
-Moreover, if there is some error, the process stops, showing where is the sizing error.
+\textbf{Assumption:} before the automated verification, which performs the verification of the intended system behavior, the sizing check of the system is performed.
+On the discover of an error, the process stops, showing the sizing error.
 
-\textbf{Assumption:} Sizing check is performed using critical period criteria.
+\textbf{Assumption:} The sizing check is performed using critical period criteria.
 
-In \textbf{Step 3}, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed.
+In \textbf{Step 3}, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site where the PV system will be deployed.
 %As a consequence, all the formulae of the employed mathematical models will also be updated. 
@@
 is it SAT?}
-In a nutshell, the model checker will process the ANSI-C code with constraints ($C$) and properties ($P$) from the PV system, and the tool will automatically verify if the PV system requirements are met.
-If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design.
-However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
+In short, the model checker will process the ANSI-C code with constraints ($C$) and properties ($P$) of the PV system, and the tool will automatically verify if the PV system requirements are met.
+If it returns a failure (i.e.
+SAT), then the tool provides a counterexample, i.e.
+a sequence of states that leads to the property violation; this information can be used as feedback to improve the PV system design.
+However, if the verification succeeds (i.e.
+UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
 
@@
 % caused by the state explosion inherent of the technique, 
-every 24 h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where it is possible to occur PV generation, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes all the remaining day (without any PV generation), when the batteries are demanded to feed the house.
+every 24 h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where PV generation is possible, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes the rest of the day (with no PV generation), when the batteries are required to feed the house.
 
-\textbf{Assumption:} day is divided in two parts (when there is and there is not PV generation, based in historical data from the location).
-Considering average temperature and solar irradiance (for every hour of the day) and the annual solar insolation (per day).
+\textbf{Assumption:} The day is divided into two parts (representing presence or absence of PV generation, based on historical data from the location), considering average temperature and solar irradiance (for every hour of the day) and  annual solar insolation (per day).
 
-Lines 1 is devoted to information from the location where the PV system will be/were deployed.
-We use annual average minimum and maximum, related to temperature ($T$) and solar irradiance ($G$), hour by hour, from~\cite{Temperature}, and ~\cite{Irradiance}.
+Lines 1 carries information from the location where the PV system will be/was deployed.
+We use the average annual minimum and maximum, both for temperature ($T$) and solar irradiance ($G$), hour by hour, from~\cite{Temperature}, and ~\cite{Irradiance}.
 
-\textbf{Premise:} The availability of temperature, solar irradiance, and solar insolation data from the location where the solar PV system will be used.
+\textbf{Premise:} Temperature, solar irradiance, and solar insolation data is available pertaining to the location where the solar PV system will be used.
 
-Line 2 represents all the information that comes from the PV sizing and from the equipment manufacturers data: specification and data from PV, batteries, inverter and charge controller.
-This item includes as information from the house's load curve.
+Line 2 represents all the information that derives from the PV sizing and from the equipment manufacturer's data: PV, battery, inverter and charge controller specification and data.
+This item also includes information from the house's load curve.
 
-\textbf{Premise:} Availability of data sheet from every element of the solar PV system to be validated.
+\textbf{Premise:} The data sheet of every element of the solar PV system to be validated is available.
 
-\textbf{Premise:} It is necessary the detailed sized project of the PV system in order to perform the validation (list of equipment and configuration, as voltage, current and how they are connected).
+\textbf{Premise:} The detailed, sized project of the PV system is necessary in order to perform the validation (list of equipment and configuration, including voltage, current and how they are connected).
 
-\textbf{Assumption:} Load curve from every house must be estimated or measured.
-Moreover, the time step is of 1 hour, and it is not considered seasonality, i.e., the load curve is the same for the entire year.
+\textbf{Assumption:} The load curve of every house must be estimated or measured.
+Moreover, the time step is 1 hour, and seasonality is not considered, i.e.
+the load curve is the same for the entire year.
 
-The first automated verification is related to the sizing check (line 3), if an error is found then the algorithm stops.
-In order to perform the sizing check, the algorithm uses Equations \eqref{eq:NTPmin}, \eqref{eq:NPSmin}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter.
+The first automated verification is the sizing check (line 3), if an error is found then the algorithm stops.
+In order to perform the sizing check, the algorithm uses Equations \eqref{eq:NTPmin}, \eqref{eq:NPSmin} and \eqref{eq:NPPmin} to verify the PV panel, Equations \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries, Equations \eqref{eq:vcvsystem}, \eqref{eq:icmin} and \eqref{eq:icicmin} to verify the charge controller; and Equations \eqref{eq:vindc}, \eqref{eq:voutac} and \eqref{eq:invcheck} to verify the inverter.
 
-Then, if there is not a sizing design flaw, two functions, called at lines 4 and 5, are responsible for discover which hour starts the PV generation and when stops.
-Those functions get this information from the array inputted to the Algorithm with the solar irradiance values.
+Then, if no sizing design flaw is found, two functions, called at lines 4 and 5, are responsible for discovering at which hour PV generation starts and when it stops.
+These functions receive this information from the array inputted to the Algorithm with the solar irradiance values.
 
-The batteries are assumed to be charged, i.e., with SOC of 100\% (line 6).
+The batteries are assumed to be charged, i.e. with SOC of 100\% (line 6).
 
-\textbf{Assumption:} Batteries are considered charged at the beginning of the project validation.
+\textbf{Assumption:} Batteries are considered charged at the start of project validation.
 
-The first for-loop at line 7 controls how many cycles of 24 h will be performed by the Algorithm.
-And the for-loop from lines 8 to 11 is responsible to discharge the battery (according the load curve) and verify the state of charge of the battery, hour-by-hour, starting at the first hour of the day after the sun goes down until the next day before the sun goes up (without PV generation).
-Following, at the next for-loop, from line 12 to 29, is performed the verification where there is solar irradiance and all the PV system works.
-The Algorithm generates information related to average temperature ($T$) and solar irradiance ($G$), hour-by-hour, using non-deterministic variables from model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range (lines 15 and 16).
+The first for-loop at line 7 controls how many 24 hours cycleswill be performed by the Algorithm.
+And the for-loop from lines 8 to 11 is responsible for discharging the battery (according the load curve) and verifying the state of charge of the battery, hourly, from the first hour of the day after the sun sets to the next day before the sun rises (without PV generation).
+Then, at the next for-loop, from line 12 to 29, verification is performed where there is solar irradiance and the whole PV system works.
+The Algorithm generates information hourly related to average temperature ($T$) and solar irradiance ($G$), using non-deterministic variables from the model checker to explore all possible states and the \textit{assume} macro to constrain the non-deterministic values using a given range (lines 15 and 16).
 %and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
@@
 
-After that, the model from PV generator is used in the function call of line 17, to produce the voltage and current considering the states of $G$ and $T$.
-With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller work as depicted in Table~\ref{table:controller} of Section~\ref{sec:controller}, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.
+After that, the model of the PV generator is used in the function call of line 17, to produce the voltage and current considering the states of $G$ and $T$.
+With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller's work, as depicted in Table~\ref{table:controller} of Section~\ref{sec:controller}, performing the charge or discharge of batteries according to the value of the different variables: if there is PV generation, the updated battery state of charge, the house's load and the PV system set-up information.
 
-At the end of last for-loop, the state of the batteries is verified again (line 27) and the hour is adjusted to the next loop (line 28).
+At the end of the last for-loop, the state of the batteries is verified again (line 27) and the hour is adjusted to the next loop (line 28).
 
@@
 
-Here is listed the assumptions adopted for scientific methods of automated verification developed on this Thesis.
+In order to be clear, we now provide a list of the assumptions adopted by the scientific automated verification methods developed in this thesis.
 
-Regarding the code in ANSI-C created to perform both methods, automated verification and automated synthesis, it was written in order to be the same independently of the verifier used.
-This means that:
+The code in ANSI-C, was created to perform both methods, automated verification and automated synthesis, regardless of the verifier used. This means that:
 
 \begin{itemize}
-\item There is not the use of '\# include' preprocessor directive, so common in the C language, which allows the use of language C libraries, including the mathematical one;
-\item Because of absence of '\# include' directive, it was necessary to create specific mathematical functions at the proposed code in order to calculate the exponential 'exp(x)' or $e^{x}$, and natural logarithm 'log(x)' functions, used for the solar PV model;
-\item There is not the presence of '\# define' preprocessor directive. Therefore were used global variables to replace it;
+\item The '\# include' preprocessor directive is not used, despite being very common in the C language, which allows the use of C language libraries, including the mathematical one;
+\item In the absence of the '\# include' directive, it was necessary to create specific mathematical functions at the proposed code in order to calculate the exponential 'exp(x)' or $e^{x}$, and natural logarithm 'log(x)' functions, used for the solar PV model;
+\item There is no '\# define' preprocessor directive. Therefore, global variables were used to replace it;
 \item The macro 'assert (expression);' must be replaced by 'if (!expression) \{ \_ \_ VERIFIER\_ error();\}'
@@
 \begin{itemize}
-\item It was used a value of bound $k$ to restrict the design-space and improve performance. The chose of value was empirical, after some tests with the code;
+\item A value of bound $k$ was used to restrict the design-space and improve performance. The choice of value was empirical, following tests with the code;
 \item All the PV system model, user requirements, assumptions, and technical information from the PV system equipment are written as an ANSI-C code.
@@
 
-Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
-Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis, however RETScreen do not have stand-alone solar PV system analysis capacity.
+Of the off-the-shelf simulation tools, only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis.
+Additionally, HOMER and RETScreen include economic analysis or even optimization-sensitive analysis; however RETScreen does not have the capacity for stand-alone solar PV system analysis.
 Therefore, in this study, HOMER Pro will be the only simulation tool used to compare with our method.
 
-Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\%, i.e., with DOD maximum of $25$\%, which is common to lead-acid batteries (adopted as standard here), and the AC voltage from the inverter is $127$ V (Brazilian standard).
+For all case studies, the minimum battery state of charge was defined at $75$\%, i.e.
+with a DOD maximum of $25$\%, which is common to lead-acid batteries (adopted as standard here), and the AC voltage from the inverter at $127$ V (Brazilian standard).
 
@@
 %We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with peak power of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).
-It was performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}.
+Five case studies evaluated the proposed approach, as described in Table~\ref{tab2}.
 %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.
-These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{TrindadeCordeiro19, Agrener2013}.
+These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas,  Brazil~\cite{TrindadeCordeiro19, Agrener2013}.
 
-Worth to mention that the load curve represents a array of $24$ integer numbers for every hour of the day (instant power in Watts) and it was estimated after visiting and survey applied in June of $2017$, before the houses were electrified.
+It is important to mention that the load curve represents an array of $24$ integer numbers, one for each hour of the day (instant power in Watts) and it was estimated after visits to the communities and a survey applied in June $2017$, before the houses were electrified.
 
@@
 \end{tabular}
-Legend: (S): Series; (P): Parallel.
+Caption: (S): Series; (P): Parallel.
 \end{scriptsize}
@@
 \item[RQ1] \textbf{(soundness)} Does the automated verification approach provide correct results?
-\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
+\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a commercial simulation tool?
 \end{enumerate}
@@
 %
-All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits.
-The setup of HOMER Pro v3.13.1 was an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB of RAM, running Windows 10.
-The experiments were performed with time out of 240 minutes.
+All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB RAM, running Ubuntu 16.04 LTS 64-bits.
+The setup of HOMER Pro v3.13.1 was an Intel Core i5-4210 (4-cores), with 1.7 GHz and 4 GB RAM, running Windows 10.
+The experiments were performed with a time out of 240 minutes.
 
-Verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the 'incremental SMT' mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled; with SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+The verification engine ESBMC, version v6.0.0 was used with the SMT solver Boolector version 3.0.1~\cite{Brummayer}\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}; and an alternative ESBMC v6.0.0 was used with the 'incremental SMT' mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled; with SMT solver Z3 version 4.7.1~\cite{DeMoura}.
 % with the goal of reducing memory usage.
 
-Verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c -\phantom{}-unwind 100 -\phantom{}-trace}.
+The verification engine CBMC 5.11 and MiniSat 2.2.1 were used in the comparison~\cite{Kroening}\footnote{Command-line: \$ cbmc filename.c -\phantom{}-unwind 100 -\phantom{}-trace}.
 
-Verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
-An alternative CPAchecker configuration was tried as well, using BMC k-induction option, but without improvements of performance or soundness in the results (so it is not reported here).
+The verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
+An alternative CPAchecker configuration was also tried, using the BMC k-induction option, but the results show no improvement in performance or soundness (so it is not reported here).
 
@@
 
-This Section presents the results, with commented outputs produced by every tool, mainly related to the reports (CBMC and ESBMC) and some graphical resources (CPAchecker and ESBMC).
+This Section presents the results, with commented outputs produced by every tool, mainly related to the reports (CBMC and ESBMC) and some graphic resources (CPAchecker and ESBMC).
 
@@
 Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
-Note that an UNKNOWN result from the proposed verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
+Note that an UNKNOWN result from the proposed verification engines does not mean that a failure was found nor that the verification was successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
 
@@
 
-The description of the experimental results can be broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
+The description of the experimental results have been broken down into three parts, one for each verification engine: ESBMC, CBMC, and CPAchecker.
 
@@
 
-Related to ESBMC, it was tried two possibilities: one with Boolector and another one with Z3.
-The 'incremental SMT' option, which uses less memory, can be performed with Z3 only since ESBMC does not support the 'incremental' mode with solver Boolector yet.
+Two alternatives were tested with ESBMC: one with Boolector and the another with Z3.
+The 'incremental SMT' option, which uses less memory, can be performed with Z3 only since ESBMC does not support the 'incremental' mode with the Boolector solver yet.
 
 Using ESBMC with Boolector led to an out of memory situation in all the case studies.
-This result was obtained in less than six minutes of execution, i.e., the $64$ GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
+This result was obtained in less than six minutes of execution, i.e.
+the $64$ GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.
 
-However, running the same version of ESBMC but using 'incremental SMT' solving with Z3, the experimentation returned was conclusive (SAT or UNSAT) to all the case studies.
+However, running the same version of ESBMC, using 'incremental SMT' solving with Z3, the experimentation results returned were conclusive (SAT or UNSAT) in all the case studies.
 
-Related to the cases that use a $700$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC could not reach an error in all the four houses and the execution time took from $04$ m $27$ s to $05$ m $08$ s.
-Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for the house $1$, with the absence of fail at the end of analysis.
-The file produced by ESBMC is $160$ lines long and $12.4$ kB of size.
-The author highlighted the result, which shows that was not found design flaws (SAT result or SUCCESS) within the bound $k$ of $100$.
+In the houses that use a $700$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC could not reach an error in any of the four houses and the execution time took from $04$ m $27$ s to $05$ m $08$ s.
+Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for house $1$, with the absence of fail at the end of the analysis.
+The file produced by ESBMC is $160$ lines long and $12.4$ kB in size.
+The author highlighted the result, which shows that no design flaws were found (SAT result or SUCCESS) within the bound $k$ of $100$.
 
@@
 
-However the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
+However the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current required by the PV system, indicating that the equipment chosen is not suited to meet the design requirements.
 
-Fig.~\ref{fig:esbmcverifhouse5} shows the report issued by the tool, with red highlights for the result, showing the incompatibility of the sized charge controller and the minimum necessary.
-The report generated by ESBMC was a text file of $14.1$ kB of size and $353$ lines of length.
-This verification took less than $1$ s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line $3$ of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.
+Fig.~\ref{fig:esbmcverifhouse5} shows the report generated by the tool, with red highlights for the result, showing the incompatibility of the sized charge controller and the minimum necessary.
+The report generated by ESBMC was a text file of $14.1$ kB in size, $353$ lines in length.
+This verification took less than $1$ s to perform, as indicated in the last line of Table~\ref{cases}, faster than the previous analysis because ESBMC stops during the sizing check, line $3$ of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of the verification code.
 
@@
 
-Concerning the CBMC tool, similar results were obtained, but with some slower time than ESBMC. The experimentation returned SAT or UNSAT to all the case studies, i.e., it was conclusive to all houses.
+Similar results were obtained with the CBMC tool, but with slower times than with ESBMC. The experimentation returned SAT or UNSAT for all the case studies, i.e. it was conclusive for all houses.
 
-Related to the 700 W PV systems (house $1$, house $2$, house $3$, and house $4$), the tool could not reach an error in all the four houses and the execution time took from $18$ m $36$ s to $19$ m $02$ s.
+In the 700 W PV systems (house $1$, house $2$, house $3$, and house $4$), the tool could not reach an error in any of the four houses in an execution time of $18$ m $36$ s to $19$ m $02$ s.
 
 Fig.
-\ref{fig:cbmcverifhouse1} shows part of report produced by CBMC when validating the house 1.
-The file produced by CBMC is $270,512$ lines long and $39$ MB of size.
-The author highlighted the result, which shows that was not found design flaws within the bound $k$ of $100$.
+\ref{fig:cbmcverifhouse1} shows part of the report produced by CBMC when validating house 1.
+This file contains $270,512$ lines and is $39$ MB in size.
+The author highlighted the result, which shows that no design flaws were found within the bound $k$ of $100$.
 
@@
 
-However the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code; with the same counterexample presented by ESBMC.
-This verification took less than $1$ s to be performed as well.
-Fig.~\ref{fig:cbmcverifhouse5} shows the (edited) report produced, with the highlights about the flaw found: the minimum controller current needed to the PV systems is not compatible with the chosen controller of the sized system.
-The report file generated contains $217$ lines and it was $13$ kB of size.
+However, the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code; with the same counterexample presented by ESBMC.
+This verification also took less than $1$ s to perform.
+Fig.~\ref{fig:cbmcverifhouse5} shows the (edited) report produced, with highlights on the flaw found: the minimum controller current needed for the PV systems is not compatible with the chosen controller of the sized system.
+The report file generated contains $217$ lines and was $13$ kB in size.
 
@@
 
-This is because the \textit{time out} limit was reached, i.e., after $4$ hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
-This is shown in Fig.~\ref{fig:cpavalidh1} is shown one of the text reports issued by CPAchecker.
-Differently of ESBMC and CBMC, CPAchecker produces a lot of different reports, notable for log, statistical, and counterexample files (which is graphical and not in text format).
+This is because the \textit{time out} limit was reached, i.e.
+after $4$ hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
+This is shown in Fig.~\ref{fig:cpavalidh1} which reproduces one of the text reports issued by CPAchecker.
+Unlike ESBMC and CBMC, CPAchecker produces many different reports, notably for log, statistical, and counterexample files (which are in graphic, not text format).
 
@@
 
-However, when validating the $1,200$ W PV system (house $5$), the tool presented a SAT message equal to the other engines, but with a execution time of $6$ seconds.
-Fig.~\ref{fig:cpavalidh5} show the result, with highlights to the line that causes the fail ($IC_{min}$) and part of the CFA (control-flow automata, represented as a control-flow graph) diagram pointing to this fail.
+However, when validating the $1,200$ W PV system (house $5$), the tool presented the same SAT produced by the other engines, but with an execution time of $6$ seconds.
+Fig.~\ref{fig:cpavalidh5} shows the result, with highlights on the line that causes the fail ($IC_{min}$) and part of the CFA (control-flow automata, represented as a control-flow graph) diagram pointing to this fail.
 
@@
 
-HOMER Pro is a powerful specialized electrical systems simulator, however even with the simulation characteristic, it in fact performs optimization when a given design is inputted to the schematic of the tool.
+HOMER Pro is a powerful specialized electrical systems simulator, however even with the simulation characteristic, it performs optimization only when a given design is inputted to the schematic of the tool.
 This means that HOMER does not maintain the characteristic of the system under evaluation.
-It starts with the inputted information, however it uses the optimization default set up to increase or decrease the characteristic of each component until the load be meet by the electric generation system, and with the lowest cost.
+It starts with the inputted information, but uses the optimization default set up to increase or decrease the characteristic of each component until the load is fulfilled by the electrical generation system, and at the lowest cost.
 
-Therefore, in order to perform a limited simulation and not exceed the values of each component (for example, the total power of the PV array under evaluation), it is necessary use the 'search space' instead of 'HOMER Optimizer' for sizing.
-That is done at the menu of each component inputted in the schematic of the tool.
+Therefore, in order to perform a limited simulation and not exceed the values of each component (for example, the total power of the PV array under evaluation), the 'search space' must be used for sizing instead of the 'HOMER Optimizer'.
+This is done on the menu of each component inputted in the schematic of the tool.
 
-Related to PV panels and batteries: If you want to simulate a particular capacity for PV and battery, you can use the 'search space' instead of 'HOMER Optimizer' for sizing.
-You can either aggregate all the PV panels together as a single PV component (in this case, the search space must vary from 0 to 1, i.e., from the option without PV panels until reach the power inputted to the component in the HOMER schematic) or add each PV components to represent the series configuration.
-For the batteries, you will have to find the equivalent capacity of the series and parallel configuration since HOMER considers only one battery component per simulation even if you add multiple battery components in the schematic.
+The PV panels and batteries: simulation of a particular capacity for PVs and batteris is possible using the 'search space' for sizing instead of the 'HOMER Optimizer'.
+It is possible either to aggregate all the PV panels as a single PV component, in which case, the search space must vary from 0 to 1, i.e.
+from the option without PV panels until it reaches the power inputted to the component in the HOMER schematic, or add each PV component to represent the series' configuration.
+For the batteries, it is necessary to find the equivalent capacity of the series and parallel configuration since HOMER considers only one battery component per simulation even if multiple battery components are added to the schematic.
 
-Other drawback of HOMER Pro is the fact that the user cannot set the autonomy of the batteries as HOMER controller will decide when it is economical to discharge the batteries during the simulation year.
-Therefore, any simulation regarding battery autonomy is not possible to be evaluated.
+Another drawback of HOMER Pro is the fact that the user cannot set battery autonomy, as the HOMER controller will decide when it is economical to discharge the batteries during the simulation year.
+It follows that simulation of battery autonomy cannot to be evaluated.
 
-Therefore, related to the comparative proposed, four $700$ W PV systems (houses $1$, $2$, $3$ and $4$) were evaluated by HOMER Pro (RQ2).
-The simulation results showed that for everyone of the sized systems, HOMER Pro concluded that it was not found feasible solution with the components inputted in the schematic.
+As part of the comparison proposed, four $700$ W PV systems (houses $1$, $2$, $3$ and $4$) were evaluated by HOMER Pro (RQ2).
+The simulation results showed that for each of the sized systems, HOMER Pro concluded that no viable solution was found with the components inputted in the schematic.
 Fig.
-\ref{fig:homersimuh2no} shows one of the screens presented by HOMER Pro software, specifically to house $2$.
+\ref{fig:homersimuh2no} shows one of the screens presented by HOMER Pro software, specifically by house $2$.
 
@@
 
-Moreover, in order to evaluate what was the problem associated with the lack of feasible solution, it was performed some empirical changes to the evaluated project.
-Fig.~\ref{fig:homersimuh2yes} shows that a configuration with higher battery capacity (3 strings of 2 batteries each, 2S-3P, of 220 Ah; instead of 2 strings of 2 batteries each as the original sized system) can solve the problem of house 2.
-The same happened to the other tree houses of $700 W$, when improved battery capacity is presented by HOMER Pro as a optimal solution.
+Moreover, in order to evaluate the problem associated with the lack of a viable solution, some empirical changes were made to the  project under evaluation.
+Fig.~\ref{fig:homersimuh2yes} shows that a configuration with higher battery capacity (3 strings of 2 batteries each, 2S-3P, of 220 Ah; instead of 2 strings of 2 batteries each as in the original sized system) can solve the problem of house 2.
+The same is true of the other three houses of $700 W$, when improved battery capacity is presented by HOMER Pro as an optimal solution.
 
@@
 \centering
-\caption{HOMER simulation screen presented for house 2 with feasible solution.}
+\caption{HOMER simulation screen presented for house 2 with viable solution.}
 \label{fig:homersimuh2yes}
@@
 The case study that was not possible to simulate was the $1,200$ W (house $5$).
-The reason is based on the fact that HOMER Pro do not allow to set up a battery autonomy (because it always size and optimize the electrical system in order to meet the load requirements for a entire year of simulation); therefore, it was was not possible to obtain any indication about the failures of this specifically PV system with simulation (RQ2).
+The reason is that HOMER Pro does not allow battery autonomy setup (because it always sizes and optimizes the electrical system in order to meet the load requirements for an entire year of simulation); therefore, it was not possible to obtain any indication about the failures of this specific PV system with simulation (RQ2).
 
@@
 
-There were divergence of results for the houses $1$, $2$, $3$ and $4$ w.r.t.
-of proposed approach: the automated evaluation shows that there is not project flaws, but simulation demanded to improve batteries capacity (adding one more string of batteries to the system).
+Results diverged for houses $1$, $2$, $3$ and $4$ w.r.t.
+the proposed approach: the automated evaluation shows there is no project flaws, but simulation demanded improvement of battery capacity (adding one more string of batteries to the system).
 
-In order to evaluate which validation is correct, it was necessary to access the access interviews performed with the dwellers of deployed systems.
-From July of $2018$ to March $2019$, a monthly visiting was performed to apply surveys to the dwellers and to collect data from a local monitoring system: not every month were reported some energy interruption of the PV systems.
+In order to evaluate which validation is correct, it was necessary to consult the access interviews conducted with the residents of the deployed systems.
+From July $2018$ to March $2019$, surveys were applied to the residents on a monthly basis and data was collected from a local monitoring system: energy interruptions of the PV systems were not reported every month.
 
-However, even when one interruption is reported in a month, this represents around $3.33$\% of interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.
+However, even when only one interruption is reported in a month, this represents around $3.33$\% interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$), and in accordance to what was described in Section~\ref{sec:availability}, the type of electrical load of the houses is not critical; this situation is considered an energy interruption, not a system flaw, further affirming RQ1.
 Therefore, the proposed approach using automated verification provides the correct evaluation of the PV system, thus answering RQ2.
 
-House $5$ presented flaws from all tools (automated verified or simulation); however, only automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
+All tools indicated flaws in house $5$ (automated verification or simulation); however, only the automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
 
-In order to validate the possible flaw identified by the automated verification from house $5$, it was surveyed the owner of the $1,200$ W system.
-It was identified that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double checked with the monitoring system from the charge controller, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house.
+In order to validate the possible flaw identified by the automated verification in house $5$, the owner of the $1,200$ W system was interviewed.
+From this it became clear that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double-checked against the monitoring system of the charge controller, which showed that the maximum power or surge power was not exceeded, thus affirming RQ1; this behavior is to be expected since the system was purchased as an off-the-shelf solution and not as a customized design for the house's electrical charges.
 
@@
 
-At this Chapter, it was reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, it was also identified five threats to the validity of the results that can further be assessed.
+This Chapter presented a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
+Nevertheless, it also identified five threats to the validity of the results that bear further assessment.
 
@@
 
-\textit{Time step:} The run-time complexity of the proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario.
+\textit{Time step:} The run-time complexity of the proposed method is an issue; the time step of one hour could be further reduced to approximate the algorithm to the real-world scenario.
 
-\textit{Case studies:} The case studies are performed only in one municipality. A more complete evaluation can be performed with more case studies.
+\textit{Case studies:} The case studies were conducted in only  one municipality. A more complete evaluation can be done with more case studies.
 
 \textit{Simulation Tool:} Only HOMER Pro was used.
-The inclusion of other specialized simulation tool or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparative.
+The inclusion of other specialized simulation tools or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparison.
 
-\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online~\cite{Temperature, Irradiance}.
-However, considering that riverside communities do not have weather stations, the data used in the present study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data.
-Therefore, the most accurate should be the use of weather stations in each location.
+\textit{Temperature and Solar Irradiance Data}: Information relating to the temperature and solar irradiance of each case study, whether it is using simulation or formal verification, comes from databases available online~\cite{Temperature, Irradiance}.
+However, in view of the fact that riverside communities do not have weather stations, the data used in the present study comes from the municipality closest (Manaus in all the case studies), where stations regularly collect the data.
+Nevertheless, accuracy recommends the use of weather stations in each location.
 
@@
 
-This Chapter showed in details how the state-of-art computer science method of automated verification was adapted in order to be used in stand-alone solar PV systems to validate their behavior.
-Moreover, is was possible to picture the comparative of how the proposed method and the traditional one of simulation work differently.
+This Chapter showed in details how the state-of-the-art computer science method of automated verification was adapted to be used in stand-alone solar PV systems in order to validate their behavior.
+Moreover, it was possible to illustrate the comparative differences in how the proposed method and the traditional method of simulation work.
 
-Detailed diagrams, flowcharts and algorithms with pseudo-code were presented with the aim to support the proposed work and to facilitate the understanding.
-And even more so, the assumptions adopted for the automated verification and simulation software were listed.
+Detailed diagrams, flowcharts and algorithms with pseudo-code were presented in support of the proposed work and to aid the understanding.
+Additionally, the assumptions adopted in relation to the automated verification and simulation software were listed.
 
-Furthermore, at this Chapter it was performed the comparative among verifiers with the proposed automated verification using model checking, which showed that 'incremental' ESBMC had the best overall performance.
-CBMC presented the same results, however with a worse time to result, and CPAchecker was not conclusive (house $1$, house $2$, house $3$, and house $4$) because the \textit{time out} was not enough to obtain some result.
+Furthermore, in this Chapter verifiers with the proposed automated verification using model checking were compared, which demonstrated that 'incremental' ESBMC had the best overall performance.
+CBMC presented the same results, but with a worse time to result, and CPAchecker was not conclusive (house $1$, house $2$, house $3$, and house $4$) because the \textit{time out} was not enough to obtain a result.
 
-A comparative with a specialized simulation tool was performed as well, however some limitations of the tool, mainly related to not allow battery autonomy setup or the oversize of the batteries bank by HOMER Pro, restricted the comparative between automated verification tools versus simulation tools.
+A comparison with a specialized simulation tool was also performed, although some of the tool's limitations, mainly related to not allow allowing battery autonomy setup or oversizing the battery bank by HOMER Pro, restricted the comparison between automated verification tools and simulation tools.
 
-Based on the fact that all case studies were deployed at the field, with regular visiting to perform interview with the dwellers, and with monitoring system in some of the houses (house $1$, house $2$, house $3$, and house $4$), it was possible to compare the computational validation (by simulation or automated verification) with the real world employment of the stand-alone solar PV systems.
-The final conclusion was that the proposed tool is sound and with an acceptable performance.
+Based on the fact that all case studies were deployed in the field, with regular visits to conduct interviews with the residents, and with monitoring systems in some of the houses (house $1$, house $2$, house $3$, and house $4$), it was possible to compare the computational validation (by simulation or automated verification) with the real world employment of stand-alone solar PV systems.
+The final conclusion was that the proposed tool is sound and has an acceptable performance.

### 2020-01-03 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

--- 2019-05-07 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
@@
-\documentclass[10pt,conference]{IEEEtran}
-% \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\bibliographystyle{IEEEtran}
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithm,algorithmic}
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
+%
+\documentclass[runningheads]{llncs}
+%
+\usepackage{xcolor}
 \usepackage{graphicx}
@@
 \usepackage{textcomp}
-\usepackage{xcolor}
-\def \BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+%\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithm,algorithmic}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
+%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
 
- \renewcommand{\baselinestretch}{0.965}
+\renewcommand{\baselinestretch}{0.97}
 
 \begin{document}
-
-\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems}
 %
-%\author{\IEEEauthorblockN{Alessandro Trindade}
-%\IEEEauthorblockA{
-%\textit{Federal University of Amazonas}, Brazil \\
-%alessandrotrindade@ufam.edu.br}
-%\and
-%\IEEEauthorblockN{Lucas Cordeiro}
-%\IEEEauthorblockA{
-%\textit{University of Manchester}, UK \\
-%lucas.cordeiro@manchester.ac.uk }
-%}
+\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM
+(Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}}
 %
-\maketitle
+%\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{Alessandro Trindade\inst{1}\orcidID{0000-0001-8262-2919} \and
+Lucas Cordeiro\inst{2}\orcidID{0000-0002-6235-4272}}
+%
+\authorrunning{A. Trindade and L. Cordeiro}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Federal University of Amazonas, Av. Gen. Rodrigo Octavio, 6200, Coroado I, 69077-000 Manaus AM Brazil \email{alessandrotrindade@ufam.edu.br} \and
+The University of Manchester, Kilburn Building, Oxford Road, Manchester M13 UK
+\email{lucas.cordeiro@manchester.ac.uk}}
+\maketitle              % typeset the header of the contribution
 
@@
 Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different intricate case studies.
+Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of seven different intricate case studies.
+
+\keywords{Automated verification  \and Model Checking \and Electric systems \and Solar photovoltaic systems.}
 \end{abstract}
-
-\begin{IEEEkeywords}
-automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
-\end{IEEEkeywords}
+%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
+\section{Introduction}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
@@
 Our work makes two major contributions.
-Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented.
+Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically their use in synthesizing PV sizing is unprecedented.
 Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries)
@@
 %
-One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
+One may notice that each iteration of the CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
 At this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.
@@
 %
-Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\ref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+
 \begin{equation}
 \label{eq:Ecorrected}
-\scriptstyle E_{corrected} = \dfrac{\scriptstyle E_{consumption}}{ \scriptstyle \eta_{b} \eta_{c} \eta_{i} }.
+E_{corrected} = \frac {E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
 \end{equation}
-%
+
 We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
-%
+
 \begin{equation}
 \label{eq:Ep}
-\scriptstyle E_{p} = \scriptstyle Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
+E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
 \end{equation}
-%
+
 \noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
@@
 \label{eq:NTPmin}
-\scriptstyle N_{TPmin} = \dfrac{\scriptstyle E_{corrected}}{\scriptstyle E_{p}}.
+N_{TPmin} = \frac{E_{corrected}}{E_{p}}.
 \end{equation}
@@
 \label{eq:NPSmin}
-\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}},
+\frac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \frac{V_{mppt,max}}{V_{maxPower,TempMin}},
 \end{equation}
@@
 \label{eq:NPPmin}
-\scriptstyle N_{PPmin} = \dfrac{\scriptstyle P_{total}}{\scriptstyle Number\,Panels\,Series \scriptstyle \times \scriptstyle P_{max,ref}},
+N_{PPmin} = \frac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
 \end{equation}
@@
 \label{eq:Cbank}
-\scriptstyle C_{bank} \scriptstyle = \dfrac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD},
+\scriptstyle C_{bank} \scriptstyle = \frac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD},
 \end{equation}
@@
 \label{eq:Nbtotal}
-\scriptstyle N_{B}total = \scriptstyle N_{BS}min \scriptstyle \times \scriptstyle N_{BP}min = \dfrac{\scriptstyle V_{system}}{\scriptstyle V_{bat}} \scriptstyle \times \dfrac{\scriptstyle C_{bank}}{\scriptstyle 1 \,Battery \, Capacity}.
+\scriptstyle N_{B}total = \scriptstyle N_{BS}min \scriptstyle \times \scriptstyle N_{BP}min = \frac{\scriptstyle V_{system}}{\scriptstyle V_{bat}} \scriptstyle \times \frac{\scriptstyle C_{bank}}{\scriptstyle 1 \,Battery \, Capacity}.
 \end{equation}
 %
-Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
+Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\ref{eq:vcvsystem} to the charge controller voltage: 
 \begin{equation}
@@
 \label{eq:iscamb}
-\scriptstyle I_{sc,amb} = \dfrac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
+\scriptstyle I_{sc,amb} = \frac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
 \end{equation}
 %
-The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin} as
+The controller must meet the maximum current from the PV array given by Eqs. \ref{eq:icmin} and \ref{eq:icicmin} as
 \begin{equation}
@@
 The inverter sizing check is performed by means of three equations.
-Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
-Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
+Eq.~\ref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
+Eq.~\ref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
+Finally, Eq.~\ref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
 %
@@
 
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (Lines 11 to 17).
+Next, we use Eq.~\ref{eq:Ecorrected}, Eq.~\ref{eq:Ep}, Eq.~\ref{eq:NTPmin}, Eq.~\ref{eq:NPSmin}, Eq.~\ref{eq:NPPmin}, Eq.~\ref{eq:Cbank}, Eq.~\ref{eq:Nbtotal}, Eq.~\ref{eq:iscamb}, and Eq.~\ref{eq:icmin} to calculate the sizing variables (Lines 11 to 17).
 The directive \textit{assume} (Lines 15, 18 and 19) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines 15, 18 and 19.
@@
 %
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{trindadeThesis_menor}{}
-%\vspace{12pt}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%divisão para o material antigo sobre verificação
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{State-of-art in Automated Verification of Electrical Systems}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The conversion of traditional power grid into a smart grid, a fundamental example of a Cyber-Physical System (CPS), raises a number of issues that requires novel methods and applications.
+In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}.
+The focus of this study was on how CPs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system, as 	probability	of	node	failure	in	the	long run, impact	of	repair	service	on	the	failure	risk, and expected energy consumption.
+%, with no interest in power generation or even solar PV systems.
+
+In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
+The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
+The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
+%The study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
+
+Other related studies from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking for CPSs in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
+In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
+The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
+%The research did no deal with solar PV systems.
+
+In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
+The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
+The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
+The author used approximate model checking of stochastic and hybrid models.
+
+In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
+The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
+%The work did not include the other components of a stand-alone solar PV system.
+
+Another work from 2018 was the approach to modeling smart grid components using a formal specification.
+The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
+The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods.
+The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
+This approach is base on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
+
+%
+% ---- Bibliography ----
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+\bibliographystyle{splncs04}
+\bibliography{trindadeThesis}
+%
+
 \end{document}
+
+%\subsection{Design and Simulation of Solar PV systems}
+%The design and validation of a PV system can be done by hand or with the aid of a software tool.
+In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
+%public domain and commercial software available for the PV market. 
+%According to \cite{Brooks}, t
+%%%%%%%%%%
+%
+%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
+%to complex financial analysis and project optimization.
+At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.

### 2020-01-07 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 %
-\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM
-(Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}}
+%\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems\thanks{Supported by Newton Fund (ref.
+261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}}
+\title{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparative\thanks{Supported by Newton Fund (ref.
+261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}}
 %
@@
 \begin{abstract}
-Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space.
+%Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space.
 We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis.
@@
 Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of seven different intricate case studies.
-
+In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends in energy access still fall short of global goals.
+Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
+Tools to evaluate or to size electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
+The use of formal methods in electrical systems is a new subject, with published research spanning only the last four years.
+Moreover, the use of automated synthesis in order to obtain optimal sizing of solar photovoltaic systems has never been done before; this is our major goal: a sound, automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis.
+We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach, with two phases linking the technical and the cost analysis.
+First, we synthesize a feasible candidate based on power reliability, but which may not attain the lowest cost.
+Second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
+If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution.
+Experimental results using seven case studies demonstrate that we can produce optimal solution within an acceptable run-time.
+We also present a comparison with a specialized simulation tool over real photovoltaic systems in order to show the effectiveness of our approach.
 \keywords{Automated verification  \and Model Checking \and Electric systems \and Solar photovoltaic systems.}
@@
 The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.
+
+Related to past work, in $2012$, a Chinese smart grid implementation considered a case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
+In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
+In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
+Finally, in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+However, prior studies did not deal with electricity generation or even solar PV systems optimization.
+Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in literature.
 
@@
 \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14};
-here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
-%
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools:
+CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.
+
+\textbf{CPAchecker}~\cite{LMU2019} is a state-of-the-art model checker, awarded with the golden medal at the annual competition in software verification: Automatic program verification requires a choice between precision and efficiency.
+The more precise a method, the fewer false positives it produces, but also the more expensive it is, and thus applicable to fewer programs.
+Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
+To experiment with the trade-off and to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
+The CPA formalism provides an interface for the definition of program analysis.
+Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analysis expressed in the CPA framework.
+In terms of the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
+The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}.
+Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.
+
+The C Bounded Model Checker (\textbf{CBMC}) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
+CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
+If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
+CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+
+The Efficient SMT-based Bounded Model Checker (\textbf{ESBMC}) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{eq:Cbank}
-\scriptstyle C_{bank} \scriptstyle = \frac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD},
+C_{bank} = \frac{E_{corrected} \times autonomy}{V_{system} \times DOD},
 \end{equation}
@@
 \label{eq:Nbtotal}
-\scriptstyle N_{B}total = \scriptstyle N_{BS}min \scriptstyle \times \scriptstyle N_{BP}min = \frac{\scriptstyle V_{system}}{\scriptstyle V_{bat}} \scriptstyle \times \frac{\scriptstyle C_{bank}}{\scriptstyle 1 \,Battery \, Capacity}.
+N_{B}total = N_{BS}min \times N_{BP}min = \frac{V_{system}}{V_{bat}} \times \frac{C_{bank}}{Battery \, Capacity}.
 \end{equation}
@@
 \label{eq:vcvsystem}
-\scriptstyle V_{c} = \scriptstyle V_{system}.
+V_{c} = V_{system}.
 \end{equation}
@@
 \label{eq:iscamb}
-\scriptstyle I_{sc,amb} = \frac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
+I_{sc,amb} = \frac{G}{G_{ref}} \left[I_{sc,ref} +  \mu_{I} \times (T-25) \right]. 
 \end{equation}
@@
 \label{eq:icmin}
-\scriptstyle I_{c,min} = \scriptstyle I_{sc,amb} \times \scriptstyle N_{PP},
+I_{c,min} = I_{sc,amb} \times N_{PP},
 \end{equation}
@@
 \label{eq:icicmin}
-\scriptstyle I_{c} \geq \scriptstyle I_{c,min}.
+I_{c} \geq I_{c,min}.
 \end{equation}
@@
 \label{eq:vindc} 
-\scriptstyle V_{in}DC = \scriptstyle V_{system}.
+V_{in}DC = V_{system}.
 \end{equation}
@@
 \label{eq:voutac} 
-\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
+V_{out}AC = V_{AC}.
 \end{equation}
@@
 \label{eq:invcheck} 
-\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
+\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
 \end{equation}
@@
 %---------------------------------------------------------------------------
-\textbf{Case studies.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}.
+
+\textbf{Case studies.} We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (\textit{Specification}).
+These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil.
+This project finished in March 2019, where we visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers.\footnote{http://star-energy.coventry.ac.uk/} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.
+
 Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems.
@@
 
-\textbf{Objectives.} Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, and \textit{RQ2} (performance) How do the software verifiers compare to each other?
+\textbf{Objectives.} Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, \textit{RQ2} (performance) How do the software verifiers compare to each other?, and \textit{RQ3} how does our formal synthesis tool compare to a specialized simulation tool?
 
-\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
+\textbf{Results.}  xxxxfalta as demais ferramentas????? CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
 The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}.
@@
 %used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
+
+\begin{table}[!t]
+\caption{Case studies and results: optimization of PV systems.}\label{tab0}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\hline
+Tools & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& CBMC & ESBMC & HOMER Pro 3.13.1\\
+\hline
+\hline
+Specification & Result & Result & Result & Result \\
+\hline
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & TO & TO & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\hline
+\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
+\hline
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & TO & TO & Not possible \\
+\hline
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} &  \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & TO & TO & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
+\hline
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & TO & TO & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
+\hline
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & TO & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
+\hline
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & TO & TO & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+\hline
+\hline
+\end{tabular}
+\\Caption: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
+\end{table}
+
 \begin{table}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{State-of-art in Automated Verification of Electrical Systems}
+%\section{State-of-art in Automated Verification of Electrical Systems}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The conversion of traditional power grid into a smart grid, a fundamental example of a Cyber-Physical System (CPS), raises a number of issues that requires novel methods and applications.
+%
+%The conversion of traditional power grid into a smart grid, a fundamental example of a Cyber-Physical System (CPS), raises a number of issues that requires novel methods and applications.
 In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
@@
 %, with no interest in power generation or even solar PV systems.
-
-In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
+%
+%In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
 The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
@@
 %The study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
-
-Other related studies from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking for CPSs in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
+%
+%Other related studies from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking for CPSs in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
 In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
@@
 %The research did no deal with solar PV systems.
-
-In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
+% 
+%In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
 The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
@@
 The author used approximate model checking of stochastic and hybrid models.
-
-In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+%
+%In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
 This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
@@
 %The work did not include the other components of a stand-alone solar PV system.
-
-Another work from 2018 was the approach to modeling smart grid components using a formal specification.
+%
+%Another work from 2018 was the approach to modeling smart grid components using a formal specification.
 The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
@@
 This approach is base on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
-
+%
 %

### 2020-01-08 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}.
-To provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
+To provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}.
+%; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
 
@@
  However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+
 Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.
+%However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
+Related to past work using formal methods based on \textit{symbolic model checking} and its application to electric systems: in $2015$ an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}; in $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}; in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}; and finally, in $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
+However, formal methods and its application to synthesize PV systems are still unexplored in literature.
 
-However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
-Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$.
-In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
-The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.
-
-Related to past work, in $2012$, a Chinese smart grid implementation considered a case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
-Finally, in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-However, prior studies did not deal with electricity generation or even solar PV systems optimization.
-Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in literature.
+Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
+In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
+The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted.
+If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost.
+Note that in this study, our focus is not on new criteria or even optimization objectives.
+Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.
 
@@
 Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically their use in synthesizing PV sizing is unprecedented.
-Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries)
-can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
+%Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
 Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
@@
 	\centering
-	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
+	\includegraphics[width=0.7\columnwidth]{fig2_rev.jpg}
 	\caption{CEGIS applied to PV system sizing.}
@@
 \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools:
+
+/////
+Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
+In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
+The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted.
+If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost.
+Note that in this study, our focus is not on new criteria or even optimization objectives.
+Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.
+////
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{iet-cps.2018.5006}; here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools:
 CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.
@@
 It indicates that was not possible to combine the items of each equipment and create a feasible solution.
-
 The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements.
@@
 
-Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+%Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
 %---------------------------------------------------------------------------
@@
 
-Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems.
+These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{TrindadeCordeiro19,Agrener2013}.
+With exception of case 7 that was idealized as a small town solution to support few lamps and an 12 kBTUs air-conditioner.
+
+Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
 Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
@@
 
-\textbf{Setup.} All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
-The experiments were performed with a predefined timeout of $240$ minutes.
+\textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits.
+Related to HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), with $1.7$ GHz and $4$ GB of RAM, running Windows 10.
+The experiments were performed with a predefined time out of $240$ minutes.
 
@@
 
-\textbf{Results.}  xxxxfalta as demais ferramentas????? CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
-The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}.
-The results were tested by manual PV sizing and were sound (\textit{RQ1}).
-%, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
-CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.
+\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
+%Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing in the left size as the integer $8$ to the solar panel (which is the model RSM36-6-150P from manufacturer Risen), battery $0$ that means the model 12MF80 of 80 Ah from Moura, charge controller $1$ that means the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ means the model IP350-11 from Epever (750 W).
+The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, presented at the counter-example as well, shows how many and how the panels and batteries are connected.
+Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes.
+%However, if it is removed this time out limitation from CPAchecker, the verifier is able to solve the optimization in $44.97$ hours.
+The violation (SAT result) indicated in Table~\ref{tab1} 
+is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
+CBMC and ESBMC are unable to produce any conclusive result.
+Situations of \textit{time out} or \textit{out of memory} occurred; this partially answers the \textit{EQ2} and \textit{EQ3}.
+
+Related to HOMER Pro, it was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}).
+Case study $3$ was not possible to be simulated since HOMER Pro does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.
+
+Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, it was observed that most results are quite similar, in terms of technical solution and cost (cf.
+Table~\ref{tab1}).
+Particularly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
+Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling.
+The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value.
+However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by the automated synthesis tool were underestimated to that specific load.
+
+In general, the size of the PV panels and battery bank were bigger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation.
+Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
+
+Related to the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter.
+The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf.
+Therefore is a PRO to the formal synthesis method.
+
+Concerning to charge controllers, as it was reported in the  section~\ref{sec:synthesisresults}, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis.
+Therefore, the formal synthesis method presents more reliable results than HOME Pro.
+
+Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
+Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters to comparative.
+
+\textbf{Conclusion.} Summarizing, the synthesis tool is capable to present a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
+In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current and voltage.
+In this respect, even the name of the manufacturer can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).
+
 %
@@
 \begin{table}[!t]
-\caption{Case studies and results: optimization of PV systems.}\label{tab0}
+\caption{Case studies and results: optimization of PV systems.}\label{tab1}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \hline
-Tools & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& CBMC & ESBMC & HOMER Pro 3.13.1\\
+Tools & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell {ESBMC 6.0.0\\(Boolector 3.0.1)} & HOMER Pro 3.13.1\\
 \hline
@@
 \hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & TO & TO & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & OM & TO & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
 \hline
-\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
+\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & OM & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
 \hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & TO & TO & Not possible \\
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & OM & TO & Not possible \\
 \hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} &  \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & TO & TO & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} &  \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & OM & TO & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
 \hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & TO & TO & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & OM & TO & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
 \hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & TO & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & OM & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
 \hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & TO & TO & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & TO & OM & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
 \hline
@@
 \end{tabular}
-\\Caption: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
+\\Caption: OM= out of memory; TO= timeout; E= energy, NTP= total number of panels, NBT= total number of batteries, LCC= life cicle cost.
 \end{table}
-
-\begin{table}
-\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
-%\begin{scriptsize}
-\begin{tabular}{|c|c|c|}
-\hline
-\hline
-Specification & \makecell{ \textbf{Case Study 1} \\ Demand=501W \\ Peak=501W \\ Energy=3,900Wh/day\\Battery autonomy=48h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC} & \makecell{\textbf{Case Study 2}\\ Demand=915W \\ Peak=980W \\Energy=4,880Wh/day\\Battery autonomy=6h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC}\\
-\hline
-\hline
-Tools & \textbf{Result} & \textbf{Result}\\
-\hline
-\makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{UNKNOWN \\(Out of Memory)} & \makecell{UNKNOWN \\(Out of Memory)}\\
-\hline
-\makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{UNKNOWN \\(Timeout)} & \makecell{UNKNOWN \\(Timeout)} \\
-\hline
-%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
-%\hline
-\makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\Property violation line 209\\NTP=1$\times$330W (1S)\\NBT=8$\times$105Ahm (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\Property violation line 209\\NTP=3$\times$330W (3S)\\NBT=2$\times$105Ah (2S)\\Controller 35A/145V\\Inverter 1,500VA/24V \\Total Cost=US\$ 2,235.57}\\
-\hline
-\hline
-\end{tabular}
-%\end{scriptsize}
-\end{table}
-%
 
@@
 %
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-01-09 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 \end{abstract}
-%
 
@@
 %While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
-Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS.
+Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis.
+% with the goal of synthesizing correct-by-construction implementations of CPS.
 These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
@@
 Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
+
 Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
-
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
@@
 %However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
-Related to past work using formal methods based on \textit{symbolic model checking} and its application to electric systems: in $2015$ an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}; in $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}; in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}; and finally, in $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
+Related to the use of formal methods based on \textit{symbolic model checking} and its application to electric systems: in $2015$ an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}; in $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}; in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}; and finally, in $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
 However, formal methods and its application to synthesize PV systems are still unexplored in literature.
@@
 Our work makes two major contributions.
-Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically their use in synthesizing PV sizing is unprecedented.
+\textbf{Firstly}, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically their use in synthesizing PV sizing is unprecedented.
 %Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
-Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
+\textbf{Secondly}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
 
@@
 %-----------------------------------------------------------
-%
+%In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis. In particular, 
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis.
+Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions) except for the automated synthesis where we also define the bound $k$ to restrict the design-space search.
+Related to the output presented by both techniques, all of them produce a SUCCESS or FAIL result considering a feasible technical solution with the lowest cost.
+On the one hand, when done by simulation we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
+Furthermore,
+%as described in this section, 
+the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{optimalsizingprocess3}
+\centering
+\caption{Comparison of optimal sizing methods.}
+\label{fig:optimization}
+\end{figure}
+
 %-----------------------------------------------------------
@@
 %-----------------------------------------------------------
-%
+Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}.
+Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do.
+The specification needs to describe the program's desired behavior to ensure that the program does what it intends.
+
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
 In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
-As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+As a result, a given candidate program $p$ is iteratively refined, to match $\sigma$ more closely.
+CEGIS represents one of the most popular approaches to program synthesis currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization.
+Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture.
+Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+%from model checking.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
+	\caption{CEGIS adapted to PV system sizing.}
+	\label{Counter-Example-Guided-Inductive-Synthesis}
+\end{figure}
 
@@
 The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
+Examples of specifications used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specifications and prices from different manufacturers and models.
 
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated.
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
-%
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.7\columnwidth]{fig2_rev.jpg}
-	\caption{CEGIS applied to PV system sizing.}
-	\label{Counter-Example-Guided-Inductive-Synthesis}
-\end{figure}
-%
-One may notice that each iteration of the CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists and our synthesis engine can then conclude that no feasible equipment combination was found.
-At this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.
-%however, $\mathcal{D}$ can represent a large number of elements for the finite set  and our synthesis engine can then conclude that no feasible equipment combination was found.
-%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}.
-In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig.
-\ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.
+If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
 
-/////
-Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
-In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
-The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted.
-If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost.
-Note that in this study, our focus is not on new criteria or even optimization objectives.
-Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.
-////
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{iet-cps.2018.5006}; here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools:
+One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists, and our synthesis engine can then conclude that no feasible equipment combination was found.
+
+In our variant CEGIS method, there exist four distinct differences related to the traditional CEGIS: 
+(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
+(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
+(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
+a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
+
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{iet-cps.2018.5006};
+here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools: 
 CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.
 
-\textbf{CPAchecker}~\cite{LMU2019} is a state-of-the-art model checker, awarded with the golden medal at the annual competition in software verification: Automatic program verification requires a choice between precision and efficiency.
+\textbf{CPAchecker}~\cite{LMU2019} is a model checker awarded with the golden medal at the annual competition in software verification: Automatic program verification requires a choice between precision and efficiency.
 The more precise a method, the fewer false positives it produces, but also the more expensive it is, and thus applicable to fewer programs.
@@
 In terms of the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}.
+The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
 Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.
@@
 If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
-CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.
+CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports Boolean Satisfiability (SAT) and SMT solvers to discharge verification conditions.
 
@@
 \end{figure}
-\\
-%
+
 The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
@@
 the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-%
+
 The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
-%
+
 \begin{equation}
@@
 \end{equation}
-%
+
 Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
-%
+
 \begin{equation}
@@
 \end{equation}
-%
+
 \begin{equation}
@@
 \end{equation}
-%
+
 \noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
@@
 Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
+
 \begin{equation}
@@
 \end{equation}
-%
+
 \noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
 $ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-%
+
 Secondly, the total (minimum) number of batteries is computed as 
@@
 \end{equation}
-%
+
 Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\ref{eq:vcvsystem} to the charge controller voltage:
+
 \begin{equation}
@@
 \end{equation}
-%
+
 The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as
-%
+
 \begin{equation}
@@
 \end{equation}
-%
+
 The controller must meet the maximum current from the PV array given by Eqs. \ref{eq:icmin} and \ref{eq:icicmin} as
+
 \begin{equation}
@@
 \end{equation}
-%
+
 The inverter sizing check is performed by means of three equations.
@@
 Finally, Eq.~\ref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
-%
+
 \begin{equation}
@@
 \end{equation}
+
 % -------------------------------------------------------
@@
 Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
-Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
 %------------------------------------------------------
@@
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
-%
+
  \begin{algorithm}
@@
 %---------------------------------------------------------------------------
-
-\textbf{Case studies.} We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (\textit{Specification}).
-These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil.
-This project finished in March 2019, where we visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers.\footnote{http://star-energy.coventry.ac.uk/} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.
-
+\textbf{Case studies.} We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} 
+(\textit{Specification}).
 These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{TrindadeCordeiro19,Agrener2013}.
 With exception of case 7 that was idealized as a small town solution to support few lamps and an 12 kBTUs air-conditioner.
+For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
 
@@
 and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
+It is important to mention that ESBMC with Z3 solver (version 4.7.1) in 'incremental mode' was tested as well in order to consume less memory; however it was reported an 'internal failure' error message caused by a bug in the solver that was not solved until the end of the tests.
+
+\textbf{Simulation Tool and Assumptions.} Related to off-the-shelf simulation tools only HOMER Pro perform off-grid system with battery backup analysis and includes economical analysis.
+Therefore, in this study, HOMER Pro will be the simulation tool used to comparison.
+Related to HOMER Pro: (a) is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; (b) it does not have the LCC cost in its reports.
+But it was possible to obtain LCC from the Net Present Cost (NPC) presented by HOMER Pro; (c) the optimization analysis of HOMER allows to define a load curve and temperature according of data collected from online databases.
+However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools; (d) it does not have a explicit equipment called charge controller.
+It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: 'load following' or 'cycle charging'~\cite{HOMER}.
+During the tests it was chosen the 'load following' controller: it produces only enough power to meet the demand~\cite{HOMER}; (e) It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
+By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
+For critical loads, 99\% is considered acceptable.
+While in a ordinary house electrical load, 95\% is considered acceptable; (f) it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; (g) the premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER will search for the optimized power of each component.
+With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
+HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
 
@@
 
-Concerning to charge controllers, as it was reported in the  section~\ref{sec:synthesisresults}, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis.
+Concerning to charge controllers, as it was reported in this  section, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis.
 Therefore, the formal synthesis method presents more reliable results than HOME Pro.
@@
 
-\textbf{Conclusion.} Summarizing, the synthesis tool is capable to present a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
-In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current and voltage.
-In this respect, even the name of the manufacturer can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).
+\textbf{Conclusion.} Summarizing, our synthesis tool is capable to present a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
+In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current and voltage.
+In this respect, even the manufacturer's brand can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).
 
@@
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
+Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
 %

### 2020-01-09 Tex/Old text/chapters/chapteroptimization.tex
CAV 2020 paper update

@@
-In this Chapter, we detail the adopted methodology to perform optimal sizing of stand-alone solar PV systems, more specifically using model checking.
+In this Chapter, we detail methodology used for optimal sizing of stand-alone solar PV systems, more specifically using model checking.
 Diagrams, flowcharts, and algorithms support and explain the solutions.
 
-Besides that, we present all the assumptions and premises adopted.
-We present as well the case studies used to evaluate the proposed approach of optimal sizing of stand-alone solar PV systems using automated synthesis.
-Moreover, the approach is compared with a simulation tool, named HOME Pro.
-The version and command-line of each verifier adopted, the computing setup, the objectives of the experimental phase, and the results itself are also described.
+In addition, we present all the underlying assumptions and premises.
+We also present the case studies used to evaluate the proposed approach for optimal sizing of stand-alone solar PV systems using automated synthesis.
+Moreover, the approach is compared with the HOME Pro simulation tool.
+The version and command-line of each verifier, the computing setup, the objectives of the experimental phase, and the results are also described.
 
-It is important to emphasize that the whole explanation about the theoretical basis of the subject discussed here is present in the Chapter~\nameref{chap:background}.
-We do suggest that this previous Chapter reading must be done to facilitate the understanding.
+It is important to emphasize that the complete explanation of the theoretical basis of the subject discussed here is presented in the Chapter~\nameref{chap:background}.
+In addition, knowledge of the literature is essential to aid understanding.
 
@@
 
-Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual, and simulation), and including the proposed automatic synthesis that is detailed in this Section.
+Fig.~\ref{fig:optimization} illustrates how to obtain optimal sizing of a stand-alone solar PV system, beginning with the traditional techniques (manual, and simulation), and moving on to the proposed automatic synthesis detailed in this Section.
 
-One more time, as depicted in automated verification process, the input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search.
-And the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.
+Once more, as described in the automated verification process, the input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search.
+And the outputs are not equal, as in the design-space coverage and, mainly, in the final result.
 
@@
 \centering
-\caption{Comparative of optimal sizing methods}
+\caption{Comparison of optimal sizing methods}
 \label{fig:optimization}
@@
 
-\subsection{Variant of CEGIS}
+\subsection{A Variant of CEGIS}
 
-In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section ~\ref{sec:ProgramSynthesis}, Fig.~\ref{Counter-Example-Guided-Inductive-Synthesis}.
-This variant was created during this Thesis and it will be detailed in this Section.
+Figure~\ref{CEGISalt} illustrates a variant of CEGIS, previously presented in Section ~\ref{sec:ProgramSynthesis}, Fig.~\ref{Counter-Example-Guided-Inductive-Synthesis}.
+This variant was created during the research for this thesis and will be detailed in this Section.
 
@@
 
-Examples of specification used by the proposed method include solar insolation (site dependent), house power demand, house consumption energy, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
-Design assumptions are considered project specification as well.
-The assumptions regarding the optimal sizing are listed in Section~\ref{sec:OptAssumptions}.
+Examples of specification used by the proposed method include solar insolation (site dependent), house power demand, house  energy consumption, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specifications and prices from different manufacturers and models.
+Design assumptions are considered additional project specifications.
+The assumptions underlying optimal sizing are listed in Section~\ref{sec:OptAssumptions}.
 
-There are four particular differences related to the traditional CEGIS described in Figure ~\ref{Counter-Example-Guided-Inductive-Synthesis} when compared to the variant CEGIS used in the proposed approach:
+The variant CEGIS used in the proposed approach differs in four specific aspects from the traditional CEGIS described in Figure ~\ref{Counter-Example-Guided-Inductive-Synthesis}:
 
 \begin{itemize}
-\item There exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
-\item If the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} 
+\item There is no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+\item If the {\sc Verify} phase is unsuccessful, a new candidate is generated by {\sc Synthesize} 
 \item The lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
-\item As a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate that could be feasible in the next iteration with a new lower bound.
+\item As a result, there is no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e.
+a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate that could be viable in the next iteration with a new lower bound.
 \end{itemize}
@@
 Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
-It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
+The analytical method of optimization was adopted, with LCC economic analysis and power reliability based on critical period criteria.
 
@@
   \STATE Declare power demand, power peak, energy consumption \\
-  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
+  \STATE Declare battery autonomy, depth of discharge, AC voltage \\
   \FOR {$HintCost=0$ to $MaxCost$}
@@
 Our synthesis algorithm will synthesize constant values; 
-it starts with the input of manufacturers data and prices of PV panels, batteries, 
-charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
+it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers and inverters (line $2$).
+After that, we define user requirements, i.e.
 house requirements and design definitions, from lines $4$ and $5$.
 
-The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. 
-In particular, it starts with cost $0$ and stops only when the algorithm finds a 
-feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
-if that happens, then our algorithm has found an optimal solution, thereby stating 
-that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
-The $MaxCost$ value at line $6$ is just a very high value put as a limit 
-to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
+The \textit{for}-loop started at line $6$ controls the lowest cost of the PV solution.
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $22$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+The $MaxCost$ value at line $6$ is just a very high value inserted as a limit to the \textit{for}-loop, that will never be reached because the optimal solution will be found first.
 
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
-from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
-That procedure ensures that our synthesis engine checks all combinations of items 
-from each equipment, and combine them to assemble a feasible (candidate) PV solution, 
-which meets the user requirements.
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$).
+This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.
 
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, 
-Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
-Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
-ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase 
-uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$.
+Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb} and Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $11$ to $17$).
+The directive \textit{assume} (lines $15$, $18$ and $19$)
+ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of Lines $15$, $18$ and $19$.
 Line $15$ is specific to the charge controller voltage check.
-Line $18$ checks the inverter check $I_{c}$, charge controller DC input voltage $V_{in}DC$, and charge controller AC output voltage $V_{in}DC$ check.
-Line $19$ ensures the power demand and the surge power of inverter.
-Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, 
-and the cost of that solution is calculated in $F_{obj}$ (line $21$). This cost is the equivalent of ~\ref{eq:LCC} described in Section ~\ref{sec:optcriteria}.
+Line $18$ checks the inverter check $I_{c}$, the charge controller DC input voltage $V_{in}DC$, and charge controller AC output voltage $V_{in}DC$ check.
+Line $19$ ensures the power demand and the surge power of the inverter.
+Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $21$).
+This cost is the equivalent to ~\ref{eq:LCC}, as described in Section ~\ref{sec:optcriteria}.
 
-If our algorithm does not find a feasible solution among the item of equipment that 
-were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
-the program finishes and does not find a solution, which indicates that it 
-was not possible to combine the items of each equipment in order to create a feasible solution.
+If our algorithm does not find a feasible solution among the item of equipment that were provided for our {\sc Synthesize} phase,  then the result is unsatisfiable (\textit{UNSAT}), i.e.
+the program finishes without finding a solution, indicating that it was not possible to combine the specific items of equipment in order to create a feasible solution.
 
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
-solution regarding the constraints and user requirements. Related to our {\sc Verify} 
-phase the challenge is to find the lowest acquisition cost from a list of equipment and 
-components that is provided from the {\sc Synthesize} phase.
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements.
+The challenge for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase.
 
-Note that the process described here is completely automated and that a validation is performed 
-by our {\sc Verify} phase to ensure that the approach is sound.
+Note that the process described here is completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
 
-\subsection{Optimization Assumptions and Premises}
+\subsection{Optimization Premises and Assumptions}
 \label{sec:OptAssumptions}
@@
 
-Here some premise are presented and some adopted assumptions are explained for the optimal sizing method, regarding the automated synthesis and simulation software.
+This section contains premises and assumptions underlying the optimal sizing method, in relation to automated synthesis and simulation software.
 
-Regarding the line $2$ of Algorithm~\ref{alg:opt-algorithm}, 
-a list of forty equipment from ten different manufacturers was provided 
-to the synthesis engine in order to allow the choice of every item 
-of PV sizing. Data sheet from each item was necessary to collect 
-technical information. Moreover, the price of each item was obtained 
-from available quotations in the market, and if the currency was not in US dollars, 
-then it was used the exchange rate of the day to convert it to US dollars.
+In line $2$ of Algorithm~\ref{alg:opt-algorithm}, the synthesis engine is provided with a list of forty items of equipment from ten different manufacturers in order to allow the engine to choose from among all items of PV sizing.
+The necessary technical information was collected from data sheet of each item.
+In addition, the price of each item was obtained from available market quotation, in US dollars.
+All the other currencies were converted to US dollars equivalents at the exchange rate of the day.
 
-With respect to power reliability, this work will rely on the critical period solar 
-energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
-The usual way is to use loss of load probability (LOLP) or loss of power 
-supply probability (LPSP). However, based on the fact that here we 
-are neither considering site characteristics nor the load changes over time, 
-which demands historical data, the reliability analysis will be developed only 
-by the critical period method of PV sizing.
+With respect to power reliability, the critical period solar energy method will be used~\cite{Pinho}, as described in Section~\ref{sec:sizing}.
+The usual way is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
+However, due to the fact that in this study we are considering neither site characteristics nor load changes over time, which demand historical data, the reliability analysis will be developed only by the critical period method of PV sizing.
 
-Regarding financial analysis:
+Financial analysis details:
 \begin{itemize}
 	\item LCC lifetime considered: $20$ years;
-	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
-	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
-	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
-This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
-Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
+	\item Installation costs: these include delivery to the isolated community and the actual installation costs: $5$\% of total cost~\cite{Agrener2013};
+	\item Value of the discount rate or interest rate: $10$\%, a good rate, considering financial investments in developing countries;
+	\item Annual operation and maintenance costs: based on past PV projects of similar size in the Brazilian Amazon, the sum of US\$ 289.64~\cite{Agrener2013} will be adopted.
+This cost includes battery replacement based on a lifetime of $4$ years for lead-acid batteries, plus inverters and controller replacement (every $10$ years).
+This means that there will be three battery bank and one inverter-controller replacement during the LCC analysis.
 \end{itemize}
 
-On the subject of PV system optimization technique, we will adopt here the intuitive method 
-since the average value daily of solar irradiance is used in the mathematical model, 
-without considering the battery's state of charge, or even the random nature 
-of solar irradiation and meteorological conditions. Therefore, all the computational 
-effort will be concentrated in our automated synthesis algorithm.
+The PV system optimization technique adopted here is the intuitive method, since the average daily value of solar irradiance is used in the mathematical model, without considering battery state of charge, or even the random nature of solar irradiation and meteorological conditions.
+Therefore, all the computational effort will be concentrated on our automated synthesis algorithm.
 
-Regarding batteries, the voltage of the system (DC bus) is set in $24$ V DC (but the value can be adjusted to $12$ or $48$ V at the code).
+With regard to batteries, the voltage of the system (DC bus) is set at $24$ V DC (but this can be adjusted to $12$ or $48$ V in the code).
 
-Related to HOMER Pro:
+HOMER Pro details:
 
 \begin{itemize}
-	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
-	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
-However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
-	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
-	\item HOMER Pro do not have a explicit equipment called charge controller.
-It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
-During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
-	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
-By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
-For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable;
-	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
-	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
+	\item HOMER Pro does not provide for the LCC cost in its reports. However, it has NPC and LCOE. For this reason, NPC was used to obtain LCC in order to allow the comparison among tools;
+	\item The optimization analysis of HOMER Pro permits the definition of a load curve and temperature on the basis of data collected automatically from online databases.
+However, in order to enable a correct comparison, the curve load and the temperature were defined exactly the same as automated synthesis tools;
+	\item Battery autonomy is not a parameter that the user can set when using HOMER Pro. The tool will always meet the user requirement, i.e. the load curve, $365$ days a year;
+	\item HOMER Pro does not have an item of equipment explicitly labeled charge controller.
+It uses a controller resource that can perform in two different ways, depending on optimization choice or user choice: load following or cycle charging~\cite{HOMER}.
+During the tests  'load following' controller was chosen: it produces only enough power to meet the demand~\cite{HOMER};
+	\item A 5\% of capacity shortage was assumed, equivalent to 95\%  availability of the PV system.
+By definition, availability is the percentage of time during which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
+For critical loads, 99\% is considered acceptable, while in an ordinary residential electrical load, 95\% is considered acceptable;
+	\item A string of two batteries was assumed in order to match the system voltage of $24$ V DC used by the automated synthesis tool;
+	\item The premise adopted when using HOMER Pro was that the user does not know the optimal solution, and that in order to obtain this solution it is necessary to include (at the design phase of the tool) generic PV and battery modules that HOMER Pro will search for the optimized power of each component.
+With that in mind, a generic flat plate PV of $1$ kW was included and generic lead-acid batteries of $1$ kW also (and with capacity of $83.4$ Ah in accordance with HOMER Pro modeling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
@@
 
-The general assumptions for the scientific method of automated synthesis are the same presented at Chapter~\nameref{chap:methodology1}, related to the code in ANSI-C, to the bound $k$, to simulation tool comparative, and to the battery state of charge.
+The general assumptions for the scientific method of automated synthesis are the same presented in Chapter~\nameref{chap:methodology1}, with respect to the code in ANSI-C, to the bound $k$, to the simulation tool comparison, and to the battery state of charge.
 
@@
 
-It was performed seven stand-alone PV system case studies to evaluate the proposed synthesis approach:
+The proposed synthesis approach was evaluated in  seven stand-alone PV system case studies:
 
@@
 
-These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{TrindadeCordeiro19, Agrener2013}.
-With exception of case 7 that was idealized as a small town solution to support few lamps and an 12 kBTUs air-conditioner.
+These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas,  Brazil~\cite{TrindadeCordeiro19, Agrener2013}, with the exception of case 7, that was idealized as a small town solution to support a few lamps and a 12 kBTUs air-conditioner.
 
@@
 on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
-$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
-Related to HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), 
-with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
-The experiments were performed with a predefined time out of $240$ minutes.
+$2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. 
+For HOMER Pro, an Intel Core i5-$4210$ ($4$-cores) was used, 
+with $1.7$ GHz and $4$ GB RAM, running Windows 10. 
+The experiments were conducted with a predefined time-out of $240$ minutes.
 
-Three start-of-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with solver Boolector 3.0.1~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engine to compare the proposed approach effectiveness and efficiency.
+Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
 Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
-The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
+The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purposes.
 
@@
 
-CPAchecker was able to synthesize the optimal sizing in six 
-out of seven case studies (cases $1$ to $6$): the result was produced within 
-the time limit, which varied from $134.71$ to $235.75$ minutes.
-Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing in the left size as the integer $8$ to the solar panel (which is the model RSM36-6-150P from manufacturer Risen), battery $0$ that means the model 12MF80 of 80 Ah from Moura, charge controller $1$ that means the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ means the model IP350-11 from Epever (750 W).
-The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, presented at the counter-example as well, shows how many and how the panels and batteries are connected.
+CPAchecker was able to synthesize optimal sizing in six 
+out of the seven case studies (cases $1$ - $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
+Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing on the left size as the integer $8$ for the solar panel (which is the model RSM36-6-150P from the manufacturer Risen), battery $0$ refers to the model 12MF80 of 80 Ah from Moura, charge controller $1$ refers to the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ refers to the model IP350-11 from Epever (750 W).
+The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counter-example as well, shows the number of panels and batteries and how they are connected.
 
-Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., 
-it was not solved within $240$ minutes. This is depicted in Fig.~\ref{fig:cpaoptcase7}. However, if it is removed this time out limitation from CPAchecker, the verifier is 
-able to solve the optimization in $44.97$ hours. 
+Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e.
+it was not solved within $240$ minutes.
+This is illustrated in Fig.~\ref{fig:cpaoptcase7}.
+However, this CPAchecker time-out limitation is removed, the verifier is able to solve the optimization in $44.97$ hours.
 The violation (SAT result) indicated in Table~\ref{tab1}
@@
 CBMC and ESBMC are unable to produce any conclusive result.
-Situations of \textit{internal failure}, \textit{time out}, 
-or \textit{out of memory} occurred; this partially answers 
-the \textit{EQ2}. Note that the internal failure presented 
-by ESBMC was a Z3 solver issue (a bug); this will demand 
-an updated version of ESBMC to fix this issue. Similarly to CPAchecker, 
-if it is removed the \textit{time out} from ESBMC with the SMT solver Boolector, 
-then the verifier is able to obtain the automated synthesis 
-in $73.18$ hours for the case study $2$. CBMC, in the other hand, only could present some result if the RAM memory of the system was bigger to avoid the \textit{memory out} issue.
+\textit{Internal failure}, \textit{time out}, or \textit{out of memory} situations occurred; this partially answers the \textit{EQ2}.
+Note that the internal failure presented by ESBMC was a Z3 solver issue (a bug), which will require an updated version of ESBMC to fix.
+Similar to CPAchecker, if the \textit{time out} is removed from ESBMC with the SMT solver Boolector, then the verifier is able to obtain the automated synthesis in $73.18$ hours for case study $2$.
+CBMC, on the other hand,  could present some result only if the RAM memory of the system was expanded in order to avoid the out of memory issue.
 
-Related to HOMER Pro, it was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much 
-faster than the proposed automated synthesis tool (cf.~\textit{EQ2}). 
-Case study $3$ was not possible to be simulated since HOMER Pro 
-does not have the feature of adjusting the battery autonomy, i.e., 
-the tool always tries to feed with electricity the given load 
-during $365$ days/year.
+HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}).
+Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e.
+the tool always tries to feed the given load with electricity $365$ days/year.
 
-Fig.~\ref{fig:homeroptc4} illustrates parts of the 9-page PDF report presented by HOMER Pro, specifically for the case 4.
+Fig.~\ref{fig:homeroptc4} illustrates parts of the 9-page PDF report presented by HOMER Pro, specifically for case 4.
 
@@
 
-It was also noted other HOMER Pro drawbacks:
+Certain other HOMER Pro drawbacks were also noted:
 
 \begin{itemize}
-\item There exists no explicit charge controller 
-as a system equipment. HOMER Pro includes automatically 
-a controller just to simulate the charge/discharge 
-of batteries and to meet the load requirement; however, 
-without costs or even with electrical characteristics 
-as maximum current and voltage, which are common during PV sizing;
-\item HOME Pro demands to include some battery specification 
-to initiate the optimization; however, it does not change 
-the electrical specifications during the simulation; 
-the presented results are multiples of the original 
-battery type suggested by the user. As example, it was 
-started with a $83.4$ Ah lead-acid battery and during 
-the simulation, HOMER Pro did not try to use other capacities or types;
-\item HOMER Pro does not present the optimal solution 
-in terms of connections of arrays of PV panels, just the 
-total in terms of power, i.e., it does not present neither models 
-and the power of each PV panel nor the total of panels in series or parallel. 
+\item System equipment does not include an explicit charge controller .
+HOMER Pro includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing;
+\item HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user.
+For example, it was started with a $83.4$ Ah lead-acid battery and during simulation, HOMER Pro did not try to use other capacities or types;
+\item HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e.
+it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
 \end{itemize}
@@
 
-Comparing the results between the formal synthesis with CPAchecker 
-and HOMER Pro, it was observed that most results are quite similar, 
+Comparing the results of the formal synthesis against those of CPAchecker and HOMER Pro, it was observed that most results are quite similar, 
 in terms of technical solution and cost (cf. Table~\ref{tab1}).
 
-Particularly related to LCC, the cost was very close in cases 
-$1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
-Even adopting the same price per kW to the PV panels, 
-inverters, and batteries, HOMER Pro does not use costs 
-related to charge controllers, which were introduced into the 
-CPAchecker modeling. The premise used in CPAchecker to adopt 
-a fixed annual cost for operation and maintenance can produce 
-some impact as well at this discrepancy; however, it is not significant
-since this annual cost is too small when compared to the resulting LCC value.
+Particularly in the case of LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with differences varying from $0.23$\% to $17.4$\%.
+Even adopting the same price per kW for PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling.
+The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well on this discrepancy; however, it is not significant since the annual cost is too small when compared to the resulting LCC value.
 
-However, there exists a huge divergence in case study $2$, 
-where the costs presented by HOMER Pro were $54$\% higher 
-than the automated synthesis tool, probably because the 
-operation and maintenance costs assumed by the automated 
-synthesis tool were underestimated to that specific load.
+However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by the automated synthesis tool were underestimated for that specific load.
 
-In general, the size of the PV panels and battery bank were 
-bigger in HOMER Pro than with the formal synthesis approach, 
-and that discrepancy is not easy to address without some real 
-systems validation. The mathematical models are different and 
-particular parameters can be tuned as well in each approach, 
-and that can justify the difference, which was presented in all 
-the case studies. As comparative, let's consider case study $1$: 
-the optimal solution provided by HOMER Pro demands $7$ $\times$ 
-more PV panels than the solution presented by the synthesis tool, 
-and HOME Pro does not show the arrangement of arrays 
-(i.e., the number of series and parallel PV panels); 
-the battery bank presented by HOMER Pro provides $500.4$ Ah 
-of capacity ($6 \times 83.4$), while the synthesis tool 
-presented an optimal solution with $420$ Ah of total capacity 
-($4 \times 105$).
+In general, the PV panels and battery bank were larger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation.
+The mathematical models are different and particular parameters can be tuned as well in each approach, and that can justify the difference, which was presented in all the case studies.
+As a comparison, consider case study $1$: the optimal solution provided by HOMER Pro requires $7$ $times$ more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e.
+the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $500.4$ Ah ($6 \times 83.4$), while the synthesis tool presented an optimal solution with a total capacity of $420$ Ah ($4 \times 105$).
 
-Just to compare the results obtained from the optimization 
-with the real-world, the authors had four PV systems deployed 
-and monitored since June $2018$ in a riverside community 
-in the Amazonas State in Brazil, with similar demands 
-presented by case studies $1$, $4$, $5$, and $6$, 
-always with a $3$ $\times$ $325$ W ($3$S) panels and 
-$4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) 
-lead-acid batteries. These solutions are more close 
-to the result presented by the proposed formal synthesis 
-approach than HOMER Pro, thereby showing that the 
-solution is sound, which answers \textit{EQ1}.
+Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+These solutions are closer to the result presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
 
-Related to the inverters, HOMER Pro suggests a value in 
-kW very close to the peak of every case study, and it 
-is just a reference value and not a commercial value of 
-the employed inverter. The proposed synthesis tool, however, 
-presents inverters that are commercial and can be found 
-off-the-shelf. Therefore is a PRO to the formal synthesis method.
+HOMER Pro suggests a value in kW for the inverters that is very close to the peak of every case study, and it is just a reference value and not a commercial value of the inverter employed.
+The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf.
+This is a clear advantage of the formal synthesis method.
 
-Concerning to charge controllers, as it was reported in 
-the section~\ref{sec:synthesisresults}, HOMER Pro does not include it 
-as an explicit equipment in its mathematical model, 
-only the synthesis tool presents a commercial controller 
-and includes it during the cost analysis. Therefore, 
-the formal synthesis method presents more reliable results than
-HOME Pro.
+As was reported in section~\ref{sec:synthesisresults}, HOMER Pro does not include charge controllers as an explicit item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis.
+The formal synthesis method, therefore, presents more reliable results than HOMER Pro.
 
-Case study $7$ was not solved by the synthesis tool 
-within the time limit established during the experimental 
-phase. Case study $3$ was not possible to simulate in HOMER Pro, 
-because its restriction does not allow one to set the battery autonomy, 
-thus resting both without parameters to comparative.
+Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
+Case study $3$ could not be simulated in HOMER Pro, because of its restriction on setting battery autonomy, thus leaving both without parameters to compare.
 
-Summarizing, the synthesis tool is capable to present a 
-solution, which is far detailed and close to the commercial 
-reality than the solution presented by HOMER Pro. 
-In particular, the automated synthesis method 
-can provide all the details of every component of 
-a PV system solution, with complete electrical details 
-from data sheet of manufacturers, including 
-the model of the component, nominal current and voltage. 
-In this respect, even the name of the manufacturer 
-can be presented (in Table~\ref{tab1} it was removed 
-to avoid some advertising).
+Summarizing, the synthesis tool is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including  the model of the component, nominal current and voltage.
+In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising).
 %used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
@@
 
-At this Section, it was reported a favorable assessment of proposed formal synthesis method. 
-Nevertheless, it was also identified three threats to the validity 
-of the experimental results, which can be further assessed and 
+In this Section, a favorable assessment was made of the proposed formal synthesis method.
+Nevertheless, three threats to the validity of the experimental results were also identified, which can be further assessed and
 constitute future work:
@@
 \begin{itemize}
-\item ($1$) improvement of the power reliability 
-analysis: to include loss of load probability or loss of power 
-supply probability, which can make the analysis more accurate; 
-\item ($2$) the cost analysis is well tailored to the Amazon region of Brazil; 
-however, a broad analysis from other isolated areas must be 
-performed in order to make the optimization general in terms 
-of applicability; 
-\item ($3$) to deploy at the field some PV systems 
-sized using the synthesized results in order to validate it.
+\item ($1$) improvement to the power reliability analysis: inclusion of loss of load probability or loss of power supply probability, in order to increase the accuracy of the analysis; 
+\item ($2$) the cost analysis is well tailored to Brazilian Amazon; however, a broad analysis of other isolated areas must be  performed in order to make the optimization general in terms of applicability;
+\item ($3$) deployment in the field of PV systems sized using the synthesized results in order to validate them.
 \end{itemize}
@@
 
-In this Chapter we showed in details how the state-of-art computer science method of automated synthesis method was adapted in order to be used in stand-alone solar PV systems to obtain the optimal project sizing.
-Moreover, is was possible to picture how the proposed method compares with the traditional use of simulation tool for the same purpose.
+In this Chapter we showed in detail how the state-of-the-art computer science method of automated synthesis has been adapted to use in stand-alone solar PV systems in order to obtain optimal project sizing.
+Moreover, it was possible to illustrate how the proposed method compares with the traditional use of a simulation tool for the same purpose.
 
-Detailed diagrams, flowcharts and algorithms with pseudo-code were presented with the aim to support the proposed work and to facilitate the understanding.
-And even more so, the assumptions adopted for the automated verification and simulation software were listed.
+Detailed diagrams, flowcharts and algorithms with pseudo-code were presented as support for the proposed work and to aid understanding.
+Also listed, were the assumptions underlying the automated verification and simulation software.
 
-It was performed the comparative among verifiers with the proposed automated synthesis using model checking, in order to obtain the optimal sizing of stand-alone solar PV systems, which showed that CPAchecker had the best overall performance.
-CBMC and ESBMC were not conclusive for all the cases, reaching the \textit{time out} stipulated ($240$ minutes) or by \textit{out of memory} issue.
-CPAchecker was not possible to present a conclusive result just in case $7$ (\textit{time out}).
+Comparison of verifiers with the proposed automated synthesis using model checking was made, in order to obtain the optimal sizing of stand-alone solar PV systems, which showed that CPAchecker had the best overall performance.
+CBMC and ESBMC were not conclusive for all the cases, reaching the \textit{time out} stipulated ($240$ minutes) or being \textit{out of memory}.
+CPAchecker was unable to present a conclusive result only in case $7$ (\textit{time out}).
 
-A comparative with a specialized simulation tool was performed as well, however in just $5$ case studies (case $1$, case $2$, case $4$, case $5$, and case $6$) it was possible comparative for the presented result.
-Some limitations of the simulation tool, mainly related to not allow battery autonomy setup, and the $time out$ or $out of memory$ messages presented by the verifiers, restricted the comparative between automated verification tools versus simulation tools.
-However, when the comparative was possible, it was noticed that the LCC was very close, and that HOMER Pro overestimated the sizing.
+A comparison with a specialized simulation tool was also made, however only $5$ case studies (case $1$, case $2$, case $4$, case $5$, and case $6$) compared to the presented result.
+Some limitations of the simulation tool, mainly related to not allowing battery autonomy setup, and the $time-out$ or $out of memory$ messages presented by the verifiers, restricted the comparison between the automated verification tools and the simulation tools.
+However, when the comparison was possible, it was noticeable that the LCC came very close, and that HOMER Pro overestimated the sizing.
 
-Based on the fact that mostly case studies were deployed at the field (case $1$, case $4$, case $5$, and case $6$), with regular visiting to perform interview with the dwellers, and with monitoring system in those houses, it was possible to compare the computer obtained results with the real world employment of the stand-alone solar PV systems.
-The final conclusion was that the proposed tool is sound, with an acceptable performance, and with a better quality of the presented output.
+Based on the fact that mostly case studies were deployed in the field (case $1$, case $4$, case $5$, and case $6$), with regular visits to conduct interviews with the residents, and consult the monitoring system in those houses, it was possible to compare the computer assisted results with the real-world employment of stand-alone solar PV systems.
+The final conclusion was that the proposed tool is sound, with an acceptable performance, and a higher quality output.

### 2020-01-10 Tex/Old text/abbreviations.tex
thesis update

@@
 AC Alternating current \\
+ANEEL National Electricity Agency (from Brazil) \\
 $C_{10}$ 10h of rated battery capacity \\
@@
 CBMC C Bounded Model Checker \\
+CEGIS Counterexample Guided Inductive Synthesis \\
+CFA Control-Flow Automata \\
 $ cos \varphi $ Power factor of the inverter \\
@@
 CPAchecker Configurable Program Analysis Checker \\
+CPES Cyber-Physical Energy Systems \\
+CPS Cyber-Physical Systems \\
 DC Direct current \\
-$DOD$ Depth of discharge ($DOC=1-SOC$) \\
+$DOD$ Depth of discharge ($DOD=1-SOC$) \\
 $E_{consumption}$ Energy consumption \\
@@
 $ G_{ref} $ Solar irradiance at STC ($1000 W/m^{2}$) \\
+GEF Global Environment Facility \\
+HDI Human Development Index \\
+IRR  Internal Rate of Return \\
 $I$ Current \\
@@
 $ I_{in} $ Input current \\
-$I_{load}$ Current that feed the load \\
+$I_{load}$ Current that feeds the load \\
 $ I_{out} $ Output current \\
@@
 $ k_{B} $ Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); \\
+LCC  Life Cycle Cost \\
+LCOE Levelized Cost of Energy \\
+LLP  Loss of Load probability \\
+LOLP Loss of Load Probability \\
+LPSP Loss of Power Supply Probability \\
 $MAX_{AC,ref}$ Peak power that the inverter can support \\
+MPPT Maximum Power Point Tracking \\
 $N$ Number of series-connected cells \\
-$N_{B}total$ Sized number of batteries \\
-$N_{BP}$ Sized number of parallel batteries \\
+$N_{B}total$ Number of sized batteries \\
+$N_{BP}$ Number of sized parallel batteries \\
 $N_{BP}min$ Total minimum number of parallel batteries \\
-$N_{BS}$ Sized number of series batteries \\
+$N_{BS}$ Number of sized series batteries \\
 $N_{BS}min$ Total minimum number of series batteries \\
 NOCT Nominal Operating Cell Temperature \\
-$N_{PS}$ Sized number of panels in series \\
+NPC  Net Present Cost \\
+$N_{PS}$ Number of sized panels in series \\
 $N_{PSmin}$ Total number of panels in series \\
-$N_{PP}$ Sized number of panels in parallel \\
+$N_{PP}$ Number of sized panels in parallel \\
 $N_{PPmin}$ Total umber of panels in parallel \\
-$ N_{TP} $ Sized number of panels \\
-$N_{TPmin}$ Total minimum number of needed solar panels \\
+$ N_{TP} $ Number of sized panels \\
+$N_{TPmin}$ Total minimum number of solar panels needed \\
 PV Photovoltaic \\
@@
 $q$ Absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $) \\
+QF  quantifier-free (formula) \\
+RQ Research Question \\
+REEEP Renewable Energy and Energy Efficiency Partnership \\
 SAT Satisfiability or Boolean satisfiability problem \\
-SAT When returns a failure from the verification tool \\
-SMT Satisfiability modulo theories \\
+SAT When the verification tool returns a failure \\
+SMT Satisfiability module theories \\
 $ SOC $ Battery state of charge \\
@@
 $ T_{ref}$ Temperature at STC ($=298.15 K$ or $25^{o}C$) \\
+UNEP United Nations Environment Programme \\
 UNSAT Condition when verification tool succeeds (could not reach an error) \\
 V Voltage \\
-$ V_{AC}  $ Voltage that the inverter supply to the house \\
+$ V_{AC}  $ Voltage that the inverter supplies to the house \\
 $V_{c}$ Battery charge voltage  \\

### 2020-01-10 Tex/Old text/chapters/appendix.tex
thesis update

@@
 %
-Here there are a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.
+Papers written during thesis elaboration with the status of every submission up to the date of this document.
 
@@
 Trindade, A., Cordeiro, L.
-\textbf{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}, submitted: 8 May 2019, status: accepted 26 September 2019; published on-line on 15 October 2019) by Elsevier Solar Energy (Impact Factor 4.674, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV) \url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X1930965X}~\cite{TrindadeCordeiro19}.
+\textbf{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}, submitted: 8 May 2019, status: accepted 26 September 2019; published online 15 October 2019 by Elsevier Solar Energy (Impact Factor 4.674, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV) \url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X1930965X}~\cite{TrindadeCordeiro19}.
 
@@
 
-\section{Congress}
+\section{Conference}
 
 Trindade, A., Cordeiro, L.
-\textbf{Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems}, submitted: 06 May 2019, status: rejected by The IEEE/ACM Automated Software Engineering (ASE 2019) Conference (New Ideas Papers) in \url{https://2019.ase-conferences.org/track/ase-2019-papers}.
-This paper is now the base of a new paper, for the 32nd International Conference on Computer-Aided Verification (CAV) 2020 with deadline in 23 January 2020 in \url{http://i-cav.org/2020/call-for-papers/}.
+\textbf{Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems}, submitted: 6 May 2019, status: rejected by The IEEE/ACM Automated Software Engineering (ASE 2019) Conference (New Ideas Papers) in \url{https://2019.ase-conferences.org/track/ase-2019-papers}.
+This paper is now the base of a new paper, for the 32nd International Conference on Computer-Aided Verification (CAV) 2020 with deadline on 23 January 2020 in \url{http://i-cav.org/2020/call-for-papers/}.

### 2020-01-10 Tex/Old text/chapters/appendixB.tex
thesis update

@@
-Here we describe the two tools created with the target to implement and validate the two scientific methodologies of the thesis.
+Here we describe the two tools created to implement and validate the two scientific methods/techniques of the thesis.
 
@@
 
-During the Ph.D.
-process, the techniques from computer science proposed to tackle issues related to solar photovoltaic systems became algorithms and programs.
-Those programs became tools, and the tools were used during comparative with simulation tools in order to validate the techniques.
+During the doctoral process, the techniques from computer science proposed to deal with issues inherent to solar photovoltaic systems became algorithms and programs.
+These programs became tools, and the tools were used for the purpose of comparison with simulation tools in order to validate the techniques.
 
-One premise of our tools was to be written as an ANSI C program, and to follow the requirements established for the International Competition on Software Verification (SV-COMP) \footnote{https://sv-comp.sosy-lab.org/}.
-That allow us to write a code that could be executed into three different verifiers without adaptation, and even in the future other verifiers can be used as well.
+One premise of our tools was that they will be written as an ANSI C program, and to follow the requirements established for the International Competition on Software Verification (SV-COMP) \footnote{https://sv-comp.sosy-lab.org/}.
+This allows us to write a code that can be executed into three different verifiers without adaptation, with the possibility that in the future, other verifiers can also be used.
 %
@@
 
-Therefore, we wrote the code without the use of '\# include', or '\# define'.
-Moreover, based on the fact that there exists no use of compiler library, it was necessary to write some functions, which perform specific calculations according to the adopted mathematical models (e.g., logarithm of natural order and exponential).
+With this in mind, the code was written without using of '\# include', or '\# define'.
+Moreover, based on the fact that a compiler library is not used, it was necessary to write in some functions which perform specific calculations depending on the mathematical models adopted (e.g.
+natural logarithms and exponents).
 
 %---------------------------------------
-\subsection{Automated Verification Tool (PV System validation)}
+\subsection{The Automated Verification Tool (for PV System validation)}
 \label{sec:automatedverification}
@@
 \begin{itemize}
-\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and datasheet information from each equipment of the PV system that will be verified;
+\item \textbf{Block 1}: global variables declaration, with weather data from the location (minimum and maximum solar irradiance and temperature, for 24 hours of the day) as array, requirements, and datasheet information pertaining to each item of equipment of the PV system to be verified;
 
-\item \textbf{Block 2}: support functions (e.g., logarithm of natural order, exponential);
+\item \textbf{Block 2}: support functions (e.g. natural logarithms,  exponents);
 
@@
 
-\item \textbf{Block 4}: main code with charge, discharge battery control, based on PV generation from solar panels and the state of charge form batteries, committing to deliver the power and energy that the house demands, according with the restrictions form the sized system.
+\item \textbf{Block 4}: main code with charge, discharge battery control, based on PV generation from solar panels and the battery state of charge, committing to deliver the power and energy that the house requires, in  accordance with the restrictions from the sized system.
 \end{itemize}
@@
 %---------------------------------------
-\subsection{Automated Synthesis Tool (PV System Optimal Sizing)}
+\subsection{The Automated Synthesis Tool (for PV System Optimal Sizing)}
 \label{sec:automatedsynthesis}
@@
 \begin{itemize}
-\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and datasheet information from each equipment of the PV system that will be verified;
+\item \textbf{Block 1}: global variables declaration, with weather data from the location, user requirements, and datasheet information on each item of equipment of the PV system to be verified;
 
-\item \textbf{Block 2}: support functions (start value with the lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);
+\item \textbf{Block 2}: support functions (start value at the lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);
 
@@
 %---------------------------------------
-\section{How to use it}
+\section{Instructions on How to Use it}
 %---------------------------------------
 
-The only block that demands user intervention to input data is the block 1 listed in~\ref{sec:automatedverification} and \ref{sec:automatedsynthesis} from the automated verification and synthesis tools respectively.
-If it is aimed to change the mathematical model adopted, so coding must be done in block 3 of the automated verification tool and block 2 of the automated synthesis tool.
+The only block that requires user intervention to input data is Block 1 listed in~\ref{sec:automatedverification} and \ref{sec:automatedsynthesis} from the automated verification and synthesis tools respectively.
+If the intention is to change the mathematical model adopted, coding must be done in Block 3 of the automated verification tool Block 2 of the automated synthesis tool.
 
-Regarding the automated verification tool, it is necessary to input the following data (editing and modifying the code):
+For the automated verification tool, it is necessary to input the following data (editing and modifying the code):
 
 \begin{itemize}
-\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
+\item Minimum and maximum solar irradiance (average value for the 24 hours of the day) at location;
 \item Minimum and maximum temperature (average for every month of the year);
-\item Local insolation (average number of sun hours by day at the location);
+\item Local insolation (average number of sun hours per day at the location);
 \item Number of solar panels in series;
@@
 \item Number of batteries in parallel;
-\item Autonomy of the batteries;
-\item Efficiency from batteries;
+\item Battery autonomy;
+\item Battery efficiency;
 \item Float, absorption, and bulk battery voltages;
@@
 \item Inverter maximum (surge) AC power reference;
-\item AC voltage (outlet standard);
+\item AC voltage (standard voltage from outlet);
 \item Power demand from the house;
@@
 
-Moreover, regarding the automated synthesis tool, it is necessary to add the following data (editing and modifying the code):
+in the case of the automated synthesis tool, the following data must be added (editing and modifying the code):
 
 \begin{itemize}
-\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
+\item Minimum and maximum solar irradiance (average value for the 24 hours of the day) at location;
 \item Minimum and maximum temperature (average for every month of the year);
-\item Local insolation (average number of sun hours by day at the location);
+\item Local insolation (average number of sun hours per day at the location);
 \item DC-bus voltage;
-\item Autonomy of the batteries;
+\item Battery autonomy;
 \item State of charge limit;
@@
 \item Reference temperature;
-\item For every item of solar PV panel list, as a matrix (area, efficiency, number of series-connected cells, Nominal Operating Cell Temperature, short-circuit current temperature coefficient, open-circuit voltage temperature coefficient, reference short-circuit current, reference open-circuit voltage, reference maximum power, reference maximum current, reference maximum voltage, maximum voltage on NOCT, cost in US dollars);
-\item For every item of batteries list, as a matrix (efficiency, voltage, capacity $C_{20}$), bulk voltage, float voltage, cost in US dollars);
-\item For every item of charge controller list, as a matrix (efficiency, nominal current, voltage output, minimum MPPT voltage, maximum current, cost in US dollars);
-\item For every item of inverter list, as a matrix (efficiency, input DC voltage, output AC voltage, reference AC power, reference maximum AC power, cost in US dollars);
-\item AC voltage (outlet standard);
+\item For every item on the solar PV panel list, as a matrix (area, efficiency, number of series-connected cells, Nominal Operating Cell Temperature, short-circuit current temperature coefficient, open-circuit voltage temperature coefficient, reference short-circuit current, reference open-circuit voltage, reference maximum power, reference maximum current, reference maximum voltage, maximum voltage on NOCT, cost in USD);
+\item For every item on the battery list, as a matrix (efficiency, voltage, capacity $C_{20}$), bulk voltage, float voltage, cost in USD);
+\item For every item on the charge controller list, as a matrix (efficiency, nominal current, voltage output, minimum MPPT voltage, maximum current, cost in USD);
+\item For every item on the inverter list, as a matrix (efficiency, input DC voltage, output AC voltage, reference AC power, reference maximum AC power, cost in USD);
+\item AC voltage (standard voltage from outlet);
 \item Power demand from the house;
@@
 
-Here we describe precisely how to use the code explained in the previous section (\ref{sec:automatedverification}) using the incremental ESBMC with the Z3 SMT solver that presented the better performance during the comparative than other verifiers.
-However, in \ref{sec:setup} it was showed how to use the code with other verifiers.
+Here we describe precisely how to use the code explained in the previous section (\ref{sec:automatedverification}) using the incremental ESBMC with the Z3 SMT solver that presented the best performance during the comparison with other verifiers.
+However, in \ref{sec:setup} it was shown how to use the code with other verifiers.
 
@@
 Installation commands can be found in \url{https://ssvlab.github.io/esbmc/documentation.html}.
-There is just the Linux version of the verifier.
+There is only the Linux version of the verifier.
 
@@
 \item -\phantom{}-no-pointer-check: says to the verifier to not check if there is pointer violation;
-\item -\phantom{}-unwind 100: it limits the bound of search (100 in this case);
-\item -\phantom{}-smt-during-symex: enable incremental SMT solving;
-\item -\phantom{}-smt-symex-guard: call the solver during symbolic execution;
+\item -\phantom{}-unwind 100: limits the bound of search (100 in this case);
+\item -\phantom{}-smt-during-symex: enables incremental SMT solving;
+\item -\phantom{}-smt-symex-guard: calls the solver during symbolic execution;
 \item -\phantom{}-z3: uses Z3 as solver.
@@
 
-Some results issued by the ESBMC verifier were shown in \ref{sec:ESBMCverification} when performing the case studies.
+Some results issued by the ESBMC verifier were shown in \ref{sec:ESBMCverification} when conducting the case studies.
 
@@
 
-Here we describe precisely how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, which presented better performance during the comparative than other verifiers.
-However, in \ref{sec:synthesissetup} it was showed how to use the code with other verifiers.
+Here we describe precisely how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, which presented the best performance during the comparison with other verifiers.
+However, in \ref{sec:synthesissetup} it was shown how to use the code with other verifiers.
 
-The CPAchecker can be downloaded from its web site in \url{https://cpachecker.sosy-lab.org/}. There are versions available to Linux and MS-Windows operational systems.
+The CPAchecker can be downloaded from its web site in \url{https://cpachecker.sosy-lab.org/}. There are versions available for Linux and MS-Windows operational systems.
 
@@
 
-Note that the default heap size is 1200m (or 1.2 GB of RAM).
-However, it is indicated to specify a significant value with '-heap' if you have more RAM available.
+Note that the default heap size is 1200m (or 1.2 GB RAM).
+However, specifying a significant value with '-heap' is recommended if you have more RAM available.
 In our case, we adjusted the heap to 64000m (64 GB).
 
-Another important issue is the time-out of the execution process: the parameter 'limits.time.cpu' at the file 'resource-limits.properties' in folder 'config/includes' must be edited according to the desired value.
-In our case, 'limits.time.cpu = 14400s', i.e., 14400 seconds or 240 minutes or 4 hours.
+Another important issue is the time-out of the execution process: the parameter 'limits.time.cpu' in the file 'resource-limits.properties' in folder 'config/includes' must be edited according to the desired value.
+In our case, 'limits.time.cpu = 14400s', i.e.
+14400 seconds or 240 minutes or 4 hours.
 
-Some results, reports, and graphics, issued by the CPAchecker verifier were depicted in \ref{sec:synthesisresults}.
+Some results, reports, and graphics, issued by the CPAchecker verifier were illustrated in \ref{sec:synthesisresults}.

### 2020-01-10 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 \centering
-\caption{Unregulated standalone SPV system with DC load. Source: \cite{Roy}.}
+\caption{Unregulated standalone solar PV system with DC load. Source: \cite{Roy}.}
 \label{fig:unregSPV}
@@
 \centering
-\caption{Regulated standalone SPV system with DC load. Source: \cite{Roy}.}
+\caption{Regulated standalone solar PV system with DC load. Source: \cite{Roy}.}
 \label{fig:regSPV1}
@@
 \centering
-\caption{Regulated standalone SPV system with battery and DC load. Source: \cite{Roy}.}
+\caption{Regulated standalone solar PV system with battery and DC load. Source: \cite{Roy}.}
 \label{fig:regSPV2}
@@
 \centering
-\caption{Regulated standalone system with battery, AC load. Source: \cite{Roy}.}
+\caption{Regulated standalone PV system with battery, AC load. Source: \cite{Roy}.}
 \label{fig:regSPV3}
@@
 
-The design and validation of a SPV system can be done by hand or with the aid of a software tool.
-
-In order to address different aspects of a project system and system's design, a lot of public domain and commercial software is available for the SPV market.
+The design and validation of a solar PV system can be done by hand or with the aid of a software tool.
+
+In order to address different aspects of a project system and system's design, a lot of public domain and commercial software is available for the solar PV market.
 According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, and to complex financial analysis software (with optimization).
@@
 
-The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the fraction of discharge, i.e., $ DOC=1-SOC $.
+The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the fraction of discharge, i.e., $ DOD=1-SOC $.
 

### 2020-01-10 Tex/Old text/chapters/conclusion.tex
thesis update

@@
-Here we present the conclusions about our research and the results obtained during the Doctoral process.
-In particular, we described two scientific methods (or techniques) from computer science, which were used to tackle solar PV systems issues, as validation over time and sizing optimization.
-A list of future contributions concludes the work; this list might foster the creation of a research group that investigates model checking techniques to electrical systems (and not only renewable sources as we have done here).
+Here we present the conclusions of our research and the results obtained during the Doctoral process.
+In particular, we described two scientific methods (or techniques) from computer science, which were used to tackle issues in PV systems, such as validation over time and sizing optimization.
+A list of future contributions concludes the study, although this list might foster the creation of a research group to investigate model checking techniques for electrical systems (and not only renewable sources as has been the focus here).
 
@@
 
-We split our contributions into two, each one concerning the scientific methods proposed with the use of model checking to solar PV systems, and the tools created to validate it.
+We split our contributions into two, each one concerning the scientific methods proposed with the use of model checking for solar PV systems, and the tools created to validate it.
 
-Concerning the first contribution presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method to validate a given stand-alone PV system.
-Our method, using model checking, can performance size check and verify, over time, whether a PV system meets electrical requirements.
-We showed that there exist various possibilities to perform that validation, such as testing, laboratory measuring, or even simulation.
+The first contribution was presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method of validating a given stand-alone PV system.
+Our method, using model checking, can perform a size check and verify, over time, whether a PV system meets electrical requirements.
+We showed that there are various possible ways to perform that validation, such as testing, laboratory measuring, or even simulation.
 However, we developed an algorithm and a tool using model checking that was feasible and effective.
-Our results were supported by case studies, by monitoring data from the field, and an interview with PV owners.
+Our results were supported by case studies, by data gathered from the field, and by interviews with PV owners.
 
-We have considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W (inverter specification), and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-Although the verification method that we proposed takes longer than simulation methods, it can avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.
+We analyzed five case studies of real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W (inverter specification), and the results of three state-of-the-art verification engines (ESBMC, CBMC, and CPAchecker).
+Although the verification method that we proposed takes longer than the simulation methods, it can avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.
 We validate these results by the sized systems deployed in the field.
@@
 Moreover, considering that HOMER Pro always performs size optimization during the simulation process, the user always has to ``adopt'' this simulation tool in order to avoid the optimization and to validate the PV system as inputted in it.
-That adaptation is not necessary using our approach, because optimization is another method different to verification.
-Besides, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature, i.e., the user can not specify the battery autonomy.
+That adaptation is not necessary using our approach, because optimization is a method separate from verification.
+Besides, only the proposed method of automated verification was able to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature, i.e.
+the user can not specify battery autonomy.
 
@@
 %
-Concerning the verification engines comparative, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented the better performance than CBMC (around four times faster), used less RAM than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker).
+In the comparison among verification engines, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented a better performance than CBMC (around four times faster), used less RAM than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB for CBMC and 19.2GB for CPAchecker).
 All our experimental results are sound since the PV owners and the monitoring system validated the possible flaws that the system could present in the field.
@@
 
-Furthermore, we have also contributions from the method described in~\autoref{chap:automatedsynthesis}.
-We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking techniques.
-The focus was on the synthesis method to obtain the optimal solution based on formal methods, which can cover better the design-space as opposed to simulation tools.
-Our thesis produced a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
+Furthermore, we also have contributions from the method described in~\autoref{chap:automatedsynthesis}, where we describe and evaluate an automated synthesis method of obtaining the optimal size of a PV system using software model checking techniques.
+The focus was on the synthesis method of obtaining the optimal solution based on formal methods, which can improve coverage of the design-space more effectively than simulation tools.
+Our thesis produced methodological research which innovated with regard to the first use of automated synthesis for optimal sizing of solar PV systems.
 
-We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase and refinement from the iterative search from the {\sc Verify} phase.
-With this approach, we obtain the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
-Our algorithm that implements this method uses a database of commercial equipment from the marketing, including the price.
-Furthermore, in order to validate our method, we considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-Besides, we used again the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
-In terms of performance and better results, CPAchecker was the winner and used for the comparative with the simulation tool.
+We proposed a variant of the CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase and refinement from the iterative search from the {\sc Verify} phase.
+Using this approach, we obtain the optimization of stand-alone PV systems, arriving at the best compromise between power reliability and system cost analysis.
+Our algorithm that implements this method uses a database of commercially available equipment, including the price.
+Furthermore, in order to validate our method, we conducted seven case studies of PV systems on two different sites in the State of Amazonas, Brazil, ranging from $253$\,W to a $1,586$\,W peak; and three state-of-the-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
+In addition, we again used the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
+In terms of performance and best results, CPAchecker was the most successful and used for the comparison with the simulation tool.
 
-In summary, our synthesis proposal is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
+In summary, our synthesis proposal is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the component model, nominal current, and voltage.
+We also cover the charge controller, which is unavailable in HOMER Pro.
+Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro.
+However, the solution presented is sound and complete; it also provides a list of equipment that can be bought direct from the manufacturer.
+
+%In summary, our synthesis proposal is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
 In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the component model, nominal current, and voltage.
@@
 %----------------------------------------------
-\section{Future Work Directions}
+\section{Areas for Further Research}
 %----------------------------------------------
 
-As the focus here was stand-alone solar PV systems, one future work will consider other types of renewable energy and even hybrid ones to allow the method to verify and to obtain the optimal sizing of typical rural electrification systems.
+As the focus here was stand-alone solar PV systems, one promising area for further research will include analysis of other types of renewable energy, even hybrid  in order to allow the method to verify and obtain optimal sizing of typical rural electrification systems.
 
-Related to automated sizing, the author plans to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil), and to validate some cases with deployed PV systems in isolated communities.
+In the area of automated sizing, the author plans to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the State of Amazonas (Brazil), and to validate some cases with deployed PV systems in isolated communities.
 
 We plan to develop the code of a general-purpose simulation tool, like MATLAB, for example, using the same mathematical model employed in our two methods.
-Thus a broader comparison can be made in order to cover all the possibilities to validate or optimize solar PV systems.
+A broader comparison can thus be made in order to cover all the possibilities of validation or optimization of  solar PV systems.
 
-One future long term direction is to foster the creation of a research group in automated verification and synthesis applied to electrical systems.
+One future long-term direction is to foster the creation of a research group in automated verification and synthesis applied to electrical systems.
 
@@
 
-The automated verification and automates synthesis methods demonstrate the effectiveness and the potential of use in stand-alone solar PV systems.
-We must address some issues in order to improve the tools, as performance and the human-computer interaction.
+The automated verification and automated synthesis methods demonstrate their effectiveness and potential for use in stand-alone solar PV systems.
+Although clearly there are still issues to address in order to improve the tools, notably performance and the human-computer interaction.
 
-About license and the use of tools mentioned in this thesis, note that HOMER Pro is available only for Microsoft Windows, and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}.
-Related to the verifiers, as CPAchecker, ESBMC and CBMC, and their solvers, they are based on open-source software license and usually allows the users to use, modify, and distribute licensed product freely.
-Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is an advantage when compared to commercial tools).
+The licensing and use of tools mentioned in this thesis is different for HOMER Pro, which is available only for use with Microsoft Windows, and whose standard annual subscription is set at US\$ $504.00$~\cite{HOMER}.
+The verifiers, CPAchecker, ESBMC and CBMC, and their solvers, are based on open-source software licenses which usually allow the users to use, modify, and distribute licensed products freely.
+Permission is granted, free of charge, to use this software for evaluation and research purposes (which is a great advantage when compared to commercial tools).
 
-The tools we described here have no similarity to any other pior work.
-We can conclude that we have have produced original research that expands the boundaries of knowledge.
-In particular, we have proposed cutting-edge computer science methodologies to solve typical electrical engineering problems and to improve the design of systems.
+The tools we have described here in no way similar to any other prior work.
+We may conclude that our research is original and expands the boundaries of knowledge.
+In particular, we have proposed cutting-edge computer science methodologies to solve typical electrical engineering problems and to improve the designing of systems.
 
-Moreover, last, but not least significant to report, one of the great things about Ph.D.
+Moreover, last but not least, one of the most important aspects of Ph.D.
+work is that the student-researcher will be able to conduct this line of research in the future.
+In that direction, we can say that with the methods proposed here,  formulated to tackle issues in the energy sector, there exists a vast field of possible future applications and developments, using different renewable sources.
+We can mention here biomass, wind, or even hybrid generation, with different mathematical models and requirements; and including smart grids, or electrical systems in general.
+Little research has been done on this until now, but the scenario is auspicious.
+%
+%Moreover, last, but not least significant to report, one of the great things about Ph.D.
 is that the student will be able to conduct its research in the future.

### 2020-01-12 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of seven different intricate case studies.
-In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends in energy access still fall short of global goals.
+
+%In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends in energy access still fall short of global goals.
 Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
@@
 The use of formal methods in electrical systems is a new subject, with published research spanning only the last four years.
-Moreover, the use of automated synthesis in order to obtain optimal sizing of solar photovoltaic systems has never been done before; this is our major goal: a sound, automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis.
+Moreover, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems has never been done before.
+Here our primary goal is to develop and evaluate a sound, automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis.
 We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach, with two phases linking the technical and the cost analysis.
-First, we synthesize a feasible candidate based on power reliability, but which may not attain the lowest cost.
+First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
 Second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
 If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution.
-Experimental results using seven case studies demonstrate that we can produce optimal solution within an acceptable run-time.
-We also present a comparison with a specialized simulation tool over real photovoltaic systems in order to show the effectiveness of our approach.
+Experimental results using seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time.
+We also present a comparison with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach.
 \keywords{Automated verification  \and Model Checking \and Electric systems \and Solar photovoltaic systems.}

### 2020-01-12 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised affiliation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-\institute{Federal University of Amazonas, Av. Gen. Rodrigo Octavio, 6200, Coroado I, 69077-000 Manaus AM Brazil \email{alessandrotrindade@ufam.edu.br} \and
-The University of Manchester, Kilburn Building, Oxford Road, Manchester M13 UK
-\email{lucas.cordeiro@manchester.ac.uk}}
+\institute{Federal University of Amazonas, Brazil \email{alessandrotrindade@ufam.edu.br} \and
+University of Manchester, UK \email{lucas.cordeiro@manchester.ac.uk}}
 \maketitle              % typeset the header of the contribution

### 2020-01-12 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We also present a comparison with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach.
-\keywords{Automated verification  \and Model Checking \and Electric systems \and Solar photovoltaic systems.}
+\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
-the seamless integration of computational  and  physical  components~\cite{NSF2015}. 
-During operation, such components must frequently adapt to the executing environment changes 
-faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
-in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
-%Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
-%Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
-%unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
-%
-%While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+%Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015}.
+During operation, such components must frequently adapt to the executing environment changes faced at run-time (dynamics of the physical processes).
+They must be able to continue behaving in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
 Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis.
-% with the goal of synthesizing correct-by-construction implementations of CPS.
 These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
@@
 
-Energy production, distribution, and optimization are all CPS problems~\cite{UC}.
+%Energy production, distribution, and optimization are all CPS problems~\cite{UC}. 
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
 Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}.
-To provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}.
-%; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.
+In order to provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}.
 
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
-; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
+In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}; and even general-purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
  However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
-Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.
-%However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}.
-Related to the use of formal methods based on \textit{symbolic model checking} and its application to electric systems: in $2015$ an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}; in $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}; in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}; and finally, in $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
+Optimization of PV systems is not a recent topic; since the 90's, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}.
+%Concerning the use of formal methods based on \textit{symbolic model checking} and its application to electric systems. 
+In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
+In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
+In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
 However, formal methods and its application to synthesize PV systems are still unexplored in literature.
@@
 Note that in this study, our focus is not on new criteria or even optimization objectives.
-Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.
+Instead, our novelty relies on a practical approach to the pursuit of the optimal solution of PV systems using formal methods.
 
-Our work makes two major contributions.
-\textbf{Firstly}, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically their use in synthesizing PV sizing is unprecedented.
-%Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms.
-\textbf{Secondly}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
+Our work makes three significant contributions.
+Firstly, the use of automated symbolic verification in PV systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically, their use in synthesizing PV sizing is unprecedented.
+Secondly, we evaluate different state-of-art symbolic software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.
+Lastly, we discuss the main challenges of applying model checking to a real-world PV setting and also reflect on lessons learned from this practical experience.
 

### 2020-01-13 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}}
-\title{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparative\thanks{Supported by Newton Fund (ref.
+\title{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref.
 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}}
@@
 Firstly, the use of automated symbolic verification in PV systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically, their use in synthesizing PV sizing is unprecedented.
-Secondly, we evaluate different state-of-art symbolic software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.
+Secondly, we evaluate different state-of-the-art symbolic software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.
 Lastly, we discuss the main challenges of applying model checking to a real-world PV setting and also reflect on lessons learned from this practical experience.
@@
 Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions) except for the automated synthesis where we also define the bound $k$ to restrict the design-space search.
-Related to the output presented by both techniques, all of them produce a SUCCESS or FAIL result considering a feasible technical solution with the lowest cost.
+In terms of the output presented by both techniques, all of them produce a SUCCESS or FAIL result considering a feasible technical solution with the lowest cost.
 On the one hand, when done by simulation we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
@@
 Therefore, in this study, HOMER Pro will be the simulation tool used to comparison.
-Related to HOMER Pro: (a) is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; (b) it does not have the LCC cost in its reports.
+HOMER Pro: (a) is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; (b) it does not have the LCC cost in its reports.
 But it was possible to obtain LCC from the Net Present Cost (NPC) presented by HOMER Pro; (c) the optimization analysis of HOMER allows to define a load curve and temperature according of data collected from online databases.
-However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools; (d) it does not have a explicit equipment called charge controller.
+However, in order to allow a correct comparison, the curve load and the temperature were defined exactly the same as automated synthesis tools; (d) it does not have a explicit equipment called charge controller.
 It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: 'load following' or 'cycle charging'~\cite{HOMER}.
@@
 \textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits.
-Related to HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), with $1.7$ GHz and $4$ GB of RAM, running Windows 10.
+For HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), with $1.7$ GHz and $4$ GB of RAM, running Windows 10.
 The experiments were performed with a predefined time out of $240$ minutes.
@@
 
-Related to HOMER Pro, it was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}).
+HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}).
 Case study $3$ was not possible to be simulated since HOMER Pro does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.
@@
 
-Related to the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter.
+For the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter.
 The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf.
@@
 Concerning to charge controllers, as it was reported in this  section, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis.
-Therefore, the formal synthesis method presents more reliable results than HOME Pro.
+Therefore, the formal synthesis method presents more reliable results than HOMER Pro.
 
 Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
-Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters to comparative.
+Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters to comparison.
 
@@
 \textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
+Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparison.
 %

### 2020-01-17 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis. In particular, 
-Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis.
-Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions) except for the automated synthesis where we also define the bound $k$ to restrict the design-space search.
-In terms of the output presented by both techniques, all of them produce a SUCCESS or FAIL result considering a feasible technical solution with the lowest cost.
-On the one hand, when done by simulation we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
-Furthermore,
-%as described in this section, 
-the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
-
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the traditional techniques (manual and simulation) and the proposed automated synthesis techniques.
+Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions).
+For the automated synthesis, we also define the bound $k$ to restrict the design-space search \textcolor{red}{What are the implications to set this bound?}.
+%
 \begin{figure}[h]
@@
 \end{figure}
+
+The output presented by both techniques, all of them produce either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
+On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
+Furthermore, the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
 

### 2020-01-17 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \usepackage{algorithm,algorithmic}
+\usepackage{wrapfig}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %-----------------------------------------------------------
-Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}.
+
+%Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}.
 Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do.
@@
 As a result, a given candidate program $p$ is iteratively refined, to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization.
+%CEGIS represents one of the most popular approaches to program synthesis currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization.
 Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture. 
-Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
-%from model checking.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
-	\caption{CEGIS adapted to PV system sizing.}
+%Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
+%
+\begin{wrapfigure}{r}{0.5\textwidth}
+\begin{center}
+%\begin{figure}[h]
+%	\centering
+	\includegraphics[width=0.5\columnwidth]{fig2_rev2.jpg}
+\end{center}	
+	\caption{CEGIS in PV system sizing.}
 	\label{Counter-Example-Guided-Inductive-Synthesis}
-\end{figure}
+%\end{figure}
+\end{wrapfigure}
 
@@
 a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
-
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{iet-cps.2018.5006};
+%
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{iet-cps.2018.5006};
 here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools: 
@@
 
-\textbf{CPAchecker}~\cite{LMU2019} is a model checker awarded with the golden medal at the annual competition in software verification: Automatic program verification requires a choice between precision and efficiency.
+%\textbf{CPAchecker}~\cite{LMU2019} is a model checker awarded with the golden medal at the annual competition in software verification: Automatic program verification requires a choice between precision and efficiency.
 The more precise a method, the fewer false positives it produces, but also the more expensive it is, and thus applicable to fewer programs.
@@
 
-The C Bounded Model Checker (\textbf{CBMC}) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
+%The C Bounded Model Checker (\textbf{CBMC}) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
 CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
@@
 
-The Efficient SMT-based Bounded Model Checker (\textbf{ESBMC}) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+%The Efficient SMT-based Bounded Model Checker (\textbf{ESBMC}) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
 ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.

### 2020-01-17 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
+
+A PV system is illustrated in Fig.\ref{fig:blockdiagram}. 
 The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. 
-%In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$).
 For night hours or rainy days, we hold batteries where power can be stored and used.
 The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required.
-That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
+The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required.
+That converter is called inverter; the AC load dictates the behavior of the AC electrical load from the house that will be fed by the system.
 
@@
 
-The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
+The sizing check stage will ensure that the system meets the standard project steps related to the critical period solar energy method~\cite{Pinho} and adopting the MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
 %
@@
 %
-%%%To select an optimal combination of components from a PV system to meet sizing constraints, 
-%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
 The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
-Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
-%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP).
-Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean?
-Remember that we have software engineering audience}.
-%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC).
-Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}. 
 Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+
 %------------------------------------------------------
@@
 
-Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Line 2).
+Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers' data and prices of PV panels, batteries, charge controllers, and inverters (Line 2).
 After that, we define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5.
@@
 
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (Lines 7 to 10).
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (Lines 7 to 10).
 That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.
@@
 
-If our algorithm does not find a feasible solution among the item of equipment that were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
-It indicates that was not possible to combine the items of each equipment and create a feasible solution.
+If our algorithm does not find a feasible solution among the item of equipment that was provided to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
+It indicates that it was not possible to combine the items of each equipment and create a feasible solution.
 The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements.
-Related to our {\sc Verify} phase the challenge is to find the lowest acquisition cost from a list of equipment and components that is provided from the {\sc Synthesize} phase.
+Related to our {\sc Verify} phase, the challenge is to find the lowest acquisition cost from a list of equipment and components that are provided from the {\sc Synthesize} phase.
 

### 2020-01-17 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+\textcolor{red}{what is the input and output of this algorithm?}
+
  \begin{algorithm}
@@
 
+\textcolor{red}{proof of correctness? complexity analysis?}
+
 %Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
@@
 %---------------------------------------------------------------------------
+
 \textbf{Case studies.} We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} 
 (\textit{Specification}).
-These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{TrindadeCordeiro19,Agrener2013}.
-With exception of case 7 that was idealized as a small town solution to support few lamps and an 12 kBTUs air-conditioner.
+These case studies were defined based on the usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{Agrener2013,TrindadeCordeiro19}.
+Except for case 7, which was idealized as a small-town solution to support few lamps and a 12k BTUs air-conditioner.
 For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
@@
 Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
-Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-It is important to mention that ESBMC with Z3 solver (version 4.7.1) in 'incremental mode' was tested as well in order to consume less memory; however it was reported an 'internal failure' error message caused by a bug in the solver that was not solved until the end of the tests.
+Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
+It is important to mention that ESBMC with Z3 solver (version 4.7.1) in ``incremental mode'' was tested as well to reduce memory consumption; however, it was reported an ``internal failure'' error message.
+%caused by a bug in the solver that was not solved until the end of the tests.
 
-\textbf{Simulation Tool and Assumptions.} Related to off-the-shelf simulation tools only HOMER Pro perform off-grid system with battery backup analysis and includes economical analysis.
+\noindent \textbf{Simulation Tool and Assumptions.} Related to off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis.
 Therefore, in this study, HOMER Pro will be the simulation tool used to comparison.
 HOMER Pro: (a) is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; (b) it does not have the LCC cost in its reports.
-But it was possible to obtain LCC from the Net Present Cost (NPC) presented by HOMER Pro; (c) the optimization analysis of HOMER allows to define a load curve and temperature according of data collected from online databases.
-However, in order to allow a correct comparison, the curve load and the temperature were defined exactly the same as automated synthesis tools; (d) it does not have a explicit equipment called charge controller.
-It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: 'load following' or 'cycle charging'~\cite{HOMER}.
-During the tests it was chosen the 'load following' controller: it produces only enough power to meet the demand~\cite{HOMER}; (e) It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
+But it was possible to obtain LCC from the Net Present Cost (NPC) presented by HOMER Pro; (c) the optimization analysis of HOMER allows us to define a load curve and temperature according to data collected from online databases.
+However, in order to allow a correct comparison, the curve load and the temperature were defined the same as automated synthesis tools; (d) it does not have a explicit equipment called a charge controller.
+It uses a controller resource that can perform in two different ways, according to the optimization choice or the user choice: ``load-following'' or ``cycle charging''~\cite{HOMER}.
+During the tests, it was chosen the ``load-following'' controller: it produces only enough power to meet the demand~\cite{HOMER}; (e) It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
 By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
 For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable; (f) it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; (g) the premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
+\textcolor{red}{This sentence is hard to understand...
+could you please break into smaller sentences?
+While in an ordinary house electrical load, 95\% is considered acceptable; (f) it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; (g) the premise adopted when using HOMER Pro it was that the user does not know the optimal solution and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER will search for the optimized power of each component}.
+With that in mind, it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.

### 2020-01-17 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits.
+\noindent \textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits.
 For HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), with $1.7$ GHz and $4$ GB of RAM, running Windows 10.
@@
 
-\textbf{Objectives.} Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, \textit{RQ2} (performance) How do the software verifiers compare to each other?, and \textit{RQ3} how does our formal synthesis tool compare to a specialized simulation tool?
+\noindent \textbf{Objectives.} Our evaluation aims to answer three experimental questions: 
+\textit{EQ1} \textbf{(soundness)} Does our automated synthesis approach provide correct results?, 
+\textit{EQ2} \textbf{(performance)} How do the software verifiers compare to each other?, and 
+\textit{EQ3} \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
 
-\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
-%Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing in the left size as the integer $8$ to the solar panel (which is the model RSM36-6-150P from manufacturer Risen), battery $0$ that means the model 12MF80 of 80 Ah from Moura, charge controller $1$ that means the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ means the model IP350-11 from Epever (750 W).
-The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, presented at the counter-example as well, shows how many and how the panels and batteries are connected.
+\noindent \textbf{Results.} CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
 Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes.
-%However, if it is removed this time out limitation from CPAchecker, the verifier is able to solve the optimization in $44.97$ hours.
 The violation (SAT result) indicated in Table~\ref{tab1} 
@@
 Table~\ref{tab1}).
-Particularly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
+Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
 Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling.
 The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value.
-However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by the automated synthesis tool were underestimated to that specific load.
+However, there exists a vast divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because of the operation and maintenance costs assumed by the automated synthesis tool were underestimated to that specific load.
 
 In general, the size of the PV panels and battery bank were bigger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation.
-Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
-These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
+\textcolor{red}{This sentence is hard to understand...
+try to break into smaller sentences...Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.} These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
 
@@
 
-\textbf{Conclusion.} Summarizing, our synthesis tool is capable to present a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
-In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current and voltage.
+\noindent \textbf{Threats to validity.} We have reported a favorable assessment of the proposed method.
+Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the complexity of the optimization, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained, and it allows a simulation-verification comparison.
+
+\noindent \textbf{Conclusion.} Summarizing, our synthesis tool is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
+In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage.
 In this respect, even the manufacturer's brand can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).
-
 %
@@
 
-\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparison.
 %

### 2020-01-18 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions).
-For the automated synthesis, we also define the bound $k$ to restrict the design-space search \textcolor{red}{What are the implications to set this bound?}.
+For the automated synthesis, we also define the bound $k$ to restrict the design-space search.
+\textcolor{red}{Limiting the length of $k$ we are reducing the time to solve the problem.
+In one hand, if $k$ is too small, maybe the approach cannot return a solution; in the other hand, it is possible that a solution cannot be found even with an infinite $k$.
+Therefore, the proper choice of $k$ is important to this method}.
 %
@@
 
-\textcolor{red}{what is the input and output of this algorithm?}
-
  \begin{algorithm}
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
+   \REQUIRE \textcolor{red}{weather data (temperature, solar irradiance), list of equipment (data sheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis)}
+ \ENSURE \textcolor{red}{FAIL with counter-example showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available}
   \STATE Initialize variables \\
@@
 
-\textcolor{red}{proof of correctness? complexity analysis?}
-
-%Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+\textcolor{red}{(proof of correctness? complexity analysis?)
+Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.}
 %---------------------------------------------------------------------------
@@
 Therefore, in this study, HOMER Pro will be the simulation tool used to comparison.
-HOMER Pro: (a) is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; (b) it does not have the LCC cost in its reports.
-But it was possible to obtain LCC from the Net Present Cost (NPC) presented by HOMER Pro; (c) the optimization analysis of HOMER allows us to define a load curve and temperature according to data collected from online databases.
-However, in order to allow a correct comparison, the curve load and the temperature were defined the same as automated synthesis tools; (d) it does not have a explicit equipment called a charge controller.
-It uses a controller resource that can perform in two different ways, according to the optimization choice or the user choice: ``load-following'' or ``cycle charging''~\cite{HOMER}.
-During the tests, it was chosen the ``load-following'' controller: it produces only enough power to meet the demand~\cite{HOMER}; (e) It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
-By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
-For critical loads, 99\% is considered acceptable.
-\textcolor{red}{This sentence is hard to understand...
-could you please break into smaller sentences?
-While in an ordinary house electrical load, 95\% is considered acceptable; (f) it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; (g) the premise adopted when using HOMER Pro it was that the user does not know the optimal solution and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER will search for the optimized power of each component}.
-With that in mind, it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling).
+HOMER Pro:
+
+\textcolor{red}{reescrevi os itens todos, para tornar a leitura mais tranquila}
+\begin{itemize}
+\item is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
+\item it does not have LCC cost in its reports, only Net Present Cost (NPC). But it was possible to obtain LCC from NPC; 
+\item the optimization analysis of HOMER allows us to define a load curve and temperature according to data collected from online databases.
+However, in order to allow a correct comparison, the curve load and the temperature were defined the same as automated synthesis tools;
+\item it does not have a explicit equipment called a charge controller.
+During the tests, it was chosen the ``load-following'' option which produces only enough power to meet the demand~\cite{HOMER} and (usually) presents a not overestimated solution;
+\item it was assumed the value of 95\% for the availability of the PV system.
+By definition, 'availability' is the percentage of time at which a power system is capable of feed the load requirements~\cite{Khatib2014}.
+For ordinary house electrical load, 95\% is considered acceptable;
+\item it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; 
+\item it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
+\end{itemize}
 
@@
 
-In general, the size of the PV panels and battery bank were bigger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation.
-\textcolor{red}{This sentence is hard to understand...
-try to break into smaller sentences...Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.} These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
+\textcolor{red}{In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach.
+Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.} These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.}
 

### 2020-01-18 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 \textcolor{red}{In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach.
-Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.} These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.}
+Just to compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.}
 

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Alessandro's changes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 For the automated synthesis, we also define the bound $k$ to restrict the design-space search.
-\textcolor{red}{Limiting the length of $k$ we are reducing the time to solve the problem.
-In one hand, if $k$ is too small, maybe the approach cannot return a solution; in the other hand, it is possible that a solution cannot be found even with an infinite $k$.
-Therefore, the proper choice of $k$ is important to this method}.
+Limiting the length of $k$, we are reducing the time to solve the problem.
+On the one hand, if $k$ is too small, the approach might not return a solution; on the other hand, a solution cannot be found even with a more significant number of $k$ due to time and memory constraints.
+Therefore, the proper choice of $k$ is essential to this method..
 %
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
-   \REQUIRE \textcolor{red}{weather data (temperature, solar irradiance), list of equipment (data sheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis)}
- \ENSURE \textcolor{red}{FAIL with counter-example showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available}
+   \REQUIRE weather data (temperature, solar irradiance), list of equipment (datasheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis).
+ \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available.
   \STATE Initialize variables \\
@@
 Related to our {\sc Verify} phase, the challenge is to find the lowest acquisition cost from a list of equipment and components that are provided from the {\sc Synthesize} phase.
+Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
 
-\textcolor{red}{(proof of correctness? complexity analysis?)
-Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.}
 %---------------------------------------------------------------------------
@@
 
-\textcolor{red}{reescrevi os itens todos, para tornar a leitura mais tranquila}
+%\textcolor{red}{reescrevi os itens todos, para tornar a leitura mais tranquila}
 \begin{itemize}
@@
 
-\textcolor{red}{In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach.
-Just to compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
-These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.}
+In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach.
+To compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
 
@@
 \begin{table}[!t]
-\caption{Case studies and results: optimization of PV systems.}\label{tab1}
+\caption{Case studies and results: optimization of PV systems \textcolor{red}{could you please remove the columns for CBMC and ESBMC and just mention in the paper that both verifiers produce MO and TO, respectively?}.}\label{tab1}
 \begin{tabular}{|c|c|c|c|c|}

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-\author{Alessandro Trindade\inst{1}\orcidID{0000-0001-8262-2919} \and
-Lucas Cordeiro\inst{2}\orcidID{0000-0002-6235-4272}}
+\author{Alessandro Trindade\inst{1} \and Lucas Cordeiro\inst{2}} %\orcidID{0000-0001-8262-2919}  \orcidID{0000-0002-6235-4272}
 %
@@
 \begin{abstract}
-%Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space.
-We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis.
-In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost.
-The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained.
-Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing.
-Our synthesis method is novel and unprecedented to streamline the design of PV systems.
-Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of seven different intricate case studies.
-
-%In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends in energy access still fall short of global goals.
-Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible.
-Tools to evaluate or to size electrification projects are available, but they are based on simulations that do not cover all aspects of the design space.
-The use of formal methods in electrical systems is a new subject, with published research spanning only the last four years.
-Moreover, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems has never been done before.
+The use of formal methods in electrical systems is a new subject, with significant research spanning only the last four years.
+However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems has never been done before.
 Here our primary goal is to develop and evaluate a sound, automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis.
@@
 Experimental results using seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time.
-We also present a comparison with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach.
-\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
+%We also present a comparison with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach.
+%\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
 \end{abstract}

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015}.
-During operation, such components must frequently adapt to the executing environment changes faced at run-time (dynamics of the physical processes).
-They must be able to continue behaving in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}.
-Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis.
-These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS.
-In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
-Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.
-
-%Energy production, distribution, and optimization are all CPS problems~\cite{UC}. 
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, in 2017, the number of people without electricity access fell below $1$ billion threshold for the first time~\cite{IEAweo2018}.
 In order to provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}.
 
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}; and even general-purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
+In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
  However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
 
-Optimization of PV systems is not a recent topic; since the 90's, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}.
-%Concerning the use of formal methods based on \textit{symbolic model checking} and its application to electric systems. 
+Optimization of PV systems is not a recent topic; since the '90s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}.
 In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
@@
 In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
-However, formal methods and its application to synthesize PV systems are still unexplored in literature.
+However, \textit{formal methods and its application to synthesize PV systems are still unexplored in literature}.
 
-Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Here, we have developed a (non-trivial) variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
 Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
-In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
+In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
 The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted.
 If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost.
-Note that in this study, our focus is not on new criteria or even optimization objectives.
+Here our focus is not on new criteria or even optimization objectives.
 Instead, our novelty relies on a practical approach to the pursuit of the optimal solution of PV systems using formal methods.
 
-Our work makes three significant contributions.
-Firstly, the use of automated symbolic verification in PV systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically, their use in synthesizing PV sizing is unprecedented.
-Secondly, we evaluate different state-of-the-art symbolic software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.
-Lastly, we discuss the main challenges of applying model checking to a real-world PV setting and also reflect on lessons learned from this practical experience.
+Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing.
+First, the use of automated symbolic verification in PV systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically, their use in synthesizing PV sizing is novel.
+Second, we evaluate our approach using different state-of-the-art symbolic verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems and compare that to HOMER.
+Lastly, we discuss the main challenges of applying formal methods to PV systems and also reflect on lessons learned from this practical experience.
 

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 2.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %-----------------------------------------------------------
-\section{BACKGROUND}
+\section{Preliminaries}
 \label{sec:AutomatedVerification}
 %-----------------------------------------------------------
-%In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis. In particular, 
+
 Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the traditional techniques (manual and simulation) and the proposed automated synthesis techniques.
-Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions).
+Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions.
 For the automated synthesis, we also define the bound $k$ to restrict the design-space search.
-Limiting the length of $k$, we are reducing the time to solve the problem.
-On the one hand, if $k$ is too small, the approach might not return a solution; on the other hand, a solution cannot be found even with a more significant number of $k$ due to time and memory constraints.
-Therefore, the proper choice of $k$ is essential to this method..
+On the one hand, if $k$ is too small, then the approach might not return a solution due to the search-space depth.
+Here we start with a low bound $k$ and incrementally increase it to avoid time and memory constraints on our verification back-end.
+Therefore, the proper choice of $k$ is essential to this method.
 %
@@
 
-The output presented by both techniques, all of them produce either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
+Both techniques (traditional and automated synthesis)  produce as output either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
 On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
-Furthermore, the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
+Furthermore, the design-space coverage during the optimal sizing search is sound and complete when using synthesis.
 
@@
 
-%Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}.
-Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do.
-The specification needs to describe the program's desired behavior to ensure that the program does what it intends.
-
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
 In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
-As a result, a given candidate program $p$ is iteratively refined, to match $\sigma$ more closely.
-%CEGIS represents one of the most popular approaches to program synthesis currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization.
+As a result, a given candidate program $p$ is iteratively refined to match $\sigma$ more closely.
 Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture.
-%Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
 %
@@
 
-The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .
+The correctness specification $\sigma$ provided to our synthesizer is of the form $\exists \vec{F}.
 \forall \vec{x}.
@@
 The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-Examples of specifications used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specifications and prices from different manufacturers and models.
+Our specification includes house demand, energy, and battery autonomy; we also provide equipment specifications and prices from different manufacturers and models.
 
@@
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
 If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
@@
 One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists, and our synthesis engine can then conclude that no feasible equipment combination was found.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times.
+However, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists, and our synthesis engine can then conclude that no possible equipment combination was found.
 
-In our variant CEGIS method, there exist four distinct differences related to the traditional CEGIS: 
+In our CEGIS variant, there exist four differences related to the traditional one: 
 (1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
 (2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
-(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
-(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
-a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
-%
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{iet-cps.2018.5006};
-here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools: 
-CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.
-
-%\textbf{CPAchecker}~\cite{LMU2019} is a model checker awarded with the golden medal at the annual competition in software verification: Automatic program verification requires a choice between precision and efficiency.
-The more precise a method, the fewer false positives it produces, but also the more expensive it is, and thus applicable to fewer programs.
-Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
-To experiment with the trade-off and to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
-The CPA formalism provides an interface for the definition of program analysis.
-Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analysis expressed in the CPA framework.
-In terms of the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}.
-Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.
-
-%The C Bounded Model Checker (\textbf{CBMC}) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}.
-CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula.
-If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}.
-CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports Boolean Satisfiability (SAT) and SMT solvers to discharge verification conditions.
-
-%The Efficient SMT-based Bounded Model Checker (\textbf{ESBMC}) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; as a result,
+(4) there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
+a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.%
+%Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; 
+%here we have used software verifiers based on SMT solvers: CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.
 

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 2.2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The sizing check stage will ensure that the system meets the standard project steps related to the critical period solar energy method~\cite{Pinho} and adopting the MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
-%
+The sizing check will ensure that the system meets the standard project steps related to the critical period solar energy method~\cite{Pinho} and the MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
 Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\ref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
@@
 the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-
-The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
+The minimum number of solar panels ($N_{TPmin}$) is computed as
 
@@
 
-\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
-%
+\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ as well as $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
 Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
@@
 
-\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
+\noindent where the variable $autonomy$ is a design definition; 
 $ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-
 Secondly, the total (minimum) number of batteries is computed as 
@@
 
-The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as
+The short circuit reference from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent:
 
@@
 
-The controller must meet the maximum current from the PV array given by Eqs. \ref{eq:icmin} and \ref{eq:icicmin} as
-
+The controller must meet the maximum current from the PV array given as
+%
 \begin{equation}
@@
 
-% -------------------------------------------------------
-\subsection{Optimal Sizing of PV Systems}
-% -------------------------------------------------------
-%
+%------------------------------------------------------
+\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
+%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
+%------------------------------------------------------
+
 The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
@@
 
-%------------------------------------------------------
-\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
-%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
-%------------------------------------------------------
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
+Notably, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
 
@@
 
-\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ as well as $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
+\noindent where $V_{mppt, max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operating voltage of the charge controller.
+$V_{maxPower, TempMax}$, as well as $V_{maxPower, TempMin}$, are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively.
+$P_{total}$ is the total power demanded from the PV system and $P_{max, ref}$ is the power supplied from one PV panel in $Watts$.
 Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
@@
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. 
-
+%
  \begin{algorithm}
@@
  \end{algorithm}
-
+%
 Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers' data and prices of PV panels, batteries, charge controllers, and inverters (Line 2).
-After that, we define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5.
+We define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5.
 
@@
 In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, that never will be reached because the optimal solution will be found first.
+The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, which will never be reached because the optimal solution will be found first.
 
@@
 That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.
-
+%
 Next, we use Eq.~\ref{eq:Ecorrected}, Eq.~\ref{eq:Ep}, Eq.~\ref{eq:NTPmin}, Eq.~\ref{eq:NPSmin}, Eq.~\ref{eq:NPPmin}, Eq.~\ref{eq:Cbank}, Eq.~\ref{eq:Nbtotal}, Eq.~\ref{eq:iscamb}, and Eq.~\ref{eq:icmin} to calculate the sizing variables (Lines 11 to 17).
-The directive \textit{assume} (Lines 15, 18 and 19) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines 15, 18 and 19.
-Therefore, our synthesis algorithm reaches Line 20 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (Line 21).
+The directive \textit{assume} (Lines 15, 18 and 19) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines 15, 18, and 19.
+Our algorithm reaches Line 20 with one feasible solution; the cost of that solution is calculated in $F_{obj}$ (Line 21).
 
@@
 Related to our {\sc Verify} phase, the challenge is to find the lowest acquisition cost from a list of equipment and components that are provided from the {\sc Synthesize} phase.
-Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+The process described here in completely automated; a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
 

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.97}
+\renewcommand{\baselinestretch}{0.98}
 
@@
 \section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
-%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
 %------------------------------------------------------
@@
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
-%  \STATE Declare list of controllers data and cost \\
-%  \STATE Declare list of batteries data and cost \\
-%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$ \\
@@
  	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
 	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
 	\STATE non-deterministic variables hold feasible equipment and cost \\
@@
 Related to our {\sc Verify} phase, the challenge is to find the lowest acquisition cost from a list of equipment and components that are provided from the {\sc Synthesize} phase.
-The process described here in completely automated; a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+The process described here is entirely automated; a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
 
@@
 For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
-
+%
 Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
-Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.
-It is important to mention that ESBMC with Z3 solver (version 4.7.1) in ``incremental mode'' was tested as well to reduce memory consumption; however, it was reported an ``internal failure'' error message.
-%caused by a bug in the solver that was not solved until the end of the tests.
+Furthermore, three start-of-art verifiers, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used to compare our approach effectiveness and efficiency.
 
 \noindent \textbf{Simulation Tool and Assumptions.} Related to off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis.
-Therefore, in this study, HOMER Pro will be the simulation tool used to comparison.
+Here HOMER Pro will be the simulation tool used for comparison.
 HOMER Pro:
 
-%\textcolor{red}{reescrevi os itens todos, para tornar a leitura mais tranquila}
 \begin{itemize}
-\item is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
-\item it does not have LCC cost in its reports, only Net Present Cost (NPC). But it was possible to obtain LCC from NPC; 
-\item the optimization analysis of HOMER allows us to define a load curve and temperature according to data collected from online databases.
-However, in order to allow a correct comparison, the curve load and the temperature were defined the same as automated synthesis tools;
-\item it does not have a explicit equipment called a charge controller.
-During the tests, it was chosen the ``load-following'' option which produces only enough power to meet the demand~\cite{HOMER} and (usually) presents a not overestimated solution;
-\item it was assumed the value of 95\% for the availability of the PV system.
-By definition, 'availability' is the percentage of time at which a power system is capable of feed the load requirements~\cite{Khatib2014}.
+\item It is available only for MS Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
+\item It does not have LCC cost in its reports, only Net Present Cost (NPC). However, it is possible to obtain LCC from NPC; 
+\item The optimization analysis of HOMER allows us to define a load curve and temperature according to data collected from online databases.
+However, to allow a correct comparison, the curve load and the temperature were defined the same as automated synthesis tools;
+\item It does not have a charge controller.
+During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution;
+\item It was assumed the value of 95\% for the availability of the PV system.
+By definition, ``availability'' is the percentage of time at which a power system is capable of feeding the load requirements~\cite{Khatib2014}.
 For ordinary house electrical load, 95\% is considered acceptable;
-\item it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; 
-\item it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling).
+\item It was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for the automated synthesis tool; 
+\item It was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
@@
 \textit{EQ1} \textbf{(soundness)} Does our automated synthesis approach provide correct results?, 
-\textit{EQ2} \textbf{(performance)} How do the software verifiers compare to each other?, and 
+\textit{EQ2} \textbf{(performance)} How do the software verifiers compare to each other for synthesizing PV systems?, and 
 \textit{EQ3} \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
@@
 The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf.
-Therefore is a PRO to the formal synthesis method.
+Therefore, this feature is a PRO to the formal synthesis method.
 
@@
 In this respect, even the manufacturer's brand can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).
-%
-%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
 
 \begin{table}[!t]
-\caption{Case studies and results: optimization of PV systems \textcolor{red}{could you please remove the columns for CBMC and ESBMC and just mention in the paper that both verifiers produce MO and TO, respectively?}.}\label{tab1}
+\caption{Case studies and results: optimization of PV systems \textcolor{red}{could you please put this table online?}.}\label{tab1}
 \begin{tabular}{|c|c|c|c|c|}
@@
 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%divisão para o material antigo sobre verificação
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{State-of-art in Automated Verification of Electrical Systems}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%The conversion of traditional power grid into a smart grid, a fundamental example of a Cyber-Physical System (CPS), raises a number of issues that requires novel methods and applications.
-In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}.
-The focus of this study was on how CPs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system, as 	probability	of	node	failure	in	the	long run, impact	of	repair	service	on	the	failure	risk, and expected energy consumption.
-%, with no interest in power generation or even solar PV systems.
-%
-%In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}.
-The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework.
-The initial focus was on relay operations and test-case generation to ensure early detection of design errors.
-%The study was limited to power system protection and did not deal with electricity generation or even solar PV systems.
-%
-%Other related studies from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking for CPSs in terms of non-functional properties such as time and energy~\cite{Cheng2015}.
-In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios.
-The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems.
-%The research did no deal with solar PV systems.
-% 
-%In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}.
-The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness.
-The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''.
-The author used approximate model checking of stochastic and hybrid models.
-%
-%In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios.
-The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior.
-%The work did not include the other components of a stand-alone solar PV system.
-%
-%Another work from 2018 was the approach to modeling smart grid components using a formal specification.
-The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}.
-The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods.
-The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other.
-This approach is base on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
-%
-%
 % ---- Bibliography ----

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\noindent \textbf{Conclusion.} Summarizing, our synthesis tool is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
+%------------------------------------
+\section{Conclusion} 
+%------------------------------------
+
+\textcolor{red}{What is the novelty of our work?
+what are the impacts/relevance of our method to the society and formal methods community?
+How formal methods can improve the people's life?
+we should emphasize the relevance of the problem we solve and give numbers to show the efficiency of our approach if compared to HOME Pro.}
+
+Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro.
 In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage.
-In this respect, even the manufacturer's brand can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).
+In this respect, even the manufacturer's brand can be presented (\textcolor{red}{shall we add this table online?} in Table~\ref{tab1} it was removed to avoid some advertising).
 

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
added additional comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+\textcolor{red}{did we address this comment of the ASE reviewer?
+``In some of the equations, the variables are not typed.
+In CPS some of the variables may belong to continuous domains (real numbers).
+You need to explain the types for variables and justify that the underlying verification tool supports those types.'' I think we should make it explicit in this section.}
+
 %------------------------------------------------------

### 2020-01-20 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
added additional comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.98}
+\renewcommand{\baselinestretch}{0.97}
 
@@
 a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.%
-%Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; 
-%here we have used software verifiers based on SMT solvers: CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.
 
@@
 
-\textbf{Case studies.} We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} 
-(\textit{Specification}).
+%---------------------------------------------------------------------------
+\subsection{Description of the Case studies}
+%---------------------------------------------------------------------------
+
+We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} 
+(\textit{Specification}) \textcolor{red}{shall we make this table available online?}.
 These case studies were defined based on the usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{Agrener2013,TrindadeCordeiro19}.
-Except for case 7, which was idealized as a small-town solution to support few lamps and a 12k BTUs air-conditioner.
+Except for case 7 that was idealized as a small-town solution to support only a few lamps and a 12k BTUs air-conditioner.
 For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
-%
 Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
@@
 
-\noindent \textbf{Simulation Tool and Assumptions.} Related to off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis.
-Here HOMER Pro will be the simulation tool used for comparison.
-HOMER Pro:
+%---------------------------------------------------------------------------
+\subsection{Simulation Tool and Assumptions}
+%---------------------------------------------------------------------------
+
+Concerning the off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis.
+Here we used HOMER Pro as a state-of-the-art simulation tool for comparison purposes.
+In particular, HOMER Pro has the following characteristics:
 
@@
 \item It is available only for MS Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
-\item It does not have LCC cost in its reports, only Net Present Cost (NPC). However, it is possible to obtain LCC from NPC; 
-\item The optimization analysis of HOMER allows us to define a load curve and temperature according to data collected from online databases.
-However, to allow a correct comparison, the curve load and the temperature were defined the same as automated synthesis tools;
+\item It does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
+\item The optimization analysis of HOMER defines a load curve and temperature according to data collected from online databases.
+However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach;
 \item It does not have a charge controller.
 During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution;
-\item It was assumed the value of 95\% for the availability of the PV system.
-By definition, ``availability'' is the percentage of time at which a power system is capable of feeding the load requirements~\cite{Khatib2014}.
+\item It was assumed the value of 95\% availability of the PV system.
+By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}.
 For ordinary house electrical load, 95\% is considered acceptable;
-\item It was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for the automated synthesis tool; 
+\item It was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
 \item It was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling).
-HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
+During run-time, HOMER decides the size in kW of each module based on feasibility and lower cost.
 \end{itemize}
 
-\noindent \textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits.
-For HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), with $1.7$ GHz and $4$ GB of RAM, running Windows 10.
-The experiments were performed with a predefined time out of $240$ minutes.
+%---------------------------------------------------------------------------
+\subsection{Objectives and Setup}
+%---------------------------------------------------------------------------
 
-\noindent \textbf{Objectives.} Our evaluation aims to answer three experimental questions: 
-\textit{EQ1} \textbf{(soundness)} Does our automated synthesis approach provide correct results?, 
-\textit{EQ2} \textbf{(performance)} How do the software verifiers compare to each other for synthesizing PV systems?, and 
-\textit{EQ3} \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
+Our evaluation aims to answer three experimental goals: 
+\begin{enumerate}
+\item[EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?, 
+\item[EG2] \textbf{(performance)} How do the software verifiers compare to each other for synthesizing PV systems?, and 
+\item[EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
+\end{enumerate}
 
-\noindent \textbf{Results.} CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
+All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits.
+For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB of RAM running Windows 10.
+\textcolor{red}{we have to explain here why we have used two different hardware platform.
+Does it influence on the results?}.
+We We perform the experiments with a predefined time out of $240$ minutes.
+
+%---------------------------------------------------------------------------
+\subsection{Results}
+%---------------------------------------------------------------------------
+
+CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
 Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes.
@@
 CBMC and ESBMC are unable to produce any conclusive result.
-Situations of \textit{time out} or \textit{out of memory} occurred; this partially answers the \textit{EQ2} and \textit{EQ3}.
+Situations of \textit{time out} or \textit{out of memory} occurred; this partially answers the \textit{EG2} and \textit{EG3}.
 
-HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}).
+HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much faster than the proposed automated synthesis tool (cf.~\textit{EG2}).
 Case study $3$ was not possible to be simulated since HOMER Pro does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.
@@
 To compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
-These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
+These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EG1}.
 
@@
 
-\noindent \textbf{Threats to validity.} We have reported a favorable assessment of the proposed method.
+%---------------------------------------------------------------------------
+\subsection{Threats to validity} 
+%---------------------------------------------------------------------------
+
+We have reported a favorable assessment of the proposed method.
 Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the complexity of the optimization, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained, and it allows a simulation-verification comparison.

### 2020-01-20 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
+CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
 Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes.
-The violation (SAT result) indicated in Table~\ref{tab1} 
-is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
+The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}.
 CBMC and ESBMC are unable to produce any conclusive result.
-Situations of \textit{time out} or \textit{out of memory} occurred; this partially answers the \textit{EG2} and \textit{EG3}.
+Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG2} and \textit{EG3} \textcolor{red}{why?
+explain it here...}.
 
-HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much faster than the proposed automated synthesis tool (cf.~\textit{EG2}).
-Case study $3$ was not possible to be simulated since HOMER Pro does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.
+HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed automated synthesis tool (cf.~\textit{EG3}) \textcolor{red}{why do we need to publish our results then?}.
+HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year \textcolor{red}{Does this feature add more complexity to our synthesis model?
+If so, we have to point it out here}.
 
-Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, it was observed that most results are quite similar, in terms of technical solution and cost (cf.
-Table~\ref{tab1}).
+Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that most results are quite similar in terms of technical solution and cost (cf.
+Table~\ref{tab1}) \textcolor{red}{If the results are quite similar and HOME Pro is faster, what is the purpose of our method here?}.
 Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
-Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling.
-The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value.
-However, there exists a vast divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because of the operation and maintenance costs assumed by the automated synthesis tool were underestimated to that specific load.
+Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model, thus making it more precise.
+\textcolor{red}{this sentence is unclear...
+Our premise to adopt a fixed annual cost for operation and maintenance is that it can produce some impact at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value}.
+We have observed that there exists a vast divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool, probably because of the operation and maintenance costs assumed by our approach were underestimated to that specific load \textcolor{red}{is it good or bad?
+the way you have written looks like HOME Pro is the best option}.
 
-In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach.
+In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our synthesis approach.
 To compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
@@
 Therefore, this feature is a PRO to the formal synthesis method.
-
-Concerning to charge controllers, as it was reported in this section, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis.
+Concerning the charge controllers, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis.
 Therefore, the formal synthesis method presents more reliable results than HOMER Pro.
-
 Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
@@
 We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the complexity of the optimization, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained, and it allows a simulation-verification comparison.
+Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the complexity of the optimization, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.
 

### 2020-01-20 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 
-\begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
+\begin{wrapfigure}{r}{0.5\textwidth}
+%\begin{figure}[h]
+\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
 \centering
@@
 \label{fig:blockdiagram} 
-\end{figure}
+\end{wrapfigure}
 
@@
 \noindent where the variable $autonomy$ is a design definition; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-Secondly, the total (minimum) number of batteries is computed as 
+$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery depth of discharge (considered of maximum of 25\% here).
+Secondly, the total (minimum) number of batteries $N_{B}total$ is computed as a product of the minimum number of batteries in series $N_{BS}min$ with the minimum number of batteries in parallel $ N_{BP}min $ and, therefore, as function of battery bank capacity $ C_{bank} $ and the capacity of the chosen battery $ Battery \, Capacity $ as
+
 \begin{equation}
@@
 
-Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\ref{eq:vcvsystem} to the charge controller voltage:
+Regarding the charge controller, it must initially meet the voltage requirement of the PV system $V_{system}$, as described by Eq.~\ref{eq:vcvsystem} to the charge controller voltage $V_{c}$:
 
@@
 
-The short circuit reference from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent:
+The short circuit reference current $ I_{sc,ref} $ from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature $ T $ is higher than the nominal or laboratory temperature, and PV system is temperature dependent.
+This corrected current is called $I_{sc,amb}$, it uses $G_{ref} = 1000$ and the ratio of current change over temperature $\mu_{I}$:
 
@@
 \label{eq:iscamb}
-I_{sc,amb} = \frac{G}{G_{ref}} \left[I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
+I_{sc,amb} = \frac{Solar \, Irradiance}{G_{ref}} \left[I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
 \end{equation}
 
-The controller must meet the maximum current from the PV array given as
+The controller must meet the maximum current from the PV array. Therefore the controller current $I_{c}$ must be less than the calculated $I_{c,min}$ and given as
 %
@@
 The inverter sizing check is performed by means of three equations.
-Eq.~\ref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Eq.~\ref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
-Finally, Eq.~\ref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
+Eq.~\ref{eq:vindc} ensures that the input voltage of the controller $V_{in}DC$ meets the system voltage.
+Eq.~\ref{eq:voutac} ensures that the output voltage of the controller $V_{out}AC$ meets the AC voltage of the load $V_{AC}$.
+Finally, Eq.~\ref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $P_{AC,ref}$ is the nominal power and $MAX_{AC,ref}$ is the peak power that the inverter can support.
 
@@
 
-\textcolor{red}{did we address this comment of the ASE reviewer?
-``In some of the equations, the variables are not typed.
-In CPS some of the variables may belong to continuous domains (real numbers).
-You need to explain the types for variables and justify that the underlying verification tool supports those types.'' I think we should make it explicit in this section.}
+\textcolor{red}{In CPS some of the variables may belong to continuous domains (real numbers).
+All the equations illustrated here produces real numbers, although when choosing batteries and panels quantities those real numbers must be translated into integer number (closest ones, considering the minimum or maximum according with each equation).
+The underlying verification tool and the simulation tool must support those type of variables in order to produce a correct result.}
 
@@
 %---------------------------------------------------------------------------
-
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
+The proposed synthesis approach was evaluated in  seven stand-alone PV system case studies: 
+\textbf{case study 1:} power peak: 342 W, power surge: 342 W, energy consumption: 3,900 Wh/day, battery autonomy: 48 h; \textbf{case study 2:} Power peak: 814 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 48 h; \textbf{case study 3:} power peak: 815 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 12 h; \textbf{case study 4:} power peak: 253 W, power surge: 722 W, energy consumption: 3,600 Wh/day, battery autonomy: 48 h; \textbf{case study 5:} power peak: 263 W, power surge: 732 W, energy consumption: 2,500 Wh/day, battery autonomy: 48 h; \textbf{case study 6:} power peak: 322 W, power surge: 896 W, energy consumption: 4,300 Wh/day, battery autonomy: 48 h; \textbf{case study 7:} power peak: 1,586 W, power surge: 2,900 W, energy consumtion: 14,000 Wh/day, battery autonomy: 48 h.
 
-We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} 
-(\textit{Specification}) \textcolor{red}{shall we make this table available online?}.
-These case studies were defined based on the usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{Agrener2013,TrindadeCordeiro19}.
-Except for case 7 that was idealized as a small-town solution to support only a few lamps and a 12k BTUs air-conditioner.
+These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas,  Brazil~\cite{TrindadeCordeiro19,Agrener2013}, with the exception of case 7, that was idealized as a small town solution to support a few lamps and a 12 kBTUs air-conditioner.
 For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
 Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
-Furthermore, three start-of-art verifiers, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used to compare our approach effectiveness and efficiency.
+
+Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
 
@@
 Concerning the off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis.
-Here we used HOMER Pro as a state-of-the-art simulation tool for comparison purposes.
+Here we used HOMER Pro version $3.13.1$ as a state-of-the-art simulation tool for comparison purposes.
 In particular, HOMER Pro has the following characteristics:
@@
 For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB of RAM running Windows 10.
-\textcolor{red}{we have to explain here why we have used two different hardware platform.
-Does it influence on the results?}.
-We We perform the experiments with a predefined time out of $240$ minutes.
+\textcolor{red}{The hardware platform was not the same because of the availability of the machines, and this has impact in respect to the performance that is less favorable to HOMER Pro}.
+We perform the experiments with a predefined time out of $240$ minutes.
 
@@
 
-CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
+A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}.
+Summarizing,  CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
 Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes.
@@
 In this respect, even the manufacturer's brand can be presented (\textcolor{red}{shall we add this table online?} in Table~\ref{tab1} it was removed to avoid some advertising).
-
-\begin{table}[!t]
-\caption{Case studies and results: optimization of PV systems \textcolor{red}{could you please put this table online?}.}\label{tab1}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\hline
-Tools & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell {ESBMC 6.0.0\\(Boolector 3.0.1)} & HOMER Pro 3.13.1\\
-\hline
-\hline
-Specification & Result & Result & Result & Result \\
-\hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & OM & TO & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
-\hline
-\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & OM & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
-\hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & OM & TO & Not possible \\
-\hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} &  \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & OM & TO & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
-\hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & OM & TO & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
-\hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & OM & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
-\hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & TO & OM & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
-\hline
-\hline
-\end{tabular}
-\\Caption: OM= out of memory; TO= timeout; E= energy, NTP= total number of panels, NBT= total number of batteries, LCC= life cicle cost.
-\end{table}
-
 %

### 2020-01-20 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 Here our focus is not on new criteria or even optimization objectives.
-Instead, our novelty relies on a practical approach to the pursuit of the optimal solution of PV systems using formal methods.
 
@@
 %---------------------------------------------------------------------------
+A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}.
 
-A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}.
-Summarizing,  CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
+Related to the verifiers comparison, CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
 Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes.
-The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}.
+The violation (SAT result) indicated in on-line Table is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}.
 CBMC and ESBMC are unable to produce any conclusive result.
-Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG2} and \textit{EG3} \textcolor{red}{why?
-explain it here...}.
-
-HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed automated synthesis tool (cf.~\textit{EG3}) \textcolor{red}{why do we need to publish our results then?}.
-HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year \textcolor{red}{Does this feature add more complexity to our synthesis model?
-If so, we have to point it out here}.
-
-Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that most results are quite similar in terms of technical solution and cost (cf.
-Table~\ref{tab1}) \textcolor{red}{If the results are quite similar and HOME Pro is faster, what is the purpose of our method here?}.
-Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
-Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model, thus making it more precise.
-\textcolor{red}{this sentence is unclear...
-Our premise to adopt a fixed annual cost for operation and maintenance is that it can produce some impact at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value}.
-We have observed that there exists a vast divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool, probably because of the operation and maintenance costs assumed by our approach were underestimated to that specific load \textcolor{red}{is it good or bad?
-the way you have written looks like HOME Pro is the best option}.
+Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG1} and \textit{EG2}, \textcolor{red}{because there are optimal solutions and CPAchecker presented the better comparative results among the verifiers}.
 
@@
 Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
-Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters to comparison.
+HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.
+\textcolor{red}{This lack of recourse is a limitation, because it is usual to establish the autonomy as a design requirement}.
+
+In terms of performance, HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed automated synthesis tool (cf.~\textit{EG3}) \textcolor{red}{but not so sound as our synthesis method}.
+
+\textcolor{red}{Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
+However, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model.
+This charge controller cost makes the synthesis approach more precise and real.
+It was observed that there exists a divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool.
+However this case study does not have a deployed PV system in order to validate which result is the correct.}
 
@@
 %------------------------------------
-
-\textcolor{red}{What is the novelty of our work?
+\textcolor{red}{
+Our novelty relies on a practical approach for to pursuit of the optimal solution of PV systems using formal methods.
+The use of formal synthesis has no precedent in literature, and we show that the results of our approach, using seven case studies, are promising.}
+%\textcolor{red}{What is the novelty of our work?
 what are the impacts/relevance of our method to the society and formal methods community?
@@
 we should emphasize the relevance of the problem we solve and give numbers to show the efficiency of our approach if compared to HOME Pro.}
-
-Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro.
-In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage.
-In this respect, even the manufacturer's brand can be presented (\textcolor{red}{shall we add this table online?} in Table~\ref{tab1} it was removed to avoid some advertising).
+Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, an state-of-the art simulation tool.
+The use of data from real deployed systems in Amazonas State, Brazil, were important in order to reach that conclusion.
+The battery autonomy feature of our synthesis approach is an advantage as well.
+In addition, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage.
+These details are important for the owner of the system and aids the process of equipment purchase.
 %
@@
 %
-
 \end{document}
-
 %\subsection{Design and Simulation of Solar PV systems}

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{red}{In CPS some of the variables may belong to continuous domains (real numbers).
-All the equations illustrated here produces real numbers, although when choosing batteries and panels quantities those real numbers must be translated into integer number (closest ones, considering the minimum or maximum according with each equation).
-The underlying verification tool and the simulation tool must support those type of variables in order to produce a correct result.}
+All the equations above model the continuous-time behavior of the PV system; they produce real numbers, but when choosing batteries and panels quantities, those real numbers must be converted into integer numbers (closest ones, considering the minimum or maximum according to each equation).
+The underlying verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
 

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %---------------------------------------------------------------------------
-\subsection{Description of the Case studies}
+\subsection{Description of the Case Studies}
 %---------------------------------------------------------------------------
-The proposed synthesis approach was evaluated in  seven stand-alone PV system case studies: 
-\textbf{case study 1:} power peak: 342 W, power surge: 342 W, energy consumption: 3,900 Wh/day, battery autonomy: 48 h; \textbf{case study 2:} Power peak: 814 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 48 h; \textbf{case study 3:} power peak: 815 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 12 h; \textbf{case study 4:} power peak: 253 W, power surge: 722 W, energy consumption: 3,600 Wh/day, battery autonomy: 48 h; \textbf{case study 5:} power peak: 263 W, power surge: 732 W, energy consumption: 2,500 Wh/day, battery autonomy: 48 h; \textbf{case study 6:} power peak: 322 W, power surge: 896 W, energy consumption: 4,300 Wh/day, battery autonomy: 48 h; \textbf{case study 7:} power peak: 1,586 W, power surge: 2,900 W, energy consumtion: 14,000 Wh/day, battery autonomy: 48 h.
 
-These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas,  Brazil~\cite{TrindadeCordeiro19,Agrener2013}, with the exception of case 7, that was idealized as a small town solution to support a few lamps and a 12 kBTUs air-conditioner.
+The proposed synthesis approach was evaluated in seven stand-alone PV system case studies.
+Here we report each case study as a tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
+\textbf{case study 1:} \{342; 342; 3,900; 48\}; \textbf{case study 2:} \{814; 980; 4,880; 48\}; \textbf{case study 3:} \{815; 980; 4,880; 12\}; \textbf{case study 4:} \{253; 722; 3,600; 48\}; \textbf{case study 5:} \{263; 732; 2,500; 48\}; \textbf{case study 6:} \{322; 896; 4,300; 48\}; \textbf{case study 7:} \{1,586; 2,900; 14,000; 48\}.
+These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized as a small-town solution to support a few lamps and a 12k BTUs air-conditioner.
 For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
@@
 For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB of RAM running Windows 10.
-\textcolor{red}{The hardware platform was not the same because of the availability of the machines, and this has impact in respect to the performance that is less favorable to HOMER Pro}.
+The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favorable to HOMER Pro..
 We perform the experiments with a predefined time out of $240$ minutes.
@@
 %---------------------------------------------------------------------------
-A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}.
+%A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}.
 
-Related to the verifiers comparison, CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
-Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes.
-The violation (SAT result) indicated in on-line Table is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}.
-CBMC and ESBMC are unable to produce any conclusive result.
-Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG1} and \textit{EG2}, \textcolor{red}{because there are optimal solutions and CPAchecker presented the better comparative results among the verifiers}.
+Concerning the verifiers' comparison, CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
+Only case study $7$ led to a \textit{time out} result in CPAchecker.
+The violation (SAT result) indicated in the on-line table\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}.
+CBMC and ESBMC are unable to produce any conclusive results since \textit{time-outs} or \textit{memory-outs} occurred; these results partially answer the \textit{EG1} and \textit{EG2}, because there exist optimal solutions for these case studies and CPAchecker presented the best results among the verifiers.
 
@@
 HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.
-\textcolor{red}{This lack of recourse is a limitation, because it is usual to establish the autonomy as a design requirement}.
+This lack of recourse is a limitation since it is usual to establish autonomy as a design requirement.
 
-In terms of performance, HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed automated synthesis tool (cf.~\textit{EG3}) \textcolor{red}{but not so sound as our synthesis method}.
-
-\textcolor{red}{Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
+In terms of performance, HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed synthesis approach (cf.~\textit{EG3}) but not sound as our method.
+Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
 However, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model.
 This charge controller cost makes the synthesis approach more precise and real.
-It was observed that there exists a divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool.
-However this case study does not have a deployed PV system in order to validate which result is the correct.}
+We observed that there exists a divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool.
+However, this case study does not have a deployed PV system in order to validate which result is correct.
 
@@
 %------------------------------------
-\textcolor{red}{
-Our novelty relies on a practical approach for to pursuit of the optimal solution of PV systems using formal methods.
-The use of formal synthesis has no precedent in literature, and we show that the results of our approach, using seven case studies, are promising.}
-%\textcolor{red}{What is the novelty of our work?
-what are the impacts/relevance of our method to the society and formal methods community?
-How formal methods can improve the people's life?
-we should emphasize the relevance of the problem we solve and give numbers to show the efficiency of our approach if compared to HOME Pro.}
+
+Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using formal methods.
+The use of formal synthesis has no precedent in literature, and we show that the results of our approach, using seven case studies, are promising.
 Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, an state-of-the art simulation tool.

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 The use of formal methods in electrical systems is a new subject, with significant research spanning only the last four years.
-However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems has never been done before.
-Here our primary goal is to develop and evaluate a sound, automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis.
-We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach, with two phases linking the technical and the cost analysis.
+However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic (PV) systems remains unexplored in literature.
+Here our primary goal is to develop and evaluate a sound, automated synthesis approach to obtaining optimal sizing of stand-alone PV systems.
+We propose a variant of the counterexample guided inductive synthesis approach, with two phases linking the technical and the cost analysis.
 First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
@@
 If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution.
-Experimental results using seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time.
-%We also present a comparison with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach.
+Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time.
+We also present a comparison with a specialized simulation tool over real PV systems to show the effectiveness of our approach.
 %\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
@@
 
-Here, we have developed a (non-trivial) variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} technique for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
 Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
@@
 If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost.
-Here our focus is not on new criteria or even optimization objectives.
 

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 2.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the traditional techniques (manual and simulation) and the proposed automated synthesis techniques.
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the traditional techniques (manual and simulation) and the proposed synthesis technique.
 Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions.
 For the automated synthesis, we also define the bound $k$ to restrict the design-space search.
-On the one hand, if $k$ is too small, then the approach might not return a solution due to the search-space depth.
 Here we start with a low bound $k$ and incrementally increase it to avoid time and memory constraints on our verification back-end.
 Therefore, the proper choice of $k$ is essential to this method.
-%
+
 \begin{figure}[h]
@@
 \begin{center}
-%\begin{figure}[h]
-%	\centering
 	\includegraphics[width=0.5\columnwidth]{fig2_rev2.jpg}
@@
 	\label{Counter-Example-Guided-Inductive-Synthesis}
-%\end{figure}
 \end{wrapfigure}
@@
 
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.
+If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution to the full synthesis formula, which is passed to {\sc Verify} to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
+If this is the case, then the algorithm terminates.
 
@@
 Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times.
-However, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists, and our synthesis engine can then conclude that no possible equipment combination was found.
+However, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists.
+%, and our synthesis engine can then conclude that no possible equipment combination was found.
 
@@
 (4) there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
-a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.%
+a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
 

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \usepackage{wrapfig}
+\usepackage{mathtools}
+\usepackage{tabularx}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
+\begin{subequations}
+  \begin{tabularx}{\textwidth}{Xp{1cm}X}
     \begin{equation}
     \label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP},
+      I_{c,min} = I_{sc,amb} \times N_{PP}.
     \end{equation}
-
+  & &
 \begin{equation}
@@
 \end{equation}
+\end{tabularx}
+\end{subequations}
 
@@
 
+\begin{subequations}
+  \begin{tabularx}{\textwidth}{Xp{1cm}X}
 \begin{equation}
@@
 \end{equation}
-
+  & &
 \begin{equation}
@@
 
-All the equations above model the continuous-time behavior of the PV system; they produce real numbers, but when choosing batteries and panels quantities, those real numbers must be converted into integer numbers (closest ones, considering the minimum or maximum according to each equation).
-The underlying verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
+All the equations above model the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones (closest ones, considering the minimum or maximum according to each equation).
+The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
 

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Here we report each case study as a tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
-\textbf{case study 1:} \{342; 342; 3,900; 48\}; \textbf{case study 2:} \{814; 980; 4,880; 48\}; \textbf{case study 3:} \{815; 980; 4,880; 12\}; \textbf{case study 4:} \{253; 722; 3,600; 48\}; \textbf{case study 5:} \{263; 732; 2,500; 48\}; \textbf{case study 6:} \{322; 896; 4,300; 48\}; \textbf{case study 7:} \{1,586; 2,900; 14,000; 48\}.
+\textbf{1:} \{342; 342; 3,900; 48\}; \textbf{2:} \{814; 980; 4,880; 48\}; \textbf{3:} \{815; 980; 4,880; 12\}; \textbf{4:} \{253; 722; 3,600; 48\}; \textbf{5:} \{263; 732; 2,500; 48\}; \textbf{6:} \{322; 896; 4,300; 48\}; \textbf{7:} \{1,586; 2,900; 14,000; 48\}.
 These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized as a small-town solution to support a few lamps and a 12k BTUs air-conditioner.
@@
 Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
-
-Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
+%
+Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
 
@@
 In particular, HOMER Pro has the following characteristics:
-
-\begin{itemize}
-\item It is available only for MS Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
-\item It does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
-\item The optimization analysis of HOMER defines a load curve and temperature according to data collected from online databases.
+(a) it is available only for MS Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
+(b) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
+(c) the optimization analysis defines a load curve and temperature according to data collected from online databases.
 However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach;
-\item It does not have a charge controller.
+(d) it does not have a charge controller.
 During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution;
-\item It was assumed the value of 95\% availability of the PV system.
+(e) it was assumed 95\% availability of the PV system.
 By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}.
-For ordinary house electrical load, 95\% is considered acceptable;
-\item It was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
-\item It was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling).
+For an ordinary house electrical load, 95\% is considered acceptable;
+(f) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
+(g) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW (and with capacity of $83.4$ Ah according to HOMER Pro modeling).
 During run-time, HOMER decides the size in kW of each module based on feasibility and lower cost.
-\end{itemize}
 
@@
 
-Concerning the verifiers' comparison, CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
+CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
 Only case study $7$ led to a \textit{time out} result in CPAchecker.
@@
 
-In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our synthesis approach.
+The size of the PV panels and battery bank were larger in HOMER Pro than with our approach.
 To compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 %\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{hyperref}
 \usepackage{algorithm,algorithmic}
@@
 
-Optimization of PV systems is not a recent topic; since the '90s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}.
+Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}.
 In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{optimalsizingprocess3}
+\includegraphics[width=0.8\textwidth]{optimalsizingprocess4}
 \centering
@@
 (3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; as a result,
-(4) there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
+(4) there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e. 
 a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
@@
 Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}. 
-Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e.
+without the operational and maintenance costs~\cite{Alsadi2018}.
 
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \REQUIRE weather data (temperature, solar irradiance), list of equipment (datasheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis).
+  \REQUIRE weather data (temperature, solar irradiance), list of equipment (datasheet and price), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis).
  \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available.
@@
 Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers' data and prices of PV panels, batteries, charge controllers, and inverters (Line 2).
-We define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5.
-
+We define user requirements, i.e.
+house requirements and design definitions, from Lines 4 and 5.
 The \textit{for}-loop started at Line 6 controls the lowest cost to the PV solution.
@@
 
-If our algorithm does not find a feasible solution among the item of equipment that was provided to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
+If our algorithm does not find a feasible solution among the item of equipment that was provided to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}), i.e.
+the program finishes and does not find a solution.
 It indicates that it was not possible to combine the items of each equipment and create a feasible solution.
@@
 %
-Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
+Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc file.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
 
@@
 (f) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
-(g) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW (and with capacity of $83.4$ Ah according to HOMER Pro modeling).
-During run-time, HOMER decides the size in kW of each module based on feasibility and lower cost.
+(g) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity).
+During run-time, HOMER decides the size in kW of each based on feasibility and lower cost.
 
@@
 %---------------------------------------------------------------------------
+Our evaluation aims to answer three experimental goals: [EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?, [EG2] \textbf{(performance)} How do the software verifiers compare to each other for synthesizing PV systems?, and [EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
 
-Our evaluation aims to answer three experimental goals: 
-\begin{enumerate}
-\item[EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?, 
-\item[EG2] \textbf{(performance)} How do the software verifiers compare to each other for synthesizing PV systems?, and 
-\item[EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
-\end{enumerate}
-
-All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits.
-For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB of RAM running Windows 10.
-The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favorable to HOMER Pro..
+All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits.
+For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10.
+The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favorable to HOMER Pro.
 We perform the experiments with a predefined time out of $240$ minutes.
@@
 %A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}. 
-
 CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
@@
 Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
-HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.
+HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e.
+the tool always tries to feed with electricity the given load during $365$ days/year.
 This lack of recourse is a limitation since it is usual to establish autonomy as a design requirement.
@@
 In terms of performance, HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed synthesis approach (cf.~\textit{EG3}) but not sound as our method.
-Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
+Comparing the results between CPAchecker and HOMER Pro, we have observed that the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
 However, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model.

### 2020-01-23 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
fixed affiliation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-\institute{Federal University of Amazonas, Brazil \email{alessandrotrindade@ufam.edu.br} \and
-University of Manchester, UK \email{lucas.cordeiro@manchester.ac.uk}}
+\institute{Federal University of Amazonas, Brazil, \email{alessandrotrindade@ufam.edu.br} \and
+University of Manchester, UK, \email{lucas.cordeiro@manchester.ac.uk}}
 \maketitle              % typeset the header of the contribution

### 2020-01-23 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using formal methods.
-The use of formal synthesis has no precedent in literature, and we show that the results of our approach, using seven case studies, are promising.
-Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, an state-of-the art simulation tool.
-The use of data from real deployed systems in Amazonas State, Brazil, were important in order to reach that conclusion.
-The battery autonomy feature of our synthesis approach is an advantage as well.
-In addition, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage.
-These details are important for the owner of the system and aids the process of equipment purchase.
+Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using contemporary formal methods.
+The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising.
+Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art simulation tool.
+In particular, the battery autonomy feature together with the details of every component of a PV system solution, e.g., complete electrical information from datasheet of manufacturers, including the component model, nominal current, and voltage, are an advantage for our synthesis approach.
+These technical details are essential for the owner of the PV system and aid the process of equipment purchase.
+Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to reach that conclusion.
+
 %

### 2020-01-23 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic (PV) systems remains unexplored in literature.
-Here our primary goal is to develop and evaluate a sound, automated synthesis approach to obtaining optimal sizing of stand-alone PV systems.
+Here our primary goal is to develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems.
 We propose a variant of the counterexample guided inductive synthesis approach, with two phases linking the technical and the cost analysis.
@@
 \textbf{1:} \{342; 342; 3,900; 48\}; \textbf{2:} \{814; 980; 4,880; 48\}; \textbf{3:} \{815; 980; 4,880; 12\}; \textbf{4:} \{253; 722; 3,600; 48\}; \textbf{5:} \{263; 732; 2,500; 48\}; \textbf{6:} \{322; 896; 4,300; 48\}; \textbf{7:} \{1,586; 2,900; 14,000; 48\}.
-These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized as a small-town solution to support a few lamps and a 12k BTUs air-conditioner.
+These case studies were defined based on the usual electrical load found in riverside communities in the Amazonas State, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized as a small-town solution to support a few lamps and a 12k BTUs air-conditioner.
 For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
@@
 
-Concerning the off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis.
+Concerning the off-the-shelf simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis.
 Here we used HOMER Pro version $3.13.1$ as a state-of-the-art simulation tool for comparison purposes.
 In particular, HOMER Pro has the following characteristics:
-(a) it is available only for MS Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
+(a) it is available only for MS-Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
 (b) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
@@
 %---------------------------------------------------------------------------
-Our evaluation aims to answer three experimental goals: [EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?, [EG2] \textbf{(performance)} How do the software verifiers compare to each other for synthesizing PV systems?, and [EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
+Our evaluation aims to answer three experimental goals: [EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?; [EG2] \textbf{(performance)} How do the symbolic verifiers compare to each other for synthesizing PV systems?; and [EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
 
@@
 The violation (SAT result) indicated in the on-line table\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}.
-CBMC and ESBMC are unable to produce any conclusive results since \textit{time-outs} or \textit{memory-outs} occurred; these results partially answer the \textit{EG1} and \textit{EG2}, because there exist optimal solutions for these case studies and CPAchecker presented the best results among the verifiers.
+CBMC and ESBMC are unable to produce any conclusive results since \textit{time-outs} or \textit{memory-outs} occurred; these results partially answer \textit{EG1} and \textit{EG2} since our approach provides optimal solutions for six case studies and CPAchecker presented the best results among the verifiers.
 
@@
 Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
-HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e.
-the tool always tries to feed with electricity the given load during $365$ days/year.
+HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.
 This lack of recourse is a limitation since it is usual to establish autonomy as a design requirement.
@@
 We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the complexity of the optimization, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.
+Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.
 

### 2020-01-23 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \usepackage{tabularx}
+\usepackage{etoolbox}
+
 % Used for displaying a sample figure. If possible, figure files should
@@
 However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic (PV) systems remains unexplored in literature.
-Here our primary goal is to develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems.
-We propose a variant of the counterexample guided inductive synthesis approach, with two phases linking the technical and the cost analysis.
+Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems.
+We propose a variant of the counterexample guided inductive synthesis approach, with two phases linking the technical and cost analysis.
 First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
-Second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
+Second, the candidate is then verified iteratively with a lower bound cost via model checking.
 If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution.
-Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time.
+Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time, which is validated via deployed systems in a riverside community in the Amazonas State (Brazil).
 We also present a comparison with a specialized simulation tool over real PV systems to show the effectiveness of our approach.
@@
 
+\vspace{-2ex}
+
 %-----------------------------------------------------------
@@
 %-----------------------------------------------------------
+
+\vspace{-1ex}
 

### 2020-01-23 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
added new reference
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 In our CEGIS variant, there exist four differences related to the traditional one: 
-(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+(1) there exists no test vector and every candidate is generated in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
 (2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
 (3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; as a result,
-(4) there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e. 
-a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
+(4) there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
 
@@
 
-All the equations above model the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones (closest ones, considering the minimum or maximum according to each equation).
+All the equations above model the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
 The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
@@
 Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}. 
-Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e.
-without the operational and maintenance costs~\cite{Alsadi2018}.
+Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
 
-Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. 
+Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
 %
@@
  \REQUIRE weather data (temperature, solar irradiance), list of equipment (datasheet and price), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis).
- \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available.
+ \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, stating that the project has no feasible solution considering the requirements and the list of equipment available.
  \STATE Initialize variables \\
@@
 Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers' data and prices of PV panels, batteries, charge controllers, and inverters (Line 2).
-We define user requirements, i.e.
-house requirements and design definitions, from Lines 4 and 5.
+We define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5.
 The \textit{for}-loop started at Line 6 controls the lowest cost to the PV solution.
 In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, which will never be reached because the optimal solution will be found first.
+The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, which will never be reached because the optimal solution will be found first (if it exists).
 
@@
 Next, we use Eq.~\ref{eq:Ecorrected}, Eq.~\ref{eq:Ep}, Eq.~\ref{eq:NTPmin}, Eq.~\ref{eq:NPSmin}, Eq.~\ref{eq:NPPmin}, Eq.~\ref{eq:Cbank}, Eq.~\ref{eq:Nbtotal}, Eq.~\ref{eq:iscamb}, and Eq.~\ref{eq:icmin} to calculate the sizing variables (Lines 11 to 17).
-The directive \textit{assume} (Lines 15, 18 and 19) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines 15, 18, and 19.
+The directive \textit{assume} (Lines 15, 18, and 19) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines 15, 18, and 19.
 Our algorithm reaches Line 20 with one feasible solution; the cost of that solution is calculated in $F_{obj}$ (Line 21).
 
-If our algorithm does not find a feasible solution among the item of equipment that was provided to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}), i.e.
-the program finishes and does not find a solution.
+If our algorithm does not find a feasible solution among the item of equipment that was provided to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
 It indicates that it was not possible to combine the items of each equipment and create a feasible solution.

### 2020-01-23 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
minor change
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
CAV 2020 paper update

@@
 %
-Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc file.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0 with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
+Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc file.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
 
@@
 %------------------------------------
-\section{Conclusion} 
+\section{Conclusions} 
 %------------------------------------

### 2020-01-26 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 \begin{abstract}
-The use of formal methods in electrical systems is a new subject, with significant research spanning only the last four years.
-However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic (PV) systems remains unexplored in literature.
+\textcolor{red}{The use of the power generation with a renewable energy source is growing rapidly due to the industrial development.
+Renewable energy is environment-friendly: clean, operates silently, long-lasting, low maintenance costs, zero fuel costs and an inexhaustible supply.
+Particularly, photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation.} The use of formal methods in electrical systems is a new subject, with significant research spanning only the last five years.
+However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature.
 Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
@@
 (a) it is available only for MS-Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
-(b) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
-(c) the optimization analysis defines a load curve and temperature according to data collected from online databases.
+\textcolor{red}{(b) it has two optimization algorithms.
+One algorithm simulates all of the feasible system configurations defined by the search space.
+Additionally, a proprietary derivative-free algorithm to search for the least-costly system;}
+(c) it does not have LCC cost in its reports, only Net Present Cost (NPC). However, we can obtain LCC from NPC; 
+(d) the optimization analysis defines a load curve and temperature according to data collected from online databases.
 However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach;
-(d) it does not have a charge controller.
+(e) it does not have a charge controller.
 During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution;
-(e) it was assumed 95\% availability of the PV system.
+(f) it was assumed 95\% availability of the PV system.
 By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}.
 For an ordinary house electrical load, 95\% is considered acceptable;
-(f) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
-(g) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity).
+(g) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
+(h) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity).
 During run-time, HOMER decides the size in kW of each based on feasibility and lower cost.

### 2020-01-26 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 Renewable energy is environment-friendly: clean, operates silently, long-lasting, low maintenance costs, zero fuel costs and an inexhaustible supply.
-Particularly, photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation.} The use of formal methods in electrical systems is a new subject, with significant research spanning only the last five years.
+Particularly, photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation.} The use of formal methods in electrical systems is a new subject with significant research spanning only the last five years.
 However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature.
 Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems.
-We propose a variant of the counterexample guided inductive synthesis approach, with two phases linking the technical and cost analysis.
+We propose a variant of the counterexample guided inductive synthesis approach with two phases linking the technical and cost analysis.
 First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
@@
 
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
+In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
 However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+\textcolor{red}{Generic optimization tools can be used as well, since that a PV system can be modeled as a non-linear set of equations.
+However, the industry demands that the presented solution be the optimum considering manufacturers, models and brands available on the market and not just minimum or maximum powers and values for the optimized items, and this is only possible with the use of specialist electrical systems optimization software.}
 
@@
 In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
-The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted.
-If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost.
+The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; \textcolor{red}{if the verification step dos not produces a FAIL result (i.e is unsatisfiable), the lower bound is adjusted; if it produces a FAIL, i.e is satisfiable, then a counterexample is provided with an optimal sizing.} % that meets both power reliability and system cost.
 
@@
 %-----------------------------------------------------------
-
 \vspace{-1ex}
@@
 %-----------------------------------------------------------
-
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
@@
 
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}. 
-The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. 
-For night hours or rainy days, we hold batteries where power can be stored and used.
-The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required.
-That converter is called inverter; the AC load dictates the behavior of the AC electrical load from the house that will be fed by the system.
+%A PV system is illustrated in Fig.\ref{fig:blockdiagram}. 
+A photovoltaic system employs: the PV generator, which can be a \textbf{panel or an array}, is a semiconductor device that can convert solar energy into DC electricity; for night hours or rainy days, we hold \textbf{batteries} where power can be stored and used; the use of batteries as a storage form implies the presence of a \textbf{charge controller}~\cite{Hansen}; the PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textbf{inverter}); the \textbf{AC load} dictates the behavior of the AC electrical load from the house that will be fed by the system.
 
-\begin{wrapfigure}{r}{0.5\textwidth}
-%\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
-\centering
-\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
-\label{fig:blockdiagram} 
-\end{wrapfigure}
-
+%\begin{wrapfigure}{r}{0.5\textwidth}
+%%\begin{figure}[h]
+%\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
+%\centering
+%\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
+%\label{fig:blockdiagram} 
+%\end{wrapfigure}
+%
 The sizing check will ensure that the system meets the standard project steps related to the critical period solar energy method~\cite{Pinho} and the MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
@@
 Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}. 
-Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
+\textcolor{red}{Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}, as shown in Eq.~\eqref{eq:LCC},}
+
+\begin{equation}
+\label{eq:LCC}
+LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
+\end{equation}
+
+\noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current prices.
 
@@
 In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, which will never be reached because the optimal solution will be found first (if it exists).
+The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, \textcolor{red}{which will be reached only if the optimal solution is not found first.
+If this $MaxCost$ was reached then there is not feasible solution to the problem.}
 
@@
 If our algorithm does not find a feasible solution among the item of equipment that was provided to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
-It indicates that it was not possible to combine the items of each equipment and create a feasible solution.
+It indicates that it is not possible to combine the items of each equipment and create a feasible solution.
 The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements.
@@
 %---------------------------------------------------------------------------
-
 The proposed synthesis approach was evaluated in seven stand-alone PV system case studies.
-Here we report each case study as a tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
+These case studies were defined based on the usual electrical load found in riverside communities in the Amazonas State, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized to support a few lamps and a 12k BTUs air-conditioner solution.
+Here we report each case study as a \textcolor{red}{4-}tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
 \textbf{1:} \{342; 342; 3,900; 48\}; \textbf{2:} \{814; 980; 4,880; 48\}; \textbf{3:} \{815; 980; 4,880; 12\}; \textbf{4:} \{253; 722; 3,600; 48\}; \textbf{5:} \{263; 732; 2,500; 48\}; \textbf{6:} \{322; 896; 4,300; 48\}; \textbf{7:} \{1,586; 2,900; 14,000; 48\}.
-These case studies were defined based on the usual electrical load found in riverside communities in the Amazonas State, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized as a small-town solution to support a few lamps and a 12k BTUs air-conditioner.
-For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
+\textcolor{red}{This 4-tuple represents part of the Algorithm~\ref{alg:verification-algorithm} inputs.} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
 Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
@@
 %---------------------------------------------------------------------------
-
 Concerning the off-the-shelf simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis.
@@
 We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.
+Nevertheless, we have also identified three threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; and (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
+%; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.
 
@@
 In particular, the battery autonomy feature together with the details of every component of a PV system solution, e.g., complete electrical information from datasheet of manufacturers, including the component model, nominal current, and voltage, are an advantage for our synthesis approach.
-These technical details are essential for the owner of the PV system and aid the process of equipment purchase.
-Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to reach that conclusion.
+These technical details are essential for the owner of the PV system and aid the process of equipment purchase and essential \textcolor{red}{to the industry that demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market; and not just maximum or minimum values of parameters that still need to be adjusted according to the chosen equipment.
+Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.}
 

### 2020-01-26 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

@@
 In particular, HOMER Pro has the following characteristics:
-(a) it is available only for MS-Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
-\textcolor{red}{(b) it has two optimization algorithms.
-One algorithm simulates all of the feasible system configurations defined by the search space.
-Additionally, a proprietary derivative-free algorithm to search for the least-costly system;}
+(a) it is available only for MS-Windows, its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
+\textcolor{red}{(b) it has two optimization algorithms: one algorithm simulates all of the feasible system configurations defined by the search space, and additionally, a proprietary derivative-free algorithm to search for the least-costly system;}
 (c) it does not have LCC cost in its reports, only Net Present Cost (NPC). However, we can obtain LCC from NPC; 

### 2020-01-27 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}
-\textcolor{red}{The use of the power generation with a renewable energy source is growing rapidly due to the industrial development.
-Renewable energy is environment-friendly: clean, operates silently, long-lasting, low maintenance costs, zero fuel costs and an inexhaustible supply.
-Particularly, photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation.} The use of formal methods in electrical systems is a new subject with significant research spanning only the last five years.
-However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature.
+The use of power generation with a renewable energy source is proliferating due to industrial development.
+Photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation.
+The use of formal methods for PV systems is a new subject with significant research spanning only the last five years.
+%However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
 Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems.
@@
 If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution.
-Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time, which is validated via deployed systems in a riverside community in the Amazonas State (Brazil).
-We also present a comparison with a specialized simulation tool over real PV systems to show the effectiveness of our approach.
+Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time.
+We also compare our formal approach with a commercial simulation tool over real PV systems to show its effectiveness.
 %\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
@@
 However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
-\textcolor{red}{Generic optimization tools can be used as well, since that a PV system can be modeled as a non-linear set of equations.
-However, the industry demands that the presented solution be the optimum considering manufacturers, models and brands available on the market and not just minimum or maximum powers and values for the optimized items, and this is only possible with the use of specialist electrical systems optimization software.}
+Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
+However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialist PV optimization software.
 
@@
 In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
-The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; \textcolor{red}{if the verification step dos not produces a FAIL result (i.e is unsatisfiable), the lower bound is adjusted; if it produces a FAIL, i.e is satisfiable, then a counterexample is provided with an optimal sizing.} % that meets both power reliability and system cost.
+The candidate solution is then verified via model checking with a lower bound that serves as the minimum cost of reference.
+If the verification step does not produce a counterexample, then the lower bound is adjusted; otherwise, we have achieved an optimal PV sizing.
 
 Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing.
-First, the use of automated symbolic verification in PV systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically, their use in synthesizing PV sizing is novel.
-Second, we evaluate our approach using different state-of-the-art symbolic verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems and compare that to HOMER.
-Lastly, we discuss the main challenges of applying formal methods to PV systems and also reflect on lessons learned from this practical experience.
+First, the use of automated verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}.
+Here the application of formal methods to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools.
+Second, we evaluate our approach using different state-of-the-art verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems and compare that to HOMER.
+Lastly, we discuss the challenges of applying formal methods to PV systems and reflect on lessons learned from this experience.
 
@@
 
-Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
+Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
 %

### 2020-01-27 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
-Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}. 
-\textcolor{red}{Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}, as shown in Eq.~\eqref{eq:LCC},}
-
+The optimal sizing of PV systems is made by the best compromise between two objectives: \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.
+This study will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}.
+Based on the fact that the deployment location is not specified, our study will use an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}, given as,
+%
 \begin{equation}
@@
 In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, \textcolor{red}{which will be reached only if the optimal solution is not found first.
-If this $MaxCost$ was reached then there is not feasible solution to the problem.}
+The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, which will be reached if the optimal solution is not found first.
+If this $MaxCost$ is reached, then there exists no feasible solution to the problem.
 
@@
 These case studies were defined based on the usual electrical load found in riverside communities in the Amazonas State, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized to support a few lamps and a 12k BTUs air-conditioner solution.
-Here we report each case study as a \textcolor{red}{4-}tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
+Here we report each case study as a 4-tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
 \textbf{1:} \{342; 342; 3,900; 48\}; \textbf{2:} \{814; 980; 4,880; 48\}; \textbf{3:} \{815; 980; 4,880; 12\}; \textbf{4:} \{253; 722; 3,600; 48\}; \textbf{5:} \{263; 732; 2,500; 48\}; \textbf{6:} \{322; 896; 4,300; 48\}; \textbf{7:} \{1,586; 2,900; 14,000; 48\}.
-\textcolor{red}{This 4-tuple represents part of the Algorithm~\ref{alg:verification-algorithm} inputs.} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
+This 4-tuple represents the Algorithm~\ref{alg:verification-algorithm} inputs.
+For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
 Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
@@
 (a) it is available only for MS-Windows, its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
-\textcolor{red}{(b) it has two optimization algorithms: one algorithm simulates all of the feasible system configurations defined by the search space, and additionally, a proprietary derivative-free algorithm to search for the least-costly system;}
-(c) it does not have LCC cost in its reports, only Net Present Cost (NPC). However, we can obtain LCC from NPC; 
+(b) it has two optimization algorithms: one algorithm simulates all of the feasible system configurations defined by the search space, and additionally, a proprietary derivative-free algorithm to search for the least-costly system;
+(c) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
 (d) the optimization analysis defines a load curve and temperature according to data collected from online databases.
@@
 The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising.
-Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art simulation tool.
-In particular, the battery autonomy feature together with the details of every component of a PV system solution, e.g., complete electrical information from datasheet of manufacturers, including the component model, nominal current, and voltage, are an advantage for our synthesis approach.
-These technical details are essential for the owner of the PV system and aid the process of equipment purchase and essential \textcolor{red}{to the industry that demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market; and not just maximum or minimum values of parameters that still need to be adjusted according to the chosen equipment.
-Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.}
+Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool.
+In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach.
+These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by off-the-shelf optimization tools and the items of equipment for solar systems available on the market to achieve accuracy.
+Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.
+
+%Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using contemporary formal methods.
+The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising.
+Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool.
+In particular, the battery autonomy feature together with the details of every component of a PV system solution are an advantage for our synthesis approach.
+These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market; and not just maximum or minimum values of parameters given by off-the-shelf optimization tools, which still need to be adjusted according to the chosen equipment.
+Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.
+
+%and aid the process of equipment purchase 
+%, e.g., complete electrical information from datasheet of manufacturers, including the component model, nominal current, and voltage,
 

### 2020-01-27 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems.
-We propose a variant of the counterexample guided inductive synthesis approach with two phases linking the technical and cost analysis.
-First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
+We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis.
+We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market.
+%First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
 Second, the candidate is then verified iteratively with a lower bound cost via model checking.
@@
 Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time.
-We also compare our formal approach with a commercial simulation tool over real PV systems to show its effectiveness.
+We also compare our CEGIS approach with a state-of-the-art commercial tool over real PV systems to show its effectiveness.
 %\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}

### 2020-01-27 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified three threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; and (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
+Nevertheless, we have also identified three threats to the validity of our results that constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; and (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
 %; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.

### 2020-01-27 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Notably, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
+The number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are resp.:
 
@@
 
-Regarding the charge controller, it must initially meet the voltage requirement of the PV system $V_{system}$, as described by Eq.~\ref{eq:vcvsystem} to the charge controller voltage $V_{c}$:
+Regarding the charge controller, it must initially meet the voltage requirement of the PV system $V_{system}$, given by Eq.~\ref{eq:vcvsystem} to the charge controller voltage: % $V_{c}$:
 
@@
  \REQUIRE weather data (temperature, solar irradiance), list of equipment (datasheet and price), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis).
- \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, stating that the project has no feasible solution considering the requirements and the list of equipment available.
+ \ENSURE FAIL with counterexample showing the optimal sizing; SUCCESS, stating that the project has no feasible solution considering the requirements and the list of equipment available.
  \STATE Initialize variables \\
@@
  \ENDFOR
- \RETURN $(\,)$ 
+% \RETURN $(\,)$ 
  \end{scriptsize}

### 2020-02-01 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 \begin{itemize}
-\item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
+\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
 Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting systems, solar lanterns, and solar power plants;
@@
 
-In the specific case of isolated communities, depending on the type of load, cost, resources availability, and the load requirements, standalone systems can be split into several categories, as described below.
+In the specific case of isolated communities, depending on the type of load, cost, resources availability, and the load requirements, stand-alone systems can be split into several categories, as described below.
 Since the goal of this Thesis is to present solutions only to isolated/ off-grid applications, on-grid or hybrid configurations are not discussed here.
@@
 
-\subsection{Unregulated standalone PV systems with DC load }
+\subsection{Unregulated Stand-alone PV Systems With DC Load }
 Usually this type of system is for low power applications, as defined by \cite{Roy}.
@@
 \centering
-\caption{Unregulated standalone solar PV system with DC load. Source: \cite{Roy}.}
+\caption{Unregulated stand-alone solar PV system with DC load. Source: \cite{Roy}.}
 \label{fig:unregSPV}
@@
 
-\subsection{Regulated standalone PV systems with DC load}
-Similar to the unregulated standalone system with DC load, the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated in Fig.\ref{fig:regSPV1}.
+\subsection{Regulated Stand-alone PV Systems With DC Load}
+Similar to the unregulated stand-alone system with DC load, the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated in Fig.\ref{fig:regSPV1}.
 Usually systems with MPPT should have a battery; otherwise, the extra power will be wasted.
@@
 \centering
-\caption{Regulated standalone solar PV system with DC load. Source: \cite{Roy}.}
+\caption{Regulated stand-alone solar PV system with DC load. Source: \cite{Roy}.}
 \label{fig:regSPV1}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Regulated standalone systems with battery and DC load}
+\subsection{Regulated Stand-alone Systems With Battery and DC load}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\caption{Regulated standalone solar PV system with battery and DC load. Source: \cite{Roy}.}
+\caption{Regulated stand-alone solar PV system with battery and DC load. Source: \cite{Roy}.}
 \label{fig:regSPV2}
@@
 According to \cite{Pinho}, PV systems that are used to feed loads with low variation of consumption can be sized to operate without the controller.
-This is known as a self-regulated standalone PV system with battery.
+This is known as a self-regulated stand-alone PV system with battery.
 However, PV panel voltage must be compatible with the battery voltage.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Regulated standalone systems with battery, AC load}
+\subsection{Regulated Stand-alone Systems With Battery and AC load}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\caption{Regulated standalone PV system with battery, AC load. Source: \cite{Roy}.}
+\caption{Regulated stand-alone PV system with battery, AC load. Source: \cite{Roy}.}
 \label{fig:regSPV3}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Design and Validation of a Solar photovoltaic system}
+\subsection{Design and Validation of a Solar PV System}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Component models for stand-alone PV systems}
-\label{model}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The main purpose of this section is to describe the models for the elements of a standalone PV system: the PV generator, battery, controller, inverter, and load.
+\label{sec:model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The main purpose of this section is to describe the models for the elements of a stand-alone PV system: the PV generator, battery, controller, inverter, and load.
 The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}.
@@
 \begin{figure}[h]
-\includegraphics[width=0.95\textwidth]{blockdiagramPVS}
+\includegraphics[width=0.95\textwidth]{blockdiagramPVS2}
 \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{PV generator (cell, module, string, and array) }
+\subsubsection{PV Generator (Cell, Module, String, and Array) }
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage.
-Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
+Therefore, the choice of the model is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.
 
@@
 \label{eq:1diodemodel}
-I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right] 
+I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right) -1 \right] 
 \end{equation}
@@
 \label{eq:Vmderiv}
-V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
+V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{aNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
 \end{equation}
@@
 
-Several models have been presented in the literature. However, regardless of the model, normally the following parameters are normally required:
+Several models have been presented in the literature. However, regardless of the model, normally the following parameters are normally required\cite{Mellit}:
 
@@
 Obviously $ 0<SOC<1 $.
-If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
-\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged).
-It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
+If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged.
+\item Charge (or discharge) regime.
+This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged).
+It is expressed in hours.
+%: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
 \item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
@@
 The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components.
-Battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP).
+Battery efficiency was described in this section, and the reliability is quantified by the concept of loss of load probability (LLP).
 LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.
@@
 
-The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.
-
-Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
+%The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.  
+%Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.
 
@@
 
-Most of the models created were used to simulate and optimize PV storage systems based on lead-acid batteries, the most commonly used batteries in PV applications, owing to their relative low cost and wide availability \cite{Copetti}.
+Most of the models created were used to simulate and optimize PV storage systems based on lead-acid batteries, the most commonly used batteries in developing countries, owing to their relative low cost and wide availability.
+% \cite{Copetti}.
 
@@
 \subsection{Sizing Stand-alone Solar Photovoltaic Systems}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The mathematical model presented in section~\ref{model} is important for project validation; however if an approach is used to perform the sizing of stand-alone PV systems, then the tool proposed in this thesis can perform system validation (the intended behavior), and moreover obtain optimal project sizing.
+\label{sec:sizing}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The mathematical model presented in section~\ref{sec:model} is important for project validation; however if an approach is used to perform the sizing of stand-alone PV systems, then the tool proposed in this thesis can perform system validation (the intended behavior), and moreover obtain optimal project sizing.
 

### 2020-02-01 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
 
-\section{Optimal Sizing of Solar PV Systems}
+\section{Methodology for Optimal Sizing of Solar PV Systems}
 
@@
   \REQUIRE weather data (temperature, solar irradiance), list of equipment (data sheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis)
- \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available
+ \ENSURE FAIL with counterexample showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available
   \STATE Initialize variables \\
@@
 
-The general assumptions for the scientific method of automated synthesis are the same presented in Chapter~\nameref{chap:methodology1}, with respect to the code in ANSI-C, to the bound $k$, to the simulation tool comparison, and to the battery state of charge.
+The general assumptions for the scientific method of automated synthesis are the same presented in Section~\ref{sec:assumptions}, with respect to the code in ANSI-C, to the bound $k$, to the simulation tool comparison, and to the battery state of charge.
 
 %---------------------------------------------------------------------------
-\section{Description of the case studies} 
+\section{Description of the Case Studies} 
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-\section{Results}  
+\section{Experimental Results}  
 \label{sec:synthesisresults}
@@
 Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing on the left size as the integer $8$ for the solar panel (which is the model RSM36-6-150P from the manufacturer Risen), battery $0$ refers to the model 12MF80 of 80 Ah from Moura, charge controller $1$ refers to the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ refers to the model IP350-11 from Epever (750 W).
-The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counter-example as well, shows the number of panels and batteries and how they are connected.
+The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.
 
@@
 \centering
-\caption{Counter-example generated by CPAchecker after validation of case 4 (file Counterexample.html).}
+\caption{Counterexample generated by CPAchecker after validation of case 4 (file Counterexample.html).}
 \label{fig:CPAoptc1}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparison between Formal Synthesis and HOMER Pro}
+\subsection{Comparison Between Formal Synthesis and HOMER Pro}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-02-01 Tex/Old text/chapters/chapterverification.tex
thesis update

@@
 
-\section{Automated Verification of Solar PV Systems}
+\section{Methodology for Automated Verification of Solar PV Systems}
 
@@
 
-In contrast, the outputs are not equal - design-space coverage and the information presented as result.
+In contrast, the outputs are not equal: design-space coverage and the information presented as result.
 Design-space coverage was shown in chapter \nameref{chap:background} to be the most complete when performed by automated verification, event using the bound $k$ to restrict the search, it not being necessary to unbound the system completely in order to discover a design flaw.
@@
 Fig.
-\ref{fig:systemverif4} shows how a real solar PV system is equivalent and converted to a model in order to be verified by model checking.
-
-Fig.~\ref{fig:systemverif} is an adaptation of the general process of real system conversion detailing the inputs, outputs, and requirements of a real solar PV system.
+\ref{fig:systemverif} showed how a general system is converted to a model in order to be verified by model checking.
+Fig.~\ref{fig:systemverif4} is an adaptation of the general diagram, replacing the original system by a PV system and detailing the inputs, outputs, and requirements.
 
@@
  \REQUIRE mathematical model (PV, batteries, inverter, charge controller), weather data (temperature, solar irradiance), system sizing details, design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (system availability, battery state of charge, 1-hour step of validation)
- \ENSURE design sizing check; FAIL with counter-example to improve the design; SUCCESS, saying that the project has no flaws
+ \ENSURE design sizing check; FAIL with counterexample to improve the design; SUCCESS, saying that the project has no flaws
   \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\
@@
 
-The experimental evaluation aims to answer two research questions:
+The experimental evaluation aims to answer two experimental questions:
 %
 \begin{enumerate}
-\item[RQ1] \textbf{(soundness)} Does the automated verification approach provide correct results?
-\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a commercial simulation tool?
+\item[EQ1] \textbf{(soundness)} Does the automated verification approach provide correct results?
+\item[EQ2] \textbf{(performance)} How do the verifiers compare to each other and to a commercial simulation tool?
 \end{enumerate}
@@
 %------------------------------------------
-\section{Results and Discussion}
+\section{Experimental Results and Discussion}
 \label{sec:results_indeed}
@@
 %
-Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
+Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer EQ2. 
 Note that an UNKNOWN result from the proposed verification engines does not mean that a failure was found nor that the verification was successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
@@
 
-As part of the comparison proposed, four $700$ W PV systems (houses $1$, $2$, $3$ and $4$) were evaluated by HOMER Pro (RQ2).
+As part of the comparison proposed, four $700$ W PV systems (houses $1$, $2$, $3$ and $4$) were evaluated by HOMER Pro (EQ2).
 The simulation results showed that for each of the sized systems, HOMER Pro concluded that no viable solution was found with the components inputted in the schematic.
@@
 The case study that was not possible to simulate was the $1,200$ W (house $5$).
-The reason is that HOMER Pro does not allow battery autonomy setup (because it always sizes and optimizes the electrical system in order to meet the load requirements for an entire year of simulation); therefore, it was not possible to obtain any indication about the failures of this specific PV system with simulation (RQ2).
+The reason is that HOMER Pro does not allow battery autonomy setup (because it always sizes and optimizes the electrical system in order to meet the load requirements for an entire year of simulation); therefore, it was not possible to obtain any indication about the failures of this specific PV system with simulation (EQ2).
 
@@
 
-However, even when only one interruption is reported in a month, this represents around $3.33$\% interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$), and in accordance to what was described in Section~\ref{sec:availability}, the type of electrical load of the houses is not critical; this situation is considered an energy interruption, not a system flaw, further affirming RQ1.
-Therefore, the proposed approach using automated verification provides the correct evaluation of the PV system, thus answering RQ2.
+However, even when only one interruption is reported in a month, this represents around $3.33$\% interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$), and in accordance to what was described in Section~\ref{sec:availability}, the type of electrical load of the houses is not critical; this situation is considered an energy interruption, not a system flaw, further affirming EQ1.
+Therefore, the proposed approach using automated verification provides the correct evaluation of the PV system, thus answering EQ2.
 
-All tools indicated flaws in house $5$ (automated verification or simulation); however, only the automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering RQ2.
+All tools indicated flaws in house $5$ (automated verification or simulation); however, only the automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering EQ2.
 
 In order to validate the possible flaw identified by the automated verification in house $5$, the owner of the $1,200$ W system was interviewed.
-From this it became clear that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double-checked against the monitoring system of the charge controller, which showed that the maximum power or surge power was not exceeded, thus affirming RQ1; this behavior is to be expected since the system was purchased as an off-the-shelf solution and not as a customized design for the house's electrical charges.
+From this it became clear that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double-checked against the monitoring system of the charge controller, which showed that the maximum power or surge power was not exceeded, thus affirming EQ1; this behavior is to be expected since the system was purchased as an off-the-shelf solution and not as a customized design for the house's electrical charges.
 

### 2020-02-01 Tex/Old text/chapters/introduction.tex
thesis update

@@
 
-However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored in the literature, which could offer a great opportunity to obtain a more effective design process for PV systems~\cite{ClarkeHV18}.
+However, formal methods based on \textit{symbolic model checking} applied to synthesize PV systems have not been further explored in the literature, which could offer a great opportunity to obtain a more effective design process for PV systems~\cite{ClarkeHV18}.
 
@@
 
-The main objective of this thesis is thus to create a new approach of formal methods and evaluate it as a solution to research issues pertaining to solar PV systems.
+The main objective of this thesis is thus to prove that is possible to use formal verification method to validate the design and to use formal synthesis method to optimize the sizing of stand-alone solar PV systems.
+Secondarily, we aim to develop two tools written in ANSI-C and platform-independent, based on the the new proposed techniques in order to evaluate different state-of-the art symbolic software verifiers (and solvers), and comparing the experimental results with simulation tool and with data from real PV systems deployed in riverside communities.
+Always evaluating correctness and performance.
+
+%The main objective of this thesis is thus to create a new approach of formal methods and evaluate it as a solution to research issues pertaining to solar PV systems.
 We therefore adopt specific computer science techniques to tackle specific issues of PV systems, such as design validation and sizing optimization.
@@
 %The thesis produces a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
-The originality of this thesis lies in the creation of an automated verification approach to solar PV systems.
+The originality of this thesis lies in the creation of an automated verification technique to solar PV systems.
 The research led to the creation of two software solutions to carry out computational experiments and to compare with commercial tools and real data from systems installed in the field.
@@
 In this study, a mathematical model of each component of a stand-alone PV system: the solar panel, charge controller, batteries, inverter, and electrical load, is used for formal verification.
-The behavior of each system component can be analyzed and observed with the support of the formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+The intended behavior of each system component can be verified and observed with the support of the formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
 The project requirements, such as battery autonomy and power demand, as well as the weather conditions, such as solar irradiance and ambient temperature, are provided for the proposed tool and automatically verified during the formal process.

### 2020-02-02 Tex/Old text/abstract.tex
thesis update

@@
 \end{center}
-With decreasing costs and increasing performance, the deployment of renewable energy systems is growing faster now than in the past decade.
+With decreasing costs and increasing performance, the deployment of renewable energy systems is now growing faster than in the past decade.
 In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends in energy access still fall short of global goals.

### 2020-02-02 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 \begin{itemize}
-\item In modeling, a model (normally mathematical) of the system is created; 
-\item In specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, such as reliability to performance, for example; 
-\item Normally it is expressed in temporal logic form ($CTL$); 
+\item In modeling, a model (usually mathematical) of the system is created; 
+\item In specification, usually a list of properties to be satisfied by the system is established, i.e., the requirements, such as reliability to performance, for example; 
+\item It is expressed usually in temporal logic form ($CTL$); 
 \item The model checking is the verification method itself. 
@@
 \item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
-Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting systems, solar lanterns, and solar power plants;
+Usually, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting systems, solar lanterns, and solar power plants;
 \item Grid-connected systems, where the solar PV system is connected to the grid.
@@
 However, PV panel voltage must be compatible with the battery voltage.
-Normally, the bank of batteries is oversized in relation to the PV panel and to the load.
-The drawback is the operation of the batteries, normally overloaded or with excessive discharges (that can damage the batteries).
+Usually, the bank of batteries is oversized in relation to the PV panel and to the load.
+The drawback is the operation of the batteries, usually overloaded or with excessive discharges (that can damage the batteries).
 
@@
 This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}.
-Based on these electronic components, four basic configurations are normally used when studying photovoltaic systems, as shown in Fig.
+Based on these electronic components, four basic configurations are usually used when studying PV systems, as shown in Fig.
 \ref{fig:equivckt}.
@@
 
-Several models have been presented in the literature. However, regardless of the model, normally the following parameters are normally required\cite{Mellit}:
+Several models have been presented in the literature. However, regardless of the model, the following parameters are usually required\cite{Mellit}:
 
@@
 
-\subsubsection{The inverter model}
+\subsubsection{The Inverter Model}
 As shown by \cite{Mellit}, PV arrays produce DC and therefore when the PV system contains an AC load, DC/AC conversion is required.
@@
 
-\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$ hours; 
+\noindent where the variable $autonomy$ is a design definition and usually has a value ranging from $6$ to $48$ hours; 
 $ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery depth of discharge (considered the maximum of 25\% here).

### 2020-02-02 Tex/Old text/chapters/introduction.tex
thesis update

@@
 Among the many CPS systems, in this thesis we will focus specifically on energy generation by stand-alone solar PV systems.
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
+The lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
 Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below the 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
@@
 
-The use of the power generation technology with a renewable energy source is developing rapidly due to the industrial development~\cite{Yatimi}.
+The use of the power generation technology with renewable energy sources is developing rapidly due to the industrial development~\cite{Yatimi}.
 Renewable energy leads to advances all over the world by protecting the environment: it is clean (low greenhouse gas emissions), operates silently, long-lasting, low maintenance costs, zero fuel costs and an  inexhaustible supply~\cite{Noroozian}.
@@
 Renewable sources of energy include hydro, wind, and solar PV.
-According to~\cite{SEIA} and~\cite{Chauhan}, solar is the most abundant source of renewable energy on earth.
+According to~\cite{SEIA} and~\cite{Chauhan}, the sun is the most abundant source of renewable energy on earth.
 In solar PV systems, solar radiation is captured from the sun and turned into electricity using solar PV cells made of silicon and other materials.
 
-Nothing more than a niche market only a few years ago, solar PV systems have become a mainstream electricity provider, with an  approximate 50\% increase in new PV installations from 2016 to 2017~\cite{EPIA}, although this growth is not driven by stand-alone systems.
+Nothing more than a niche market only a few years ago, solar PV systems have become a mainstream electricity provider, with an  approximate 50\% increase (or 100.9 GW)in new PV installations from 2016 to 2017~\cite{EPIA}, although this growth is not driven by stand-alone systems.
 
@@
 %-------------------------------------------------
+%
+%Global demand for energy is predicted to increase in the coming decades.
+The International Energy Agency’s 2007 World Energy Outlook states that between now and 2030:Global energy needs are expected to grow, with fossil fuels remaining the dominant source.
+%Between 2005 and 2030, energy needs are projected to expand by 55 per cent, with demand increasing from 11.4 billion tons of oil equivalent to 17.7 billion.
+Between 2005 and 2030, energy consumption is expected to increase by 50 per cent, with the bulk of the demand coming from developing countries.
+Oil, coal and gas together account for the majority of global primary energy consumption.
+However,
+%
+
+Energy access is an important issue because it can put together economic growth, human development and environmental sustainability.
+Energy has long been recognized as essential for humanity to develop and thrive, but the adoption in 2015 by 193 countries of a goal to ensure access to affordable, reliable, sustainable and modern energy for all by 2030, as part of the new United Nations Sustainable Development Goals (SDGs), marked a new level of political recognition~\cite{IEAweo2018}.
+
+The International Energy Agency (IEA) revealed that from 2000 to 2016 nearly all of those who gained access to electricity worldwide did so through new grid connections, mostly with power generation from fossil fuels.
+Over the last five years, however, renewable sources have started to gain ground, as have off-grid and mini-grid systems.
+By 2030, renewable energy sources power over 60\% of new access, and off-grid and mini-grid systems provide the means for almost half of new access~\cite{IEAweo2018}.
+Moreover, if we focus into the Amazonas State, Brazil, where around 5\% of the population in 2018 were isolated in 2,261 communities (or 41,167 houses), without electrical energy or even road access, using just boats by rivers, therefore energy is a very important issue.
+
+Under this scenario, it is important to have very well designed PV systems that won't fail when installed in the field and at the lowest acquisition cost possible.
 
@@
 The main objective of this thesis is thus to prove that is possible to use formal verification method to validate the design and to use formal synthesis method to optimize the sizing of stand-alone solar PV systems.
-Secondarily, we aim to develop two tools written in ANSI-C and platform-independent, based on the the new proposed techniques in order to evaluate different state-of-the art symbolic software verifiers (and solvers), and comparing the experimental results with simulation tool and with data from real PV systems deployed in riverside communities.
+Secondarily, we aim to develop two tools written in ANSI-C and platform-independent, based on the the new proposed techniques in order to evaluate different state-of-the art symbolic software verifiers (and solvers), and comparing the experimental results with simulation tool and with data from real PV systems installed in riverside communities.
 Always evaluating correctness and performance.
@@
 In this study, a mathematical model of each component of a stand-alone PV system: the solar panel, charge controller, batteries, inverter, and electrical load, is used for formal verification.
-The intended behavior of each system component can be verified and observed with the support of the formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
+The intended behavior of each system component can be verified and observed with the support of formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself.
 The project requirements, such as battery autonomy and power demand, as well as the weather conditions, such as solar irradiance and ambient temperature, are provided for the proposed tool and automatically verified during the formal process.
@@
 
-The proposed method is applied by means of an algorithm implemented using the C programming language.
+The proposed technique is applied by means of an algorithm implemented using the C programming language.
 We performed computing experimentation in three state-of-the-art model checkers to formally verify PV designs, aiming to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
@@
 
-With respect to the \textbf{automated synthesis} method and optimal sizing of stand-alone PV systems, this thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input.
+With respect to the \textbf{automated synthesis} technique and optimal sizing of stand-alone PV systems, this thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input.
 Given a correctness specification $\sigma$, the proposed method uses $\sigma$ as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$ with respect to power reliability.
@@
 Instead, the novelty lies in the practical approach to the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tools.
+
+Simply put, we aim to present new techniques that will ensure that you have good designs of stand-alone solar PV systems, that do not cause a drop in energy supply, and that these systems are designed at the lowest possible cost.
 
@@
 Validation when a sized system must be evaluated in order to decide if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or when the user tries to obtain a better solution that he or she has.
-We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in a comparison with specialized simulation tools, supported by real data from deployed PV systems.
+We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in a comparison with specialized simulation tools, supported by real data from installed PV systems.
 
@@
 \begin{figure}[h]
-\includegraphics[width=0.85\textwidth]{verification_outline2.png}
+\includegraphics[width=0.85\textwidth]{verification_outline3.png}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.85\textwidth]{optimization_outline2.png}
+\includegraphics[width=0.85\textwidth]{optimization_outline3.png}
 \centering
@@
 
-With respect to the proposed \textbf{automated verification} method, this thesis makes three main contributions: \textbf{first}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; \textbf{second}, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies; \textbf{third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.
+With respect to the proposed \textbf{automated verification} technique, this thesis makes three main contributions: \textbf{first}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; \textbf{second}, we evaluate the verification technique by comparing three state-of-the-art model checkers in five real case studies; \textbf{third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.
 
@@
 The choice of the active voice comes from the choice of the English language, which in the thesis studied was always presented in the active voice.
-The decision to use the English language stems from the possibility that the research may lead to further developments and activities, without the need for translation.
+The decision to use the English language stems from the possibility that the research may lead to further developments and activities,  in the possibility of reaching a larger number of people and helping in the internationalization of the Federal University of Amazonas.

### 2020-02-02 Tex/Old text/resumo.tex
thesis update

@@
 Em 2017, pela primeira vez, o número de pessoas sem acesso a eletricidade ficou abaixo de 1 bilhão, mas os dados quanto à universalização do acesso a energia ficaram aquém das metas globais.
-Particular atenção é dada aos sistemas isolados solares fotovoltaicos em áreas rurais ou onde a extensão da rede é inviável.
+Particular atenção é dada aos sistemas isolados solares fotovoltaicos em áreas rurais ou onde as elevadas extensões tornam a rede inviável.
 Ferramentas para avaliar ou dimensionar projetos de eletrificação estão disponíveis, mas elas são baseadas em simulações que não cobrem todos os aspectos do espaço de projeto.
-Por outro lado, o uso de métodos formais para modelar e validar qualquer tipo de sistema está crescendo com o tempo, principalmente para encontrar bugs em sistemas complexos de \textit{hardware} e \textit{software}: seu objetivo é estabelecer a corretude do sistema com rigor matemático.
+Por outro lado, o uso de métodos formais para modelar e validar qualquer tipo de sistema está crescendo com o tempo, principalmente para encontrar "bugs" em sistemas complexos de \textit{hardware} e \textit{software}: seu objetivo é estabelecer a corretude do sistema com rigor matemático.
 O uso de métodos formais em sistemas elétricos é um assunto recente, com pesquisas sendo publicadas apenas nos últimos quatro anos.
-Além disso, a síntese automatizada nunca foi usada antes para obter um ótimo dimensionamento de sistemas solares fotovoltaicos .
+Além disso, a síntese automatizada nunca foi usada antes para se obter um ótimo dimensionamento de sistemas solares fotovoltaicos.
 Esta tese marca duas conquistas principais: (1) a primeira aplicação de verificação de modelos de \textit{software} para verificar o projeto de um sistema isolado solar fotovoltaico, incluindo painel solar, controlador de carga, bateria, inversor e carga elétrica; e (2) uma abordagem confiável e automatizada para obter o dimensionamento ótimo de sistemas fotovoltaicos usando a síntese de programas onde cada componente e função de um sistema solar fotovoltaico é descrito, incluindo suas propriedades, e o modelo comportamental que representa o dimensionamento ótimo é sintetizado automaticamente.

### 2020-02-03 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 \begin{itemize}
-\item Formal Specification: During the formal specification phase, the engineer rigorously defines a system using a modeling language.
+\item Formal Specification.
+During the formal specification phase, the engineer rigorously defines a system using a modeling language.
 Modeling languages are fixed grammars which allow users to model complex structures from predefined types (that are rigorously defined).
-This process of formal specification is similar to the process of converting a word problem into algebraic notation and helps engineers to clearly define their problems, goals and solutions.
+This process of formal specification is similar to the process of converting a word problem into algebraic notation and helps researchers and engineers to clearly define their problems, goals and solutions.
 Several engineers who have used formal specifications claim that the clarity that this stage produces is a benefit in itself~\cite{Kling95}.
-\item Verification: As stated above, formal methods differ from other specification systems by their heavy emphasis on provability and correctness.
+\item Verification.
+As stated above, formal methods differ from other specification systems by their heavy emphasis on provability and correctness.
 In building a system using formal specification, the designer is actually developing a set of theorems about his system.
@@
 These tools can prove simple theorems, verify the semantics of theorems, and provide assistance for verifying more complicated proofs, with feedback about the trace of the error (in order to correct the system and the specification of it).
-\item Implementation: Once the model has been specified and verified, it is implemented by converting the specification into code.
+\item Implementation. Once the model has been specified and verified, it is implemented by converting the specification into code.
 
@@
 
-Here it is worth mentioning that the term "model" is not used here with its dictionary definition. In other words, the problem is not dealing with an abstraction of the actual system under study.
+Here it is worth mentioning that the term "model" is not used here with its dictionary definition.
+In other words, the problem is not dealing with an abstraction of the actual system under study.
+Therefore, model can be defined as a (usually finite-state) description of the system to be analyzed.
 
@@
 According to \cite{Roy}, a PV system is designed to supply electrical loads.
-This load can be of the Alternating Current (AC) type or the Direct Current (DC) type.
-The supply electricity can be needed either in daytime or nighttime (in particular cases, in both).
+These loads can be of the Alternating Current (AC) type or the Direct Current (DC) type.
+The electricity supply can be needed either in daytime or nighttime (most cases, in both).
 The most basic PV system can supply only in daytime.
-For the night hours or rainy days, batteries are needed, where power can be stored and used \cite{Gules}.
+For the night hours or rainy days, batteries are needed, where power can be stored for later use~\cite{Gules}.
 
@@
 \begin{itemize}
-\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
+\item Stand-alone systems, or off-grid systems, where the energy is generated and consumed in the same place and which does not interact with the main grid.
 Usually, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting systems, solar lanterns, and solar power plants;
-\item Grid-connected systems, where the solar PV system is connected to the grid.
-The grid-connected system can be either a grid-tied system, which can only feed power into the grid, with the result that this system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards.
-Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode;
-\item Solar PV hybrid systems: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
-In this type of system, the main objective is to bring more reliability into the overall system at an affordable cost by adding one or more energy sources.
+\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be: 
+\begin{itemize}
+\item Grid-tied system, which can only feed power into the grid, with the result that this system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards;
+\item Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode. 
+\end{itemize}
+\item Solar PV hybrid systems.
+In a hybrid system, other source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand.
+In this type of system, the main objective is to bring more reliability into the overall system at an affordable cost by adding distinct energy sources.
 \end{itemize}
@@
 
-There is a resource, called maximum power point tracking (MPPT), which is an electronic control mechanism that maintains the PV operating at a voltage that corresponds to maximum power voltage, which maximizes the transfer of power while avoiding loss of PV cells \cite{Pinho}.
+\subsection{MPPT}
+
+There is a resource, called maximum power point tracking (MPPT), which is an electronic control mechanism that maintains the PV panel operating at a voltage that corresponds to maximum power voltage, which maximizes the transfer of power while avoiding loss of PV cells \cite{Pinho}.
 This resource is found in modern PV systems and is strongly indicated due to its advantages.
@@
 \subsection{Unregulated Stand-alone PV Systems With DC Load }
+
 Usually this type of system is for low power applications, as defined by \cite{Roy}.
 The PV system is directly connected to the load without any MPPT controller, as shown in Fig.\ref{fig:unregSPV}.
-At night, the system will not provide any supply because of the absence of a battery.
+At night, the system will not provide any power because of the absence of a battery.
 
@@
 Usually systems with MPPT should have a battery; otherwise, the extra power will be wasted.
+This is an inadequate use of PV systems, but it can be found in isolated communities in Brazil.
 
@@
 
-Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}.
+This configuration have PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}.
 The battery is used to store the extra power from the PV system.
-A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module.
+A charge controller is necessary for this type of system because it insures that the battery ios charged with the correct voltage and current.
 Extra charging and deep discharging can reduce the battery life \cite{Kim}.
@@
 
-According to \cite{Pinho}, PV systems that are used to feed loads with low variation of consumption can be sized to operate without the controller.
+A PV systems that are used to feed loads with low variation of consumption can be sized to operate without the controller.
 This is known as a self-regulated stand-alone PV system with battery.
-However, PV panel voltage must be compatible with the battery voltage.
+However, the PV panel voltage must be compatible with the battery voltage.
 Usually, the bank of batteries is oversized in relation to the PV panel and to the load.
@@
 This system is similar to the previous one, but the AC load draws the power from the PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}.
-This solution has an cost increase because it has more equipment.
-However, AC availability has the advantage of permitting the use of a higher number of AC appliances in homes or consumer units.
-This configuration is this thesis since it is currently the most common system used specifically for remote rural areas of developing countries or areas where the grid extension is not feasible.
+This solution has a cost increase because it has more equipment.
+However, AC availability has the advantage of allowing the use of a higher number of AC appliances in homes or consumer units.
+This is the base configuration for this thesis since it is currently the most common system used specifically for remote rural areas of developing countries or areas where the grid extension is not feasible.
 %stand-alone systems are one the most used solutions, and 
@@
 
-In order to address different aspects of a project system and system's design, a lot of public domain and commercial software is available for the solar PV market.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, and to complex financial analysis software (with optimization).
+In order to address different aspects of a project system and system's design, many public domain and commercial software are available for the solar PV market.
+According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization).
 Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
@@
 The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year.
-To represent the system's physical characteristics, PVWatts requires values for six inputs: System DC size; Module type; Array type; System losses; Array tilt angle; Array azimuth angle.
+To represent the system's physical characteristics, PVWatts requires values for six inputs: system DC size; module type; array type; system losses; array tilt angle; array azimuth angle.
 
@@
 Department of Energy and National Renewable Energy Laboratory.
-According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications, and (also) to provide information for readers who do not plan to use the model, but want to learn about its capabilities.
+According to \cite{NRELBlair} and \cite{Cameron2008}, SAM is intended to help users to determine whether the model meets their project constraints/specifications.
 SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: project managers and engineers; financial and policy analysts; technology developers; and researchers.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Component models for stand-alone PV systems}
+\subsection{Component Models for Stand-alone PV Systems}
 \label{sec:model}
@@
 
-To increase their utility, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module).
+To increase their application usage, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module).
 For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
@@
 The PV modules are generally rated under standard test conditions (STC), which leads to the following specification by the manufacturers:  solar radiation of 1000 W/m$^{2}$, cell temperature of 25$^{o}$C, and solar spectrum of 1.5.
-The parameters required for the input of the PV modules are dependent on the meteorological conditions of the area to be serviced by photovoltaic solution.
+The parameters required for the input of the PV modules are dependent on the meteorological conditions of the area to be serviced by the photovoltaic solution.
 However, the climatic conditions are unpredictable due to the random nature of their occurrence \cite{Jakhrani}.
@@
 An overestimation of up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}.
+
 The growing demand for photovoltaics technologies has led to research into the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}.
@@
 This happens because numerical methods give approximate solutions to the nonlinear problems without searching for exact solutions.
-However, numerical methods are time consuming and need long term time series data, which is not available in developing countries.
-\cite{Jakhrani} used mixed methodology bringing analytical and numerical steps together.
-\cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation (essays).
-And \cite{Tian} used a mix of analytical and experimental methodology to establish the unknown parameters, but samples of the PV modules are necessary to perform some essays, when we use the experimental technique.
+However, numerical methods are time consuming and need long term time series data, which may not be available in developing countries.
+Reference~\cite{Jakhrani} used mixed methodology bringing analytical and numerical steps together.
+\cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation.
+And \cite{Tian} used a mix of analytical and experimental methodology to establish the unknown parameters, but samples of the PV modules are necessary to perform some tests, when we use the experimental technique.
 
 Therefore, a wide variety of models exists for estimation of the power output of PV modules (and $I-V$ or $P-V$ curves).
-However, this study will rely on the simplified 1-diode model, that was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested.
+However, this study will rely on the simplified 1-diode model, that was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% for the selected PV panels tested.
 In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation.
@@
 
-Equation \ref{eq:exp} is not explicit with regard to the key PV  parameters, it therefore needs to be rewritten in a different way.
+Equations \ref{eq:exp} and \ref{eq:Im} are not explicit with regard to the key PV  parameters, it therefore needs to be rewritten in a different way.
 A PV cell has a hybrid behavior, i.e., a current-source at the short-circuit point and a voltage-source at the open-circuit point \cite{Saloux}.
@@
 
-The derivative of Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell, thus generating the Equation \ref{eq:Vmderiv}.
+Equation \ref{eq:didv} is used to calculate the output voltage that corresponds to the maximum power operation condition of the cell, thus generating the Equation \ref{eq:Vmderiv}.
 
@@
 If the PV cells are in parallel, then there is a parallel array.
-There will therefore be a change in the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
+There will therefore be a change in the $ I_{ph} $ and $ I_{0} $ and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
 
@@
 
-\noindent where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Battery Storage Model }
+\noindent where $ V_{one panel} $ is the maximum voltage from Equation \ref{eq:Vmfinal}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Battery Storage Model}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Because of the fluctuating nature of the output delivered by the PV arrays, batteries are an essential part of a PV system.
-Thus, during the hours of sunshine, the PV system feeds the load directly and excess electrical energy is stored in the battery.
-During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery \cite{Mellit}.
+Thus, during the hours of sunshine, the PV system feeds the load directly and excess electrical energy is stored in the batteries.
+During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery bank~\cite{Mellit}.
 
@@
 
-Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
+Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the $C_{10}$ capacity.
 
@@
 
-It is worth mentioning that, specifically for PV systems used in Brazil, a Regulation (RN 493/2012), issued by the Brazilian Electricity Regulatory Agency (Aneel) establishes a minimum of 48 hours of battery autonomy for stand-alone solar PV systems, among others related definitions.
+It is worth mentioning that, specifically for PV systems used in Brazil, a Regulation (RN 493/2012), issued by the Brazilian Electricity Regulatory Agency (ANEEL) establishes a minimum of 48 hours of battery autonomy for stand-alone solar PV systems, among others related definitions.
 
@@
 
-The controller is a set of items (DC-DC converter, a MPPT and switches) and can be defined as the responsible for managing the energy flow to the PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
+The controller is a set of items (DC-DC converter, a MPPT algorithm and switches) and can be defined as the responsible for managing the energy flow to the PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
 According to \cite{Pinho}, controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.
 
-Currently, controllers with MPPT mechanisms are the most widely used nowadays,  and they maintain the PV operating at the stage of maximum power.
+Currently, controllers with MPPT algorithms are the most widely used nowadays,  and they maintain the PV operating at the stage of maximum power.
 
@@
 
-A DC-DC converter can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
-In addition, there is the Cuk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.
-
-For the Cuk converter, the relationship is expressed by Equation  \ref{eq:voutvin} as shown in \cite{Abdulateef}.
+A DC-DC converter used in these applications can either be step-up (Boost), step-down (Buck), or both increase and decrease (Buck-Boost) the voltage, as defined by \cite{Mahanta}.
+In addition, there is the Cúk converter, which is a Buck-Boost converter with an inverting topology \cite{Catherine}.
+
+For the Cúk converter, the relationship is expressed by Equation \ref{eq:voutvin} as shown in \cite{Abdulateef}.
 
@@
 
-As the MPPT definition and the equations to get the maximum power from the PV panels were described at the end of the PV panel modeling, what is important here is that Equation \ref{eq:voutvin} defines the relationship between the input signal, the efficiency of the controller and the output power.
+As the MPPT definition and the equations to get the maximum power from the PV panels were described at the end of the PV panel modeling, what is important here is that Equation \ref{eq:potcont} defines the relationship between the input signal, the efficiency of the controller and the output power.
 
 \subsubsection{The Inverter Model}
-As shown by \cite{Mellit}, PV arrays produce DC and therefore when the PV system contains an AC load, DC/AC conversion is required.
+As shown by \cite{Mellit}, PV arrays produce DC voltage and therefore when the PV system contains an AC load, DC/AC conversion is required.
 An inverter is a converter, where the power flows from the DC to the AC side, having DC voltage as input and producing AC voltage as output.
@@
 to the critical period method for solar energy system sizing~\cite{Pinho} and adopting a MPPT (Maximum Power Point Tracking) charge controller,
-which is the most common one in use. Firstly, we need to correct the energy consumption estimated for the load 
+which is the most common in use. Firstly, we need to correct the energy consumption estimated for the load 
 ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
@@
 
-Equation \ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted by the project.
+Equation \ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted in the project.
 
@@
 
-In this Section, all the background and theoretical base needed to understand the concepts, techniques, tools, and criteria used during the following Sections were presented.
+In this Chapter, all the background and theoretical base needed to understand the concepts, techniques, tools, and criteria used during the following Sections were presented.
 

### 2020-02-03 Tex/Old text/abstract.tex
thesis update

@@
 This thesis marks the achievement of two major goals: first, the application of software model checking to verify formally the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load; second, a sound, automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis.
-For the formal verification, we used case studies from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1.200 W, in order to evaluate the proposed approach and to compare  it with a specialized simulation tool.
+For the formal verification, we used case studies from real photovoltaic systems deployed in five different sites, ranging from $975$ W to $1,300$ W, in order to evaluate the proposed approach and to compare  it with a specialized simulation tool.
 Different verification tools are evaluated also, in order to compare performance and soundness.

### 2020-02-03 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 
-There is a resource, called maximum power point tracking (MPPT), which is an electronic control mechanism that maintains the PV panel operating at a voltage that corresponds to maximum power voltage, which maximizes the transfer of power while avoiding loss of PV cells \cite{Pinho}.
+There is a feature, called maximum power point tracking (MPPT), which is a control mechanism that maintains the PV panel operating at a voltage that corresponds to maximum power voltage, which maximizes the transfer of power while avoiding loss of PV cells \cite{Pinho}.
 This resource is found in modern PV systems and is strongly indicated due to its advantages.
@@
 \ref{fig:ivcurve}.
+Note that the MPPT point from the PV panel is illustrated, highlighting the maximum voltage $ V_{m} $ and maximum current $ I_{m} $ that a panel can produce.
 
@@
 \noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found on the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) at the location of the PV system.
+In this thesis is not considered shading, which can impact in the cell temperature as well.
 
@@
 Thus, during the hours of sunshine, the PV system feeds the load directly and excess electrical energy is stored in the batteries.
-During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery bank~\cite{Mellit}.
+During the night, or during a period with low solar irradiation, energy is supplied to the load from the battery bank ~\cite{Mellit}.
 
@@
 \label{eq:stor}
-Storage capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
-\end{equation}
-
-\noindent where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
+Storage \, capacity = \dfrac{N_{C}E_{load}}{DOD \eta _{b}}
+\end{equation}
+
+\noindent where $ DOD $ is the maximum possible depth of battery discharge, $ E_{load} $ is the average energy consumed by the load corrected according PV equipment efficiency, $ N_{C} $ is the largest number of continuous cloudy days of the area, and $ \eta_{b} $ is the efficiency of the battery.
 
 As an example of this formula's application, as shown in \cite{Abdulateef}, considering that an off-grid PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of battery discharge $DOD$ of $0.8$ and battery efficiency at $80\%$.
+In this thesis, the adopted efficiency of the battery will be considered constant and equal to $86\%$ as expected to lead-acid batteries~\cite{Pinho}.
 
@@
 Since the selected DC bus voltage is $48 V$, then the required Ampere-hours of the battery is $1173 Ah$ ($56.3 kWh/48$).
-If a single battery is 12 V and 350 Ah, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$).
+If a single battery is 12 V and 350 Ah, then four batteries are connected in series ($4 \times 350 Ah = 1400 Ah$) and a total of 16 batteries is defined (an array of 4 to reach the 48 V of the DC bus in four arrays to feed the $Ah$ demanded).
 
@@
 
-It is worth mentioning that, specifically for PV systems used in Brazil, a Regulation (RN 493/2012), issued by the Brazilian Electricity Regulatory Agency (ANEEL) establishes a minimum of 48 hours of battery autonomy for stand-alone solar PV systems, among others related definitions.
+It is worth mentioning that, specifically for PV systems used in Brazil, a Regulation (RN 493/2012), issued by the Brazilian Electricity Regulatory Agency (ANEEL) recommends a minimum of 48 hours of battery autonomy for stand-alone solar PV systems, among others related definitions.
 
@@
 The controller is a set of items (DC-DC converter, a MPPT algorithm and switches) and can be defined as the responsible for managing the energy flow to the PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage.
-According to \cite{Pinho}, controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.
+Controllers aim to protect the battery (or batteries) against the excessive charge and discharge, improving its lifetime.
 
@@
 \cite{Mellit} established that the controller allows the management of energy between the load and the battery.
-The input signals for the regulator model are the battery current ($ I_{br} $), the PV generator's voltage ($ V_{PV} $), the PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $).
-The outputs are battery current ($ I_{rb} $) and used current ($ I_{u} $).
+The input signals for the regulator model are the battery current, the PV generator's voltage, the PV generator's current, and battery voltage.
+The outputs are battery current and used current.
 
@@
 This can be done by using a switch with a hysteresis cycle, as illustrated in Fig.
-\ref{fig:controllerover}.
+\ref{fig:controllerover} in a on-off charge controller model.
 
@@
 \label{eq:poutcont}
-P_{in} = P_{out}
-\end{equation}
-
-Assuming that the efficiency of the controller ($ \eta_{c} $) is data provided by the manufacturer, from Equation \ref{eq:poutcont} it is possible to reach Equation \ref{eq:potcont}.
+P_{in} \eta_{c} = P_{out}
+\end{equation}
+
+Assuming that the efficiency of the controller ($ \eta_{c} $) is data provided by the manufacturer (ideally constant in this thesis), from Equation \ref{eq:poutcont} it is possible to reach Equation \ref{eq:potcont}.
 
@@
 
-The DC/DC converter should always operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
+The DC/DC converter tries always to operate in the MPPT to maximize the PV array efficiency and consequently increase the efficiency of the PV system, as defined in \cite{Yatimi}.
 
@@
 \label{eq:efficinv}
+P_{out} = \eta_{i} P_{in} = \eta_{i} V_{DC} I_{DC}
 \eta_{i} = \dfrac{P_{out}}{P_{in}} = \dfrac{V_{AC} I_{AC} cos\varphi}{V_{DC}I_{DC}}
@@
 
-\noindent where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be found from the inverter's data-sheet.
+\noindent where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery).
+%,  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be found from the inverter's data-sheet.
 
@@
 to the critical period method for solar energy system sizing~\cite{Pinho} and adopting a MPPT (Maximum Power Point Tracking) charge controller,
-which is the most common in use. Firstly, we need to correct the energy consumption estimated for the load 
+which is the most common in use. Firstly, we need to correct the daily energy consumption estimated for the load 
 ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), 
@@
 \label{eq:Ep}
-E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
-\end{equation}
-
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
+E_{p} = Solar\_Irradiation \times Panel\_Area \times \eta_{p} \times 1000,
+\end{equation}
+
+\noindent where the solar irradiation, also called solar exposure of insolation per day, is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
 the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents PV panel efficiency.
@@
 \label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
-\end{equation}
-
-\noindent where the variable $autonomy$ is a design definition and usually has a value ranging from $6$ to $48$ hours; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery depth of discharge (considered the maximum of 25\% here).
+C_{bank} = \dfrac{Eq.~\eqref{eq:stor}}{V_{system}},
+\end{equation}
+
+\noindent where %the variable $autonomy$ is a design definition and usually has a value ranging from $6$ to $48$ hours; 
+$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery depth of discharge.
 %

### 2020-02-03 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
 \begin{figure}[h]
-\includegraphics[width=1.0\textwidth]{optimalsizingprocess2g}
+\includegraphics[width=1.0\textwidth]{optimalsizingprocess3g}
 \centering
@@
 
-Examples of specification used by the proposed method include solar insolation (site dependent), house power demand, house  energy consumption, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specifications and prices from different manufacturers and models.
+Examples of specification used by the proposed method include insolation (site dependent), house power demand, house  energy consumption, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specifications and prices from different manufacturers and models.
 Design assumptions are considered additional project specifications.
@@
 The necessary technical information was collected from data sheet of each item.
-In addition, the price of each item was obtained from available market quotation, in US dollars.
-All the other currencies were converted to US dollars equivalents at the exchange rate of the day.
+In addition, the price of each item was obtained from available market quotation from internet, in US dollars.
+All the other currencies were converted to US dollars equivalents at the exchange rate of the day (May and June of 2019).
 
@@
 	\item Installation costs: these include delivery to the isolated community and the actual installation costs: $5$\% of total cost~\cite{Agrener2013};
-	\item Value of the discount rate or interest rate: $10$\%, a good rate, considering financial investments in developing countries;
+	\item Value of the discount rate or interest rate: $10$\%, a reasonable rate, considering financial investments in developing countries;
 	\item Annual operation and maintenance costs: based on past PV projects of similar size in the Brazilian Amazon, the sum of US\$ 289.64~\cite{Agrener2013} will be adopted.
-This cost includes battery replacement based on a lifetime of $4$ years for lead-acid batteries, plus inverters and controller replacement (every $10$ years).
-This means that there will be three battery bank and one inverter-controller replacement during the LCC analysis.
+This cost includes battery replacement based on a lifetime of $4$ years for lead-acid batteries, plus inverters and controller replacement (every $8$ years).
+This means that there will be four battery bank and two inverter-controller replacement during the LCC analysis.
 \end{itemize}
@@
 However, in order to enable a correct comparison, the curve load and the temperature were defined exactly the same as automated synthesis tools;
-	\item Battery autonomy is not a parameter that the user can set when using HOMER Pro. The tool will always meet the user requirement, i.e. the load curve, $365$ days a year;
+	\item Battery autonomy is not a parameter that the user can set when using HOMER Pro. The tool will always try to meet the system requirement, i.e. the load curve, $365$ days a year;
 	\item HOMER Pro does not have an item of equipment explicitly labeled charge controller.
-It uses a controller resource that can perform in two different ways, depending on optimization choice or user choice: load following or cycle charging~\cite{HOMER}.
-During the tests  'load following' controller was chosen: it produces only enough power to meet the demand~\cite{HOMER};
+It uses a controller resource that can operate in two different ways, depending on optimization choice or user choice: `load following' or `cycle charging'~\cite{HOMER}.
+During the tests  `load following' controller was chosen: it produces only enough power to meet the demand~\cite{HOMER};
 	\item A 5\% of capacity shortage was assumed, equivalent to 95\%  availability of the PV system.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Threats to validity}
+\section{Threats to Validity}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-02-03 Tex/Old text/chapters/chapterverification.tex
thesis update

@@
 Note that, on the one hand, although the input information is the same for all the techniques, automated validation is different in that it is possible to define the bound $k$ to restrict the space-design search.
-Among the possible inputs are: weather data at the location (temperature, solar irradiance, and solar insolation); system sizing information regarding specifications and configuration of PV panels, charge controller, inverter, batteries, DC bus  voltage; and requirements (battery autonomy, electric load demand, electric peak power demand, energy consumption, load curve, and AC voltage).
+Among the possible inputs are: weather data at the location (temperature, solar irradiance, and insolation); system sizing information regarding specifications and configuration of PV panels, charge controller, inverter, batteries, DC bus  voltage; and requirements (battery autonomy, electric load demand, electric peak power demand, energy consumption, load curve, and AC voltage).
 
@@
 With respect to the results presented, a project validated manually is just a piece of paper; simulation software produces success - fail information and can additionally present the optimized design if the system evaluated has some flaw, with graphics and reports; testing (whether laboratory or field) uses  measurement equipment and/or data from monitoring systems.
-Automated verification, as proposed in this thesis, presents success-fail information also, however the output is not graphic  (as will be shown in the  \autoref{chap:automatedverification}), is summarized in reports with details about the variables and states of the project that cause a project flaw (in this case,  where a design flaw is detected).
+Automated verification, as proposed in this thesis, presents success-fail information also, however the output is not graphic  (as will be shown), is summarized in reports with details about the variables and states of the project that cause a project flaw (in this case,  where a design flaw is detected).
 
 \begin{figure}[h]
-\includegraphics[width=1.0\textwidth]{PVprojectvalidation2g}
+\includegraphics[width=1.0\textwidth]{PVprojectvalidation3g}
 \centering
@@
 
-Starting at his point, it will be shown how the proposed automated verification of stand-alone solar PV systems functions.
+Starting at this point, it will be shown how the proposed automated verification of stand-alone solar PV systems functions.
 
@@
 
-\textbf{Assumption:} The day is divided into two parts (representing presence or absence of PV generation, based on historical data from the location), considering average temperature and solar irradiance (for every hour of the day) and  annual solar insolation (per day).
+\textbf{Assumption:} The day is divided into two parts (representing presence or absence of PV generation, based on historical data from the location), considering average temperature and solar irradiance (for every hour of the day) and  annual insolation (per day).
 
@@
 
-\textbf{Premise:} Temperature, solar irradiance, and solar insolation data is available pertaining to the location where the solar PV system will be used.
+\textbf{Premise:} Temperature, solar irradiance, and insolation data is available pertaining to the location where the solar PV system will be used.
 
@@
  \ENSURE design sizing check; FAIL with counterexample to improve the design; SUCCESS, saying that the project has no flaws
-  \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\
+  \STATE $declare \, min \, and \, max \, solar \, irradiance[24h], \, and \, temperature[24h]$\\
   \STATE $declare \, case \, studies \, details: \, sizing \, and \, manufacturers \, data $ \\
@@
 \begin{itemize}
-\item The '\# include' preprocessor directive is not used, despite being very common in the C language, which allows the use of C language libraries, including the mathematical one;
-\item In the absence of the '\# include' directive, it was necessary to create specific mathematical functions at the proposed code in order to calculate the exponential 'exp(x)' or $e^{x}$, and natural logarithm 'log(x)' functions, used for the solar PV model;
-\item There is no '\# define' preprocessor directive. Therefore, global variables were used to replace it;
-\item The macro 'assert (expression);' must be replaced by 'if (!expression) \{ \_ \_ VERIFIER\_ error();\}'
-\item The macro 'assume (expression);' must be replaced by '\_ \_ VERIFIER\_ assume(expression)';
+\item The `\# include' preprocessor directive is not used, despite being very common in the C language, which allows the use of C language libraries, including the mathematical one;
+\item In the absence of the `\# include' directive, it was necessary to create specific mathematical functions at the proposed code in order to calculate the exponential `$exp(x)$' or $e^{x}$, and natural logarithm `$log(x)$' functions, used for the solar PV model;
+\item There is no `\# define' preprocessor directive. Therefore, global variables were used to replace it;
+\item The macro `assert (expression);' must be replaced by `if (!expression) \{ \_ \_ VERIFIER\_ error();\}';
+\item The macro `assume (expression);' must be replaced by `\_ \_ VERIFIER\_ assume(expression);';
 \item It is not possible to use the \# if, \# else, \# elif, \# endif or \# ifdef, \# ifndef commands.
@@
 
-For all case studies, the minimum battery state of charge was defined at $75$\%, i.e.
-with a DOD maximum of $25$\%, which is common to lead-acid batteries (adopted as standard here), and the AC voltage from the inverter at $127$ V (Brazilian standard).
+For all case studies, the minimum battery state of charge was defined at $75$\%, and the efficiency of $86$\%, which is common to lead-acid batteries (adopted as standard here), and the AC voltage from the inverter at $127$ V (Brazilian standard).
+According with the evaluated local of the PV systems installation, the considered insolation for the worst month is $3.8 kWh/m^{2}$ per day.
 
@@
 \hline
-Power peak (W)& 342  & 253  & 263 & 322 & 814 \\
+Load power peak (W)& 342  & 253  & 263 & 322 & 814 \\
 \hline
-Power surge (W)& 342 & 722 & 732 & 896 & 980\\
+Load Power surge (W)& 342 & 722 & 732 & 896 & 980\\
 \hline
@@
 
-In the houses that use a $700$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC could not reach an error in any of the four houses and the execution time took from $04$ m $27$ s to $05$ m $08$ s.
+In the houses that use a $975$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC could not reach an error in any of the four houses and the execution time took from $04$ m $27$ s to $05$ m $08$ s.
 Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for house $1$, with the absence of fail at the end of the analysis.
@@
 
-In the 700 W PV systems (house $1$, house $2$, house $3$, and house $4$), the tool could not reach an error in any of the four houses in an execution time of $18$ m $36$ s to $19$ m $02$ s.
+In the $975$ W PV systems (house $1$, house $2$, house $3$, and house $4$), the tool could not reach an error in any of the four houses in an execution time of $18$ m $36$ s to $19$ m $02$ s.
 
@@
 Finally, the CPAchecker tool presented some different results.
-Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the $700$ W systems (house $1$, house $2$, house $3$, and house $4$).
+Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the $975$ W systems (house $1$, house $2$, house $3$, and house $4$).
 
@@
 
-Therefore, in order to perform a limited simulation and not exceed the values of each component (for example, the total power of the PV array under evaluation), the 'search space' must be used for sizing instead of the 'HOMER Optimizer'.
+Therefore, in order to perform a limited simulation and not exceed the values of each component (for example, the total power of the PV array under evaluation), the `search space' must be used for sizing instead of the `HOMER Optimizer'.
 This is done on the menu of each component inputted in the schematic of the tool.
 
-The PV panels and batteries: simulation of a particular capacity for PVs and batteris is possible using the 'search space' for sizing instead of the 'HOMER Optimizer'.
+The PV panels and batteries: simulation of a particular capacity for PVs and batteris is possible using the `search space' for sizing instead of the `HOMER Optimizer'.
 It is possible either to aggregate all the PV panels as a single PV component, in which case, the search space must vary from 0 to 1, i.e.
@@
 
-As part of the comparison proposed, four $700$ W PV systems (houses $1$, $2$, $3$ and $4$) were evaluated by HOMER Pro (EQ2).
+As part of the comparison proposed, four $975$ W PV systems (houses $1$, $2$, $3$ and $4$) were evaluated by HOMER Pro (EQ2).
 The simulation results showed that for each of the sized systems, HOMER Pro concluded that no viable solution was found with the components inputted in the schematic.
@@
 Fig.~\ref{fig:homersimuh2yes} shows that a configuration with higher battery capacity (3 strings of 2 batteries each, 2S-3P, of 220 Ah; instead of 2 strings of 2 batteries each as in the original sized system) can solve the problem of house 2.
-The same is true of the other three houses of $700 W$, when improved battery capacity is presented by HOMER Pro as an optimal solution.
+The same is true of the other three houses of $975 W$, when improved battery capacity is presented by HOMER Pro as an optimal solution.
 
@@
 
-Results diverged for houses $1$, $2$, $3$ and $4$ w.r.t.
-the proposed approach: the automated evaluation shows there is no project flaws, but simulation demanded improvement of battery capacity (adding one more string of batteries to the system).
+Results diverged for houses $1$, $2$, $3$ and $4$ with respect to the proposed approach: the automated evaluation shows there is no project flaws, but simulation demanded improvement of battery capacity (adding one more string of batteries to the system).
 

### 2020-02-03 Tex/Old text/chapters/conclusion.tex
thesis update

@@
 
-We analyzed five case studies of real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W (inverter specification), and the results of three state-of-the-art verification engines (ESBMC, CBMC, and CPAchecker).
+We analyzed five case studies of real PV systems deployed in five different sites, ranging from $975$ W to $1,300$ W (inverter specification), and the results of three state-of-the-art verification engines (ESBMC, CBMC, and CPAchecker).
 Although the verification method that we proposed takes longer than the simulation methods, it can avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.

### 2020-02-04 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool that executes detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
-Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, solar insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
+Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
 Variations in wind speed and in load within each time step are factored into the performance predictions.
@@
 \begin{itemize}
-\item $I_{ph}$ is the photocurrent delivered by the constant current source; 
+\item $I_{ph}$ is the photocurrent delivered by the constant current source. $I_{ph}$ is usually approximated to the reference short-circuit current of the PV panel ($I_{sc}$); 
 \item $ I_{0} $ is the reverse saturation current corresponding to the diode; 
@@
 % \cite{Copetti}.
+Batteries with modern technologies, as nickel–cadmium battery (NiCd), nickel metal hydrate (NiMH), lithium-ion (Li-ion), among others, although they have advantages (greater efficiency, longer life-time, greater depth of discharge), they are generally not economically viable in most PV systems.
+Table~\ref{table:batteries} shows the main features of some rechargeable batteries that are available at the market nowadays.
+
+\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+\renewcommand{\arraystretch}{1.3}
+\caption{Technical data for some rechargeable batteries. Adapted from \cite{Pinho}}
+\label{table:batteries}
+\centering
+\begin{tabular}{c | c | c | c | c }
+\hline
+\hline
+Technology & \makecell{Efficiency \\ \%} & \makecell{Life Time \\ years} & \makecell{Number of \\ Cycles} & \makecell{Operational \\ Temperature}\\
+\hline
+Lead-acid (Pb-acid) & 80-90 & 3-20 & 250-500 & -15 to +50 \\
+\hline
+Nickel–cadmium (NiCd) & 60-70 & 3-25 & 300-700 & -45 to +50 \\
+\hline
+Nickel metal hydrate (NiMH) & 80-90 & 2-5 & 300-600 & -20 to +60 \\
+\hline
+Lithium-ion (Li-ion) & 90-95 & - & 500-1000 & -20 to +60 \\
+\hline
+\hline
+\end{tabular}
+\end{table}
 

### 2020-02-04 Tex/Old text/chapters/chapterverification.tex
thesis update

@@
 
-It is important to emphasize that the theoretical basis of the subject presented in this chapter was discussed in Chapter 1, ~\nameref{chap:background}.
-In addition, knowledge of the literature is essentila to aid understanding.
+It is important to emphasize that the theoretical basis of the subject presented in this chapter was discussed in Chapter 2, ~\nameref{chap:background}.
+In addition, knowledge of the literature is essential to aid understanding.
 
@@
 In contrast, the outputs are not equal: design-space coverage and the information presented as result.
-Design-space coverage was shown in chapter \nameref{chap:background} to be the most complete when performed by automated verification, event using the bound $k$ to restrict the search, it not being necessary to unbound the system completely in order to discover a design flaw.
+Design-space coverage was shown in chapter 2 (\nameref{chap:background}) to be the most complete when performed by automated verification, event using the bound $k$ to restrict the search, it not being necessary to unbound the system completely in order to discover a design flaw.
 Moreover, testing and simulation depend on the test vector used as input to evaluate the system.
@@
 % caused by the state explosion inherent of the technique, 
-every 24 h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where PV generation is possible, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes the rest of the day (with no PV generation), when the batteries are required to feed the house.
+every 24 h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one where PV generation is possible, during daylight, with a duration in hours depending on each site (but dependent on the sun and weather conditions); and (b) one that includes the rest of the day (with no PV generation), when the batteries are required to supply energy to the house.
 
@@
 \begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|c|}
+\begin{tabular}{c|c|c|c|c|c}
 \hline
@@
 \hline
-Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
+Charge Controller & \multicolumn{5}{c}{With MPPT of 150 V/35 A}\\
 \hline
-Inverter & \multicolumn{4}{|c|}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
+Inverter & \multicolumn{4}{c}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
 \hline
@@
 \hline
-Load curve (W) & \multicolumn{5}{|l|}{\makecell{House 1: 118-118-118-46-46-46-95-95-170-170-296-242-242-95-95-95-95-95-342-288-288-288-288-118\\House 2: 136-136-136-136-136-136-67-67-184-184-184-184-184-67-67-67-67-67-253-253-253-253-253-136\\House 3: 113-113-113-113-113-113-67-67-217-97-97-97-97-97-97-97-97-97-263-113-113-113-113-113\\House 4: 207-207-207-135-135-135-66-66-161-161-233-253-248-66-66-66-66-66-302-317-322-302-302-207\\House 5: 45-16-16-16-16-16-0-0-0-72-72-222-150-150-0-0-72-72-814-814-814-742-742-16}}\\
+Load curve (W) & \multicolumn{5}{l}{\makecell{House 1: 118-118-118-46-46-46-95-95-170-170-296-242-242-95-95-95-95-95-342-288-288-288-288-118\\House 2: 136-136-136-136-136-136-67-67-184-184-184-184-184-67-67-67-67-67-253-253-253-253-253-136\\House 3: 113-113-113-113-113-113-67-67-217-97-97-97-97-97-97-97-97-97-263-113-113-113-113-113\\House 4: 207-207-207-135-135-135-66-66-161-161-233-253-248-66-66-66-66-66-302-317-322-302-302-207\\House 5: 45-16-16-16-16-16-0-0-0-72-72-222-150-150-0-0-72-72-814-814-814-742-742-16}}\\
 \hline
@@
 \begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{c|c|c|c|c}
 \hline
 \hline
-\multicolumn{5}{|c|}{Model Checker (SAT/UNSAT: time and message)}\\
+\multicolumn{5}{c}{Model Checker (SAT/UNSAT: time and message)}\\
 \hline
@@
 \hline
-House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{$\leq$ 1 sec \\(SAT Line 337)} & \makecell{6 sec \\ (SAT line 337)}\\
+House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT)} & \makecell{$\leq$ 1 sec \\(SAT)} & \makecell{6 sec \\ (SAT)}\\
 \hline
@@
 
-Detailed diagrams, flowcharts and algorithms with pseudo-code were presented in support of the proposed work and to aid the understanding.
+Detailed diagrams, flowcharts and algorithm with pseudo-code were presented in support of the proposed work and to aid the understanding.
 Additionally, the assumptions adopted in relation to the automated verification and simulation software were listed.
@@
 
-A comparison with a specialized simulation tool was also performed, although some of the tool's limitations, mainly related to not allow allowing battery autonomy setup or oversizing the battery bank by HOMER Pro, restricted the comparison between automated verification tools and simulation tools.
+A comparison with a specialized simulation tool was also performed, although some of the tool's limitations, mainly related to not allowing battery autonomy setup or oversizing the battery bank by HOMER Pro, restricted the comparison between automated verification tools and simulation tools.
 

### 2020-02-04 Tex/Old text/chapters/conclusion.tex
thesis update

@@
 In particular, we described two scientific methods (or techniques) from computer science, which were used to tackle issues in PV systems, such as validation over time and sizing optimization.
-A list of future contributions concludes the study, although this list might foster the creation of a research group to investigate model checking techniques for electrical systems (and not only renewable sources as has been the focus here).
+A list of future contributions concludes the study, although this list might foster the creation of a research group to investigate model checking techniques for electrical systems and not only renewable sources as has been the focus here.
 
@@
 
-In the area of automated sizing, the author plans to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the State of Amazonas (Brazil), and to validate some cases with deployed PV systems in isolated communities.
+In the area of automated sizing, we plan to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the State of Amazonas (Brazil), and to validate some cases with deployed PV systems in isolated communities.
 

### 2020-02-04 Tex/Old text/chapters/introduction.tex
thesis update

@@
 
-Chapter '~\nameref{chap:background}' presents the theoretical basis of formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.
+Chapter `~\nameref{chap:background}' presents the theoretical basis of formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.
 
-Chapter '~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new method of PV systems validation.
+Chapter `~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new method of PV systems validation.
 
-Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science and its application to obtain the optimal sizing of stand-alone solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with a  simulation tool and from data collected from fieldwork.
+Chapter `~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science and its application to obtain the optimal sizing of stand-alone solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with a  simulation tool and from data collected from fieldwork.
 
-In the '~\nameref{chap:conclusions}' we present the main contributions, future work directions and concluding remarks.
+In the `~\nameref{chap:conclusions}' we present the main contributions, future work directions and concluding remarks.
 
@@
 
+~\autoref{chap:data} presents detailed data from all the equipment used during the experimental part of the thesis, covering information from data-sheet, electrical features, brands and models.
+
 It is worth mentioning that we decided, with the consent of the coordination of the graduate program, that this document would be written in the active voice and entirely in English.

### 2020-02-04 Tex/Old text/chapters/conclusion.tex
thesis update

@@
 Our method, using model checking, can perform a size check and verify, over time, whether a PV system meets electrical requirements.
-We showed that there are various possible ways to perform that validation, such as testing, laboratory measuring, or even simulation.
-However, we developed an algorithm and a tool using model checking that was feasible and effective.
+There are various possible ways to perform that validation, such as testing, laboratory measuring, or even simulation.
+However, we developed an algorithm and a tool using model checking that is feasible and effective.
 Our results were supported by case studies, by data gathered from the field, and by interviews with PV owners.
@@
 %
-In the comparison among verification engines, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented a better performance than CBMC (around four times faster), used less RAM than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB for CBMC and 19.2GB for CPAchecker).
+In the comparison among verification engines, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented a better performance than CBMC (around four times faster), used less RAM than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB for CBMC and 19.2GB for CPAchecker) as expected and explained in Section~\ref{sec:ESBMC}.
 All our experimental results are sound since the PV owners and the monitoring system validated the possible flaws that the system could present in the field.

### 2020-02-04 Tex/Old text/chapters/introduction.tex
thesis update

@@
 Nothing more than a niche market only a few years ago, solar PV systems have become a mainstream electricity provider, with an  approximate 50\% increase (or 100.9 GW)in new PV installations from 2016 to 2017~\cite{EPIA}, although this growth is not driven by stand-alone systems.
-
 However, in order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed.
@@
 
-Simply put, we aim to present new techniques that will ensure that you have good designs of stand-alone solar PV systems, that do not cause a drop in energy supply, and that these systems are designed at the lowest possible cost.
+\textbf{Simply put, we aim to present new techniques that will guarantee a good design of stand-alone solar PV systems, that do not cause a drop in energy supply after deployment, and that these systems are designed at the lowest possible cost.}
 

### 2020-02-04 Tex/Old text/abbreviations.tex
thesis update

@@
     \vspace{0.9cm}
-    \textbf{List of Abbreviations, Units and NomenclatureList of Abbreviations, Units and Nomenclature}
+    \textbf{List of Abbreviations, Units and Nomenclature}
 \end{center}
@@
 DC Direct current \\
-$DOD$ Depth of discharge ($DOD=1-SOC$) \\
+$DOD$ Maximum depth of discharge ($DOD=1-SOC$), considering the battery autonomy \\
+$DOD_{day}$ Depth of discharge for one day \\
 $E_{consumption}$ Energy consumption \\
@@
 $E_{p}$ Energy produced by one panel \\
+EQ Experimental Question \\
 ESBMC Efficient SMT-based Bounded Model Checker \\
@@
 HDI Human Development Index \\
+IEA International Energy Agency \\
 IRR  Internal Rate of Return \\
 $I$ Current \\
+$Insolation$ Also called solar irradiation or solar exposure ($kWh/m^{2}$ per day) \\
 $I_{0}$ Reverse saturation current \\
@@
 $ I_{DC} $ Current required by the inverter from the DC source \\
+$I_{min,DCbus}$ Minimum DC bus current to be considered during sizing \\
 $ I_{in} $ Input current \\
@@
 $I_{pv}$ Current from the PV system \\
+$I_{total,PVpanels}$ Total current supplied by the PV panels array \\
 $ I_{sc} $ Short-circuit current \\
@@
 LCOE Levelized Cost of Energy \\
-LLP  Loss of Load probability \\
-LOLP Loss of Load Probability \\
+LLP  (or LPLP) Loss of Load probability \\
 LPSP Loss of Power Supply Probability \\
@@
 P Power \\
+$P_{min,panels}$ Minimum power that the PV panels must supply, used during PV sizing \\
 $P_{in}$ Input power \\
@@
 SAT When the verification tool returns a failure \\
+SDGs Sustainable Development Goals \\
 SMT Satisfiability module theories \\
@@
 $ V_{system} $ DC voltage of the bus \\
+$V_{total,PVpanels}$ Total voltage supplied by the PV panels array \\
 $V_{T}$ Thermal voltage ($ V_{T}=k_{B}T/q $) \\

### 2020-02-04 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 \subsection{ESBMC}
+\label{sec:ESBMC}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the fraction of discharge, i.e., $ DOD=1-SOC $.
+However it is worth to separate the $DOD$ into two different definitions when the battery autonomy is bigger than one day ($24$ hours).
+Therefore, here in this thesis, the definition given here is for maximum $DOD$.
+When we deal with daily $DOD$ we will call it of $DOD_{day}$, and obviously the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
 
@@
 As an example of this formula's application, as shown in \cite{Abdulateef}, considering that an off-grid PV system is intended to supply $1.5 kW/48 V$ for 24 hours ($=36 kWh$); The largest number of continuous cloudy days in the selected site is about 1 day; For a maximum depth of battery discharge $DOD$ of $0.8$ and battery efficiency at $80\%$.
+
 In this thesis, the adopted efficiency of the battery will be considered constant and equal to $86\%$ as expected to lead-acid batteries~\cite{Pinho}.
@@
 controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
-%
+
 \begin{equation}
 \label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
-\end{equation}
-
-We also need to estimate the energy that can be produced by each panel, called $E_{p}$, in Watt-hour ($Wh$), defined as
-%
-\begin{equation}
-\label{eq:Ep}
-E_{p} = Solar\_Irradiation \times Panel\_Area \times \eta_{p} \times 1000,
-\end{equation}
-
-\noindent where the solar irradiation, also called solar exposure of insolation per day, is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
-the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents PV panel efficiency.
-The total minimum number of solar panels needed ($N_{TPmin}$) is computed as
-%
-\begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
-\end{equation}
-
-Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) is respectively given by
-%
-\begin{equation}
-\label{eq:NPSmin}
-\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
-\end{equation}
-%
-\begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
-\end{equation}
-%
-\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ 
-is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and 
-$V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering 
-the maximum and minimum operational temperature, respectively; 
-$P_{total}$ is the total power demanded from the PV system and 
-$P_{max,ref}$ is the power supplied by one PV panel in $Watts$.
-As for batteries, we must first define the total capacity of the battery bank, which can be described as
-%
+E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \times \eta_{c} \times \eta_{i} }.
+\end{equation}
+
+We must estimate the total power that will be demanded from the PV panels, as defined by Eq. ~\eqref{eq:Pminpanel}.
+
+\begin{equation}
+\label{eq:Pminpanel}
+P_{min,panels} = \dfrac{1.25 \times E_{corrected}}{Insolation},
+\end{equation}
+
+\noindent where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
+A factor of $20$\% for losses is considered, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
+
+In one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
+In other hand, the arrangement, if in series or parallel connections, it will depends on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as shown in Eq.~\eqref{eq:Icmin} and
+\eqref{eq:Vcmin}.
+
+\begin{equation}
+\label{eq:Icmin}
+I_{c} \geq I_{total,PVpanels},
+\end{equation}
+
+\begin{equation}
+\label{eq:Vcmin}
+V_{c} \geq V_{total,PVpanels},
+\end{equation}
+
+Related to the batteries, the energy $E_{b}$ to be demanded by the PV system, in order to meet the load requirements, is defined by Eq.~\eqref{eq:Ebat}.
+
+\begin{equation}
+\label{eq:Ebat}
+E_{b} = \dfrac{Autonomy \times E_{corrected}}{DOD},
+\end{equation}
+
+\noindent where $Autonomy$ is a number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries.
+
+In order to define the $DOD_{day}$ we use Eq.~\eqref{eq:DODday}.
+Moreover, the minimum current from DC bus is defined by Eq.~\eqref{eq:Idcbus}.
+This equation is important to define the battery arrangement of the system (series and parallel connections).
+
+\begin{equation}
+\label{eq:DODday}
+DOD_{day} = \dfrac{E_{corrected} \times 100}{E_{b}},
+\end{equation}
+
+\begin{equation}
+\label{eq:Idcbus}
+I_{min,DCbus} = \dfrac{E_{b}}{V_{system}},
+\end{equation}
+
+\noindent where $V_{system}$ is the DC voltage of the bus. As for batteries, we must first define the total capacity of the battery bank, which can be described as
+
 \begin{equation}
@@
 
-\noindent where %the variable $autonomy$ is a design definition and usually has a value ranging from $6$ to $48$ hours; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery depth of discharge.
+%\noindent where %the variable $autonomy$ is a design definition and usually has a value ranging from $6$ to $48$ hours; 
+%$ V_{system} $ is the DC voltage of the bus.
 %
-Second, the total number of batteries is computed as
-
-\begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
-\end{equation}
 
@@
 
-The short circuit reference information from the manufacturer's solar panel must be corrected 
-to the cell temperature because field temperature is higher than  nominal or laboratory temperature, 
-and the PV system is temperature dependent, as shown by Equation~\eqref{eq:iscamb}. 
-%
+The short circuit reference information from the manufacturer's solar panel must be corrected   to the cell temperature because field temperature is higher than  nominal or laboratory temperature, and the PV system is temperature dependent, as shown by Equation~\eqref{eq:iscamb}.
+
 \begin{equation}
@@
 The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin}.
-%
+
 \begin{equation}
@@
 
-The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that 
-the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the 
-output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that 
-the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), 
-where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; 
-$MAX_{AC,ref}$ is the peak power that the inverter can support.
-%
+The inverter sizing check is performed by means of three equations.
+Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
+Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
+Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
+
 \begin{equation}
@@
 Moreover, it is important to verify the compatibility between charge controller and inverter, because there are some models that are not compatible with equipment from other manufacturers.
+Moreover, it is important to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side.
+Then the controller can be overcharged during this operation and to burn.
 

### 2020-02-04 code/PVcode_rev3_house1.c
code update

@@ -1,0 +1,519 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev3 - FEB 2020
+ Description : New sizing code Prof Wilson (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE3 
[…]

### 2020-02-04 code/PVcode_rev3_house2.c

@@ -1,0 +1,520 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev3 - FEB 2020
+ Description : New sizing code Prof Wilson (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE3 
[…]

### 2020-02-04 code/PVcode_rev3_house3.c

@@ -1,0 +1,520 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev3 - FEB 2020
+ Description : New sizing code Prof Wilson (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE3 
[…]

### 2020-02-04 code/PVcode_rev3_house4.c

@@ -1,0 +1,520 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev3 - FEB 2020
+ Description : New sizing code Prof Wilson (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE3 
[…]

### 2020-02-04 code/PVcode_rev3_house5.c

@@ -1,0 +1,520 @@
+/*
+ ============================================================================
+ Name        : PVcode.c
+ Author      : Alessandro
+ Version     : rev3 - FEB 2020
+ Description : New sizing code Prof Wilson (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int PACref = 700, MAXACref = 1600, NBS = 2, NBP = 2, capacity = 220, autonomy = 48, NPP = 1, NPS = 3, VC = 24, Vsystem = 24;
+// int bankcapacity = 440; //(capacity*NBP);
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12;
+// int DODmax = 50, DODday = 25;
+// float Vbulk = 28.80; //(14.40*NBS);
+// float Vfloat = 26.40; //(13.20*NBS);
+// float nb = 0.86;
+// float ni = 0.93;
+// int VoutAC = 110, VinDC = 24, VAC = 127;
+//HOUSE3 
[…]

### 2020-02-05 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
 In this Chapter, we detail methodology used for optimal sizing of stand-alone solar PV systems, more specifically using model checking.
-Diagrams, flowcharts, and algorithms support and explain the solutions.
+Diagrams, flowcharts, and algorithm give support and explain the solutions.
 
@@
 Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
-and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
+and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc -benchmark filename.c} version 1.8 in a configuration as bound model checking and with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
 Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
@@
 \begin{scriptsize}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{c|c|c|c|c}
 \hline

### 2020-02-05 Tex/Old text/chapters/chapterverification.tex
thesis update

@@
 
-The verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
+The verification engine CPAchecker 1.8 was used in a configuration of bound model checking\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc -benchmark filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}.
 An alternative CPAchecker configuration was also tried, using the BMC k-induction option, but the results show no improvement in performance or soundness (so it is not reported here).
@@
 \hline
-\multicolumn{5}{c}{Model Checker (SAT/UNSAT: time and message)}\\
+\multicolumn{5}{c}{Model Checker (SAT/UNSAT: time, message, and used memory)}\\
 \hline
@@
 \hline
-House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 08 s \\(UNSAT)} & \makecell{19 m 02 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+House 1 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT) \\ 44 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.36 s \\ (SAT) \\ 173 MB}\\
 \hline
-House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 27 s \\(UNSAT)} & \makecell{18 m 59 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+House 2 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT)\\ 44 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.34 s \\ (SAT)\\174 MB}\\
 \hline
-House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 07 s \\(UNSAT)} & \makecell{18 m 39 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+House 3 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT)\\ 45 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.38 s \\ (SAT)\\ 174 MB}\\
 \hline
-House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 37 s \\(UNSAT)} & \makecell{18 m 36 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
+House 4 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT)\\ 45 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.46 s \\ (SAT)\\ 176 MB}\\
 \hline
-House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT)} & \makecell{$\leq$ 1 sec \\(SAT)} & \makecell{6 sec \\ (SAT)}\\
+House 5 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT)\\ 45 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.19 s \\ (SAT)\\ 174 MB}\\
 \hline

### 2020-02-05 Tex/Old text/chapters/chapterverification.tex
thesis update

@@
 \hline
-Load Power surge (W)& 342 & 722 & 732 & 896 & 980\\
+Load power surge (W)& 342 & 722 & 732 & 896 & 980\\
 \hline
@@
 Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer EQ2. 
-Note that an UNKNOWN result from the proposed verification engines does not mean that a failure was found nor that the verification was successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.
+Note that an UNKNOWN result from the proposed verification engines does not mean that a failure was found nor that the verification was successful: it indicates that the verification engine led to an \textit{out of memory} situation and the design-state explosion was a issue during the run-time.
+It worth to mention that none of the verifiers and solvers reached the \textit{time out} limit during the experimental evaluation.
 
@@
 \end{tabular}
+\\Caption: (SAT): wrong sizing of PV panels (minimum total installed power not satisfied).
 \end{scriptsize}
@@
 
-Using ESBMC with Boolector led to an out of memory situation in all the case studies.
+Using ESBMC with Boolector led to an 'out of memory' situation in all the case studies.
 This result was obtained in less than six minutes of execution, i.e.
@@
 
-However, running the same version of ESBMC, using 'incremental SMT' solving with Z3, the experimentation results returned were conclusive (SAT or UNSAT) in all the case studies.
+However, running the same version of ESBMC, using 'incremental SMT' solving with Z3, the experimentation results returned were conclusive (SAT) in all the case studies.
+Moreover, the flaw identified was the same for all cases: the sized total PV panels power was not enough to meet the design requirements of the system (energy and power load demand).
+Put it simple, the designed PV systems will fail when deployed at the field.
+Based on the fact that the tool stops when the first flaw is identified, the rest of the validation procedure was not even reached.
+Worth to mention that if we remove the PV panels validation from the tool, the next flaw identified during experimentation was the battery array sizing (not enough to meet the design requirements as well).
 
-In the houses that use a $975$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC could not reach an error in any of the four houses and the execution time took from $04$ m $27$ s to $05$ m $08$ s.
-Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for house $1$, with the absence of fail at the end of the analysis.
-The file produced by ESBMC is $160$ lines long and $12.4$ kB in size.
-The author highlighted the result, which shows that no design flaws were found (SAT result or SUCCESS) within the bound $k$ of $100$.
+In the houses that use a $975$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC reached an error in any of the four houses and the execution time took less than $01$ s.
+Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for house $1$, with the FAIL identified.
+The author highlighted the result, which shows that the design flaw was found (SAT result or SUCCESS) within the bound $k$ of $100$, when a expected PV panels total power of $1,636.76$ W is expected and the sized system has only $975$ W.
+This flaw is related to Eq.~\eqref{eq:Pminpanel}.
 
 \begin{figure}[h]
-\includegraphics[width=0.65\textwidth]{esbmcverifh1.png}
+\fbox{\includegraphics[width=1.0\textwidth]{esbmcverifh1.png}}
 \centering
-\caption{Report generated by ESBMC (with Z3 solver) after validation of House 1.}
+\caption{Report generated by ESBMC (Z3 solver) after validation of House 1.}
 \label{fig:esbmcverifhouse1}
@@
 
-However the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current required by the PV system, indicating that the equipment chosen is not suited to meet the design requirements.
-
-Fig.~\ref{fig:esbmcverifhouse5} shows the report generated by the tool, with red highlights for the result, showing the incompatibility of the sized charge controller and the minimum necessary.
-The report generated by ESBMC was a text file of $14.1$ kB in size, $353$ lines in length.
-This verification took less than $1$ s to perform, as indicated in the last line of Table~\ref{cases}, faster than the previous analysis because ESBMC stops during the sizing check, line $3$ of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of the verification code.
+Related to the $1,300$ W PV system (house $5$), the same fail occurred (SAT), thereby indicating that the system is \textit{incorrectly} sized.
+Fig.~\ref{fig:esbmcverifhouse5} shows the report generated by the tool, with highlights for the result, showing the incompatibility of the sized PV panels array of $1,300$ W and the minimum necessary of $2,048.05$W.
+This verification took less than $1$ s to perform, as indicated in the last line of Table~\ref{cases}.
 
 \begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{esbmcverifh5.png}
+\fbox{\includegraphics[width=1.0\textwidth]{esbmcverifh5.png}}
 \centering
-\caption{Report generated by ESBMC (with Z3 solver) after validation of House 5.}
+\caption{Report generated by ESBMC (Z3 solver) after validation of House 5.}
 \label{fig:esbmcverifhouse5}
@@
 
-%At the terminal, the command used to perform the verification is:
-%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
-%
-%Where:
-%
-%\begin{itemize}
-%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
-%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
-%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
-%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving.
-There are other options, but this parameter is necessary because the complexity of the algorithms.
-The incremental SMT solving uses few RAM memory, compared with other SMT solving.
-%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory.
-The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
-%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
-%\end{itemize}
-%
-
 \subsection{CBMC}
 
-Similar results were obtained with the CBMC tool, but with slower times than with ESBMC. The experimentation returned SAT or UNSAT for all the case studies, i.e. it was conclusive for all houses.
-
-In the $975$ W PV systems (house $1$, house $2$, house $3$, and house $4$), the tool could not reach an error in any of the four houses in an execution time of $18$ m $36$ s to $19$ m $02$ s.
-
-Fig.
-\ref{fig:cbmcverifhouse1} shows part of the report produced by CBMC when validating house 1.
-This file contains $270,512$ lines and is $39$ MB in size.
-The author highlighted the result, which shows that no design flaws were found within the bound $k$ of $100$.
-
-\begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{cbmcverifh1.png}
-\centering
-\caption{Report generated by CBMC after validation of House 1.}
-\label{fig:cbmcverifhouse1}
-\end{figure}
-
-However, the $1,200$ W PV system (house $5$) failed (SAT) in line $337$ of the code; with the same counterexample presented by ESBMC.
-This verification also took less than $1$ s to perform.
-Fig.~\ref{fig:cbmcverifhouse5} shows the (edited) report produced, with highlights on the flaw found: the minimum controller current needed for the PV systems is not compatible with the chosen controller of the sized system.
-The report file generated contains $217$ lines and was $13$ kB in size.
-
-\begin{figure}[h]
-\includegraphics[width=0.7\textwidth]{cbmcverifh5.png}
-\centering
-\caption{Report generated by CBMC after validation of House 5.}
-\label{fig:cbmcverifhouse5}
-\end{figure}
+CBMC was unable to produce a SAT or UNSAT result.
+In less of the 25 minutes of code execution at the setup configuration, the verifier engine consumed all the available RAM memory and produced an UNKNOWN result, i.e the result was inconclusive for all houses.
 
@@
 
-Finally, the CPAchecker tool presented some different results.
-Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the $975$ W systems (house $1$, house $2$, house $3$, and house $4$).
+Finally, the CPAchecker tool presented some similar qualitative results but with different performance when compared with ESBMC (with Z3 solver).
+The verification engine presented an SAT result (a FAIL) for all the $975$ W systems (house $1$, house $2$, house $3$, and house $4$) and to $1,300$ W system.
 
-This is because the \textit{time out} limit was reached, i.e.
-after $4$ hours of execution the tool was unable to decide if the verification was SAT or UNSAT.
-This is shown in Fig.~\ref{fig:cpavalidh1} which reproduces one of the text reports issued by CPAchecker.
-Unlike ESBMC and CBMC, CPAchecker produces many different reports, notably for log, statistical, and counterexample files (which are in graphic, not text format).
+Once again the problem of the minimum PV panels sizing expected was indicates as a flaw.
+The time to result was obtained in less than 5 seconds, around 4 seconds slower than ESBMC (with Z3); and the consumed memory by the CPAchecker was $3.86$ time bigger than ESBMC (with Z3).
+
+Figure~\ref{fig:cpavalidh1} reproduces one of the text reports issued by CPAchecker.
+Unlike ESBMC and CBMC, CPAchecker produces many different reports, notably for log, statistical, and counterexample files.
+There is a HTML version of the counterexample which produces graphic output, not only text format.
 
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{CPA_verif_h1.png}
+\fbox{\includegraphics[width=1.0\textwidth]{CPA_verif_h1.png}}
 \centering
-\caption{CPAchecker time out result for house 1 validation (file CPALog.txt).}
+\caption{CPAchecker text result for house 1 validation (file CPALog.txt).}
 \label{fig:cpavalidh1}
@@
 
-However, when validating the $1,200$ W PV system (house $5$), the tool presented the same SAT produced by the other engines, but with an execution time of $6$ seconds.
-Fig.~\ref{fig:cpavalidh5} shows the result, with highlights on the line that causes the fail ($IC_{min}$) and part of the CFA (control-flow automata, represented as a control-flow graph) diagram pointing to this fail.
+Figure~\ref{fig:cpavalidh5} shows the result for the $1,300$ W house, with highlights on the line that causes the fail and part of the CFA (control-flow automata, represented as a control-flow graph) diagram pointing to this fail.
 
 \begin{figure}[h]
-\includegraphics[width=1.0\textwidth]{CPA_verif_h5.png}
+\fbox{\includegraphics[width=1.0\textwidth]{CPA_verif_h5.png}}
 \centering
-\caption{CPAchecker time out result for house 5 validation (file Counterexample.html).}
+\caption{CPAchecker graphic result for house 5 validation (file Counterexample.html).}
 \label{fig:cpavalidh5}
@@
 
-The case study that was not possible to simulate was the $1,200$ W (house $5$).
+The case study that was not possible to simulate was the $1,300$ W (house $5$).
 The reason is that HOMER Pro does not allow battery autonomy setup (because it always sizes and optimizes the electrical system in order to meet the load requirements for an entire year of simulation); therefore, it was not possible to obtain any indication about the failures of this specific PV system with simulation (EQ2).
-
-%
-%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components.
-Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions.
-The season has impact since the case studies are from the rain forest, where clouds are always present.
-As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
-%
-%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool.
-Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance.
-The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system.
-All the simulations took less than 5 seconds (each) to be performed.
-%
-%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check.
-The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel.
-That verification took 63.3 hours to be performed.
-Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on).
-That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing.
-The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%.
-The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries.
-The proposed tool took 409.3 hours to find this error at house 1.
-This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
-Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
 
@@
 
-Results diverged for houses $1$, $2$, $3$ and $4$ with respect to the proposed approach: the automated evaluation shows there is no project flaws, but simulation demanded improvement of battery capacity (adding one more string of batteries to the system).
+Results do not diverged for houses $1$, $2$, $3$, $4$, and $5$ with respect to the proposed approach: the automated evaluation shows there is project flaws, from the PV panels to the battery arrays sizing.
+Simulation demanded improvement of battery capacity (adding one more string of batteries to the system) and to the PV panels array (when the HOMER Pro tool was doing optimization of the original sized solution).
 
@@
 
-In order to validate the possible flaw identified by the automated verification in house $5$, the owner of the $1,200$ W system was interviewed.
+In order to validate the possible flaw identified by the automated verification in house $5$, the owner of the $1,300$ W system was interviewed.
 From this it became clear that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double-checked against the monitoring system of the charge controller, which showed that the maximum power or surge power was not exceeded, thus affirming EQ1; this behavior is to be expected since the system was purchased as an off-the-shelf solution and not as a customized design for the house's electrical charges.
@@
 Furthermore, in this Chapter verifiers with the proposed automated verification using model checking were compared, which demonstrated that 'incremental' ESBMC had the best overall performance.
-CBMC presented the same results, but with a worse time to result, and CPAchecker was not conclusive (house $1$, house $2$, house $3$, and house $4$) because the \textit{time out} was not enough to obtain a result.
+CBMC was not conclusive, presented out of memory issues in all cases.
+CPAchecker had similar quality results than ESBMC, but with a slower performance for all cases.
 
-A comparison with a specialized simulation tool was also performed, although some of the tool's limitations, mainly related to not allowing battery autonomy setup or oversizing the battery bank by HOMER Pro, restricted the comparison between automated verification tools and simulation tools.
+A comparison with a specialized simulation tool was also performed, although some of the tool's limitations, mainly related to not allowing battery autonomy setup.
+The need of better PV panels and/or battery sizing by HOMER Pro and the verifier engines showed the flaws identified by the tools.
 

### 2020-02-05 Tex/Old text/chapters/chapterverification.tex
thesis update

@@
 
-In the houses that use a $975$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC reached an error in any of the four houses and the execution time took less than $01$ s.
+In the houses that use a $975$ W PV system (house $1$, house $2$, house $3$, and house $4$), ESBMC reached an error in all the four houses and the execution time took less than $01$ s.
 Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool for house $1$, with the FAIL identified.
-The author highlighted the result, which shows that the design flaw was found (SAT result or SUCCESS) within the bound $k$ of $100$, when a expected PV panels total power of $1,636.76$ W is expected and the sized system has only $975$ W.
+The authors highlighted the result, which shows that the design flaw was found (SAT result or SUCCESS) within the bound $k$ of $100$, when a PV panels total power of $1,636.76$ W is expected and the sized system has only $975$ W.
 This flaw is related to Eq.~\eqref{eq:Pminpanel}.
@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{homersimuh2no.png}
+\fbox{\includegraphics[width=1.0\textwidth]{homersimuh2no.png}}
 \centering
@@
 
+Further tests were performed in HOMER Pro.
+For example, to the case 1, that consumes $3.9$ kWh/day of energy: with the optimizer feature turned on, the total of PV panels minimum power expected to meet the load requirement was $2,530$ W.
+For the $3.6$ kWh/day of case 2, the PV panel solution indicated was $2,420$ W.
+For the $2.5$ kWh/day of case 3, the PV panel solution indicated was $1,590$ W.
+And, finally, for the $4.3$ kWh/day of case 4, the PV panel solution was $3,150$ W.
+
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{homersimuh2yes.png}
+\fbox{\includegraphics[width=1.0\textwidth]{homersimuh2yes.png}}
 \centering
@@
 
-In order to evaluate which validation is correct, it was necessary to consult the access interviews conducted with the residents of the deployed systems.
-From July $2018$ to March $2019$, surveys were applied to the residents on a monthly basis and data was collected from a local monitoring system: energy interruptions of the PV systems were not reported every month.
+In order to evaluate the validation results, it was necessary to consult the interviews conducted with the residents of the $975$ W deployed systems.
+From July $2018$ to March $2019$, surveys were applied to the residents on a monthly basis and data was collected from a local monitoring system: energy interruptions of the PV systems were not reported every month and, in some, cases, the maximum of 3 interruptions were reported.
+In one hand, when only one interruption is reported per month, this represents around $3.33$\% interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$).
+In other hand, when 3 interruptions are reported\footnote{Crossed information from interviews and collected data from the systems shows that the residents try to hide (or minimize) the interruption problems of the PV systems.
+Probably because they need of the system and they try not to emphasize this issue}, this means $10$\% of interruption, or $90$\% of availability.
+In accordance to what was described in Section~\ref{sec:availability}, the type of electrical load of the houses is not critical.
+Therefore any availability below of $95$\% is a sizing flaw, further affirming EQ1.
+Moreover, the proposed approach using automated verification provides the correct evaluation of the PV system, as the simulation did, thus answering EQ2.
 
-However, even when only one interruption is reported in a month, this represents around $3.33$\% interruption for the entire period ($1/30$), which indicates $96.97$\% of availability of the PV system ($96.67\% = 100\%-3.33\%$), and in accordance to what was described in Section~\ref{sec:availability}, the type of electrical load of the houses is not critical; this situation is considered an energy interruption, not a system flaw, further affirming EQ1.
-Therefore, the proposed approach using automated verification provides the correct evaluation of the PV system, thus answering EQ2.
-
-All tools indicated flaws in house $5$ (automated verification or simulation); however, only the automated verification approaches indicated which design error was responsible for the flaw (charge controller specification), further answering EQ2.
+The automated verification tools indicated flaws in house $5$ as well; and was not possible to get HOMER Pro evaluation because of the autonomy restriction, further answering EQ2.
 
 In order to validate the possible flaw identified by the automated verification in house $5$, the owner of the $1,300$ W system was interviewed.
-From this it became clear that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double-checked against the monitoring system of the charge controller, which showed that the maximum power or surge power was not exceeded, thus affirming EQ1; this behavior is to be expected since the system was purchased as an off-the-shelf solution and not as a customized design for the house's electrical charges.
+From this it became clear that, in fact, the system does not meet the battery autonomy when all loads are turned on, and this was double-checked against the monitoring system of the charge controller, which showed that the maximum power or surge power was not exceeded.
+Even during the daylight, there is not enough energy produced by the solar PV panels to feed the loads, thus affirming EQ1; this behavior is to be expected since the system was purchased as an off-the-shelf solution and not as a customized design for the house's electrical charges.
 
@@
 This Chapter presented a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
-Nevertheless, it also identified five threats to the validity of the results that bear further assessment.
+Nevertheless, it also identified six threats to the validity of the results that bear further assessment.
 
@@
 
-\textit{Simulation Tool:} Only HOMER Pro was used.
+\textit{Simulation tool:} Only HOMER Pro was used.
 The inclusion of other specialized simulation tools or even a general simulation tool that uses the same mathematical model adopted by the automated verification could change the comparison.
 
-\textit{Temperature and Solar Irradiance Data}: Information relating to the temperature and solar irradiance of each case study, whether it is using simulation or formal verification, comes from databases available online~\cite{Temperature, Irradiance}.
+\textit{Temperature and solar irradiance data}: Information relating to the temperature and solar irradiance of each case study, whether it is using simulation or formal verification, comes from databases available online~\cite{Temperature, Irradiance}.
 However, in view of the fact that riverside communities do not have weather stations, the data used in the present study comes from the municipality closest (Manaus in all the case studies), where stations regularly collect the data.
 Nevertheless, accuracy recommends the use of weather stations in each location.
+
+\textit{Energy consumption estimation}: All the PV size verification procedure start from the value of energy demanded from every house.
+However, this is a estimated value.
+Most recent information from field indicates that this value is overestimated and probably must be adjusted based on real data from a monitoring systems.
+The fact of the residents receive training to save energy is other issue that can reduce the total demanded energy from the PV systems.
+Therefore a most accurate validation can be performed when a real load curve is available for every case study.
 
@@
 
-Based on the fact that all case studies were deployed in the field, with regular visits to conduct interviews with the residents, and with monitoring systems in some of the houses (house $1$, house $2$, house $3$, and house $4$), it was possible to compare the computational validation (by simulation or automated verification) with the real world employment of stand-alone solar PV systems.
+Based on the fact that all case studies were deployed in the field, with regular visits to conduct interviews with the residents (house $1$, house $2$, house $3$, and house $4$), it was possible to compare the computational validation (by simulation or automated verification) with the real world employment of stand-alone solar PV systems.
+Although residents report few monthly problems in homes that use a $975$ W solution, it is clear that in fact the interruption problem is much greater, as the original sized PV system is underestimated when it comes to power generation from solar panels and energy storage in batteries.
+The $1,300$ W system was classified as problematic by the owner, and our automated verification technique shows the design flaws.
 The final conclusion was that the proposed tool is sound and has an acceptable performance.

### 2020-02-06 code/PVcode_rev3_house1.c
code update

@@ -94,8 +94,8 @@ int N = 72;    //N=number of series-connected cells
 int NOCT = 45; //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
 int Gref = 1000; //reference irradiance is 1000 W/m²
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
-float mii = 0.053; //short-circuit current temperature coefficient (A/K)
-float miv = -0.31; //open-circuit voltage temperature coefficient (V/K)
+float mii = 0.00053; //short-circuit current temperature coefficient (A/K)
+float miv = -0.0031; //open-circuit voltage temperature coefficient (V/K)
 float Iscref = 9.34;
 float Vocref = 45.5;
 float Imref = 8.78;
@@ -329,7 +329,7 @@ DODdaycalc = Ecorrected * 100/Eb;
 
 //check DC bus current
 IminDCbus = Eb/Vsystem;
-if( ! (IminDCbus <= (NPP * capacity)) ){ __VERIFIER_error();};
+if( ! (IminDCbus <= (NBP * capacity)) ){ __VERIFIER_error();};
 
 //controller vs inverter check
 if( ! ((VCmax* IC * nc) >= PACref) ){ __VERIFIER_error();};

### 2020-02-06 code/PVcode_rev3_house4.c

@@ -95,8 +95,8 @@ int N = 72;    //N=number of series-connected cells
 int NOCT = 45; //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
 int Gref = 1000; //reference irradiance is 1000 W/m²
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
-float mii = 0.053; //short-circuit current temperature coefficient (A/K)
-float miv = -0.31; //open-circuit voltage temperature coefficient (V/K)
+float mii = 0.00053; //short-circuit current temperature coefficient (A/K)
+float miv = -0.0031; //open-circuit voltage temperature coefficient (V/K)
 float Iscref = 9.34;
 float Vocref = 45.5;
 float Imref = 8.78;
@@ -330,7 +330,7 @@ DODdaycalc = Ecorrected * 100/Eb;
 
 //check DC bus current
 IminDCbus = Eb/Vsystem;
-if( ! (IminDCbus <= (NPP * capacity)) ){ __VERIFIER_error();};
+if( ! (IminDCbus <= (NBP * capacity)) ){ __VERIFIER_error();};
 
 //controller vs inverter check
 if( ! ((VCmax* IC * nc) >= PACref) ){ __VERIFIER_error();};

### 2020-02-06 code/opt_PVcode_rev7_case1.c

@@ -1,0 +1,279 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev7_CASEx
+ Author      : Alessandro Trindade
+ Version     : rev7 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2020-02-06 code/opt_PVcode_rev8_case1.c

@@ -1,0 +1,283 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev7_CASEx
+ Author      : Alessandro Trindade
+ Version     : rev7 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2020-02-06 Tex/Old text/chapters/chapter02.tex
thesis update
revised Chapter 2

@@
 
+In this Thesis, CPAchecker will be configurated as bounded model checker.
+
 %-----------------------------------------------------------
@@
 
-In order to address different aspects of a project system and system's design, many public domain and commercial software are available for the solar PV market.
-According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, to complex financial analysis software (with optimization).
-Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
-
-Manufacturers and integrators also have their own proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback of just including their own products among the possibilities of choice.
+In order to address different aspects of a project system and system's design, many commercial tools are available for the solar PV market.
+According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation to site survey and system design tools, to sophisticated financial analysis software (with optimization).
+Some tools also provide support to rebate program applications and tax incentives (specific to each country or region).
+In contrast, other programs and worksheets focus on the technical aspects of system sizing and design.
+
+Manufacturers and integrators also have their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback of just including their products among the possibilities of choice.
 In this study, the most widely used tools are presented:
@@
 According to \cite{Freeman} and \cite{NRELDobos}, this is a web application developed by the National Renewable Energy Laboratory (NREL), which estimates the electricity production of a grid-connected roof- or ground-mounted photovoltaic system based on a few inputs.
-According to \cite{NRELDobos}, using the calculator, requires information about the system's location, basic design parameters, and system economics.
+According to \cite{NRELDobos}, using the calculator requires information about the system's location, basic design parameters, and system economics.
 PVWatts calculates estimated values for the system's annual and monthly electricity production, and for the electricity's monetary value.
-This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin film photovoltaic modules.
+This tool is suitable for very preliminary studies of a potential location for a photovoltaic system that uses crystalline silicon or thin-film photovoltaic modules.
 The production estimates that PVWatts computation does not account for many factors that are important in the design of a photovoltaic system, which makes it necessary to have the support of an energy expert.
-The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over a period of one year.
-To represent the system's physical characteristics, PVWatts requires values for six inputs: system DC size; module type; array type; system losses; array tilt angle; array azimuth angle.
+The calculator estimates the monthly and annual electricity production of a photovoltaic system using an hour-by-hour simulation over one year.
+To represent the system's physical characteristics, PVWatts requires values for six inputs: system DC size, module type, array type, system losses, array tilt angle, and array azimuth angle.
 
@@
 SAM is a performance and financial model designed to facilitate decision making for people involved in the renewable energy industry: project managers and engineers; financial and policy analysts; technology developers; and researchers.
-SAM makes performance predictions and energy cost estimates for grid-connected power projects based on installation and operating costs and system design parameters that user specifies as inputs to the model.
-Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates, or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement.
-SAM is an electrical power generation model and assumes that the renewable energy system delivers power either to an electric grid, or to a grid-connected building or facility to meet the electric load.
+SAM makes performance predictions and energy cost estimates for grid-connected power projects based on installation and operating costs and system design parameters that the user specifies as inputs to the model.
+Projects can be either on the customer side of the utility meter, where they buy and sell electricity at retail rates or on the utility side of the meter, where they sell electricity at a price negotiated through a power purchase agreement.
+SAM is an electrical power generation model and assumes that the renewable energy system delivers power either to an electric grid or to a grid-connected building or facility to meet the electric load.
 It does not model thermal energy systems that meet a thermal process load.
-As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems, and does not model systems with electricity storage batteries.
+As mentioned in \cite{NRELBlair}, SAM does not model isolated or off-grid power systems and does not model systems with electricity storage batteries.
 
@@
 
-As defined in \cite{HOMER}, this is actually a set of two tools: HOMER Legacy and HOMER Pro.
+As defined in \cite{HOMER}, this is a set of two tools: HOMER Legacy and HOMER Pro.
 HOMER is an acronym for Hybrid Optimization Model for Multiple Energy Resources.
@@
 Since 2016 Homer Legacy can be found at the HOMER web site, but it is only available for students and nonprofit organizations, as defined in \cite{HOMER}, and has no support available.
-For a short-time only the commercial version will remain.
-
-The commercial version (paid), known as HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing micro-grid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
+For a short time, only the commercial version will remain.
+
+The commercial version (paid), known as HOMER Pro, as defined in \cite{Swarnkar}, is a tool for optimizing the microgrid design in all sectors, from village power and island utilities to grid-connected campuses and military bases.
 HOMER Pro puts together three tools in one product: optimization, simulation, and sensitivity analysis.
-It provides the detailed rigor of chronological simulation and optimization in a model that is intended to be easy to use and is adaptable to a wide variety of projects.
+It provides the full rigor of historical simulation and optimization in a model that is intended to be easy to use and is adaptable to a wide variety of projects.
 For a village or community-scale power system, HOMER can model both the technical and economic factors involved in the project.
 For larger systems, HOMER can provide an overview that compares the cost and feasibility of different configurations.
-Chronological simulation is essential for modeling variable resources, such as solar and wind power and for combined heat and power applications, where the thermal load is variable.
+Historical simulation is essential for modeling variable resources, such as solar and wind power, and for combined heat and power applications, where the thermal load is variable.
 HOMER's sensitivity analysis helps determine the potential impact of uncertain factors such as fuel prices or wind speed on a given system.
@@
 
-As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
+As mentioned in \cite{Pradhan}, RETScreen is a decision-support tool designed to help decision-makers and energy professionals to evaluate the financial viability of renewable energy, energy efficiency, and/or co-generation projects.
 
@@
 \item And the current (2016) RETScreen Expert, which allows users to evaluate energy investments over an entire project life-cycle (including benchmarking, feasibility, and performance analysis) in a fully integrated way, and within one software platform.
-This version is only Windows-based and has a complete paid version, via annual subscription way.
+This version is only Windows-based and has a complete paid version via an annual subscription way.
 \end{itemize}
 
-As described by \cite{Pradhan}, RETScreen performs a standard five-step analysis: setting and site conditions; energy model; cost analysis; emission analysis, financial analysis, sensitivity, and risk analysis.
-It is developed and maintained by the Government of Canada, through the CanmetENERGY Varennes Research Centre of Natural Resources; in collaboration with: NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
-RETScreen is available in 36 languages; it is a multi-awarded tool, and includes equipment databases for components manufactured and available worldwide.
+As described by \cite{Pradhan}, RETScreen performs a standard five-step analysis: setting and site conditions, energy model, cost analysis, emission analysis, financial analysis, sensitivity, and risk analysis.
+It is developed and maintained by the Government of Canada through the CanmetENERGY Varennes Research Centre of Natural Resources, in collaboration with NASA; Renewable Energy and Energy Efficiency Partnership (REEEP); United Nations Environment Programme (UNEP), and the Global Environment Facility (GEF).
+RETScreen is available in 36 languages; it is a multi-awarded tool and includes equipment databases for components manufactured and available worldwide.
 
@@
 The Hybrid2 software package, as described in \cite{Mills}, is a user-friendly tool that executes detailed long-term performance and economic analysis on a wide variety of hybrid power systems.
-Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, insolation, and temperature; and the power system is designed or selected by the user, in order to predict the performance of the hybrid power system.
+Hybrid2 is a probabilistic/time series computer model, using time series data for loads, wind speed, insolation, and temperature.
+The power system is designed or selected by the user to predict the hybrid power system performance.
 Variations in wind speed and in load within each time step are factored into the performance predictions.
@@
 
-Table \ref{table:softwares} summarizes the tools described in this paper.
-Where just Hybrid2 is mentioned, no technical support is available; only HOMER, RETScreen and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis; only HOMER and RETScreen are complete, including economic analysis and even optimization-sensitive analysis.
+Table~\ref{table:softwares} summarizes the tools described in this thesis, where just Hybrid2 is mentioned, no technical support is available.
+Only HOMER, RETScreen, and Hybrid2 perform off-grid system or battery backup analysis; all the tools perform solar photovoltaic analysis.
+Only HOMER and RETScreen are complete, including economic analysis and even optimization-sensitive analysis.
 However, only the paid version of these software packages have all the features, and they run only on Windows-based operating systems.
@@
 Considering that the focus of this research is on off-grid solutions and supported tools, only HOMER remains for comparison.
-All tools need some parameters inherently from the manufacturer's catalog, so the project starts with manufacturer's and integrator's tool to define the basic items of the project: panels, inverters, controllers, and batteries.
+All tools need some parameters inherently from the manufacturer's catalog, so the project starts with the manufacturer's and integrator's tool to define the essential items of the project: panels, inverters, controllers, and batteries.
 The potential solution is then analyzed by another tool to validate or even optimize the solution.
-The challenge of this study therefore is to prove that it is possible to use automated verification to validate an off-grid PV solution.
+The challenge of this study, therefore, is to prove that it is possible to use automated verification to validate an off-grid PV solution.
 
@@
 
-The main purpose of this section is to describe the models for the elements of a stand-alone PV system: the PV generator, battery, controller, inverter, and load.
+The primary purpose of this section is to describe the models for the elements of a stand-alone PV system: the PV generator, battery, controller, inverter, and load.
 The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}.
@@
 
-The basic element of a PV System is the PV cell, also called a Solar Cell.
+The fundamental element of a PV System is the PV cell, also called a Solar Cell.
 A PV / Solar Cell is a semiconductor device that can convert solar energy into DC electricity.
@@
 
-To increase their application usage, a number of individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module).
-For instance, a 12 V Panel will have 36 cells connected in series and a 24 V Panel will have 72 PV cells connected in series.
-In addition, to achieve the desired voltage and current, modules are wired in series (strings) and parallel into what is called a PV array, as shown in Fig.\ref{fig:celmodarray}.
+In order to increase their application usage, many individual PV cells are interconnected together in a sealed, weatherproof package called Panel (or Module).
+For instance, a 12 V Panel will have 36 cells connected in series, and a 24 V Panel will have 72 PV cells connected in series.
+Besides, to achieve the desired voltage and current, modules are wired in series (strings) and parallel into what is called a PV array, as shown in Fig.\ref{fig:celmodarray}.
 The flexibility of the modular PV system allows designers to create PV systems that can meet a wide variety of electrical demands.
@@
 The growing demand for photovoltaics technologies has led to research into the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}.
-Modeling PV modules is one of the major components responsible for proper functioning of PV systems.
+Modeling PV modules is one of the major components responsible for the proper functioning of PV systems.
 However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage.
@@
 
-The performance of photovoltaic systems (solar cell/panels), that is, the output current/voltage curve ($I-V$ curve), is usually studied using an equivalent circuit model.
+The performance of photovoltaic systems (solar cells/panels), that is, the output current/voltage curve ($I-V$ curve), is usually studied using an equivalent circuit model.
 This equivalent circuit consists of a current source with one or two diodes connected in parallel, and up to two resistors, one connected in parallel and the other one in series, to take into account energy losses in this model \cite{Cubas}.
@@
 \label{eq:1diodemodel}
-I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right) -1 \right] 
-\end{equation}
-
-Where:
+I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right) -1 \right], 
+\end{equation}
+
+\noindent where:
 \begin{itemize}
@@
 \label{eq:1d1rmodel}
-I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] 
-\end{equation}
-
-Where $R_{s}$ is the series resistor.
+I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right], 
+\end{equation}
+
+\noindent where $R_{s}$ is the series resistor.
 
@@
 \label{eq:1d2rmodel}
-I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}}
-\end{equation}
-
-Where $R_{sh}$ is the shunt resistor.
+I =I_{ph}-I_{0}\left[ exp \left( \dfrac{V+IR_{s}}{NaV_{T}} \right) -1 \right] - \dfrac{V+IR_{s}}{R_{sh}},
+\end{equation}
+
+\noindent where $R_{sh}$ is the shunt resistor.
 
@@
 For this reason, researchers gradually focused on searching out the approximate methods for the calculation of unknown parameters, proceeding along three different paths.
-The analytical methods give exact solutions by means of algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
-However, due to the implicit nature and nonlinearity of PV cell or module characteristics, it is hard to discover the analytical solution of all unknown parameters, as described in \cite{Hasan}.
+The analytical methods give exact solutions through algebraic equations, as done by \cite{Cubas} and \cite{Brano}.
+However, due to the inherent nature and nonlinearity of PV cell or module characteristics, it is hard to discover the analytical solution of all unknown parameters, as described in \cite{Hasan}.
 Thus, numerical methods such as the Newton-Raphson method or the Levenberg-Marquardt algorithm were preferred, as described by \cite{Mellit}.
-This happens because numerical methods give approximate solutions to the nonlinear problems without searching for exact solutions.
-However, numerical methods are time consuming and need long term time series data, which may not be available in developing countries.
-Reference~\cite{Jakhrani} used mixed methodology bringing analytical and numerical steps together.
-\cite{Shenawy} create a method to discover the unknown parameters of the PV panels through experimentation.
-And \cite{Tian} used a mix of analytical and experimental methodology to establish the unknown parameters, but samples of the PV modules are necessary to perform some tests, when we use the experimental technique.
+This happens because numerical methods give approximate solutions to nonlinear problems without searching for exact solutions.
+However, numerical methods are time-consuming and need long term time series data, which may not be available in developing countries.
+Reference~\cite{Jakhrani} used mixed methodology, bringing analytical and numerical steps together.
+\cite{Shenawy} et al.
+create a method to discover the unknown parameters of the PV panels through experimentation.
+Furthermore, \cite{Tian} used a mix of analytical and experimental methodology to establish the unknown parameters.
+However, samples of the PV modules are necessary to perform some tests when we use the experimental technique.
 
 Therefore, a wide variety of models exists for estimation of the power output of PV modules (and $I-V$ or $P-V$ curves).
-However, this study will rely on the simplified 1-diode model, that was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% for the selected PV panels tested.
-In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation.
+However, this study will rely on the simplified 1-diode model, which was shown by \cite{Saloux} that has a small error rate, between 0.03\% and 4.68\% for the selected PV panels tested.
+Besides, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation.
 
@@
 As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system.
-An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
-
-With that in mind, it is important to mention that even if formal verification or a simulation shows that a PV system fails, this  does not mean that the sizing is wrong.
-It is important to evaluate how critical the load application is and the evaluation period.
+The seasonal availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
+
+With that in mind, it is essential to mention that even if formal verification or a simulation shows that a PV system fails, this does not mean that the sizing is wrong.
+It is essential to evaluate how critical the load application is and the evaluation period.
 However, this analysis can be useful, for example, to improve sized battery autonomy.
@@
 
-The mathematical model presented in section~\ref{sec:model} is important for project validation; however if an approach is used to perform the sizing of stand-alone PV systems, then the tool proposed in this thesis can perform system validation (the intended behavior), and moreover obtain optimal project sizing.
-
-The sizing check stage can ensure that the system meets the standard project steps related 
-to the critical period method for solar energy system sizing~\cite{Pinho} and adopting a MPPT (Maximum Power Point Tracking) charge controller,
+The mathematical model presented in Section~\ref{sec:model} is vital for project validation.
+However, if an approach is used to perform the sizing of stand-alone PV systems, then the tool proposed in this thesis can perform system validation (the intended behavior), and obtain optimal project sizing.
+
+The sizing check stage can ensure that the system meets the standard project steps related to the critical period method for solar energy system sizing~\cite{Pinho} and adopting an MPPT (Maximum Power Point Tracking) charge controller,
 which is the most common in use. Firstly, we need to correct the daily energy consumption estimated for the load 
@@
 
-In one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
-In other hand, the arrangement, if in series or parallel connections, it will depends on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as shown in Eq.~\eqref{eq:Icmin} and
+On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
+On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as shown in Eq.~\eqref{eq:Icmin} and
 \eqref{eq:Vcmin}.
@@
 
-\noindent where $Autonomy$ is a number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries.
+\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries.
 
@@
 The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
-In addition, the final sizing check is performed by Equation \ref{eq:numberofc}, which validates the number of controllers adopted.
+Besides, the final sizing check is performed by Equation \ref{eq:numberofc}, which validates the number of controllers adopted.
 
@@
 
-The inverter sizing check is performed by means of three equations.
+The inverter sizing check is performed through three equations.
 Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
 Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
-Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
+Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
 
@@
 
-Moreover, it is important to verify the compatibility between charge controller and inverter, because there are some models that are not compatible with equipment from other manufacturers.
-Moreover, it is important to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side.
+Moreover, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers.
+Moreover, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side.
 Then the controller can be overcharged during this operation and to burn.
@@
 
-During the PV system design, one of the most important aspects in ensuring power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
+During the PV system design, one of the essential aspects of ensuring power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
 The reason is that solar energy production is intermittent and, therefore, the energy generated will usually not match the load demand.
@@
 
-There are different methods of expressing system reliability, where the most popular ones 
-are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
-In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one) the load will never be fulfilled.
+There are different methods of expressing system reliability, where the most popular ones are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
+In both methods, if the probability is zero, then the load will always be fulfilled; otherwise (i.e., probability of one), the load will never be fulfilled.
 
 LOLP is the probability for the case when load demand exceeds the power generation of the PV system.
-On one hand, we claim that we have a reliable PV system when it is able to generate sufficient power to fulfill the demanded load within a time span.
-On the other, LPSP is defined as the probability of the system generating insufficient power to satisfy the load demand.
+On the one hand, we claim that we have a reliable PV system when it can generate sufficient power to fulfill the demanded load within a period.
+On the other hand, LPSP is defined as the probability of the system generating insufficient power to satisfy the load demand.
 The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing in system performance.
-However, data is not always available and dynamic analysis is complex; and this is a drawback of both LOLP and LPSP~\cite{Alsadi2018}.
+However, data is not always available, and dynamic analysis is complex; this is a drawback of both LOLP and LPSP~\cite{Alsadi2018}.
 
@@
 Their main objective is to determine whether the project is an acceptable investment.
-The usual way is to perform economic analysis after reliability analysis with the goal of proposing a system with high reliability at the lowest cost~\cite{Alsadi2018}.
+The usual way is to perform economic analysis after reliability analysis to propose a system with high reliability at the lowest cost~\cite{Alsadi2018}.
 The most commonly used methods include: Net Present Cost (NPC)~\cite{Park2004}, the Levelized Cost of Energy (LCOE)~\cite{Zhou2010}, or the Life Cycle Cost (LCC)~\cite{Applasamy2011}.
@@
 The NPC is the present value of all the costs over the project lifetime, minus the present value of all the revenues that it earns over the project lifetime.
-The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
+The net present worth is found by discounting all cash inflows and outflows, including the cost of installation, replacement, and maintenance of the PV system, at an internal rate of return (IRR)~\cite{Park2004}.
 IRR is used to evaluate the attractiveness of a project or investment.
@@
 The intuitive method is simple, easily implemented, and can be used to give a rough suggestion for the preliminary design.
-The sizing rules are based on the designer's experience, using lowest performance data for a time period or by directly using average value (daily, monthly, or annual) of solar irradiance.
-This method does not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
-
-in the numerical method, the design is simulated for each time step within a period.
-Battery state of charge is calculated and investigated.
+The sizing rules are based on the designer's experience, using the lowest performance data for a time period or by directly using average value (daily, monthly, or annual) of solar irradiance.
+This method does not consider the battery's state of charge or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
+
+In the numerical method, the design is simulated for each time step within a period.
+The battery state of charge is calculated and investigated.
 Although very accurate, it is also complex, demanding more calculation time~\cite{Park2004}.
@@
 Analytical methods are used to obtain a close relation or correlation in the form of an equation between capacities and reliabilities.
-The sizing task becomes much simpler than in the numerical technique; however, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
+The sizing task becomes much more straightforward than in the numerical technique.
+However, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
 
@@
 
-In this Chapter, all the background and theoretical base needed to understand the concepts, techniques, tools, and criteria used during the following Sections were presented.
+In this chapter, all the background and theoretical base needed to understand the concepts, techniques, tools, and criteria used during the following Sections were presented.
 
@@
 
-The importance of mathematical rigor to the models and representation of systems was emphasized, and that the automated verification method can be applied to any kind of system (from the most simple to the most complex).
+The importance of mathematical rigor to the models and representation of systems was emphasized, and that the automated verification method can be applied to any system (from the most simple to the most complex).
 
 State-of-the-art automated verification tools were described with respect to their characteristics and techniques.
-Simulation tools were also described and the reason why HOMER Pro was the chosen for the comparison was explained.
+Simulation tools were also described and the reason why HOMER Pro was chosen for the comparison was explained.
 

### 2020-02-06 Tex/Old text/chapters/introduction.tex
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2020-02-04 Tex/Old text/chapters/introduction.tex
@@
 
-While some existing research efforts do aim enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
+While some existing research efforts do aim to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}.
 Among the opportunities for enhancements in the development processes for CPS software, there exists the need to develop new techniques and tools to support CPS requirement gathering and analysis to synthesize \textit{correct-by-construction} implementations of CPS.
 These techniques have to deal with predefined requirements enforced by nature and inherited constraints of the target CPS.
-In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
+Besides, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}.
 Uncertainty and variability, at the same time, can be dealt with by formal verification~\cite{NESSI}.
 
-Among the many CPS systems, in this thesis we will focus specifically on energy generation by stand-alone solar PV systems.
+Among the many CPS systems, in this thesis, we will focus specifically on energy generation by stand-alone solar PV systems.
 The lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below the 1 billion threshold for the first time in 2017~\cite{IEAweo2018}.
+Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below the 1 billion thresholds for the first time in 2017~\cite{IEAweo2018}.
 The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
@@
 Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
-It follows that, increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
+It follows that increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
 
-The use of the power generation technology with renewable energy sources is developing rapidly due to the industrial development~\cite{Yatimi}.
+The use of power generation technology with renewable energy sources is developing rapidly due to industrial development~\cite{Yatimi}.
 Renewable energy leads to advances all over the world by protecting the environment: it is clean (low greenhouse gas emissions), operates silently, long-lasting, low maintenance costs, zero fuel costs and an inexhaustible supply~\cite{Noroozian}.
@@
 Nothing more than a niche market only a few years ago, solar PV systems have become a mainstream electricity provider, with an approximate 50\% increase (or 100.9 GW)in new PV installations from 2016 to 2017~\cite{EPIA}, although this growth is not driven by stand-alone systems.
-
 However, in order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed.
@@
 Moreover, the optimum sizing of these devices is essential for reliable operation.
-Therefore, these systems need to be designed in accordance with the site, the land area available, load requirement, load pattern, environmental conditions, and economics in order to utilize available resources efficiently and economically~\cite{Rawat}.
+Therefore, these systems need to be designed under the site, the land area available, load requirement, load pattern, environmental conditions, and economics in order to utilize available resources efficiently and economically~\cite{Rawat}.
 
@@
 
-Energy access is an important issue because it can put together economic growth, human development and environmental sustainability.
+Energy access is an essential issue because it can put together economic growth, human development, and environmental sustainability.
 Energy has long been recognized as essential for humanity to develop and thrive, but the adoption in 2015 by 193 countries of a goal to ensure access to affordable, reliable, sustainable and modern energy for all by 2030, as part of the new United Nations Sustainable Development Goals (SDGs), marked a new level of political recognition~\cite{IEAweo2018}.
 
-The International Energy Agency (IEA) revealed that from 2000 to 2016 nearly all of those who gained access to electricity worldwide did so through new grid connections, mostly with power generation from fossil fuels.
+The International Energy Agency (IEA) revealed that from 2000 to 2016, nearly all of those who gained access to electricity worldwide did so through new grid connections, mostly with power generation from fossil fuels.
 Over the last five years, however, renewable sources have started to gain ground, as have off-grid and mini-grid systems.
 By 2030, renewable energy sources power over 60\% of new access, and off-grid and mini-grid systems provide the means for almost half of new access~\cite{IEAweo2018}.
-Moreover, if we focus into the Amazonas State, Brazil, where around 5\% of the population in 2018 were isolated in 2,261 communities (or 41,167 houses), without electrical energy or even road access, using just boats by rivers, therefore energy is a very important issue.
+Moreover, if we focus on the Amazonas State, Brazil, where around 5\% of the population in 2018 was isolated in 2,261 communities (or 41,167 houses), without electrical energy or even road access, using just boats by rivers, therefore energy is a fundamental issue.
 
-Under this scenario, it is important to have very well designed PV systems that won't fail when installed in the field and at the lowest acquisition cost possible.
+Under this scenario, it is crucial to have very well designed PV systems that will not fail when installing in the field and at the lowest acquisition cost possible.
 
 In order to address different aspects of a solar PV project, there is a variety of public domain and commercial software solutions available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general-purpose simulation tools such as PSpice, and the MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
-According to~\cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation to site survey and system design tools, and to sophisticated financial analysis software (with optimization).
-Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
+According to~\cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation to site survey and system design tools, and sophisticated financial analysis software (with optimization).
+Some tools also provide support to rebate program applications and tax incentives (specific to each country or region).
+In contrast, other programs and worksheets focus on the technical aspects of system sizing and design.
 %
-Manufacturers and integrators also have their own proprietary software to perform system sizing~\cite{Zhou2010}, with the drawback of indicating only their own products among the possibilities of choice, which restricts their solution.
+Manufacturers and integrators also have their proprietary software to perform system sizing~\cite{Zhou2010}, with the drawback of indicating only their products among the possibilities of choice, which restricts their solution.
 %
@@
 Simulation has the advantage of being cheap (if compared to testing in real systems) and can be employed before the system design is concluded.
-However, it has the drawback of an incomplete coverage since the verification of all possible combinations, and of potential system failures is unfeasible~\cite{ClarkeHV18}.
+However, it has the drawback of incomplete coverage since the verification of all possible combinations, and potential system failures are unfeasible~\cite{ClarkeHV18}.
 
@@
 Thus, problems such as incompleteness, ambiguities, and inconsistencies, which are generally discovered only in the later stages of the design, can be detected in advance, as described by \cite{Trindade,TrindadeDJISC17}.
-Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the given system meets the requirements.
+Model-checking algorithms can then verify the system model by systematically exploring all its states to check whether the given system meets the requirements.
 %
@@
 %automated synthesis
-Optimization of PV systems is not a recent topic; since the $1990$s different techniques have been developed and evaluated using a wide variety of criteria to find the ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods~\cite{Applasamy2011}.
+Optimization of PV systems is not a recent topic; since the $1990$s different techniques have been developed and evaluated using a wide variety of criteria to find the ultimate combinations for design parameters based on intuitive, numerical, and analytical methods~\cite{Applasamy2011}.
 The ideal combination for any PV system is made by the best compromise between two considered objectives, which are \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.
 
-However, formal methods based on \textit{symbolic model checking} applied to synthesize PV systems have not been further explored in the literature, which could offer a great opportunity to obtain a more effective design process for PV systems~\cite{ClarkeHV18}.
+However, formal methods based on \textit{symbolic model checking} applied to synthesize PV systems have not been further explored in the literature, which could offer an excellent opportunity to obtain a more effective design process for PV systems~\cite{ClarkeHV18}.
 
@@
 
-The main objective of this thesis is thus to prove that is possible to use formal verification method to validate the design and to use formal synthesis method to optimize the sizing of stand-alone solar PV systems.
-Secondarily, we aim to develop two tools written in ANSI-C and platform-independent, based on the the new proposed techniques in order to evaluate different state-of-the art symbolic software verifiers (and solvers), and comparing the experimental results with simulation tool and with data from real PV systems installed in riverside communities.
-Always evaluating correctness and performance.
+The main objective of this thesis is thus to prove that it is possible to use a formal verification method to validate the design and to use a formal synthesis method to optimize the sizing of stand-alone solar PV systems.
+Secondarily, we aim to develop two tools written in ANSI-C and platform-independent, based on the new proposed techniques to evaluate different state-of-the-art symbolic software verifiers (and solvers).
+We also aim to compare the experimental results with the simulation tool and with data from real PV systems installed in riverside communities, thereby evaluating correctness and performance.
 
@@
 %The thesis produces a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
-The originality of this thesis lies in the creation of an automated verification technique to solar PV systems.
+The originality of this thesis lies in the creation of an automated verification technique for solar PV systems.
 The research led to the creation of two software solutions to carry out computational experiments and to compare with commercial tools and real data from systems installed in the field.
@@
 
-The proposed technique is applied by means of an algorithm implemented using the C programming language.
-We performed computing experimentation in three state-of-the-art model checkers to formally verify PV designs, aiming to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
+The proposed technique is applied through an algorithm implemented using the C programming language.
+We employed three state-of-the-art model checkers to verify PV designs formally, thus aiming to evaluate performance and correctness.
+The C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
 %three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}.
@@
 
-With respect to the \textbf{automated synthesis} technique and optimal sizing of stand-alone PV systems, this thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input.
-Given a correctness specification $\sigma$, the proposed method uses $\sigma$ as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$ with respect to power reliability.
+Concerning the \textbf{automated synthesis} technique and optimal sizing of stand-alone PV systems, this thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input.
+Given a correctness specification $\sigma$, the proposed method uses $\sigma$ as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$ for power reliability.
 In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, which may not attain the lowest cost.
@@
 
-Simply put, we aim to present new techniques that will ensure that you have good designs of stand-alone solar PV systems, that do not cause a drop in energy supply, and that these systems are designed at the lowest possible cost.
+\textbf{ We aim to present new techniques that will guarantee a good design of stand-alone solar PV systems, that do not cause a drop in energy supply after deployment, and that these systems are designed at the lowest possible cost.}
 
@@
 
-Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system and optimal sizing.
-Validation when a sized system must be evaluated in order to decide if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or when the user tries to obtain a better solution that he or she has.
-We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in a comparison with specialized simulation tools, supported by real data from installed PV systems.
+Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems to tackle two issues: validation of a designed system and optimal sizing.
+Validation when a sized system must be evaluated in order to decide if it meets the design requirements and user needs.
+\textcolor{red}{this sentence is confusing...
+Optimization, when there exist just the requirements and the PV system, is not sized, or when the user tries to obtain a better solution that he or she has}.
+We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in comparison with specialized simulation tools, supported by real data from installed PV systems.
 
@@
 We thus develop algorithms and the corresponding tools; moreover, we evaluate them with several case studies, in a comparative with specialized simulation tools, supported by real data from deployed PV systems.
-Fig.\ref{fig:validation_outline} outlines the proposed solution to perform the validation of stand-alone solar PV systems via automated verification.
+Fig.~\ref{fig:validation_outline} outlines the proposed solution to perform the validation of stand-alone solar PV systems via automated verification.
 Fig.\ref{fig:optimization_outline} illustrates the proposed solution to obtain the optimal sizing of stand-alone solar PV systems via automated synthesis.
 We pictured here only a summary of each phase of our proposed approach, highlighting the input parameters, the outputs for the validation, or the optimal size of the solar PV system; more details will be presented in the next chapters.
-Moreover, the illustrations show the methodological approach with respect to comparative result analysis, employing our approaches, the commercial software tool, and data from real PV systems deployed in the field.
+Moreover, the illustrations show the methodological approach concerning comparative result analysis, employing our approaches, the commercial software tool, and data from real PV systems deployed in the field.
 
@@
 
-With respect to the proposed \textbf{automated verification} technique, this thesis makes three main contributions: \textbf{first}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; \textbf{second}, we evaluate the verification technique by comparing three state-of-the-art model checkers in five real case studies; \textbf{third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.
+\textcolor{red}{The following two paragraphs are too long! Please consider breaking them into smaller sentences!}
+
+Concerning the proposed \textbf{automated verification} technique, this thesis makes three main contributions: \textbf{first}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; \textbf{second}, we evaluate the verification technique by comparing three state-of-the-art model checkers in five real case studies; \textbf{third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.
 
 In the area of \textbf{automated synthesis}, our study makes a further three original contributions: \textbf{first}, it is the first application of a sound and automated formal synthesis approach which can provide accurate results for optimal sizing of stand-alone PV systems; \textbf{second}, we propose a variant CEGIS method of synthesis with striking differences of how the Synthesize and Verify phases from the original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and \textbf{third}, experimental results in seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tools: our solution is far more detailed and closer to real PV systems than solutions presented by simulation.
+
 % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers.
@@
 
-In this section we discuss only the use of formal methods in electrical systems in general since optimization of PV sizing is currently not obtained by formal methods or even program synthesis.
+In this section, we discuss only the use of formal methods in electrical systems in general since the optimization of PV sizing is currently not obtained by formal methods or even program synthesis.
 %Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.
@@
 The formal specification presented can be considered a first step towards modeling smart grids using formal methods.
-The starting point of this study was that a smart home can be considered an integrated system consisting of various objects and systems, which communicate and interact with each other.
-This approach is based on Petri nets and works under the assumption that modeling smart homes leads to a clear understanding of the overall behavior of the smart grids.
+The starting point of this study was that a smart home could be considered an integrated system consisting of various objects and systems, which communicate and interact with each other.
+This approach is based on Petri nets and works under the assumption that modeling smart homes lead to a clear understanding of the overall behavior of the smart grids.
 
@@
 Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in the literature.
-Moreover, it is precisely on these gaps that this thesis is focused.
+Moreover, it is precisely on these gaps that this thesis is focused on.
 
@@
 
-This introduction has outlined the context, motivation, and problem addressed by this thesis and the objectives, solution, and contributions of the research.
+This introduction has outlined the context, motivation, and problem addressed by this thesis and the objectives, solutions, and contributions of the research.
 The remaining chapters are organized as follows:
@@
 
-In the `~\nameref{chap:conclusions}' we present the main contributions, future work directions and concluding remarks.
+In the `~\nameref{chap:conclusions}', we present the main contributions, future work directions and concluding remarks.
 
@@
 
-~\autoref{chap:tools} depicts the tools created during the Ph.D process to implement and validate the two scientific methods of the thesis (and instructions for their use).
+~\autoref{chap:tools} depicts the tools created during the Ph.D. process to implement and validate the two scientific methods of the thesis (and instructions for their use).
 
-~\autoref{chap:data} presents detailed data from all the equipment used during the experimental part of the thesis, covering information from data-sheet, electrical features, brands and models.
+~\autoref{chap:data} presents detailed data from all the equipment used during the experimental part of the thesis, covering information from data-sheet, electrical features, brands, and models.
 
@@
 The choice of the active voice comes from the choice of the English language, which in the thesis studied was always presented in the active voice.
-The decision to use the English language stems from the possibility that the research may lead to further developments and activities,  in the possibility of reaching a larger number of people and helping in the internationalization of the Federal University of Amazonas.
+The decision to use the English language stems from the possibility that the research may lead to further developments and activities, in the possibility of reaching a more significant number of people and helping in the internationalization of the Federal University of Amazonas.

### 2020-02-06 Tex/Old text/chapters/introduction.tex
added dssynth reference
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Formal methods based on model checking offer a great potential to obtain a faster and more effective verification in the design process~\cite{ClarkeHV18}, including, for example, applications to CPS~\cite{Abateetal2017,AbateBCCDKK17,Bessa,ChavesBCKF17}, with behavior that is, in principle, well determined.
+Formal methods based on model checking offer a great potential to obtain a faster and more effective verification in the design process~\cite{ClarkeHV18}, including, for example, applications to CPS~\cite{Abateetal2017,AbateBCCDKK17,Bessa,ChavesBCKF17,AbateBCCCDKKP17}, with behavior that is, in principle, well determined.
 Any system type can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; one can then try to produce a formal proof or otherwise establish that the program meets its specification~\cite{DBLP:journals/sttt/GadelhaIC17}.

### 2020-02-06 Tex/Old text/chapters/chapter02.tex
added recent version of ESBMC
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C~\cite{esbmc2018}, C++~\cite{RamalhoFSMC013}, Qt~\cite{MonteiroGCF17}, and CUDA~\cite{PereiraASMMFC17} programs, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C~\cite{esbmc2018,GadelhaMCN19}, C++~\cite{RamalhoFSMC013}, Qt~\cite{MonteiroGCF17}, and CUDA~\cite{PereiraASMMFC17} programs, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
 

### 2020-02-06 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 
-In this Thesis, CPAchecker will be configurated as bounded model checker.
+In this thesis, CPAchecker will be configured as a bounded model checker.
 
@@
 In the specific case of isolated communities, depending on the type of load, cost, resources availability, and the load requirements, stand-alone systems can be split into several categories, as described below.
-Since the goal of this Thesis is to present solutions only to isolated/ off-grid applications, on-grid or hybrid configurations are not discussed here.
+Since the goal of this thesis is to present solutions only to isolated/ off-grid applications, on-grid or hybrid configurations are not discussed here.
 

### 2020-02-06 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
-In this Chapter, we detail methodology used for optimal sizing of stand-alone solar PV systems, more specifically using model checking.
+In this chapter, we detail methodology used for optimal sizing of stand-alone solar PV systems, more specifically using model checking.
 Diagrams, flowcharts, and algorithm give support and explain the solutions.
@@
 
-It is important to emphasize that the complete explanation of the theoretical basis of the subject discussed here is presented in the Chapter~\nameref{chap:background}.
+It is important to emphasize that the complete explanation of the theoretical basis of the subject discussed here is presented in the chapter~\nameref{chap:background}.
 In addition, knowledge of the literature is essential to aid understanding.
@@
 
-In this Chapter we showed in detail how the state-of-the-art computer science method of automated synthesis has been adapted to use in stand-alone solar PV systems in order to obtain optimal project sizing.
+In this chapter we showed in detail how the state-of-the-art computer science method of automated synthesis has been adapted to use in stand-alone solar PV systems in order to obtain optimal project sizing.
 Moreover, it was possible to illustrate how the proposed method compares with the traditional use of a simulation tool for the same purpose.
 
-Detailed diagrams, flowcharts and algorithms with pseudo-code were presented as support for the proposed work and to aid understanding.
+Detailed diagrams, flowcharts and algorithm with pseudo-code were presented as support for the proposed work and to aid understanding.
 Also listed, were the assumptions underlying the automated verification and simulation software.

### 2020-02-06 Tex/Old text/chapters/chapterverification.tex
thesis update

@@
-In this Chapter, we detail the methodology adopted to perform formal verification of stand-alone solar PV systems using formal methods, more specifically model checking.
+In this chapter, we detail the methodology adopted to perform formal verification of stand-alone solar PV systems using formal methods, more specifically model checking.
 Diagrams, flowcharts, and algorithms support and explain the solutions.
 The experimentation, case studies, and results are also presented.
-In addition, the Chapter contains a comparison with a specialized simulation tool, and also the use of different verifiers that evaluate performance by means of automated verification.
+In addition, the chapter contains a comparison with a specialized simulation tool, and also the use of different verifiers that evaluate performance by means of automated verification.
 Tables, commented reports, and graphic outputs are presented to aid  understanding.
@@
 Unlike premises, assumptions are not explicit and need to be deciphered.
-With that in mind, we perform a detailed explanation of all assumptions over the course of the Chapter.
+With that in mind, we perform a detailed explanation of all assumptions over the course of the chapter.
 
-It is important to emphasize that the theoretical basis of the subject presented in this chapter was discussed in Chapter 2, ~\nameref{chap:background}.
+It is important to emphasize that the theoretical basis of the subject presented in this chapter was discussed in chapter 2, ~\nameref{chap:background}.
 In addition, knowledge of the literature is essential to aid understanding.
@@
 
-This Chapter presented a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
+This chapter presented a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
 Nevertheless, it also identified six threats to the validity of the results that bear further assessment.
@@
 
-This Chapter showed in details how the state-of-the-art computer science method of automated verification was adapted to be used in stand-alone solar PV systems in order to validate their behavior.
+This chapter showed in details how the state-of-the-art computer science method of automated verification was adapted to be used in stand-alone solar PV systems in order to validate their behavior.
 Moreover, it was possible to illustrate the comparative differences in how the proposed method and the traditional method of simulation work.
@@
 
-Furthermore, in this Chapter verifiers with the proposed automated verification using model checking were compared, which demonstrated that 'incremental' ESBMC had the best overall performance.
+Furthermore, in this chapter verifiers with the proposed automated verification using model checking were compared, which demonstrated that 'incremental' ESBMC had the best overall performance.
 CBMC was not conclusive, presented out of memory issues in all cases.

### 2020-02-06 Tex/Old text/chapters/introduction.tex
thesis update

@@
 Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems to tackle two issues: validation of a designed system and optimal sizing.
-Validation when a sized system must be evaluated in order to decide if it meets the design requirements and user needs.
-\textcolor{red}{this sentence is confusing...
-Optimization, when there exist just the requirements and the PV system, is not sized, or when the user tries to obtain a better solution that he or she has}.
+
+Validation is a important issue when a sized system must be evaluated in order to decide if it meets the design requirements and user needs.
+In other words, it is a way to guarantee that a sized PV system will not fail (stopping to supply energy to a house, for example) after deployment at the field.
+
+\textcolor{red}{Optimization is important when there exist (just) the requirements of the house to be electrified.
+In our particular case, we need a optimal PV system solution, in technical and economical terms, that can show us a list of equipment to be bought and how it will be connected together (configuration)}.
+
 We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in comparison with specialized simulation tools, supported by real data from installed PV systems.
@@
 
-\textcolor{red}{The following two paragraphs are too long! Please consider breaking them into smaller sentences!}
+\textcolor{red}{My comment: paragraphs broken in small and organized parts:}
 
-Concerning the proposed \textbf{automated verification} technique, this thesis makes three main contributions: \textbf{first}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; \textbf{second}, we evaluate the verification technique by comparing three state-of-the-art model checkers in five real case studies; \textbf{third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.
+Concerning the proposed \textbf{automated verification} technique, this thesis makes three main contributions: 
+\begin{itemize}
+\item \textbf{First}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system;
+\item \textbf{Second}, we evaluate the verification technique by comparing three state-of-the-art model checkers in five real case studies; and 
+\item \textbf{Third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.
+\end{itemize}
 
-In the area of \textbf{automated synthesis}, our study makes a further three original contributions: \textbf{first}, it is the first application of a sound and automated formal synthesis approach which can provide accurate results for optimal sizing of stand-alone PV systems; \textbf{second}, we propose a variant CEGIS method of synthesis with striking differences of how the Synthesize and Verify phases from the original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and \textbf{third}, experimental results in seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tools: our solution is far more detailed and closer to real PV systems than solutions presented by simulation.
+In the area of \textbf{automated synthesis}, our study makes a further three original contributions: 
+\begin{itemize}
+\item \textbf{First}, it is the first application of a sound and automated formal synthesis approach which can provide accurate results for optimal sizing of stand-alone PV systems; 
+\item \textbf{Second}, we propose a variant CEGIS method of synthesis with striking differences of how the Synthesize and Verify phases from the original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and
+\item \textbf{Third}, experimental results in seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tools: our solution is far more detailed and closer to real PV systems than solutions presented by simulation.
+\end{itemize}
 

### 2020-02-06 code/PVcode_rev3_house1.c
code update

@@ -93,6 +93,7 @@ int VoutAC = 110, VinDC = 24, VAC = 127;
 int N = 72;    //N=number of series-connected cells
 int NOCT = 45; //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
 int Gref = 1000; //reference irradiance is 1000 W/m²
+int G = 800;
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
 float mii = 0.00053; //short-circuit current temperature coefficient (A/K)
 float miv = -0.0031; //open-circuit voltage temperature coefficient (V/K)
@@ -362,7 +363,7 @@ if( ! ((VCmax* IC * nc) >= PACref) ){ __VERIFIER_error();};
 	//controller check, considering just one controller
 	if( ! ( VC == Vsystem ) ){ __VERIFIER_error(); }
 
-	Iscamb = Iscref*(1+mii*(Tcell-25)); //from each PV panel
+	Iscamb = G*Iscref*(1+mii*(Tcell-25))/Gref; //from each PV panel
 	ICmin = Iscamb * NPP;
 	if( ! ( IC >= ICmin ) ){ __VERIFIER_error(); }
 

### 2020-02-06 code/PVcode_rev3_house2.c

@@ -94,6 +94,7 @@ int maxTemp [12] = {30,30,30,30,30,30,30,31,32,32,31,30};
 int N = 72;    //N=number of series-connected cells
 int NOCT = 45; //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
 int Gref = 1000; //reference irradiance is 1000 W/m²
+int g = 800;
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
 float mii = 0.00053; //short-circuit current temperature coefficient (A/K)
 float miv = -0.0031; //open-circuit voltage temperature coefficient (V/K)
@@ -363,7 +364,7 @@ if( ! ((VCmax* IC * nc) >= PACref) ){ __VERIFIER_error();};
 	//controller check, considering just one controller
 	if( ! ( VC == Vsystem ) ){ __VERIFIER_error(); }
 
-	Iscamb = Iscref*(1+mii*(Tcell-25)); //from each PV panel
+	Iscamb = G*Iscref*(1+mii*(Tcell-25))/Gref; //from each PV panel
 	ICmin = Iscamb * NPP;
 	if( ! ( IC >= ICmin ) ){ __VERIFIER_error(); }
 

### 2020-02-06 code/PVcode_rev3_house3.c

@@ -94,6 +94,7 @@ int maxTemp [12] = {30,30,30,30,30,30,30,31,32,32,31,30};
 int N = 72;    //N=number of series-connected cells
 int NOCT = 45; //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
 int Gref = 1000; //reference irradiance is 1000 W/m²
+int G = 800;
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
 float mii = 0.00053; //short-circuit current temperature coefficient (A/K)
 float miv = -0.0031; //open-circuit voltage temperature coefficient (V/K)
@@ -363,7 +364,7 @@ if( ! ((VCmax* IC * nc) >= PACref) ){ __VERIFIER_error();};
 	//controller check, considering just one controller
 	if( ! ( VC == Vsystem ) ){ __VERIFIER_error(); }
 
-	Iscamb = Iscref*(1+mii*(Tcell-25)); //from each PV panel
+	Iscamb = G*Iscref*(1+mii*(Tcell-25))/Gref; //from each PV panel
 	ICmin = Iscamb * NPP;
 	if( ! ( IC >= ICmin ) ){ __VERIFIER_error(); }
 

### 2020-02-06 code/PVcode_rev3_house4.c

@@ -94,6 +94,7 @@ int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,
 int N = 72;    //N=number of series-connected cells
 int NOCT = 45; //Nominal Operating Cell Temperature=45°C +-2 at G=800 W/m2, light spectrum AM 1.5G, windspeed=1m/s, air temp at 20°C
 int Gref = 1000; //reference irradiance is 1000 W/m²
+int G = 800;
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
 float mii = 0.00053; //short-circuit current temperature coefficient (A/K)
 float miv = -0.0031; //open-circuit voltage temperature coefficient (V/K)
@@ -363,7 +364,7 @@ if( ! ((VCmax* IC * nc) >= PACref) ){ __VERIFIER_error();};
 	//controller check, considering just one controller
 	if( ! ( VC == Vsystem ) ){ __VERIFIER_error(); }
 
-	Iscamb = Iscref*(1+mii*(Tcell-25)); //from each PV panel
+	Iscamb = G*Iscref*(1+mii*(Tcell-25))/Gref; //from each PV panel
 	ICmin = Iscamb * NPP;
 	if( ! ( IC >= ICmin ) ){ __VERIFIER_error(); }
 

### 2020-02-06 code/opt_PVcode_rev9_case1.c

@@ -1,0 +1,286 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev7_CASEx
+ Author      : Alessandro Trindade
+ Version     : rev7 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2020-02-07 code/opt_PVcode_rev9_case1.c
code update

@@ -147,7 +147,7 @@ int FHintCost(void){
 ----------------------------------*/
 int Faux (int cost){
 	int NTP, NPP, NPS, NBtotal, NBS, NBP, NPPmin, ICmin;
-	int DODmax;
+	int DODmax, arrang, NPmin;
 	float Ecorrected, Ep, NTPmin, NPSmin1, NPSmin2, Cbank, Iscamb, NBSmin, NBPmin, Fobj;
 float Pminpanels, ItotalPVpanels, VtotalPVpanels, Eb, DODdaycalc, IminDCbus, equipcost;
 	unsigned char PanelChoice, BatteryChoice, ControllerChoice, InverterChoice;
@@ -210,8 +210,29 @@ float Pminpanels, ItotalPVpanels, VtotalPVpanels, Eb, DODdaycalc, IminDCbus, equ
 	Pminpanels = 1.25 * Ecorrected / Insol;
 
 ////definir arranjos de painéis solares para tentativa de projeto ótimo NPS, NPP
-	NPP = 1;
-	NPS = ((Pminpanels-1) / Pmref)+1;
+
+arrang = nondet_uint();
+
+//	NPP = 1; //arrangement for series connection
+//	NPS = ((Pminpanels-1) / Pmref)+1;  //arrangement for series connection
+NPmin = ((Pminpanels -1)/ Pmref)+1;
+if (NPmin >= 3) {
+	arrang = nondet_uint();
+	__VERIFIER_assume( (arrang >= 1) && (arrang <= 2) );
+	if (arrang == 1) { //series arrangement of PV array
+		NPP = 1;
+		NPS = NPmin;
+	}
+	if (arrang == 2) { //parallel arrangement of PV array
+		NPP = 2;
+		if ((NPmin % 2) == 0) NPS = NPmin/2; //even number
+		else NPS = (NPmin + 1)/2; //odd number
+	}	
+} 
+else { //1 or two panels in series
+NPP = 1;
+NPS = NPmin;
+}
 
 //
 

### 2020-02-07 code/opt_PVcode_rev9_case1.c
code update

@@ -246,9 +246,10 @@ __VERIFIER_assume ( (IC >= ItotalPVpanels) );
 VtotalPVpanels = NPS * Vmref;
 __VERIFIER_assume ( (VCmax >= VtotalPVpanels) );
 
-DODmax = (100-SOClimit);
+DODmax = (100-SOClimit)*2;
 //checking batteries
-Eb = (autonomy/24) * Ecorrected/((float)(DODmax/100)),
+//Eb = (autonomy/24) * Ecorrected/((float)(DODmax/100));
+Eb = (autonomy/24) * Ecorrected*100/DODmax;
 
 DODdaycalc = Ecorrected * 100/Eb;
 

### 2020-02-07 code/opt_PVcode_rev9_case1.c
code update

@@ -82,13 +82,16 @@ float BatteryData [10][6] = {{0.85, 12, 80, 14.4, 13.8, 131.00},
 // victron MPPT (35-145, 15-75, 15-100, 50-100), Epever (TRIRON 2210N 20A 12/24V, TRIRON 3210N 30A 12/24V, TRIRON 4210N 40A 12/24V), Epsolar (Tracer-2210RN 20A 12/24V, New Tracer-3215BN 30A 12/24V), Schneider Electric (XW-MPPT 60/150)
 float ControllerData [10][6] = {{0.98, 35, 24, 13, 145, 294.95},
 			       {0.98, 15, 24, 13, 75, 88.40},
-			       {0.98, 15, 24, 13, 100, 137.70},
+//			       {0.98, 15, 24, 13, 100, 137.70},
+
                                {0.98, 50, 24, 13, 100, 294.95},
 			       {0.98, 20, 24, 13, 100, 132.25},
 			       {0.98, 30, 24, 13, 100, 161.00},
 			       {0.98, 40, 24, 13, 100, 184.75},
 			       {0.97, 20, 24, 13, 100, 217.25},
-			       {0.97, 30, 24, 13, 100, 297.25},
+//			       {0.97, 30, 24, 13, 100, 297.25},
+{0.98, 50, 48, 13, 150, 347.82},
+{0.98, 60, 48, 13, 150, 388.91},
 			       {0.96, 60, 60, 13, 140, 1072.50}};
 
 // inverter data  	{efficiency, VinDC, VoutAC, PACref, MAXACref, cost}   //???VinDC pode variar tem range
@@ -211,7 +214,7 @@ float Pminpanels, ItotalPVpanels, VtotalPVpanels, Eb, DODdaycalc, IminDCbus, equ
 
 ////definir arranjos de painéis solares para tentativa de projeto ótimo NPS, NPP
 
-arrang = nondet_uint();
+//arrang = nondet_uint();
 
 //	NPP = 1; //arrangement for series connection
 //	NPS = ((Pminpanels-1) / Pmref)+1;  //arrangement for series connection

### 2020-02-07 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 
-Moreover, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers.
-Moreover, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side.
+Besides that, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers.
+Furthermore, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side.
 Then the controller can be overcharged during this operation and to burn.

### 2020-02-07 Tex/Old text/chapters/chapterverification.tex
thesis update

@@
 The first automated verification is the sizing check (line 3), if an error is found then the algorithm stops.
-In order to perform the sizing check, the algorithm uses Equations \eqref{eq:NTPmin}, \eqref{eq:NPSmin} and \eqref{eq:NPPmin} to verify the PV panel, Equations \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries, Equations \eqref{eq:vcvsystem}, \eqref{eq:icmin} and \eqref{eq:icicmin} to verify the charge controller; and Equations \eqref{eq:vindc}, \eqref{eq:voutac} and \eqref{eq:invcheck} to verify the inverter.
+In order to perform the sizing check, the algorithm uses Equations \eqref{eq:Ecorrected}, and \eqref{eq:Pminpanel} to verify the PV panel, Equations \eqref{eq:Ebat}, \eqref{eq:DODday}, \eqref{eq:Idcbus}, \eqref{eq:Cbank}, and \eqref{eq:batcheck} to verify the batteries, Equations \eqref{eq:Icmin}, \eqref{eq:Vcmin}, \eqref{eq:vcvsystem}, \eqref{eq:icmin} and \eqref{eq:icicmin} to verify the charge controller; and Equations \eqref{eq:vindc}, \eqref{eq:voutac} and \eqref{eq:invcheck} to verify the inverter.
 

### 2020-02-07 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \REQUIRE weather data (temperature, solar irradiance), list of equipment (data sheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis)
- \ENSURE FAIL with counterexample showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available
+  \REQUIRE weather data (temperature, solar irradiance); list of PV panels, controllers, batteries, and inverters datasheet information and cost; design requirements (load curve, peak demand, load surge power, daily energy consumption, battery autonomy, AC voltage); design assumptions (battery state of charge, depth of discharge, criteria and objectives for technical and cost analysis)
+ \ENSURE FAIL with counterexample showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment
   \STATE Initialize variables \\
-  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
-%  \STATE Declare list of controllers data and cost \\
-%  \STATE Declare list of batteries data and cost \\
-%  \STATE Declare list of inverters data and cost \\
   \STATE Declare the maximum possible cost $MaxCost$  \\
-  \STATE Declare power demand, power peak, energy consumption \\
-  \STATE Declare battery autonomy, depth of discharge, AC voltage \\
-  \FOR {$HintCost=0$ to $MaxCost$}
+  \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
+  \FOR {$HintCost=MinCost$ to $MaxCost$}
  	\STATE Declare non-deterministic variable to select PV Panel from list \\
@@
  	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
- 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
-	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
+ 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
+	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
+	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{mref}))$ \\
+	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
+	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
  	\STATE Calculate $C_{bank}$ \\
-	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
-	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
- 	\STATE Calculate $I_{sc,amb}$ \\
- 	\STATE Calculate $I_{c,min}$ \\
- 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
-	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
+	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BT}$ \\
+	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
+ 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
+	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
 	\STATE non-deterministic variables hold feasible equipment and cost  \\

### 2020-02-09 code/opt_PVcode_rev10_case1.c
code update

@@ -2,7 +2,7 @@
  ============================================================================
  Name        : opt_PVcode_rev7_CASEx
  Author      : Alessandro Trindade
- Version     : rev7 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method
+ Version     : rev10 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method
  Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
  //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
  ============================================================================*/
@@ -120,29 +120,28 @@ unsigned char nondet_uchar();
 
 
 int FHintCost(void){
-	int lowervalue, cost=0, cont;
-	lowervalue=(int)PanelData[0][12];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)PanelData[cont][12] < lowervalue) lowervalue=(int)PanelData[cont][12];
-	}
-	cost = lowervalue;
-	lowervalue=(int)BatteryData[0][5];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)BatteryData[cont][5] < lowervalue) lowervalue=(int)BatteryData[cont][5];
-	}
-	cost = cost+lowervalue;
-	lowervalue=(int)ControllerData[0][5];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)ControllerData[cont][5] < lowervalue) lowervalue=(int)ControllerData[cont][5];
-	}
-	cost = cost+lowervalue;
-	lowervalue=(int)InverterData[0][5];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)InverterData[cont][5] < lowervalue) lowervalue=(int)InverterData[cont][5];
-	}
-	cost = cost+lowervalue;
-//	cost = (cost + lowervalue) + (cost + lowervalue)*0.05+20*289.64;
-	return(cost);
+//	int lowervalue, cost=0, cont;
+//	lowervalue=(int)PanelData[0][12];
+//	for (cont=1; cont <= 9; cont++) {
+//		if ((int)PanelData[cont][12] < lowervalue) lowervalue=(int)PanelData[cont][12];
+//	}
[…]

### 2020-02-09 code/opt_PVcode_rev11_case1.c

@@ -2,7 +2,7 @@
  ============================================================================
  Name        : opt_PVcode_rev7_CASEx
  Author      : Alessandro Trindade
- Version     : rev7 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method
+ Version     : rev10 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method
  Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
  //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
  ============================================================================*/
@@ -120,29 +120,28 @@ unsigned char nondet_uchar();
 
 
 int FHintCost(void){
-	int lowervalue, cost=0, cont;
-	lowervalue=(int)PanelData[0][12];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)PanelData[cont][12] < lowervalue) lowervalue=(int)PanelData[cont][12];
-	}
-	cost = lowervalue;
-	lowervalue=(int)BatteryData[0][5];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)BatteryData[cont][5] < lowervalue) lowervalue=(int)BatteryData[cont][5];
-	}
-	cost = cost+lowervalue;
-	lowervalue=(int)ControllerData[0][5];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)ControllerData[cont][5] < lowervalue) lowervalue=(int)ControllerData[cont][5];
-	}
-	cost = cost+lowervalue;
-	lowervalue=(int)InverterData[0][5];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)InverterData[cont][5] < lowervalue) lowervalue=(int)InverterData[cont][5];
-	}
-	cost = cost+lowervalue;
-//	cost = (cost + lowervalue) + (cost + lowervalue)*0.05+20*289.64;
-	return(cost);
+//	int lowervalue, cost=0, cont;
+//	lowervalue=(int)PanelData[0][12];
+//	for (cont=1; cont <= 9; cont++) {
+//		if ((int)PanelData[cont][12] < lowervalue) lowervalue=(int)PanelData[cont][12];
+//	}
[…]

### 2020-02-09 code/opt_PVcode_rev12_case1.c

@@ -2,7 +2,7 @@
  ============================================================================
  Name        : opt_PVcode_rev7_CASEx
  Author      : Alessandro Trindade
- Version     : rev7 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method
+ Version     : rev10 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method
  Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
  //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
  ============================================================================*/
@@ -120,29 +120,28 @@ unsigned char nondet_uchar();
 
 
 int FHintCost(void){
-	int lowervalue, cost=0, cont;
-	lowervalue=(int)PanelData[0][12];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)PanelData[cont][12] < lowervalue) lowervalue=(int)PanelData[cont][12];
-	}
-	cost = lowervalue;
-	lowervalue=(int)BatteryData[0][5];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)BatteryData[cont][5] < lowervalue) lowervalue=(int)BatteryData[cont][5];
-	}
-	cost = cost+lowervalue;
-	lowervalue=(int)ControllerData[0][5];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)ControllerData[cont][5] < lowervalue) lowervalue=(int)ControllerData[cont][5];
-	}
-	cost = cost+lowervalue;
-	lowervalue=(int)InverterData[0][5];
-	for (cont=1; cont <= 9; cont++) {
-		if ((int)InverterData[cont][5] < lowervalue) lowervalue=(int)InverterData[cont][5];
-	}
-	cost = cost+lowervalue;
-//	cost = (cost + lowervalue) + (cost + lowervalue)*0.05+20*289.64;
-	return(cost);
+//	int lowervalue, cost=0, cont;
+//	lowervalue=(int)PanelData[0][12];
+//	for (cont=1; cont <= 9; cont++) {
+//		if ((int)PanelData[cont][12] < lowervalue) lowervalue=(int)PanelData[cont][12];
+//	}
[…]

### 2020-02-13 code/opt_PVcode_rev13_case2.c
code update

@@ -27,7 +27,7 @@ int G = 800;
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
 
 //data from the house
-int Phouse = 342, Psurge = 342, Econsumption = 3900;
+int Phouse = 814, Psurge = 980, Econsumption = 4800;
 
 //must define
 int MaxCost=10000; //10 million maximum cost just to control the loop of main function

### 2020-02-13 code/opt_PVcode_rev13_case3.c

@@ -27,7 +27,7 @@ int G = 800;
 float Tref = 298.15; //reference temperature is 25oC or 298.15K
 
 //data from the house
-int Phouse = 342, Psurge = 342, Econsumption = 3900;
+int Phouse = 815, Psurge = 980, Econsumption = 4880;
 
 //must define
 int MaxCost=10000; //10 million maximum cost just to control the loop of main function

### 2020-02-13 code/opt_PVcode_rev13_case4.c

@@ -8,13 +8,26 @@
  ============================================================================*/
 
 //case studies
-//case1       int Phouse = 342, Psurge = 342, Econsumption = 3900;
-//case2       int Phouse = 814, Psurge = 980, Econsumption = 4800;
-//case3       int Phouse = 815, Psurge = 980, Econsumption = 4880;
-//case4       int Phouse = 253, Psurge = 722, Econsumption = 3600;
-//case5       int Phouse = 263, Psurge = 732, Econsumption = 2500;
-//case6       int Phouse = 322, Psurge = 896, Econsumption = 4300;
-//case7       int Phouse = 1586, Psurge = 2900, Econsumption = 14400;
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
+// int loadcurve[24] = {45,16,16,16,16,16,0,0,0,72,72,222,150,150,0,0,72,72,814,814,814,742,742,16};
[…]

### 2020-02-13 code/opt_PVcode_rev13_casex.c

@@ -8,13 +8,26 @@
  ============================================================================*/
 
 //case studies
-//case1       int Phouse = 342, Psurge = 342, Econsumption = 3900;
-//case2       int Phouse = 814, Psurge = 980, Econsumption = 4800;
-//case3       int Phouse = 815, Psurge = 980, Econsumption = 4880;
-//case4       int Phouse = 253, Psurge = 722, Econsumption = 3600;
-//case5       int Phouse = 263, Psurge = 732, Econsumption = 2500;
-//case6       int Phouse = 322, Psurge = 896, Econsumption = 4300;
-//case7       int Phouse = 1586, Psurge = 2900, Econsumption = 14400;
+//HOUSE1 
+// int loadcurve[24] = {118,118,118,46,46,46,95,95,170,170,296,242,242,95,95,95,95,95,342,288,288,288,288,118};
+// int Phouse = 501, Psurge = 501, Econsumption = 3900;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE2 
+// int loadcurve[24] = {136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136};
+// int Phouse = 253, Psurge = 722, Econsumption = 3600;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE3 
+// int loadcurve[24] = {113,113,113,113,113,113,67,67,217,97,97,97,97,97,97,97,97,97,263,113,113,113,113,113};
+// int Phouse = 263, Psurge = 732, Econsumption = 2500;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE4 
+// int loadcurve[24] = {207,207,207,135,135,135,66,66,161,161,233,253,248,66,66,66,66,66,302,317,322,302,302,207};
+// int Phouse = 322, Psurge = 896, Econsumption = 4300;
+// int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+//HOUSE5 
[…]

### 2020-02-13 code/teste_eb.c

@@ -1,0 +1,53 @@
+int MaxCost=10000; //10 million maximum cost just to control the loop of main function
+int Vsystem = 24;  //12V, 24V, 36V or 48V: DC Bus voltage definition
+int autonomy = 48; //autonomy in hours
+int SOClimit = 75, SOCabsorption = 95, SOCfull = 100, Vbat = 12, VAC = 127;
+int Econsumption = 3900;
+float nb=0.85, nc=0.93, ni=0.98;
+float Insol = 3.80;
+
+//global variables
+float SOC = 100; //battery is charged when starts the verification
+extern void __VERIFIER_error() __attribute__ ((__noreturn__));
+extern void __VERIFIER_assume(int expression);
+unsigned int nondet_uint();
+unsigned char nondet_uchar();
+
+int main (){
+	float Ecorrected, Pminpanels, ItotalPVpanels, VtotalPVpanels, Eb, DODdaycalc;
+	int NTP, NPmin, NPP, NPS, NBC, NBP, NPPmin, NBtotal,DODmax;
+	float Pmref = 330, Imref=8.88, Vmref=37, IC=40, VCmax=150;
+
+	//Econsumption = energy consumed in one day from the house
+	Ecorrected = Econsumption / (nb*nc*ni);
+
+	Pminpanels = 1.25 * Ecorrected / Insol;
+
+NPmin = ((Pminpanels -1)/ Pmref)+1;
+
+		NPP = 2;
+		if ((NPmin % 2) == 0) NPS = NPmin/2; //even number
+		else NPS = (NPmin + 1)/2; //odd number
+
+NTP = NPS * NPP;
+
+//checking power from PV panels
+/////////////////////////////////////__VERIFIER_assume  (Pminpanels <= (NPS*NPP*Pmref));
+
+//checking voltage and current from the PV panel and the controller
+ItotalPVpanels = NPP * Imref;
+__VERIFIER_assume ( (IC >= ItotalPVpanels) );
+
+VtotalPVpanels = NPS * Vmref;
+__VERIFIER_assume ( (VCmax >= VtotalPVpanels) );
+
+DODmax = (100-SOClimit)*2;
+//checking batteries
+Eb = (autonomy/24) * Ecorrected*100/DODmax;
+
+
+if (!(Eb > 15000)) { __VERIFIER_error(); }
+	return 0;
+}
+
+

### 2020-02-13 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 The battery is used to store the extra power from the PV system.
-A charge controller is necessary for this type of system because it insures that the battery ios charged with the correct voltage and current.
+A charge controller is necessary for this type of system because it insures that the battery is charged with the correct voltage and current.
 Extra charging and deep discharging can reduce the battery life \cite{Kim}.
+The controller includes a DC-DC converter that is not shown in Fig.\ref{fig:regSPV2}, but it is inherent of a typical MPPT controller.
 

### 2020-02-13 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
   \REQUIRE weather data (temperature, solar irradiance); list of PV panels, controllers, batteries, and inverters datasheet information and cost; design requirements (load curve, peak demand, load surge power, daily energy consumption, battery autonomy, AC voltage); design assumptions (battery state of charge, depth of discharge, criteria and objectives for technical and cost analysis)
- \ENSURE FAIL with counterexample showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment
+ \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
   \STATE Initialize variables \\
@@
 	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
- 	\STATE Calculate $C_{bank}$ \\
-	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BT}$ \\
+ 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
+	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
 	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
@@
 Our synthesis algorithm will synthesize constant values; 
-it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers and inverters (line $2$).
-After that, we define user requirements, i.e.
-house requirements and design definitions, from lines $4$ and $5$.
+it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers and inverters.
+Moreover, we define design (house) requirements and design assumptions.
+The assumptions are present in sections~\ref{sec:assumptions} and~\ref{sec:OptAssumptions}.
 
-The \textit{for}-loop started at line $6$ controls the lowest cost of the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $22$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value at line $6$ is just a very high value inserted as a limit to the \textit{for}-loop, that will never be reached because the optimal solution will be found first.
+The \textit{for}-loop started at line $4$ controls the lowest cost of the PV solution.
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $21$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+The $MaxCost$ value at line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
 
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$).
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (lines $5$ to $8$).
 This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.
 
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb} and Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $11$ to $17$).
-The directive \textit{assume} (lines $15$, $18$ and $19$)
-ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of Lines $15$, $18$ and $19$.
-Line $15$ is specific to the charge controller voltage check.
-Line $18$ checks the inverter check $I_{c}$, the charge controller DC input voltage $V_{in}DC$, and charge controller AC output voltage $V_{in}DC$ check.
-Line $19$ ensures the power demand and the surge power of the inverter.
-Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $21$).
-This cost is the equivalent to ~\ref{eq:LCC}, as described in Section ~\ref{sec:optcriteria}.
+Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $9$ to $15$).
+The directive \textit{assume} (lines $11$, $16$, $17$ and $18$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of lines $11$, $16$, $17$ and $18$.
+Line $11$ is specific to PV panels.
+Line $16$ is for the battery bank.
+Line $17$ is the charge controller voltage check.
+Line $18$ does the inverter check and ensures the power demand and the surge power of the inverter.
+Therefore, our synthesis algorithm reaches line $19$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $20$).
+This cost is the equivalent to~\ref{eq:LCC}, as described in Section~\ref{sec:optcriteria}.
 
@@
 
-In line $2$ of Algorithm~\ref{alg:opt-algorithm}, the synthesis engine is provided with a list of forty items of equipment from ten different manufacturers in order to allow the engine to choose from among all items of PV sizing.
+As input of Algorithm~\ref{alg:opt-algorithm}, the synthesis engine is provided with a list of forty items of equipment from ten different manufacturers in order to allow the engine to choose from among all items of PV sizing.
 The necessary technical information was collected from data sheet of each item.
@@
 
-With regard to batteries, the voltage of the system (DC bus) is set at $24$ V DC (but this can be adjusted to $12$ or $48$ V in the code).
+With regard to batteries, the voltage of the system (DC bus) is set at $24$ V DC, but this can be adjusted to $12$ or $48$ V in the code.
 
@@
 However, this CPAchecker time-out limitation is removed, the verifier is able to solve the optimization in $44.97$ hours.
-The violation (SAT result) indicated in Table~\ref{tab1}
-is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
+
+The violation (SAT result) indicated all over the Table~\ref{tab1} 
+is the $assert$ of line $21$ from Algorithm~\ref{alg:verification-algorithm}.
 %The results were tested by manual PV sizing and were sound (\textit{RQ1}).

### 2020-02-13 Tex/Old text/chapters/introduction.tex
thesis update

@@
 
-In this section, we discuss only the use of formal methods in electrical systems in general since the optimization of PV sizing is currently not obtained by formal methods or even program synthesis.
-%Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.
+In this section, we discuss initially the use of formal methods in electrical systems in general since the optimization of PV sizing is currently not obtained by formal methods or even program synthesis.
+Further, at the end of this section, we do a parallel about how software simulation tools address the issues related to solar PV systems.%Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.
 
@@
 
+Software simulation tools, when compared to the proposed automated verification techniques, has a common part of the approach that is the use of mathematical models in order to describe how the equipment or the PV system items behave itself over the time or when a specific input is applied to the system.
+However, simulation tools have a focus dependence with the choice of  \textbf{input} whereas the proposed techniques focus on the mathematical rigor of the solution and the search of an \textbf{output} that falsifies the expected requirements of the system~\cite{ClarkeHV18}.
+Therefore, simulation software focus on the inputs whereas our techniques focus on the outputs.
+
 %----------------------------------------------

### 2020-02-13 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
 In addition, the price of each item was obtained from available market quotation from internet, in US dollars.
-All the other currencies were converted to US dollars equivalents at the exchange rate of the day (May and June of 2019).
+Preferably, we sought equipment sold in the Brazilian market, in Reais $R\$$, having been converted to US dollars using the exchange rate of the day (May and June of 2019).
 
@@
 and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc -benchmark filename.c} version 1.8 in a configuration as bound model checking and with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
-Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
+An ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.
+
 The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purposes.
@@
 \hline
-Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
+Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
 \hline
@@
 \hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & TO & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
 \hline
-\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
+\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
 \hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & XX & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
 \hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
 \hline
@@
 \hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & XX & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
 \hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & XX & YY & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
 \hline
@@
 
-CBMC and ESBMC are unable to produce any conclusive result.
+An internal failure was presented by ESBMC when using Z3 solver in all case studies.
+It corresponds to a 'bug' at the Z3 solver which will require an updated version of ESBMC to fix it.
+CBMC was unable to produce any conclusive result.
+\textit{Out of memory} situations occurred in all case studies.
+Those specific results partially answers the \textit{EQ2}
+
+ESBMC are unable to produce any conclusive result.
 \textit{Internal failure}, \textit{time out}, or \textit{out of memory} situations occurred; this partially answers the \textit{EQ2}.
-Note that the internal failure presented by ESBMC was a Z3 solver issue (a bug), which will require an updated version of ESBMC to fix.
 Similar to CPAchecker, if the \textit{time out} is removed from ESBMC with the SMT solver Boolector, then the verifier is able to obtain the automated synthesis in $73.18$ hours for case study $2$.
-CBMC, on the other hand,  could present some result only if the RAM memory of the system was expanded in order to avoid the out of memory issue.
 

### 2020-02-13 code/opt_PVcode_rev13_case6.c
code update

@@ -1,0 +1,301 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev13_CASEx
+ Author      : Alessandro Trindade
+ Version     : rev13 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method (5 equipment)
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//case1       int Phouse = 342, Psurge = 342, Econsumption = 3900;
+//case2       int Phouse = 814, Psurge = 980, Econsumption = 4800;
+//case3       int Phouse = 815, Psurge = 980, Econsumption = 4880;
+//case4       int Phouse = 253, Psurge = 722, Econsumption = 3600;
+//case5       int Phouse = 263, Psurge = 732, Econsumption = 2500;
+//case6       int Phouse = 322, Psurge = 896, Econsumption = 4300;
+//case7       int Phouse = 1586, Psurge = 2900, Econsumption = 14400;
+
+//data from Manaus
+int minSolarIrrad [24] = {0,0,0,0,0,0,25,135,274,422,509,537,503,505,430,281,80,10,0,0,0,0,0,0};
+int maxSolarIrrad [24] = {0,0,0,0,0,4,87,295,487,648,751,852,817,742,610,418,128,51,0,0,0,0,0,0};
+int minTemp [12] = {23,23,23,23,23,23,23,23,23,24,24,23};
+int maxTemp [12] = {30,30,30,30,30,30,30,31,32,32,31,30};
+float Insol = 3.80; //(kWh/m2/day CRESESB 2016)
+int Gref = 1000; //reference irradiance is 1000 W/m²
+int G = 800;
+float Tref = 298.15; //reference temperature is 25oC or 298.15K
+
+//data from the house
+int Phouse = 322, Psurge = 896, Econsumption = 4300;
+
+//must define
+int MaxCost=10000; //10 million maximum cost just to control the loop of main function
[…]

### 2020-02-13 code/opt_PVcode_rev13_case7.c

@@ -1,0 +1,301 @@
+/*
+ ============================================================================
+ Name        : opt_PVcode_rev13_CASEx
+ Author      : Alessandro Trindade
+ Version     : rev13 - Feb 2020: 40 equipment, lowerbound defined by SW, better HintCost, reviewed sizing method (5 equipment)
+ Description : stand-alone PV sizing optimization (Universal: CBMC, ESBMC, UAutomizer and CPChecker)
+ //assume (exp);  MUST BE REPLACE BY:   if (!expr) { __VERIFIER_error(); }
+ ============================================================================*/
+
+//case studies
+//case1       int Phouse = 342, Psurge = 342, Econsumption = 3900;
+//case2       int Phouse = 814, Psurge = 980, Econsumption = 4800;
+//case3       int Phouse = 815, Psurge = 980, Econsumption = 4880;
+//case4       int Phouse = 253, Psurge = 722, Econsumption = 3600;
+//case5       int Phouse = 263, Psurge = 732, Econsumption = 2500;
+//case6       int Phouse = 322, Psurge = 896, Econsumption = 4300;
+//case7       int Phouse = 1586, Psurge = 2900, Econsumption = 14400;
+
+//data from Manaus
+int minSolarIrrad [24] = {0,0,0,0,0,0,25,135,274,422,509,537,503,505,430,281,80,10,0,0,0,0,0,0};
+int maxSolarIrrad [24] = {0,0,0,0,0,4,87,295,487,648,751,852,817,742,610,418,128,51,0,0,0,0,0,0};
+int minTemp [12] = {23,23,23,23,23,23,23,23,23,24,24,23};
+int maxTemp [12] = {30,30,30,30,30,30,30,31,32,32,31,30};
+float Insol = 3.80; //(kWh/m2/day CRESESB 2016)
+int Gref = 1000; //reference irradiance is 1000 W/m²
+int G = 800;
+float Tref = 298.15; //reference temperature is 25oC or 298.15K
+
+//data from the house
+int Phouse = 1586, Psurge = 2900, Econsumption = 14400;
+
+//must define
+int MaxCost=10000; //10 million maximum cost just to control the loop of main function
[…]

### 2020-02-13 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
 \item Case Study 6: Power peak: 322 W, power surge: 896 W, energy consumption: 4,300 Wh/day, battery autonomy: 48 h;
-\item Case Study 7: Power peak: 1,586 W, power surge: 2,900 W, energy consumtion: 14,000 Wh/day, battery autonomy: 48h.
+\item Case Study 7: Power peak: 1,586 W, power surge: 2,900 W, energy consumption: 14,000 Wh/day, battery autonomy: 48h.
 \end{itemize}
@@
 \hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & TO & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
 \hline
@@
 \hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & XX & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO & TO & Not possible \\
 \hline
@@
 \hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S+2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S+2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
 \hline

### 2020-02-14 Tex/Old text/chapters/chapter02.tex
thesis update

@@
 \item Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
-\item Back-end: supports SAT and SMT solvers to discharge verification conditions.
+\item Back-end: supports SAT and SMT solvers to discharge verification conditions (VCs).
 \end{itemize}
@@
 \item Preprocessing steps deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally 
-\item The SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+\item The SMT solving stage, where all constraints (C) and properties (P) of the system are encoded into SMT and checked for satisfiability ($C \wedge \neg P$).
 \end{itemize}

### 2020-02-14 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
 	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
-	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{mref}))$ \\
+	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{m,ref}))$ \\
 	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
@@
 Note that the process described here is completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+
+The Algorithm~\ref{alg:opt-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verified ($C \wedge \neg P$).
+The quantifier-free formulae $C$ and $P$ are shown in Eq.~\ref{eq:quant_free_formulae_c} and Eq.~\ref{eq:quant_free_formulae_p}, respectively.
+Where $nd\_uchar$ denotes a non-deterministic unsigned char value.
+The conditional expression $ite(f,t_1,t_2)$ takes a Boolean formula $f$ and depending on its value selects either the second or the third argument.
+The function $select(a,i)$ denotes the value of $a$ at index position $i$.
+Worth to mention that it was removed from the representation all the bounds checks for arrays and matrices, and the division by zero check.
+During the verification process, the arithmetic operators induce checks to ensure that the arithmetic operations do not overflow and/ or underflow.
+
+\begin{equation}
+\label{eq:quant_free_formulae_c}
+\begin{scriptsize}
+C := \left [ \begin{array}{ll} 
+	panelchoice = nd\_uchar \\
+	\wedge \, \, batterychoice = nd\_uchar \\
+	\wedge \, \, controllerchoice = nd\_uchar \\
+	\wedge \, \, inverterchoice = nd\_uchar \\
+	\wedge \, \, P_{m,ref} = select \, (PanelData \, [panelchoice][8]) \\
+	\wedge \, \, I_{m,ref} = select \, (PanelData \, [panelchoice][9]) \\
+	\wedge \, \, V_{m,ref} = select \, (PanelData \, [panelchoice][10]) \\
+	\wedge \, \, Panel_{Cost} = select \, (PanelData \, [panelchoice][12]) \\
+	\wedge \, \, \eta_{b} = select \, (BatteryData \, [batterychoice][0]) \\
+	\wedge \, \, Vbat = select \, (BatteryData \, [batterychoice][1]) \\
+	\wedge \, \, Capacity = select \, (BatteryData \, [batterychoice][2]) \\
+	\wedge \, \, Battery_{Cost} = select \, (BatteryData \, [batterychoice][5]) \\
+	\wedge \, \, \eta_{c} = select \, (ControllerData \, [controllerchoice][0]) \\
+	\wedge \, \, I_{c} = select \, (ControllerData \, [controllerchoice][1]) \\
+	\wedge \, \, V_{c,max} = select \, (ControllerData \, [controllerchoice][4]) \\
+	\wedge \, \, Controller_{Cost} = select \, (ControllerData \, [controllerchoice][5]) \\
+	\wedge \, \, \eta_{i} = select \, (InverterData \, [inverterchoice][0]) \\
+	\wedge \, \, V_{in,DC} = select \, (InverterData \, [inverterchoice][1]) \\
+	\wedge \, \, V_{out,AC} = select \, (InverterData \, [inverterchoice][2]) \\
+	\wedge \, \, P_{AC,ref} = select \, (InverterData \, [inverterchoice][3]) \\
+	\wedge \, \, MAX_{AC,ref} = select \, (InverterData \, [inverterchoice][4]) \\
+	\wedge \, \, Inverter_{Cost} = select \, (InverterData \, [inverterchoice][5]) \\
+	\wedge \, \, E_{corrected} = E_{consumption} / (\eta_{b} \times \eta_{c} \times \eta_{i}) \\
+	\wedge \, \, P_{min,panels} = 1.25 \times E_{corrected} / Insolation \\
+	\wedge \, \, N_{Pmin} = (int)(P_{min,panels} -1) / P{m,ref} + 1 \\
+	\wedge \, \, N_{PP} = 2 \\
+	\wedge \, \, N_{PS} = ite ( ((N_{Pmin} \% 2) == 0), (N_{Pmin}/2), ((N_{Pmin}+1) / 2) ) \\
+	\wedge \, \, N_{TP} = N_{PP} \times N_{PS} \\
+	\wedge \, \, I_{total,PVpanels} = 2 \times I_{m,ref} \\
+	\wedge \, \, V_{total,PVpanels} = N_{PS} \times V_{m,ref} \\
+	\wedge \, \, DOD_{max} = (100-SOC_{min}) \times 2 \\
+	\wedge \, \, E_{b} = (autonomy/24) \times E_{corrected} \times 100/ DOD_{max} \\
+	\wedge \, \, I_{min,DCbus} = E_{b}/(float)V_{system} \\
+	\wedge \, \, N_{BS} = 24 / Vbat \\
+	\wedge \, \, N_{BP} = ((I_{min,DCbus} - 1) / Capacity + 1) \\
+	\wedge \, \, N_{Btotal} = N_{BS} \times N_{BP} \\
+	\wedge \, \, F_{obj} = N_{TP} \times Panel_{Cost} + N_{Btotal} \times Battery_{Cost} + Controller_{Cost} + Inverter_{Cost} + O\&M_{Cost} + Inst_{Cost} \\
+              \end{array} \right ]  \\ 
+\end{scriptsize}
+\end{equation}
+
+\begin{equation}              
+\label{eq:quant_free_formulae_p}
+\begin{scriptsize}
+P := \left [ \begin{array}{ll} 
+	((panelchoice \geq 0) \, \, \wedge \, \, (panelchoice \leq 9)) \\
+	\wedge \, \, ((batterychoice \geq 0) \, \, \wedge \, \, (batterychoice \leq 9)) \\
+	\wedge \, \, ((controllerchoice \geq 0) \, \, \wedge \, \, (controllerchoice \leq 9)) \\
+	\wedge \, \, ((inverterchoice \geq 0) \, \, \wedge \, \, (inverterchoice \leq 9)) \\
+	\wedge \, \, (I_{c} \geq I_{total,PVpanels}) \\
+	\wedge \, \, (V_{c,max} \geq V_{total,PVpanels}) \\
+	\wedge \, \, ((V_{c,max} \times I_{C} \times \eta_{c}) \geq P_{AC,ref}) \\
+	\wedge \, \, (V_{in,DC} \geq 24)  \\
+	\wedge \, \, ((V_{out,AC} \geq OutletVoltage-10\%) \, \, \wedge \, \, (V_{out,AC} <= OutletVoltage+10\%)) \\
+	\wedge \, \, ((MaximumLoadPower \leq P_{AC,ref}) \, \, \wedge \, \, (SurgeLoadPower \leq MAX_{AC,ref})) \\
+	\wedge \, \, (F_{ob} > Value_{Iterative,optimal}) \\
+              \end{array} \right ]  \\
+\end{scriptsize}
+\end{equation}
 

### 2020-02-14 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
 \hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO & TO & Not possible \\
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P+2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
 \hline
@@
 \hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & XX & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
 \hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & XX & YY & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
 \hline

### 2020-02-14 Tex/Old text/chapters/chapteroptimization.tex
thesis update

@@
 with $1.7$ GHz and $4$ GB RAM, running Windows 10. 
-The experiments were conducted with a predefined time-out of $240$ minutes.
+The experiments were conducted with a predefined time-out of $660$ minutes.
 
-Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock},
+Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} version 6.0.0 configured for incremental loop unwinding verification with the  Boolector 3.0.1 solver~\cite{Brummayer},  %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, ESBMC {Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}
 and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc -benchmark filename.c} version 1.8 in a configuration as bound model checking and with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
@@
 \hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
 \hline
@@
 \hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P+2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
 \hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
 \hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S+2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S+2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
 \hline
@@
 
-CPAchecker was able to synthesize optimal sizing in six 
-out of the seven case studies (cases $1$ - $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
-Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing on the left size as the integer $8$ for the solar panel (which is the model RSM36-6-150P from the manufacturer Risen), battery $0$ refers to the model 12MF80 of 80 Ah from Moura, charge controller $1$ refers to the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ refers to the model IP350-11 from Epever (750 W).
+The violation (SAT result) indicated all over the Table~\ref{tab1} 
+is the $assert$ of line $21$ from Algorithm~\ref{alg:verification-algorithm} and indicates that an optimal solution was found.
+
+CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.
+
+CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $254.25$ to $548$ minutes.
+Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left size as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron  Energy, and the inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power.
 The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.
 
-Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e.
-it was not solved within $240$ minutes.
-This is illustrated in Fig.~\ref{fig:cpaoptcase7}.
-However, this CPAchecker time-out limitation is removed, the verifier is able to solve the optimization in $44.97$ hours.
-
-The violation (SAT result) indicated all over the Table~\ref{tab1} 
-is the $assert$ of line $21$ from Algorithm~\ref{alg:verification-algorithm}.
-%The results were tested by manual PV sizing and were sound (\textit{RQ1}).
-%, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.
+Case studies $2$, $3$, $6$, and $7$  led to a \textit{time out} result in CPAchecker, i.e.  it was not solved within $660$ minutes.
 
 \begin{figure}[h]
-\includegraphics[width=1.0\textwidth]{CPA_opt_c4.png}
+\fbox{\includegraphics[width=1.0\textwidth]{CPA_opt_c5.png}}
 \centering
-\caption{Counterexample generated by CPAchecker after validation of case 4 (file Counterexample.html).}
+\caption{Counterexample generated by CPAchecker after validation of case 5 (file Counterexample.html).}
 \label{fig:CPAoptc1}
@@
 
+An internal failure was presented by ESBMC when using Z3 solver in all case studies.
+It corresponds to a 'bug' in the Z3 solver which will require an updated version of ESBMC to fix it.
+However, when using the incremental BMC configuration of ESBMC with Boolector solver, the verifier engine was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response varying from $36.70$ to $620$ minutes.
+Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated.
+ESBMC with this configuration was not possible to obtain a optimal solution in cases $2$ and $7$.
+Case $2$ reached a  \textit{time out} result after $660$ minutes of processing.
+Moreover, case $7$ resulted in a UNSAT result, i.e the verifier engine was not possible to get a feasible solution considering the list of equipment.
+This SAT situation was reached after just $0.48$ minutes.
+
 \begin{figure}[h]
-\includegraphics[width=1.0\textwidth]{CPAchecker_timeout_case7.png}
+\fbox{\includegraphics[width=1.0\textwidth]{ESBMC_SAT_case3.png}}
 \centering
-\caption{CPAchecker time out result for case 7 optimization (file CPALog.txt).}
-\label{fig:cpaoptcase7}
+\caption{ESBMC counterexample for case 3 optimization.}
+\label{fig:esbmcoptcase3}
 \end{figure}
 
-An internal failure was presented by ESBMC when using Z3 solver in all case studies.
-It corresponds to a 'bug' at the Z3 solver which will require an updated version of ESBMC to fix it.
-CBMC was unable to produce any conclusive result.
-\textit{Out of memory} situations occurred in all case studies.
-Those specific results partially answers the \textit{EQ2}
-
-ESBMC are unable to produce any conclusive result.
-\textit{Internal failure}, \textit{time out}, or \textit{out of memory} situations occurred; this partially answers the \textit{EQ2}.
-Similar to CPAchecker, if the \textit{time out} is removed from ESBMC with the SMT solver Boolector, then the verifier is able to obtain the automated synthesis in $73.18$ hours for case study $2$.
+Those specific results partially answers the \textit{EQ2}.
 
@@
 
-Comparing the results of the formal synthesis against those of CPAchecker and HOMER Pro, it was observed that most results are quite similar, 
-in terms of technical solution and cost (cf. Table~\ref{tab1}).
+Comparing the results of the formal synthesis with CPAchecker, and ESBMC, against those of  HOMER Pro, it was observed some distinct results, in terms of technical solution and cost (cf.
+Table~\ref{tab1}).
+Related to performance there is a huge difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in opposite of an average of $234$ minutes for the automated synthesis technique.
 
-Particularly in the case of LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with differences varying from $0.23$\% to $17.4$\%.
-Even adopting the same price per kW for PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling.
-The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well on this discrepancy; however, it is not significant since the annual cost is too small when compared to the resulting LCC value.
+Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, always having a higher estimation from the automated synthesis technique.
+However, considering that the cost of individual item of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.
 
-However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by the automated synthesis tool were underestimated for that specific load.
+In one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool.
+The difference varied from $19$\% to $65$\%.
+In the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro.
+The difference was among $34$\% to $68$\%.
 
-In general, the PV panels and battery bank were larger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation.
-The mathematical models are different and particular parameters can be tuned as well in each approach, and that can justify the difference, which was presented in all the case studies.
-As a comparison, consider case study $1$: the optimal solution provided by HOMER Pro requires $7$ $times$ more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e.
-the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $500.4$ Ah ($6 \times 83.4$), while the synthesis tool presented an optimal solution with a total capacity of $420$ Ah ($4 \times 105$).
+Those discrepancies are not easy to address without some real systems validation.
+The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.
+
+As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e.
+the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.
 
 Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
-These solutions are closer to the result presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
+These solutions are closer to the results from PV panel, controller and inverter presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
+However the solution presented for the battery bank is very different.
 
@@
 Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
-Case study $3$ could not be simulated in HOMER Pro, because of its restriction on setting battery autonomy, thus leaving both without parameters to compare.
+Case study $2$ was solved just by the ESBMC verifier engine.
+Case study $3$ could not be simulated in HOMER Pro, because of its restriction on setting battery autonomy, thus leaving those three cases without parameters to compare.
 
@@
 
-Comparison of verifiers with the proposed automated synthesis using model checking was made, in order to obtain the optimal sizing of stand-alone solar PV systems, which showed that CPAchecker had the best overall performance.
-CBMC and ESBMC were not conclusive for all the cases, reaching the \textit{time out} stipulated ($240$ minutes) or being \textit{out of memory}.
-CPAchecker was unable to present a conclusive result only in case $7$ (\textit{time out}).
+Comparison of verifiers with the proposed automated synthesis using model checking was made, in order to obtain the optimal sizing of stand-alone solar PV systems, which showed that ESBMC had the best overall performance.
+CBMC was not conclusive for all the cases, and CPAchecker was unable to present a conclusive result in cases $2$, $3$, and $7$,  (\textit{time out}).
 
-A comparison with a specialized simulation tool was also made, however only $5$ case studies (case $1$, case $2$, case $4$, case $5$, and case $6$) compared to the presented result.
-Some limitations of the simulation tool, mainly related to not allowing battery autonomy setup, and the $time-out$ or $out of memory$ messages presented by the verifiers, restricted the comparison between the automated verification tools and the simulation tools.
-However, when the comparison was possible, it was noticeable that the LCC came very close, and that HOMER Pro overestimated the sizing.
+A comparison with a specialized simulation tool was also made, however only $4$ case studies (case $1$, case $4$, case $5$, and case $6$) compared to the presented result.
+Some limitations of the simulation tool, mainly related to not allowing battery autonomy setup, and the $time-out$ or $out \, of \, memory$ messages presented by the verifiers, restricted the comparison between the automated verification tools and the simulation tools.
+However, when the comparison was possible, it was noticeable that the LCC was not so distant, that HOMER Pro produces a bigger PV panel sizing, and moreover that the synthesis tool produces bigger battery bank.
 

### 2020-02-14 Tex/Old text/chapters/conclusion.tex
thesis update

@@
 
-The first contribution was presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method of validating a given stand-alone PV system.
+The first contribution was presented in~\autoref{chap:automatedverification}, we described and evaluated an automated verification method of validating a given stand-alone PV system.
 Our method, using model checking, can perform a size check and verify, over time, whether a PV system meets electrical requirements.
 There are various possible ways to perform that validation, such as testing, laboratory measuring, or even simulation.
-However, we developed an algorithm and a tool using model checking that is feasible and effective.
+However, we developed an algorithm and a tool using model checking that is feasible and effective, although our technique does not replace the others.
 Our results were supported by case studies, by data gathered from the field, and by interviews with PV owners.
 
-We analyzed five case studies of real PV systems deployed in five different sites, ranging from $975$ W to $1,300$ W (inverter specification), and the results of three state-of-the-art verification engines (ESBMC, CBMC, and CPAchecker).
-Although the verification method that we proposed takes longer than the simulation methods, it can avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$.
-We validate these results by the sized systems deployed in the field.
+We analyzed five case studies of real PV systems deployed in five different sites, ranging from $975$ W to $1,300$ W (inverter specification), and the results of three state-of-the-art verification engines (ESBMC, CBMC, and CPAchecker).The verification method with ESBMC was faster than the simulation method.
+We validate the overall results by the sized systems deployed in the field.
 
@@
 %
-In the comparison among verification engines, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented a better performance than CBMC (around four times faster), used less RAM than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB for CBMC and 19.2GB for CPAchecker) as expected and explained in Section~\ref{sec:ESBMC}.
+In the comparison among verification engines, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented a better performance than CBMC, used less RAM than CBMC and CPAchecker as expected and explained in Section~\ref{sec:ESBMC}.
 All our experimental results are sound since the PV owners and the monitoring system validated the possible flaws that the system could present in the field.
@@
 In addition, we again used the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
-In terms of performance and best results, CPAchecker was the most successful and used for the comparison with the simulation tool.
+In terms of performance and best results, ESBMC was the most successful and used for the comparison with the simulation tool.
 
 In summary, our synthesis proposal is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
-In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the component model, nominal current, and voltage.
+In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including the component model, nominal current, and voltage.
 We also cover the charge controller, which is unavailable in HOMER Pro.

### 2020-02-14 Tex/Old text/chapters/introduction.tex
thesis update

@@
 
-\textcolor{red}{Optimization is important when there exist (just) the requirements of the house to be electrified.
-In our particular case, we need a optimal PV system solution, in technical and economical terms, that can show us a list of equipment to be bought and how it will be connected together (configuration)}.
+Optimization is important when there exist (just) the requirements of the house to be electrified.
+In our particular case, we need a optimal PV system solution, in technical and economical terms, that can show us a list of equipment to be bought and how it will be connected together (configuration).
 
@@
 %----------------------------------------------
-
-\textcolor{red}{My comment: paragraphs broken in small and organized parts:}
 

### 2020-02-16 Tex/Old text/chapters/chapter04.tex
Thesis update
revised Chapter 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
-In this Chapter, we detail the adopted methodology to perform optimal sizing of stand-alone solar PV systems, more specifically using model checking.
+In this chapter, we detail the adopted methodology to perform optimal sizing of stand-alone solar PV systems, more specifically using model checking.
 Diagrams, flowcharts, and algorithms support and explain the solutions.
 
-Besides that, we present all the assumptions and premises adopted. This chapter supports as well the results/conclusions, with direct impact on it.
+Besides that, we present all the assumptions and premises adopted. This chapter supports the results/conclusions, with a direct impact on it.
 
 It is important to emphasize that the whole explanation about the theoretical basis of the subject discussed here is present in the previous chapter.
-In addition, we do suggest that previous reading must be done to facilitate the understanding.
+Besides, we do suggest that previous reading must be done to facilitate understanding.
 
+%------------------------------------------------------------------------
 \section{Optimal Sizing of Solar PV Systems}
+%------------------------------------------------------------------------
 
@@
 
-One more time, as depicted in automated verification process, the input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search.
-And the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.
+One more time, as depicted in the automated verification process, the input information is the same for all the methods, with the difference that in automated validation, it is possible to define the bound $k$ to restrict the design-space search.
+Furthermore, the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.
 
 \begin{figure}[h]
-\includegraphics[width=1.0\textwidth]{optimalsizingprocess2}
+\includegraphics[width=1.0\textwidth]{optimalsizingprocess2g}
 \centering
@@
 
+ %------------------------------------------------------
 \subsection{Variant of CEGIS} 
+%------------------------------------------------------
 
-In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section ~\ref{sec:ProgramSynthesis}, Fig.~\ref{Counter-Example-Guided-Inductive-Synthesis}.
-This variant was created during this Thesis and it will be detailed in this Section.
+In Figure~\ref{CEGISalt}, it is illustrated a variant of CEGIS previously presented in Section~\ref{sec:ProgramSynthesis}, Fig.~\ref{Counter-Example-Guided-Inductive-Synthesis}.
+This variant was created during this Thesis, and it will be detailed in this section.
 
@@
 
-Examples of specification used by the proposed method include solar insolation (site dependent), house power demand, house consumption energy, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.
-Design assumptions are considered project specification as well.
+Examples of specifications used by the proposed method include solar insolation (site dependent), house power demand, house consumption energy, estimated load curve, AC voltage, and battery autonomy.
+We provide a list of equipment specifications and prices from different manufacturers and models.
+Design assumptions are considered project specifications as well.
 The assumptions regarding the optimal sizing are listed in Section~\ref{sec:OptAssumptions}.
 
-There are four particular differences related to the traditional CEGIS described in Figure ~\ref{Counter-Example-Guided-Inductive-Synthesis} when compared to the variant CEGIS used in the proposed approach:
+There exist four distinct differences related to the traditional CEGIS described in Figure ~\ref{Counter-Example-Guided-Inductive-Synthesis} when compared to the variant CEGIS used in the proposed approach:
 
 \begin{itemize}
-\item There exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
-\item If the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} 
+\item There exists no test vector, and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+\item If the {\sc Verify} phase is unsuccessful; then a new candidate is generated by {\sc Synthesize} 
 \item The lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
-\item As a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate that could be feasible in the next iteration with a new lower bound.
+\item As a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase.
+This means that a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate that could be feasible in the next iteration with a new lower bound.
 \end{itemize}
 
-Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here we have used symbolic software verifiers based on SMT solvers.
+Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here, we have used symbolic software verifiers based on SMT solvers.
 
@@
 Our synthesis algorithm will synthesize constant values; 
-it starts with the input of manufacturers data and prices of PV panels, batteries, 
-charge controllers and inverters (line $2$). After that, we define user requirements, i.e., 
+it starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers, and inverters (line $2$). After that, we define user requirements, i.e., 
 house requirements and design definitions, from lines $4$ and $5$.
 
-The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. 
-In particular, it starts with cost $0$ and stops only when the algorithm finds a 
+The \textit{for}-loop started at line $6$ controls the lowest cost to the PV solution. In particular, it starts with cost $0$ and stops when the algorithm finds a 
 feasible solution in which the cost breaks the $assertion$ stated in line $22$; 
-if that happens, then our algorithm has found an optimal solution, thereby stating 
-that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
+if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). 
 The $MaxCost$ value at line $6$ is just a very high value put as a limit 
@@
 
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant 
-from a given list of PV panels, controllers, batteries and inverters (lines $7$ to $10$). 
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (lines $7$ to $10$). 
 That procedure ensures that our synthesis engine checks all combinations of items 
@@
 
-If our algorithm does not find a feasible solution among the item of equipment that 
-were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., 
-the program finishes and does not find a solution, which indicates that it 
-was not possible to combine the items of each equipment in order to create a feasible solution.
+If our algorithm does not find a feasible solution from the equipment provided to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}).
+This means that the program finishes and does not find a solution, which indicates that it was not possible to combine the items of each equipment in order to create a feasible solution.
 
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate 
-solution regarding the constraints and user requirements. Related to our {\sc Verify} 
-phase the challenge is to find the lowest acquisition cost from a list of equipment and 
-components that is provided from the {\sc Synthesize} phase.
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements. Related to our {\sc Verify} 
+phase, the challenge is to find the lowest acquisition cost from a list of equipment and components that are provided from the {\sc Synthesize} phase.
 
-Note that the process described here is completely automated and that a validation is performed 
-by our {\sc Verify} phase to ensure that the approach is sound.
+Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Optimization Assumptions and Premises}
@@
 
-Here some premise are presented and some adopted assumptions are explained for the optimal sizing method, regarding the automated synthesis and simulation software.
+Here some premises are presented, and some adopted assumptions are explained for the optimal sizing method regarding the automated synthesis and simulation software.
 
 Regarding the line $2$ of Algorithm~\ref{alg:opt-algorithm}, 
-a list of forty equipment from ten different manufacturers was provided 
-to the synthesis engine in order to allow the choice of every item 
-of PV sizing. Data sheet from each item was necessary to collect 
-technical information. Moreover, the price of each item was obtained 
-from available quotations in the market, and if the currency was not in US dollars, 
+a list of forty equipment from ten different manufacturers was provided to the synthesis engine in order to allow the choice of every item of PV sizing.
+Datasheet from each item was necessary to collect technical information.
+Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars,
 then it was used the exchange rate of the day to convert it to US dollars.
 
-With respect to power reliability, this work will rely on the critical period solar 
-energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
-The usual way is to use loss of load probability (LOLP) or loss of power 
+Concerning power reliability, this work will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}. 
+The usual way is to use the loss of load probability (LOLP) or loss of power 
 supply probability (LPSP). However, based on the fact that here we 
@@
 	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
-This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
+This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every ten years).
 Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
@@
 
-On the subject of PV system optimization technique, we will adopt here the intuitive method 
-since the average value daily of solar irradiance is used in the mathematical model, 
-without considering the battery's state of charge, or even the random nature 
-of solar irradiation and meteorological conditions. Therefore, all the computational 
-effort will be concentrated in our automated synthesis algorithm.
+On the subject of PV system optimization technique, we will adopt here the intuitive method since the average value daily of solar irradiance is used in the mathematical model, 
+without considering the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions.
+Therefore, all the computational effort will be concentrated in our automated synthesis algorithm.
 
@@
 \begin{itemize}
-	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
-	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases.
+	\item HOMER Pro does not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
+	\item The optimization analysis of HOMER Pro allows defining a load curve and temperature according to data collected automatically from online databases.
 However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
-	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
-	\item HOMER Pro do not have a explicit equipment called charge controller.
-It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
+	\item Battery autonomy is not a parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
+	\item HOMER Pro does not have a piece of explicit equipment called a charge controller.
+It uses a controller resource that can perform in two different ways, according to the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
 During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
@@
 For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable;
+While in an ordinary house electrical load, 95\% is considered acceptable;
 	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
-	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
+	\item The premise adopted when using HOMER Pro was that the user does not know the optimal solution.
+In order to obtain this solution, it is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component.
+With that in mind, it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with the capacity of $83.4$ Ah according to HOMER Pro modeling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
@@
 
+%----------------------------------------------------
 \section{General Assumptions}
+%----------------------------------------------------
 
-The general assumptions for the scientific method of automated synthesis are the same presented at Chapter~\nameref{chap:methodology1}, related to the code in ANSI-C, to the bound $k$, to simulation tool comparative, and to the battery state of charge.
+The general assumptions for the scientific method of automated synthesis are the same presented at Chapter~\nameref{chap:methodology1}, related to the code in ANSI-C, to the bound $k$, to simulation tool comparative, and the battery state of charge.
 
+%----------------------------------------------------
 \section{Conclusion}
+%----------------------------------------------------
 
-In this Chapter we showed in details how the state-of-art computer science method of automated synthesis method was adapted in order to be used in stand-alone solar PV systems to obtain the optimal project sizing.
-Moreover, is was possible to picture how the proposed method compares with the traditional use of simulation tool for the same purpose.
+In this chapter, we have described in detail how the state-of-art computer science method of automated synthesis method was adapted in order to be used in stand-alone solar PV systems to obtain the optimal project sizing.
+Moreover, it was possible to picture how the proposed method compares with the traditional use of a simulation tool for the same purpose.
 
-Detailed diagrams, flowcharts and algorithms with pseudo-code were presented with the aim to support the proposed work and to facilitate the understanding.
-And even more so, the assumptions adopted for the automated verification and simulation software were listed, because those assumptions have impact at the results there will be presented at  \autoref{chap:automatedsynthesis}.
+Detailed diagrams, flowcharts, and algorithms with pseudo-code were presented with the aim to support the proposed work and to facilitate the understanding.
+Furthermore, even more so, the assumptions adopted for the automated verification and simulation software were listed because those assumptions have an impact on the results, there will be presented at \autoref{chap:automatedsynthesis}.

### 2020-02-16 Tex/Old text/chapters/conclusion.tex
revised Chapter 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-We analyzed five case studies of real PV systems deployed in five different sites, ranging from $975$ W to $1,300$ W (inverter specification), and the results of three state-of-the-art verification engines (ESBMC, CBMC, and CPAchecker).The verification method with ESBMC was faster than the simulation method.
+We analyzed five case studies of real PV systems deployed in five different sites, ranging from $975$ W to $1,300$ W (inverter specification), and the results of three state-of-the-art verification engines (ESBMC, CBMC, and CPAchecker).
+The verification method with ESBMC was faster than the simulation method.
 We validate the overall results by the sized systems deployed in the field.
@@
 Moreover, considering that HOMER Pro always performs size optimization during the simulation process, the user always has to ``adopt'' this simulation tool in order to avoid the optimization and to validate the PV system as inputted in it.
-That adaptation is not necessary using our approach, because optimization is a method separate from verification.
-Besides, only the proposed method of automated verification was able to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature, i.e.
-the user can not specify battery autonomy.
+That adaptation is not necessary using our approach because optimization is a method separate from verification.
+Besides, only the proposed method of automated verification was able to validate a system with a specific battery autonomy since HOMER Pro does not have this feature, i.e., the user can not specify battery autonomy.
 
@@
 The focus was on the synthesis method of obtaining the optimal solution based on formal methods, which can improve coverage of the design-space more effectively than simulation tools.
-Our thesis produced methodological research which innovated with regard to the first use of automated synthesis for optimal sizing of solar PV systems.
+Our thesis produced methodological research that innovated concerning the first use of automated synthesis for optimal sizing of solar PV systems.
 
@@
 Furthermore, in order to validate our method, we conducted seven case studies of PV systems on two different sites in the State of Amazonas, Brazil, ranging from $253$\,W to a $1,586$\,W peak; and three state-of-the-art verification engines were considered (ESBMC, CBMC, and CPAchecker).
-In addition, we again used the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
-In terms of performance and best results, ESBMC was the most successful and used for the comparison with the simulation tool.
+Besides, we again used the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
+In terms of performance and best results, ESBMC was the most successful and used for comparison with the simulation tool.
 
-In summary, our synthesis proposal is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
-In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including the component model, nominal current, and voltage.
+In summary, our synthesis proposal is capable of presenting a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the component model, nominal current, and voltage.
 We also cover the charge controller, which is unavailable in HOMER Pro.
 Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro.
-However, the solution presented is sound and complete; it also provides a list of equipment that can be bought direct from the manufacturer.
+However, the solution presented is sound and complete; it also provides a list of equipment that can be bought directly from the manufacturer.
 
@@
 
-As the focus here was stand-alone solar PV systems, one promising area for further research will include analysis of other types of renewable energy, even hybrid  in order to allow the method to verify and obtain optimal sizing of typical rural electrification systems.
+As the focus here was stand-alone solar PV systems, one promising area for further research will include analysis of other types of renewable energy, including hybrid to allow the method to verify and obtain optimal sizing of typical rural electrification systems.
+We will also investigate fault localization techniques~\cite{AlvesCF15,AlvesCF17} to automatically find the root cause of errors when our verification method detects a property violation in the design of PV systems.
 
@@
 The automated verification and automated synthesis methods demonstrate their effectiveness and potential for use in stand-alone solar PV systems.
-Although clearly there are still issues to address in order to improve the tools, notably performance and the human-computer interaction.
+Although there exist still issues to address in order to improve the tools, notably performance, and the human-computer interaction.
 
-The licensing and use of tools mentioned in this thesis is different for HOMER Pro, which is available only for use with Microsoft Windows, and whose standard annual subscription is set at US\$ $504.00$~\cite{HOMER}.
-The verifiers, CPAchecker, ESBMC and CBMC, and their solvers, are based on open-source software licenses which usually allow the users to use, modify, and distribute licensed products freely.
+The licensing and use of tools mentioned in this thesis are different for HOMER Pro, which is available only for use with Microsoft Windows, and whose standard annual subscription is set at US\$ $504.00$~\cite{HOMER}.
+The verifiers, CPAchecker, ESBMC, and CBMC, and their solvers, are based on open-source software licenses, which usually allow the users to use, modify, and distribute licensed products freely.
 Permission is granted, free of charge, to use this software for evaluation and research purposes (which is a great advantage when compared to commercial tools).
 
-The tools we have described here in no way similar to any other prior work.
+The tools we have described here in no way are similar to any other prior work.
 We may conclude that our research is original and expands the boundaries of knowledge.
-In particular, we have proposed cutting-edge computer science methodologies to solve typical electrical engineering problems and to improve the designing of systems.
+In particular, we have proposed cutting-edge computer science methodologies to solve typical electrical engineering problems and to improve the design of systems.
 
-Moreover, last but not least, one of the most important aspects of Ph.D.
+Moreover, last but not least, one of the essential aspects of Ph.D.
 work is that the student-researcher will be able to conduct this line of research in the future.
@@
 Little research has been done on this until now, but the scenario is auspicious.
+
 %

### 2020-03-12 Tex/CAV2019/CAV2020_rebuttal_rev0.txt
CAV2020 rebuttal

SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro
Category: Industrial Experience Reports & Case Studies

================REBUTTAL====================================

*****************Reviewer 1*********************************
Q2: Isn't CBMC a model checker for C/C++? Can't you use directly an SMT solver like Z3?
Answer: The algorithm was written in Language C (we are sorry, but it seems that this information is not present at the peper), and the code was the same for all verifier engines (CBMC, ESBMC, and CPAchecker). This technique (the use of formal synthesis in order to obtain the optimal sizing of solar PV systems) was one part of a Thesis defended by one author in January of 2020; and we treid different verifier engines (and solvers), but the combination ESBMC with Z3 version 4.7.1 presented an internal failure in all case studies. It corresponds to a ’bug’ in the Z3 solver which will require an updated version of ESBMC to fix it.

*******************Reviewer 2*******************************
Question for authors #1: Currently, the CEGIS loop results in a *single input* being added at each iteration. This may require a large number of iterations for the synthesis component to produce a candidate that succeeds in the verifier. Is there a more *general* constraint that the verifier can produce, to help the synthesizer more quickly rule out bad candidates?
Answer: We realized that just after the paper submission. In a updated version of the algorithm (not the one presented at this paper), we inclued a minimum cost for the beginning of iterative loop. This cost is the lowest among the list of equipment used, considering a configuration of just one solar PV panel, one charge controller, one battery, and one inverter. Indeed, if we use a bigger list of equipment then the time to result is bigger.

Question for authors #2: Where does the verification step occur in Algorithm 1? Unless I'm missing something, the VERIFY and SYNTHESIZE phases don't show up explicitly in Algorithm 1.
Answer: We will try to explain better here: the SYNTHESIZE phase is obtained by an feasible combination of equipment that meet the properties collected from the electrical requirements of the equipment itself (power, current or voltage). As told at the paper, this phase produces one feasible solution at line 20. The VERIFY phase is the responsible to obtain the lowest cost (minimum cost is the optimization objective function) considering the iterative steps taken from the 'for' loop that goes from line 6 to 22 of the algorithm 1. The code will cause an FAIL when the optimal sizing is found or when there is not feasible solution (SUCCESS).

Question for authors #3: My understanding is that the verification step uses a model checker. What exactly does the model look like?
Answer: Yes, we use model checking. The model (constraint and properties) is obtained from the math model used for the sizing, from the electrical characteristic of the equipment (in order to combine electrical compatibility among equipment, as current, voltage, or power), from the 'assumes' included explicitly at the algorithm 1, and from the objective function (minimum cost of the feasible PV sizing solution). We created a specific page for the C^(not)P, after the paper was finished, and it is present in:

Question for authors #4: In regards to the mismatched Windows/Ubuntu machine specs in section 4.3, why couldn't you just use separate Windows/Ubuntu VMs on the same host machine?
Answer: Yes, the ideal should be to use the same hardware configuration for the tests. However we got restrictions related to the licence for the HOMER Pro, and we did not have autonomy to change the Linux VM machine because it was shared with other PhD students with lots of experiments running.

****************REVIEWER 3************************************
1. You mention in the last sentence of Section 2 that the requirements involve non-linear equations. In many cases, it is sufficient for the requirements to be monotonic (for example, doubling the solar irradiance will conceivably always increase power output, even if it does not double it, or increasing panel efficiency will necessarily increase power output). Have you thought of exploiting such monotonicity properties for the purposes of optimization?

2. Your choice of words in Figure 2 (and elsewhere in the paper) is a bit non-standard. In traditional usage, failure to verify a candidate program results in a counter-example and successful verification results in termination of the CEGIS loop.

3. In any case, why do you describe the algorithm as a CEGIS loop when it could more simply be described as iteratively increasing the target cost and using a constraint solver to determine whether the target cost is feasible?

*********************REVIEWER 4*******************************
However, I have some reservations about the technical approach. First, the target problem here is one of optimization, but the synthesis algorithm does not model the optimality objective explicitly, instead relying on standard CEGIS. A quantitative synthesis approach, which casts synthesis as constrained optimization over a space of programs, seems more appropriate. Second, the application demands reasoning about constraints in nonlinear real arithmetic, which is a hard problem. It is not clear how this problem will be solved.

Finally, the paper claims that the method does can lead to "more accurate results than existing commercial tools." However, this claim is not validated through an empirical evaluation.

*******************************************************************
*****************ORIGINAL COMMENTS*********************************
*******************************************************************

----------------------- REVIEW 1 ---------------------
SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro

----------- Overall evaluation -----------
SCORE: 1 (weak accept)
----- TEXT:
This (tool) paper describes a new application area for SMT-based synthesis in the domain of photovoltaic systems. The method is a standard CEGIS approach + constantly increasing the allowed cost as long as there is no feasible solution. The case studies (based on the real data of electrical load) compare the developed tool to a commercial software called Homer.

I appreciate the application of formal methods in industrial applications (especially for clean and affordable energy), and believe that the paper (while not in the main focus of the conference) could be a nice addition to CAV.

One drawback is that I could not really see a conclusive answer to EG3 (how does the is formal synthesis tool compare to a specialized simulation tool?). In particular, do the case studies (except for #2) have deployed systems that allow to validate the synthesized results?

For rebuttal:
Q1: Is this optimization problem beyond the scope (or ability) of probabilistic programming?
Q2: Isn't CBMC a model checker for C/C++? Can't you use directly an SMT solver like Z3?

----------------------- REVIEW 2 ---------------------
SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro

----------- Overall evaluation -----------
SCORE: 1 (weak accept)
----- TEXT:
======= Paper Summary =======

This paper presents a program synthesis-based approach for solving the optimal PV sizing problem, which consists of selecting optimal parameters for photovoltaic (PV) systems. The tool uses a CEGIS loop architecture, with a synthesizer producing a candidate solution that is correct for a finite number of inputs, and a verifier checking whether the candidate is correct for *all* inputs. To evaluate the tool, the authors apply it to real-world electrical systems, including one in the Amazonas State, Brazil.

======= Contributions =======

The paper presents the following contributions:

#1. The paper is one of the first to apply formal methods to PV system design.

#2. The approach translates problems in the PV design space into a form that can be tackled using efficient off-the-shelf verification tools.

#3. The paper contains meaningful real-world applications of the approach, and discusses ways to improve on the state of the art in this area.

======= General Questions/Comments =======

Cons:
- The techniques are not particularly novel (CEGIS, model-checking, etc. are used in a mostly black-box way).
- There are some shortcomings and unclear components of the algorithm. For example, the CEGIS loop could iterate a huge number of times, due to the simple strategy for adding inputs to the synthesis component. Additionally, the verification/synthesis components are not described in detail.

Pros:
- The paper describes a tool which targets a vital real-world problem. I think it's fantastic to see researchers applying formal methods in areas related to renewable energy.
- The overall CEGIS approach seems promising, and the experimental results seem good.

Question for authors #1: Currently, the CEGIS loop results in a *single input* being added at each iteration. This may require a large number of iterations for the synthesis component to produce a candidate that succeeds in the verifier. Is there a more *general* constraint that the verifier can produce, to help the synthesizer more quickly rule out bad candidates?

Question for authors #2: Where does the verification step occur in Algorithm 1? Unless I'm missing something, the VERIFY and SYNTHESIZE phases don't show up explicitly in Algorithm 1.

Question for authors #3: My understanding is that the verification step uses a model checker. What exactly does the model look like?

Question for authors #4: In regards to the mismatched Windows/Ubuntu machine specs in section 4.3, why couldn't you just use separate Windows/Ubuntu VMs on the same host machine?

Suggestions for improvement:
- I don't quite understand why a *counterexample* from the verifier represents "success" of the tool. Usually a generated counterexample would be sent back to the synthesizer to help improve the next generated candidate. It would be helpful if this is clarified in the next revision.
- It would be helpful if the "PV sizing" problem could be more precisely articulated.

======= Conclusion =======

This is an interesting application of program synthesis to an important problem in the real world. Although the tool primarily uses existing techniques, it seems to perform well compared to existing tools in the PV design domain.

======= Nitpicks =======

- page 2: "reasoning of a model" --> "reasoning about a model"
- page 7: "ensure that the approach is sound" --> "ensure that the solution is sound"
- page 10: "HOME Pro was unable" --> "HOMER Pro was unable"
- page 10: "but not sound as our method" --> "but not sound, as is our method"
- page 10: "approach to pursuit the" --> "approach to pursue the"
- page 10: "which is far detailed" --> "which is far more detailed"

----------------------- REVIEW 3 ---------------------
SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro

----------- Overall evaluation -----------
SCORE: -2 (reject)
----- TEXT:
Overview of the Paper
---------------------

The choice of optimal photovoltaic cells (in terms of weather, cost, efficiency, surface area, number of panels, etc.) is an important challenge in the widespread deployment of decentralized solar energy harvesting systems. This paper considers the use of CEGIS-based techniques in combination of program verifiers such as CPAchecker, CBMC, or ESBMC to make optimal decisions.

The algorithm takes as input a list of panel types and associated equipment, including batteries, controllers, inverters, and installation-specific details, such as weather data, power demand etc. The problem is to identify the most cost-effective installation which satisfies the given requirements. The core technique appears to involve repeatedly checking whether a solar panel configuration exists with a given target cost, which starts at 0 and iteratively increases until it reaches some pre-defined maximum. In each step, the installation parameters are non-deterministically chosen, and a program verifier determines whether there is a choice of these parameters which leads to the requirements being satisfied.

Experiments are presented which evaluate the system on a selection of six installation requirements. CBMC is able to generate an optimal configuration for all but one of the settings.

Appraisal
---------

It is unclear to me that CAV is an appropriate venue for such a paper. The specific domain of solar photovoltaics is outside my area of expertise, and I presume, outside the expertise of the average CAV attendee. The paper seems better suited to a conference on smart cities, IoT, or energy systems.

One potential reason to accept this at CAV would be if the technique involved some novelty at the level of the optimization algorithm. Examples include (a) a non-trivial use of CEGIS to perform optimization, (b) a close synergy between program synthesis and the application domain of photovoltaic cells, or (c) a failure of off-the-shelf numerical optimizers to succeed at this task. Unfortunately, the paper could not convince me of this.

I therefore do not vote for this paper to be accepted.

Questions and Comments for the Authors
--------------------------------------

1. You mention in the last sentence of Section 2 that the requirements involve non-linear equations. In many cases, it is sufficient for the requirements to be monotonic (for example, doubling the solar irradiance will conceivably always increase power output, even if it does not double it, or increasing panel efficiency will necessarily increase power output). Have you thought of exploiting such monotonicity properties for the purposes of optimization?

2. Your choice of words in Figure 2 (and elsewhere in the paper) is a bit non-standard. In traditional usage, failure to verify a candidate program results in a counter-example and successful verification results in termination of the CEGIS loop.

3. In any case, why do you describe the algorithm as a CEGIS loop when it could more simply be described as iteratively increasing the target cost and using a constraint solver to determine whether the target cost is feasible?

----------------------- REVIEW 4 ---------------------
SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro

----------- Overall evaluation -----------
SCORE: -2 (reject)
----- TEXT:
Summary:

The paper is a case study of the application of program synthesis to obtaining the optimal sizing of solar photovoltaic (PV) systems.

Evaluation:

The paper is on an interesting topic. Prior work has sought to verify the correctness of PV panels. The automatic synthesis of safe-by-construction parameters of PV panels is a natural next step. Also, the authors have taken care to use real data from the Amazonas state.

However, I have some reservations about the technical approach. First, the target problem here is one of optimization, but the synthesis algorithm does not model the optimality objective explicitly, instead relying on standard CEGIS. A quantitative synthesis approach, which casts synthesis as constrained optimization over a space of programs, seems more appropriate. Second, the application demands reasoning about constraints in nonlinear real arithmetic, which is a hard problem. It is not clear how this problem will be solved. Finally, the paper claims that the method does can lead to "more accurate results than existing commercial tools." However, this claim is not validated through an empirical evaluation.

------------------------------------------------------

### 2020-04-07 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
paper update 2020

--- 2019-09-28 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
@@
-%% bare_jrnl.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
 \documentclass[journal]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
+
 \ifCLASSINFOpdf
@@
 
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
 % *** PDF, URL AND HYPERLINK PACKAGES ***
@@
 % The paper headers
-\markboth{IEEE Transactions on Sustainable Energy,~Vol.~XX, No.~YY, September~2019}%
+\markboth{IEEE Transactions on Sustainable Energy,~Vol.~XX, No.~YY, April~2020}%
 {Trindade and Cordeiro: An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems}
@@
 % column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
 
@@
 
-Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
 Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
@@
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
+All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.
 
@@
 	\item Operation and maintenance annual costs: based on PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
-This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years).
+This cost includes the battery replacement based on its lifetime, plus inverters and controller replacement (every $10$ years).
+We adopted lead-acid batteries, the cheapest and most common kind used nowadays; and it means a $4$ years lifetime.
 Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
+Worth to mention that  those data can be adjusted in our algorithm.
 \end{itemize}
@@
 
-Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
+Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common adopted for lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
 
@@
 Related to HOMER Pro, it was able to evaluate six case studies, and within a time shorter than $30$ seconds, which was much faster than our automated synthesis tool (cf.~\textit{EQ2}).
-We were unable to simulate case study $3$ since HOMER Pro does not have the feature of adjusting the battery autonomy (the tool always meets the user requirement, i.e., the load curve during the $365$ days of the year).
+It produces very  We were unable to simulate case study $3$ since HOMER Pro does not have the feature of adjusting the battery autonomy (the tool always meets the user requirement, i.e., the load curve during the $365$ days of the year).
 Other HOMER Pro drawbacks, when compared to our automated synthesis method: (a) There exists no explicit charge controller as a system equipment.
@@
 
-Concerning the charge controllers, as we reported in the previous section, HOMER Pro does not include it as an explicit equipment in its mathematical model; only our synthesis tool presents a commercial controller and includes it during the cost analysis.
+Concerning the charge controllers, as we reported in the previous section, HOMER Pro does not include it as an explicit equipment in its mathematical model and does not includes the cost for the charge controller; only our synthesis tool presents a commercial controller and includes it during the cost analysis.
 Therefore, the formal synthesis method presents more reliable results than HOME Pro.

### 2020-04-18 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

--- 2020-01-27 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
@@
 \begin{abstract}
-The use of power generation with a renewable energy source is proliferating due to industrial development.
-Photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation.
+The use of power generation with renewable energy sources is proliferating due to industrial development.
+Photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel energy generation.
 The use of formal methods for PV systems is a new subject with significant research spanning only the last five years.
-%However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
-Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems.
+Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing PV systems.
+More specifically, we use a stand-alone configuration for this work since it is currently the most common system used for remote rural areas of developing countries or areas where the grid extension is not feasible.
 We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis.
 We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market.
+Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time.
+We also compare our CEGIS approach with a commercial tool specialized in PV systems optimization, with both results being simulated with an complete and accurate design software called PVsyst; furthermore, real PV systems comparison are used in order to show our approach effectiveness.
 %First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
@@
 If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution.
-Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time.
-We also compare our CEGIS approach with a state-of-the-art commercial tool over real PV systems to show its effectiveness.
-%\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
+%However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
+\keywords{Formal symthesis \and Automated verification  \and Model Checking \and Solar photovoltaic systems.}
 \end{abstract}

### 2020-04-19 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{optimalsizingprocess4}
+\includegraphics[width=0.9\textwidth]{optimalsizingprocess4}
 \centering
@@
 Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture.
+
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{fig2_rev2.jpg}
 %
-\begin{wrapfigure}{r}{0.5\textwidth}
-\begin{center}
-	\includegraphics[width=0.5\columnwidth]{fig2_rev2.jpg}
-\end{center}	
+%\begin{wrapfigure}{r}{0.5\textwidth}
+%\begin{center}
+%	\includegraphics[width=0.5\columnwidth]{fig2_rev2.jpg}
+%\end{center}	
 	\caption{CEGIS in PV system sizing.}
 	\label{Counter-Example-Guided-Inductive-Synthesis}
-\end{wrapfigure}
+%\end{wrapfigure}
+\end{figure}
 
@@
 
-%A PV system is illustrated in Fig.\ref{fig:blockdiagram}. 
-A photovoltaic system employs: the PV generator, which can be a \textbf{panel or an array}, is a semiconductor device that can convert solar energy into DC electricity; for night hours or rainy days, we hold \textbf{batteries} where power can be stored and used; the use of batteries as a storage form implies the presence of a \textbf{charge controller}~\cite{Hansen}; the PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textbf{inverter}); the \textbf{AC load} dictates the behavior of the AC electrical load from the house that will be fed by the system.
+A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It 
+%A photovoltaic system 
+employs: the PV generator, which can be a \textbf{panel or an array}, is a semiconductor device that can convert solar energy into DC electricity; for night hours or rainy days, we hold \textbf{batteries} where power can be stored and used; the use of batteries as a storage form implies the presence of a \textbf{charge controller}~\cite{Hansen}; the PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textbf{inverter}); the \textbf{AC load} dictates the behavior of the AC electrical load from the house that will be fed by the system.
 
 %\begin{wrapfigure}{r}{0.5\textwidth}
-%%\begin{figure}[h]
-%\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
-%\centering
-%\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
-%\label{fig:blockdiagram} 
-%\end{wrapfigure}
-%
-The sizing check will ensure that the system meets the standard project steps related to the critical period solar energy method~\cite{Pinho} and the MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice.
-Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\ref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+\begin{figure}[h]
+\includegraphics[width=0.8\textwidth]{blockdiagramPVS2_rev}
+\centering
+\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
+\label{fig:blockdiagram} 
+\end{figure}
+
+The sizing check stage can ensure that the system meets the standard project steps related to the critical period method (worst month) for solar energy system sizing~\cite{Pinho} and adopting an MPPT (Maximum Power Point Tracking) charge controller, which is the most common in use.
+Firstly, we need to correct the daily energy consumption estimated for the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
 
@@
 \label{eq:Ecorrected}
-E_{corrected} = \frac {E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
+E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \times \eta_{c} \times \eta_{i} }.
 \end{equation}
 
-We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
+We must estimate the total power that will be demanded from the PV panels, as defined by Eq. ~\eqref{eq:Pminpanel}.
 
 \begin{equation}
-\label{eq:Ep}
-E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
+\label{eq:Pminpanel}
+P_{min,panels} = \dfrac{1.25 \times E_{corrected}}{Insolation},
 \end{equation}
 
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
-the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-The minimum number of solar panels ($N_{TPmin}$) is computed as
+\noindent where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
+A factor of $20$\% for losses is considered, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
+
+On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
+On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as shown in Eq.~\eqref{eq:Icmin} and
+\eqref{eq:Vcmin}.
 
 \begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \frac{E_{corrected}}{E_{p}}.
-\end{equation}
-
-The number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are resp.:
-
-\begin{equation}
-\label{eq:NPSmin}
-\frac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \frac{V_{mppt,max}}{V_{maxPower,TempMin}},
+\label{eq:Icmin}
+I_{c} \geq I_{total,PVpanels},
 \end{equation}
@@
 \begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \frac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
+\label{eq:Vcmin}
+V_{c} \geq V_{total,PVpanels},
 \end{equation}
 
-\noindent where $V_{mppt, max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operating voltage of the charge controller.
-$V_{maxPower, TempMax}$, as well as $V_{maxPower, TempMin}$, are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively.
-$P_{total}$ is the total power demanded from the PV system and $P_{max, ref}$ is the power supplied from one PV panel in $Watts$.
-Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
+Related to the batteries, the energy $E_{b}$ to be demanded by the PV system, in order to meet the load requirements, is defined by Eq.~\eqref{eq:Ebat}.
+
+\begin{equation}
+\label{eq:Ebat}
+E_{b} = \dfrac{Autonomy \times E_{corrected}}{DOD},
+\end{equation}
+
+\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries, usually is a design definition and has a value ranging from $0.5$ to $2$ days.
+$DOD$ is the
+the depth of discharge or the fraction of discharge (usually 25\% for lead-acid batteries, and 80\% for lithium batteries).
+However it is worth to separate the $DOD$ into two different definitions when the battery autonomy is bigger than one day ($24$ hours).
+Therefore, here in this thesis, the definition given here is for maximum $DOD$.
+When we deal with daily $DOD$ we will call it of $DOD_{day}$, and obviously the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
+
+In order to define the $DOD_{day}$ we use Eq.~\eqref{eq:DODday}.
+Moreover, the minimum current from DC bus is defined by Eq.~\eqref{eq:Idcbus}.
+This equation is important to define the battery arrangement of the system (series and parallel connections).
+
+\begin{equation}
+\label{eq:DODday}
+DOD_{day} = \dfrac{E_{corrected} \times 100}{E_{b}},
+\end{equation}
+
+\begin{equation}
+\label{eq:Idcbus}
+I_{min,DCbus} = \dfrac{E_{b}}{V_{system}},
+\end{equation}
+
+\noindent where $V_{system}$ is the DC voltage of the bus.
+
+As for batteries, we must first define the total capacity of the battery bank, which can be described as
 
@@
 \label{eq:Cbank}
-C_{bank} = \frac{E_{corrected} \times autonomy}{V_{system} \times DOD},
+C_{bank} = \dfrac{Autonomy E_{load}}{DOD \eta _{b} V_{system}},
 \end{equation}
 
-\noindent where the variable $autonomy$ is a design definition; 
-$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery depth of discharge (considered of maximum of 25\% here).
-Secondly, the total (minimum) number of batteries $N_{B}total$ is computed as a product of the minimum number of batteries in series $N_{BS}min$ with the minimum number of batteries in parallel $ N_{BP}min $ and, therefore, as function of battery bank capacity $ C_{bank} $ and the capacity of the chosen battery $ Battery \, Capacity $ as
+\noindent where $ E_{load} $ is the average energy consumed by the load corrected according PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
+
+Equation \ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted in the project.
 
 \begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min = \frac{V_{system}}{V_{bat}} \times \frac{C_{bank}}{Battery \, Capacity}.
+\label{eq:batcheck}
+\left( N_{BS} \times N_{BP} \right) \geq N_{B}total
 \end{equation}
 
-Regarding the charge controller, it must initially meet the voltage requirement of the PV system $V_{system}$, given by Eq.~\ref{eq:vcvsystem} to the charge controller voltage: % $V_{c}$:
+The charge controller must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem}.
 
@@
 
-The short circuit reference current $ I_{sc,ref} $ from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature $ T $ is higher than the nominal or laboratory temperature, and PV system is temperature dependent.
-This corrected current is called $I_{sc,amb}$, it uses $G_{ref} = 1000$ and the ratio of current change over temperature $\mu_{I}$:
+The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because field temperature is higher than nominal or laboratory temperature, and the PV system is temperature dependent, as shown by Equation~\eqref{eq:iscamb}.
 
@@
 \label{eq:iscamb}
-I_{sc,amb} = \frac{Solar \, Irradiance}{G_{ref}} \left[I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
+I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
 \end{equation}
 
-The controller must meet the maximum current from the PV array. Therefore the controller current $I_{c}$ must be less than the calculated $I_{c,min}$ and given as
-%
-\begin{subequations}
-  \begin{tabularx}{\textwidth}{Xp{1cm}X}
+The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin}.
+
 \begin{equation}
 \label{eq:icmin}
-      I_{c,min} = I_{sc,amb} \times N_{PP}.
+I_{c,min} = I_{sc,amb} \times N_{PP},
 \end{equation}
-  & &
+
 \begin{equation}
@@
 \end{equation}
-\end{tabularx}
-\end{subequations}
 
-The inverter sizing check is performed by means of three equations.
-Eq.~\ref{eq:vindc} ensures that the input voltage of the controller $V_{in}DC$ meets the system voltage.
-Eq.~\ref{eq:voutac} ensures that the output voltage of the controller $V_{out}AC$ meets the AC voltage of the load $V_{AC}$.
-Finally, Eq.~\ref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $P_{AC,ref}$ is the nominal power and $MAX_{AC,ref}$ is the peak power that the inverter can support.
+The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
+Besides, the final sizing check is performed by Equation \ref{eq:numberofc}, which validates the number of controllers adopted.
 
-\begin{subequations}
-  \begin{tabularx}{\textwidth}{Xp{1cm}X}
+\begin{equation}
+\label{eq:numberofcmin}
+number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
+\end{equation}
+
+\begin{equation}
+\label{eq:numberofc}
+N_{controller} \geq number_{controllers}
+\end{equation}
+
+The inverter sizing check is performed through three equations.
+Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
+Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
+Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
+
 \begin{equation}
@@
 \end{equation}
-  & &
+
 \begin{equation}
@@
 \end{equation}
-\end{tabularx}
-\end{subequations}
 
@@
 \end{equation}
+
+Some inverter models allow parallel operation of more than one unit, besides the integration in order to create bi-phase and three-phase circuits.
+It is advisable to use pure sine wave inverters, especially for electronic loads sensitive to harmonic distortion waves.
+
+Besides that, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers.
+Furthermore, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side.
+Then the controller can be overcharged during this operation and to burn.
 

### 2020-04-19 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

@@
 We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market.
-Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time.
-We also compare our CEGIS approach with a commercial tool specialized in PV systems optimization, with both results being simulated with an complete and accurate design software called PVsyst; furthermore, real PV systems comparison are used in order to show our approach effectiveness.
+Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different verification tools are evaluated, in order to evaluate performance and soundness.
+We also compare our  CEGIS approach with a commercial tool specialized in PV systems optimization, with both results being validated with a complete and accurate commercial design software; furthermore, some real PV systems comparison are used in order to show our approach effectiveness.
 %First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
@@
 Progress has been made worldwide; in particular, in 2017, the number of people without electricity access fell below $1$ billion threshold for the first time~\cite{IEAweo2018}.
+The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
+Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}.
+Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
+It follows that increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
 In order to provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}.
@@
 Here the application of formal methods to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools.
-Second, we evaluate our approach using different state-of-the-art verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems and compare that to HOMER.
+Second, we evaluate our approach using different state-of-the-art verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems and compare that to HOMER Pro optimization, with the results being validated with a complete and accurate commercial design software called PVsyst.
 Lastly, we discuss the challenges of applying formal methods to PV systems and reflect on lessons learned from this experience.
@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{fig2_rev2.jpg}
+\begin{center}
+\includegraphics[width=0.75\textwidth]{fig2_rev2.jpg}
+\end{center}
 %
@@
 
-Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
-%
+Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
+The analytical method of optimization was adopted, with LCC economic analysis and power reliability based on critical period criteria (worst month's method).
+
  \begin{algorithm}
@@
  \begin{algorithmic}[1]
- \begin{scriptsize}
  \renewcommand{\algorithmicrequire}{\textbf{Input:}}
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
- \REQUIRE weather data (temperature, solar irradiance), list of equipment (datasheet and price), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis).
- \ENSURE FAIL with counterexample showing the optimal sizing; SUCCESS, stating that the project has no feasible solution considering the requirements and the list of equipment available.
+  \REQUIRE weather data (temperature, solar irradiance); list of PV panels, controllers, batteries, and inverters datasheet information and cost; design requirements (load curve, peak demand, load surge power, daily energy consumption, battery autonomy, AC voltage); design assumptions (battery state of charge, depth of discharge, criteria and objectives for technical and cost analysis)
+ \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
   \STATE Initialize variables \\
- \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
   \STATE Declare the maximum possible cost $MaxCost$  \\
- \STATE Declare power demand, power peak, energy consumption \\
- \STATE Declare battery autonomy, depth of discharge, AC voltage \\
- \FOR {$HintCost=0$ to $MaxCost$}
+  \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
+  \FOR {$HintCost=MinCost$ to $MaxCost$}
  	\STATE Declare non-deterministic variable to select PV Panel from list \\
@@
  	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
- 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
-	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
- 	\STATE Calculate $C_{bank}$ \\
-	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
-	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
- 	\STATE Calculate $I_{sc,amb}$ \\
- 	\STATE Calculate $I_{c,min}$ \\
- 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
-	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
+ 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
+	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
+	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{m,ref}))$ \\
+	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
+	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
+ 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
+	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
+	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
+ 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
+	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
 	\STATE non-deterministic variables hold feasible equipment and cost  \\
-	\STATE $F_{obj} \leftarrow N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
+	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
 	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
   \ENDFOR
-% \RETURN $(\,)$ 
- \end{scriptsize}
+ \RETURN $(\,)$ 
  \end{algorithmic} 
- \label{alg:verification-algorithm}
+ \label{alg:opt-algorithm}
  \end{algorithm}
-%
-Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers' data and prices of PV panels, batteries, charge controllers, and inverters (Line 2).
-We define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5.
-The \textit{for}-loop started at Line 6 controls the lowest cost to the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, which will be reached if the optimal solution is not found first.
-If this $MaxCost$ is reached, then there exists no feasible solution to the problem.
 
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (Lines 7 to 10).
-That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.
-%
-Next, we use Eq.~\ref{eq:Ecorrected}, Eq.~\ref{eq:Ep}, Eq.~\ref{eq:NTPmin}, Eq.~\ref{eq:NPSmin}, Eq.~\ref{eq:NPPmin}, Eq.~\ref{eq:Cbank}, Eq.~\ref{eq:Nbtotal}, Eq.~\ref{eq:iscamb}, and Eq.~\ref{eq:icmin} to calculate the sizing variables (Lines 11 to 17).
-The directive \textit{assume} (Lines 15, 18, and 19) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines 15, 18, and 19.
-Our algorithm reaches Line 20 with one feasible solution; the cost of that solution is calculated in $F_{obj}$ (Line 21).
+Our synthesis algorithm will synthesize constant values; 
+it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers and inverters. Moreover, we define design (house) requirements and design assumptions.
 
-If our algorithm does not find a feasible solution among the item of equipment that was provided to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution.
-It indicates that it is not possible to combine the items of each equipment and create a feasible solution.
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements.
-Related to our {\sc Verify} phase, the challenge is to find the lowest acquisition cost from a list of equipment and components that are provided from the {\sc Synthesize} phase.
-The process described here is entirely automated; a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+The \textit{for}-loop started at line $4$ controls the lowest cost of the PV solution.
+In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $21$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+The $MaxCost$ value at line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
+
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (lines $5$ to $8$).
+This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.
+
+Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $9$ to $15$).
+The directive \textit{assume} (lines $11$, $16$, $17$ and $18$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of lines $11$, $16$, $17$ and $18$.
+Line $11$ is specific to PV panels.
+Line $16$ is for the battery bank.
+Line $17$ is the charge controller voltage check.
+Line $18$ does the inverter check and ensures the power demand and the surge power of the inverter.
+Therefore, our synthesis algorithm reaches line $19$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $20$). This cost is the equivalent to~\ref{eq:LCC}.
+
+If our algorithm does not find a feasible solution among the item of equipment that were provided for our {\sc Synthesize} phase,  then the result is unsatisfiable (\textit{UNSAT}), i.e.
+the program finishes without finding a solution, indicating that it was not possible to combine the specific items of equipment in order to create a feasible solution.
+
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements.
+The challenge for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase.
+
+Note that the process described here is completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
 
@@
 \textbf{1:} \{342; 342; 3,900; 48\}; \textbf{2:} \{814; 980; 4,880; 48\}; \textbf{3:} \{815; 980; 4,880; 12\}; \textbf{4:} \{253; 722; 3,600; 48\}; \textbf{5:} \{263; 732; 2,500; 48\}; \textbf{6:} \{322; 896; 4,300; 48\}; \textbf{7:} \{1,586; 2,900; 14,000; 48\}.
-This 4-tuple represents the Algorithm~\ref{alg:verification-algorithm} inputs.
+This 4-tuple represents the Algorithm~\ref{alg:opt-algorithm} inputs.
 For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
@@
 %---------------------------------------------------------------------------
-\subsection{Simulation Tool and Assumptions}
+\subsection{Optimization/Simulation Tools and Assumptions}
 %---------------------------------------------------------------------------
-Concerning the off-the-shelf simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis.
+Concerning the off-the-shelf optimization/simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis.
 Here we used HOMER Pro version $3.13.1$ as a state-of-the-art simulation tool for comparison purposes.
@@
 
+PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation and data analysis of complete solar PV System.
+Contains: design, sizing, 3D shading scene, simulation, grid and off-grid features for PV systems.
+It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis (PV system over the years).
+However, it does not performs optimization.
+Therefore, in this paper, PVsyst will be used to validate the optimal sizing obtained from the proposed technique and from the HOMER Pro.
+
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-%A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}. 
-CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours.
-Only case study $7$ led to a \textit{time out} result in CPAchecker.
-The violation (SAT result) indicated in the on-line table\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}.
-CBMC and ESBMC are unable to produce any conclusive results since \textit{time-outs} or \textit{memory-outs} occurred; these results partially answer \textit{EG1} and \textit{EG2} since our approach provides optimal solutions for six case studies and CPAchecker presented the best results among the verifiers.
 
-The size of the PV panels and battery bank were larger in HOMER Pro than with our approach.
-To compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
-These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EG1}.
+The results are presented at Table~\ref{tab1}.
 
-For the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter.
-The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf.
-Therefore, this feature is a PRO to the formal synthesis method.
-Concerning the charge controllers, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis.
-Therefore, the formal synthesis method presents more reliable results than HOMER Pro.
+\begin{table}
+\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
+\begin{scriptsize}
+\begin{tabular}{c|c|c|c|c}
+\hline
+\hline
+Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
+\hline
+\hline
+Specification & Result & Result & Result & Result \\
+\hline
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\hline
+\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
+\hline
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
+\hline
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
+\hline
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
+\hline
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
+\hline
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+\hline
+\hline
+\end{tabular}
+\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
+\end{scriptsize}
+\end{table}
+
+The violation (SAT result) indicated all over the Table~\ref{tab1} 
+is the $assert$ of line $21$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
+
+CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.
+
+CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $254.25$ to $548$ minutes.
+Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left size as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron  Energy, and the inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power.
+The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.
+
+Case studies $2$, $3$, $6$, and $7$  led to a \textit{time out} result in CPAchecker, i.e.  it was not solved within $660$ minutes.
+
+\begin{figure}[h]
+\fbox{\includegraphics[width=1.0\textwidth]{CPA_opt_c5.png}}
+\centering
+\caption{Counterexample generated by CPAchecker after validation of case 5 (file Counterexample.html).}
+\label{fig:CPAoptc1}
+\end{figure}
+
+An internal failure was presented by ESBMC when using Z3 solver in all case studies.
+It corresponds to a 'bug' in the Z3 solver which will require an updated version of ESBMC to fix it.
+However, when using the incremental BMC configuration of ESBMC with Boolector solver, the verifier engine was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response varying from $36.70$ to $620$ minutes.
+Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated.
+ESBMC with this configuration was not possible to obtain a optimal solution in cases $2$ and $7$.
+Case $2$ reached a  \textit{time out} result after $660$ minutes of processing.
+Moreover, case $7$ resulted in a UNSAT result, i.e the verifier engine was not possible to get a feasible solution considering the list of equipment.
+This SAT situation was reached after just $0.48$ minutes.
+
+\begin{figure}[h]
+\fbox{\includegraphics[width=1.0\textwidth]{ESBMC_SAT_case3.png}}
+\centering
+\caption{ESBMC counterexample for case 3 optimization.}
+\label{fig:esbmcoptcase3}
+\end{figure}
+
+Those specific results partially answers the \textit{EQ2}.
+
+HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}).
+Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e.
+the tool always tries to feed the given load with electricity $365$ days/year.
+
+Certain other HOMER Pro drawbacks were also noted:
+
+\begin{itemize}
+\item System equipment does not include an explicit charge controller .
+HOMER Pro includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing;
+\item HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user.
+For example, it was started with a $83.4$ Ah lead-acid battery and during simulation, HOMER Pro did not try to use other capacities or types;
+\item HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e.
+it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Comparison Between Formal Synthesis and HOMER Pro, using PVsyst}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Comparing the results of the formal synthesis with CPAchecker, and ESBMC, against those of  HOMER Pro, it was observed some distinct results, in terms of technical solution and cost (cf.
+Table~\ref{tab1}).
+Related to performance there is a huge difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in opposite of an average of $234$ minutes for the automated synthesis technique.
+
+Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, always having a higher estimation from the automated synthesis technique.
+However, considering that the cost of individual item of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.
+
+In one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool.
+The difference varied from $19$\% to $65$\%.
+In the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro.
+The difference was among $34$\% to $68$\%.
+
+Those discrepancies are not easy to address without some real systems validation.
+The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.
+
+As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e.
+the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.
+
+Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+These solutions are closer to the results from PV panel, controller and inverter presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
+However the solution presented for the battery bank is very different.
+
+HOMER Pro suggests a value in kW for the inverters that is very close to the peak of every case study, and it is just a reference value and not a commercial value of the inverter employed.
+The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf.
+This is a clear advantage of the formal synthesis method.
+
+HOMER Pro does not include charge controllers as an explicit item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis.
+The formal synthesis method, therefore, presents more reliable results than HOMER Pro.
+
 Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
-HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.
-This lack of recourse is a limitation since it is usual to establish autonomy as a design requirement.
+Case study $2$ was solved just by the ESBMC verifier engine.
+Case study $3$ could not be simulated in HOMER Pro, because of its restriction on setting battery autonomy, thus leaving those three cases without parameters to compare.
 
-In terms of performance, HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed synthesis approach (cf.~\textit{EG3}) but not sound as our method.
-Comparing the results between CPAchecker and HOMER Pro, we have observed that the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%.
-However, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model.
-This charge controller cost makes the synthesis approach more precise and real.
-We observed that there exists a divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool.
-However, this case study does not have a deployed PV system in order to validate which result is correct.
+Summarizing, the synthesis tool is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including  the model of the component, nominal current and voltage.
+In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising).
 
@@
 
-We have reported a favorable assessment of the proposed method.
+We have reported a favourable assessment of the proposed method.
 Nevertheless, we have also identified three threats to the validity of our results that constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; and (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
-%; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.
 

### 2020-04-22 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

@@
 
-All the equations above model the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
+All the equations above model the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
 The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
@@
 This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.
+A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine in order to allow the choice of every item of PV sizing.
+Data sheet from each item was necessary to collect technical information.
+Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
+All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.
 
@@
 Concerning the off-the-shelf optimization/simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis.
-Here we used HOMER Pro version $3.13.1$ as a state-of-the-art simulation tool for comparison purposes.
+Here we used HOMER Pro version $3.13.1$ as a state-of-the-art optimization tool for comparison purposes.
 In particular, HOMER Pro has the following characteristics:
@@
 
-PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation and data analysis of complete solar PV System.
-Contains: design, sizing, 3D shading scene, simulation, grid and off-grid features for PV systems.
-It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis (PV system over the years).
+In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a complete simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank, in a comparison for a entire years weather data of simulation in order to guarantee that the proposed sizing meets the electrification requirements.
+PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation and data analysis of solar PV systems.
+It contains: design, sizing, 3D shading scene, simulation, grid and off-grid features.
+It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis.
 However, it does not performs optimization.
-Therefore, in this paper, PVsyst will be used to validate the optimal sizing obtained from the proposed technique and from the HOMER Pro.
+Drawbacks of PVsyst: it does nor perform optimization therefore it needs the system sized in order to validated it, PVsyst does not have commercial inverter equipment and therefore does not consider surge power demand as the ones produced by air conditioners and refrigerators for few seconds.
+PVsyst is a paid software with $30$-day test possibility and runs only in MS-Windows operational system.
 
@@
 For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10.
-The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favorable to HOMER Pro.
-We perform the experiments with a predefined time out of $240$ minutes.
+The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favourable to HOMER Pro.
+PVsyst used the same configuration as HOMER Pro.
+We perform the experiments with a predefined time out of $660$ minutes.
 
@@
 \end{tabular}
-\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
+\\Legend: OM = out of memory; TO = time out; IF = internal failure; E = energy;        NTP = total number of panels, NBtotal = total number of batteries, NPS = number of panels in series; NPP = number of panels in parallel, NBS = number of batteries in series; NBP = number of batteries in parallel; LCC = Life Cycle Cost.
 \end{scriptsize}
@@
 Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left size as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron  Energy, and the inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power.
-The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.
+The variables NTP, NPS, NPP, NBS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.
 
@@
 
-Certain other HOMER Pro drawbacks were also noted:
-
-\begin{itemize}
-\item System equipment does not include an explicit charge controller .
-HOMER Pro includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing;
-\item HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user.
-For example, it was started with a $83.4$ Ah lead-acid battery and during simulation, HOMER Pro did not try to use other capacities or types;
-\item HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e.
+Certain other HOMER Pro drawbacks were also noted: (1) System equipment does not include an explicit charge controller .
+HOMER Pro includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing; (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user.
+For example, it was started with a $83.4$ Ah lead-acid battery and during simulation, HOMER Pro did not try to use other capacities or types; and (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e.
 it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
-\end{itemize}
 
@@
 Table~\ref{tab1}).
-Related to performance there is a huge difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in opposite of an average of $234$ minutes for the automated synthesis technique.
+Related to performance there is a huge difference in favour of HOMER Pro that obtained the results in considerably less time: few seconds in opposite of an average of $234$ minutes for the automated synthesis technique.
 
@@
 The difference was among $34$\% to $68$\%.
+The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.
 
 Those discrepancies are not easy to address without some real systems validation.
-The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.
+However we use the simulation software PVsyst in order to validate the optimal sizing produced.
+According PVsyst, we have to each case study:
 
-As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e.
+\begin{itemize}
+  	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries.
+This is a case that was deployed at the field ($975$ W of panels and $440$ Ah of batteries), and simulation showed that the availability is lower than the $95$\% ($91.06$\% to be precise), therefore the sizing that was done "by hand" is not correct.
+Concerning our produced sizing, it was not found error during the 365-day of the year simulation, the same result for HOMER Pro.
+However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
+	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries.
+This case has not field deployed to compare, and our approach did not produce solution.
+Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
+	\item Case study 3: only our approach produced the optimal solution because there is the requirement of 12 hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than 24 hours;
+	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries.
+This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $87$\%.
+Concerning our optimal solution it was not found error, the same as HOMER Pro.
+However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
+	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries.
+This one was deployed at the field, and PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries).
+Concerning our optimal solution it was not found error, the same as HOMER Pro.
+However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
+	\item Case study 6:
+	\item Case study 7:
+\end{itemize}
+
+%As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e.
 the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.
-
+%
 Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
@@
 HOMER Pro suggests a value in kW for the inverters that is very close to the peak of every case study, and it is just a reference value and not a commercial value of the inverter employed.
-The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf.
+The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst.
 This is a clear advantage of the formal synthesis method.
@@
 
-Summarizing, the synthesis tool is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+Summarizing, our synthesis tool is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
 In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including  the model of the component, nominal current and voltage.
 In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising).
+Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results.
 
@@
 These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by off-the-shelf optimization tools and the items of equipment for solar systems available on the market to achieve accuracy.
-Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.
+It is worth mentioning that our synthesis technique was developed and uses open-source tools and environment, in contrast to the optimization and simulation tools used in this work.
+Lastly, the use of data from real deployed systems in Amazonas State (Brazil) and the validation through PVsyst was essential to validate the comparison.
 
@@
 Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.
-
 %and aid the process of equipment purchase 
 %, e.g., complete electrical information from datasheet of manufacturers, including the component model, nominal current, and voltage, 
-
 %

### 2020-04-22 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

@@
 It contains: design, sizing, 3D shading scene, simulation, grid and off-grid features.
-It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis.
+It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis~\cite{PVsyst2017}.
 However, it does not performs optimization.
@@
 
-Those specific results partially answers the \textit{EQ2}.
+Those specific results partially answers the \textit{EG2}.
 
-HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}).
+HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EG3}).
 Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e.
@@
 it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
+
+The authors had four PV systems deployed and monitored since June $2018$ in a riverside community in State of Amazonas, Brazil, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total of $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
 
@@
 However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
-	\item Case study 6:
-	\item Case study 7:
+	\item Case study 6: PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries.
+This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $85.65$\%.
+Concerning our optimal solution it was not found error, the same as HOMER Pro.
+However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary;
+	\item Case study 7: PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries.
+This case has not field deployed to compare, and our approach did not produce feasible solution with the equipment list available.
+Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
 \end{itemize}
+
+Each simulation with PVsyst took 4 seconds.
+Overall, those comparison between our approach and optimization tool, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.
 
@@
 the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.
-%
-Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
-These solutions are closer to the results from PV panel, controller and inverter presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.
-However the solution presented for the battery bank is very different.
 
-HOMER Pro suggests a value in kW for the inverters that is very close to the peak of every case study, and it is just a reference value and not a commercial value of the inverter employed.
+HOMER Pro suggests a value in kW for the inverters that is very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed.
 The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst.

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
Revised Section 4.6
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The results are presented at Table~\ref{tab1}.
+The results are presented in Table~\ref{tab1}.
 
@@
 We have reported a favourable assessment of the proposed method.
-Nevertheless, we have also identified three threats to the validity of our results that constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; and (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
+Nevertheless, we have also identified four threats to the validity of our results that constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing; and (4) the underlying symbolic verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory; we could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
 

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
Revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %---------------------------------------------------------------------------
+
 The proposed synthesis approach was evaluated in seven stand-alone PV system case studies.
@@
 
-In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a complete simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank, in a comparison for a entire years weather data of simulation in order to guarantee that the proposed sizing meets the electrification requirements.
-PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation and data analysis of solar PV systems.
-It contains: design, sizing, 3D shading scene, simulation, grid and off-grid features.
-It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis~\cite{PVsyst2017}.
-However, it does not performs optimization.
-Drawbacks of PVsyst: it does nor perform optimization therefore it needs the system sized in order to validated it, PVsyst does not have commercial inverter equipment and therefore does not consider surge power demand as the ones produced by air conditioners and refrigerators for few seconds.
+In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a complete simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank.
+We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements.
+PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation, and data analysis of solar PV systems.
+PVsyst contains: design, sizing, 3D shading scene, simulation, grid, and off-grid features.
+It uses comprehensive irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}.
+However, it does not perform optimization.
+Drawbacks of PVsyst: it does not perform optimization; therefore, it needs the system sized in order to validate it.
+PVsyst does not have commercial inverter equipment and therefore does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds.
 PVsyst is a paid software with $30$-day test possibility and runs only in MS-Windows operational system.
@@
 %---------------------------------------------------------------------------
+
 Our evaluation aims to answer three experimental goals: [EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?; [EG2] \textbf{(performance)} How do the symbolic verifiers compare to each other for synthesizing PV systems?; and [EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
@@
 For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10.
-The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favourable to HOMER Pro.
+The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favorable to HOMER Pro.
 PVsyst used the same configuration as HOMER Pro.
@@
 The violation (SAT result) indicated all over the Table~\ref{tab1} 
-is the $assert$ of line $21$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
+is the $assert$ of the line $21$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
 
@@
 CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $254.25$ to $548$ minutes.
-Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left size as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron  Energy, and the inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power.
-The variables NTP, NPS, NPP, NBS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.
+Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left side as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron Energy.
+The inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power.
+The variables NTP, NPS, NPP, NBS, NBP, and NBTotal, also presented in the counterexample, shows the number of panels and batteries and how they are connected.
 
 Case studies $2$, $3$, $6$, and $7$ led to a \textit{time out} result in CPAchecker, i.e. it was not solved within $660$ minutes.  
-
+%
 \begin{figure}[h]
@@
 An internal failure was presented by ESBMC when using Z3 solver in all case studies.
-It corresponds to a 'bug' in the Z3 solver which will require an updated version of ESBMC to fix it.
+It corresponds to a 'bug' in the Z3 solver, which will require an updated version of ESBMC to fix it.
 However, when using the incremental BMC configuration of ESBMC with Boolector solver, the verifier engine was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response varying from $36.70$ to $620$ minutes.
 Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated.
-ESBMC with this configuration was not possible to obtain a optimal solution in cases $2$ and $7$.
+ESBMC with this configuration was not possible to obtain an optimal solution in cases $2$ and $7$.
 Case $2$ reached a \textit{time out} result after $660$ minutes of processing.
-Moreover, case $7$ resulted in a UNSAT result, i.e the verifier engine was not possible to get a feasible solution considering the list of equipment.
+Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was not possible to get a feasible solution considering the list of equipment.
 This SAT situation was reached after just $0.48$ minutes.
@@
 HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EG3}).
-Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e.
-the tool always tries to feed the given load with electricity $365$ days/year.
+Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year.
 
-Certain other HOMER Pro drawbacks were also noted: (1) System equipment does not include an explicit charge controller .
-HOMER Pro includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing; (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user.
-For example, it was started with a $83.4$ Ah lead-acid battery and during simulation, HOMER Pro did not try to use other capacities or types; and (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e.
-it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
+Certain other HOMER Pro drawbacks were also noted: (1) System equipment does not include an explicit charge controller.
+HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement.
+However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing.
+(2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user.
+For example, it was started with a $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types.
+(3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
 
-The authors had four PV systems deployed and monitored since June $2018$ in a riverside community in State of Amazonas, Brazil, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total of $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+The authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the State of Amazonas, Brazil, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, a total of $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
 
@@
 Table~\ref{tab1}).
-Related to performance there is a huge difference in favour of HOMER Pro that obtained the results in considerably less time: few seconds in opposite of an average of $234$ minutes for the automated synthesis technique.
+Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $234$ minutes for the automated synthesis technique.
 
 Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, always having a higher estimation from the automated synthesis technique.
-However, considering that the cost of individual item of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.
+However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.
 
-In one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool.
+On the one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool.
 The difference varied from $19$\% to $65$\%.
-In the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro.
-The difference was among $34$\% to $68$\%.
+On the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro.
+The difference was between $34$\% to $68$\%.
 The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.
@@
 Those discrepancies are not easy to address without some real systems validation.
-However we use the simulation software PVsyst in order to validate the optimal sizing produced.
-According PVsyst, we have to each case study:
+However, we use the simulation software PVsyst in order to validate the optimal sizing produced.
+According to PVsyst, we have to each case study:
 
@@
  	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries.
-This is a case that was deployed at the field ($975$ W of panels and $440$ Ah of batteries), and simulation showed that the availability is lower than the $95$\% ($91.06$\% to be precise), therefore the sizing that was done "by hand" is not correct.
+This is a case that was deployed at the field ($975$ W of panels and $440$ Ah of batteries), and simulation showed that the availability is lower than the $95$\% ($91.06$\% to be precise); therefore the sizing that was done "by hand" is not correct.
 Concerning our produced sizing, it was not found error during the 365-day of the year simulation, the same result for HOMER Pro.
-However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
 	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries.
-This case has not field deployed to compare, and our approach did not produce solution.
-Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
-	\item Case study 3: only our approach produced the optimal solution because there is the requirement of 12 hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than 24 hours;
+This case has not field deployed to compare, and our approach did not produce a solution.
+Only HOMER Pro left to comparison.
+However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
+	\item Case study 3: only our approach produced the optimal solution because there is a requirement of 12 hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than 24 hours;
 	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries.
 This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $87$\%.
-Concerning our optimal solution it was not found error, the same as HOMER Pro.
+Concerning our optimal solution, it was not found error, the same as HOMER Pro.
 However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
@@
 This one was deployed at the field, and PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries).
-Concerning our optimal solution it was not found error, the same as HOMER Pro.
+Concerning our optimal solution, it was not found error, the same as HOMER Pro.
 However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
@@
 This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $85.65$\%.
-Concerning our optimal solution it was not found error, the same as HOMER Pro.
-However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary;
+Concerning our optimal solution, it was not found error, the same as HOMER Pro.
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary;
 	\item Case study 7: PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries.
-This case has not field deployed to compare, and our approach did not produce feasible solution with the equipment list available.
-Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
+This case has not field deployed to compare, and our approach did not produce a feasible solution with the equipment list available.
+Only HOMER Pro left to comparison.
+However, PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
 \end{itemize}
@@
 Each simulation with PVsyst took 4 seconds.
-Overall, those comparison between our approach and optimization tool, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.
+Overall, those comparisons between our approach and optimization tool, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.
 
-%As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e.
-the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.
+HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed.
+The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst.
+This is a definite advantage of the formal synthesis method.
 
-HOMER Pro suggests a value in kW for the inverters that is very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed.
-The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst.
-This is a clear advantage of the formal synthesis method.
-
-HOMER Pro does not include charge controllers as an explicit item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis.
+HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis.
 The formal synthesis method, therefore, presents more reliable results than HOMER Pro.
@@
 
-Summarizing, our synthesis tool is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
-In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including  the model of the component, nominal current and voltage.
+Summarizing, our synthesis tool is capable of presenting a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage.
 In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising).

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
revised paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
-\keywords{Formal symthesis \and Automated verification  \and Model Checking \and Solar photovoltaic systems.}
+%\keywords{Formal symthesis \and Automated verification  \and Model Checking \and Solar photovoltaic systems.}
 \end{abstract}
@@
 The analytical method of optimization was adopted, with LCC economic analysis and power reliability based on critical period criteria (worst month's method).
-
+%
  \begin{algorithm}
@@
  \end{algorithm}
-
+%
 Our synthesis algorithm will synthesize constant values; 
@@
 
-If our algorithm does not find a feasible solution among the item of equipment that were provided for our {\sc Synthesize} phase,  then the result is unsatisfiable (\textit{UNSAT}), i.e.
-the program finishes without finding a solution, indicating that it was not possible to combine the specific items of equipment in order to create a feasible solution.
-
+If our algorithm does not find a feasible solution among the item of equipment that were provided for our {\sc Synthesize} phase,  then the result is unsatisfiable (\textit{UNSAT}), i.e., the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution.
+%
 The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements.
 The challenge for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase.
-
+%
 Note that the process described here is completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
@@
 
-In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a complete simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank.
+In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank.
 We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements.
-PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation, and data analysis of solar PV systems.
+PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation, and data analysis of solar PV systems.
 PVsyst contains: design, sizing, 3D shading scene, simulation, grid, and off-grid features.
-It uses comprehensive irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}.
-However, it does not perform optimization.
-Drawbacks of PVsyst: it does not perform optimization; therefore, it needs the system sized in order to validate it.
-PVsyst does not have commercial inverter equipment and therefore does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds.
+It uses comprehensive irradiation data from Meteonorm,\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}.
+However, it does not perform optimization; therefore, PVsyst needs the system sized in order to validate it.
+Furthermore, PVsyst does not have commercial inverter equipment and, as a result, does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds.
 PVsyst is a paid software with $30$-day test possibility and runs only in MS-Windows operational system.
@@
 The results are presented in Table~\ref{tab1}. 
-
+%
 \begin{table}
@@
 \end{table}
-
+%
 The violation (SAT result) indicated all over the Table~\ref{tab1} 
 is the $assert$ of the line $21$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
+Here, CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.
 
-CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.
-
-CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $254.25$ to $548$ minutes.
+CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $4$ to $9$ hours. 
 Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left side as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron Energy.
@@
 The variables NTP, NPS, NPP, NBS, NBP, and NBTotal, also presented in the counterexample, shows the number of panels and batteries and how they are connected.
-
-Case studies $2$, $3$, $6$, and $7$ led to a \textit{time out} result in CPAchecker, i.e. it was not solved within $660$ minutes.  
+Case studies $2$, $3$, $6$, and $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $660$ minutes.  
 %
@@
 \centering
-\caption{Counterexample generated by CPAchecker after validation of case 5 (file Counterexample.html).}
+\caption{Counterexample generated by CPAchecker after validation of case $5$.}
 \label{fig:CPAoptc1}
@@
 
-An internal failure was presented by ESBMC when using Z3 solver in all case studies.
-It corresponds to a 'bug' in the Z3 solver, which will require an updated version of ESBMC to fix it.
-However, when using the incremental BMC configuration of ESBMC with Boolector solver, the verifier engine was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response varying from $36.70$ to $620$ minutes.
-Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated.
-ESBMC with this configuration was not possible to obtain an optimal solution in cases $2$ and $7$.
-Case $2$ reached a \textit{time out} result after $660$ minutes of processing.
-Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was not possible to get a feasible solution considering the list of equipment.
-This SAT situation was reached after just $0.48$ minutes.
+%An internal failure was presented by ESBMC when using Z3 solver in all case studies. It corresponds to a 'bug' in the Z3 solver, which will require an updated version of ESBMC to fix it.
 
-\begin{figure}[h]
-\fbox{\includegraphics[width=1.0\textwidth]{ESBMC_SAT_case3.png}}
-\centering
-\caption{ESBMC counterexample for case 3 optimization.}
-\label{fig:esbmcoptcase3}
-\end{figure}
+Here we used ESBMC in incremental BMC configuration with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours.
+%Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated. 
+ESBMC with this configuration was unable to obtain an optimal solution in cases $2$ and $7$.
+Case $2$ reached a \textit{time out} result after $11$ hours.
+Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was unable to provide a feasible solution considering the equipment list \textcolor{red}{why?
+is it a bug in ESBMC?}.
+This UNSAT situation was reached in less than one minute.
+%
+%\begin{figure}[h]
+%\fbox{\includegraphics[width=1.0\textwidth]{ESBMC_SAT_case3.png}}
+%\centering
+%\caption{ESBMC counterexample for case 3 optimization.}
+%\label{fig:esbmcoptcase3}
+%\end{figure}
+%
+These experimental results partially answers the \textit{EG2} \textcolor{red}{why ``partially''? explain here}.
 
-Those specific results partially answers the \textit{EG2}.
-
-HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EG3}).
+HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EG3}).
 Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year.
 
-Certain other HOMER Pro drawbacks were also noted: (1) System equipment does not include an explicit charge controller.
+Some HOMER Pro drawbacks were also noted: (1) System equipment does not include an explicit charge controller.
 HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement.
@@
 
-Comparing the results of the formal synthesis with CPAchecker, and ESBMC, against those of HOMER Pro, it was observed some distinct results, in terms of technical solution and cost (cf.
+If we compare the results of the formal synthesis with CPAchecker and ESBMC against those of HOMER Pro, we observed some distinct results in terms of the technical solution and cost (cf.
 Table~\ref{tab1}).
-Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $234$ minutes for the automated synthesis technique.
+Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
 
-Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, always having a higher estimation from the automated synthesis technique.
+Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, always producing a higher estimation from the automated synthesis technique.
 However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.
 
-On the one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool.
+On the one hand, concerning the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the ones produced by the simulation tool.
 The difference varied from $19$\% to $65$\%.
-On the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro.
+On the other hand, concerning the battery bank, the results were smaller in terms of capacity to the HOMER Pro.
 The difference was between $34$\% to $68$\%.
-The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.
+The mathematical models are different and particular parameters can be tuned as well on each technique, and that can justify the difference, which was presented in all the case studies.
 
 Those discrepancies are not easy to address without some real systems validation.
-However, we use the simulation software PVsyst in order to validate the optimal sizing produced.
+However, we use the simulation software PVsyst to validate the optimal sizing produced.
 According to PVsyst, we have to each case study:
@@
  	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries.
-This is a case that was deployed at the field ($975$ W of panels and $440$ Ah of batteries), and simulation showed that the availability is lower than the $95$\% ($91.06$\% to be precise); therefore the sizing that was done "by hand" is not correct.
-Concerning our produced sizing, it was not found error during the 365-day of the year simulation, the same result for HOMER Pro.
+We deployed this case study in field ($975$ W of panels and $440$ Ah of batteries); simulations showed that the availability is lower than the $95$\%; therefore, the sizing that was manually carried out is not correct.
+Concerning our produced sizing, it was not found error during the $365$-day of the year simulation, the same result for HOMER Pro.
 However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
 	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries.
-This case has not field deployed to compare, and our approach did not produce a solution.
-Only HOMER Pro left to comparison.
+We did not deploy this case study in the field to perform a comparative evaluation; our approach did not produce a solution.
+Only HOMER Pro was left for comparison.
 However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
-	\item Case study 3: only our approach produced the optimal solution because there is a requirement of 12 hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than 24 hours;
+	\item Case study 3: only our approach produced the optimal solution because there exists a requirement of $12$ hours of battery autonomy.
+HOMER Pro and PVsyst do not allow autonomy less than $24$ hours;
 	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries.
-This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $87$\%.
-Concerning our optimal solution, it was not found error, the same as HOMER Pro.
-However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
+We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $87$\%.
+Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
 	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries.
-This one was deployed at the field, and PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries).
-Concerning our optimal solution, it was not found error, the same as HOMER Pro.
-However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
+We deployed this case study in the field; PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries).
+Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
 	\item Case study 6: PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries.
-This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $85.65$\%.
-Concerning our optimal solution, it was not found error, the same as HOMER Pro.
+We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $85.65$\%.
+Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
 However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary;
 	\item Case study 7: PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries.
-This case has not field deployed to compare, and our approach did not produce a feasible solution with the equipment list available.
-Only HOMER Pro left to comparison.
+We did not deploy this case study in the field deployed to perform a comparative evaluation; our approach did not produce a feasible solution with the equipment list available.
+Only HOMER Pro was left for comparisons.
 However, PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
@@
 
-Each simulation with PVsyst took 4 seconds.
+Each simulation with PVsyst took $4$ seconds.
 Overall, those comparisons between our approach and optimization tool, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.
@@
 HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed.
-The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst.
-This is a definite advantage of the formal synthesis method.
+The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf.
+Moreover, our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro or PVsyst.
+This feature is a definite advantage of the formal synthesis method.
 
@@
 Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
-Case study $2$ was solved just by the ESBMC verifier engine.
+Case study $2$ was solved just by the ESBMC verification engine.
 Case study $3$ could not be simulated in HOMER Pro, because of its restriction on setting battery autonomy, thus leaving those three cases without parameters to compare.
 
-Summarizing, our synthesis tool is capable of presenting a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+In summary, our synthesis tool can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
 In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage.
@@
 
-We have reported a favourable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing; and (4) the underlying symbolic verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory; we could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
+We have reported a favorable assessment of the proposed method.
+Nevertheless, we have also identified four threats to the validity of our results that constitute future work.
+(1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate.
+(2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis.
+(3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
+(4) the underlying symbolic verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory; we could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
 
@@
 These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by off-the-shelf optimization tools and the items of equipment for solar systems available on the market to achieve accuracy.
-It is worth mentioning that our synthesis technique was developed and uses open-source tools and environment, in contrast to the optimization and simulation tools used in this work.
+It is worth mentioning that our synthesis technique was developed and used open-source tools and environment, in contrast to the optimization and simulation tools used in this work.
 Lastly, the use of data from real deployed systems in Amazonas State (Brazil) and the validation through PVsyst was essential to validate the comparison.

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \end{equation}
-
+& &
 \begin{equation}
@@
 The analytical method of optimization was adopted, with LCC economic analysis and power reliability based on critical period criteria (worst month's method).
+
+\textcolor{red}{could you condense this algorithm by joining lines 5 to 8?}
+
 %
@@
 \begin{figure}[h]
-\fbox{\includegraphics[width=1.0\textwidth]{CPA_opt_c5.png}}
+\fbox{\includegraphics[width=0.9\textwidth]{CPA_opt_c5.png}}
 \centering
@@
 Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
-
-Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, always producing a higher estimation from the automated synthesis technique.
+%
+Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, producing a higher estimation from the automated synthesis technique.
 However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.
@@
 The difference was between $34$\% to $68$\%.
-The mathematical models are different and particular parameters can be tuned as well on each technique, and that can justify the difference, which was presented in all the case studies.
+The mathematical models are different and particular parameters can be tuned for each technique, and that can justify the difference, which was presented in all the case studies.
 
@@
 Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries than necessary;
 	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries.
@@
 	\item Case study 7: PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries.
-We did not deploy this case study in the field deployed to perform a comparative evaluation; our approach did not produce a feasible solution with the equipment list available.
+We did not deploy this case study in the field to perform comparisons; our approach did not produce a feasible solution with the equipment list available.
 Only HOMER Pro was left for comparisons.

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing PV systems.
-More specifically, we use a stand-alone configuration for this work since it is currently the most common system used for remote rural areas of developing countries or areas where the grid extension is not feasible.
+We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is unfeasible.
 We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis.
 We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market.
-Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different verification tools are evaluated, in order to evaluate performance and soundness.
-We also compare our  CEGIS approach with a commercial tool specialized in PV systems optimization, with both results being validated with a complete and accurate commercial design software; furthermore, some real PV systems comparison are used in order to show our approach effectiveness.
+Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different verification tools are evaluated to check performance and soundness.
+We also compare our CEGIS approach with a commercial tool specialized in PV systems optimization.
+Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness.
 %First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
@@
 Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}.
-Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
+There exists a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
 It follows that increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
-In order to provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}.
+In order to provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the connections needed~\cite{Hussein2012}.
 

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 However, we use the simulation software PVsyst to validate the optimal sizing produced.
-According to PVsyst, we have to each case study:
-
-\begin{itemize}
- 	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries.
+%According to PVsyst, we have to each case study:
+%
+%\begin{itemize}
+ For case study 1, PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries.
 We deployed this case study in field ($975$ W of panels and $440$ Ah of batteries); simulations showed that the availability is lower than the $95$\%; therefore, the sizing that was manually carried out is not correct.
 Concerning our produced sizing, it was not found error during the $365$-day of the year simulation, the same result for HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
-	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries.
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary.
+For case study 2, PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries.
 We did not deploy this case study in the field to perform a comparative evaluation; our approach did not produce a solution.
 Only HOMER Pro was left for comparison.
-However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
-	\item Case study 3: only our approach produced the optimal solution because there exists a requirement of $12$ hours of battery autonomy.
-HOMER Pro and PVsyst do not allow autonomy less than $24$ hours;
-	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries.
+However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary.
+
+For case study 3, only our approach produced the optimal solution because there exists a requirement of $12$ hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than $24$ hours;
+For case study 4, PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries.
 We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $87$\%.
 Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries than necessary;
-	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries.
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries than necessary.
+For case study 5, PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries.
 We deployed this case study in the field; PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries).
 Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
-	\item Case study 6: PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries.
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary.
+
+For case study 6, PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries.
 We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $85.65$\%.
 Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary;
-	\item Case study 7: PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries.
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary.
+For case study 7, PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries.
 We did not deploy this case study in the field to perform comparisons; our approach did not produce a feasible solution with the equipment list available.
@@
 However, PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
-\end{itemize}
+%\end{itemize}
 

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
VSTTE 2020 paper update

@@
 \begin{figure}[h]
-\includegraphics[width=0.9\textwidth]{optimalsizingprocess4}
+\fbox{\includegraphics[width=0.9\textwidth]{optimalsizingprocess4}}
 \centering
@@
 \begin{center}
-\includegraphics[width=0.75\textwidth]{fig2_rev2.jpg}
+\fbox{\includegraphics[width=0.75\textwidth]{fig2_rev2.jpg}}
 \end{center}
@@
 \begin{figure}[h]
-\includegraphics[width=0.8\textwidth]{blockdiagramPVS2_rev}
+\fbox{\includegraphics[width=0.8\textwidth]{blockdiagramPVS2_rev}}
 \centering
@@
 $DOD$ is the
-the depth of discharge or the fraction of discharge (usually 25\% for lead-acid batteries, and 80\% for lithium batteries).
+the depth of discharge or the fraction of discharge.
+The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries; that represents a State of Charge (SOC) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
 However it is worth to separate the $DOD$ into two different definitions when the battery autonomy is bigger than one day ($24$ hours).
@@
 Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load.
+Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load, i.e.
+the outlet voltage.
 Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
@@
 
-\textcolor{red}{could you condense this algorithm by joining lines 5 to 8?}
-
-%
- \begin{algorithm}
+ \begin{algorithm}[h]
  \caption{Synthesis algorithm}
@@
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
-  \REQUIRE weather data (temperature, solar irradiance); list of PV panels, controllers, batteries, and inverters datasheet information and cost; design requirements (load curve, peak demand, load surge power, daily energy consumption, battery autonomy, AC voltage); design assumptions (battery state of charge, depth of discharge, criteria and objectives for technical and cost analysis)
+  \REQUIRE weather data (temperature, solar irradiance); data from panels, controllers, batteries, and inverters; design requirements (load curve, peak demand, load surge power, energy consumption, battery autonomy, AC voltage); design assumptions (SOC, DOD, criteria and objectives for technical and cost analysis)
  \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
@@
   \FOR {$HintCost=MinCost$ to $MaxCost$} 
- 	\STATE Declare non-deterministic variable to select PV Panel from list \\
- 	\STATE Declare non-deterministic variable to select Controller from list \\
- 	\STATE Declare non-deterministic variable to select Battery from list \\
- 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
+ 	\STATE Declare non-deterministic variables to select PV Panel, Controller, Battery, and Inverter from list \\
+% 	\STATE Declare non-deterministic variable to select Controller from list \\
+% 	\STATE Declare non-deterministic variable to select Battery from list \\
+% 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
  	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
@@
  \end{algorithm}
-%
+
 Our synthesis algorithm will synthesize constant values; 
@@
 The \textit{for}-loop started at line $4$ controls the lowest cost of the PV solution.
-In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $21$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+In particular, it starts with cost $MinCost$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $18$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
 The $MaxCost$ value at line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
 
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (lines $5$ to $8$).
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (line $5$).
 This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.
@@
 Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $9$ to $15$).
-The directive \textit{assume} (lines $11$, $16$, $17$ and $18$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of lines $11$, $16$, $17$ and $18$.
-Line $11$ is specific to PV panels.
-Line $16$ is for the battery bank.
-Line $17$ is the charge controller voltage check.
-Line $18$ does the inverter check and ensures the power demand and the surge power of the inverter.
-Therefore, our synthesis algorithm reaches line $19$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $20$). This cost is the equivalent to~\ref{eq:LCC}.
+The directive \textit{assume} (lines $8$, $13$, $14$ and $15$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines.
+Line $5$ is specific to PV panels.
+Line $13$ is for the battery bank.
+Line $14$ is the charge controller voltage check.
+Line $15$ does the inverter check and ensures the power demand and the surge power of the inverter.
+Therefore, our synthesis algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$). This cost is the equivalent to~\ref{eq:LCC}.
 
@@
 The violation (SAT result) indicated all over the Table~\ref{tab1} 
-is the $assert$ of the line $21$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
+is the $assert$ of the line $18$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
 Here, CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.
@@
 ESBMC with this configuration was unable to obtain an optimal solution in cases $2$ and $7$.
-Case $2$ reached a \textit{time out} result after $11$ hours.
-Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was unable to provide a feasible solution considering the equipment list \textcolor{red}{why?
-is it a bug in ESBMC?}.
+Case $2$ produced a \textit{time out}.
+Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was unable to provide a feasible solution.
+However this is not a bug, and it means that the available list of equipment can not produce an feasible solution that satisfies electrical compatibility or the design requirements.
 This UNSAT situation was reached in less than one minute.
@@
 %
-These experimental results partially answers the \textit{EG2} \textcolor{red}{why ``partially''? explain here}.
+These experimental results answers the \textit{EG2}.
 
@@
 %According to PVsyst, we have to each case study:
+\textcolor{red}{do you think whether it is possible to summarise these results in a table?}
 %

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

@@
 Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing PV systems.
-We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is unfeasible.
+We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is infeasible.
 We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis.
@@
 In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
-However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is infeasible~\cite{ClarkeHV18}.
 Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
@@
 In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
+In $2017$, a researcher suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}.
 In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
@@
 %A photovoltaic system 
-employs: the PV generator, which can be a \textbf{panel or an array}, is a semiconductor device that can convert solar energy into DC electricity; for night hours or rainy days, we hold \textbf{batteries} where power can be stored and used; the use of batteries as a storage form implies the presence of a \textbf{charge controller}~\cite{Hansen}; the PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textbf{inverter}); the \textbf{AC load} dictates the behavior of the AC electrical load from the house that will be fed by the system.
+employs: the PV generator, which can be a \textbf{panel or an array}, is a semiconductor device that can convert solar energy into DC electricity; for night hours or rainy days, we hold \textbf{batteries} where power can be stored and used; the use of batteries as a storage form implies the presence of a \textbf{charge controller}~\cite{Hansen}; the PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textbf{inverter}); the \textbf{AC load} dictates the behaviour of the AC electrical load from the house that will be fed by the system.
 
@@
 the depth of discharge or the fraction of discharge.
-The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries; that represents a State of Charge (SOC) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
+The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
 However it is worth to separate the $DOD$ into two different definitions when the battery autonomy is bigger than one day ($24$ hours).
@@
 For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10.
-The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favorable to HOMER Pro.
+The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favourable to HOMER Pro.
 PVsyst used the same configuration as HOMER Pro.
@@
 Table~\ref{tab1}).
-Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
+Concerning the performance, there exists a vast difference in favour of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
 %
@@
 Those discrepancies are not easy to address without some real systems validation.
-However, we use the simulation software PVsyst to validate the optimal sizing produced.
-%According to PVsyst, we have to each case study:
-\textcolor{red}{do you think whether it is possible to summarise these results in a table?}
-%
+However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in ~\ref{tab2}.
+Worth to mention that PVsyst has a pre-sizing feature, indicated in the table, that presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers data or models for it; this feature was used as reference mainly with HOMER Pro, where there is not equipment brands or models (only power and capacities specification).
+The full feature of PVsyst was used with the field deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according with the sized system.%According to PVsyst, we have to each case study:
+
+\begin{table}
+\caption{Optimal sizing validation with PVsyst.}
+\label{tab2}
+\begin{scriptsize}
+\begin{tabular}{c|c|c|c|c}
+\hline
+\hline
+CS & \makecell{PVsyst\\(pre-sizing)}& \makecell{Field\\deployed\\validation}& \makecell{Formal synthesis\\sizing\\validation}& \makecell{HOMER Pro\\sizing\\validation}\\
+\hline
+\hline
+CS 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail.
+$<$ 95\%\\(91.06\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.16 $\times$\\Batteries oversized in 1.39 $\times$}\\
+\hline
+CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)} & \makecell{NA\\There is not real PV system\\available for comparison} & \makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.6 $\times$\\Batteries oversized in 1.74 $\times$}\\
+\hline
+CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} & \makecell{NA\\There is not real PV system\\available for comparison} & \makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
+\hline
+CS 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)} & \makecell{No error found \\95.76\% of avail.} & \makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized in 2.24 $\times$\\Batteries oversized in 1.41 $\times$}\\
+\hline
+CS 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 1.93 $\times$\\Batteries oversized in 1.56 $\times$}\\
+\hline
+CS 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail.
+$<$ 95\%\\(85.65\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.42 $\times$\\Batteries oversized in 1.38 $\times$}\\
+\hline
+CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)} & \makecell{NA\\There is not real PV system\\available for comparison} & \makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.9 $\times$\\Batteries oversized in 1.99 $\times$}\\
+\hline
+\hline
+\end{tabular}
+\\Legend: CS = case study; NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater as a design requirement).
+\end{scriptsize}
+\end{table}
+
 %\begin{itemize}
- For case study 1, PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries.
+%For case study 1, PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries.
 We deployed this case study in field ($975$ W of panels and $440$ Ah of batteries); simulations showed that the availability is lower than the $95$\%; therefore, the sizing that was manually carried out is not correct.
 Concerning our produced sizing, it was not found error during the $365$-day of the year simulation, the same result for HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary.
-For case study 2, PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries.
+However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.39$ times more for batteries capability than necessary.
+%For case study 2, PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries.
 We did not deploy this case study in the field to perform a comparative evaluation; our approach did not produce a solution.
@@
 However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary.
-
-For case study 3, only our approach produced the optimal solution because there exists a requirement of $12$ hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than $24$ hours;
-For case study 4, PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries.
+%
+%For case study 3, only our approach produced the optimal solution because there exists a requirement of $12$ hours of battery autonomy.
+HOMER Pro and PVsyst do not allow autonomy less than $24$ hours;
+%For case study 4, PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries.
 We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $87$\%.
@@
 However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries than necessary.
-For case study 5, PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries.
+%For case study 5, PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries.
 We deployed this case study in the field; PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries).
@@
 However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary.
-
-For case study 6, PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries.
+%
+%For case study 6, PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries.
 We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $85.65$\%.
@@
 However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary.
-For case study 7, PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries.
+%For case study 7, PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries.
 We did not deploy this case study in the field to perform comparisons; our approach did not produce a feasible solution with the equipment list available.
@@
 Each simulation with PVsyst took $4$ seconds.
-Overall, those comparisons between our approach and optimization tool, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.
+Case study $3$ was not possible to be validated by PVsyst because the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a 24 h minimum autonomy).
+Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there is not deployed equivalent system in the field, and the synthesis technique did not presented a solution (our technique presented a \textit{time out} in case study $2$ and a \textit{UNSAT} in case study $7$).
+
+Overall, those comparisons among our approach, the optimization software, and the deployed systems, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.
 
@@
 The formal synthesis method, therefore, presents more reliable results than HOMER Pro.
-
-Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
+%
+%Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
 Case study $2$ was solved just by the ESBMC verification engine.
@@
 In summary, our synthesis tool can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
-In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage.
+In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data-sheet, including the model of the component, nominal current, and voltage.
 In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising).
-Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results.
+Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results, mainly concerning PV panels.
 
@@
 
-We have reported a favorable assessment of the proposed method.
+We have reported a favourable assessment of the proposed method.
 Nevertheless, we have also identified four threats to the validity of our results that constitute future work.

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
revised VSTTE 2020 paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 The use of power generation with renewable energy sources is proliferating due to industrial development.
-Photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel energy generation.
+Photovoltaic (PV) panels have emerged as an alternative to the fossil or nuclear fuel energy generation.
 The use of formal methods for PV systems is a new subject with significant research spanning only the last five years.
@@
 Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness.
-%First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost.
-Second, the candidate is then verified iteratively with a lower bound cost via model checking.
-If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution.
-%However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
-%\keywords{Formal symthesis \and Automated verification  \and Model Checking \and Solar photovoltaic systems.}
 \end{abstract}
@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, in 2017, the number of people without electricity access fell below $1$ billion threshold for the first time~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, in 2017, the number of people without electricity access fell below $1$ billion thresholds for the first time~\cite{IEAweo2018}.
 The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
@@
 In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
-However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is infeasible~\cite{ClarkeHV18}.
-Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
+However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations, and potential failures of a system are infeasible~\cite{ClarkeHV18}.
+Non-linear optimization tools could be employed since a PV system is typically modeled as a non-linear set of equations.
 However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialist PV optimization software.
@@
 In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, a researcher suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}.
+In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
 In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
@@
 Here the application of formal methods to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools.
-Second, we evaluate our approach using different state-of-the-art verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems and compare that to HOMER Pro optimization, with the results being validated with a complete and accurate commercial design software called PVsyst.
+Second, we evaluate our approach using different state-of-the-art verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.
+We compare that to HOMER Pro optimization, with the results being validated with accurate commercial design software called PVsyst.
 Lastly, we discuss the challenges of applying formal methods to PV systems and reflect on lessons learned from this experience.
@@
 Both techniques (traditional and automated synthesis) produce as output either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
-On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
+On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
 Furthermore, the design-space coverage during the optimal sizing search is sound and complete when using synthesis.
@@
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
-In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
+In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as a starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
 As a result, a given candidate program $p$ is iteratively refined to match $\sigma$ more closely.
@@
 However, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists.
-%, and our synthesis engine can then conclude that no possible equipment combination was found.
 
@@
 (3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; as a result,
-(4) there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
+(4) there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase.
+In particular, a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
 
@@
 A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It 
-%A photovoltaic system 
 employs: the PV generator, which can be a \textbf{panel or an array}, is a semiconductor device that can convert solar energy into DC electricity; for night hours or rainy days, we hold \textbf{batteries} where power can be stored and used; the use of batteries as a storage form implies the presence of a \textbf{charge controller}~\cite{Hansen}; the PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textbf{inverter}); the \textbf{AC load} dictates the behaviour of the AC electrical load from the house that will be fed by the system.
 
-%\begin{wrapfigure}{r}{0.5\textwidth}
 \begin{figure}[h]
@@
 
-\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries, usually is a design definition and has a value ranging from $0.5$ to $2$ days.
-$DOD$ is the
-the depth of discharge or the fraction of discharge.
+\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days.
+$DOD$ is the depth of discharge or the fraction of discharge.
 The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
-However it is worth to separate the $DOD$ into two different definitions when the battery autonomy is bigger than one day ($24$ hours).
-Therefore, here in this thesis, the definition given here is for maximum $DOD$.
-When we deal with daily $DOD$ we will call it of $DOD_{day}$, and obviously the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
+However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is bigger than one day ($24$ hours).
+Therefore, here in this thesis, the definition given here is for a maximum of $DOD$.
+When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
 
 In order to define the $DOD_{day}$ we use Eq.~\eqref{eq:DODday}.
-Moreover, the minimum current from DC bus is defined by Eq.~\eqref{eq:Idcbus}.
+Moreover, the minimum current from the DC bus is defined by Eq.~\eqref{eq:Idcbus}.
 This equation is important to define the battery arrangement of the system (series and parallel connections).
@@
 
-\noindent where $ E_{load} $ is the average energy consumed by the load corrected according PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
+\noindent where $ E_{load} $ is the average energy consumed by the load corrected according to PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
 
@@
 Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load, i.e.
-the outlet voltage.
+Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load, i.e., the outlet voltage.
 Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
@@
 
-All the equations above model the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
+All the equations above model the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
 The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
@@
  	\STATE Declare non-deterministic variables to select PV Panel, Controller, Battery, and Inverter from list \\
-% 	\STATE Declare non-deterministic variable to select Controller from list \\
-% 	\STATE Declare non-deterministic variable to select Battery from list \\
-% 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
  	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
@@
 Our synthesis algorithm will synthesize constant values; 
-it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers and inverters. Moreover, we define design (house) requirements and design assumptions.
+it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers, and inverters. Moreover, we define design (house) requirements and design assumptions.
 
 The \textit{for}-loop started at line $4$ controls the lowest cost of the PV solution.
-In particular, it starts with cost $MinCost$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $18$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+In particular, it starts with cost $MinCost$ and stops when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $18$.
+If that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
 The $MaxCost$ value at line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
 
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (line $5$).
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (line $5$).
 This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.
 A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine in order to allow the choice of every item of PV sizing.
-Data sheet from each item was necessary to collect technical information.
+Datasheet from each item was necessary to collect technical information.
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
@@
 Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $9$ to $15$).
-The directive \textit{assume} (lines $8$, $13$, $14$ and $15$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines.
+The directive \textit{assume} (lines $8$, $13$, $14$, and $15$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines.
 Line $5$ is specific to PV panels.
@@
 
-If our algorithm does not find a feasible solution among the item of equipment that were provided for our {\sc Synthesize} phase,  then the result is unsatisfiable (\textit{UNSAT}), i.e., the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution.
+If our algorithm does not find a feasible solution among the item of equipment that was provided for our {\sc Synthesize} phase, then the result is unsatisfiable (\textit{UNSAT}).
+In particular, the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution.
 %
@@
 %
-Note that the process described here is completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
 
@@
 We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements.
-PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation, and data analysis of solar PV systems.
-PVsyst contains: design, sizing, 3D shading scene, simulation, grid, and off-grid features.
+PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation and data analysis of solar PV systems.
+PVsyst contains design, sizing, 3D shading scene, simulation, grid, and off-grid features.
 It uses comprehensive irradiation data from Meteonorm,\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}.
@@
 
-%An internal failure was presented by ESBMC when using Z3 solver in all case studies. It corresponds to a 'bug' in the Z3 solver, which will require an updated version of ESBMC to fix it.
-
 Here we used ESBMC in incremental BMC configuration with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours.
-%Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated. 
-ESBMC with this configuration was unable to obtain an optimal solution in cases $2$ and $7$.
+ESBMC, with this configuration, was unable to obtain an optimal solution in cases $2$ and $7$.
 Case $2$ produced a \textit{time out}.
 Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was unable to provide a feasible solution.
-However this is not a bug, and it means that the available list of equipment can not produce an feasible solution that satisfies electrical compatibility or the design requirements.
+However, this is not a bug, and it means that the available list of equipment can not produce a feasible solution that satisfies electrical compatibility or design requirements.
 This UNSAT situation was reached in less than one minute.
-%
-%\begin{figure}[h]
-%\fbox{\includegraphics[width=1.0\textwidth]{ESBMC_SAT_case3.png}}
-%\centering
-%\caption{ESBMC counterexample for case 3 optimization.}
-%\label{fig:esbmcoptcase3}
-%\end{figure}
-%
-These experimental results answers the \textit{EG2}.
+These experimental results answer the \textit{EG2}.
 
@@
 Table~\ref{tab1}).
-Concerning the performance, there exists a vast difference in favour of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
+Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
 %
@@
 However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in ~\ref{tab2}.
-Worth to mention that PVsyst has a pre-sizing feature, indicated in the table, that presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers data or models for it; this feature was used as reference mainly with HOMER Pro, where there is not equipment brands or models (only power and capacities specification).
-The full feature of PVsyst was used with the field deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according with the sized system.%According to PVsyst, we have to each case study:
+Note that PVsyst has a pre-sizing feature, indicated in the table, that presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it.
+This feature was used as reference mainly with HOMER Pro, where there is not equipment brands or models (only power and capacities specification).
+The full feature of PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.
 
@@
 
-%\begin{itemize}
-%For case study 1, PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries.
-We deployed this case study in field ($975$ W of panels and $440$ Ah of batteries); simulations showed that the availability is lower than the $95$\%; therefore, the sizing that was manually carried out is not correct.
-Concerning our produced sizing, it was not found error during the $365$-day of the year simulation, the same result for HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.39$ times more for batteries capability than necessary.
-%For case study 2, PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries.
-We did not deploy this case study in the field to perform a comparative evaluation; our approach did not produce a solution.
-Only HOMER Pro was left for comparison.
-However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary.
-%
-%For case study 3, only our approach produced the optimal solution because there exists a requirement of $12$ hours of battery autonomy.
-HOMER Pro and PVsyst do not allow autonomy less than $24$ hours;
-%For case study 4, PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries.
-We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $87$\%.
-Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries than necessary.
-%For case study 5, PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries.
-We deployed this case study in the field; PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries).
-Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary.
-%
-%For case study 6, PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries.
-We deployed this case study in the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed an incorrect sizing since the system availability was only $85.65$\%.
-Concerning our optimal solution, it was not found an error, the same as HOMER Pro.
-However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary.
-%For case study 7, PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries.
-We did not deploy this case study in the field to perform comparisons; our approach did not produce a feasible solution with the equipment list available.
-Only HOMER Pro was left for comparisons.
-However, PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
-%\end{itemize}
-
 Each simulation with PVsyst took $4$ seconds.
 Case study $3$ was not possible to be validated by PVsyst because the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a 24 h minimum autonomy).
-Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there is not deployed equivalent system in the field, and the synthesis technique did not presented a solution (our technique presented a \textit{time out} in case study $2$ and a \textit{UNSAT} in case study $7$).
+Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there is not deployed equivalent system in the field, and the synthesis technique did not present a solution (our technique presented a \textit{time out} in case study $2$ and a \textit{UNSAT} in the case study $7$).
 
@@
 The formal synthesis method, therefore, presents more reliable results than HOMER Pro.
-%
-%Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase.
-Case study $2$ was solved just by the ESBMC verification engine.
-Case study $3$ could not be simulated in HOMER Pro, because of its restriction on setting battery autonomy, thus leaving those three cases without parameters to compare.
 
 In summary, our synthesis tool can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
-In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data-sheet, including the model of the component, nominal current, and voltage.
-In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising).
+In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage.
+In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising).
 Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results, mainly concerning PV panels.
@@
 
-We have reported a favourable assessment of the proposed method.
+We have reported a favorable assessment of the proposed method.
 Nevertheless, we have also identified four threats to the validity of our results that constitute future work.
@@
 (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
-(4) the underlying symbolic verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory; we could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
+(4) the underlying symbolic verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory.
+We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
 
@@
 
-%Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using contemporary formal methods.
-The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising.
-Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool.
-In particular, the battery autonomy feature together with the details of every component of a PV system solution are an advantage for our synthesis approach.
-These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market; and not just maximum or minimum values of parameters given by off-the-shelf optimization tools, which still need to be adjusted according to the chosen equipment.
-Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.
-%and aid the process of equipment purchase 
-%, e.g., complete electrical information from datasheet of manufacturers, including the component model, nominal current, and voltage, 
 %

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.96}
+\renewcommand{\baselinestretch}{0.98}
 
@@
 This feature was used as reference mainly with HOMER Pro, where there is not equipment brands or models (only power and capacities specification).
-The full feature of PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.
+PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.
 
@@
 Each simulation with PVsyst took $4$ seconds.
-Case study $3$ was not possible to be validated by PVsyst because the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a 24 h minimum autonomy).
-Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there is not deployed equivalent system in the field, and the synthesis technique did not present a solution (our technique presented a \textit{time out} in case study $2$ and a \textit{UNSAT} in the case study $7$).
+We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a 24 h minimum autonomy).
+Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there exists no deployed equivalent system in the field, and the synthesis technique did not present a solution due to time-out and internal failures in the underlying verification engine.
+%(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).
 

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market.
-Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different verification tools are evaluated to check performance and soundness.
+Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness.
 We also compare our CEGIS approach with a commercial tool specialized in PV systems optimization.

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness.
+\keywords{Formal Synthesis \and Automated Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
 \end{abstract}
@@
 In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
-The candidate solution is then verified via model checking with a lower bound that serves as the minimum cost of reference.
+The candidate solution is then verified via software model checking with a lower bound that serves as the minimum cost of reference.
 If the verification step does not produce a counterexample, then the lower bound is adjusted; otherwise, we have achieved an optimal PV sizing.
@@
 Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing.
-First, the use of automated verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}.
-Here the application of formal methods to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools.
-Second, we evaluate our approach using different state-of-the-art verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.
+First, the use of automated software verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}.
+Here the application of software verification to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools.
+Second, we evaluate our approach using different state-of-the-art software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.
 We compare that to HOMER Pro optimization, with the results being validated with accurate commercial design software called PVsyst.
-Lastly, we discuss the challenges of applying formal methods to PV systems and reflect on lessons learned from this experience.
+Lastly, we discuss the challenges of applying software verification to PV systems and reflect on lessons learned from this experience.
 

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 For the automated synthesis, we also define the bound $k$ to restrict the design-space search.
-Here we start with a low bound $k$ and incrementally increase it to avoid time and memory constraints on our verification back-end.
+Here we start with a low bound $k$ and incrementally increase it to avoid time and memory constraints on our verification engine.
 Therefore, the proper choice of $k$ is essential to this method.
@@
 
-A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It 
-employs: the PV generator, which can be a \textbf{panel or an array}, is a semiconductor device that can convert solar energy into DC electricity; for night hours or rainy days, we hold \textbf{batteries} where power can be stored and used; the use of batteries as a storage form implies the presence of a \textbf{charge controller}~\cite{Hansen}; the PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textbf{inverter}); the \textbf{AC load} dictates the behaviour of the AC electrical load from the house that will be fed by the system.
+A PV system is illustrated in Fig.\ref{fig:blockdiagram}.
+It employs the PV generator (\textit{panel or an array}), which is a semiconductor device that can convert solar energy into DC electricity.
+For night hours or rainy days, we hold \textit{batteries}, where power can be stored and used.
+The use of batteries as a storage form implies the presence of a \textit{charge controller}~\cite{Hansen}.
+The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textit{inverter}).
+The \textit{AC load} dictates the behavior of the AC electrical load from the house that will be fed by the system.
 
@@
 On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
-On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as shown in Eq.~\eqref{eq:Icmin} and
+On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as described by Eqs.~\eqref{eq:Icmin} and
 \eqref{eq:Vcmin}.
@@
 
-Related to the batteries, the energy $E_{b}$ to be demanded by the PV system, in order to meet the load requirements, is defined by Eq.~\eqref{eq:Ebat}.
+Concerning the batteries, the energy $E_{b}$ to be demanded by the PV system, in order to meet the load requirements, is defined by Eq.~\eqref{eq:Ebat}.
 
@@
 The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
-However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is bigger than one day ($24$ hours).
-Therefore, here in this thesis, the definition given here is for a maximum of $DOD$.
+However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours).
+Therefore, here in this study, the definition given here is for a maximum of $DOD$.
 When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
 
-In order to define the $DOD_{day}$ we use Eq.~\eqref{eq:DODday}.
+In order to define the $DOD_{day}$, we use Eq.~\eqref{eq:DODday}.
 Moreover, the minimum current from the DC bus is defined by Eq.~\eqref{eq:Idcbus}.
@@
 \noindent where $ E_{load} $ is the average energy consumed by the load corrected according to PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
-
-Equation \ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted in the project.
+%
+Eq.~\ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted in the project.
 
@@
 
-The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because field temperature is higher than nominal or laboratory temperature, and the PV system is temperature dependent, as shown by Equation~\eqref{eq:iscamb}.
+The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because field temperature is higher than nominal or laboratory temperature, and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb}.
 
@@
 
-The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Equation \ref{eq:numberofcmin}.
-Besides, the final sizing check is performed by Equation \ref{eq:numberofc}, which validates the number of controllers adopted.
+The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Eq.~\eqref{eq:numberofcmin}.
+Besides, the final sizing check is performed by Eq.~\eqref{eq:numberofc}, which validates the number of controllers adopted.
 
@@
 
-Some inverter models allow parallel operation of more than one unit, besides the integration in order to create bi-phase and three-phase circuits.
-It is advisable to use pure sine wave inverters, especially for electronic loads sensitive to harmonic distortion waves.
+Some inverter models allow parallel operation of more than one unit, besides the integration to create bi- and three-phase circuits.
+It is advisable to use pure sine wave inverters for electronic loads sensitive to harmonic distortion waves.
 
@@
 Furthermore, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side.
-Then the controller can be overcharged during this operation and to burn.
+Then the controller can be overcharged during this operation and burn.
 

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

@@
 
-Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} technique for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} technique for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
 Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
@@
 Both techniques (traditional and automated synthesis) produce as output either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
-On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
+On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is mathematical reasoning about a model, presents a counterexample with the optimal solution stored in variables.
 Furthermore, the design-space coverage during the optimal sizing search is sound and complete when using synthesis.
@@
 %
-Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
 
@@
 
-Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using contemporary formal methods.
+Our novelty relies on a practical approach to pursue the optimal solution of PV systems using contemporary formal methods.
 The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising.
-Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool.
+Our synthesis tool can present a solution, which is far more detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool.
 In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach.

### 2020-04-25 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

@@
 In particular, Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis.
-Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions) except for the automated synthesis where we also define the bound $k$ to restrict the design-space search.
+Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions; except for the automated synthesis where we also define the bound $k$ to restrict the design-space search.
 Related to the output presented by both techniques, all of them produce a successful or fail result considering a feasible technical solution with the lowest cost.
@@
 
-Related to off-the-shelf simulation tools only HOMER Pro perform off-grid system with battery backup analysis and includes economical analysis.
+Related to off-the-shelf simulation tools only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis.
 Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
@@
 While in a ordinary house electrical load, 95\% is considered acceptable; (f) it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; (g) the premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling).
+With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modelling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
@@
 This section describes our case studies, experimental setup,  objectives, and results to evaluate our proposed synthesis approach.
-We also compare our approach with a specialized simulation tool (HOME Pro).
+We also compare our approach with a specialized simulation tool (HOMER Pro).
 
@@
 This may explain the difference presented in all case studies.
-As comparative, consider case study $1$: the optimal solution provided by HOMER Pro demands $7$ $\times$ more PV panels than the solution presented by our synthesis tool, and HOME Pro does not show the arrangement of arrays (i.e., the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides $500.4$ Ah of capacity ($6 \times 83.4$), while our synthesis tool presented an optimal solution with $420$ Ah of total capacity ($4 \times 105$).
+As comparative, consider case study $1$: the optimal solution provided by HOMER Pro demands $7$ $\times$ more PV panels than the solution presented by our synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e., the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides $500.4$ Ah of capacity ($6 \times 83.4$), while our synthesis tool presented an optimal solution with $420$ Ah of total capacity ($4 \times 105$).
 
@@
 Concerning the charge controllers, as we reported in the previous section, HOMER Pro does not include it as an explicit equipment in its mathematical model and does not includes the cost for the charge controller; only our synthesis tool presents a commercial controller and includes it during the cost analysis.
-Therefore, the formal synthesis method presents more reliable results than HOME Pro.
+Therefore, the formal synthesis method presents more reliable results than HOMER Pro.
 

### 2020-04-25 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

@@
 To simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}; and even general-purpose simulation tools, as  MATLAB~\cite{Benatiallah2017}.
-However, these tools rely on simulation, with the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
+However, these tools rely on simulation, with the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is infeasible~\cite{ClarkeHV18}.
 
@@
 In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
+In $2017$, a researcher suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}.
 Finally, in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
@@
 The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required.
-The AC load dictates the AC electrical load behavior from the house.
+The AC load dictates the AC electrical load behaviour from the house.
 %
@@
 
-During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
+During the PV system design, one of the most important aspects to ensure power system reliability is to analyse power supply availability~\cite{Alsadi2018}.
 The reason is that solar energy production is intermittent and, therefore, the energy generated usually does not match with the load demand.
@@
 LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
-On the one hand,  we have a reliable PV system when it can generate sufficient power to fulfill the demanded load within a period.
+On the one hand,  we have a reliable PV system when it can generate sufficient power to fulfil the demanded load within a period.
 On the other hand, LPSP is defined as the probability of the case when the system generates insufficient power to satisfy the load demand.
@@
 Analytical methods are used to obtain a close relation or correlation in the form of an equation between capacities and reliabilities.
-The sizing task becomes much more straightforward than numerical technique; however, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
+The sizing task becomes much more straightforward than numerical technique; however, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analysed.
 
@@
 
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
-Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies all behaviors explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}.
+Although simulation and testing explore possible behaviours and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
+Formal verification conducts an exhaustive exploration of all possible behaviours; when a design is said to be ``correct'' by a formal verification method, it implies all behaviours explored, and questions regarding adequate coverage or missed behaviour becomes irrelevant~\cite{Clarke2012}.
 Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
@@
 ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$.
-Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, and we calcuate the cost of that solution in $F_{obj}$ (line $21$).
+Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, and we calculate the cost of that solution in $F_{obj}$ (line $21$).
 
@@
 with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
-Our experiments were performed with a predefined timeout of $240$ minutes.
+Our experiments were performed with a predefined time out of $660$ minutes.
 
@@
 CPAchecker was able to synthesize the optimal sizing in six out of seven case studies: the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
-Only case study $7$ led to a \textit{timeout} result, i.e., it was not solved within $240$ minutes.
-However, if we remove this timeout limitation from CPAchecker, the verifier can solve the optimization in $44.97$ hours.
+Only case study $7$ led to a \textit{time out} result, i.e., it was not solved within $240$ minutes.
+However, if we remove this time out limitation from CPAchecker, the verifier can solve the optimization in $44.97$ hours.
 The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
@@
 related to charge controllers, which we introduced into the 
-CPAchecker modeling. The premise used in CPAchecker to adopt 
+CPAchecker modelling. The premise used in CPAchecker to adopt 
 a fixed annual cost for operation and maintenance can produce 
@@
 
-We have reported a favorable assessment of our formal synthesis method to obtain the optimal size of the PV system. 
+We have reported a favourable assessment of our formal synthesis method to obtain the optimal size of the PV system. 
 Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and 

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

@@
 However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations, and potential failures of a system are infeasible~\cite{ClarkeHV18}.
-Non-linear optimization tools could be employed since a PV system is typically modeled as a non-linear set of equations.
+Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
 However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialist PV optimization software.
@@
 The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textit{inverter}).
-The \textit{AC load} dictates the behavior of the AC electrical load from the house that will be fed by the system.
+The \textit{AC load} dictates the behaviour of the AC electrical load from the house that will be fed by the system.
 
@@
 PVsyst used the same configuration as HOMER Pro.
-We perform the experiments with a predefined time out of $660$ minutes.
+We perform the experiments with a predefined \textit{time out} of $660$ minutes.
 
@@
 We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a 24 h minimum autonomy).
-Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there exists no deployed equivalent system in the field, and the synthesis technique did not present a solution due to time-out and internal failures in the underlying verification engine.
+Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there exists no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine.
 %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
revised Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness.
-\keywords{Formal Synthesis \and Automated Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
+\keywords{Formal Synthesis \and Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
 \end{abstract}
@@
 \noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current prices.
-
-Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
+Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using software model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
 The analytical method of optimization was adopted, with LCC economic analysis and power reliability based on critical period criteria (worst month's method).
-
+%
  \begin{algorithm}[h]
@@
 it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers, and inverters. Moreover, we define design (house) requirements and design assumptions. 
-
-The \textit{for}-loop started at line $4$ controls the lowest cost of the PV solution.
+%
+The \textit{for}-loop started in line $4$ controls the lowest cost of the PV solution.
 In particular, it starts with cost $MinCost$ and stops when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $18$.
 If that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value at line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
+The $MaxCost$ value in line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
 
@@
 This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.
-A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine in order to allow the choice of every item of PV sizing.
+A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine to allow the choice of every item of PV sizing.
 Datasheet from each item was necessary to collect technical information.
@@
 Line $15$ does the inverter check and ensures the power demand and the surge power of the inverter.
-Therefore, our synthesis algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$). This cost is the equivalent to~\ref{eq:LCC}.
+Therefore, our synthesis algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$).
+This cost is the equivalent to Eq.~\eqref{eq:LCC}.
 
@@
 Note that PVsyst has a pre-sizing feature, indicated in the table, that presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it.
-This feature was used as reference mainly with HOMER Pro, where there is not equipment brands or models (only power and capacities specification).
+This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification).
 PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.
@@
 \hline
-CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)} & \makecell{NA\\There is not real PV system\\available for comparison} & \makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.6 $\times$\\Batteries oversized in 1.74 $\times$}\\
+CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.6 $\times$\\Batteries oversized in 1.74 $\times$}\\
 \hline
-CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} & \makecell{NA\\There is not real PV system\\available for comparison} & \makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
+CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
 \hline
@@
 \hline
-CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)} & \makecell{NA\\There is not real PV system\\available for comparison} & \makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.9 $\times$\\Batteries oversized in 1.99 $\times$}\\
+CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.9 $\times$\\Batteries oversized in 1.99 $\times$}\\
 \hline
@@
 Lastly, the use of data from real deployed systems in Amazonas State (Brazil) and the validation through PVsyst was essential to validate the comparison.
+For future work, we will investigate the application of probabilistic programming within our research so that we can analyze the trade-off between performance and precision.
 

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 (h) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity).
-During run-time, HOMER decides the size in kW of each based on feasibility and lower cost.
+During run-time, HOMER decides the size in kW of each one based on feasibility and lower cost.
 
-In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank.
+In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$ \textcolor{red}{add citation?}, with plenty of commercial equipment in its data bank.
 We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements.
-PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation and data analysis of solar PV systems.
+PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation, and data analysis of solar PV systems.
 PVsyst contains design, sizing, 3D shading scene, simulation, grid, and off-grid features.
-It uses comprehensive irradiation data from Meteonorm,\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}.
-However, it does not perform optimization; therefore, PVsyst needs the system sized in order to validate it.
+It uses comprehensive irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}.
+However, it does not perform optimization; therefore, PVsyst needs the system sized to validate it.
 Furthermore, PVsyst does not have commercial inverter equipment and, as a result, does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds.
-PVsyst is a paid software with $30$-day test possibility and runs only in MS-Windows operational system.
+PVsyst is a commerical software with $30$-day test possibility and runs only in MS-Windows OS.
 
@@
 
-Our evaluation aims to answer three experimental goals: [EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?; [EG2] \textbf{(performance)} How do the symbolic verifiers compare to each other for synthesizing PV systems?; and [EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
+Our evaluation aims to answer three experimental goals: [EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?; [EG2] \textbf{(performance)} How do the software verifiers compare to each other for synthesizing PV systems?; and [EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
 
@@
 For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10.
-The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favourable to HOMER Pro.
+The ideal scenario would be to use the same hardware configuration for the experiments.
+However, we faced restrictions concerning the license for the HOMER Pro tool; besides, we did not have the autonomy to change the Linux VM machine installed in the servers of our university due to the internal policy.
+This has an impact on performance, which is less favourable to HOMER Pro.
 PVsyst used the same configuration as HOMER Pro.
 We perform the experiments with a predefined \textit{time out} of $660$ minutes.
+
+%The hardware platform was not the same because of the availability of the machines;
 
@@
 The violation (SAT result) indicated all over the Table~\ref{tab1} 
-is the $assert$ of the line $18$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
+is the $assert$ of the line $18$ in Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
 Here, CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.
@@
 The variables NTP, NPS, NPP, NBS, NBP, and NBTotal, also presented in the counterexample, shows the number of panels and batteries and how they are connected.
-Case studies $2$, $3$, $6$, and $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $660$ minutes.  
+Case studies $2$, $3$, $6$, and $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $11$ hours.  
 %
@@
 
-Here we used ESBMC in incremental BMC configuration with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours.
+Here we used ESBMC in incremental mode with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours.
 ESBMC, with this configuration, was unable to obtain an optimal solution in cases $2$ and $7$.
 Case $2$ produced a \textit{time out}.
-Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was unable to provide a feasible solution.
+Moreover, case $7$ resulted in a UNSAT result, i.e., ESBMC was unable to provide a feasible solution.
 However, this is not a bug, and it means that the available list of equipment can not produce a feasible solution that satisfies electrical compatibility or design requirements.
@@
 
-Some HOMER Pro drawbacks were also noted: (1) System equipment does not include an explicit charge controller.
+Some HOMER Pro drawbacks were also noted.
+(1) System equipment does not include an explicit charge controller.
 HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison Between Formal Synthesis and HOMER Pro, using PVsyst}
+\subsection{Comparison Between Formal Synthesis and HOMER Pro}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The difference varied from $19$\% to $65$\%.
-On the other hand, concerning the battery bank, the results were smaller in terms of capacity to the HOMER Pro.
+On the other hand, concerning the battery bank, the results were smaller in terms of capacity for HOMER Pro.
 The difference was between $34$\% to $68$\%.
@@
 Those discrepancies are not easy to address without some real systems validation.
-However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in ~\ref{tab2}.
-Note that PVsyst has a pre-sizing feature, indicated in the table, that presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it.
+However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}.
+Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it.
 This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification).
@@
 
-Overall, those comparisons among our approach, the optimization software, and the deployed systems, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.
+Overall, those comparisons among our approach, the optimization software, and the deployed systems, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EG1} and {EG3}.
 
 HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed.
-The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf.
+The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf.
 Moreover, our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro or PVsyst.
@@
 Nevertheless, we have also identified four threats to the validity of our results that constitute future work.
-(1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate.
-(2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis.
-(3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
-(4) the underlying symbolic verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory.
+First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate.
+Second, improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis.
+Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
+Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory.
 We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
@@
 These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by off-the-shelf optimization tools and the items of equipment for solar systems available on the market to achieve accuracy.
-It is worth mentioning that our synthesis technique was developed and used open-source tools and environment, in contrast to the optimization and simulation tools used in this work.
+
+It is worth mentioning that our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work.
+We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers.
 Lastly, the use of data from real deployed systems in Amazonas State (Brazil) and the validation through PVsyst was essential to validate the comparison.

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

@@
 
-In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$ \textcolor{red}{add citation?}, with plenty of commercial equipment in its data bank.
+In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$~\cite{PVsyst}, with plenty of commercial equipment in its data bank.
 We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements.

### 2020-04-27 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
IEEE paper update

@@
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.
+All this data is available online\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.
 
@@
 Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
+The Algorithm~\ref{alg:opt-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verify ($C \wedge \neg P$), as shown online\footnote{\url{https://drive.google.com/file/d/1Q_hlgUt6AWrNeOtxhFlIpW4P4OPrPyIA/view?usp=sharing}}.
 
@@
 %
-Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc file.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
+Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
 
@@
 Furthermore, PVsyst does not have commercial inverter equipment and, as a result, does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds.
-PVsyst is a commerical software with $30$-day test possibility and runs only in MS-Windows OS.
+PVsyst is a commerical software with $30$-day test possibility and runs only in MS-Windows.
 
@@
 Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year.
-
 Some HOMER Pro drawbacks were also noted.
@@
 
-The authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the State of Amazonas, Brazil, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, a total of $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+The authors have real PV systems deployed since June $2018$ in a riverside community in the State of Amazonas, Brazil, GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If we compare the results of the formal synthesis with CPAchecker and ESBMC against those of HOMER Pro, we observed some distinct results in terms of the technical solution and cost (cf.
+If we compare the results of the formal synthesis against those of HOMER Pro, we observed some distinct results in terms of the technical solution and cost (cf.
 Table~\ref{tab1}).
@@
 Each simulation with PVsyst took $4$ seconds.
-We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a 24 h minimum autonomy).
+We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum).
 Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there exists no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine.
@@
 
-HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed.
+HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not a commercial value.
 The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf.
@@
 This feature is a definite advantage of the formal synthesis method.
-
 HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis.
@@
 %---------------------------------------------------------------------------
-
 We have reported a favorable assessment of the proposed method.
@@
 We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
-
 %------------------------------------
@@
 %------------------------------------
-
 Our novelty relies on a practical approach to pursue the optimal solution of PV systems using contemporary formal methods.
 The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising.
-Our synthesis tool can present a solution, which is far more detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool.
+Our synthesis tool can present a solution, which is far more detailed and closer to the commercial reality than the solution presented by the commercial tool.
 In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach.
-These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by off-the-shelf optimization tools and the items of equipment for solar systems available on the market to achieve accuracy.
-
+These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.
 It is worth mentioning that our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work.
 We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers.
-Lastly, the use of data from real deployed systems in Amazonas State (Brazil) and the validation through PVsyst was essential to validate the comparison.
-For future work, we will investigate the application of probabilistic programming within our research so that we can analyze the trade-off between performance and precision.
+Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison.
+For future work, we will investigate the application of probabilistic programming within our research for the trade-off between performance and precision.
 

### 2020-04-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

@@
 \thanks{The work of A. Trindade was supported in part by Newton Fund under Grant $261881580$, and in part by FAPEAM- Amazonas Foundation for Research under Grant PROTI-Pesquisa $2018$.}
-\thanks{Manuscript received September XY, 2019; revised XXXXX 11, 2019.}}
+\thanks{Manuscript received May XY, 2020; revised XXXXX 11, 2020.}}
 
@@
 All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.
+\url{https://drive.google.com/file/d/1XOQMC0zdybvTLyBLo-TlChLdwDFUlUCT/view?usp=sharing}
 
@@
 These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil.
-This project finished in March 2019, where we visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers.\footnote{http://star-energy.coventry.ac.uk/} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.
+This project finished in March 2019, where we visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers.\footnote{\url{http://star-energy.coventry.ac.uk/}} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.
 

### 2020-04-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

@@
 \usepackage{xcolor}
+\usepackage{wrapfig}
+\usepackage{mathtools}
+\usepackage{tabularx}
+\usepackage{etoolbox}
 
+%\usepackage{hyperref}
 % *** Do not adjust lengths that control margins, column widths, etc. ***
@@
 Experimental results using seven case studies and commercial equipment data show that our synthesis method can produce within an acceptable run-time the optimal system sizing.
-We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which can provide a more detailed and accurate solution than that simulation tool.
+We also compare our approach with a commercial tool specialized in photovoltaic systems optimization.
+Both results are validated with commercial design software; furthermore, some real deployed systems comparison are used to show our approach effectiveness.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Automated verification, model checking, program synthesis, electrical systems, solar photovoltaic systems.
+Formal Synthesis, software verification, model checking, solar photovoltaic systems.
 \end{IEEEkeywords}
@@
 As a result,
-In summary, this paper makes the following original contributions: (i) It is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems; (ii) We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop to reach the optimal cost solution of the system; and (iii)  Experimental results with seven case studies show that formal synthesis approach qualitatively outperforms an existing state-of-the-art simulation tool.
-Our solution is far detailed and closer to the commercial reality (real PV systems) than the solution presented by simulation.
-
+In summary, this paper makes the following original contributions: (i) It is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems; (ii) We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop to reach the optimal cost solution of the system; and (iii)  Experimental results with seven case studies show that formal synthesis approach qualitatively outperforms an existing state-of-the-art optimization tool.
+Our solution is far detailed and closer to the commercial reality (real PV systems).
+The results are validated with an accurate commercial design software called PVsyst.
 %\textit{Contribution}.
@@
 Considering other studies carried out in the last two decades, we considerably advance the state-of-the-art in applied energy to optimally design PV systems.
-
 %\textit{Outline}.
@@
 \begin{figure}[h]
-\includegraphics[width=0.4\textwidth]{blockdiagramPVS2_rev}
+\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
 \centering
@@
 
-We adopted a critical period solar energy method~\cite{Pinho}; in particular, maximum power point tracking (MPPT) charge controller, which is the most common nowadays.
-First, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+We adopted a critical period (worst month) solar energy method~\cite{Pinho}; in particular, maximum power point tracking (MPPT) charge controller, which is the most common nowadays.
+Firstly, we need to correct the daily energy consumption estimated for the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered as follows
 
@@
 \label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \eta_{c} \eta_{i} }.
+E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \times \eta_{c} \times \eta_{i} }.
 \end{equation}
 
-We also need to estimate the energy that each panel produces, called $E_{p}$, in Wh, defined as
+We must estimate the total power that will be demanded from the PV panels, as defined by Eq. ~\eqref{eq:Pminpanel}.
 
 \begin{equation}
-\label{eq:Ep}
-E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
+\label{eq:Pminpanel}
+P_{min,panels} = \dfrac{1.25 \times E_{corrected}}{Insolation},
 \end{equation}
 
-\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where we deploy the PV system; 
-the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
-We compute the total minimum number of needed solar panels ($N_{TPmin}$) as
+\noindent where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
+A factor of $20$\% for losses is considered, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
+
+On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
+On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current ($I_{c} \geq I_{total,PVpanels}$) and voltage ($V_{c} \geq V_{total,PVpanels}$).
+
+Concerning the batteries, the energy $E_{b}$ to be demanded by the PV system, in order to meet the load requirements, is defined by Eq.~\eqref{eq:Ebat}.
 
 \begin{equation}
-\label{eq:NTPmin}
-N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
+\label{eq:Ebat}
+E_{b} = \dfrac{Autonomy \times E_{corrected}}{DOD},
 \end{equation}
 
-Notably, we give the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) by
+\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days.
+$DOD$ is the depth of discharge or the fraction of discharge.
+The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
+However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours).
+Therefore, here in this study, the definition given here is for a maximum of $DOD$.
+When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
+
+In order to define the $DOD_{day}$, we use $DOD_{day} = \dfrac{E_{corrected} \times 100}{E_{b}}$.
+Moreover, the minimum current from the DC bus is defined by $I_{min,DCbus} = \dfrac{E_{b}}{V_{system}}$.
+Those equations are important to define the battery arrangement of the system (series and parallel connections).
+Where $V_{system}$ is the DC voltage of the bus.
+
+As for batteries, we must first define the total capacity of the battery bank, which can be described as
 
 \begin{equation}
-\label{eq:NPSmin}
-\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}},
+\label{eq:Cbank}
+C_{bank} = \dfrac{Autonomy E_{load}}{DOD \eta _{b} V_{system}},
 \end{equation}
 
+\noindent where $ E_{load} $ is the average energy consumed by the load corrected according to PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
+%
+Eq.~\ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted.
+
 \begin{equation}
-\label{eq:NPPmin}
-N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
+\label{eq:batcheck}
+\left( N_{BS} \times N_{BP} \right) \geq N_{B}total
 \end{equation}
 
-\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ 
-is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and 
-$V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering 
-the maximum and minimum operational temperature, respectively; 
-$P_{total}$ is the total power demanded from the PV system and 
-$P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
-Regarding batteries, we must first define the total capacity of the battery bank as
-%
-\begin{equation}
-\label{eq:Cbank}
-C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD},
-\end{equation}
-
-\noindent where the variable $autonomy$ is a design definition and typically has a value ranging from $6$ to $48$h; $ V_{system} $ 
-is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
-%
-Second, we compute the total (minimum) number of batteries as 
-%
-\begin{equation}
-\label{eq:Nbtotal}
-N_{B}total = N_{BS}min \times N_{BP}min
-\end{equation}
-
-\begin{equation}
-\label{eq:Nbtotal2}
-N_{B}total = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
-\end{equation}
-
-Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage:
+The charge controller must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem}.
 
@@
 
-The short circuit reference information from the manufacturer's solar panel must be corrected 
-to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as
+The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because field temperature is higher than nominal or laboratory temperature, and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb}.
 
@@
 
-The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin} as
+The controller must meet the maximum current from the PV array ($I_{c,min} = I_{sc,amb} \times N_{PP}$ and $I_{c} \geq I_{c,min}$).
 
-\begin{equation}
-\label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP},
-\end{equation}
-
-\begin{equation}
-\label{eq:icicmin}
-I_{c} \geq I_{c,min}.
-\end{equation}
-
-The inverter sizing check is performed using three equations. Eq.~\eqref{eq:vindc} ensures that 
-the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the 
-output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that 
-the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), 
-where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; 
-$MAX_{AC,ref}$ is the peak power that the inverter can support.
-
-\begin{equation}
-\label{eq:vindc} 
-V_{in}DC = V_{system}.
-\end{equation}
-
-\begin{equation}
-\label{eq:voutac} 
-V_{out}AC = V_{AC}.
-\end{equation}
+The inverter sizing check is performed through three equations: $V_{in}DC = V_{system}$ ensures that the input voltage of the controller meets the system voltage; $V_{out}AC = V_{AC}$ ensures that the output voltage of the controller meets the AC voltage of the load, i.e., the outlet voltage.
+Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
 
@@
 \end{equation}
+
+Some inverter models allow parallel operation of more than one unit, besides the integration to create bi- and three-phase circuits.
+It is advisable to use pure sine wave inverters for electronic loads sensitive to harmonic distortion waves.
+
+Besides that, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers.
+Furthermore, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side (and a controller overcharge).
+
+All the equations model the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones (it is not possible to deploy a fraction of panels or batteries).
+The verification and simulation tools need to handle non-linear real arithmetic to produce the  result.
 
@@
 
-\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs
-in present worth.
+\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs in present worth.
 
@@
 
-To perform the automated formal synthesis, we use a state-of-the-art model checker, awarded with the golden medal at the annual competition in software verification: \textbf{CPAchecker}~\cite{LMU2019}.
+////////////////////////ESBMC////////////To perform the automated formal synthesis, we use a state-of-the-art model checker, awarded with the golden medal at the annual competition in software verification: \textbf{CPAchecker}~\cite{LMU2019}.
 Automatic program verification requires a choice between precision and efficiency.
@@
 BMC algorithms traverses a finite state machine for a fixed number of steps, $k$, and checks whether violation occurs with this bound.
-
 %The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}.
@@
 The use of SMT by CPAchecker, instead of Boolean Satisfiability SAT from the original BMC, comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.
-
 %
@@
 	\centering
-	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
+%	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
+	\includegraphics[width=0.5\textwidth]{fig2_rev2.jpg}
 	\caption{CEGIS adapted to PV system sizing.}
@@
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
-We adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
-%
+We adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the worst month criteria.
+
  \begin{algorithm}
@@
  \begin{algorithmic}[1]
+ \begin{scriptsize}
  \renewcommand{\algorithmicrequire}{\textbf{Input:}}
  \renewcommand{\algorithmicensure}{\textbf{Output:}}
+ \REQUIRE weather data (temperature, solar irradiance); data from panels, controllers, batteries, and inverters; design requirements (load curve, peak demand, load surge power, energy consumption, battery autonomy, AC voltage); design assumptions (SOC, DOD, criteria and objectives for technical and cost analysis)
+ \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
  \STATE Initialize variables \\
-  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
-%  \STATE Declare list of controllers data and cost \\
-%  \STATE Declare list of batteries data and cost \\
-%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$ \\
-  \STATE Declare power demand, power peak, energy consumption \\
-  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
-  \FOR {$HintCost=0$ to $MaxCost$}
- 	\STATE Non-deterministic variable selects PV Panel from list \\
- 	\STATE Non-deterministic variable selects Controller from list \\
- 	\STATE Non-deterministic variable selects Battery from list \\
- 	\STATE Non-deterministic variable selects Inverter from list \\ 	
- 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
-	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
- 	\STATE Calculate $C_{bank}$ \\
-	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
-	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
- 	\STATE Calculate $I_{sc,amb}$ \\
- 	\STATE Calculate $I_{c,min}$ \\
- 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
-	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
-%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
-	\STATE Variables hold feasible PV system candidate and cost  \\
+ \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
+ \FOR {$HintCost=MinCost$ to $MaxCost$} 
+ 	\STATE Declare non-deterministic variables to select PV Panel, Controller, Battery, and Inverter from list \\
+ 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
+	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
+	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{m,ref}))$ \\
+	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
+	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
+ 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
+	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
+	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
+ 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
+	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
+	\STATE non-deterministic variables hold feasible equipment and cost \\
 	\STATE $F_{obj} \leftarrow N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
@@
  \RETURN $(\,)$ 
+ \end{scriptsize}
  \end{algorithmic} 
@@
  \end{algorithm}
+
+Our synthesis algorithm will synthesize constant values; it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers, and inverters.
+Moreover, we define design (house) requirements and design assumptions.
 %
-Our synthesis algorithm will synthesize constant values.
-It starts with the input of manufacturers' data and prices of PV panels, batteries, charge controllers, and inverters (line $2$).
-After that, we define user requirements, i.e., house requirements and design definitions, from lines $4$ and $5$.
+The \textit{for}-loop started in line $4$ controls the lowest cost of the PV solution.
+In particular, it starts with cost $MinCost$ and stops when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $18$.
+If that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+The $MaxCost$ value in line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
 
-The \textit{for}-loop on line 6 ensures the search for the lowest cost to the PV solution.
-The $MaxCost$ value is a very high value put as a limit to the loop, which never will be reached because the optimal solution will be found first.
-The formal guarantee of this statement is based on the fact that the cost is verified just after a feasible technical candidate if found on {\sc Synthesize} phase.
-In particular, the loop starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $22$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (line $5$).
+This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.
+A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine to allow the choice of every item of PV sizing.
+Datasheet from each item was necessary to collect technical information.
+Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
+All this data is available online\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.
 
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (lines $7$ to $10$).
-That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.
+Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:invcheck} to calculate the sizing variables (lines $9$ to $15$).
+The directive \textit{assume} (lines $8$, $13$, $14$, and $15$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines.
+Line $5$ is specific to PV panels.
+Line $13$ is for the battery bank.
+Line $14$ is the charge controller voltage check.
+Line $15$ does the inverter check and ensures the power demand and the surge power of the inverter.
+Therefore, our synthesis algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$).
+This cost is the equivalent to Eq.~\eqref{eq:LCC}.
 
-Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep},Eq.~\eqref{eq:NTPmin}, 
-Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, 
-Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $11$ to $17$). The directive \textit{assume} (lines $15$, $18$ and $19$) 
-ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines $15$, $18$ and $19$.
-Therefore, our synthesis algorithm reaches line $20$ with one feasible solution, and we calculate the cost of that solution in $F_{obj}$ (line $21$).
-
-If our algorithm does not find a feasible solution among the item of equipment that we provide to our {\sc Synthesize} phase, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution, which indicates that it was not possible to combine the items of each equipment in order to create a feasible solution.
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements.
-Related to our {\sc Verify} phase, the challenge is to find the lowest acquisition cost from a list of equipment and components that are provided from the {\sc Synthesize} phase.
-Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
+If our algorithm does not find a feasible solution among the item of equipment that was provided for our {\sc Synthesize} phase, then the result is unsatisfiable (\textit{UNSAT}).
+In particular, the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution.
+%
+The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements.
+The challenge for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase.
+%
+Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
+The Algorithm~\ref{alg:verification-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verify ($C \wedge \neg P$), as shown online\footnote{\url{https://drive.google.com/file/d/1uOWXdQqkKMNxHLj66S-QxTriVioLxpcv/view?usp=sharing}}.
 
@@
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.
-\url{https://drive.google.com/file/d/1XOQMC0zdybvTLyBLo-TlChLdwDFUlUCT/view?usp=sharing}
+All this data is available online\footnote{\url{https://drive.google.com/file/d/1XOQMC0zdybvTLyBLo-TlChLdwDFUlUCT/view?usp=sharing}}.
 
@@
 
-This section describes our case studies, experimental setup,  objectives, and results to evaluate our proposed synthesis approach.
+This section describes our case studies, experimental set-up,  objectives, and results to evaluate our proposed synthesis approach.
 We also compare our approach with a specialized simulation tool (HOMER Pro).
@@
 We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (\textit{Specification}).
-These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil.
-This project finished in March 2019, where we visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers.\footnote{\url{http://star-energy.coventry.ac.uk/}} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.
+These case studies were defined based on real houses visited by the team of a Newton Fund project in 14 riverside communities\footnote{\url{http://star-energy.coventry.ac.uk/}} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found into each house.
 
-\begin{table}[!t]
-\caption{Case studies and results: optimization of PV systems.}\label{tab1}
+\begin{table}
+\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
 \begin{scriptsize}
-\begin{tabular}{|c|c|c|}
+\begin{tabular}{c|c|c}
 \hline
 \hline
-Tools & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
+Tools & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& HOMER Pro 3.13.1\\
 \hline
 \hline
-Specification & Result & Result \\
+Specification & Result & Result\\
 \hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
+\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
 \hline
-\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
+\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
 \hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
+\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & Not possible \\
 \hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} &  \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
+\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
 \hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
+\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
 \hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
+\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
 \hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
+\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & UNSAT (0.48 min) & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
 \hline
@@
 \end{tabular}
-\\Caption: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
+\\Legend: OM = out of memory; TO = time out; IF = internal failure; E = energy;    NTP = total number of panels, NBtotal = total number of batteries, NPS = number of panels in series; NPP = number of panels in parallel, NBS = number of batteries in series; NBP = number of batteries in parallel; LCC = Life Cycle Cost.
 \end{scriptsize}
@@
 %---------------------------------------------------------------------------
-\subsection{Setup} 
+\subsection{Set-up} 
 %---------------------------------------------------------------------------
 
-The start-of-art verification tool CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} was used as our verification engine to compare our approach effectiveness and efficiency.
-The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purpose.
+The state-of-art verification tool ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer} was used as our reference verification engine.
+The optimization tool HOMER Pro version $3.13.1$ was used for comparative purpose.
+The optimal sizing produced by ESBMC and HOMER Pro are validated with tool PVsyst v$6.86$~\cite{PVsyst}.
+PVsyst is a MS-Windows software package developed used for the study, sizing, simulation, and data analysis of solar PV systems, with a comprehensive list of commercial equipment.
+PVsyst does not performs optimization and does not have commercial inverter equipment.
 
-All experiments regarding the verification tools were conducted 
-on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
-$2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. 
-For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores), 
-with $1.7$ GHz and $4$ GB of RAM, running Windows 10. 
+All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits.
+For HOMER Pro and PVsyst, we have used an Intel Core i5-$4210$ ($4$-cores), with $1.7$ GHz and $4$ GB of RAM, running Windows 10.
 Our experiments were performed with a predefined time out of $660$ minutes.
@@
 We have reported a favourable assessment of our formal synthesis method to obtain the optimal size of the PV system.
-Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and 
-constitute future work: ($1$) improvement of the power reliability 
-analysis: to include loss of load probability or loss of power 
-supply probability, which can make the analysis more precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, 
-based on historical data; 
-($2$) the cost analysis is well-tailored to the Amazon region of Brazil; 
-however, a broad analysis from other isolated areas must be 
-performed to make the optimization general in terms 
-of applicability in other isolated areas of the world, such as India and China; ($3$) to deploy at the field some PV systems 
-sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
+Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and constitute future work: ($1$) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, based on historical data; ($2$) the cost analysis is well-tailored to the Amazon region of Brazil; however, a broad analysis from other isolated areas must be performed to make the optimization general in terms of applicability in other isolated areas of the world, such as India and China; ($3$) to deploy at the field some PV systems sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
 
@@
 The focus was on the synthesis method to obtain the optimal solution based on formal methods, which can cover better the design-space as opposed to simulation tools.
-We have considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; one state-of-art verification engine was considered (CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) to compare the results.
-
+We have considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; one state-of-art verification engine was considered (ESBMC), in addition to a specialized off-the-shelf optimization tool (HOMER Pro) to compare the results.
+The use of data from real deployed systems in Brazil and the validation through PVsyst was essential to perform the comparison.
 The paper produced a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
@@
 Moreover, we extended the CEGIS synthesis method and implemented this extension within our proposed formal synthesis tool, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
-
 For future work, we plan to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil) and to validate some cases with the deployment of real PV systems in isolated communities.
@@
 %
-
 % use section* for acknowledgment
-\section*{Acknowledgment}
-
-The authors would like to thank to University of Sheffield's QR GCRF for HOMER Pro license.
-
+%\section*{Acknowledgment}
+%
+%The authors would like to thank to University of Sheffield's QR GCRF for HOMER Pro license.
+%
 % Can use something like this to put references on a page
 % by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
+%\ifCLASSOPTIONcaptionsoff
+%  \newpage
+%\fi
+%
 % trigger a \newpage just before the given reference

### 2020-04-29 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

@@
 We also compare our approach with a commercial tool specialized in photovoltaic systems optimization.
-Both results are validated with commercial design software; furthermore, some real deployed systems comparison are used to show our approach effectiveness.
+Both results are validated with commercial design software in order to show our approach effectiveness.
 \end{abstract}
@@
 
-////////////////////////ESBMC////////////To perform the automated formal synthesis, we use a state-of-the-art model checker, awarded with the golden medal at the annual competition in software verification: \textbf{CPAchecker}~\cite{LMU2019}.
-Automatic program verification requires a choice between precision and efficiency.
-The more precise a method, the fewer false positives it produces, but also the more expensive it is, and thus applicable to fewer programs.
-Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking.
-To experiment with the trade-off and to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting.
-The CPA formalism provides an interface for the definition of program analysis.
-Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analysis expressed in the CPA framework.
-In terms of the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges.
-The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}.
-Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.
+To perform the automated formal synthesis, we use a state-of-the-art model checker.
+ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
 
@@
 \end{tabular}
-\\Legend: OM = out of memory; TO = time out; IF = internal failure; E = energy;    NTP = total number of panels, NBtotal = total number of batteries, NPS = number of panels in series; NPP = number of panels in parallel, NBS = number of batteries in series; NBP = number of batteries in parallel; LCC = Life Cycle Cost.
+\\Legend: TO= time out; E= energy; NTP= total number of panels, NBtotal= total number of batteries, NPS= number of panels in series; NPP= number of panels in parallel, NBS= number of batteries in series; NBP= number of batteries in parallel; LCC= Life Cycle Cost.
 \end{scriptsize}
@@
 %---------------------------------------------------------------------------
-\subsection{Set-up} 
+\subsection{Set-up and Objectives} 
 %---------------------------------------------------------------------------
@@
 The optimal sizing produced by ESBMC and HOMER Pro are validated with tool PVsyst v$6.86$~\cite{PVsyst}.
-PVsyst is a MS-Windows software package developed used for the study, sizing, simulation, and data analysis of solar PV systems, with a comprehensive list of commercial equipment.
-PVsyst does not performs optimization and does not have commercial inverter equipment.
+PVsyst is a MS-Windows software used for the study, sizing, simulation, and data analysis of solar PV systems, with a comprehensive list of commercial equipment.
+PVsyst does not perform optimization nor does it have commercial inverter equipment.
 
@@
 
-%---------------------------------------------------------------------------
-\subsection{Objectives} 
-%---------------------------------------------------------------------------
-
-Our evaluation aims to answer two experimental questions:
-
-\begin{enumerate}
-
-\item[EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
-
-\item[EQ2] \textbf{(performance)} how does our formal synthesis tool compare to a specialized simulation tool?
-
-\end{enumerate}
+Our evaluation aims to answer two experimental questions: [EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
+[EQ2] \textbf{(performance)} how does our formal synthesis tool compare to a specialized optimization tool?
 
@@
 %---------------------------------------------------------------------------
+ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours.
+ESBMC, with this configuration, was unable to obtain an optimal solution in cases $2$ and $7$.
+Case $2$ produced a \textit{time out}.
+Moreover, case $7$ resulted in a UNSAT result, i.e., ESBMC was unable to provide a feasible solution.
+However, this is not a bug, and it means that the available list of equipment can not produce a feasible solution that satisfies electrical compatibility or design requirements.
+This UNSAT situation was reached in less than one minute.
+%These experimental results answer the \textit{EQ2}.
 
-CPAchecker was able to synthesize the optimal sizing in six out of seven case studies: the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes.
-Only case study $7$ led to a \textit{time out} result, i.e., it was not solved within $240$ minutes.
-However, if we remove this time out limitation from CPAchecker, the verifier can solve the optimization in $44.97$ hours.
-The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}.
-As an interesting feature of the automated synthesis, we present every optimal sizing as a detailed list of equipment with brand (in Table~\ref{tab1} it was removed to avoid some advertising) and model taken from the list provided to the algorithm.
-Moreover, we present the number of series and parallel solar panels and batteries.
+HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}).
+Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year.
+Some HOMER Pro drawbacks were also noted.
+(1) System equipment does not include an explicit charge controller.
+HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement.
+However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing.
+(2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user.
+For example, it was started with a $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types.
+(3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
 
-Related to HOMER Pro, it was able to evaluate six case studies, and within a time shorter than $30$ seconds, which was much faster than our automated synthesis tool (cf.~\textit{EQ2}).
-It produces very  We were unable to simulate case study $3$ since HOMER Pro does not have the feature of adjusting the battery autonomy (the tool always meets the user requirement, i.e., the load curve during the $365$ days of the year).
-Other HOMER Pro drawbacks, when compared to our automated synthesis method: (a) There exists no explicit charge controller as a system equipment.
-HOMER includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics as maximum current and voltage, which are common during PV sizing; (b) HOMER demands to include some battery specification to initiate the optimization; however, it does not change the electrical specifications during the simulation; the presented results are multiples of the original battery type suggested by the user.
-As example, it was started with a $83.4$ Ah lead-acid battery, and during the simulation, HOMER Pro did not try to use other capacities or types; (c) HOMER does not present the optimal solution in terms of connections of arrays of PV panels, just the total in terms of power, i.e., it does present neither models and the power of each PV panel nor the total of panels in series or parallel; (d) Battery autonomy is not a parameter that the user can set when using HOMER.
+%The authors have real PV systems deployed since June $2018$ in a riverside community in the State of Amazonas, Brazil, GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+%
+If we compare the results of the formal synthesis against those of HOMER Pro, we observed some distinct results in terms of the technical solution and cost (cf.
+Table~\ref{tab1}).
+Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
+%
+Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, producing a higher estimation from the automated synthesis technique.
+However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.
 
-Comparing the results between the formal synthesis with CPAchecker and HOMER Pro (cf.~\textit{EQ2}), 
-we observed that most results are quite similar, in terms of technical solution and cost (cf. Table~\ref{tab1}). 
-Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
-Even adopting the same price per kW to the PV panels, 
-inverters, and batteries, HOMER Pro does not use costs 
-related to charge controllers, which we introduced into the 
-CPAchecker modelling. The premise used in CPAchecker to adopt 
-a fixed annual cost for operation and maintenance can produce 
-some impact as well at this discrepancy; however, it is not significant
-since this annual cost is too small when compared to the resulting LCC value.
-However, there exists a considerable divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our automated synthesis tool, probably because we underestimated the operation and maintenance costs assumed by our automated synthesis tool to that specific load.
+On the one hand, concerning the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the ones produced by the simulation tool.
+The difference varied from $19$\% to $65$\%.
+On the other hand, concerning the battery bank, the results were smaller in terms of capacity for HOMER Pro.
+The difference was between $34$\% to $68$\%.
+The mathematical models are different and particular parameters can be tuned for each technique, and that can justify the difference, which was presented in all the case studies.
 
-In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach, and determining which one is the correct depends on a comparison with field-deployed solar systems.
-The mathematical models are different in our model and the simulation tool, and particular parameters can be tuned.
-This may explain the difference presented in all case studies.
-As comparative, consider case study $1$: the optimal solution provided by HOMER Pro demands $7$ $\times$ more PV panels than the solution presented by our synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e., the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides $500.4$ Ah of capacity ($6 \times 83.4$), while our synthesis tool presented an optimal solution with $420$ Ah of total capacity ($4 \times 105$).
+Those discrepancies are not easy to address without some real systems validation.
+However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}.
+Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it.
+This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification).
+PVsyst was used with the formal synthesis sizing solution, where brands and models were simulated in PVsyst according to the sized system.
 
-To compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil (coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W), with similar power demands presented by case studies $1$, $4$, $5$, and $6$,
-always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
-These solutions are closer to the result presented by our formal synthesis approach than HOMER Pro, thereby showing that our solution is sound, which answers \textit{EQ1}.
+\begin{table}
+\caption{Optimal sizing validation with PVsyst.}
+\label{tab2}
+\begin{scriptsize}
+\begin{tabular}{c|c|c|c}
+\hline
+\hline
+CS & \makecell{PVsyst\\(pre-sizing)}&\makecell{Formal synthesis\\sizing\\validation}& \makecell{HOMER Pro\\sizing\\validation}\\
+\hline
+\hline
+CS 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.16$\times$\\Batteries oversized: 1.39$\times$}\\
+\hline
+CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)}&\makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.6$\times$\\Batteries oversized: 1.74$\times$}\\
+\hline
+CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} &\makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
+\hline
+CS 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)}&\makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized: 2.24$\times$\\Batteries oversized: 1.41$\times$}\\
+\hline
+CS 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 1.93$\times$\\Batteries oversized:  1.56$\times$}\\
+\hline
+CS 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.42$\times$\\Batteries oversized: 1.38$\times$}\\
+\hline
+CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)}&\makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.9$\times$\\Batteries oversized: 1.99$\times$}\\
+\hline
+\hline
+\end{tabular}
+\\Legend: CS = case study; NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater).
+\end{scriptsize}
+\end{table}
 
-Related to the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter.
-Our synthesis tool, however,
-presents inverters that are commercial and can be found off-the-shelf; therefore, our approach is a PRO to the formal synthesis method.
+Each simulation with PVsyst took $4$ seconds.
+We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum).
+Case studies $2$ and $7$ had only HOMER Pro sizing validation, because the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine.
+%(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).
 
-Concerning the charge controllers, as we reported in the previous section, HOMER Pro does not include it as an explicit equipment in its mathematical model and does not includes the cost for the charge controller; only our synthesis tool presents a commercial controller and includes it during the cost analysis.
-Therefore, the formal synthesis method presents more reliable results than HOMER Pro.
+Overall, those comparison between our approach and the optimization software, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EQ1} and {EQ2}.
 
-Our synthesis tool did not solve the case study $7$  within the time limit established during the experimental phase.
-Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters for comparison.
+HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not a commercial value.
+The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf.
+Moreover, our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro or PVsyst.
+This feature is a definite advantage of the formal synthesis method.
+HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis.
+The formal synthesis method, therefore, presents more reliable results than HOMER Pro.
+
+In summary, our synthesis tool can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+In particular, the automated synthesis method can provide all the details of every component of a PV system solution, including the model of the component, nominal current, and voltage.
+In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising).
+Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results, mainly concerning PV panels.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 We have reported a favourable assessment of our formal synthesis method to obtain the optimal size of the PV system.
-Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and constitute future work: ($1$) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, based on historical data; ($2$) the cost analysis is well-tailored to the Amazon region of Brazil; however, a broad analysis from other isolated areas must be performed to make the optimization general in terms of applicability in other isolated areas of the world, such as India and China; ($3$) to deploy at the field some PV systems sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
+Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and constitute future work: ($1$) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, based on historical data; ($2$) the cost analysis is well-tailored to the Amazon region of Brazil; however, a broad analysis from other isolated areas must be performed to make the optimization general in terms of applicability in other isolated areas of the world, such as India and China; ($3$) to deploy some PV systems sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking techniques.
@@
 We have considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; one state-of-art verification engine was considered (ESBMC), in addition to a specialized off-the-shelf optimization tool (HOMER Pro) to compare the results.
-The use of data from real deployed systems in Brazil and the validation through PVsyst was essential to perform the comparison.
+The  validation through PVsyst was essential to perform the comparison.
 The paper produced a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
@@
 %\end{figure}
-
 % Note that the IEEE typically puts floats only at the top, even when this
 % results in a large percentage of a column being occupied by floats.
-
 % An example of a double column floating figure using two subfigures.
@@
 % e.g., \subfloat[].
-
 % An example of a floating table. Note that, for IEEE style tables, the
@@
 %\end{table}
-
 % Note that the IEEE does not put floats in the very first column
@@
 % \fnbelowfloat command of the stfloats package.
-
 % if have a single appendix:

### 2020-04-30 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

@@
 \markboth{IEEE Transactions on Sustainable Energy,~Vol.~XX, No.~YY, April~2020}%
-{Trindade and Cordeiro: An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems}
+{Trindade and Cordeiro: Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis}
 % The only time the second header will appear is for the odd numbered pages
@@
 Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}.
+The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
+Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}.
 Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for three-quarters of the additional connections needed to provide universal electricity~\cite{Hussein2012}; specifically, grid extension are the standard in urban areas~\cite{IEAweo2018}.

### 2020-04-30 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

@@
 \begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
+\hspace*{-1cm}\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{optimalsizingprocess3}
+\hspace*{-1cm}\includegraphics[width=0.55\textwidth]{optimalsizingprocess4}
 \centering
@@
 ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
-ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
+ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{\url{http://smtlib.cs.uiowa.edu/}} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
 This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
@@
 A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine to allow the choice of every item of PV sizing.
-Datasheet from each item was necessary to collect technical information.
+Data-sheet from each item was necessary to collect technical information\footnote{\url{http://tiny.cc/4ny4nz}}.
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-All this data is available online\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.
+%All this data is available online\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.
 
@@
 Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
-The Algorithm~\ref{alg:verification-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verify ($C \wedge \neg P$), as shown online\footnote{\url{https://drive.google.com/file/d/1uOWXdQqkKMNxHLj66S-QxTriVioLxpcv/view?usp=sharing}}.
+The Algorithm~\ref{alg:verification-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verify ($C \wedge \neg P$), as shown online\footnote{\url{http://tiny.cc/ity4nz}}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to our synthesis engine in order to allow the choice of every item of PV sizing.
+%
+%Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to our synthesis engine in order to allow the choice of every item of PV sizing.
 Data sheet from each item was necessary to collect technical information.
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-All this data is available online\footnote{\url{https://drive.google.com/file/d/1XOQMC0zdybvTLyBLo-TlChLdwDFUlUCT/view?usp=sharing}}.
+%All this data is available online\footnote{\url{https://drive.google.com/file/d/1XOQMC0zdybvTLyBLo-TlChLdwDFUlUCT/view?usp=sharing}}.
 
@@
 \begin{table}
-\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
+\caption{Case studies and results: optimization of PV systems.}\label{tab1}
 \begin{scriptsize}
@@
 The optimization tool HOMER Pro version $3.13.1$ was used for comparative purpose.
-The optimal sizing produced by ESBMC and HOMER Pro are validated with tool PVsyst v$6.86$~\cite{PVsyst}.
+The optimal sizing produced by ESBMC and HOMER Pro were validated with PVsyst v$6.86$~\cite{PVsyst}.
 PVsyst is a MS-Windows software used for the study, sizing, simulation, and data analysis of solar PV systems, with a comprehensive list of commercial equipment.
-PVsyst does not perform optimization nor does it have commercial inverter equipment.
+PVsyst does not perform optimization.
+% nor does it have commercial inverter equipment.
 
@@
 \hline
-CS & \makecell{PVsyst\\(pre-sizing)}&\makecell{Formal synthesis\\sizing\\validation}& \makecell{HOMER Pro\\sizing\\validation}\\
+\makecell{Case\\Study} & \makecell{PVsyst\\(pre-sizing)}&\makecell{Formal synthesis\\optimal sizing\\validation}& \makecell{HOMER Pro\\optimal sizing\\validation}\\
 \hline
 \hline
-CS 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.16$\times$\\Batteries oversized: 1.39$\times$}\\
+\# 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.16$\times$\\Batteries oversized: 1.39$\times$}\\
 \hline
-CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)}&\makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.6$\times$\\Batteries oversized: 1.74$\times$}\\
+\# 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)}&\makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.6$\times$\\Batteries oversized: 1.74$\times$}\\
 \hline
-CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} &\makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
+\# 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} &\makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
 \hline
-CS 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)}&\makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized: 2.24$\times$\\Batteries oversized: 1.41$\times$}\\
+\# 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)}&\makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized: 2.24$\times$\\Batteries oversized: 1.41$\times$}\\
 \hline
-CS 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 1.93$\times$\\Batteries oversized:  1.56$\times$}\\
+\# 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 1.93$\times$\\Batteries oversized:  1.56$\times$}\\
 \hline
-CS 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.42$\times$\\Batteries oversized: 1.38$\times$}\\
+\# 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.42$\times$\\Batteries oversized: 1.38$\times$}\\
 \hline
-CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)}&\makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.9$\times$\\Batteries oversized: 1.99$\times$}\\
+\# 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)}&\makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.9$\times$\\Batteries oversized: 1.99$\times$}\\
 \hline
@@
 \end{tabular}
-\\Legend: CS = case study; NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater).
+\\Legend: NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater).
 \end{scriptsize}

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
-\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
+\thanks{L. Cordeiro is with the Department of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
 \thanks{The work of A. Trindade was supported in part by Newton Fund under Grant $261881580$, and in part by FAPEAM- Amazonas Foundation for Research under Grant PROTI-Pesquisa $2018$.}
@@
 \begin{abstract}
-There exist various methods and tools to size solar photovoltaic systems; however, these tools rely on simulations, which do not cover all aspects of the design space during the search for optimal solution.
+There exist various methods and tools to size solar photovoltaic systems; however, these tools rely on simulations, which do not cover all aspects of the design space during the search for the optimal solution.
 In prior studies in optimal sizing, the focus was always on criteria or objectives.
-Here, we present a new sound and automated approach to obtain optimal sizing  using an unprecedented program synthesis.
-Our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases linking the technical and cost analysis: first we synthesize a feasible candidate based on power reliability, but that may not achieve the lowest cost; second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
+Here, we present a new sound and complete approach to obtaining optimal sizing using an unprecedented program synthesis technique.
+Our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases linking the technical and cost analysis.
+First, we synthesize a feasible candidate based on power reliability, but that may not achieve the lowest cost.
+Second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking.
 If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample provides the optimal solution.
@@
 We also compare our approach with a commercial tool specialized in photovoltaic systems optimization.
-Both results are validated with commercial design software in order to show our approach effectiveness.
+Both results are validated with commercial design software to show the effectiveness of our approach.
 \end{abstract}

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{IEEEkeywords}
-Formal Synthesis, software verification, model checking, solar photovoltaic systems.
+Formal synthesis, software verification, model checking, solar photovoltaic systems.
 \end{IEEEkeywords}
@@
 \IEEEPARstart{L}{ack} of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion thresholds for the first time in $2017$~\cite{IEAweo2018}.
 The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
 Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}.
-Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for three-quarters of the additional connections needed to provide universal electricity~\cite{Hussein2012}; specifically, grid extension are the standard in urban areas~\cite{IEAweo2018}.
+Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for three-quarters of the additional connections needed to provide universal electricity~\cite{Hussein2012}; grid extension are the standard in urban areas~\cite{IEAweo2018}.
 
@@
 %
-To simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}; and even general-purpose simulation tools, as  MATLAB~\cite{Benatiallah2017}.
+In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}; and general-purpose simulation tools, as MATLAB~\cite{Benatiallah2017}.
 However, these tools rely on simulation, with the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is infeasible~\cite{ClarkeHV18}.
-
+%
 Optimization of PV systems is not a recent topic; since the $90$'s different techniques using a wide variety of criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods were developed and evaluated~\cite{Applasamy2011}.
@@
 In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, a researcher suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}.
+In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
 Finally, in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
@@
 Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
+If the user gives a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
 In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
@@
 If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost.
-Note that in this study, our focus is not on new criteria or even optimization objectives.
-Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.
+Here our focus is not on new criteria or even optimization objectives.
+Our novelty relies on a practical approach to the pursuit of the optimal solution of PV systems using formal methods.
 
@@
 As a result,
-In summary, this paper makes the following original contributions: (i) It is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems; (ii) We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop to reach the optimal cost solution of the system; and (iii)  Experimental results with seven case studies show that formal synthesis approach qualitatively outperforms an existing state-of-the-art optimization tool.
-Our solution is far detailed and closer to the commercial reality (real PV systems).
-The results are validated with an accurate commercial design software called PVsyst.
+In summary, this paper makes the following original contributions.
+(i) It is the first application of a sound and complete formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems.
+(ii) We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop to reach the optimal cost solution of the system.
+(iii) Experimental results with seven case studies show that the formal synthesis approach qualitatively outperforms an existing state-of-the-art optimization tool.
+Our solution is far detailed and closer to commercial reality (real PV systems).
+The results are validated with accurate commercial design software called PVsyst.
 %\textit{Contribution}.

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required.
-The AC load dictates the AC electrical load behaviour from the house.
+The AC load dictates the AC electrical load behavior from the house.
 %
@@
 
-In this section, we explain the adopted method to size stand-alone solar PV systems, and what criteria and technique are possible to apply for the optimal sizing.
+In this section, we explain the adopted method to size stand-alone solar PV systems, and what criteria and technique can be applied to optimal sizing.
 
@@
 
-We adopted a critical period (worst month) solar energy method~\cite{Pinho}; in particular, maximum power point tracking (MPPT) charge controller, which is the most common nowadays.
+We adopted a critical period (worst month) solar energy method~\cite{Pinho}; in particular, the maximum power point tracking (MPPT) charge controller, which is the most common nowadays.
 Firstly, we need to correct the daily energy consumption estimated for the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered as follows
-
+%
 \begin{equation}
@@
 
-We must estimate the total power that will be demanded from the PV panels, as defined by Eq. ~\eqref{eq:Pminpanel}.
-
+We must estimate the total power that will be demanded from the PV panels, as defined by Eq.~\eqref{eq:Pminpanel}.
+%
 \begin{equation}
@@
 On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current ($I_{c} \geq I_{total,PVpanels}$) and voltage ($V_{c} \geq V_{total,PVpanels}$).
-
+%
 Concerning the batteries, the energy $E_{b}$ to be demanded by the PV system, in order to meet the load requirements, is defined by Eq.~\eqref{eq:Ebat}.
-
+%
 \begin{equation}
@@
 
-\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days.
+\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries; it is usually a design definition, which has a value ranging from $0.5$ to $2$ days.
 $DOD$ is the depth of discharge or the fraction of discharge.
@@
 However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours).
-Therefore, here in this study, the definition given here is for a maximum of $DOD$.
+In this study, the definition given here is for a maximum of $DOD$.
 When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
@@
 Moreover, the minimum current from the DC bus is defined by $I_{min,DCbus} = \dfrac{E_{b}}{V_{system}}$.
-Those equations are important to define the battery arrangement of the system (series and parallel connections).
-Where $V_{system}$ is the DC voltage of the bus.
+Those equations are important to define the system battery arrangement (series and parallel), where $V_{system}$ is the DC voltage of the bus.
 
 As for batteries, we must first define the total capacity of the battery bank, which can be described as
-
+%
 \begin{equation}
@@
 %
-Eq.~\ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted.
-
+Eq.~\ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted as
+%
 \begin{equation}
 \label{eq:batcheck}
-\left( N_{BS} \times N_{BP} \right) \geq N_{B}total
+\left( N_{BS} \times N_{BP} \right) \geq N_{B}total.
 \end{equation}
 
-The charge controller must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem}.
-
+The charge controller must initially meet the voltage requirement of the PV system, as described by
+% 
 \begin{equation}
@@
 
-The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because field temperature is higher than nominal or laboratory temperature, and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb}.
-
+The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because field temperature is higher than nominal or laboratory temperature, and the PV system is temperature dependent, as described by
+%
 \begin{equation}
@@
 Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
-
+%
 \begin{equation}
@@
 
-All the equations model the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones (it is not possible to deploy a fraction of panels or batteries).
+All the equations model the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones (it is not possible to deploy a fraction of panels or batteries).
 The verification and simulation tools need to handle non-linear real arithmetic to produce the result.
@@
 
-We need to evaluate \textit{power reliability} and \textit{system cost analysis} for the underlying system to select an optimal PV system to meet sizing constraints.
+We need to evaluate \textit{power reliability} and \textit{system cost analysis} for the underlying system to select an optimal PV system to meet size constraints.
 An ideal combination of any PV system consists of the best compromise between these two objectives or criteria.
+During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
+The reason is that solar energy production is intermittent and, therefore, the energy generated usually does not match with the load demand.
 
-During the PV system design, one of the most important aspects to ensure power system reliability is to analyse power supply availability~\cite{Alsadi2018}.
-The reason is that solar energy production is intermittent and, therefore, the energy generated usually does not match with the load demand.
-A reliable power is a generation system that has sufficient power to feed load demand in a period.
+Reliable power is a generation system that has sufficient power to feed load demand in a period.
 There exist different methods to express system reliability, where the most popular ones are the loss of load probability (LOLP) and the loss of power supply probability (LPSP)~\cite{Alsadi2018}.
-In both methods, if the probability is zero, then the load is always fulfilled; otherwise (i.e., probability of one) the load is never fulfilled.
-LOLP is the probability for the case when a load demand exceeds the generation power by the PV system.
-On the one hand,  we have a reliable PV system when it can generate sufficient power to fulfil the demanded load within a period.
+In both methods, if the probability is zero, then the load is always fulfilled; otherwise (i.e., probability of one), the load is never fulfilled.
+LOLP is the probability for the case when load demand exceeds the generation power by the PV system.
+On the one hand, we have a reliable PV system when it can generate sufficient power to fulfill the demanded load within a period.
 On the other hand, LPSP is defined as the probability of the case when the system generates insufficient power to satisfy the load demand.
-The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changing on system performance.
-However, data is not always available and dynamic analysis is complex; and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
+The main approaches to LPSP demand simulation or probabilistic treatment of time series data to predict dynamic changes in system performance.
+However, data is not always available, and dynamic analysis is complex; and this is a drawback of LOLP and LPSP~\cite{Alsadi2018}.
 
@@
 IRR is used to evaluate the attractiveness of a project or investment.
-We define LCOE as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
+We define LCOE as the average cost per kWh of usable electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost are considered~\cite{Kamel2005}.
 LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.
-LCC is the estimation of the sum of installation cost, operating and maintenance of a PV system for some time, and expressed in today's value~\cite{Applasamy2011}.
+LCC is the estimation of the sum of installation cost, operating, and maintenance of a PV system for some time, and expressed in today's value~\cite{Applasamy2011}.
 Eq.~\eqref{eq:LCC} is used to calculate LCC of a PV system,
@@
 The sizing rules rely on the designer's experience, using the lowest performance either in a time data or by directly using average value (daily, monthly, or annual) of solar irradiance.
-This method does not consider the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
+This method does not consider the battery's state of charge or even the random nature of solar irradiation and meteorological conditions~\cite{Alsadi2018}.
 For the numerical method, the design simulates for each time step within a period to calculate and investigate the state of charge of batteries.
@@
 Analytical methods are used to obtain a close relation or correlation in the form of an equation between capacities and reliabilities.
-The sizing task becomes much more straightforward than numerical technique; however, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analysed.
+The sizing task becomes much more straightforward than the numerical technique.
+However, the relation cannot be applied to different sites since it is specific to one place of deployment of the PV system, thereby demanding adaptation if another site is analyzed.
 

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
revised Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-All the equations model the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones (it is not possible to deploy a fraction of panels or batteries).
+%All the equations model the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones (it is not possible to deploy a fraction of panels or batteries).
 The verification and simulation tools need to handle non-linear real arithmetic to produce the result.
@@
 
-In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.
-In particular, Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis.
-Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions; except for the automated synthesis where we also define the bound $k$ to restrict the design-space search.
-Related to the output presented by both techniques, all of them produce a successful or fail result considering a feasible technical solution with the lowest cost.
-On the one hand, when done by simulation we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
-Furthermore, as described in this section, the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
+In this section, we present our methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis.
+Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions, except for the automated synthesis, where we also define the bound $k$ to restrict the design-space search.
+Concerning the output presented by both techniques, all of them produce a successful or fail result considering a feasible technical solution with the lowest cost.
+On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables.
+Furthermore, the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
 %
 \begin{figure}[h]
-\hspace*{-1cm}\includegraphics[width=0.55\textwidth]{optimalsizingprocess4}
+\hspace*{-1cm}\includegraphics[width=0.5\textwidth]{optimalsizingprocess4}
 \centering
@@
 
-Although simulation and testing explore possible behaviours and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw.
-Formal verification conducts an exhaustive exploration of all possible behaviours; when a design is said to be ``correct'' by a formal verification method, it implies all behaviours explored, and questions regarding adequate coverage or missed behaviour becomes irrelevant~\cite{Clarke2012}.
-Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}.
+Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether new trajectories may contain a flaw.
+Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies all behaviors explored, and questions regarding adequate coverage or missed behavior become irrelevant~\cite{Clarke2012}.
+Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is \textit{model checking}~\cite{Clarke2012}.
 
@@
 ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
-ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
+ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the formal system specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
 ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{\url{http://smtlib.cs.uiowa.edu/}} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}.
-This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
+This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of the formula state-space to be searched, because it solves and disregards data during the process, incrementally.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex, and the computing platform does not have a large amount of memory to deal with the entire design space state.
 
@@
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
-In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
-As a result, a given candidate program $p$ is iteratively refined, to match $\sigma$ more closely.
-CEGIS represents one of the most popular approaches to program synthesis currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization.
-Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture.
-Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.
-%from model checking.
+In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as a starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
+As a result, a given candidate program $p$ is iteratively refined to match $\sigma$ more closely.
+CEGIS represents one of the most popular approaches to program synthesis currently used in practice for cyber-physical systems~\cite{Abateetal2017}.
+%, as energy production, distribution, and optimization.
+Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the architecture. 
+%Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}. %from model checking.
 %
@@
 %	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
-	\includegraphics[width=0.5\textwidth]{fig2_rev2.jpg}
+	\includegraphics[width=0.48\textwidth]{fig2_rev2.jpg}
 	\caption{CEGIS adapted to PV system sizing.}
@@
 
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
+In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method~\cite{AbateCAV2018}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
 Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
@@
 One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists, and our synthesis engine can then conclude that no feasible equipment combination was found.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times.
+However, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists, and our synthesis engine can then conclude that no possible equipment combination was found.
 
 In our variant CEGIS method, there exist four distinct differences related to the traditional CEGIS: 
-(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+(1) there exists no test vector, and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
 (2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
@@
 Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; here, we have used symbolic software verifiers based on SMT solvers.
-
+%
 Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking.
-We adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the worst month criteria.
+We adopted the analytical method of optimization, with LCC economic analysis and power reliability based on the worst month criteria.
 
@@
 If that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value in line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
+The $MaxCost$ value in line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, which has two properties.
+(1) It will never be reached because the optimal solution will be found first (SAT result) or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
 
@@
 A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine to allow the choice of every item of PV sizing.
-Data-sheet from each item was necessary to collect technical information\footnote{\url{http://tiny.cc/4ny4nz}}.
-Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
+Data-sheet from each item was necessary to collect technical information.\footnote{\url{http://tiny.cc/4ny4nz}} Moreover, the price of each item was obtained from available quotations in the market in US dollars.
+%, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
 %All this data is available online\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.
@@
 Line $14$ is the charge controller voltage check.
-Line $15$ does the inverter check and ensures the power demand and the surge power of the inverter.
-Therefore, our synthesis algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$).
-This cost is the equivalent to Eq.~\eqref{eq:LCC}.
+Line $15$ does the inverter check and ensures the power demand and the inverter surge power.
+Our algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$). This cost is the equivalent to Eq.~\eqref{eq:LCC}.
 
@@
 %
-Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
-The Algorithm~\ref{alg:verification-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verify ($C \wedge \neg P$), as shown online\footnote{\url{http://tiny.cc/ity4nz}}.
+Note that the process is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
+Algorithm~\ref{alg:verification-algorithm} is transformed by the verification engines into the Boolean expressions, which are passed to the solver to verify ($C \wedge \neg P$), as shown online.\footnote{\url{http://tiny.cc/ity4nz}}
 
@@
 
-With respect to power reliability, this work will rely on the critical period solar 
-energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
-The usual way is to use loss of load probability (LOLP) or loss of power 
-supply probability (LPSP). However, we are neither considering site characteristics nor the load changes over time, 
-which demands historical data, the reliability analysis will be developed only 
-by the critical period method of PV sizing.
+Concerning power reliability, this work will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}.
+The usual way is to use LOLP or LPSP.
+However, we are neither considering site characteristics nor the load changes over time, which demands historical data.
+The reliability analysis will be developed only by the critical period method of PV sizing.
 %
@@
 \begin{itemize}
-	\item LCC lifetime considered: $20$ years;
-	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
-	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
-	\item Operation and maintenance annual costs: based on PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}.
-This cost includes the battery replacement based on its lifetime, plus inverters and controller replacement (every $10$ years).
-We adopted lead-acid batteries, the cheapest and most common kind used nowadays; and it means a $4$ years lifetime.
+	\item \textit{LCC lifetime considered}: $20$ years;
+	\item \textit{Installation costs}: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
+	\item \textit{Discount or interest rate value}: $10$\%, which is a good rate considering financial investments in developing countries;
+	\item \textit{Operation and maintenance annual costs}: based on PV projects of similar size in the Amazon region of Brazil, we will adopt US\$ 289.64~\cite{Agrener2013}.
+This cost includes the battery replacement based on its lifetime, plus inverters and controller replacement (every $10$ year).
+We adopted lead-acid batteries, the cheapest and most common kind used nowadays; and it means a $4$ year lifetime.
 Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
-Worth to mention that  those data can be adjusted in our algorithm.
+Note that those data can be adjusted in our algorithm.
 \end{itemize}
 
-On the subject of PV system optimization technique, we will adopt here the intuitive method 
-since the average value daily of solar irradiance is used in the mathematical model, 
-without considering the battery's state of charge, or even the random nature 
-of solar irradiation and meteorological conditions. Therefore, all the computational 
-effort will be concentrated in our automated synthesis algorithm.
+On the subject of PV system optimization technique, we will adopt here the intuitive method since the average value daily of solar irradiance is used in the mathematical model,  without considering the battery's state of charge, or even the random nature of solar irradiation and meteorological conditions.
+Therefore, all the computational effort will be concentrated in our automated synthesis algorithm.
 
-Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common adopted for lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
+Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is commonly adopted for lead-acid batteries), the system voltage is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).
 
-Related to off-the-shelf simulation tools only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis.
+Related to off-the-shelf simulation tools, only HOMER Pro performs off-grid systems with battery backup analysis and includes economical analysis.
 Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.
-Related to HOMER Pro: (a) is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; (b) it does not have the LCC cost in its reports.
+Related to HOMER Pro: (a) is available only for Microsoft Windows, and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; (b) it does not have the LCC cost in its reports.
 It has NPC and LCOE.
-Therefore NPC was used to obtain LCC in order to allow the comparative; (c) the optimization analysis of HOMER allows to define a load curve and temperature according of data collected from online databases.
-However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools; (d) it does not have a explicit equipment called charge controller.
-It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
-During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER}; (e) It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
+Therefore NPC was used to obtain LCC in order to allow the comparative; (c) the optimization analysis of HOMER allows us to define a load curve and temperature according to data collected from online databases.
+However, in order to allow a correct comparative, the curve load and the temperature were defined the same as automated synthesis tools; (d) it does not have explicit equipment called a charge controller.
+It uses a controller resource that can perform in two different ways, according to the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}.
+During the tests, it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER}; (e) It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system.
 By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}.
 For critical loads, 99\% is considered acceptable.
-While in a ordinary house electrical load, 95\% is considered acceptable; (f) it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; (g) the premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER will search for the optimized power of each component.
-With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modelling).
+While in an ordinary house electrical load, 95\% is considered acceptable; (f) it was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool; (g) the premise adopted when using HOMER Pro it was that the user does not know the optimal solution and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER will search for the optimized power of each component.
+With that in mind, it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with the capacity of $83.4$ Ah according to HOMER Pro modeling).
 HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (\textit{Specification}).
-These case studies were defined based on real houses visited by the team of a Newton Fund project in 14 riverside communities\footnote{\url{http://star-energy.coventry.ac.uk/}} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found into each house.
+These case studies were defined based on real houses visited by the team of a Newton Fund project in 14 riverside communities.\footnote{\url{http://star-energy.coventry.ac.uk/}} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found into each house.
 
@@
 The state-of-art verification tool ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer} was used as our reference verification engine.
-The optimization tool HOMER Pro version $3.13.1$ was used for comparative purpose.
+The optimization tool HOMER Pro version $3.13.1$ was used for comparative purposes.
 The optimal sizing produced by ESBMC and HOMER Pro were validated with PVsyst v$6.86$~\cite{PVsyst}.
-PVsyst is a MS-Windows software used for the study, sizing, simulation, and data analysis of solar PV systems, with a comprehensive list of commercial equipment.
+PVsyst is an MS-Windows software used for the study, sizing, simulation, and data analysis of solar PV systems, with a comprehensive list of commercial equipment.
 PVsyst does not perform optimization.
 % nor does it have commercial inverter equipment.
+
+Our evaluation aims to answer two experimental questions: [EQ1] \textbf{(soundness and completeness)} does our automated synthesis approach provide correct results?
+[EQ2] \textbf{(performance)} how does our formal synthesis tool compare to a specialized optimization tool?
 
@@
 
-Our evaluation aims to answer two experimental questions: [EQ1] \textbf{(soundness)} does our automated synthesis approach provide correct results?
-[EQ2] \textbf{(performance)} how does our formal synthesis tool compare to a specialized optimization tool?
-
 %---------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------
-ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours.
+ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/SAT response, varying from $36$ minutes to $10$ hours.
 ESBMC, with this configuration, was unable to obtain an optimal solution in cases $2$ and $7$.
@@
 %
-If we compare the results of the formal synthesis against those of HOMER Pro, we observed some distinct results in terms of the technical solution and cost (cf.
+If we compare the results of the formal synthesis against those of HOMER Pro, we observed some different results in terms of the technical solution and cost (cf.
 Table~\ref{tab1}).
@@
 Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, producing a higher estimation from the automated synthesis technique.
-However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.
+However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain different results.
 
@@
 The difference was between $34$\% to $68$\%.
-The mathematical models are different and particular parameters can be tuned for each technique, and that can justify the difference, which was presented in all the case studies.
+The mathematical models are different and particular parameters can be tuned for each technique; that can justify the difference, which was presented in all the case studies.
 
 Those discrepancies are not easy to address without some real systems validation.
-However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}.
+We use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}.
 Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it.
@@
 We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum).
-Case studies $2$ and $7$ had only HOMER Pro sizing validation, because the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine.
+Case studies $2$ and $7$ had only HOMER Pro sizing validation because the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine.
 %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).
 
-Overall, those comparison between our approach and the optimization software, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EQ1} and {EQ2}.
+Overall, those comparisons between our approach and the optimization software, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EQ1} and {EQ2}.
 
-HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not a commercial value.
+HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not commercial value.
 The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf.
-Moreover, our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro or PVsyst.
+Our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro or PVsyst.
 This feature is a definite advantage of the formal synthesis method.
-HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis.
-The formal synthesis method, therefore, presents more reliable results than HOMER Pro.
+HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only our approach presents a commercial controller and includes it during the cost analysis.
+Our approach, therefore, presents more reliable results than HOMER Pro.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We have reported a favourable assessment of our formal synthesis method to obtain the optimal size of the PV system.
-Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and constitute future work: ($1$) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, based on historical data; ($2$) the cost analysis is well-tailored to the Amazon region of Brazil; however, a broad analysis from other isolated areas must be performed to make the optimization general in terms of applicability in other isolated areas of the world, such as India and China; ($3$) to deploy some PV systems sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
+We have reported a favorable assessment of our formal synthesis method to obtain the optimal size of the PV system.
+Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and constitute future work: ($1$) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more precise by considering the dynamics of the weather characteristics over the year or by electric load changes over time, based on historical data; ($2$) the cost analysis is well-tailored to the Amazon region of Brazil; however, a broad analysis from other isolated areas must be performed to make the optimization general in terms of applicability in other isolated areas of the world, such as India and China; ($3$) to deploy some PV systems sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
 

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking techniques.
+We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking.
 The focus was on the synthesis method to obtain the optimal solution based on formal methods, which can cover better the design-space as opposed to simulation tools.
-We have considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; one state-of-art verification engine was considered (ESBMC), in addition to a specialized off-the-shelf optimization tool (HOMER Pro) to compare the results.
+We have considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak.
+One state-of-art verification engine was considered (ESBMC), in addition to a specialized off-the-shelf optimization tool (HOMER Pro) to compare the results.
 The validation through PVsyst was essential to perform the comparison.
-The paper produced a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
+The paper produced methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
+
 In summary, our synthesis tool is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro.
-In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current, and voltage; we also cover the charge controller, which is unavailable in HOMER Pro.
+In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from the datasheet of manufacturers, including the model of the component, nominal current, and voltage.
+We also cover the charge controller, which is unavailable in HOMER Pro.
 Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro; however, the presented solution is sound and complete; it also provides a list of equipment to be bought from manufacturers.
 Moreover, we extended the CEGIS synthesis method and implemented this extension within our proposed formal synthesis tool, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.
-For future work, we plan to improve the power reliability analysis, to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil) and to validate some cases with the deployment of real PV systems in isolated communities.
+For future work, we plan to improve the power reliability analysis to address the restriction to only allow automated synthesis of riverside communities in the Amazonas state (Brazil) and to validate some cases with the deployment of real PV systems in isolated communities.
 

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
removed basic stuff of PS
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}.
+%Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}.
 Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do.

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
removed basic stuff of MC
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether new trajectories may contain a flaw.
+%Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether new trajectories may contain a flaw.
 Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies all behaviors explored, and questions regarding adequate coverage or missed behavior become irrelevant~\cite{Clarke2012}.

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

@@
 \IEEEPARstart{L}{ack} of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion thresholds for the first time in $2017$~\cite{IEAweo2018}.
-The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
-Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}.
-Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for three-quarters of the additional connections needed to provide universal electricity~\cite{Hussein2012}; grid extension are the standard in urban areas~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion thresholds for the first time in $2017$: the share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
+%Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}.
+Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for three-quarters of the additional connections needed to provide universal electricity~\cite{Hussein2012}.
+%; grid extension are the standard in urban areas~\cite{IEAweo2018}.
 
@@
 %
-In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}; and general-purpose simulation tools, as MATLAB~\cite{Benatiallah2017}.
+%In order to simulate or evaluate a PV system, t
+There exist various specialized tools, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}; and general-purpose simulation tools, as MATLAB~\cite{Benatiallah2017}.
 However, these tools rely on simulation, with the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is infeasible~\cite{ClarkeHV18}.
@@
 In $2012$, a Chinese smart grid implementation considered a case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}.
-In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
+%In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
 In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
 Finally, in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-However, prior studies did not deal with electricity generation or even solar PV systems optimization.
+However, prior studies did not deal with solar PV systems optimization.
 Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in literature.
@@
 Fig.\ref{fig:blockdiagram} illustrates a stand-alone PV system block diagram.
-The PV generator (a panel or an array) is a semiconductor device that can convert solar energy into DC electricity.
+The PV generator is a semiconductor device that can convert solar energy into DC electricity.
 For night hours or rainy days, we hold batteries where power can be stored and used.
-The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}.
-The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required.
+The use of batteries implies the presence of a charge controller~\cite{Hansen}.
+The PV arrays produce DC, and therefore a DC/AC conversion (inverter) is required.
 The AC load dictates the AC electrical load behavior from the house.
@@
 We need to evaluate \textit{power reliability} and \textit{system cost analysis} for the underlying system to select an optimal PV system to meet size constraints.
-An ideal combination of any PV system consists of the best compromise between these two objectives or criteria.
+%An ideal combination of any PV system consists of the best compromise between these two objectives or criteria.
 During the PV system design, one of the most important aspects to ensure power system reliability is to analyze power supply availability~\cite{Alsadi2018}.
 The reason is that solar energy production is intermittent and, therefore, the energy generated usually does not match with the load demand.
-
 Reliable power is a generation system that has sufficient power to feed load demand in a period.
@@
 In both methods, if the probability is zero, then the load is always fulfilled; otherwise (i.e., probability of one), the load is never fulfilled.
-LOLP is the probability for the case when load demand exceeds the generation power by the PV system.
+%LOLP is the probability for the case when load demand exceeds the generation power by the PV system.
 On the one hand, we have a reliable PV system when it can generate sufficient power to fulfill the demanded load within a period.
@@
 \begin{figure}[h]
-\hspace*{-1cm}\includegraphics[width=0.5\textwidth]{optimalsizingprocess4}
+%\hspace*{-1cm} 
+\includegraphics[width=0.5\textwidth]{optimalsizingprocess4}
 \centering
@@
 This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of the formula state-space to be searched, because it solves and disregards data during the process, incrementally.
-This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex, and the computing platform does not have a large amount of memory to deal with the entire design space state.
+This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and it reduces the memory needed, helping to deal with the entire design space state.
 
@@
 The specification needs to describe the program's desired behavior to ensure that the program does what it intends.
-
 The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
@@
 %	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
-	\includegraphics[width=0.48\textwidth]{fig2_rev2.jpg}
+	\hspace*{-1cm}\includegraphics[width=0.55\textwidth]{fig2_rev2.jpg}
 	\caption{CEGIS adapted to PV system sizing.}
@@
 Concerning power reliability, this work will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}.
-The usual way is to use LOLP or LPSP.
+%The usual way is to use LOLP or LPSP.
 However, we are neither considering site characteristics nor the load changes over time, which demands historical data.
@@
 
-This section describes our case studies, experimental set-up,  objectives, and results to evaluate our proposed synthesis approach.
-We also compare our approach with a specialized simulation tool (HOMER Pro).
+This section describes our case studies, experimental set-up, and results to evaluate our proposed synthesis approach. We compare our approach with a specialized optimization tool.
 
@@
 We have reported a favorable assessment of our formal synthesis method to obtain the optimal size of the PV system.
-Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and constitute future work: ($1$) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more precise by considering the dynamics of the weather characteristics over the year or by electric load changes over time, based on historical data; ($2$) the cost analysis is well-tailored to the Amazon region of Brazil; however, a broad analysis from other isolated areas must be performed to make the optimization general in terms of applicability in other isolated areas of the world, such as India and China; ($3$) to deploy some PV systems sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
+Nevertheless, we have also identified three main threats to the validity of our experimental results, which can %be further assessed and
+constitute future work: ($1$) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more precise by considering the dynamics of the weather characteristics over the year or by electric load changes over time%, based on historical data
+; ($2$) the cost analysis is well-tailored to the Amazon region of Brazil; however, a broad analysis from other isolated areas must be performed to make the optimization general in terms of applicability in other isolated areas of the world%, such as India and China
+; ($3$) to deploy some PV systems sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
 

### 2020-05-03 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

@@
 %Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}.
-Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for three-quarters of the additional connections needed to provide universal electricity~\cite{Hussein2012}.
+Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for 75\% of the connections needed to provide universal electricity~\cite{Hussein2012}.
 %; grid extension are the standard in urban areas~\cite{IEAweo2018}.
@@
 %In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
-Finally, in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+In $2017$ happened the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}.
+A verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018} in $2018$.
+Finally, in $2019$, a formal verification technique was applied to validate the sizing of a stand-alone PV system~\cite{TrindadeCordeiro19}.
 However, prior studies did not deal with solar PV systems optimization.
@@
 %\hspace*{-1cm} 
-\includegraphics[width=0.5\textwidth]{optimalsizingprocess4}
+\includegraphics[width=0.51\textwidth]{optimalsizingprocess4}
 \centering
@@
 %	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
-	\hspace*{-1cm}\includegraphics[width=0.55\textwidth]{fig2_rev2.jpg}
+	\hspace*{-1cm}\includegraphics[width=0.5\textwidth]{fig2_rev3}
 	\caption{CEGIS adapted to PV system sizing.}
@@
 
-Our evaluation aims to answer two experimental questions: [EQ1] \textbf{(soundness and completeness)} does our automated synthesis approach provide correct results?
-[EQ2] \textbf{(performance)} how does our formal synthesis tool compare to a specialized optimization tool?
+Our evaluation aims to answer two experimental questions: [\textbf{EQ1}] \textbf{(soundness and completeness)} does our automated synthesis approach provide correct results?
+[\textbf{EQ2}] \textbf{(performance)} how does our formal synthesis tool compare to a specialized optimization tool?
 
@@
 
-HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}).
+HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool.
 Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year.
@@
 Table~\ref{tab1}).
-Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
-%
-Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, producing a higher estimation from the automated synthesis technique.
+Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, producing a higher estimation from the automated synthesis technique.
 However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain different results.
@@
 
-Those discrepancies are not easy to address without some real systems validation.
+Related to the inverters, HOMER Pro suggests a value in kW that is very close to the maximum load of every case study, but it is not commercial value.
+The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf.
+Our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro.
+This feature is a definite advantage of the formal synthesis method.
+HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only our approach presents a commercial controller and includes it during the cost analysis.
+Our approach, therefore, presents more reliable results than HOMER Pro.
+
+The discrepancies between the two approaches are not easy to address without some real systems validation.
 We use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}.
@@
 This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification).
-PVsyst was used with the formal synthesis sizing solution, where brands and models were simulated in PVsyst according to the sized system.
+PVsyst full feature of sizing validation was used only with the formal synthesis optimal sizing, where brands and models were simulated in PVsyst according to the sized system produced by ESBMC.
 
@@
 We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum).
-Case studies $2$ and $7$ had only HOMER Pro sizing validation because the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine.
+Case studies $2$ and $7$ had only HOMER Pro sizing validation because the synthesis technique did not present a solution due to \textit{time out} and the UNSAT response in the underlying verification engine.
 %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).
 
-Overall, those comparisons between our approach and the optimization software, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EQ1} and {EQ2}.
-
-HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not commercial value.
-The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf.
-Our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro or PVsyst.
-This feature is a definite advantage of the formal synthesis method.
-HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only our approach presents a commercial controller and includes it during the cost analysis.
-Our approach, therefore, presents more reliable results than HOMER Pro.
-
-In summary, our synthesis tool can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
-In particular, the automated synthesis method can provide all the details of every component of a PV system solution, including the model of the component, nominal current, and voltage.
-In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising).
-Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results, mainly concerning PV panels.
+%Overall, those comparisons between our approach and the optimization software, with validation through simulation tool, show that the synthesis solution is sound and complete, 
+%
+In summary, HOMER Pro is faster and can present a report with easier-to-read information and more graphics related to every optimization.
+However, our synthesis tool can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+In particular, the automated synthesis technique can provide all the details of every component of a PV system solution, including the model of the component, nominal current, and voltage.
+In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising); which answer partially \textbf{EQ2}.
+Moreover, the validation through PVsyst simulation, using the optimal PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are sound and complete, and not as oversized as HOMER Pro results, mainly concerning PV panels.
+This answers \textbf{EQ1} and \textbf{EQ2}.
 

### 2020-06-20 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

--- 2020-04-27 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
@@
 Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing PV systems.
-We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is infeasible.
+We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is not feasible.
 We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis.
@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, in 2017, the number of people without electricity access fell below $1$ billion thresholds for the first time~\cite{IEAweo2018}.
+Progress has been made worldwide; in particular, in 2017, the number of people without electricity access fell below $1$ billion for the first time~\cite{IEAweo2018}.
 The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
@@
 In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
-However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations, and potential failures of a system are infeasible~\cite{ClarkeHV18}.
+However, these tools are based on simulation; they have the drawback of incomplete coverage since verification of all possible combinations, and potential failures of a system are not feasible~\cite{ClarkeHV18}.
 Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
-However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialist PV optimization software.
+However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialized PV optimization software.
 
@@
 In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, a researcher suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}.
+In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}.
 In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
 In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
-However, \textit{formal methods and its application to synthesize PV systems are still unexplored in literature}.
+However, \textit{formal methods and its application to synthesize PV systems are not explored in literature}.
 
@@
 
-Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the traditional techniques (manual and simulation) and the proposed synthesis technique.
+Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the manual or simulation techniques and the proposed synthesis technique.
 Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions.
-For the automated synthesis, we also define the bound $k$ to restrict the design-space search.
+However, when using automated synthesis, we also define the bound $k$ to restrict the design-space search.
 Here we start with a low bound $k$ and incrementally increase it to avoid time and memory constraints on our verification engine.
@@
 
-Both techniques (traditional and automated synthesis) produce as output either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
+The techniques (manual, simulation and automated synthesis) produce as output either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
 On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is mathematical reasoning about a model, presents a counterexample with the optimal solution stored in variables.
@@
 The sizing check stage can ensure that the system meets the standard project steps related to the critical period method (worst month) for solar energy system sizing~\cite{Pinho} and adopting an MPPT (Maximum Power Point Tracking) charge controller, which is the most common in use.
-Firstly, we need to correct the daily energy consumption estimated for the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
+Firstly, we need to correct the daily energy consumption estimated for the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho}.
 
@@
 \label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \times \eta_{c} \times \eta_{i} }.
+E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \times \eta_{c} \times \eta_{i} }
 \end{equation}
 
-We must estimate the total power that will be demanded from the PV panels, as defined by Eq. ~\eqref{eq:Pminpanel}.
+We must estimate the total power that will be demanded from the PV panels, as defined by Eq.
+~\eqref{eq:Pminpanel}.
+Where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
+A factor of $20$\% for losses is considered, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
 
@@
 \label{eq:Pminpanel}
-P_{min,panels} = \dfrac{1.25 \times E_{corrected}}{Insolation},
+P_{min,panels} = \dfrac{1.25 \times E_{corrected}}{Insolation}
 \end{equation}
 
-\noindent where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
-A factor of $20$\% for losses is considered, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
-
 On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
-On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as described by Eqs.~\eqref{eq:Icmin} and
-\eqref{eq:Vcmin}.
+On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as described by Eqs.~\eqref{eq:Icmin} and \eqref{eq:Vcmin}.
 
@@
 \label{eq:Icmin}
-I_{c} \geq I_{total,PVpanels},
+I_{c} \geq I_{total,PVpanels}
 \end{equation}
@@
 \label{eq:Vcmin}
-V_{c} \geq V_{total,PVpanels},
+V_{c} \geq V_{total,PVpanels}
 \end{equation}
@@
 \label{eq:Ebat}
-E_{b} = \dfrac{Autonomy \times E_{corrected}}{DOD},
+E_{b} = \dfrac{Autonomy \times E_{corrected}}{DOD}
 \end{equation}
 
-\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days.
+\noindent Where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days.
 $DOD$ is the depth of discharge or the fraction of discharge.
@@
 However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours).
-Therefore, here in this study, the definition given here is for a maximum of $DOD$.
+Therefore, the definition given here is for a maximum of $DOD$.
 When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
@@
 This equation is important to define the battery arrangement of the system (series and parallel connections).
+Where $V_{system}$ is the DC voltage of the bus.
 
@@
 \label{eq:DODday}
-DOD_{day} = \dfrac{E_{corrected} \times 100}{E_{b}},
+DOD_{day} = \dfrac{E_{corrected} \times 100}{E_{b}}
 \end{equation}
@@
 \label{eq:Idcbus}
-I_{min,DCbus} = \dfrac{E_{b}}{V_{system}},
+I_{min,DCbus} = \dfrac{E_{b}}{V_{system}}
 \end{equation}
@@
 
-\noindent where $V_{system}$ is the DC voltage of the bus.
-
-As for batteries, we must first define the total capacity of the battery bank, which can be described as
+As for batteries, we must first define the total capacity of the battery bank, which can be described as shown in Eq.~\ref{eq:Cbank}.
+where $ E_{load} $ is the average energy consumed by the load corrected according to PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
 
@@
 \label{eq:Cbank}
-C_{bank} = \dfrac{Autonomy E_{load}}{DOD \eta _{b} V_{system}},
+C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}
 \end{equation}
 
-\noindent where $ E_{load} $ is the average energy consumed by the load corrected according to PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
-%
 Eq.~\ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted in the project.
@@
 \label{eq:vcvsystem}
-V_{c} = V_{system}.
+V_{c} = V_{system}
 \end{equation}
 
-The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because field temperature is higher than nominal or laboratory temperature, and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb}.
+The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel.
+Where $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.
 
@@
 \label{eq:iscamb}
-I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
+I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right] 
 \end{equation}
 
-The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin}.
+The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin}. Where $N_{PP}$ is the number of parallel panels adopted.
 
@@
 \label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP},
+I_{c,min} = I_{sc,amb} \times N_{PP}
 \end{equation}
@@
 \label{eq:icicmin}
-I_{c} \geq I_{c,min}.
+I_{c} \geq I_{c,min}
 \end{equation}
@@
 \label{eq:vindc} 
-V_{in}DC = V_{system}.
+V_{in}DC = V_{system}
 \end{equation}
@@
 \label{eq:voutac} 
-V_{out}AC = V_{AC}.
+V_{out}AC = V_{AC}
 \end{equation}
@@
 \label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
+\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right]
 \end{equation}
@@
 \label{eq:LCC}
-LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
+LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M}
 \end{equation}
 
-\noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current prices.
+\noindent Where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current prices.
 Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using software model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
@@
 %
-Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
+Three state-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
 

### 2020-06-22 Tex/CAV2019/reply VSTTE JUNE2020.tex
VSTTE rebuttal

--- 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
@@
 \newtheorem{myassumption}{Assumption}
-\newcommand{\mstitle}{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}
-\newcommand{\refnumber}{SE-D-19-01248}
+\newcommand{\mstitle}{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison}
+\newcommand{\refnumber}{Paper 14}
 \newenvironment{resposta}{~~~\begin{quote}\color{blue}\textbf{Response:}}{\end{quote}}
@@
 {\bf Please Reply to:}\\
-Assistant Professor Alessandro Trindade\\
+Adjunct Professor Alessandro Trindade\\
 Universidade Federal do Amazonas\\
@@
 \begin{flushleft}
-    Mario A. Medina, PhD, PE\\
-    Associate Editor\\
-	Solar Energy
+	Nadia Polikarpova and Maria Christakis \\
+	PC co-chairs,\\
+	VSTTE'20
     \end{flushleft}
@@
 
-\indent Dear Mario,
+\indent Dear Nadia Polikarpova and Maria Christakis,
 \vi
@@
 
-According to the associate editor and reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text.
-The revision included the Abstract, Introduction, Methodology, and Results sections.
+According to the reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text.
+The revision included the Abstract, Introduction, Methodology?????, and Results????
+sections.
 
@@
 
-We hope those modifications in our manuscript and also our responses are sufficient to make our work suitable for publication in {\bf Solar Energy}.
+We hope those modifications in our manuscript and also our responses are sufficient to make our work suitable for publication.
 

### 2020-06-22 Tex/CAV2019/reply VSTTE JUNE2020.tex
VSTTE rebuttal

@@
 \newpage
-\subsection*{Reviewer \#2 comments followed by the authors' answers:}
+\subsection*{Reviewer \#1 comments followed by the authors' answers:}
 
@@
 
-In the manuscript, the authors report about the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load.
-They show, case studies, from real photovoltaic systems deployed in five different places, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools.
-Also, the authors reported the evaluated different verification tools, in order to compare performance and soundness.
-Data from practical applications show the effectiveness of their approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
+The paper presents an application of program verification and synthesis to select a combination of photovoltaic (PV) components that are optimally sized from a given set of available commercial components.
+The approach is compared to a commercial simulation tool, and generates PV systems that have better power characteristics.
 
-I have specifics questions and suggestions in order to improvement the manuscript.
+The application of existing verification and synthesis techniques for solving the real-world problem of designing optimal PV systems is very interesting, and certainly in scope of VSTTE.
+However, the current presentation of the paper needs to be substantially improved.
 
-(1) To clarify the figure 2, i recommend write "current" inside the figure, don't put just I.
+First, it is not entirely clear who the paper is primarily aimed at.
+For a software verification conference, it assumes too much knowledge of PV systems and the physics involved, but on the other hand, includes too little detail about the actual verification and synthesis technique.
+For example, the background in section 2.2 is not accessible to a general verification audience.
+Rather, I would suggest to provide a much more high-level background on PV systems, and simply state that such a system can be modelled using a set of equations, possibly giving the (main) variables.
+Similarly, many of the PV-specific details in the evaluation are not accesible for a general verification audience, and need to be discussed at a higher level.
 
 \begin{resposta} 
-We thank the reviewer for this insightful comment.
-Indeed, it summarizes what was intended to be studied in this manuscript.
-Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modeling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.
-Regarding Figure 2, we fixed it as recommended by the reviewer.
-Moreover, we applied the same procedure to voltage $V$, in order to keep consistency throughout our manuscript.
+Alessandro: acho que o revisor tem razão.
+Creio que valeria a pena tratar a parte da modelagem e fenômenos da geração de energia a um nível mais alto.
+Vou trabalhar isso mas sem remover toda a modelagem.
 
@@
 
-(2) This software model checking has performance in comparison the other commercials software,how is this performance?, Could you give the areas where your software performs better than commercial software?
+Secondly, the problem that the paper is trying to solve needs to be stated precisely and early.
+In particular, it is not clear to me what the optimization objective is, i.e.
+what does 'optimal sizing' mean?
+Do you optimize for cost, or power consumption, or both?
+Currently, it is not until section 3 (page 8), that the paper seems to explain that the optimization is done w.r.t.
+to cost, but the evaluation seems to contradict this, because the commercial solution is regarded as not optimal, even though it has the lowest cost (in dollars).
 
 \begin{resposta} 
-Note that our options about specialized off-the-shelf tools to design stand-alone solar PV systems are very limited in literature, which motivated us to perform further studies in this area.
-In particular, as described in Section 2.1, only Hybrid2 and HOMER Pro perform off-grid with battery analysis of PV systems.
-Hybrid2 is not supported anymore, thereby being in disuse.
-We have updated this information in our manuscript (Section 2.1 as well).
-Therefore, in this particular research field (stand-alone solar PV systems), only HOMER Pro could be used for comparative purposes.
-However, in our experiments we could use some general simulation tools with the same mathematical model adopted by our automated verification tool.
-However, this would represent an unfair comparison since we would need to tweak the simulation tools to prepare them for comparison purposes, which could introduce errors.
-We have described this limitation in Section 5.4 (``Threats to Validity'') in order to state that additional comparisons could be carried out with general simulation tools if they employ similar mathematical models as the ones described here.
-Moreover, we mentioned the possibility to include this general purpose software tool comparative as future work (Section 6).
-
-Note that model checking and software simulations are two different techniques that use mathematical models.
-However, the way they work is completely different.
-On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
-On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
-In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation.
-Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in Section 1 (Introduction).
-
-Importantly, model checking explores more efficiently the design-space because the system specification is based on a formal notation, which gets converted into Boolean algebra; the evaluation of variables is made automatically by a Boolean Satisfiability (SAT) solver based on the system's constraints, i.e., system information and electrical load demand transformed into properties (e.g., use defined demands and non-deterministic variables to model the respective weather that does not have precise forecasting).
-This resulting mathematical model is submitted to full exploration of all possible states to find a configuration, where an error might occur or not.
-Logically, depending on the number of variables, state-explosion can occur and the model checking process might be time-consuming to transverse the entire state-space.
-
-However, the authors demonstrated in $2016$ [1] that model checking can present better performance than software simulation if one performs hardware-software partitioning in specifically amount of instances.
-
-[1] Trindade, A.B. and Cordeiro, Applying SMT-based verification to hardware/software partitioning in embedded systems. Des Autom Embed Syst (2016) 20: 1. https://doi.org/10.1007/s10617-015-9163-z
+Alessandro: realmente a definição de optimal sizing não é colocada logo de início.
+Realmente a definição só vem na página 8, não tem na Introdução.
+Vou melhorar a parte introdutória e onde explica o comparativo da solução ótima.
+No comparativo, o ótimo de uma ferramenta é apenas o ótimo da ferramenta, não necessariamente o ótimo do comparativo com outras ferramentas.
+Vou deixar isso claro lá também na parte de avaliação perto do quadro comparativo.
 
@@
 
-(3) In text reference at figure 1 the authors do not describe all symbols drawn into image, for instances, what is means G, T.
-I suspect that in section 4 they define which are the variables (Irradiation and temperature).
-I suggest you define those symbols in the text that that figure describes.
+Then, I am confused about which verification, resp.
+synthesis, technique is actually being used.
+This is partially due to lack of details, but also because of inconsistencies in the paper.
+In different places, the paper describes the technique as CEGIS, or as model checking, or as optimization.
 
 \begin{resposta} 
-Indeed, we have missed this particular information in the paragraph that describes the mentioned figure.
-We thank you so much for this observation.
-We have revised our manuscript to describe every employed symbol.
-The revised version of these paragraphs in Section ``2.2 Component models for a stand-alone PV system'' are now described as: ``A stand-alone PV system is illustrated in Fig.1.
-The PV generator is a semiconductor device that can convert solar energy into DC electricity, with high dependence on two weather variables from the site, where the system is deployed: solar irradiance $G$ and temperature $T$.
-For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller.
-The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter).
-The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
-At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.''.
+Alessandro: Pra mim, é o desenvolvimento de uma técnica (como já discutimos em janeiro), que usa model checking e, como é feita em duas etapas, ela lembra o modo como o CEGIS funciona.
+E como o resultado é uma solução ótima, o resultado é uma otimização.
+Creio que isto deva ir pra introdução também (e pro abstract).
+
 \end{resposta}
 
-(4) Are the verification results carried out affected by the different characteristics of the computers?
+Algorithm 1 to me seems to construct a contraint and then tries to solve it for the nondeterministic variables to obtain a solution, and to use essentially a linear search to find the minimum cost.
+Is this correct?
+If so, it is unclear to me how this fits with the CEGIS algorithm in Fig.
+2, and where model checking is used.
 
 \begin{resposta} 
-Indeed, we did not inform the impact of changing the computer setup or related issues.
-We thank the reviewer for this observation.
-We have revised our manuscript to include the following paragraph in Section "5.2 Objectives and Setup": ``Note that the results presented here depend on the computer's processor and memory, the version of each software verifier (i.e., CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the implemented model (software created by the authors) to be solved.
-Additionally, any change from HOMER Pro to another simulation tool can also influence the measured time to obtain results.''.
+Alessandro: Provavelmente eu tenha que melhorar o texto, pois a escolha de uma solução factível ou não achar uma solução factível já é por model checking ( e isso corresponde a 1a parte da técnica), a 2a parte é uma busca linear mas com teste de SUCCESS ou FAIL para gerar contraexemplo (e, pra mim, é model checking de novo).Pra mim, estamos aplicando model checking duas vezes na técnica.
+\textbf{Que achas?}
+
+\end{resposta}
+
+Finally, section 2.2 presents nonlinear continuous real-valued constraints.How can the discrete solvers used handle these constraints?
+
+\begin{resposta} 
+Alessandro: Essa questão é para se pensar.
+Pra mim, a não linearidade das equações do artigo anterior de validação de sistemas solares estava mais claro pois usamos equações exponenciais e logaritmas.
+Nesse, a não linearidade se deve ao fato de a curva do ótimo global não ser contínua, pois pegamos valores específicos de variáveis não determinísticas, valores inteiros...daí eu não sei responder o que o revisor questionou.
+
+Lucas: Modelamos essas usando aritmética de ponto flutuante.
+É apenas uma aproximação dos números reais.
+No entanto, neste trabalho, não nos preocupamos em calcular o erro de arredondamento.
+Precisamos enfatizar isso no texto.
+Esse nosso paper descreve um pouco sobre esses erros: https://arxiv.org/pdf/2004.12699.pdf
+
 \end{resposta}
@@
 
-\subsection*{Reviewer \#4 comments followed by the authors' answers:}
+\subsection*{Reviewer \#2 comments followed by the authors' answers:}
 
@@
 
-(5) The topic itself is interest for the PV application. However some section including abstract and result must be rewritten to be enhanced, here are the comments:
+This paper presents a novel approach based on formal methods in order to obtain the optimal size of solar photovoltaic systems.
+The paper first introduces the basic formalization of such systems (in Section 2), then it discusses how these were modeled by means of formal methods (Section 3), and it then presents and discusses the experimental results (Section 4) comparing it with a commercial tool performing the same tasks using a different approach (HOMER).
 
--       The manuscript illustrated the main drawback from other existed work that they are based on simulation and the proposed approach is claimed to do evaluation based real PV system as illustrated in the abstract, however the evolution is based on simulation model, mathematical, and information from website data such as Weather base and Energy Plus.
-The author should present real data measurement for more accurate results then compared and the main difference should be clarified.
+Pros
+--------
+
+* This paper extends the application of formal methods to a novel scenario (aka optimization of solar photovoltaic systems).
+
+* Overall, the formal approach seems to be sound and robust, even if I was not able to fully understand the background (see cons below).
+
+* The authors have carried out very deep experiments.
+In particular, the algorithm was tested using 3 different state-of-the-art verifiers, and the results were compared with a commercial solution.
+In addition, since it is not straightforward to evaluate the results without a real system validation, the authors used a simulation tool.
 
 \begin{resposta} 
-We appreciate these comments; we actually realized that the contributions of our manuscript were unclear.
-We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modeling, which was already investigated in prior studies over the last two decades.
-Moreover, we compare the results of using automated verification with simulation; real PV systems were employed just to validate the results presented by both approaches (model checking and simulation).
-Note that the automated verification and simulation tools are intended to be used during the design of the PV system, i.e., before actually buying or deploying the equipment.
-This information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.
-
-The authors hold real load curve and information collected from monitoring system using Raspberry Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result), we understand that this comparison is not appropriate.
-
-The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, as presented in our "References" section: (Weatherbase, 2018) and (EnergyPlus, 2018).
-Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure for not using weather base stations in each place since House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data).
-Because of that, we decided to add this discussion in Section ``5.4 Threats to Validity''.
-We thank you for that specific comment.
+Thank you.
 \end{resposta}
 
-(6)      Section 5 "Experimental Evolution" It can be changed to Verification result, otherwise the author should clarify the real measurements of the system.
+Cons
+--------
+
+* For someone not familiar with the topic (like myself and, I would expect, 95\% of VSTTE community), it might be difficult to understand the overall setup, since Section 2 fails to provide some of the background (see minor comments below)
 
 \begin{resposta} 
-We thank the reviewer for this comment.
-We implemented as suggested, i.e., we changed the section title to ``Verification and Simulation Results" since the results are related to both verification and simulation tools.
-The data collected from dwellers with real PV systems were used just to confirm (or not) flaws and complains about the equipment deployed in the field.
+Mesmo do revisor 1. Mudanças que farei endereçarão isso
 
-The authors hold real load curve and information collected from monitoring system using Raspberry Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result, as described in Section 4 of our manuscript), so we understand that this comparison is not appropriate.
-
-Note that model checking and software simulations are two different techniques that use mathematical models.
-However, the way they work is completely different.
-On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
-On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
-In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation.
-Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in Section 1 (Introduction).
 \end{resposta}
 
-(7)       Can the author present the main waveform of the PV system in the steady state operation and under failure or any environmental change? wave-forms such as: Input power, VMPP, IMPP, AC load
+* In general, I would say that the experimental results are not outstanding, but they show some potential in applying a total different approach to this field.
+However, the authors at the beginning state that the goal is to compute a solution with minimal cost, but then in Table 1 Homer computed cheapest solutions in all the cases, then it looks like the introduced approach is worse than existing commercial tools.
+Then the following discussion is a bit shallow: Table 2 "show that the synthesis solution is sound and complete, which answers EG1 and EG3", but EG3 is about "how does our formal synthesis tool compare to a specialized simulation tool?" (so I am still not sure if Homer is sound and complete and what's the comparison).
+Finally, the three drawbacks of Homer are discussed at the end of Section 4.4, but this is not about the costs of the system, and not connect to the three experimental goals.
 
 \begin{resposta}
+Preciso pensar aqui
 
-We agree with the reviewer that we could further improve the explanation of our study.
-In our manuscript, we compare model checking with software simulation.
-However, the way they work is completely different.
-On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output.
-On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property.
-In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation.
-Therefore, we can prove the absence of system flaws using model checking.
-This information was included in the revised version of our manuscript in Section 1 (Introduction).
+\end{resposta}
 
-When we work with waveform, we are performing testing or simulation, and that is different of automated verification.
-We consider that this comment (number $7$ in this Reply Letter) is related to the experimental question done by the same reviewer in (6).
-As a result, we expect that the explanations given in (6), together with the consequent updated manuscript, can cover any further concerns about this particular issue.
+- Almost all equations end with a comma, please remove it
+
+\begin{resposta}
+Thank you for the advice. We removed all the commas.
+
 \end{resposta}
+
+- Page 2: specialist PV optimization software -> specialized PV optimization software
+done
+
+\begin{resposta}
+Thank you, we corrected the text as suggested.
+\end{resposta}
+
+- In the introduction it is stated that formal methods for PV systems are unexplored in literature.
+I think a discussion about why this is the case, and what is intuitively needed to apply them to this new scenario would help the reader to understand the potential and impact of the novel approach
+
+\begin{resposta}
+Concordo. Vou fazer isso no texto
+\end{resposta}
+
+- Section 2.2: some parts of this section are not well explained.
+To people that do not know this field, some choices feel completely arbitrary: why a factor of 20\% for losses is considered in equation 2?
+Similarly, why DOD is 75\%?
+I guess these are standard values, but maybe some citations of papers using the same parameters (or discussing them) might be helpful to convince the reader about the robustness of the formalization
+
+\begin{resposta}
+Concordo. Vou acrescer isso no texto
+\end{resposta}
+
+- page 6: Therefore, here in this study, the definition given here -> Therefore, the definition given here
+
+\begin{resposta}
+Thank you, we corrected the text as suggested.
+\end{resposta}
+
+- From equation 9 on I was lost. What are G, G\_ref, and T equation 9? Why you have T - 25 here? What is N\_PP in equation 10a?
+
+\begin{resposta}
+Thank you, you were right. The whole sentence was rebuild, with correct mention and explanation about the elements.
+\end{resposta}
+
+- Equation 6 is missing the 'x' to represent multiplications
+
+\begin{resposta}
+Thank you, we corrected the text.
+\end{resposta}
+
+- Page 10: start-of-the-art -> state-of-the-art
+done
+
+\begin{resposta}
+Thank you, we corrected the text as suggested.
+\end{resposta}
+
+\end{quote}
+\newpage
+
+\subsection*{Reviewer \#3 comments followed by the authors' answers:}
+
+\begin{quote}
+The paper describes a system for optimally sizing PV systems.
+A detailed account is given of both modeling parameters, evaluation method
+and evaluation results. The details, covered in the paper, contain
+a substantial amount of information on PV optimization and approaches
+for solving the constraints. It uses methods developed in the FM
+community, such as CBMC with MiniSAT, MathSat and Boolector and compares with
+available commercial tools based on other technologies.
+The substantial results are impressive and be inspirational.
+There are also some drawbacks that makes the material not well
+accessible:
+- The description is very tedious and mixes a lot of low level
+  information that is really only interesting to the authors
+  and not suitable for a conference paper. More emphasis should
+  be applied to the overall principles, and then details should be
+  presented as instantiations.
+  Essentially, parts of the paper, such as section 2.2 are not
+  really useful. It is not possible for a reader to keep track of
+  the many variables that are introduced. I don't see how they add
+  conceptual value.
+  Algorithm 1 also contains too many references to inlined variables.
+
+\begin{resposta} 
+Repete o revisor 1. As mudanças que farei matam essas questões
+\end{resposta}
+
+ I do have some doubts about suitable the encodings that
+  the authors choose, in particular, how relevant full fledged
+  floating point reasoning is, but have no way to check.
+  For a conference paper I am quite willing to give the paper a
+  pass on this doubt as exposing details in the encodings could
+  make the paper even less accessible.
+- The paper contains several awkwardly formulated sentences. Examples
+  are listed below.
+
+The net effect is that the paper reads as a tour-de-force in "we did all of this hard work", but does not read "let us explain you something new and interesting from what we learned to inspire you".
+
+Overall, based on the substance of the results, the paper remains adequate for the venue.
+
+\begin{resposta}
+Thank you.
+\end{resposta}
+
+Examples of awkward sentences:
+
+Progress has been made worldwide; in particular, in 2017, the number
+of people without electricity access fell below 1 billion thresholds
+-> Progress has been made worldwide; in particular, in 2017, the number
+of people without electricity access fell below 1 billion
+
+\begin{resposta}
+Thank you, we corrected the text as suggested.
+\end{resposta}
+
+they have the drawback of an incomplete coverage ->
+they have the drawback of incomplete coverage
+
+\begin{resposta}
+Thank you, we corrected the text as suggested.
+\end{resposta}
+
+are infeasible
+
+\begin{resposta}
+Thank you, we corrected the the two occurrences to "not feasible".
+\end{resposta}
+
+In 2017, a researcher suggested the application of formal methods to verify and
+control the behaviour of computational devices in a smart grid [2].
+
+\begin{resposta}
+Thank you, we corrected the text to ?In 2017, it was suggested the application...?.
+\end{resposta}
+
+are still unexplored in literature
+$->$
+
+\begin{resposta}
+Thank you, we corrected the text as "systems are not explored in literature".
+\end{resposta}
+
+using the traditional techniques
+->
+
+\begin{resposta}
+Thank you, we corrected the text as "using the manual or simulation techniques and...".
+\end{resposta}
+
+For the automated synthesis
+->
+
+\begin{resposta}
+Thank you, we corrected the text as "However, when using automated synthesis..".
+\end{resposta}
+
 \end{quote}

### 2020-06-24 Tex/CAV2019/replyVSTTEJUNE2020.tex
added response
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2020-06-22 Tex/CAV2019/reply VSTTE JUNE2020.tex
@@
 Alessandro: Provavelmente eu tenha que melhorar o texto, pois a escolha de uma solução factível ou não achar uma solução factível já é por model checking ( e isso corresponde a 1a parte da técnica), a 2a parte é uma busca linear mas com teste de SUCCESS ou FAIL para gerar contraexemplo (e, pra mim, é model checking de novo).Pra mim, estamos aplicando model checking duas vezes na técnica.
-\textbf{Que achas?}
+\textbf{Que achas?}  \textbf{Lucas: Concordo.
+Nao poderia aplicar uma busca binaria como fizemos no nosso journal do IJES?}
 
@@
 
-- Page 2: specialist PV optimization software -> specialized PV optimization software
+- Page 2: specialist PV optimization software -$>$ specialized PV optimization software
 done
@@
 
-- page 6: Therefore, here in this study, the definition given here -> Therefore, the definition given here
+- page 6: Therefore, here in this study, the definition given here -$>$ Therefore, the definition given here
 
@@
 \begin{resposta}
-Thank you, we corrected the text.
+Implemented as suggested.
 \end{resposta}
 
-- Page 10: start-of-the-art -> state-of-the-art
+- Page 10: start-of-the-art -$>$ state-of-the-art
 done
@@
 \begin{resposta}
-Thank you, we corrected the text as suggested.
+Implemented as suggested.
 \end{resposta}
@@
 of people without electricity access fell below 1 billion thresholds
--> Progress has been made worldwide; in particular, in 2017, the number
+-$>$ Progress has been made worldwide; in particular, in 2017, the number
 of people without electricity access fell below 1 billion
@@
 \begin{resposta}
-Thank you, we corrected the text as suggested.
+Implemented as suggested.
 \end{resposta}
 
-they have the drawback of an incomplete coverage ->
+they have the drawback of an incomplete coverage -$>$
 they have the drawback of incomplete coverage
@@
 \begin{resposta}
-Thank you, we corrected the the two occurrences to "not feasible".
+Thank you, we corrected the the two occurrences to ``not feasible''.
 \end{resposta}
@@
 are still unexplored in literature
-$->$
+-$>$
 
@@
 using the traditional techniques
-->
+-$>$
 
@@
 For the automated synthesis
-->
+-$>$
 

### 2020-06-24 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, in 2017, the number of people without electricity access fell below $1$ billion for the first time~\cite{IEAweo2018}.
+Progress has been made worldwide; \textcolor{blue}{in particular, in 2017, the number of people without electricity access fell below $1$ billion for the first time}~\cite{IEAweo2018}.
 The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.

### 2020-06-24 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
-However, these tools are based on simulation; they have the drawback of incomplete coverage since verification of all possible combinations, and potential failures of a system are not feasible~\cite{ClarkeHV18}.
+However, these tools are based on simulation; \textcolor{blue}{they have the drawback of incomplete coverage} since verification of all possible combinations, and potential failures of a system are \textcolor{blue}{not feasible}~\cite{ClarkeHV18}.
 Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
@@
 In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}.
+\textcolor{blue}{In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid (e.g.,~\cite{Abate2017})}.
 In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.

### 2020-06-24 Tex/CAV2019/replyVSTTEJUNE2020.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta}
-Thank you, we corrected the the two occurrences to ``not feasible''.
+We have replace ``infeasible'' by ``not feasible''.
 \end{resposta}
@@
 \begin{resposta}
-Thank you, we corrected the text to ?In 2017, it was suggested the application...?.
+We have rewritten this sentence as ``In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid [2]''.
 \end{resposta}

### 2020-06-24 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
-However, \textit{formal methods and its application to synthesize PV systems are not explored in literature}.
+\textcolor{blue}{However, \textit{formal methods and its application to synthesize PV systems are not explored in literature}}.
 
@@
 
-Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the manual or simulation techniques and the proposed synthesis technique.
+\textcolor{blue}{Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the manual or simulation techniques and the proposed synthesis technique}.
 Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions.
-However, when using automated synthesis, we also define the bound $k$ to restrict the design-space search.
+\textcolor{blue}{However, when using automated synthesis, we also define the bound $k$ to restrict the design-space search}.
 Here we start with a low bound $k$ and incrementally increase it to avoid time and memory constraints on our verification engine.

### 2020-06-24 Tex/CAV2019/replyVSTTEJUNE2020.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta}
-Thank you, we corrected the text as "systems are not explored in literature".
+We have updated this sentence as ``However, formal methods and its application to synthesize PV systems are not explored in literature''.
 \end{resposta}
@@
 \begin{resposta}
-Thank you, we corrected the text as "using the manual or simulation techniques and...".
+We have updated this sentence as ``Fig. 1 illustrates how to obtain the optimal sizing of a stand-alone PV system using the manual or simulation techniques and the proposed synthesis technique''.
 \end{resposta}
@@
 \begin{resposta}
-Thank you, we corrected the text as "However, when using automated synthesis..".
+We have updated this sentence as ``However, when using automated synthesis, we also define the bound $k$ to restrict the design-space search''.
 \end{resposta}

### 2020-06-24 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
-However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialized PV optimization software.
+However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with \textcolor{blue}{specialized PV optimization software}.
 
@@
 However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours).
-Therefore, the definition given here is for a maximum of $DOD$.
+\textcolor{blue}{Therefore, the definition given here is for a maximum of $DOD$}.
 When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
@@
 \label{eq:Cbank}
-C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}
+\textcolor{blue}{C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}}
 \end{equation}
@@
 
-The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel.
-Where $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.
+\textcolor{blue}{The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel.
+$G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.}
 
@@
 %
-Three state-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
+Three \textcolor{blue}{state-of-the-art} verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
 

### 2020-06-24 Tex/CAV2019/replyVSTTEJUNE2020.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{resposta}
-Thank you for the advice. We removed all the commas.
-
+Implemented as suggested.
 \end{resposta}
@@
 - Page 2: specialist PV optimization software -$>$ specialized PV optimization software
-done
 
 \begin{resposta}
-Thank you, we corrected the text as suggested.
+We have fixed this typo.
 \end{resposta}
@@
 \begin{resposta}
-Thank you, you were right. The whole sentence was rebuild, with correct mention and explanation about the elements.
+We have updated the entire paragraph to explain the meaning of these variables as follows: ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.
+(9) for the ambient short-circuit current from the PV panel.
+$G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.''
 \end{resposta}

### 2020-07-02 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

@@
 \begin{abstract}
-The use of power generation with renewable energy sources is proliferating due to industrial development.
-Photovoltaic (PV) panels have emerged as an alternative to the fossil or nuclear fuel energy generation.
+\textcolor{blue}{In the current scenario, energy demand rises by 1.3\% each year to 2040, and photovoltaic (PV) systems} have emerged as an alternative to the fossil or nuclear fuel energy generation.
 The use of formal methods for PV systems is a new subject with significant research spanning only the last five years.
-Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing PV systems.
-We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is not feasible.
+Here we develop and evaluate \textcolor{blue}{an} automated synthesis approach to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model and the optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house}.
+%We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is not feasible. 
 We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis.
-We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market.
+We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market.
 Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness.
-We also compare our CEGIS approach with a commercial tool specialized in PV systems optimization.
+We also compare our approach with a commercial tool specialized in PV systems optimization.
 Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness.
@@
 
-In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
-However, these tools are based on simulation; \textcolor{blue}{they have the drawback of incomplete coverage} since verification of all possible combinations, and potential failures of a system are \textcolor{blue}{not feasible}~\cite{ClarkeHV18}.
-Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
-However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with \textcolor{blue}{specialized PV optimization software}.
+In order to evaluate \textcolor{blue}{or to obtain the optimal sizing of} a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
+However, these tools are based on simulation; \textcolor{blue}{they have the drawback of incomplete coverage of design-space} since verification of all possible combinations, and potential failures of a system are \textcolor{blue}{not feasible}~\cite{ClarkeHV18}.
+
+%Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
+
+However, the industry demands the \textcolor{blue}{design solution to be the optimum, considering equipment manufacturers, and models available on the market and not just minimum or maximum values of current or power for the optimized items.
+It is necessary to evaluate the electrical compatibility among the equipment as well.
+This can only be achieved with specialized PV optimization software.
+The optimal solution, therefore, is the lowest cost from a list of equipment that meets the electrical demands from a house.
+It is based on Life Cycle Cost (LCC) analysis, where the acquisition and replacement cost are considered over a specific period of time in years.}
 
 Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}.
-In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-\textcolor{blue}{In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid (e.g.,~\cite{Abate2017})}.
-In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
-\textcolor{blue}{However, \textit{formal methods and its application to synthesize PV systems are not explored in literature}}.
+\textcolor{blue}{Related to the use of automated verification or synthesis to electrical systems we can mention:} in $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}; \textcolor{blue}{in $2017$, it was suggested the application of formal methods to verify and control the behaviour of devices in a smart grid (e.g.,~\cite{Abate2017})}; in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}; and in $2019$, an automated verification methodology was proposed to validate \textcolor{blue}{the sizing of} stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
+\textcolor{blue}{However, \textit{formal methods and its application to synthesize PV systems are not explored in literature, mainly because it is necessary background and experience, at the same time, in computer science and PV systems, what is not so common}}.
 
-Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} technique for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
+Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} technique for synthesizing optimal sizing of stand-alone PV systems.
 Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
@@
 %-----------------------------------------------------------
-\section{Preliminaries}
+\section{Background}
 \label{sec:AutomatedVerification}
@@
 Where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
-A factor of $20$\% for losses is considered, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
+\textcolor{blue}{An empirical factor of $20$\% for losses is considered~\cite{Pinho}}, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
 
@@
 $DOD$ is the depth of discharge or the fraction of discharge.
-The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
+The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries \textcolor{blue}{and represent an intrinsic and empirical feature of those type of batteries~\cite{Pinho} in order to guarantee its lifetime}; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
 However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours).
@@
 This study will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}.
-Based on the fact that the deployment location is not specified, our study will use an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}, given as,
+\textcolor{blue}{Our study will use an adapted Life Cycle Cost (LCC) analysis, where the acquisition cost of every item of equipment is considered, plus the installation cost, the operational and maintenance costs}~\cite{Alsadi2018}, given as,
 %
@@
 \noindent Where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current prices.
+\textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according with Amazon State literature data\cite{Agrener2013}.}
+
 Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using software model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
-The analytical method of optimization was adopted, with LCC economic analysis and power reliability based on critical period criteria (worst month's method).
-%
+The analytical method of optimization was adopted.
+
  \begin{algorithm}[h]
@@
 
+xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx We must realize as well, and we added a highlight about this in the Results section, that a optimal solution from a tool is not necessarily the same optimal of other tool, mainly when the data base of equipment items (with different costs) are not the same.
+
 %---------------------------------------------------------------------------
@@
 
+\textcolor{blue}{Now that we proved that our technique has a promising result for PV system sizing optimization, our focus will be the improvement with the search mechanism used in the phase 3 of our synthesis technique, in order to speed up the time to response.
+Using binary search or even solver that is specific to perform optimization with model checking as $\nu Z$.}
+
 %

### 2020-07-02 Tex/CAV2019/replyVSTTEJUNE2020.tex
VSTTE rebuttal

@@
 According to the reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text.
-The revision included the Abstract, Introduction, Methodology?????, and Results????
-sections.
+The revision included the Abstract, Introduction, Background, Synthesizing Optimal Sizing, Results, and Conclusions sections.
 
@@
 Rather, I would suggest to provide a much more high-level background on PV systems, and simply state that such a system can be modelled using a set of equations, possibly giving the (main) variables.
-Similarly, many of the PV-specific details in the evaluation are not accesible for a general verification audience, and need to be discussed at a higher level.
+Similarly, many of the PV-specific details in the evaluation are not accessible for a general verification audience, and need to be discussed at a higher level.
 
 \begin{resposta} 
-Alessandro: acho que o revisor tem razão.
-Creio que valeria a pena tratar a parte da modelagem e fenômenos da geração de energia a um nível mais alto.
-Vou trabalhar isso mas sem remover toda a modelagem.
+We thank the reviewer for this insightful comment and suggestion.
+Indeed, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
+The paper was reviewed and the PV sizing modelling was changed to a more higher level of explanation.
+Different parts of the above mentioned sections in blue indicate where we changed/reviewed the text.
 
@@
 \begin{resposta} 
-Alessandro: realmente a definição de optimal sizing não é colocada logo de início.
-Realmente a definição só vem na página 8, não tem na Introdução.
-Vou melhorar a parte introdutória e onde explica o comparativo da solução ótima.
-No comparativo, o ótimo de uma ferramenta é apenas o ótimo da ferramenta, não necessariamente o ótimo do comparativo com outras ferramentas.
-Vou deixar isso claro lá também na parte de avaliação perto do quadro comparativo.
+We thank the reviewer again.
+Indeed, we had to revise the Abstract, the Introduction, and the Synthesizing Optimal Sizing sections in order to address more correctly what is PV optimal sizing.
+We must realize as well, and we added a highlight about this in the Results section, that a optimal solution from a tool is not necessarily the same optimal of other tool, mainly when the data base of equipment items (with different costs) are not the same.
 
@@
 \begin{resposta} 
+We thank the reviewer again for this insightful comment and suggestion. Indeed, we had to revise every section of the paper in order to address the specific issues highlighted by the reviewer......
 Alessandro: Pra mim, é o desenvolvimento de uma técnica (como já discutimos em janeiro), que usa model checking e, como é feita em duas etapas, ela lembra o modo como o CEGIS funciona.
@@
 
-Algorithm 1 to me seems to construct a contraint and then tries to solve it for the nondeterministic variables to obtain a solution, and to use essentially a linear search to find the minimum cost.
+Algorithm 1 to me seems to construct a constraint and then tries to solve it for the nondeterministic variables to obtain a solution, and to use essentially a linear search to find the minimum cost.
 Is this correct?
@@
 Nao poderia aplicar uma busca binaria como fizemos no nosso journal do IJES?}
+acrescentei busca binária e $\nu Z$ na conclusão.
 
@@
 
-Finally, section 2.2 presents nonlinear continuous real-valued constraints.How can the discrete solvers used handle these constraints?
+Finally, section 2.2 presents nonlinear continuous real-valued constraints. How can the discrete solvers used handle these constraints?
 
@@
 This paper presents a novel approach based on formal methods in order to obtain the optimal size of solar photovoltaic systems.
-The paper first introduces the basic formalization of such systems (in Section 2), then it discusses how these were modeled by means of formal methods (Section 3), and it then presents and discusses the experimental results (Section 4) comparing it with a commercial tool performing the same tasks using a different approach (HOMER).
+The paper first introduces the basic formalization of such systems (in Section 2), then it discusses how these were modelled by means of formal methods (Section 3), and it then presents and discusses the experimental results (Section 4) comparing it with a commercial tool performing the same tasks using a different approach (HOMER).
 
@@
 \begin{resposta} 
-Thank you.
+Thank you. We appreciate the compliment.
 \end{resposta}
@@
 \begin{resposta} 
-Mesmo do revisor 1. Mudanças que farei endereçarão isso
+We thank the reviewer for this insightful comment and suggestion.
+He/she is right and it was the same observation did by Reviewer \#1.
+In order to correct this issue, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
+The paper was reviewed and the PV sizing modelling was passed to a more higher level of explanation.
+Different parts of the paper in blue indicate where we changed/reviewed the text.
 
@@
 \begin{resposta}
-Concordo. Vou fazer isso no texto
+We appreciate this Reviewer's suggestion.
+Indeed only with a double background and experience, specifically in computer science and in electrical engineering, is that is possible to realize that the tool (formal synthesis) can solve, and with remarkable results, the PV system sizing issue.
+Therefore we included a specific text in the Introduction section:
+"However, formal methods and its application to synthesize PV systems are not explored in literature, mainly because it is necessary background and experience, at the same time, in computer science and PV systems, what is not so common."
 \end{resposta}
@@
 \begin{resposta}
-Concordo. Vou acrescer isso no texto
+The reviewer is right, we missed the details about why those values are taken.
+Therefore we reviewed the text to: "The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime".
 \end{resposta}

### 2020-07-05 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

@@
 The sizing check stage can ensure that the system meets the standard project steps related to the critical period method (worst month) for solar energy system sizing~\cite{Pinho} and adopting an MPPT (Maximum Power Point Tracking) charge controller, which is the most common in use.
-Firstly, we need to correct the daily energy consumption estimated for the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho}.
 
-\begin{equation}
-\label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \times \eta_{c} \times \eta_{i} }
-\end{equation}
+\textcolor{blue}{In this paper, which audience is targeted to be from software verification area, we decided to use a higher level explanation about the PV sizing.
+The sizing process involve a set of 18 equations, related to electrical engineering area, which are detailed in <GoogleDrive here>.
+The flowchart pictured in Fig.~\ref{fig:flow}  is the overview of the steps that must be taken in order to size a stand-alone PV system}
 
-We must estimate the total power that will be demanded from the PV panels, as defined by Eq.
-~\eqref{eq:Pminpanel}.
-Where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
-\textcolor{blue}{An empirical factor of $20$\% for losses is considered~\cite{Pinho}}, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
+\begin{figure}[h]
+\fbox{\includegraphics[width=0.8\textwidth]{flowchart2}}
+\centering
+\caption{High level description of stand-alone PV system sizing process.}
+\label{fig:flow} 
+\end{figure}
 
-\begin{equation}
-\label{eq:Pminpanel}
-P_{min,panels} = \dfrac{1.25 \times E_{corrected}}{Insolation}
-\end{equation}
+\textcolor{blue}{On the left side of Fig.~\ref{fig:flow} it is possible to visualize the inputs need to size a PV system.
+There are requirements from the house to be electrified, there are design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}.
+Related to the equipment list, the designer can use few equipment or a vast one.
+It is possible, as well, do not adopt commercial equipment list.
+However, the result is a PV sizing of specific power/current/ or voltage values, and usually just close of real equipment that can be found in the market.
+That possibility has the drawback of possible incompatibility among equipment when the real one are bought and deployed.}
 
-On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
-On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as described by Eqs.~\eqref{eq:Icmin} and \eqref{eq:Vcmin}.
+\textcolor{blue}{There are specific steps that aim the calculation of some variables and other related to the electrical compatibility validation among equipment items.
+Those represent different shades of gray of the  rectangle boxes.
+The start point usually is a candidate list of PV panels, change controller, battery, and inverter, as indicated at the top of Fig.~\ref{fig:flow}.
+The arrows, in the right side, it shows a point where some specific item is validated.
+The flowchart do not shows the returning point, but if the candidate item is not compatible with other, or do not meet some calculated requirement, it must be changed to other in order to follow the indicated flux.
+At the end of the flow, all the items are defined and the sizing is finished.}
 
-\begin{subequations}
- \begin{tabularx}{\textwidth}{Xp{1cm}X}
-\begin{equation}
-\label{eq:Icmin}
-I_{c} \geq I_{total,PVpanels}
-\end{equation}
- & &
-\begin{equation}
-\label{eq:Vcmin}
-V_{c} \geq V_{total,PVpanels}
-\end{equation}
-\end{tabularx}
-\end{subequations}
-
-Concerning the batteries, the energy $E_{b}$ to be demanded by the PV system, in order to meet the load requirements, is defined by Eq.~\eqref{eq:Ebat}.
-
-\begin{equation}
-\label{eq:Ebat}
-E_{b} = \dfrac{Autonomy \times E_{corrected}}{DOD}
-\end{equation}
-
-\noindent Where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days.
-$DOD$ is the depth of discharge or the fraction of discharge.
-The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries \textcolor{blue}{and represent an intrinsic and empirical feature of those type of batteries~\cite{Pinho} in order to guarantee its lifetime}; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
-However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours).
-\textcolor{blue}{Therefore, the definition given here is for a maximum of $DOD$}.
-When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
-
-In order to define the $DOD_{day}$, we use Eq.~\eqref{eq:DODday}.
-Moreover, the minimum current from the DC bus is defined by Eq.~\eqref{eq:Idcbus}.
-This equation is important to define the battery arrangement of the system (series and parallel connections).
-Where $V_{system}$ is the DC voltage of the bus.
-
-\begin{subequations}
- \begin{tabularx}{\textwidth}{Xp{1cm}X}
-\begin{equation}
-\label{eq:DODday}
-DOD_{day} = \dfrac{E_{corrected} \times 100}{E_{b}}
-\end{equation}
- & &
-\begin{equation}
-\label{eq:Idcbus}
-I_{min,DCbus} = \dfrac{E_{b}}{V_{system}}
-\end{equation}
-\end{tabularx}
-\end{subequations}
-
-As for batteries, we must first define the total capacity of the battery bank, which can be described as shown in Eq.~\ref{eq:Cbank}.
-where $ E_{load} $ is the average energy consumed by the load corrected according to PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
-
-\begin{equation}
-\label{eq:Cbank}
-\textcolor{blue}{C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}}
-\end{equation}
-
-Eq.~\ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted in the project.
-
-\begin{equation}
-\label{eq:batcheck}
-\left( N_{BS} \times N_{BP} \right) \geq N_{B}total
-\end{equation}
-
-The charge controller must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem}.
-
-\begin{equation}
-\label{eq:vcvsystem}
-V_{c} = V_{system}
-\end{equation}
-
-\textcolor{blue}{The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel.
-$G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.}
-
-\begin{equation}
-\label{eq:iscamb}
-I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right] 
-\end{equation}
-
-The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin}. Where $N_{PP}$ is the number of parallel panels adopted.
-
-\begin{subequations}
- \begin{tabularx}{\textwidth}{Xp{1cm}X}
-\begin{equation}
-\label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP}
-\end{equation}
-& &
-\begin{equation}
-\label{eq:icicmin}
-I_{c} \geq I_{c,min}
-\end{equation}
-\end{tabularx}
-\end{subequations}
-
-The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Eq.~\eqref{eq:numberofcmin}.
-Besides, the final sizing check is performed by Eq.~\eqref{eq:numberofc}, which validates the number of controllers adopted.
-
-\begin{equation}
-\label{eq:numberofcmin}
-number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
-\end{equation}
-
-\begin{equation}
-\label{eq:numberofc}
-N_{controller} \geq number_{controllers}
-\end{equation}
-
-The inverter sizing check is performed through three equations.
-Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage.
-Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load, i.e., the outlet voltage.
-Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
-
-\begin{subequations}
- \begin{tabularx}{\textwidth}{Xp{1cm}X}
-\begin{equation}
-\label{eq:vindc} 
-V_{in}DC = V_{system}
-\end{equation}
-& &
-\begin{equation}
-\label{eq:voutac} 
-V_{out}AC = V_{AC}
-\end{equation}
-\end{tabularx}
-\end{subequations}
-
-\begin{equation}
-\label{eq:invcheck} 
-\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right]
-\end{equation}
-
-Some inverter models allow parallel operation of more than one unit, besides the integration to create bi- and three-phase circuits.
-It is advisable to use pure sine wave inverters for electronic loads sensitive to harmonic distortion waves.
-
-Besides that, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers.
-Furthermore, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side.
-Then the controller can be overcharged during this operation and burn.
-
-All the equations above model the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
+\textcolor{blue}{All the 18 equations used, model} the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
 The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.

### 2020-07-05 Tex/CAV2019/VSTTE_PV_sizing_Trindade_Cordeiro_2020.tex
VSTTE rebuttal

--- 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\documentclass[runningheads]{llncs}
-%
+\documentclass[12pt,a4paper]{article}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{algorithm,algorithmic}
 \usepackage{xcolor}
-\usepackage{graphicx}
-\usepackage{makecell}
-\usepackage{textcomp}
-%\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{hyperref}
-\usepackage{algorithm,algorithmic}
-\usepackage{wrapfig}
-\usepackage{mathtools}
-\usepackage{tabularx}
-\usepackage{etoolbox}
-
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-
-\renewcommand{\baselinestretch}{0.975}
+%\documentclass[runningheads]{llncs}
 
 \begin{document}
-%
-%\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems\thanks{Supported by Newton Fund (ref.
-261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}}
-\title{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref.
-261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{Alessandro Trindade\inst{1} \and Lucas Cordeiro\inst{2}} %\orcidID{0000-0001-8262-2919} \orcidID{0000-0002-6235-4272}
-%
-\authorrunning{A. Trindade and L. Cordeiro}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{Federal University of Amazonas, Brazil, \email{alessandrotrindade@ufam.edu.br} \and
-University of Manchester, UK, \email{lucas.cordeiro@manchester.ac.uk}}
-\maketitle       % typeset the header of the contribution
 
-\begin{abstract}
-The use of power generation with renewable energy sources is proliferating due to industrial development.
-Photovoltaic (PV) panels have emerged as an alternative to the fossil or nuclear fuel energy generation.
-The use of formal methods for PV systems is a new subject with significant research spanning only the last five years.
-Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing PV systems.
-We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is infeasible.
-We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis.
-We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market.
-Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness.
-We also compare our CEGIS approach with a commercial tool specialized in PV systems optimization.
-Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness.
-\keywords{Formal Synthesis \and Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
-\end{abstract}
+\begin{center}
+\textbf{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison} \\
+
+VSTTE 2020 - 12th Working Conference on Verified Software: Theories, Tools, and Experiments\\
+
+Alessandro Trindade and Lucas Cordeiro \\
+\end{center}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}.
-Progress has been made worldwide; in particular, in 2017, the number of people without electricity access fell below $1$ billion thresholds for the first time~\cite{IEAweo2018}.
-The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}.
-Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}.
-There exists a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.
-It follows that increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
-In order to provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the connections needed~\cite{Hussein2012}.
-
-In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
-However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations, and potential failures of a system are infeasible~\cite{ClarkeHV18}.
-Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
-However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialist PV optimization software.
-
-Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}.
-In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-In $2017$, a researcher suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}.
-In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
-In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
-However, \textit{formal methods and its application to synthesize PV systems are still unexplored in literature}.
-
-Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} technique for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data.
-Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
-In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
-The candidate solution is then verified via software model checking with a lower bound that serves as the minimum cost of reference.
-If the verification step does not produce a counterexample, then the lower bound is adjusted; otherwise, we have achieved an optimal PV sizing.
-
-Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing.
-First, the use of automated software verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}.
-Here the application of software verification to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools.
-Second, we evaluate our approach using different state-of-the-art software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.
-We compare that to HOMER Pro optimization, with the results being validated with accurate commercial design software called PVsyst.
-Lastly, we discuss the challenges of applying software verification to PV systems and reflect on lessons learned from this experience.
-
-\vspace{-2ex}
-
-%-----------------------------------------------------------
-\section{Preliminaries}
-\label{sec:AutomatedVerification}
-%-----------------------------------------------------------
-\vspace{-1ex}
-
-Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system using the traditional techniques (manual and simulation) and the proposed synthesis technique.
-Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions.
-For the automated synthesis, we also define the bound $k$ to restrict the design-space search.
-Here we start with a low bound $k$ and incrementally increase it to avoid time and memory constraints on our verification engine.
-Therefore, the proper choice of $k$ is essential to this method.
-
-\begin{figure}[h]
-\fbox{\includegraphics[width=0.9\textwidth]{optimalsizingprocess4}}
-\centering
-\caption{Comparison of optimal sizing methods.}
-\label{fig:optimization}
-\end{figure}
-
-Both techniques (traditional and automated synthesis) produce as output either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
-On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is mathematical reasoning about a model, presents a counterexample with the optimal solution stored in variables.
-Furthermore, the design-space coverage during the optimal sizing search is sound and complete when using synthesis.
-
-%-----------------------------------------------------------
-\subsection{Program Synthesis}
-\label{sec:ProgramSynthesis}
-%-----------------------------------------------------------
-The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
-In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as a starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
-As a result, a given candidate program $p$ is iteratively refined to match $\sigma$ more closely.
-Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture.
-
-\begin{figure}[h]
-\begin{center}
-\fbox{\includegraphics[width=0.75\textwidth]{fig2_rev2.jpg}}
-\end{center}
-%
-%\begin{wrapfigure}{r}{0.5\textwidth}
-%\begin{center}
-%	\includegraphics[width=0.5\columnwidth]{fig2_rev2.jpg}
-%\end{center}	
-	\caption{CEGIS in PV system sizing.}
-	\label{Counter-Example-Guided-Inductive-Synthesis}
-%\end{wrapfigure}
-\end{figure}
-
-The correctness specification $\sigma$ provided to our synthesizer is of the form $\exists \vec{F}.
-\forall \vec{x}.
-\sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers.
-The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part.
-Our specification includes house demand, energy, and battery autonomy; we also provide equipment specifications and prices from different manufacturers and models.
-
-In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated.
-Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution to the full synthesis formula, which is passed to {\sc Verify} to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$).
-If this is the case, then the algorithm terminates.
-
-One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times.
-However, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists.
-
-In our CEGIS variant, there exist four differences related to the traditional one: 
-(1) there exists no test vector and every candidate is generated in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
-(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
-(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; as a result,
-(4) there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase.
-In particular, a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sizing Stand-alone Solar PV Systems}
+\section{Sizing Stand-alone Solar PV Systems}
 \label{sec:sizing}
@@
 \label{eq:Ecorrected}
-E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \times \eta_{c} \times \eta_{i} }.
+E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \times \eta_{c} \times \eta_{i} }
 \end{equation}
 
-We must estimate the total power that will be demanded from the PV panels, as defined by Eq. ~\eqref{eq:Pminpanel}.
+We must estimate the total power that will be demanded from the PV panels, as defined by Eq.
+~\eqref{eq:Pminpanel}.
+Where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
+\textcolor{blue}{An empirical factor of $20$\% for losses is considered~\cite{Pinho}}, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
 
@@
 \label{eq:Pminpanel}
-P_{min,panels} = \dfrac{1.25 \times E_{corrected}}{Insolation},
+P_{min,panels} = \dfrac{1.25 \times E_{corrected}}{Insolation}
 \end{equation}
 
-\noindent where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
-A factor of $20$\% for losses is considered, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
+On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
+On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as described by Eqs.~\eqref{eq:Icmin} and \eqref{eq:Vcmin}.
 
-On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$.
-On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as described by Eqs.~\eqref{eq:Icmin} and
-\eqref{eq:Vcmin}.
-
-\begin{subequations}
- \begin{tabularx}{\textwidth}{Xp{1cm}X}
 \begin{equation}
 \label{eq:Icmin}
-I_{c} \geq I_{total,PVpanels},
+I_{c} \geq I_{total,PVpanels}
 \end{equation}
- & &
+
 \begin{equation}
 \label{eq:Vcmin}
-V_{c} \geq V_{total,PVpanels},
+V_{c} \geq V_{total,PVpanels}
 \end{equation}
-\end{tabularx}
-\end{subequations}
 
@@
 \label{eq:Ebat}
-E_{b} = \dfrac{Autonomy \times E_{corrected}}{DOD},
+E_{b} = \dfrac{Autonomy \times E_{corrected}}{DOD}
 \end{equation}
 
-\noindent where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days.
+\noindent Where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days.
 $DOD$ is the depth of discharge or the fraction of discharge.
-The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
+The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries \textcolor{blue}{and represent an intrinsic and empirical feature of those type of batteries~\cite{Pinho} in order to guarantee its lifetime}; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
 However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours).
-Therefore, here in this study, the definition given here is for a maximum of $DOD$.
+\textcolor{blue}{Therefore, the definition given here is for a maximum of $DOD$}.
 When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
@@
 This equation is important to define the battery arrangement of the system (series and parallel connections).
+Where $V_{system}$ is the DC voltage of the bus.
 
-\begin{subequations}
- \begin{tabularx}{\textwidth}{Xp{1cm}X}
 \begin{equation}
 \label{eq:DODday}
-DOD_{day} = \dfrac{E_{corrected} \times 100}{E_{b}},
+DOD_{day} = \dfrac{E_{corrected} \times 100}{E_{b}}
 \end{equation}
- & &
+
 \begin{equation}
 \label{eq:Idcbus}
-I_{min,DCbus} = \dfrac{E_{b}}{V_{system}},
+I_{min,DCbus} = \dfrac{E_{b}}{V_{system}}
 \end{equation}
-\end{tabularx}
-\end{subequations}
 
-\noindent where $V_{system}$ is the DC voltage of the bus.
-
-As for batteries, we must first define the total capacity of the battery bank, which can be described as
+As for batteries, we must first define the total capacity of the battery bank, which can be described as shown in Eq.~\ref{eq:Cbank}.
+where $ E_{load} $ is the average energy consumed by the load corrected according to PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
 
@@
 \label{eq:Cbank}
-C_{bank} = \dfrac{Autonomy E_{load}}{DOD \eta _{b} V_{system}},
+\textcolor{blue}{C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}}
 \end{equation}
 
-\noindent where $ E_{load} $ is the average energy consumed by the load corrected according to PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.
-%
 Eq.~\ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted in the project.
@@
 \label{eq:vcvsystem}
-V_{c} = V_{system}.
+V_{c} = V_{system}
 \end{equation}
 
-The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because field temperature is higher than nominal or laboratory temperature, and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb}.
+\textcolor{blue}{The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel.
+$G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.}
 
@@
 \label{eq:iscamb}
-I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
+I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right] 
 \end{equation}
 
-The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin}.
+The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin}. Where $N_{PP}$ is the number of parallel panels adopted.
 
-\begin{subequations}
- \begin{tabularx}{\textwidth}{Xp{1cm}X}
 \begin{equation}
 \label{eq:icmin}
-I_{c,min} = I_{sc,amb} \times N_{PP},
+I_{c,min} = I_{sc,amb} \times N_{PP}
 \end{equation}
-& &
+
 \begin{equation}
 \label{eq:icicmin}
-I_{c} \geq I_{c,min}.
+I_{c} \geq I_{c,min}
 \end{equation}
-\end{tabularx}
-\end{subequations}
 
@@
 
-\begin{subequations}
- \begin{tabularx}{\textwidth}{Xp{1cm}X}
 \begin{equation}
 \label{eq:vindc} 
-V_{in}DC = V_{system}.
+V_{in}DC = V_{system}
 \end{equation}
-& &
+
 \begin{equation}
 \label{eq:voutac} 
-V_{out}AC = V_{AC}.
+V_{out}AC = V_{AC}
 \end{equation}
-\end{tabularx}
-\end{subequations}
 
@@
 
-All the equations above model the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
-The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
-
-%------------------------------------------------------
-\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
-%------------------------------------------------------
-
-The optimal sizing of PV systems is made by the best compromise between two objectives: \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.
-This study will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}.
-Based on the fact that the deployment location is not specified, our study will use an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}, given as,
-%
-\begin{equation}
-\label{eq:LCC}
-LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
-\end{equation}
-
-\noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current prices.
-Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using software model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
-The analytical method of optimization was adopted, with LCC economic analysis and power reliability based on critical period criteria (worst month's method).
-%
- \begin{algorithm}[h]
- \caption{Synthesis algorithm}
- \begin{algorithmic}[1]
- \renewcommand{\algorithmicrequire}{\textbf{Input:}}
- \renewcommand{\algorithmicensure}{\textbf{Output:}}
- \REQUIRE weather data (temperature, solar irradiance); data from panels, controllers, batteries, and inverters; design requirements (load curve, peak demand, load surge power, energy consumption, battery autonomy, AC voltage); design assumptions (SOC, DOD, criteria and objectives for technical and cost analysis)
- \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
- \STATE Initialize variables \\
- \STATE Declare the maximum possible cost $MaxCost$ \\
- \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
- \FOR {$HintCost=MinCost$ to $MaxCost$} 
- 	\STATE Declare non-deterministic variables to select PV Panel, Controller, Battery, and Inverter from list \\
- 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
-	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
-	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{m,ref}))$ \\
-	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
-	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
- 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
-	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
-	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
- 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
-	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
-	\STATE non-deterministic variables hold feasible equipment and cost \\
-	\STATE $F_{obj} \leftarrow N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
-	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
- \ENDFOR
- \RETURN $(\,)$ 
- \end{algorithmic} 
- \label{alg:opt-algorithm}
- \end{algorithm}
-
-Our synthesis algorithm will synthesize constant values; 
-it starts with the input of the manufacturer's data and prices of PV panels, batteries, charge controllers, and inverters. Moreover, we define design (house) requirements and design assumptions. 
-%
-The \textit{for}-loop started in line $4$ controls the lowest cost of the PV solution.
-In particular, it starts with cost $MinCost$ and stops when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $18$.
-If that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value in line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
-
-Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (line $5$).
-This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.
-A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine to allow the choice of every item of PV sizing.
-Datasheet from each item was necessary to collect technical information.
-Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.
-
-Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $9$ to $15$).
-The directive \textit{assume} (lines $8$, $13$, $14$, and $15$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines.
-Line $5$ is specific to PV panels.
-Line $13$ is for the battery bank.
-Line $14$ is the charge controller voltage check.
-Line $15$ does the inverter check and ensures the power demand and the surge power of the inverter.
-Therefore, our synthesis algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$).
-This cost is the equivalent to Eq.~\eqref{eq:LCC}.
-
-If our algorithm does not find a feasible solution among the item of equipment that was provided for our {\sc Synthesize} phase, then the result is unsatisfiable (\textit{UNSAT}).
-In particular, the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution.
-%
-The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements.
-The challenge for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase.
-%
-Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
-
-%---------------------------------------------------------------------------
-\section{Results and Discussion}
-%---------------------------------------------------------------------------
-%---------------------------------------------------------------------------
-\subsection{Description of the Case Studies}
-%---------------------------------------------------------------------------
-
-The proposed synthesis approach was evaluated in seven stand-alone PV system case studies.
-These case studies were defined based on the usual electrical load found in riverside communities in the Amazonas State, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized to support a few lamps and a 12k BTUs air-conditioner solution.
-Here we report each case study as a 4-tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
-\textbf{1:} \{342; 342; 3,900; 48\}; \textbf{2:} \{814; 980; 4,880; 48\}; \textbf{3:} \{815; 980; 4,880; 12\}; \textbf{4:} \{253; 722; 3,600; 48\}; \textbf{5:} \{263; 732; 2,500; 48\}; \textbf{6:} \{322; 896; 4,300; 48\}; \textbf{7:} \{1,586; 2,900; 14,000; 48\}.
-This 4-tuple represents the Algorithm~\ref{alg:opt-algorithm} inputs.
-For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house.
-Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.
-%
-Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc file.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.
-
-%---------------------------------------------------------------------------
-\subsection{Optimization/Simulation Tools and Assumptions}
-%---------------------------------------------------------------------------
-Concerning the off-the-shelf optimization/simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis.
-Here we used HOMER Pro version $3.13.1$ as a state-of-the-art optimization tool for comparison purposes.
-In particular, HOMER Pro has the following characteristics:
-(a) it is available only for MS-Windows, its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
-(b) it has two optimization algorithms: one algorithm simulates all of the feasible system configurations defined by the search space, and additionally, a proprietary derivative-free algorithm to search for the least-costly system;
-(c) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
-(d) the optimization analysis defines a load curve and temperature according to data collected from online databases.
-However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach;
-(e) it does not have a charge controller.
-During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution;
-(f) it was assumed 95\% availability of the PV system.
-By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}.
-For an ordinary house electrical load, 95\% is considered acceptable;
-(g) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
-(h) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity).
-During run-time, HOMER decides the size in kW of each one based on feasibility and lower cost.
-
-In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$~\cite{PVsyst}, with plenty of commercial equipment in its data bank.
-We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements.
-PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation, and data analysis of solar PV systems.
-PVsyst contains design, sizing, 3D shading scene, simulation, grid, and off-grid features.
-It uses comprehensive irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}.
-However, it does not perform optimization; therefore, PVsyst needs the system sized to validate it.
-Furthermore, PVsyst does not have commercial inverter equipment and, as a result, does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds.
-PVsyst is a commerical software with $30$-day test possibility and runs only in MS-Windows OS.
-
-%---------------------------------------------------------------------------
-\subsection{Objectives and Setup}
-%---------------------------------------------------------------------------
-
-Our evaluation aims to answer three experimental goals: [EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?; [EG2] \textbf{(performance)} How do the software verifiers compare to each other for synthesizing PV systems?; and [EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?
-
-All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits.
-For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10.
-The ideal scenario would be to use the same hardware configuration for the experiments.
-However, we faced restrictions concerning the license for the HOMER Pro tool; besides, we did not have the autonomy to change the Linux VM machine installed in the servers of our university due to the internal policy.
-This has an impact on performance, which is less favourable to HOMER Pro.
-PVsyst used the same configuration as HOMER Pro.
-We perform the experiments with a predefined \textit{time out} of $660$ minutes.
-
-%The hardware platform was not the same because of the availability of the machines;
-
-%---------------------------------------------------------------------------
-\subsection{Results}
-%---------------------------------------------------------------------------
-
-The results are presented in Table~\ref{tab1}. 
-%
-\begin{table}
-\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
-\begin{scriptsize}
-\begin{tabular}{c|c|c|c|c}
-\hline
-\hline
-Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
-\hline
-\hline
-Specification & Result & Result & Result & Result \\
-\hline
-\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
-\hline
-\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
-\hline
-\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
-\hline
-\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
-\hline
-\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
-\hline
-\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
-\hline
-\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
-\hline
-\hline
-\end{tabular}
-\\Legend: OM = out of memory; TO = time out; IF = internal failure; E = energy;    NTP = total number of panels, NBtotal = total number of batteries, NPS = number of panels in series; NPP = number of panels in parallel, NBS = number of batteries in series; NBP = number of batteries in parallel; LCC = Life Cycle Cost.
-\end{scriptsize}
-\end{table}
-%
-The violation (SAT result) indicated all over the Table~\ref{tab1} 
-is the $assert$ of the line $18$ in Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
-Here, CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.
-
-CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $4$ to $9$ hours. 
-Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left side as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron Energy.
-The inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power.
-The variables NTP, NPS, NPP, NBS, NBP, and NBTotal, also presented in the counterexample, shows the number of panels and batteries and how they are connected.
-Case studies $2$, $3$, $6$, and $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $11$ hours.  
-%
-\begin{figure}[h]
-\fbox{\includegraphics[width=0.9\textwidth]{CPA_opt_c5.png}}
-\centering
-\caption{Counterexample generated by CPAchecker after validation of case $5$.}
-\label{fig:CPAoptc1}
-\end{figure}
-
-Here we used ESBMC in incremental mode with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours.
-ESBMC, with this configuration, was unable to obtain an optimal solution in cases $2$ and $7$.
-Case $2$ produced a \textit{time out}.
-Moreover, case $7$ resulted in a UNSAT result, i.e., ESBMC was unable to provide a feasible solution.
-However, this is not a bug, and it means that the available list of equipment can not produce a feasible solution that satisfies electrical compatibility or design requirements.
-This UNSAT situation was reached in less than one minute.
-These experimental results answer the \textit{EG2}.
-
-HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EG3}).
-Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year.
-
-Some HOMER Pro drawbacks were also noted.
-(1) System equipment does not include an explicit charge controller.
-HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement.
-However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing.
-(2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user.
-For example, it was started with a $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types.
-(3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
-
-The authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the State of Amazonas, Brazil, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, a total of $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison Between Formal Synthesis and HOMER Pro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If we compare the results of the formal synthesis with CPAchecker and ESBMC against those of HOMER Pro, we observed some distinct results in terms of the technical solution and cost (cf.
-Table~\ref{tab1}).
-Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
-%
-Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, producing a higher estimation from the automated synthesis technique.
-However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.
-
-On the one hand, concerning the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the ones produced by the simulation tool.
-The difference varied from $19$\% to $65$\%.
-On the other hand, concerning the battery bank, the results were smaller in terms of capacity for HOMER Pro.
-The difference was between $34$\% to $68$\%.
-The mathematical models are different and particular parameters can be tuned for each technique, and that can justify the difference, which was presented in all the case studies.
-
-Those discrepancies are not easy to address without some real systems validation.
-However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}.
-Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it.
-This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification).
-PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.
-
-\begin{table}
-\caption{Optimal sizing validation with PVsyst.}
-\label{tab2}
-\begin{scriptsize}
-\begin{tabular}{c|c|c|c|c}
-\hline
-\hline
-CS & \makecell{PVsyst\\(pre-sizing)}& \makecell{Field\\deployed\\validation}& \makecell{Formal synthesis\\sizing\\validation}& \makecell{HOMER Pro\\sizing\\validation}\\
-\hline
-\hline
-CS 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail.
-$<$ 95\%\\(91.06\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.16 $\times$\\Batteries oversized in 1.39 $\times$}\\
-\hline
-CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.6 $\times$\\Batteries oversized in 1.74 $\times$}\\
-\hline
-CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
-\hline
-CS 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)} & \makecell{No error found \\95.76\% of avail.} & \makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized in 2.24 $\times$\\Batteries oversized in 1.41 $\times$}\\
-\hline
-CS 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 1.93 $\times$\\Batteries oversized in 1.56 $\times$}\\
-\hline
-CS 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail.
-$<$ 95\%\\(85.65\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.42 $\times$\\Batteries oversized in 1.38 $\times$}\\
-\hline
-CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.9 $\times$\\Batteries oversized in 1.99 $\times$}\\
-\hline
-\hline
-\end{tabular}
-\\Legend: CS = case study; NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater as a design requirement).
-\end{scriptsize}
-\end{table}
-
-Each simulation with PVsyst took $4$ seconds.
-We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a 24 h minimum autonomy).
-Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there exists no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine.
-%(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).
-
-Overall, those comparisons among our approach, the optimization software, and the deployed systems, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EG1} and {EG3}.
-
-HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed.
-The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf.
-Moreover, our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro or PVsyst.
-This feature is a definite advantage of the formal synthesis method.
-
-HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis.
-The formal synthesis method, therefore, presents more reliable results than HOMER Pro.
-
-In summary, our synthesis tool can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
-In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage.
-In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising).
-Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results, mainly concerning PV panels.
-
-%---------------------------------------------------------------------------
-\subsection{Threats to validity} 
-%---------------------------------------------------------------------------
-
-We have reported a favorable assessment of the proposed method.
-Nevertheless, we have also identified four threats to the validity of our results that constitute future work.
-First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate.
-Second, improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis.
-Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
-Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory.
-We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
-
-%------------------------------------
-\section{Conclusions} 
-%------------------------------------
-
-Our novelty relies on a practical approach to pursue the optimal solution of PV systems using contemporary formal methods.
-The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising.
-Our synthesis tool can present a solution, which is far more detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool.
-In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach.
-These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by off-the-shelf optimization tools and the items of equipment for solar systems available on the market to achieve accuracy.
-
-It is worth mentioning that our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work.
-We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers.
-Lastly, the use of data from real deployed systems in Amazonas State (Brazil) and the validation through PVsyst was essential to validate the comparison.
-For future work, we will investigate the application of probabilistic programming within our research so that we can analyze the trade-off between performance and precision.
-
-%
-% ---- Bibliography ----
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
 \bibliographystyle{splncs04}
 \bibliography{trindadeThesis}
-%
+
 \end{document}
-%\subsection{Design and Simulation of Solar PV systems}
-%The design and validation of a PV system can be done by hand or with the aid of a software tool.
-In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
-%public domain and commercial software available for the PV market. 
-%According to \cite{Brooks}, t
-%%%%%%%%%%
-%
-%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
-%to complex financial analysis and project optimization.
-At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.

### 2020-07-05 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

@@
 The flowchart do not shows the returning point, but if the candidate item is not compatible with other, or do not meet some calculated requirement, it must be changed to other in order to follow the indicated flux.
-At the end of the flow, all the items are defined and the sizing is finished.}
+The last rectangle box check the inverter electrical compatibility with the DC-bus voltage, with the required AC voltage from outlet; moreover, the inverter specified power must be lower than the charge controller power in order to avoid it to burn by overcharge.
+At the end of the flowchart, all the items are defined and the sizing is finished.}
 

### 2020-07-05 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

--- 2020-07-05 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
@@
 \textcolor{blue}{In this paper, which audience is targeted to be from software verification area, we decided to use a higher level explanation about the PV sizing.
-The sizing process involve a set of 18 equations, related to electrical engineering area, which are detailed in <GoogleDrive here>.
-The flowchart pictured in Fig.~\ref{fig:flow}  is the overview of the steps that must be taken in order to size a stand-alone PV system}
+The sizing process involve a set of eighteen equations, related to electrical engineering area, which are detailed online\footnote{\url{https://drive.google.com/file/d/1C\_OEo06Or0TrcaysHtYQAP1awa9VNR-T/view?usp=sharing }}.
+The flowchart pictured in Fig.~\ref{fig:flow}  is the overview of the steps that must be taken in order to size a stand-alone PV system.}
 
 \begin{figure}[h]
-\fbox{\includegraphics[width=0.8\textwidth]{flowchart2}}
+\fbox{\includegraphics[width=0.9\textwidth]{flowchart}}
 \centering
-\caption{High level description of stand-alone PV system sizing process.}
+\caption{\textcolor{blue}{High level description of stand-alone PV system sizing process.}}
 \label{fig:flow} 
@@
 
-\textcolor{blue}{On the left side of Fig.~\ref{fig:flow} it is possible to visualize the inputs need to size a PV system.
+\textcolor{blue}{On the left side of Fig.~\ref{fig:flow} it is possible to visualize the \textbf{inputs} need to size a PV system.
 There are requirements from the house to be electrified, there are design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}.
@@
 
-\textcolor{blue}{There are specific steps that aim the calculation of some variables and other related to the electrical compatibility validation among equipment items.
+\textcolor{blue}{There are specific steps that aim the calculation of some variables and other related to the electrical compatibility validation among equipment items, both enumerated from \textbf{i} to \textbf{xiv} in Fig.~\ref{fig:flow}.
 Those represent different shades of gray of the  rectangle boxes.
-The start point usually is a candidate list of PV panels, change controller, battery, and inverter, as indicated at the top of Fig.~\ref{fig:flow}.
+The start point usually is a candidate list of PV panels, change controller, battery, and inverter, as indicated at the top of the flowchart.
 The arrows, in the right side, it shows a point where some specific item is validated.
 The flowchart do not shows the returning point, but if the candidate item is not compatible with other, or do not meet some calculated requirement, it must be changed to other in order to follow the indicated flux.
-At the end of the flow, all the items are defined and the sizing is finished.}
+The last rectangle box checks the inverter electrical compatibility with the DC-bus voltage, with the required AC voltage from outlet; moreover, the inverter specified power must be lower than the charge controller power in order to avoid it to burn by overcharge.
+At the end of the flowchart, all the items are defined and the PV sizing is finished.}
 
-\textcolor{blue}{All the 18 equations used, model} the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
+\textcolor{blue}{All the equations used, model} the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
 The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
+
+\textcolor{blue}{Our mathematical model uses floating point arithmetic.
+It is just an approximation of the real numbers.
+However, in this work, we are not concerned with calculating the rounding error, which is negligible when we consider the size of the physical quantities and the variables adopted~\cite{DBLP:journals/corr/abs-2004-12699}.}
 
@@
  	\STATE Declare non-deterministic variables to select PV Panel, Controller, Battery, and Inverter from list \\
- 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
-	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
-	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{m,ref}))$ \\
-	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
-	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
- 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
-	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
-	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
- 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
-	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
+ 	\STATE Calculate steps i and ii of Fig.~\ref{fig:flow} \\
+	\STATE Define PV panels arrangement: step iii of Fig.~\ref{fig:flow} \\
+	\STATE Calculate  step iv of Fig.~\ref{fig:flow} \\
+	\STATE Enforce electrical compatibility in step v of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
+	\STATE Calculate steps vi to viii of Fig.~\ref{fig:flow} \\
+	\STATE Define battery arrangement according step ix of Fig.~\ref{fig:flow} \\
+	\STATE Enforce electrical compatibility in step x of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
+	\STATE Correct variables to ambient temperature: step xi of Fig.~\ref{fig:flow} \\
+	\STATE Enforce electrical compatibility in step xii of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
+	\STATE Define number of charge controllers: step xiii of Fig.~\ref{fig:flow}\\
+	\STATE Enforce electrical compatibilities in step xiv of Fig.~\ref{fig:flow} with statement \textbf{assume} and define the inverter \\
 	\STATE non-deterministic variables hold feasible equipment and cost \\
@@
 
-Next, we use from Eq.~\eqref{eq:Ecorrected} to Eq.~\eqref{eq:icmin} to calculate the sizing variables (lines $9$ to $15$).
-The directive \textit{assume} (lines $8$, $13$, $14$, and $15$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines.
-Line $5$ is specific to PV panels.
-Line $13$ is for the battery bank.
-Line $14$ is the charge controller voltage check.
-Line $15$ does the inverter check and ensures the power demand and the surge power of the inverter.
-Therefore, our synthesis algorithm reaches line $16$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $17$).
-This cost is the equivalent to Eq.~\eqref{eq:LCC}.
+\textcolor{blue}{Next, we use a set of equations to calculate the sizing variables (lines $6$, $7$, $8$, $10$, $11$, $13$, $15$).
+The statements \textit{assume} (lines $9$, $12$, $14$, and $16$) ensures compatibility of the items chosen from the list of equipment: the {\sc Verify} phase uses only items (among all the possible ones) that satisfy the statements of those lines.
+Line $12$ is for the battery bank.
+Lines $9$ and $14$ are the charge controller voltage check.
+Line $16$ does the inverter check and ensures the power demand and the surge power of the inverter.
+Therefore, our synthesis algorithm reaches line $17$ with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (line $18$).
+This cost is the equivalent to Eq.~\eqref{eq:LCC}.}
 
@@
 
-In summary, our synthesis tool can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
+In summary, our synthesis technique can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
 In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage.
@@
 
-xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx We must realize as well, and we added a highlight about this in the Results section, that a optimal solution from a tool is not necessarily the same optimal of other tool, mainly when the data base of equipment items (with different costs) are not the same.
+\textcolor{blue}{Worth to mention that an optimal solution from a tool is not necessarily the same optimal from other tool, mainly when the data base of equipment items (with different costs) are not the same.
+Therefore the comparison must take this issue into account.}
 
@@
 Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison.
-For future work, we will investigate the application of probabilistic programming within our research for the trade-off between performance and precision.
-
-\textcolor{blue}{Now that we proved that our technique has a promising result for PV system sizing optimization, our focus will be the improvement with the search mechanism used in the phase 3 of our synthesis technique, in order to speed up the time to response.
-Using binary search or even solver that is specific to perform optimization with model checking as $\nu Z$.}
+For future work, %we will investigate the application of probabilistic programming within our research for the trade-off between performance and precision.
+\textcolor{blue}{now that we proved that our technique has a promising result for PV system sizing optimization, our focus will be the improvement with the search mechanism used in the {\sc Verify} phase of our synthesis technique, in order to speed up the time to response.
+Using binary search or even a solver that is specific to perform optimization with model checking as $\nu Z$.}
 

### 2020-07-05 Tex/CAV2019/VSTTE_PV_sizing_Trindade_Cordeiro_2020_unmarked.tex
VSTTE rebuttal

--- 2020-07-05 Tex/CAV2019/VSTTE_PV_sizing_Trindade_Cordeiro_2020.tex
@@
 \begin{center}
-\textbf{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison} \\
-
+\textbf{\LARGE Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison} \\
+\hfill \break
 VSTTE 2020 - 12th Working Conference on Verified Software: Theories, Tools, and Experiments\\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sizing Stand-alone Solar PV Systems}
+\section*{Sizing Stand-alone Solar PV Systems}
 \label{sec:sizing}
@@
 Where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed.
-\textcolor{blue}{An empirical factor of $20$\% for losses is considered~\cite{Pinho}}, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
+An empirical factor of $20$\% for losses is considered~\cite{Pinho}, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.
 
@@
 $DOD$ is the depth of discharge or the fraction of discharge.
-The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries \textcolor{blue}{and represent an intrinsic and empirical feature of those type of batteries~\cite{Pinho} in order to guarantee its lifetime}; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
+The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries~\cite{Pinho} in order to guarantee its lifetime; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$.
 However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours).
-\textcolor{blue}{Therefore, the definition given here is for a maximum of $DOD$}.
+Therefore, the definition given here is for a maximum of $DOD$.
 When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.
@@
 \label{eq:Cbank}
-\textcolor{blue}{C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}}
+C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}
 \end{equation}
@@
 
-\textcolor{blue}{The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel.
-$G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.}
+The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent (heat can reduce output efficiency by 10-25\%), as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel.
+$G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.
 

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \textcolor{blue}{In the current scenario, energy demand rises by 1.3\% each year to 2040, and photovoltaic (PV) systems} have emerged as an alternative to the fossil or nuclear fuel energy generation.
-The use of formal methods for PV systems is a new subject with significant research spanning only the last five years.
-Here we develop and evaluate \textcolor{blue}{an} automated synthesis approach to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model and the optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house}.
-%We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is not feasible. 
+The use of formal methods for PV systems is a new subject with significant research spanning only five years.
+Here we develop and evaluate \textcolor{blue}{an} automated synthesis approach to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model.
+The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house}.
 We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis.

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 It follows that increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.
-In order to provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the connections needed~\cite{Hussein2012}.
+To provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the connections needed~\cite{Hussein2012}.
 
-In order to evaluate \textcolor{blue}{or to obtain the optimal sizing of} a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
+To evaluate \textcolor{blue}{or to obtain the optimal sizing of} a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}.
 However, these tools are based on simulation; \textcolor{blue}{they have the drawback of incomplete coverage of design-space} since verification of all possible combinations, and potential failures of a system are \textcolor{blue}{not feasible}~\cite{ClarkeHV18}.
 
-%Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations.
-
-However, the industry demands the \textcolor{blue}{design solution to be the optimum, considering equipment manufacturers, and models available on the market and not just minimum or maximum values of current or power for the optimized items.
+However, the industry demands the \textcolor{blue}{design solution to be the optimum, considering equipment manufacturers and models available on the market and not just minimum or maximum values of current or power for the optimized items.
 It is necessary to evaluate the electrical compatibility among the equipment as well.
-This can only be achieved with specialized PV optimization software.
-The optimal solution, therefore, is the lowest cost from a list of equipment that meets the electrical demands from a house.
-It is based on Life Cycle Cost (LCC) analysis, where the acquisition and replacement cost are considered over a specific period of time in years.}
+This evaluation can only be achieved with specialized PV optimization software.
+Therefore, the optimal solution is the lowest cost from a list of equipment that meets the electrical demands of a house.
+It is based on Life Cycle Cost (LCC) analysis \textcolor{red}{add citation}, where the acquisition and replacement cost are considered over a specific period in years.}
 
 Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}.
-\textcolor{blue}{Related to the use of automated verification or synthesis to electrical systems we can mention:} in $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}; \textcolor{blue}{in $2017$, it was suggested the application of formal methods to verify and control the behaviour of devices in a smart grid (e.g.,~\cite{Abate2017})}; in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}; and in $2019$, an automated verification methodology was proposed to validate \textcolor{blue}{the sizing of} stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
-\textcolor{blue}{However, \textit{formal methods and its application to synthesize PV systems are not explored in literature, mainly because it is necessary background and experience, at the same time, in computer science and PV systems, what is not so common}}.
+\textcolor{blue}{Concerning the use of automated verification or synthesis to electrical systems, we can mention that} in $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
+\textcolor{blue}{In $2017$, it was suggested the application of formal methods to verify and control the behavior of devices in a smart grid (e.g.,~\cite{Abate2017})}.
+In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
+Lastly, in $2019$, an automated verification methodology was proposed to validate \textcolor{blue}{the sizing of} stand-alone solar PV systems~\cite{TrindadeCordeiro19}.
+\textcolor{blue}{However, \textit{formal methods and its application to synthesize PV systems are not explored in literature, mainly because it requires background and experience in computer science and PV systems, which is not common}}.
 
 Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} technique for synthesizing optimal sizing of stand-alone PV systems.
-Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
+If we provide a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
 In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
@@
 First, the use of automated software verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}.
-Here the application of software verification to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools.
+The application of software verification to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools.
 Second, we evaluate our approach using different state-of-the-art software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Therefore, the proper choice of $k$ is essential to this method.
-
+%
 \begin{figure}[h]
@@
 
-The techniques (manual, simulation and automated synthesis) produce as output either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
+The techniques (manual, simulation, and automated synthesis) produce either a SUCCESS or FAIL result, thereby considering a feasible technical solution with the lowest cost.
 On the one hand, when done by simulation, we get a report or graphical result; on the other hand, the automated synthesis technique, which is mathematical reasoning about a model, presents a counterexample with the optimal solution stored in variables.
@@
 %-----------------------------------------------------------
-The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$.
+The basic idea of program synthesis is to automatically construct a $ P $ program that satisfies a correctness specification $\sigma$.
 In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as a starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}.
@@
 Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture.
-
+%
 \begin{figure}[h]
@@
 \end{center}
-%
-%\begin{wrapfigure}{r}{0.5\textwidth}
-%\begin{center}
-%	\includegraphics[width=0.5\columnwidth]{fig2_rev2.jpg}
-%\end{center}	
 	\caption{CEGIS in PV system sizing.}
 	\label{Counter-Example-Guided-Inductive-Synthesis}
-%\end{wrapfigure}
 \end{figure}
@@
 One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis.
-Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times.
+Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, the refinement loop can only iterate over a finite number of times.
 However, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists.
@@
 In our CEGIS variant, there exist four differences related to the traditional one: 
-(1) there exists no test vector and every candidate is generated in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
+(1) there exists no test vector, and every candidate is generated in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
 (2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
@@
 A PV system is illustrated in Fig.\ref{fig:blockdiagram}.
-It employs the PV generator (\textit{panel or an array}), which is a semiconductor device that can convert solar energy into DC electricity.
+It employs the PV generator (\textit{panel or an array}), a semiconductor device that can convert solar energy into DC electricity.
 For night hours or rainy days, we hold \textit{batteries}, where power can be stored and used.
@@
 The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textit{inverter}).
-The \textit{AC load} dictates the behaviour of the AC electrical load from the house that will be fed by the system.
-
+The \textit{AC load} dictates the behavior of the AC electrical load from the house that will be fed by the system.
+%
 \begin{figure}[h]
@@
 
-The sizing check stage can ensure that the system meets the standard project steps related to the critical period method (worst month) for solar energy system sizing~\cite{Pinho} and adopting an MPPT (Maximum Power Point Tracking) charge controller, which is the most common in use.
+The sizing check stage can ensure that the system meets the standard project steps related to the critical period method (worst month) for solar energy system sizing~\cite{Pinho}.
+It adopts an MPPT (Maximum Power Point Tracking) charge controller, which is the most common in use.
 
-\textcolor{blue}{In this paper, which audience is targeted to be from software verification area, we decided to use a higher level explanation about the PV sizing.
-The sizing process involve a set of eighteen equations, related to electrical engineering area, which are detailed online\footnote{\url{https://drive.google.com/file/d/1C\_OEo06Or0TrcaysHtYQAP1awa9VNR-T/view?usp=sharing }}.
-The flowchart pictured in Fig.~\ref{fig:flow}  is the overview of the steps that must be taken in order to size a stand-alone PV system.}
-
+\textcolor{blue}{In this paper, which audience is targeted to be from the software verification area, we decided to use a higher-level explanation about the PV sizing.
+The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online \textcolor{red}{I was unable to open this file}\footnote{\url{https://drive.google.com/file/d/1C\_OEo06Or0TrcaysHtYQAP1awa9VNR-T/view?usp=sharing}}.
+The flowchart pictured in Fig.~\ref{fig:flow} is the overview of the steps that must be taken to size a stand-alone PV system.}
+%
 \begin{figure}[h]
@@
 
-\textcolor{blue}{On the left side of Fig.~\ref{fig:flow} it is possible to visualize the \textbf{inputs} need to size a PV system.
-There are requirements from the house to be electrified, there are design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}.
-Related to the equipment list, the designer can use few equipment or a vast one.
-It is possible, as well, do not adopt commercial equipment list.
-However, the result is a PV sizing of specific power/current/ or voltage values, and usually just close of real equipment that can be found in the market.
-That possibility has the drawback of possible incompatibility among equipment when the real one are bought and deployed.}
+\textcolor{blue}{On the left side of Fig.~\ref{fig:flow}, we can visualize the needed \textbf{inputs} to size a PV system.
+There exist requirements from the house to be electrified; in particular, there exist design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}.
+Related to the equipment list, the designer can use a few equipments or a vast one.
+We can also decide not to adopt the commercial equipment list.
+However, the result is a PV sizing of specific power, current, or voltage values, and usually just close to original equipment, which can be found in the market.
+This possibility has the drawback of possible incompatibility among equipment when the real one is bought and deployed.}
 
-\textcolor{blue}{There are specific steps that aim the calculation of some variables and other related to the electrical compatibility validation among equipment items, both enumerated from \textbf{i} to \textbf{xiv} in Fig.~\ref{fig:flow}.
-Those represent different shades of gray of the  rectangle boxes.
-The start point usually is a candidate list of PV panels, change controller, battery, and inverter, as indicated at the top of the flowchart.
-The arrows, in the right side, it shows a point where some specific item is validated.
-The flowchart do not shows the returning point, but if the candidate item is not compatible with other, or do not meet some calculated requirement, it must be changed to other in order to follow the indicated flux.
-The last rectangle box checks the inverter electrical compatibility with the DC-bus voltage, with the required AC voltage from outlet; moreover, the inverter specified power must be lower than the charge controller power in order to avoid it to burn by overcharge.
-At the end of the flowchart, all the items are defined and the PV sizing is finished.}
+\textcolor{blue}{There exist specific steps that aim the calculation of some variables and others related to the electrical compatibility validation among equipment items, both enumerated from \textbf{i} to \textbf{xiv}, as illustrated in Fig.~\ref{fig:flow}; those represent different shades of gray of the rectangle boxes.
+The start point is usually a candidate list of PV panels, charge controller, battery, and inverter, as indicated at the top of the flowchart.
+The arrows, on the right side, show a point where some specific item is validated.
+The diagram does not show the returning location.
+However, if the candidate item is not compatible with others or does not meet some requirement, it must be changed to follow the indicated flux.
+The last rectangle box checks the inverter electrical compatibility with the DC-bus voltage, with the required AC voltage from the outlet.
+Besides, the inverter specified power must be lower than the charge controller power to avoid it from burning by overcharge.
+At the end of the flowchart, all the items are defined, and the PV sizing is finished.}
 
-\textcolor{blue}{All the equations used, model} the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
+\textcolor{blue}{These equations model} the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation.
 The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
-
-\textcolor{blue}{Our mathematical model uses floating point arithmetic.
+\textcolor{blue}{Our mathematical model uses floating-point arithmetic.
 It is just an approximation of the real numbers.
-However, in this work, we are not concerned with calculating the rounding error, which is negligible when we consider the size of the physical quantities and the variables adopted~\cite{DBLP:journals/corr/abs-2004-12699}.}
+However, in this work, we are not concerned with calculating the rounding error, which is negligible when considering the size of the physical quantities and the variables adopted~\cite{DBLP:journals/corr/abs-2004-12699}.}
 

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised Section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The optimal sizing of PV systems is made by the best compromise between two objectives: \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.
+The best compromise between two objectives makes the optimal sizing of PV systems: \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.
 This study will rely on the critical period solar energy method~\cite{Pinho}, as described in Section~\ref{sec:sizing}.
@@
 
-\noindent Where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current prices.
-\textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according with Amazon State literature data\cite{Agrener2013}.}
+\noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current rates.
+\textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}.}
 
-Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using software model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
+Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using software model checking as a backend verification engine~\cite{DBLP:journals/corr/abs-1909-13139}.
 The analytical method of optimization was adopted.
@@
  	\STATE Declare non-deterministic variables to select PV Panel, Controller, Battery, and Inverter from list \\
- 	\STATE Calculate steps i and ii of Fig.~\ref{fig:flow} \\
-	\STATE Define PV panels arrangement: step iii of Fig.~\ref{fig:flow} \\
-	\STATE Calculate  step iv of Fig.~\ref{fig:flow} \\
-	\STATE Enforce electrical compatibility in step v of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
-	\STATE Calculate steps vi to viii of Fig.~\ref{fig:flow} \\
-	\STATE Define battery arrangement according step ix of Fig.~\ref{fig:flow} \\
-	\STATE Enforce electrical compatibility in step x of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
-	\STATE Correct variables to ambient temperature: step xi of Fig.~\ref{fig:flow} \\
-	\STATE Enforce electrical compatibility in step xii of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
-	\STATE Define number of charge controllers: step xiii of Fig.~\ref{fig:flow}\\
-	\STATE Enforce electrical compatibilities in step xiv of Fig.~\ref{fig:flow} with statement \textbf{assume} and define the inverter \\
-	\STATE non-deterministic variables hold feasible equipment and cost \\
+ 	\STATE Calculate Steps i and ii of Fig.~\ref{fig:flow} \\
+	\STATE Define PV panels arrangement: Step iii of Fig.~\ref{fig:flow} \\
+	\STATE Calculate Step iv of Fig.~\ref{fig:flow} \\
+	\STATE Enforce electrical compatibility in Step v of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
+	\STATE Calculate Steps vi to viii of Fig.~\ref{fig:flow} \\
+	\STATE Define battery arrangement according Step ix of Fig.~\ref{fig:flow} \\
+	\STATE Enforce electrical compatibility in Step x of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
+	\STATE Correct variables to ambient temperature: Step xi of Fig.~\ref{fig:flow} \\
+	\STATE Enforce electrical compatibility in Step xii of Fig.~\ref{fig:flow} with statement \textbf{assume} \\
+	\STATE Define number of charge controllers: Step xiii of Fig.~\ref{fig:flow}\\
+	\STATE Enforce electrical compatibilities in Step xiv of Fig.~\ref{fig:flow} with statement \textbf{assume} and define the inverter \\
+	\STATE Non-deterministic variables hold feasible equipment and cost \\
 	\STATE $F_{obj} \leftarrow N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
@@
 The \textit{for}-loop started in line $4$ controls the lowest cost of the PV solution.
-In particular, it starts with cost $MinCost$ and stops when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $18$.
-If that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
-The $MaxCost$ value in line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that: (1) it will never be reached because the optimal solution will be found first (SAT result); or (2) it will be reached when the search engine did not find a feasible solution for the optimization (UNSAT result).
+In particular, it begins with a value $MinCost$ and stops when the algorithm finds a feasible solution in which the value breaks the $assertion$ stated in line $18$.
+If that happens, then our algorithm has found an optimal solution, thereby indicating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).
+The $MaxCost$ value in line $2$ is just a very high value inserted as a limit to the \textit{for}-loop, that meets one of the following requirements.
+(1) It will never be reached because the optimal solution will be found first (SAT result); or (2) it will be achieved when the search engine did not find a feasible solution for the optimization (UNSAT result).
 
@@
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-All this data is available online\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.
+All this data is available online \textcolor{red}{I was unable to open this file}\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.
 
@@
 The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements.
-The challenge for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase.
+The problem for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase.
 %
 Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
-The Algorithm~\ref{alg:opt-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verify ($C \wedge \neg P$), as shown online\footnote{\url{https://drive.google.com/file/d/1Q_hlgUt6AWrNeOtxhFlIpW4P4OPrPyIA/view?usp=sharing}}.
+The verification engines transform the Algorithm~\ref{alg:opt-algorithm} into the Boolean expressions that are passed to the solver to verify ($C \wedge \neg P$), as described online\footnote{\url{https://drive.google.com/file/d/1Q_hlgUt6AWrNeOtxhFlIpW4P4OPrPyIA/view?usp=sharing}}.
 

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 For an ordinary house electrical load, 95\% is considered acceptable;
-(g) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
+(g) it was assumed a string of two batteries to match the voltage of the $24$ V DC system, which was used for our automated synthesis tool; 
 (h) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity).
@@
 
-In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$~\cite{PVsyst}, with plenty of commercial equipment in its data bank.
+To validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a simulation tool, called PVsyst version $6.86$~\cite{PVsyst}, with plenty of commercial equipment in its data bank.
 We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements.
-PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation, and data analysis of solar PV systems.
+PVsyst is a PC software package developed by a Swiss company used for the study, sizing, simulation and data analysis of solar PV systems.
 PVsyst contains design, sizing, 3D shading scene, simulation, grid, and off-grid features.
-It uses comprehensive irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}.
+It uses comprehensive irradiation data from Meteonorm,\footnote{https://meteonorm.com/en/} and aging analysis~\cite{PVsyst2017}.
 However, it does not perform optimization; therefore, PVsyst needs the system sized to validate it.
 Furthermore, PVsyst does not have commercial inverter equipment and, as a result, does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds.
-PVsyst is a commerical software with $30$-day test possibility and runs only in MS-Windows.
+PVsyst is commercial software with a $30$-day test possibility and runs only in MS-Windows.
 
@@
 The ideal scenario would be to use the same hardware configuration for the experiments.
-However, we faced restrictions concerning the license for the HOMER Pro tool; besides, we did not have the autonomy to change the Linux VM machine installed in the servers of our university due to the internal policy.
-This has an impact on performance, which is less favourable to HOMER Pro.
+However, we faced restrictions concerning the license for the HOMER Pro tool; besides, we did not have the autonomy to change the Linux VM machine installed in our university's servers due to the internal policy.
+This setup has an impact on performance, which is less favorable to HOMER Pro.
 PVsyst used the same configuration as HOMER Pro.
 We perform the experiments with a predefined \textit{time out} of $660$ minutes.
-
-%The hardware platform was not the same because of the availability of the machines;
 
@@
 %
-The violation (SAT result) indicated all over the Table~\ref{tab1} 
-is the $assert$ of the line $18$ in Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.
-Here, CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.
+The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of the line $18$ in Algorithm~\ref{alg:opt-algorithm} and suggests that an optimal solution was found.
+Here, CBMC was unable to produce any conclusive result; \textit{out of memory} situations occurred in all case studies.
 
@@
 
-Here we used ESBMC in incremental mode with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours.
+Here we used ESBMC in BMC incremental mode with Boolector; ESBMC was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response, varying from $36$ minutes to $10$ hours.
 ESBMC, with this configuration, was unable to obtain an optimal solution in cases $2$ and $7$.
@@
 (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user.
-For example, it was started with a $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types.
+For example, it was started with an $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types.
 (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-If we compare the results of the formal synthesis against those of HOMER Pro, we observed some distinct results in terms of the technical solution and cost (cf.
+
+If we compare the formal synthesis results against those of HOMER Pro, we observed some distinct effects in terms of the technical solution and cost (cf.
 Table~\ref{tab1}).
 Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $4$ hours for the automated synthesis technique.
-%
 Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, producing a higher estimation from the automated synthesis technique.
@@
 The difference varied from $19$\% to $65$\%.
-On the other hand, concerning the battery bank, the results were smaller in terms of capacity for HOMER Pro.
+On the other hand, concerning the battery bank, the results were smaller in terms of HOMER Pro capacity.
 The difference was between $34$\% to $68$\%.
@@
 PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.
-
+%
 \begin{table}
@@
 We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum).
-Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there exists no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine.
+Case studies $2$ and $7$ had only HOMER Pro sizing validation.
+There is no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine.
 %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).
 
-Overall, those comparisons among our approach, the optimization software, and the deployed systems, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EG1} and {EG3}.
+Overall, those comparisons with our approach, the optimization software, and the deployed systems, with validation through simulation tool, show that the synthesis solution is sound and complete, which answers \textit{EG1} and {EG3}.
 
-HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not a commercial value.
+HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not commercial.
 The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf.
-Moreover, our synthesis approach considers surge power demand from the house, which is not considered by HOMER Pro or PVsyst.
+Moreover, our synthesis approach considers surge power demand from the house, which is not viewed by HOMER Pro or PVsyst.
 This feature is a definite advantage of the formal synthesis method.
@@
 
-In summary, our synthesis technique can present a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro.
-In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage.
+In summary, our synthesis technique can present a solution that is far more detailed and closer to commercial conditions than the answer given by HOMER Pro.
+In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical information from the manufacturer datasheet, including the model of the component, nominal current, and voltage.
 In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1}, it was removed to avoid unauthorized advertising).
@@
 
-\textcolor{blue}{Worth to mention that an optimal solution from a tool is not necessarily the same optimal from other tool, mainly when the data base of equipment items (with different costs) are not the same.
-Therefore the comparison must take this issue into account.}
+\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same.
+Therefore, the comparison must take this issue into account.}
 
@@
 %---------------------------------------------------------------------------
+
 We have reported a favorable assessment of the proposed method.
 Nevertheless, we have also identified four threats to the validity of our results that constitute future work.
-First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate.
-Second, improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis.
+First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the study more accurate.
+Second, improvement of the system cost analysis by adding operational and maintenance costs to the adopted LCC analysis.
 Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.
@@
 We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
+
 %------------------------------------

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %------------------------------------
-Our novelty relies on a practical approach to pursue the optimal solution of PV systems using contemporary formal methods.
-The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising.
-Our synthesis tool can present a solution, which is far more detailed and closer to the commercial reality than the solution presented by the commercial tool.
+
+Our novelty relies on a practical approach to pursue the optimal PV systems' optimal solution using contemporary formal methods.
+The use of formal synthesis to design PV systems has no precedent in literature; we show that our approach results, using seven case studies, are promising.
+Our synthesis tool can present a solution that is far more detailed and closer to commercial reality than the solution given by the commercial tool.
 In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach.
-These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.
-It is worth mentioning that our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work.
+These technical details are essential for the PV system owner since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.
+
+Our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work.
 We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers.
 Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison.
-For future work, %we will investigate the application of probabilistic programming within our research for the trade-off between performance and precision.
-\textcolor{blue}{now that we proved that our technique has a promising result for PV system sizing optimization, our focus will be the improvement with the search mechanism used in the {\sc Verify} phase of our synthesis technique, in order to speed up the time to response.
-Using binary search or even a solver that is specific to perform optimization with model checking as $\nu Z$.}
+\textcolor{blue}{Now that we proved that our technique has a promising result for PV system sizing optimization, our focus for future work will be the improvement with the search mechanism used in the {\sc Verify} phase of our synthesis technique, to speed up the time to respond.
+Our plan is to use binary search or even a solver that is specific to perform optimization with model checking as $\nu Z$~\cite{BjornerPF15}.}
 

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

@@
 Therefore, the optimal solution is the lowest cost from a list of equipment that meets the electrical demands of a house.
-It is based on Life Cycle Cost (LCC) analysis \textcolor{red}{add citation}, where the acquisition and replacement cost are considered over a specific period in years.}
+It is based on Life Cycle Cost (LCC) analysis~\cite{Alsadi2018}, where the acquisition and replacement cost are considered over a specific period in years.}
 
@@
 \textcolor{blue}{In this paper, which audience is targeted to be from the software verification area, we decided to use a higher-level explanation about the PV sizing.
-The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online \textcolor{red}{I was unable to open this file}\footnote{\url{https://drive.google.com/file/d/1C\_OEo06Or0TrcaysHtYQAP1awa9VNR-T/view?usp=sharing}}.
+The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online \textcolor{red}{I was unable to open this file}\footnote{\url{https://tinyurl.com/yck7dfxt}}.
 The flowchart pictured in Fig.~\ref{fig:flow} is the overview of the steps that must be taken to size a stand-alone PV system.}
@@
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-All this data is available online \textcolor{red}{I was unable to open this file}\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.
+All this data is available online \textcolor{red}{I was unable to open this file}\footnote{\url{https://tinyurl.com/ycgbsgkp}}.
 
@@
 Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
-The verification engines transform the Algorithm~\ref{alg:opt-algorithm} into the Boolean expressions that are passed to the solver to verify ($C \wedge \neg P$), as described online\footnote{\url{https://drive.google.com/file/d/1Q_hlgUt6AWrNeOtxhFlIpW4P4OPrPyIA/view?usp=sharing}}.
+The verification engines transform the Algorithm~\ref{alg:opt-algorithm} into the Boolean expressions that are passed to the solver to verify ($C \wedge \neg P$), as described online\footnote{\url{https://tinyurl.com/yajfmavl}}.
 

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
Revised changes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.975}
+\renewcommand{\baselinestretch}{0.99}
 
@@
 \textcolor{blue}{In this paper, which audience is targeted to be from the software verification area, we decided to use a higher-level explanation about the PV sizing.
-The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online \textcolor{red}{I was unable to open this file}\footnote{\url{https://tinyurl.com/yck7dfxt}}.
-The flowchart pictured in Fig.~\ref{fig:flow} is the overview of the steps that must be taken to size a stand-alone PV system.}
+The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online.\footnote{\url{https://tinyurl.com/yck7dfxt}} The flowchart pictured in Fig.~\ref{fig:flow} is the overview of the steps that must be taken to size a stand-alone PV system.}
 %
@@
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-All this data is available online \textcolor{red}{I was unable to open this file}\footnote{\url{https://tinyurl.com/ycgbsgkp}}.
+All this data is available online.
+\footnote{\url{https://tinyurl.com/ycgbsgkp}}
 

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
Revised changes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.
-All this data is available online.
-\footnote{\url{https://tinyurl.com/ycgbsgkp}}
+All this data is available online.\footnote{\url{https://tinyurl.com/ycgbsgkp}}
 
@@
 Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
-The verification engines transform the Algorithm~\ref{alg:opt-algorithm} into the Boolean expressions that are passed to the solver to verify ($C \wedge \neg P$), as described online\footnote{\url{https://tinyurl.com/yajfmavl}}.
+The verification engines transform the Algorithm~\ref{alg:opt-algorithm} into the Boolean expressions that are passed to the solver to verify ($C \wedge \neg P$), as described online.\footnote{\url{https://tinyurl.com/yajfmavl}}
 

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

@@
 The use of formal methods for PV systems is a new subject with significant research spanning only five years.
-Here we develop and evaluate \textcolor{blue}{an} automated synthesis approach to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model.
-The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house}.
-We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis.
-We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market.
+Here we develop and evaluate \textcolor{blue}{an} automated synthesis technique to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis.
+The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement costs and the operation \& maintenance costs over a 20-year period.
+We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the optimization}.
+We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market \textcolor{blue}{for PV systems}.
 Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness.
@@
 
-Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using software model checking as a backend verification engine~\cite{DBLP:journals/corr/abs-1909-13139}.
+Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems.
+It uses  software model checking as a backend verification engine~\cite{DBLP:journals/corr/abs-1909-13139}.
 The analytical method of optimization was adopted.
@@
 (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
+\textcolor{blue}{The cost of every equipment item used in HOMER Pro is an US-based cost, without adaptation regardless of where the equipment is installed.}
 
@@
 
-HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not commercial.
+\textcolor{blue}{Related to the cost (LCC) present by both tools, HOMER Pro do not use the real cost for PV systems deployed in Brazil; therefore the optimal solution presented by HOMER Pro is notoriously cheaper than our technique.
+However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, then our technique is more indicated.}
+
+\textcolor{blue}{Besides that,} HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not commercial.
 The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf.

### 2020-07-06 Tex/CAV2019/replyVSTTEJUNE2020.tex
VSTTE rebuttal

@@
 Indeed, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
-The paper was reviewed and the PV sizing modelling was changed to a more higher level of explanation.
-Different parts of the above mentioned sections in blue indicate where we changed/reviewed the text.
+The paper was reviewed and the PV sizing modelling was changed to a higher level of explanation, with a flowchart.
+The Algorithm's pseudo-code followed the same idea.
+Besides that, in case of interest about the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF file that can be accessed as well.
 
@@
 \begin{resposta} 
-We thank the reviewer again for this insightful comment and suggestion. Indeed, we had to revise every section of the paper in order to address the specific issues highlighted by the reviewer......
-Alessandro: Pra mim, é o desenvolvimento de uma técnica (como já discutimos em janeiro), que usa model checking e, como é feita em duas etapas, ela lembra o modo como o CEGIS funciona.
-E como o resultado é uma solução ótima, o resultado é uma otimização.
-Creio que isto deva ir pra introdução também (e pro abstract).
+We thank the reviewer again for this insightful comment.
+Indeed, we had to revise some specific parts of the paper where CEGIS, technique, or optimization appeared (Abstract, Introduction, and Background sections).
+Our proposal is a technique, that is based on CEGIS when we consider the use of synthesis and automated verification, and we aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization).
+We expect that the reviewed text can clarify the issue.
 
@@
 \begin{resposta} 
-Alessandro: Provavelmente eu tenha que melhorar o texto, pois a escolha de uma solução factível ou não achar uma solução factível já é por model checking ( e isso corresponde a 1a parte da técnica), a 2a parte é uma busca linear mas com teste de SUCCESS ou FAIL para gerar contraexemplo (e, pra mim, é model checking de novo).Pra mim, estamos aplicando model checking duas vezes na técnica.
-\textbf{Que achas?}  \textbf{Lucas: Concordo.
-Nao poderia aplicar uma busca binaria como fizemos no nosso journal do IJES?}
-acrescentei busca binária e $\nu Z$ na conclusão.
+We will try to clarify this issue.
+We use 4 nondeterministic variables hold the position of 4 matrices with complete datasheet information from a equipment item.
+We have 4 variables and 4 matrices: one to PV panels, one to batteries, one to inverter, and one to the charge controller.
+Those nondeterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}: this is the phase {\sc Synthesize} of the technique.
+For the {\sc Verify} phase, is performed a linear search for the lowest cost, and the search is based in FAIL or SUCCESS check from a cost that is linearly incremented in this model.
+The model checking is used during this {\sc Verify} phase: if the process FAIL then a optimal solution is found, if SUCCESSES then there is not a feasible solution from the equipment list inputted of the technique.
+We added a future work at the end of the CONCLUSIONS section, related to the possibility of speed up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
 
@@
 \begin{resposta} 
-Alessandro: Essa questão é para se pensar.
-Pra mim, a não linearidade das equações do artigo anterior de validação de sistemas solares estava mais claro pois usamos equações exponenciais e logaritmas.
-Nesse, a não linearidade se deve ao fato de a curva do ótimo global não ser contínua, pois pegamos valores específicos de variáveis não determinísticas, valores inteiros...daí eu não sei responder o que o revisor questionou.
-
-Lucas: Modelamos essas usando aritmética de ponto flutuante.
-É apenas uma aproximação dos números reais.
-No entanto, neste trabalho, não nos preocupamos em calcular o erro de arredondamento.
-Precisamos enfatizar isso no texto.
-Esse nosso paper descreve um pouco sobre esses erros: https://arxiv.org/pdf/2004.12699.pdf
+We model these PV sizing constraints using floating point arithmetic.
+It is just an approximation of the real numbers.
+However, in this work, we are not concerned with calculating the rounding error, which is negligible when we consider the size of the physical quantities and the variables adopted.
+We added this information at the end of section 2.2.
+Therefore, we thank you the question and the possibility to clarify this issue in the paper.
 
@@
 He/she is right and it was the same observation did by Reviewer \#1.
-In order to correct this issue, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
-The paper was reviewed and the PV sizing modelling was passed to a more higher level of explanation.
-Different parts of the paper in blue indicate where we changed/reviewed the text.
+We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
+The paper was reviewed and the PV sizing modelling was changed to a higher level of explanation, with a flowchart.
+The Algorithm's pseudo-code followed the same idea.
+Besides that, in case of interest about the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
 
@@
 \begin{resposta}
-Preciso pensar aqui
+Indeed the optimal sizing means the lowest cost from a feasible (technical) solution.
+When we compare just the LCC you are right: HOMER Pro produces the lowest values in mostly case-studies.
+However, we prove that using a simulation tool (PVsyst) with the optimal produced from our technique and from HOMER, that our technical solution is better to meet the house's requirements.
+We added two sentences in order to clarify this issue.
+
+In section 4.4 Results: "The cost of every equipment item used in HOMER Pro is an US-based cost, without adaptation regardless of where the equipment is installed."
+
+In section 4.5 Comparison Between Formal Synthesis and HOMER Pro: "Related to the cost (LCC) present by both tools, HOMER Pro do not use the real cost for PV systems deployed in Brazil; therefore the optimal solution presented by HOMER Pro is notoriously cheaper than our technique.
+However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, then our technique is more indicated."
 
@@
 The reviewer is right, we missed the details about why those values are taken.
-Therefore we reviewed the text to: "The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime".
+Therefore we reviewed the complementary online text to: "The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime".
 \end{resposta}
@@
 \begin{resposta}
-We have updated the entire paragraph to explain the meaning of these variables as follows: ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.
+We have updated the entire paragraph in the complementary online file to explain the meaning of these variables as follows: ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.
 (9) for the ambient short-circuit current from the PV panel.
@@
 \begin{resposta} 
-Repete o revisor 1. As mudanças que farei matam essas questões
+We thank the reviewer for this insightful comment and suggestion.
+Those are the same observations did by Reviewer \#1 and \#2.
+We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
+The paper was reviewed and the PV sizing modelling was changed to a higher level of explanation, with a flowchart.
+The Algorithm's pseudo-code followed the same idea.
+Besides that, in case of interest about the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
+
 \end{resposta}
@@
   make the paper even less accessible.
+
+\begin{resposta}
+Related to the floating point reasoning: we model the PV sizing constraints using floating point arithmetic.
+It is just an approximation of the real numbers.
+However, in this work, we are not concerned with calculating the rounding error, which is negligible when we consider the size of the physical quantities and the variables adopted.
+We added this information at the end of section 2.2.
+Therefore, we thank you the question and the possibility to clarify this issue in the paper.
+\end{resposta}
+
 - The paper contains several awkwardly formulated sentences. Examples

### 2020-07-07 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised paper and reply letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.99}
+\renewcommand{\baselinestretch}{0.97}
 
@@
 Here we develop and evaluate \textcolor{blue}{an} automated synthesis technique to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis.
-The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement costs and the operation \& maintenance costs over a 20-year period.
+The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement costs and the operation \& maintenance costs over $20$ years.
 We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the optimization}.
@@
 This evaluation can only be achieved with specialized PV optimization software.
-Therefore, the optimal solution is the lowest cost from a list of equipment that meets the electrical demands of a house.
+Therefore, the optimal solution is the lowest cost from a list of equipment that meets the house's electrical demands.
 It is based on Life Cycle Cost (LCC) analysis~\cite{Alsadi2018}, where the acquisition and replacement cost are considered over a specific period in years.}
@@
 Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}.
-\textcolor{blue}{Concerning the use of automated verification or synthesis to electrical systems, we can mention that} in $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}.
-\textcolor{blue}{In $2017$, it was suggested the application of formal methods to verify and control the behavior of devices in a smart grid (e.g.,~\cite{Abate2017})}.
+\textcolor{blue}{Concerning the use of automated verification or synthesis to electrical systems, we can mention that} in $2015$, an automated simulation-based verification technique was applied to verify the correctness of the power system protection settings~\cite{Sengupta2015}.
+\textcolor{blue}{In $2017$, Abate suggested the application of formal methods to verify and control the behavior of devices in a smart grid (e.g.,~\cite{Abate2017})}.
 In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}.
@@
 Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} technique for synthesizing optimal sizing of stand-alone PV systems.
-If we provide a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability.
+If we provide a correctness specification $ \sigma $, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $ \sigma $ related to power reliability.
 In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost.
@@
 The application of software verification to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools.
-Second, we evaluate our approach using different state-of-the-art software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems.
+Second, we evaluate our approach using different state-of-the-art software verifiers to obtain the best performance in our verification backend for synthesizing optimal PV systems.
 We compare that to HOMER Pro optimization, with the results being validated with accurate commercial design software called PVsyst.
@@
 (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
-\textcolor{blue}{The cost of every equipment item used in HOMER Pro is an US-based cost, without adaptation regardless of where the equipment is installed.}
+\textcolor{blue}{The cost of every equipment item used in HOMER Pro is a US-based cost, without adaptation regardless of where the equipment is installed.}
 
@@
 However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}.
-Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it.
+Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only) without using manufacturers' data or models for it.
 This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification).
@@
 
-\textcolor{blue}{Related to the cost (LCC) present by both tools, HOMER Pro do not use the real cost for PV systems deployed in Brazil; therefore the optimal solution presented by HOMER Pro is notoriously cheaper than our technique.
+\textcolor{blue}{Related to the cost (LCC) present by both tools, HOMER Pro does not use the real cost for PV systems deployed in Brazil; therefore, the optimal solution presented by HOMER Pro is notoriously cheaper than our technique.
 However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, then our technique is more indicated.}
@@
 Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory.
-We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
+We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which approximates the real one.
 
@@
 Our synthesis tool can present a solution that is far more detailed and closer to commercial reality than the solution given by the commercial tool.
-In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach.
-These technical details are essential for the PV system owner since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.
+In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is advantageous for our synthesis approach.
+These technical details are essential for the PV system owner.
+The industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.
 
@@
 \textcolor{blue}{Now that we proved that our technique has a promising result for PV system sizing optimization, our focus for future work will be the improvement with the search mechanism used in the {\sc Verify} phase of our synthesis technique, to speed up the time to respond.
-Our plan is to use binary search or even a solver that is specific to perform optimization with model checking as $\nu Z$~\cite{BjornerPF15}.}
+We plan to use parallel binary search~\cite{TrindadeDJISC17} or even a solver that is specific to perform optimization with model checking as $\nu Z$~\cite{BjornerPF15}.}
 

### 2020-07-07 Tex/CAV2019/replyVSTTEJUNE2020.tex
revised paper and reply letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2020-07-02 Tex/CAV2019/replyVSTTEJUNE2020.tex
@@
 We thank you for asking us to comply with your reviewers' reports.
-We are submitting a revised version of our manuscript entitled 
-``{\em \mstitle}'' by Alessandro Trindade and Lucas Cordeiro. 
-This revised version carefully addresses each comment provided 
-by the reviewers, as suggested in your original decision letter. 
-In particular, our reply letter describes all modifications we made 
-to our manuscript and the respective responses to the comments 
-raised by the reviewers.
+We are submitting a revised version of our manuscript entitled  ``{\em \mstitle}'' by Alessandro Trindade and Lucas Cordeiro.
+This revised version carefully addresses each comment provided by the reviewers, as suggested in the original notification.
+In particular, our reply letter describes all modifications we have made to our manuscript and the respective responses to the comments raised by the reviewers.
 
@@
 
-The authors would like to thank the anonymous reviewers for their valuable and constructive comments and suggestions, which helped us significantly improve the quality of our manuscript.
+The authors would like to thank the anonymous reviewers for their valuable and constructive comments and suggestions, which helped us significantly improve our manuscript quality.
 
-According to the reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text.
+According to the reviewers' comments, our manuscript was carefully revised, and all detailed changes are highlighted in blue color, along with the original text.
 The revision included the Abstract, Introduction, Background, Synthesizing Optimal Sizing, Results, and Conclusions sections.
 
-Our responses  to all comments (in blue color) are given in the sequel, with clear indications about how and where they were addressed along our manuscript.
+Our responses to all comments (in blue color) are given in the sequel, with clear indications about how and where they were addressed in our manuscript.
 
-We hope those modifications in our manuscript and also our responses are sufficient to make our work suitable for publication.
+We hope those modifications in our manuscript and our responses are sufficient to make our work suitable for publication in the \textbf{12th Working Conference on Verified Software: Theories, Tools, and Experiments}.
 
@@
 \begin{resposta} 
-We thank the reviewer for this insightful comment and suggestion.
-Indeed, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
-The paper was reviewed and the PV sizing modelling was changed to a more higher level of explanation.
-Different parts of the above mentioned sections in blue indicate where we changed/reviewed the text.
-
+We thank the reviewer for these insightful comments and suggestions.
+We had to revise the Background and the Synthesizing Optimal Sizing sections to address the right conference attendants' profile.
+Our manuscript was entirely revised, and the PV sizing modeling was changed to a higher level of explanation, with a flowchart.
+The proposed synthesis algorithm followed the same principle.
+Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF file that can be accessed.
 \end{resposta}
@@
 Indeed, we had to revise the Abstract, the Introduction, and the Synthesizing Optimal Sizing sections in order to address more correctly what is PV optimal sizing.
-We must realize as well, and we added a highlight about this in the Results section, that a optimal solution from a tool is not necessarily the same optimal of other tool, mainly when the data base of equipment items (with different costs) are not the same.
-
+We must realize as well, and we added a highlight about this in the Results section.
+An optimal solution from a tool is not necessarily the same optimal of another tool, mainly when the database of equipment items (with different costs) are not the same.
 \end{resposta}
@@
 \begin{resposta} 
-We thank the reviewer again for this insightful comment and suggestion. Indeed, we had to revise every section of the paper in order to address the specific issues highlighted by the reviewer......
-Alessandro: Pra mim, é o desenvolvimento de uma técnica (como já discutimos em janeiro), que usa model checking e, como é feita em duas etapas, ela lembra o modo como o CEGIS funciona.
-E como o resultado é uma solução ótima, o resultado é uma otimização.
-Creio que isto deva ir pra introdução também (e pro abstract).
-
+We thank the reviewer again for this insightful comment.
+We had to revise some specific parts of the paper, where the CEGIS technique, or optimization appeared (Abstract, Introduction, and Background sections).
+Our proposal is a technique based on CEGIS when considering the use of synthesis and automated verification.
+We aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization).
+We expect that the revised sections can clarify the issue.
+\textcolor{red}{Which changes did you implement?
+please specify them here}.
 \end{resposta}
@@
 \begin{resposta} 
-Alessandro: Provavelmente eu tenha que melhorar o texto, pois a escolha de uma solução factível ou não achar uma solução factível já é por model checking ( e isso corresponde a 1a parte da técnica), a 2a parte é uma busca linear mas com teste de SUCCESS ou FAIL para gerar contraexemplo (e, pra mim, é model checking de novo).Pra mim, estamos aplicando model checking duas vezes na técnica.
-\textbf{Que achas?}  \textbf{Lucas: Concordo.
-Nao poderia aplicar uma busca binaria como fizemos no nosso journal do IJES?}
-acrescentei busca binária e $\nu Z$ na conclusão.
-
+\textcolor{red}{where do we address this comment? Please indicate the section.}
+We use four nondeterministic variables to hold four matrices with complete datasheet information from an equipment item.
+We have four variables and four matrices: one to PV panels, one to batteries, one to the inverter, and one to the charge controller.
+Those nondeterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}.
+The candidate solution is proposed in the phase {\sc Synthesize} of the technique.
+For the {\sc Verify} phase, we performed a linear search for the lowest cost, and the result is based on FAIL or SUCCESS check from a cost that is linearly incremented in this model.
+The model checking is used during this {\sc Verify} phase.
+If the process produces FAIL, then an optimal solution is found.
+If SUCCESS is provided, there is no feasible solution from the equipment list provided by the technique.
+We added a future work at the end of the CONCLUSIONS section, related to the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
 \end{resposta}
@@
 \begin{resposta} 
-Alessandro: Essa questão é para se pensar.
-Pra mim, a não linearidade das equações do artigo anterior de validação de sistemas solares estava mais claro pois usamos equações exponenciais e logaritmas.
-Nesse, a não linearidade se deve ao fato de a curva do ótimo global não ser contínua, pois pegamos valores específicos de variáveis não determinísticas, valores inteiros...daí eu não sei responder o que o revisor questionou.
-
-Lucas: Modelamos essas usando aritmética de ponto flutuante.
-É apenas uma aproximação dos números reais.
-No entanto, neste trabalho, não nos preocupamos em calcular o erro de arredondamento.
-Precisamos enfatizar isso no texto.
-Esse nosso paper descreve um pouco sobre esses erros: https://arxiv.org/pdf/2004.12699.pdf
-
+We model these PV sizing constraints using floating-point arithmetic.
+It is just an approximation of the real numbers.
+However, in this work, we are not concerned with calculating the rounding error, which is negligible when considering the size of the physical quantities and the variables adopted.
+We added this information at the end of Section 2.2.
+Therefore, we thank the reviewer for the question and the possibility of clarifying this issue in our manuscript.
 \end{resposta}
@@
 \begin{resposta} 
-Thank you. We appreciate the compliment.
+We thank the reviewer for these comments.
 \end{resposta}
@@
 We thank the reviewer for this insightful comment and suggestion.
-He/she is right and it was the same observation did by Reviewer \#1.
-In order to correct this issue, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
-The paper was reviewed and the PV sizing modelling was passed to a more higher level of explanation.
-Different parts of the paper in blue indicate where we changed/reviewed the text.
-
+You are correct; Reviewer \#1 also provided the same observation.
+We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
+Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf.
+Figure 4).
+In Section 3, the synthesis algorithm followed the same idea.
+Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
 \end{resposta}
@@
 \begin{resposta}
-Preciso pensar aqui
+Indeed the optimal sizing means the lowest cost from a feasible (technical) solution.
+When we compare just the LCC, you are correct: HOMER Pro produces the lowest values in most case-studies.
+However, we prove that using a simulation tool (PVsyst) with the optimal produced from our technique and HOMER, our technical solution is better to meet the house's requirements.
+We added two sentences in order to clarify this issue.
 
+Section 4.4 Results: ``The cost of every equipment item used in HOMER Pro is a US-based cost, without adaptation regardless of where the equipment is installed.''
+
+Section 4.5 Comparison Between Formal Synthesis and HOMER Pro: ``Related to the cost (LCC) present by both tools, HOMER Pro does not use the real cost for PV systems deployed in Brazil.
+The optimal solution presented by HOMER Pro is notoriously cheaper than our technique.
+However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, our technique is more indicated.''
 \end{resposta}
@@
 \begin{resposta}
-We appreciate this Reviewer's suggestion.
-Indeed only with a double background and experience, specifically in computer science and in electrical engineering, is that is possible to realize that the tool (formal synthesis) can solve, and with remarkable results, the PV system sizing issue.
-Therefore we included a specific text in the Introduction section:
-"However, formal methods and its application to synthesize PV systems are not explored in literature, mainly because it is necessary background and experience, at the same time, in computer science and PV systems, what is not so common."
+We appreciate the reviewer's suggestion.
+Indeed only with background and experience, specifically in computer science and in electrical engineering, we can realize that the tool (formal synthesis) can solve, and with remarkable results, the PV system sizing issue.
+Therefore, we included a specific text in the Introduction section to address this particular comment:
+``However, formal methods and its application to synthesize PV systems are not explored in literature, mainly because it is necessary background and experience, at the same time, in computer science and PV systems, what is not so common.''
 \end{resposta}
@@
 \begin{resposta}
-The reviewer is right, we missed the details about why those values are taken.
-Therefore we reviewed the text to: "The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime".
+We agree with the reviewer.
+We missed the details about why those values are taken.
+Therefore, we revised the corresponding online text to: ``The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime''.
 \end{resposta}
@@
 \begin{resposta}
-We have updated the entire paragraph to explain the meaning of these variables as follows: ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.
+We have updated the entire paragraph in the complementary online file to explain the meaning of these variables.
+``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.
 (9) for the ambient short-circuit current from the PV panel.
@@
 \begin{resposta} 
-Repete o revisor 1. As mudanças que farei matam essas questões
+We thank the reviewer for these insightful comments and suggestions.
+Those are the same observations did by Reviewer \#1 and \#2.
+We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
+Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf.
+Figure 4).
+In Section 3, the synthesis algorithm followed the same idea.
+Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
 \end{resposta}
@@
   make the paper even less accessible.
+
+\begin{resposta}
+Concerning the floating-point reasoning: we model the PV sizing constraints using floating-point arithmetic.
+It is just an approximation of the real numbers.
+However, in this work, we are not concerned with calculating the rounding error, which is negligible when considering the size of the physical quantities and the variables adopted.
+We added this information at the end of Section 2.2.
+Therefore, we thank the reviewer for the question and the possibility to clarify this issue in the paper.
+\end{resposta}
+
 - The paper contains several awkwardly formulated sentences. Examples
@@
 \begin{resposta}
-Thank you.
+We thank the reviewer.
 \end{resposta}
@@
 \begin{resposta}
-We have rewritten this sentence as ``In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid [2]''.
+We have rewritten this sentence as ``In $2017$, Abate suggested the application of formal methods to verify and control the behavior of devices in a smart grid [2]''.
 \end{resposta}

### 2020-07-07 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{blue}{Related to the cost (LCC) present by both tools, HOMER Pro does not use the real cost for PV systems deployed in Brazil; therefore, the optimal solution presented by HOMER Pro is notoriously cheaper than our technique.
+\textcolor{blue}{Concerning the cost (LCC) present by both tools, HOMER Pro does not use the real cost for PV systems deployed in Brazil; therefore, the optimal solution presented by HOMER Pro is notoriously cheaper than our technique.
 However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, then our technique is more indicated.}

### 2020-07-07 Tex/CAV2019/replyVSTTEJUNE2020.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Section 4.5 Comparison Between Formal Synthesis and HOMER Pro: ``Related to the cost (LCC) present by both tools, HOMER Pro does not use the real cost for PV systems deployed in Brazil.
+Section 4.5 Comparison Between Formal Synthesis and HOMER Pro: ``Concerning the cost (LCC) present by both tools, HOMER Pro does not use the real cost for PV systems deployed in Brazil.
 The optimal solution presented by HOMER Pro is notoriously cheaper than our technique.

### 2020-07-07 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \textcolor{blue}{Concerning the cost (LCC) present by both tools, HOMER Pro does not use the real cost for PV systems deployed in Brazil; therefore, the optimal solution presented by HOMER Pro is notoriously cheaper than our technique.
-However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, then our technique is more indicated.}
+However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, our technique is more indicated.}
 

### 2020-07-07 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{blue}{In this paper, which audience is targeted to be from the software verification area, we decided to use a higher-level explanation about the PV sizing.
-The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online.\footnote{\url{https://tinyurl.com/yck7dfxt}} The flowchart pictured in Fig.~\ref{fig:flow} is the overview of the steps that must be taken to size a stand-alone PV system.}
+\textcolor{blue}{Since this paper's audience is targeted to be from the software verification area, we decided to use a higher-level explanation about the PV sizing.
+The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online.\footnote{\url{https://tinyurl.com/yck7dfxt}} Fig.~\ref{fig:flow} illustrates the overview of the steps that must be taken to size a stand-alone PV system.}
 %
@@
 
-\textcolor{blue}{On the left side of Fig.~\ref{fig:flow}, we can visualize the needed \textbf{inputs} to size a PV system.
-There exist requirements from the house to be electrified; in particular, there exist design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}.
-Related to the equipment list, the designer can use a few equipments or a vast one.
+\textcolor{blue}{On the left side of Fig.~\ref{fig:flow}, we describe the needed \textbf{inputs} to size a PV system.
+There exist requirements from the house to be electrified; in particular, we have the design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}.
+Concerning the equipment list, the designer can use a few equipments or a vast one.
 We can also decide not to adopt the commercial equipment list.
@@
 The diagram does not show the returning location.
-However, if the candidate item is not compatible with others or does not meet some requirement, it must be changed to follow the indicated flux.
+However, if the candidate item is not compatible with others or does not meet some requirement, it must be changed to follow the indicated flow.
 The last rectangle box checks the inverter electrical compatibility with the DC-bus voltage, with the required AC voltage from the outlet.
@@
 
-\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same.
+\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same \textcolor{red}{add citation}.
 Therefore, the comparison must take this issue into account.}
@@
 Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison.
-\textcolor{blue}{Now that we proved that our technique has a promising result for PV system sizing optimization, our focus for future work will be the improvement with the search mechanism used in the {\sc Verify} phase of our synthesis technique, to speed up the time to respond.
+\textcolor{blue}{We have shown that our technique has a promising result for PV system sizing optimization.
+Our focus for future work consists of improving the search mechanism used in the {\sc Verify} phase of our synthesis technique to speed up the overall time.
 We plan to use parallel binary search~\cite{TrindadeDJISC17} or even a solver that is specific to perform optimization with model checking as $\nu Z$~\cite{BjornerPF15}.}

### 2020-07-07 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Here we develop and evaluate \textcolor{blue}{an} automated synthesis technique to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis.
-The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement costs and the operation \& maintenance costs over $20$ years.
+The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement, operation, and maintenance costs over $20$ years.
 We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the optimization}.
@@
 However, the industry demands the \textcolor{blue}{design solution to be the optimum, considering equipment manufacturers and models available on the market and not just minimum or maximum values of current or power for the optimized items.
-It is necessary to evaluate the electrical compatibility among the equipment as well.
-This evaluation can only be achieved with specialized PV optimization software.
+We need to evaluate the electrical compatibility among the equipment, which can only be achieved with specialized PV optimization software.
 Therefore, the optimal solution is the lowest cost from a list of equipment that meets the house's electrical demands.
-It is based on Life Cycle Cost (LCC) analysis~\cite{Alsadi2018}, where the acquisition and replacement cost are considered over a specific period in years.}
+Our analysis is based on Life Cycle Cost (LCC)~\cite{Alsadi2018}, where the acquisition and replacement cost are considered over a specific period.}
 

### 2020-07-07 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

@@
 The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement, operation, and maintenance costs over $20$ years.
-We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the optimization}.
+We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the PV sizing optimization}.
 We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market \textcolor{blue}{for PV systems}.
@@
 
+\textcolor{blue}{Summarizing: Our proposal is a technique based on CEGIS and we aim to synthesize the optimal solution of a PV system. Therefore, our technique produces an optimization.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current rates.
-\textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}.}
+\textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}; and a LCC lifetime analysis of 20 years.}
 
@@
 The problem for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase.
+
+\textcolor{blue}{Summarizing: We use four non-deterministic variables to index four matrices with complete datasheet information from an equipment item.
+We have four variables and four matrices: one to PV panels, one to batteries, one to the inverter, and one to the charge controller.
+Those non-deterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}.
+The candidate solution is proposed in the phase {\sc Synthesize} of the technique.
+For the {\sc Verify} phase, we performed a linear search for the lowest cost, and the result is based on FAIL or SUCCESS check from a cost that is linearly incremented in this model.
+The model checking is used during this {\sc Verify} phase.
+If the process produces FAIL, then an optimal solution is found.
+If SUCCESS is presented, i.e.
+the property holds, there is no feasible solution from the equipment list provided by the technique.}
 %
@@
 
-\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same \textcolor{red}{add citation}.
+\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same \cite{Alsadi2018}.
 Therefore, the comparison must take this issue into account.}

### 2020-07-07 Tex/CAV2019/replyVSTTEJUNE2020.tex
VSTTE rebuttal

@@
 We thank the reviewer again for this insightful comment.
-We had to revise some specific parts of the paper, where the CEGIS technique, or optimization appeared (Abstract, Introduction, and Background sections).
+We had to revise some specific parts of the paper, where the CEGIS technique, or optimization appeared (Abstract, and Background sections).
 Our proposal is a technique based on CEGIS when considering the use of synthesis and automated verification.
 We aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization).
-We expect that the revised sections can clarify the issue.
-\textcolor{red}{Which changes did you implement?
-please specify them here}.
+We expect that the revised sections below can clarify the issue, besides the next answer related to Algorithm 1.
+
+Into the Abstract section now we have: "Here we develop and evaluate an automated synthesis technique to obtain optimal sizing of PV systems based on Life Cycle Cost (LCC) analysis.
+The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement, operation, and maintenance costs over $20$ years.
+We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the PV sizing optimization."
+
+In the Background section now we have: "Summarizing: Our proposal is a technique based on CEGIS and we aim to synthesize the optimal solution of a PV system.
+Therefore, our technique produces an optimization."
+
+\textcolor{red}{The two above sentences are new}.
+
 \end{resposta}
@@
 \begin{resposta} 
-\textcolor{red}{where do we address this comment? Please indicate the section.}
-We use four nondeterministic variables to hold four matrices with complete datasheet information from an equipment item.
+We use four non-deterministic variables to index four matrices with complete datasheet information from an equipment item.
 We have four variables and four matrices: one to PV panels, one to batteries, one to the inverter, and one to the charge controller.
-Those nondeterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}.
+Those non-deterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}.
 The candidate solution is proposed in the phase {\sc Synthesize} of the technique.
@@
 If the process produces FAIL, then an optimal solution is found.
-If SUCCESS is provided, there is no feasible solution from the equipment list provided by the technique.
-We added a future work at the end of the CONCLUSIONS section, related to the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
+If SUCCESS is presented, i.e.
+the property holds, there is no feasible solution from the equipment list provided by the technique.
+\textcolor{red}{This explanation was included at page 9, in the end of section "Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems".}
+We added a future work at the end of the CONCLUSIONS section as well, related to the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
 \end{resposta}

### 2020-07-08 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised paper and letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{blue}{Summarizing: Our proposal is a technique based on CEGIS and we aim to synthesize the optimal solution of a PV system. Therefore, our technique produces an optimization.}
+\textcolor{blue}{In summary, our proposal is a technique based on CEGIS, which aims to synthesize the optimal solution of a PV system; therefore, our technique addresses an optimization problem.}
 

### 2020-07-08 Tex/CAV2019/replyVSTTEJUNE2020.tex
revised paper and letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We thank the reviewer again for this insightful comment.
-We had to revise some specific parts of the paper, where the CEGIS technique, or optimization appeared (Abstract, and Background sections).
+We had to revise some specific parts of the paper, where the CEGIS technique or optimization appeared (Abstract and Background sections).
 Our proposal is a technique based on CEGIS when considering the use of synthesis and automated verification.
 We aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization).
-We expect that the revised sections below can clarify the issue, besides the next answer related to Algorithm 1.
+We expect that the revised sections below clarify the issue, besides the next answer related to Algorithm 1.
 
-Into the Abstract section now we have: "Here we develop and evaluate an automated synthesis technique to obtain optimal sizing of PV systems based on Life Cycle Cost (LCC) analysis.
+In the Abstract section, we now have: ``Here we develop and evaluate an automated synthesis technique to obtain optimal sizing of PV systems based on Life Cycle Cost (LCC) analysis.
 The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement, operation, and maintenance costs over $20$ years.
-We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the PV sizing optimization."
+We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the PV sizing optimization.''
 
-In the Background section now we have: "Summarizing: Our proposal is a technique based on CEGIS and we aim to synthesize the optimal solution of a PV system.
-Therefore, our technique produces an optimization."
-
-\textcolor{red}{The two above sentences are new}.
-
+In the Background section, we now have: ``In summary, our proposal is a technique based on CEGIS, which aims to synthesize the optimal solution of a PV system; therefore, our technique addresses an optimization problem.''
 \end{resposta}

### 2020-07-08 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised paper and letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 There exist requirements from the house to be electrified; in particular, we have the design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}.
-Concerning the equipment list, the designer can use a few equipments or a vast one.
+Concerning the equipment list, the designer can use a few pieces of equipment or a vast one.
 We can also decide not to adopt the commercial equipment list.
@@
 \noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current rates.
-\textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}; and a LCC lifetime analysis of 20 years.}
+\textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}; and an LCC lifetime analysis of 20 years.}
 
@@
 Each simulation with PVsyst took $4$ seconds.
-We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum).
+We were unable to validate the case study $3$ using PVsyst.
+The battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum).
 Case studies $2$ and $7$ had only HOMER Pro sizing validation.
@@
 
-\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same \cite{Alsadi2018}.
+\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) is not the same \cite{Alsadi2018}.
 Therefore, the comparison must take this issue into account.}
@@
 Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory.
-We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which approximates the real one.
+We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, approximating the real one.
 
@@
 \bibliography{trindadeThesis}
+
 %

### 2020-07-08 Tex/CAV2019/replyVSTTEJUNE2020.tex
revised paper and letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-%\vi
-
-%Thank you very much in advance.
-
 \vi\vi
@@
 
-Algorithm 1 to me seems to construct a constraint and then tries to solve it for the nondeterministic variables to obtain a solution, and to use essentially a linear search to find the minimum cost.
+Algorithm 1 to me seems to construct a constraint and then tries to solve it for the non-deterministic variables to obtain a solution, and to use essentially a linear search to find the minimum cost.
 Is this correct?
@@
 If the process produces FAIL, then an optimal solution is found.
-If SUCCESS is presented, i.e.
-the property holds, there is no feasible solution from the equipment list provided by the technique.
-\textcolor{red}{This explanation was included at page 9, in the end of section "Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems".}
-We added a future work at the end of the CONCLUSIONS section as well, related to the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
+If SUCCESS is presented, i.e., the property holds, there is no feasible solution from the equipment list provided by the technique.
+This explanation was included at the end of the section ``Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems".
+We added a future work at the end of the Conclusions section concerning the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
 \end{resposta}
@@
 You are correct; Reviewer \#1 also provided the same observation.
-We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
+We had to revise the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile.
 Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf.
@@
 In Section 3, the synthesis algorithm followed the same idea.
-Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
+Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed.
 \end{resposta}
@@
 \begin{resposta}
-We have updated the entire paragraph in the complementary online file to explain the meaning of these variables.
+We have updated the entire paragraph in the complimentary online file to explain the meaning of these variables.
 ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.
@@
 The paper describes a system for optimally sizing PV systems.
-A detailed account is given of both modeling parameters, evaluation method
-and evaluation results. The details, covered in the paper, contain
+A detailed account is given of both modeling parameters, evaluation method and evaluation results. The details, covered in the paper, contain
 a substantial amount of information on PV optimization and approaches
@@
 Those are the same observations did by Reviewer \#1 and \#2.
-We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile.
+We had to revise the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile.
 Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf.
@@
 
-% \printbibliography
 \end{document}

### 2020-07-08 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
fit the paper into 16 pages
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The authors have real PV systems deployed since June $2018$ in a riverside community in the State of Amazonas, Brazil, GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
+We have real PV systems deployed since June $2018$ in a riverside community in the State of Amazonas, Brazil, GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.
 
@@
 
-\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) is not the same \cite{Alsadi2018}.
+\textcolor{blue}{An optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) is not the same \cite{Alsadi2018}.
 Therefore, the comparison must take this issue into account.}
@@
 Our synthesis tool can present a solution that is far more detailed and closer to commercial reality than the solution given by the commercial tool.
-In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is advantageous for our synthesis approach.
-These technical details are essential for the PV system owner.
+The battery autonomy feature, together with the details of every component of a PV system solution, is advantageous for our synthesis approach; these details are essential for the PV system owner.
 The industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.

### 2020-07-08 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

@@
 \noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current rates.
-\textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}; and an LCC lifetime analysis of 20 years.}
+\textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}; and a LCC lifetime analysis of 20 years.}
 

### 2020-07-08 Tex/CAV2019/replyVSTTEJUNE2020.tex
VSTTE rebuttal

@@
 \usepackage{epstopdf}
-\usepackage{url}
+%\usepackage{url}
+\usepackage{hyperref}
 %\usepackage{mathtools}
@@
 
-According to the reviewers' comments, our manuscript was carefully revised, and all detailed changes are highlighted in blue color, along with the original text.
+According to the reviewers' comments, our manuscript was carefully revised%, and all detailed changes are highlighted in blue color, along with the original text
+.
 The revision included the Abstract, Introduction, Background, Synthesizing Optimal Sizing, Results, and Conclusions sections.
+A highlighted version of the entire paper is available in \url{https://tinyurl.com/y9scqv6g} if the reviewers would like access.
 
@@
 We thank the reviewer for these insightful comments and suggestions.
-We had to revise the Background and the Synthesizing Optimal Sizing sections to address the right conference attendants' profile.
-Our manuscript was entirely revised, and the PV sizing modeling was changed to a higher level of explanation, with a flowchart.
-The proposed synthesis algorithm followed the same principle.
-Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF file that can be accessed.
+We had to revise parts of the Background and the Synthesizing Optimal Sizing sections to address the right conference attendants' profile.
+The PV sizing modeling was changed to a higher level of explanation, with a flowchart in page 6 (Fig.4).
+The proposed synthesis algorithm followed the same principle in page 8.
+Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, that we removed from the paper, we created a link to a 5-page PDF online file that can be accessed.
 \end{resposta}
@@
 We thank the reviewer again.
-Indeed, we had to revise the Abstract, the Introduction, and the Synthesizing Optimal Sizing sections in order to address more correctly what is PV optimal sizing.
-We must realize as well, and we added a highlight about this in the Results section.
-An optimal solution from a tool is not necessarily the same optimal of another tool, mainly when the database of equipment items (with different costs) are not the same.
+Indeed, we had to revise parts of the Abstract, the Introduction, and the Synthesizing Optimal Sizing sections in order to address more correctly what is PV optimal sizing.
+We must realize as well, and we added a highlight about this in the Results section: "An optimal solution from a tool is not necessarily the same optimal of another tool, mainly when the database of equipment items (with different costs) are not the same."
 \end{resposta}
@@
 You are correct; Reviewer \#1 also provided the same observation.
-We had to revise the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile.
+We had to revise parts of the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile.
 Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf.
-Figure 4).
-In Section 3, the synthesis algorithm followed the same idea.
-Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed.
+Figure 4 at page 6).
+In Section 3 (page 8), the synthesis algorithm followed the same idea.
+Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, that was removed from this revised paper, we created a link to a 5-page PDF complementary file that can be accessed.
 \end{resposta}
@@
 We missed the details about why those values are taken.
+Considering that the new paper version has a higher level explanation for the PV sizing, we removed this part and transferred it to the complementary PDF text.
 Therefore, we revised the corresponding online text to: ``The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime''.
@@
 Those are the same observations did by Reviewer \#1 and \#2.
-We had to revise the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile.
+We had to revise parts of the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile.
 Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf.
-Figure 4).
-In Section 3, the synthesis algorithm followed the same idea.
-Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
+Figure 4 at page 6).
+In Section 3, the synthesis algorithm followed the same idea (page 8).
+Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, that was removed from this revised version of the paper, we created a link to a 5-page PDF complementary file that can be accessed as well.
 \end{resposta}
